### 2019-05-02 paper/sample-sigconf.tex
empty templates for paper & thesis

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-9999-9/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title is Hope}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  %\includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\verb|\documentclass[sigconf]{acmart}|.

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for all short- and
full-length articles, and optional for two-page abstracts.

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  %\includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{The 1907 Franklin Model D roadster.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
{\bfseries also} include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed {\itshape below} the figure.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, an article in a proceedings (of a conference,
  symposium, workshop for example) (paginated proceedings article)
  \cite{Andler79}, a proceedings article with all possible elements
  \cite{Smith10}, an example of an enumerated proceedings article
  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
  doctoral dissertation \cite{Clarkson85}, a master's thesis:
  \cite{anisi03}, an online document / world wide web resource
  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
  (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2019-05-02 thesis/img/plot.tex
empty templates for paper & thesis

\providecommand{\myrootdir}{..}
\documentclass[tikz]{standalone}
\onlyifstandalone{
\usepackage{pgfplots}
% This small hack is required to set the search path correctly
% Just provide the current directory this file is in relatively to the root dir
\pgfplotsset{table/search path={./img/}}
}
\begin{document}
\begin{tikzpicture}
 \begin{axis}[
   xlabel={input $i$},
   ylabel={result},
   grid=major,
   legend pos=north west,
  ]
  \addlegendentry{$i+2$}
  \addplot[blue,mark=x,thick] table[y index=1] {\myrootdir/data/plot-mult.dat};
  \addlegendentry{$2 \cdot i$}
  \addplot[red,mark=x,thick] table[y index=2] {\myrootdir/data/plot-mult.dat};
  \addlegendentry{$-1^{i}$}
  \addplot[green,mark=x,thick] table[y index=3] {\myrootdir/data/plot-mult.dat};
\end{axis}
\end{tikzpicture}
\end{document}

### 2019-05-02 thesis/mini/abstract.tex
empty templates for paper & thesis

\providecommand{\myrootdir}{..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}

\chapter*{\myAbstractTitle}

It is just a small template, that is hopefully helpful for writing your thesis.
First, it gives a short introduction to its usage and the personalizations.
Finally, it presents several examples of frequently used pieces of layout.

\end{document}

### 2019-05-02 thesis/mini/acknowledgments.tex
empty templates for paper & thesis

\providecommand{\myrootdir}{..}
\documentclass[\myrootdir/main.tex]{subfiles}

% Just delete this file, if you don't want to acknowledge anything.
% The corresponding page disappears automatically from all output documents

\begin{document}
\thispagestyle{empty}

\vspace*{2cm}

\begin{center}
{\usekomafont{section} \myAcknowTitle}
\end{center}

\vspace{1cm}
\noindent
If you want, you can use this section to thank your supervisors, your universities or just anybody else who has helped you writing your thesis.
But for this template, I want to abuse this section for a little request.
I cannot and do not want to track who is using this template, but I am curious how many students have actually used it.
So in case you wish to give something back to the author of this template, please consider writing an email to \href{mailto:danke@hutzelmann.net}{\nolinkurl{danke@hutzelmann.net}}.
A simple \enquote{Thanks} is already enough, but if you want to provide more details, please add the name of your study program, the name of your thesis and tell me, what you liked and disliked the most about this template.
\todo{Write this email \smiley{}}
Thank you very much for your help!

\end{document}

### 2019-05-02 thesis/zyx/TUMinfo/1-cover.tex
empty templates for paper & thesis

\providecommand{\myrootdir}{../..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}

\begin{titlepage}
\centering

\includegraphics[height=2.5cm]{\logotum}

\vspace{1cm}

{\LARGE \textsc{\ifthenelse{\equal{\mylanguage}{de}}{Fakultät für Informatik}{Department of Informatics}}}\\[0.8em]
{\Large \textsc{\ifthenelse{\equal{\mylanguage}{de}}{Technische Universität München}{Technical University of Munich}}}

\vspace{5em}
{\Large \myThesisType}
\vspace{5em}

\begin{spacing}{1.1}
\Huge \bfseries \myTitle
\end{spacing}

\vspace{1.5em}

{\Large \myAuthor}

\vfill

\includegraphics[height=2.5cm]{\logoinf}

\cleardoublepage
\end{titlepage}
\end{document}

### 2019-05-02 thesis/zyx/TUMinfo/3-statement.tex
empty templates for paper & thesis

\providecommand{\myrootdir}{../..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}
\thispagestyle{empty}
\phantom{.}
\vfill

{\setlength{\parindent}{0cm}%

\ifthenelse{\equal{\mylanguage}{de}}{%
\begin{otherlanguage}{ngerman}
Ich versichere, dass ich diese {\myThesisType} selbstständig verfasst und nur die angegebenen Quellen und Hilfsmittel verwendet habe.

\vspace{7em}
Garching, den \myHandIn \hfill \myAuthor
\end{otherlanguage}
}{%
I confirm that this \MakeLowercase{\myThesisType} is my own work and I have documented all sources and material used.
\vspace{7em}

Garching, \myHandIn \hfill \myAuthor
}
}

\vspace{3em}

\end{document}

### 2019-05-02 thesis/code/hello.c

@@ -1,0 +1,5 @@
+#include <stdio.h>
+
+int main(int argc, char** argv) {
+  puts("Hello World!");
+}

### 2019-05-03 paper/sample-sigconf.tex
clean out paper template

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{The Name of the Title is Hope}
+\title{Analyzing Buildlogs Using Programming by Example}
 
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-\author{Ben Trovato}
-\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
-\authornotemark[1]
-\email{webmaster@marysville-ohio.com}
-\affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \postcode{43017-6221}
-}
-
-\author{Lars Th{\o}rv{\"a}ld}
-\affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
-
-\author{Valerie B\'eranger}
-\affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
-}
-
-\author{Aparna Patel}
-\affiliation{%
- \institution{Rajiv Gandhi University}
- \streetaddress{Rono-Hills}
- \city{Doimukh}
- \state{Arunachal Pradesh}
- \country{India}}
-
-\author{Huifen Chan}
-\affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
-
-\author{Charles Palmer}
-\affiliation{%
-  \institution{Palmer Research Laboratories}
-  \streetaddress{8600 Datapoint Drive}
-  \city{San Antonio}
-  \state{Texas}
-  \postcode{78229}}
-\email{cpalmer@prl.com}
-
-\author{John Smith}
-\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
-\email{jsmith@affiliation.org}
-
-\author{Julius P. Kumquat}
-\affiliation{\institution{The Kumquat Consortium}}
-\email{jpkumquat@consortium.net}
+\author{Carolin Brandt}
 
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+\renewcommand{\shortauthors}{Brandt, et al.}
 
@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+  ...
 \end{abstract}
@@
 %%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+%\begin{CCSXML}
+%<ccs2012>
+% <concept>
+%  <concept_id>10010520.10010553.10010562</concept_id>
+%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+%  <concept_significance>500</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010575.10010755</concept_id>
+%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+%  <concept_significance>300</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010553.10010554</concept_id>
+%  <concept_desc>Computer systems organization~Robotics</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10003033.10003083.10003095</concept_id>
+%  <concept_desc>Networks~Network reliability</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+%</ccs2012>
+%\end{CCSXML}
+%
+%\ccsdesc[500]{Computer systems organization~Embedded systems}
+%\ccsdesc[300]{Computer systems organization~Redundancy}
+%\ccsdesc{Computer systems organization~Robotics}
+%\ccsdesc[100]{Networks~Network reliability}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
-
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-\begin{teaserfigure}
-  %\includegraphics[width=\textwidth]{sampleteaser}
-  \caption{Seattle Mariners at Spring Training, 2010.}
-  \Description{Enjoying the baseball game from the third-base
-  seats. Ichiro Suzuki preparing to bat.}
-  \label{fig:teaser}
-\end{teaserfigure}
+\keywords{ci, buildlogs, programming by example}
 
@@
 \maketitle
-
-\section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
-
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
-
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
-
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
-
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the
-source file:
-\verb|\documentclass[sigconf]{acmart}|.
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for all short- and
-full-length articles, and optional for two-page abstracts.
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  %\includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{The 1907 Franklin Model D roadster.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-{\bfseries also} include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed {\itshape below} the figure.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, an article in a proceedings (of a conference,
-  symposium, workshop for example) (paginated proceedings article)
-  \cite{Andler79}, a proceedings article with all possible elements
-  \cite{Smith10}, an example of an enumerated proceedings article
-  \cite{VanGundy07}, an informally published work \cite{Harel78}, a
-  doctoral dissertation \cite{Clarkson85}, a master's thesis:
-  \cite{anisi03}, an online document / world wide web resource
-  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
-  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-  (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
 \end{document}

### 2019-05-03 paper/paper.tex
outline, introduction notes

--- 2019-05-03 paper/sample-sigconf.tex
@@
 
+\section{Introduction}
+ci important for sw projects, broken build stops dev process until its fixed, shortening fixing time important to increase dev productivity, to detect underlying failure huge buildlog has to be read, finding relevant information between a lot of lines unimportant for that task, extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity, few existing approaches on specifically that domain, ...
+our approach ...
+
+\section{Related Work}
+\paragraph{CI Research}
+google paper, ing \& os java paper, travistorrent
+\paragraph{Analyzing Buildlogs}
+maven/java paper
+\paragraph{Information Extraction}
+prose flashextract
+
+TODO put in proper references to the papers youre surely gonna need here
+
+\section{Background}
+program synthesis from example, neccessary theoretical stuff
+
+here all the references to prose theoretical papers
+
+\section{Data collection}
+describe process of collecting buildlog files, sampling
+
+\section{Meta-Model}
+describe metamodel of data obtainable from buildlogs
+
+\section{Our Tool}
+
+\section{Evaluation}
+
+\section{Conclusion and Future Work}
+
 %%

### 2019-05-06 paper/paper.tex
add references to outline

@@
 \paragraph{CI Research}
-google paper, ing \& os java paper, travistorrent
+google paper \cite{seo2014programmers}, ing \& os java paper \cite{vassallo2017a-tale}, travistorrent \cite{beller2017oops}
 \paragraph{Analyzing Buildlogs}
-maven/java paper
+maven/java paper \cite{vassallo2018un-break}
 \paragraph{Information Extraction}
-prose flashextract
-
-TODO put in proper references to the papers youre surely gonna need here
+prose flashextract \cite{le2014flashextract:}, more papers with other approaches of extraction? especially: other extraction from similar data formats
 
 \section{Background}
-program synthesis from example, neccessary theoretical stuff
-
-here all the references to prose theoretical papers
+program synthesis from example, neccessary theoretical stuff,
+here all the references to prose theoretical papers \cite{le2014flashextract:}, \cite{polozov2015flashmeta:}, \cite{mitchell1982generalization},
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
+\bibliography{paper}
 

### 2019-05-24 paper/paper.tex
update literature with IR stuff, bullet points for related work in paper, update worklog 24.5.

--- 2019-05-03 paper/sample-sigconf.tex
@@
 \documentclass[sigconf]{acmart}
+
+% TODO remove XD
+\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
+\usepackage[color=ballblue]{todonotes}
 
@@
 
+\section{Introduction}
+
+ci important for sw projects,
+
+broken build stops dev process until its fixed,
+
+shortening fixing time important to increase dev productivity,
+
+to detect underlying failure huge buildlog has to be read, finding relevant information between a lot of lines unimportant for that task,
+
+extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity,
+
+traditional: regexes built for exact information extraction
+
+hard to maintain, regex understanding effort, don't generalize / have to be redone when a bulidlog changes / language or build tool is switched,
+
+... our approach ...,
+
+... paper structure ...
+
+\section{Related Work}
+\paragraph{CI Research}
+- se research community is starting to look into builodlogs
+
+- paper at google: ...et al., large study at google, quantitative analysis of which errors appear during builds at google, java and c++ projects, build parser for error messages in logs, results: very few types of errors make up most of the failures, most dependency issues or type missmatchs, (experienced developers have similar failure rates to all other devs?), most errors fixed in 2 build iterations, emphasize that more specific failure messages \& fix proposals would be valuable,
+...
+compared to us: we could support this research by enabling easier data extraction form the analyzed logs, tool could also be used by google for more concise information extracted form the logs and given to the user directly → faster failure resolvement \cite{seo2014programmers},
+
+- ing vs.
+oss (java): Vasssalo et al., comparing builds from java oss projects and ING Nederland, borad taxonomy and anlaysis of failures during the ci process, oss mainly falis due to unit testing, Ing / industrial ...
+/ bank / mainly duriing release preparation phase  → oss and industrial veeery different
+
+... compared to our approach: flexible enough for different kind of logs e.g. oss and ing → again, helping research \cite{vassallo2017a-tale},
+
+- Beller et al., largescale analyzis of over 2 Mio buildlogs of oss in java and ruby obtained from travis ci, tests are central part of ci and main reason for builds to fail, ci adoption \& influence of failed tests orthogonal to chosen programming language, build time main factor in feedback delay (useful to mention in our paper?
+we minimize more at another stage: understanding)
+
+... compared to our approach: development custom log analysis for build failures specific for java and ruby. With pbe we could replace / simplyfy the manual regex construction\ \cite{beller2017oops}
+
+\todo[inline]{might be far too long... compress \& talk about differentiation to our work once}
+
+\paragraph{Analyzing Buildlogs}
+Vassallo et al., goal: support developer in finding reasons for a build break fast, developed tool: analyze buildlogs, summarize, link realated stack overflow discussions (thesis: created metamodel of bulildlog structure for maven, contains references to original output of build stages, built specific parser for these logs + the metamodel, tool BART (build abstraction and recovery tool) works with hint generators that operate on the metamodel instantiation to not have every hint generator parse the whole log again), in their evaluation found that "dependency breaks and testing failures seem to be easy to understand" and that a good summary highlighting the locality of the issues seems to be an important factor of fixing time.
+\cite{vassallo2018un-break}
+
+...
+compared to our work: they focused on java/maven, we want to explore supporting a wide variety of buildlogs.
+our metamodel inspired by them, our pbe tool should replace their not closer described "parser" to fill a metamodel instantiation
+
+\paragraph{Information Extraction from semi-structured data using program synthesis}
+- Le et al.
+developed FlashExtract, a framework to extract revelanvt data from semi-structured documents using examples, users can extract multiple fields and structure them with hierachy and sequence, uses inductive synthesis algorithm to synthesize intended program, domain-independent approach, eliminates the need for the user to understand structure of entire document or to be able to code (yes, developers can code, but still effort \& maintenance of old code difficult)
+
+...
+compared to our approach: we use exactly their framework for our information extraction, apply it to the domain of buildlogs, MAYBE: adopt internals (ranking, if explained before here) to the specifics of the use case buildlog
+
+\todo[inlince]{stuff below maybe in theoretical background better}
+technical: extract by generating various programs for slicing substrings, either absolute positions or regexes for slicing boundaries, regexes with lookahead/lookbehind, various programs which comply with examples are generated, ranked by how likely they are intended, make example: regex more likely than absolute positions for slicing boundaries
+
+- include \cite{smith1997information}? other specific approaches of information extraction from semi-structured data? alternatively: rename to program synthesis
+
+for that paper: extract information from semi-structured text documents, exemplary french govermental documents \todo{check that that is correct}, divide into "contexts" by headers / subsections, extract desired "concepts" from specified contexts via possible start regex and keywords, end by next concept starting or end regex, \todo{do they have an evaluation?}
+
+\paragraph{Information retrieval}
+realted topic: Getting Information out of (semi-structured) data. A lot of focus on NLP and text summarization or similarity measurement.
+
+Differentiation: we do not compare different documents -> no use for similarity computations, programmers expect precise information: (TODO why?) rough summarization of buildlogs often uninteresting: a lot of repeated parts that are in all bulidlogs.
+For developer mostly one specific information (why did it fail?) and maybe supporting data (stacktraces, error messages) relevant.
+If we want to incorporate our results into another tool (travis button with failed test, predictive CI) they need to be \textbf{exact}.
+We are not trying to generally summarize bulidlogs here, we are trying to replace regular expression manual creation by pbe.
+
+\section{Background}
+
+\paragraph{semi-structured data}
+characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here!
+-> impact on our work with buildlogs) \cite{abiteboul1997querying}
+
+maybe: reference \cite{smith1997information} and explain approach of first structuring into sections / "contexts" before extracting acutal information.
+but only if we actually do that and not just always parse the whole log.
+
+program synthesis from example, neccessary theoretical stuff,
+here all the references to prose theoretical papers \cite{le2014flashextract:}, \cite{polozov2015flashmeta:}, \cite{mitchell1982generalization},
+
+\section{Data collection}
+describe process of collecting buildlog files, sampling
+
+\section{Meta-Model}
+describe metamodel of data obtainable from buildlogs
+
+\section{Our Tool}
+
+\section{Evaluation}
+
+\section{Conclusion and Future Work}
+
 %%

### 2019-05-28 paper/paper.tex
move rw points to thesis, write short ones for paper

--- 2019-05-03 paper/paper.tex
@@
 \section{Introduction}
-ci important for sw projects, broken build stops dev process until its fixed, shortening fixing time important to increase dev productivity, to detect underlying failure huge buildlog has to be read, finding relevant information between a lot of lines unimportant for that task, extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity, few existing approaches on specifically that domain, ...
-our approach ...
+
+ci important for sw projects,
+
+broken build stops dev process until its fixed,
+
+shortening fixing time important to increase dev productivity,
+
+to detect underlying failure huge buildlog has to be read, dev has to find relevant information between a lot of lines unimportant for the task,
+
+extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity,
+
+traditional: regexes built for exact information extraction
+
+hard to maintain, regex understanding effort, don't generalize / have to be redone when a bulidlog changes / language or build tool is switched,
+
+... our approach ...,
+
+... paper structure ...
 
 \section{Related Work}
-\paragraph{CI Research}
-google paper, ing \& os java paper, travistorrent
-\paragraph{Analyzing Buildlogs}
-maven/java paper
-\paragraph{Information Extraction}
-prose flashextract
 
-TODO put in proper references to the papers youre surely gonna need here
+\paragraph{Continious integration and analysis of buildlogs}
+se research community started to look into buildlogs as CI becomes a vital part of a modern se process
+
+e.g. Seo at al studying the kinds of errors which lead builds to fail at google and their resolvement time \cite{seo2014programmers}
+
+Vasallo et al compared build failure reasons in java open source software and at one industrial company \cite{vassallo2017a-tale}
+
+Beller et al.
+conducted a large scale empirical analysis of java and ruby buildlogs from travis ci, found that tests are central to CI and main reason for builds to fail \todo{should I mention a key outcome like this or only what they did?}
+
+Vasallo et al.
+also build a tool to support developers to find reasons for build breaks fast, analyzes and summarizes relevant parts of a buildlog, links to related stack overflow discussions, they found that \begin{quotation}
+	dependency breaks and testing failures seem to be easy to understand
+\end{quotation} and a good summary highlighting the locality of the issues seems to be an important factor of fixing time \cite{vassallo2018un-break}
+
+relation to our work: we could support this research by enabling easier data extraction from the analyzed buildlogs, most focus on single/few languages with our tool they could more easily cover multiple ones
+
+\paragraph{Information Extraction from semi-structured data using program synthesis}
+Le et al.
+developed FlashExtract as part of the PROSE Framework, tool to synthesize programs based on a few given examples, extract substrings from semi-structured texts, users can extract multiple fields and structure them with hierarchy and sequence, uses inductive synthesis algorithm to synthesize intended program, eliminates the need for the user to understand structure of entire document or to be able to code
+
+we are applying their library to the domain of buildlogs, using programming by example to take away the need to tediously develop and maintain the regular expressions, traditionally used in information extraction
 
 \section{Background}
-program synthesis from example, neccessary theoretical stuff
 
-here all the references to prose theoretical papers
+\paragraph{semi-structured data}
+characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here!
+-> impact on our work with buildlogs) \cite{abiteboul1997querying}
+
+maybe: reference \cite{smith1997information} and explain approach of first structuring into sections / "contexts" before extracting acutal information.
+but only if we actually do that and not just always parse the whole log.
+
+program synthesis from example, neccessary theoretical stuff,
+here all the references to prose theoretical papers \cite{le2014flashextract:}, \cite{polozov2015flashmeta:}, \cite{mitchell1982generalization},
 

### 2019-05-28 thesis/txt/related-work.tex
move rw points to thesis, write short ones for paper

\providecommand{\myrootdir}{..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}

\chapter{Related Work}
\paragraph{CI Research}
- se research community is starting to look into builodlogs

- paper at google: ...et al., large study at google, quantitative analysis of which errors appear during builds at google, java and c++ projects, build parser for error messages in logs, results: very few types of errors make up most of the failures, most dependency issues or type missmatchs, (experienced developers have similar failure rates to all other devs?), most errors fixed in 2 build iterations, emphasize that more specific failure messages \& fix proposals would be valuable,
... compared to us: we could support this research by enabling easier data extraction form the analyzed logs, tool could also be used by google for more concise information extracted form the logs and given to the user directly -> faster failure resolvement \cite{seo2014programmers},

- ing vs. oss (java): Vasssalo et al., comparing builds from java oss projects and ING Nederland, borad taxonomy and anlaysis of failures during the ci process, oss mainly falis due to unit testing, Ing / industrial ... / bank / mainly duriing release preparation phase -> oss and industrial veeery different

... compared to our approach: flexible enough for different kind of logs e.g. oss and ing -> again, helping research \cite{vassallo2017a-tale},

- Beller et al., largescale analyzis of over 2 Mio buildlogs of oss in java and ruby obtained from travis ci, tests are central part of ci and main reason for builds to fail, ci adoption \& influence of failed tests orthogonal to chosen programming language, build time main factor in feedback delay (useful to mention in our paper? we minimize more at another stage: understanding)

... compared to our approach: development custom log analysis for build failures specific for java and ruby. With pbe we could replace / simplyfy the manual regex construction\ \cite{beller2017oops}

\todo[inline]{might be far too long... compress \& talk about differentiation to our work once}

\paragraph{Analyzing Buildlogs}
Vassallo et al., goal: support developer in finding reasons for a build break fast, developed tool: analyze buildlogs, summarize, link realated stack overflow discussions (thesis: created metamodel of bulildlog structure for maven, contains references to original output of build stages, built specific parser for these logs + the metamodel, tool BART (build abstraction and recovery tool) works with hint generators that operate on the metamodel instantiation to not have every hint generator parse the whole log again), in their evaluation found that "dependency breaks and testing failures seem to be easy to understand" and that a good summary highlighting the locality of the issues seems to be an important factor of fixing time. \cite{vassallo2018un-break}

... compared to our work: they focused on java/maven, we want to explore supporting a wide variety of buildlogs. our metamodel inspired by them, our pbe tool should replace their not closer described "parser" to fill a metamodel instantiation

\paragraph{Information Extraction from semi-structured data using program synthesis}
- Le et al. developed FlashExtract, a framework to extract revelanvt data from semi-structured documents using examples, users can extract multiple fields and structure them with hierachy and sequence, uses inductive synthesis algorithm to synthesize intended program, domain-independent approach, eliminates the need for the user to understand structure of entire document or to be able to code (yes, developers can code, but still effort \& maintenance of old code difficult)

... compared to our approach: we use exactly their framework for our information extraction, apply it to the domain of buildlogs, MAYBE: adopt internals (ranking, if explained before here) to the specifics of the use case buildlog

\todo[inlince]{stuff below maybe in theoretical background better}
technical: extract by generating various programs for slicing substrings, either absolute positions or regexes for slicing boundaries, regexes with lookahead/lookbehind, various programs which comply with examples are generated, ranked by how likely they are intended, make example: regex more likely than absolute positions for slicing boundaries

- include \cite{smith1997information}? other specific approaches of information extraction from semi-structured data? alternatively: rename to program synthesis

for that paper: extract information from semi-structured text documents, exemplary french govermental documents \todo{check that that is correct}, divide into "contexts" by headers / subsections, extract desired "concepts" from specified contexts via possible start regex and keywords, end by next concept starting or end regex, \todo{do they have an evaluation?}

\paragraph{Information retrieval}
realted topic: Getting Information out of (semi-structured) data. A lot of focus on NLP and text summarization or similarity measurement.

Differentiation: we do not compare different documents -> no use for similarity computations, programmers expect precise information: (TODO why?) rough summarization of buildlogs often uninteresting: a lot of repeated parts that are in all bulidlogs. For developer mostly one specific information (why did it fail?) and maybe supporting data (stacktraces, error messages) relevant. If we want to incorporate our results into another tool (travis button with failed test, predictive CI) they need to be \textbf{exact}. We are not trying to generally summarize bulidlogs here, we are trying to replace regular expression manual creation by pbe.

\end{document}

### 2019-05-28 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisProgram.cs
generified analysis to enable sequence extracting programs

@@ -2,28 +2,30 @@
 using System.Collections.Generic;
 using System.IO;
 using System.Xml.Serialization;
-using static pbeextractionbuildlogs.AnalysisSession;
 
 namespace pbeextractionbuildlogs
 {
-	/// <summary>
-	/// Represents one learnt/learnable Program
-	/// </summary>
-	public class AnalysisProgram
+	public class NamedProgram
 	{
 		/// <summary>
 		/// Filename to save the corresponding data under.
 		/// </summary>
-		public string SaveName { get; }
+		public string SaveName { get; protected set; }
+	}
 
+	/// <summary>
+	/// Represents one learnt/learnable Program
+	/// </summary>
+	public class AnalysisProgram<SessionType, OutputType> : NamedProgram where SessionType : AnalysisSession<OutputType>, new()
+	{
 		string saveFilePath => Config.PROGRAM_DATA_DIRECTORY + SaveName + ".xml";
 
-		AnalysisSession analysisSession;
+		SessionType analysisSession;
 
 		/// <summary>
 		/// Data needed for the learning lesson.
 		/// </summary>
-		public SessionData LearningData { get; private set; }
+		public SessionData<ExampleData<OutputType>> LearningData { get; private set; }
 
 		/// <summary>
 		/// LogKind this programm analyzes
@@ -36,11 +38,11 @@ namespace pbeextractionbuildlogs
 		public MetaModelObject Target { get; }
 		// MAYBE: private AnalysisSession analysisSession;
 
-		public AnalysisProgram(string saveName, LogKind logKind, MetaModelObject target, SessionData learningData = null, bool takeFromFileIfPossible = false)
+		public AnalysisProgram(string saveName, LogKind logKind, MetaModelObject target, SessionData<ExampleData<OutputType>> learningData = null, bool takeFromFileIfPossible = false)
 		{
 			if (learningData == null)
 			{
-				learningData = new SessionData();
+				learningData = new SessionData<ExampleData<OutputType>>();
 			}
 
 			if (takeFromFileIfPossible && File.Exists(Config.PROGRAM_DATA_DIRECTORY + SaveName + ".xml"))
@@ -57,33 +59,31 @@ namespace pbeextractionbuildlogs
 			Target = target;
 		}
 
-		public AnalysisProgram AddOnlyInput(string inputPath)
+		public AnalysisProgram<SessionType, OutputType> AddOnlyInput(string inputPath)
 		{
[…]

### 2019-05-28 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs

@@ -8,45 +8,75 @@ using System.Xml.Serialization;
 using Microsoft.ProgramSynthesis.DslLibrary;
 using Microsoft.ProgramSynthesis.Extraction.Text;
 using Microsoft.ProgramSynthesis.Extraction.Text.Constraints;
+using Microsoft.ProgramSynthesis.Wrangling.Session;
 
 namespace pbeextractionbuildlogs
 {
+	#region data-classes
+
+	public class ExampleData<OutputType>
+	{
+		public string InputPath;
+		public OutputType Output;
+
+		public ExampleData(string inputPath, OutputType output)
+		{
+			InputPath = inputPath;
+			Output = output;
+		}
+	}
+
+	public class SessionData<ExampleData>
+	{
+		public List<string> InputPaths = new List<string>();
+		public List<ExampleData> Examples = new List<ExampleData>();
+	}
+
+	#endregion data-classes
+
 	/// <summary>
 	///  Invariant: Files do not move or disappear.
 	/// </summary>
-	public class AnalysisSession
+	///
+	public static class AnalysisUtil
 	{
-		public struct ExampleData
-		{
-			public string InputPath;
-			public string Output;
+		private static readonly Dictionary<string, StringRegion> fileCache = new Dictionary<string, StringRegion>();
 
-			public ExampleData(string inputPath, string output)
+		public static StringRegion RegionFromFile(string path)
+		{
+			if (fileCache.ContainsKey(path))
 			{
-				this.InputPath = inputPath;
-				this.Output = output;
+				return fileCache[path];
 			}
+			string text = File.ReadAllText(path);
+			StringRegion region = RegionSession.CreateStringRegion(text);
+			fileCache[path] = region;
+			return region;
 		}
+	}
 
-		public class SessionData
-		{
-			public List<string> InputPaths = new List<string>();
-			public List<ExampleData> Examples = new List<ExampleData>();
-		}
+	public abstract class AnalysisSession<OutputType>
+	{
+		public abstract AnalysisSession<OutputType> AddInput(string inputPath);
+		public abstract AnalysisSession<OutputType> AddExample(ExampleData<OutputType> exampleData);
+		public abstract AnalysisSession<OutputType> AddCompletelyNegativeExample(string inputPath);
+		public abstract OutputType Analyze(string inputPath);
+		public abstract string CurrentProgram();
+	}
 
-		// TODO support sequence regions?
[…]

### 2019-05-28 pbe-extraction-buildlogs/pbe-extraction-buildlogs/ConsoleInteraction.cs

@@ -25,7 +25,7 @@ namespace pbeextractionbuildlogs
 		{
 			Console.WriteLine("Welcome to the buildlog analyzer! We make parsing bulidlogs fun with examples \U0001F389");
 
-			AnalysisSession analysisSession = new AnalysisSession();
+			RegionAnalysisSession analysisSession = new RegionAnalysisSession();
 
 			while (true)
 			{
@@ -35,14 +35,14 @@ namespace pbeextractionbuildlogs
 					new Choice("p", "\U0001F5A8 Print the current program or", () => PrintCurrentProgram(analysisSession)),
 					new Choice("s", "\U0001F4C1 Save the current exampleset or", () => SaveProgram(analysisSession)),
 					new Choice("l", "\U0001F4C2 Load a saved exampleset or", () => analysisSession = LoadProgram(analysisSession)),
-					new Choice("r", "\U0001F5D1 Reset the current exampleset?", () => analysisSession = new AnalysisSession()),
+					new Choice("r", "\U0001F5D1 Reset the current exampleset?", () => analysisSession = new RegionAnalysisSession()),
 					new Choice("d", "Print differentiating examples", async () => await analysisSession.PrintSeparatingExamples()),
 					new Choice("td", "TestDiverting", () => TestDiverting(analysisSession))
 					);
 			}
 		}
 
-		private static void TestDiverting(AnalysisSession session)
+		private static void TestDiverting(RegionAnalysisSession session)
 		{
 			session
 				//.AddExample("mini/5.log", "Execution failed for task ':app:connectedAndroidTest'.")
@@ -51,7 +51,7 @@ namespace pbeextractionbuildlogs
 			Console.Out.WriteLine("Exectued TestDiverting.");
 		}
 
-		private static void AddInput(AnalysisSession analysisSession)
+		private static void AddInput(RegionAnalysisSession analysisSession)
 		{
 			var inputPath = RequestBuildlogFilePath();
 			analysisSession.AddInput(inputPath);
@@ -68,7 +68,7 @@ namespace pbeextractionbuildlogs
 				new Choice("n", "\U0001F645 No.", () => { }));
 		}
 
-		private static void RunOnTestInput(AnalysisSession analysisSession)
+		private static void RunOnTestInput(RegionAnalysisSession analysisSession)
 		{
 			var inputPath = RequestBuildlogFilePath();
 			var output = analysisSession.Analyze(inputPath);
@@ -83,24 +83,24 @@ namespace pbeextractionbuildlogs
 			}
 		}
 
[…]

### 2019-05-28 pbe-extraction-buildlogs/pbe-extraction-buildlogs/ConsoleOutput.cs

@@ -5,24 +5,20 @@ namespace pbeextractionbuildlogs
 {
 	public class ConsoleOutput
 	{
-		public ConsoleOutput()
-		{
-		}
-
-		public static string PrintAnalysisResult(AnalysisResult analysisResult, int indentation)
+		public static string PrintAnalysisResult<OutputType>(AnalysisResult<OutputType> analysisResult, int indentation)
 		{
 			bool isFolder = analysisResult.FurtherResults.Count != 0;
 			string output = Indentation(indentation) + PrintHeader(analysisResult, true, isFolder);
 
 			if (isFolder)
 			{
-				output += analysisResult.FurtherResults.Select(ar => PrintAnalysisResult((AnalysisResult)ar, indentation + 1)).Aggregate((i, j) => i + "\n" + j);
+				output += analysisResult.FurtherResults.Select(ar => PrintAnalysisResult((AnalysisResult<OutputType>)ar, indentation + 1)).Aggregate((i, j) => i + "\n" + j);
 			}
 			else
 			{
 				output += Indentation(indentation + 1) + "Analysis " + (analysisResult.Successful ? "succeded" : "failed") + ".\n";
-				output += Indentation(indentation + 1) + "Output was: " + analysisResult.Output + "\n";
-				output += Indentation(indentation + 1) + "Desired output was: " + analysisResult.DesiredOutput + "\n";
+				output += Indentation(indentation + 1) + "Output was: " + PrintOutput(analysisResult.Output) + "\n";
+				output += Indentation(indentation + 1) + "Desired output was: " + PrintOutput(analysisResult.DesiredOutput) + "\n";
 			}
 
 			return output;
@@ -40,7 +36,7 @@ namespace pbeextractionbuildlogs
 			return "Result of " + (isAnalysis ? "analyzing" : "benchmarking") + " the " + (isFolder ? "folder" : "file") + " " + result.Path + " with the program " + result.ProgramName + ":\n";
 		}
 
-		public static string PrintEvaluationResult(AnalysisResult analysisResult, BenchmarkResult benchmarkResult)
+		public static string PrintEvaluationResult<OutputType>(AnalysisResult<OutputType> analysisResult, BenchmarkResult benchmarkResult)
 		{
 			string output = "Result of analyzing and benchmarking " + analysisResult.Path;
 			// TODO implement printing of evaluation results
@@ -50,6 +46,19 @@ namespace pbeextractionbuildlogs
 		private static string Indentation(int indentation)
 		{
[…]

### 2019-05-28 pbe-extraction-buildlogs/pbe-extraction-buildlogs/MainClass.cs

@@ -62,7 +62,8 @@ namespace pbeextractionbuildlogs
 		{
 			Console.WriteLine(
 				ConsoleOutput.PrintAnalysisResult(
-					programCollection.Analyze(opts.ProgramName, Config.SAMPLE_DIRECTORY + opts.Path, true), 0));
+					// FIXME distinguish between string and string[] here. Maybe with a simple mapping of prog names to output type
+					programCollection.Analyze<string>(opts.ProgramName, Config.SAMPLE_DIRECTORY + opts.Path, true), 0));
 		}
 
 		private static void Benchmark(BenchmarkOptions opts, ProgramCollection programCollection)
@@ -76,7 +77,7 @@ namespace pbeextractionbuildlogs
 		{
 			Console.WriteLine(
 				ConsoleOutput.PrintEvaluationResult(
-					programCollection.Analyze(opts.ProgramName, Config.SAMPLE_DIRECTORY + opts.Path, true),
+					programCollection.Analyze<string>(opts.ProgramName, Config.SAMPLE_DIRECTORY + opts.Path, true),
 					programCollection.Benchmark(opts.ProgramName, Config.SAMPLE_DIRECTORY + opts.Path, true)));
 		}
 

### 2019-05-28 pbe-extraction-buildlogs/pbe-extraction-buildlogs/MicroBenchmarking.cs

@@ -18,7 +18,7 @@ namespace pbeextractionbuildlogs
 		[Benchmark]
 		public void BenchmarkConnectbot()
 		{
-			AnalysisSession analysisSession = new AnalysisSession();
+			RegionAnalysisSession analysisSession = new RegionAnalysisSession();
 
 			//analysisSession
 			//	.AddExample(SAMPLE_PATH + "c1.log", "travis_time:start:0479293b")

### 2019-05-28 pbe-extraction-buildlogs/pbe-extraction-buildlogs/ProgramCollection.cs

@@ -12,10 +12,10 @@ namespace pbeextractionbuildlogs
 		public List<GeneralResult> FurtherResults { get; set; } = new List<GeneralResult>();
 	}
 
-	public class AnalysisResult : GeneralResult
+	public class AnalysisResult<OutputType> : GeneralResult
 	{
-		public string Output { get; set; }
-		public string DesiredOutput { get; set; }
+		public OutputType Output { get; set; }
+		public OutputType DesiredOutput { get; set; }
 		public bool Successful { get; set; }
 	}
 
@@ -29,7 +29,7 @@ namespace pbeextractionbuildlogs
 	/// </summary>
 	public class ProgramCollection
 	{
-		public List<AnalysisProgram> AnalysisPrograms = new List<AnalysisProgram>();
+		public List<NamedProgram> AnalysisPrograms = new List<NamedProgram>();
 
 		/// <summary>
 		/// If the given path references a folder all files inside are processed by function and the results given back in a list, additionally true is returned. If the path leads to a file an empty list and false is returned.
@@ -55,13 +55,13 @@ namespace pbeextractionbuildlogs
 		/// <param name="path"></param>
 		/// <param name="mightBeFolder"></param>
 		/// <returns></returns>
-		public AnalysisResult Analyze(string programName, string path, bool mightBeFolder)
+		public AnalysisResult<OutputType> Analyze<OutputType>(string programName, string path, bool mightBeFolder)
 		{
-			var result = new AnalysisResult();
+			var result = new AnalysisResult<OutputType>();
 			var wasFolder = false;
 			if (mightBeFolder)
 			{
-				var tuple = IfPathIsFolderRunOnFolder(programName, path, Analyze);
+				var tuple = IfPathIsFolderRunOnFolder(programName, path, Analyze<OutputType>);
 				result.FurtherResults = tuple.Item1;
 				wasFolder = tuple.Item2;
 			}
@@ -70,13 +70,24 @@ namespace pbeextractionbuildlogs
 
 			if (!wasFolder)
 			{
-				var program = GetProgramForSaveName(programName);
-				var output = program.ApplyToFile(path);
-				result.Output = output;
+				if (typeof(OutputType) == typeof(string))
+				{
+					var program = GetProgramForSaveName<RegionAnalysisSession, string>(programName);
+					var output = program.ApplyToFile(path);
[…]

### 2019-06-09 paper/paper.tex
several example extraction programs, description of what is extractable, readme updates

@@
 
-ci important for sw projects,
-
-broken build stops dev process until its fixed,
-
-shortening fixing time important to increase dev productivity,
+shortening fixing time for broken builds important to increase dev productivity,
 
@@
 
-extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity,
+extracting the dev-relevant information from logs and present only them in a structured way could be improvement on dev productivity,
 
@@
 
-... our approach ...,
+...
+what we do: collected a diverse set of buildlogs from travis ci, designed a metamodel of the contained (extractable?) information, labeled the collected buildlogs, built a tool which uses the PROSE library and can extract information from buildlogs based on examples, evaluated tool/learning ability/accuracy on created dataset, results ...
 
-... paper structure ...
+explicit: contributions
 
@@
 
-\paragraph{Continious integration and analysis of buildlogs}
-se research community started to look into buildlogs as CI becomes a vital part of a modern se process
+\subsection{Continuous Integration}
+several researchers done this and that
 
-e.g. Seo at al studying the kinds of errors which lead builds to fail at google and their resolvement time \cite{seo2014programmers}
+The software engineering research community started looking into buildlogs as more as continuous integration becomes a vital part of a modern software engineering process.
+Seo et al.~\cite{seo2014programmers} found that few error types such as dependency issues and type mismatches are most prominent cause of build failures at google and that most failures are resolved within two builds.
+Vassalo et al.~\cite{vassallo2017a-tale} found that the reasons for CI builds to fail are very different at open source and industrial projects using java. 
+Beller et al.~\cite{beller2017oops} 
+3 log analysis papers
 
-Vasallo et al compared build failure reasons in java open source software and at one industrial company \cite{vassallo2017a-tale}
+\subsection{Tool}
+improving time developers take to understand buildlogs, vasallo by summarizing relevant information in java/maven buildlogs and augmenting with links to related stack overflow  posts, amar et al.
+(by removing lines that appear both in passing and failing buildlogs and therefore) reducing the lines needed to be inspected, information retrieval techniques to identify most important lines for investigation and categorize the build failure cause
 
-Beller et al.
-conducted a large scale empirical analysis of java and ruby buildlogs from travis ci, found that tests are central to CI and main reason for builds to fail \todo{should I mention a key outcome like this or only what they did?}
-
-Vasallo et al.
-also build a tool to support developers to find reasons for build breaks fast, analyzes and summarizes relevant parts of a buildlog, links to related stack overflow discussions, they found that \begin{quotation}
-	dependency breaks and testing failures seem to be easy to understand
-\end{quotation} and a good summary highlighting the locality of the issues seems to be an important factor of fixing time \cite{vassallo2018un-break}
+bart paper, icse paper???
 
@@
 
-\paragraph{Information Extraction from semi-structured data using program synthesis}
+\subsection{Information Extraction and Retrieval}
+flashextract paper, icse paper???
+
 Le et al.
@@
 
-\section{Background}
+\section{Method}
+\subsection{Data collection}
+describe process of collecting buildlog files, sampling
+querying ghtorrent and travis api with (insert fancy name for data collection tool) for x buildlogs of each status of the top-watched repositories on github that also use travis ci,
+\subsection{Meta-Model}
+through manual examination of y of the buildlogs we collected designed a metamodell  of the contained/extractable/useful/interesting information,
 
-\paragraph{semi-structured data}
-characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here!
--> impact on our work with buildlogs) \cite{abiteboul1997querying}
+... explain metamodel + figure ...
+\subsection{Our Tool}
+... interaction and usage and output of tool, maybe integration possibilities ...
 
-maybe: reference \cite{smith1997information} and explain approach of first structuring into sections / "contexts" before extracting acutal information.
-but only if we actually do that and not just always parse the whole log.
+... necessary or interesting implementation details ...
 
-program synthesis from example, neccessary theoretical stuff,
-here all the references to prose theoretical papers \cite{le2014flashextract:}, \cite{polozov2015flashmeta:}, \cite{mitchell1982generalization},
+\section{Results}
+... achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data ...
 
-\section{Data collection}
-describe process of collecting buildlog files, sampling
-
-\section{Meta-Model}
-describe metamodel of data obtainable from buildlogs
-
-\section{Our Tool}
-
-\section{Evaluation}
+\section{Analysis}
+...
+our tool works well for defined cases, limitations of tool/prose/regex usage in general, every x weeks extraction has to be rewritten to keep accuracy, well improved if only y new examples have to be added ...
 
 \section{Conclusion and Future Work}
+... repeat everything and results ...
+
+... future: make avaliable to other researchers, integrate into travis, common extend evaluation and data collection, use dataset to evaluate against existing approaches ...
 

### 2019-06-09 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisProgram.cs

@@ -10,7 +10,7 @@ namespace pbeextractionbuildlogs
 		/// <summary>
 		/// Filename to save the corresponding data under.
 		/// </summary>
-		public string SaveName { get; protected set; }
+		public string SaveName { get; set; }
 	}
 
 	/// <summary>
@@ -25,18 +25,28 @@ namespace pbeextractionbuildlogs
 		/// <summary>
 		/// Data needed for the learning lesson.
 		/// </summary>
-		public SessionData<ExampleData<OutputType>> LearningData { get; private set; }
+		public SessionData<ExampleData<OutputType>> LearningData { get; set; }
 
 		/// <summary>
 		/// LogKind this programm analyzes
 		/// </summary>
-		public LogKind LogKind { get; }
+		public LogKind LogKind { get; set; }
 
 		/// <summary>
 		/// TODO doc
 		/// </summary>
-		public MetaModelObject Target { get; }
+		public MetaModelObject Target { get; set; }
 		// MAYBE: private AnalysisSession analysisSession;
+
+		public static AnalysisProgram<SessionType, OutputType> LoadAnalysisProgram(string saveName)
+		{
+			return (new AnalysisProgram<SessionType, OutputType>
+			{
+				SaveName = saveName,
+			}).Load();
+		}
+
+		public AnalysisProgram() { }
 
 		public AnalysisProgram(string saveName, LogKind logKind, MetaModelObject target, SessionData<ExampleData<OutputType>> learningData = null, bool takeFromFileIfPossible = false)
 		{
@@ -124,21 +134,21 @@ namespace pbeextractionbuildlogs
 		/// </summary>
 		public void Save()
 		{
-			XmlSerializer serializer = new XmlSerializer(LearningData.GetType());
+			XmlSerializer serializer = new XmlSerializer(GetType());
 			Directory.CreateDirectory(Config.PROGRAM_DATA_DIRECTORY.Remove(Config.PROGRAM_DATA_DIRECTORY.Length - 1));
 			using (StreamWriter file = new StreamWriter(File.Create(saveFilePath)))
 			{
-				serializer.Serialize(file, LearningData);
+				serializer.Serialize(file, this);
 			}
 		}
 
-		public void Load()
+		public AnalysisProgram<SessionType, OutputType> Load()
 		{
 			// TODO: auch andere sachen serializieren??
-			XmlSerializer serializer = new XmlSerializer(new SessionData<ExampleData<OutputType>>().GetType());
[…]

### 2019-06-09 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs

@@ -19,6 +19,8 @@ namespace pbeextractionbuildlogs
 		public string InputPath;
 		public OutputType Output;
 
+		public ExampleData() { }
+
 		public ExampleData(string inputPath, OutputType output)
 		{
 			InputPath = inputPath;
@@ -48,7 +50,7 @@ namespace pbeextractionbuildlogs
 			{
 				return fileCache[path];
 			}
-			string text = File.ReadAllText(path);
+			string text = File.ReadAllText(path).Replace("\r\n", "\n").Replace("\r", "\n").Replace("\n\r", "\n").Replace(((char)0x1b).ToString(), "");
 			StringRegion region = RegionSession.CreateStringRegion(text);
 			fileCache[path] = region;
 			return region;
@@ -78,7 +80,7 @@ namespace pbeextractionbuildlogs
 		{
 			var inputRegion = AnalysisUtil.RegionFromFile(exampleData.InputPath);
 			var startIndex = inputRegion.S.IndexOf(exampleData.Output, StringComparison.Ordinal);
-			var outputRegion = inputRegion.Slice((uint)startIndex, (uint)(startIndex + exampleData.Output.Length));
+			var outputRegion = inputRegion.Slice((uint)startIndex, (uint)(startIndex) + ((uint)exampleData.Output.Length));
 			session.Constraints.Add(new RegionExample(inputRegion, outputRegion));
 
 			return this;
@@ -102,10 +104,17 @@ namespace pbeextractionbuildlogs
 			RegionProgram topRankedProgram = session.Learn();
 			if (topRankedProgram == null)
 			{
-				Console.Error.WriteLine("no program found");
-				return null;
+				Console.WriteLine("no program found");
+				return "no program found";
 			}
+			Console.WriteLine("Learned Program:");
+			Console.WriteLine(topRankedProgram);
+			Console.WriteLine();
 			StringRegion output = topRankedProgram.Run(inputRegion);
+			if (output == null)
+			{
+				return "no extraction found for this input";
+			}
 			return output?.Value;
 		}
 

### 2019-06-09 pbe-extraction-buildlogs/pbe-extraction-buildlogs/Config.cs

@@ -3,10 +3,12 @@ namespace pbeextractionbuildlogs
 {
 	public class Config
 	{
-		public static string ROOT_DIRECTORY = "../../../";
-		public static string PROGRAM_DATA_DIRECTORY = "../../../ressources/analysis-programs/";
-		public static string SAMPLE_DIRECTORY = "/Volumes/LacisBackup/buildlogs/";
+		//public static string ROOT_DIRECTORY = "../../../";
+		public static string ROOT_DIRECTORY = "";
+		public static string PROGRAM_DATA_DIRECTORY = ROOT_DIRECTORY +
+			"ressources/analysis-programs/";
+		public static string SAMPLE_DIRECTORY = ROOT_DIRECTORY + "samples/";
 
-		public static string LOG_KIND_FILE_PATH = "../../../ressources/log-kinds.txt";
+		public static string LOG_KIND_FILE_PATH = ROOT_DIRECTORY + "ressources/log-kinds.txt";
 	}
 }

### 2019-06-09 pbe-extraction-buildlogs/pbe-extraction-buildlogs/LogKind.cs

@@ -9,8 +9,10 @@ namespace pbeextractionbuildlogs
 	/// </summary>
 	public class LogKind
 	{
-		public string Language { get; }
-		public string BuildTool { get; }
+		public string Language { get; set; }
+		public string BuildTool { get; set; }
+
+		public LogKind() { }
 
 		public LogKind(string language, string buildTool)
 		{

### 2019-06-09 pbe-extraction-buildlogs/pbe-extraction-buildlogs/MainClass.cs

@@ -35,7 +35,6 @@ namespace pbeextractionbuildlogs
 		{
 			// setup
 			ProgramCollection programCollection = new ProgramCollection();
-			programCollection.AddTravisWorkerProgram();
 
 			Parser.Default.ParseArguments<AnalysisOptions, BenchmarkOptions, EvaluateOptions, InteractionOptions>(args)
 				.WithParsed<AnalysisOptions>(opts => Analyze(opts, programCollection))
@@ -43,19 +42,6 @@ namespace pbeextractionbuildlogs
 				.WithParsed<EvaluateOptions>(opts => Evaluate(opts, programCollection))
 				.WithParsed<InteractionOptions>(_ => ConsoleInteraction.Run())
 				.WithNotParsed(errs => Console.WriteLine(errs));
-
-			//if (args.Length == 1)
-			//{
-			//	if (args[0] == "-bc")
-			//	{
-			//		new MicroBenchmarking().BenchmarkConnectbot();
-			//	}
-			//	else if (args[0] == "-b")
-			//	{
-			//		var summary = BenchmarkRunner.Run<MicroBenchmarking>();
-			//		Console.WriteLine("Total Time: " + summary.TotalTime);
-			//	}
-			//}
 		}
 
 		private static void Analyze(AnalysisOptions opts, ProgramCollection programCollection)

### 2019-06-09 pbe-extraction-buildlogs/pbe-extraction-buildlogs/ProgramCollection.cs

@@ -31,6 +31,21 @@ namespace pbeextractionbuildlogs
 	{
 		public List<NamedProgram> AnalysisPrograms = new List<NamedProgram>();
 
+		public ProgramCollection()
+		{
+			LoadProgramCollection();
+		}
+
+		private void LoadProgramCollection()
+		{
+			AnalysisPrograms.Add(AnalysisProgram<RegionAnalysisSession, string>.LoadAnalysisProgram("travis-worker"));
+			AnalysisPrograms.Add(AnalysisProgram<RegionAnalysisSession, string>.LoadAnalysisProgram("travis-worker-short"));
+			AnalysisPrograms.Add(AnalysisProgram<RegionAnalysisSession, string>.LoadAnalysisProgram("travis-worker-long"));
+			AnalysisPrograms.Add(AnalysisProgram<RegionAnalysisSession, string>.LoadAnalysisProgram("android-failure"));
+			AnalysisPrograms.Add(AnalysisProgram<RegionAnalysisSession, string>.LoadAnalysisProgram("android-failure-with-dependencies"));
+			AnalysisPrograms.Add(AnalysisProgram<RegionAnalysisSession, string>.LoadAnalysisProgram("newline-test"));
+		}
+
 		/// <summary>
 		/// If the given path references a folder all files inside are processed by function and the results given back in a list, additionally true is returned. If the path leads to a file an empty list and false is returned.
 		/// </summary>
@@ -84,6 +99,11 @@ namespace pbeextractionbuildlogs
 					result.Output = (OutputType)(object)output;
 				}
 
+				//if (result.Output == null)
+				//{
+				//	result.Output = "Sadly we could not extract anything from that input";
+				//}
+
 
 				// TODO get desired output from somewhere
 				result.DesiredOutput = result.Output;
@@ -127,28 +147,5 @@ namespace pbeextractionbuildlogs
 			}
 			return (pbeextractionbuildlogs.AnalysisProgram<SessionType, OutputType>)program;
 		}
-
-		public AnalysisProgram<RegionAnalysisSession, string> AddTravisWorkerProgram()
-		{
-			AnalysisProgram<RegionAnalysisSession, string> program = new AnalysisProgram<RegionAnalysisSession, string>("travis-worker", new LogKind("all", "all"), MetaModelObject.TravisWorker, takeFromFileIfPossible: false);
-			program
[…]

### 2019-06-10 thesis/txt/background.tex
add missing files

\providecommand{\myrootdir}{..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}

\section{Background}

\subsection{semi-structured data}
characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here! -> impact on our work with buildlogs) \cite{abiteboul1997querying}

maybe: reference \cite{smith1997information} and explain approach of first structuring into sections / "contexts" before extracting acutal information. but only if we actually do that and not just always parse the whole log.

program synthesis from example, neccessary theoretical stuff,
here all the references to prose theoretical papers \cite{le2014flashextract:}, \cite{polozov2015flashmeta:}, \cite{mitchell1982generalization},

\end{document}

### 2019-06-14 paper/paper.tex
start to properly redo paper bullet points, colored commands for semantic notes

--- 2019-05-28 paper/paper.tex
@@
 % TODO remove XD
-\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
-\usepackage[color=ballblue]{todonotes}
-
+\usepackage{xcolor}
+\newcommand{\secfunc}[1]{{\color{magenta}#1}}
+\newcommand{\mention}[1]{{\color{cyan}#1}}
+\newcommand{\plan}[1]{{\color{purple}#1}}
+\newcommand{\bp}[1]{{\color{violet}#1}}
+\newcommand{\draft}[1]{{\color{blue}#1}}
+\newcommand{\review}[1]{{\color{black}#1}}
+\newcommand{\todo}[1]{{\color{orange}#1}}
 %%
@@
 
+\secfunc{section function - secfunc} \\
+\mention{things to mention / reference - mention} \\
+\plan{what to write here - plan} \\
+\bp{actual bullet points - bp} \\
+\draft{final text drafty - draft} \\
+\review{final text review ready - review} \\
+\todo{ToDo - todo} \\
+
 \section{Introduction}
+\secfunc{why? what? research questions? purpose? hypothesis? wide $\rightarrow$ narrow}
 
-ci important for sw projects,
+\bp{build break priority for developers \mention{bart paper}
 
-broken build stops dev process until its fixed,
+decreasing the time until a fix therefore improves overall productivity
 
-shortening fixing time important to increase dev productivity,
+most time spend: reading very long and verbose buildlog
 
-to detect underlying failure huge buildlog has to be read, dev has to find relevant information between a lot of lines unimportant for the task,
+recovering relevant information from between many uninteresting other lines
 
-extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity,
+support: extract desired information and present in a structured way
 
-traditional: regexes built for exact information extraction
+usually: tools use handcrafted regular expressions
 
-hard to maintain, regex understanding effort, don't generalize / have to be redone when a bulidlog changes / language or build tool is switched,
+but: tedious / mentally complicated work, especially when maintenance is needed some months in the future -> reunderstanding old regular expressions is known to be difficult / dreading task for developers
 
-... our approach ...,
+we: take this burden of developers by enabling them to define extraction programs through simply giving examples of the desired extractions
 
-... paper structure ...
+collect a diverse set of buildlogs to  develop a metamodel of the contained information
+
+implement prototype for pbe extractions in buildlogs using the microsoft PROSE library
+
+showed that our tool is capable of extracting various desired informations, shortens development time in comparison to manual regex construction and performs more accurate than other semi-supervised methods
+
+}
 
@@
 
-\paragraph{Continious integration and analysis of buildlogs}
-se research community started to look into buildlogs as CI becomes a vital part of a modern se process
+\subsection{Continuous Integration}
 
-e.g. Seo at al studying the kinds of errors which lead builds to fail at google and their resolvement time \cite{seo2014programmers}
+\plan{more research into CI now, large scale analyses of buildlogs, open source from travis ci and industrial}
 
-Vasallo et al compared build failure reasons in java open source software and at one industrial company \cite{vassallo2017a-tale}
+\mention{google build analysis}
+\plan{google, java and c++, anlyzed frequency and reasons for failures, few error kinds responsible for most failures, dependency errors appear most, most fixed in two build iterations}
 
-Beller et al.
-conducted a large scale empirical analysis of java and ruby buildlogs from travis ci, found that tests are central to CI and main reason for builds to fail \todo{should I mention a key outcome like this or only what they did?}
+\mention{java os vs ing}
+\plan{oss and ing for java projects, classfied failures, cluster analysis, similarities: few compilation \& many testing failures, differences: oss mainly unit testing failures, industrial mainly release preparation}
 
-Vasallo et al.
-also build a tool to support developers to find reasons for build breaks fast, analyzes and summarizes relevant parts of a buildlog, links to related stack overflow discussions, they found that \begin{quotation}
-	dependency breaks and testing failures seem to be easy to understand
-\end{quotation} and a good summary highlighting the locality of the issues seems to be an important factor of fixing time \cite{vassallo2018un-break}
+\mention{travistorrent}
+\plan{java and ruby builds \& logs from travis ci, manually built parser to extract failure reasons, most builds fail because of tests, number of tests \& kind \& failure rates very dependent on programming language, low failure rates hint at pretested code on CI server}
 
-relation to our work: we could support this research by enabling easier data extraction from the analyzed buildlogs, most focus on single/few languages with our tool they could more easily cover multiple ones
+\plan{our work: support such research through building log file evaluation easier, enable them to cover more languages and build tool kinds}
 
-\paragraph{Information Extraction from semi-structured data using program synthesis}
-Le et al.
-developed FlashExtract as part of the PROSE Framework, tool to synthesize programs based on a few given examples, extract substrings from semi-structured texts, users can extract multiple fields and structure them with hierarchy and sequence, uses inductive synthesis algorithm to synthesize intended program, eliminates the need for the user to understand structure of entire document or to be able to code
+\subsection{Tool}
 
-we are applying their library to the domain of buildlogs, using programming by example to take away the need to tediously develop and maintain the regular expressions, traditionally used in information extraction
+\mention{bart}
 
-\section{Background}
+\mention{icse paper}
 
-\paragraph{semi-structured data}
-characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here!
--> impact on our work with buildlogs) \cite{abiteboul1997querying}
+\subsection{Information Extraction and Retrieval}
 
-maybe: reference \cite{smith1997information} and explain approach of first structuring into sections / "contexts" before extracting acutal information.
-but only if we actually do that and not just always parse the whole log.
+\mention{PROSE fashextract}
 
-program synthesis from example, neccessary theoretical stuff,
-here all the references to prose theoretical papers \cite{le2014flashextract:}, \cite{polozov2015flashmeta:}, \cite{mitchell1982generalization},
+\mention{queriying semi structured data}
 
-\section{Data collection}
-describe process of collecting buildlog files, sampling
+\mention{sth about IR / paragraph retrieval}
 
-\section{Meta-Model}
-describe metamodel of data obtainable from buildlogs
+\plan{difference of us to IR (imprecise \& rough)}
 
-\section{Our Tool}
+\section{Method}
+\secfunc{how? when? material? narrow}
 
-\section{Evaluation}
+\todo{want?: flow of research figure}
+
+\todo{study design vs. study carry out}
+
+\subsection{Data collection}
+\plan{describe process of collecting buildlog files, sampling}
+
+\bp{querying ghtorrent and travis api with (insert fancy name for data collection tool) for x buildlogs of each status of the top-watched repositories on github that also use travis ci}
+
+\subsection{Meta-Model}
+\bp{through manual examination of y of the buildlogs we collected designed a metamodell  of the contained/extractable/useful/interesting information}
+
+\plan{figure with metamodel}
+
+\plan{explain (shortly? partly?) meta model classes}
+
+\subsection{Our Tool}
+\plan{interaction and usage and output of tool, maybe integration possibilities}
+
+\plan{necessary or interesting implementation details}
+
+\section{Results}
+\secfunc{hard numbers! answers to research questions, narrow}
+
+\plan{achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data}
+
+\section{Analysis / Discussion}
+\secfunc{interpretation, implication of answers and why does it matter, comparison to previous findings, narrow $\rightarrow$ wide}
+
+\plan{our tool works well for defined cases, limitations of tool/prose/regex usage in general, every x weeks extraction has to be rewritten to keep accuracy, well improved if only y new examples have to be added}
 
 \section{Conclusion and Future Work}
+\secfunc{summarize, results again, future research}
+
+\plan{repeat everything and results}
+
+\plan{future}
+
+\bp{make avaliable to other researchers
+
+integrate into travis
+
+\plan{as always} extend evaluation and data collection
+
+use dataset to evaluate against existing approaches
+
+}
 

### 2019-06-14 data-collection/collect-travis-logs.rb

@@ -147,6 +147,8 @@ class LogCollector
         p builds_per_state
         builds_per_state.each do |state, builds|
           builds.each do |build|
+            next if build.jobs.empty?
+
             job_id = build.jobs[0].id
             log = TravisRequester.retrieve_log_travis(job_id)
             directory_path = "logs/#{lang}/#{repo_slug.gsub('/', '@')}/#{state}"

### 2019-06-14 paper/paper.tex
reintegrate some bullet points from old draft

@@
 
+\plan{improving time developers take to understand buildlogs, vasallo by summarizing relevant information in java/maven buildlogs and augmenting with links to related stack overflow  posts, amar et al.
+(by removing lines that appear both in passing and failing buildlogs and therefore) reducing the lines needed to be inspected, information retrieval techniques to identify most important lines for investigation and categorize the build failure cause (-> automatic rerun because of environmental failure?)
+}
+
 \subsection{Information Extraction and Retrieval}
+
+\plan{Le et al.
+developed FlashExtract as part of the PROSE Framework, tool to synthesize programs based on a few given examples, extract substrings from semi-structured texts, users can extract multiple fields and structure them with hierarchy and sequence, uses \todo{inductive - explain or throw out} synthesis algorithm to synthesize intended program, eliminates the need for the user to understand structure of entire document or to be able to code
+
+we are applying their library to the domain of buildlogs, using programming by example to take away the need to tediously develop and maintain the regular expressions, traditionally used in information extraction
+}
 
@@
 
+\plan{characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here!
+-> impact on our work with buildlogs) \cite{abiteboul1997querying}}
+
 \mention{sth about IR / paragraph retrieval}
+\plan{practices from information retrieval, cutting into lines or paragraphs, calculating similarities through methods xy}
 
@@
 \plan{interaction and usage and output of tool, maybe integration possibilities}
+
+\plan{capabilities: give example extractions \& limitations}
 

### 2019-06-15 paper/paper.tex
intrduction draft 1, related work 2/3 parts

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Analyzing Buildlogs Using Programming by Example}
+\title{Analyzing Build Logs Using Programming by Example}
 
@@
 
-\bp{build break priority for developers \mention{bart paper}
+\draft{Fixing a broken continuous integration build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.
+During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to recover the relevant information from between many uninteresting other lines.
 
-decreasing the time until a fix therefore improves overall productivity
+One way to support them would be to extract the desired Information and present it in and present it in a structured way.
+Usually such functionality is realized by tools that employ handrcrafted regular expressions to find the desired text parts within the build log.
+However, creating these regular expressions is a tedious and mentally complicated work, especially when they have to be maintained some months in the future \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
+Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.
 
-most time spend: reading very long and verbose buildlog
-
-recovering relevant information from between many uninteresting other lines
-
-support: extract desired information and present in a structured way
-
-usually: tools use handcrafted regular expressions
-
-but: tedious / mentally complicated work, especially when maintenance is needed some months in the future -> reunderstanding old regular expressions is known to be difficult / dreading task for developers
-
-we: take this burden of developers by enabling them to define extraction programs through simply giving examples of the desired extractions
-
-collect a diverse set of buildlogs to  develop a metamodel of the contained information
-
-implement prototype for pbe extractions in buildlogs using the microsoft PROSE library
-
-showed that our tool is capable of extracting various desired informations, shortens development time in comparison to manual regex construction and performs more accurate than other semi-supervised methods
-
+We implemented \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples using the Microsoft PROSE library~\cite{le2014flashextract:}.
+After collecting a diverse set of build logs from Travis CI we designed a meta-model of the contained information.
+Our evaluation of ALBE showed that it is able to define extractinos for various desired informations, that it shortens development time in comparison to manual regex cnosturction and ...
 }
@@
 
-\plan{more research into CI now, large scale analyses of buildlogs, open source from travis ci and industrial}
+\draft{
+The software engineering research community started to look into build logs as continuous integration becomes a vital part of a modern software engineering process.
+Reserachers have analyzed industrial and open source logs for failure reasons and their impact on development.
 
-\mention{google build analysis}
-\plan{google, java and c++, anlyzed frequency and reasons for failures, few error kinds responsible for most failures, dependency errors appear most, most fixed in two build iterations}
+Seo et al.~\cite{seo2014programmers} found that at google few error types such as dependency mismatches are the most prominent cause of build failures and most failures are resolved within two builds.
+Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in java to industrial ones.
+They determined that testing failures outweigh compilation errors and that open source bulids fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
+Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
+They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being pretested before sent to the CI server.
 
-\mention{java os vs ing}
-\plan{oss and ing for java projects, classfied failures, cluster analysis, similarities: few compilation \& many testing failures, differences: oss mainly unit testing failures, industrial mainly release preparation}
-
-\mention{travistorrent}
-\plan{java and ruby builds \& logs from travis ci, manually built parser to extract failure reasons, most builds fail because of tests, number of tests \& kind \& failure rates very dependent on programming language, low failure rates hint at pretested code on CI server}
-
-\plan{our work: support such research through building log file evaluation easier, enable them to cover more languages and build tool kinds}
+All these researchers described building parsers in order to evaluate the studied build logs.
+Our work could support their research by easing the parser development and enable them to cover more languages and build tools easier.
+}
 
@@
 
-\mention{bart}
+\draft{
+Vassallo et al.~\cite{vassallo2018un-break} also made it their task to shortening the time it takes developers to understand builogs.
+They summarize relevant information in Java/maven buildlogs and augment them with links to related stack overflow posts.
+They observed that highlighting the locality and context of an issue is helpful to programmers.
+We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.
 
-\mention{icse paper}
-
-\plan{improving time developers take to understand buildlogs, vasallo by summarizing relevant information in java/maven buildlogs and augmenting with links to related stack overflow  posts, amar et al.
-(by removing lines that appear both in passing and failing buildlogs and therefore) reducing the lines needed to be inspected, information retrieval techniques to identify most important lines for investigation and categorize the build failure cause (-> automatic rerun because of environmental failure?)
+Amar et al.~\mention{cite icse paper} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
+Further they employ information retrieval techniques to identify the lines most likely hinting at the cause of the error.
+In contrast to that, instead of comparing whole our tool ALBE extracts specific parts of the build logs.
+As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
 }

### 2019-06-15 paper/paper.tex
ie / ir start for related work, draft data collection

@@
 
-\plan{Le et al.
-developed FlashExtract as part of the PROSE Framework, tool to synthesize programs based on a few given examples, extract substrings from semi-structured texts, users can extract multiple fields and structure them with hierarchy and sequence, uses \todo{inductive - explain or throw out} synthesis algorithm to synthesize intended program, eliminates the need for the user to understand structure of entire document or to be able to code
+\plan{
+explain / define information retrieval \bp{matching text piece to similar (maybe labeled) ones in order to identify ... topic}
 
-we are applying their library to the domain of buildlogs, using programming by example to take away the need to tediously develop and maintain the regular expressions, traditionally used in information extraction
+apply to our use case: paragraph/passage retrieval \bp{for our use case this could be done by slicing the builog into lines similar as \mention{paper about passage retrieval} does it with ...}
+
+define information extraction \bp{pulling specific information out of text is called information extraction}
+
+short: difference to retrieval, fuzzyness
+
+\bp{in our work we decided to focus on the extraction of exact information from build logs}
 }
 
-\mention{PROSE fashextract}
+\draft{
+Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft PROgram Synthesis using Examples} (PROSE) framework.
+It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples.
+Users can extract multiple fields and structure them with hierarchy and sequence.
+FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.
 
-\mention{queriying semi structured data}
+We are applying their functionality to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information extraction.
+}
 
-\plan{characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here!
--> impact on our work with buildlogs) \cite{abiteboul1997querying}}
+\subsection{Semi-Structured Data}
 
-\mention{sth about IR / paragraph retrieval}
-\plan{practices from information retrieval, cutting into lines or paragraphs, calculating similarities through methods xy}
+\draft{
+Software build logs are inherently semi-structured data. \todo{explain the different charactersitics and relate to buildlogs}
+Serge Abiteboul characterized semi-structured data as having an irregular, implicit, partial and rapidly evolving texture.
+}
 
-\plan{difference of us to IR (imprecise \& rough)}
+\plan{characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access \cite{abiteboul1997querying}}
 
@@
 \subsection{Data collection}
+
+\draft{
+In order to build a tool which facilitates information extraction from build logs we first had \todo{which time form here?
+past or present?} to get an impression on what kinds of build logs occur in projects, what possibly extractable information they contain and how structured or unstructured they are.
+}
+
+\subsubsection{Design}
+\bp{
+realistic image (for open source software) we sample from popular GitHub repositories that also use Travis CI.
+
+\draft{Obtaining the newes logs from them would entail sampling mostly logs of succeeding builds as the distribution of build states on a Travis CI repository is highly skewed towards successfull builds~\cite{beller2017oops}.
+Therefore we stratify our collection of logs and select an equal amount of logs from each type of Travis CI build status.}
+}
+
+\subsubsection{Execution}
+\bp{
+built tool X \todo{data collection tool name, LogCollector?}
+
+queryed ghtorrent dataset from the first of april 2018 through google bigquery
+
+poked Travis CI for active status of project and collected sampled builds through Travis ruby library
+
+downloaded logs throuh Travis Rest API \todo{look up version}
+}
+
 \plan{describe process of collecting buildlog files, sampling}
@@
 
-\plan{figure with metamodel}
+\todo{figure with metamodel}
 

### 2019-06-16 paper/paper.tex
correct introduction + rw, try to write ie/ir part, evaluation draft, research flow image

@@
 
-\secfunc{section function - secfunc} \\
-\mention{things to mention / reference - mention} \\
-\plan{what to write here - plan} \\
-\bp{actual bullet points - bp} \\
-\draft{final text drafty - draft} \\
-\review{final text review ready - review} \\
-\todo{ToDo - todo} \\
+\secfunc{section function - \textbackslash secfunc} \\
+\mention{things to mention / reference - \textbackslash mention} \\
+\plan{what to write here - \textbackslash plan} \\
+\bp{actual bullet points - \textbackslash bp} \\
+\draft{final text drafty - \textbackslash draft} \\
+\review{final text review ready - \textbackslash review} \\
+\todo{ToDo - \textbackslash todo} \\
 
@@
 
-\draft{Fixing a broken continuous integration build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.
+\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.
 During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to recover the relevant information from between many uninteresting other lines.
 
-One way to support them would be to extract the desired Information and present it in and present it in a structured way.
-Usually such functionality is realized by tools that employ handrcrafted regular expressions to find the desired text parts within the build log.
-However, creating these regular expressions is a tedious and mentally complicated work, especially when they have to be maintained some months in the future \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
+One way to support them would be to extract the desired information and present it in a structured way.
+Usually such functionality is realized by tools that employ handcrafted regular expressions to find the desired text parts within the build log.
+However, creating these regular expressions is tedious and mentally complicated task, especially when they have to be maintained some months in the future \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
 Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.
 
-We implemented \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples using the Microsoft PROSE library~\cite{le2014flashextract:}.
+We implemented \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples.
 After collecting a diverse set of build logs from Travis CI we designed a meta-model of the contained information.
-Our evaluation of ALBE showed that it is able to define extractinos for various desired informations, that it shortens development time in comparison to manual regex cnosturction and ...
+Our evaluation of ALBE showed that it is able to define extractions for various desired informations, that it shortens development time in comparison to manual regular expression construction and ...
 }
+
+\todo{Research Questions!}
+
+\bp{ RQ1: how many and which kind of samples does pbe need to be competitive with existing methods? }
+
+\bp{ can pbe extraction replace or even exceed existing methods for our use case? }
+
+\bp{ What are the limitations of extractions? (only interesting when specified with PROSE library..)}
+
+\bp{ Adjustements / Improvements to PROSE for extracting specifically from build logs }
 
@@
 
-\draft{
+\review{
 The software engineering research community started to look into build logs as continuous integration becomes a vital part of a modern software engineering process.
-Reserachers have analyzed industrial and open source logs for failure reasons and their impact on development.
+Researchers have analyzed industrial and open source logs for failure reasons and their impact on development.
 
-Seo et al.~\cite{seo2014programmers} found that at google few error types such as dependency mismatches are the most prominent cause of build failures and most failures are resolved within two builds.
-Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in java to industrial ones.
-They determined that testing failures outweigh compilation errors and that open source bulids fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
+Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at google.
+In addition most failures are resolved within two builds.
+Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones.
+They determined that testing failures outweigh compilation errors.
+Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
 Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
-They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being pretested before sent to the CI server.
+They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.
 
@@
 
-\subsection{Tool}
+\subsection{Tools}
 
-\draft{
-Vassallo et al.~\cite{vassallo2018un-break} also made it their task to shortening the time it takes developers to understand builogs.
-They summarize relevant information in Java/maven buildlogs and augment them with links to related stack overflow posts.
+\review{
+Vassallo et al.~\cite{vassallo2018un-break} also made it their task to shorten the time it takes developers to understand build logs.
+They summarize relevant information in Java/maven build logs and augment them with links to related stack overflow posts.
 They observed that highlighting the locality and context of an issue is helpful to programmers.
@@
 
-Amar et al.~\mention{cite icse paper} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
+Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
 Further they employ information retrieval techniques to identify the lines most likely hinting at the cause of the error.
-In contrast to that, instead of comparing whole our tool ALBE extracts specific parts of the build logs.
+In contrast to that, our tool ALBE extracts specific parts of the build logs.
 As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
@@
 
-\plan{
-explain / define information retrieval \bp{matching text piece to similar (maybe labeled) ones in order to identify ... topic}
+\draft{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
+Usually this is done by removing irrelevant terms and stop words, stemming and weighting the remaining words before comparing the similar of those weights against other text parts.~\cite{panichella2016parameterizing} For our use case this could be applied by slicing the build logs into lines or small sections.
+Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
 
-apply to our use case: paragraph/passage retrieval \bp{for our use case this could be done by slicing the builog into lines similar as \mention{paper about passage retrieval} does it with ...}
+In our work we focus on a more precise form of information extraction where we try to obtain a specific detail from a build log instead of retrieving the general idea of a document part.}
 
-define information extraction \bp{pulling specific information out of text is called information extraction}
-
-short: difference to retrieval, fuzzyness
-
-\bp{in our work we decided to focus on the extraction of exact information from build logs}
-}
-
-\draft{
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft PROgram Synthesis using Examples} (PROSE) framework.
+\review{
+Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework.
 It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples.
@@
 \draft{
-Software build logs are inherently semi-structured data. \todo{explain the different charactersitics and relate to buildlogs}
-Serge Abiteboul characterized semi-structured data as having an irregular, implicit, partial and rapidly evolving texture.
+Software build logs are inherently semi-structured data. \todo{explain the different characteristics and relate to build logs}
+Serge Abiteboul~\cite{abiteboul1997querying} characterized semi-structured data as having an irregular, implicit, partial and rapidly evolving texture.
 }
-
-\plan{characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access \cite{abiteboul1997querying}}
 
@@
 \todo{study design vs. study carry out}
+
+\begin{figure}
+	\includegraphics[width=0.5\textwidth, trim={0.5cm 5cm 3cm 2cm}, clip]{img/flow-of-research.pdf}
+	\caption{Flow of Research}
+\end{figure}
 
@@
 
-\draft{Obtaining the newes logs from them would entail sampling mostly logs of succeeding builds as the distribution of build states on a Travis CI repository is highly skewed towards successfull builds~\cite{beller2017oops}.
+\draft{Obtaining the newest logs from them would entail sampling mostly logs of succeeding builds as the distribution of build states on a Travis CI repository is highly skewed towards successful builds~\cite{beller2017oops}.
 Therefore we stratify our collection of logs and select an equal amount of logs from each type of Travis CI build status.}
@@
 
-queryed ghtorrent dataset from the first of april 2018 through google bigquery
+queryed ghtorrent dataset from the first of April 2018 through google BigQuery
 
@@
 
-downloaded logs throuh Travis Rest API \todo{look up version}
+downloaded logs through Travis Rest API \todo{look up version}
 }
 
-\plan{describe process of collecting buildlog files, sampling}
+\subsection{Meta-Model}
+\bp{through manual examination of y of the build logs we collected designed a meta-model  of the contained/extractable/useful/interesting information}
 
-\bp{querying ghtorrent and travis api with (insert fancy name for data collection tool) for x buildlogs of each status of the top-watched repositories on github that also use travis ci}
-
-\subsection{Meta-Model}
-\bp{through manual examination of y of the buildlogs we collected designed a metamodell  of the contained/extractable/useful/interesting information}
-
-\todo{figure with metamodel}
+\todo{figure with meta-model}
+\begin{figure}
+	\includegraphics[width=0.5\textwidth, trim={0.5cm 4cm 3cm 0.5cm}, clip]{img/meta-model.pdf}
+	\caption{Meta-Model}
+\end{figure}
 
@@
 
-\subsection{Our Tool}
-\plan{interaction and usage and output of tool, maybe integration possibilities}
+\subsection{Our Tool: ALBE \textemdash \ Analyzing Logs By Example}
 
-\plan{capabilities: give example extractions \& limitations}
+\plan{
+techstacky: C\#, dot net core, Microsoft PROSE library specifically their TextExtraction DSL
 
-\plan{necessary or interesting implementation details}
+samples \& learning: labeled data is in xml files, parsed (and shuffled) for examples, program learned for specific instruction
+
+interaction: user can analyze given file with program defined by specific exampleset, if there: describe how to use iteratively growing / shuffling learning process
+}
+
+\subsubsection{Capabilities}
+
+\plan{
+Example extractions: travis worker, android failure, what we do evaluations on
+}
+
+\subsubsection{Limitations}
+
+\plan{
+Travis worker both kinds at once, explain PROSE limitations on arbitrary OR regexes
+
+for all limitations: why? and how would we solve that?
+}
+
+\subsection{Evaluation}
+\bp{
+To evaluate our tool we did xyz, we wanted to measure: accuracy of extractions, impression on effort of creating such extraction, compare both to existing methods
+}
+
+\subsubsection{Extraction Accuracy}
+
+\bp{we labelled x logs from project y using language z / build tool b. (do for one, maybe extend with further one)
+
+evaluated accuracy \todo{<define accuracy for us>} with growing number of 
+\begin{itemize}
+	\item random selected
+	\item chronologically sampled
+	\item hand selected 
+\end{itemize}
+samples.
+}
+
+\subsubsection{Compare to Traditional Methods}
+\paragraph{TravisTorrent}
+\bp{Beller et al.
+\mention{cite correct travistorrent paper} reported on manually constructing a parser with regular expressions for ruby \& Java and common build tools / output formats there, they can extract \todo{<explain there extractions, with example necessary?}
+
+android-failure example: decided not to implement as to complicated \todo{<- that kind of already belongs into results, how do we describe the \emph{method} of this comparison accurately??}
+}
+
+\paragraph{Manual Regex Construction}
+\plan{
+for something where I did not look at the synthesized program
+
+alternative: small study with other developers on manual vs. pbe extraction
+}
+
+\paragraph{IR paragraph stuff}
+\plan{
+maybe simple setup with lines implementing vector comparison on keywords ourselves -> how can we reuse the labeling for the c\# tool?
+}
+
+\paragraph{Keyword search}
+\plan{
+either: we give a list of keywords generally associated with the thing we want to extract (e.g. failure/error/..) -> write nicely how we brainstormed that
+
+or: small study of what developers would search for (maybe literature already did that?)
+
+or: relate to samples? search for already seen words from last failure
+}
 
@@
 
-\plan{achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data}
+\plan{graphs!, achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data}
 

### 2019-06-18 data-collection/collect-travis-logs.rb
small improvements: ruby tool output & end after number of trys no buildlogs with rare states, timing of learning in c# tool, black headings in paper draft, worklog update 17.6.

@@ -12,6 +12,15 @@ module Config
   def self.config
     YAML.load_file('config.yml')
   end
+
+  def self.identifier
+    "-#{config['repo_selection']['languages']}" \
+      "-#{config['repo_selection']['repos_per_language']}" \
+      "-#{config['repo_selection']['repos_to_try_per_language']}" \
+      "-#{config['log_selection']['total_log_count']}" \
+      "-#{config['log_selection']['log_count_per_state']}" \
+      "-#{config['log_selection']['try_count']}"
+  end
 end
 
 # retrieves Buildlogs using webrequests to the Travis API or the amazon servers
@@ -47,17 +56,23 @@ class TravisRequester
     repo = Travis::Repository.find(repo_slug)
     categorized_builds = {}
     build_count = 0
+    tried_count = 0
 
     repo.each_build do |build|
       if categorized_builds[build.state].nil?
         categorized_builds[build.state] = []
-        puts build.state
+        puts "Found new state #{build.state}"
       end
       if categorized_builds[build.state].length < Config.config['log_selection']['log_count_per_state']
         categorized_builds[build.state] << build
         build_count += 1
       end
       break if build_count >= Config.config['log_selection']['total_log_count']
+
+      tried_count += 1
+      break if tried_count >= Config.config['log_selection']['try_count']
+
+      puts "tried #{tried_count}" if (tried_count % 20).zero?
     end
 
     categorized_builds
@@ -115,12 +130,14 @@ class LogCollector
 
   # collect popular repos for popular languages on github
   def self.repos_to_analyze
-    result_file = File.open('repos-to-analyze.txt', 'w')
+    puts 'Collect repos to analyze'
+    puts ''
+    result_file = File.open("repos-to-analyze#{Config.identifier}.txt", 'w')
     active_repos = {}
     languages = GHTorrentParser.popular_languages(Config.config['repo_selection']['languages'])
     languages.each do |lang_result|
       lang = lang_result[:language]
-      puts "Current Language: #{lang}"
+      puts "Language: #{lang}"
       result_file.puts(lang)
 
       active_repos[lang] = active_repos(lang)
@@ -130,8 +147,6 @@ class LogCollector
       puts ''
     end
 
-    puts active_repos
-    puts "language count: #{active_repos.keys.length}"
     # puts "count for travis enabled repos: #{active_repos.transform_values { |_, slugs| slugs.length }}"
     result_file.close
[…]

### 2019-06-18 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs

@@ -1,5 +1,6 @@
 ﻿using System;
 using System.Collections.Generic;
+using System.Diagnostics;
 using System.IO;
 using System.Linq;
 using System.Threading.Tasks;
@@ -101,7 +102,13 @@ namespace pbeextractionbuildlogs
 		public override string Analyze(string inputPath)
 		{
 			var inputRegion = AnalysisUtil.RegionFromFile(inputPath);
+
+			Console.WriteLine("Starting to learn program");
+			Stopwatch learningStopwatch = Stopwatch.StartNew();
 			RegionProgram topRankedProgram = session.Learn();
+			learningStopwatch.Stop();
+			Console.WriteLine("Learning took " + learningStopwatch.Elapsed);
+
 			if (topRankedProgram == null)
 			{
 				Console.WriteLine("no program found");
@@ -110,7 +117,13 @@ namespace pbeextractionbuildlogs
 			Console.WriteLine("Learned Program:");
 			Console.WriteLine(topRankedProgram);
 			Console.WriteLine();
+
+			Console.WriteLine("Starting to apply program");
+			Stopwatch applyingStopwatch = Stopwatch.StartNew();
 			StringRegion output = topRankedProgram.Run(inputRegion);
+			applyingStopwatch.Stop();
+			Console.WriteLine("Applying took " + applyingStopwatch.Elapsed);
+
 			if (output == null)
 			{
 				return "no extraction found for this input";

### 2019-06-24 paper/paper.tex
small improvements: ruby tool output & end after number of trys no buildlogs with rare states, timing of learning in c# tool, black headings in paper draft, worklog update 17.6.
output of c# tool in explanation file, try docs folder for publishing, annibales feedback bullet points into paper

@@
 \section{Introduction}
-\secfunc{why? what? research questions? purpose? hypothesis? wide $\rightarrow$ narrow}
+\secfunc{why? what? research questions? purpose? hypothesis? wide $\rightarrow$ narrow
+
+problem, done in literature, why not eough? our approach
+}
 
 \review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.
-During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to recover the relevant information from between many uninteresting other lines.
+
+\plan{why are logs so difficult: mention heterogenous, semi-structured (paper reference for that?), big data (refercene paper about log sizes), in distributed systems probably distributed (really also for buildlog?)
+
+to combat that useres write tools to <extract / rerieve superbegriff> information from buildlogs.
+
+one possibility IR: classfy specifict part of program as similar to others (list IR technique) to see whether it is correclated to a failure.
+but not as good: not a real summarization technique, more what is similar to the last few times it faied.
+
+way to extract fine grained information: regular expressions which have to be written manually
+
+MAYBE IN THE other paragraph. here only half fitting?
+}
+
+During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to retrieve the relevant information from between many uninteresting other lines.
 
@@
 Usually such functionality is realized by tools that employ handcrafted regular expressions to find the desired text parts within the build log.
-However, creating these regular expressions is tedious and mentally complicated task, especially when they have to be maintained some months in the future \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
+However, creating these regular expressions is tedious, mentally complicated and usually error-prone task.
+Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
 Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.
@@
 
-Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at google.
+Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google.
 In addition most failures are resolved within two builds.
@@
 \draft{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
-Usually this is done by removing irrelevant terms and stop words, stemming and weighting the remaining words before comparing the similar of those weights against other text parts.~\cite{panichella2016parameterizing} For our use case this could be applied by slicing the build logs into lines or small sections.
+Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
+On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other.~\cite{panichella2016parameterizing} For our use case this could be applied by slicing the build logs into lines or small sections.
 Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
-
-In our work we focus on a more precise form of information extraction where we try to obtain a specific detail from a build log instead of retrieving the general idea of a document part.}
+Instead of recieving a paragraph which is similar to a givien query, our works focus more on obtaining specific pieces of texts through regular expressions.
 
@@
 
-\subsubsection{Design}
+\subsubsection{Design} ...
 \bp{
@@
 
-\subsubsection{Execution}
+\subsubsection{Execution} ...
 \bp{
@@
 
-\subsubsection{Capabilities}
+\subsubsection{Capabilities} ...
 
@@
 
-\subsubsection{Limitations}
+\subsubsection{Limitations} ...
 
@@
 \subsubsection{Extraction Accuracy}
+...
 
@@
 \subsubsection{Compare to Traditional Methods}
-\paragraph{TravisTorrent}
+\paragraph{TravisTorrent} ...
 \bp{Beller et al.
@@
 
-\paragraph{Manual Regex Construction}
+\paragraph{Manual Regex Construction} ...
 \plan{
@@
 
-\paragraph{IR paragraph stuff}
+\paragraph{IR paragraph stuff} ...
 \plan{
@@
 
-\paragraph{Keyword search}
+\paragraph{Keyword search} ...
 \plan{

### 2019-06-25 paper/paper.tex
fix paper typos & compilation errors

@@
 
-\plan{why are logs so difficult: mention heterogenous, semi-structured (paper reference for that?), big data (refercene paper about log sizes), in distributed systems probably distributed (really also for buildlog?)
+\plan{why are logs so difficult: mention heterogeneous, semi-structured (paper reference for that?), big data (reference paper about log sizes), in distributed systems probably distributed (really also for build log?)
 
-to combat that useres write tools to <extract / rerieve superbegriff> information from buildlogs.
+to combat that users write tools to <extract / retrieve superbegriff> information from build logs.
 
-one possibility IR: classfy specifict part of program as similar to others (list IR technique) to see whether it is correclated to a failure.
-but not as good: not a real summarization technique, more what is similar to the last few times it faied.
+one possibility IR: classify specific part of program as similar to others (list IR technique) to see whether it is correlated to a failure.
+but not as good: not a real summarization technique, more what is similar to the last few times it failed.
 
@@
 
-MAYBE IN THE other paragraph. here only half fitting?
+\todo{maybe other paragraph. here only half fitting?}
 }
@@
 
-\draft{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
+\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
 Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
@@
 Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
-Instead of recieving a paragraph which is similar to a givien query, our works focus more on obtaining specific pieces of texts through regular expressions.
+Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}
 

### 2019-07-07 paper/paper.tex
initial corrections from moritz second review

@@
 
-One way to support them would be to extract the desired information and present it in a structured way.
-Usually such functionality is realized by tools that employ handcrafted regular expressions to find the desired text parts within the build log.
+A way to support them would be to extract the desired information and present it in a structured way.
+One approach to realize such functionality are tools that employ handcrafted regular expressions to find the desired text parts within the build log.
 However, creating these regular expressions is tedious, mentally complicated and usually error-prone task.
-Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
+Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers.
 Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.
@@
 \review{
-The software engineering research community started to look into build logs as continuous integration becomes a vital part of a modern software engineering process.
-Researchers have analyzed industrial and open source logs for failure reasons and their impact on development.
-
+Various researchers have analyzed industrial and open source logs for failure reasons and their impact on development.
 Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google.
@@
 \review{
-Vassallo et al.~\cite{vassallo2018un-break} also made it their task to shorten the time it takes developers to understand build logs.
-They summarize relevant information in Java/maven build logs and augment them with links to related stack overflow posts.
+Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs.
+They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts.
 They observed that highlighting the locality and context of an issue is helpful to programmers.
@@
 Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
-Further they employ information retrieval techniques to identify the lines most likely hinting at the cause of the error.
+They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the error.
 In contrast to that, our tool ALBE extracts specific parts of the build logs.
@@
 Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
-On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other.~\cite{panichella2016parameterizing} For our use case this could be applied by slicing the build logs into lines or small sections.
+On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
+For our use case, this could be applied by slicing the build logs into lines or small sections.
 Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
@@
 
-We are applying their functionality to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information extraction.
+We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information extraction.
 }

### 2019-07-07 data-collection/collect-travis-logs.rb

@@ -190,7 +190,7 @@ class LogCollector
   # find a job that has the given state, return the job_id
   def self.identify_job_with_state(build, state)
     build.jobs.each do |job|
-      return job.id if job.state == state
+      return job.id if job.state == state..
     end
   end
 

### 2019-07-07 pbe-extraction-buildlogs/pbe-extraction-buildlogs/DataClasses.cs

@@ -11,8 +11,38 @@ namespace pbeextractionbuildlogs
 		public OutputType Output { get; set; }
 		public OutputType DesiredOutput { get; set; }
 		public bool Successful { get; set; }
+
+		[XmlIgnore]
 		public TimeSpan LearningDuration { get; set; }
+
+		[XmlElement("LearningDuration")]
+		public long LearningDurationSubstitute
+		{
+			get
+			{
+				return LearningDuration.Ticks;
+			}
+			set
+			{
+				LearningDuration = TimeSpan.FromTicks(value);
+			}
+		}
+
+		[XmlIgnore]
 		public TimeSpan ApplicationDuration { get; set; }
+
+		[XmlElement("ApplicationDuration")]
+		public long ApplicationDurationSubstitute
+		{
+			get
+			{
+				return ApplicationDuration.Ticks;
+			}
+			set
+			{
+				ApplicationDuration = TimeSpan.FromTicks(value);
+			}
+		}
 
 		/// <summary>
 		/// used for representing results of analyzed folders

### 2019-07-07 evaluation/Evaluation.Rmd
add missing logfiles, add evaluation plotting code

---
title: "Evaluation of Experiment Data"
output: html_notebook
---
# Evaluating our experiment data

## Preparing the data

```{r}
# Load the packages required to read XML files.
library("XML")
library("methods")
library("graphics")

setwd("/Users/Laci/Documents/Delft/master-thesis/pbe-extraction-buildlogs/results")

# Convert the input xml file to a data frame.
oldw <- getOption("warn")
options(warn = -1)

xml <- xmlTreeParse(file = "android-failure-with-dependencies_ManualSelection.xml")

nanosecsToTime <- function(ticks=numeric){
  sec <- ticks / 1e7
  return(as.POSIXct(sec, origin="1970-01-01", tz="UTC"))
}

data <- data.frame(ExampleCount = numeric(), TestOutput = character(), DesiredTestOutput = character(), Accuracy = numeric(), Successful = logical(), LearningDuration = as.POSIXct(character()), ApplicationDuration = as.POSIXct(character()), stringsAsFactors=FALSE)
#print(str(data))
#str(data)
#results <- xmlRoot(xml)#[['Results']]
results <- xml[['doc']]$children$EvaluationResultOfString[['Results']]
#print(results)
for (i in seq_along(1:length(results))) {
  item <- results[[i]]
  exampleCount <- length(item[['key']][[1]][['Examples']])
  test <- item[['value']][[1]][[1]]
  testOutput <- xmlValue(test[['Output']][[1]])
  desiredTestOutput <-  xmlValue(test[['DesiredOutput']][[1]])
  accuracy <- 3 # TODO
  successful <-  as.logical(xmlValue(test[['Successful']][[1]]))
  learningDuration <-  nanosecsToTime(as.numeric(xmlValue(test[['LearningDuration']][[1]])))
  #print(as.numeric(xmlValue(test[['ApplicationDuration']][[1]])))
  applicationDuration <-  nanosecsToTime(as.numeric(xmlValue(test[['ApplicationDuration']][[1]])))
  #rs <- getNodeSet(xml, '//Results/item')
  #print(typeof(sapply(rs, function(x) x[['key']][[1]][['Examples']])[[1]]))#[[0]][['Examples']])

  data = rbind(data, data.frame(ExampleCount=exampleCount, TestOutput=testOutput, DesiredTestOutput=desiredTestOutput, Accuracy=accuracy, Successful=successful, LearningDuration=learningDuration, ApplicationDuration=applicationDuration, stringsAsFactors=FALSE))
}
#print(results_set)
print(data)
  options(warn = oldw)
```

## Calculating Accuracy
```{r}
library("stringdist")

escapeStringAsNotRegex <- function(x=character()){
  return(gsub("([.|()\\^{}+$*?]|\\[|\\])", "\\\\\\1", x))
}

# print(data$TestOutput)
# print('')
# print(data$DesiredTestOutput)
for (row in 1:nrow(data)) {
  testOutput <- data[row, "TestOutput"]
  desiredTestOutput <-data[row, "DesiredTestOutput"]
  successful <- grepl(escapeStringAsNotRegex(testOutput), desiredTestOutput)
  data[row, "Successful"] <- as.logical(successful)
  # print(nchar(testOutput))
  # print(nchar(desiredTestOutput))
  # print(testOutput)
  # print(desiredTestOutput)
  accuracy <- nchar(testOutput)/nchar(desiredTestOutput)
  accuracy2 <- stringsim(testOutput, desiredTestOutput)
  print(accuracy)
  print(accuracy2)
  data[row, "Accuracy"] <- accuracy
}
print(data)
```

## Plotting the data
```{r}
plot_data <- str(data[c("ExampleCount", "Accuracy", "LearningDuration", "ApplicationDuration")])
print(str(plot_data))
plot(plot_data)
```

### 2019-07-08 evaluation/Evaluation.Rmd
learned program saved in evaluation results, plotting results, worklog update 8.7.

@@
 ---
-# Evaluating our experiment data
+# Fun with Data and Plots
 
-## Preparing the data
+## Preparing the data & Calculating Accuracy
 
@@
 library("graphics")
+library("stringdist")
 
-setwd("/Users/Laci/Documents/Delft/master-thesis/pbe-extraction-buildlogs/results")
-
-# Convert the input xml file to a data frame.
-oldw <- getOption("warn")
-options(warn = -1)
-
-xml <- xmlTreeParse(file = "android-failure-with-dependencies_ManualSelection.xml")
+escapeStringAsNotRegex <- function(x=character()){
+  return(gsub("([.|()\\^{}+$*?]|\\[|\\])", "\\\\\\1", x))
+}
 
@@
 
-data <- data.frame(ExampleCount = numeric(), TestOutput = character(), DesiredTestOutput = character(), Accuracy = numeric(), Successful = logical(), LearningDuration = as.POSIXct(character()), ApplicationDuration = as.POSIXct(character()), stringsAsFactors=FALSE)
+# Convert the input xml file to a data frame.
+getDataFrameForResultsFile <- function(path){
+  oldw <- getOption("warn")
+  options(warn = -1)
+
+  setwd("/Users/Laci/Documents/Delft/master-thesis/pbe-extraction-buildlogs/results")
+  xml <- xmlTreeParse(file = path)
+
+  data <- data.frame(ExampleCount = numeric(), LearnedProgram = character(), TestOutput = character(), DesiredTestOutput = character(), Accuracy = numeric(), Successful = logical(), LearningDuration = as.POSIXct(character()), ApplicationDuration = as.POSIXct(character()), stringsAsFactors=FALSE)
   #print(str(data))
@@
     test <- item[['value']][[1]][[1]]
+    learnedProgram <- xmlValue(test[['LearnedProgram']][[1]])
     testOutput <- xmlValue(test[['Output']][[1]])
@@
 
-  data = rbind(data, data.frame(ExampleCount=exampleCount, TestOutput=testOutput, DesiredTestOutput=desiredTestOutput, Accuracy=accuracy, Successful=successful, LearningDuration=learningDuration, ApplicationDuration=applicationDuration, stringsAsFactors=FALSE))
+    data = rbind(data, data.frame(ExampleCount=exampleCount, LearnedProgram = learnedProgram, TestOutput=testOutput, DesiredTestOutput=desiredTestOutput, Accuracy=accuracy, Successful=successful, LearningDuration=learningDuration, ApplicationDuration=applicationDuration, stringsAsFactors=FALSE))
   }
   #print(results_set)
-print(data)
   options(warn = oldw)
-```
-
-## Calculating Accuracy
-```{r}
-library("stringdist")
-
-escapeStringAsNotRegex <- function(x=character()){
-  return(gsub("([.|()\\^{}+$*?]|\\[|\\])", "\\\\\\1", x))
-}
 
@@
   }
-print(data)
+  return(data)
+}
 ```
@@
 ```{r}
-plot_data <- str(data[c("ExampleCount", "Accuracy", "LearningDuration", "ApplicationDuration")])
-print(str(plot_data))
-plot(plot_data)
+library("ggplot2")
+
+#data <- getDataFrameForResultsFile("android-failure-with-dependencies_ManualSelection.xml")
+data <- getDataFrameForResultsFile("android-failure-with-dependencies_ManualSelection.xml")
+
+plot_data <- data[c("ExampleCount", "Accuracy", "LearningDuration", "ApplicationDuration")]
+print(plot_data)
+
+#plot(plot_data)
+p <- ggplot(data = plot_data, aes(x = plot_data$ExampleCount, y = plot_data$ApplicationDuration)) + 
+  geom_point(aes(col=plot_data$LearningDuration, size=plot_data$Accuracy)) + 
+  labs(subtitle="", 
+       y="application duration", 
+       x="example count", 
+       title="Scatterplot", 
+       caption = "android-failure manual example selection") +
+  scale_y_datetime(breaks = seq(from = min(data$ApplicationDuration), to = max(data$ApplicationDuration), by = 0.04), date_labels = "%OS3 sec")
+  # scale_x_datetime(date_labels = "%M min")
+plot(p)
 ```

### 2019-07-08 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs

@@ -108,6 +108,7 @@ namespace pbeextractionbuildlogs
 			Console.WriteLine("Learned Program:");
 			Console.WriteLine(topRankedProgram);
 			Console.WriteLine();
+			result.LearnedProgram = topRankedProgram.ToString();
 
 			Console.WriteLine("Starting to apply program");
 			Stopwatch applyingStopwatch = Stopwatch.StartNew();

### 2019-07-08 pbe-extraction-buildlogs/pbe-extraction-buildlogs/DataClasses.cs

@@ -8,6 +8,7 @@ namespace pbeextractionbuildlogs
 	{
 		public string Path { get; set; }
 		public string ProgramName { get; set; }
+		public string LearnedProgram { get; set; }
 		public OutputType Output { get; set; }
 		public OutputType DesiredOutput { get; set; }
 		public bool Successful { get; set; }

### 2019-07-08 pbe-extraction-buildlogs/pbe-extraction-buildlogs/MainClass.cs

@@ -66,15 +66,22 @@ namespace pbeextractionbuildlogs
 
 		private static void RunEvaluation(EvaluateOptions opts)
 		{
-			ExampleSelection exampleSelection = new ManualSelection();
-			if (opts.ExampleSelection == "random")
+			ExampleSelection exampleSelection;
+			switch (opts.ExampleSelection)
 			{
-				exampleSelection = new RandomSelection();
+				case "random":
+					exampleSelection = new RandomSelection();
+					break;
+				case "chronological":
+					exampleSelection = new ChronologicalSelection();
+					break;
+				case "manual":
+					exampleSelection = new ManualSelection();
+					break;
+				default:
+					throw new ArgumentException("Selection mode should be either 'random', 'chronological' or 'manual'");
 			}
-			else if (opts.ExampleSelection == "chronological")
-			{
-				exampleSelection = new ChronologicalSelection();
-			}
+
 			exampleSelection.IncludeAllInputs = opts.IncludeAllInputs;
 			exampleSelection.TestCount = opts.TestCount;
 			exampleSelection.LearningStepCount = opts.LearningStepCount;

### 2019-07-16 evaluation/Evaluation.Rmd
first kind of working IR extraction

@@
 
-escapeStringAsNotRegex <- function(x=character()){
-  return(gsub("([.|()\\^{}+$*?]|\\[|\\])", "\\\\\\1", x))
-}
+main_path <<- "/Users/Laci/Documents/Delft/master-thesis"
 
-nanosecsToTime <- function(ticks=numeric){
-  sec <- ticks / 1e7
-  return(as.POSIXct(sec, origin="1970-01-01", tz="UTC"))
-}
+## load other modules
+source(paste(main_path, "/evaluation/utilities.R", sep = ""))
 
@@
 #data <- getDataFrameForResultsFile("android-failure-with-dependencies_ManualSelection.xml")
-data <- getDataFrameForResultsFile("android-failure-with-dependencies_ManualSelection.xml")
+data <- getDataFrameForResultsFile("android-failure-with-dependencies_ChronologicalSelection.xml")
 
@@
        title="Scatterplot", 
-       caption = "android-failure manual example selection") +
+       caption = "android-failure chronological example selection") +
   scale_y_datetime(breaks = seq(from = min(data$ApplicationDuration), to = max(data$ApplicationDuration), by = 0.04), date_labels = "%OS3 sec")
   # scale_x_datetime(date_labels = "%M min")
+ggsave("android-chronological.png", p) ## TODO make work
 plot(p)

### 2019-07-16 paper/paper.tex
first kind of working IR extraction

@@
 
-problem, done in literature, why not eough? our approach
+problem, done in literature, why not enough? our approach
 }
 
-\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.
+\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the success build state is restored improves the overall productivity of developers.
 
@@
 
-During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to retrieve the relevant information from between many uninteresting other lines.
+During this assignment an engineer spends a lot of their time \todo{or: find percentage to cite} reading very long and verbose build logs, trying to retrieve the relevant information from between many uninteresting other lines.
+\todo{add anecdotal evidence, watchdog paper?}
 
@@
 Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers.
-Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.
+Our goal is to evaluate an alternative way of taking this burden of programmers.
+By simply giving examples of the desired extractions they should be able to define extraction programs.
 
-We implemented \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples.
-After collecting a diverse set of build logs from Travis CI we designed a meta-model of the contained information.
-Our evaluation of ALBE showed that it is able to define extractions for various desired informations, that it shortens development time in comparison to manual regular expression construction and ...
+We implement \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples.
+After collecting a diverse set of build logs from Travis CI we design a meta-model of the contained information.
+We evaluate ALBE on logs from selected GitHub repositories on the accuracy of extraction for a varying number and selection of in-output-examples.
+Furthermore we compare the tool to classical information retrieval and plain keyword search.
+Our evaluation of ALBE shows that it is able to define extractions for various desired informations, that it shortens development time in comparison to manual regular expression construction and ...
 }
@@
 \section{Related Work}
+
+\todo{More glue \& sentences that give an overview over the next paragraph}
+
+\subsection{Bulidlogs Analysis Tools}
+
+\review{
+Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs.
+They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts.
+They observed that highlighting the locality and context of an issue is helpful to programmers.
+We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.
+
+Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
+They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the error.
+In contrast to that, our tool ALBE extracts specific parts of the build logs.
+As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
+}
 
@@
 Our work could support their research by easing the parser development and enable them to cover more languages and build tools easier.
-}
-
-\subsection{Tools}
-
-\review{
-Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs.
-They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts.
-They observed that highlighting the locality and context of an issue is helpful to programmers.
-We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.
-
-Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
-They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the error.
-In contrast to that, our tool ALBE extracts specific parts of the build logs.
-As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
 }

### 2019-07-16 evaluation/ComparisonIR.R

@@ -11,53 +11,70 @@ library(stopwords)
 library(NMOF)
 library(xtable)
 
-main_path <<- "/Users/Laci/Documents/Delft/master-thesis"
 
-## 1. load utility functions 
-source(paste(main_path, "/evaluation/utilities.R", sep=""))
+
 # source(paste(main_path, "/metaheuristics.R", sep=""))
 
-## parse the analysis programs xml files
-setwd(paste(main_path, "/pbe-extraction-buildlogs/ressources/analysis-programs", sep=""))
+# print(str(examples))
 
-path <- 'android-failure-with-dependencies.xml'
-xml <- xmlTreeParse(file = path)
+######## tdm for log file data #######
+output_path <-
+  paste(main_path, "/evaluation/split_samples", sep = "")
 
-examples <- data.frame(input_path = character(), output = character(), stringsAsFactors=FALSE)
-exampleset <- xml[['doc']]$children$AnalysisProgramOfRegionAnalysisSessionString[['LearningData']][['Examples']]
-sample_path <- paste(main_path, "/pbe-extraction-buildlogs/samples/", sep="")
-for (i in seq_along(1:length(exampleset))){
-  example <- exampleset[[i]]
-  examples <- rbind(examples, data.frame(input_path=paste(sample_path, xmlValue(example[['InputPath']][[1]]), sep=''), output=xmlValue(example[['Output']][[1]])))
-}
-print(str(examples))
-
-## 2. Set path to the dataset
-# Todo: possibly change this -> we need (line based?) splitting of the files from the xml inputs
-system <- "datasets/LANG"
-
-output_path <- paste(main_path, "/evaluation/split_samples", sep="");
-
-## 3. read the oracle
-# Todo: so construct which values we acutally have to learn from -> which lines are actually in the labeled desired results
-# duplicate_graph <- paste(system, "/bugrepo/duplicates.json", sep="");
-# duplicate_graph <- oracle2graph(duplicate_graph)
-# plot(duplicate_graph)
-
-## 4. Set the path to the output directory
-#file_output <- "results.csv"
+## 5. split the main file in separate paragraphs & files
+# 5.1 Split text in sub-files
 files <- examples$input_path
+split_files(files, output_path)
 
-## 5. split the main file (cataining all reports) in separate files (one for each report)
[…]

### 2019-07-16 evaluation/example-set.R

@@ -1,0 +1,36 @@
+## loading the exampleset data
+
+## parse the analysis programs xml files
+get_exampleset <- function(path) {
+  setwd(
+    paste(
+      main_path,
+      "/pbe-extraction-buildlogs/ressources/analysis-programs",
+      sep = ""
+    )
+  )
+  
+  xml <- xmlTreeParse(file = path)
+  
+  examples <-
+    data.frame(
+      input_path = character(),
+      output = character(),
+      stringsAsFactors = FALSE
+    )
+  exampleset <-
+    xml[['doc']]$children$AnalysisProgramOfRegionAnalysisSessionString[['LearningData']][['Examples']]
+  for (i in seq_along(1:length(exampleset))) {
+    example <- exampleset[[i]]
+    examples <-
+      rbind(
+        examples,
+        data.frame(
+          input_path = xmlValue(example[['InputPath']][[1]]),
+          output = xmlValue(example[['Output']][[1]]),
+          stringsAsFactors = FALSE
+        )
+      )
+  }
+  return(examples)
+}

### 2019-07-16 evaluation/fitness_functions.R

@@ -1,70 +1,0 @@
-#fitness function
-fitness_LDA<-function(x=c()){
-  numero_topic<-round(x[1]) #x[1] = number of topics k
-  iteration<-round(x[2])    #x[2] =  number of gibbs iteration
-  pAlpha<-x[3]              #x[3] = Alpha
-  pDelta<-x[4]              #x[4] = Beta
-
-  #apply LDA to the term-by-document matrix
-  ldm <- LDA(tdm, method="Gibbs", control = list(alpha=pAlpha, delta=pDelta, iter=iteration, seed=5, nstart=1), k = numero_topic)  # k = num of topics
-  pldm <- posterior(ldm)
-  names(pldm)
-
-  #compute the topic-by-term matrix
-  names(tdm$dimnames)
-  docs<-tdm$dimnames$Docs
-  topics<-names(terms(ldm))
-  matrix<-pldm$topics
-  dimnames(matrix)<-list(docs,topics)
-
-  #compute the distance between documents in the topics space
-  distances <- as.matrix(dist(matrix, method = "euclidean", diag = T, upper = T))
-
-  #computing number of clusters
-  clustering<-matrix("",length(rownames(matrix)),1)
-  for (i in 1:length(rownames(matrix))) {
-    flag<-(matrix[i,]==max(matrix[i,]))# each documents belongs to the cluster with the higher probability
-    flag<-which(flag==TRUE)
-    topics <- sort(flag)
-    clustering[i,1]<-paste(topics, collapse = '_')
-  }
-  rownames(clustering)<-rownames(matrix)
-
-  clusters<-unique(clustering)
-  count <- 1
-  for (clust in clusters){
-    clustering[clustering[,1] == clust,1] <- count
-    count <- count+1
-  }
-   cluster_objects<-list();
-   cluster_objects$clustering <- as.numeric(clustering)
-
-  cohesion <- matrix(nrow = length(rownames(distances)), ncol = 1)
-  for (i in 1:length(rownames(distances))){
-    cohesion[i,1] <- max(distances[clustering[,1] == clustering[i,1],i])
-  }
-
-  separation <- matrix(nrow = length(rownames(distances)), ncol = 1)
-  for (i in 1:length(rownames(distances))){
-    separation[i,1] <- min(distances[clustering[,1] != clustering[i,1],i])
-  }
-
-  sil <- matrix(nrow = length(rownames(distances)), ncol = 1)
[…]

### 2019-07-16 evaluation/information-retrieval.R

@@ -1,0 +1,77 @@
+library(dplyr)
+
+
+main_path <<- "/Users/Laci/Documents/Delft/master-thesis"
+sample_path <<-
+  paste(main_path, "/pbe-extraction-buildlogs/samples", sep = "")
+
+## load other modules
+source(paste(main_path, "/evaluation/utilities.R", sep = ""))
+source(paste(main_path, "/evaluation/example-set.R", sep = ""))
+
+## load example set
+path <- 'android-failure.xml'
+#path <- 'travis-worker-short.xml'
+examples <- get_exampleset(path)
+
+## select on which examples to train / test
+train_examples <- examples[c(1, 3:4), ]
+test_examples <- examples[c(2:2), ]
+
+# we collect all line which contain (parts)
+# of the output the extraction should yield
+# (defined in the training examples)
+
+train_lines <- get_ided_line_samples(train_examples)
+test_lines <- get_ided_line_samples(test_examples, only_output_lines = FALSE)
+
+total_lines <- rbind(train_lines, test_lines)
+
+prep_fun <- identity
+tok_fun <- word_tokenizer
+
+it_total <- itoken(total_lines$lines, preprocessor = prep_fun, tokenizer = tok_fun, ids = total_lines$id)
+it_train <- itoken(train_lines$lines, preprocessor = prep_fun, tokenizer = tok_fun, ids = train_lines$id)
+it_test <- itoken(test_lines$lines, preprocessor = prep_fun, tokenizer = tok_fun, ids = test_lines$id)
+
+
+## prepare vocabulary
+# todo n-grams?
+vocab <- create_vocabulary(it_total)
+pruned_vocab <- prune_vocabulary(vocab, term_count_min = 2, doc_proportion_max = 0.7, doc_proportion_min = 0)
+vectorizer <- vocab_vectorizer(pruned_vocab)
+
+dtm_train <- create_dtm(it_train, vocab)
+dtm_test <- create_dtm(it_test, vocab)
+
+
+## tf-idf transformation
+tfidf = TfIdf$new()
+# fit model to train data and transform train data with fitted model
+dtm_train_tfidf = fit_transform(dtm_train, tfidf)
+# tfidf modified by fit_transform() call!
+# apply pre-trained tf-idf transformation to test data
+dtm_test_tfidf  = create_dtm(it_test, vectorizer) %>% 
+  transform(tfidf)
+
[…]

### 2019-07-16 evaluation/utilities.R

@@ -1,99 +1,137 @@
-library(igraph)
 library(stringr)
-library(jsonlite)
+library(stringi)
+library(wordcloud)
+library(NLP)
 
-split_document <- function(files, output_path){
-  for (file in files){
-    print(file)
-    file_content <- read.delim(paste(input_path, file, sep=""))
-    print(file_content)
+## split the given text into
+## lines
+## and save to separate files in output_path, identified by the file_name_base
+split_text <- function(text, file_name_base,  output_path) {
+  split <- stri_split_lines(text, omit_empty = TRUE)
+  setwd(output_path)
+  filename <-
+    gsub('.', '', gsub('/', '', file_name_base, fixed = TRUE), fixed = TRUE)
+  for (i in seq_along(split[[1]])) {
+    writeLines(split[[1]][[i]], paste(filename, i, ".txt", sep = ''))
+  }
+}
+
+get_lines_containing_output <-
+  function(file_name, base_path, output, only_output_lines = TRUE) {
+    lines <- read_build_log_from_file(file_name, base_path)
+
+    if (only_output_lines) {
+      lines_with_output_regex <- paste("\n[^\n]*", escapeStringAsNotRegex(output), "[^\n]*\n", sep = "")
+      output_postion <- str_locate(lines, regex(lines_with_output_regex))
+
+      lines <- substr(lines, output_postion[[1]], output_postion[[2]])
+    }
+
+    split <- stri_split_lines(lines, omit_empty = TRUE)
+    return(split)
+  }
+
+## gets all the lines for a sample with ids.
+## returns all lines of the logfile if only_output_lines = FALSE
+get_ided_line_samples <- function(examples, only_output_lines = TRUE) {
+  train_lines <- data.frame(id = character(), lines = character(), stringsAsFactors = FALSE)
+
+  for (example_row in 1:nrow(examples)) {
+    i_p <- examples[example_row, "input_path"]
+    o <- examples[example_row, "output"]
+    output_lines <- get_lines_containing_output(i_p, sample_path, o, only_output_lines = only_output_lines)
+    
+    lines_frame <- data.frame(lines = output_lines, stringsAsFactors = FALSE)
+    colnames(lines_frame)[1] <- "lines"
+    ids <- paste(collapse_input_path(i_p), rownames(lines_frame), sep = ":")
+    lines_frame <- cbind(id=ids, lines_frame, stringsAsFactors = FALSE)
+
+    train_lines <- rbind(train_lines, lines_frame)
+  }
+
[…]

### 2019-07-16 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs

@@ -28,7 +28,7 @@ namespace pbeextractionbuildlogs
 			{
 				return fileCache[path];
 			}
-			string text = File.ReadAllText(path).Replace("\r\n", "\n").Replace("\r", "\n").Replace("\n\r", "\n").Replace(((char)0x1b).ToString(), "");
+			string text = File.ReadAllText(path).Replace("\r\n", "\n").Replace("\n\r", "\n").Replace("\r", "\n").Replace(((char)0x1b).ToString(), "");
 			StringRegion region = RegionSession.CreateStringRegion(text);
 			fileCache[path] = region;
 			return region;

### 2019-09-30 pbe-extraction-buildlogs/pbe-extraction-buildlogs/Config.cs
add keywords and categories to C# results, save c# results to correct location & update dockerfile to do the same

@@ -8,7 +8,7 @@ namespace pbeextractionbuildlogs
 		public static string PROGRAM_DATA_DIRECTORY = ROOT_DIRECTORY +
 			"tool/example-sets/";
 		public static string SAMPLE_DIRECTORY = ROOT_DIRECTORY + "tool/samples/";
-		public static string RESULT_DIRECTORY = ROOT_DIRECTORY + "tool/results/pbe";
+		public static string RESULT_DIRECTORY = ROOT_DIRECTORY + "evaluation/results/pbe/";
 
 		public static string LOG_KIND_FILE_PATH = ROOT_DIRECTORY + "pbe-extraction-buildlogs/ressources/log-kinds.txt";
 	}

### 2019-09-30 pbe-extraction-buildlogs/pbe-extraction-buildlogs/DataClasses.cs

@@ -12,6 +12,8 @@ namespace pbeextractionbuildlogs
 		public OutputType Output { get; set; }
 		public OutputType DesiredOutput { get; set; }
 		public bool Successful { get; set; }
+		public string AllKeywords { get; set; }
+		public string Categories { get; set; }
 
 		[XmlIgnore]
 		public TimeSpan LearningDuration { get; set; }
@@ -67,13 +69,23 @@ namespace pbeextractionbuildlogs
 		public bool IncludeAllInputs { get; set; }
 		public int TestCount { get; set; }
 		public int LearningStepCount { get; set; }
+		public abstract string Name { get; }
 	}
 
-	public class RandomSelection : ExampleSelection { }
+	public class RandomSelection : ExampleSelection
+	{
+		public override string Name => "random";
+	}
 
-	public class ChronologicalSelection : ExampleSelection { }
+	public class ChronologicalSelection : ExampleSelection
+	{
+		public override string Name => "chronological";
+	}
 
-	public class ManualSelection : ExampleSelection { }
+	public class ManualSelection : ExampleSelection
+	{
+		public override string Name => "manual";
+	}
 
 
 
@@ -81,6 +93,8 @@ namespace pbeextractionbuildlogs
 	{
 		public string InputPath;
 		public OutputType Output;
+		public string Keywords;
+		public string Category;
 
 		public ExampleData() { }
 

### 2019-09-30 pbe-extraction-buildlogs/pbe-extraction-buildlogs/MainClass.cs

@@ -181,7 +181,7 @@ namespace pbeextractionbuildlogs
 			Directory.CreateDirectory(
 				Config.RESULT_DIRECTORY.Remove(Config.RESULT_DIRECTORY.Length - 1));
 			var progSaveName = result.ProgramName.Replace("/", "@");
-			using (StreamWriter file = new StreamWriter(File.Create(Config.RESULT_DIRECTORY + progSaveName + "_" + result.ExampleSelection.GetType().Name + ".xml")))
+			using (StreamWriter file = new StreamWriter(File.Create(Config.RESULT_DIRECTORY + progSaveName + "-" + "pbe" + "-" + result.ExampleSelection.Name + "-" + result.ExampleSelection.LearningStepCount + "-" + result.ExampleSelection.TestCount + ".xml")))
 			{
 				serializer.Serialize(file, result);
 			}

### 2019-09-30 evaluation/evaluate-results.R
keyword evaluation

@@ -40,6 +40,9 @@ getDataFrameForPBEResultsFile <- function(path) {
       nanosecsToTime(as.numeric(xmlValue(test[["LearningDuration"]][[1]])))
     applicationDuration <-
       nanosecsToTime(as.numeric(xmlValue(test[["ApplicationDuration"]][[1]])))
+    allKeywords <- xmlValue(test[["AllKeywords"]][[1]])
+    searchKeywords <- select_keywords_to_search(allKeywords)
+    categories <- xmlValue(test[["Categories"]][[1]])
     
     data = rbind(
       data,
@@ -52,6 +55,9 @@ getDataFrameForPBEResultsFile <- function(path) {
         Successful = successful,
         LearningDuration = learningDuration,
         ApplicationDuration = applicationDuration,
+        SearchKeywords = searchKeywords,
+        AllKeywords = allKeywords,
+        Categories = categories,
         stringsAsFactors = FALSE
       )
     )
@@ -81,16 +87,9 @@ calculate_accuracy <- function(data) {
 
 save_evaluation_result <- function(result, program_name, technique, selection, learning_step_count, test_count) {
   result <- calculate_accuracy(result)
-  plot_data <-
-    result[c("ExampleCount",
-             "Accuracy",
-             "LearningDuration",
-             "ApplicationDuration")]
   setwd(paste0(main_path, "/evaluation/results/", technique))
   results_file_name <- evaluation_identification(technique, gsub("/", "@", program_name), selection, learning_step_count, test_count)
-  # ggsave(paste0(results_file_name, ".svg"), p)
 
-  # TODO handle keywords andd categories somehow
   write.csv(
     transform(result,
     LearningDuration = format(LearningDuration, "%M.%OS3"),

### 2019-09-30 evaluation/run-evaluation.rb

@@ -7,8 +7,8 @@ example_sets.each do |example_set|
 
   selection = "chronological"
   test_count = 1
-  learning_step_count = 3
-  technique = "ir"
+  learning_step_count = 1
+  technique = "pbe"
 
   run_eval = "ruby ../tool/run-extraction.rb -a evaluate -t #{technique} -e #{example_set} -s #{selection} -l #{learning_step_count} -c #{test_count} -v"
 

### 2019-09-30 r-extractions/example-set.R

@@ -35,16 +35,16 @@ get_exampleset <- function(program) {
     example <- exampleset[[i]]
     output <- xmlValue(example[["Output"]])
     keywords <- xmlValue(example[["Keywords"]])
-    if (keywords.endsWith(,))
+    if (endsWith(keywords, ",")) {
       keywords <- paste0(keywords, " ")
-    end
+    }
     examples <-
       rbind(
         examples,
         data.frame(
           input_path = xmlValue(example[["InputPath"]]),
           output = output,
-          keywords = xmlValue(example[["Keywords"]]),
+          keywords = keywords,
           category = xmlValue(example[["Category"]]),
           stringsAsFactors = FALSE
         )
@@ -55,11 +55,10 @@ get_exampleset <- function(program) {
 
 ## returns a string which is a concatenation of the categories of the given examples
 get_categories_chain <- function(examples) {
-  return(paste(examples$category, sep = "-"))
+  return(paste(examples$category, collapse = "-"))
 }
 
 ## returns the list of all keywords of the given examples (with possibly duplicates)
 get_keywords_chain <- function(examples) {
-  print(examples$keywords)
-  return(paste(examples$keywords, sep = ", "))
+  return(paste(examples$keywords, collapse = ", "))
 }

### 2019-09-30 r-extractions/keyword-search.R

@@ -5,7 +5,6 @@
 suppressPackageStartupMessages({
   library(optigrab)
   library(stringi)
-  library(plyr)
 })
 
 main_path <<- "/Users/Laci/Documents/Delft/master-thesis"
@@ -15,8 +14,9 @@ sample_path <<-
 ## load other modules
 source(paste(main_path, "/r-extractions/utilities.R", sep = ""))
 source(paste(main_path, "/r-extractions/example-set.R", sep = ""))
+source(paste(main_path, "/evaluation/evaluate-results.R", sep = ""))
 
-run_analysis <- function(file, keywords) {
+run_analysis <- function(file, keywords, context_width) {
   log <- read_build_log_from_file(file, sample_path)
   lines <- unlist(stri_split_lines(log, omit_empty = TRUE))
 
@@ -24,20 +24,38 @@ run_analysis <- function(file, keywords) {
   for (i in 1:length(keywords)) {
     filtered_lines <- filtered_lines | str_detect(lines, fixed(keywords[i]))
   }
-  # TODO context
-  return(join_extracted_lines(lines[filtered_lines]))
+  context_added_lines <- filtered_lines
+  if (context_width > 0) {
+    for (i in 1:length(filtered_lines)) {
+      if (filtered_lines[i]) {
+        for (j in 1:context_width) {
+          context_added_lines[i-j] = TRUE
+          context_added_lines[i+j] = TRUE
+        }
+      }
+    }
+  }
+  return(join_extracted_lines(lines[context_added_lines]))
 }
 
 run_keyword_search_step <- function(train_examples, test_examples, step_results) {
-  # TODO somehow consolidate keywords
-  # search for them in text and extract stuff around it
-  print(step_results[1, "AllKeywords"])
-  keywords_chain = strsplit(step_results[1, "AllKeywords"], ", ", fixed=TRUE)
-  print(keywords_chain)
-  kwdf = data.frame(words = keywords_chain)
-  print(kwdf)
-  print(count(kwdf))
-  print(step_results)
+  start_time_learning <- Sys.time()
+  keywords_chain <- strsplit(step_results[1, "AllKeywords"], ", ")[[1]]
+  selected <- select_keywords_to_search(keywords_chain)
+  step_results[1, "SearchKeywords"] <- paste(selected, collapse = ", ")
+  step_results[1, "LearnedProgram"] <- paste(selected, collapse = ", ")
+
+  end_time_learning <- Sys.time()
[…]

### 2019-09-30 r-extractions/utilities.R

@@ -232,10 +232,26 @@ run_evaluation <-
       step_results[1, "AllKeywords"] <- get_keywords_chain(train_examples)
       step_results[1, "Categories"] <- get_categories_chain(train_examples)
       
-      step_method(train_examples, test_examples, step_results)
+      step_results <- step_method(train_examples, test_examples, step_results)
       
       results <- rbind(results, step_results)
     }
     
     results <- save_evaluation_result(results, program, technique, selection, learning_step_count, test_count)
+    #print(results)
   }
+
+select_keywords_to_search <- function(all_keywords) {
+  filtered_keywords <- character()
+  for (kw in 1:length(all_keywords)) {
+    if (all_keywords[kw] != "") {
+      filtered_keywords <- c(filtered_keywords, all_keywords[kw])
+    }
+  }
+
+  keyword_freq <- as.data.frame(table(filtered_keywords), stringsAsFactors = FALSE)
+  print(keyword_freq)
+  max_kw <- max(keyword_freq$Freq)
+  selected <- keyword_freq[keyword_freq$Freq >= max_kw, ]$filtered_keywords
+  return(selected)
+}

### 2019-09-30 data-collection/dev-mail/devmail.rb
mail corrections from Taicos feedback

@@ -98,11 +98,12 @@ def send_mails
     mail_text = ''
     rows.each_with_index do |row, index|
       replacement = {
-        email: 'laci_noire@live.de', # row['email'].strip,
+        email: 'carolin.brandt@tum.de', # row['email'].strip,
         build_num: row['build_number'].strip,
         repo_name: row['repository_name'].strip,
         dev_name: row['dev_name'].strip,
-        commit_sha: row['commit_sha'].strip[0..7],
+        commit_sha_short: row['commit_sha'].strip[0..7],
+        commit_sha_long: row['commit_sha'],
         commit_date: Time.parse(row['commit_date'].strip).httpdate,
         extraction: row['output'].strip,
         repo_owner: row['repository_owner'].strip,
@@ -118,7 +119,7 @@ def send_mails
       mail_text += txt
     end
     #puts mail_text
-    smail('laci_noire@live.de', mail_text)
+    smail('carolin.brandt@tum.de', mail_text)
     break
   end
 end

### 2019-09-30 data-collection/dev-mail/devmail.rb
handle empty job ids

@@ -27,6 +27,9 @@ def fill_extraction_data(row)
   output = xml.at("//AnalysisProgramOfRegionAnalysisSessionString/LearningData/Examples/ExampleDataOfString[#{log_index}]/Output")
   row['output'] = output
 
+  jobs_url_job_id = row['job_id'] == 'job_id_not_found' ? 'builds/' + row['build_id'].strip : 'jobs/' + row['job_id'].strip
+  row['jobs_url_job_id'] = jobs_url_job_id
+
   row
 end
 
@@ -93,22 +96,24 @@ def send_mails
   puts mail_groups.keys.count
 
   mail_groups.each do |mail, rows|
-    next if mail == 'no_mail_found' || mail == 'no_user_found'
+    next if ['no_mail_found', 'no_user_found'].include?(mail)
 
     mail_text = ''
     rows.each_with_index do |row, index|
+      dev_name = row['dev_name'] == 'no_username_found' ? '' : row['dev_name'].strip
+      jobs_url_job_id = row['job_id'] == 'job_id_not_found' ? 'builds/' + row['build_id'].strip : 'jobs/' + row['job_id'].strip
       replacement = {
         email: 'carolin.brandt@tum.de', # row['email'].strip,
         build_num: row['build_number'].strip,
         repo_name: row['repository_name'].strip,
-        dev_name: row['dev_name'].strip,
+        dev_name: row['dev_name'] == dev_name,
         commit_sha_short: row['commit_sha'].strip[0..7],
         commit_sha_long: row['commit_sha'],
         commit_date: Time.parse(row['commit_date'].strip).httpdate,
         extraction: row['output'].strip,
         repo_owner: row['repository_owner'].strip,
         build_id: row['build_id'].strip,
-        job_id: row['job_id'].strip,
+        jobs_url_job_id: jobs_url_job_id,
         mail_count: rows.length
       }
       if index.zero?

### 2019-09-30 evaluation/convert-pbe-results-to-xml.R
write script to convert pbe results to same format as other extractions

@@ -1,0 +1,21 @@
+#!/usr/bin/env Rscript
+
+suppressPackageStartupMessages({
+  library(optigrab)
+})
+
+main_path <<- "/Users/Laci/Documents/Delft/master-thesis"
+
+## load other modules
+source(paste(main_path, "/evaluation/evaluate-results.R", sep = ""))
+
+file <- opt_get_verb()
+name_parts <- strsplit(file, "-", fixed = TRUE)[[1]]
+end <- length(name_parts)
+print(name_parts)
+print(end)
+
+data <-
+  getDataFrameForPBEResultsFile(file)
+
+result <- save_evaluation_result(data, paste(name_parts[1:(end - 4)], collapse = "-"), name_parts[[end - 3]], name_parts[[end - 2]], name_parts[[end - 1]], gsub(".xml", "", name_parts[[end]]))

### 2019-09-30 evaluation/evaluate-results.R

@@ -18,7 +18,7 @@ getDataFrameForPBEResultsFile <- function(path) {
   oldw <- getOption("warn")
   options(warn = -1)
   
-  setwd(paste(main_path, "/tool/results/pbe", sep = ""))
+  setwd(paste(main_path, "/evaluation/results/pbe", sep = ""))
   xml <- xmlTreeParse(file = path)
   
   data <- empty_results_data_frame()
@@ -87,6 +87,8 @@ calculate_accuracy <- function(data) {
 
 save_evaluation_result <- function(result, program_name, technique, selection, learning_step_count, test_count) {
   result <- calculate_accuracy(result)
+  print(technique)
+  message(paste0(main_path, "/evaluation/results/", technique))
   setwd(paste0(main_path, "/evaluation/results/", technique))
   results_file_name <- evaluation_identification(technique, gsub("/", "@", program_name), selection, learning_step_count, test_count)
 

### 2019-09-30 evaluation/plot-prose.R

@@ -1,11 +1,0 @@
-#!/usr/bin/env Rscript
-
-main_path <<- "/Users/Laci/Documents/Delft/master-thesis"
-
-## load other modules
-source(paste(main_path, "/evaluation/evaluate-results.R", sep = ""))
-
-data <-
-  getDataFrameForPBEResultsFile("android-failure-with-dependencies_ManualSelection.xml")
-
-result <- plot_evaluation_result(data, "android-failure-with-dependencies", "pbe", "manual", 0, 0)

### 2019-09-30 evaluation/run-evaluation.rb
fixes for evaluation runs on server

@@ -7,8 +7,8 @@ example_sets.each do |example_set|
 
   selection = "chronological"
   test_count = 1
-  learning_step_count = 1
-  technique = "pbe"
+  learning_step_count = 5
+  technique = "<technique>"
 
   run_eval = "ruby ../tool/run-extraction.rb -a evaluate -t #{technique} -e #{example_set} -s #{selection} -l #{learning_step_count} -c #{test_count} -v"
 

### 2019-10-01 paper/paper.tex
writing masterplan - first completeish version

@@
 \plan{why are logs so difficult: mention heterogeneous, semi-structured (paper reference for that?), big data (reference paper about log sizes), in distributed systems probably distributed (really also for build log?)
-
+g
 to combat that users write tools to <extract / retrieve superbegriff> information from build logs.

### 2019-10-01 paper/paper.tex
continue on masterplan, structure drafts in master thesis and paper

--- 2019-07-07 paper/paper.tex
@@
 \section{Introduction}
-\secfunc{why? what? research questions? purpose? hypothesis? wide $\rightarrow$ narrow
-
-problem, done in literature, why not eough? our approach
-}
-
-\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.
-
-\plan{why are logs so difficult: mention heterogeneous, semi-structured (paper reference for that?), big data (reference paper about log sizes), in distributed systems probably distributed (really also for build log?)
-
-to combat that users write tools to <extract / retrieve superbegriff> information from build logs.
-
-one possibility IR: classify specific part of program as similar to others (list IR technique) to see whether it is correlated to a failure.
-but not as good: not a real summarization technique, more what is similar to the last few times it failed.
-
-way to extract fine grained information: regular expressions which have to be written manually
-
-\todo{maybe other paragraph. here only half fitting?}
-}
-
-During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to retrieve the relevant information from between many uninteresting other lines.
-
-A way to support them would be to extract the desired information and present it in a structured way.
-One approach to realize such functionality are tools that employ handcrafted regular expressions to find the desired text parts within the build log.
-However, creating these regular expressions is tedious, mentally complicated and usually error-prone task.
-Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers.
-Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.
-
-We implemented \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples.
-After collecting a diverse set of build logs from Travis CI we designed a meta-model of the contained information.
-Our evaluation of ALBE showed that it is able to define extractions for various desired informations, that it shortens development time in comparison to manual regular expression construction and ...
-}
-
-\todo{Research Questions!}
-
-\bp{ RQ1: how many and which kind of samples does pbe need to be competitive with existing methods? }
-
-\bp{ can pbe extraction replace or even exceed existing methods for our use case? }
-
-\bp{ What are the limitations of extractions? (only interesting when specified with PROSE library..)}
-
-\bp{ Adjustements / Improvements to PROSE for extracting specifically from build logs }
+\subsection{Motivation}
+\subsection{Contribution}
+\subsection{Overview}
 
@@
 
-\subsection{Continuous Integration}
+%\section{Method}
+\section{Characterizing Build Log Information Extraction Techniques}
+\subsection{Characteristics of a Build Log}
+\subsubsection{Model of Extractable Data in Build Logs}
+\subsection{Model for Information Extraction Techniques}
+\subsection{Program Synthesis by Example}
+\subsection{Text Similarity}
+\subsection{Keyword Search}
 
-\review{
-Various researchers have analyzed industrial and open source logs for failure reasons and their impact on development.
-Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google.
-In addition most failures are resolved within two builds.
-Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones.
-They determined that testing failures outweigh compilation errors.
-Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
-Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
-They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.
+\section{Our Information Extraction Tool}
+\subsection{Unified Interface}
+\subsection{Program Synthesis by Example}
+\subsection{Text Similarity}
+\subsection{Keyword Search}
 
-All these researchers described building parsers in order to evaluate the studied build logs.
-Our work could support their research by easing the parser development and enable them to cover more languages and build tools easier.
-}
-
-\subsection{Tools}
-
-\review{
-Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs.
-They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts.
-They observed that highlighting the locality and context of an issue is helpful to programmers.
-We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.
-
-Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
-They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the error.
-In contrast to that, our tool ALBE extracts specific parts of the build logs.
-As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
-}
-
-\subsection{Information Extraction and Retrieval}
-
-\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
-Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
-On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
-For our use case, this could be applied by slicing the build logs into lines or small sections.
-Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
-Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}
-
-\review{
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework.
-It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples.
-Users can extract multiple fields and structure them with hierarchy and sequence.
-FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.
-
-We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information extraction.
-}
-
-\subsection{Semi-Structured Data}
-
-\draft{
-Software build logs are inherently semi-structured data. \todo{explain the different characteristics and relate to build logs}
-Serge Abiteboul~\cite{abiteboul1997querying} characterized semi-structured data as having an irregular, implicit, partial and rapidly evolving texture.
-}
-
-\section{Method}
-\secfunc{how? when? material? narrow}
-
-\todo{want?: flow of research figure}
-
-\todo{study design vs. study carry out}
-
-\begin{figure}
-	\includegraphics[width=0.5\textwidth, trim={0.5cm 5cm 3cm 2cm}, clip]{img/flow-of-research.pdf}
-	\caption{Flow of Research}
-\end{figure}
-
-\subsection{Data collection}
-
-\draft{
-In order to build a tool which facilitates information extraction from build logs we first had \todo{which time form here?
-past or present?} to get an impression on what kinds of build logs occur in projects, what possibly extractable information they contain and how structured or unstructured they are.
-}
-
-\subsubsection{Design} ...
-\bp{
-realistic image (for open source software) we sample from popular GitHub repositories that also use Travis CI.
-
-\draft{Obtaining the newest logs from them would entail sampling mostly logs of succeeding builds as the distribution of build states on a Travis CI repository is highly skewed towards successful builds~\cite{beller2017oops}.
-Therefore we stratify our collection of logs and select an equal amount of logs from each type of Travis CI build status.}
-}
-
-\subsubsection{Execution} ...
-\bp{
-built tool X \todo{data collection tool name, LogCollector?}
-
-queryed ghtorrent dataset from the first of April 2018 through google BigQuery
-
-poked Travis CI for active status of project and collected sampled builds through Travis ruby library
-
-downloaded logs through Travis Rest API \todo{look up version}
-}
-
-\subsection{Meta-Model}
-\bp{through manual examination of y of the build logs we collected designed a meta-model  of the contained/extractable/useful/interesting information}
-
-\todo{figure with meta-model}
-\begin{figure}
-	\includegraphics[width=0.5\textwidth, trim={0.5cm 4cm 3cm 0.5cm}, clip]{img/meta-model.pdf}
-	\caption{Meta-Model}
-\end{figure}
-
-\plan{explain (shortly? partly?) meta model classes}
-
-\subsection{Our Tool: ALBE \textemdash \ Analyzing Logs By Example}
-
-\plan{
-techstacky: C\#, dot net core, Microsoft PROSE library specifically their TextExtraction DSL
-
-samples \& learning: labeled data is in xml files, parsed (and shuffled) for examples, program learned for specific instruction
-
-interaction: user can analyze given file with program defined by specific exampleset, if there: describe how to use iteratively growing / shuffling learning process
-}
-
-\subsubsection{Capabilities} ...
-
-\plan{
-Example extractions: travis worker, android failure, what we do evaluations on
-}
-
-\subsubsection{Limitations} ...
-
-\plan{
-Travis worker both kinds at once, explain PROSE limitations on arbitrary OR regexes
-
-for all limitations: why? and how would we solve that?
-}
-
-\subsection{Evaluation}
-\bp{
-To evaluate our tool we did xyz, we wanted to measure: accuracy of extractions, impression on effort of creating such extraction, compare both to existing methods
-}
-
-\subsubsection{Extraction Accuracy}
-...
-
-\bp{we labelled x logs from project y using language z / build tool b. (do for one, maybe extend with further one)
-
-evaluated accuracy \todo{<define accuracy for us>} with growing number of 
-\begin{itemize}
-	\item random selected
-	\item chronologically sampled
-	\item hand selected 
-\end{itemize}
-samples.
-}
-
-\subsubsection{Compare to Traditional Methods}
-\paragraph{TravisTorrent} ...
-\bp{Beller et al.
-\mention{cite correct travistorrent paper} reported on manually constructing a parser with regular expressions for ruby \& Java and common build tools / output formats there, they can extract \todo{<explain there extractions, with example necessary?}
-
-android-failure example: decided not to implement as to complicated \todo{<- that kind of already belongs into results, how do we describe the \emph{method} of this comparison accurately??}
-}
-
-\paragraph{Manual Regex Construction} ...
-\plan{
-for something where I did not look at the synthesized program
-
-alternative: small study with other developers on manual vs. pbe extraction
-}
-
-\paragraph{IR paragraph stuff} ...
-\plan{
-maybe simple setup with lines implementing vector comparison on keywords ourselves -> how can we reuse the labeling for the c\# tool?
-}
-
-\paragraph{Keyword search} ...
-\plan{
-either: we give a list of keywords generally associated with the thing we want to extract (e.g. failure/error/..) -> write nicely how we brainstormed that
-
-or: small study of what developers would search for (maybe literature already did that?)
-
-or: relate to samples? search for already seen words from last failure
-}
+\section{The Failing Build Logs Data Set}
+\subsection{Data Structure / Points}
+\subsection{Build Log Collection}
+\subsection{Validation of Labeled Data}
 
 \section{Results}
-\secfunc{hard numbers! answers to research questions, narrow}
+evaluations run \& graphs \& data
 
-\plan{graphs!, achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data}
+\section{Discussion}
+comparing extraction techniques,e
+\subsection{Threats to Validity}
 
-\section{Analysis / Discussion}
-\secfunc{interpretation, implication of answers and why does it matter, comparison to previous findings, narrow $\rightarrow$ wide}
+\section{Conclusion}
 
-\plan{our tool works well for defined cases, limitations of tool/prose/regex usage in general, every x weeks extraction has to be rewritten to keep accuracy, well improved if only y new examples have to be added}
-
-\section{Conclusion and Future Work}
-\secfunc{summarize, results again, future research}
-
-\plan{repeat everything and results}
-
-\plan{future}
-
-\bp{make avaliable to other researchers
-
-integrate into travis
-
-\plan{as always} extend evaluation and data collection
-
-use dataset to evaluate against existing approaches
-
-}
+\subsection{Future Work}
 

### 2019-10-01 paper/paper_old.tex
continue on masterplan, structure drafts in master thesis and paper

%%
%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

% TODO remove XD
\usepackage{xcolor}
\newcommand{\secfunc}[1]{{\color{magenta}#1}}
\newcommand{\mention}[1]{{\color{cyan}#1}}
\newcommand{\plan}[1]{{\color{purple}#1}}
\newcommand{\bp}[1]{{\color{violet}#1}}
\newcommand{\draft}[1]{{\color{blue}#1}}
\newcommand{\review}[1]{{\color{black}#1}}
\newcommand{\todo}[1]{{\color{orange}#1}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-9999-9/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Analyzing Build Logs Using Programming by Example}

\author{Carolin Brandt}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Brandt, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  ...
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>10010520.10010553.10010562</concept_id>
%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010575.10010755</concept_id>
%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
%  <concept_significance>300</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010553.10010554</concept_id>
%  <concept_desc>Computer systems organization~Robotics</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>10003033.10003083.10003095</concept_id>
%  <concept_desc>Networks~Network reliability</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{ci, buildlogs, programming by example}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\secfunc{section function - \textbackslash secfunc} \\
\mention{things to mention / reference - \textbackslash mention} \\
\plan{what to write here - \textbackslash plan} \\
\bp{actual bullet points - \textbackslash bp} \\
\draft{final text drafty - \textbackslash draft} \\
\review{final text review ready - \textbackslash review} \\
\todo{ToDo - \textbackslash todo} \\

\section{Introduction}
\secfunc{why? what? research questions? purpose? hypothesis? wide $\rightarrow$ narrow

problem, done in literature, why not enough? our approach
}

\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the success build state is restored improves the overall productivity of developers.

\plan{why are logs so difficult: mention heterogeneous, semi-structured (paper reference for that?), big data (reference paper about log sizes), in distributed systems probably distributed (really also for build log?)
g
to combat that users write tools to <extract / retrieve superbegriff> information from build logs.

one possibility IR: classify specific part of program as similar to others (list IR technique) to see whether it is correlated to a failure. but not as good: not a real summarization technique, more what is similar to the last few times it failed.

way to extract fine grained information: regular expressions which have to be written manually

\todo{maybe other paragraph. here only half fitting?}
}

During this assignment an engineer spends a lot of their time \todo{or: find percentage to cite} reading very long and verbose build logs, trying to retrieve the relevant information from between many uninteresting other lines. \todo{add anecdotal evidence, watchdog paper?}

A way to support them would be to extract the desired information and present it in a structured way.
One approach to realize such functionality are tools that employ handcrafted regular expressions to find the desired text parts within the build log.
However, creating these regular expressions is tedious, mentally complicated and usually error-prone task. Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers.
Our goal is to evaluate an alternative way of taking this burden of programmers.
By simply giving examples of the desired extractions they should be able to define extraction programs.

We implement \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples.
After collecting a diverse set of build logs from Travis CI we design a meta-model of the contained information.
We evaluate ALBE on logs from selected GitHub repositories on the accuracy of extraction for a varying number and selection of in-output-examples.
Furthermore we compare the tool to classical information retrieval and plain keyword search.
Our evaluation of ALBE shows that it is able to define extractions for various desired informations, that it shortens development time in comparison to manual regular expression construction and ...
}

\todo{Research Questions!}

\bp{ RQ1: how many and which kind of samples does pbe need to be competitive with existing methods? }

\bp{ can pbe extraction replace or even exceed existing methods for our use case? }

\bp{ What are the limitations of extractions? (only interesting when specified with PROSE library..)}

\bp{ Adjustements / Improvements to PROSE for extracting specifically from build logs }

\section{Related Work}

\todo{More glue \& sentences that give an overview over the next paragraph}

\subsection{Bulidlogs Analysis Tools}

\review{
Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs. They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts. They observed that highlighting the locality and context of an issue is helpful to programmers. We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.

Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs. They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the error. In contrast to that, our tool ALBE extracts specific parts of the build logs. As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
}

\subsection{Continuous Integration}

\review{
Various researchers have analyzed industrial and open source logs for failure reasons and their impact on development. Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google. In addition most failures are resolved within two builds. Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones. They determined that testing failures outweigh compilation errors. Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects. Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds. They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.

All these researchers described building parsers in order to evaluate the studied build logs. Our work could support their research by easing the parser development and enable them to cover more languages and build tools easier.
}

\subsection{Information Extraction and Retrieval}

\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix. On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}. For our use case, this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}

\review{
Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework. It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples. Users can extract multiple fields and structure them with hierarchy and sequence. FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.

We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information extraction.
}

\subsection{Semi-Structured Data}

\draft{
Software build logs are inherently semi-structured data. \todo{explain the different characteristics and relate to build logs}
Serge Abiteboul~\cite{abiteboul1997querying} characterized semi-structured data as having an irregular, implicit, partial and rapidly evolving texture.
}

\section{Method}
\secfunc{how? when? material? narrow}

\todo{want?: flow of research figure}

\todo{study design vs. study carry out}

\begin{figure}
	\includegraphics[width=0.5\textwidth, trim={0.5cm 5cm 3cm 2cm}, clip]{img/flow-of-research.pdf}
	\caption{Flow of Research}
\end{figure}

\subsection{Data collection}

\draft{
In order to build a tool which facilitates information extraction from build logs we first had \todo{which time form here? past or present?} to get an impression on what kinds of build logs occur in projects, what possibly extractable information they contain and how structured or unstructured they are.
}

\subsubsection{Design} ...
\bp{
realistic image (for open source software) we sample from popular GitHub repositories that also use Travis CI.

\draft{Obtaining the newest logs from them would entail sampling mostly logs of succeeding builds as the distribution of build states on a Travis CI repository is highly skewed towards successful builds~\cite{beller2017oops}. Therefore we stratify our collection of logs and select an equal amount of logs from each type of Travis CI build status.}
}

\subsubsection{Execution} ...
\bp{
built tool X \todo{data collection tool name, LogCollector?}

queryed ghtorrent dataset from the first of April 2018 through google BigQuery

poked Travis CI for active status of project and collected sampled builds through Travis ruby library

downloaded logs through Travis Rest API \todo{look up version}
}

\subsection{Meta-Model}
\bp{through manual examination of y of the build logs we collected designed a meta-model  of the contained/extractable/useful/interesting information}

\todo{figure with meta-model}
\begin{figure}
	\includegraphics[width=0.5\textwidth, trim={0.5cm 4cm 3cm 0.5cm}, clip]{img/meta-model.pdf}
	\caption{Meta-Model}
\end{figure}

\plan{explain (shortly? partly?) meta model classes}

\subsection{Our Tool: ALBE \textemdash \ Analyzing Logs By Example}

\plan{
techstacky: C\#, dot net core, Microsoft PROSE library specifically their TextExtraction DSL

samples \& learning: labeled data is in xml files, parsed (and shuffled) for examples, program learned for specific instruction

interaction: user can analyze given file with program defined by specific exampleset, if there: describe how to use iteratively growing / shuffling learning process
}

\subsubsection{Capabilities} ...

\plan{
Example extractions: travis worker, android failure, what we do evaluations on
}

\subsubsection{Limitations} ...

\plan{
Travis worker both kinds at once, explain PROSE limitations on arbitrary OR regexes

for all limitations: why? and how would we solve that?
}

\subsection{Evaluation}
\bp{
To evaluate our tool we did xyz, we wanted to measure: accuracy of extractions, impression on effort of creating such extraction, compare both to existing methods
}

\subsubsection{Extraction Accuracy}
...

\bp{we labelled x logs from project y using language z / build tool b. (do for one, maybe extend with further one)

evaluated accuracy \todo{<define accuracy for us>} with growing number of 
\begin{itemize}
	\item random selected
	\item chronologically sampled
	\item hand selected 
\end{itemize}
samples.
}

\subsubsection{Compare to Traditional Methods}
\paragraph{TravisTorrent} ...
\bp{Beller et al. \mention{cite correct travistorrent paper} reported on manually constructing a parser with regular expressions for ruby \& Java and common build tools / output formats there, they can extract \todo{<explain there extractions, with example necessary?}

android-failure example: decided not to implement as to complicated \todo{<- that kind of already belongs into results, how do we describe the \emph{method} of this comparison accurately??}
}

\paragraph{Manual Regex Construction} ...
\plan{
for something where I did not look at the synthesized program

alternative: small study with other developers on manual vs. pbe extraction
}

\paragraph{IR paragraph stuff} ...
\plan{
maybe simple setup with lines implementing vector comparison on keywords ourselves -> how can we reuse the labeling for the c\# tool?
}

\paragraph{Keyword search} ...
\plan{
either: we give a list of keywords generally associated with the thing we want to extract (e.g. failure/error/..) -> write nicely how we brainstormed that

or: small study of what developers would search for (maybe literature already did that?)

or: relate to samples? search for already seen words from last failure
}

\section{Results}
\secfunc{hard numbers! answers to research questions, narrow}

\plan{graphs!, achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data}

\section{Analysis / Discussion}
\secfunc{interpretation, implication of answers and why does it matter, comparison to previous findings, narrow $\rightarrow$ wide}

\plan{our tool works well for defined cases, limitations of tool/prose/regex usage in general, every x weeks extraction has to be rewritten to keep accuracy, well improved if only y new examples have to be added}

\section{Conclusion and Future Work}
\secfunc{summarize, results again, future research}

\plan{repeat everything and results}

\plan{future}

\bp{make avaliable to other researchers

integrate into travis

\plan{as always} extend evaluation and data collection

use dataset to evaluate against existing approaches

}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2019-10-03 thesis/txt/0-intrdouction.tex
first complete draft thesis introduction, chapters and structure in separate files

\providecommand{\myrootdir}{..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}

\chapter{Introduction}
\plan{motivate why information extraction from build logs}
Many software projects now use continious integration (CI) to improve \mention{reasons to do this, look into Proksch papers}. Theses CI builds often produce very long and verbose build logs \mention{log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.

These build logs are a highly valuable data source. First of all, for the developers that read them to analyze why their build failed or .. \mention{find more reasons}. Second, for reasearchers that can harvest the information contained in the logs (and their metadata) to study the software engineering process of a project. However they can only harvest the information within the build logs if they can adequately extract the information relevant to them.

There are many different extraction techniques use for this task. Beller et al.  used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI \cite{beller2017oops}, while Vassallo et al. wrote a custom parser for Java Maven buildlogs to gather information for build repair hints \cite{vassallo2018un-break}. Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build.~\cite{amar2019mining} \bp{anecdotal: keyword search?}. Apart from those there are various more extraction techniques like searching for keywords, ... \todo{more?} \bp{problem which to choose}

With our work we want to support developers, researchers or project managers in deciding which technique is the best one for their use case.

\plan{what we do in this thesis}

We aim to define a model to characterize the different extraction techniques and answer what influences the suitability of a technique. We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by Example using the Microsoft PROSE library, a common text similarity approach and simple keyword search. Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this extractions and a categorization of the extractions according to their structural position within the log \todo{is this understandable here? leave out?}.

\plan{research questions}

We aim to answer the following research questions:

\begin{itemize}
  \item{RQ1:} Is Programming by Example suited to extract information from CI build logs?
  \item{RQ2:} What criteria influence the suitability of an information extraction technique for CI build logs?
  \item{RQ3:} When are text similarity or keyword search better suited for information extraction from CI build logs?
\end{itemize}

\plan{contributions}

Our work contributes:

\begin{itemize}
  \item A model to characterize information extraction techniques from \todo{CI?} build logs
  \item A model to characterize use case scenarios for information extraction from CI build logs
  \item A model of the extractable information in CI build logs
  \item A tool unifying several information extraction techniques namely:
        \begin{itemize}
          \item our implementation of regular expression program synthesis using the Microsoft PROSE library,
          \item a common information retrieval approach using text similarity, and
          \item a simple keyword search approach
        \end{itemize}
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the extractions according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information extraction techniques \todo{not quite clear \emph{what} we evaluate here}
  \item A extendable model \todo{really? maybe scheme, decision tree} supporting decision on the three information extraction techniques relative to a given use case scenario
\end{itemize}

\plan{structure overview}
This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information extraction and retrieval techniques to program synthesis by examples.
Next, chapter \ref{models} present our models for information extraction techniques, use case scenarios for those and extractable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation, as well as their theoretical foundations.
Chapter \ref{data-set} describes the creation of our log data set collected from failed Travis CI build logs, and the labeling and validation process.
Following, Chapter \ref{implementation} our implementation and the usage of our unified information extraction tool, used for the evaluation study of our models described in Chapter \ref{evaluation}. There we also describe the resulting instantiation of our reccomendation model for regex program synthesis, text similarity and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{conclusion}.
\end{document}

### 2019-10-03 thesis/txt/1-related-work.tex
first complete draft thesis introduction, chapters and structure in separate files

\providecommand{\myrootdir}{..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}

\chapter{Related Work}

\section{CI Research}
\section{Build log analysis and augmentation}
\section{Production Log analysis}
\section{Information extraction and retrieval techniques}
IR papers, maybe something about keyword search?
\section{Program Synthesis by Example}

\end{document}

### 2019-10-03 thesis/txt/2-models.tex
first complete draft thesis introduction, chapters and structure in separate files

\providecommand{\myrootdir}{..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}

\chapter{Information Extraction Techniques}
overview introduction text
\label{models}

\section{Our Model for IE Techniques}
\section{Our Model for extraction tasks}
\section{Our Model for extractable information}

\section{PROSE Program Synthesis}

\section{IR Similarity}

\section{Keyword search}

\section{further thechniques}

\end{document}

### 2019-10-03 thesis/txt2/1-manual.tex
first complete draft thesis introduction, chapters and structure in separate files

\providecommand{\myrootdir}{..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}

\chapter{User manual}

Indeed, another long manual for something which should not require any guidance.
However, it is highly recommended to read it thoroughly as it covers a lot of non-standard LaTeX features and helps you with getting the most out of this template.
Have fun!

\section{First steps}

\subsection{Compile it!}

Before modifying any file, try if you can compile it!
I -- a long year Linux enthusiast -- prefer vim and just running make in the project directory.
But other toolchains works as well.
For some files, I also use \href{https://github.com/alexandervdm/gummi}{gummi} -- especially for drawing images --, but as long as you have LaTeX installed on your system, almost every editor should work as well.
I have also tested it with \href{http://www.texstudio.org/}{TeXstudio}.
Although the navigation over the structure panel seems to be broken (it does not recognize the \texttt{\textbackslash subfile} commands correctly), compilation works perfectly.
As a workaround for broken navigation, I suggest compiling \texttt{main.tex} once, view the resulting PDF and use a right click on any text with \enquote{Go to Source} to jump to the corresponding \texttt{.tex}-file

\subsection{Personalize the template}

Your thesis is a very personal project, but -- nevertheless -- after all, it is an official document.
Hence, there must be a lot of formal stuff in place.
This template takes care of the layout, but you must provide the content.
To add your personal information (e.g. your name, Topic, supervisors, etc.), just open \texttt{./mini/myconfig.sty} with your favorite tex(t)-editor and edit the corresponding dummy data.

In the \texttt{./mini}-directory you also find the dummy text for the abstract and the acknowledgments for the preface of the thesis.
I do not suggest to start writing your thesis with those pieces of text, but if you want to add or adjust them later -- now you know where they are waiting for you to fill them.

If you lack any LaTeX-package for some special purposes, feel free to add it to the package list in \texttt{./zxy/mypackages.sty}.
The template does not split the package list into multiple files (e.g. for \enquote{template-packages} and \enquote{user-packages}) to avoid double-listing of any package.
Furthermore the order of the packages matters in rare corner cases you can solve some conflicts just by reordering.
Inside the \texttt{zyx}-directory you also find all the internal files for setting up the cover and the surrounding pages.
The average user should not be required to touch these files, but if something is broken, this is most likely the place to fix it.

\newpage
\subsection{Start writing}

Of course, the biggest part of the thesis document is writing text.
This template uses the \texttt{./txt}-directory for all of it.
For the inclusion into the \texttt{main.pdf}, you must put a corresponding entry into \texttt{main.tex}.
The name of the file does not matter as the sequence of the entries in the tex-code determines the order of the included chapters.

Although I recommend adding a (not necessarily serial) number in front of the file names to represent the correct order in file browsers and across multiple editors.
As a good starting point for new files just copy the \texttt{0-empty.tex} file and start writing in there.
If you prefer having a subdirectory for each chapter, just create new folders inside the \texttt{txt}-directory.
Afterward, adjust the file names inside \texttt{main.tex} corresponding to your subdirectory names and adapt the \texttt{\textbackslash myrootdir}-entry in the new/moved file (most likely to \enquote{\texttt{../..}} for one nested subdirectory).

\section{Core ideas}

\subsection{Each \texttt{.tex}-file can be compiled on its own}
Every file with a \texttt{.tex}-file extension can be compiled without any of the other \texttt{.tex}-files.
If you want someone to read your abstract or only one of your chapters, just only compile the corresponding \texttt{.tex}-file and you get a single PDF only containing the current file.
This is very convenient when drawing pictures with tikz (inside the img-folder) as they must be compiled and adjusted many times before they look perfect and having them separated speeds up their compile time immensely.
Additionally, the generated pictures can be reused in other documents -- for example in your final presentation.

For being compilable the \href{https://www.ctan.org/pkg/subfiles}{subfiles package} for regular LaTeX-Documents and the \href{https://www.ctan.org/pkg/standalone}{standalone package} for tikz images.
As the files for this template are split over multiple directories, LaTeX has some problems with the path construction for the separate files.
As a countermeasure, this template uses the variable \texttt{\textbackslash myrootdir} giving the relative path from the current file to the root directory of the template, that is defined in the first line of most \texttt{.tex}-files.
Normally, it is just \enquote{\texttt{..}} to go one directory upwards, e.g. from the \texttt{txt} directory into the root directory.

\subsection{Separate blown up LaTeX code from written text}

Nothing is more distracting when reading text than huge blocks of random LaTeX macros spread between it.
Hence, this templates does its best to split layout logic and the actual content into separate files.
For example, the main file does not start with a few hundred lines of template and package stuff before you can organize your files.
With all images, code snippets and table data in distinct folders, the plain text remains very compact and clean what increases the readability.
That also has a nice side effect: Everything inside the \texttt{zyx} directory requires a quite a decent LaTeX-skill, whereas adding new text becomes a fairly simple task.

\subsection{Folder Structure}

\paragraph{The root directory} only contains few files, and the average user should not be required to add a new file there.
\texttt{main.tex} is the entry point to your thesis.
\texttt{Makefile}, \texttt{README.md} and \texttt{.gitignore} are needed to be at the top level to form a reasonable project setup.
The \texttt{literature.bib} is the container for all the literature referenced anywhere in the thesis.
Most scientific databases provide snippets in the BibTeX format that can directly be copied into it.
However, be careful: Even the same database is not entirely consistent with the format of conference names and the longer the list becomes, the more likely it requires some manual adjustments.
Finally, \texttt{dictionary.txt} is a helper file for the hunspell spell checker set up in the \texttt{Makefile}.
It keeps all user defined words so that they can also be committed into the version control system.

\paragraph{code} contains all code files listed in your thesis.
With keeping the corresponding extension, they get the proper syntax highlighting in your editor, and you can still compile them with their native compiler what prevents syntax errors.
If you only want to include some parts of the file, please use the \texttt{firstline} and \texttt{lastline} option for the selection and do not ruin the file by deleting non-relevant code.

\paragraph{data} concentrates pure data information potentially used in plots and tables by LaTeX.
In the ideal use case, you write small scripts that collect and generate these data files.
When later something changes in your data (e.g. fixed bugs, environment changes, etc.) you simply have to rerun these scripts and the data in the documents get updated without touching a single line of LaTeX-code.
Although these files are named \texttt{*.dat}, any standard text editor can open them.
For more details about the usage look at the snippets in \cref{sec:presenting-data}.

\paragraph{img} is the place for all images and pictures included in your thesis.
The best way is to write your images with tikz, but having vector graphics in PDFs there is also fine (\texttt{git add -f name.pdf} may be helpful).
You should avoid pixel based pictures like PNGs or JPGs wherever you can.

\paragraph{mini} is a collection of some little files that must be adjusted by the user but does not fit into any other directory, e.g. the abstract or your configuration details.

\paragraph{txt} comprises all text files of your thesis, e.g. one file for each chapter or section in your thesis.
Don't forget to register them in the \texttt{main.tex}.

\paragraph{zyx} is a very strange name for a directory.
It hides all LaTeX logic to compose the template and can be ignored by the average user.
I choose this name because there exist no human word listed after this letters in a dictionary.
Hence, it is always the last directory inside a directory what makes it easier to recognize and ignore it.
Furthermore, it is still somehow pronounceable.

\vfill
\newpage

Nevertheless, feel free to adapt the directory structure to your needs and delete folders if you do not need them.
There is no reason for keeping empty directories that only mess up your environment.

\section{Minor Features}

\subsection{One or two sides per page}
Depending on the amount of text you have written for your thesis, the final document will probably contain a lot of sides.
Hence, I suggest printing two sides per page (one on the front and one on the back).
In this way, the resulting book becomes not so thick and costs a lot less money for printing.
If you want to use a single side per page layout instead, you can change this the \texttt{main.tex} by adjusting the \texttt{documentclass}.
But no worry when you do not want to decide this now.
The layout can also be adapted later as both setups have the same text dimensions and your text will look identical on both of them.
No matter what design you chose, please don't forget to give a corresponding hint to the print shop.
Finally, a small remark for all those, who look at this template with hawk eyes:
The text is intentional not perfectly centered -- instead the inner margin is a little bit bigger than the outer margin.
That results in better readability after the pages are bound and glued to a book.

\subsection{Integrated git version information}
During writing your thesis, it is highly recommended to put your work under a version control system: to store older thoughts in case you need them later, for an easier backup and to proof that you have not copy-pasted your thesis.
This template is prepared for git as it already provides a \texttt{.gitignore} file covering the most frequent use cases.
So just initialize a new git repository in the root directory, and everything sets up automatically.

But there are even more benefits of using git for the template.
It automatically adds the currently checked out branch and tag of the directory when the compilation starts as a keyword to the generated pdf document.
That is particularly useful during the end phase of the thesis, where you most likely distribute some pdfs to different reviewers and it is quite easy to lost track, who has received which version, as some reviews arrive later than others.
Depending on your pdf-viewer you can find it most likely somewhere under properties.

If you are not using the root directory of this template is the main directory of your git repository, you have to adjust the optional argument (the text between \texttt{[~]}) in \texttt{./zyx/mypackages.sty} for the \texttt{gitinfo}-package with the (relative) path to your git directory.
In the rare case that your reviewer wants to print your thesis and returns a stack of paper with handwritten notes to you, the pdf meta-information is not helpful, but you can uncomment two lines in {./zyx/mypackages.sty} after the \texttt{gitinfo}-package to print it on every page.

\subsection{Create Submission Archive}
After you are done with your thesis, your advisors may also want a copy of its source code.
Of course, direct access to the git-repository is the best, but this also contains a lot of meta-data that arise privacy concerns (e.g. when exactly what part of the text was written).
A good trade-off is to put all source files (i.e. all files under version control) and the final pdf into an archive.
\texttt{make submit} creates such an archive.

\subsection{Speedup compilation of large tikz-images}
The standalone package that is used to include tikz-images into the main document has a mode, where it compiles the pictures first and then includes the generated pdf version afterward.
That has the effect that the pictures only have to be compiled once after they have changed and remains cached.
However, this mode requires a compilation flag that allows LaTeX to open new processes (Did you know that LaTeX is Turing complete?).
To enable this feature, you have to add \enquote{\texttt{-shell-escape}} to the compile flags inside the Makefile or your IDE.
Otherwise, you will end up getting \enquote{Can be used only in preamble}-errors.
For details, how to switch this mode, have a look at the corresponding comment in the code for \cref{fig:bluecircle} and the \texttt{all} target in the Makefile or the instruction of your IDE to add this flag.
As a security warning for IDE users: If you are also compiling \enquote{untrusted} LaTeX code with your IDE, you should remove the flag beforehand as it prevents you from opening a shell for a potential attacker (and yes, of course, you can trust this template).

\subsection{Spell Checking}
Detecting spelling and grammar errors inside multiple LaTeX documents is quite a complicated task because all the LaTeX commands obliterate the flow of the text.
However, nothing can ruin a thesis as fast and gratuitous as spelling errors in each sentence.
Of course, you can find somebody to proofread your thesis, but some automated tools as a first layer can be vital.
Unfortunately, I am not aware of any flawless tool for this purpose.

This template implements the nerdy Linux-way for spell checking.
You can use \texttt{make spell} to run \href{https://hunspell.github.io/}{Hunspell} on all text files.
All custom words added during the review are stored into the \texttt{dictionary.txt}.
It is not an optimal solution, but better than nothing.

As a more modern approach, some students have used \href{https://grammarly.com/}{Grammarly}.
But keep in mind, it is a commercial, cloud-based startup.
So expect all your text to be stored and evaluated permanently in the united states, what is not an option for all situations.
Furthermore, you have to compile and copy\&paste all your text from the PDF into their web interface.
Nevertheless, it helps a lot with comma placement and correct cases.

\end{document}

### 2019-10-03 thesis/txt2/2-background.tex
first complete draft thesis introduction, chapters and structure in separate files

--- 2019-06-10 thesis/txt/background.tex
@@
 
-\section{Background}
+\chapter{Background}
 
-\subsection{semi-structured data}
+\section{semi-structured data}
 characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here!

### 2019-10-03 thesis/txt2/2-snippets.tex
first complete draft thesis introduction, chapters and structure in separate files

\providecommand{\myrootdir}{..}
\documentclass[\myrootdir/main.tex]{subfiles}

\begin{document}

\chapter{Helpful snippets}

This chapter just randomly uses some snippets and frequently used code patterns you probably might find useful.
The content is pure nonsense, but the underlying LaTeX code can easily be modified and adapted to the real text of your thesis.

\section{Structuring text}

First of all, there are a few elements that help you structure your text.

\subsection{Lists and enumerations}

Sometimes using lists and enumerations are the best way to present your data, although some authors see this as a bad writing style.

\begin{itemize}
 \item One item
 \item Another item
 \item the last item
\end{itemize}

\noindent Or enumerations are also possible

\begin{enumerate}
 \item Number one
 \item here comes number two
 \item All good things come in threes
\end{enumerate}

\subsection{Fancy lists}

But if you want to use lists, there are also some ways to get a better layout with them.

\begin{enumerate}[label=\textbf{[\Roman*]}]
 \item Even more enumerations
 \item But this time with custom style
 \item \ldots this list also needs a third item
 \item and a fourth to show roman enumerations better \ldots
\end{enumerate}

Or just use them for better alignment

\begin{description}[align=right,labelwidth=2cm]
 \item [Head] \texttt{~(Q.Q)~}
 \item [Body] \texttt{(/~n~\textbackslash{})}
 \item [Feet] \texttt{~~"~"~~}
 \item [Info] In the rare case you do not recognize it, this is an ASCII-owl.
\end{description}

\section{Using pictures}

Showing some pictures lighten up the thesis and simplify the explanations.
There are multiple ways to include a picture.
Which one fits best for your needs depends on the original image and the targeted quality of the print.
Overall, pixel based graphics are more frequent but results in bigger PDFs and a mediocre printing quality.
Vector based graphics are smaller and looks brilliant with a professional printer.
Nevertheless, it is much harder to create them.
The inclusion of both formats in LaTeX is quite similar.

\subsection{Drawing with \href{https://ctan.org/pkg/pgf}{\texttt{tikz}}}

This is the way you want to draw pictures in LaTeX!
But be warned, tikz's syntax is similarly powerful (or ugly) as plain LaTeX, and of course, you can use all LaTeX constructs in there as well.
This template is designed to have separate LaTeX files for each tikz picture, that can be compiled standalone.
That is very handy while drawing them because it allows real-time previews of the image using a suitable editor (e.g. gummi).
The final document includes the stored code like a regular graphic.
\Cref{fig:bluecircle} gives an example.

\begin{figure}[htb]
\centering
\input{\myrootdir/img/circle}
% For a speed up with standalone tikz-pictures replace the above line with:
%\includestandalone{\myrootdir/img/circle}
\caption{A blue circle}
\label{fig:bluecircle}
\end{figure}

\subsection{Standard include}

OK, normal pictures can be included as well \ldots your images should, of course, be located in the img-folder \ldots not like this template does in \cref{fig:selogo} \ldots

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{\myrootdir/zyx/TUMinfo/logos/2015_Logo_TUM_CMYK.pdf}
\caption{TUM logo scaled to half of the page width}
\label{fig:selogo}
\end{figure}

\newpage

\subsection{Side-by-side images}

If you run out of space, it might be helpful to put the images side by side as used as an example with \cref{fig:left-example} and \cref{fig:right-example}.

\begin{figure}[htb]
\centering
\begin{minipage}{0.46\textwidth}
\includegraphics[width=\textwidth]{example-image-a}
\caption{Left image}
\label{fig:left-example}
\end{minipage}
\qquad
\begin{minipage}{0.46\textwidth}
\includegraphics[width=\textwidth]{example-image-b}
\caption{Right image}
\label{fig:right-example}
\end{minipage}
\end{figure}

\section{Presenting data}
\label{sec:presenting-data}

LaTeX provides many ways to present your data in beautiful ways.
This template shows only a few of them, but hopefully, they are the most useful ones.
Most importantly, this \texttt{.tex} does not contain a single data point shown in the following plots and tables.
Everything is read from corresponding files in the \texttt{data}-directory.
I highly recommend keeping this approach for your visualizations as well, as these external files can easily be generated by external programs and can be updated flawlessly if any data changes.

\subsection{Beatiful plots}

\begin{figure}
\centering
\input{\myrootdir/img/plot}
% For a speed up with standalone tikz-pictures replace the above line with:
%\includestandalone{\myrootdir/img/plot}
\caption{Example plot from external \texttt{.dat}-file}
\label{fig:plot-mult}
\end{figure}

When presenting a lot of complex data, visualizing them with plots is one of the best approaches you can choose.
But don't forget to separate data from code.
By the way, \texttt{pgfplot} can do way more things than you can see in \cref{fig:plot-mult}.

\subsection{Beautiful tables}

There are dozens of packages in LaTeX to compose tables.
This template focuses on the \href{https://ctan.org/pkg/booktabs}{\texttt{booktabs}}-package, but you can use what ever table fits best for you.
For using getting the best control over the inclusion of external \texttt{csv}-files you should familiarize yourself with the \href{https://www.ctan.org/pkg/csvsimple}{\texttt{csvsimple}}-package.

\subsubsection{Tables with a lot of numbers}
When you have tons of numbers, why not use a table filling a complete page like \cref{tab:101}

\begin{table}[p]
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill$\;$}}c|*{10}{r}@{}}
\toprule
  \headcol{$\times$} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\midrule
\csvreader[no head,late after line=\\,late after last line=\\\bottomrule]{\myrootdir/data/101.csv}{}{%
\thecsvrow & \csvlinetotablerow}%
\end{tabular*}
\caption{The small $1 \cdot 1$}
\label{tab:101}
\end{table}

\clearpage % Small trick for better page breaks
\phantom{.}\vspace{-4em} % Big trick for better page breaks ^^
\subsubsection{Better number alignments}

\begin{wraptable}{o}{0.2\textwidth}
\vspace{-4em} % This number must be adjusted when used in a different context
\centering
\begin{tabular}{rD{.}{.}{3}}
\toprule
 \headcol{$n$} & \headcol{$n \cdot \sqrt{n}$} \\
\midrule
\csvreader[no head,late after line=\\,late after last line=\\\bottomrule]{\myrootdir/data/squares.csv}{}{%
\thecsvrow & \csvcolii}%
\end{tabular}
\caption{Square~roots}
\label{tab:roots}
\vspace{-2.5em} % This number must be adjusted when used in a different context
\end{wraptable}

When showing a lot of numbers with decimals, LaTeX offers a special alignment on the dot between the digits, what looks much better than just align right (see \cref{tab:roots}).
Have a look at the \href{https://ctan.org/pkg/dcolumn}{\texttt{dcolumn}}-package for more details.

This table also shows another neat feature:
You can put small tables on the side of your page and let the text float around it.
Of course, there is not much space for the caption, but for some tiny tables, it might also be helpful.

\subsubsection{Side-by-side tables}

If your tables are only very narrow, why not split them in two and show them more space efficiently side by side as in \cref{tab:twocolumn}?

\begin{table}[htb]
\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill$\;$}}ccc@{}}
\toprule
  \headcol{Alpha} & \headcol{Beta} & \headcol{Gamma} \\
\midrule
\csvreader[head to column names,late after line=\\,late after last line=\\\bottomrule,%
% The trick is the filter expression with the line numer
filter expr={test{\ifnumless{\thecsvinputline}{5}}}%
]{\myrootdir/data/sidebyside.csv}{}{\Alpha & \Beta & \Gamma}
\end{tabular*}
%%%%%
\hfill
\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill$\;$}}ccc@{}}
\toprule
  \headcol{Alpha} & \headcol{Beta} & \headcol{Gamma} \\
\midrule
\csvreader[head to column names,late after line=\\,late after last line=\\\bottomrule,%
% The trick is the filter expression with the line numer
filter expr={test{\ifnumgreater{\thecsvinputline}{4}}}%
]{\myrootdir/data/sidebyside.csv}{}{\Alpha & \Beta & \Gamma}
\end{tabular*}
\caption{Example for a table spread over two sides}
\label{tab:twocolumn}
\end{table}

\vspace{-1.5em} % Small trick for better page breaks
\section{Printing source code}

Including source code is simple and may look quite beautiful.
I recommend putting the actual code as a distinct file into the code directory with the correct extension.
Thereby you get perfect syntax highlighting from your local editor, and you can even compile or execute these files separately.
Latex can include each file with a single line of code.
You only must not use too many characters in one line in your code to avoid overlaps.

\lstinputlisting[float=t,language=C,caption=Hello World,label=lst:hello]{\myrootdir/code/hello.c}

\section{Miscellaneous}

While writing, you may leave some open tasks as todos for later.
Of course, there is also a command for this: \todo{Search for TODO in the text and fix them}
Furthermore, you can use all types of symbols (e.g. $\diameter$, €, \ldots).
And finally just a small citation from a random book by \textcite{Kemper2015} -- just to add the bibliography.
If you need direct quotes, just use the \enquote{quote-command} for simple quotation.

\end{document}

### 2019-10-03 thesis/txt/1-related-work.tex
put pictures for explanations in various sections

@@
 \chapter{Related Work}
+\todo{introduction \& glue text}
 
 \section{CI Research}
+\mention{look into proksch papers}
+Various researchers have analyzed industrial and open source logs for failure reasons and their impact on development.
+Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google.
+In addition most failures are resolved within two builds.
+Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones.
+They determined that testing failures outweigh compilation errors.
+Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
+Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
+They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.
+
+All these researchers described building parsers in order to evaluate the studied build logs.
+Our work could support their research by easing the parser development and enable them to cover more languages and build tools easier.
+
 \section{Build log analysis and augmentation}
+Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs.
+They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts.
+They observed that highlighting the locality and context of an issue is helpful to programmers.
+We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.
+
+Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
+They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the error.
+In contrast to that, our tool ALBE extracts specific parts of the build logs.
+As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
+
 \section{Production Log analysis}
+\mention{logpai and drain}
+
+\mention{ask Jean?}
+
 \section{Information extraction and retrieval techniques}
+\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
+Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
+On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
+For our use case, this could be applied by slicing the build logs into lines or small sections.
+Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
+Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}
+
 IR papers, maybe something about keyword search?
+
 \section{Program Synthesis by Example}
+\review{
+Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework.
+It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples.
+Users can extract multiple fields and structure them with hierarchy and sequence.
+FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.
+
+We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information extraction.
+}
+\mention{prose theory paper \cite{polozov2015flashmeta:}}
+\mention{\cite{rolim2017learning}}
 

### 2019-10-03 thesis/txt/2-models.tex
put pictures for explanations in various sections

@@
 \chapter{Information Extraction Techniques}
+\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
 overview introduction text
@@
 \section{Our Model for IE Techniques}
+\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
 \section{Our Model for extraction tasks}
+\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
 \section{Our Model for extractable information}
+\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
 
 \section{PROSE Program Synthesis}
+\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
 
 \section{IR Similarity}
+\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
 
 \section{Keyword search}
+\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
 
-\section{further thechniques}
+\section{further techniques}
 

### 2019-10-03 thesis/txt/1-related-work.tex
filling various sections with points on what to write about

@@
 \todo{introduction \& glue text}
+This section presents various research works adjecent or foundational for our work.
+Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation.
+We differentiate our work from the more common production runtime log analysis and cover different information extraction and retrieval techniques.
+Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.
 
-\section{CI Research}
+\section{Continuous Integration Research}
 \mention{look into proksch papers}
@@
 
-IR papers, maybe something about keyword search?
+\mention{IR papers, maybe something about keyword search?}
 

### 2019-10-03 thesis/txt/2-models.tex
filling various sections with points on what to write about

@@
 \chapter{Information Extraction Techniques}
+\label{models}
 \includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
-overview introduction text
-\label{models}
+Many different information extraction techniques ... this section describes the concepitonal / theoretical results of our thesis ... 
+We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly. 
+Additionally we present a complimentary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
+From our analysis of build logs we share our notion of the extractable information within a build log.
 
@@
 \includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+A build log information extraction technique (BLIE technique) consumes a build log (text file) and produces a certain output (text).
+\todo{make picture, output can be contained in log or not, can be continuous substring or selected lines etc.}.
+\begin{itemize}
+  \item{Target}{Extractable Information} each extraction technique \todo{instantiation!} targets a specific information
+  \item{Setup Overhead}{Time}
+  \item{Performance}{Performance} split into learning performance
+\end{itemize}
+
+Example instantiations of this task later in this chapter, namely for the three techniques we are comparing: PROSE program synthesis, IR text similarity, and simple keyword search. \todo{ref?}
+
 \section{Our Model for extraction tasks}
 \includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+aims to describe an information extraction task of a developer or a researcher.
+\begin{itemize}
+  \item \todo{describe all classes}
+  \item{Setup Overhead}{Time}
+  \item{Performance}{Performance} split into learning performance
+\end{itemize}
+\todo{give 2-3 concrete example instantiations here}
+
 \section{Our Model for extractable information}
 \includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+during our inital exploration \& data collection for the Failing Build Log Data Set, wanted to get an impression about the information one would want to extract from a build log
+\begin{itemize}
+  \item \todo{describe all classes}
+  \item{Setup Overhead}{Time}
+  \item{Performance}{Performance} split into learning performance
+\end{itemize}
+\todo{differentiate Travis CI specific things, explain high variability for instantiations}
+\todo{give at least one concrete example instantiation, best from a log in the data set, not too long so maybe it goes in the abstract?, picture/graphic with marked parts here?}
 
@@
 \includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
+\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?, describe regex programs}
 
@@
 \includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
+\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}
 
@@
 \includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
+\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}
 
 \section{further techniques}
+\todo{maybe: instantiate model, or at least partly talk about it}
+\todo{diffing, manual regex?, other summarization?, BART? <- we could reference that from related work then}
 

### 2019-10-03 thesis/txt/3-data-set.tex
first complete draft thesis introduction, chapters and structure in separate files
put pictures for explanations in various sections
filling various sections with points on what to write about

--- 2019-10-03 thesis/txt/2-models.tex
@@
 
-\chapter{Information Extraction Techniques}
-overview introduction text
-\label{models}
+\chapter{The Failing Build Logs Data Set}
+\includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
 
-\section{Our Model for IE Techniques}
-\section{Our Model for extraction tasks}
-\section{Our Model for extractable information}
+\label{data-set}
+\section{Motivation}
+originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how strutured or unstructured they are.
+Then labeling of one build log information, namely the reason the build failed, as well as keywords and stuructural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results
 
-\section{PROSE Program Synthesis}
+\section{Log Collector}
+ghtorrent, travis, implementation description, reference CLI interface nicely?
+describe special cases?
+\todo{image! like in travistorrent paper}
 
-\section{IR Similarity}
+\section{Collection Process}
+differentiate original collection and for data set?
+actual instantiation: 30 langs, 3 repos that use Travis, 10 failed logs each -> 80 useable, x logs
+our impression?
+\todo{image!}
 
-\section{Keyword search}
+\section{Labeling (better name?)}
+  \subsection{Build Failure Reason}
 
-\section{further thechniques}
+    \paragraph{Description}
+    WHY?
+one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined extraction   cause that would be simple for PROSE extraction -> better comparability
+    \paragraph{Labeling Process}
+
+  \subsection{Keywords}
+
+    \paragraph{Description}
+
+    \paragraph{Labeling Process}
+
+  \subsection{Categories}
+
+    \paragraph{Description}
+
+    \paragraph{Labeling Process}
+
+\section{Validation of our data set}
+\todo{copy over from md doc}
+
+\subsection{Inter-Rater Reliability}
+
+\subsection{Sending Mails out to developers}
 

### 2019-10-03 thesis/txt/4-tool.tex
first complete draft thesis introduction, chapters and structure in separate files
put pictures for explanations in various sections
filling various sections with points on what to write about

--- 2019-10-03 thesis/txt/2-models.tex
@@
 
-\chapter{Information Extraction Techniques}
-overview introduction text
-\label{models}
+\chapter{Our Information Extraction Tool}
+\label{implementation}
+describe implemantation of Tool
+\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
 
-\section{Our Model for IE Techniques}
-\section{Our Model for extraction tasks}
-\section{Our Model for extractable information}
+\section{common interface} 
+unification tool, reference CLI somehow nicely?,
+ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)
 
 \section{PROSE Program Synthesis}
+implementation details :)
+C#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)
 
 \section{IR Similarity}
+impl details,
+R, text2vec, tokenized vectors, impl of preprocessing?
+don't repeat from IE models section!
 
 \section{Keyword search}
-
-\section{further thechniques}
+impl details,
+R, simple!
 

### 2019-10-03 thesis/txt/5-study.tex
first complete draft thesis introduction, chapters and structure in separate files
put pictures for explanations in various sections
filling various sections with points on what to write about

--- 2019-10-03 thesis/txt/2-models.tex
@@
 
-\chapter{Information Extraction Techniques}
-overview introduction text
-\label{models}
+\chapter{Technique Comparison Study}
+\label{evaluation}
 
-\section{Our Model for IE Techniques}
-\section{Our Model for extraction tasks}
-\section{Our Model for extractable information}
+\section{Study Design}
+\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+\todo{run!}
+how are keywords for the search selected?
 
-\section{PROSE Program Synthesis}
+\section{Study Results}
+\todo{accuracy (or so) of extractions with growing example number // overall averages \& detailed look on special cases //}
 
-\section{IR Similarity}
-
-\section{Keyword search}
-
-\section{further thechniques}
+\section{resulting Reccomending Scheme}
+\todo{draw decision tree}
 

### 2019-10-03 thesis/txt/6-conclusion.tex
first complete draft thesis introduction, chapters and structure in separate files
filling various sections with points on what to write about

--- 2019-10-03 thesis/txt/2-models.tex
@@
 
-\chapter{Information Extraction Techniques}
-overview introduction text
-\label{models}
+\chapter{Conclusion}
+\label{conclusion}
+answer research questions (again)
 
-\section{Our Model for IE Techniques}
-\section{Our Model for extraction tasks}
-\section{Our Model for extractable information}
-
-\section{PROSE Program Synthesis}
-
-\section{IR Similarity}
-
-\section{Keyword search}
-
-\section{further thechniques}
+\section{Future Work}
+\begin{itemize}
+  \item more techniques (which kinds of techniques? express in model! e.g. diffs might not work?), same evaluation, ir automated keyword search/expansion
+  \item other works with data set: what else could this be used for?
+  \item refine / improve techniques with the results automatically obtainable for evaluation with data set
+    \begin{itemize}
+      \item pbe: ranking adjustments, or even new dsl components?
+      \item ir: meta-parameter optimizations
+    \end{itemize}
+  \item socio-technical: how do developers interact with buildlogs?
+\end{itemize}
 

### 2019-10-05 evaluation/evaluate-results.R
vim in docker containers, keyword dockerfile, saving input paths of test examplesets in evaluation results

@@ -32,6 +32,7 @@ getDataFrameForPBEResultsFile <- function(path) {
     
     test <- item[["value"]][[1]][[1]]
     learnedProgram <- xmlValue(test[["LearnedProgram"]][[1]])
+    testInputPath <- xmlValue(tes[["TestInputPath"]][[1]])
     testOutput <- xmlValue(test[["Output"]][[1]])
     desiredTestOutput <-  xmlValue(test[["DesiredOutput"]][[1]])
     accuracy <- 3
@@ -49,6 +50,7 @@ getDataFrameForPBEResultsFile <- function(path) {
       data.frame(
         ExampleCount = exampleCount,
         LearnedProgram = learnedProgram,
+        TestInputPath = testInputPath,
         TestOutput = testOutput,
         DesiredTestOutput = desiredTestOutput,
         Accuracy = accuracy,

### 2019-10-05 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs

@@ -77,6 +77,7 @@ namespace pbeextractionbuildlogs
 			learningStopwatch.Stop();
 			consolePrinter.WriteLine("Learning took " + learningStopwatch.Elapsed);
 			result.LearningDuration = learningStopwatch.Elapsed;
+			result.TestInputPath = inputPath;
 
 			if (topRankedProgram == null)
 			{

### 2019-10-05 pbe-extraction-buildlogs/pbe-extraction-buildlogs/DataClasses.cs

@@ -9,6 +9,7 @@ namespace pbeextractionbuildlogs
 		public string Path { get; set; }
 		public string ProgramName { get; set; }
 		public string LearnedProgram { get; set; }
+		public string TestInputPath { get; set; }
 		public OutputType Output { get; set; }
 		public OutputType DesiredOutput { get; set; }
 		public bool Successful { get; set; }

### 2019-10-05 r-extractions/information-retrieval.R

@@ -111,6 +111,7 @@ run_learning_step <- function(train_examples, test_examples, step_results) {
     subset(test_lines, id %in% names(filtered_similarity_sums))
   step_results[1, "TestOutput"] <-
     join_extracted_lines(extracted_lines[["lines"]])
+  step_results[1, "TestInputPath"] <- train_examples[1, "input_path"]
   
   end_time_application <- Sys.time()
   step_results[1, "ApplicationDuration"] <-

### 2019-10-05 r-extractions/keyword-search.R

@@ -46,7 +46,8 @@ run_keyword_search_step <- function(train_examples, test_examples, step_results)
   step_results[1, "LearnedProgram"] <- paste(selected, collapse = ", ")
 
   end_time_learning <- Sys.time()
-  step_results[1, "LearningDuration"] = sys_timing_to_time(start_time_learning, end_time_learning)
+  step_results[1, "LearningDuration"] <- sys_timing_to_time(start_time_learning, end_time_learning)
+  step_results[1, "TestInputPath"] <- test_examples[1, "input_path"]
 
   start_time_application <- Sys.time()
 

### 2019-10-05 r-extractions/utilities.R

@@ -159,6 +159,7 @@ empty_results_data_frame <- function() {
     data.frame(
       ExampleCount = numeric(),
       LearnedProgram = character(),
+      TestInputPath = character(),
       TestOutput = character(),
       DesiredTestOutput = character(),
       Accuracy = numeric(),

### 2019-10-05 data-collection/dev-mail/devmail.rb
truncate output for mails after 10 lines

@@ -25,6 +25,7 @@ def fill_extraction_data(row)
   # end
 
   output = xml.at("//AnalysisProgramOfRegionAnalysisSessionString/LearningData/Examples/ExampleDataOfString[#{log_index}]/Output")
+  output = output.lines[0, 10].join('') if output.lines.count > 10
   row['output'] = output
 
   jobs_url_job_id = row['job_id'] == 'job_id_not_found' ? 'builds/' + row['build_id'].strip : 'jobs/' + row['job_id'].strip

### 2019-10-05 thesis/txt/0-introduction.tex
filling various sections with points on what to write about
notes in various thesis parts

--- 2019-10-03 thesis/txt/0-intrdouction.tex
@@
 \mention{find more reasons}.
-Second, for reasearchers that can harvest the information contained in the logs (and their metadata) to study the software engineering process of a project.
+Second, for researchers that can harvest the information contained in the logs (and their metadata) to study the software engineering process of a project.
 However they can only harvest the information within the build logs if they can adequately extract the information relevant to them.
@@
 used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI \cite{beller2017oops}, while Vassallo et al.
-wrote a custom parser for Java Maven buildlogs to gather information for build repair hints \cite{vassallo2018un-break}.
+wrote a custom parser for Java Maven build logs to gather information for build repair hints \cite{vassallo2018un-break}.
 Recently Amar et al.
@@
 \begin{itemize}
-  \item{RQ1:} Is Programming by Example suited to extract information from CI build logs?
-  \item{RQ2:} What criteria influence the suitability of an information extraction technique for CI build logs?
-  \item{RQ3:} When are text similarity or keyword search better suited for information extraction from CI build logs?
+  \item[RQ1:] What criteria influence the suitability of an information extraction technique for CI build logs?
+  \item[RQ2:] Is Programming by Example suited to extract information from CI build logs?
+  \item[RQ3:] When are text similarity or keyword search better suited for information extraction from CI build logs?
 \end{itemize}
@@
         \end{itemize}
+  \item Log Collector Tool
   \item A validated data set of about 800 logs from failed Travis CI builds labeled with:

### 2019-10-05 thesis/txt/3-data-set.tex
notes in various thesis parts

@@
 \section{Log Collector}
-ghtorrent, travis, implementation description, reference CLI interface nicely?
-describe special cases?
-\todo{image! like in travistorrent paper}
+To collect a broad range of build logs we built the \texttt{Log Collector} using ruby.
+
+  \subsection{Sampling Repositories}
+  Our first task was to determine a set of repositories to query logs from.
+Our \texttt{GHTorrentParser} can query the GHTorrent dataset for the most popular languages on github and the most popular repositories for a given language.
+\emph{Popularity} in this case is defined as the number of watches.
+Our \texttt{TravisRequester} can then check for a given repository whether it uses Travis CI.
+
+  \subsection{Sampling Builds}
+  The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API, to obtain the newest builds for a given repository.
+As most builds on Travis CI are successful \mention{citation needed} we use a stratified sampling approach: \texttt{TravisRequester} saves the found builds in logs in buckets according to their state.
+We encountered the following states during our data collection passes:
+  \begin{itemize}
+    \item \todo{fill /5 mins/}
+  \end{itemize}
+  \texttt{TravisRequester} saves up to a configured number of builds per state and searches through a configured number of maximum checked builds.
+
+  \subsection{Sampling Logs}
+  For each build the \texttt{TravisRequester} then selects a log to download. Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
+  A single build can consist of multiple jobs, e.g. building and executing tests in various different testing environments.
+  \texttt{TravisRequester} therefore queries each build for a job, which has the same state.
+  A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
+  For the selected jobs, our tool then queries the Travis API V3 and obtains the respective build log.
+
+\todo{image! like in travistorrent paper, /draft 10 mins/}
 
 \section{Collection Process}
-differentiate original collection and for data set?
-actual instantiation: 30 langs, 3 repos that use Travis, 10 failed logs each -> 80 useable, x logs
+For our inital data collection \emdash to get an impression of build logs from various projects and languages \emdash we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
+For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
 our impression?
@@
 \section{Labeling (better name?)}
+For our study, described in Chapter \ref{study}, we want to investigate the extraction capabilities of three techniques.
+Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}.
+Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output.
+Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.
+
   \subsection{Build Failure Reason}

### 2019-10-05 thesis/txt/4-tool.tex
notes in various thesis parts

@@
 implementation details :)
-C#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)
+C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)
 

### 2019-10-05 paper/paper.tex
paper sturcture and introduction ideas

@@
 \subsection{Motivation}
+Many software projects now use continious integration (CI) to improve \mention{reasons to do this, look into Proksch papers}.
+Theses CI builds often produce very long and verbose build logs \mention{log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.
+
+These build logs are a highly valuable data source.
+First of all, for the developers that read them to analyze why their build failed or ..
+\mention{find more reasons}.
+Second, for reasearchers that can harvest the information contained in the logs (and their metadata) to study the software engineering process of a project.
+However they can only harvest the information within the build logs if they can adequately extract the information relevant to them.
+
+There are many different extraction techniques use for this task.
+Beller et al.
+used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI \cite{beller2017oops}, while Vassallo et al.
+wrote a custom parser for Java Maven buildlogs to gather information for build repair hints \cite{vassallo2018un-break}.
+Recently Amar et al.
+greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build.~\cite{amar2019mining} \bp{anecdotal: keyword search?}.
+Apart from those there are various more extraction techniques like searching for keywords, ...
+\todo{more?} \bp{problem which to choose}
+
+With our work we want to support developers, researchers or project managers in deciding which technique is the best one for their use case.
+\todo{describe what we do and our results!}
 \subsection{Contribution}
+\begin{itemize}
+  \item[RQ1:] What criteria influence the suitability of an information extraction technique for CI build logs?
+  \item[RQ2:] Is Programming by Example suited to extract information from CI build logs?
+  \item[RQ3:] When are text similarity or keyword search better suited for information extraction from CI build logs?
+\end{itemize}
 \subsection{Overview}
+This paper first presents an overview over research works related to our topic.
+Then we characterize build logs and different techniques used for extracting information from them.
+We explain our three focus techniques for this work, namely PROSE regular expression program synthesis by example, text similarity and simple keyword search.
+Further, Section \ref{data-set} presents our data set and the labeling and validation process. Section \ref{study} describes our study comparing our three focus techniques.
 
 \section{Related Work}
+similar to before:
+\subsection{Build Log Analysis Tools}
+\subsection{Continuous Integration}
+\subsection{Information Extraction and Retrieval}
+\subsection{Runtime Log Parsing}
+\subsection{Semi-Structured Data?}
 
@@
 \subsection{Characteristics of a Build Log}
-\subsubsection{Model of Extractable Data in Build Logs}
+describe semi-strutcturedness, separate from runtime logs?
+\subsubsection{Extractable Data in Build Logs}
+leave out?
 \subsection{Model for Information Extraction Techniques}
-\subsection{Program Synthesis by Example}
-\subsection{Text Similarity}
-\subsection{Keyword Search}
-
-\section{Our Information Extraction Tool}
-\subsection{Unified Interface}
+picture from thesis: configuration, output accuracy, ...
 \subsection{Program Synthesis by Example}
@@
 \section{The Failing Build Logs Data Set}
+\label{data-set}
 \subsection{Data Structure / Points}
@@
 
-\section{Results}
+\section{Technique Comparison Study}
+\label{study}
 evaluations run \& graphs \& data
+\subsection{Study Design}
 
-\section{Discussion}
+\subsection{Study Execution}
+
+\subsection{Results}
+
+\subsection{Discussion}
 comparing extraction techniques,e

### 2019-10-05 tool/run-extraction.rb
add keyword eval to unification code

@@ -31,7 +31,7 @@ class Optparser
 
     opt_parser = OptionParser.new do |opts|
       opts.banner = 'Usage: ruby run-extraction.rb -a analyze -t <technique: ir, pbe, random> -e <example_set> -p <path_to_file_to_analyze>'
-      opts.separator '       ruby run-extraction.rb -a evaluate -t <technique: ir, pbe> -e <example_set> -s <selection_technique> -l <step_count_for_learning> -c <test_count>'
+      opts.separator '       ruby run-extraction.rb -a evaluate -t <technique: ir, pbe, keyword> -e <example_set> -s <selection_technique> -l <step_count_for_learning> -c <test_count>'
       opts.separator '       ruby run-extraction.rb -a analyze -t keyword -k <keyword, keyword, ...> -p <path_to_file_to_analyze>'
       opts.separator '       ruby run-extraction.rb -a analyze -t regex -r <regex to match extraction> -p <path_to_file_to_analyze>'
 
@@ -129,8 +129,19 @@ class Optparser
   end
 
   def self.print_keyword_options(opts)
-    opt_arr = ['--file', opts.file_path, '--keywords']
-    opt_arr << opts.keywords
+    opt_arr = [opts.action]
+
+    opt_arr << '--verbose' if opts.verbose
+
+    if opts.action == :analyze
+      opt_arr << ['--file', opts.file_path, '--keywords']
+      opt_arr << opts.keywords
+    elsif opts.action == :evaluate
+      opt_arr << '--program' << opts.example_set
+      opt_arr << '--selection' << opts.selection
+      opt_arr << '--learning-step-count' << opts.learning_step_count
+      opt_arr << '--test-count' << opts.test_count
+    end
     opt_arr.join(' ')
   end
 

### 2019-10-06 evaluation/evaluate-results.R
IoU calculated with accuracy, random evaluation coded & in unification tool

@@ -36,6 +36,7 @@ getDataFrameForPBEResultsFile <- function(path) {
     testOutput <- xmlValue(test[["Output"]][[1]])
     desiredTestOutput <-  xmlValue(test[["DesiredOutput"]][[1]])
     accuracy <- 3
+    iou <- 5
     successful <-  as.logical(xmlValue(test[["Successful"]][[1]]))
     learningDuration <-
       nanosecsToTime(as.numeric(xmlValue(test[["LearningDuration"]][[1]])))
@@ -54,6 +55,7 @@ getDataFrameForPBEResultsFile <- function(path) {
         TestOutput = testOutput,
         DesiredTestOutput = desiredTestOutput,
         Accuracy = accuracy,
+        IoU = iou,
         Successful = successful,
         LearningDuration = learningDuration,
         ApplicationDuration = applicationDuration,
@@ -74,15 +76,19 @@ calculate_accuracy <- function(data) {
   for (row in 1:nrow(data)) {
     testOutput <- data[row, "TestOutput"]
     desiredTestOutput <- data[row, "DesiredTestOutput"]
-    
+
     successful <-
       grepl(testOutput, desiredTestOutput, fixed = TRUE)
     data[row, "Successful"] <- as.logical(successful)
-    
-    accuracy <- nchar(testOutput) / nchar(desiredTestOutput)
-    accuracy2 <- stringsim(testOutput, desiredTestOutput)
-    
+
+    accuracy2 <- stringsim(testOutput, desiredTestOutput)✌
     data[row, "Accuracy"] <- accuracy2
+
+    testOutputLines <- stri_split_lines(testOutput)
+    desiredTestOutputLines <- stri_split_lines(desiredTestOutput)
+    intersection_over_union <- length(intersect(testOutputLines, desiredTestOutputLines))/length(union(testOutputLines, desiredTestOutputLines))
+
+    data[row, "IoU"] <- intersection_over_union
   }
   return(data)
 }

### 2019-10-06 r-extractions/information-retrieval.R

@@ -106,7 +106,8 @@ run_learning_step <- function(train_examples, test_examples, step_results) {
   sorted_similarity_sums <- sort(similarity_sums, decreasing = TRUE)
 
   # select the lines to count as extracted
-  filtered_similarity_sums <- sorted_similarity_sums[1:min(10,length(sorted_similarity_sums))] 
+  avg_output_line_count <- avg_output_line_count(train_examples)
+  filtered_similarity_sums <- sorted_similarity_sums[1:min(avg_output_line_count, length(sorted_similarity_sums))] 
   extracted_lines <-
     subset(test_lines, id %in% names(filtered_similarity_sums))
   step_results[1, "TestOutput"] <-

### 2019-10-06 r-extractions/keyword-search.R

@@ -71,13 +71,13 @@ run_keyword_search_extraction <- function() {
   } else if (verb == "evaluate") {
     program <- opt_get("program")
     run_evaluation(program = program,
-                     selection = opt_get("selection"),
-                     include_inputs = opt_get("include-inputs", n = 0),
-                     test_count = as.integer(opt_get("test-count")),
-                     learning_step_count = as.integer(opt_get("learning-step-count")),
-                     verbose = opt_get("verbose", n = 0),
-                     step_method = run_keyword_search_step,
-                     technique = "keyword")
+                   selection = opt_get("selection"),
+                   include_inputs = opt_get("include-inputs", n = 0),
+                   test_count = as.integer(opt_get("test-count")),
+                   learning_step_count = as.integer(opt_get("learning-step-count")),
+                   verbose = opt_get("verbose", n = 0),
+                   step_method = run_keyword_search_step,
+                   technique = "keyword")
   }
 }
 

### 2019-10-06 r-extractions/random-selection.R

@@ -15,20 +15,51 @@ sample_path <<-
 source(paste(main_path, "/r-extractions/utilities.R", sep = ""))
 source(paste(main_path, "/r-extractions/example-set.R", sep = ""))
 
-run_analysis <- function(file, program) {
+run_analysis <- function(file, examples) {
   log <- read_build_log_from_file(file, sample_path)
   lines <- unlist(stri_split_lines(log, omit_empty = TRUE))
 
-  examples <- get_exampleset(program)
-  output_line_counts <- map(examples$output, function (x) str_count(x, "\n") + 1)
-  avg_output_line_count <- mean(unlist(output_line_counts))
+  return(join_extracted_lines(sample(lines, avg_output_line_count(examples))))
+}
 
-  return(join_extracted_lines(sample(lines, avg_output_line_count)))
+run_random_extraction_step <- function(train_examples, test_examples, step_results) {
+  start_time_learning <- Sys.time()
+  avg_output_line_count <- avg_output_line_count(train_examples)
+  step_results[1, "LearnedProgram"] <- paste(avg_output_line_count, collapse = ", ")
+
+  end_time_learning <- Sys.time()
+  step_results[1, "LearningDuration"] <- sys_timing_to_time(start_time_learning, end_time_learning)
+  step_results[1, "TestInputPath"] <- test_examples[1, "input_path"]
+
+  start_time_application <- Sys.time()
+
+  output <- run_analysis(test_examples[1, "input_path"], examples)
+
+  end_time_application <- Sys.time()
+  step_results[1, "ApplicationDuration"] = sys_timing_to_time(start_time_application, end_time_application)
+
+  step_results[1, "TestOutput"] <- output
+  step_results
 }
 
 run_random_selection_extraction <- function() {
-  result <- run_analysis(file = opt_get("file"), program = opt_get("program"))
-  cat(result)
+  verb <- opt_get_verb()
+
+  if (verb == "analyze") {
+    result <- run_analysis(file = opt_get("file"), examples = get_exampleset(opt_get("program")))
+    cat(result)
+  } else if (verb == "evaluate") {
+    program <- opt_get("program")
+    run_evaluation(program = program,
+                   selection = opt_get("selection"),
+                   include_inputs = opt_get("include-inputs", n = 0),
+                   test_count = as.integer(opt_get("test-count")),
+                   learning_step_count = as.integer(opt_get("learning-step-count")),
+                   verbose = opt_get("verbose", n = 0),
[…]

### 2019-10-06 r-extractions/utilities.R

@@ -163,6 +163,7 @@ empty_results_data_frame <- function() {
       TestOutput = character(),
       DesiredTestOutput = character(),
       Accuracy = numeric(),
+      IoU = numeric(),
       Successful = logical(),
       LearningDuration = as.POSIXct(character()),
       ApplicationDuration = as.POSIXct(character()),
@@ -255,4 +256,10 @@ select_keywords_to_search <- function(all_keywords) {
   max_kw <- max(keyword_freq$Freq)
   selected <- keyword_freq[keyword_freq$Freq >= max_kw, ]$filtered_keywords
   return(selected)
+}
+
+avg_output_line_count <- function(examples) {
+  output_line_counts <- map(examples$output, function (x) str_count(x, "\n") + 1)
+  avg_output_line_count <- mean(unlist(output_line_counts))
+  return(avg_output_line_count)
 }

### 2019-10-06 tool/run-extraction.rb

@@ -31,7 +31,7 @@ class Optparser
 
     opt_parser = OptionParser.new do |opts|
       opts.banner = 'Usage: ruby run-extraction.rb -a analyze -t <technique: ir, pbe, random> -e <example_set> -p <path_to_file_to_analyze>'
-      opts.separator '       ruby run-extraction.rb -a evaluate -t <technique: ir, pbe, keyword> -e <example_set> -s <selection_technique> -l <step_count_for_learning> -c <test_count>'
+      opts.separator '       ruby run-extraction.rb -a evaluate -t <technique: ir, pbe, keyword, random> -e <example_set> -s <selection_technique> -l <step_count_for_learning> -c <test_count>'
       opts.separator '       ruby run-extraction.rb -a analyze -t keyword -k <keyword, keyword, ...> -p <path_to_file_to_analyze>'
       opts.separator '       ruby run-extraction.rb -a analyze -t regex -r <regex to match extraction> -p <path_to_file_to_analyze>'
 
@@ -146,7 +146,17 @@ class Optparser
   end
 
   def self.print_random_options(opts)
-    opt_arr = ['--program', opts.example_set, '--file', opts.file_path]
+    opt_arr = [opts.action, '--program', opts.example_set]
+
+    opt_arr << '--verbose' if opts.verbose
+
+    if opts.action == :analyze
+      opt_arr = ['--file', opts.file_path]
+    elsif opts.action == :evaluate
+      opt_arr << '--selection' << opts.selection
+      opt_arr << '--learning-step-count' << opts.learning_step_count
+      opt_arr << '--test-count' << opts.test_count
+    end
     opt_arr.join(' ')
   end
 

### 2019-10-07 thesis/txt/3-data-set.tex
cleaned writing doc

@@
 \section{Collection Process}
-For our inital data collection \emdash to get an impression of build logs from various projects and languages \emdash we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
+For our inital data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
 For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
@@
     \paragraph{Description}
+    learning steps combining keywords -> similar to how devs would learn from reading those models
 

### 2019-10-07 thesis/txt/0-introduction.tex
some thesis corrections to hand in toc & introduction for first review

--- 2019-10-03 thesis/txt/0-intrdouction.tex
@@
 Many software projects now use continious integration (CI) to improve \mention{reasons to do this, look into Proksch papers}.
-Theses CI builds often produce very long and verbose build logs \mention{log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.
+These CI builds often produce very long and verbose build logs \mention{add log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.
 
@@
 \mention{find more reasons}.
-Second, for reasearchers that can harvest the information contained in the logs (and their metadata) to study the software engineering process of a project.
-However they can only harvest the information within the build logs if they can adequately extract the information relevant to them.
+Second, for researchers that can harvest the information contained in the logs -- and their metadata -- to study the software engineering process of a project.
+However they can only utilize the information within the build logs if they can adequately extract the information relevant to them.
 
@@
 Beller et al.
-used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI \cite{beller2017oops}, while Vassallo et al.
-wrote a custom parser for Java Maven buildlogs to gather information for build repair hints \cite{vassallo2018un-break}.
+used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI~\cite{beller2017oops}, while Vassallo et al.
+wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
 Recently Amar et al.
-greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build.~\cite{amar2019mining} \bp{anecdotal: keyword search?}.
+greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.
+\bp{anecdotal: keyword search?}.
 Apart from those there are various more extraction techniques like searching for keywords, ...
-\todo{more?} \bp{problem which to choose}
+\todo{more?} \bp{introduce problem: which one to choose}
 
@@
 
-\plan{what we do in this thesis}
+\plan{what we do in this thesis:}
 
 We aim to define a model to characterize the different extraction techniques and answer what influences the suitability of a technique.
-We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by Example using the Microsoft PROSE library, a common text similarity approach and simple keyword search.
+We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by example using the Microsoft PROSE library, a common text similarity approach and simple keyword search.
 Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this extractions and a categorization of the extractions according to their structural position within the log \todo{is this understandable here?
 leave out?}.
-
-\plan{research questions}
 
@@
 \begin{itemize}
-  \item{RQ1:} Is Programming by Example suited to extract information from CI build logs?
-  \item{RQ2:} What criteria influence the suitability of an information extraction technique for CI build logs?
-  \item{RQ3:} When are text similarity or keyword search better suited for information extraction from CI build logs?
+  \item[\textbf{RQ1:}] What criteria influence the suitability of an information extraction technique for CI build logs?
+  \item[\textbf{RQ2:}] Is Programming by Example suited to extract information from CI build logs?
+  \item[\textbf{RQ3:}] When are text similarity or keyword search better suited for information extraction from CI build logs?
 \end{itemize}
 
-\plan{contributions}
+Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for extraction tasks requiring a high precision, ...
+.
+Extracting information by using text similarity of examples is suitable when ...
+.
+Simple keyword search is suitable ...
+.
+
+\plan{contributions:}
 
@@
         \end{itemize}
+  \item The \emph{LogCollector}, a tool to gather logs from Travis CI
   \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
@@
         \end{itemize}
-  \item An evaluation of our model for the three implemented information extraction techniques \todo{not quite clear \emph{what} we evaluate here}
-  \item A extendable model \todo{really? maybe scheme, decision tree} supporting decision on the three information extraction techniques relative to a given use case scenario
+  \item An evaluation of our model for the three implemented information extraction techniques \todo{describe \emph{what} we look for with this evaluation}
+  \item A extendable sceme supporting decision on (our three) information extraction techniques relative to a given use case scenario
 \end{itemize}
 
-\plan{structure overview}
+\plan{structure overview:}
+
 This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information extraction and retrieval techniques to program synthesis by examples.
-Next, chapter \ref{models} present our models for information extraction techniques, use case scenarios for those and extractable information from CI build logs.
+Next, chapter \ref{models} present our models for information extraction techniques, use case scenarios for such techniques and extractable information from CI build logs.
 It also introduces the three techniques, we focus on during our research evaluation, as well as their theoretical foundations.
-Chapter \ref{data-set} describes the creation of our log data set collected from failed Travis CI build logs, and the labeling and validation process.
-Following, Chapter \ref{implementation} our implementation and the usage of our unified information extraction tool, used for the evaluation study of our models described in Chapter \ref{evaluation}.
-There we also describe the resulting instantiation of our reccomendation model for regex program synthesis, text similarity and keyword search.
+Chapter \ref{data-set} describes the creation of our \emph{The Failing Build Logs Data Set} collected from failed Travis CI build logs, and the labeling and validation process.
+Following, Chapter \ref{implementation} our implementation of the three chosen information extraction techniques and the usage of our unified information extraction tool.
+This tool is also used for the evaluation study of our models described in Chapter \ref{evaluation}.
+There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity and keyword search.
 Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{conclusion}.

### 2019-10-07 thesis/txt/2-models.tex
notes in various thesis parts
some thesis corrections to hand in toc & introduction for first review

@@
 
-\section{Our Model for IE Techniques}
+\section{Characteristics of a Buildlog}
+various tools writing in there, each own internal syntax, no common formatting agreements across tools, Travis Output additional newlines / coloring
+
+\subsection{Comparison to Runtime Logs}
+\todo{or did we do that in related work enough?}
+
+\section{Our Model for Information Extraction Techniques}
 \includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+\plan{model = making a picture with boxes to visualize what we are talking about}
 A build log information extraction technique (BLIE technique) consumes a build log (text file) and produces a certain output (text).
@@
 
-\section{Our Model for extraction tasks}
+\section{Our Model for Information Extraction Tasks}
 \includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
@@
 
-\section{Our Model for extractable information}
+\section{Our Model for Extractable Information in Build Logs}
 \includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
@@
 
-\section{further techniques}
+\section{Further Techniques}
 \todo{maybe: instantiate model, or at least partly talk about it}

### 2019-10-07 thesis/txt/5-study.tex
some thesis corrections to hand in toc & introduction for first review

@@
 \label{evaluation}
+running evaluation to compare the different techniques
 
@@
 \todo{run!}
-how are keywords for the search selected?
+
+taking The Failing Build Log Data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?
 
@@
 
-\section{resulting Reccomending Scheme}
+\section{Resulting Recommending Scheme}
 \todo{draw decision tree}
 
+interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques
+
 \end{document}

### 2019-10-08 evaluation/evaluate-results.R
eval fixes from server

@@ -81,11 +81,11 @@ calculate_accuracy <- function(data) {
       grepl(testOutput, desiredTestOutput, fixed = TRUE)
     data[row, "Successful"] <- as.logical(successful)
 
-    accuracy2 <- stringsim(testOutput, desiredTestOutput)✌
+    accuracy2 <- stringsim(testOutput, desiredTestOutput)
     data[row, "Accuracy"] <- accuracy2
 
-    testOutputLines <- stri_split_lines(testOutput)
-    desiredTestOutputLines <- stri_split_lines(desiredTestOutput)
+    testOutputLines <- stri_split_lines1(testOutput)
+    desiredTestOutputLines <- stri_split_lines1(desiredTestOutput)
     intersection_over_union <- length(intersect(testOutputLines, desiredTestOutputLines))/length(union(testOutputLines, desiredTestOutputLines))
 
     data[row, "IoU"] <- intersection_over_union

### 2019-10-08 r-extractions/information-retrieval.R

@@ -6,6 +6,7 @@ suppressPackageStartupMessages({
   library(dplyr)
   library(text2vec)
   library(optigrab)
+  library(purrr)
 })
 
 main_path <<- "/Users/Laci/Documents/Delft/master-thesis"

### 2019-10-08 r-extractions/random-selection.R

@@ -14,6 +14,7 @@ sample_path <<-
 ## load other modules
 source(paste(main_path, "/r-extractions/utilities.R", sep = ""))
 source(paste(main_path, "/r-extractions/example-set.R", sep = ""))
+source(paste(main_path, "/evaluation/evaluate-results.R", sep = ""))
 
 run_analysis <- function(file, examples) {
   log <- read_build_log_from_file(file, sample_path)
@@ -33,7 +34,7 @@ run_random_extraction_step <- function(train_examples, test_examples, step_resul
 
   start_time_application <- Sys.time()
 
-  output <- run_analysis(test_examples[1, "input_path"], examples)
+  output <- run_analysis(test_examples[1, "input_path"], train_examples)
 
   end_time_application <- Sys.time()
   step_results[1, "ApplicationDuration"] = sys_timing_to_time(start_time_application, end_time_application)
@@ -57,8 +58,7 @@ run_random_selection_extraction <- function() {
                    learning_step_count = as.integer(opt_get("learning-step-count")),
                    verbose = opt_get("verbose", n = 0),
                    step_method = run_random_extraction_step,
-                   technique = "keyword")
-    cat(result)
+                   technique = "random")
   }
 }
 

### 2019-10-08 thesis/txt/1-related-work.tex

@@
 
-\section{Build log analysis and augmentation}
+\section{Build Log Analysis and Augmentation}
 Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs.
@@
 
-\section{Production Log analysis}
+\section{Production Log Analysis}
 \mention{logpai and drain}
@@
 
-\section{Information extraction and retrieval techniques}
+\section{Information Extraction and Retrieval Techniques}
 \review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.

### 2019-10-08 thesis/txt/3-data-set.tex

@@
 
-\section{Labeling (better name?)}
+\section{Labeling}
 For our study, described in Chapter \ref{study}, we want to investigate the extraction capabilities of three techniques.
@@
     \paragraph{Description}
+    for simple keyword search - imitate what users would search for ad-hoc
+
     learning steps combining keywords -> similar to how devs would learn from reading those models
@@
 
-\section{Validation of our data set}
+\section{Validation}
 \todo{copy over from md doc}
@@
 \subsection{Inter-Rater Reliability}
+re-labeling of parts of the labels - cohen's kappa
 
-\subsection{Sending Mails out to developers}
+\subsection{Sending Mails to Developers}
+study description \& results
 

### 2019-10-08 thesis/txt/4-tool.tex

--- 2019-10-03 thesis/txt/2-models.tex
@@
 
-\chapter{Information Extraction Techniques}
-overview introduction text
-\label{models}
+\chapter{Our Information Extraction Tool}
+\label{implementation}
+describe implemantation of Tool
+\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
 
-\section{Our Model for IE Techniques}
-\section{Our Model for extraction tasks}
-\section{Our Model for extractable information}
+\section{Common Interface} 
+unification tool, reference CLI somehow nicely?,
+
+ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)
 
 \section{PROSE Program Synthesis}
+implementation details :)
+
+C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)
 
 \section{IR Similarity}
+impl details,
+
+R, text2vec, tokenized vectors, impl of preprocessing?
+
+don't repeat from IE models section!
 
 \section{Keyword search}
+impl details,
 
-\section{further thechniques}
+R, simple!
 

### 2019-10-08 thesis/txt/0-introduction.tex
literature research about CI and benefits

@@
 \plan{motivate why information extraction from build logs}
-Many software projects now use continious integration (CI) to improve \mention{reasons to do this, look into Proksch papers}.
+Many software projects now use continuous integration (CI)~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
 These CI builds often produce very long and verbose build logs \mention{add log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.

### 2019-10-09 thesis/txt/0-introduction.tex
writing on models chapter, putting pictures into figures, update label names

@@
 This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information extraction and retrieval techniques to program synthesis by examples.
-Next, chapter \ref{models} present our models for information extraction techniques, use case scenarios for such techniques and extractable information from CI build logs.
+Next, chapter \ref{sec:models} present our models for information extraction techniques, use case scenarios for such techniques and extractable information from CI build logs.
 It also introduces the three techniques, we focus on during our research evaluation, as well as their theoretical foundations.
-Chapter \ref{data-set} describes the creation of our \emph{The Failing Build Logs Data Set} collected from failed Travis CI build logs, and the labeling and validation process.
-Following, Chapter \ref{implementation} our implementation of the three chosen information extraction techniques and the usage of our unified information extraction tool.
-This tool is also used for the evaluation study of our models described in Chapter \ref{evaluation}.
+Chapter \ref{sec:data-set} describes the creation of our \emph{The Failing Build Logs Data Set} collected from failed Travis CI build logs, and the labeling and validation process.
+Following, Chapter \ref{sec:implementation} our implementation of the three chosen information extraction techniques and the usage of our unified information extraction tool.
+This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}.
 There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity and keyword search.
-Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{conclusion}.
+Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
 \end{document}

### 2019-10-09 thesis/txt/2-models.tex
writing on models chapter, putting pictures into figures, update label names

@@
 \chapter{Information Extraction Techniques}
-\label{models}
-\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
-Many different information extraction techniques ... this section describes the concepitonal / theoretical results of our thesis ... 
+\label{sec:models}
+%\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
+Many different information extraction techniques ... this section describes the conceptional / theoretical results of our thesis ...
 We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly.
@@
 
-\section{Characteristics of a Buildlog}
-various tools writing in there, each own internal syntax, no common formatting agreements across tools, Travis Output additional newlines / coloring
+\section{Characteristics of a Build Log}
+The idea of CI is, to integrate new software changes fast and often to catch errors early.
+After making a change, the developer commits and pushes it to a shared source code repository.
+Companies often use a specific CI server, e.g.
+Travis CI, linked to their source code repository.
+A CI build might then be triggered by a push on specific branches or after a pull request was created.
+When such a CI build is triggered, it typically runs through these stages:
+\begin{itemize}
+	\item Pulling in the new, changed version of the source code.
+	\item Running static analysis tools~\cite{zampetti2017open}.
+	\item Building the software, i.e. compiling and packaging it~\cite{phillips2014understanding}.
+	\item Running automated tests.
+\end{itemize}
+However these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects \mention{citation needed, zampetti2017open?}.
+Some smaller projects might just use CI to make sure their code compiles as a minimal check before reviewing a pull request, other projects might have various stages of extensive automated testing.
+
+Independent from the actual composition of the CI build process, most software tools used within a build will write out log messages to the console \mention{citation needed, paper about usages of console.log?}.
+Often, the console output is the only means to for a build tool to communicate with its users.
+Tools print progress updates, error and warning messages on the console.
+
+The structure of this output is chosen by every tool themselves.
+Many have implicit or explicit structuring rules, some adhere to predefined standards \mention{phpunit, ruby, xuint output?}.
+However, when anlayzing build logs we might not have access to the exact build configuration (which tools are used in which order) or might not have access to a useable definition of the output sturcture of a specific tool.
+Therefore we describe build logs as semi-structured.
+
+Semi-structured for build logs means for us that the log text is:
+\begin{itemize}
+	\item[implicitly stuructured], we do not have access to explicit structuring elements or an explicit structure description
+	\item[irregular], the structure changes without notice \todo{we saw this in our data collection, random newlines}
+\end{itemize}
 
@@
 
+\section{Our Model for Extractable Information in Build Logs}
+\begin{figure}[h]
+  \centering
+\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+  \caption{Information extractable from build logs}
+  \label{fig:build-log-information-draft}
+\end{figure}
+Continuous integration build logs contain a huge amount of information about the various stages in the CI build they correspond to.
+In this section we present our model to more precisely describe our notion of a information extractable from a CI build log.
+
+A \emph{build log information} for us has:
+\begin{itemize}
+	\item a \emph{textual representation} within the build log, more specifically a substring of the log string
+\end{itemize}
+With this build information items can be hierachically ordered by their textual representations containing each other.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{img/mt-graphics-BuildLogInformation.pdf}
+	\caption{Build Log Information}
+	\label{fig:build-log-information}
+\end{figure}
+During our inital exploration \& data collection for the \emph{Failing Build Log Data Set}, wanted to get an impression about the information one would want to extract from a build log.
+Within the Travis CI build logs we found various different informations possibly interesting to be extracted
+\begin{itemize}
+	\item[Travis Build Step] A Travis CI build consists of several build steps defined within the Travis CI configuration language.
+Within the build log each of these steps are framed by \lstinline{travis_fold:start:<build step name>} and \lstinline{travis_fold:end:<build step name>}.
+	      A build step contains
+	      \begin{itemize}
+		      \item[Build Step Name] The string Travis uses to identify the step within start \& end statements.
+		      \item[Build Step Output] The output generated during the build step. The textual representation of the \texttt{Build Step Output} is the substring between the start \& end statements.
+	      \end{itemize}
+	\item[Travis Timing] Travis can measure the time of specified sections of the build process.
+It represents those by \lstinline{travis_time:start:<timing section id>} and \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
+\end{itemize}
+
+\todo{differentiate Travis CI specific things, explain high variability for instantiations}
+\todo{give at least one concrete example instantiation, best from a log in the data set, not too long so maybe it goes in the abstract?, picture/graphic with marked parts here?}
+
 \section{Our Model for Information Extraction Techniques}
+\begin{figure}[h]
+	\centering
 	\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+	\caption{Model for an information extraction technique}
+	\label{fig:model-ie-technique}
+\end{figure}
 \plan{model = making a picture with boxes to visualize what we are talking about}
@@
 \section{Our Model for Information Extraction Tasks}
+\begin{figure}[h]
+	\centering
 	\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+	\caption{Model for information extraction task}
+	\label{fig:modelt-ie-task}
+\end{figure}
 aims to describe an information extraction task of a developer or a researcher.
@@
 
-\section{Our Model for Extractable Information in Build Logs}
-\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
-during our inital exploration \& data collection for the Failing Build Log Data Set, wanted to get an impression about the information one would want to extract from a build log
-\begin{itemize}
-  \item \todo{describe all classes}
-  \item{Setup Overhead}{Time}
-  \item{Performance}{Performance} split into learning performance
-\end{itemize}
-\todo{differentiate Travis CI specific things, explain high variability for instantiations}
-\todo{give at least one concrete example instantiation, best from a log in the data set, not too long so maybe it goes in the abstract?, picture/graphic with marked parts here?}
-
 \section{PROSE Program Synthesis}
+\begin{figure}[h]
+  \centering
 \includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
+  \caption{Synthesizing regular expression programs by example using PROSE}
+  \label{fig:prose-explanation}
+\end{figure}
 \todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?, describe regex programs}
 
-\section{IR Similarity}
+\section{Text Similarity}
+\begin{figure}[h]
+  \centering
 \includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
+  \caption{Extracting information using text similarity}
+  \label{fig:text-similarity-explanation}
+\end{figure}
 \todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}
@@
 \section{Keyword search}
+\begin{figure}[h]
+  \centering
 \includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
+  \caption{Extracting information using keyword search}
+  \label{fig:keword-search-explanation}
+\end{figure}
 \todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}

### 2019-10-09 thesis/txt/3-data-set.tex
writing on models chapter, putting pictures into figures, update label names

@@
 
-\label{data-set}
+\label{sec:data-set}
 \section{Motivation}
@@
 Then labeling of one build log information, namely the reason the build failed, as well as keywords and stuructural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results
+
+\section{Related Data Sets}
+\todo{kind of related work for data set? the two mortiz sent, more?}
 
@@
 \section{Labeling}
-For our study, described in Chapter \ref{study}, we want to investigate the extraction capabilities of three techniques.
+For our study, described in Chapter \ref{sec:study}, we want to investigate the extraction capabilities of three techniques.
 Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}.

### 2019-10-09 thesis/txt/4-tool.tex
writing on models chapter, putting pictures into figures, update label names

@@
 \chapter{Our Information Extraction Tool}
-\label{implementation}
+\label{sec:implementation}
 describe implemantation of Tool
+\begin{figure}[h]
+	\centering
 	\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+	\caption{Our tool unifying different information extraction techniques for build logs}
+	\label{fig:tool}
+\end{figure}
 
 \section{Common Interface}
+\begin{lstlisting}
+Usage: ruby run-extraction.rb -a analyze -t <technique: ir, pbe, random> -e <example_set> -p <path_to_file_to_analyze>
+       ruby run-extraction.rb -a evaluate -t <technique: ir, pbe, keyword, random> -e <example_set> -s <selection_technique> -l <step_count_for_learning> -c <test_count>
+       ruby run-extraction.rb -a analyze -t keyword -k <keyword, keyword, ...> -p <path_to_file_to_analyze>
+       ruby run-extraction.rb -a analyze -t regex -r <regex to match extraction> -p <path_to_file_to_analyze>
+
+Specific options:
+    -a, --action ACTION              Either run an extraction for a example set ('analyze') or run the whole evaluation of it ('evaluate')
+    -t, --technique TECHNIQUE        The technique used for creating the extraction program (pbe, ir, keyword, random)
+    -e, --example-set EXAMPLE_SET    The filename of the example set to use
+    -p, --path PATH                  The path to the file to be analyzed relative to the 'tool/samples' folder
+    -s, --selection SELECTION        The example sequence selection technique to use for evaluation (chronological, random, manual (= like defined in file))
+    -l, --learning-step-count COUNT  How many steps with increasing example set size to do during evaluation
+    -c, --test-count COUNT           How many test files to evaluate the generated program in each learning step of the evaluation
+    -v, --verbose                    Print additional interesting output apart from only the extraction output
+    -k, --keywords X,Y,Z             Keywords too filter lines for during keyword search based extraction
+    -r, --regex REGEX                Regex to match on build log file content in regex based extraction
+
+Common options:
+    -h, --help                       Show this message
+\end{lstlisting}
 unification tool, reference CLI somehow nicely?,

### 2019-10-11 thesis/txt/2-models.tex
wrting about tool impl and data set data points

@@
 \end{itemize}
+
+\plan{a build consists of various steps, executed by different tools, these are often orchestrated by at least one overarching tool.
+// picture: overarching tool travis and it calls different tools which tehn output sequentiall, travis sometimes outputs something in between -> that is how the build log is made up // we have this structure though it is not always apparent from the build log / edges between the systems can look very different, mostly no agreed model, we: look at differen techniques to extract certain pieces of information \emh{without complete parsing the whole log in to a structure} -> we don't necesarrily want to understand the whole log sturcture just extract one specifi information relevant to us}
 
@@
 	\item{Performance}{Performance} split into learning performance
+	\item \textbf{Configuration Scope} for one repository/project, a language/logkind, global
 \end{itemize}

### 2019-10-11 thesis/txt/3-data-set.tex
wrting about tool impl and data set data points

@@
 
-\section{Labeling}
+\section{Build Failure Reason}
+\todo{WHY?
+one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined extraction   cause that would be simple for PROSE extraction -> better comparability}
+
+\section{Data Model}
 For our study, described in Chapter \ref{sec:study}, we want to investigate the extraction capabilities of three techniques.
@@
 
-  \subsection{Build Failure Reason}
+\subsection{Example Set}
+Our data set is organized in example sets.
+One example set always contains build log in/output examples from the same software repository or project and for one specific build log information.
+They are all from one repository because we investigate information extraction techniques which are always configured to the scope of one particular software repository or project.
+Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.
+
+\subsection{In / Output Example}
+In/output examples (I/O examples) are used to configure two of the information extraction techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
+In our data set they always consist of an \emph{input path}, linking to the build log file which is the input for this example.
+The \emph{output} is a substring of that build log, the textual representation of the targeted build log information within the input build log.
+
+\subsection{Keywords}
+The keyword search is configured by a list of keywords which are searched in the document with plain text search.
+In order to compare it to the two other techniques, each in/output example is associated with a list of 1 - 3 keywords that can be found close to the textual representation of the targeted build log information.
 
 \paragraph{Description}
-    WHY?
-one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined extraction   cause that would be simple for PROSE extraction -> better comparability
-    \paragraph{Labeling Process}
+\todo{for simple keyword search - imitate what users would search for ad-hoc}
 
-  \subsection{Keywords}
-
-    \paragraph{Description}
-    for simple keyword search - imitate what users would search for ad-hoc
-
-    learning steps combining keywords -> similar to how devs would learn from reading those models
-
-    \paragraph{Labeling Process}
+\todo{learning steps combining keywords -> similar to how devs would learn from reading those models}
 
 \subsection{Categories}
+Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
+The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the extraction.
+To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
+If two extractions are at the same structural location with the build log, meaning they are surrounded by a similar markings, the fall into the same category.
+For most cases, two build failure reason examples which fall into one category are outputted either within the same build step or by the same build step tool.
 
-    \paragraph{Description}
+\section{Labeling}
+\subsection{Output Examples: Build Failure Reason}
+We labeled the first occuring substring describing the failure. If there were multiple errors described we took the first continuous block of error description.
 
-    \paragraph{Labeling Process}
+The labeler read or skimmed through build log and copy out the substring describing the reason the build failed.
+Whitespace or special characters were preserved, as they might be crucial for an information extraction technique to detect the desired.
+Because we are using xml to save our example sets, we also had to make sure to escape respective special characters (ampersand, less than).
 
 \section{Validation}
-\todo{copy over from md doc}
+We vaildated our collected labels in two different ways.
+We did a second pass of labeling the build failure reason, keywords and categoies on a subset of the data and compared the results to calculate the inter-rater reliability using cohens kappa.
+In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set and asked them whether our extraction of the log part describing the reason the build failed was correct.
+In the following we describe the results of those two validation studies.
 

### 2019-10-11 thesis/txt/4-tool.tex
wrting about tool impl and data set data points

@@
 \label{sec:implementation}
-describe implemantation of Tool
+We implemented prototypes for our three focus information extraction techniques to evaluate them on our collected build logs.
+This section will present our unified interface and describe the implementation of each of the techniques.
+
 \begin{figure}[h]
@@
 \end{lstlisting}
+As we implemented the information extraction techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interfaces.
+Our unified interface then in turn calls the various different IE techniques over the command line.
+
+We provide two different modes: \emph{analysis} and \emph{evaluation}.
+The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting extraction on the console output.
+The \emph{evaluation} takes an
+
 unification tool, reference CLI somehow nicely?,
@@
 \section{PROSE Program Synthesis}
+The first technique we implemented was the PROSE regular expression program synthesis. As it is based on the PROSE library from Microsoft provided in C\# we also chose C\# for our tool. 
 implementation details :)

### 2019-10-11 thesis/txt/2-models.tex
small fixes in devmail and make thesis compile

--- 2019-10-09 thesis/txt/2-models.tex
@@
 \end{itemize}
+
+\plan{a build consists of various steps, executed by different tools, these are often orchestrated by at least one overarching tool.
+// picture: overarching tool travis and it calls different tools which tehn output sequentiall, travis sometimes outputs something in between -> that is how the build log is made up // we have this structure though it is not always apparent from the build log / edges between the systems can look very different, mostly no agreed model, we: look at differen techniques to extract certain pieces of information \emph{without complete parsing the whole log in to a structure} -> we don't necesarrily want to understand the whole log sturcture just extract one specifi information relevant to us}
 

### 2019-10-11 data-collection/dev-mail/devmail.rb

@@ -98,7 +98,7 @@ def send_mails
 
   mail_groups.each do |mail, rows|
     next if ['no_mail_found', 'no_user_found'].include?(mail)
-    next if rows[0]['language'] != 'Clojure'
+    next if rows[0]['language'] != 'Erlang'
 
     mail_text = ''
     rows.each_with_index do |row, index|
@@ -127,7 +127,7 @@ def send_mails
     end
     puts mail_text
     smail('hey@carolin-brandt.de', mail_text)
-    break
+    # break
   end
 end
 

### 2019-10-11 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisProgram.cs
less output in eval to not hide error messages, random: handle avg output lines longer than example log

@@ -103,7 +103,7 @@ namespace pbeextractionbuildlogs
 
 			if (verbose)
 			{
-				Console.WriteLine(Describe(learningData));
+				//Console.WriteLine(Summarize(learningData));
 			}
 
 			result.AllKeywords = string.Join(", ", learningData.Examples.Select(ex => ex.Keywords));

### 2019-10-11 r-extractions/random-selection.R

@@ -20,7 +20,7 @@ run_analysis <- function(file, examples) {
   log <- read_build_log_from_file(file, sample_path)
   lines <- unlist(stri_split_lines(log, omit_empty = TRUE))
 
-  return(join_extracted_lines(sample(lines, avg_output_line_count(examples))))
+  return(join_extracted_lines(sample(lines, min(avg_output_line_count(examples), length(lines)))))
 }
 
 run_random_extraction_step <- function(train_examples, test_examples, step_results) {

### 2019-10-11 r-extractions/utilities.R

@@ -252,9 +252,9 @@ select_keywords_to_search <- function(all_keywords) {
   }
 
   keyword_freq <- as.data.frame(table(filtered_keywords), stringsAsFactors = FALSE)
-  print(keyword_freq)
   max_kw <- max(keyword_freq$Freq)
   selected <- keyword_freq[keyword_freq$Freq >= max_kw, ]$filtered_keywords
+  print(selected)
   return(selected)
 }
 

### 2019-10-11 evaluation/evaluate-results.R
try to fix stringdist segfault by checking for null string

@@ -81,7 +81,11 @@ calculate_accuracy <- function(data) {
       grepl(testOutput, desiredTestOutput, fixed = TRUE)
     data[row, "Successful"] <- as.logical(successful)
 
-    accuracy2 <- stringsim(testOutput, desiredTestOutput)
+    accuracy2 <- 0
+    if (testOutput != "" || desiredTestOutput != "") {
+      accuracy2 <- stringsim(testOutput, desiredTestOutput)
+    }
+
     data[row, "Accuracy"] <- accuracy2
 
     testOutputLines <- stri_split_lines1(testOutput)

### 2019-10-11 evaluation/evaluate-results.R
also do not call stringsim on nil strings

@@ -82,7 +82,7 @@ calculate_accuracy <- function(data) {
     data[row, "Successful"] <- as.logical(successful)
 
     accuracy2 <- 0
-    if (testOutput != "" || desiredTestOutput != "") {
+    if (testOutput != "" && desiredTestOutput != "" && testOutupt != nil && desiredTestOutput != nil  ) {
       accuracy2 <- stringsim(testOutput, desiredTestOutput)
     }
 

### 2019-10-11 r-extractions/utilities.R

@@ -254,7 +254,6 @@ select_keywords_to_search <- function(all_keywords) {
   keyword_freq <- as.data.frame(table(filtered_keywords), stringsAsFactors = FALSE)
   max_kw <- max(keyword_freq$Freq)
   selected <- keyword_freq[keyword_freq$Freq >= max_kw, ]$filtered_keywords
-  print(selected)
   return(selected)
 }
 

### 2019-10-11 evaluation/evaluate-results.R
fixes for stringsim complie errors

@@ -82,7 +82,7 @@ calculate_accuracy <- function(data) {
     data[row, "Successful"] <- as.logical(successful)
 
     accuracy2 <- 0
-    if (testOutput != "" && desiredTestOutput != "" && testOutupt != nil && desiredTestOutput != nil  ) {
+    if (testOutput != "" && desiredTestOutput != "" && !is.null(testOutput) && !is.null(desiredTestOutput)) {
       accuracy2 <- stringsim(testOutput, desiredTestOutput)
     }
 

### 2019-10-11 evaluation/evaluate-results.R
handle strings too long for strindist

@@ -82,8 +82,12 @@ calculate_accuracy <- function(data) {
     data[row, "Successful"] <- as.logical(successful)
 
     accuracy2 <- 0
-    if (testOutput != "" && desiredTestOutput != "" && !is.null(testOutput) && !is.null(desiredTestOutput)) {
+    if (nchar(testOutput) < 55000 && nchar(desiredTestOutput) < 55000) {
+      print(nchar(testOutput))
+      print(nchar(desiredTestOutput))
       accuracy2 <- stringsim(testOutput, desiredTestOutput)
+    } else {
+      accuracy2 <- -1
     }
 
     data[row, "Accuracy"] <- accuracy2

### 2019-10-15 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs
boild eval files to pbe failures, output debug pbe

@@ -41,6 +41,8 @@ namespace pbeextractionbuildlogs
 		{
 			var inputRegion = AnalysisUtil.RegionFromFile(exampleData.InputPath);
 			var startIndex = inputRegion.S.IndexOf(exampleData.Output, StringComparison.Ordinal);
+			Console.WriteLine(exampleData.InputPath)
+			Console.WriteLine(exampleData.Output)
 			var outputRegion = inputRegion.Slice((uint)startIndex, (uint)(startIndex) + ((uint)exampleData.Output.Length));
 			session.Constraints.Add(new RegionExample(inputRegion, outputRegion));
 

### 2019-10-15 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs
c# has semicolons! 😆

@@ -41,8 +41,8 @@ namespace pbeextractionbuildlogs
 		{
 			var inputRegion = AnalysisUtil.RegionFromFile(exampleData.InputPath);
 			var startIndex = inputRegion.S.IndexOf(exampleData.Output, StringComparison.Ordinal);
-			Console.WriteLine(exampleData.InputPath)
-			Console.WriteLine(exampleData.Output)
+			Console.WriteLine(exampleData.InputPath);
+			Console.WriteLine(exampleData.Output);
 			var outputRegion = inputRegion.Slice((uint)startIndex, (uint)(startIndex) + ((uint)exampleData.Output.Length));
 			session.Constraints.Add(new RegionExample(inputRegion, outputRegion));
 

### 2019-10-15 data-collection/dev-mail/devmail.rb
fixes devmail

@@ -62,15 +62,18 @@ end
 def smail(to, txt)
   # smtp = Net::SMTP.new('srv23.dsbsrv.de', 25)
   # smtp.set_debug_output $stderr
-  Net::SMTP.start('srv23.dsbsrv.de',
-                  25,
-                  'localhost',
-                  Config.config['email']['username'],
-                  Config.config['email']['password'], :plain) do |smtp|
+  server = Net::SMTP.new('postout.lrz.de',
+                         587)
+  server.enable_starttls
+
+  server.start('localhost',
+               Config.config['email']['username'],
+               Config.config['email']['password'], :plain) do |smtp|
     begin
-      smtp.send_message(txt, 'Carolin Brandt <c.e.brandt@tudelft.nl>', to)
+      smtp.send_message(txt, 'carolin.brandt@tum.de', to)
       puts "[#{Time.now}] Sent email to #{to}"
-    rescue
+    rescue => error
+      puts error
       puts "[#{Time.now}] Cannot send email to #{to}"
     end
   end
@@ -81,8 +84,23 @@ def render_erb(template, locals)
   ERB.new(template).result(OpenStruct.new(locals).instance_eval { binding })
 end
 
+
+
 # sends out mails for all entries of the buildcsv
 def send_mails
+  number_to_word = {
+    1 => 'one',
+    2 => 'two',
+    3 => 'three',
+    4 => 'four',
+    5 => 'five',
+    6 => 'six',
+    7 => 'seven',
+    8 => 'eight',
+    9 => 'nine',
+    10 => 'ten'
+  }
+
   csv = CSV.read('dev-mail/builds2.csv', headers: true)
 
   mail_groups = {}
@@ -98,17 +116,17 @@ def send_mails
 
   mail_groups.each do |mail, rows|
     next if ['no_mail_found', 'no_user_found'].include?(mail)
-    next if rows[0]['language'] != 'Erlang'
+    next if rows[0]['language'] != 'xxx'
 
     mail_text = ''
     rows.each_with_index do |row, index|
       dev_name = row['dev_name'] == 'no_username_found' ? '' : row['dev_name'].strip
       jobs_url_job_id = row['job_id'] == 'job_id_not_found' ? 'builds/' + row['build_id'].strip : 'jobs/' + row['job_id'].strip
       replacement = {
-        email: 'hey@carolin-brandt.de', # row['email'].strip,
+        email: mail.strip,
         build_num: row['build_number'].strip,
         repo_name: row['repository_name'].strip,
[…]

### 2019-10-15 thesis/txt/0-introduction.tex
[wip] toc corrections

@@
   \item[\textbf{RQ1:}] What criteria influence the suitability of an information extraction technique for CI build logs?
-  \item[\textbf{RQ2:}] Is Programming by Example suited to extract information from CI build logs?
-  \item[\textbf{RQ3:}] When are text similarity or keyword search better suited for information extraction from CI build logs?
+  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to extract information from CI build logs?
+  \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
+  \item[\textbf{RQ2.2:}] How accurate are the extractions of PBE, TS and SKWS?
+  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
 \end{itemize}

### 2019-10-15 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs
escape for continuous newlines in example sets

@@ -42,7 +42,6 @@ namespace pbeextractionbuildlogs
 			var inputRegion = AnalysisUtil.RegionFromFile(exampleData.InputPath);
 			var startIndex = inputRegion.S.IndexOf(exampleData.Output, StringComparison.Ordinal);
 			Console.WriteLine(exampleData.InputPath);
-			Console.WriteLine(exampleData.Output);
 			var outputRegion = inputRegion.Slice((uint)startIndex, (uint)(startIndex) + ((uint)exampleData.Output.Length));
 			session.Constraints.Add(new RegionExample(inputRegion, outputRegion));
 

### 2019-10-16 thesis/txt/0-introduction.tex
writing about prose technique and some literature notes

@@
 \chapter{Introduction}
-\plan{motivate why information extraction from build logs}
-Many software projects now use continuous integration (CI)~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
-These CI builds often produce very long and verbose build logs \mention{add log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.
+%Many s These CI builds often produce very long and verbose build logs \mention{add log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.
 
-These build logs are a highly valuable data source.
+%These build logs are a highly valuable data source.
 First of all, for the developers that read them to analyze why their build failed or ..
@@
 
-There are many different extraction techniques use for this task.
+%There are many different extraction techniques use for this task.
 Beller et al.
@@
 
-With our work we want to support developers, researchers or project managers in deciding which technique is the best one for their use case.
+%With our work we want to support developers, researchers or project managers in deciding which technique is the best one for their use case. 
+Continuous Integration (CI) has become a best practice in software engineering and many software projects now use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
+A build on a CI server typically not only compiles and packages the software, but also executes test~\cite{beller2017oops} and various kinds of static analysis~\cite{zampetti2017open}.
 
-\plan{what we do in this thesis:}
+CI builds often produce very long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build.
+The structure of these logs changes greatly from project to project and highly depends on the tools and environment used.
+Build logs are a highly valuable data source. First of all, for the developers that read them to analyze why their build failed or how different stages of the build process perform.
+Second, for researchers that can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project.
+However these two groups can only utilize the information within the build logs if they can adequately extract the information relevant to them.
+
+There are many different extraction techniques used for this task.
+Beller et al.
+used regular expressions when analyzing the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
+Such regular expressions are developed by looking at a few exemplary build logs and maintaining them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
+Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
+Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.
+
+Currently we only have anecdotal evidence on the performance of these techniques and when to use which.
+Developers and researches have little support while choosing which one to use for an extraction task.
+Our goal for this thesis is to investigate different information extraction techniques and describe under which circumstances we recommend each of the techniques.
 
 We aim to define a model to characterize the different extraction techniques and answer what influences the suitability of a technique.
-We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by example using the Microsoft PROSE library, a common text similarity approach and simple keyword search.
-Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this extractions and a categorization of the extractions according to their structural position within the log \todo{is this understandable here?
-leave out?}.
+We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by example using the Microsoft PROSE library (referred to as PBE), a common text similarity approach (referred to as TS) and simple keyword search (referred to as SKWS).
+Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this extractions and a categorization of the extractions according to their structural position within the log.
 
 We aim to answer the following research questions:
-
 \begin{itemize}
@@
 
+\plan{results and conclusions of my work}
 Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for extraction tasks requiring a high precision, ...
@@
 
-\plan{contributions:}
-
-Our work contributes:
-
+\paragraph{Our work contributes:}
 \begin{itemize}
-  \item A model to characterize information extraction techniques from \todo{CI?} build logs
+  \item A model of the extractable information in CI build logs
+  \item A model to characterize information extraction techniques from CI build logs
   \item A model to characterize use case scenarios for information extraction from CI build logs
-  \item A model of the extractable information in CI build logs
   \item A tool unifying several information extraction techniques namely:
         \begin{itemize}
-          \item our implementation of regular expression program synthesis using the Microsoft PROSE library,
-          \item a common information retrieval approach using text similarity, and
-          \item a simple keyword search approach
+          \item our implementation of regular expression program synthesis using the Microsoft PROSE library (PBE),
+          \item a common information retrieval approach using text similarity (TS), and
+          \item a simple keyword search approach (SKWS)
         \end{itemize}
-  \item The \emph{LogCollector}, a tool to gather logs from Travis CI
+  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
   \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
@@
   \item An evaluation of our model for the three implemented information extraction techniques \todo{describe \emph{what} we look for with this evaluation}
-  \item A extendable sceme supporting decision on (our three) information extraction techniques relative to a given use case scenario
+  \item A extendable scheme supporting decision on (our three) information extraction techniques relative to a given use case scenario
 \end{itemize}
-
-\plan{structure overview:}
 

### 2019-10-16 thesis/txt/1-related-work.tex
writing on models chapter, putting pictures into figures, update label names
[wip] toc corrections
writing about prose technique and some literature notes

@@
 \chapter{Related Work}
+\label{sec:rw}
 \todo{introduction \& glue text}
@@
 
-\section{Continuous Integration Research}
+\section{Continuous Integration}
 \mention{look into proksch papers}
@@
 \section{Production Log Analysis}
-\mention{logpai and drain}
+\mention{logpai and drain, [7] K. Fisher and D. Walker. The pads project: an overview. In ICDT,
+2011.
+[8] K. Fisher, D. Walker, K. Q. Zhu, and P. White. From dirt to shovels:
+fully automatic tool generation from ad hoc data. In POPL, 2008.[23] Q. Xi and D. Walker. A context-free markup language for semi- structured text. In PLDI, pages 221–232, 2010.
+ The PADS project [7] has en- abled simplification of ad hoc data processing tasks for programmers
+accounts addresses split chairs awk banks companies countries hadoop horses instruments ls-l mgx namephone nozzle numbertext papers pldi12 pldi13 pop13 quotes speechbench techfest ucla-faculty users
+accounts addresses split chairs awk banks companies countries hadoop horses instruments ls-l mgx namephone nozzle numbertext papers pldi12 pldi13 pop13 quotes speechbench techfest ucla-faculty users
+abt amazon apple barnes bestbuy bigtray bol buy cameraword cnet cooking-bw dealtime drugstore ebay mgzoutlet mediaworld nthbutsw powells googlepdct yahooshop shopping shopzilla target tigerdirect venere
+abt amazon apple barnes bestbuy bigtray bol buy cameraword cnet cooking-bw dealtime drugstore ebay mgzoutlet mediaworld nthbutsw powells googlepdct yahooshop shopping shopzilla target tigerdirect venere
+hg_ex12 hg_ex18 hg_ex2 hg_ex26 hg_ex29 hg_ex3 hg_ex39 _h8d62ck1* 03PFMJOU* 2003Fall 64040 anrep9899* bali ch15_e compliance* DataDiction* deliverable* e_Bubble_* flip_usd5 Funded - F ge-revenues HOSPITAL* pwpSurvey* SOA4-YEAR* young_table
+hg_ex12 hg_ex18 hg_ex2 hg_ex26 hg_ex29 hg_ex3 hg_ex39 _h8d62ck1* 03PFMJOU* 2003Fall 64040 anrep9899* bali ch15_e compliance* DataDiction* deliverable* e_Bubble_* flip_usd5 Funded - F ge-revenues HOSPITAL* pwpSurvey* SOA4-YEAR* young_table
+seconds
+# examples
+seconds
+examples
+seconds
+examples
+by contributing along several dimensions: development of domain specific languages for describing text structure or data format, learn- ing algorithms for automatically inferring such formats [8], and a markup language to allow users to add simple annotations to enable more effective learning of text structure [23] While PADS supports parsing of entire files, FlashExtract allows users to extract only parts of the file thereby avoiding unnecessary complications.
+PADS’s learner only supports a fixed line-by-line chunking strategy to split the records; in contrast, FlashExtract can learn chunking (aka, struc- ture boundaries) from examples, making it suitable for extracting data fields and records that have arbitrary length (and might cross multiple lines).
+Finally, PADS primarily targets ad hoc text files.
+Although one can view webpages and spreadsheet as text files, it is unclear if the PADS learning algorithm can be adapted to work effectively for webpages and spreadsheets.
+}
 

### 2019-10-16 thesis/txt/2-models.tex
[wip] toc corrections
writing about prose technique and some literature notes

@@
 \section{Characteristics of a Build Log}
-The idea of CI is, to integrate new software changes fast and often to catch errors early.
+The idea of CI is, to integrate new software changes fast and often to catch errors early~\cite{humble2010continuous}.
 After making a change, the developer commits and pushes it to a shared source code repository.
@@
 \begin{itemize}
-	\item[implicitly stuructured], we do not have access to explicit structuring elements or an explicit structure description
-	\item[irregular], the structure changes without notice \todo{we saw this in our data collection, random newlines}
+	\item \textbf{implicitly stuructured}, we do not have access to explicit structuring elements or an explicit structure description
+	\item \textbf{irregular}, the structure changes without notice \todo{we saw this in our data collection, random newlines}
 \end{itemize}
@@
 
-\subsection{Comparison to Runtime Logs}
-\todo{or did we do that in related work enough?}
-
-\section{Our Model for Extractable Information in Build Logs}
+\section{Extractable Information in Build Logs}
 \begin{figure}[h]
@@
 \begin{itemize}
-	\item[Travis Build Step] A Travis CI build consists of several build steps defined within the Travis CI configuration language.
+	\item \textbf{Travis Build Step} A Travis CI build consists of several build steps defined within the Travis CI configuration language.
 Within the build log each of these steps are framed by \lstinline{travis_fold:start:<build step name>} and \lstinline{travis_fold:end:<build step name>}.
@@
 	      \begin{itemize}
-		      \item[Build Step Name] The string Travis uses to identify the step within start \& end statements.
-		      \item[Build Step Output] The output generated during the build step. The textual representation of the \texttt{Build Step Output} is the substring between the start \& end statements.
+		      \item \textbf{Build Step Name} The string Travis uses to identify the step within start \& end statements.
+		      \item \textbf{Build Step Output} The output generated during the build step. The textual representation of the \texttt{Build Step Output} is the substring between the start \& end statements.
 	      \end{itemize}
-	\item[Travis Timing] Travis can measure the time of specified sections of the build process.
+	\item \textbf{Travis Timing} Travis can measure the time of specified sections of the build process.
 It represents those by \lstinline{travis_time:start:<timing section id>} and \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
@@
 
-\section{Our Model for Information Extraction Techniques}
+\section{Characteristics of Information Extraction Techniques}
 \begin{figure}[h]
@@
 \end{figure}
-\plan{model = making a picture with boxes to visualize what we are talking about}
+For this thesis we want to evaluate different Information Extraction Techniques in their application to CI build logs.
+We focus on techniques that do not attempt or require to parse the structure of a whole build log, but rather focus on extracting just one specific information
 A build log information extraction technique (BLIE technique) consumes a build log (text file) and produces a certain output (text).
@@
 \begin{itemize}
-	\item{Target}{Extractable Information} each extraction technique \todo{instantiation!} targets a specific information
-	\item{Setup Overhead}{Time}
-	\item{Performance}{Performance} split into learning performance
+	\item \textbf{Target}{Extractable Information} each extraction technique \todo{instantiation!} targets a specific information
+	\item \textbf{Setup Overhead}{Time}
+	\item \textbf{Performance}{Performance} split into learning performance
 	\item \textbf{Configuration Scope} for one repository/project, a language/logkind, global
@@
 
-\section{Our Model for Information Extraction Tasks}
+\section{Information Extraction Tasks}
 \begin{figure}[h]
@@
 \end{figure}
+\subsection{Overview}
+\emph{Programming by Example (PBE)} is a technique where programs are synthesized according to in and output examples provided by the user.
+It enables users to create programs without requiring programming knowledge~\cite{mayer2015user}.
+Applied A to the task of text extraction through regular expressions it relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
+We chose to investigate the applicability of generating regular expression programs by example to extracting information from build logs.
+In this work we refer to our interpretation of this technique as \emph{PBE}.
+\todo{distinguish PBE for buildlogs}
+
+Generally, we are interested in whether a Programming by Example could replace manually writing regular expressions.
+Writing and especially maintaining regular expressions is known to be a difficult, tedious and error-prone task~\cite{michael2019regexes}.
+There are two ways to approach this question: from the usability side or the technical side.
+
+When studying the applicability of PBE from the \emph{usability} perspective you run into questions like
+\begin{itemize}
+	\item Are users faster when using PBE compared to manual regex construction?
+	\item Are users more comfortable using PBE over manual regex construction?
+	\item Are users confident in the resulting regular expression program from PBE?
+	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
+\end{itemize}
+Some of these were already evaluated in existing works about PBE and user interaction~\cite{mayer2015user} \mention{other works?}.
+Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
+Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on syntesizing programs from examples in an unknow interface.
+Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
+We feel such questions of usability can be answered separately from the application domain of build logs.
+
+For our work we chose to look at the applicability of PBE from the \emph{technical} perspective.
+We investigate whether current program synthesis techniques are able to learn programs for information extraction tasks in the domain of CI build logs.
+Furthermore we gather insights in how PBE has to be applied to yield useable results and perform best.
+Our implementation of PBE \todo{which we name technique name x}, is mainly based on the Flash Extract DSL~\cite{flahsextractpaper} of the PROSE library by Microsoft\mention{cite prose website}.
+Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
+In the following we will explain the concept of how we apply PBE to information extraction from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.
+
+\subsection*{Configuration / Input / Output}
+In/Output examples (I/O examples) are the main driver of Programming by Example.
+When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
+In the implementation we did have to apply a few text replacements as described in \ref{sec:impl-preprocessing}.
+The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the syntesized program when given the corresponding input file.
+One or multiple I/O examples are needed as configuration for PBEBL, they are used to define substring of a log should be extracted.
+For execution PBEBL takes a build file as input and returns a substring of the build file content.
+
+\subsection*{Synthesizing Programs with Flash Extract}
+\todo{maybe scrap this section / incorporate last sentence somewhere else, expalnation will mostly be in rw. How to usefully sturcture the stuff above this?}
+In the following we want to give an impression on how the PROSE library and specifically the Flash Extract DSL synthesize programs for extracting substrings from text via regular expressions.
+\todo{how much can/should we explain here?
+possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
+Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm. Both are described in \todo{ref rw sections}.
+
+\subsection*{Model instantiation}
+
 \todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?, describe regex programs}
@@
 \end{figure}
+\paragraph{Overview}
+Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}.
+We describe CI build logs as semi-structured,
 \todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}

### 2019-10-16 thesis/txt/4-tool.tex
[wip] toc corrections
writing about prose technique and some literature notes

@@
 
-\chapter{Our Information Extraction Tool}
+\chapter{Information Extraction Tool}
 \label{sec:implementation}
@@
 
+\section{Overall Implementation Remarks}
+There are multiple implementation specialities that span over all languages, frameworks and implemented techniques.
+The following section discusses preprocessing and escaping of the parsed build log files / example sets, as well as ... \todo{more?}
+
+\subsection{Preprocessing Log Text}
+\label{sec:impl-preprocessing}
+
 \section{PROSE Program Synthesis}
+\label{sec:impl-pbe}
 The first technique we implemented was the PROSE regular expression program synthesis. As it is based on the PROSE library from Microsoft provided in C\# we also chose C\# for our tool. 

### 2019-10-16 thesis/txt/0-introduction.tex
ie -> ir

@@
 
-%There are many different extraction techniques use for this task.
+%There are many different retrieval techniques use for this task.
 Beller et al.
@@
 \bp{anecdotal: keyword search?}.
-Apart from those there are various more extraction techniques like searching for keywords, ...
+Apart from those there are various more retrieval techniques like searching for keywords, ...
 \todo{more?} \bp{introduce problem: which one to choose}
@@
 
-There are many different extraction techniques used for this task.
+There are many different retrieval techniques used for this task.
 Beller et al.
@@
 Currently we only have anecdotal evidence on the performance of these techniques and when to use which.
-Developers and researches have little support while choosing which one to use for an extraction task.
-Our goal for this thesis is to investigate different information extraction techniques and describe under which circumstances we recommend each of the techniques.
+Developers and researches have little support while choosing which one to use for an retrieval task.
+Our goal for this thesis is to investigate different information retrieval techniques and describe under which circumstances we recommend each of the techniques.
 
-We aim to define a model to characterize the different extraction techniques and answer what influences the suitability of a technique.
+We aim to define a model to characterize the different retrieval techniques and answer what influences the suitability of a technique.
 We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by example using the Microsoft PROSE library (referred to as PBE), a common text similarity approach (referred to as TS) and simple keyword search (referred to as SKWS).
-Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this extractions and a categorization of the extractions according to their structural position within the log.
+Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this retrievals and a categorization of the retrievals according to their structural position within the log.
 
@@
 \begin{itemize}
-  \item[\textbf{RQ1:}] What criteria influence the suitability of an information extraction technique for CI build logs?
+  \item[\textbf{RQ1:}] What criteria influence the suitability of an information retrieval technique for CI build logs?
   \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to extract information from CI build logs?
   \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
-  \item[\textbf{RQ2.2:}] How accurate are the extractions of PBE, TS and SKWS?
+  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS and SKWS?
   \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
@@
 \plan{results and conclusions of my work}
-Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for extraction tasks requiring a high precision, ...
+Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision, ...
 .
@@
   \item A model of the extractable information in CI build logs
-  \item A model to characterize information extraction techniques from CI build logs
-  \item A model to characterize use case scenarios for information extraction from CI build logs
-  \item A tool unifying several information extraction techniques namely:
+  \item A model to characterize information retrieval techniques from CI build logs
+  \item A model to characterize use case scenarios for information retrieval from CI build logs
+  \item A tool unifying several information retrieval techniques namely:
         \begin{itemize}
@@
           \item keywords developers would use to search for these descriptions of the build failure reason, and
-          \item a categorization of the extractions according to their structural position within the build log
+          \item a categorization of the retrievals according to their structural position within the build log
         \end{itemize}
-  \item An evaluation of our model for the three implemented information extraction techniques \todo{describe \emph{what} we look for with this evaluation}
-  \item A extendable scheme supporting decision on (our three) information extraction techniques relative to a given use case scenario
+  \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
+  \item A extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
 \end{itemize}
 
-This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information extraction and retrieval techniques to program synthesis by examples.
-Next, chapter \ref{sec:models} present our models for information extraction techniques, use case scenarios for such techniques and extractable information from CI build logs.
+This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information retrieval techniques to program synthesis by examples.
+Next, chapter \ref{sec:models} present our models for information retrieval techniques, use case scenarios for such techniques and extractable information from CI build logs.
 It also introduces the three techniques, we focus on during our research evaluation, as well as their theoretical foundations.
 Chapter \ref{sec:data-set} describes the creation of our \emph{The Failing Build Logs Data Set} collected from failed Travis CI build logs, and the labeling and validation process.
-Following, Chapter \ref{sec:implementation} our implementation of the three chosen information extraction techniques and the usage of our unified information extraction tool.
+Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
 This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}.

### 2019-10-16 thesis/txt/1-related-work.tex
ie -> ir

@@
 Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation.
-We differentiate our work from the more common production runtime log analysis and cover different information extraction and retrieval techniques.
+We differentiate our work from the more common production runtime log analysis and cover different information retrieval techniques.
 Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.
@@
 They observed that highlighting the locality and context of an issue is helpful to programmers.
-We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.
+We strive to enable a similar summarization by text retrieval while also covering a wider array of programming languages.
+\todo{reference their new paper}
 
@@
 
-\section{Information Extraction and Retrieval Techniques}
+\section{Information retrieval and Retrieval Techniques}
 \review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
@@
 \section{Program Synthesis by Example}
+\todo{how much can/should we explain here?
+possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
 \review{
@@
 
-We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information extraction.
+We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information retrieval.
 }

### 2019-10-16 thesis/txt/3-data-set.tex
ie -> ir

@@
 \todo{WHY?
-one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined extraction   cause that would be simple for PROSE extraction -> better comparability}
+one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined retrieval   cause that would be simple for PROSE retrieval -> better comparability}
 
 \section{Data Model}
-For our study, described in Chapter \ref{sec:study}, we want to investigate the extraction capabilities of three techniques.
+For our study, described in Chapter \ref{sec:study}, we want to investigate the retrieval capabilities of three techniques.
 Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}.
@@
 One example set always contains build log in/output examples from the same software repository or project and for one specific build log information.
-They are all from one repository because we investigate information extraction techniques which are always configured to the scope of one particular software repository or project.
+They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
 Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.
@@
 \subsection{In / Output Example}
-In/output examples (I/O examples) are used to configure two of the information extraction techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
+In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
 In our data set they always consist of an \emph{input path}, linking to the build log file which is the input for this example.
@@
 Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
-The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the extraction.
+The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
 To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
-If two extractions are at the same structural location with the build log, meaning they are surrounded by a similar markings, the fall into the same category.
+If two retrievals are at the same structural location with the build log, meaning they are surrounded by a similar markings, the fall into the same category.
 For most cases, two build failure reason examples which fall into one category are outputted either within the same build step or by the same build step tool.
@@
 The labeler read or skimmed through build log and copy out the substring describing the reason the build failed.
-Whitespace or special characters were preserved, as they might be crucial for an information extraction technique to detect the desired.
+Whitespace or special characters were preserved, as they might be crucial for an information retrieval technique to detect the desired.
 Because we are using xml to save our example sets, we also had to make sure to escape respective special characters (ampersand, less than).
@@
 We did a second pass of labeling the build failure reason, keywords and categoies on a subset of the data and compared the results to calculate the inter-rater reliability using cohens kappa.
-In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set and asked them whether our extraction of the log part describing the reason the build failed was correct.
+In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set and asked them whether our retrieval of the log part describing the reason the build failed was correct.
 In the following we describe the results of those two validation studies.

### 2019-10-16 thesis/txt/4-tool.tex
ie -> ir

@@
 
-\chapter{Information Extraction Tool}
+\chapter{Information Retrieval Tool}
 \label{sec:implementation}
-We implemented prototypes for our three focus information extraction techniques to evaluate them on our collected build logs.
+We implemented prototypes for our three focus information retrieval techniques to evaluate them on our collected build logs.
 This section will present our unified interface and describe the implementation of each of the techniques.
@@
 	\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
-	\caption{Our tool unifying different information extraction techniques for build logs}
+	\caption{Our tool unifying different information retrieval techniques for build logs}
 	\label{fig:tool}
@@
 Specific options:
-    -a, --action ACTION              Either run an extraction for a example set ('analyze') or run the whole evaluation of it ('evaluate')
-    -t, --technique TECHNIQUE        The technique used for creating the extraction program (pbe, ir, keyword, random)
+    -a, --action ACTION              Either run an retrieval for a example set ('analyze') or run the whole evaluation of it ('evaluate')
+    -t, --technique TECHNIQUE        The technique used for creating the retrieval program (pbe, ir, keyword, random)
     -e, --example-set EXAMPLE_SET    The filename of the example set to use
@@
     -c, --test-count COUNT           How many test files to evaluate the generated program in each learning step of the evaluation
-    -v, --verbose                    Print additional interesting output apart from only the extraction output
-    -k, --keywords X,Y,Z             Keywords too filter lines for during keyword search based extraction
-    -r, --regex REGEX                Regex to match on build log file content in regex based extraction
+    -v, --verbose                    Print additional interesting output apart from only the retrieval output
+    -k, --keywords X,Y,Z             Keywords too filter lines for during keyword search based retrieval
+    -r, --regex REGEX                Regex to match on build log file content in regex based retrieval
 
@@
 \end{lstlisting}
-As we implemented the information extraction techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interfaces.
+As we implemented the information retrieval techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interfaces.
 Our unified interface then in turn calls the various different IE techniques over the command line.
@@
 We provide two different modes: \emph{analysis} and \emph{evaluation}.
-The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting extraction on the console output.
+The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting retrieval on the console output.
 The \emph{evaluation} takes an

### 2019-10-16 thesis/txt/5-study.tex
writing on models chapter, putting pictures into figures, update label names
[wip] toc corrections
ie -> ir

@@
 \chapter{Technique Comparison Study}
-\label{evaluation}
+\label{sec:study}
+\section{Introduction}
 running evaluation to compare the different techniques
 
-\section{Study Design}
+\section{Method}
+\begin{figure}[h]
+	\centering
 	\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+	\caption{Process of our technique comparison study}
+	\label{fig:study}
+\end{figure}
 \todo{run!}
@@
 
-\section{Study Results}
-\todo{accuracy (or so) of extractions with growing example number // overall averages \& detailed look on special cases //}
+\section{Results}
+\todo{accuracy (or so) of retrievals with growing example number // overall averages \& detailed look on special cases //}
 
-\section{Resulting Recommending Scheme}
+\section{Discussion}
 \todo{draw decision tree}
@@
 interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques
+\section{Threats to Validity}
 

### 2019-10-16 data-collection/dev-mail/devmail.rb
remove bcc from devmail, boil down pbe failing logs more

@@ -129,7 +129,7 @@ def send_mails
         dev_name: dev_name.split(' ')[0]&.strip,
         commit_sha_short: row['commit_sha'].strip[0..7],
         commit_sha_long: row['commit_sha'],
-        commit_date: Time.parse(row['commit_date'].strip).httpdate,
+        commit_date: Time.parse(row['commit_date']&.strip).httpdate,
         extraction: row['output'].strip,
         repo_owner: row['repository_owner'].strip,
         build_id: row['build_id'].strip,
@@ -148,7 +148,6 @@ def send_mails
     mail_text += post_text
     puts 'sent mail to ' + mail.strip + ' with language ' + rows[0]['language'] + ' and repo ' + rows[0]['repo_slug']
     smail(mail.strip, mail_text)
-    break
   end
 end
 

### 2019-10-16 thesis/txt/0-introduction.tex
fixes from Taicos introduction review

@@
 %With our work we want to support developers, researchers or project managers in deciding which technique is the best one for their use case. 
-Continuous Integration (CI) has become a best practice in software engineering and many software projects now use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
-A build on a CI server typically not only compiles and packages the software, but also executes test~\cite{beller2017oops} and various kinds of static analysis~\cite{zampetti2017open}.
+Continuous Integration (CI) has become a best practice in software engineering.
+Many software projects now use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
+A build on a CI server typically not only compiles and packages the software, but also executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.
 
-CI builds often produce very long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build.
-The structure of these logs changes greatly from project to project and highly depends on the tools and environment used.
-Build logs are a highly valuable data source. First of all, for the developers that read them to analyze why their build failed or how different stages of the build process perform.
-Second, for researchers that can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project.
-However these two groups can only utilize the information within the build logs if they can adequately extract the information relevant to them.
+CI builds produce long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build.
+The structure of these logs changes greatly from project to project~\cite{staahl2014modeling} as it highly depends on the tools and environment used.
+Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform.
+Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project.
+However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.
 
-There are many different retrieval techniques used for this task.
+There are different retrieval techniques used to retrieve information from CI build logs.
 Beller et al.
-used regular expressions when analyzing the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at a few exemplary build logs and maintaining them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
+use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
+In general, such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
 Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
-Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.
+Recently, Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.
 
-Currently we only have anecdotal evidence on the performance of these techniques and when to use which.
-Developers and researches have little support while choosing which one to use for an retrieval task.
-Our goal for this thesis is to investigate different information retrieval techniques and describe under which circumstances we recommend each of the techniques.
+Currently there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
+Developers and researches have little support while choosing which technique to use for an retrieval task.
+The goal for this thesis is to investigate different information retrieval techniques and describe under which circumstances we recommend each of the techniques.
 
 We aim to define a model to characterize the different retrieval techniques and answer what influences the suitability of a technique.
-We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by example using the Microsoft PROSE library (referred to as PBE), a common text similarity approach (referred to as TS) and simple keyword search (referred to as SKWS).
-Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this retrievals and a categorization of the retrievals according to their structural position within the log.
+We support our assumption by implementing and evaluating three techniques:
+\begin{itemize}
+  \item regular expression synthesis by example using the Microsoft PROSE library (referred to as PBE),
+  \item a common text similarity approach (referred to as TS) and
+  \item simple keyword search (referred to as SKWS)
+\end{itemize}
+To evaluate these techniques we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
+Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.
 
@@
 \begin{itemize}
-  \item[\textbf{RQ1:}] What criteria influence the suitability of an information retrieval technique for CI build logs?
-  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to extract information from CI build logs?
+  \item[\textbf{RQ1:}] Which criteria influence the suitability of an information retrieval technique for CI build logs?
+  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to retrieve information from CI build logs?
   \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
@@
 .
-Extracting information by using text similarity of examples is suitable when ...
+Retrieving information by using text similarity of examples is suitable when ...
 .
@@
 \begin{itemize}
-  \item A model of the extractable information in CI build logs
+  \item A model of the retrievable information in CI build logs
   \item A model to characterize information retrieval techniques from CI build logs
@@
 This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information retrieval techniques to program synthesis by examples.
-Next, chapter \ref{sec:models} present our models for information retrieval techniques, use case scenarios for such techniques and extractable information from CI build logs.
-It also introduces the three techniques, we focus on during our research evaluation, as well as their theoretical foundations.
-Chapter \ref{sec:data-set} describes the creation of our \emph{The Failing Build Logs Data Set} collected from failed Travis CI build logs, and the labeling and validation process.
+Next, chapter \ref{sec:models} present our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs.
+It also introduces the three techniques, we focus on during our research evaluation.
+Chapter \ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
 Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.

### 2019-10-16 thesis/txt/2-models.tex
fixes from Taicos introduction review

@@
 
-\chapter{Information Extraction Techniques}
+\chapter{Information Retrieval Techniques}
 \label{sec:models}
 %\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
-Many different information extraction techniques ... this section describes the conceptional / theoretical results of our thesis ...
+Many different information retrieval techniques ... this section describes the conceptional / theoretical results of our thesis ...
 We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly.
 Additionally we present a complimentary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
-From our analysis of build logs we share our notion of the extractable information within a build log.
+From our analysis of build logs we share our notion of the retrievable information within a build log.
 
@@
 \plan{a build consists of various steps, executed by different tools, these are often orchestrated by at least one overarching tool.
-// picture: overarching tool travis and it calls different tools which tehn output sequentiall, travis sometimes outputs something in between -> that is how the build log is made up // we have this structure though it is not always apparent from the build log / edges between the systems can look very different, mostly no agreed model, we: look at differen techniques to extract certain pieces of information \emph{without complete parsing the whole log in to a structure} -> we don't necesarrily want to understand the whole log sturcture just extract one specifi information relevant to us}
+// picture: overarching tool travis and it calls different tools which tehn output sequentiall, travis sometimes outputs something in between -> that is how the build log is made up // we have this structure though it is not always apparent from the build log / edges between the systems can look very different, mostly no agreed model, we: look at differen techniques to retrieve certain pieces of information \emph{without complete parsing the whole log in to a structure} -> we don't necesarrily want to understand the whole log sturcture just retrieve one specifi information relevant to us}
 
-\section{Extractable Information in Build Logs}
+\section{Retrievable Information in Build Logs}
 \begin{figure}[h]
@@
 \includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
-  \caption{Information extractable from build logs}
+  \caption{Information retrievable from build logs}
   \label{fig:build-log-information-draft}
@@
 Continuous integration build logs contain a huge amount of information about the various stages in the CI build they correspond to.
-In this section we present our model to more precisely describe our notion of a information extractable from a CI build log.
+In this section we present our model to more precisely describe our notion of a information retrievable from a CI build log.
 
@@
 \end{figure}
-During our inital exploration \& data collection for the \emph{Failing Build Log Data Set}, wanted to get an impression about the information one would want to extract from a build log.
-Within the Travis CI build logs we found various different informations possibly interesting to be extracted
+During our inital exploration \& data collection for the \emph{Failing Build Log Data Set}, wanted to get an impression about the information one would want to retrieve from a build log.
+Within the Travis CI build logs we found various different informations possibly interesting to be retrieved
 \begin{itemize}
@@
 
-\section{Characteristics of Information Extraction Techniques}
+\section{Characteristics of Information Retrieval Techniques}
 \begin{figure}[h]
@@
 	\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
-	\caption{Model for an information extraction technique}
+	\caption{Model for an information retrieval technique}
 	\label{fig:model-ie-technique}
 \end{figure}
-For this thesis we want to evaluate different Information Extraction Techniques in their application to CI build logs.
+For this thesis we want to evaluate different information retrieval techniques in their application to CI build logs.
 We focus on techniques that do not attempt or require to parse the structure of a whole build log, but rather focus on extracting just one specific information
-A build log information extraction technique (BLIE technique) consumes a build log (text file) and produces a certain output (text).
+A build log information retrieval technique (BLIR technique) consumes a build log (text file) and produces a certain output (text).
 \todo{make picture, output can be contained in log or not, can be continuous substring or selected lines etc.}.
 \begin{itemize}
-	\item \textbf{Target}{Extractable Information} each extraction technique \todo{instantiation!} targets a specific information
+	\item \textbf{Target}{Extractable Information} each retrieval technique \todo{instantiation!} targets a specific information
 	\item \textbf{Setup Overhead}{Time}
@@
 
-\section{Information Extraction Tasks}
+\section{Information Retrieval Tasks}
 \begin{figure}[h]
@@
 \end{figure}
-aims to describe an information extraction task of a developer or a researcher.
+aims to describe an information retrieval task of a developer or a researcher.
 \begin{itemize}
@@
 \end{figure}
-\subsection{Overview}
+\subsection*{Overview}
 \emph{Programming by Example (PBE)} is a technique where programs are synthesized according to in and output examples provided by the user.
@@
 For our work we chose to look at the applicability of PBE from the \emph{technical} perspective.
-We investigate whether current program synthesis techniques are able to learn programs for information extraction tasks in the domain of CI build logs.
+We investigate whether current program synthesis techniques are able to learn programs for information retrieval tasks in the domain of CI build logs.
 Furthermore we gather insights in how PBE has to be applied to yield useable results and perform best.
@@
 Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
-In the following we will explain the concept of how we apply PBE to information extraction from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.
+In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.
 
@@
 
-\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?, describe regex programs}
+\todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?, describe regex programs}
 
@@
 We describe CI build logs as semi-structured,
-\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}
+\todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?}
 
-\section{Keyword search}
+\section{Keyword Search}
 \begin{figure}[h]
@@
 \end{figure}
-\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}
+\todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?}
 

### 2019-10-18 thesis/txt/0-introduction.tex
writing loads of stuff on models, semi-structured data in rw, example pictures of build logs

@@
 The structure of these logs changes greatly from project to project~\cite{staahl2014modeling} as it highly depends on the tools and environment used.
-Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform.
-Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project.
+Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform\mention{ citation needed }.
+Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project\mention{ citation needed vassallo beller}.
 However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.
 
-There are different retrieval techniques used to retrieve information from CI build logs.
+There are different techniques used to retrieve information from CI build logs.
 Beller et al.
@@
 Developers and researches have little support while choosing which technique to use for an retrieval task.
-The goal for this thesis is to investigate different information retrieval techniques and describe under which circumstances we recommend each of the techniques.
+The goal for this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.
 
-We aim to define a model to characterize the different retrieval techniques and answer what influences the suitability of a technique.
+We aim to define a model to characterize the different IR techniques as well as the information retrievable from CI build logs.
+For our first research question we analyze which criteria influence the suitability of an IR technique.
 We support our assumption by implementing and evaluating three techniques:
@@
 \end{itemize}
-To evaluate these techniques we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
-Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.
-
-We aim to answer the following research questions:
+Our second research question asks in which cases PBE, TS and SKWS are suited to retrieve information from continuous integration build logs.
+RQ2 is refined sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples the techniques need to perform best, the accuracy of the retrieved output and how diverse the configuring examples can be structurally.
+\begin{simplebox}{Research Questions}
 \begin{itemize}
@@
 \end{itemize}
+\end{simplebox}
+To evaluate PBE, TS and SKWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
+Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.
 
@@
         \begin{itemize}
-          \item our implementation of regular expression program synthesis using the Microsoft PROSE library (PBE),
+          \item regular expression program synthesis from examples using the Microsoft PROSE library (PBE),
           \item a common information retrieval approach using text similarity (TS), and

### 2019-10-18 thesis/txt/1-related-work.tex
fixes from Taicos introduction review
writing loads of stuff on models, semi-structured data in rw, example pictures of build logs

@@
  The PADS project [7] has en- abled simplification of ad hoc data processing tasks for programmers
-accounts addresses split chairs awk banks companies countries hadoop horses instruments ls-l mgx namephone nozzle numbertext papers pldi12 pldi13 pop13 quotes speechbench techfest ucla-faculty users
-accounts addresses split chairs awk banks companies countries hadoop horses instruments ls-l mgx namephone nozzle numbertext papers pldi12 pldi13 pop13 quotes speechbench techfest ucla-faculty users
-abt amazon apple barnes bestbuy bigtray bol buy cameraword cnet cooking-bw dealtime drugstore ebay mgzoutlet mediaworld nthbutsw powells googlepdct yahooshop shopping shopzilla target tigerdirect venere
-abt amazon apple barnes bestbuy bigtray bol buy cameraword cnet cooking-bw dealtime drugstore ebay mgzoutlet mediaworld nthbutsw powells googlepdct yahooshop shopping shopzilla target tigerdirect venere
-hg_ex12 hg_ex18 hg_ex2 hg_ex26 hg_ex29 hg_ex3 hg_ex39 _h8d62ck1* 03PFMJOU* 2003Fall 64040 anrep9899* bali ch15_e compliance* DataDiction* deliverable* e_Bubble_* flip_usd5 Funded - F ge-revenues HOSPITAL* pwpSurvey* SOA4-YEAR* young_table
-hg_ex12 hg_ex18 hg_ex2 hg_ex26 hg_ex29 hg_ex3 hg_ex39 _h8d62ck1* 03PFMJOU* 2003Fall 64040 anrep9899* bali ch15_e compliance* DataDiction* deliverable* e_Bubble_* flip_usd5 Funded - F ge-revenues HOSPITAL* pwpSurvey* SOA4-YEAR* young_table
-seconds
-# examples
-seconds
-examples
-seconds
-examples
 by contributing along several dimensions: development of domain specific languages for describing text structure or data format, learn- ing algorithms for automatically inferring such formats [8], and a markup language to allow users to add simple annotations to enable more effective learning of text structure [23] While PADS supports parsing of entire files, FlashExtract allows users to extract only parts of the file thereby avoiding unnecessary complications.
@@
 
-\section{Information retrieval and Retrieval Techniques}
-\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
+\section{Information Extraction and Retrieval Techniques}
+\todo{explain difference here, reference pads and stuff}
+\review{Getting the general tot p cic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
 Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
@@
 
+\section{Semi-Structured Data}
+\label{sec:rw-semi-structured-data}
+Serge Abiteboul ``characterizes essential aspects of semi-structured data''~\cite{abiteboul1997querying} in the context of integrating data from various data sources.
+The content of CI build logs is combined from several tools involved in the build process and several of Abiteboul's aspects can be applied to build logs.
+
+The structure of build logs
+\begin{itemize}
+  \item is \textbf{implicit}, as we do not have access to explicit structuring elements or an explicit structure description and computation is required to obtain the structure which is present.
+  \item is \textbf{irregular}, as changes in the build process or execution environment might change it without notice.
+  We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
+  You can see an example of this in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.
+  \item is \textbf{partial}, some parts are highly structured by e.g. structure indicating special characters and others are unstructured, e.g. natural language text in error messages.
+  \item can described with an \textbf{a-posteriori data guide} than an a-priori schema.
+  There is no fixed specification on how build tools have to structure their output, more we afterwards extract structuring patterns in the produced output.
+  \item has a \textbf{rapidly evolving} schema.
+  Modifications in the build configuration change the tools involved in the build and therefore the composition of the build log.
+\end{itemize}
+
+Abiteboul proposes an approach to overlay the semi-structured data with a structured layer.
+The additional layer can answer queries and give access to the semi-structured data relevant to the query.
+In contrast to that, this thesis takes a look at techniques to gater a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.
 \end{document}

### 2019-10-18 thesis/txt/2-models.tex
writing loads of stuff on models, semi-structured data in rw, example pictures of build logs

@@
 The idea of CI is, to integrate new software changes fast and often to catch errors early~\cite{humble2010continuous}.
-After making a change, the developer commits and pushes it to a shared source code repository.
-Companies often use a specific CI server, e.g.
-Travis CI, linked to their source code repository.
+After making a change, the developer commits and pushes it to a shared source code repository. Companies often use a specific CI server, e.g. Travis CI, linked to their source code repository.
 A CI build might then be triggered by a push on specific branches or after a pull request was created.
 When such a CI build is triggered, it typically runs through these stages:
+
 \begin{itemize}
-	\item Pulling in the new, changed version of the source code.
+	\item \todo{look for more in modelling paper zampetti}
+	\item Pulling the new, changed version of the source code onto the server.
 	\item Running static analysis tools~\cite{zampetti2017open}.
 	\item Building the software, i.e. compiling and packaging it~\cite{phillips2014understanding}.
-	\item Running automated tests.
-\end{itemize}
-However these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects \mention{citation needed, zampetti2017open?}.
-Some smaller projects might just use CI to make sure their code compiles as a minimal check before reviewing a pull request, other projects might have various stages of extensive automated testing.
-
-Independent from the actual composition of the CI build process, most software tools used within a build will write out log messages to the console \mention{citation needed, paper about usages of console.log?}.
-Often, the console output is the only means to for a build tool to communicate with its users.
-Tools print progress updates, error and warning messages on the console.
-
-The structure of this output is chosen by every tool themselves.
-Many have implicit or explicit structuring rules, some adhere to predefined standards \mention{phpunit, ruby, xuint output?}.
-However, when anlayzing build logs we might not have access to the exact build configuration (which tools are used in which order) or might not have access to a useable definition of the output sturcture of a specific tool.
-Therefore we describe build logs as semi-structured.
-
-Semi-structured for build logs means for us that the log text is:
-\begin{itemize}
-	\item \textbf{implicitly stuructured}, we do not have access to explicit structuring elements or an explicit structure description
-	\item \textbf{irregular}, the structure changes without notice \todo{we saw this in our data collection, random newlines}
+	\item Running automated tests~\cite{beller2017oops}.
 \end{itemize}
 
-\plan{a build consists of various steps, executed by different tools, these are often orchestrated by at least one overarching tool.
-// picture: overarching tool travis and it calls different tools which tehn output sequentiall, travis sometimes outputs something in between -> that is how the build log is made up // we have this structure though it is not always apparent from the build log / edges between the systems can look very different, mostly no agreed model, we: look at differen techniques to retrieve certain pieces of information \emph{without complete parsing the whole log in to a structure} -> we don't necesarrily want to understand the whole log sturcture just retrieve one specifi information relevant to us}
+However these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects \mention{citation needed, zampetti2017open?}.
+Some smaller projects might use CI to just make sure their code compiles as a minimal check before reviewing a pull request.
+Other projects might have various stages of extensive automated testing.
+
+Most software tools used within a build will write out log messages to the console \mention{citation needed, paper about usages of console.log?}.
+To communicate progress updates, error and warning messages to the user.
+This combined output is referred to as build log.
+The structure of their output is chosen by every tool themselves.
+Many have implicit or explicit structuring rules, some adhere to predefined standards \mention{phpunit, ruby, xuint output?}.
+\todo{figure X} shows how different tools contribute to the whole build log.
+
+When analyzing build logs we might not have access to the exact build configuration, describing which tools are used in which order, or might not have access to a useable definition of the output structure of a specific tool.
+As the structure of a build log is not known to us, we describe build logs as semi-structured. Section \ref{sec:rw-semi-structured-data} describes different properties of semi-structured data.
 
@@
 Continuous integration build logs contain a huge amount of information about the various stages in the CI build they correspond to.
-In this section we present our model to more precisely describe our notion of a information retrievable from a CI build log.
+In this section we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
 
-A \emph{build log information} for us has:
-\begin{itemize}
-	\item a \emph{textual representation} within the build log, more specifically a substring of the log string
-\end{itemize}
-With this build information items can be hierachically ordered by their textual representations containing each other.
+The central class of our model is the \emph{build log information} (BLI), representing an piece of information possibly retrievable from a build log.
+\emph{Possibly}, because a build log information is not necessarily present in every build log.
+If it is present, we call it a \emph{build log information instantiation} (BLII), which always relates to a specific build log, the one it is appearing in.
+\todo{add to model, build, build log, bulidloginformationinstantiation as association name to the type build log information}
+Each BLII for us has a \emph{textual representation} within the build log.
+This textual representation is always a substring of the log text.
+With this build log information \todo{akward class names like BuildLogInformation? s would be possible then} can be hierarchically ordered by their textual representations containing each other.
+As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section \ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for build log informations whose structure we definetely know.
+Most build log information types can appear in various hierarchical arrangements and therefore not contained in any other type in the model.
 
@@
 \end{figure}
-During our inital exploration \& data collection for the \emph{Failing Build Log Data Set}, wanted to get an impression about the information one would want to retrieve from a build log.
-Within the Travis CI build logs we found various different informations possibly interesting to be retrieved
+During our initial exploration and log data collection for the \emph{Failing Build Log Data Set}, we collected a broad set of build logs from 29 languages and 87 repositories.
+We inspected them to get an impression about the information one would want to retrieve from a build log.
+Within the build logs from Travis CI we found various different information types possibly interesting to be retrieved:
+
 \begin{itemize}
 	\item \textbf{Travis Build Step} A Travis CI build consists of several build steps defined within the Travis CI configuration language.
-Within the build log each of these steps are framed by \lstinline{travis_fold:start:<build step name>} and \lstinline{travis_fold:end:<build step name>}.
+Within the build log each of these steps are framed by \lstinline{travis_fold:start:<build step name>} and \\ \lstinline{travis_fold:end:<build step name>}.
+	These build steps could be categorized, for example into \textbf{Test Step}, \textbf{Linter Step}, \textbf{Travis Worker}, \textbf{Git Fetch}, or \textbf{Sudoers} are some that we encountered in the logs.
 	A build step contains
 	\begin{itemize}
-		      \item \textbf{Build Step Name} The string Travis uses to identify the step within start \& end statements.
-		      \item \textbf{Build Step Output} The output generated during the build step. The textual representation of the \texttt{Build Step Output} is the substring between the start \& end statements.
+		\item \textbf{Build Step Name} The string Travis CI uses to identify the step within start and end statements.
+		\item \textbf{Build Step Output} The output generated during the build step.
+The textual representation of the \texttt{Build Step Output} Instantiation is the substring between the start and end statements.
 	\end{itemize}
+	You can see an example of a Travis Build Step and its components within a build log in Figure \ref{fig:log-1}.
+
+	\item \textbf{Non-Travis Build Step??}
+	\item 
 	\item \textbf{Travis Timing} Travis can measure the time of specified sections of the build process.
-It represents those by \lstinline{travis_time:start:<timing section id>} and \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
+	You can see an example of a Travis Build Step and its components within a build log in Figure \ref{fig:log-1}.
+	%It represents those by \lstinline{travis_time:start:<timing section id>} and \\ \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
+
+	\item \textbf{Travis Worker} Travis CI mentions for each build which machine is executing it.
+	Retrieving this information from multiple build logs could for example help visualize the impact of the build server assignment algorithm.
+	The Travis Worker is a good example to show that the same BLI can have different textual representations in different build logs.
+	You can see examples of Travis Worker instantiations in Figure \ref{fig:log-0} and Figure \ref{fig:log-2}.
+
+	\item \textbf{Travis System Info} At the beginning of each log Travis CI describes the tech stack of the server executing the build.
+	The system info could be retrieved from both failing and successful logs and compared to identify if a failure is possibly based on the execution environment.
+	You can see an example of a Travis System Info instantiation within a build log in Figure \ref{fig:log-0}.
+
+	\item \textbf{Triggering Command} Travis CI logs the commands it uses to call certain tools.
+	These come from the \texttt{travis.yml} configuring the build.
+	Retrieving this information from the log could for example be useful when reverse engineering the build configuration.
+	You can see an example of a Triggering Command instantiation within a build log in Figure \ref{fig:log-3}.
+
+	\item \textbf{Exit Code} Travis CI prints all exit codes of commands.
+	This information could be used to fill an overview of the build steps and why they failed.
+	You can see an example of an Exit Code instantiation within a build log in Figure \ref{fig:log-3}.
+
+	\item \textbf{Error Message} Various tools involved in the build process might output messages of errors that occurred during their execution.
+	Retrieving these and showing them to developers could help them understand quicker why the build failed.
+	You can see an example of and Error Message instantiation within a build log in Figure \ref{fig:log-3}.
+
+	\item \textbf{Warning Message} In addition to errors, tools also print warning messages.
+	These could be collected, counted and presented to developers, encouraging them to resolve them in order to improve their software.
+	You can see examples of WarningMessage instantiations within build logs in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.
+
+	\item \todo{name, explanation, ref to example image, example what to be used for}
 \end{itemize}
 
-\todo{differentiate Travis CI specific things, explain high variability for instantiations}
-\todo{give at least one concrete example instantiation, best from a log in the data set, not too long so maybe it goes in the abstract?, picture/graphic with marked parts here?}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/log0.png}
+	\caption{Excerpt from a build log showing textual representations of a long Travis Worker instantiation and a Travis System Info instantiation}
+	\label{fig:log-0}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/log1.png}
+	\caption{Excerpt from a build log showing textual representations of a Travis Timing instantiation and a Travis Build Step, containing the Build Step Name and the Build Step Output}
+	\label{fig:log-1}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/log2.png}
+	\caption{Excerpt from a build log showing textual representations of a short Travis Worker instantiation}
+	\label{fig:log-2}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/log3.png}
+	\caption{Excerpt from a build log showing textual representations of Error Message, Exit Code and Triggering Command instantiations}
+	\label{fig:log-3}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/log4.png}
+	\caption{Excerpt from a build log showing textual representations of Warning Message instantiations}
+	\label{fig:log-4}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/log5.png}
+	\caption{Excerpt from a build log showing textual representations of Warning Message instantiations}
+	\label{fig:log-5}
+\end{figure}
 
@@
 	\item \textbf{Target}{Extractable Information} each retrieval technique \todo{instantiation!} targets a specific information
-	\item \textbf{Setup Overhead}{Time}
-	\item \textbf{Performance}{Performance} split into learning performance
+	\item \textbf{Setup Overhead} {Time}
+	\item \textbf{Performance} {Performance} split into learning performance
 	\item \textbf{Configuration Scope} for one repository/project, a language/logkind, global
+	\item \textbf{Granularity} of extraction, i.e. the smallest extractable text piece
 \end{itemize}
@@
 	\item{Performance}{Performance} split into learning performance
+	\item 
 \end{itemize}
@@
 
-\todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?, describe regex programs}
-
 \section{Text Similarity}
@@
 \paragraph{Overview}
-Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}.
+Text Similarity approaches are more and more used to filter unstructured textual software artifacts. \mention{cite papers that do exactily this. also lda possbible here}
+One common and simple technique the Vector Space Model \mention{citation needed, for VSM and that it is common maybe?}.
+We investigate when it is a suitable technique to retrieve information from build logs.
+
+\paragraph{Configuration / Input / Output}
+To configure a retrieval though text similarity we chose to use the same concept of I/O examples as for PBE.
+The output strings of a given example set define our search query.
+A retrieval run then takes as input a log file and outputs the parts most similar to the search query.
+
+\paragraph{Similariy Calculation}
+The TS retrieval technique works on a granularity of lines.
+First, the search query is processed.
+The output strings of the example set configuring the technique are split into single lines.
+For each line we apply preprocessing: Splitting it into tokens, in our case words.
+%Commonly text similarity techniques employ further normalization like removing special characters and stop words.
+%We chose to keep the build log lines as complete as possible, as we often saw special characters and words identifying an interesting area.
+Then we build a document-term-frequency matrix over the lines of the output strings and prune very often or very rarely appearing words.
+Next, the algorithm applies term-frequency inverse document frequency, a best practice for natural language queries~\cite{lee1997document}.
+To retrieve the desired information from a build log, we parse the whole text and process it in the same way.
+The algorithm calculates the cosine simlarity~\mention{citation?} to compare each line of the build log with each line of the search query.
+After summing up the similarities of each build log line to all the query lines, we sort the build log lines in decreasing similarity.
+The average number of lines in the I/O example output strings determines how many of the most similar lines are returned as the output of the retrieval run.
+
+\paragraph{Instantiate Retrieval Technique Model}
+
+%Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}.
 We describe CI build logs as semi-structured,
-\todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?}
 
@@
 \end{figure}
+
+\paragraph{Overview}
+When we are looking for a specific information within a great amount of unstructured information, a first ad-hoc approach is to search for keywords in the text we assume to be near the information we are looking for.
+This was one of the most common approaches we took when searching for the build failure reason within a log when creating our data set.
+As this is a technique readily available in many tools developers use to view build logs, we want to study when such a simple search for keywords is recommendable for retrieving information from CI build logs.
+
+\paragraph{Configuration / Input / Output}
+SKWS is configured by giving a set of keywords.
+For a retrieval run we then take a whole build log file as input and search for all exact occurrences of the keywords.
+As keywords are often not directly describing the desired information but rather adjacent to the desired information, this technique not only retrieves the line with the keyword, but only the context around it.
+We chose a context of 10 lines above and below the keyword appearance.
+
+\paragraph{Instantiation of Model}
+
 \todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?}

### 2019-10-22 thesis/txt/1-related-work.tex
data analysis, after many tries now in python notebooks with pandas

@@
 \begin{itemize}
-  \item is \textbf{implicit}, as we do not have access to explicit structuring elements or an explicit structure description and computation is required to obtain the structure which is present.
-  \item is \textbf{irregular}, as changes in the build process or execution environment might change it without notice.
+  \item is \textbf{implicit}.
+  We do not have access to explicit structuring elements or an explicit structure description.
+  Computation is required to infer the present structure.
+  \item is \textbf{irregular}.
+  Changes in the build process or execution environment might change the structure of a build log without notice.
   We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.

### 2019-10-22 evaluation/evaluate-results.R

@@ -32,7 +32,7 @@ getDataFrameForPBEResultsFile <- function(path) {
     
     test <- item[["value"]][[1]][[1]]
     learnedProgram <- xmlValue(test[["LearnedProgram"]][[1]])
-    testInputPath <- xmlValue(tes[["TestInputPath"]][[1]])
+    testInputPath <- xmlValue(test[["TestInputPath"]][[1]])
     testOutput <- xmlValue(test[["Output"]][[1]])
     desiredTestOutput <-  xmlValue(test[["DesiredOutput"]][[1]])
     accuracy <- 3

### 2019-10-24 thesis/txt/0-introduction.tex
writing a lot in chapter 2, various figures, data analysis and figures in thesis

@@
 \chapter{Introduction}
-%Many s These CI builds often produce very long and verbose build logs \mention{add log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.
-
-%These build logs are a highly valuable data source.
-First of all, for the developers that read them to analyze why their build failed or ..
-\mention{find more reasons}.
-Second, for researchers that can harvest the information contained in the logs -- and their metadata -- to study the software engineering process of a project.
-However they can only utilize the information within the build logs if they can adequately extract the information relevant to them.
-
-%There are many different retrieval techniques use for this task.
-Beller et al.
-used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI~\cite{beller2017oops}, while Vassallo et al.
-wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
-Recently Amar et al.
-greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.
-\bp{anecdotal: keyword search?}.
-Apart from those there are various more retrieval techniques like searching for keywords, ...
-\todo{more?} \bp{introduce problem: which one to choose}
-
-%With our work we want to support developers, researchers or project managers in deciding which technique is the best one for their use case. 
+\plan{finalized, out for review}
 Continuous Integration (CI) has become a best practice in software engineering.
@@
 Currently there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
-Developers and researches have little support while choosing which technique to use for an retrieval task.
+Developers and researches have little support while choosing which technique to use for a retrieval task.
 The goal for this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.
 
-We aim to define a model to characterize the different IR techniques as well as the information retrievable from CI build logs.
+We aim to define a model to characterize different IR techniques as well as the information retrievable from CI build logs.
 For our first research question we analyze which criteria influence the suitability of an IR technique.
@@
 \begin{itemize}
-  \item regular expression synthesis by example using the Microsoft PROSE library (referred to as PBE),
+  \item regular expression program synthesis from examples using the Microsoft PROSE library (referred to as PBE),
   \item a common text similarity approach (referred to as TS) and
@@
 Our second research question asks in which cases PBE, TS and SKWS are suited to retrieve information from continuous integration build logs.
-RQ2 is refined sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples the techniques need to perform best, the accuracy of the retrieved output and how diverse the configuring examples can be structurally.
+RQ2 is refined into sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples a technique needs to perform best, the accuracy of the retrieved output and how diverse the configuring examples can be structurally.
 \begin{simplebox}{Research Questions}

### 2019-10-24 thesis/txt/1-related-work.tex
writing a lot in chapter 2, various figures, data analysis and figures in thesis

@@
 \chapter{Related Work}
+\plan{all of RW: 4 - 5 pages left to do + some research!}
+\plan{write, 1/3 page, blocked by: other sections}
 \label{sec:rw}
@@
 \section{Continuous Integration}
+\plan{extend, 1 page}
 \mention{look into proksch papers}
@@
 \section{Build Log Analysis and Augmentation}
+\label{sec:rw-bl-analysis}
+\plan{extend, 1 page}
 Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs.
@@
 \section{Production Log Analysis}
+\plan{research + write, 1/2 - 1 page}
 \mention{logpai and drain, [7] K. Fisher and D. Walker. The pads project: an overview. In ICDT,
@@
 \section{Information Extraction and Retrieval Techniques}
-\todo{explain difference here, reference pads and stuff}
+\plan{research + write, 1/2 - 1 page}
+\todo{explain difference here, reference pads(maybe that is already in log anlysis!) and stuff}
 \review{Getting the general tot p cic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
@@
 \section{Program Synthesis by Example}
+\plan{extend, 1 page}
 \todo{how much can/should we explain here?
@@
 
+\todo{maybe scrap this section / incorporate last sentence somewhere else, expalnation will mostly be in rw. How to usefully sturcture the stuff above this?}
+In the following we want to give an impression on how the PROSE library and specifically the Flash Extract DSL synthesize programs for extracting substrings from text via regular expressions.
+\todo{how much can/should we explain here?
+possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
+Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm. Both are described in \todo{ref rw sections}.
+
 \section{Semi-Structured Data}
+\plan{finalized, out for review}
 \label{sec:rw-semi-structured-data}
@@
   You can see an example of this in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.
-  \item is \textbf{partial}, some parts are highly structured by e.g. structure indicating special characters and others are unstructured, e.g. natural language text in error messages.
-  \item can described with an \textbf{a-posteriori data guide} than an a-priori schema.
-  There is no fixed specification on how build tools have to structure their output, more we afterwards extract structuring patterns in the produced output.
+  \item is \textbf{partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, e.g.\ natural language text in error messages.
+  \item can be described with an \textbf{a-posteriori data guide} rather than an a-priori schema.
+  There is no fixed specification on how build tools have to structure their output.
+  We afterwards extract structuring patterns in the produced output.
   \item has a \textbf{rapidly evolving} schema.
-  Modifications in the build configuration change the tools involved in the build and therefore the composition of the build log.
+  Modifications in the build configuration might change the tools involved in the build and therefore the composition of the build log.
 \end{itemize}

### 2019-10-24 thesis/txt/2-models.tex
writing a lot in chapter 2, various figures, data analysis and figures in thesis

@@
 
-\chapter{Information Retrieval Techniques}
+\chapter{Information Retrieval Techniques for Build Logs}
+\plan{whole chapter: some reordering and reviewing to do, write about 3 pages about ir technique model classes and ir tasks and other techniques}
+\plan{write, 1/3 page, blocked by: rest of chapter}
 \label{sec:models}
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/build-overview.pdf}
+	\caption{The different entities involved in a build}
+	\label{fig:build-overview}
+\end{figure}
+
 \section{Characteristics of a Build Log}
+\plan{citations needed, make clean figure of contribution of tools to log, 1 caro-review before finalized}
 The idea of CI is, to integrate new software changes fast and often to catch errors early~\cite{humble2010continuous}.
-After making a change, the developer commits and pushes it to a shared source code repository. Companies often use a specific CI server, e.g. Travis CI, linked to their source code repository.
+After making a change, the developer commits and pushes it to a shared source code repository.
+Companies often use a specific CI server, e.g.\ Travis CI, linked to their source code repository.
 A CI build might then be triggered by a push on specific branches or after a pull request was created.
@@
 
-Most software tools used within a build will write out log messages to the console \mention{citation needed, paper about usages of console.log?}.
-To communicate progress updates, error and warning messages to the user.
-This combined output is referred to as build log.
+Software tools involved in the build write out log messages to the console \mention{citation needed, paper about usages of console.log?}.
+They communicate progress updates, error and warning messages to the user.
+We refer to to the sum of this output as build log.
 The structure of their output is chosen by every tool themselves.
 Many have implicit or explicit structuring rules, some adhere to predefined standards \mention{phpunit, ruby, xuint output?}.
-\todo{figure X} shows how different tools contribute to the whole build log.
+Figure \ref{fig:tool-log-contribution} shows how different tools contribute to the whole build log.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, trim={0cm 15cm 0cm 0cm}, clip]{img/tool-log-contribution.pdf}
+	\caption{Contribution of different tools to the build log}
+	\label{fig:tool-log-contribution}
+\end{figure}
 
@@
 \section{Retrievable Information in Build Logs}
+\plan{fix naming, then review again}
 \begin{figure}[h]
 	\centering
-\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
 	\caption{Information retrievable from build logs}
-  \label{fig:build-log-information-draft}
+	\label{fig:build-log-information}
 \end{figure}
@@
 In this section we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
+Figure \ref{fig:build-log-information} shows the model.
 
-The central class of our model is the \emph{build log information} (BLI), representing an piece of information possibly retrievable from a build log.
-\emph{Possibly}, because a build log information is not necessarily present in every build log.
-If it is present, we call it a \emph{build log information instantiation} (BLII), which always relates to a specific build log, the one it is appearing in.
-\todo{add to model, build, build log, bulidloginformationinstantiation as association name to the type build log information}
+The central class of our model is the \emph{BuildLogInformation} (BLI), representing an piece of information possibly retrievable from a build log.
+\emph{Possibly}, because a BuildLogInformation is not necessarily present in every build log.
+If it is present, we call it a \emph{BuildLogInformation instantiation} (BLII), which always relates to a specific build log, the one it is appearing in.
+
 Each BLII for us has a \emph{textual representation} within the build log.
 This textual representation is always a substring of the log text.
-With this build log information \todo{akward class names like BuildLogInformation? s would be possible then} can be hierarchically ordered by their textual representations containing each other.
-As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section \ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for build log informations whose structure we definetely know.
+BuildLogInformations can be hierarchically ordered by their textual representations containing each other.
+As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section \ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for BuildLogInformations whose structure we definetely know.
 Most build log information types can appear in various hierarchical arrangements and therefore not contained in any other type in the model.
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{img/mt-graphics-BuildLogInformation.pdf}
-	\caption{Build Log Information}
-	\label{fig:build-log-information}
-\end{figure}
 During our initial exploration and log data collection for the \emph{Failing Build Log Data Set}, we collected a broad set of build logs from 29 languages and 87 repositories.
@@
 \begin{itemize}
-	\item \textbf{Travis Build Step} A Travis CI build consists of several build steps defined within the Travis CI configuration language.
-Within the build log each of these steps are framed by \lstinline{travis_fold:start:<build step name>} and \\ \lstinline{travis_fold:end:<build step name>}.
-	These build steps could be categorized, for example into \textbf{Test Step}, \textbf{Linter Step}, \textbf{Travis Worker}, \textbf{Git Fetch}, or \textbf{Sudoers} are some that we encountered in the logs.
-	A build step contains
+	\item \textbf{BuildPhase} Build logs can be divided in the sections produced by different tools.
+	      These build steps could be for example be a \texttt{TestPhase}, \textbf{LinterPhase}, \textbf{TravisWorker}, \textbf{GitFetch}, or \textbf{Sudoers} are some that we encountered in the logs.
+
+	\item \textbf{TravisPhase} Travis CI build logs consists of several build phases defined within the Travis CI configuration language.
+Within the build log each of these steps are framed by \lstinline{travis_fold:start:<travis phase name>} and \\ \lstinline{travis_fold:end:<build step name>}.
+
+	      A TravisPhase always contains:
 	      \begin{itemize}
-		\item \textbf{Build Step Name} The string Travis CI uses to identify the step within start and end statements.
-		\item \textbf{Build Step Output} The output generated during the build step.
+		      \item \textbf{TravisPhaseName} The string Travis CI uses to identify the phase within start and end statements.
+		      \item \textbf{TravisPhaseOutput} The output generated during the build step.
 The textual representation of the \texttt{Build Step Output} Instantiation is the substring between the start and end statements.
 	      \end{itemize}
-	You can see an example of a Travis Build Step and its components within a build log in Figure \ref{fig:log-1}.
+	      You can see an example of a TravisPhase and its components within a build log in Figure \ref{fig:log-1}.
 
-	\item \textbf{Non-Travis Build Step??}
 	\item
-	\item \textbf{Travis Timing} Travis can measure the time of specified sections of the build process.
+	\item \textbf{TravisTiming} Travis can measure the time of specified sections of the build process.
+	      Timing information can be useful to retrieve when you want to automatically monitor the performance of your bui
 	      You can see an example of a Travis Build Step and its components within a build log in Figure \ref{fig:log-1}.
@@
 
-	\item \textbf{Travis Worker} Travis CI mentions for each build which machine is executing it.
+	\item \textbf{TravisWorker} Travis CI mentions for each build which machine is executing it.
 	      Retrieving this information from multiple build logs could for example help visualize the impact of the build server assignment algorithm.
-	The Travis Worker is a good example to show that the same BLI can have different textual representations in different build logs.
-	You can see examples of Travis Worker instantiations in Figure \ref{fig:log-0} and Figure \ref{fig:log-2}.
+	      The TravisWorker is a good example to show that the same BLI can have different textual representations in different build logs.
+	      You can see examples of TravisWorker instantiations in Figure \ref{fig:log-0} and Figure \ref{fig:log-2}.
 
-	\item \textbf{Travis System Info} At the beginning of each log Travis CI describes the tech stack of the server executing the build.
+	\item \textbf{TravisSystemInfo} At the beginning of each log Travis CI describes the tech stack of the server executing the build.
 	      The system info could be retrieved from both failing and successful logs and compared to identify if a failure is possibly based on the execution environment.
-	You can see an example of a Travis System Info instantiation within a build log in Figure \ref{fig:log-0}.
+	      You can see an example of a TravisSystemInfo instantiation within a build log in Figure \ref{fig:log-0}.
 
-	\item \textbf{Triggering Command} Travis CI logs the commands it uses to call certain tools.
+	\item \textbf{TriggeringCommand} Travis CI logs the commands it uses to call certain tools.
 	      These come from the \texttt{travis.yml} configuring the build.
 	      Retrieving this information from the log could for example be useful when reverse engineering the build configuration.
-	You can see an example of a Triggering Command instantiation within a build log in Figure \ref{fig:log-3}.
+	      You can see an example of a TriggeringCommand instantiation within a build log in Figure \ref{fig:log-3}.
 
-	\item \textbf{Exit Code} Travis CI prints all exit codes of commands.
+	\item \textbf{ExitCode} Travis CI prints all exit codes of commands.
 	      This information could be used to fill an overview of the build steps and why they failed.
-	You can see an example of an Exit Code instantiation within a build log in Figure \ref{fig:log-3}.
+	      You can see an example of an ExitCode instantiation within a build log in Figure \ref{fig:log-3}.
 
-	\item \textbf{Error Message} Various tools involved in the build process might output messages of errors that occurred during their execution.
+	\item \textbf{ErrorMessage} Various tools involved in the build process might output messages of errors that occurred during their execution.
 	      Retrieving these and showing them to developers could help them understand quicker why the build failed.
-	You can see an example of and Error Message instantiation within a build log in Figure \ref{fig:log-3}.
+	      You can see an example of and ErrorMessage instantiation within a build log in Figure \ref{fig:log-3}.
 
-	\item \textbf{Warning Message} In addition to errors, tools also print warning messages.
+	\item \textbf{WarningMessage} In addition to errors, tools also print warning messages.
 	      These could be collected, counted and presented to developers, encouraging them to resolve them in order to improve their software.
@@
 
-	\item \todo{name, explanation, ref to example image, example what to be used for}
 \end{itemize}
 
-\begin{figure}[h]
+\begin{figure}[hp]
 	\centering
@@
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[hp]
 	\centering
@@
 \section{Characteristics of Information Retrieval Techniques}
+\plan{describe model classes, 1 page text}
 \begin{figure}[h]
 	\centering
-	\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
-	\caption{Model for an information retrieval technique}
+	\includegraphics[width=\textwidth, clip]{img/ir-technique.pdf}
+	\caption{Model for an Information Retrieval Technique}
 	\label{fig:model-ie-technique}
 \end{figure}
-For this thesis we want to evaluate different information retrieval techniques in their application to CI build logs.
-We focus on techniques that do not attempt or require to parse the structure of a whole build log, but rather focus on extracting just one specific information
-A build log information retrieval technique (BLIR technique) consumes a build log (text file) and produces a certain output (text).
-\todo{make picture, output can be contained in log or not, can be continuous substring or selected lines etc.}.
+For this thesis we want to evaluate different information retrieval techniques when applied to CI build logs.
+We focus on techniques that do not require to parse the structure of a whole build log, but rather focus on extracting just one specified information.
+We refer to such a technique as BuildLogInformationRetrievalTechnique (BLIRT).
+
+A BLIRT run consumes a build log (text file) and produces a certain output (text).
+
+A BLIRT
 \begin{itemize}
-	\item \textbf{Target}{Extractable Information} each retrieval technique \todo{instantiation!} targets a specific information
-	\item \textbf{Setup Overhead} {Time}
-	\item \textbf{Performance} {Performance} split into learning performance
-	\item \textbf{Configuration Scope} for one repository/project, a language/logkind, global
-	\item \textbf{Granularity} of extraction, i.e. the smallest extractable text piece
+	\item targets a specific \textbf{BuildLogInformation}.
+	\item identifies the text part to retrieve through an \textbf{IdentificationTechnique}.
+	\item is configured by a \textbf{Configuration}
+	      \begin{itemize}
+		      \item each configuration addresses a specific \textbf{Scope}.
+		            The Scope can be a specific project, a tool involved in the build, a programming language or global, configuring a retrieval technique for all possible build logs.
+	      \end{itemize}
+	\item can retrieve text passages with a specific \textbf{Granularity}, i.e. the smallest extractable text piece.
+	      The Granularity can be at the level of characters, lines or paragraphs.
 \end{itemize}
 
-Example instantiations of this task later in this chapter, namely for the three techniques we are comparing: PROSE program synthesis, IR text similarity, and simple keyword search. \todo{ref?}
+The last sections of this chapter show instantiations of this model for the three techniques we analyze and an additional one from related works.
 
 \section{Information Retrieval Tasks}
+\plan{what do we need here?, come up with model if we keep this, 1 page text max.}
+Previous sections gave various examples of situations where a developer or a researcher wants to retrieve information from a build log.
+The goal of this work is to clarify which BLIRT is suited for their specific task.
+In this section we structure we present different important characteristics of such an IR task.
+You can see the model in Figure \ref{fig:model-ir-task}
+
 \begin{figure}[h]
 	\centering
-	\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
-	\caption{Model for information extraction task}
-	\label{fig:modelt-ie-task}
+	\includegraphics[width=\textwidth, clip]{img/ir-task.pdf}
+	\caption{Model for an Information Retrieval Task}
+	\label{fig:model-ir-task}
 \end{figure}
-aims to describe an information retrieval task of a developer or a researcher.
+
+A InformationRetrievalTask
 \begin{itemize}
-	\item \todo{describe all classes}
-	\item{Setup Overhead}{Time}
-	\item{Performance}{Performance} split into learning performance
-	\item 
+	\item has a specific amount and kind of \textbf{Configuration} available.
+	      This represents how much data is available for the technique to learn what to extract.
+	      For a BLIRT to be suited the available configuration has to match to needed configuration of the technique.
+	\item is connected to a \textbf{TextProcessor} retrieving the output.
+	      This can be for example a developer reading the output or a program.
+	      Different TextProcessors require different accuracies in the output, e.g.
+a program needs exact retrievals to process automatically, while a developer can cope easier with falsely extracted lines.
 \end{itemize}
@@
 
+\begin{figure}[hp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/pbe-technique.pdf}
+		\caption{Synthesizing Regular Expression Programs by Example Using PROSE}
+		\label{fig:prose-explanation}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/ts-technique.pdf}
+		\caption{Retrieving Information Using Text Similarity}
+		\label{fig:text-similarity-explanation}
+	\end{minipage}
+\end{figure}
+
 \section{PROSE Program Synthesis}
-\begin{figure}[h]
-  \centering
-\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
-  \caption{Synthesizing regular expression programs by example using PROSE}
-  \label{fig:prose-explanation}
-\end{figure}
-\subsection*{Overview}
+\plan{2 caro-reviews before finalized}
+
+\subsection{Introduction}
 \emph{Programming by Example (PBE)} is a technique where programs are synthesized according to in and output examples provided by the user.
 It enables users to create programs without requiring programming knowledge~\cite{mayer2015user}.
-Applied A to the task of text extraction through regular expressions it relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
+Applied to the task of text extraction through regular expressions it relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
 We chose to investigate the applicability of generating regular expression programs by example to extracting information from build logs.
 In this work we refer to our interpretation of this technique as \emph{PBE}.
-\todo{distinguish PBE for buildlogs}
+In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.
+Figure \ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE.
 
+\subsection{Method}
+In/Output examples (I/O examples) are the main driver of Programming by Example.
+When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
+In the implementation we did have to apply a few text replacements as described in \ref{sec:impl-preprocessing}.
+The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the synthesized program when given the corresponding input file.
+One or multiple I/O examples are needed as configuration for PBE, they are used to define substring of a log should be extracted.Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm.
+Both are described in \todo{ref rw sections}.
+%For execution PBE takes a build file as input and returns a substring of the build file content.
+
+\subsection{Perspective: Usability vs. Technical Aspects}
 Generally, we are interested in whether a Programming by Example could replace manually writing regular expressions.
@@
 Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
-In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.
-
-\subsection*{Configuration / Input / Output}
-In/Output examples (I/O examples) are the main driver of Programming by Example.
-When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
-In the implementation we did have to apply a few text replacements as described in \ref{sec:impl-preprocessing}.
-The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the syntesized program when given the corresponding input file.
-One or multiple I/O examples are needed as configuration for PBEBL, they are used to define substring of a log should be extracted.
-For execution PBEBL takes a build file as input and returns a substring of the build file content.
-
-\subsection*{Synthesizing Programs with Flash Extract}
-\todo{maybe scrap this section / incorporate last sentence somewhere else, expalnation will mostly be in rw. How to usefully sturcture the stuff above this?}
-In the following we want to give an impression on how the PROSE library and specifically the Flash Extract DSL synthesize programs for extracting substrings from text via regular expressions.
-\todo{how much can/should we explain here?
-possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
-Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm. Both are described in \todo{ref rw sections}.
-
-\subsection*{Model instantiation}
 
 \section{Text Similarity}
-\begin{figure}[h]
-  \centering
-\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
-  \caption{Extracting information using text similarity}
-  \label{fig:text-similarity-explanation}
-\end{figure}
-\paragraph{Overview}
+\plan{2 caro-reviews before finalized}
+
+\subsection{Overview}
 Text Similarity approaches are more and more used to filter unstructured textual software artifacts. \mention{cite papers that do exactily this. also lda possbible here}
@@
 We investigate when it is a suitable technique to retrieve information from build logs.
+In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (TS), the concrete implementation is described in \ref{sec:impl-ts}.
+Figure \ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for TS.
 
-\paragraph{Configuration / Input / Output}
+\subsection{Method}
 To configure a retrieval though text similarity we chose to use the same concept of I/O examples as for PBE.
-The output strings of a given example set define our search query.
-A retrieval run then takes as input a log file and outputs the parts most similar to the search query.
+The lines of the output strings of a given example set define our search query.
 
-\paragraph{Similariy Calculation}
-The TS retrieval technique works on a granularity of lines.
 First, the search query is processed.
@@
 
-\paragraph{Instantiate Retrieval Technique Model}
-
 %Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}.
@@
 
-\section{Keyword Search}
-\begin{figure}[h]
+\begin{figure}[hp]
 	\centering
-\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
-  \caption{Extracting information using keyword search}
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/skws-technique.pdf}
+		\caption{Retrieving Information Using Simple Keyword Search}
 		\label{fig:keword-search-explanation}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/diff-technique.pdf}
+		\caption{Retrieving Information Using Amar et al.'s Line Diff Approach}
+		\label{fig:diff-technique-model}
+	\end{minipage}
 \end{figure}
 
-\paragraph{Overview}
+\section{Simple Keyword Search}
+\plan{2 caro-reviews before finalized}
+
+\subsection{Overview}
 When we are looking for a specific information within a great amount of unstructured information, a first ad-hoc approach is to search for keywords in the text we assume to be near the information we are looking for.
@@
 As this is a technique readily available in many tools developers use to view build logs, we want to study when such a simple search for keywords is recommendable for retrieving information from CI build logs.
+In the following we will explain how we use simple keyword search to retrieve information from CI build logs (SKWS), the concrete implementation is described in \ref{sec:impl-skws}.
+Figure \ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.
 
-\paragraph{Configuration / Input / Output}
+\subsection{Method}
 SKWS is configured by giving a set of keywords.
@@
 
-\paragraph{Instantiation of Model}
-
-\todo{explanation of process, the way our tool does it, instantiate model of retrieval technique, probably no additional theoretical stuff really needed here?}
-
 \section{Further Techniques}
+\plan{decide: what to mention here, max 1 page text}
 \todo{maybe: instantiate model, or at least partly talk about it}
@@
 
+Amar et al.
+used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}d \cite{amar2019mining}, as we describe in more detail in Section \ref{sec:rw-bl-analysis}
+Figure \ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
+
 \end{document}

### 2019-10-24 thesis/txt/3-data-set.tex
writing a lot in chapter 2, various figures, data analysis and figures in thesis

@@
 For each build the \texttt{TravisRequester} then selects a log to download. Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
-A single build can consist of multiple jobs, e.g. building and executing tests in various different testing environments.
+A single build can consist of multiple jobs, e.g.\ building and executing tests in various different testing environments.
 \texttt{TravisRequester} therefore queries each build for a job, which has the same state.
@@
 re-labeling of parts of the labels - cohen's kappa
+\subsubsection{Introduction}
+\subsubsection{Method}
+\subsubsection{Results}
+\subsubsection{Discussion}
+\subsubsection{Threats to Validity}
 
 \subsection{Sending Mails to Developers}
-study description \& results
+\subsubsection{Introduction}
+For the \emph{Failing Build Log Data Set} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
+As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with differen build logs and systems.
+We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
+
+The person who probably knows best why a build failed is the one committing the changes which triggered the build.
+If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
+In this section we describe how we validate the extractions of the build failure reason the \emph{Failing Build Log Data Set} describes.
+\subsubsection{Method}
+Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information. 
+\subsubsection{Results}
+\subsubsection{Discussion}
+\subsubsection{Threats to Validity}
+
+\section{Threats to Validity}
+\bp{some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed
+
+we are not developers of the projects and we did not analyze their travis configuration: possible that we labeled parts that presented an error, though the build did not fail because of that error
+
+end all the points with: we tried to remedy this by (e.g.\ validations)
+}
 

### 2019-10-24 thesis/txt/5-study.tex
writing a lot in chapter 2, various figures, data analysis and figures in thesis

@@
 \section{Introduction}
-running evaluation to compare the different techniques
+To investigate how different factors \todo{do we list these somewhere?} influence BLIRTs we evaluate the three techniques implemented in our tool on the \emph{Failing Build Log Data Set}.
 
-\section{Method}
 \begin{figure}[h]
@@
 \end{figure}
-\todo{run!}
+
+\section{Method}
+We configure the technique for every example set with an increasing count of I/O examples and then run the retrieval on the next I/O example, the \emph{test I/O example}.
+The output from the test I/O example is the oracle for our evaluation.
+The examples are sorted and selected chronologically, i.e. the technique is configured with examples from the directly preceeding build logs to extract information from the test log.
+The extraction quality of a BLIRT run is evaluated on only one build log, as it should be suitable for every coming example.
+Especially the one directly succeeding the configuration.
+If the information retrieval there is bad, we expect the user to directly change the configuration again or be dissapointed with his selection of technique.
+
+When evaluating a BLIRT run we measure the following data points:
+\begin{itemize}
+	\item \textbf{Successful} A BLIRT run is successful when the retrieved output contains all the lines the oracle output.
+	\item \textbf{Accuracy} \todo{currently: levenstein difference of input and output, maybe: change to false pos and neg lines}
+	\item \textbf{Proximity} \todo{can we usefully calculate that????}
+\end{itemize}
 
@@
 \todo{accuracy (or so) of retrievals with growing example number // overall averages \& detailed look on special cases //}
+\begin{figure}[hp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/accuracy-success-all.pdf}
+		\caption{caption}
+		\label{fig:accuracy-success-all}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/line-diff-all.pdf}
+		\caption{caption}
+		\label{fig:line-diff-all}
+	\end{minipage}
+\end{figure}
+
+\begin{figure}[hp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/ouput-failed-pbe.pdf}
+		\caption{caption}
+		\label{fig:ouput-failed-pbe}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
+		\caption{caption}
+		\label{fig:success-all}
+	\end{minipage}
+\end{figure}
+
+\begin{figure}[hp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
+		\caption{caption}
+		\label{fig:success-examples-ir}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
+		\caption{caption}
+		\label{fig:success-examples-kw}
+	\end{minipage}
+\end{figure}
+
+\begin{figure}[hp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
+		\caption{caption}
+		\label{fig:success-examples-pbe}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
+		\caption{caption}
+		\label{fig:success-examples-pbe}
+	\end{minipage}
+\end{figure}
 

### 2019-10-25 thesis/txt/0-introduction.tex
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet

@@
 The structure of these logs changes greatly from project to project~\cite{staahl2014modeling} as it highly depends on the tools and environment used.
-Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform\mention{ citation needed }.
-Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project\mention{ citation needed vassallo beller}.
+Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform.
+Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
 However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.
@@
 Developers and researches have little support while choosing which technique to use for a retrieval task.
-The goal for this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.
+The goal of this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.
 
-We aim to define a model to characterize different IR techniques as well as the information retrievable from CI build logs.
-For our first research question we analyze which criteria influence the suitability of an IR technique.
+We aim to define a model to characterize different IR techniques, as well as the information retrievable from CI build logs.
+For our first research question, we analyze which criteria influence the suitability of an IR technique.
 We support our assumption by implementing and evaluating three techniques:
@@
 Our second research question asks in which cases PBE, TS and SKWS are suited to retrieve information from continuous integration build logs.
-RQ2 is refined into sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples a technique needs to perform best, the accuracy of the retrieved output and how diverse the configuring examples can be structurally.
+RQ2 is refined into sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples a technique needs to perform best, the accuracy of the retrieved output and how structurally diverse the configuring examples can be.
 \begin{simplebox}{Research Questions}
@@
   \item[\textbf{RQ1:}] Which criteria influence the suitability of an information retrieval technique for CI build logs?
-  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to retrieve information from CI build logs?
-  \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
-  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS and SKWS?
+  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
+  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
+  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
   \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
@@
   \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
-  \item A extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
+  \item An extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
 \end{itemize}
 
-This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information retrieval techniques to program synthesis by examples.
-Next, chapter \ref{sec:models} present our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs.
+This thesis first presents an overview of the related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
+Next, chapter \ref{sec:models} presents our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs.
 It also introduces the three techniques, we focus on during our research evaluation.
@@
 This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}.
-There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity and keyword search.
+There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity, and keyword search.
 Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.

### 2019-10-25 thesis/txt/2-models.tex
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet

@@
 \begin{itemize}
-	\item \todo{look for more in modelling paper zampetti}
 	\item Pulling the new, changed version of the source code onto the server.
@@
 	\item Running automated tests~\cite{beller2017oops}.
+	\item Deployment of the build artifact~\cite{schermann2016empirical}.
 \end{itemize}
 
-However these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects \mention{citation needed, zampetti2017open?}.
+However these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects~\cite{staahl2014modeling}.
 Some smaller projects might use CI to just make sure their code compiles as a minimal check before reviewing a pull request.
@@
 
-Software tools involved in the build write out log messages to the console \mention{citation needed, paper about usages of console.log?}.
-They communicate progress updates, error and warning messages to the user.
+Software tools involved in the build write out log messages to the console.
+They communicate progress updates, error and warning messages to the user~\cite{yuan2012characterizing}.
 We refer to to the sum of this output as build log.
 The structure of their output is chosen by every tool themselves.
-Many have implicit or explicit structuring rules, some adhere to predefined standards \mention{phpunit, ruby, xuint output?}.
+Many have implicit or explicit structuring rules, some adhere to predefined standards like RSpec or PHPUnit~\cite{phpunit2019logging,rspec2019format}.
 Figure \ref{fig:tool-log-contribution} shows how different tools contribute to the whole build log.
@@
 \end{figure}
-Continuous integration build logs contain a huge amount of information about the various stages in the CI build they correspond to.
+Continuous integration build logs contain a huge amount of information about the stages in the CI build they correspond to.
 In this section we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
@@
 
-During our initial exploration and log data collection for the \emph{Failing Build Log Data Set}, we collected a broad set of build logs from 29 languages and 87 repositories.
+During our initial exploration and log data collection for the \emph{Failing Build Log Data Set}, we collected a broad set of build logs from 29 languages and 87 repositories from Travis CI~\cite{travisci2019webpage}.
 We inspected them to get an impression about the information one would want to retrieve from a build log.
-Within the build logs from Travis CI we found various different information types possibly interesting to be retrieved:
+Within the build logs from Travis CI we found different information types possibly interesting to be retrieved:
 
@@
 	\item \textbf{WarningMessage} In addition to errors, tools also print warning messages.
-	      These could be collected, counted and presented to developers, encouraging them to resolve them in order to improve their software.
+	      These could be collected, counted and presented to developers, encouraging them to resolve them to improve their software.
 	      You can see examples of WarningMessage instantiations within build logs in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.
@@
 One or multiple I/O examples are needed as configuration for PBE, they are used to define substring of a log should be extracted.Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm.
-Both are described in \todo{ref rw sections}.
+Both are described in Section \ref{sec:rw-prose}.
 %For execution PBE takes a build file as input and returns a substring of the build file content.
@@
 \end{itemize}
-Some of these were already evaluated in existing works about PBE and user interaction~\cite{mayer2015user} \mention{other works?}.
+Some of these were already evaluated in existing works about PBE and user interaction~\cite{mayer2015user,lau2009why-programming-by-demonstration,miller2001outlier}.
 Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
-Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on syntesizing programs from examples in an unknow interface.
+Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on synthesizing programs from examples in an unknow interface.
 Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
@@
 Furthermore we gather insights in how PBE has to be applied to yield useable results and perform best.
-Our implementation of PBE \todo{which we name technique name x}, is mainly based on the Flash Extract DSL~\cite{flahsextractpaper} of the PROSE library by Microsoft\mention{cite prose website}.
+Our implementation of PBE, is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
 Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
@@
 \subsection{Overview}
-Text Similarity approaches are more and more used to filter unstructured textual software artifacts. \mention{cite papers that do exactily this. also lda possbible here}
-One common and simple technique the Vector Space Model \mention{citation needed, for VSM and that it is common maybe?}.
+Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+One common and simple technique the Vector Space Model~\cite{schutze2008introduction}.
 We investigate when it is a suitable technique to retrieve information from build logs.
@@
 To retrieve the desired information from a build log, we parse the whole text and process it in the same way.
-The algorithm calculates the cosine simlarity~\mention{citation?} to compare each line of the build log with each line of the search query.
+The algorithm calculates the cosine simlarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
 After summing up the similarities of each build log line to all the query lines, we sort the build log lines in decreasing similarity.
@@
 %Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}.
-We describe CI build logs as semi-structured,
 
@@
 		\caption{Retrieving Information Using Simple Keyword Search}
-		\label{fig:keword-search-explanation}
+		\label{fig:keyword-search-explanation}
 	\end{minipage}\hfill
@@
 \plan{decide: what to mention here, max 1 page text}
-\todo{maybe: instantiate model, or at least partly talk about it}
-\todo{diffing, manual regex?, other summarization?, BART? <- we could reference that from related work then}
 

### 2019-10-25 thesis/txt/3-data-set.tex
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet

@@
 \section{Motivation}
-originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how strutured or unstructured they are.
-Then labeling of one build log information, namely the reason the build failed, as well as keywords and stuructural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results
+originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how structured or unstructured they are.
+Then labeling of one build log information, namely the reason the build failed, as well as keywords and structural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results
 
@@
 Our first task was to determine a set of repositories to query logs from.
-Our \texttt{GHTorrentParser} can query the GHTorrent dataset for the most popular languages on github and the most popular repositories for a given language.
+Our \texttt{GHTorrentParser} can query the GHTorrent~\cite{gousios2013ghtorrent} data set for the most popular languages on github and the most popular repositories for a given language.
 \emph{Popularity} in this case is defined as the number of watches.
@@
 \subsection{Sampling Builds}
-The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API, to obtain the newest builds for a given repository.
+The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, to obtain the newest builds for a given repository.
 As most builds on Travis CI are successful \mention{citation needed} we use a stratified sampling approach: \texttt{TravisRequester} saves the found builds in logs in buckets according to their state.
@@
 \subsection{Sampling Logs}
-For each build the \texttt{TravisRequester} then selects a log to download. Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
+For each build the \texttt{TravisRequester} then selects a log to download.
+Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
 A single build can consist of multiple jobs, e.g.\ building and executing tests in various different testing environments.
@@
 \section{Collection Process}
-For our inital data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
+For our initial data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
 For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
@@
 \subsection{Output Examples: Build Failure Reason}
-We labeled the first occuring substring describing the failure. If there were multiple errors described we took the first continuous block of error description.
+We labeled the first occuring substring describing the failure.
+If there were multiple errors described we took the first continuous block of error description.
 
@@
 Because we are using xml to save our example sets, we also had to make sure to escape respective special characters (ampersand, less than).
+
+\section{Threats to Validity}
+\bp{some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed
+
+we are not developers of the projects and we did not analyze their travis configuration: possible that we labeled parts that presented an error, though the build did not fail because of that error
+
+end all the points with: we tried to remedy this by (e.g.\ validations)
+}
 
@@
 For the \emph{Failing Build Log Data Set} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
-As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with differen build logs and systems.
+As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
 We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
@@
 Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
+We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure \ref{fig:dev-mail} shows one of the mails sent out.
+The email included links to the corresponding commits, build overview and log file.
+We asked the receivers to fill out a short survey in case our extraction was not correct.
+Look at Figure \ref{fig:dev-survey} to get an impression of the survey.
+In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
+As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/dev-mail.png}
+	\caption{An example of the mails we sent out to developers for validation of our labeled log part}
+	\label{fig:dev-mail}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/dev-survey.png}
+	\caption{Survey for the validation with developers}
+	\label{fig:dev-survey}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received.pdf}
+		\caption{Proportions of Mails and Logs answered, undelivered and unanswered}
+		\label{fig:mails-answers-received}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
+		\caption{Responses to our developer survey}
+		\label{fig:mails-extraction-correct}
+	\end{minipage}
+\end{figure}
+
 \subsubsection{Results}
+In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
+32 of these mails could not be delivered, e.g. because they were addressed at noreply mail addresses.
+These 32 mails related to 68 of the build logs.
+We received answers from 61 developers, responding about 144 build logs.
+The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure \ref{fig:mails-answers-received}.
+
+Of the 144 answers, 132 said our extraction was correct.
+26 answered either "close, but not quite correct" or "no, the build failed for another reason".
+We manually inspected these negative answers and found that extractions were correct after all.
+This yields 12 log extractions in our example set that were not correct, shown in Figure \ref{fig:mails-extraction-correct}.
+
 \subsubsection{Discussion}
+This study highly strengthens the trust in the validity of the extracted build failure reasons in the \emph{Failing Build Log Data Set}.
+The study received answers about 18\% of the logs labelled in our build log, of which, after manual correction, 91\% said our labelled extractions were accurate.
+
+Most of the initial ``incorrect'' answers we adjusted in them manual inspection, stated that the proposed extraction did not show the whole reason the build failed.
+This is because we had to trim long labeled extractions to keep the emails readable.
+
+One of our extractions only showed a warning and the developer propose to also include the line above, stating that warnings are treated as errors in the build.
+In others that were identified as ``incorrect'' we labelled the error message of an error that later ignored and did not lead to the build failing.
+
 \subsubsection{Threats to Validity}
 
-\section{Threats to Validity}
-\bp{some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed
-
-we are not developers of the projects and we did not analyze their travis configuration: possible that we labeled parts that presented an error, though the build did not fail because of that error
-
-end all the points with: we tried to remedy this by (e.g.\ validations)
-}
-
 \end{document}

### 2019-10-25 thesis/txt/2-models.tex
various small fixes, citing webpages

@@
 We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly.
-Additionally we present a complimentary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
-From our analysis of build logs we share our notion of the retrievable information within a build log.
+Additionally, we present a complementary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
+From our analysis of build logs, we share our notion of retrievable information within a build log.
 
-\begin{figure}[h]
+\begin{figure}[htbp]
 	\centering
@@
 \section{Characteristics of a Build Log}
-\plan{citations needed, make clean figure of contribution of tools to log, 1 caro-review before finalized}
 The idea of CI is, to integrate new software changes fast and often to catch errors early~\cite{humble2010continuous}.
@@
 
-However these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects~\cite{staahl2014modeling}.
+However, these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects~\cite{staahl2014modeling}.
 Some smaller projects might use CI to just make sure their code compiles as a minimal check before reviewing a pull request.
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
 	\centering
@@
 
-\section{Retrievable Information in Build Logs}
-\plan{fix naming, then review again}
-\begin{figure}[h]
+\begin{figure}[htbp]
 	\centering
@@
 \end{figure}
+\section{Retrievable Information in Build Logs}
 Continuous integration build logs contain a huge amount of information about the stages in the CI build they correspond to.
-In this section we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
+In this section, we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
 Figure \ref{fig:build-log-information} shows the model.
 
-The central class of our model is the \emph{BuildLogInformation} (BLI), representing an piece of information possibly retrievable from a build log.
+The central class of our model is the \emph{BuildLogInformation} (BLI), representing a piece of information possibly retrievable from a build log.
 \emph{Possibly}, because a BuildLogInformation is not necessarily present in every build log.
@@
 BuildLogInformations can be hierarchically ordered by their textual representations containing each other.
-As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section \ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for BuildLogInformations whose structure we definetely know.
+As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section \ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for BuildLogInformations whose structure we definitely know.
 Most build log information types can appear in various hierarchical arrangements and therefore not contained in any other type in the model.
@@
 \begin{itemize}
-	\item \textbf{BuildPhase} Build logs can be divided in the sections produced by different tools.
+	\item \textbf{BuildPhase} Build logs can be divided into the sections produced by different tools.
 	      These build steps could be for example be a \texttt{TestPhase}, \textbf{LinterPhase}, \textbf{TravisWorker}, \textbf{GitFetch}, or \textbf{Sudoers} are some that we encountered in the logs.
 
-	\item \textbf{TravisPhase} Travis CI build logs consists of several build phases defined within the Travis CI configuration language.
-Within the build log each of these steps are framed by \lstinline{travis_fold:start:<travis phase name>} and \\ \lstinline{travis_fold:end:<build step name>}.
+	\item \textbf{TravisPhase} Travis CI build logs consist of several build phases defined within the Travis CI configuration language.
+Within the build log each of these steps is framed by \lstinline{travis_fold:start:<travis phase name>} and \\ \lstinline{travis_fold:end:<build step name>}.
 
@@
 	\item \textbf{TravisTiming} Travis can measure the time of specified sections of the build process.
-	      Timing information can be useful to retrieve when you want to automatically monitor the performance of your bui
+	      Timing information can be useful to retrieve when you want to automatically monitor the performance of your build.
 	      You can see an example of a Travis Build Step and its components within a build log in Figure \ref{fig:log-1}.
@@
 	      These come from the \texttt{travis.yml} configuring the build.
-	      Retrieving this information from the log could for example be useful when reverse engineering the build configuration.
+	      Retrieving this information from the log could, for example, be useful when reverse engineering the build configuration.
 	      You can see an example of a TriggeringCommand instantiation within a build log in Figure \ref{fig:log-3}.
@@
 
-\begin{figure}[hp]
+\begin{figure}[htbp]
 	\centering
@@
 \end{figure}
-\begin{figure}[hp]
+\begin{figure}[htbp]
 	\centering
@@
 
-\section{Characteristics of Information Retrieval Techniques}
-\plan{describe model classes, 1 page text}
-\begin{figure}[h]
+\begin{figure}[htbp]
 	\centering
@@
 \end{figure}
-For this thesis we want to evaluate different information retrieval techniques when applied to CI build logs.
+\section{Characteristics of Information Retrieval Techniques}
+\plan{describe model classes, 1 page text}
+For this thesis, we want to evaluate different information retrieval techniques when applied to CI build logs.
 We focus on techniques that do not require to parse the structure of a whole build log, but rather focus on extracting just one specified information.
@@
 	      This represents how much data is available for the technique to learn what to extract.
-	      For a BLIRT to be suited the available configuration has to match to needed configuration of the technique.
+	      For a BLIRT to be suited the available configuration has to match the needed configuration of the technique.
 	\item is connected to a \textbf{TextProcessor} retrieving the output.
@@
 We chose to investigate the applicability of generating regular expression programs by example to extracting information from build logs.
-In this work we refer to our interpretation of this technique as \emph{PBE}.
+In this work, we refer to our interpretation of this technique as \emph{PBE}.
 In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.
@@
 When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
-In the implementation we did have to apply a few text replacements as described in \ref{sec:impl-preprocessing}.
+In the implementation, we had to apply a few text replacements as described in \ref{sec:impl-preprocessing}.
 The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the synthesized program when given the corresponding input file.
-One or multiple I/O examples are needed as configuration for PBE, they are used to define substring of a log should be extracted.Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm.
+One or multiple I/O examples are needed as configuration for PBE, they are used to define substring of a log should be extracted.
+Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm.
 Both are described in Section \ref{sec:rw-prose}.
@@
 \subsection{Perspective: Usability vs. Technical Aspects}
-Generally, we are interested in whether a Programming by Example could replace manually writing regular expressions.
+Generally, we are interested in whether Programming by Example could replace manually writing regular expressions.
 Writing and especially maintaining regular expressions is known to be a difficult, tedious and error-prone task~\cite{michael2019regexes}.
@@
 Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
-Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on synthesizing programs from examples in an unknow interface.
+Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on synthesizing programs from examples in an unknown interface.
 Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
@@
 
-For our work we chose to look at the applicability of PBE from the \emph{technical} perspective.
-We investigate whether current program synthesis techniques are able to learn programs for information retrieval tasks in the domain of CI build logs.
-Furthermore we gather insights in how PBE has to be applied to yield useable results and perform best.
-Our implementation of PBE, is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
+For our work, we chose to look at the applicability of PBE from the \emph{technical} perspective.
+We investigate whether current program synthesis techniques can learn programs for information retrieval tasks in the domain of CI build logs.
+Furthermore, we gather insights into how PBE has to be applied to yield useable results and perform best.
+Our implementation of PBE is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
 Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
@@
 
-\subsection{Overview}
+\subsection{Introduction}
 Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
@@
 To retrieve the desired information from a build log, we parse the whole text and process it in the same way.
-The algorithm calculates the cosine simlarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
+The algorithm calculates the cosine similarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
 After summing up the similarities of each build log line to all the query lines, we sort the build log lines in decreasing similarity.
@@
 
-\subsection{Overview}
-When we are looking for a specific information within a great amount of unstructured information, a first ad-hoc approach is to search for keywords in the text we assume to be near the information we are looking for.
+\subsection{Introduction}
+When we are looking for a specific piece of information within a great amount of unstructured information, a first ad-hoc approach is to search for keywords in the text we assume to be near the information we are looking for.
 This was one of the most common approaches we took when searching for the build failure reason within a log when creating our data set.
@@
 SKWS is configured by giving a set of keywords.
-For a retrieval run we then take a whole build log file as input and search for all exact occurrences of the keywords.
-As keywords are often not directly describing the desired information but rather adjacent to the desired information, this technique not only retrieves the line with the keyword, but only the context around it.
+For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the keywords.
+As keywords are often not directly describing the desired information but rather adjacent to the desired information, this technique not only retrieves the line with the keyword but also the context around it.
 We chose a context of 10 lines above and below the keyword appearance.
@@
 
-Amar et al.
-used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}d \cite{amar2019mining}, as we describe in more detail in Section \ref{sec:rw-bl-analysis}
+Amar et al. used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section \ref{sec:rw-bl-analysis}.
 Figure \ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.

### 2019-10-29 thesis/txt/2-models.tex
loads of new images, updates to the plotting, integrated images in study results

@@
 \plan{write, 1/3 page, blocked by: rest of chapter}
-\label{sec:models}
+\label{sec:ir-techniques}
 %\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
@@
 \section{Characteristics of a Build Log}
+\label{sec:bl-characteristics}
 The idea of CI is, to integrate new software changes fast and often to catch errors early~\cite{humble2010continuous}.
@@
 \section{Retrievable Information in Build Logs}
+\label{sec:bli}
 Continuous integration build logs contain a huge amount of information about the stages in the CI build they correspond to.
@@
 \section{Characteristics of Information Retrieval Techniques}
+\label{sec:blirt}
 \plan{describe model classes, 1 page text}
@@
 \section{Information Retrieval Tasks}
+\label{sec:blir-tasks}
 \plan{what do we need here?, come up with model if we keep this, 1 page text max.}
@@
 
-\section{PROSE Program Synthesis}
+\section{Regular Expression Program Synthesis by Example}
+\label{sec:expl-pbe}
 \plan{2 caro-reviews before finalized}
@@
 \section{Text Similarity}
+\label{sec:expl-ts}
 \plan{2 caro-reviews before finalized}
@@
 \section{Simple Keyword Search}
+\label{sec:expl-skws}
 \plan{2 caro-reviews before finalized}
@@
 \section{Further Techniques}
+\label{sec:expl-rlr}
 \plan{decide: what to mention here, max 1 page text}
 
+\paragraph{Log Diff}
 Amar et al. used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section \ref{sec:rw-bl-analysis}.
 Figure \ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
+\paragraph{Random Line Retrieval}
+In our evaluation we want to compare against a basic deadline of randomly extracted lines.
+The random line retrieval technique (RLR) averages the number of lines in the outputs of the configuring examples and extracts this many lines randomly from the build log.
 

### 2019-10-29 thesis/txt/5-study.tex
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet
loads of new images, updates to the plotting, integrated images in study results

@@
 \section{Method}
+\bp{We compare three different techniques: PBE, TS, SKWS (itemize and link to their explanation?) and as a baseline: random line rerieval (RLR): retrieves random lines from the build log, (describe in chapper about BLIRTs??), number of lines: average of output lines from past}
 We configure the technique for every example set with an increasing count of I/O examples and then run the retrieval on the next I/O example, the \emph{test I/O example}.
@@
 	\item \textbf{Accuracy} \todo{currently: levenstein difference of input and output, maybe: change to false pos and neg lines}
-	\item \textbf{Proximity} \todo{can we usefully calculate that????}
+	\item \textbf{Proximity} \todo{No! let's do that with "}
 \end{itemize}
@@
 \section{Results}
-\todo{accuracy (or so) of retrievals with growing example number // overall averages \& detailed look on special cases //}
-\begin{figure}[hp]
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
+	\caption{Distribution of Category Combinations in the Example Sets used for Configuration in our Study}
+	\label{fig:categories-dataset}
+\end{figure}
+\begin{figure}[htbp]
 	\centering
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/accuracy-success-all.pdf}
-		\caption{caption}
-		\label{fig:accuracy-success-all}
+		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
+		\caption{Distribution of the Count of Categories within the Examples used for Configuartion in our Study}
+		\label{fig:categorycount-examplecount-dataset}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/line-diff-all.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
 		\caption{caption}
-		\label{fig:line-diff-all}
+		\label{fig:xxx}
+	\end{minipage}
+\end{figure}
+\subsection{Category Distribution in Data Set}
+Categories distributed in over data set
+- why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
+- Figure \ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
+- Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.
+
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
+		\caption{Successful Extractions per Number of Examples for PBE}
+		\label{fig:success-examples-pbe}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
+		\caption{Successful Extractions per Number of Examples for TS}
+		\label{fig:success-examples-ir}
+	\end{minipage}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
+		\caption{Successful Extractions per Number of Examples for SKWS}
+		\label{fig:success-examples-kw}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-rn.pdf}
+		\caption{Successful Extractions per Number of Examples for RLR}
+		\label{fig:success-examples-rn}
 	\end{minipage}
@@
 
-\begin{figure}[hp]
+\subsection{Regular Expression Program Synthesis by Example}
+
+\begin{figure}[htbp]
 	\centering
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/ouput-failed-pbe.pdf}
-		\caption{caption}
-		\label{fig:ouput-failed-pbe}
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
+		\caption{Successful Extractions per Number of Examples for PBE}
+		\label{fig:success-examples-pbe}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
-		\caption{caption}
-		\label{fig:success-all}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-pbe.pdf}
+		\caption{Precision of Extractions per Number of Examples for PBE}
+		\label{fig:precision-pbe}
+	\end{minipage}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-pbe.pdf}
+		\caption{Precision of PBE Extractions by CategoryCount}
+		\label{fig:precision-categorycount-examplecount-pbe}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-pbe.pdf}
+		\caption{Reasons for PBE Runs to Fail}
+		\label{fig:failure-reason-pbe}
 	\end{minipage}
@@
 
-\begin{figure}[hp]
+This section addresses the results produced by the PBE technique in our study.
+We start by comparing success rate and precision for different example counts and showing the influence of example categories.
+Next we go into detail in which cases pbe fails
+\subsubsection{Success-Rate}
+\subsubsection{Precision}
+\subsubsection{Example Categories}
+\subsubsection{Specific Failure Reasons}
+\todo{FAILURE REASON AGAINST EXAMPLE CATEGORIES}
+% \subsection{Successful Extractions}
+% successful is interpreted by us as: all lines that were desired (within our oracle) were also extracted during the test
+
+% Figure \ref{fig:success-all} shows how successful the four different tecnhiques were in our study.
+% Figure \ref{fig:success-examples-pbe} shows that the success rate for PBE decreases with increasing example count for pbe.
+Section \ref{TODO ref to pbe section} explains in more detail whi this fails
+% Figure \ref{fig:success-examples-ir} shows that the success rate for TS varies but stays roughly the same for different example counts
+% Figure \ref{fig:success-examples-kw} shows that the success rate for KWS varies but stays roughly the same for different example counts
+% Figure \ref{fig:success-examples-pbe} shows that
+
+\subsection{Text Similarity}
+
+\begin{figure}[htbp]
 	\centering
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
-		\caption{caption}
+		\caption{Successful Extractions per Number of Examples for TS}
 		\label{fig:success-examples-ir}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
-		\caption{caption}
-		\label{fig:success-examples-kw}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-ir.pdf}
+		\caption{Precision of Extractions per Number of Examples for TS}
+		\label{fig:precision-ir}
+	\end{minipage}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-ir.pdf}
+		\caption{Precision of TS Extractions by CategoryCount}
+		\label{fig:precision-categorycount-examplecount-ir}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+		\caption{xxx}
+		\label{fig:xxx}
 	\end{minipage}
@@
 
-\begin{figure}[hp]
+\subsubsection{Success-Rate}
+\subsubsection{Precision}
+\subsubsection{Example Categories}
+
+\subsection{Simple Keyword Search}
+
+\begin{figure}[htbp]
 	\centering
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
-		\caption{caption}
-		\label{fig:success-examples-pbe}
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
+		\caption{Successful Extractions per Number of Examples for SKWS}
+		\label{fig:success-examples-kw}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
-		\caption{caption}
-		\label{fig:success-examples-pbe}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-kw.pdf}
+		\caption{Precision of Extractions per Number of Examples for SKWS}
+		\label{fig:precision-kw}
 	\end{minipage}
 \end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-kw.pdf}
+		\caption{Precision of SKWS Extractions by CategoryCount}
+		\label{fig:precision-categorycount-examplecount-kw}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+		\caption{xxx}
+		\label{fig:xxx}
+	\end{minipage}
+\end{figure}
+
+\subsubsection{Success-Rate}
+\subsubsection{Precision}
+\subsubsection{Example Categories}
+
+\subsection{Random Line Retrieval}
+
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-rn.pdf}
+		\caption{Successful Extractions per Number of Examples for RLR}
+		\label{fig:success-examples-rn}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-rn.pdf}
+		\caption{Precision of Extractions per Number of Examples for RLR}
+		\label{fig:precision-rn}
+	\end{minipage}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-rn.pdf}
+		\caption{Precision of RLR Extractions by CategoryCount}
+		\label{fig:precision-categorycount-examplecount-rn}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+		\caption{xxx}
+		\label{fig:xxx}
+	\end{minipage}
+\end{figure}
+
+For completion this section reports the results for the random line retrieval technique, explained in detail in Section \ref{sec:}
+
+\subsubsection{Success-Rate}
+\subsubsection{Precision}
+\subsubsection{Example Categories}
+
+\subsection{Comparing All Techniques}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
+		\caption{Successful Extractions for all Techniques Compared}
+		\label{fig:success-all}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
+		\caption{Precision of Extractions for all Techniques Compared}
+		\label{fig:precision-all}
+	\end{minipage}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
+		\caption{\todo{todo}}
+		\label{fig:precision-category-singularity-all}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/single-cateogry-precision-all.pdf}
+		\caption{\todo{todo}}
+		\label{fig:single-cateogry-precision-all}
+	\end{minipage}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-all.pdf}
+		\caption{\todo{todo}}
+		\label{fig:precision-categorycount-examplecount-all}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+		\caption{\todo{todo}}
+		\label{fig:xxx}
+	\end{minipage}
+\end{figure}
+
+\subsubsection{Success-Rate}
+\subsubsection{Precision}
+\subsubsection{Example Categories}
 

### 2019-10-29 thesis/txt/5-study.tex
renamings in big study data analysis

@@
 \end{figure}
+
 \begin{figure}[htbp]
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
-		\caption{Distribution of the Count of Categories within the Examples used for Configuartion in our Study}
+		\caption{Distribution of the Count of Categories within the Examples used for Configuration in our Study}
 		\label{fig:categorycount-examplecount-dataset}
@@
 		\caption{caption}
-		\label{fig:xxx}
+		\label{fig:xxxy}
 	\end{minipage}
 \end{figure}
+
 \subsection{Category Distribution in Data Set}
@@
 - Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.
-
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
-		\caption{Successful Extractions per Number of Examples for PBE}
-		\label{fig:success-examples-pbe}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
-		\caption{Successful Extractions per Number of Examples for TS}
-		\label{fig:success-examples-ir}
-	\end{minipage}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
-		\caption{Successful Extractions per Number of Examples for SKWS}
-		\label{fig:success-examples-kw}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-rn.pdf}
-		\caption{Successful Extractions per Number of Examples for RLR}
-		\label{fig:success-examples-rn}
-	\end{minipage}
-\end{figure}
 
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-pbe.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-PBE.pdf}
 		\caption{Successful Extractions per Number of Examples for PBE}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-pbe.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-PBE.pdf}
 		\caption{Precision of Extractions per Number of Examples for PBE}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-pbe.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-PBE.pdf}
 		\caption{Precision of PBE Extractions by CategoryCount}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-pbe.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
 		\caption{Reasons for PBE Runs to Fail}
@@
 Section \ref{TODO ref to pbe section} explains in more detail whi this fails
-% Figure \ref{fig:success-examples-ir} shows that the success rate for TS varies but stays roughly the same for different example counts
-% Figure \ref{fig:success-examples-kw} shows that the success rate for KWS varies but stays roughly the same for different example counts
+% Figure \ref{fig:success-examples-ts} shows that the success rate for TS varies but stays roughly the same for different example counts
+% Figure \ref{fig:success-examples-skws} shows that the success rate for KWS varies but stays roughly the same for different example counts
 % Figure \ref{fig:success-examples-pbe} shows that
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-ir.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-TS.pdf}
 		\caption{Successful Extractions per Number of Examples for TS}
-		\label{fig:success-examples-ir}
+		\label{fig:success-examples-ts}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-ir.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-TS.pdf}
 		\caption{Precision of Extractions per Number of Examples for TS}
-		\label{fig:precision-ir}
+		\label{fig:precision-ts}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-ir.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-TS.pdf}
 		\caption{Precision of TS Extractions by CategoryCount}
-		\label{fig:precision-categorycount-examplecount-ir}
+		\label{fig:precision-categorycount-examplecount-ts}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-kw.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWSpdf}
 		\caption{Successful Extractions per Number of Examples for SKWS}
-		\label{fig:success-examples-kw}
+		\label{fig:success-examples-skws}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-kw.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWSpdf}
 		\caption{Precision of Extractions per Number of Examples for SKWS}
-		\label{fig:precision-kw}
+		\label{fig:precision-skws}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-kw.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWSpdf}
 		\caption{Precision of SKWS Extractions by CategoryCount}
-		\label{fig:precision-categorycount-examplecount-kw}
+		\label{fig:precision-categorycount-examplecount-skws}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-rn.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-RLR.pdf}
 		\caption{Successful Extractions per Number of Examples for RLR}
-		\label{fig:success-examples-rn}
+		\label{fig:success-examples-rlr}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-rn.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-RLR.pdf}
 		\caption{Precision of Extractions per Number of Examples for RLR}
-		\label{fig:precision-rn}
+		\label{fig:precision-rlr}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-rn.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-RLR.pdf}
 		\caption{Precision of RLR Extractions by CategoryCount}
-		\label{fig:precision-categorycount-examplecount-rn}
+		\label{fig:precision-categorycount-examplecount-rlr}
 	\end{minipage}\hfill

### 2019-10-30 thesis/txt/5-study.tex
some additional graphics and graphics cleanups

@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWSpdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWS.pdf}
 		\caption{Successful Extractions per Number of Examples for SKWS}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWSpdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWS.pdf}
 		\caption{Precision of Extractions per Number of Examples for SKWS}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWSpdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWS.pdf}
 		\caption{Precision of SKWS Extractions by CategoryCount}

### 2019-10-30 evaluation/evaluate-results.R
during evaluation, track test input file line count to calc accuracy later, track test category and context size factor for meta-optimization of ts/skws/random exrtaction

@@ -45,6 +45,8 @@ getDataFrameForPBEResultsFile <- function(path) {
     allKeywords <- xmlValue(test[["AllKeywords"]][[1]])
     searchKeywords <- select_keywords_to_search(allKeywords)
     categories <- xmlValue(test[["Categories"]][[1]])
+    testInputLineCount <- xmlValue(test[["TestInputLineCount"]][[1]])
+    testCategory <- xmlValue(test[["TestCategory"]][[1]])
     
     data = rbind(
       data,
@@ -62,6 +64,9 @@ getDataFrameForPBEResultsFile <- function(path) {
         SearchKeywords = searchKeywords,
         AllKeywords = allKeywords,
         Categories = categories,
+        TestInputLineCount = testInputLineCount,
+        TestCategory = testCategory,
+        ContextSizeFactor = 1,
         stringsAsFactors = FALSE
       )
     )

### 2019-10-30 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisProgram.cs

@@ -145,6 +145,7 @@ namespace pbeextractionbuildlogs
 				{
 					var analysisResult = ApplyToFileWithLearningData(Config.SAMPLE_DIRECTORY + testSample.InputPath, currentLearningData, new AnalysisResult<OutputType>(), false);
 					analysisResult.DesiredOutput = testSample.Output;
+					analysisResult.TestCategory = testSample.Category;
 					// Console.WriteLine(ConsoleOutput.PrintAnalysisResult(analysisResult, 0, true));
 					testResults.Add(analysisResult);
 				}

### 2019-10-30 pbe-extraction-buildlogs/pbe-extraction-buildlogs/AnalysisSession.cs

@@ -69,6 +69,7 @@ namespace pbeextractionbuildlogs
 			ConsolePrinter consolePrinter = new ConsolePrinter(verbose);
 
 			var inputRegion = AnalysisUtil.RegionFromFile(inputPath);
+			result.TestInputLineCount = AnalysisUtil.BuildlogLineCount(inputPath);
 
 			consolePrinter.WriteLine("Starting to learn program");
 			Stopwatch learningStopwatch = Stopwatch.StartNew();

### 2019-10-30 pbe-extraction-buildlogs/pbe-extraction-buildlogs/DataClasses.cs

@@ -10,6 +10,8 @@ namespace pbeextractionbuildlogs
 		public string ProgramName { get; set; }
 		public string LearnedProgram { get; set; }
 		public string TestInputPath { get; set; }
+		public int TestInputLineCount { get; set; }
+		public string TestCategory { get; set; }
 		public OutputType Output { get; set; }
 		public OutputType DesiredOutput { get; set; }
 		public bool Successful { get; set; }

### 2019-10-30 pbe-extraction-buildlogs/pbe-extraction-buildlogs/Util.cs

@@ -1,6 +1,7 @@
 ﻿using System;
 using System.Collections.Generic;
 using System.IO;
+using System.Linq;
 using System.Text;
 using System.Xml.Serialization;
 using Microsoft.ProgramSynthesis.DslLibrary;
@@ -50,6 +51,11 @@ namespace pbeextractionbuildlogs
 			StringRegion region = RegionSession.CreateStringRegion(text);
 			fileCache[path] = region;
 			return region;
+		}
+
+		public static int BuildlogLineCount(string path)
+		{
+			return File.ReadLines(path).Count();
 		}
 	}
 

### 2019-10-30 r-extractions/information-retrieval.R

@@ -37,6 +37,7 @@ run_learning_step <- function(train_examples, test_examples, step_results) {
   train_lines <- get_ided_line_samples(train_examples)
   test_lines <-
     get_ided_line_samples(test_examples, only_output_lines = FALSE)
+  step_results[1, "TestInputLineCount"] <- length(test_lines)
   total_lines <- rbind(train_lines, test_lines)
   
   prep_fun <- identity
@@ -107,13 +108,17 @@ run_learning_step <- function(train_examples, test_examples, step_results) {
   sorted_similarity_sums <- sort(similarity_sums, decreasing = TRUE)
 
   # select the lines to count as extracted
-  avg_output_line_count <- avg_output_line_count(train_examples)
+  context_size_factor <- 1
+  avg_output_line_count <- avg_output_line_count(train_examples) * context_size_factor
+
   filtered_similarity_sums <- sorted_similarity_sums[1:min(avg_output_line_count, length(sorted_similarity_sums))] 
   extracted_lines <-
     subset(test_lines, id %in% names(filtered_similarity_sums))
   step_results[1, "TestOutput"] <-
     join_extracted_lines(extracted_lines[["lines"]])
-  step_results[1, "TestInputPath"] <- train_examples[1, "input_path"]
+  step_results[1, "TestInputPath"] <- test_examples[1, "input_path"]
+  step_results[1, "TestCategory"] <- test_examples[1, "category"]
+  step_results[1, "ContextSizeFactor"] <- context_size_factor
   
   end_time_application <- Sys.time()
   step_results[1, "ApplicationDuration"] <-

### 2019-10-30 r-extractions/keyword-search.R

@@ -16,7 +16,7 @@ source(paste(main_path, "/r-extractions/utilities.R", sep = ""))
 source(paste(main_path, "/r-extractions/example-set.R", sep = ""))
 source(paste(main_path, "/evaluation/evaluate-results.R", sep = ""))
 
-run_analysis <- function(file, keywords, context_width) {
+run_analysis <- function(file, keywords, context_width, step_results) {
   log <- read_build_log_from_file(file, sample_path)
   lines <- unlist(stri_split_lines(log, omit_empty = TRUE))
 
@@ -35,7 +35,9 @@ run_analysis <- function(file, keywords, context_width) {
       }
     }
   }
-  return(join_extracted_lines(lines[context_added_lines]))
+  step_results[1, "TestOutput"] <- join_extracted_lines(lines[context_added_lines])
+  step_results[1, "TestInputLineCount"] <- length(lines)
+  return(step_results)
 }
 
 run_keyword_search_step <- function(train_examples, test_examples, step_results) {
@@ -45,19 +47,24 @@ run_keyword_search_step <- function(train_examples, test_examples, step_results)
   step_results[1, "SearchKeywords"] <- paste(selected, collapse = ", ")
   step_results[1, "LearnedProgram"] <- paste(selected, collapse = ", ")
 
+  # select the lines to count as extracted
+  context_size_factor <- 1
+  avg_output_line_count <- avg_output_line_count(train_examples) * context_size_factor
+
   end_time_learning <- Sys.time()
   step_results[1, "LearningDuration"] <- sys_timing_to_time(start_time_learning, end_time_learning)
   step_results[1, "TestInputPath"] <- test_examples[1, "input_path"]
 
   start_time_application <- Sys.time()
 
-  output <- run_analysis(test_examples[1, "input_path"], selected, context_width = 10)
+  step_results <- run_analysis(test_examples[1, "input_path"], selected, context_width = avg_output_line_count, step_results)
 
   end_time_application <- Sys.time()
   step_results[1, "ApplicationDuration"] = sys_timing_to_time(start_time_application, end_time_application)
+  step_results[1, "TestCategory"] <- test_examples[1, "category"]
+  step_results[1, "ContextSizeFactor"] <- context_size_factor
 
-  step_results[1, "TestOutput"] <- output
-  step_results
+  return(step_results)
 }
 
 run_keyword_search_extraction <- function() {
@@ -66,7 +73,7 @@ run_keyword_search_extraction <- function() {
[…]

### 2019-10-30 r-extractions/random-selection.R

@@ -16,11 +16,19 @@ source(paste(main_path, "/r-extractions/utilities.R", sep = ""))
 source(paste(main_path, "/r-extractions/example-set.R", sep = ""))
 source(paste(main_path, "/evaluation/evaluate-results.R", sep = ""))
 
-run_analysis <- function(file, examples) {
+run_analysis <- function(file, examples, step_results) {
   log <- read_build_log_from_file(file, sample_path)
   lines <- unlist(stri_split_lines(log, omit_empty = TRUE))
 
-  return(join_extracted_lines(sample(lines, min(avg_output_line_count(examples), length(lines)))))
+  step_results[1, "TestInputLineCount"] <- length(lines)
+
+  # select the lines to count as extracted
+  context_size_factor <- 1
+  avg_output_line_count <- avg_output_line_count(examples) * context_size_factor
+  step_results[1, "ContextSizeFactor"] <- context_size_factor
+
+  step_results[1, "TestOutput"] <- join_extracted_lines(sample(lines, min(avg_output_line_count, length(lines))))
+  return(step_results)
 }
 
 run_random_extraction_step <- function(train_examples, test_examples, step_results) {
@@ -34,20 +42,20 @@ run_random_extraction_step <- function(train_examples, test_examples, step_resul
 
   start_time_application <- Sys.time()
 
-  output <- run_analysis(test_examples[1, "input_path"], train_examples)
+  step_results <- run_analysis(test_examples[1, "input_path"], train_examples, step_results)
 
   end_time_application <- Sys.time()
   step_results[1, "ApplicationDuration"] = sys_timing_to_time(start_time_application, end_time_application)
+  step_results[1, "TestCategory"] <- test_examples[1, "category"]
 
-  step_results[1, "TestOutput"] <- output
-  step_results
+  return(step_results)
 }
 
 run_random_selection_extraction <- function() {
   verb <- opt_get_verb()
 
   if (verb == "analyze") {
-    result <- run_analysis(file = opt_get("file"), examples = get_exampleset(opt_get("program")))
+    result <- run_analysis(file = opt_get("file"), examples = get_exampleset(opt_get("program")), empty_results_data_frame())[1, "TestOutput"]
     cat(result)
   } else if (verb == "evaluate") {
     program <- opt_get("program")

### 2019-10-30 r-extractions/utilities.R

@@ -170,6 +170,9 @@ empty_results_data_frame <- function() {
       SearchKeywords = character(),
       AllKeywords = character(),
       Categories = character(),
+      TestInputLineCount = numeric(),
+      TestCategory = numeric(),
+      ContextSizeFactor = numeric(),
       stringsAsFactors = FALSE
     )
   )

### 2019-10-30 r-extractions/keyword-search.R
fixes for new eval runs

@@ -5,6 +5,7 @@
 suppressPackageStartupMessages({
   library(optigrab)
   library(stringi)
+  library(purrr)
 })
 
 main_path <<- "/Users/Laci/Documents/Delft/master-thesis"

### 2019-10-30 r-extractions/keyword-search.R
keep empty lines in r extractions

@@ -19,7 +19,7 @@ source(paste(main_path, "/evaluation/evaluate-results.R", sep = ""))
 
 run_analysis <- function(file, keywords, context_width, step_results) {
   log <- read_build_log_from_file(file, sample_path)
-  lines <- unlist(stri_split_lines(log, omit_empty = TRUE))
+  lines <- unlist(stri_split_lines(log, omit_empty = FALSE))
 
   filtered_lines <- logical(length(lines))
   for (i in 1:length(keywords)) {

### 2019-10-30 r-extractions/random-selection.R

@@ -18,7 +18,7 @@ source(paste(main_path, "/evaluation/evaluate-results.R", sep = ""))
 
 run_analysis <- function(file, examples, step_results) {
   log <- read_build_log_from_file(file, sample_path)
-  lines <- unlist(stri_split_lines(log, omit_empty = TRUE))
+  lines <- unlist(stri_split_lines(log, omit_empty = FALSE))
 
   step_results[1, "TestInputLineCount"] <- length(lines)
 

### 2019-10-30 r-extractions/utilities.R

@@ -59,7 +59,7 @@ get_lines_containing_output <-
     }
     
     if (split_into_lines) {
-      output_lines <- stri_split_lines(output_lines, omit_empty = TRUE)
+      output_lines <- stri_split_lines(output_lines, omit_empty = FALSE)
     }
     return(output_lines)
   }

### 2019-10-31 thesis/txt/3-data-set.tex
various small fixes, citing webpages
bigger data sets for meta-parameter optimization

@@
 \section{Labeling}
-\subsection{Output Examples: Build Failure Reason}
+\subsection*{Output Examples: Build Failure Reason}
 We labeled the first occuring substring describing the failure.
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received.pdf}
-		\caption{Proportions of Mails and Logs answered, undelivered and unanswered}
-		\label{fig:mails-answers-received}
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-mails.pdf}
+		\caption{Proportions of Mails answered, unanswered, not delivered and no mail found}
+		\label{fig:mails-answers-received-mails}
 	\end{minipage}\hfill
@@
 \end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
+		\caption{Proportions of Logs answered, undelivered and unanswered}
+		\label{fig:mails-answers-received-builds}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/logs-per-mail.pdf}
+		\caption{Responses to our developer survey}
+		\label{fig:mails-logs-per-mail}
+	\end{minipage}
+\end{figure}
 
@@
 We received answers from 61 developers, responding about 144 build logs.
-The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure \ref{fig:mails-answers-received}.
+The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure \ref{fig:mails-answers-received-mails} and Figure \ref{fig: mails-answers-received-builds}.
 

### 2019-10-31 evaluation/evaluate-results.R

@@ -18,7 +18,7 @@ getDataFrameForPBEResultsFile <- function(path) {
   oldw <- getOption("warn")
   options(warn = -1)
   
-  setwd(paste(main_path, "/evaluation/results/pbe", sep = ""))
+  setwd(paste(main_path, "/evaluation/results/context-factor-size/pbe", sep = ""))
   xml <- xmlTreeParse(file = path)
   
   data <- empty_results_data_frame()
@@ -45,8 +45,12 @@ getDataFrameForPBEResultsFile <- function(path) {
     allKeywords <- xmlValue(test[["AllKeywords"]][[1]])
     searchKeywords <- select_keywords_to_search(allKeywords)
     categories <- xmlValue(test[["Categories"]][[1]])
+    print('xxxx')
+    print(test)
     testInputLineCount <- xmlValue(test[["TestInputLineCount"]][[1]])
+    print(testInputLineCount)
     testCategory <- xmlValue(test[["TestCategory"]][[1]])
+    print(testCategory)
     
     data = rbind(
       data,
@@ -106,8 +110,8 @@ calculate_accuracy <- function(data) {
 
 save_evaluation_result <- function(result, program_name, technique, selection, learning_step_count, test_count) {
   result <- calculate_accuracy(result)
-  print(technique)
-  message(paste0(main_path, "/evaluation/results/", technique))
+  #print(technique)
+  #message(paste0(main_path, "/evaluation/results/", technique))
   setwd(paste0(main_path, "/evaluation/results/", technique))
   results_file_name <- evaluation_identification(technique, gsub("/", "@", program_name), selection, learning_step_count, test_count)
 

### 2019-11-01 thesis/txt/2-models.tex
incorporate kw 44 structure feedback in thesis, some plot advancements

@@
 
-\chapter{Information Retrieval Techniques for Build Logs}
+\chapter{Chunk Retrieval Techniques for Build Logs}
 \plan{whole chapter: some reordering and reviewing to do, write about 3 pages about ir technique model classes and ir tasks and other techniques}
@@
 \end{figure}
-\section{Retrievable Information in Build Logs}
+\section{Information Chunks in Build Logs}
 \label{sec:bli}
@@
 \end{figure}
-\section{Characteristics of Information Retrieval Techniques}
+\section{Characteristics of Chunk Retrieval Techniques}
 \label{sec:blirt}
@@
 
-\section{Information Retrieval Tasks}
-\label{sec:blir-tasks}
-\plan{what do we need here?, come up with model if we keep this, 1 page text max.}
-Previous sections gave various examples of situations where a developer or a researcher wants to retrieve information from a build log.
-The goal of this work is to clarify which BLIRT is suited for their specific task.
-In this section we structure we present different important characteristics of such an IR task.
-You can see the model in Figure \ref{fig:model-ir-task}
+% \section{Information Retrieval Tasks}
+% \label{sec:blir-tasks}
+% \plan{what do we need here?, come up with model if we keep this, 1 page text max.}
+% Previous sections gave various examples of situations where a developer or a researcher wants to retrieve information from a build log.
+% The goal of this work is to clarify which BLIRT is suited for their specific task.
+% In this section we structure we present different important characteristics of such an IR task.
+% You can see the model in Figure \ref{fig:model-ir-task}
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/ir-task.pdf}
-	\caption{Model for an Information Retrieval Task}
-	\label{fig:model-ir-task}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth, clip]{img/ir-task.pdf}
+% 	\caption{Model for an Information Retrieval Task}
+% 	\label{fig:model-ir-task}
+% \end{figure}
 
-A InformationRetrievalTask
-\begin{itemize}
-	\item has a specific amount and kind of \textbf{Configuration} available.
-	      This represents how much data is available for the technique to learn what to extract.
-	      For a BLIRT to be suited the available configuration has to match the needed configuration of the technique.
-	\item is connected to a \textbf{TextProcessor} retrieving the output.
-	      This can be for example a developer reading the output or a program.
-	      Different TextProcessors require different accuracies in the output, e.g.
+% A InformationRetrievalTask
+% \begin{itemize}
+% 	\item has a specific amount and kind of \textbf{Configuration} available.
+% 	      This represents how much data is available for the technique to learn what to extract.
+% 	      For a BLIRT to be suited the available configuration has to match the needed configuration of the technique.
+% 	\item is connected to a \textbf{TextProcessor} retrieving the output.
+% 	      This can be for example a developer reading the output or a program.
+% 	      Different TextProcessors require different accuracies in the output, e.g.
 a program needs exact retrievals to process automatically, while a developer can cope easier with falsely extracted lines.
-\end{itemize}
-\todo{give 2-3 concrete example instantiations here}
+% \end{itemize}
+% \todo{give 2-3 concrete example instantiations here}
 
@@
 
-\section{Regular Expression Program Synthesis by Example}
+\subsection{Regular Expression Program Synthesis by Example (PBE)}
 \label{sec:expl-pbe}
@@
 
-\subsection{Introduction}
 \emph{Programming by Example (PBE)} is a technique where programs are synthesized according to in and output examples provided by the user.
@@
 
-\subsection{Method}
+\paragraph{Method}
 In/Output examples (I/O examples) are the main driver of Programming by Example.
@@
 
-\subsection{Perspective: Usability vs. Technical Aspects}
-Generally, we are interested in whether Programming by Example could replace manually writing regular expressions.
-Writing and especially maintaining regular expressions is known to be a difficult, tedious and error-prone task~\cite{michael2019regexes}.
-There are two ways to approach this question: from the usability side or the technical side.
+% \subsection{Perspective: Usability vs. Technical Aspects}
+% Generally, we are interested in whether Programming by Example could replace manually writing regular expressions.
+% Writing and especially maintaining regular expressions is known to be a difficult, tedious and error-prone task~\cite{michael2019regexes}.
+% There are two ways to approach this question: from the usability side or the technical side.
 
-When studying the applicability of PBE from the \emph{usability} perspective you run into questions like
-\begin{itemize}
-	\item Are users faster when using PBE compared to manual regex construction?
-	\item Are users more comfortable using PBE over manual regex construction?
-	\item Are users confident in the resulting regular expression program from PBE?
-	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
-\end{itemize}
-Some of these were already evaluated in existing works about PBE and user interaction~\cite{mayer2015user,lau2009why-programming-by-demonstration,miller2001outlier}.
-Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
-Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on synthesizing programs from examples in an unknown interface.
-Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
-We feel such questions of usability can be answered separately from the application domain of build logs.
+% When studying the applicability of PBE from the \emph{usability} perspective you run into questions like
+% \begin{itemize}
+% 	\item Are users faster when using PBE compared to manual regex construction?
+% 	\item Are users more comfortable using PBE over manual regex construction?
+% 	\item Are users confident in the resulting regular expression program from PBE?
+% 	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
+% \end{itemize}
+% Some of these were already evaluated in existing works about PBE and user interaction~\cite{mayer2015user,lau2009why-programming-by-demonstration,miller2001outlier}.
+% Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
+% Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on synthesizing programs from examples in an unknown interface.
+% Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
+% We feel such questions of usability can be answered separately from the application domain of build logs.
 
-For our work, we chose to look at the applicability of PBE from the \emph{technical} perspective.
-We investigate whether current program synthesis techniques can learn programs for information retrieval tasks in the domain of CI build logs.
-Furthermore, we gather insights into how PBE has to be applied to yield useable results and perform best.
-Our implementation of PBE is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
-Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
+% For our work, we chose to look at the applicability of PBE from the \emph{technical} perspective.
+% We investigate whether current program synthesis techniques can learn programs for information retrieval tasks in the domain of CI build logs.
+% Furthermore, we gather insights into how PBE has to be applied to yield useable results and perform best.
+% Our implementation of PBE is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
+% Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
 
-\section{Text Similarity}
+\subsection{Common Text Similarity (CTS)}
 \label{sec:expl-ts}
@@
 
-\subsection{Introduction}
 Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
@@
 
-\subsection{Method}
+\paragraph{Method}
 To configure a retrieval though text similarity we chose to use the same concept of I/O examples as for PBE.
@@
 
-\section{Simple Keyword Search}
+\subsection{Keyword Search (KWS)}
 \label{sec:expl-skws}
@@
 
-\subsection{Introduction}
 When we are looking for a specific piece of information within a great amount of unstructured information, a first ad-hoc approach is to search for keywords in the text we assume to be near the information we are looking for.
@@
 
-\subsection{Method}
+\paragraph{Method}
 SKWS is configured by giving a set of keywords.
@@
 
-\section{Further Techniques}
+\subsection{Random Line Retrieval (RLR)}
+
+\subsection{Other Techniques}
 \label{sec:expl-rlr}

### 2019-11-01 thesis/txt/3-data-set.tex
incorporate kw 44 structure feedback in thesis, some plot advancements

@@
 
-\chapter{The Failing Build Logs Data Set}
+\chapter{BUILDS - BUIld Log Data Set}
 \includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
@@
 
-\section{Log Collector}
+\section{Log Collection}
 To collect a broad range of build logs we built the \texttt{Log Collector} using ruby.
 
-\subsection{Sampling Repositories}
+\subsection{Repository Sampling}
 Our first task was to determine a set of repositories to query logs from.
@@
 
-\subsection{Sampling Builds}
+\subsection{Build Sampling}
 The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, to obtain the newest builds for a given repository.
@@
 
-\subsection{Sampling Logs}
+\subsection{Log Sampling}
 For each build the \texttt{TravisRequester} then selects a log to download.
@@
 
-\section{Collection Process}
-For our initial data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
-For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
-our impression?
-\todo{image!}
+% \section{Collection Process}
+% For our initial data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
+% For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
+% our impression?
+% \todo{image!}
 
-\section{Build Failure Reason}
-\todo{WHY?
+% TODO describe somewhere else
+% \section{Build Failure Reason}
+% \todo{WHY?
 one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined retrieval   cause that would be simple for PROSE retrieval -> better comparability}
 
-\section{Data Model}
+\section{Data Structure}
 For our study, described in Chapter \ref{sec:study}, we want to investigate the retrieval capabilities of three techniques.
@@
 
-\subsection{Example Set}
+\paragraph{Example Set}
 Our data set is organized in example sets.
@@
 
-\subsection{In / Output Example}
+\paragraph{In / Output Example}
 In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
@@
 
-\subsection{Keywords}
+\paragraph{Keywords}
 The keyword search is configured by a list of keywords which are searched in the document with plain text search.
@@
 
-\paragraph{Description}
-\todo{for simple keyword search - imitate what users would search for ad-hoc}
+% \paragraph{Description}
+% \todo{for simple keyword search - imitate what users would search for ad-hoc}
 
-\todo{learning steps combining keywords -> similar to how devs would learn from reading those models}
+% \todo{learning steps combining keywords -> similar to how devs would learn from reading those models}
 
-\subsection{Categories}
+\paragraph{Categories}
 Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
@@
 
-\subsection{Sending Mails to Developers}
+\subsection{Developer Survey}
 \subsubsection{Introduction}

### 2019-11-01 thesis/txt/5-study.tex
incorporate kw 44 structure feedback in thesis, some plot advancements

@@
 
-\chapter{Technique Comparison Study}
+\chapter{Empirical Comparison Study}
 \label{sec:study}
-\section{Introduction}
 To investigate how different factors \todo{do we list these somewhere?} influence BLIRTs we evaluate the three techniques implemented in our tool on the \emph{Failing Build Log Data Set}.
@@
 
-\section{Method}
+\section{Study Design}
 \bp{We compare three different techniques: PBE, TS, SKWS (itemize and link to their explanation?) and as a baseline: random line rerieval (RLR): retrieves random lines from the build log, (describe in chapper about BLIRTs??), number of lines: average of output lines from past}
@@
 
-\subsection{Regular Expression Program Synthesis by Example}
+\subsection{Regular Expression Program Synthesis by Example (PBE)}
 
@@
 
-\subsection{Text Similarity}
+\subsection{Common Text Similarity (CTS)}
 
@@
 
-\subsection{Simple Keyword Search}
+\subsection{Keyword Search (KWS)}
 
@@
 
-\subsection{Random Line Retrieval}
+\subsection{Random Line Retrieval (RLR)}
 

### 2019-11-04 thesis/txt/1-related-work.tex
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet
incorporate kw 44 structure feedback in thesis, some plot advancements
incorporate second kw 44 sturcture feedback

@@
 
-\chapter{Related Work}
+\chapter{Background}
 \plan{all of RW: 4 - 5 pages left to do + some research!}
@@
 \todo{introduction \& glue text}
-This section presents various research works adjecent or foundational for our work.
+This section presents various research works adjacent or foundational for our work.
 Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation.
@@
 
-\section{Build Log Analysis and Augmentation}
+\section{Build Log Analysis and Augmentation - Related Work}
 \label{sec:rw-bl-analysis}
@@
 
-\section{Production Log Analysis}
+\section{System Log Analysis}
 \plan{research + write, 1/2 - 1 page}
@@
 \mention{ask Jean?}
-
-\section{Information Extraction and Retrieval Techniques}
-\plan{research + write, 1/2 - 1 page}
-\todo{explain difference here, reference pads(maybe that is already in log anlysis!) and stuff}
-\review{Getting the general tot p cic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
-Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
-On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
-For our use case, this could be applied by slicing the build logs into lines or small sections.
-Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
-Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}
-
-\mention{IR papers, maybe something about keyword search?}
-
-\section{Program Synthesis by Example}
-\plan{extend, 1 page}
-\todo{how much can/should we explain here?
-possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
-\review{
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework.
-It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples.
-Users can extract multiple fields and structure them with hierarchy and sequence.
-FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.
-
-We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information retrieval.
-}
-\mention{prose theory paper \cite{polozov2015flashmeta:}}
-\mention{\cite{rolim2017learning}}
-
-\todo{maybe scrap this section / incorporate last sentence somewhere else, expalnation will mostly be in rw. How to usefully sturcture the stuff above this?}
-In the following we want to give an impression on how the PROSE library and specifically the Flash Extract DSL synthesize programs for extracting substrings from text via regular expressions.
-\todo{how much can/should we explain here?
-possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
-Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm. Both are described in \todo{ref rw sections}.
 
@@
   Modifications in the build configuration might change the tools involved in the build and therefore the composition of the build log.
+  Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adopt their log messages over time~\cite{yuan2012characterizing}.
 \end{itemize}
@@
 In contrast to that, this thesis takes a look at techniques to gater a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.
+
+\section{Information Extraction and Retrieval Techniques}
+\plan{research + write, 1/2 - 1 page}
+\todo{explain difference here, reference pads(maybe that is already in log anlysis!) and stuff}
+\review{Getting the general tot p cic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
+Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
+On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
+For our use case, this could be applied by slicing the build logs into lines or small sections.
+Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
+Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}
+
+\mention{IR papers, maybe something about keyword search?}
+
+\section{Program Synthesis by Example}
+\label{sec:rw-prose}
+\plan{extend, 1 page}
+\todo{how much can/should we explain here?
+possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
+\review{
+Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework.
+It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples.
+Users can extract multiple fields and structure them with hierarchy and sequence.
+FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.
+
+We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information retrieval.
+}
+\mention{prose theory paper \cite{polozov2015flashmeta:}}
+\mention{\cite{rolim2017learning}}
+
+\todo{maybe scrap this section / incorporate last sentence somewhere else, expalnation will mostly be in rw. How to usefully sturcture the stuff above this?}
+In the following we want to give an impression on how the PROSE library and specifically the Flash Extract DSL synthesize programs for extracting substrings from text via regular expressions.
+\todo{how much can/should we explain here?
+possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
+Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm. Both are described in \todo{ref rw sections}.
 \end{document}

### 2019-11-04 thesis/txt/5-study.tex
incorporate second kw 44 sturcture feedback

@@
 
-\subsection{Random Line Retrieval (RLR)}
+% \subsection{Random Line Retrieval (RLR)}
 
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-RLR.pdf}
-		\caption{Successful Extractions per Number of Examples for RLR}
-		\label{fig:success-examples-rlr}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-RLR.pdf}
-		\caption{Precision of Extractions per Number of Examples for RLR}
-		\label{fig:precision-rlr}
-	\end{minipage}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-RLR.pdf}
-		\caption{Precision of RLR Extractions by CategoryCount}
-		\label{fig:precision-categorycount-examplecount-rlr}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-		\caption{xxx}
-		\label{fig:xxx}
-	\end{minipage}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-RLR.pdf}
+% 		\caption{Successful Extractions per Number of Examples for RLR}
+% 		\label{fig:success-examples-rlr}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-RLR.pdf}
+% 		\caption{Precision of Extractions per Number of Examples for RLR}
+% 		\label{fig:precision-rlr}
+% 	\end{minipage}
+% \end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-RLR.pdf}
+% 		\caption{Precision of RLR Extractions by CategoryCount}
+% 		\label{fig:precision-categorycount-examplecount-rlr}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+% 		\caption{xxx}
+% 		\label{fig:xxx}
+% 	\end{minipage}
+% \end{figure}
 
-For completion this section reports the results for the random line retrieval technique, explained in detail in Section \ref{sec:}
+% For completion this section reports the results for the random line retrieval technique, explained in detail in Section \ref{sec:}
 
-\subsubsection{Success-Rate}
-\subsubsection{Precision}
-\subsubsection{Example Categories}
+% \subsubsection{Success-Rate}
+% \subsubsection{Precision}
+% \subsubsection{Example Categories}
 

### 2019-11-04 thesis/txt/5-study.tex
restart study chapter

@@
 \label{sec:study}
-To investigate how different factors \todo{do we list these somewhere?} influence BLIRTs we evaluate the three techniques implemented in our tool on the \emph{Failing Build Log Data Set}.
+To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{Failing Build Log Data Set}.
+This chapter describes our study design, the analysis of the study results and threats to the validity of our conclusions.
+The analysis of the study results first focusses on each of the three techniques and describes how each one performs best.
+Later we compare them against each other and describe their trade offs against each other.
+This chapter answers our second research question and its subquestions:
+\begin{simplebox}{Research Questions}
+\begin{itemize}
+  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
+  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
+  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
+  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
+\end{itemize}
+\end{simplebox}
 
@@
 	\centering
-	\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
-	\caption{Process of our technique comparison study}
+	\includegraphics[width=\textwidth, clip]{img/study-design.pdf}
+	\caption{Study Design of our technique comparison study}
 	\label{fig:study}
@@
 \section{Study Design}
-\bp{We compare three different techniques: PBE, TS, SKWS (itemize and link to their explanation?) and as a baseline: random line rerieval (RLR): retrieves random lines from the build log, (describe in chapper about BLIRTs??), number of lines: average of output lines from past}
-We configure the technique for every example set with an increasing count of I/O examples and then run the retrieval on the next I/O example, the \emph{test I/O example}.
-The output from the test I/O example is the oracle for our evaluation.
-The examples are sorted and selected chronologically, i.e. the technique is configured with examples from the directly preceeding build logs to extract information from the test log.
-The extraction quality of a BLIRT run is evaluated on only one build log, as it should be suitable for every coming example.
-Especially the one directly succeeding the configuration.
-If the information retrieval there is bad, we expect the user to directly change the configuration again or be dissapointed with his selection of technique.
+For the comparison study we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections \ref{sec:expl-pbe},\ref{sec:expl-ts} and \ref{sec:expl-skws}.
+RLR, explained in Section \ref{sec:expl-rlr}, acts as a baseline for the comparison.
+We run four techniques on the example sets from the \emph{Failing Build Log Data Set}.
 
-When evaluating a BLIRT run we measure the following data points:
-\begin{itemize}
-	\item \textbf{Successful} A BLIRT run is successful when the retrieved output contains all the lines the oracle output.
-	\item \textbf{Accuracy} \todo{currently: levenstein difference of input and output, maybe: change to false pos and neg lines}
-	\item \textbf{Proximity} \todo{No! let's do that with "}
-\end{itemize}
+The examples are sorted chronologically, i.e. a technique is configured with examples from the directly preceding build logs.
+For each example set and each technique, we select one to five successive I/O examples as configuration, the \emph{configuring I/O examples}, and run the chunk retrieval on the next I/O example, the \emph{test I/O example}.
 
-taking The Failing Build Log Data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?
+For each of our evaluation runs we measure the desired vs. actual output lines of the chunk retrieval.
+The desired output is given by the output of the test I/O example, which acts as the oracle for our evaluation.
+From this we obtain true/false positives/negatives and calculate precision, recall and accuracy, which we use to answer \textbf{RQ2.2}.
+We register the number of examples used as configuration for each run to answer \textbf{RQ2.1} and their structural categories to answer \textbf{RQ2.3}.
 
-\section{Results}
+%taking The Failing Build Log Data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
-	\caption{Distribution of Category Combinations in the Example Sets used for Configuration in our Study}
-	\label{fig:categories-dataset}
-\end{figure}
+\section{Analysis}
+This section presents the evaluation results for PBE, CTS and KWS separately and discusses under which circumstances these techniques yield best results.
+Afterwards it compares the three techniques with each other and RLR as baseline.
+The section concludes with recommendations on which technique is suited for different situations.
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
+% 	\caption{Distribution of Category Combinations in the Example Sets used for Configuration in our Study}
+% 	\label{fig:categories-dataset}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
+% 		\caption{Distribution of the Count of Categories within the Examples used for Configuration in our Study}
+% 		\label{fig:categorycount-examplecount-dataset}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+% 		\caption{caption}
+% 		\label{fig:xxxy}
+% 	\end{minipage}
+% \end{figure}
+
+% \subsection{Category Distribution in Data Set}
+% Categories distributed in over data set
+% - why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
+% - Figure \ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
+% - Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.
 
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
-		\caption{Distribution of the Count of Categories within the Examples used for Configuration in our Study}
-		\label{fig:categorycount-examplecount-dataset}
+		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
+		\caption{Success of Chunk Retrieval Runs with PBE}
+		\label{fig:failure-reason-PBE}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-		\caption{caption}
-		\label{fig:xxxy}
-	\end{minipage}
-\end{figure}
-
-\subsection{Category Distribution in Data Set}
-Categories distributed in over data set
-- why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
-- Figure \ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
-- Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.
-
-\subsection{Regular Expression Program Synthesis by Example (PBE)}
-
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-PBE.pdf}
-		\caption{Successful Extractions per Number of Examples for PBE}
-		\label{fig:success-examples-pbe}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-PBE.pdf}
-		\caption{Precision of Extractions per Number of Examples for PBE}
-		\label{fig:precision-pbe}
+		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+		\caption{Success of Chunk Retrieval Runs with PBE Compared with Category Count}
+		\label{fig:failure-reason-categorycount-PBE}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-PBE.pdf}
-		\caption{Precision of PBE Extractions by CategoryCount}
-		\label{fig:precision-categorycount-examplecount-pbe}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
+		\caption{Precision of PBE Chunk Retrieval Results Compared with Example Count}
+		\label{fig:precision-extraction-result-PBE}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
-		\caption{Reasons for PBE Runs to Fail}
-		\label{fig:failure-reason-pbe}
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-singlecategory-swarm-PBE.pdf}
+		\caption{Precision of PBE Chunk Retrieval Compare with Example Count and Category Singularity}
+		\label{fig:precision-singlecategory-swarm-PBE}
 	\end{minipage}
 \end{figure}
+\subsection{Regular Expression Program Synthesis by Example (PBE)}
+Out of the 400 runs in our evaluation, 5 runs per each of the 80 example sets, PBE extracted all the desired lines in 138 cases.
+Figure \ref{fig:failure-reason-PBE} shows that in 89 cases a program was successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
+In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
+In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring examples.
 
-This section addresses the results produced by the PBE technique in our study.
-We start by comparing success rate and precision for different example counts and showing the influence of example categories.
-Next we go into detail in which cases pbe fails
-\subsubsection{Success-Rate}
-\subsubsection{Precision}
-\subsubsection{Example Categories}
-\subsubsection{Specific Failure Reasons}
-\todo{FAILURE REASON AGAINST EXAMPLE CATEGORIES}
+Figure \ref{fig:failure-reason-categorycount-PBE} shows that the success of the program syntesis algorithm highly depends on the structural categories present in the configuring examples.
+Programs could only be synthesized if at maximum two categories were present.
+
+More than three examples yield no improvement in the precision of PBE chunk retrieval, as you can see in Figures \ref{fig:precision-extraction-result-PBE} and \ref{fig:precision-singlecategory-swarm-PBE}.
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-PBE.pdf}
+% 		\caption{Successful Extractions per Number of Examples for PBE}
+% 		\label{fig:success-examples-pbe}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-PBE.pdf}
+% 		\caption{Precision of Extractions per Number of Examples for PBE}
+% 		\label{fig:precision-pbe}
+% 	\end{minipage}
+% \end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-PBE.pdf}
+% 		\caption{Precision of PBE Extractions by CategoryCount}
+% 		\label{fig:precision-categorycount-examplecount-pbe}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
+% 		\caption{Reasons for PBE Runs to Fail}
+% 		\label{fig:failure-reason-pbe}
+% 	\end{minipage}
+% \end{figure}
+
+% This section addresses the results produced by the PBE technique in our study.
+% We start by comparing success rate and precision for different example counts and showing the influence of example categories.
+% Next we go into detail in which cases pbe fails
+% \subsubsection{Success-Rate}
+% \subsubsection{Precision}
+% \subsubsection{Example Categories}
+% \subsubsection{Specific Failure Reasons}
+% \todo{FAILURE REASON AGAINST EXAMPLE CATEGORIES}
 % \subsection{Successful Extractions}
@@
 
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-TS.pdf}
-		\caption{Successful Extractions per Number of Examples for TS}
-		\label{fig:success-examples-ts}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-TS.pdf}
-		\caption{Precision of Extractions per Number of Examples for TS}
-		\label{fig:precision-ts}
-	\end{minipage}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-TS.pdf}
-		\caption{Precision of TS Extractions by CategoryCount}
-		\label{fig:precision-categorycount-examplecount-ts}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-		\caption{xxx}
-		\label{fig:xxx}
-	\end{minipage}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-TS.pdf}
+% 		\caption{Successful Extractions per Number of Examples for TS}
+% 		\label{fig:success-examples-ts}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-TS.pdf}
+% 		\caption{Precision of Extractions per Number of Examples for TS}
+% 		\label{fig:precision-ts}
+% 	\end{minipage}
+% \end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-TS.pdf}
+% 		\caption{Precision of TS Extractions by CategoryCount}
+% 		\label{fig:precision-categorycount-examplecount-ts}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+% 		\caption{xxx}
+% 		\label{fig:xxx}
+% 	\end{minipage}
+% \end{figure}
 
-\subsubsection{Success-Rate}
-\subsubsection{Precision}
-\subsubsection{Example Categories}
+% \subsubsection{Success-Rate}
+% \subsubsection{Precision}
+% \subsubsection{Example Categories}
 
@@
 
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWS.pdf}
-		\caption{Successful Extractions per Number of Examples for SKWS}
-		\label{fig:success-examples-skws}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWS.pdf}
-		\caption{Precision of Extractions per Number of Examples for SKWS}
-		\label{fig:precision-skws}
-	\end{minipage}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWS.pdf}
-		\caption{Precision of SKWS Extractions by CategoryCount}
-		\label{fig:precision-categorycount-examplecount-skws}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-		\caption{xxx}
-		\label{fig:xxx}
-	\end{minipage}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWS.pdf}
+% 		\caption{Successful Extractions per Number of Examples for SKWS}
+% 		\label{fig:success-examples-skws}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWS.pdf}
+% 		\caption{Precision of Extractions per Number of Examples for SKWS}
+% 		\label{fig:precision-skws}
+% 	\end{minipage}
+% \end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWS.pdf}
+% 		\caption{Precision of SKWS Extractions by CategoryCount}
+% 		\label{fig:precision-categorycount-examplecount-skws}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+% 		\caption{xxx}
+% 		\label{fig:xxx}
+% 	\end{minipage}
+% \end{figure}
 
-\subsubsection{Success-Rate}
-\subsubsection{Precision}
-\subsubsection{Example Categories}
+% \subsubsection{Success-Rate}
+% \subsubsection{Precision}
+% \subsubsection{Example Categories}
 
@@
 \subsection{Comparing All Techniques}
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
-		\caption{Successful Extractions for all Techniques Compared}
-		\label{fig:success-all}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
-		\caption{Precision of Extractions for all Techniques Compared}
-		\label{fig:precision-all}
-	\end{minipage}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
+% 		\caption{Successful Extractions for all Techniques Compared}
+% 		\label{fig:success-all}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
+% 		\caption{Precision of Extractions for all Techniques Compared}
+% 		\label{fig:precision-all}
+% 	\end{minipage}
+% \end{figure}
 
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
-		\caption{\todo{todo}}
-		\label{fig:precision-category-singularity-all}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/single-cateogry-precision-all.pdf}
-		\caption{\todo{todo}}
-		\label{fig:single-cateogry-precision-all}
-	\end{minipage}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
+% 		\caption{\todo{todo}}
+% 		\label{fig:precision-category-singularity-all}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/single-cateogry-precision-all.pdf}
+% 		\caption{\todo{todo}}
+% 		\label{fig:single-cateogry-precision-all}
+% 	\end{minipage}
+% \end{figure}
 
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-all.pdf}
-		\caption{\todo{todo}}
-		\label{fig:precision-categorycount-examplecount-all}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-		\caption{\todo{todo}}
-		\label{fig:xxx}
-	\end{minipage}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-all.pdf}
+% 		\caption{\todo{todo}}
+% 		\label{fig:precision-categorycount-examplecount-all}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+% 		\caption{\todo{todo}}
+% 		\label{fig:xxx}
+% 	\end{minipage}
+% \end{figure}
 
-\subsubsection{Success-Rate}
-\subsubsection{Precision}
-\subsubsection{Example Categories}
+% \subsubsection{Success-Rate}
+% \subsubsection{Precision}
+% \subsubsection{Example Categories}
 
-\section{Discussion}
-\todo{draw decision tree}
+% \section{Discussion}
+% \todo{draw decision tree}
 
-interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques
+% interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques
 \section{Threats to Validity}
+%chronologically selected examples -> very specific view
 

### 2019-11-05 thesis/txt/5-study.tex
new chapter 6: discussion, start on results for CTS, replotting quite some things

@@
 To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{Failing Build Log Data Set}.
-This chapter describes our study design, the analysis of the study results and threats to the validity of our conclusions.
-The analysis of the study results first focusses on each of the three techniques and describes how each one performs best.
-Later we compare them against each other and describe their trade offs against each other.
-This chapter answers our second research question and its subquestions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
-  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
-  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
-  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
-\end{itemize}
-\end{simplebox}
+This chapter describes our study design and presents the results of the study.
+The analysis of the study results first focusses on each of the three techniques and later we compare them against each other.
 
@@
 	\includegraphics[width=\textwidth, clip]{img/study-design.pdf}
-	\caption{Study Design of our technique comparison study}
+	\caption{Study design of our technique comparison study}
 	\label{fig:study}
@@
 We register the number of examples used as configuration for each run to answer \textbf{RQ2.1} and their structural categories to answer \textbf{RQ2.3}.
+\todo{mention / explain retrival size facto}
 
@@
 
-\section{Analysis}
-This section presents the evaluation results for PBE, CTS and KWS separately and discusses under which circumstances these techniques yield best results.
+\section{Results}
+This section presents the evaluation results for PBE, CTS and KWS separately.
 Afterwards it compares the three techniques with each other and RLR as baseline.
-The section concludes with recommendations on which technique is suited for different situations.
 
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
-		\caption{Success of Chunk Retrieval Runs with PBE}
+		\caption{Results of chunk retrieval with PBE}
 		\label{fig:failure-reason-PBE}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-		\caption{Success of Chunk Retrieval Runs with PBE Compared with Category Count}
+		\caption{Results of chunk retrieval with PBE for numbers of categories present in configuring I/O examples}
 		\label{fig:failure-reason-categorycount-PBE}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
-		\caption{Precision of PBE Chunk Retrieval Results Compared with Example Count}
+		\caption{Precision chunk retrieval with PBE for increasing count of configuring I/O examples}
 		\label{fig:precision-extraction-result-PBE}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-singlecategory-swarm-PBE.pdf}
-		\caption{Precision of PBE Chunk Retrieval Compare with Example Count and Category Singularity}
-		\label{fig:precision-singlecategory-swarm-PBE}
+		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+		\caption{xxx}
+		\label{fig:xxx}
 	\end{minipage}
@@
 \subsection{Regular Expression Program Synthesis by Example (PBE)}
-Out of the 400 runs in our evaluation, 5 runs per each of the 80 example sets, PBE extracted all the desired lines in 138 cases.
-Figure \ref{fig:failure-reason-PBE} shows that in 89 cases a program was successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
+Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
+Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
+Figure \ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
 In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
-In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring examples.
+In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring I/O examples.
 
-Figure \ref{fig:failure-reason-categorycount-PBE} shows that the success of the program syntesis algorithm highly depends on the structural categories present in the configuring examples.
-Programs could only be synthesized if at maximum two categories were present.
+Figure \ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of categories present in the configuring I/O examples.
+It shows that the program synthesis is more likely to succeed when there are few categories present in the configuring I/O examples.
+When two categories present, PROSE could not synthesize a program consistent with all configuring I/O examples in most cases.
+For three or more categories PROSE could never synthesize a consistent program.
 
-More than three examples yield no improvement in the precision of PBE chunk retrieval, as you can see in Figures \ref{fig:precision-extraction-result-PBE} and \ref{fig:precision-singlecategory-swarm-PBE}.
+Figure \ref{fig:precision-extraction-result-PBE} compares the precision of the PBE chunk retrieval runs with the count of configuring I/O examples.
+For one example there is a high number of empty extraction outputs, meaning that the regular expression synthesized from this one I/O example could not be applied to the test I/O example.
+For two or more I/O examples the chunk retrieval is either successful or no consistent program could be synthesized.
 
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-PBE.pdf}
-% 		\caption{Successful Extractions per Number of Examples for PBE}
-% 		\label{fig:success-examples-pbe}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-PBE.pdf}
-% 		\caption{Precision of Extractions per Number of Examples for PBE}
-% 		\label{fig:precision-pbe}
-% 	\end{minipage}
-% \end{figure}
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-PBE.pdf}
-% 		\caption{Precision of PBE Extractions by CategoryCount}
-% 		\label{fig:precision-categorycount-examplecount-pbe}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
-% 		\caption{Reasons for PBE Runs to Fail}
-% 		\label{fig:failure-reason-pbe}
-% 	\end{minipage}
-% \end{figure}
-
-% This section addresses the results produced by the PBE technique in our study.
-% We start by comparing success rate and precision for different example counts and showing the influence of example categories.
-% Next we go into detail in which cases pbe fails
-% \subsubsection{Success-Rate}
-% \subsubsection{Precision}
-% \subsubsection{Example Categories}
-% \subsubsection{Specific Failure Reasons}
-% \todo{FAILURE REASON AGAINST EXAMPLE CATEGORIES}
-% \subsection{Successful Extractions}
-% successful is interpreted by us as: all lines that were desired (within our oracle) were also extracted during the test
-
-% Figure \ref{fig:success-all} shows how successful the four different tecnhiques were in our study.
-% Figure \ref{fig:success-examples-pbe} shows that the success rate for PBE decreases with increasing example count for pbe.
-Section \ref{TODO ref to pbe section} explains in more detail whi this fails
-% Figure \ref{fig:success-examples-ts} shows that the success rate for TS varies but stays roughly the same for different example counts
-% Figure \ref{fig:success-examples-skws} shows that the success rate for KWS varies but stays roughly the same for different example counts
-% Figure \ref{fig:success-examples-pbe} shows that
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-TS.pdf}
+		\caption{Paieya}
+		\label{fig:recall-precision-examplecount-TS}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-TS.pdf}
+		\caption{nei}
+		\label{fig:recall-precision-categorycount-TS}
+	\end{minipage}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-TS.pdf}
+		\caption{neind}
+		\label{fig:contextsizefactor-precision-recall-TS}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+		\caption{xxx}
+		\label{fig:xxx}
+	\end{minipage}
+\end{figure}
 
 \subsection{Common Text Similarity (CTS)}
+Figure \ref{fig:recall-precision-examplecount-TS} presents precision and recall of chunk retrieval using CTS in our study for different numbers of configuring I/O examples.
+The count of configuring I/O examples has no visible influence on recall and precision of the chunk retrieval with CTS.
+
+Figure \ref{fig:recall-precision-categorycount-TS} shows the same measurements for different category counts in the configuring I/O examples.
+With increasing category count, precision and recall decrease.
+Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.
+
+Figure \ref{fig:contextsizefactor-precision-recall-TS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS.
+The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
+The recall ranges
 

### 2019-11-05 thesis/txt/6-discussion.tex
new chapter 6: discussion, start on results for CTS, replotting quite some things

--- 2019-10-25 thesis/txt/0-introduction.tex
@@
 \begin{document}
+\chapter{Discussion}
 
-\chapter{Introduction}
-\plan{finalized, out for review}
-Continuous Integration (CI) has become a best practice in software engineering.
-Many software projects now use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
-A build on a CI server typically not only compiles and packages the software, but also executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.
-
-CI builds produce long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build.
-The structure of these logs changes greatly from project to project~\cite{staahl2014modeling} as it highly depends on the tools and environment used.
-Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform.
-Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
-However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.
-
-There are different techniques used to retrieve information from CI build logs.
-Beller et al.
-use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
-In general, such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
-Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
-Recently, Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.
-
-Currently there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
-Developers and researches have little support while choosing which technique to use for a retrieval task.
-The goal of this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.
-
-We aim to define a model to characterize different IR techniques, as well as the information retrievable from CI build logs.
-For our first research question, we analyze which criteria influence the suitability of an IR technique.
-We support our assumption by implementing and evaluating three techniques:
-\begin{itemize}
-  \item regular expression program synthesis from examples using the Microsoft PROSE library (referred to as PBE),
-  \item a common text similarity approach (referred to as TS) and
-  \item simple keyword search (referred to as SKWS)
-\end{itemize}
-Our second research question asks in which cases PBE, TS and SKWS are suited to retrieve information from continuous integration build logs.
-RQ2 is refined into sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples a technique needs to perform best, the accuracy of the retrieved output and how structurally diverse the configuring examples can be.
+This chapter answers our second research question and its subquestions:
 \begin{simplebox}{Research Questions}
 \begin{itemize}
-  \item[\textbf{RQ1:}] Which criteria influence the suitability of an information retrieval technique for CI build logs?
   \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
@@
 \end{simplebox}
-To evaluate PBE, TS and SKWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
-Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.
 
-\plan{results and conclusions of my work}
-Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision, ...
-.
-Retrieving information by using text similarity of examples is suitable when ...
-.
-Simple keyword search is suitable ...
-.
+\section{wip: best usage of single techniques}
+\subsection{wip: best usage of PBE}
+\subsection{wip: best usage of CTS}
+\subsection{wip: best usage of KWS}
 
-\paragraph{Our work contributes:}
-\begin{itemize}
-  \item A model of the retrievable information in CI build logs
-  \item A model to characterize information retrieval techniques from CI build logs
-  \item A model to characterize use case scenarios for information retrieval from CI build logs
-  \item A tool unifying several information retrieval techniques namely:
-        \begin{itemize}
-          \item regular expression program synthesis from examples using the Microsoft PROSE library (PBE),
-          \item a common information retrieval approach using text similarity (TS), and
-          \item a simple keyword search approach (SKWS)
-        \end{itemize}
-  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
-  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
-        \begin{itemize}
-          \item the substring of the log describing the reason the build failed,
-          \item keywords developers would use to search for these descriptions of the build failure reason, and
-          \item a categorization of the retrievals according to their structural position within the build log
-        \end{itemize}
-  \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
-  \item An extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
-\end{itemize}
+\section{wip:when to choose which technique}
 
-This thesis first presents an overview of the related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
-Next, chapter \ref{sec:models} presents our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs.
-It also introduces the three techniques, we focus on during our research evaluation.
-Chapter \ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
-Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
-This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}.
-There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity, and keyword search.
-Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
 \end{document}

### 2019-11-05 thesis/txt/5-study.tex
describe more results for kws and all techniques, draft out conclusions section

@@
 We register the number of examples used as configuration for each run to answer \textbf{RQ2.1} and their structural categories to answer \textbf{RQ2.3}.
-\todo{mention / explain retrival size facto}
+\todo{mention / explain retrival size factor}
+\todo{introduce special words / measurements like ``successful''?}
 
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
-		\caption{Precision chunk retrieval with PBE for increasing count of configuring I/O examples}
+		\caption{Precision of chunk retrieval with PBE for increasing count of configuring I/O examples}
 		\label{fig:precision-extraction-result-PBE}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-TS.pdf}
-		\caption{Paieya}
+		\caption{Precision and recall of chunk retrieval with CTS for increasing count of configuring I/O examples}
 		\label{fig:recall-precision-examplecount-TS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-TS.pdf}
-		\caption{nei}
+		\caption{Precision and recall of chunk retrieval with CTS for increasing number of categories present in the configuring I/O examples}
 		\label{fig:recall-precision-categorycount-TS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-TS.pdf}
-		\caption{neind}
+		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
 		\label{fig:contextsizefactor-precision-recall-TS}
@@
 The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
-The recall ranges
+The recall ranges from 30\% to 55\%.
 
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-TS.pdf}
-% 		\caption{Successful Extractions per Number of Examples for TS}
-% 		\label{fig:success-examples-ts}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-TS.pdf}
-% 		\caption{Precision of Extractions per Number of Examples for TS}
-% 		\label{fig:precision-ts}
-% 	\end{minipage}
-% \end{figure}
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-TS.pdf}
-% 		\caption{Precision of TS Extractions by CategoryCount}
-% 		\label{fig:precision-categorycount-examplecount-ts}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-% 		\caption{xxx}
-% 		\label{fig:xxx}
-% 	\end{minipage}
-% \end{figure}
-
-% \subsubsection{Success-Rate}
-% \subsubsection{Precision}
-% \subsubsection{Example Categories}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-SKWS.pdf}
+		\caption{Precision and recall of chunk retrieval with SKWS for increasing count of configuring I/O examples}
+		\label{fig:recall-precision-examplecount-SKWS}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-SKWS.pdf}
+		\caption{Precision and recall of chunk retrieval with SKWS for increasing number of categories present in the configuring I/O examples}
+		\label{fig:recall-precision-categorycount-SKWS}
+	\end{minipage}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-SKWS.pdf}
+		\caption{Precision and recall of chunk retrieval with SKWS compared to retrieval size factors}
+		\label{fig:contextsizefactor-precision-recall-SKWS}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+		\caption{xxx}
+		\label{fig:xxx}
+	\end{minipage}
+\end{figure}
 
 \subsection{Keyword Search (KWS)}
+\todo{plot accuracy? especiall against retrieval size factor, could be that we are soon extracting all/most avaliable lines}
+Figure \ref{fig:recall-precision-examplecount-SKWS} presents precision and recall of chunk retrieval using SKWS in our study for different numbers of configuring I/O examples.
+The recall jumps from 53\% to over 70\% for more than two configuring I/O examples, while the precision stays constant at around 16\%.
 
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWS.pdf}
-% 		\caption{Successful Extractions per Number of Examples for SKWS}
-% 		\label{fig:success-examples-skws}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWS.pdf}
-% 		\caption{Precision of Extractions per Number of Examples for SKWS}
-% 		\label{fig:precision-skws}
-% 	\end{minipage}
-% \end{figure}
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWS.pdf}
-% 		\caption{Precision of SKWS Extractions by CategoryCount}
-% 		\label{fig:precision-categorycount-examplecount-skws}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-% 		\caption{xxx}
-% 		\label{fig:xxx}
-% 	\end{minipage}
-% \end{figure}
+Figure \ref{fig:recall-precision-categorycount-SKWS} shows the same measurements for different category counts in the configuring I/O examples.
+There is no clear trend visible in precision and recall for an increasing amount of categories in the configuring I/O examples
 
-% \subsubsection{Success-Rate}
-% \subsubsection{Precision}
-% \subsubsection{Example Categories}
+Figure \ref{fig:contextsizefactor-precision-recall-SKWS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with SKWS.
+The precision ranges from 19\% when retrieving half expected number of lines to 10\% when 2.5 times the expected number of lines.
+The recall ranges from 58\% to 75\%.
 
-% \subsection{Random Line Retrieval (RLR)}
-
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-RLR.pdf}
-% 		\caption{Successful Extractions per Number of Examples for RLR}
-% 		\label{fig:success-examples-rlr}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-RLR.pdf}
-% 		\caption{Precision of Extractions per Number of Examples for RLR}
-% 		\label{fig:precision-rlr}
-% 	\end{minipage}
-% \end{figure}
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-RLR.pdf}
-% 		\caption{Precision of RLR Extractions by CategoryCount}
-% 		\label{fig:precision-categorycount-examplecount-rlr}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-% 		\caption{xxx}
-% 		\label{fig:xxx}
-% 	\end{minipage}
-% \end{figure}
-
-% For completion this section reports the results for the random line retrieval technique, explained in detail in Section \ref{sec:}
-
-% \subsubsection{Success-Rate}
-% \subsubsection{Precision}
-% \subsubsection{Example Categories}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
+		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR}
+		\label{fig:precision-all}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
+		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR for single and multiple categories present in the configuring I/O examples}
+		\label{fig:precision-category-singularity-all}
+	\end{minipage}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
+		\caption{Successful chunk retrievals for PBE, CTS, KWS and RLR}
+		\label{fig:success-all}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
+		\caption{\todo{pointplot precision and recall for all techniques compared, also aganist example/category count?}}
+		\label{fig:xxx}
+	\end{minipage}
+\end{figure}
 
 \subsection{Comparing All Techniques}
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
-% 		\caption{Successful Extractions for all Techniques Compared}
-% 		\label{fig:success-all}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
-% 		\caption{Precision of Extractions for all Techniques Compared}
-% 		\label{fig:precision-all}
-% 	\end{minipage}
-% \end{figure}
+Figure \ref{fig:precision-all}: PBE highest precision if extraction successful, also highest recall of all?. CTS still good also when not all information extracted
 
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
-% 		\caption{\todo{todo}}
-% 		\label{fig:precision-category-singularity-all}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/single-cateogry-precision-all.pdf}
-% 		\caption{\todo{todo}}
-% 		\label{fig:single-cateogry-precision-all}
-% 	\end{minipage}
-% \end{figure}
+Figure \ref{fig:precision-category-singularity-all}: pbe very good for a single category, very bad for multilpe, performance of others quite similar for single vs.
+multiple categories, CTS slightly impacted, random benefits (<- do we need to explain that in text?)
 
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-all.pdf}
-% 		\caption{\todo{todo}}
-% 		\label{fig:precision-categorycount-examplecount-all}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-% 		\caption{\todo{todo}}
-% 		\label{fig:xxx}
-% 	\end{minipage}
-% \end{figure}
-
-% \subsubsection{Success-Rate}
-% \subsubsection{Precision}
-% \subsubsection{Example Categories}
-
-% \section{Discussion}
-% \todo{draw decision tree}
-
-% interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques
-\section{Threats to Validity}
-%chronologically selected examples -> very specific view
+Figure \ref{fig:success-all} pbe and kws best at extracting all desired lines, precision fig: pbe with higher precision
 

### 2019-11-05 thesis/txt/6-discussion.tex
describe more results for kws and all techniques, draft out conclusions section

@@
 \section{wip: best usage of single techniques}
+
 \subsection{wip: best usage of PBE}
+\paragraph{wip: input}
+when textual representation of blii to extract is only of one structural category. 1-3 examples enough.
+\paragraph{wip: output usage}
+very precise output & high recall if synthesis and extraction yields result: good for computer consumed retrievals.
+If there is an output user can have high confidence it is the correct output.
+Clearly detectable when there is no program synthesized / empty output -> system can go to fail-safe state.
+
 \subsection{wip: best usage of CTS}
+\paragraph{wip: input}
+retrieval size factor 1 gives best balance of recall and precision, can handle different structural categories but bit of decline in retrieval quality, more examples do not improve quality in the number of examples we tested -> ir techniques commonly use a lot more examples for learning on
+\paragraph{wip: output usage}
+
 \subsection{wip: best usage of KWS}
+\paragraph{wip: input}
+category count has little influence -> suited if there is little prior knowledge on what the build failed / will fail.
+e.g.
+builds with a lot of steps and no pre-categorization of what step failed available
+retrieval size factor: at least 1, more seems to have positive, but marginal influence
+\paragraph{wip: output usage}
+very low precision, only useful to filter lines in build log for further processing, e.g. reading by a developer
 
 \section{wip:when to choose which technique}
+TABLE!
+\paragraph{wip: input}
+number of categories:
+one? -> pbe
+two? -> CTS
+more? -> KWS
+
+availaable examples:
+
+\paragraph{wip: output usage}
+precision needed:
+
+\begin{table}[htbp]
+\begin{tabular}{ |c||c|c|c| }
+  Technique & \multicolumn{3}{|c|}{Number of Categories in configuring examples} \\
+  \hline
+  & one & two & more \\
+  PBE & yes & no & no \\ 
+  CTS & yes & yes & no \\ 
+  KWS & yes & yes & yes \\ 
+  \hline
+\end{tabular}
+\caption{The small $1 \cdot 1$}
+\label{tab:101}
+\end{table}
+
+\section{Threats to Validity}
+chronologically selected examples -> very specific view, devs/users might pick more representative examples
+
+very few evaluation runs with a high number of categories in configuring I/O examples -> because we chose to create such a ``realistic'' data set, from data set we see that many structural categories uncommon
 

### 2019-11-06 thesis/txt/0-introduction.tex
add 3 plots, describe new plots in results, discuss results cleaner

@@
 There are different techniques used to retrieve information from CI build logs.
-Beller et al.
-use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
+Beller et al.\ use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
 In general, such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
-Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
-Recently, Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.
+Vassallo et al.\ wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
+Recently, Amar et al.\ greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.
 
@@
 \plan{results and conclusions of my work}
-Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision, ...
-.
-Retrieving information by using text similarity of examples is suitable when ...
-.
-Simple keyword search is suitable ...
-.
+Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision,.
+Retrieving information by using text similarity of examples is suitable when.
+Simple keyword search is suitable.
 
@@
 This thesis first presents an overview of the related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
-Next, chapter \ref{sec:models} presents our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs.
+Next, chapter~\ref{sec:models} presents our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs.
 It also introduces the three techniques, we focus on during our research evaluation.
-Chapter \ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
-Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
-This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}.
+Chapter~\ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
+Following, Chapter~\ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
+This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}.
 There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity, and keyword search.
-Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
+Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
 \end{document}

### 2019-11-06 thesis/txt/1-related-work.tex
add 3 plots, describe new plots in results, discuss results cleaner

@@
   We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
-  You can see an example of this in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.
+  You can see an example of this in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.
   \item is \textbf{partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, e.g.\ natural language text in error messages.
@@
 possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
-\review{
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework.
+\review{Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework.
 It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples.
@@
 }
-\mention{prose theory paper \cite{polozov2015flashmeta:}}
+\mention{prose theory paper~\cite{polozov2015flashmeta:}}
 \mention{\cite{rolim2017learning}}

### 2019-11-06 thesis/txt/2-models.tex
incorporate second kw 44 sturcture feedback
restart study chapter
add 3 plots, describe new plots in results, discuss results cleaner

@@
 Many have implicit or explicit structuring rules, some adhere to predefined standards like RSpec or PHPUnit~\cite{phpunit2019logging,rspec2019format}.
-Figure \ref{fig:tool-log-contribution} shows how different tools contribute to the whole build log.
+Figure~\ref{fig:tool-log-contribution} shows how different tools contribute to the whole build log.
 
@@
 When analyzing build logs we might not have access to the exact build configuration, describing which tools are used in which order, or might not have access to a useable definition of the output structure of a specific tool.
-As the structure of a build log is not known to us, we describe build logs as semi-structured. Section \ref{sec:rw-semi-structured-data} describes different properties of semi-structured data.
+As the structure of a build log is not known to us, we describe build logs as semi-structured. Section~\ref{sec:rw-semi-structured-data} describes different properties of semi-structured data.
 
@@
 In this section, we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
-Figure \ref{fig:build-log-information} shows the model.
+Figure~\ref{fig:build-log-information} shows the model.
 
@@
 BuildLogInformations can be hierarchically ordered by their textual representations containing each other.
-As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section \ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for BuildLogInformations whose structure we definitely know.
+As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section~\ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for BuildLogInformations whose structure we definitely know.
 Most build log information types can appear in various hierarchical arrangements and therefore not contained in any other type in the model.
@@
 	      \end{itemize}
-	      You can see an example of a TravisPhase and its components within a build log in Figure \ref{fig:log-1}.
+	      You can see an example of a TravisPhase and its components within a build log in Figure~\ref{fig:log-1}.
 
@@
 	      Timing information can be useful to retrieve when you want to automatically monitor the performance of your build.
-	      You can see an example of a Travis Build Step and its components within a build log in Figure \ref{fig:log-1}.
+	      You can see an example of a Travis Build Step and its components within a build log in Figure~\ref{fig:log-1}.
 	      %It represents those by \lstinline{travis_time:start:<timing section id>} and \\ \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
@@
 	      The TravisWorker is a good example to show that the same BLI can have different textual representations in different build logs.
-	      You can see examples of TravisWorker instantiations in Figure \ref{fig:log-0} and Figure \ref{fig:log-2}.
+	      You can see examples of TravisWorker instantiations in Figure~\ref{fig:log-0} and Figure~\ref{fig:log-2}.
 
@@
 	      The system info could be retrieved from both failing and successful logs and compared to identify if a failure is possibly based on the execution environment.
-	      You can see an example of a TravisSystemInfo instantiation within a build log in Figure \ref{fig:log-0}.
+	      You can see an example of a TravisSystemInfo instantiation within a build log in Figure~\ref{fig:log-0}.
 
@@
 	      Retrieving this information from the log could, for example, be useful when reverse engineering the build configuration.
-	      You can see an example of a TriggeringCommand instantiation within a build log in Figure \ref{fig:log-3}.
+	      You can see an example of a TriggeringCommand instantiation within a build log in Figure~\ref{fig:log-3}.
 
@@
 	      This information could be used to fill an overview of the build steps and why they failed.
-	      You can see an example of an ExitCode instantiation within a build log in Figure \ref{fig:log-3}.
+	      You can see an example of an ExitCode instantiation within a build log in Figure~\ref{fig:log-3}.
 
@@
 	      Retrieving these and showing them to developers could help them understand quicker why the build failed.
-	      You can see an example of and ErrorMessage instantiation within a build log in Figure \ref{fig:log-3}.
+	      You can see an example of and ErrorMessage instantiation within a build log in Figure~\ref{fig:log-3}.
 
@@
 	      These could be collected, counted and presented to developers, encouraging them to resolve them to improve their software.
-	      You can see examples of WarningMessage instantiations within build logs in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.
+	      You can see examples of WarningMessage instantiations within build logs in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.
 
@@
 % In this section we structure we present different important characteristics of such an IR task.
-% You can see the model in Figure \ref{fig:model-ir-task}
+% You can see the model in Figure~\ref{fig:model-ir-task}
 
@@
 In this work, we refer to our interpretation of this technique as \emph{PBE}.
-In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.
-Figure \ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE.
+In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in~\ref{sec:impl-pbe}.
+Figure~\ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE.
 
@@
 When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
-In the implementation, we had to apply a few text replacements as described in \ref{sec:impl-preprocessing}.
+In the implementation, we had to apply a few text replacements as described in~\ref{sec:impl-preprocessing}.
 The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the synthesized program when given the corresponding input file.
@@
 Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm.
-Both are described in Section \ref{sec:rw-prose}.
+Both are described in Section~\ref{sec:rw-prose}.
 %For execution PBE takes a build file as input and returns a substring of the build file content.
@@
 We investigate when it is a suitable technique to retrieve information from build logs.
-In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (TS), the concrete implementation is described in \ref{sec:impl-ts}.
-Figure \ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for TS.
+In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (TS), the concrete implementation is described in~\ref{sec:impl-ts}.
+Figure~\ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for TS.
 
@@
 As this is a technique readily available in many tools developers use to view build logs, we want to study when such a simple search for keywords is recommendable for retrieving information from CI build logs.
-In the following we will explain how we use simple keyword search to retrieve information from CI build logs (SKWS), the concrete implementation is described in \ref{sec:impl-skws}.
-Figure \ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.
+In the following we will explain how we use simple keyword search to retrieve information from CI build logs (SKWS), the concrete implementation is described in~\ref{sec:impl-skws}.
+Figure~\ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.
 
@@
 
-\subsection{Random Line Retrieval (RLR)}
-
 \subsection{Other Techniques}
@@
 \paragraph{Log Diff}
-Amar et al. used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section \ref{sec:rw-bl-analysis}.
-Figure \ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
-\paragraph{Random Line Retrieval}
+Amar et al. used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
+Figure~\ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
+\paragraph{Random Line Retrieval (RLR)}
 In our evaluation we want to compare against a basic deadline of randomly extracted lines.

### 2019-11-06 thesis/txt/3-data-set.tex
incorporate second kw 44 sturcture feedback
add 3 plots, describe new plots in results, discuss results cleaner

@@
 \section{Data Structure}
-For our study, described in Chapter \ref{sec:study}, we want to investigate the retrieval capabilities of three techniques.
+For our study, described in Chapter~\ref{sec:study}, we want to investigate the retrieval capabilities of three techniques.
 Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}.
@@
 
-\section{Threats to Validity}
+\section{Validation}
 \bp{some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed
@@
 }
-
-\section{Validation}
 We vaildated our collected labels in two different ways.
@@
 Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
-We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure \ref{fig:dev-mail} shows one of the mails sent out.
+We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
 The email included links to the corresponding commits, build overview and log file.
 We asked the receivers to fill out a short survey in case our extraction was not correct.
-Look at Figure \ref{fig:dev-survey} to get an impression of the survey.
+Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
 In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
@@
 We received answers from 61 developers, responding about 144 build logs.
-The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure \ref{fig:mails-answers-received-mails} and Figure \ref{fig: mails-answers-received-builds}.
+The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig: mails-answers-received-builds}.
 
@@
 We manually inspected these negative answers and found that extractions were correct after all.
-This yields 12 log extractions in our example set that were not correct, shown in Figure \ref{fig:mails-extraction-correct}.
+This yields 12 log extractions in our example set that were not correct, shown in Figure~\ref{fig:mails-extraction-correct}.
 

### 2019-11-06 thesis/txt/5-study.tex
add 3 plots, describe new plots in results, discuss results cleaner

@@
 \section{Study Design}
-For the comparison study we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections \ref{sec:expl-pbe},\ref{sec:expl-ts} and \ref{sec:expl-skws}.
-RLR, explained in Section \ref{sec:expl-rlr}, acts as a baseline for the comparison.
+For the comparison study we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},\ref{sec:expl-ts} and~\ref{sec:expl-skws}.
+RLR, explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
 We run four techniques on the example sets from the \emph{Failing Build Log Data Set}.
@@
 The examples are sorted chronologically, i.e. a technique is configured with examples from the directly preceding build logs.
-For each example set and each technique, we select one to five successive I/O examples as configuration, the \emph{configuring I/O examples}, and run the chunk retrieval on the next I/O example, the \emph{test I/O example}.
+For each example set and each technique, we select one to five consecutive I/O examples as configuration, the \emph{configuring I/O examples}, and run the chunk retrieval on the following I/O example, the \emph{test I/O example}.
 
@@
 The desired output is given by the output of the test I/O example, which acts as the oracle for our evaluation.
-From this we obtain true/false positives/negatives and calculate precision, recall and accuracy, which we use to answer \textbf{RQ2.2}.
-We register the number of examples used as configuration for each run to answer \textbf{RQ2.1} and their structural categories to answer \textbf{RQ2.3}.
-\todo{mention / explain retrival size factor}
-\todo{introduce special words / measurements like ``successful''?}
+From this we obtain true/false positives/negatives and calculate precision, recall and accuracy.
+We use these values to answer \textbf{RQ2.2}.
+If all desired lines are extracted, i.e. recall is one, we say a chunk retrieval run was \emph{successful}.
+To answer \textbf{RQ2.1}, we register the number configuring I/O examples for each run.
+The structural categories of the configuring I/O examples are saved to answer \textbf{RQ2.3}.
+Recall and precision of those techniques vary with the number of lines selected for retrieval.
+We evaluate the impact of varying the number of extracted lines by multiplying the average number of lines present in the configuring examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
 
@@
 % - why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
-% - Figure \ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
-% - Figure \ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.
+% - Figure~\ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
+% - Figure~\ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.
 
@@
 Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
-Figure \ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
+Figure~\ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
 In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
@@
 
-Figure \ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of categories present in the configuring I/O examples.
+Figure~\ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of sturctural categories present in the configuring I/O examples.
 It shows that the program synthesis is more likely to succeed when there are few categories present in the configuring I/O examples.
-When two categories present, PROSE could not synthesize a program consistent with all configuring I/O examples in most cases.
-For three or more categories PROSE could never synthesize a consistent program.
+When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all configuring I/O examples.
+For three or more present categories PROSE could never synthesize a consistent program.
 
-Figure \ref{fig:precision-extraction-result-PBE} compares the precision of the PBE chunk retrieval runs with the count of configuring I/O examples.
-For one example there is a high number of empty extraction outputs, meaning that the regular expression synthesized from this one I/O example could not be applied to the test I/O example.
-For two or more I/O examples the chunk retrieval is either successful or no consistent program could be synthesized.
+Figure~\ref{fig:precision-extraction-result-PBE} compares the precision of the PBE chunk retrieval runs with the count of configuring I/O examples.
+For one example there is a high number of empty extraction outputs, meaning that the regular expression synthesized from this one configuring I/O example could not be applied to the test I/O example.
+For two or more I/O examples the chunk retrieval is in most cases either successful or no consistent program could be synthesized.
 
@@
 \subsection{Common Text Similarity (CTS)}
-Figure \ref{fig:recall-precision-examplecount-TS} presents precision and recall of chunk retrieval using CTS in our study for different numbers of configuring I/O examples.
+Figure~\ref{fig:recall-precision-examplecount-TS} presents precision and recall of chunk retrieval using CTS for different numbers of configuring I/O examples.
 The count of configuring I/O examples has no visible influence on recall and precision of the chunk retrieval with CTS.
 
-Figure \ref{fig:recall-precision-categorycount-TS} shows the same measurements for different category counts in the configuring I/O examples.
+Figure~\ref{fig:recall-precision-categorycount-TS} shows the same measurements for different category counts in the configuring I/O examples.
 With increasing category count, precision and recall decrease.
@@
 
-Figure \ref{fig:contextsizefactor-precision-recall-TS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS.
+Figure~\ref{fig:contextsizefactor-precision-recall-TS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS.
 The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-SKWS.pdf}
-		\caption{Precision and recall of chunk retrieval with SKWS compared to retrieval size factors}
+		\caption{Precision and recall of chunk retrieval with SKWS compared to retrieval size factor}
 		\label{fig:contextsizefactor-precision-recall-SKWS}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-		\caption{xxx}
-		\label{fig:xxx}
+		\includegraphics[width=\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-SKWS.pdf}
+		\caption{Ratio of lines retrieved with SKWS compared to retrieval size factor}
+		\label{fig:retrievalsizefactor-retrievalratio-SKWS}
 	\end{minipage}
@@
 \subsection{Keyword Search (KWS)}
-\todo{plot accuracy? especiall against retrieval size factor, could be that we are soon extracting all/most avaliable lines}
-Figure \ref{fig:recall-precision-examplecount-SKWS} presents precision and recall of chunk retrieval using SKWS in our study for different numbers of configuring I/O examples.
+Figure~\ref{fig:recall-precision-examplecount-SKWS} presents precision and recall of chunk retrieval using SKWS in our study for different numbers of configuring I/O examples.
 The recall jumps from 53\% to over 70\% for more than two configuring I/O examples, while the precision stays constant at around 16\%.
 
-Figure \ref{fig:recall-precision-categorycount-SKWS} shows the same measurements for different category counts in the configuring I/O examples.
+Figure~\ref{fig:recall-precision-categorycount-SKWS} shows the same measurements for different category counts in the configuring I/O examples.
 There is no clear trend visible in precision and recall for an increasing amount of categories in the configuring I/O examples
 
-Figure \ref{fig:contextsizefactor-precision-recall-SKWS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with SKWS.
+Figure~\ref{fig:contextsizefactor-precision-recall-SKWS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with SKWS.
 The precision ranges from 19\% when retrieving half expected number of lines to 10\% when 2.5 times the expected number of lines.
@@
 
+Figure~\ref{fig:retrievalsizefactor-retrievalratio-SKWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS.
+When retrieving the mean number of lines in the configuring I/O examples, 15\% of the log lines are retrieved on average.
+This proportion goes up to 25\% when retrieving 1.5 times more lines.
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
+% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR}
+% 		\label{fig:precision-all}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
+% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR for single and multiple categories present in the configuring I/O examples}
+% 		\label{fig:precision-category-singularity-all}
+% 	\end{minipage}
+% \end{figure}
 \begin{figure}[htbp]
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
-		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR}
-		\label{fig:precision-all}
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
+		\caption{Success of chunk retrievals for PBE, CTS, KWS and RLR}
+		\label{fig:success-partial-all}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
-		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR for single and multiple categories present in the configuring I/O examples}
-		\label{fig:precision-category-singularity-all}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-all.pdf}
+		\caption{Precision and Recall of PBE, CTS, KWS and RLR compared}
+		\label{fig:recall-precision-all}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
-		\caption{Successful chunk retrievals for PBE, CTS, KWS and RLR}
-		\label{fig:success-all}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
+		\caption{Precision and Recall of PBE, CTS, KWS and RLR compared when configuring I/O examples are from a single category}
+		\label{fig:recall-precision-singlecategory-all}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-		\caption{\todo{pointplot precision and recall for all techniques compared, also aganist example/category count?}}
-		\label{fig:xxx}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
+		\caption{Precision and Recall of PBE, CTS, KWS and RLR compared when configuring I/O examples are from multiple categories}
+		\label{fig:recall-precision-multicategory-all}
 	\end{minipage}
@@
 
+% \begin{table}[htbp]
+% \centering
+% \begin{tabular}{ |c||c|c|c| }
+% 	\hline
+%   Technique & \multicolumn{3}{|c|}{Desired Lines extracted} \\
+%   \hline
+%   & all [0.345 , 0.2025, 0.3825, 0.005 ] & partial [0.045 , 0.5875, 0.4525, 0.3025] & none [0.61  , 0.21  , 0.165 , 0.6925] \\
+%   \hline
+%   & recall = 1 & 0 < recall < 1 & recall = 0 \\
+%   \hline
+%   PBE & 138 & 18 & 244 \\ 
+%   CTS & 81 & 235 & 84 \\ 
+%   KWS & 153 & 181 & 66 \\ 
+%   RLR & 2 & 121 & 277 \\ 
+%   \hline
+% \end{tabular}
+% \caption{Comparison of successful extractions for PBE, CTS, KWS and RLR}
+% \label{tab:101}
+% \end{table}
+
 \subsection{Comparing All Techniques}
-Figure \ref{fig:precision-all}: PBE highest precision if extraction successful, also highest recall of all?. CTS still good also when not all information extracted
+Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval of the different techniques in our study.
+CTS and KWS extract at least some of the desired lines in 79\% and 88.5\%.
+With 38.25\%, KWS also has the highest number of successful extractions, followed by PBE with 34.5\%.
+PBE has the lowest number of partial extraction with only 18 out of 400 chunk retrieval runs.
 
-Figure \ref{fig:precision-category-singularity-all}: pbe very good for a single category, very bad for multilpe, performance of others quite similar for single vs.
-multiple categories, CTS slightly impacted, random benefits (<- do we need to explain that in text?)
+The averaged precision and recall of all techniques is compared in Figure~\ref{fig:recall-precision-all}.
+PBE has a high skew towards one and zero for both measurements, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
+Chunk retrieval with CTS has the highest average precision with 46\% and the second best recall with 45\%.
+KWS has the smallest precision of the three chunk retrieval techniques.
+With 16\% it is still higher than the precision of the RLR baseline with 7\%.
+KWS has the highest recall of all techniques with 70\%.
 
-Figure \ref{fig:success-all} pbe and kws best at extracting all desired lines, precision fig: pbe with higher precision
+The influence of a single structural category present in the configuring I/O examples compared to multiple categories present is shown in Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all}.
+For more than one present category, precision and recall of PBE greatly decrease.
+For CTS and KWS the values also decrease slightly, while RLR is not impacted by the number of structural categories present.
 

### 2019-11-06 thesis/txt/6-discussion.tex
add 3 plots, describe new plots in results, discuss results cleaner

--- 2019-11-05 thesis/txt/6-discussion.tex
@@
 \begin{itemize}
-  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
-  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
-  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
-  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
+  \item[\textbf{RQ2:}] When are PBE, CTS, and KWS suited to retrieve information from CI build logs?
+  \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
+  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, CTS, and KWS?
+  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
 \end{itemize}
@@
 
-\section{wip: best usage of single techniques}
-\subsection{wip: best usage of PBE}
-\subsection{wip: best usage of CTS}
-\subsection{wip: best usage of KWS}
+The first section discusses for PBE, CTS and KWS separately in which cases they perform best.
+It details for which types of input build logs, available configuration I/O examples and use case of the retrieved output each technique is suited.
+The next section compares the three techniques and clarifies which one is recommended by our study results for different use cases.
 
-\section{wip:when to choose which technique}
+\section{Interpretation of Study Results}
+This section discusses the study results for each of the analyzed chunk retrieval techniques separately.
+It gives recommendations on which kind of configuration is best for each technique and for what kind of usage the output is suitable.
+
+\subsection{Regular Expression Program Synthesis by Example (PBE)}
+\paragraph{Configuration and Input}
+Our study results show, that chunk retrieval with PBE gives best results when the configuring I/O examples are from one structural category.
+This means it is suited to retrieve BLIs, whose textual representation always has the same surrounding structure.
+To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.
+
+When all configuring I/O Examples are of the same structure, one to three examples are enough input for PROSE to synthesize a correct regular expression program.
+In our study, additional examples did not improve the quality of teh chunk retrieval.
+
+\paragraph{Retrieval Output Usage}
+When the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and high recall for chunk retrieval.
+A failure in the program synthesis or no output from the synthesized program is clearly identified by the tool.
+Therefore, if there is an output, the user can have high confidence it is the correct output.
+This makes output from PBE chunk retrieval well suited for consumption of other software components,
+
+\subsection{Common Text Similarity (CTS)}
+\paragraph{Configuration and Input}
+Chunk retrieval using CTS also yields good results if more than one structural category is present in the configuring I/O examples.
+The number of configuring I/O examples had no measurable influence on the extraction quality in our study.
+Information retrieval techniques like text similarity commonly learn on a higher number of examples than we used for our study.
+Future work is needed to investigate how many examples yield improvements in the chunk retrieval over a single configuring I/O example.
+
+Extracting the average number of lines present in the configuring I/O examples seems to give the best balance of precision and recall for CTS.
+
+\paragraph{Retrieval Output Usage}
+CTS has good precision and recall on average, though the quality of a chunk retrieval run is very hard to predict from the given result.
+Therefore, retrieval output from CTS is suited to be read by a human.
+
+\subsection{Keyword Search (KWS)}
+\paragraph{Configuration and Input}
+The number of structural categories in the configuring I/O examples have little impact on the extraction quality of KWS.
+This makes KWS a good technique if there is little prior knowledge on how the desired BLI is represented in the build log to be analyzed.
+For the example of extracting the build failure reason, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
+
+To achieve good recall of the retrieval, at least two examples should be given as configuration.
+
+Retrieving the average number of lines present in the outputs of the configuring I/O examples around every found keyword yields reasonable recall.
+Selecting 1.5 times as many lines around every found keyword does improve the recall in our study but also increases the proportion of lines retrieved overall and therefore decreases precision.
+
+\paragraph{Retrieval Output Usage}
+Even though KWS has the highest recall of all three techniques, its precision is also the lowest.
+The output of a chunk retrieval with KWS is well suited to be read by humans, matching our 
+very low precision, only useful to filter lines in build log for further processing, e.g. reading by a developer
+
+\section{Choosing a Suitable Chunk Retrieval Technique}
+This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS.
+It recommends which technique to use depending on the available configuration and 
+TABLE!
+\paragraph{Configuration and Input}
+number of categories:
+one? -> pbe
+two? -> CTS
+more? -> KWS
+available examples:
+little?
+-> try pbe (This depends on the categories!
+here we might want a decision tree to represent the importance of these characteristics against each other?
+<- this would also anwser RQ1: which ones of the criteria we compare are the most important)
+multiple -> kws
+very many? -> CTS
+
+\paragraph{Retrieval Output Usage}
+precision needed:
+
+\begin{table}[htbp]
+\begin{tabular}{ |c||c|c|c| }
+  Technique & \multicolumn{3}{|c|}{Number of Categories in configuring examples} \\
+  \hline
+  & one & two & more \\
+  PBE & yes & no & no \\ 
+  CTS & yes & yes & no \\ 
+  KWS & yes & yes & yes \\ 
+  \hline
+\end{tabular}
+\caption{The small $1 \cdot 1$}
+\label{tab:101}
+\end{table}
+
+\section{Threats to Validity}
+chronologically selected examples -> very specific view, devs/users might pick more representative examples
+
+very few evaluation runs with a high number of categories in configuring I/O examples -> because we chose to create such a ``realistic'' data set, from data set we see that many structural categories uncommon
 

### 2019-11-06 thesis/txt/2-models.tex
adress some linter warnings from lacheck and style-check.rb

@@
 %\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
-Many different information retrieval techniques ... this section describes the conceptional / theoretical results of our thesis ...
+Many different information retrieval techniques\textellipsis this section describes the conceptional / theoretical results of our thesis\textellipsis
 We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly.
@@
 	\item Running static analysis tools~\cite{zampetti2017open}.
-	\item Building the software, i.e. compiling and packaging it~\cite{phillips2014understanding}.
+	\item Building the software, i.e.\ compiling and packaging it~\cite{phillips2014understanding}.
 	\item Running automated tests~\cite{beller2017oops}.
@@
 	      \end{itemize}
-	\item can retrieve text passages with a specific \textbf{Granularity}, i.e. the smallest extractable text piece.
+	\item can retrieve text passages with a specific \textbf{Granularity}, i.e.\ the smallest extractable text piece.
 	      The Granularity can be at the level of characters, lines or paragraphs.
@@
 In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in~\ref{sec:impl-pbe}.
-Figure~\ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE.
+Figure~\ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE\@.
 
@@
 In/Output examples (I/O examples) are the main driver of Programming by Example.
-When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
+When extracting information from build logs the \emph{input} is always a whole build log, i.e.\ the whole text of the build log file without any preprocessing.
 In the implementation, we had to apply a few text replacements as described in~\ref{sec:impl-preprocessing}.
@@
 \paragraph{Method}
-To configure a retrieval though text similarity we chose to use the same concept of I/O examples as for PBE.
+To configure a retrieval though text similarity we chose to use the same concept of I/O examples as for PBE\@.
 The lines of the output strings of a given example set define our search query.
@@
 \paragraph{Log Diff}
-Amar et al. used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
+Amar et al.\ used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
 Figure~\ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.

### 2019-11-06 thesis/txt/4-tool.tex
fixes from Taicos introduction review
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet
incorporate kw 44 structure feedback in thesis, some plot advancements
adress some linter warnings from lacheck and style-check.rb

@@
 
-\chapter{Information Retrieval Tool}
+\chapter{Tool Implementation}
 \label{sec:implementation}
@@
 
-\section{Common Interface}
+%\section{Common Interface}
 \begin{lstlisting}
@@
 
-\section{Overall Implementation Remarks}
+%\section{Overall Implementation Remarks}
 There are multiple implementation specialities that span over all languages, frameworks and implemented techniques.
-The following section discusses preprocessing and escaping of the parsed build log files / example sets, as well as ... \todo{more?}
+The following section discusses preprocessing and escaping of the parsed build log files / example sets, as well as\textellipsis \todo{more?}
 
-\subsection{Preprocessing Log Text}
+\subsection*{Preprocessing Log Text}
 \label{sec:impl-preprocessing}
 
-\section{PROSE Program Synthesis}
+%\section*{PBE}
 \label{sec:impl-pbe}
@@
 
-\section{IR Similarity}
+%\section*{IR Similarity}
+\label{sec:impl-ts}
 impl details,
@@
 
-\section{Keyword search}
+%\section*{Keyword search}
+\label{sec:impl-skws}
 impl details,

### 2019-11-06 thesis/txt/5-study.tex
adress some linter warnings from lacheck and style-check.rb

@@
 
-The examples are sorted chronologically, i.e. a technique is configured with examples from the directly preceding build logs.
+The examples are sorted chronologically, i.e.\ a technique is configured with examples from the directly preceding build logs.
 For each example set and each technique, we select one to five consecutive I/O examples as configuration, the \emph{configuring I/O examples}, and run the chunk retrieval on the following I/O example, the \emph{test I/O example}.
 
-For each of our evaluation runs we measure the desired vs. actual output lines of the chunk retrieval.
+For each of our evaluation runs we measure the desired and the actual output lines of the chunk retrieval.
 The desired output is given by the output of the test I/O example, which acts as the oracle for our evaluation.
@@
 We use these values to answer \textbf{RQ2.2}.
-If all desired lines are extracted, i.e. recall is one, we say a chunk retrieval run was \emph{successful}.
+If all desired lines are extracted, i.e.\ recall is one, we say a chunk retrieval run was \emph{successful}.
 To answer \textbf{RQ2.1}, we register the number configuring I/O examples for each run.
@@
 Recall and precision of those techniques vary with the number of lines selected for retrieval.
-We evaluate the impact of varying the number of extracted lines by multiplying the average number of lines present in the configuring examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
+We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the configuring examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
 
@@
 Figure~\ref{fig:recall-precision-examplecount-TS} presents precision and recall of chunk retrieval using CTS for different numbers of configuring I/O examples.
-The count of configuring I/O examples has no visible influence on recall and precision of the chunk retrieval with CTS.
+The count of configuring I/O examples has no visible influence on recall and precision of the chunk retrieval with CTS\@.
 
@@
 
-Figure~\ref{fig:contextsizefactor-precision-recall-TS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS.
+Figure~\ref{fig:contextsizefactor-precision-recall-TS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS\@.
 The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
@@
 
-Figure~\ref{fig:contextsizefactor-precision-recall-SKWS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with SKWS.
+Figure~\ref{fig:contextsizefactor-precision-recall-SKWS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with KWS\@.
 The precision ranges from 19\% when retrieving half expected number of lines to 10\% when 2.5 times the expected number of lines.
@@
 
-Figure~\ref{fig:retrievalsizefactor-retrievalratio-SKWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS.
+Figure~\ref{fig:retrievalsizefactor-retrievalratio-SKWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS\@.
 When retrieving the mean number of lines in the configuring I/O examples, 15\% of the log lines are retrieved on average.
@@
 
-The influence of a single structural category present in the configuring I/O examples compared to multiple categories present is shown in Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all}.
+Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the configuring I/O examples compared to multiple categories present.
 For more than one present category, precision and recall of PBE greatly decrease.
-For CTS and KWS the values also decrease slightly, while RLR is not impacted by the number of structural categories present.
+For CTS and KWS the values also decrease slightly, while RLR is not affected by the number of structural categories present.
 

### 2019-11-06 thesis/txt/6-discussion.tex
adress some linter warnings from lacheck and style-check.rb

@@
 When all configuring I/O Examples are of the same structure, one to three examples are enough input for PROSE to synthesize a correct regular expression program.
-In our study, additional examples did not improve the quality of teh chunk retrieval.
+In our study, additional examples did not improve the quality of the chunk retrieval.
 
@@
 Therefore, if there is an output, the user can have high confidence it is the correct output.
-This makes output from PBE chunk retrieval well suited for consumption of other software components,
+This makes output from PBE chunk retrieval well suited for consumption of other software components.
 
@@
 
-Extracting the average number of lines present in the configuring I/O examples seems to give the best balance of precision and recall for CTS.
+Extracting the average number of lines present in the configuring I/O examples seems to give the best balance of precision and recall for CTS\@.
 
@@
 \paragraph{Configuration and Input}
-The number of structural categories in the configuring I/O examples have little impact on the extraction quality of KWS.
+The number of structural categories in the configuring I/O examples have little impact on the extraction quality of KWS\@.
 This makes KWS a good technique if there is little prior knowledge on how the desired BLI is represented in the build log to be analyzed.
@@
 Even though KWS has the highest recall of all three techniques, its precision is also the lowest.
-The output of a chunk retrieval with KWS is well suited to be read by humans, matching our 
-very low precision, only useful to filter lines in build log for further processing, e.g. reading by a developer
+The output of a chunk retrieval with KWS is well suited to be read by humans.
 
 \section{Choosing a Suitable Chunk Retrieval Technique}
-This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS.
+This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS\@.
 It recommends which technique to use depending on the available configuration and 
@@
 \begin{table}[htbp]
-\begin{tabular}{ |c||c|c|c| }
+\begin{tabular}{|c||c|c|c|}
   Technique & \multicolumn{3}{|c|}{Number of Categories in configuring examples} \\

### 2019-11-07 thesis/txt/0-introduction.tex
change easy feedback from moritz paper review

@@
 \chapter{Introduction}
-\plan{finalized, out for review}
-Continuous Integration (CI) has become a best practice in software engineering.
-Many software projects now use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
-A build on a CI server typically not only compiles and packages the software, but also executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.
+Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
+Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
+A build on a CI server typically compiles and packages the software, executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.
 
-CI builds produce long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build.
-The structure of these logs changes greatly from project to project~\cite{staahl2014modeling} as it highly depends on the tools and environment used.
-Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform.
-Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
+CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
+The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and environment used.
+Build logs are a valuable data source: For developers, who read them to analyze why their build failed or how different stages of the build process perform.
+Second, For researchers, who can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
 However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.
 
-There are different techniques used to retrieve information from CI build logs.
-Beller et al.\ use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
-In general, such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
+There are different techniques to retrieve information from CI build logs.
+Beller et al.\ use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from Travis CI~\cite{beller2017oops}.
+Such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
 Vassallo et al.\ wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
@@
 
-Currently there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
-Developers and researches have little support while choosing which technique to use for a retrieval task.
+At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
+Developers and researches currently have little support while choosing which technique to use for a retrieval task.
 The goal of this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.
@@
 For our first research question, we analyze which criteria influence the suitability of an IR technique.
-We support our assumption by implementing and evaluating three techniques:
+We implement and evaluate three chunk retrieval techniques:
 \begin{itemize}
-  \item regular expression program synthesis from examples using the Microsoft PROSE library (referred to as PBE),
-  \item a common text similarity approach (referred to as TS) and
-  \item simple keyword search (referred to as SKWS)
+  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
+  \item a common text similarity approach (referred to as CTS) and
+  \item keyword search (referred to as KWS)
 \end{itemize}
@@
 \begin{itemize}
-  \item[\textbf{RQ1:}] Which criteria influence the suitability of an information retrieval technique for CI build logs?
-  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
-  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
-  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
-  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
+  \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
+  \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
+  \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
+  \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
+  \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, TS, and KWS?
 \end{itemize}
@@
 \begin{itemize}
-  \item A model of the retrievable information in CI build logs
+  \item A model of the contained and retrievable information in CI build logs
   \item A model to characterize information retrieval techniques from CI build logs
@@
         \end{itemize}
-  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
+  %\item The \emph{LogCollector}, a tool to gather build logs from Travis CI
   \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
@@
   \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
-  \item An extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
+  \item \todo{guidlines on when to use which technique, also guidelines for each technique}
 \end{itemize}
 
+\todo{update}
 This thesis first presents an overview of the related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.

### 2019-11-07 thesis/txt/1-related-work.tex
change easy feedback from moritz paper review

@@
 \todo{introduction \& glue text}
-This section presents various research works adjacent or foundational for our work.
+This section presents various research works adjacent or foundational to our work.
 Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation.
@@
 Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.
+% moritz: nice formulation :)
 
@@
 We strive to enable a similar summarization by text retrieval while also covering a wider array of programming languages.
+\todo{mention which technique}
 \todo{reference their new paper}
 
-Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
+Amar et al.~\cite{amar2019mining} reduced the lines \todo{portions?} of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
 They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the error.

### 2019-11-07 thesis/txt/2-models.tex
change easy feedback from moritz paper review

@@
 \plan{describe model classes, 1 page text}
+\todoo{do we need / want the the model images???}
 For this thesis, we want to evaluate different information retrieval techniques when applied to CI build logs.
@@
 
-\subsection{Regular Expression Program Synthesis by Example (PBE)}
+\subsection{Program Synthesis by Example (PBE)}
 \label{sec:expl-pbe}

### 2019-11-07 thesis/txt/3-data-set.tex
adress some linter warnings from lacheck and style-check.rb
change easy feedback from moritz paper review

@@
 \section{Related Data Sets}
-\todo{kind of related work for data set? the two mortiz sent, more?}
+\todo{kind of related work for data set? the non system one moritz sent, travis torrent, check msr, new paper in rw / other rw parpers, more?}
 
@@
 		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-mails.pdf}
-		\caption{Proportions of Mails answered, unanswered, not delivered and no mail found}
+		\caption{Number of mails answered, unanswered and not delivered}
 		\label{fig:mails-answers-received-mails}
@@
 		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
-		\caption{Responses to our developer survey}
+		\caption{Label correctness as validated by developers}
 		\label{fig:mails-extraction-correct}
@@
 		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
-		\caption{Proportions of Logs answered, undelivered and unanswered}
+		\caption{Proportions of logs answered, undelivered and unanswered}
 		\label{fig:mails-answers-received-builds}
@@
 		\includegraphics[width=\textwidth, clip]{img/dev-mails/logs-per-mail.pdf}
-		\caption{Responses to our developer survey}
+		\caption{Average number of logs per sent out mail}
 		\label{fig:mails-logs-per-mail}
@@
 In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
-32 of these mails could not be delivered, e.g. because they were addressed at noreply mail addresses.
+32 of these mails could not be delivered, e.g.\ because they were addressed at noreply mail addresses.
 These 32 mails related to 68 of the build logs.
@@
 Of the 144 answers, 132 said our extraction was correct.
-26 answered either "close, but not quite correct" or "no, the build failed for another reason".
+26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
 We manually inspected these negative answers and found that extractions were correct after all.

### 2019-11-07 thesis/txt/0-introduction.tex
update and improvements on introduction

@@
 CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
-The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and environment used.
+The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
 Build logs are a valuable data source: For developers, who read them to analyze why their build failed or how different stages of the build process perform.
-Second, For researchers, who can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
+Second, for researchers, who can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
 However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.
 
-There are different techniques to retrieve information from CI build logs.
-Beller et al.\ use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from Travis CI~\cite{beller2017oops}.
+There are different techniques to retrieve information from CI build logs. Beller et al.\ use regular expressions to analyze the failure reasons of build logs from Travis CI~\cite{beller2017oops}.
 Such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
-Vassallo et al.\ wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
-Recently, Amar et al.\ greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.
+Vassallo et al.\ wrote a custom parser for build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
+Recently, Amar et al.\ reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and a successful build~\cite{amar2019mining}.
 
+These approaches have various downsides and strengths:
+Regular expressions are very exact but difficult to maintain~\cite{michael2019regexes}.
+Custom parsers are powerful though fragile towards changes in the log structure.
+Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
 At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
 Developers and researches currently have little support while choosing which technique to use for a retrieval task.
-The goal of this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.
 
-We aim to define a model to characterize different IR techniques, as well as the information retrievable from CI build logs.
-For our first research question, we analyze which criteria influence the suitability of an IR technique.
+The goal of this thesis is to investigate different chunk retrieval techniques (CR techniques) for build logs and describe under which circumstances we recommend each of the techniques.
+We aim to define a model to characterize different CR techniques, as well as the information retrievable from CI build logs.
+For \textbf{RQ1}, we analyze which criteria influence the suitability of an CR technique for CI build logs.
 We implement and evaluate three chunk retrieval techniques:
@@
 \end{itemize}
-Our second research question asks in which cases PBE, TS and SKWS are suited to retrieve information from continuous integration build logs.
-RQ2 is refined into sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples a technique needs to perform best, the accuracy of the retrieved output and how structurally diverse the configuring examples can be.
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
-  \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
-  \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, TS, and KWS?
-\end{itemize}
-\end{simplebox}
-To evaluate PBE, TS and SKWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
+\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
+\textbf{RQ2} is refined into sub-questions along the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
+how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the configuring examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
+% \begin{simplebox}{Research Questions}
+% \begin{itemize}
+%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
+%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
+%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
+%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
+%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
+% \end{itemize}
+% \end{simplebox}
+To evaluate PBE, CTS and KWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
 Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.
 
-\plan{results and conclusions of my work}
-Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision,.
-Retrieving information by using text similarity of examples is suitable when.
-Simple keyword search is suitable.
+Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that
+\begin{itemize}
+  \item PBE yields very accurate results when configured with 1 to 3 examples from a single structural category.
+  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
+  A small increase in the number of examples used in the configuration has no visible influence and fewer structural categories improve the retrieval accuracy.
+  \item KWS has the highest recall of all techniques combined with considerable lower recall.
+  It is the only technique where retrieval quality does not decrease with and increasing number of structural categories in the configuring examples.
+\end{itemize}
+We recommend PBE for use cases where the desired information is always represented in the same structurally predictable way and a high confidence in the exactness of the chunk retrieval is required.
+CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
+In cases where the representation fo the desired information is unpredictable or varies greatly, KWS is the best technique to choose.
+Though the low precision of the output requires a human to interpret the output of the chunk retrieval.
 
@@
 \begin{itemize}
-  \item A model of the contained and retrievable information in CI build logs
-  \item A model to characterize information retrieval techniques from CI build logs
-  \item A model to characterize use case scenarios for information retrieval from CI build logs
-  \item A tool unifying several information retrieval techniques namely:
+  \item A model of the contained and retrievable information in CI build logs.
+  \item A model to characterize chunk retrieval techniques from CI build logs.
+  %\item A model to characterize use case scenarios for information retrieval from CI build logs
+  \item A tool unifying several chunk retrieval techniques namely:
         \begin{itemize}
-          \item regular expression program synthesis from examples using the Microsoft PROSE library (PBE),
-          \item a common information retrieval approach using text similarity (TS), and
-          \item a simple keyword search approach (SKWS)
+          \item program synthesis from examples using the Microsoft PROSE library (PBE),
+          \item a common information retrieval approach using text similarity (CTS), and
+          \item a keyword search approach (KWS)
         \end{itemize}
@@
           \item keywords developers would use to search for these descriptions of the build failure reason, and
-          \item a categorization of the retrievals according to their structural position within the build log
+          \item a categorization of the retrievals according to their structural position within the build log.
         \end{itemize}
-  \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
-  \item \todo{guidlines on when to use which technique, also guidelines for each technique}
+  \item A study comparing the effectiveness of the three implemented techniques.
+  \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
+  \item Guidelines on choosing a suitable chunk retrieval technique. % TODO for a given use case or so?
 \end{itemize}
 
-\todo{update}
-This thesis first presents an overview of the related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
-Next, chapter~\ref{sec:models} presents our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs.
-It also introduces the three techniques, we focus on during our research evaluation.
-Chapter~\ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
-Following, Chapter~\ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
+This thesis first presents an overview of related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
+Next, chapter~\ref{sec:models} characterizes chunk retrieval techniques and contained and retrievable information from CI build logs.
+It also introduces the three investigated techniques PBE, CTS and KWS.
+Chapter~\ref{sec:data-set} describes the creation of the \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs, including the labeling and the validation process.
+Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
 This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}.
-There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity, and keyword search.
+Chapter~\ref{sec:discussion} presents the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
 Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.

### 2019-11-07 thesis/txt/2-models.tex
update and improvements on introduction

@@
 \plan{describe model classes, 1 page text}
-\todoo{do we need / want the the model images???}
+\todo{do we need / want the the model images???}
 For this thesis, we want to evaluate different information retrieval techniques when applied to CI build logs.

### 2019-11-07 thesis/txt/6-discussion.tex
change easy feedback from moritz paper review
update and improvements on introduction

@@
 \chapter{Discussion}
+\label{sec:discussion}
 
-This chapter answers our second research question and its subquestions:
+This chapter presents the answers to our research questions:
 \begin{simplebox}{Research Questions}
 \begin{itemize}
-  \item[\textbf{RQ2:}] When are PBE, CTS, and KWS suited to retrieve information from CI build logs?
+  \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
+  \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, CTS, and KWS?
-  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
+  \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
+  \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
 \end{itemize}
@@
 
-\subsection{Regular Expression Program Synthesis by Example (PBE)}
+\subsection{Program Synthesis by Example (PBE)}
 \paragraph{Configuration and Input}

### 2019-11-07 thesis/mini/acknowledgments.tex
tud logo

@@
 \noindent
-If you want, you can use this section to thank your supervisors, your universities or just anybody else who has helped you writing your thesis.
-But for this template, I want to abuse this section for a little request.
-I cannot and do not want to track who is using this template, but I am curious how many students have actually used it.
-So in case you wish to give something back to the author of this template, please consider writing an email to \href{mailto:danke@hutzelmann.net}{\nolinkurl{danke@hutzelmann.net}}.
-A simple \enquote{Thanks} is already enough, but if you want to provide more details, please add the name of your study program, the name of your thesis and tell me, what you liked and disliked the most about this template.
-\todo{Write this email \smiley{}}
-Thank you very much for your help!
+%I want to thank Moritz Beller for: support when coming to delft, great support and detailed feedback.
+invaluable contribution to this work and the large amount of things I learned about reserach in these last five months
+% annibale for his neverending input on study ideas, his expertise on information retrieval
+% prof. pretschner for his feedback and critical questions on the whether my evaluation is actually meaningful
+% prof. knapp?
+% Taico for his relentless support, upcheering in the emotional valleys of throwing everything out of the window and listening to my enthusiastic detailed descriptions of ?
+% Michi for his calming input and critical reflection of my working ethics
+% my new founld colleagues from SERG (xavier, enrique, ayoushi, pouria, luis, joseph), sparking joy in lunch and coffee breaks, good breaks for my focussed mind
+% the fourth floor group in welcoming me in a new country as I was one of them and showing me that even when you go to a completely new place you can find awesome friends there as well
+
+% If you want, you can use this section to thank your supervisors, your universities or just anybody else who has helped you writing your thesis.
+% But for this template, I want to abuse this section for a little request.
+% I cannot and do not want to track who is using this template, but I am curious how many students have actually used it.
+% So in case you wish to give something back to the author of this template, please consider writing an email to \href{mailto:danke@hutzelmann.net}{\nolinkurl{danke@hutzelmann.net}}.
+% A simple \enquote{Thanks} is already enough, but if you want to provide more details, please add the name of your study program, the name of your thesis and tell me, what you liked and disliked the most about this template.
+% \todo{Write this email \smiley{}}
+% Thank you very much for your help!
 

### 2019-11-08 thesis/txt/0-introduction.tex
small corrections before sending to annibale

@@
 Second, for researchers, who can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
-However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.
+However, these two groups can only use the information within the build logs if they can adequately retrieve the information relevant to them.
 
@@
 These approaches have various downsides and strengths:
-Regular expressions are very exact but difficult to maintain~\cite{michael2019regexes}.
+Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.
 Custom parsers are powerful though fragile towards changes in the log structure.
@@
 We aim to define a model to characterize different CR techniques, as well as the information retrievable from CI build logs.
-For \textbf{RQ1}, we analyze which criteria influence the suitability of an CR technique for CI build logs.
+For \textbf{RQ1}, we analyze which criteria influence the suitability of a CR technique for CI build logs.
 We implement and evaluate three chunk retrieval techniques:
@@
   A small increase in the number of examples used in the configuration has no visible influence and fewer structural categories improve the retrieval accuracy.
-  \item KWS has the highest recall of all techniques combined with considerable lower recall.
-  It is the only technique where retrieval quality does not decrease with and increasing number of structural categories in the configuring examples.
+  \item KWS has the highest recall of all techniques combined with much lower recall.
+  It is the only technique where retrieval quality does not decrease with an increasing number of structural categories in the configuring examples.
 \end{itemize}
-We recommend PBE for use cases where the desired information is always represented in the same structurally predictable way and a high confidence in the exactness of the chunk retrieval is required.
+We recommend PBE for use cases where the desired information is always represented in the same structurally predictable way and high confidence in the exactness of the chunk retrieval is required.
 CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
@@
 This thesis first presents an overview of related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
-Next, chapter~\ref{sec:models} characterizes chunk retrieval techniques and contained and retrievable information from CI build logs.
-It also introduces the three investigated techniques PBE, CTS and KWS.
+Next, chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and contained and retrievable information from CI build logs.
+It also introduces the three investigated techniques PBE, CTS and KWS\@.
 Chapter~\ref{sec:data-set} describes the creation of the \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs, including the labeling and the validation process.

### 2019-11-08 thesis/txt/1-related-work.tex
adress review of semi-sturctured data rw section

@@
 \section{Semi-Structured Data}
-\plan{finalized, out for review}
 \label{sec:rw-semi-structured-data}
-Serge Abiteboul ``characterizes essential aspects of semi-structured data''~\cite{abiteboul1997querying} in the context of integrating data from various data sources.
-The content of CI build logs is combined from several tools involved in the build process and several of Abiteboul's aspects can be applied to build logs.
+Serge Abiteboul introduced a theory of semi-structured data in his report from 1997 about integrating data from several sources~\cite{abiteboul1997querying}.
+He proposes essential characteristics of semi-structured data, and we show how five of these map to the context of build logs.
 
@@
 \begin{itemize}
-  \item is \textbf{implicit}.
-  We do not have access to explicit structuring elements or an explicit structure description.
+  \item \textbf{is implicit}.
+  We might not have access to explicit structuring elements or an explicit structure description.
   Computation is required to infer the present structure.
-  \item is \textbf{irregular}.
-  Changes in the build process or execution environment might change the structure of a build log without notice.
+  \item \textbf{is irregular}.
+  Changes in the build process or execution environment might change the structure of a build log.
   We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
   You can see an example of this in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.
-  \item is \textbf{partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, e.g.\ natural language text in error messages.
-  \item can be described with an \textbf{a-posteriori data guide} rather than an a-priori schema.
-  There is no fixed specification on how build tools have to structure their output.
+  \item \textbf{is partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, e.g.\ natural language text in error messages.
+  \item can be described with an \textbf{analytical data guide} rather than a beforehand defined schema.
+  There is no fixed specification on how build tools structure their output.
   We afterwards extract structuring patterns in the produced output.
-  \item has a \textbf{rapidly evolving} schema.
+  \item \textbf{has a rapidly evolving schema}.
   Modifications in the build configuration might change the tools involved in the build and therefore the composition of the build log.

### 2019-11-08 thesis/txt/2-models.tex
small corrections before sending to annibale
incorporate feedback about techniques section

@@
 \chapter{Chunk Retrieval Techniques for Build Logs}
-\plan{whole chapter: some reordering and reviewing to do, write about 3 pages about ir technique model classes and ir tasks and other techniques}
-\plan{write, 1/3 page, blocked by: rest of chapter}
-\label{sec:ir-techniques}
-%\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
+\label{sec:techniques}
+This chapter presents the characteristics of a build log
 Many different information retrieval techniques\textellipsis this section describes the conceptional / theoretical results of our thesis\textellipsis
@@
 	\includegraphics[width=\textwidth, clip]{img/build-overview.pdf}
-	\caption{The different entities involved in a build}
+	\caption{The different entities related to a CI build}
 	\label{fig:build-overview}
@@
 \label{sec:bl-characteristics}
-The idea of CI is, to integrate new software changes fast and often to catch errors early~\cite{humble2010continuous}.
+The idea of CI is to catch errors early, by integrating new software changes fast and often~\cite{humble2010continuous}.
 After making a change, the developer commits and pushes it to a shared source code repository.
 Companies often use a specific CI server, e.g.\ Travis CI, linked to their source code repository.
-A CI build might then be triggered by a push on specific branches or after a pull request was created.
-When such a CI build is triggered, it typically runs through these stages:
+A push on specific branches or the creation of a pull request triggers a CI build.
 
+A CI build typically runs through these stages:
 \begin{itemize}
 	\item Pulling the new, changed version of the source code onto the server.
+	\item Building the software, i.e.\ compiling and packaging it~\cite{phillips2014understanding}.
 	\item Running static analysis tools~\cite{zampetti2017open}.
-	\item Building the software, i.e.\ compiling and packaging it~\cite{phillips2014understanding}.
 	\item Running automated tests~\cite{beller2017oops}.
@@
 However, these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects~\cite{staahl2014modeling}.
-Some smaller projects might use CI to just make sure their code compiles as a minimal check before reviewing a pull request.
+Some smaller projects might use CI to just ensure their code compiles as a minimal check before reviewing a pull request.
 Other projects might have various stages of extensive automated testing.
@@
 They communicate progress updates, error and warning messages to the user~\cite{yuan2012characterizing}.
-We refer to to the sum of this output as build log.
+We refer to to the concatenation of this output as build log.
 The structure of their output is chosen by every tool themselves.
@@
 When analyzing build logs we might not have access to the exact build configuration, describing which tools are used in which order, or might not have access to a useable definition of the output structure of a specific tool.
-As the structure of a build log is not known to us, we describe build logs as semi-structured. Section~\ref{sec:rw-semi-structured-data} describes different properties of semi-structured data.
+Therefore build logs are semi-structured, as described in Section~\ref{sec:rw-semi-structured-data}.
 
@@
 \end{figure}
+
 \section{Information Chunks in Build Logs}
 \label{sec:bli}
-Continuous integration build logs contain a huge amount of information about the stages in the CI build they correspond to.
+CI build logs contain a huge amount of information about the stages in the CI build they correspond to.
 In this section, we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
@@
 We inspected them to get an impression about the information one would want to retrieve from a build log.
-Within the build logs from Travis CI we found different information types possibly interesting to be retrieved:
+Within the build logs from Travis CI we found different possibly interesting information types to be retrieved:
 
@@
 	      \end{itemize}
-	      You can see an example of a TravisPhase and its components within a build log in Figure~\ref{fig:log-1}.
+	       Figure~\ref{fig:log-1} shows an example of a TravisPhase and its components within a build log.
 
@@
 	      Timing information can be useful to retrieve when you want to automatically monitor the performance of your build.
-	      You can see an example of a Travis Build Step and its components within a build log in Figure~\ref{fig:log-1}.
+	      Figure~\ref{fig:log-1} shows an example of a Travis Build Step and its components within a build log.
 	      %It represents those by \lstinline{travis_time:start:<timing section id>} and \\ \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
@@
 	      The TravisWorker is a good example to show that the same BLI can have different textual representations in different build logs.
-	      You can see examples of TravisWorker instantiations in Figure~\ref{fig:log-0} and Figure~\ref{fig:log-2}.
+	      Figure~\ref{fig:log-0} and Figure~\ref{fig:log-2} show examples of TravisWorker instantiations.
 
@@
 	      The system info could be retrieved from both failing and successful logs and compared to identify if a failure is possibly based on the execution environment.
-	      You can see an example of a TravisSystemInfo instantiation within a build log in Figure~\ref{fig:log-0}.
+	      Figure~\ref{fig:log-0} shows an example of a TravisSystemInfo instantiation within a build log.
 
@@
 	      Retrieving this information from the log could, for example, be useful when reverse engineering the build configuration.
-	      You can see an example of a TriggeringCommand instantiation within a build log in Figure~\ref{fig:log-3}.
+	      Figure~\ref{fig:log-3} shows an example of a TriggeringCommand instantiation within a build log.
 
@@
 	      This information could be used to fill an overview of the build steps and why they failed.
-	      You can see an example of an ExitCode instantiation within a build log in Figure~\ref{fig:log-3}.
+	      Figure~\ref{fig:log-3} shows an example of an ExitCode instantiation within a build log.
 
@@
 	      Retrieving these and showing them to developers could help them understand quicker why the build failed.
-	      You can see an example of and ErrorMessage instantiation within a build log in Figure~\ref{fig:log-3}.
+	      Figure~\ref{fig:log-3} shows an example of and ErrorMessage instantiation within a build log.
 
@@
 	      These could be collected, counted and presented to developers, encouraging them to resolve them to improve their software.
-	      You can see examples of WarningMessage instantiations within build logs in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.
+	      Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} show examples of WarningMessage instantiations within build logs.
 
@@
 \label{sec:blirt}
-\plan{describe model classes, 1 page text}
-\todo{do we need / want the the model images???}
 For this thesis, we want to evaluate different information retrieval techniques when applied to CI build logs.
@@
 
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/pbe-technique.pdf}
-		\caption{Synthesizing Regular Expression Programs by Example Using PROSE}
-		\label{fig:prose-explanation}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/ts-technique.pdf}
-		\caption{Retrieving Information Using Text Similarity}
-		\label{fig:text-similarity-explanation}
-	\end{minipage}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/pbe-technique.pdf}
+% 		\caption{Synthesizing Regular Expression Programs by Example Using PROSE}
+% 		\label{fig:prose-explanation}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/ts-technique.pdf}
+% 		\caption{Retrieving Information Using Text Similarity}
+% 		\label{fig:text-similarity-explanation}
+% 	\end{minipage}
+% \end{figure}
 
@@
 \label{sec:expl-pbe}
-\plan{2 caro-reviews before finalized}
-
-\emph{Programming by Example (PBE)} is a technique where programs are synthesized according to in and output examples provided by the user.
-It enables users to create programs without requiring programming knowledge~\cite{mayer2015user}.
-Applied to the task of text extraction through regular expressions it relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
+\emph{Programming by Example} is a technique which synthesizes programs according to in and output examples provided by the user.
+It enables users to create programs without a priori programming knowledge~\cite{mayer2015user}.
+In the context of text extraction through regular expressions, Programming by Example relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
 We chose to investigate the applicability of generating regular expression programs by example to extracting information from build logs.
@@
 In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in~\ref{sec:impl-pbe}.
-Figure~\ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE\@.
+%Figure~\ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE\@.
 
-\paragraph{Method}
-In/Output examples (I/O examples) are the main driver of Programming by Example.
-When extracting information from build logs the \emph{input} is always a whole build log, i.e.\ the whole text of the build log file without any preprocessing.
-In the implementation, we had to apply a few text replacements as described in~\ref{sec:impl-preprocessing}.
-The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the synthesized program when given the corresponding input file.
-One or multiple I/O examples are needed as configuration for PBE, they are used to define substring of a log should be extracted.
-Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm.
+\paragraph{Configuration}
+In/output examples (I/O examples) are the main driver of Programming by Example.
+When retrieving information from build logs the \emph{input} is always a whole build log, i.e.\ the whole text of the build log file.
+The \emph{output} is always a substring of the log file text, representing the substring that should be retrieved by the synthesized program when given the corresponding input file.
+One or multiple I/O examples configure a chunk retrieval with PBE, they define the substring of a build log that should be extracted.
+The PROSE program synthesis then tries to construct a regular expression program consistent with all configuring I/O examples.
+A program is consistent with an I/O example if it returns the defined output when executed on the defined input.
+PBE reports an error back to the user if no consistent program could be synthesized.
+The program synthesis builds on the Flash Extract DSL, which in turn uses the FlashMeta algorithm.
 Both are described in Section~\ref{sec:rw-prose}.
+
+\paragraph{Application}
+A chunk retrieval run with PBE takes a build log file as input and applies the synthesized regular expression program.
+It then returns the substring of the build log matched by the program or an empty string if the program found no match.
 %For execution PBE takes a build file as input and returns a substring of the build file content.
 
-% \subsection{Perspective: Usability vs. Technical Aspects}
-% Generally, we are interested in whether Programming by Example could replace manually writing regular expressions.
-% Writing and especially maintaining regular expressions is known to be a difficult, tedious and error-prone task~\cite{michael2019regexes}.
-% There are two ways to approach this question: from the usability side or the technical side.
+\paragraph{Perspective: Usability vs. Technical Aspects}
+Generally, we are interested in whether Programming by Example could replace manually writing regular expressions.
+Writing and especially maintaining regular expressions is known to be a difficult, tedious and error-prone task~\cite{michael2019regexes}.
+There are two ways to approach this question: from the usability side or the technical side.
 
-% When studying the applicability of PBE from the \emph{usability} perspective you run into questions like
-% \begin{itemize}
-% 	\item Are users faster when using PBE compared to manual regex construction?
-% 	\item Are users more comfortable using PBE over manual regex construction?
-% 	\item Are users confident in the resulting regular expression program from PBE?
-% 	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
-% \end{itemize}
-% Some of these were already evaluated in existing works about PBE and user interaction~\cite{mayer2015user,lau2009why-programming-by-demonstration,miller2001outlier}.
+When studying the applicability of PBE from the \emph{usability} perspective, typical questions are:
+\begin{itemize}
+	\item Are users more efficient when using PBE compared to manual regex construction?
+	\item Are users more comfortable using PBE over manual regex construction?
+	\item Are users confident in the resulting regular expression program from PBE?
+	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
+\end{itemize}
+Some of these are evaluated in existing works about PBE and user interaction~\cite{mayer2015user,lau2009why-programming-by-demonstration,miller2001outlier}.
 % Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
@@
 
-% For our work, we chose to look at the applicability of PBE from the \emph{technical} perspective.
-% We investigate whether current program synthesis techniques can learn programs for information retrieval tasks in the domain of CI build logs.
-% Furthermore, we gather insights into how PBE has to be applied to yield useable results and perform best.
-% Our implementation of PBE is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
-% Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
+For our work, we chose to look at the applicability of PBE from the \emph{technical} perspective.
+We investigate whether current program synthesis techniques can learn programs for information retrieval tasks in the domain of CI build logs.
+Furthermore, we gather insights into how PBE has to be applied to yield useable results and perform best.
+Our implementation of PBE is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
+Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
 
@@
 \plan{2 caro-reviews before finalized}
-
 Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
 One common and simple technique the Vector Space Model~\cite{schutze2008introduction}.
-We investigate when it is a suitable technique to retrieve information from build logs.
-In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (TS), the concrete implementation is described in~\ref{sec:impl-ts}.
-Figure~\ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for TS.
+We investigate when text similarity is a suitable technique to retrieve information from build logs.
+In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (CTS), the concrete implementation is described in~\ref{sec:impl-ts}.
+%Figure~\ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for CTS.
 
-\paragraph{Method}
+\paragraph{Configuration}
 To configure a retrieval though text similarity we chose to use the same concept of I/O examples as for PBE\@.
-The lines of the output strings of a given example set define our search query.
-
-First, the search query is processed.
-The output strings of the example set configuring the technique are split into single lines.
-For each line we apply preprocessing: Splitting it into tokens, in our case words.
+The lines of the output strings of the configuring I/O examples define our search query.
+The algorithm splits the search query into single lines and identifies tokens, in our case words.
 %Commonly text similarity techniques employ further normalization like removing special characters and stop words.
 %We chose to keep the build log lines as complete as possible, as we often saw special characters and words identifying an interesting area.
-Then we build a document-term-frequency matrix over the lines of the output strings and prune very often or very rarely appearing words.
-Next, the algorithm applies term-frequency inverse document frequency, a best practice for natural language queries~\cite{lee1997document}.
-To retrieve the desired information from a build log, we parse the whole text and process it in the same way.
+Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
+Next, the algorithm applies term-frequency inverse document frequency to the matrix, a best practice for natural language queries~\cite{lee1997document}.
+
+\paragraph{Application}
+To retrieve the desired information from a build log, we parse the whole text and process it in the same way as the search query.
 The algorithm calculates the cosine similarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
-After summing up the similarities of each build log line to all the query lines, we sort the build log lines in decreasing similarity.
-The average number of lines in the I/O example output strings determines how many of the most similar lines are returned as the output of the retrieval run.
+After summing up the similarities of each build log line to all search query lines, we sort the build log lines in decreasing similarity.
+The average number of lines in the outputs of the configuring I/O examples determines how many of the most similar lines are returned as the output of the retrieval run.
 
-%Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}.
-
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/skws-technique.pdf}
-		\caption{Retrieving Information Using Simple Keyword Search}
-		\label{fig:keyword-search-explanation}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/diff-technique.pdf}
-		\caption{Retrieving Information Using Amar et al.'s Line Diff Approach}
-		\label{fig:diff-technique-model}
-	\end{minipage}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/skws-technique.pdf}
+% 		\caption{Retrieving Information Using Simple Keyword Search}
+% 		\label{fig:keyword-search-explanation}
+% 	\end{minipage}\hfill
+% 	\begin{minipage}{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth, clip]{img/diff-technique.pdf}
+% 		\caption{Retrieving Information Using Amar et al.'s Line Diff Approach}
+% 		\label{fig:diff-technique-model}
+% 	\end{minipage}
+% \end{figure}
 
@@
 \label{sec:expl-skws}
-\plan{2 caro-reviews before finalized}
+When developers are looking for a specific piece of information within a great amount of unstructured information, they search for related keywords as a first ad-hoc approach.
+This was one of the most common approaches we took when searching for the build failure reason within a log when creating our \emph{Failing Build Logs Data Set}.
+As this is a technique readily available in many tools developers use to view build logs, we want to study when such a keyword search is recommendable for retrieving information from CI build logs.
+In the following we will explain how we use simple keyword search to retrieve information from CI build logs (KWS), the concrete implementation is described in~\ref{sec:impl-skws}.
+%Figure~\ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.
 
-When we are looking for a specific piece of information within a great amount of unstructured information, a first ad-hoc approach is to search for keywords in the text we assume to be near the information we are looking for.
-This was one of the most common approaches we took when searching for the build failure reason within a log when creating our data set.
-As this is a technique readily available in many tools developers use to view build logs, we want to study when such a simple search for keywords is recommendable for retrieving information from CI build logs.
-In the following we will explain how we use simple keyword search to retrieve information from CI build logs (SKWS), the concrete implementation is described in~\ref{sec:impl-skws}.
-Figure~\ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.
+\paragraph{Configuration}
+A set of keywords configures the chunk retrieval with KWS.
+To better compare KWS with PBE and CTS, we also configure it through I/O examples.
+We link each I/O example with keywords, which appear in the desired output or close to it in the input build log.
+The configuring keywords for KWS are the ones that appear most often in the keywords of the configuring I/O examples.
 
-\paragraph{Method}
-SKWS is configured by giving a set of keywords.
-For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the keywords.
-As keywords are often not directly describing the desired information but rather adjacent to the desired information, this technique not only retrieves the line with the keyword but also the context around it.
-We chose a context of 10 lines above and below the keyword appearance.
+\paragraph{Application}
+For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the configuring keywords.
+As keywords are often not directly describing the desired information but rather adjacent to the desired information, this technique retrieves the lines around not only retrieves the line with the keyword but also the lines around it.
+The number of surrounding lines retrieved is the average of lines in the output of the configuring I/O examples.
 
@@
 \label{sec:expl-rlr}
+Apart from the three techniques we investigate, there are further build log analysis techniques mentioned in literature and used in industry.
+This section shows how they are described with our notion of chunk retrieval techniques.
 \plan{decide: what to mention here, max 1 page text}
@@
 \paragraph{Log Diff}
-Amar et al.\ used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
-Figure~\ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
+Amar et al.\ use a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
+The configuration for the technique is the log from the last successful build.
+This techniques retrieves all lines from a build log which are not present in the configuring build log.
+%Figure~\ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
 \paragraph{Random Line Retrieval (RLR)}
-In our evaluation we want to compare against a basic deadline of randomly extracted lines.
-The random line retrieval technique (RLR) averages the number of lines in the outputs of the configuring examples and extracts this many lines randomly from the build log.
+In our evaluation we want to compare against a baseline of randomly extracted lines.
+The average number of lines in the outputs of a set of I/O examples is the configuration for random line retrieval (RLR).
+It retrieves this number of lines randomly sampled from the build log.
 

### 2019-11-10 thesis/txt/2-models.tex
finish updating techniques section, write implementation section

@@
 \label{sec:techniques}
-This chapter presents the characteristics of a build log
-Many different information retrieval techniques\textellipsis this section describes the conceptional / theoretical results of our thesis\textellipsis
-We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly.
-Additionally, we present a complementary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
-From our analysis of build logs, we share our notion of retrievable information within a build log.
+This chapter presents how a build log is created by a continuous integration (CI) build.
+It explains our notion of retrievable information contained in build logs.
+We introduce our notion of chunk retrieval techniques to retrieve information from build logs and present the three chunk retrieval techniques we investigate for this thesis:
+Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
 
@@
 The idea of CI is to catch errors early, by integrating new software changes fast and often~\cite{humble2010continuous}.
-After making a change, the developer commits and pushes it to a shared source code repository.
-Companies often use a specific CI server, e.g.\ Travis CI, linked to their source code repository.
+Companies often link a specific CI server, e.g.\ Travis CI, to their source code repository.
+After making a change, the developer commits and pushes the new version of the code to the repository.
 A push on specific branches or the creation of a pull request triggers a CI build.
@@
 \begin{itemize}
-	\item Pulling the new, changed version of the source code onto the server.
+	\item Pulling the new, changed version of the source code into the build environment.
 	\item Building the software, i.e.\ compiling and packaging it~\cite{phillips2014understanding}.
@@
 \label{sec:bli}
-CI build logs contain a huge amount of information about the stages in the CI build they correspond to.
-In this section, we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
-Figure~\ref{fig:build-log-information} shows the model.
+CI build logs contain a great amount of information about the CI build they correspond to.
+In this section we describe our notion of a information retrievable from a CI build log.
+We present examples of information contained in Travis CI build logs and illustrate use cases for a developer or researcher to retrieve them.
 
 The central class of our model is the \emph{BuildLogInformation} (BLI), representing a piece of information possibly retrievable from a build log.
-\emph{Possibly}, because a BuildLogInformation is not necessarily present in every build log.
-If it is present, we call it a \emph{BuildLogInformation instantiation} (BLII), which always relates to a specific build log, the one it is appearing in.
+\emph{Possibly}, because a BLI is not necessarily present in every build log.
+If it is present, we call it a \emph{BuildLogInformation instantiation} (BLII), which always relates to a specific build log, the one this instantiation is appearing in.
+Figure~\ref{fig:build-overview} presents the relation between a BLI and other entities involved in a CI build.
 
@@
 This textual representation is always a substring of the log text.
-BuildLogInformations can be hierarchically ordered by their textual representations containing each other.
-As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section~\ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for BuildLogInformations whose structure we definitely know.
-Most build log information types can appear in various hierarchical arrangements and therefore not contained in any other type in the model.
+BLIs can be hierarchically ordered by their textual representations containing each other.
+As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section~\ref{sec:rw-semi-structured-data}, this section only presents hierarchical ordering or containment for BLIs whose structure we definitely know.
+Most BLI types can appear in various hierarchical arrangements and are therefore not contained in any other type in our explanation.
 
@@
 We inspected them to get an impression about the information one would want to retrieve from a build log.
-Within the build logs from Travis CI we found different possibly interesting information types to be retrieved:
+In the following we describe the possibly interesting information types to be retrieved from Travis CI build logs.
+All BLIs containing ``Travis'' in their name are specific to Travis CI build logs, the others can also apply to build logs from another CI environment.
+Figure~\ref{fig:build-log-information} shows an overview of these BLIs.
 
@@
 	\item \textbf{TravisPhase} Travis CI build logs consist of several build phases defined within the Travis CI configuration language.
-Within the build log each of these steps is framed by \lstinline{travis_fold:start:<travis phase name>} and \\ \lstinline{travis_fold:end:<build step name>}.
+Within the build log each of these phases is framed by \lstinline{travis_fold:start:<travis phase name>} and \\ \lstinline{travis_fold:end:<travis phase name>}.
 
@@
 		      \item \textbf{TravisPhaseName} The string Travis CI uses to identify the phase within start and end statements.
-		      \item \textbf{TravisPhaseOutput} The output generated during the build step.
-The textual representation of the \texttt{Build Step Output} Instantiation is the substring between the start and end statements.
+		      \item \textbf{TravisPhaseOutput} The output generated during the travis phase.
+The textual representation of the \texttt{TravisPhaseOutput} instantiation is the substring between the start and end statements.
 	      \end{itemize}
-	       Figure~\ref{fig:log-1} shows an example of a TravisPhase and its components within a build log.
+				 Retrieving the names of the phases of a Travis CI build log could be used to afterwards reconstruct an overview of the executed steps within a build.
+	       Figure~\ref{fig:log-1} shows an example of a TravisPhase instantiation and its components within a build log.
 
-	\item
 	\item \textbf{TravisTiming} Travis can measure the time of specified sections of the build process.
-	      Timing information can be useful to retrieve when you want to automatically monitor the performance of your build.
-	      Figure~\ref{fig:log-1} shows an example of a Travis Build Step and its components within a build log.
+				A developer can retrieve this timing information to automatically monitor the performance of their build.
+	      Figure~\ref{fig:log-1} shows an example of a TravisTiming instantiation.
 	      %It represents those by \lstinline{travis_time:start:<timing section id>} and \\ \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
 
-	\item \textbf{TravisWorker} Travis CI mentions for each build which machine is executing it.
-	      Retrieving this information from multiple build logs could for example help visualize the impact of the build server assignment algorithm.
-	      The TravisWorker is a good example to show that the same BLI can have different textual representations in different build logs.
-	      Figure~\ref{fig:log-0} and Figure~\ref{fig:log-2} show examples of TravisWorker instantiations.
+	\item \textbf{TravisWorker} Travis CI mentions for each build which machine is executing the build.
+	      Retrieving this information from multiple build logs can help visualize the impact of the build server assignment algorithm.
+	      The TravisWorker is a good example that the same BLI can have different textual representations in different build logs.
+	      Figure~\ref{fig:log-0} and Figure~\ref{fig:log-2} show examples of different TravisWorker instantiations.
 
 	\item \textbf{TravisSystemInfo} At the beginning of each log Travis CI describes the tech stack of the server executing the build.
-	      The system info could be retrieved from both failing and successful logs and compared to identify if a failure is possibly based on the execution environment.
+				A developer can retrieve the system information from both failing and successful logs to identify if a failure could be based on the execution environment.
 	      Figure~\ref{fig:log-0} shows an example of a TravisSystemInfo instantiation within a build log.
 
-	\item \textbf{TriggeringCommand} Travis CI logs the commands it uses to call certain tools.
+	\item \textbf{TravisTriggeringCommand} Travis CI logs the commands it uses to call certain tools.
 	      These come from the \texttt{travis.yml} configuring the build.
-	      Retrieving this information from the log could, for example, be useful when reverse engineering the build configuration.
-	      Figure~\ref{fig:log-3} shows an example of a TriggeringCommand instantiation within a build log.
+				This information can be useful for a researcher to retrieve when reverse engineering the build configuration.
+	      Figure~\ref{fig:log-3} shows an example of a TravisTriggeringCommand instantiation.
 
 	\item \textbf{ExitCode} Travis CI prints all exit codes of commands.
-	      This information could be used to fill an overview of the build steps and why they failed.
+				A researcher can retrieve this information to fill an overview of the build steps and why they failed.
 	      Figure~\ref{fig:log-3} shows an example of an ExitCode instantiation within a build log.
 
-	\item \textbf{ErrorMessage} Various tools involved in the build process might output messages of errors that occurred during their execution.
-	      Retrieving these and showing them to developers could help them understand quicker why the build failed.
-	      Figure~\ref{fig:log-3} shows an example of and ErrorMessage instantiation within a build log.
+	\item \textbf{ErrorMessage} Various tools involved in the build process output messages of errors that occurred during their execution.
+	      Retrieving these and showing them to developers can help them understand quicker why the build failed.
+	      Figure~\ref{fig:log-3} shows an example of and ErrorMessage instantiation.
 
 	\item \textbf{WarningMessage} In addition to errors, tools also print warning messages.
-	      These could be collected, counted and presented to developers, encouraging them to resolve them to improve their software.
+				Developers can collect and count them to encourage their team to resolve them.
 	      Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} show examples of WarningMessage instantiations within build logs.
@@
 	\includegraphics[width=\textwidth, clip]{img/log0.png}
-	\caption{Excerpt from a build log showing textual representations of a long Travis Worker instantiation and a Travis System Info instantiation}
+	\caption{Excerpt from a build log showing textual representations of a long TravisWorker instantiation and a TravisSystemInfo instantiation}
 	\label{fig:log-0}
@@
 	\includegraphics[width=\textwidth, clip]{img/log1.png}
-	\caption{Excerpt from a build log showing textual representations of a Travis Timing instantiation and a Travis Build Step, containing the Build Step Name and the Build Step Output}
+	\caption{Excerpt from a build log showing textual representations of a TravisTiming instantiation and a TravisPhase, containing the TravisPhaseName and the TravisPhaseOutput}
 	\label{fig:log-1}
@@
 	\includegraphics[width=\textwidth, clip]{img/log2.png}
-	\caption{Excerpt from a build log showing textual representations of a short Travis Worker instantiation}
+	\caption{Excerpt from a build log showing textual representations of a short TravisWorker instantiation}
 	\label{fig:log-2}
@@
 	\includegraphics[width=\textwidth, clip]{img/log3.png}
-	\caption{Excerpt from a build log showing textual representations of Error Message, Exit Code and Triggering Command instantiations}
+	\caption{Excerpt from a build log showing textual representations of ErrorMessage, ExitCode and TravisTriggeringCommand instantiations}
 	\label{fig:log-3}
@@
 	\includegraphics[width=\textwidth, clip]{img/log4.png}
-	\caption{Excerpt from a build log showing textual representations of Warning Message instantiations}
+	\caption{Excerpt from a build log showing textual representations of WarningMessage instantiations}
 	\label{fig:log-4}
@@
 	\includegraphics[width=\textwidth, clip]{img/log5.png}
-	\caption{Excerpt from a build log showing textual representations of Warning Message instantiations}
+	\caption{Excerpt from a build log showing textual representations of WarningMessage instantiations}
 	\label{fig:log-5}
@@
 \label{sec:blirt}
-For this thesis, we want to evaluate different information retrieval techniques when applied to CI build logs.
-We focus on techniques that do not require to parse the structure of a whole build log, but rather focus on extracting just one specified information.
-We refer to such a technique as BuildLogInformationRetrievalTechnique (BLIRT).
+For this thesis, we want to evaluate different \emph{chunk retrieval techniques} (CRTs) when applied to CI build logs.
+A chunk retrieval does not require to parse the structure of a whole build log.
+It focus on extracting just one information, specified by its configuration.
 
-A BLIRT run consumes a build log (text file) and produces a certain output (text).
+Each CRT has a specific \textit{granularity}, i.e.\ the smallest retrievable text piece and uses a specific \textit{identification technique} to select the log parts it retrieves.
+The \textit{configuration} instantiates a CRT to target a specific BLI and supplies the necessary information for the CRT to identify the textual representation of the targeted BLI in a build log.
+Each configuration addresses a specific \textit{scope}.
+The scope an be a specific project, a tool involved in the build, a programming language or global, configuring a retrieval technique for all possible build logs.
+A \textit{CRT run} consumes a build log as a plain text file and produces a string output, which consists of substrings of the build log text.
 
-A BLIRT
-\begin{itemize}
-	\item targets a specific \textbf{BuildLogInformation}.
-	\item identifies the text part to retrieve through an \textbf{IdentificationTechnique}.
-	\item is configured by a \textbf{Configuration}
-	      \begin{itemize}
-		      \item each configuration addresses a specific \textbf{Scope}.
-		            The Scope can be a specific project, a tool involved in the build, a programming language or global, configuring a retrieval technique for all possible build logs.
-	      \end{itemize}
-	\item can retrieve text passages with a specific \textbf{Granularity}, i.e.\ the smallest extractable text piece.
-	      The Granularity can be at the level of characters, lines or paragraphs.
-\end{itemize}
+The following sections of this chapter introduce the three CTRs we investigate: Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
+Lastly we describe other techniques which can also be comprehended as CRTs.
+Table \ref{tab:ctr} shows a comparison of the presented techniques.
 
-The last sections of this chapter show instantiations of this model for the three techniques we analyze and an additional one from related works.
-
-% \section{Information Retrieval Tasks}
-% \label{sec:blir-tasks}
-% \plan{what do we need here?, come up with model if we keep this, 1 page text max.}
-% Previous sections gave various examples of situations where a developer or a researcher wants to retrieve information from a build log.
-% The goal of this work is to clarify which BLIRT is suited for their specific task.
-% In this section we structure we present different important characteristics of such an IR task.
-% You can see the model in Figure~\ref{fig:model-ir-task}
-
-% \begin{figure}[htbp]
-% 	\centering
-% 	\includegraphics[width=\textwidth, clip]{img/ir-task.pdf}
-% 	\caption{Model for an Information Retrieval Task}
-% 	\label{fig:model-ir-task}
-% \end{figure}
-
-% A InformationRetrievalTask
-% \begin{itemize}
-% 	\item has a specific amount and kind of \textbf{Configuration} available.
-% 	      This represents how much data is available for the technique to learn what to extract.
-% 	      For a BLIRT to be suited the available configuration has to match the needed configuration of the technique.
-% 	\item is connected to a \textbf{TextProcessor} retrieving the output.
-% 	      This can be for example a developer reading the output or a program.
-% 	      Different TextProcessors require different accuracies in the output, e.g.
-a program needs exact retrievals to process automatically, while a developer can cope easier with falsely extracted lines.
-% \end{itemize}
-% \todo{give 2-3 concrete example instantiations here}
-
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/pbe-technique.pdf}
-% 		\caption{Synthesizing Regular Expression Programs by Example Using PROSE}
-% 		\label{fig:prose-explanation}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/ts-technique.pdf}
-% 		\caption{Retrieving Information Using Text Similarity}
-% 		\label{fig:text-similarity-explanation}
-% 	\end{minipage}
-% \end{figure}
+\begin{table}[htbp]
+\centering
+\caption{Chunk Retrieval Techniques}
+\begin{tabularx}{\textwidth}{|X|l|X|l|X|} 
+\hline
+Name                         & Acronym & Identification Technique                                   & Granularity & Configuration             \\ 
+\hline
+\hline
+Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In / Output Examples      \\
+\hline
+Common Text Similarity       & CTS     & Tf-idf \& cosine similarity, mean number of lines expected & Line        & Output Examples           \\
+\hline
+Keyword Search               & KWS     & Keywords, mean number of lines expected                    & Line        & Keywords, Context Length  \\
+\hline
+Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval Length          \\
+\hline
+Diff Approach                &         & Line not present in successful log                         & Line        & Successful Log File       \\
+\hline
+\end{tabularx}
+\label{tab:ctr}
+\end{table}
 
@@
 In the context of text extraction through regular expressions, Programming by Example relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
-We chose to investigate the applicability of generating regular expression programs by example to extracting information from build logs.
-In this work, we refer to our interpretation of this technique as \emph{PBE}.
-In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in~\ref{sec:impl-pbe}.
+We chose to investigate the applicability of generating regular expression programs by example to retrieving information chunks from build logs.
+In this work, we refer to our interpretation of Programming by Example as \emph{PBE}.
+In the following we will explain the concept of how we apply PBE to chunk retrieval from CI build logs, the concrete implementation is described in~\ref{sec:impl-pbe}.
 %Figure~\ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE\@.
@@
 In/output examples (I/O examples) are the main driver of Programming by Example.
-When retrieving information from build logs the \emph{input} is always a whole build log, i.e.\ the whole text of the build log file.
+When retrieving information chunks from build logs the \emph{input} is always a whole build log, i.e.\ the whole text of the build log file.
 The \emph{output} is always a substring of the log file text, representing the substring that should be retrieved by the synthesized program when given the corresponding input file.
@@
 \paragraph{Application}
-A chunk retrieval run with PBE takes a build log file as input and applies the synthesized regular expression program.
+A CTR run with PBE takes a build log file as input and applies the synthesized regular expression program.
 It then returns the substring of the build log matched by the program or an empty string if the program found no match.
@@
 \label{sec:expl-ts}
-\plan{2 caro-reviews before finalized}
 Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
 One common and simple technique the Vector Space Model~\cite{schutze2008introduction}.
-We investigate when text similarity is a suitable technique to retrieve information from build logs.
+We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
 In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (CTS), the concrete implementation is described in~\ref{sec:impl-ts}.
@@
 \paragraph{Configuration}
-To configure a retrieval though text similarity we chose to use the same concept of I/O examples as for PBE\@.
+To configure a chunk retrieval though text similarity we chose to use the same concept of I/O examples as for PBE\@.
 The lines of the output strings of the configuring I/O examples define our search query.
@@
 
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/skws-technique.pdf}
-% 		\caption{Retrieving Information Using Simple Keyword Search}
-% 		\label{fig:keyword-search-explanation}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/diff-technique.pdf}
-% 		\caption{Retrieving Information Using Amar et al.'s Line Diff Approach}
-% 		\label{fig:diff-technique-model}
-% 	\end{minipage}
-% \end{figure}
-
 \subsection{Keyword Search (KWS)}
@@
 This was one of the most common approaches we took when searching for the build failure reason within a log when creating our \emph{Failing Build Logs Data Set}.
-As this is a technique readily available in many tools developers use to view build logs, we want to study when such a keyword search is recommendable for retrieving information from CI build logs.
+As this is a technique readily available in many tools developers use to view build logs, we want to study when such a keyword search is recommendable for retrieving information chunks from CI build logs.
 In the following we will explain how we use simple keyword search to retrieve information from CI build logs (KWS), the concrete implementation is described in~\ref{sec:impl-skws}.
@@
 This section shows how they are described with our notion of chunk retrieval techniques.
-\plan{decide: what to mention here, max 1 page text}
 

### 2019-11-10 thesis/txt/4-tool.tex
finish updating techniques section, write implementation section

@@
 \label{sec:implementation}
-We implemented prototypes for our three focus information retrieval techniques to evaluate them on our collected build logs.
-This section will present our unified interface and describe the implementation of each of the techniques.
+To evaluate PBE, CTS and KWS on the \emph{Failing Build Log Data Set} we implemented them and a unifying interface to retrieve chunks from build logs.
 
@@
 %\section{Common Interface}
-\begin{lstlisting}
-Usage: ruby run-extraction.rb -a analyze -t <technique: ir, pbe, random> -e <example_set> -p <path_to_file_to_analyze>
-       ruby run-extraction.rb -a evaluate -t <technique: ir, pbe, keyword, random> -e <example_set> -s <selection_technique> -l <step_count_for_learning> -c <test_count>
-       ruby run-extraction.rb -a analyze -t keyword -k <keyword, keyword, ...> -p <path_to_file_to_analyze>
-       ruby run-extraction.rb -a analyze -t regex -r <regex to match extraction> -p <path_to_file_to_analyze>
+% \begin{lstlisting}
+% Usage: ruby run-extraction.rb
+%             -a analyze -t <technique: ir, pbe, random> -e <example_set> -p <path_to_file_to_analyze>
+%        ruby run-extraction.rb -a evaluate -t <technique: ir, pbe, keyword, random> -e <example_set> -s <selection_technique> -l <step_count_for_learning> -c <test_count>
+%        ruby run-extraction.rb -a analyze -t keyword -k <keyword, keyword, ...> -p <path_to_file_to_analyze>
+%        ruby run-extraction.rb -a analyze -t regex -r <regex to match extraction> -p <path_to_file_to_analyze>
 
-Specific options:
-    -a, --action ACTION              Either run an retrieval for a example set ('analyze') or run the whole evaluation of it ('evaluate')
-    -t, --technique TECHNIQUE        The technique used for creating the retrieval program (pbe, ir, keyword, random)
-    -e, --example-set EXAMPLE_SET    The filename of the example set to use
-    -p, --path PATH                  The path to the file to be analyzed relative to the 'tool/samples' folder
-    -s, --selection SELECTION        The example sequence selection technique to use for evaluation (chronological, random, manual (= like defined in file))
-    -l, --learning-step-count COUNT  How many steps with increasing example set size to do during evaluation
-    -c, --test-count COUNT           How many test files to evaluate the generated program in each learning step of the evaluation
-    -v, --verbose                    Print additional interesting output apart from only the retrieval output
-    -k, --keywords X,Y,Z             Keywords too filter lines for during keyword search based retrieval
-    -r, --regex REGEX                Regex to match on build log file content in regex based retrieval
+% Specific options:
+%     -a, --action ACTION              Either run an retrieval for a example set ('analyze') or run the whole evaluation of it ('evaluate')
+%     -t, --technique TECHNIQUE        The technique used for creating the retrieval program (pbe, ir, keyword, random)
+%     -e, --example-set EXAMPLE_SET    The filename of the example set to use
+%     -p, --path PATH                  The path to the file to be analyzed relative to the 'tool/samples' folder
+%     -s, --selection SELECTION        The example sequence selection technique to use for evaluation (chronological, random, manual (= like defined in file))
+%     -l, --learning-step-count COUNT  How many steps with increasing example set size to do during evaluation
+%     -c, --test-count COUNT           How many test files to evaluate the generated program in each learning step of the evaluation
+%     -v, --verbose                    Print additional interesting output apart from only the retrieval output
+%     -k, --keywords X,Y,Z             Keywords too filter lines for during keyword search based retrieval
+%     -r, --regex REGEX                Regex to match on build log file content in regex based retrieval
 
-Common options:
-    -h, --help                       Show this message
-\end{lstlisting}
-As we implemented the information retrieval techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interfaces.
+% Common options:
+%     -h, --help                       Show this message
+% \end{lstlisting}
+
+The unified interface is implemented in Ruby and gives access to all the CTRs we implemented.
+This section describes how to use it to retrieve chunks for a build log or evaluate a CRT.
+% As we implemented the information retrieval techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interface.
 Our unified interface then in turn calls the various different IE techniques over the command line.
 
-We provide two different modes: \emph{analysis} and \emph{evaluation}.
-The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting retrieval on the console output.
+To retrieve chunks from a build log use the option \texttt{-a analyze} with these options:
+\begin{itemize}
+    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
+    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. For pbe, ir and random analysis only. See Section \ref{sec:todo} for the definition of an example set.
+    \item \texttt{-p} \textbf{Build Log Path} The path to the file to be analyzed.
+    \item \texttt{-k} \textbf{Keywords} The keywords to search for, only for keyword analysis.
+\end{itemize}
+
+To evaluate a CTR use the option \textttt{-a evaluate} with these options:
+\begin{itemize}
+    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
+    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section \ref{sec:todo} for the definition of an example set.
+    \item \texttt{-s} \textbf{Selection Technique} \texttt{chronological, random or manual} How the order of the examples should be selected during learning.
+    Manual selects the examples according to the sequence defined in the example set file.
+    \item \texttt{-l} \textbf{Learning Step Count} How many learning steps should be evaluated, the maximum number of examples to learn with.
+    The referenced example set must define at least \emph{Learning Step Count + Test Count} examples.
+    \item \texttt{-t} \textbf{Test Count} On how many following examples the learned technique should be tested.
+    Currently only \texttt{1} is supported.
+\end{itemize}
+
+The unification tool calls the separate chunk retrieval implementations over the command line.
+Our implementation of the PBE chunk retrieval in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
+We implemented the CTS chunk retrieval using R and the text2vec~\cite{text2vec2019webpage} library.
+KWS and RLR are implemented with R.
+
+% We provide two different modes: \emph{analysis} and \emph{evaluation}.
+% The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting retrieval on the console output.
 The \emph{evaluation} takes an
 
-unification tool, reference CLI somehow nicely?,
+% unification tool, reference CLI somehow nicely?,
 
-ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)
+% ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)
 
 %\section{Overall Implementation Remarks}
-There are multiple implementation specialities that span over all languages, frameworks and implemented techniques.
-The following section discusses preprocessing and escaping of the parsed build log files / example sets, as well as\textellipsis \todo{more?}
+% There are multiple implementation specialities that span over all languages, frameworks and implemented techniques.
+% The following section discusses preprocessing and escaping of the parsed build log files / example sets, as well as\textellipsis \todo{more?}
 
-\subsection*{Preprocessing Log Text}
-\label{sec:impl-preprocessing}
+% \subsection*{Preprocessing Log Text}
+% \label{sec:impl-preprocessing}
 
 %\section*{PBE}
-\label{sec:impl-pbe}
-The first technique we implemented was the PROSE regular expression program synthesis. As it is based on the PROSE library from Microsoft provided in C\# we also chose C\# for our tool. 
-implementation details :)
+% \paragraph{Program Synthesis by Example (PBE)}
+% \label{sec:impl-pbe}
+% Our implementation of the PBE chunk retrieval in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
+% % The first technique we implemented was the PROSE regular expression program synthesis. As it is based on the PROSE library from Microsoft provided in C\# we also chose C\# for our tool. 
+% % implementation details :)
 
-C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)
+% % C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)
 
-%\section*{IR Similarity}
-\label{sec:impl-ts}
-impl details,
+% \paragraph{Common Text Similarity (CTS)}
+% \label{sec:impl-ts}
+% We implemented the CTS chunk retrieval using R and the text2vec library.
 
-R, text2vec, tokenized vectors, impl of preprocessing?
+% % impl details,
 
-don't repeat from IE models section!
+% % R, text2vec, tokenized vectors, impl of preprocessing?
 
-%\section*{Keyword search}
-\label{sec:impl-skws}
-impl details,
+% % don't repeat from IE models section!
 
-R, simple!
+% \paragraph{Keyword Search (KWs)}
+% \label{sec:impl-skws}
+% impl details,
+
+% R, simple!
 

### 2019-11-11 thesis/txt/1-related-work.tex
first half of prose rw section

@@
 \label{sec:rw}
-\todo{introduction \& glue text}
 This section presents various research works adjacent or foundational to our work.
 Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation.
-We differentiate our work from the more common production runtime log analysis and cover different information retrieval techniques.
+We differentiate our work from the more common system log analysis and show how we classify build logs as semi-structured data.
+We cover different information retrieval and extraction techniques \todo{half sentence missing: specify which techniques? 'used in software reasearch' 'used to assist software engineers'}.
 Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.
+\todo{do we also mention more things?}
 % moritz: nice formulation :)
@@
 \label{sec:rw-prose}
-\plan{extend, 1 page}
-\todo{how much can/should we explain here?
-possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
-\review{Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework.
-It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples.
+Programming by Example enables end users to automate repetitive tasks.
+The user provides examples for the input and the corresponding output and a synthesis algorithm tries to create the program intended by the user.
+This section introduces the theoretical foundations of the program synthesis algorithm implemented in the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
+It presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our PBE chunk retrieval technique.
+Further, this section covers further applications and extensions of the PROSE program synthesis, as well as previous work about
+
+\paragraph{FlashMeta: Inductive Program Synthesis}
+The FlashMeta framework presented by Polozov and Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program synthesis in the Microsoft PROSE framework.
+FlashMeta separates the inductive synthesis algorithm from the domain specific capabilities of the desired program, by encoding the possible program space in a domain specific language (DSL).
+The user specifies their intent by providing in / output examples (I/O examples).
+FlashMeta uses \emph{witness functions}, provided by the DSL, to divide the synthesis into smaller subtasks.
+For each of these subtasks it enumerates all possible programs that solve the subtask consistent with the set of I/O examples.
+A program is consistent with a set of I/O examples if it produces the corresponding output for each input example~\cite{mitchell1982generalization}.
+The subprograms are stored in a \emph{version space algebra} (VSA)~\cite{mitchell1982generalization}, which efficiently saves candidate programs for tasks by sharing common subexpressions.
+The enumerated programs are ranked according to which ones the user most likely intended.
+The ranking characteristics are also provided by the DSL.
+From the ranked VSA, FlashMeta can then return a ranked list of complete programs consistent with the users example.
+
+The different applications of PROSE presented in the following paragraphs are all implemented as DSLs for the FlashMeta synthesis algorithm.
+
+\paragraph{FlashExtract: Data Extraction by Example}
+Le et al.~\cite{le2014flashextract:} developed FlashExtract as DSL for the Microsoft PROSE framework.
+Its instantiation for text specifies text extraction programs from semi-structured text based on regular expressions.
+The authors also provide instantiations to extract data from webpages and spreadsheets.
 Users can extract multiple fields and structure them with hierarchy and sequence.
-FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.
+FlashExtract synthesizes programs to extract each of the fields leveraging the information about hierarchical containment and sequentiality.
+It eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.
 
-We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information retrieval.
-}
-\mention{prose theory paper~\cite{polozov2015flashmeta:}}
-\mention{\cite{rolim2017learning}}
+The text instantiation of FlashExtract models the extraction of a single substring as a pair of two cut positions.
+A position is either specified by an absolute character index or a pair of two regular expression (regex).
+The first regex matches the substring directly before the characterized position, the second regex directly after.
+A regex in FlashExtract is a concatenation of tokens, e.g.\ standard character classes or string literals frequently occurring in the input examples.
 
-\todo{maybe scrap this section / incorporate last sentence somewhere else, expalnation will mostly be in rw. How to usefully sturcture the stuff above this?}
-In the following we want to give an impression on how the PROSE library and specifically the Flash Extract DSL synthesize programs for extracting substrings from text via regular expressions.
-\todo{how much can/should we explain here?
-possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
-Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm. Both are described in \todo{ref rw sections}.
+We apply the text instantiation of FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information retrieval.
+
+\paragraph{Other Applications for Program Synthesis by Example}
+refazer, program transformations~\cite{rolim2017learning}
+spred sheets ~\cite{gulwani2011automating}
+table transformations~\cite{harris2011spreadsheet}
+SOME MISSING
+
+\paragraph{Improving the Program Synthesis}
+predictive data extraction~\cite{raza2017automated}
+instead of only attributing program simplicity by program syntax e.g.
+shortness also take exectution traces (e.g.
+which substrings extraction sare performed) and output similarity to each other~\cite{ellis2017learning}
+
+\paragraph{Perspective: Usability vs. Technical Aspects} maybe: usability perspecitve / usability of pbe \todo{REWORK}
+Generally, we are interested in whether Programming by Example could replace manually writing regular expressions.
+Writing and especially maintaining regular expressions is known to be a difficult, tedious and error-prone task~\cite{michael2019regexes}.
+There are two ways to approach this question: from the usability side or the technical side.
+When studying the applicability of PBE from the \emph{usability} perspective, typical questions are:
+\begin{itemize}
+	\item Are users more efficient when using PBE compared to manual regex construction?
+	\item Are users more comfortable using PBE over manual regex construction?
+	\item Are users confident in the resulting regular expression program from PBE?
+	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
+\end{itemize}
+Some of these are evaluated in existing works about PBE and user interaction~\cite{mayer2015user,lau2009why-programming-by-demonstration,miller2001outlier}.
+% Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
+% Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on synthesizing programs from examples in an unknown interface.
+% Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
+% We feel such questions of usability can be answered separately from the application domain of build logs.
+
+For our work, we chose to look at the applicability of PBE from the \emph{technical} perspective.
+We investigate whether current program synthesis techniques can learn programs for information retrieval tasks in the domain of CI build logs.
+Furthermore, we gather insights into how PBE has to be applied to yield useable results and perform best.
+Our implementation of PBE is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
+Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
+
 \end{document}

### 2019-11-11 thesis/txt/2-models.tex
first half of prose rw section

@@
 
-\paragraph{Perspective: Usability vs. Technical Aspects}
-Generally, we are interested in whether Programming by Example could replace manually writing regular expressions.
-Writing and especially maintaining regular expressions is known to be a difficult, tedious and error-prone task~\cite{michael2019regexes}.
-There are two ways to approach this question: from the usability side or the technical side.
-
-When studying the applicability of PBE from the \emph{usability} perspective, typical questions are:
-\begin{itemize}
-	\item Are users more efficient when using PBE compared to manual regex construction?
-	\item Are users more comfortable using PBE over manual regex construction?
-	\item Are users confident in the resulting regular expression program from PBE?
-	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
-\end{itemize}
-Some of these are evaluated in existing works about PBE and user interaction~\cite{mayer2015user,lau2009why-programming-by-demonstration,miller2001outlier}.
-% Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
-% Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on synthesizing programs from examples in an unknown interface.
-% Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
-% We feel such questions of usability can be answered separately from the application domain of build logs.
-
-For our work, we chose to look at the applicability of PBE from the \emph{technical} perspective.
-We investigate whether current program synthesis techniques can learn programs for information retrieval tasks in the domain of CI build logs.
-Furthermore, we gather insights into how PBE has to be applied to yield useable results and perform best.
-Our implementation of PBE is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
-Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
-
 \subsection{Common Text Similarity (CTS)}

### 2019-11-11 thesis/txt/2-models.tex
apply linter and grammarly recommendations

@@
 CI build logs contain a great amount of information about the CI build they correspond to.
-In this section we describe our notion of a information retrievable from a CI build log.
+In this section, we describe our notion of a information retrievable from a CI build log.
 We present examples of information contained in Travis CI build logs and illustrate use cases for a developer or researcher to retrieve them.
@@
 We inspected them to get an impression about the information one would want to retrieve from a build log.
-In the following we describe the possibly interesting information types to be retrieved from Travis CI build logs.
+In the following, we describe the possibly interesting information types to be retrieved from Travis CI build logs.
 All BLIs containing ``Travis'' in their name are specific to Travis CI build logs, the others can also apply to build logs from another CI environment.
@@
 		      \item \textbf{TravisPhaseName} The string Travis CI uses to identify the phase within start and end statements.
-		      \item \textbf{TravisPhaseOutput} The output generated during the travis phase.
+		      \item \textbf{TravisPhaseOutput} The output generated during the TravisPhase.
 The textual representation of the \texttt{TravisPhaseOutput} instantiation is the substring between the start and end statements.
 	      \end{itemize}
-				 Retrieving the names of the phases of a Travis CI build log could be used to afterwards reconstruct an overview of the executed steps within a build.
+				 Retrieving the names of the phases of a Travis CI build log could be used to afterward reconstruct an overview of the executed steps within a build.
 	       Figure~\ref{fig:log-1} shows an example of a TravisPhase instantiation and its components within a build log.
@@
 Each configuration addresses a specific \textit{scope}.
-The scope an be a specific project, a tool involved in the build, a programming language or global, configuring a retrieval technique for all possible build logs.
+The scope can be a specific project, a tool involved in the build, a programming language or global, configuring a retrieval technique for all possible build logs.
 A \textit{CRT run} consumes a build log as a plain text file and produces a string output, which consists of substrings of the build log text.
@@
 Lastly we describe other techniques which can also be comprehended as CRTs.
-Table \ref{tab:ctr} shows a comparison of the presented techniques.
+Table~\ref{tab:ctr} shows a comparison of the presented techniques.
 
@@
 \paragraph{Configuration}
-A set of keywords configures the chunk retrieval with KWS.
+A set of keywords configures the chunk retrieval with KWS\@.
 To better compare KWS with PBE and CTS, we also configure it through I/O examples.
@@
 For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the configuring keywords.
-As keywords are often not directly describing the desired information but rather adjacent to the desired information, this technique retrieves the lines around not only retrieves the line with the keyword but also the lines around it.
+As keywords are often not directly describing the desired information but rather next to the desired information, this technique retrieves the lines around not only retrieves the line with the keyword but also the lines around it.
 The number of surrounding lines retrieved is the average of lines in the output of the configuring I/O examples.
@@
 The configuration for the technique is the log from the last successful build.
-This techniques retrieves all lines from a build log which are not present in the configuring build log.
+This technique retrieves all lines from a build log that are not present in the configuring build log.
 %Figure~\ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
 \paragraph{Random Line Retrieval (RLR)}
-In our evaluation we want to compare against a baseline of randomly extracted lines.
+In our evaluation, we want to compare against a baseline of randomly extracted lines.
 The average number of lines in the outputs of a set of I/O examples is the configuration for random line retrieval (RLR).

### 2019-11-11 thesis/txt/1-related-work.tex
finish first full version of prose rw for thesis, start on ir and ie part

@@
 They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.
-
+~\cite{vassallo2019every}
 All these researchers described building parsers in order to evaluate the studied build logs.
@@
 \section{Information Extraction and Retrieval Techniques}
+
+The process of automatically selecting documents related to a given \emph{search query} is called \emph{Information Retrieval}~\cite{schutze2008introduction}.
+%Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+
+\emph{Information Extraction} techniques aim to automatically structure unstructured information to support subsequent processing.
+The IEPAD tool created by Chang et al.~\cite{chang2003automatic} automatically identifies data extraction patterns in semi-structured web pages, without requiring user-labeled training examples.
+PADS: stuff one section up^
+
+We investigate chunk retrieval techniques which do not aim at inferring the whole structure of a build log, but instead focus on extracting one information characterized by a user.
+
 \plan{research + write, 1/2 - 1 page}
@@
 It presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our PBE chunk retrieval technique.
-Further, this section covers further applications and extensions of the PROSE program synthesis, as well as previous work about
+Further, this section covers further applications and extensions of the PROSE program synthesis.
 
@@
 From the ranked VSA, FlashMeta can then return a ranked list of complete programs consistent with the users example.
+
+In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples not to be processed by the synthesized program.
 
@@
 
-We apply the text instantiation of FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information retrieval.
+Microsoft's system log analysis tool Azure Monitor lets users define custom log fields using the FlashExtract~\cite{azure2019custom}.
+The ConvertFrom-String function in PowerShell allows a user to specify a example template for extracting hierarchical data from a text document~\cite{powershell2019convert}.
 
-\paragraph{Other Applications for Program Synthesis by Example}
-refazer, program transformations~\cite{rolim2017learning}
-spred sheets ~\cite{gulwani2011automating}
-table transformations~\cite{harris2011spreadsheet}
-SOME MISSING
+We apply the text instantiation of FlashExtract to the domain of build logs with our chunk retrieval technique PBE\@.
 
-\paragraph{Improving the Program Synthesis}
-predictive data extraction~\cite{raza2017automated}
-instead of only attributing program simplicity by program syntax e.g.
-shortness also take exectution traces (e.g.
-which substrings extraction sare performed) and output similarity to each other~\cite{ellis2017learning}
+\paragraph{Other Applications of Program Synthesis by Example}
+Rolim et al.~\cite{rolim2017learning} use code edits as examples to learn automatic program transformations.
+Their DSL for PROSE abstracts over variables and subexpressions by describing rewrite rules applied to the abstract syntax tree.
+The synthesized transformations proposes fixes for student assignments based on corrections from other students and to automates repetitive refactoring tasks.
 
-\paragraph{Perspective: Usability vs. Technical Aspects} maybe: usability perspecitve / usability of pbe \todo{REWORK}
-Generally, we are interested in whether Programming by Example could replace manually writing regular expressions.
-Writing and especially maintaining regular expressions is known to be a difficult, tedious and error-prone task~\cite{michael2019regexes}.
-There are two ways to approach this question: from the usability side or the technical side.
-When studying the applicability of PBE from the \emph{usability} perspective, typical questions are:
-\begin{itemize}
-	\item Are users more efficient when using PBE compared to manual regex construction?
-	\item Are users more comfortable using PBE over manual regex construction?
-	\item Are users confident in the resulting regular expression program from PBE?
-	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
-\end{itemize}
-Some of these are evaluated in existing works about PBE and user interaction~\cite{mayer2015user,lau2009why-programming-by-demonstration,miller2001outlier}.
-% Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
-% Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on synthesizing programs from examples in an unknown interface.
-% Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
-% We feel such questions of usability can be answered separately from the application domain of build logs.
+In 2011 Gulwani and Harris applied a less generic predecessor of the FlashMeta framework to string manipulation within spreadsheets~\cite{gulwani2011automating} and spreadsheet transformations~\cite{harris2011spreadsheet}.
 
-For our work, we chose to look at the applicability of PBE from the \emph{technical} perspective.
-We investigate whether current program synthesis techniques can learn programs for information retrieval tasks in the domain of CI build logs.
-Furthermore, we gather insights into how PBE has to be applied to yield useable results and perform best.
-Our implementation of PBE is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
-Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.
+Raza and Gulwani~\cite{raza2017automated} present an automated algorithm that tries to predict data extraction programs from only input examples.
+Their tool can split system log statements into table columns or extract data from lists on webpages into spreadsheets.
+
+In a program synthesis shorter and simpler program often receive a better ranking.
+Ellis and Gulwani~\cite{ellis2017learning} improved the accuracy of the PROSE program learner even further by also taking into account the execution traces of the program candidates.
+For example, a program that extracts overlapping substrings is ranked lower than a program without overlapping extractions.
+They also weigh the produced output of applying a program to input only examples and prefer programs which produces output structurally similar to the provided output examples.
+
+\paragraph{User Interaction with Programming by Example}
+I/O examples are an ambiguous specification of a program and user confidence in the correctness of the synthesized program is important for a wide adoption of Programming by Example based systems~\cite{lau2009why-programming-by-demonstration}.
+Miller and Myers~\cite{miller2001outlier} uncover outliers in input data provided to a Programming by Example text editing task.
+For the PROSE framework, Mayer et al.~\cite{mayer2015user} compare two approaches for disambiguation by the user.
+With their first approach, the user can browse lower ranked program candidates in a tree like natural language transformation of the constructed VSA.
+The second approach actively asks the user to resolve ambiguous output possibilities for input only examples.
 

### 2019-11-12 thesis/txt/1-related-work.tex
drafts on ir / ie and system log analysis rw sections

@@
 
-\section{System Log Analysis}
-\plan{research + write, 1/2 - 1 page}
-\mention{logpai and drain, [7] K. Fisher and D. Walker. The pads project: an overview. In ICDT,
-2011.
-[8] K. Fisher, D. Walker, K. Q. Zhu, and P. White. From dirt to shovels:
-fully automatic tool generation from ad hoc data. In POPL, 2008.[23] Q. Xi and D. Walker. A context-free markup language for semi- structured text. In PLDI, pages 221–232, 2010.
- The PADS project [7] has en- abled simplification of ad hoc data processing tasks for programmers
-by contributing along several dimensions: development of domain specific languages for describing text structure or data format, learn- ing algorithms for automatically inferring such formats [8], and a markup language to allow users to add simple annotations to enable more effective learning of text structure [23] While PADS supports parsing of entire files, FlashExtract allows users to extract only parts of the file thereby avoiding unnecessary complications.
-PADS’s learner only supports a fixed line-by-line chunking strategy to split the records; in contrast, FlashExtract can learn chunking (aka, struc- ture boundaries) from examples, making it suitable for extracting data fields and records that have arbitrary length (and might cross multiple lines).
-Finally, PADS primarily targets ad hoc text files.
-Although one can view webpages and spreadsheet as text files, it is unclear if the PADS learning algorithm can be adapted to work effectively for webpages and spreadsheets.
-}
+\section{System Log Analysis} \todo{parsing?}
 
-\mention{ask Jean?}
+A related field of log processing is the processing of system log files produced during runtime.
+A main difference in system logs is that they are fundamentally structured through events.
+Each line in the log file represents one event.
+The first goal in parsing system log files is to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
+Next the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
+The output of a log parser is a structured log, composed of a list of timed events and the corresponding parameter values~\cite{he2016evaluation}.
+This structured log is then the input to various machine learning and data mining processes.
+They mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
+Xu et al.~\cite{xu2009detecting} leveraged the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
+
+The techniques developer for system logs can also be applied to build logs.
+One example is comparing execution traces to reference traces of intended behaviour to detect anomalies.
+Amar et al.~\cite{amar2019mining} employed a similar approach to detect relevant lines in build logs.
+
+Classic log parsers interpret the whole log file into a sequence of events.
+A similar approach could also be applied to build logs to determine the sequence of executed buidl steps or phases.
+In this thesis we focus on extracting a single speficied information from the build log as a whole with chunk retrieval techniques.
+Chunk retrieval technques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g. through regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
 
@@
 
-The process of automatically selecting documents related to a given \emph{search query} is called \emph{Information Retrieval}~\cite{schutze2008introduction}.
-%Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+The process of automatically selecting unstructured documents related to a given \emph{search query} is called \emph{Information Retrieval}~\cite{schutze2008introduction}.
+For this, algorithms try to determine the general topic or conceptual information of the document.
+Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix and weighing the terms with tf-idf~\cite{lee1997document}.
+On the matrix the algorithms apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
+
+Information retrieval techniques are leveraged to improve software engineering in various areas.
+Antoniol et al.~\cite{antoniol2002recovering} query manual pages and requirements with program identifiers to create trace links between code and documentation.
+The same task is addressed by Marcus et al.~\cite{marcus2005recovery}, who also incorporate source code comments into their query.
+Panichella et al.~\cite{panichella2016parameterizing} and Runeson et al.~\cite{runeson2007detection} apply similar information retrieval techniques to detect duplicated bug reports.
+
+Salton et al.~\cite{salton1993approaches} retrieve text parts relevant for a given user query by calcluating global document similarity scores and refining the output through local passage similarity.
+Similarity is also calculated using term vectors.
 
@@
 The IEPAD tool created by Chang et al.~\cite{chang2003automatic} automatically identifies data extraction patterns in semi-structured web pages, without requiring user-labeled training examples.
-PADS: stuff one section up^
+They split the semi-structured documents into tokens, discover repetitive patterns using occurrence-counting suffix trees and select the most regular and compact patterns to define extraction.
 
-We investigate chunk retrieval techniques which do not aim at inferring the whole structure of a build log, but instead focus on extracting one information characterized by a user.
+\todo{regex generation}
+Bartoli et al.~\cite{bartoli2012automatic} leverage genetic programming to generate regular expressions based on user examples.
+Their approach also reprensents the regular expressions in a tree structure and mutates them to maximize extraction accuracy on the provided examples while minimizing the length of the regular expression.
+Their evaluation shows that their algorithm is on average faster and more accurate than humans~\cite{bartoli2016on-the-automatic}.
 
-\plan{research + write, 1/2 - 1 page}
-\todo{explain difference here, reference pads(maybe that is already in log anlysis!) and stuff}
-\review{Getting the general tot p cic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
-Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
-On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
-For our use case, this could be applied by slicing the build logs into lines or small sections.
-Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
-Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}
+The WHISK system by Stephen Soderland~\cite{soderland1999learning} learns text extraction regular expressions for semi-structured text.
+The system interleaves the learning process with the example annotation and reduces the number of required examples by presenting examples that eliminate ambiguities between learning candidates.
 
-\mention{IR papers, maybe something about keyword search?}
+Dan Smith and Mauricio Lopez~\cite{smith1997information} extract structured information from sets of semi-structured documents that contain similar information but are strucutured differently.
+The user provides rules of each piece of information, detailing in which section of the document it might be present.
+Identifying keywords and regular expressions determine whether the information is present and where it starts and ends.
+
+The PADS project~\cite{fisher2011the-pads} is centered around declaring grammars for the information contained in semi-structured documents.
+Based on this declarative data description various tools are generated like format converters, e.g. to XML, data adaptors to other tools, statistical analyzers and visualizers.
+Manually defined PADS grammars eliminate the need to develop a custom data extraction parser.
+Xi and Walker developed ANNE~\cite{xi2010a-context-free}, which can infer context-free PADS grammars from a small number of user annotations and the raw document data.
+Fisher et al.~\cite{fisher2008from} fully automated the grammar generation.
+They split the data into chunks, lines or documents, and further into tokens.
+Parentheses are used to infer hierarchical structure information.
+The system guesses grammar operators unifying single tokens or subexpressions, scores the resulting grammars and applys appropriate rewrite rules to refine the candidate grammars.
+
+The presented information extraction approaches support parsing and structuring of entire files, while we investigate chunk retrieval techniques which do not aim at inferring the whole structure of a build log.
+Instead focus on extracting one specific information characterized by a user.
 

### 2019-11-13 thesis/txt/0-introduction.tex
most of expanding for rw on ci and build logs, annibales feedback on introduction

@@
 
-There are different techniques to retrieve information from CI build logs. Beller et al.\ use regular expressions to analyze the failure reasons of build logs from Travis CI~\cite{beller2017oops}.
+There are different techniques to retrieve information from CI build logs. Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
 Such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
@@
 Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
-At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
-Developers and researches currently have little support while choosing which technique to use for a retrieval task.
+At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred over other alternatives.
+Developers and researches currently have little support while choosing which technique to use for a task.
 
-The goal of this thesis is to investigate different chunk retrieval techniques (CR techniques) for build logs and describe under which circumstances we recommend each of the techniques.
+The goal of this thesis is to investigate different chunk retrieval techniques (CR techniques) for build logs and describe under which circumstances each techniques is recommended over another.
 We aim to define a model to characterize different CR techniques, as well as the information retrievable from CI build logs.
@@
 \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-\textbf{RQ2} is refined into sub-questions along the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
+\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
 how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the configuring examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
@@
 % \end{simplebox}
-To evaluate PBE, CTS and KWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
+To evaluate PBE, CTS and KWS we create a dataset, namely the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
 Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.
@@
 In cases where the representation fo the desired information is unpredictable or varies greatly, KWS is the best technique to choose.
-Though the low precision of the output requires a human to interpret the output of the chunk retrieval.
+However, the low precision requires a human to interpret the output of the chunk retrieval.
 
@@
   %\item The \emph{LogCollector}, a tool to gather build logs from Travis CI
-  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
+  \item A validated data set of about 800 logs from failed Travis CI builds manually-labelled with:
         \begin{itemize}
@@
 
-This thesis first presents an overview of related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
-Next, chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and contained and retrievable information from CI build logs.
-It also introduces the three investigated techniques PBE, CTS and KWS\@.
+This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
+Next, chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
+It also introduces the three investigated techniques: PBE, CTS and KWS\@.
 Chapter~\ref{sec:data-set} describes the creation of the \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs, including the labeling and the validation process.
@@
 This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}.
-Chapter~\ref{sec:discussion} presents the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
+Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
 Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.

### 2019-11-13 thesis/txt/1-related-work.tex
most of expanding for rw on ci and build logs, annibales feedback on introduction

@@
 Various researchers have analyzed industrial and open source logs for failure reasons and their impact on development.
+
 Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google.
 In addition most failures are resolved within two builds.
+The build logs were the primary data source for their analysis and they developed a custom parser to classfiy error messages reported by Java and C++ builds. 
+Small percentage of error types account for most of the build failures.
+
 Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones.
@@
 Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
+analyzed the collected buildlogs by extractino eeror messages using regular expressions.
+The regular expressions were looking for keywords identified in a manual analysis.
+
+Vassallo et al.~\cite{vassallo2018continuous} conducted a survey study on how ci influences developers to continiously refactor their code to fix ci quality analysis warnings.
+Their results indicate that refactoring is rather spread in the ci environment and deemed important by the surveyed developers.
+``Lack of time'' and ``absence of a proper test suite'' are named as the main barriers to continuous refactoring.
+
+Vassallo et al.~\cite{vassallo2019automated} analyzed build logs, source code repository content and build metadata of open source repositories for CI anti-patterns.
+
+Rausch et al.~\cite{rausch2017empirical} analyzed CI builds of open soucre java procjects and categorize why builds failed.
+Most fail because of test  and for most porojects over half of failed biuilds follow another failed build.
+Found that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
+
+Automated static analysis tools are the focus of Zampetti et al.~\cite{zampetti2017open} in ther study of java projects from GitHub.
+Their results show that static analysis in responsible for a small amount of build failures and mainly responsible for warned builds.
+Almost all projects use custom configurations for the static analysis, however the configuration rarely changes.
+Failures because of static analysis warings are fixed in a short timeframe.
+
+Stahl and Bosch~\cite{staahl2014modeling} provide a hollistic review of literature on automatic build environments in industry projects.
+They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
+
+~\cite{holck2003continuous}
+
+~\cite{schermann2016towards}
+
+~\cite{hilton2017trade-offs}
+
+~\cite{hilton2016usage}
+
+Vasilescu et al.~\cite{vasilescu2015quality} analyzed a broad rage of open source projects written in popular languages on GitHub.
+They compared their usage of CI with the successful merges of pull requests and found that CI increase the number of successful merges, internal as well as external contributions, and allows the team members to uncover more bugs.
+
+In a new study, vasallo et al. interviewed developers on how they determine why a CI build failed.
+They model how these developers resolve failures and found that error identification trhough inspecting the build logs is a central activity. \todo{check!}
+found that locating the error within the build log and using the additional informatino provided with and around the error message to understand the details of the failures are the first and most important steps when developers want to fix a build failure.
+~\cite{vassallo2019every}
+
+identfy noise in buidl breakage data.
+take travistorrent data set and classify build failures according to whether they were caused by an enviornmental failure or caused by a develpoer change.
+They also identify cascading buildfailures created by existing unfixed errors and allowed failures, whose results were later labeled by developers to be ignored.
+thy found that about half of the failed biudls in travistorrent fall in at las one of the labeled categiries and that these, when regarded as noise, considerably impact observations reported by other works trying to model build breakages.
+their analysis starts with manual eval of logs, selected keywords and strings that identify cetrain kind of label, coded script that looked for exactly these to classify and validated the results with another manual classification.
+similar techniques -> keywords, slightly different goal as they want to classify the whole log, not extract substring from it.
+~\cite{ghaleb2019studying}
+
 Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
 They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.
-~\cite{vassallo2019every}
+they focus their analysis on java and ruby build logs for which they build custom parsers with regular expressions to extract the reason a build failed.
+
 All these researchers described building parsers in order to evaluate the studied build logs.
@@
 \plan{extend, 1 page}
-Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs.
-They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts.
+Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
+They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators leveraging this structured access to the information within the build log.
+They implement several hint generators, for example one that queries stack overflow for discussions related to why the build failed.
+Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
 They observed that highlighting the locality and context of an issue is helpful to programmers.
+
 We strive to enable a similar summarization by text retrieval while also covering a wider array of programming languages.
-\todo{mention which technique}
-\todo{reference their new paper}
 
-Amar et al.~\cite{amar2019mining} reduced the lines \todo{portions?} of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
-They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the error.
+BART (2019) Jenkins-Plugin. https://plugins.jenkins.io/bart. Accessed: 2019-07-24
+
+Amar et al.~\cite{amar2019mining}  compare different approaches to reduce the portions of a log to be inspected by the engineer.
+The techniques remove lines that appear both in passing and failing build logs and use a modified Term Frequency Inverse Document Frequency weighting to identify term vectors likely to occur with failures.
+They use the term vectors and cosine similarity to further filter the log portions only present in failing build logs.
+Their diff technique can be interpreted as a chunk retrieval technique, though the user can not specify an information to target.
+The information retrieved is always difference to what was before \todo{wait not quite the past failures (environmental in that case) specify the information!}
+They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the erro.
 In contrast to that, our tool ALBE extracts specific parts of the build logs.

### 2019-11-14 thesis/txt/1-related-work.tex
write about last ci papers, fix references

@@
 
-~\cite{holck2003continuous}
+Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
+Developers use CI to ensure consistency and quality across different execution environments and increase confidence into the code they deploy.
 
-~\cite{schermann2016towards}
-
-~\cite{hilton2017trade-offs}
-
-~\cite{hilton2016usage}
+Hilton et al.~\cite{hilton2016usage} analyze how and why open source projects use CI.
+They observe CI usage in a broad range of projects, it supports them to catch bugs earlier and have more confidence in a successful build and shorten release cycles.
 
@@
 We strive to enable a similar summarization by text retrieval while also covering a wider array of programming languages.
-
-BART (2019) Jenkins-Plugin. https://plugins.jenkins.io/bart. Accessed: 2019-07-24
 

### 2019-11-14 thesis/txt/3-data-set.tex
write about last ci papers, fix references

@@
 \paragraph{Example Set}
+\label{sec:example-set}
 Our data set is organized in example sets.
@@
 We received answers from 61 developers, responding about 144 build logs.
-The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig: mails-answers-received-builds}.
+The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds}.
 

### 2019-11-17 thesis/txt/0-introduction.tex
new data set name, change chapter 3 name, incorporate rest of annibales feedback

@@
 \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the configuring examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
+how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
 % \begin{simplebox}{Research Questions}
@@
 % \end{simplebox}
-To evaluate PBE, CTS and KWS we create a dataset, namely the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
+To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
 Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.
 
-Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that
+Our study of the three techniques on \emph{LogChunks} shows that
 \begin{itemize}
@@
 CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the representation fo the desired information is unpredictable or varies greatly, KWS is the best technique to choose.
+In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
 However, the low precision requires a human to interpret the output of the chunk retrieval.
@@
 
-This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
-Next, chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
+This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
+Chapter~\ref{sec:rw} presents existing work on information extraction and retrieval techniques and program synthesis from examples.
+Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
 It also introduces the three investigated techniques: PBE, CTS and KWS\@.
-Chapter~\ref{sec:data-set} describes the creation of the \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs, including the labeling and the validation process.
+Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
 Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.

### 2019-11-17 thesis/txt/1-related-work.tex
new data set name, change chapter 3 name, incorporate rest of annibales feedback

@@
 \chapter{Background}
+\plan{whole RW currently highly work in progress, text not yet coherent!}
 \plan{all of RW: 4 - 5 pages left to do + some research!}
@@
   Changes in the build process or execution environment might change the structure of a build log.
-  We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
+  We observed this in the logs we collected for the \emph{LogChunks} data set, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
   You can see an example of this in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.

### 2019-11-17 thesis/txt/2-models.tex
new data set name, change chapter 3 name, incorporate rest of annibales feedback

@@
 
-\chapter{Chunk Retrieval Techniques for Build Logs}
+\chapter{Introduction to Chunk Retrieval Techniques}
 \label{sec:techniques}
@@
 
-During our initial exploration and log data collection for the \emph{Failing Build Log Data Set}, we collected a broad set of build logs from 29 languages and 87 repositories from Travis CI~\cite{travisci2019webpage}.
+During our initial exploration and log data collection for the \emph{LogChunks} data set, we collected a broad set of build logs from 29 languages and 87 repositories from Travis CI~\cite{travisci2019webpage}.
 We inspected them to get an impression about the information one would want to retrieve from a build log.
@@
 When developers are looking for a specific piece of information within a great amount of unstructured information, they search for related keywords as a first ad-hoc approach.
-This was one of the most common approaches we took when searching for the build failure reason within a log when creating our \emph{Failing Build Logs Data Set}.
+This was one of the most common approaches we took when searching for the build failure reason within a log when creating our \emph{LogChunks} data set.
 As this is a technique readily available in many tools developers use to view build logs, we want to study when such a keyword search is recommendable for retrieving information chunks from CI build logs.

### 2019-11-17 thesis/txt/3-data-set.tex
new data set name, change chapter 3 name, incorporate rest of annibales feedback

@@
 
-\chapter{BUILDS - BUIld Log Data Set}
+\chapter{LogChunks Data Set}
 \includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
@@
 % For our initial data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
-% For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
+% For \emph{LogChunks} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
 % our impression?
@@
 \subsubsection{Introduction}
+After the manual labeling of the data set we performed a second labeling of a sample of the build logs to validate the labels.
 \subsubsection{Method}
+For each label category: Build Failure Reason, keywords and category, we relabeled 30 randomly sampled logs.
+compared the labeles, \todo{discussed about it}.
 \subsubsection{Results}
+
 \subsubsection{Discussion}
+main takeaway: overlap yes, but high variation
+
+build failure reason: should we extract the information \emph{that} the build failed as well?
+our data set extracts the parts describing \emph{why}, but leaves out the lines stating that the build failed (e.g. step xy exited with 1).
+
+keywords: first labeler allowed also longer strings with spaces and adhered to capitalization.
+second one ignored captialization and focussed on the keyword.
+so only one word was allowed.
+also the first one labeled always a full repository at a time.
+so could take into consideration patterns and see what keywords are exception specific and would only retrieve the failure reason if this specific exception occured.
+second labeler only one build log excerpt (+ context) per repository.
+also: influene of ansi color codes ``merror'' vs. ``error'' first labeler known as ansi color codes, second one counted it into the word (whole word always)
+first was also more inclined to search for a subpart of a word to make it more generalizeable (``failure`` instead of ``failures'')
+
+categories: description for the second labeling stated: sort into categories on why build failed.
+was exectued with sorting into test/linter/compilation.
+in the case of the selected repositories everything was labeled as test.
+mostly correct (one linter), but more importantly no difference was made in which test step failed / how the failed tests were represented.
+the categories are thought as structural categories.
+so the surrounding sturcture and the way a test failure is communicated is important. e.g. if several tests are run then it is important which ones failed
+
+main influence / implication: the labels we select are not black/white.
+accurate description of what we do is very very important.
+mainly influenced how we described our data points in the earlier sections.
 \subsubsection{Threats to Validity}
@@
 \subsubsection{Introduction}
-For the \emph{Failing Build Log Data Set} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
+For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
 As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
@@
 If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
-In this section we describe how we validate the extractions of the build failure reason the \emph{Failing Build Log Data Set} describes.
+In this section we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
 \subsubsection{Method}
@@
 \subsubsection{Discussion}
-This study highly strengthens the trust in the validity of the extracted build failure reasons in the \emph{Failing Build Log Data Set}.
+This study highly strengthens the trust in the validity of the extracted build failure reasons in \emph{LogChunks}.
 The study received answers about 18\% of the logs labelled in our build log, of which, after manual correction, 91\% said our labelled extractions were accurate.

### 2019-11-17 thesis/txt/4-tool.tex
first half of prose rw section
write about last ci papers, fix references
new data set name, change chapter 3 name, incorporate rest of annibales feedback

@@
 \label{sec:implementation}
-To evaluate PBE, CTS and KWS on the \emph{Failing Build Log Data Set} we implemented them and a unifying interface to retrieve chunks from build logs.
+To evaluate PBE, CTS and KWS on \emph{LogChunks} we implemented them and a unifying interface to retrieve chunks from build logs.
 
@@
     \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
-    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. For pbe, ir and random analysis only. See Section \ref{sec:todo} for the definition of an example set.
+    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique.
+For pbe, ir and random analysis only.
+See Section \ref{sec:example-set} for the definition of an example set.
     \item \texttt{-p} \textbf{Build Log Path} The path to the file to be analyzed.
@@
 
-To evaluate a CTR use the option \textttt{-a evaluate} with these options:
+To evaluate a CTR use the option \texttt{-a evaluate} with these options:
 \begin{itemize}
     \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
-    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section \ref{sec:todo} for the definition of an example set.
+    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section \ref{sec:example-set} for the definition of an example set.
     \item \texttt{-s} \textbf{Selection Technique} \texttt{chronological, random or manual} How the order of the examples should be selected during learning.

### 2019-11-17 thesis/txt/5-study.tex
change easy feedback from moritz paper review
new data set name, change chapter 3 name, incorporate rest of annibales feedback

@@
 \label{sec:study}
-To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{Failing Build Log Data Set}.
+To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{LogChunks} data set.
 This chapter describes our study design and presents the results of the study.
@@
 RLR, explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
-We run four techniques on the example sets from the \emph{Failing Build Log Data Set}.
+We run four techniques on the example sets from \emph{LogChunks}.
 
@@
 
-%taking The Failing Build Log Data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?
+%taking The LogChunks data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?
 
@@
 \end{figure}
-\subsection{Regular Expression Program Synthesis by Example (PBE)}
+\subsection{Program Synthesis by Example (PBE)}
 Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.

### 2019-11-18 thesis/txt/1-related-work.tex
rework rw section, incorporate Taico's feedback on techniques section

@@
 \section{Continuous Integration}
-\plan{extend, 1 page}
-\mention{look into proksch papers}
-Various researchers have analyzed industrial and open source logs for failure reasons and their impact on development.
+This section starts with an overview on research into why CI is used and its impact on development.
+It presents analyses on why CI builds fail and how testing and static anlysis tools are used within CI.
+We explain how researchers compose data sets for their work on CI and how chunk retrieval techniques can support them.
 
+\paragraph{Motivation for CI and impact of CI}
+Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
+Developers use CI to ensure consistency and quality across different execution environments and increase confidence into the code they deploy.
+Hilton et al.~\cite{hilton2016usage} also analyze how and why open source projects use CI.
+They observe CI usage in a broad range of projects, it supports them to catch bugs earlier and have more confidence in a successful build and shorten release cycles.
+Stahl and Bosch~\cite{staahl2014modeling} provide a hollistic review of literature on automatic build environments in industry projects.
+They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
+Vasilescu et al.~\cite{vasilescu2015quality} analyzed a broad rage of open source projects written in popular languages on GitHub.
+They compared their usage of CI with the successful merges of pull requests and found that CI increase the number of successful merges, internal as well as external contributions, and allows the team members to uncover more bugs.
+In a new study, Vasallo et al.~\cite{vassallo2019every} interview developers on how they determine why a CI build failed.
+They model how these developers resolve failures.
+The first and most important steps when developers want to fix a build failure is locating the error within the build log.
+Then the developers use the additional information provided with and around the error message to understand the details of the failures.
+% Vassallo et al.~\cite{vassallo2018continuous} conducted a survey study on how ci influences developers to continuously refactor their code to fix ci quality analysis warnings.
+% Their results indicate that refactoring is rather spread in the ci environment and deemed important by the surveyed developers.
+% ``Lack of time'' and ``absence of a proper test suite'' are named as the main barriers to continuous refactoring.
+% Vassallo et al.~\cite{vassallo2019automated} analyzed build logs, source code repository content and build metadata of open source repositories for CI anti-patterns.
+
+\paragraph{Build Failures in CI}
+Various researchers looked into why CI builds fail and the impact of build failures on the development workflow.
 Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google.
-In addition most failures are resolved within two builds.
-The build logs were the primary data source for their analysis and they developed a custom parser to classfiy error messages reported by Java and C++ builds. 
-Small percentage of error types account for most of the build failures.
-
+In addition most failures are resolved within two builds and a small percentage of error types account for most of the build failures.
+Rausch et al.~\cite{rausch2017empirical} analyzed CI builds of open source java procjects and categorize why builds failed.
+Most fail because of test  and for most porojects over half of failed biuilds follow another failed build.
+Found that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
 Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones.
@@
 Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
-analyzed the collected buildlogs by extractino eeror messages using regular expressions.
-The regular expressions were looking for keywords identified in a manual analysis.
 
-Vassallo et al.~\cite{vassallo2018continuous} conducted a survey study on how ci influences developers to continiously refactor their code to fix ci quality analysis warnings.
-Their results indicate that refactoring is rather spread in the ci environment and deemed important by the surveyed developers.
-``Lack of time'' and ``absence of a proper test suite'' are named as the main barriers to continuous refactoring.
-
-Vassallo et al.~\cite{vassallo2019automated} analyzed build logs, source code repository content and build metadata of open source repositories for CI anti-patterns.
-
-Rausch et al.~\cite{rausch2017empirical} analyzed CI builds of open soucre java procjects and categorize why builds failed.
-Most fail because of test  and for most porojects over half of failed biuilds follow another failed build.
-Found that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
-
+\paragraph{Static Analysis and Testing in CI}
 Automated static analysis tools are the focus of Zampetti et al.~\cite{zampetti2017open} in ther study of java projects from GitHub.
@@
 Almost all projects use custom configurations for the static analysis, however the configuration rarely changes.
-Failures because of static analysis warings are fixed in a short timeframe.
-
-Stahl and Bosch~\cite{staahl2014modeling} provide a hollistic review of literature on automatic build environments in industry projects.
-They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
-
-Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
-Developers use CI to ensure consistency and quality across different execution environments and increase confidence into the code they deploy.
-
-Hilton et al.~\cite{hilton2016usage} analyze how and why open source projects use CI.
-They observe CI usage in a broad range of projects, it supports them to catch bugs earlier and have more confidence in a successful build and shorten release cycles.
-
-Vasilescu et al.~\cite{vasilescu2015quality} analyzed a broad rage of open source projects written in popular languages on GitHub.
-They compared their usage of CI with the successful merges of pull requests and found that CI increase the number of successful merges, internal as well as external contributions, and allows the team members to uncover more bugs.
-
-In a new study, vasallo et al. interviewed developers on how they determine why a CI build failed.
-They model how these developers resolve failures and found that error identification trhough inspecting the build logs is a central activity. \todo{check!}
-found that locating the error within the build log and using the additional informatino provided with and around the error message to understand the details of the failures are the first and most important steps when developers want to fix a build failure.
-~\cite{vassallo2019every}
-
-identfy noise in buidl breakage data.
-take travistorrent data set and classify build failures according to whether they were caused by an enviornmental failure or caused by a develpoer change.
-They also identify cascading buildfailures created by existing unfixed errors and allowed failures, whose results were later labeled by developers to be ignored.
-thy found that about half of the failed biudls in travistorrent fall in at las one of the labeled categiries and that these, when regarded as noise, considerably impact observations reported by other works trying to model build breakages.
-their analysis starts with manual eval of logs, selected keywords and strings that identify cetrain kind of label, coded script that looked for exactly these to classify and validated the results with another manual classification.
-similar techniques -> keywords, slightly different goal as they want to classify the whole log, not extract substring from it.
-~\cite{ghaleb2019studying}
-
+Failures because of static analysis warnings are fixed in a short time frame.
 Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
 They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.
-they focus their analysis on java and ruby build logs for which they build custom parsers with regular expressions to extract the reason a build failed.
 
-All these researchers described building parsers in order to evaluate the studied build logs.
-Our work could support their research by easing the parser development and enable them to cover more languages and build tools easier.
+\paragraph{Data Sets powering CI Research}
+The works presented in this section are based on either developer surveys or data sets, containing build metadata or build logs.
+Seo et al..~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
+Beller et al. created the \emph{TravisTorrent} data set~\cite{beller2017travistorrent} providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
+TravisTorrent was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
+Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
+They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
+They also identify cascading build failures created by existing unfixed errors and allowed failures, whose results were later labeled by developers to be ignored.
+About half of the failed builds in \emph{TravisTorrent} fall into at least one of these categories.
+When regarded as noise they considerably impact observations reported by other works modeling build breakages.
+
+\paragraph{Build Log Analysis in CI Research}
+For Seo et al.~\cite{seo2014programmers} the build logs were the primary data source for their analysis and they developed a custom parser to classify error messages reported by Java and C++ builds. 
+Vassallo et al.~\cite{vassallo2017a-tale} analyzed collected build logs by extraction error messages using regular expressions.
+The regular expressions were looking for keywords identified in a manual analysis.
+The analysis of Ghaleb et al.~\cite{ghaleb2019studying} starts with manual categorization of build logs.
+They select keywords and strings that identify one of their noise categories and coded script to automatically classify logs based on these keywords.
+To validate the script results, they performed another manual classification.
+Beller et al.~\cite{beller2017oops} focus their analysis on java and ruby build logs for which they built custom parsers with regular expressions to extract the reason a build failed.
+
+\paragraph{Supporting Log Analysis with Chunk Retrieval}
+To leverage the valuable information within build logs these researchers built parsers and regular expression based programs.
+This task of retrieving specific chunks of text from the build logs can be solved by the chunk retrieval techniques we compare in this thesis.
+Our results can support researchers in choosing a suitable technique for their data set of build logs and the chunks they want to retrieve.
+By relieving them from building custom parsers we enable them to cover more languages and build tools in their studies.
 
@@
 \label{sec:rw-bl-analysis}
-\plan{extend, 1 page}
+Build logs are a valuable data source for developers to find out why their build failed.
+Various researchers are looking into supporting developers to process the verbose build logs.
 Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
-They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators leveraging this structured access to the information within the build log.
-They implement several hint generators, for example one that queries stack overflow for discussions related to why the build failed.
+They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
+The hint generators leverage this structured access to the information within the build log to propose fixes.
+One of the hint generators for example queries stack overflow for discussions related to why the build failed.
+In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
 Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
-They observed that highlighting the locality and context of an issue is helpful to programmers.
+The chunk retrieval techniques we compare in this thesis can be used to fill similar structured representations with information from build logs.
+As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, the main influence factor on the structure of a build log.
 
-We strive to enable a similar summarization by text retrieval while also covering a wider array of programming languages.
+Amar et al.~\cite{amar2019mining} compare different approaches to reduce the portions of a log to be inspected by a developer.
+The techniques remove lines that appear both in passing and failing build logs and use a modified term frequency inverse document frequency weighting to identify term vectors likely to occur with failures.
+They use the term vectors and cosine similarity to further filter the log portions only present in failing build logs.
+Their diff technique can be interpreted as a chunk retrieval technique, the targeted information is defined by the past failures used as basis for the weighted term vectors.
 
-Amar et al.~\cite{amar2019mining}  compare different approaches to reduce the portions of a log to be inspected by the engineer.
-The techniques remove lines that appear both in passing and failing build logs and use a modified Term Frequency Inverse Document Frequency weighting to identify term vectors likely to occur with failures.
-They use the term vectors and cosine similarity to further filter the log portions only present in failing build logs.
-Their diff technique can be interpreted as a chunk retrieval technique, though the user can not specify an information to target.
-The information retrieved is always difference to what was before \todo{wait not quite the past failures (environmental in that case) specify the information!}
-They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the erro.
-In contrast to that, our tool ALBE extracts specific parts of the build logs.
-As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
+Travis already provides a basic structuring of build logs within their log viewer using \emph{log folds}~\cite{travis2019logfolds}.
+They add fold identifiers around common commands and setup or teardown build phases and collapse the contained lines by default.
 
-\section{System Log Analysis} \todo{parsing?}
+\section{System Log Analysis}
 
@@
 
-The techniques developer for system logs can also be applied to build logs.
-One example is comparing execution traces to reference traces of intended behaviour to detect anomalies.
+The techniques developed for system log analysis can also be applied to build logs.
+One example is comparing execution traces to reference traces of intended behavior to detect anomalies.
 Amar et al.~\cite{amar2019mining} employed a similar approach to detect relevant lines in build logs.
@@
 Classic log parsers interpret the whole log file into a sequence of events.
-A similar approach could also be applied to build logs to determine the sequence of executed buidl steps or phases.
-In this thesis we focus on extracting a single speficied information from the build log as a whole with chunk retrieval techniques.
-Chunk retrieval technques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g. through regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
+In this thesis we taka a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
+Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g. through regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
 
@@
 
-The process of automatically selecting unstructured documents related to a given \emph{search query} is called \emph{Information Retrieval}~\cite{schutze2008introduction}.
-For this, algorithms try to determine the general topic or conceptual information of the document.
+The chunk retrieval techniques we compare in this thesis use different techniques from the fields of information extraction and retrieval.
+This section presents existing approaches to extract structured information from semi-structured data and how these approaches differ from chunk retrieval.
+Further we illustrate how information retrieval techniques, basis for our chunk retrieval technique CTS, are used in software engineering research.
+
+\paragraph{Information Extraction from Semi-Structured Documents}
+\emph{Information extraction} techniques aim at structuring unstructured information to support subsequent processing.
+
+The PADS project~\cite{fisher2011the-pads} is centered around declaring grammars for the information contained in semi-structured documents.
+Based on this declarative data description various tools are generated like format converters, e.g. to XML, data adaptors to other tools, statistical analyzers and visualizers.
+Manually defined PADS grammars eliminate the need to develop a custom data extraction parser.
+Xi and Walker developed ANNE~\cite{xi2010a-context-free}, which can infer context-free PADS grammars from a small number of user annotations and the raw document data.
+Fisher et al.~\cite{fisher2008from} fully automated the generation of PADS grammars.
+They split the data into chunks, lines or documents, and further into tokens.
+Parentheses are used to infer hierarchical structure information.
+The system guesses grammar operators unifying single tokens or subexpressions, scores the resulting grammars and applies appropriate rewrite rules to refine the candidate grammars.
+
+The IEPAD tool created by Chang et al.~\cite{chang2003automatic} automatically identifies data extraction patterns in semi-structured web pages, without requiring user-labeled training examples.
+They split the semi-structured documents into tokens, discover repetitive patterns using occurrence-counting suffix trees and select the most regular and compact patterns to define extraction.
+
+Dan Smith and Mauricio Lopez~\cite{smith1997information} extract structured information from sets of semi-structured documents that contain similar information but are structured differently.
+The user provides rules of each piece of information, detailing in which section of the document it might be present.
+Identifying keywords and regular expressions determine whether the information is present and where it starts and ends.
+
+These information extraction approaches support parsing and structuring of entire files.
+We investigate chunk retrieval techniques which do not aim at inferring the whole structure of a build log.
+Instead, chunk retrieval focuses on extracting one specific information characterized by the user.
+
+\paragraph{Information Retrieval in Software Engineering Research}
+The process of automatically selecting unstructured documents related to a given \emph{search query} is called \emph{information retrieval}~\cite{schutze2008introduction}.
+
+In information retrieval, algorithms try to determine the general topic or conceptual information of the document.
 Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix and weighing the terms with tf-idf~\cite{lee1997document}.
@@
 Panichella et al.~\cite{panichella2016parameterizing} and Runeson et al.~\cite{runeson2007detection} apply similar information retrieval techniques to detect duplicated bug reports.
+Salton et al.~\cite{salton1993approaches} retrieve text parts relevant for a given user query by calculating global document similarity scores and refining the output through local passage similarity.
+They also calculate similarity with term vectors.
 
-Salton et al.~\cite{salton1993approaches} retrieve text parts relevant for a given user query by calcluating global document similarity scores and refining the output through local passage similarity.
-Similarity is also calculated using term vectors.
-
-\emph{Information Extraction} techniques aim to automatically structure unstructured information to support subsequent processing.
-The IEPAD tool created by Chang et al.~\cite{chang2003automatic} automatically identifies data extraction patterns in semi-structured web pages, without requiring user-labeled training examples.
-They split the semi-structured documents into tokens, discover repetitive patterns using occurrence-counting suffix trees and select the most regular and compact patterns to define extraction.
-
-\todo{regex generation}
-Bartoli et al.~\cite{bartoli2012automatic} leverage genetic programming to generate regular expressions based on user examples.
-Their approach also reprensents the regular expressions in a tree structure and mutates them to maximize extraction accuracy on the provided examples while minimizing the length of the regular expression.
-Their evaluation shows that their algorithm is on average faster and more accurate than humans~\cite{bartoli2016on-the-automatic}.
-
-The WHISK system by Stephen Soderland~\cite{soderland1999learning} learns text extraction regular expressions for semi-structured text.
-The system interleaves the learning process with the example annotation and reduces the number of required examples by presenting examples that eliminate ambiguities between learning candidates.
-
-Dan Smith and Mauricio Lopez~\cite{smith1997information} extract structured information from sets of semi-structured documents that contain similar information but are strucutured differently.
-The user provides rules of each piece of information, detailing in which section of the document it might be present.
-Identifying keywords and regular expressions determine whether the information is present and where it starts and ends.
-
-The PADS project~\cite{fisher2011the-pads} is centered around declaring grammars for the information contained in semi-structured documents.
-Based on this declarative data description various tools are generated like format converters, e.g. to XML, data adaptors to other tools, statistical analyzers and visualizers.
-Manually defined PADS grammars eliminate the need to develop a custom data extraction parser.
-Xi and Walker developed ANNE~\cite{xi2010a-context-free}, which can infer context-free PADS grammars from a small number of user annotations and the raw document data.
-Fisher et al.~\cite{fisher2008from} fully automated the grammar generation.
-They split the data into chunks, lines or documents, and further into tokens.
-Parentheses are used to infer hierarchical structure information.
-The system guesses grammar operators unifying single tokens or subexpressions, scores the resulting grammars and applys appropriate rewrite rules to refine the candidate grammars.
-
-The presented information extraction approaches support parsing and structuring of entire files, while we investigate chunk retrieval techniques which do not aim at inferring the whole structure of a build log.
-Instead focus on extracting one specific information characterized by a user.
+Our chunk retrieval technique CTS uses the same approach of term vectors to identify which lines to extract from a log file.
 
@@
 The user provides examples for the input and the corresponding output and a synthesis algorithm tries to create the program intended by the user.
-This section introduces the theoretical foundations of the program synthesis algorithm implemented in the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-It presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our PBE chunk retrieval technique.
-Further, this section covers further applications and extensions of the PROSE program synthesis.
+This section introduces the theoretical foundations of the program synthesis algorithm of the \emph{Program Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
+The PROSE framework is developed by Microsoft Research.
+The section next presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
+Further, we cover additional applications and extensions of the PROSE program synthesis and alternative research on generating regular expressions from examples.
 
@@
 FlashMeta separates the inductive synthesis algorithm from the domain specific capabilities of the desired program, by encoding the possible program space in a domain specific language (DSL).
-The user specifies their intent by providing in / output examples (I/O examples).
+The user specifies the desired program behavior by providing in / output examples (I/O examples).
 FlashMeta uses \emph{witness functions}, provided by the DSL, to divide the synthesis into smaller subtasks.
 For each of these subtasks it enumerates all possible programs that solve the subtask consistent with the set of I/O examples.
-A program is consistent with a set of I/O examples if it produces the corresponding output for each input example~\cite{mitchell1982generalization}.
-The subprograms are stored in a \emph{version space algebra} (VSA)~\cite{mitchell1982generalization}, which efficiently saves candidate programs for tasks by sharing common subexpressions.
-The enumerated programs are ranked according to which ones the user most likely intended.
-The ranking characteristics are also provided by the DSL.
+A program is consistent with a set of I/O examples if, for each input example, it produces the corresponding output~\cite{mitchell1982generalization}.
+The possible subprograms are joined and stored in a \emph{version space algebra} (VSA)~\cite{mitchell1982generalization}.
+This a tree structure, which space-efficiently saves candidate programs for tasks by sharing common subexpressions.
+Next, FlashMeta ranks the enumerated programs according to which ones the user most likely intended.
+The DSL also provides the ranking characteristics.
 From the ranked VSA, FlashMeta can then return a ranked list of complete programs consistent with the users example.
 
-In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples not to be processed by the synthesized program.
+In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples.
+Negative input examples should not to be processed by the synthesized program.
 
-The different applications of PROSE presented in the following paragraphs are all implemented as DSLs for the FlashMeta synthesis algorithm.
+The different applications of PROSE presented in the following paragraphs were all eventually implemented as DSLs for the FlashMeta synthesis algorithm.
 
 \paragraph{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as DSL for the Microsoft PROSE framework.
-Its instantiation for text specifies text extraction programs from semi-structured text based on regular expressions.
-The authors also provide instantiations to extract data from webpages and spreadsheets.
+Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL for the Microsoft PROSE framework.
+It enables a user to define text extraction programs for text, websites and spreadsheets by giving I/O examples.
+FlashExtract's instantiation for text synthesizes text extraction programs from semi-structured text based on regular expressions.
 Users can extract multiple fields and structure them with hierarchy and sequence.
@@
 
-Microsoft's system log analysis tool Azure Monitor lets users define custom log fields using the FlashExtract~\cite{azure2019custom}.
-The ConvertFrom-String function in PowerShell allows a user to specify a example template for extracting hierarchical data from a text document~\cite{powershell2019convert}.
+Apart from automatic completion in Excel spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for two other Microsoft product features:
+Microsoft's system log analysis tool Azure Monitor lets users define custom log fields~\cite{azure2019custom}.
+The ConvertFrom-String function in PowerShell allows a user to specify an example template to extract hierarchical data from a text document~\cite{powershell2019convert}.
 
@@
 \paragraph{Other Applications of Program Synthesis by Example}
+Gulwani and Harris apply a less generic predecessor of the FlashMeta framework to string manipulation within spreadsheets~\cite{gulwani2011automating} and spreadsheet transformations~\cite{harris2011spreadsheet}.
+
 Rolim et al.~\cite{rolim2017learning} use code edits as examples to learn automatic program transformations.
@@
 The synthesized transformations proposes fixes for student assignments based on corrections from other students and to automates repetitive refactoring tasks.
-
-In 2011 Gulwani and Harris applied a less generic predecessor of the FlashMeta framework to string manipulation within spreadsheets~\cite{gulwani2011automating} and spreadsheet transformations~\cite{harris2011spreadsheet}.
 
@@
 In a program synthesis shorter and simpler program often receive a better ranking.
-Ellis and Gulwani~\cite{ellis2017learning} improved the accuracy of the PROSE program learner even further by also taking into account the execution traces of the program candidates.
+Ellis and Gulwani~\cite{ellis2017learning} improve the accuracy of the PROSE program learner even further by also taking the execution traces of the program candidates into account.
 For example, a program that extracts overlapping substrings is ranked lower than a program without overlapping extractions.
-They also weigh the produced output of applying a program to input only examples and prefer programs which produces output structurally similar to the provided output examples.
+They also weigh the produced output of applying a program to input only examples and prefer programs which produces output structurally similar to provided output examples.
 
@@
 
+\paragraph{Further Approaches to Regular Expression Generation from Examples}
+Bartoli et al.~\cite{bartoli2012automatic} leverage genetic programming to generate regular expressions based on user examples.
+Their approach also represents the regular expressions in a tree structure and mutates them to maximize extraction accuracy on the provided examples while minimizing the length of the regular expression.
+Their evaluation shows that their algorithm is on average faster and more accurate than humans~\cite{bartoli2016on-the-automatic}.
+The WHISK system by Stephen Soderland~\cite{soderland1999learning} learns text extraction regular expressions for semi-structured text.
+The system interleaves the learning process with the example annotation and reduces the number of required examples by presenting examples that eliminate ambiguities between learning candidates.
+
 \end{document}

### 2019-11-18 thesis/txt/2-models.tex
rework rw section, incorporate Taico's feedback on techniques section

@@
 \label{sec:techniques}
-This chapter presents how a build log is created by a continuous integration (CI) build.
-It explains our notion of retrievable information contained in build logs.
-We introduce our notion of chunk retrieval techniques to retrieve information from build logs and present the three chunk retrieval techniques we investigate for this thesis:
+This chapter introduces the concept of chunk retrieval techniques.
+We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
+This chapter first presents how a build log, the input to our chunk retrieval, is created by a continuous integration (CI) build.
+Next, it describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
+We illustrate why it is useful to extract the presented information chunks.
+The following section introduces our concept of chunk retrieval techniques, which retrieve information chunks from build logs.
+We present the three chunk retrieval techniques we investigate for this thesis:
 Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
@@
 The idea of CI is to catch errors early, by integrating new software changes fast and often~\cite{humble2010continuous}.
-Companies often link a specific CI server, e.g.\ Travis CI, to their source code repository.
+Companies link a CI server, e.g.\ Travis CI, to their source code repository.
 After making a change, the developer commits and pushes the new version of the code to the repository.
@@
 
-A CI build typically runs through these stages:
+A CI build typically runs through the following stages:
 \begin{itemize}
@@
 They communicate progress updates, error and warning messages to the user~\cite{yuan2012characterizing}.
-We refer to to the concatenation of this output as build log.
+We refer to to the concatenation of this output as \emph{build log}.
 The structure of their output is chosen by every tool themselves.
@@
 
-When analyzing build logs we might not have access to the exact build configuration, describing which tools are used in which order, or might not have access to a useable definition of the output structure of a specific tool.
-Therefore build logs are semi-structured, as described in Section~\ref{sec:rw-semi-structured-data}.
+When analyzing build logs we do not necessarily have access to the exact build configuration, describing which tools are used in which order.
+We also do not necessarily have access to a useable definition of the output structure of a specific tool.
+Therefore, build logs are semi-structured, as described in Section~\ref{sec:rw-semi-structured-data}.
 
@@
 CI build logs contain a great amount of information about the CI build they correspond to.
-In this section, we describe our notion of a information retrievable from a CI build log.
-We present examples of information contained in Travis CI build logs and illustrate use cases for a developer or researcher to retrieve them.
+This section defines our concept of information retrievable from a CI build log.
+We use the introduced terms throughout the following sections and chapters to talk about the characteristics of chunk retrieval techniques.
+To illustrate why chunk retrieval from build logs is useful, we present examples of information contained in Travis CI build logs and describe use cases for developers and researchers to retrieve them.
 
@@
 \emph{Possibly}, because a BLI is not necessarily present in every build log.
-If it is present, we call it a \emph{BuildLogInformation instantiation} (BLII), which always relates to a specific build log, the one this instantiation is appearing in.
+If it is present, we call it a \emph{BuildLogInformation instantiation} (BLII).
+A BLII is always contained in a specific build log.
 Figure~\ref{fig:build-overview} presents the relation between a BLI and other entities involved in a CI build.
 
-Each BLII for us has a \emph{textual representation} within the build log.
+Each BLII has a \emph{textual representation} within the build log.
 This textual representation is always a substring of the log text.
-BLIs can be hierarchically ordered by their textual representations containing each other.
-As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section~\ref{sec:rw-semi-structured-data}, this section only presents hierarchical ordering or containment for BLIs whose structure we definitely know.
+BLIs can be hierarchically ordered, determined by how their textual representations contain each other.
+As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section~\ref{sec:rw-semi-structured-data}, this section only presents hierarchical containment for BLIs whose structure we definitely know.
 Most BLI types can appear in various hierarchical arrangements and are therefore not contained in any other type in our explanation.
@@
 During our initial exploration and log data collection for the \emph{LogChunks} data set, we collected a broad set of build logs from 29 languages and 87 repositories from Travis CI~\cite{travisci2019webpage}.
-We inspected them to get an impression about the information one would want to retrieve from a build log.
-In the following, we describe the possibly interesting information types to be retrieved from Travis CI build logs.
+We inspected them to get an impression of the information one would want to retrieve from a build log.
+In the following, we describe information types which could be retrieved from Travis CI build logs.
 All BLIs containing ``Travis'' in their name are specific to Travis CI build logs, the others can also apply to build logs from another CI environment.
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/ir-technique.pdf}
-	\caption{Model for an Information Retrieval Technique}
-	\label{fig:model-ie-technique}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth, clip]{img/ir-technique.pdf}
+% 	\caption{Model for an Information Retrieval Technique}
+% 	\label{fig:model-ie-technique}
+% \end{figure}
 \section{Characteristics of Chunk Retrieval Techniques}
@@
 In the context of text extraction through regular expressions, Programming by Example relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
-We chose to investigate the applicability of generating regular expression programs by example to retrieving information chunks from build logs.
-In this work, we refer to our interpretation of Programming by Example as \emph{PBE}.
-In the following we will explain the concept of how we apply PBE to chunk retrieval from CI build logs, the concrete implementation is described in~\ref{sec:impl-pbe}.
+In this work, we refer to our interpretation of Programming by Example as \emph{PBE}\@.
+We investigate the suitability of PBE to retrieve information chunks from build logs.
+In the following, we explain the configuration and application of PBE to chunk retrieval from CI build logs.
+The concrete implementation is described in~\ref{sec:impl-pbe}.
 %Figure~\ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE\@.
@@
 The \emph{output} is always a substring of the log file text, representing the substring that should be retrieved by the synthesized program when given the corresponding input file.
-One or multiple I/O examples configure a chunk retrieval with PBE, they define the substring of a build log that should be extracted.
+One or multiple I/O examples configure a chunk retrieval with PBE: they define the substring of a build log that should be extracted.
 The PROSE program synthesis then tries to construct a regular expression program consistent with all configuring I/O examples.
@@
 \label{sec:expl-ts}
-Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-One common and simple technique the Vector Space Model~\cite{schutze2008introduction}.
+Text Similarity approaches are used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+One common and simple technique is the Vector Space Model~\cite{schutze2008introduction}.
 We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
@@
 \paragraph{Configuration}
-To configure a chunk retrieval though text similarity we chose to use the same concept of I/O examples as for PBE\@.
+To configure chunk retrieval though text similarity we chose to use the same concept of I/O examples as for PBE\@.
 The lines of the output strings of the configuring I/O examples define our search query.
@@
 Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
-Next, the algorithm applies term-frequency inverse document frequency to the matrix, a best practice for natural language queries~\cite{lee1997document}.
+Next, the algorithm applies term frequency inverse document frequency to the matrix, a best practice for natural language queries~\cite{lee1997document}.
 
@@
 \label{sec:expl-skws}
-When developers are looking for a specific piece of information within a great amount of unstructured information, they search for related keywords as a first ad-hoc approach.
+When developers are looking for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is searching for related keywords.
 This was one of the most common approaches we took when searching for the build failure reason within a log when creating our \emph{LogChunks} data set.
-As this is a technique readily available in many tools developers use to view build logs, we want to study when such a keyword search is recommendable for retrieving information chunks from CI build logs.
-In the following we will explain how we use simple keyword search to retrieve information from CI build logs (KWS), the concrete implementation is described in~\ref{sec:impl-skws}.
+As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is recommendable for retrieving information chunks from CI build logs.
+In the following we will explain how we use simple keyword search to retrieve information from CI build logs (KWS).
+The concrete implementation is described in~\ref{sec:impl-skws}.
 %Figure~\ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.
@@
 For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the configuring keywords.
-As keywords are often not directly describing the desired information but rather next to the desired information, this technique retrieves the lines around not only retrieves the line with the keyword but also the lines around it.
+As keywords are often not directly describing the desired information, but rather appear close to the desired information, KWS also retrieves the lines around the found keyword.
 The number of surrounding lines retrieved is the average of lines in the output of the configuring I/O examples.
@@
 \paragraph{Log Diff}
-Amar et al.\ use a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
-The configuration for the technique is the log from the last successful build.
-This technique retrieves all lines from a build log that are not present in the configuring build log.
+Amar et al.\ use a technique based on line diffs and information retrieval to identify relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
+The configuration for the technique is the log from the last successful build and relevant past failures.
+This technique retrieves the lines from a build log that are not present in the successful build log and contain terms related to the given past failures.
 %Figure~\ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.

### 2019-11-20 thesis/txt/1-related-work.tex
rework TOC with latest Feedback from Moritz, replace log screenshots

@@
 
-\chapter{Background}
-\plan{whole RW currently highly work in progress, text not yet coherent!}
-\plan{all of RW: 4 - 5 pages left to do + some research!}
-\plan{write, 1/3 page, blocked by: other sections}
+\chapter{Background and Related Work}
 \label{sec:rw}
 This section presents various research works adjacent or foundational to our work.
-Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation.
-We differentiate our work from the more common system log analysis and show how we classify build logs as semi-structured data.
-We cover different information retrieval and extraction techniques \todo{half sentence missing: specify which techniques? 'used in software reasearch' 'used to assist software engineers'}.
-Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.
-\todo{do we also mention more things?}
+To start, we describe studies about continuous integration (CI) and how they gather information about CI usage in software projects.
+Next, the section moves on to works about build log analysis and their augmentation, which are related to the techniques we analyze in this thesis.
+We differentiate our work from system log analysis and show how we classify build logs as semi-structured data.
+The section describes how chunk retrieval can be employed as a part of presented information extraction approaches.
+We introduce how information retrieval techniques, the basis for CTS, are used to improve software development.
+Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library, the foundation of PBE\@.
 % moritz: nice formulation :)
 
-\section{Continuous Integration}
+\section{Continuous Integration and Build Logs}
+\subsection{Continuous Integration}
 This section starts with an overview on research into why CI is used and its impact on development.
-It presents analyses on why CI builds fail and how testing and static anlysis tools are used within CI.
+It presents analyses on why CI builds fail and how testing and static analysis tools are used within CI\@.
 We explain how researchers compose data sets for their work on CI and how chunk retrieval techniques can support them.
 
-\paragraph{Motivation for CI and impact of CI}
+\paragraph{Motivation for CI and Impact of CI}
 Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
 Developers use CI to ensure consistency and quality across different execution environments and increase confidence into the code they deploy.
-Hilton et al.~\cite{hilton2016usage} also analyze how and why open source projects use CI.
+Hilton et al.~\cite{hilton2016usage} also analyze how and why open source projects use CI\@.
 They observe CI usage in a broad range of projects, it supports them to catch bugs earlier and have more confidence in a successful build and shorten release cycles.
-Stahl and Bosch~\cite{staahl2014modeling} provide a hollistic review of literature on automatic build environments in industry projects.
+Stahl and Bosch~\cite{staahl2014modeling} provide a holistic review of literature on automatic build environments in industry projects.
 They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
@@
 
-\paragraph{Data Sets powering CI Research}
+\paragraph{Data Sets Powering CI Research}
 The works presented in this section are based on either developer surveys or data sets, containing build metadata or build logs.
 Seo et al..~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
-Beller et al. created the \emph{TravisTorrent} data set~\cite{beller2017travistorrent} providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
+Beller et al.\ created the \emph{TravisTorrent} data set~\cite{beller2017travistorrent} providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
 TravisTorrent was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
@@
 
-\section{Build Log Analysis and Augmentation - Related Work}
+\subsection{Augmentation of Build Logs}
 \label{sec:rw-bl-analysis}
@@
 
-\section{System Log Analysis}
-
-A related field of log processing is the processing of system log files produced during runtime.
-A main difference in system logs is that they are fundamentally structured through events.
-Each line in the log file represents one event.
-The first goal in parsing system log files is to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
-Next the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
-The output of a log parser is a structured log, composed of a list of timed events and the corresponding parameter values~\cite{he2016evaluation}.
-This structured log is then the input to various machine learning and data mining processes.
-They mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
-Xu et al.~\cite{xu2009detecting} leveraged the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied to build logs.
-One example is comparing execution traces to reference traces of intended behavior to detect anomalies.
-Amar et al.~\cite{amar2019mining} employed a similar approach to detect relevant lines in build logs.
-
-Classic log parsers interpret the whole log file into a sequence of events.
-A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
-In this thesis we taka a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
-Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g. through regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\section{Semi-Structured Data}
+\subsection{Build Logs as Semi-Structured Data}
 \label{sec:rw-semi-structured-data}
@@
 
-\section{Information Extraction and Retrieval Techniques}
+\subsection{System Log Analysis}
+\label{sec:log-analysis}
+A related field of log processing is the processing of system log files produced during runtime.
+A main difference in system logs is that they are fundamentally structured through events.
+Each line in the log file represents one event.
+The first goal in parsing system log files is to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
+Next the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
+The output of a log parser is a structured log, composed of a list of timed events and the corresponding parameter values~\cite{he2016evaluation}.
+This structured log is then the input to various machine learning and data mining processes.
+They mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
+Xu et al.~\cite{xu2009detecting} leveraged the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
+
+The techniques developed for system log analysis can also be applied to build logs.
+One example is comparing execution traces to reference traces of intended behavior to detect anomalies.
+Amar et al.~\cite{amar2019mining} employed a similar approach to detect relevant lines in build logs.
+
+Classic log parsers interpret the whole log file into a sequence of events.
+A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
+In this thesis we taka a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
+Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ through regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+
+\section{Foundational Techniques}
+% \section{Information Extraction and Retrieval Techniques}
 
@@
 
-\paragraph{Information Extraction from Semi-Structured Documents}
+\subsection{Information Extraction} %from Semi-Structured Documents
 \emph{Information extraction} techniques aim at structuring unstructured information to support subsequent processing.
@@
 The PADS project~\cite{fisher2011the-pads} is centered around declaring grammars for the information contained in semi-structured documents.
-Based on this declarative data description various tools are generated like format converters, e.g. to XML, data adaptors to other tools, statistical analyzers and visualizers.
+Based on this declarative data description various tools are generated like format converters, e.g.\ to XML, data adaptors to other tools, statistical analyzers and visualizers.
 Manually defined PADS grammars eliminate the need to develop a custom data extraction parser.
-Xi and Walker developed ANNE~\cite{xi2010a-context-free}, which can infer context-free PADS grammars from a small number of user annotations and the raw document data.
+Xi and Walker developed ANNE~\cite{xi2010a-context-free}, which can infer context-free PADS grammars from a few user annotations and the raw document data.
 Fisher et al.~\cite{fisher2008from} fully automated the generation of PADS grammars.
@@
 
-\paragraph{Information Retrieval in Software Engineering Research}
+\subsection{Information Retrieval}% in Software Engineering Research
 The process of automatically selecting unstructured documents related to a given \emph{search query} is called \emph{information retrieval}~\cite{schutze2008introduction}.
@@
 
-\section{Program Synthesis by Example}
+\subsection{Program Synthesis by Example}
 \label{sec:rw-prose}
@@
 For the PROSE framework, Mayer et al.~\cite{mayer2015user} compare two approaches for disambiguation by the user.
-With their first approach, the user can browse lower ranked program candidates in a tree like natural language transformation of the constructed VSA.
+With their first approach, the user can browse lower ranked program candidates in a tree like natural language transformation of the constructed VSA\@.
 The second approach actively asks the user to resolve ambiguous output possibilities for input only examples.

### 2019-11-20 thesis/txt/2-models.tex
rework TOC with latest Feedback from Moritz, replace log screenshots

@@
 
-\chapter{Introduction to Chunk Retrieval Techniques}
+\chapter{Chunk Retrieval Techniques for Build Logs}
 \label{sec:techniques}
@@
 
-	\item \textbf{ExitCode} Travis CI prints all exit codes of commands.
+	\item \textbf{TravisExitCode} Travis CI prints all exit codes of commands.
 				A researcher can retrieve this information to fill an overview of the build steps and why they failed.
-	      Figure~\ref{fig:log-3} shows an example of an ExitCode instantiation within a build log.
+	      Figure~\ref{fig:log-3} shows an example of an TravisExitCode instantiation within a build log.
 
@@
 	\centering
-	\includegraphics[width=\textwidth, clip]{img/log0.png}
-	\caption{Excerpt from a build log showing textual representations of a long TravisWorker instantiation and a TravisSystemInfo instantiation}
+	\includegraphics[width=\textwidth, clip]{img/log02.png}
+	\caption{Excerpt from a build log showing textual representations of a long TravisWorker instantiation and a TravisSystemInfo}
 	\label{fig:log-0}
@@
 	\centering
-	\includegraphics[width=\textwidth, clip]{img/log1.png}
-	\caption{Excerpt from a build log showing textual representations of a TravisTiming instantiation and a TravisPhase, containing the TravisPhaseName and the TravisPhaseOutput}
+	\includegraphics[width=\textwidth, clip]{img/log12.png}
+	\caption{Excerpt from a build log showing textual representations of a TravisTiming and a TravisPhase, containing the TravisPhaseName and the TravisPhaseOutput}
 	\label{fig:log-1}
@@
 	\centering
-	\includegraphics[width=\textwidth, clip]{img/log2.png}
-	\caption{Excerpt from a build log showing textual representations of a short TravisWorker instantiation}
+	\includegraphics[width=\textwidth, clip]{img/log22.png}
+	\caption{Excerpt from a build log showing the textual representation of a short TravisWorker}
 	\label{fig:log-2}
@@
 	\centering
-	\includegraphics[width=\textwidth, clip]{img/log3.png}
-	\caption{Excerpt from a build log showing textual representations of ErrorMessage, ExitCode and TravisTriggeringCommand instantiations}
+	\includegraphics[width=\textwidth, clip]{img/log32.png}
+	\caption{Excerpt from a build log showing textual representations of an ErrorMessage, an ExitCode and a TravisTriggeringCommand}
 	\label{fig:log-3}
@@
 	\centering
-	\includegraphics[width=\textwidth, clip]{img/log4.png}
-	\caption{Excerpt from a build log showing textual representations of WarningMessage instantiations}
+	\includegraphics[width=\textwidth, clip]{img/log42.png}
+	\caption{Excerpt from a build log showing the textual representation of a WarningMessage}
 	\label{fig:log-4}
@@
 	\centering
-	\includegraphics[width=\textwidth, clip]{img/log5.png}
-	\caption{Excerpt from a build log showing textual representations of WarningMessage instantiations}
+	\includegraphics[width=\textwidth, clip]{img/log52.png}
+	\caption{Excerpt from a build log showing the textual representation of another WarningMessage}
 	\label{fig:log-5}
@@
 \label{sec:expl-rlr}
-Apart from the three techniques we investigate, there are further build log analysis techniques mentioned in literature and used in industry.
+There are further build log analysis techniques mentioned in literature and used in industry.
 This section shows how they are described with our notion of chunk retrieval techniques.

### 2019-11-20 thesis/txt/3-data-set.tex
rework TOC with latest Feedback from Moritz, replace log screenshots

@@
 \chapter{LogChunks Data Set}
+\label{sec:data-set}
 \includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
 
-\label{sec:data-set}
-\section{Motivation}
 originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how structured or unstructured they are.
@@
 
-\subsection{Repository Sampling}
+\paragraph{Repository Sampling}
 Our first task was to determine a set of repositories to query logs from.
@@
 
-\subsection{Build Sampling}
+\paragraph{Build Sampling}
 The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, to obtain the newest builds for a given repository.
@@
 \begin{itemize}
-	\item \todo{fill /5 mins/}
+	\item \todo{fill /5 mins/}~\cite{travis2009buildstatus}
 \end{itemize}
@@
 
-\subsection{Log Sampling}
+\paragraph{Log Sampling}
 For each build the \texttt{TravisRequester} then selects a log to download.
@@
 
-\section{Data Structure}
+\section{Data Schema}
 For our study, described in Chapter~\ref{sec:study}, we want to investigate the retrieval capabilities of three techniques.
@@
 
-\section{Labeling}
-\subsection*{Output Examples: Build Failure Reason}
+\section{Labeling Process}
+\paragraph{Output Examples: Build Failure Reason}
 We labeled the first occuring substring describing the failure.
@@
 
-\subsection{Inter-Rater Reliability}
+\subsection{Inter-Rater Reliability Study}
 re-labeling of parts of the labels - cohen's kappa
@@
 For each label category: Build Failure Reason, keywords and category, we relabeled 30 randomly sampled logs.
-compared the labeles, \todo{discussed about it}.
+compared the labels, \todo{discussed about it}.
 \subsubsection{Results}

### 2019-11-20 thesis/txt/5-study.tex
rework TOC with latest Feedback from Moritz, replace log screenshots

@@
 
-\chapter{Empirical Comparison Study}
+\chapter{Empirical Comparison}
 \label{sec:study}
@@
 
-\subsection{Comparing All Techniques}
+\subsection{Comparison of All Techniques}
 Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval of the different techniques in our study.

### 2019-11-21 thesis/txt/0-introduction.tex
correct introduction a bit, introduction version to send to prof. pretschner, update plots

@@
 There are different techniques to retrieve information from CI build logs. Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
-Such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
+Such regular expressions are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
 Vassallo et al.\ wrote a custom parser for build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
@@
 
-The goal of this thesis is to investigate different chunk retrieval techniques (CR techniques) for build logs and describe under which circumstances each techniques is recommended over another.
-We aim to define a model to characterize different CR techniques, as well as the information retrievable from CI build logs.
-For \textbf{RQ1}, we analyze which criteria influence the suitability of a CR technique for CI build logs.
+The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances each techniques is recommended over another.
+We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
+For \textbf{RQ1}, we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
 We implement and evaluate three chunk retrieval techniques:
@@
 \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
+how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
 % \begin{simplebox}{Research Questions}
@@
 To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
-Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.
+Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
 
@@
 \begin{itemize}
-  \item PBE yields very accurate results when configured with 1 to 3 examples from a single structural category.
+  \item PBE yields very accurate results when trained with 1 to 3 examples from a single structural category.
   \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
-  A small increase in the number of examples used in the configuration has no visible influence and fewer structural categories improve the retrieval accuracy.
-  \item KWS has the highest recall of all techniques combined with much lower recall.
-  It is the only technique where retrieval quality does not decrease with an increasing number of structural categories in the configuring examples.
+  A small increase in the number of training examples has no visible influence.
+  Fewer structural categories improve the retrieval accuracy.
+  \item KWS has the highest recall of all techniques combined with much lower precision.
+  It is the only technique where retrieval accuracy does not decrease with an increasing number of structural categories in the training examples.
 \end{itemize}
-We recommend PBE for use cases where the desired information is always represented in the same structurally predictable way and high confidence in the exactness of the chunk retrieval is required.
+We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in the accuracy of the chunk retrieval is required.
 CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
@@
           \item a common information retrieval approach using text similarity (CTS), and
-          \item a keyword search approach (KWS)
+          \item a keyword search approach (KWS).
         \end{itemize}
@@
           \item the substring of the log describing the reason the build failed,
-          \item keywords developers would use to search for these descriptions of the build failure reason, and
-          \item a categorization of the retrievals according to their structural position within the build log.
+          \item keywords developers would use to search for these substrings, and
+          \item a categorization of the substrings according to their structural representation within the build log.
         \end{itemize}
@@
 This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
-Chapter~\ref{sec:rw} presents existing work on information extraction and retrieval techniques and program synthesis from examples.
+Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques and program synthesis from examples.
 Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
@@
 Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
-This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}.
+This tool is also used for the comparison described in Chapter~\ref{sec:study}.
 Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
-Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
+Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.\\\\
+
+Following you find selected graphs from the study results section. RLR stands for the baseline technique \emph{Random Line Retrieval}:
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
+		\caption{Success of chunk retrievals for all techniques}
+		\label{fig:success-partial-all}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
+		\caption{Precision and Recall of all techniques compared when training examples are in \emph{one structural category}}
+		\label{fig:recall-precision-singlecategory-all}
+\end{figure}
+\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
+		\caption{Precision and Recall of all techniques compared when training examples are in \emph{multiple structural categories}}
+		\label{fig:recall-precision-multicategory-all}
+\end{figure}
+
 \end{document}

### 2019-11-21 thesis/txt/3-data-set.tex
correct introduction a bit, introduction version to send to prof. pretschner, update plots

@@
 \includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+This chapter describes the creation of the \emph{LogChunks} data set.
+\emph{LogChunks} encompasses about 800 build logs produced by a wide variety of programming languages.
+For each build log we manually labeled which substring describes why the build failed.
+Four our evaluation of the chunk retrieval techniques PBE, CTS and KWS we added search keywords and structural categories to each of the labeled substrings.
 
-originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how structured or unstructured they are.
-Then labeling of one build log information, namely the reason the build failed, as well as keywords and structural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results
+First, we present related data sets and show how \emph{LogChunks} differs.
+Second, this chapter describes our log collection process and details the data schema of \emph{LogChunks}.
+Further, it presents the labeling process and how we validated the obtained data points.
+In our first validation study, a second person also labeled a sample of the build logs.
+For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled actually describes the reason the build failed.
 
 \section{Related Data Sets}
-\todo{kind of related work for data set? the non system one moritz sent, travis torrent, check msr, new paper in rw / other rw parpers, more?}
+\paragraph{TravisTorrent}
 

### 2019-11-21 thesis/txt/5-study.tex
correct introduction a bit, introduction version to send to prof. pretschner, update plots

@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-TS.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
 		\caption{Precision and recall of chunk retrieval with CTS for increasing count of configuring I/O examples}
-		\label{fig:recall-precision-examplecount-TS}
+		\label{fig:recall-precision-examplecount-CTS}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-TS.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
 		\caption{Precision and recall of chunk retrieval with CTS for increasing number of categories present in the configuring I/O examples}
-		\label{fig:recall-precision-categorycount-TS}
+		\label{fig:recall-precision-categorycount-CTS}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-TS.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
 		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
-		\label{fig:contextsizefactor-precision-recall-TS}
+		\label{fig:contextsizefactor-precision-recall-CTS}
 	\end{minipage}\hfill
@@
 \subsection{Common Text Similarity (CTS)}
-Figure~\ref{fig:recall-precision-examplecount-TS} presents precision and recall of chunk retrieval using CTS for different numbers of configuring I/O examples.
+Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision and recall of chunk retrieval using CTS for different numbers of configuring I/O examples.
 The count of configuring I/O examples has no visible influence on recall and precision of the chunk retrieval with CTS\@.
 
-Figure~\ref{fig:recall-precision-categorycount-TS} shows the same measurements for different category counts in the configuring I/O examples.
+Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for different category counts in the configuring I/O examples.
 With increasing category count, precision and recall decrease.
@@
 
-Figure~\ref{fig:contextsizefactor-precision-recall-TS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS\@.
+Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS\@.
 The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-SKWS.pdf}
-		\caption{Precision and recall of chunk retrieval with SKWS for increasing count of configuring I/O examples}
-		\label{fig:recall-precision-examplecount-SKWS}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
+		\caption{Precision and recall of chunk retrieval with KWS for increasing count of configuring I/O examples}
+		\label{fig:recall-precision-examplecount-KWS}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-SKWS.pdf}
-		\caption{Precision and recall of chunk retrieval with SKWS for increasing number of categories present in the configuring I/O examples}
-		\label{fig:recall-precision-categorycount-SKWS}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
+		\caption{Precision and recall of chunk retrieval with KWS for increasing number of categories present in the configuring I/O examples}
+		\label{fig:recall-precision-categorycount-KWS}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-SKWS.pdf}
-		\caption{Precision and recall of chunk retrieval with SKWS compared to retrieval size factor}
-		\label{fig:contextsizefactor-precision-recall-SKWS}
+		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
+		\caption{Precision and recall of chunk retrieval with KWS compared to retrieval size factor}
+		\label{fig:contextsizefactor-precision-recall-KWS}
 	\end{minipage}\hfill
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-SKWS.pdf}
-		\caption{Ratio of lines retrieved with SKWS compared to retrieval size factor}
-		\label{fig:retrievalsizefactor-retrievalratio-SKWS}
+		\includegraphics[width=\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
+		\caption{Ratio of lines retrieved with KWS compared to retrieval size factor}
+		\label{fig:retrievalsizefactor-retrievalratio-KWS}
 	\end{minipage}
@@
 \subsection{Keyword Search (KWS)}
-Figure~\ref{fig:recall-precision-examplecount-SKWS} presents precision and recall of chunk retrieval using SKWS in our study for different numbers of configuring I/O examples.
+Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision and recall of chunk retrieval using KWS in our study for different numbers of configuring I/O examples.
 The recall jumps from 53\% to over 70\% for more than two configuring I/O examples, while the precision stays constant at around 16\%.
 
-Figure~\ref{fig:recall-precision-categorycount-SKWS} shows the same measurements for different category counts in the configuring I/O examples.
+Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for different category counts in the configuring I/O examples.
 There is no clear trend visible in precision and recall for an increasing amount of categories in the configuring I/O examples
 
-Figure~\ref{fig:contextsizefactor-precision-recall-SKWS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with KWS\@.
+Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with KWS\@.
 The precision ranges from 19\% when retrieving half expected number of lines to 10\% when 2.5 times the expected number of lines.
@@
 
-Figure~\ref{fig:retrievalsizefactor-retrievalratio-SKWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS\@.
+Figure~\ref{fig:retrievalsizefactor-retrievalratio-KWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS\@.
 When retrieving the mean number of lines in the configuring I/O examples, 15\% of the log lines are retrieved on average.
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for PBE, CTS, KWS and RLR}
+		\caption{Success of chunk retrievals for all techniques}
 		\label{fig:success-partial-all}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-all.pdf}
-		\caption{Precision and Recall of PBE, CTS, KWS and RLR compared}
+		\caption{Precision and Recall of all techniques compared}
 		\label{fig:recall-precision-all}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision and Recall of PBE, CTS, KWS and RLR compared when configuring I/O examples are from a single category}
+		\caption{Precision and Recall of all techniques compared when training examples are from 1 category}
 		\label{fig:recall-precision-singlecategory-all}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision and Recall of PBE, CTS, KWS and RLR compared when configuring I/O examples are from multiple categories}
+		\caption{Precision and Recall of all techniques compared when training examples are >1 categories}
 		\label{fig:recall-precision-multicategory-all}

### 2019-11-22 thesis/txt/3-data-set.tex
work on dataset section

@@
 
+\section{Motivation}
+% For our study, described in Chapter~\ref{sec:study}, we want to investigate the retrieval capabilities of three techniques.
+% Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}.
+% Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output.
+% Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples
+In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
+One example set always contains build log in/output examples from the same software repository or project and for one specific build log information.
+They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
+Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
+The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
+To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
+
 \section{Related Data Sets}
+
 \paragraph{TravisTorrent}
+The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI.
+It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc}, related data from GHTorrent~\cite{gousios2013ghtorrent}, the corresponding git repository and data obtained through analysis of the build logs.
+The data obtained through build logs contains the names of failing test cases, similar to the reason the build failed in \emph{LogChunks}.
+However, these values are obtained through a manually developed parser, which only supports specific Ruby test runners and Java Maven or JUnit logs.
+\emph{LogChunks} provides manually labeled data points on the description of the build failure reason for a much wider selection of programming languages.
+
+\paragraph{Travis CI Build Log Data Set}
+Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected a large amount of Travis CI build logs from 130 github repositories to analyze their use of the Checkstyle plugin.
+They selected Maven repsitories that included the Checkstyle plugin and also used Travis CI.
+Their data set only provides the plain build logs, whereas \emph{LogChunks} provides manually analyzed build logs from Travis CI.
 
 \section{Log Collection}
-To collect a broad range of build logs we built the \texttt{Log Collector} using ruby.
+In the following we describe how we select the repositories, builds and Logs for \emph{LogChunks}.
+To collect the build logs we built the  \texttt{GHTorrentParser},\texttt{LogCollector} and \texttt{TravisRequester} using Ruby.
 
 \paragraph{Repository Sampling}
-Our first task was to determine a set of repositories to query logs from.
-Our \texttt{GHTorrentParser} can query the GHTorrent~\cite{gousios2013ghtorrent} data set for the most popular languages on github and the most popular repositories for a given language.
-\emph{Popularity} in this case is defined as the number of watches.
-Our \texttt{TravisRequester} can then check for a given repository whether it uses Travis CI.
+First, we determine a set of repositories to query logs from.
+Our \texttt{GHTorrentParser} queries the \emph{GHTorrent}~\cite{gousios2013ghtorrent} data set for the most popular languages on GitHub~\cite{github2019website}.
+It then retrieves the most popular repositories for a given language.
+\emph{Popularity} is defined as the number of watches.
+The \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, can then check for a given repository whether it uses Travis CI.
+
+For \emph{LogChunks} we queried GHTorrent from 01/04/2018 for the three most popular repositories of each of the 30 most popular languages.
 
 \paragraph{Build Sampling}
-The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, to obtain the newest builds for a given repository.
-As most builds on Travis CI are successful \mention{citation needed} we use a stratified sampling approach: \texttt{TravisRequester} saves the found builds in logs in buckets according to their state.
-We encountered the following states during our data collection passes:
+The \texttt{LogCollector} uses the \texttt{TravisRequester} to obtain the newest builds for a given repository.
+Wwe use a stratified sampling approach: \texttt{TravisRequester} saves the obtained builds in buckets according to their status.
+We encountered the following statuses during our data collection:
 \begin{itemize}
-	\item \todo{fill /5 mins/}~\cite{travis2009buildstatus}
+	\item created
+	\item started
+	\item cancelled
+	\item passed
+	\item errored
+	\item failed
 \end{itemize}
-\texttt{TravisRequester} saves up to a configured number of builds per state and searches through a configured number of maximum checked builds.
+The user of \texttt{TravisRequester} configures how many builds should be checked and how many builds per status should be saved.
+
+To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to a 1000 builds per repository and kept ten for each status.
+We discarded all statuses except one, namely ``failed''~\cite{travis2009buildstatus}, to make the most use of Travis' existing categorization of build status.
+%Travis assigns the Status ``failed'' when the build faults in the central script phase.
+%``Errored'' is assigned when the build faults during the setup or teardown phase.
 
@@
 For each build the \texttt{TravisRequester} then selects a log to download.
-Logs in Travis CI are not directly attributed to \texttt{build}s, but to \texttt{job}s.
-A single build can consist of multiple jobs, e.g.\ building and executing tests in various different testing environments.
-\texttt{TravisRequester} therefore queries each build for a job, which has the same state.
+Travis CI attributes logs to \emph{jobs}.
+A single build can consist of multiple jobs, e.g.\ building the same code version and executing tests in various different testing environments.
 A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
-For the selected jobs, our tool then queries the Travis API V3 and obtains the respective build log.
+\texttt{TravisRequester} queries each build for the first job, which has the same state.
+For the selected jobs, the tool queries the Travis API V3 over HTTP to obtains the corresponding build log.
+
+We manually inspected the collected build logs and had to discard logs from three repositories.
+One had only one failed build, two others had empty build logs on Travis CI.
+In total we collected 798 \todo{check} logs from 80 repositories.
 
@@
 
-% TODO describe somewhere else
 % \section{Build Failure Reason}
@@
 \section{Data Schema}
-For our study, described in Chapter~\ref{sec:study}, we want to investigate the retrieval capabilities of three techniques.
-Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}.
-Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output.
-Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.
+For each repository, \emph{LogChunks} has a list of \emph{examples}.
+Each example consists of:
+\begin{itemize}
+	\item \textbf{Input:} the relative path to the input build log.
+	\item \textbf{BuildFailureReason:} the substring of the log describing the reason the build failed.
+	\item \textbf{Keywords:} keywords a developer would use to search for the BuildFailureReason.
+	\item \textbf{Category:} a categorization of the structural representation of the BuildFailureReason within the build log.
+				The category is relative to the other examples for the same repository.
+\end{itemize}
+Following, this section describes the BuildFailureReason, Keywords and Category in more detail.
+.
 
-\paragraph{Example Set}
-\label{sec:example-set}
-Our data set is organized in example sets.
+\paragraph{BuildFailureReason}
+The \emph{BuildFailureReason} is the substring of the build logs that describes why the build failed.
+This could be the failing test case, the description of a failed linter rule or a compiler error.
+The \emph{BuildFailureReason} is one continuous string cut from the build log.
+If there are multiple errors leading for the build to fail, the substring contains the first appearing continuous error descriptions.
+\emph{Continuous} means that no lines reporting of normal build behavior are interrupting the error descriptions.
+Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
+For a few logs we were unable to define the section detailing why the build failed, e.g. because this information was logged in another log file.
+In these instances the \emph{BuildFailureReason} contains the lines describing that the build failed.
+
+\paragraph{Keywords}
+The \emph{Keywords} contain a list of one to three keywords appearing within the \emph{BuildFailureReason} or in the area around it in the build log.
+We aim to select keywords a developer would use to search for the \emph{BuildFailureReason} when inspecting the build log.
+
+\paragraph{Category}
+For each repository, we assign \emph{structural categories} to the examples.
+The structural category compares how the \emph{BuildFailureReasons} are represented within the build logs.
+Build tools highlight their error messages with markings, e.g. starting each line with ``\texttt{ERROR}'', surrounding lines filled with special characters or additional empty log lines.
+Two examples fall into the same structural categories if they are surrounded by similar markings.
+For most cases, two BuildFailureReason examples which fall into one category are outputted either within the same build phase or by the same build tool.
+For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
+
+% \paragraph{Example Set}
+% \label{sec:example-set}
+% Our data set is organized in example sets.
 One example set always contains build log in/output examples from the same software repository or project and for one specific build log information.
 They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
-Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.
+% Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.
 
-\paragraph{In / Output Example}
-In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
-In our data set they always consist of an \emph{input path}, linking to the build log file which is the input for this example.
-The \emph{output} is a substring of that build log, the textual representation of the targeted build log information within the input build log.
+% \paragraph{In / Output Example}
+% In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
+% In our data set they always consist of an \emph{input path}, linking to the build log file which is the input for this example.
+% The \emph{output} is a substring of that build log, the textual representation of the targeted build log information within the input build log.
+
+% \paragraph{Keywords}
+% The keyword search is configured by a list of keywords which are searched in the document with plain text search.
+% In order to compare it to the two other techniques, each in/output example is associated with a list of 1 - 3 keywords that can be found close to the textual representation of the targeted build log information.
+
+% % \paragraph{Description}
+% % \todo{for simple keyword search - imitate what users would search for ad-hoc}
+
+% % \todo{learning steps combining keywords -> similar to how devs would learn from reading those models}
+
+% \paragraph{Categories}
+% Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
+% The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
+% To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
+% If two retrievals are at the same structural location with the build log, meaning they are surrounded by a similar markings, the fall into the same category.
+% For most cases, two build failure reason examples which fall into one category are outputted either within the same build step or by the same build step tool.
+
+\section{Labeling Process}
+
+\paragraph{BuildFailureReason}
+For each repository, the labeler skimmed through the build logs and tried to identify the first occurrence of a description why the build failed.
+They copied out the first continuous description as the BuildFailureReason.
+They preserved whitespace and special characters, as they might be crucial to detect the targeted substring.
 
 \paragraph{Keywords}
-The keyword search is configured by a list of keywords which are searched in the document with plain text search.
-In order to compare it to the two other techniques, each in/output example is associated with a list of 1 - 3 keywords that can be found close to the textual representation of the targeted build log information.
+We presented the BuildFailureReason substring and ten lines above and below to the labeler.
+Their task was to note down three strings they would put into a document search function to find this failure description.
+The string should appear in or around the BuildFailureReason substring and is case-sensitive.
+There are no special limitations on the string itself, especially spaces are also allowed.
+Regular Expressions are not allowed.
 
-% \paragraph{Description}
-% \todo{for simple keyword search - imitate what users would search for ad-hoc}
-
-% \todo{learning steps combining keywords -> similar to how devs would learn from reading those models}
-
-\paragraph{Categories}
-Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
-The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
-To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
-If two retrievals are at the same structural location with the build log, meaning they are surrounded by a similar markings, the fall into the same category.
-For most cases, two build failure reason examples which fall into one category are outputted either within the same build step or by the same build step tool.
-
-\section{Labeling Process}
-\paragraph{Output Examples: Build Failure Reason}
-We labeled the first occuring substring describing the failure.
-If there were multiple errors described we took the first continuous block of error description.
-
-The labeler read or skimmed through build log and copy out the substring describing the reason the build failed.
-Whitespace or special characters were preserved, as they might be crucial for an information retrieval technique to detect the desired.
-Because we are using xml to save our example sets, we also had to make sure to escape respective special characters (ampersand, less than).
+\paragraph{Category}
+To label the \emph{structural categories} we again presented the BuildFailureReason and the surrounding context to the labeler for all logs from a repository.
+We asked them to assign numerical categories according to whether the BuildFailureReason substring had the same structural representation, i.e. the same surrounding or identifying characters.
+The labeler should start the categories with 0 and increase as new ones appear.
+For reproducibility we presented the logs in chronological build order.
 
 \section{Validation}
-\bp{some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed
-
-we are not developers of the projects and we did not analyze their travis configuration: possible that we labeled parts that presented an error, though the build did not fail because of that error
-
-end all the points with: we tried to remedy this by (e.g.\ validations)
-}
-We vaildated our collected labels in two different ways.
-We did a second pass of labeling the build failure reason, keywords and categoies on a subset of the data and compared the results to calculate the inter-rater reliability using cohens kappa.
-In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set and asked them whether our retrieval of the log part describing the reason the build failed was correct.
-In the following we describe the results of those two validation studies.
+We validate our collected data points in two different ways.
+A different labeler performed a second pass of labeling the build failure reason, keywords and categories on a subset of the data.
+We compared the results to calculate the inter-rater reliability using Cohens kappa.
+In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set.
+We asked them whether our retrieval of the log part describing the reason the build failed was correct.
+This sections describes these two validation studies.
 

### 2019-11-22 thesis/txt/6-discussion.tex
rework TOC with latest Feedback from Moritz, replace log screenshots
work on dataset section

@@
 
-\section{Choosing a Suitable Chunk Retrieval Technique}
+\section{Recommendations of Suitable Techniques}
 This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS\@.
@@
 
+some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed
+
 \end{document}

### 2019-11-22 thesis/txt/0-introduction.tex
incorporate feedback about study / results section

@@
   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-  \item Guidelines on choosing a suitable chunk retrieval technique. % TODO for a given use case or so?
+  \item Guidelines on choosing a suitable chunk retrieval technique.
 \end{itemize}
@@
 Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
-Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.\\\\
-
-Following you find selected graphs from the study results section. RLR stands for the baseline technique \emph{Random Line Retrieval}:
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques}
-		\label{fig:success-partial-all}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision and Recall of all techniques compared when training examples are in \emph{one structural category}}
-		\label{fig:recall-precision-singlecategory-all}
-\end{figure}
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision and Recall of all techniques compared when training examples are in \emph{multiple structural categories}}
-		\label{fig:recall-precision-multicategory-all}
-\end{figure}
+Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
 

### 2019-11-22 thesis/txt/5-study.tex
incorporate feedback about study / results section

@@
 \label{sec:study}
-To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{LogChunks} data set.
-This chapter describes our study design and presents the results of the study.
-The analysis of the study results first focusses on each of the three techniques and later we compare them against each other.
+To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluate them on the \emph{LogChunks} data set.
+This chapter describes our study design, detailing which metrics we measure to answer our research questions.
+In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.
 
@@
 
+\begin{simplebox}{Research Questions}
+\begin{itemize}
+  \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
+  \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
+  \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
+  \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
+  \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
+\end{itemize}
+\end{simplebox}
+
 \section{Study Design}
-For the comparison study we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},\ref{sec:expl-ts} and~\ref{sec:expl-skws}.
+For the comparison, we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},\ref{sec:expl-ts} and~\ref{sec:expl-skws}.
 RLR, explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
-We run four techniques on the example sets from \emph{LogChunks}.
+We run four techniques on the Examples from \emph{LogChunks}.
 
-The examples are sorted chronologically, i.e.\ a technique is configured with examples from the directly preceding build logs.
-For each example set and each technique, we select one to five consecutive I/O examples as configuration, the \emph{configuring I/O examples}, and run the chunk retrieval on the following I/O example, the \emph{test I/O example}.
+\paragraph{Training and Test Set}
+The data set for this study are the examples from \emph{LogChunks}.
+They contain build logs, the substring describing the reason the build failed, keywords to search for that substring and which structural category the substring belongs to.
 
-For each of our evaluation runs we measure the desired and the actual output lines of the chunk retrieval.
-The desired output is given by the output of the test I/O example, which acts as the oracle for our evaluation.
-From this we obtain true/false positives/negatives and calculate precision, recall and accuracy.
-We use these values to answer \textbf{RQ2.2}.
-If all desired lines are extracted, i.e.\ recall is one, we say a chunk retrieval run was \emph{successful}.
-To answer \textbf{RQ2.1}, we register the number configuring I/O examples for each run.
-The structural categories of the configuring I/O examples are saved to answer \textbf{RQ2.3}.
-Recall and precision of those techniques vary with the number of lines selected for retrieval.
-We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the configuring examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
+For each repository in \emph{LogChunks}, we split the examples chronologically into training and test set.
+Therefore we train on examples from past build logs and test on future build logs.
+
+\paragraph{RQ 2.1: Size of Training and Test Set}
+To analyze how many examples the chunk retrieval techniques need to perform best, we evaluate the techniques with different training set sizes.
+We run each technique with one to five examples from each repository within \emph{LogChunks}.
+The size of the test set is one.
+
+\paragraph{RQ 2.2: Recording Structural Categories}
+To determine how structurally similar the examples for the chunk retrieval techniques need to be, we record the structural categories of the examples in the training and test sets.
+
+\paragraph{RQ2.3: Accuracy Metrics}
+To measure the accuracy of the retrieved chunks we save the actual output lines of each chunk retrieval run ($retrievedlines$).
+As oracle in our evaluation, we save the desired lines from the output of the test example ($desiredlines$).
+We calculate the following metrics:
+\begin{itemize}
+	\item \todo{FILL}
+	\item True positives: $TP = desiredlines \cap retrievedlines$
+	\item False positives: $FP = retrievedlines - desiredlines$
+	\item True negatives: $TN = allloglines - (retrievedlines \cup desiredlines)$
+	\item False negatives: $FN = desiredlines - retrievedlines$
+	\item Precision: $Precision = TP / retrievedlines$
+	\item Recall: $Recall = TP / desiredlines$
+	\item F-Score:
+	\item Successful Extraction: $true if Recall == 1$
+\end{itemize}
+
+% The examples are sorted chronologically, i.e.\ a technique is configured with examples from the directly preceding build logs.
+% For each example set and each technique, we select one to five consecutive I/O examples as configuration, the \emph{training examples}, and run the chunk retrieval on the following I/O example, the \emph{test example}.
+
+% For each of our evaluation runs we measure the desired and the actual output lines of the chunk retrieval.
+% The desired output is given by the output of the test example, which acts as the oracle for our evaluation.
+% From this we obtain true/false positives/negatives and calculate precision, recall and accuracy.
+% We use these values to answer \textbf{RQ2.2}.
+% If all desired lines are extracted, i.e.\ recall is one, we say a chunk retrieval run was \emph{successful}.
+% To answer \textbf{RQ2.1}, we register the number training examples for each run.
+% The structural categories of the training examples are saved to answer \textbf{RQ2.3}.
+Recall and precision of CTS and KWS vary with the number of lines selected for retrieval.
+We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the training examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
 
@@
 \section{Results}
-This section presents the evaluation results for PBE, CTS and KWS separately.
-Afterwards it compares the three techniques with each other and RLR as baseline.
+This section presents the results for PBE, CTS and KWS separately.
+Afterwards we compare the three techniques with each other and RLR as baseline.
 
@@
 		\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
@@
 		\label{fig:failure-reason-PBE}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
+\end{figure}
+
+\begin{figure}[htbp]
 		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-		\caption{Results of chunk retrieval with PBE for numbers of categories present in configuring I/O examples}
+		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training set}
 		\label{fig:failure-reason-categorycount-PBE}
-	\end{minipage}
 \end{figure}
+
 \begin{figure}[htbp]
 		\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
-		\caption{Precision of chunk retrieval with PBE for increasing count of configuring I/O examples}
+		\caption{Precision of chunk retrieval with PBE for increasing training set size}
 		\label{fig:precision-extraction-result-PBE}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-		\caption{xxx}
-		\label{fig:xxx}
-	\end{minipage}
 \end{figure}
+
 \subsection{Program Synthesis by Example (PBE)}
@@
 In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
-In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring I/O examples.
+In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the training examples.
 
-Figure~\ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of sturctural categories present in the configuring I/O examples.
-It shows that the program synthesis is more likely to succeed when there are few categories present in the configuring I/O examples.
-When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all configuring I/O examples.
+Figure~\ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training examples.
+It shows that the program synthesis is more likely to succeed when there are few categories present in the training examples.
+When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all training examples.
 For three or more present categories PROSE could never synthesize a consistent program.
 
-Figure~\ref{fig:precision-extraction-result-PBE} compares the precision of the PBE chunk retrieval runs with the count of configuring I/O examples.
-For one example there is a high number of empty extraction outputs, meaning that the regular expression synthesized from this one configuring I/O example could not be applied to the test I/O example.
+Figure~\ref{fig:precision-extraction-result-PBE} compares the precision of the PBE chunk retrieval runs with the training set size.
+For one example there is a high number of empty extraction outputs, meaning that the regular expression synthesized from this one training example could not be applied to the test example.
 For two or more I/O examples the chunk retrieval is in most cases either successful or no consistent program could be synthesized.
@@
 		\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision and recall of chunk retrieval with CTS for increasing count of configuring I/O examples}
+		\caption{Precision and recall of chunk retrieval with CTS for increasing training set size}
 		\label{fig:recall-precision-examplecount-CTS}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
+\end{figure}
+
+\begin{figure}[htbp]
 		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision and recall of chunk retrieval with CTS for increasing number of categories present in the configuring I/O examples}
+		\caption{Precision and recall of chunk retrieval with CTS for increasing number of structural categories in the training set}
 		\label{fig:recall-precision-categorycount-CTS}
-	\end{minipage}
 \end{figure}
+
 \begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
 		\centering
@@
 		\label{fig:contextsizefactor-precision-recall-CTS}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-		\caption{xxx}
-		\label{fig:xxx}
-	\end{minipage}
 \end{figure}
@@
 \subsection{Common Text Similarity (CTS)}
-Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision and recall of chunk retrieval using CTS for different numbers of configuring I/O examples.
-The count of configuring I/O examples has no visible influence on recall and precision of the chunk retrieval with CTS\@.
+Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision and recall of chunk retrieval using CTS for increasing training set size.
+The size of the training set has no visible influence on recall and precision of the chunk retrieval with CTS\@.
 
-Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for different category counts in the configuring I/O examples.
+Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for different category counts in the training examples.
 With increasing category count, precision and recall decrease.
@@
 		\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision and recall of chunk retrieval with KWS for increasing count of configuring I/O examples}
+		\caption{Precision and recall of chunk retrieval with KWS for increasing training set size}
 		\label{fig:recall-precision-examplecount-KWS}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
+\end{figure}
+
+\begin{figure}[htbp]
 		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision and recall of chunk retrieval with KWS for increasing number of categories present in the configuring I/O examples}
+		\caption{Precision and recall of chunk retrieval with KWS for increasing number of structural categories in the training set}
 		\label{fig:recall-precision-categorycount-KWS}
-	\end{minipage}
 \end{figure}
+
 \begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
 		\centering
@@
 		\label{fig:contextsizefactor-precision-recall-KWS}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
+\end{figure}
+
+\begin{figure}[htbp]
 		\centering
@@
 		\label{fig:retrievalsizefactor-retrievalratio-KWS}
-	\end{minipage}
 \end{figure}
@@
 \subsection{Keyword Search (KWS)}
-Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision and recall of chunk retrieval using KWS in our study for different numbers of configuring I/O examples.
-The recall jumps from 53\% to over 70\% for more than two configuring I/O examples, while the precision stays constant at around 16\%.
+Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision and recall of chunk retrieval using KWS in our study for different numbers of training examples.
+The recall increases by 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
 
-Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for different category counts in the configuring I/O examples.
-There is no clear trend visible in precision and recall for an increasing amount of categories in the configuring I/O examples
+Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for different category counts in the training examples.
+There is no clear trend visible in precision and recall for an increasing amount of categories in the training examples
 
@@
 Figure~\ref{fig:retrievalsizefactor-retrievalratio-KWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS\@.
-When retrieving the mean number of lines in the configuring I/O examples, 15\% of the log lines are retrieved on average.
+When retrieving the mean number of lines in the training examples, 15\% of the log lines are retrieved on average.
 This proportion goes up to 25\% when retrieving 1.5 times more lines.
@@
 % 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
-% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR for single and multiple categories present in the configuring I/O examples}
+% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR for single and multiple categories present in the training examples}
 % 		\label{fig:precision-category-singularity-all}
@@
 % \end{figure}
+
 \begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
 		\centering
@@
 		\label{fig:success-partial-all}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
+\end{figure}
+
+\begin{figure}[htbp]
 		\centering
@@
 		\label{fig:recall-precision-all}
-	\end{minipage}
 \end{figure}
+
 \begin{figure}[htbp]
 	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision and Recall of all techniques compared when training examples are from 1 category}
+		\caption{Precision and Recall of all techniques compared when training examples are in \emph{one} structural category}
 		\label{fig:recall-precision-singlecategory-all}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
+\end{figure}
+
+\begin{figure}[htbp]
 		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision and Recall of all techniques compared when training examples are >1 categories}
+		\caption{Precision and Recall of all techniques compared when training examples are in \emph{more than one} structural categories}
 		\label{fig:recall-precision-multicategory-all}
-	\end{minipage}
 \end{figure}
@@
 
-Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the configuring I/O examples compared to multiple categories present.
+Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
 For more than one present category, precision and recall of PBE greatly decrease.

### 2019-11-22 thesis/txt/3-data-set.tex
incorporate feedback about study / results section
try stuff on plots, add to discussion a bit

@@
 We encountered the following statuses during our data collection:
+\begin{multicols}{3}
 \begin{itemize}
@@
 \end{itemize}
+\end{multicols}
 The user of \texttt{TravisRequester} configures how many builds should be checked and how many builds per status should be saved.
@@
 For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
+	\caption{Distribution of the categories in LogChunks}
+	\label{fig:categorycount-examplecount-dataset}
+\end{figure}
 

### 2019-11-22 thesis/txt/5-study.tex
try stuff on plots, add to discussion a bit

@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
 		\caption{Results of chunk retrieval with PBE}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
 		\caption{Precision and recall of chunk retrieval with KWS for increasing training set size}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
 		\caption{Precision and recall of chunk retrieval with KWS for increasing number of structural categories in the training set}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
 		\caption{Precision and recall of chunk retrieval with KWS compared to retrieval size factor}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
 		\caption{Ratio of lines retrieved with KWS compared to retrieval size factor}

### 2019-11-22 thesis/txt/6-discussion.tex
try stuff on plots, add to discussion a bit

@@
 \begin{tabular}{|c||c|c|c|}
-  Technique & \multicolumn{3}{|c|}{Number of Categories in configuring examples} \\
+  & PBE & CTS & KWS \\
   \hline
-  & one & two & more \\
-  PBE & yes & no & no \\ 
-  CTS & yes & yes & no \\ 
-  KWS & yes & yes & yes \\ 
+  \hline
+  Structural Categories & 1 & best if 1 & no influence \\
+  Training Set Size & 1 - 3 & no influence & > 2 \\ 
+  Precision & high (if synthesis succeeds) & medium & low \\ 
+  Recall & high (if synthesis succeeds) & medium & high \\ 
+  Confidence in Output Correctness & high & low & low (precision), high (recall) \\ 
+  Output Consumption by & program & human & human \\ 
   \hline
 \end{tabular}
-\caption{The small $1 \cdot 1$}
+\caption{Recommendations for each of the investigated chunk retrieval techniques}
 \label{tab:101}
 \end{table}
+
+\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.75\textwidth, clip]{img/crt-recommendation.pdf}
+		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
+		\label{fig:fcrt-recommendation}
+\end{figure}
 

### 2019-11-26 thesis/txt/0-introduction.tex
describe inter-rater reliability, conclusion and fw, add se logos

@@
 The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
-Build logs are a valuable data source: For developers, who read them to analyze why their build failed or how different stages of the build process perform.
-Second, for researchers, who can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
+Build logs are a valuable data source for developers and researchers.
+Developers read them to analyze why their build failed or how different stages of the build process perform.
+Researchers can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
 However, these two groups can only use the information within the build logs if they can adequately retrieve the information relevant to them.
@@
   \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
-  \item a common text similarity approach (referred to as CTS) and
-  \item keyword search (referred to as KWS)
+  \item a common text similarity approach (referred to as CTS), and
+  \item keyword search (referred to as KWS).
 \end{itemize}
@@
 \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
+How many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is(\textbf{RQ2.3}).
 % \begin{simplebox}{Research Questions}
@@
   \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
-  A small increase in the number of training examples has no visible influence.
+  A small increase in the number of training examples has no noticeable influence.
   Fewer structural categories improve the retrieval accuracy.
-  \item KWS has the highest recall of all techniques combined with much lower precision.
+  \item KWS has the highest recall of all techniques, however much lower precision.
   It is the only technique where retrieval accuracy does not decrease with an increasing number of structural categories in the training examples.
@@
 In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
-However, the low precision requires a human to interpret the output of the chunk retrieval.
+However, its low precision requires a human to interpret the output of the chunk retrieval.
 
@@
 This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
-Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques and program synthesis from examples.
+Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques, as well as program synthesis from examples.
 Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
-It also introduces the three investigated techniques: PBE, CTS and KWS\@.
+It also introduces the three investigated techniques PBE, CTS and KWS\@.
 Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
-Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
+Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
 This tool is also used for the comparison described in Chapter~\ref{sec:study}.
 Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
-Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
+Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion-fw}.
 

### 2019-11-26 thesis/txt/3-data-set.tex
describe inter-rater reliability, conclusion and fw, add se logos

@@
 One had only one failed build, two others had empty build logs on Travis CI.
-In total we collected 798 \todo{check} logs from 80 repositories.
-
-\todo{image! like in travistorrent paper, /draft 10 mins/}
+In total we collected 797 logs from 80 repositories.
 
@@
 \section{Data Schema}
+\label{sec:data-schema}
 For each repository, \emph{LogChunks} has a list of \emph{examples}.
@@
 Following, this section describes the BuildFailureReason, Keywords and Category in more detail.
-.
 
@@
 \section{Labeling Process}
+\label{sec:labeling-process}
 
@@
 They preserved whitespace and special characters, as they might be crucial to detect the targeted substring.
+To support exact learning of regular expressions identifying the labeled substrings the labeler aimed to start and end the labeled substring at consistent locations around the fault description.
 
@@
 \subsection{Inter-Rater Reliability Study}
-re-labeling of parts of the labels - cohen's kappa
-\subsubsection{Introduction}
-After the manual labeling of the data set we performed a second labeling of a sample of the build logs to validate the labels.
-\subsubsection{Method}
-For each label category: Build Failure Reason, keywords and category, we relabeled 30 randomly sampled logs.
-compared the labels, \todo{discussed about it}.
-\subsubsection{Results}
+To evaluate the validity of our labeled data points we perform a second labeling of a sample from \emph{LogChunks}.
 
-\subsubsection{Discussion}
-main takeaway: overlap yes, but high variation
+\paragraph{Method}
+A second labeler processed 30 random generated logs for each data point in \emph{LogChunks}.
+We followed the same labeling process as described in Section \ref{labeling-process}.
+For the build failure reason and the keywords, we presented 30 randomly sampled build logs from distinct repositories in \emph{LogChunks}.
+As the structural categories are always relative to the other logs from the same repository we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.
 
-build failure reason: should we extract the information \emph{that} the build failed as well?
-our data set extracts the parts describing \emph{why}, but leaves out the lines stating that the build failed (e.g. step xy exited with 1).
+\paragraph{Results}
+For the first labeled data point, namely the substring describing why the build failed, the two labelers exactly agreed in six cases.
+In 15 cases the second labeler selected more lines than the first one, in five there was partial overlap and in 4 they completely disagreed.
 
-keywords: first labeler allowed also longer strings with spaces and adhered to capitalization.
-second one ignored captialization and focussed on the keyword.
-so only one word was allowed.
-also the first one labeled always a full repository at a time.
-so could take into consideration patterns and see what keywords are exception specific and would only retrieve the failure reason if this specific exception occured.
-second labeler only one build log excerpt (+ context) per repository.
-also: influene of ansi color codes ``merror'' vs. ``error'' first labeler known as ansi color codes, second one counted it into the word (whole word always)
-first was also more inclined to search for a subpart of a word to make it more generalizeable (``failure`` instead of ``failures'')
+Regarding the keywords the two labelers completely agreed in nine cases and completely disagreed in two cases.
+In nine cases there was partial overlap in the keywords of the two labelers, in two the first labeler selected additional keywords compared to the second, while the second labeler labeled additional keywords in seven cases.
 
-categories: description for the second labeling stated: sort into categories on why build failed.
-was exectued with sorting into test/linter/compilation.
-in the case of the selected repositories everything was labeled as test.
+When classifying the labeled substrings into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.
+
+\paragraph{Discussion}
+The results of this validation study show that there is overlap in the data from the two labelers, however also a high variation.
+We mainly attribute this to not specific enough instructions to the second labeler.
+There were implicit, inconsistent assumptions both labelers created during their work.
+In the following we describe the inconsistent assumptions between both labelers for each data point and the implications on our description of the data classes.
+
+For the first data class, the reason the build failed, it was ambiguous whether the labeled substring should contain the information \emph{that} the build failed.
+This concerns statements like \texttt{The build exited with 1}.
+The second labeler included such statements, while the first one only focussed on the log parts describing \emph{why} the build failed, e.g. the name of the failing test case.
+
+While labeling the keywords a developer would use to search for the log part describing why the build failed, the first labeler allowed arbitrary, case-sensitive strings.
+In contrast to that, the second labeler focussed on actual \emph{words}, delimited by spaces or special characters, while ignoring capitalization.
+A second difference was that the first labeler was presented with all substrings from a repository, yielding more general keywords than the second labeler.
+Their keywords were in part specific to the failure itself and therefore would not have caught a log part describing a different reason for the build to fail in the test build log.
+%so could take into consideration patterns and see what keywords are exception specific and would only retrieve the failure reason if this specific exception occured.
+%also: influene of ansi color codes ``merror'' vs. ``error'' first labeler known as ansi color codes, second one counted it into the word (whole word always)
+%first was also more inclined to search for a subpart of a word to make it more generalizeable (``failure`` instead of ``failures'')
+
+For the structural categories this validation study showed a high overlap.
+In our instructions to the second labeler we did not emphasize the \emph{structural} aspect enough.
+They sorted into categories along \emph{why} the build failed, putting failing tests from different test runners into the same category even though the failing tests were presented differently in the log.
+
+% categories: description for the second labeling stated: sort into categories on why build failed.
+% was exectued with sorting into test/linter/compilation.
+% in the case of the selected repositories everything was labeled as test.
 mostly correct (one linter), but more importantly no difference was made in which test step failed / how the failed tests were represented.
-the categories are thought as structural categories.
-so the surrounding sturcture and the way a test failure is communicated is important. e.g. if several tests are run then it is important which ones failed
+% the categories are thought as structural categories.
+% so the surrounding sturcture and the way a test failure is communicated is important. e.g. if several tests are run then it is important which ones failed
 
-main influence / implication: the labels we select are not black/white.
-accurate description of what we do is very very important.
-mainly influenced how we described our data points in the earlier sections.
-\subsubsection{Threats to Validity}
-
-\subsection{Developer Survey}
-\subsubsection{Introduction}
-For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
-As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
-We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
-
-The person who probably knows best why a build failed is the one committing the changes which triggered the build.
-If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
-In this section we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
-\subsubsection{Method}
-Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
-We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
-The email included links to the corresponding commits, build overview and log file.
-We asked the receivers to fill out a short survey in case our extraction was not correct.
-Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
-In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
-As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.
+Our main learning from this study is that adequately communicating all decisions and assumptions on how data is labeled is important and difficult.
+We reviewed the misunderstandings and incorporated more thorough descriptions of our data classes in Secton \ref{sec:data-schema}.
 
@@
 \end{figure}
+
+\subsection{Developer Survey}
+
+\paragraph{Introduction}
+For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
+As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
+We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
+
+The person who probably knows best why a build failed is the one committing the changes which triggered the build.
+If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
+In this section we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
+\paragraph{Method}
+Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
+We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
+The email included links to the corresponding commits, build overview and log file.
+We asked the receivers to fill out a short survey in case our extraction was not correct.
+Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
+In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
+As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.
 
@@
 
-\subsubsection{Results}
+\paragraph{Results}
 In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
@@
 
-\subsubsection{Discussion}
+\paragraph{Discussion}
 This study highly strengthens the trust in the validity of the extracted build failure reasons in \emph{LogChunks}.
@@
 
-\subsubsection{Threats to Validity}
-
 \end{document}

### 2019-11-26 thesis/txt/5-study.tex
describe inter-rater reliability, conclusion and fw, add se logos

@@
 
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
-		\caption{Results of chunk retrieval with PBE}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training set}
-		\label{fig:failure-reason-categorycount-PBE}
-\end{figure}
-
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
-		\caption{Precision of chunk retrieval with PBE for increasing training set size}
-		\label{fig:precision-extraction-result-PBE}
-\end{figure}
-
 \subsection{Program Synthesis by Example (PBE)}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
+		\includegraphics[width=0.5\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
+		\caption{Results of chunk retrieval with PBE}
+		\label{fig:failure-reason-PBE}
+\end{figure}
+
+\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training set}
+		\label{fig:failure-reason-categorycount-PBE}
+\end{figure}
+
+\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
+		\caption{Precision of chunk retrieval with PBE for increasing training set size}
+		\label{fig:precision-extraction-result-PBE}
+\end{figure}
+
+\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
 		\caption{Precision and recall of chunk retrieval with CTS for increasing training set size}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
 		\caption{Precision and recall of chunk retrieval with CTS for increasing number of structural categories in the training set}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
 		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
+		\includegraphics[width=0.5\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
 		\caption{Ratio of lines retrieved with KWS compared to retrieval size factor}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/success-partial-all.pdf}
 		\caption{Success of chunk retrievals for all techniques}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-all.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-all.pdf}
 		\caption{Precision and Recall of all techniques compared}
@@
 	\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
 		\caption{Precision and Recall of all techniques compared when training examples are in \emph{one} structural category}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
 		\caption{Precision and Recall of all techniques compared when training examples are in \emph{more than one} structural categories}

### 2019-11-26 thesis/txt/6-discussion.tex
describe inter-rater reliability, conclusion and fw, add se logos

--- 2019-11-07 thesis/txt/6-discussion.tex
@@
 
-\section{Choosing a Suitable Chunk Retrieval Technique}
-This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS\@.
-It recommends which technique to use depending on the available configuration and 
-TABLE!
-\paragraph{Configuration and Input}
-number of categories:
-one? -> pbe
-two? -> CTS
-more? -> KWS
-available examples:
-little?
--> try pbe (This depends on the categories!
-here we might want a decision tree to represent the importance of these characteristics against each other?
-<- this would also anwser RQ1: which ones of the criteria we compare are the most important)
-multiple -> kws
-very many? -> CTS
+\section{Recommendations of Suitable Techniques}
+% This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS\@.
+% It recommends which technique to use depending on the available configuration and 
+After discussing three chunk retrieval techniques separately we know want to unify out results into one recommendation scheme.
+We present a decision tree, which asks questions to a developer or researcher who wants to retrieve information chunks from build logs.
+The answers lead the user to more questions or the recommended technique as leaf nodes.
+Figure \ref{fig:crt-recommendation} presents the decision tree.
 
-\paragraph{Retrieval Output Usage}
-precision needed:
+\emph{Caveat!} This is a preliminary theory based on the results from our comparison study.
+The recommendations are therefore likely based on our implementation of the chunk retrieval techniques as well as the logs in the LogChunks data set.
+This decision tree is the answer to our first research question "which factors influence the suitability of a chunk retrieval technique".
+The earlier in the decision tree an aspect is noted, the more important it is in distinguishing the techniques.
+
+First and most important aspect are the structural categories.
+Are the textual representations of the BuildLogInformation your would like to extract always presented in the same structural way within the build logs?
+Meaning that all training examples are in the same structural category and the expected output in the log the chunk retrieval is applied to as well.
+
+If the textual representations of the BuildLogInformation are from multiple structural categories, meaning the are  not presented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS.
+If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS.
+We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the accuracy of the outcome and the user rather have some bad output instead of no output at all.
+When the representations are from one structural category and the user wishes a high confidence in the correct need of the output or prefers no output over bad output, we recommend PBE.
 
 \begin{table}[htbp]
-\begin{tabular}{|c||c|c|c|}
-  Technique & \multicolumn{3}{|c|}{Number of Categories in configuring examples} \\
-  \hline
-  & one & two & more \\
-  PBE & yes & no & no \\ 
-  CTS & yes & yes & no \\ 
-  KWS & yes & yes & yes \\ 
-  \hline
-\end{tabular}
-\caption{The small $1 \cdot 1$}
-\label{tab:101}
+\centering
+\begin{tabularx}{\textwidth}{@{}llll@{}}
+  \toprule
+  & PBE & CTS & KWS \\
+  \midrule
+  Structural Categories & 1 & best if 1 & no influence \\
+  Training Set Size & 1 - 3 & no influence & > 2 \\ 
+  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
+  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
+  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
+  Output Consumption by & program & human & human \\ 
+  \bottomrule
+\end{tabularx}
+\caption{Recommendations for each of the investigated chunk retrieval techniques}
+\label{tab:single-technique-recommendations}
 \end{table}
 
+\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.75\textwidth, clip]{img/crt-recommendation.pdf}
+		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
+		\label{fig:crt-recommendation}
+\end{figure}
+
 \section{Threats to Validity}
+
+There are several threats to the validity of the conclusions of our work.
+
+\paragraph{Implementation}
+Our results are highly dependent on the libraries we used and our implementation of the investigated chunk retrieval techniques.
+Our implementation of PBE is mainly based on the program synthesis provided by PROSE.
+It's limitations are therefore also mainly influenced by this library.
+For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with (too many?) top level OR operators.
+This limitation was necessary to keep the synthesis performance reasonable.
+
+Our implementation of CTS is dependent on the information retrieval library tex2vec and the way they split strings into word tokens.
+We intentionally chose a simple, minimally configured and tuned approach to compare against.
+Of course tuning the text similarity meta parameters more to the specific use case Of build log chunk retrieval or training  examples in specific instances would yield better chunk retrieval results.
+
+\paragraph{Data Set} the outcomes of our comparison study are highly dependent on the build logs from the LogChunks data set.
+It only consists of build logs from open source and therefore it is not clear whether our results are generalizable to industry projects.
+We only collected build logs from Travis CI, however we chose to evaluate on a BuildLogInformation, the reason the build failed, which format is not dependent on Travis CI.
+This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI runner.
+
+\paragraph{Training set size}
+Especially the results for CTS are influences by the fact that we only trained on one to five examples.
+Information retrieval tasks commonly learn on larger data sets. \mention{CITATION NEEDED}
+We chose this small training set size as the examples would always have to be provided per repository and we expect a developer to not want to have to provide more examples than the small numbers we evaluated on.
+
+\bp{
 chronologically selected examples -> very specific view, devs/users might pick more representative examples
@@
 
+some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed}
 \end{document}

### 2019-11-26 thesis/txt/7-conclusion.tex
new chapter 6: discussion, start on results for CTS, replotting quite some things
describe inter-rater reliability, conclusion and fw, add se logos

--- 2019-10-03 thesis/txt/2-models.tex
@@
 
-\chapter{Information Extraction Techniques}
-overview introduction text
-\label{models}
+\chapter{Conclusion and Future Work}
+\label{sec:conclusion-fw}
+The goal of this thesis is to support researches and developers when they decide how to analyze build logs.
+We implemented and compared three different chunk retrieval techniques on our \emph{LogChunks} data set.
+Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
+Secondary factors are confidence in the produced output and whether precision or recall are more important for the task at hand.
 
-\section{Our Model for IE Techniques}
-\section{Our Model for extraction tasks}
-\section{Our Model for extractable information}
-
-\section{PROSE Program Synthesis}
-
-\section{IR Similarity}
-
-\section{Keyword search}
-
-\section{further thechniques}
+In the following we describe various future research opportunities based on our work:
+\begin{itemize}
+  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set specifically for our comparison study, though it can be the basis for various further analyses of build log data.
+  The keywords can be investigated to answer which keywords do developers use to search for the reason the build failed within build logs.
+  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from one repository.
+  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment agnostic analysis tools.
+  \item \textbf{Comparison with more Chunk Retrieval Techniques} This thesis investigates the three chunk retrieval techniques PBE, CTS and KWS.
+more techniques (which kinds of techniques?
+express in model!
+e.g.\ diffs might not work?), same evaluation, ir automated keyword search/expansion
+  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations existing techniques applied to chunk retrieval from build logs.
+  In a next step, each of these techniques could be refined and configured to better approach the domain of build logs.
+  The \emph{LogChunks} data set and our study results act as a baseline to evaluate further technique improvements.
+  We propose the following improvements:
+    \begin{itemize}
+      \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
+      The ranking rules provided by the FlashExtract DSL could be adapted to fit common build log chunk retrieval tasks.
+      FlashExtract includes special tokens when enumerating possible regular expressions.
+      These could be extended with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
+      \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
+      We propose to further investigate improvements in preprocessing of the log text, tokenization of the log lines into terms and stop words lists.
+    \end{itemize}
+  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focussed on precision and recall.
+  In addition to that, we propose to investigate how useful these outputs are to developers through controlled experiments.
+\end{itemize}
 

### 2019-11-28 thesis/txt/2-models.tex
reworking on most sections and linter fixes

@@
 We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
-This chapter first presents how a build log, the input to our chunk retrieval, is created by a continuous integration (CI) build.
+This chapter first presents how a build log, which we take as input to the chunk retrieval, is created by a continuous integration (CI) build.
 Next, it describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
 We illustrate why it is useful to extract the presented information chunks.
-The following section introduces our concept of chunk retrieval techniques, which retrieve information chunks from build logs.
-We present the three chunk retrieval techniques we investigate for this thesis:
+The following section introduces our concept of chunk retrieval techniques.
+We present the three chunk retrieval techniques we investigate in this thesis:
 Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
@@
 
-The central class of our model is the \emph{BuildLogInformation} (BLI), representing a piece of information possibly retrievable from a build log.
-\emph{Possibly}, because a BLI is not necessarily present in every build log.
-If it is present, we call it a \emph{BuildLogInformation instantiation} (BLII).
-A BLII is always contained in a specific build log.
-Figure~\ref{fig:build-overview} presents the relation between a BLI and other entities involved in a CI build.
+Central to this explanation is the piece of \emph{information} possibly retrievable from a build log.
+\emph{Possibly}, because an information is not necessarily present in every build log.
+If it is present, we call the text part which describes the information the \emph{information chunk} or in short \emph{chunk}.
+Each chunk is always contained in a specific build log.
+Figure~\ref{fig:build-overview} presents the relation between an information, a chunk and other entities involved in a CI build.
 
-Each BLII has a \emph{textual representation} within the build log.
-This textual representation is always a substring of the log text.
-BLIs can be hierarchically ordered, determined by how their textual representations contain each other.
-As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section~\ref{sec:rw-semi-structured-data}, this section only presents hierarchical containment for BLIs whose structure we definitely know.
-Most BLI types can appear in various hierarchical arrangements and are therefore not contained in any other type in our explanation.
+Chunks can be hierarchically ordered, determined by how their textual representations contain each other.
+As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section~\ref{sec:rw-semi-structured-data}, this section only presents hierarchical containment for chunks whose hierarchy we definitely know.
+Most chunks can appear in various hierarchical arrangements and are therefore not contained in any other type in our explanation.
 
@@
 We inspected them to get an impression of the information one would want to retrieve from a build log.
-In the following, we describe information types which could be retrieved from Travis CI build logs.
-All BLIs containing ``Travis'' in their name are specific to Travis CI build logs, the others can also apply to build logs from another CI environment.
-Figure~\ref{fig:build-log-information} shows an overview of these BLIs.
+In the following, we describe examples of information chunks that can be retrieved from Travis CI build logs.
+All information examples containing ``Travis'' in their name are specific to Travis CI build logs, the others can also apply to build logs from another CI environment.
+Figure~\ref{fig:build-log-information} shows an overview of these information examples.
 
@@
 	\item \textbf{BuildPhase} Build logs can be divided into the sections produced by different tools.
-	      These build steps could be for example be a \texttt{TestPhase}, \textbf{LinterPhase}, \textbf{TravisWorker}, \textbf{GitFetch}, or \textbf{Sudoers} are some that we encountered in the logs.
+	      These build steps could be for example be a \textbf{TestPhase}, \textbf{LinterPhase}, \textbf{TravisWorker} or \textbf{GitFetch} are some that we encountered in the logs.
 
@@
 
-	      A TravisPhase always contains:
+	      A TravisPhase contains:
 	      \begin{itemize}
 		      \item \textbf{TravisPhaseName} The string Travis CI uses to identify the phase within start and end statements.
-		      \item \textbf{TravisPhaseOutput} The output generated during the TravisPhase.
-The textual representation of the \texttt{TravisPhaseOutput} instantiation is the substring between the start and end statements.
+		      \item \textbf{TravisPhaseOutput} The output generated during the TravisPhase. The chunk presenting the \texttt{TravisPhaseOutput} is the string between the start and end statements.
 	      \end{itemize}
 				 Retrieving the names of the phases of a Travis CI build log could be used to afterward reconstruct an overview of the executed steps within a build.
-	       Figure~\ref{fig:log-1} shows an example of a TravisPhase instantiation and its components within a build log.
+	       Figure~\ref{fig:log-1} shows an example of a TravisPhase chunk and its components within a build log.
 
@@
 				A developer can retrieve this timing information to automatically monitor the performance of their build.
-	      Figure~\ref{fig:log-1} shows an example of a TravisTiming instantiation.
+	      Figure~\ref{fig:log-1} shows an example of a TravisTiming chunk.
 	      %It represents those by \lstinline{travis_time:start:<timing section id>} and \\ \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}
@@
 	      Retrieving this information from multiple build logs can help visualize the impact of the build server assignment algorithm.
-	      The TravisWorker is a good example that the same BLI can have different textual representations in different build logs.
-	      Figure~\ref{fig:log-0} and Figure~\ref{fig:log-2} show examples of different TravisWorker instantiations.
+	      The TravisWorker is a good example that chunks belonging to the same information can have different textual representations in different build logs.
+	      Figure~\ref{fig:log-0} and Figure~\ref{fig:log-2} show examples of different TravisWorker chunks.
 
@@
 				A developer can retrieve the system information from both failing and successful logs to identify if a failure could be based on the execution environment.
-	      Figure~\ref{fig:log-0} shows an example of a TravisSystemInfo instantiation within a build log.
+	      Figure~\ref{fig:log-0} shows an example of a TravisSystemInfo chunk within a build log.
 
@@
 	      These come from the \texttt{travis.yml} configuring the build.
-				This information can be useful for a researcher to retrieve when reverse engineering the build configuration.
-	      Figure~\ref{fig:log-3} shows an example of a TravisTriggeringCommand instantiation.
+				This information can be useful for a researcher to retrieve when they reverse engineer the build configuration.
+	      Figure~\ref{fig:log-3} shows an example of a TravisTriggeringCommand chunk.
 
 	\item \textbf{TravisExitCode} Travis CI prints all exit codes of commands.
-				A researcher can retrieve this information to fill an overview of the build steps and why they failed.
-	      Figure~\ref{fig:log-3} shows an example of an TravisExitCode instantiation within a build log.
+				A researcher can retrieve these chunks to fill an overview of the build steps and why they failed.
+	      Figure~\ref{fig:log-3} shows an example of a TravisExitCode chunk within a build log.
 
 	\item \textbf{ErrorMessage} Various tools involved in the build process output messages of errors that occurred during their execution.
-	      Retrieving these and showing them to developers can help them understand quicker why the build failed.
-	      Figure~\ref{fig:log-3} shows an example of and ErrorMessage instantiation.
+	      A developer can retrieve them understand why the build failed.
+	      Figure~\ref{fig:log-3} shows an example of and ErrorMessage chunk.
 
@@
 				Developers can collect and count them to encourage their team to resolve them.
-	      Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} show examples of WarningMessage instantiations within build logs.
+	      Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} show examples of WarningMessage chunks within build logs.
 
@@
 	\includegraphics[width=\textwidth, clip]{img/log02.png}
-	\caption{Excerpt from a build log showing textual representations of a long TravisWorker instantiation and a TravisSystemInfo}
+	\caption{Excerpt from a build log showing a long TravisWorker chunk and a TravisSystemInfo chunk}
 	\label{fig:log-0}
@@
 	\includegraphics[width=\textwidth, clip]{img/log12.png}
-	\caption{Excerpt from a build log showing textual representations of a TravisTiming and a TravisPhase, containing the TravisPhaseName and the TravisPhaseOutput}
+	\caption{Excerpt from a build log showing a TravisTiming chunk and a TravisPhase chunk, containing the TravisPhaseName chunk and the TravisPhaseOutput chunk}
 	\label{fig:log-1}
@@
 	\includegraphics[width=\textwidth, clip]{img/log22.png}
-	\caption{Excerpt from a build log showing the textual representation of a short TravisWorker}
+	\caption{Excerpt from a build log showing a short TravisWorker chunk}
 	\label{fig:log-2}
@@
 	\includegraphics[width=\textwidth, clip]{img/log32.png}
-	\caption{Excerpt from a build log showing textual representations of an ErrorMessage, an ExitCode and a TravisTriggeringCommand}
+	\caption{Excerpt from a build log showing chunk an ErrorMessage, an ExitCode chunk and a TravisTriggeringCommand chunk}
 	\label{fig:log-3}
@@
 	\includegraphics[width=\textwidth, clip]{img/log42.png}
-	\caption{Excerpt from a build log showing the textual representation of a WarningMessage}
+	\caption{Excerpt from a build log showing a WarningMessage chunk}
 	\label{fig:log-4}
@@
 	\includegraphics[width=\textwidth, clip]{img/log52.png}
-	\caption{Excerpt from a build log showing the textual representation of another WarningMessage}
+	\caption{Excerpt from a build log showin another WarningMessage chunk}
 	\label{fig:log-5}
@@
 \label{sec:blirt}
-For this thesis, we want to evaluate different \emph{chunk retrieval techniques} (CRTs) when applied to CI build logs.
-A chunk retrieval does not require to parse the structure of a whole build log.
-It focus on extracting just one information, specified by its configuration.
+For this thesis, we want to evaluate different techniques to retrieve information chunks from build logs, which we call \emph{chunk retrieval techniques}.
+The techniques we investigate do not require to parse the structure of a whole build log, but focus on extracting just one specific information.
 
-Each CRT has a specific \textit{granularity}, i.e.\ the smallest retrievable text piece and uses a specific \textit{identification technique} to select the log parts it retrieves.
-The \textit{configuration} instantiates a CRT to target a specific BLI and supplies the necessary information for the CRT to identify the textual representation of the targeted BLI in a build log.
+The user provides a \textit{configuration} that specifies which information the chunk retrieval should target and supplies the necessary information for the technique to identify the targeted information chunk in a build log.
+Each chunk retrieval has a specific \textit{granularity}, i.e.\ the smallest retrievable text piece and uses a specific \textit{identification technique} to select the log parts it retrieves.
 Each configuration addresses a specific \textit{scope}.
-The scope can be a specific project, a tool involved in the build, a programming language or global, configuring a retrieval technique for all possible build logs.
-A \textit{CRT run} consumes a build log as a plain text file and produces a string output, which consists of substrings of the build log text.
+The scope can be a specific project, a tool involved in the build, a programming language or global, when configuring a retrieval technique for all possible build logs.
+A \emph{run} of a chunk retrieval technique consumes a build log as a plain text file and produces a string output, which consists of substrings of the build log text.
 
-The following sections of this chapter introduce the three CTRs we investigate: Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
-Lastly we describe other techniques which can also be comprehended as CRTs.
+The following sections of this chapter introduce the three chunk retrieval techniques we investigate: program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
+Lastly we describe other techniques which can also be treated as chunk retrieval techniques.
 Table~\ref{tab:ctr} shows a comparison of the presented techniques.
@@
 \caption{Chunk Retrieval Techniques}
-\begin{tabularx}{\textwidth}{|X|l|X|l|X|} 
-\hline
+\begin{tabularx}{\textwidth}{@{}XlXlX@{}} 
+\toprule
 Name                         & Acronym & Identification Technique                                   & Granularity & Configuration             \\ 
-\hline
-\hline
+\midrule
 Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In / Output Examples      \\
-\hline
 Common Text Similarity       & CTS     & Tf-idf \& cosine similarity, mean number of lines expected & Line        & Output Examples           \\
-\hline
 Keyword Search               & KWS     & Keywords, mean number of lines expected                    & Line        & Keywords, Context Length  \\
-\hline
 Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval Length          \\
-\hline
-Diff Approach                &         & Line not present in successful log                         & Line        & Successful Log File       \\
-\hline
+Diff Approach                &         & Line not present in successful log, informatino retrieval  & Line        & Successful Log File       \\
+\bottomrule
 \end{tabularx}
@@
 In the following, we explain the configuration and application of PBE to chunk retrieval from CI build logs.
-The concrete implementation is described in~\ref{sec:impl-pbe}.
-%Figure~\ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE\@.
 
 \paragraph{Configuration}
-In/output examples (I/O examples) are the main driver of Programming by Example.
-When retrieving information chunks from build logs the \emph{input} is always a whole build log, i.e.\ the whole text of the build log file.
-The \emph{output} is always a substring of the log file text, representing the substring that should be retrieved by the synthesized program when given the corresponding input file.
-One or multiple I/O examples configure a chunk retrieval with PBE: they define the substring of a build log that should be extracted.
-The PROSE program synthesis then tries to construct a regular expression program consistent with all configuring I/O examples.
-A program is consistent with an I/O example if it returns the defined output when executed on the defined input.
-PBE reports an error back to the user if no consistent program could be synthesized.
+In/output examples are the main driver of Programming by Example.
+We refer to in/output examples as \emph{examples}.
+When retrieving information chunks from build logs the \emph{input} is a whole build log, i.e.\ the whole text of the build log file.
+The \emph{output} is a substring of the log file text, representing the substring that should be retrieved by the synthesized program when given the corresponding input file.
+One or multiple examples, the training examples, configure a chunk retrieval with PBE: they define the substring of a build log that should be extracted.
+The PROSE program synthesis then tries to construct a regular expression program consistent with all training examples.
+A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
+PBE reports an error back to the user if it could not synthesize a consistent program.
 The program synthesis builds on the Flash Extract DSL, which in turn uses the FlashMeta algorithm.
@@
 \paragraph{Application}
-A CTR run with PBE takes a build log file as input and applies the synthesized regular expression program.
+A run of PBE takes a build log file as input and applies the synthesized regular expression program.
 It then returns the substring of the build log matched by the program or an empty string if the program found no match.
-%For execution PBE takes a build file as input and returns a substring of the build file content.
 
@@
 In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (CTS), the concrete implementation is described in~\ref{sec:impl-ts}.
-%Figure~\ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for CTS.
 
 \paragraph{Configuration}
-To configure chunk retrieval though text similarity we chose to use the same concept of I/O examples as for PBE\@.
-The lines of the output strings of the configuring I/O examples define our search query.
+To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@.
+The lines of the output strings of the training examples define our search query.
 The algorithm splits the search query into single lines and identifies tokens, in our case words.
-%Commonly text similarity techniques employ further normalization like removing special characters and stop words.
-%We chose to keep the build log lines as complete as possible, as we often saw special characters and words identifying an interesting area.
 Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
@@
 After summing up the similarities of each build log line to all search query lines, we sort the build log lines in decreasing similarity.
-The average number of lines in the outputs of the configuring I/O examples determines how many of the most similar lines are returned as the output of the retrieval run.
+The average number of lines in the outputs of the training examples determines how many of the most similar lines are returned as the output of the retrieval run.
 
@@
 When developers are looking for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is searching for related keywords.
-This was one of the most common approaches we took when searching for the build failure reason within a log when creating our \emph{LogChunks} data set.
-As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is recommendable for retrieving information chunks from CI build logs.
+This was one of the most common approaches we took when searching for the reason the build failed within a log while creating our \emph{LogChunks} data set.
+As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
 In the following we will explain how we use simple keyword search to retrieve information from CI build logs (KWS).
-The concrete implementation is described in~\ref{sec:impl-skws}.
-%Figure~\ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.
 
@@
 A set of keywords configures the chunk retrieval with KWS\@.
-To better compare KWS with PBE and CTS, we also configure it through I/O examples.
-We link each I/O example with keywords, which appear in the desired output or close to it in the input build log.
-The configuring keywords for KWS are the ones that appear most often in the keywords of the configuring I/O examples.
+To better compare KWS with PBE and CTS, we also configure it through examples.
+We link each example with keywords, which appear in the desired output or close to it in the input build log.
+The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.
 
 \paragraph{Application}
-For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the configuring keywords.
+For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the keywords.
 As keywords are often not directly describing the desired information, but rather appear close to the desired information, KWS also retrieves the lines around the found keyword.
-The number of surrounding lines retrieved is the average of lines in the output of the configuring I/O examples.
+The number of surrounding lines retrieved is the average of lines in the output of the training examples.
 
@@
 \label{sec:expl-rlr}
-There are further build log analysis techniques mentioned in literature and used in industry.
-This section shows how they are described with our notion of chunk retrieval techniques.
+Literature mentions further build log analysis techniques.
+This section describes them with our notion of chunk retrieval techniques.
 
@@
 This technique retrieves the lines from a build log that are not present in the successful build log and contain terms related to the given past failures.
-%Figure~\ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
+
 \paragraph{Random Line Retrieval (RLR)}
 In our evaluation, we want to compare against a baseline of randomly extracted lines.
-The average number of lines in the outputs of a set of I/O examples is the configuration for random line retrieval (RLR).
+The average number of lines in the outputs of the training examples is the configuration for random line retrieval (RLR).
 It retrieves this number of lines randomly sampled from the build log.

### 2019-11-28 thesis/txt/3-data-set.tex
reworking on most sections and linter fixes

@@
 In our first validation study, a second person also labeled a sample of the build logs.
-For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled actually describes the reason the build failed.
+For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled really describes the reason the build failed.
 
 \section{Motivation}
-% For our study, described in Chapter~\ref{sec:study}, we want to investigate the retrieval capabilities of three techniques.
-% Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}.
-% Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output.
-% Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples
 In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
@@
 \paragraph{TravisTorrent}
-The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI.
+The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI\@.
 It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc}, related data from GHTorrent~\cite{gousios2013ghtorrent}, the corresponding git repository and data obtained through analysis of the build logs.
@@
 Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected a large amount of Travis CI build logs from 130 github repositories to analyze their use of the Checkstyle plugin.
-They selected Maven repsitories that included the Checkstyle plugin and also used Travis CI.
-Their data set only provides the plain build logs, whereas \emph{LogChunks} provides manually analyzed build logs from Travis CI.
+They selected Maven repsitories that included the Checkstyle plugin and also used Travis CI\@.
+Their data set only provides the plain build logs, whereas \emph{LogChunks} provides manually analyzed build logs from Travis CI\@.
 
@@
 It then retrieves the most popular repositories for a given language.
-\emph{Popularity} is defined as the number of watches.
-The \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, can then check for a given repository whether it uses Travis CI.
+We define \emph{Popularity} as the number of watches.
+The \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, can then check for a given repository whether it uses Travis CI\@.
 
@@
 We discarded all statuses except one, namely ``failed''~\cite{travis2009buildstatus}, to make the most use of Travis' existing categorization of build status.
-%Travis assigns the Status ``failed'' when the build faults in the central script phase.
-%``Errored'' is assigned when the build faults during the setup or teardown phase.
 
@@
 We manually inspected the collected build logs and had to discard logs from three repositories.
-One had only one failed build, two others had empty build logs on Travis CI.
+One had only one failed build, two others had empty build logs on Travis CI\@.
 In total we collected 797 logs from 80 repositories.
-
-% \section{Collection Process}
-% For our initial data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
-% For \emph{LogChunks} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
-% our impression?
-% \todo{image!}
-
-% \section{Build Failure Reason}
-% \todo{WHY?
-one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined retrieval   cause that would be simple for PROSE retrieval -> better comparability}
 
@@
 Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
-For a few logs we were unable to define the section detailing why the build failed, e.g. because this information was logged in another log file.
+For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
 In these instances the \emph{BuildFailureReason} contains the lines describing that the build failed.
@@
 The structural category compares how the \emph{BuildFailureReasons} are represented within the build logs.
-Build tools highlight their error messages with markings, e.g. starting each line with ``\texttt{ERROR}'', surrounding lines filled with special characters or additional empty log lines.
+Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'', surrounding lines filled with special characters or additional empty log lines.
 Two examples fall into the same structural categories if they are surrounded by similar markings.
@@
 \end{figure}
-
-% \paragraph{Example Set}
-% \label{sec:example-set}
-% Our data set is organized in example sets.
-One example set always contains build log in/output examples from the same software repository or project and for one specific build log information.
-They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
-% Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.
-
-% \paragraph{In / Output Example}
-% In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
-% In our data set they always consist of an \emph{input path}, linking to the build log file which is the input for this example.
-% The \emph{output} is a substring of that build log, the textual representation of the targeted build log information within the input build log.
-
-% \paragraph{Keywords}
-% The keyword search is configured by a list of keywords which are searched in the document with plain text search.
-% In order to compare it to the two other techniques, each in/output example is associated with a list of 1 - 3 keywords that can be found close to the textual representation of the targeted build log information.
-
-% % \paragraph{Description}
-% % \todo{for simple keyword search - imitate what users would search for ad-hoc}
-
-% % \todo{learning steps combining keywords -> similar to how devs would learn from reading those models}
-
-% \paragraph{Categories}
-% Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
-% The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
-% To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
-% If two retrievals are at the same structural location with the build log, meaning they are surrounded by a similar markings, the fall into the same category.
-% For most cases, two build failure reason examples which fall into one category are outputted either within the same build step or by the same build step tool.
 
@@
 To label the \emph{structural categories} we again presented the BuildFailureReason and the surrounding context to the labeler for all logs from a repository.
-We asked them to assign numerical categories according to whether the BuildFailureReason substring had the same structural representation, i.e. the same surrounding or identifying characters.
+We asked them to assign numerical categories according to whether the BuildFailureReason substring had the same structural representation, i.e.\ the same surrounding or identifying characters.
 The labeler should start the categories with 0 and increase as new ones appear.
@@
 A different labeler performed a second pass of labeling the build failure reason, keywords and categories on a subset of the data.
-We compared the results to calculate the inter-rater reliability using Cohens kappa.
 In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set.
@@
 A second labeler processed 30 random generated logs for each data point in \emph{LogChunks}.
-We followed the same labeling process as described in Section \ref{labeling-process}.
+We followed the same labeling process as described in Section~\ref{labeling-process}.
 For the build failure reason and the keywords, we presented 30 randomly sampled build logs from distinct repositories in \emph{LogChunks}.
@@
 This concerns statements like \texttt{The build exited with 1}.
-The second labeler included such statements, while the first one only focussed on the log parts describing \emph{why} the build failed, e.g. the name of the failing test case.
+The second labeler included such statements, while the first one only focussed on the log parts describing \emph{why} the build failed, e.g.\ the name of the failing test case.
 
@@
 Their keywords were in part specific to the failure itself and therefore would not have caught a log part describing a different reason for the build to fail in the test build log.
-%so could take into consideration patterns and see what keywords are exception specific and would only retrieve the failure reason if this specific exception occured.
-%also: influene of ansi color codes ``merror'' vs. ``error'' first labeler known as ansi color codes, second one counted it into the word (whole word always)
-%first was also more inclined to search for a subpart of a word to make it more generalizeable (``failure`` instead of ``failures'')
 
@@
 
-% categories: description for the second labeling stated: sort into categories on why build failed.
-% was exectued with sorting into test/linter/compilation.
-% in the case of the selected repositories everything was labeled as test.
-mostly correct (one linter), but more importantly no difference was made in which test step failed / how the failed tests were represented.
-% the categories are thought as structural categories.
-% so the surrounding sturcture and the way a test failure is communicated is important. e.g. if several tests are run then it is important which ones failed
-
 Our main learning from this study is that adequately communicating all decisions and assumptions on how data is labeled is important and difficult.
-We reviewed the misunderstandings and incorporated more thorough descriptions of our data classes in Secton \ref{sec:data-schema}.
+We reviewed the misunderstandings and incorporated more thorough descriptions of our data classes in Section~\ref{sec:data-schema}.
 
@@
 If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
-In this section we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
+In this section, we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
 \paragraph{Method}
@@
 In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
-As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.
+As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
 
@@
 We received answers from 61 developers, responding about 144 build logs.
-The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds}.
+Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.
 

### 2019-11-28 thesis/txt/5-study.tex
reworking on most sections and linter fixes

@@
 To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluate them on the \emph{LogChunks} data set.
-This chapter describes our study design, detailing which metrics we measure to answer our research questions.
+This chapter describes our study design and which metrics we measure to answer our research questions.
 In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.
@@
 We run four techniques on the Examples from \emph{LogChunks}.
-
 \paragraph{Training and Test Set}
-The data set for this study are the examples from \emph{LogChunks}.
-They contain build logs, the substring describing the reason the build failed, keywords to search for that substring and which structural category the substring belongs to.
+We use \emph{LogChunks} as the data set for our study.
+For each one of 80 repositories it contains about 10 build logs, manually labeled with the substring describing the reason the build failed.
+In addition to that, it contains keywords to search for that substring and which structural category the substring belongs to.
 
 For each repository in \emph{LogChunks}, we split the examples chronologically into training and test set.
-Therefore we train on examples from past build logs and test on future build logs.
-
+Therefore, we train on examples from past build logs and test on future build logs.
 \paragraph{RQ 2.1: Size of Training and Test Set}
 To analyze how many examples the chunk retrieval techniques need to perform best, we evaluate the techniques with different training set sizes.
-We run each technique with one to five examples from each repository within \emph{LogChunks}.
+We train each technique with one to five examples from each of the repositories within \emph{LogChunks}.
 The size of the test set is one.
-
 \paragraph{RQ 2.2: Recording Structural Categories}
 To determine how structurally similar the examples for the chunk retrieval techniques need to be, we record the structural categories of the examples in the training and test sets.
+\paragraph{RQ2.3: Accuracy Metrics}
+To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($retrievedlines$).
+As oracle in our evaluation, we save the desired lines from the output of the test example ($desiredlines$).
 
-\paragraph{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the actual output lines of each chunk retrieval run ($retrievedlines$).
-As oracle in our evaluation, we save the desired lines from the output of the test example ($desiredlines$).
 We calculate the following metrics:
 \begin{itemize}
-	\item \todo{FILL}
 	\item True positives: $TP = desiredlines \cap retrievedlines$
-	\item False positives: $FP = retrievedlines - desiredlines$
-	\item True negatives: $TN = allloglines - (retrievedlines \cup desiredlines)$
-	\item False negatives: $FN = desiredlines - retrievedlines$
+	%\item False positives: $FP = retrievedlines - desiredlines$
+	%\item True negatives: $TN = allloglines - (retrievedlines \cup desiredlines)$
+	%\item False negatives: $FN = desiredlines - retrievedlines$
 	\item Precision: $Precision = TP / retrievedlines$
 	\item Recall: $Recall = TP / desiredlines$
-	\item F-Score:
-	\item Successful Extraction: $true if Recall == 1$
+	%\item F-Score:
+	\item Successful Retrieval: $true if Recall == 1$
 \end{itemize}
 
-% The examples are sorted chronologically, i.e.\ a technique is configured with examples from the directly preceding build logs.
-% For each example set and each technique, we select one to five consecutive I/O examples as configuration, the \emph{training examples}, and run the chunk retrieval on the following I/O example, the \emph{test example}.
+Precision of a chunk retrieval describes which proportion of the retrieved lines were not targeted.
+Recall of a chunk retrieval describes which proportion of the targeted lines were retrieved.
+Throughout the presentation and discussion of our results we keep these two metrics separate, as they might have a different weight when choosing a suitable technique for a task.
 
-% For each of our evaluation runs we measure the desired and the actual output lines of the chunk retrieval.
-% The desired output is given by the output of the test example, which acts as the oracle for our evaluation.
-% From this we obtain true/false positives/negatives and calculate precision, recall and accuracy.
-% We use these values to answer \textbf{RQ2.2}.
-% If all desired lines are extracted, i.e.\ recall is one, we say a chunk retrieval run was \emph{successful}.
-% To answer \textbf{RQ2.1}, we register the number training examples for each run.
-% The structural categories of the training examples are saved to answer \textbf{RQ2.3}.
 Recall and precision of CTS and KWS vary with the number of lines selected for retrieval.
 We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the training examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
-
-%taking The LogChunks data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?
 
@@
 
-% \begin{figure}[htbp]
-% 	\centering
-% 	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
-% 	\caption{Distribution of Category Combinations in the Example Sets used for Configuration in our Study}
-% 	\label{fig:categories-dataset}
-% \end{figure}
-
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/categorycount-examplecount-dataset.pdf}
-% 		\caption{Distribution of the Count of Categories within the Examples used for Configuration in our Study}
-% 		\label{fig:categorycount-examplecount-dataset}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
-% 		\caption{caption}
-% 		\label{fig:xxxy}
-% 	\end{minipage}
-% \end{figure}
-
-% \subsection{Category Distribution in Data Set}
-% Categories distributed in over data set
-% - why are we looking at that?: interesting how categories are distributed for this real world example of build Failure reasons in travis ci categorization
-% - Figure~\ref{fig:categories-dataset} shows the distribution of categories in the configuring example sets in rou study
-% - Figure~\ref{fig:categorycount-examplecount-dataset} shows the category count separated by the different example count.
-
 \subsection{Program Synthesis by Example (PBE)}
@@
 Figure~\ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
-In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
-In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the training examples.
+In 30 cases the synthesized program did not extract all of the desired lines and had an average recall of 28\%.
+In 173 cases the PROSE program synthesis could not synthesize a regular expression program that is consistent with all of the training examples.
 
@@
 For one example there is a high number of empty extraction outputs, meaning that the regular expression synthesized from this one training example could not be applied to the test example.
-For two or more I/O examples the chunk retrieval is in most cases either successful or no consistent program could be synthesized.
+For two or more training examples the chunk retrieval is in most cases either successful or no consistent program could be synthesized.
 
@@
 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training set}
+		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training and test set}
 		\label{fig:failure-reason-categorycount-PBE}
@@
 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision and recall of chunk retrieval with CTS for increasing number of structural categories in the training set}
+		\caption{Precision and recall of chunk retrieval with CTS for increasing number of structural categories in the training and test set}
 		\label{fig:recall-precision-categorycount-CTS}
@@
 \subsection{Common Text Similarity (CTS)}
-Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision and recall of chunk retrieval using CTS for increasing training set size.
-The size of the training set has no visible influence on recall and precision of the chunk retrieval with CTS\@.
+Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision and recall of chunk retrieval using CTS for an increasing number of training examples.
+When using one to five training examples, the size of the training set has no noticeable influence on recall and precision of the chunk retrieval with CTS.
 
-Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for different category counts in the training examples.
+Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for an increasing number of structural categories in the training and test examples.
 With increasing category count, precision and recall decrease.
-Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.
+Especially for more than four categories present we have no chunk retrieval runs where all desired lines were extracted.
 
@@
 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision and recall of chunk retrieval with KWS for increasing number of structural categories in the training set}
+		\caption{Precision and recall of chunk retrieval with KWS for increasing number of structural categories in the training and test set}
 		\label{fig:recall-precision-categorycount-KWS}
@@
 \subsection{Keyword Search (KWS)}
-Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision and recall of chunk retrieval using KWS in our study for different numbers of training examples.
-The recall increases by 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
+Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision and recall of chunk retrieval using KWS for different numbers of training examples.
+The recall increases by about 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
 
-Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for different category counts in the training examples.
-There is no clear trend visible in precision and recall for an increasing amount of categories in the training examples
+Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for increasing number of structural categories in the training and test examples.
+There is no clear trend visible in precision and recall for an increasing amount of categories in the training and test examples
 
@@
 Figure~\ref{fig:retrievalsizefactor-retrievalratio-KWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS\@.
-When retrieving the mean number of lines in the training examples, 15\% of the log lines are retrieved on average.
+When retrieving the average number of lines in the outputs of the training examples, 15\% of the log lines are retrieved on average.
 This proportion goes up to 25\% when retrieving 1.5 times more lines.
-
-% \begin{figure}[htbp]
-% 	\centering
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
-% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR}
-% 		\label{fig:precision-all}
-% 	\end{minipage}\hfill
-% 	\begin{minipage}{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
-% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR for single and multiple categories present in the training examples}
-% 		\label{fig:precision-category-singularity-all}
-% 	\end{minipage}
-% \end{figure}
 
@@
 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-all.pdf}
-		\caption{Precision and Recall of all techniques compared}
+		\caption{Precision and recall of all techniques compared}
 		\label{fig:recall-precision-all}
@@
 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision and Recall of all techniques compared when training examples are in \emph{one} structural category}
+		\caption{Precision and recall of all techniques compared when training examples are in \emph{one} structural category}
 		\label{fig:recall-precision-singlecategory-all}
@@
 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision and Recall of all techniques compared when training examples are in \emph{more than one} structural categories}
+		\caption{Precision and recall of all techniques compared when training examples are in \emph{more than one} structural categories}
 		\label{fig:recall-precision-multicategory-all}
@@
 
-% \begin{table}[htbp]
-% \centering
-% \begin{tabular}{ |c||c|c|c| }
-% 	\hline
-%   Technique & \multicolumn{3}{|c|}{Desired Lines extracted} \\
-%   \hline
-%   & all [0.345 , 0.2025, 0.3825, 0.005 ] & partial [0.045 , 0.5875, 0.4525, 0.3025] & none [0.61  , 0.21  , 0.165 , 0.6925] \\
-%   \hline
-%   & recall = 1 & 0 < recall < 1 & recall = 0 \\
-%   \hline
-%   PBE & 138 & 18 & 244 \\ 
-%   CTS & 81 & 235 & 84 \\ 
-%   KWS & 153 & 181 & 66 \\ 
-%   RLR & 2 & 121 & 277 \\ 
-%   \hline
-% \end{tabular}
-% \caption{Comparison of successful extractions for PBE, CTS, KWS and RLR}
-% \label{tab:101}
-% \end{table}
-
 \subsection{Comparison of All Techniques}
 Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval of the different techniques in our study.
-CTS and KWS extract at least some of the desired lines in 79\% and 88.5\%.
+CTS and KWS extract some of the desired lines in 79\% and 88.5\%.
 With 38.25\%, KWS also has the highest number of successful extractions, followed by PBE with 34.5\%.
@@
 The averaged precision and recall of all techniques is compared in Figure~\ref{fig:recall-precision-all}.
-PBE has a high skew towards one and zero for both measurements, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
+The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
 Chunk retrieval with CTS has the highest average precision with 46\% and the second best recall with 45\%.
@@
 Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
-For more than one present category, precision and recall of PBE greatly decrease.
-For CTS and KWS the values also decrease slightly, while RLR is not affected by the number of structural categories present.
+For more than one present category, the recall of PBE decreases greatly.
+For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.
 

### 2019-11-28 thesis/txt/6-discussion.tex
reworking on most sections and linter fixes

--- 2019-11-22 thesis/txt/6-discussion.tex
@@
 The first section discusses for PBE, CTS and KWS separately in which cases they perform best.
-It details for which types of input build logs, available configuration I/O examples and use case of the retrieved output each technique is suited.
-The next section compares the three techniques and clarifies which one is recommended by our study results for different use cases.
+It details for which types of input build logs, available training examples and consumption of the retrieved output each technique is suited.
+In the following section we discuss which of these criteria should influence the decision on a technique most.
+Based on our empirical comparison, we present a decision tree between the three techniques we investigated.
 
@@
 This section discusses the study results for each of the analyzed chunk retrieval techniques separately.
-It gives recommendations on which kind of configuration is best for each technique and for what kind of usage the output is suitable.
+It gives recommendations on which kind of information chunk targets are best for each technique and for what kind of usage the output is suitable.
 
@@
 \paragraph{Configuration and Input}
-Our study results show, that chunk retrieval with PBE gives best results when the configuring I/O examples are from one structural category.
-This means it is suited to retrieve BLIs, whose textual representation always has the same surrounding structure.
+Our study results show that chunk retrieval with PBE gives best results when the training examples are from one structural category.
+This means it is suited to retrieve information chunks that always have the same surrounding structure.
 To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.
 
-When all configuring I/O Examples are of the same structure, one to three examples are enough input for PROSE to synthesize a correct regular expression program.
-In our study, additional examples did not improve the quality of the chunk retrieval.
+When the training examples are of the same structure, one to three examples are enough input for PROSE to synthesize a regular expression program.
+In our study, additional training examples did not improve the chunk retrieval.
 
 \paragraph{Retrieval Output Usage}
-When the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and high recall for chunk retrieval.
-A failure in the program synthesis or no output from the synthesized program is clearly identified by the tool.
+If the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and high recall.
+The tool clearly identifies a failing program synthesis or no output from the program applied to a build log.
 Therefore, if there is an output, the user can have high confidence it is the correct output.
@@
 \paragraph{Configuration and Input}
-Chunk retrieval using CTS also yields good results if more than one structural category is present in the configuring I/O examples.
-The number of configuring I/O examples had no measurable influence on the extraction quality in our study.
+Chunk retrieval using CTS also yields better results the fewer structural categories are present in the training examples.
+The number of training examples had no noticeable influence on the extraction quality in our study.
 Information retrieval techniques like text similarity commonly learn on a higher number of examples than we used for our study.
-Future work is needed to investigate how many examples yield improvements in the chunk retrieval over a single configuring I/O example.
+Future work is needed to investigate how many examples yield improvements in the chunk retrieval over a single training example.
 
-Extracting the average number of lines present in the configuring I/O examples seems to give the best balance of precision and recall for CTS\@.
+Extracting the average number of lines present in the training examples seems to give the best balance of precision and recall for CTS\@.
 
@@
 \paragraph{Configuration and Input}
-The number of structural categories in the configuring I/O examples have little impact on the extraction quality of KWS\@.
+The number of structural categories in the training examples have little impact on the extraction quality of KWS\@.
 This makes KWS a good technique if there is little prior knowledge on how the desired BLI is represented in the build log to be analyzed.
-For the example of extracting the build failure reason, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
+For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
 
-To achieve good recall of the retrieval, at least two examples should be given as configuration.
+With at least two training examples KWS achieves good recall.
 
-Retrieving the average number of lines present in the outputs of the configuring I/O examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does improve the recall in our study but also increases the proportion of lines retrieved overall and therefore decreases precision.
+Retrieving the average number of lines present in the outputs of the training examples around every found keyword yields reasonable recall.
+Selecting 1.5 times as many lines around every found keyword does improve the recall within our study but also increases the proportion of lines retrieved overall and therefore decreases precision.
 
@@
 \section{Recommendations of Suitable Techniques}
-This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS\@.
-It recommends which technique to use depending on the available configuration and 
-TABLE!
-\paragraph{Configuration and Input}
-number of categories:
-one? -> pbe
-two? -> CTS
-more? -> KWS
-available examples:
-little?
--> try pbe (This depends on the categories!
-here we might want a decision tree to represent the importance of these characteristics against each other?
-<- this would also anwser RQ1: which ones of the criteria we compare are the most important)
-multiple -> kws
-very many? -> CTS
+% This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS\@.
+% It recommends which technique to use depending on the available configuration and 
+After discussing three chunk retrieval techniques separately we now want to unify out results into one recommendation scheme.
+We present a decision tree, which asks questions to a developer or researcher who wants to retrieve information chunks from build logs.
+The answers lead the user to more questions or the recommended technique as leaf nodes.
+Figure~\ref{fig:crt-recommendation} presents the decision tree.
 
-\paragraph{Retrieval Output Usage}
-precision needed:
+\emph{Caveat!} This is a preliminary theory based on the results from our comparison study.
+The recommendations are therefore likely based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
+This decision tree is the answer to our first research question about which criteria influence the suitability of a chunk retrieval technique.
+The earlier in the decision tree a criterion is noted, the more important it is when distinguishing the techniques.
+
+The first and most important aspect are the structural categories.
+Are the information chunks you would like to retrieve always presented in the same structural way within the build logs?
+Then the information chunks in all training examples and the analyzed build log are in the same structural category.
+
+If the information chunks are from multiple structural categories, meaning the are not represented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS\@.
+If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
+We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the accuracy of the outcome and the user rather have output with low recall instead of no output at all.
+When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.
 
 \begin{table}[htbp]
-\begin{tabular}{|c||c|c|c|}
+\centering
+\begin{tabularx}{\textwidth}{@{}llll@{}}
+  \toprule
   & PBE & CTS & KWS \\
-  \hline
-  \hline
-  Structural Categories & 1 & best if 1 & no influence \\
+  \midrule
+  Structural Categories & 1 & less is better & no influence \\
   Training Set Size & 1 - 3 & no influence & > 2 \\ 
-  Precision & high (if synthesis succeeds) & medium & low \\ 
-  Recall & high (if synthesis succeeds) & medium & high \\ 
-  Confidence in Output Correctness & high & low & low (precision), high (recall) \\ 
+  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
+  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
+  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
   Output Consumption by & program & human & human \\ 
-  \hline
-\end{tabular}
+  \bottomrule
+\end{tabularx}
 \caption{Recommendations for each of the investigated chunk retrieval techniques}
-\label{tab:101}
+\label{tab:single-technique-recommendations}
 \end{table}
@@
 		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
-		\label{fig:fcrt-recommendation}
+		\label{fig:crt-recommendation}
 \end{figure}
@@
 \section{Threats to Validity}
-chronologically selected examples -> very specific view, devs/users might pick more representative examples
 
-very few evaluation runs with a high number of categories in configuring I/O examples -> because we chose to create such a ``realistic'' data set, from data set we see that many structural categories uncommon
+There are several threats to the validity of the conclusions of our work.
 
-some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed
+\paragraph{Implementation}
+Our results are highly dependent on our implementation of the investigated chunk retrieval techniques and the libraries we used.
+Our implementation of PBE is mainly based on the program synthesis provided by PROSE\@.
+Its limitations are therefore also mainly influenced by this library.
+For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with (too many?) top level OR operators.
+\mention{CITATION NEEDED}
+This limitation was necessary to keep the synthesis performance reasonable.
 
+Our implementation of CTS is dependent on the library tex2vec and the way they split strings into word tokens.
+We intentionally chose a simple, minimally configured and tuned approach to compare against.
+Tuning the text similarity meta-parameters more to the specific use case of chunk retrieval from build logs would yield better chunk retrieval results.
+
+\paragraph{Data Set}
+The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
+It only consists of build logs from open source and therefore it is not clear whether our results are generalizable to industry projects.
+We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
+This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI environment.
+
+\paragraph{Training Set Size}
+Especially the results for CTS are influenced by the fact that we only trained on one to five examples.
+Information retrieval techniques commonly learn on larger data sets. \mention{CITATION NEEDED}
+We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.
+
+\paragraph{Few Samples with Many Structural Categories}
+Our comparison study shows fewer measurements with many structural categories than with one category.
+This stems from the fact that we use such a realistic data set which in many cases has only one or few structural categories.
+% \bp{
+% chronologically selected examples -> very specific view, devs/users might pick more representative examples
+
+% very few evaluation runs with a high number of categories in configuring I/O examples -> because we chose to create such a ``realistic'' data set, from data set we see that many structural categories uncommon
+
+% some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed}
 \end{document}

### 2019-11-28 thesis/txt/7-conclusion.tex
reworking on most sections and linter fixes

@@
 Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
-Secondary factors are confidence in the produced output and whether precision or recall are more important for the task at hand.
+Secondary factors are confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.
 
@@
 \begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set specifically for our comparison study, though it can be the basis for various further analyses of build log data.
-  The keywords can be investigated to answer which keywords do developers use to search for the reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from one repository.
+  \item \textbf{Further Analysis of the \emph{LogChunks} Data Set} We created the \emph{LogChunks} data set specifically for our comparison study, though it can be the basis for various further analyses of build log data.
+  The keywords, for example, can be investigated to answer which keywords do developers use to search for the reason the build failed within build logs.
+  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
   We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This thesis investigates the three chunk retrieval techniques PBE, CTS and KWS.
-more techniques (which kinds of techniques?
-express in model!
-e.g.\ diffs might not work?), same evaluation, ir automated keyword search/expansion
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations existing techniques applied to chunk retrieval from build logs.
+  \item \textbf{Comparison with more Chunk Retrieval Techniques} This thesis investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
+  Our study design can be reused to evaluate other build log analysis techniques.
+  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
   In a next step, each of these techniques could be refined and configured to better approach the domain of build logs.
@@
       \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
-      The ranking rules provided by the FlashExtract DSL could be adapted to fit common build log chunk retrieval tasks.
+      We could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
       FlashExtract includes special tokens when enumerating possible regular expressions.
-      These could be extended with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
+      We could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
       \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.

### 2019-11-29 thesis/txt/2-models.tex
updated model graphics and dev mail screenshot

@@
 Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval Length          \\
-Diff Approach                &         & Line not present in successful log, informatino retrieval  & Line        & Successful Log File       \\
+Diff Approach                &         & Line not present in successful log, information retrieval  & Line        & Successful Log File       \\
 \bottomrule

### 2019-11-29 thesis/txt/6-discussion.tex
updated model graphics and dev mail screenshot

@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/crt-recommendation.pdf}
+		\includegraphics[width=\textwidth, clip]{img/crt-recommendation.pdf}
 		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
@@
 Its limitations are therefore also mainly influenced by this library.
-For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with (too many?) top level OR operators.
-\mention{CITATION NEEDED}
+For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
 This limitation was necessary to keep the synthesis performance reasonable.
@@
 \paragraph{Training Set Size}
-Especially the results for CTS are influenced by the fact that we only trained on one to five examples.
-Information retrieval techniques commonly learn on larger data sets. \mention{CITATION NEEDED}
+Especially the results for CTS might influenced by the fact that we only trained on one to five examples.
 We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.

### 2019-12-02 thesis/txt/0-introduction.tex
update graphics to violin plots, adjust some text and make graphics color blind accessible

@@
 How many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is(\textbf{RQ2.3}).
-% \begin{simplebox}{Research Questions}
-% \begin{itemize}
-%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
-%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
-%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
-% \end{itemize}
-% \end{simplebox}
 To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
@@
 \begin{itemize}
-  \item PBE yields very accurate results when trained with 1 to 3 examples from a single structural category.
-  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
+  \item PBE yields very accurate results when trained with two examples from a single structural category.
+  \item CTS shows the best average precision, though precision and recall of a retrieval is hard to determine from the given result.
   A small increase in the number of training examples has no noticeable influence.
-  Fewer structural categories improve the retrieval accuracy.
+  Fewer structural categories improve precision and recall of the retrieval.
   \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the only technique where retrieval accuracy does not decrease with an increasing number of structural categories in the training examples.
+  It is the technique with the best recall when multiple structural categories are present in the training examples.
 \end{itemize}
-We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in the accuracy of the chunk retrieval is required.
+We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in precision and recall of the chunk retrieval is required.
 CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
@@
   \item A model to characterize chunk retrieval techniques from CI build logs.
-  %\item A model to characterize use case scenarios for information retrieval from CI build logs
   \item A tool unifying several chunk retrieval techniques namely:
@@
         \end{itemize}
-  %\item The \emph{LogCollector}, a tool to gather build logs from Travis CI
   \item A validated data set of about 800 logs from failed Travis CI builds manually-labelled with:
@@
 
+Following we show selected plots from the study results section. RLR stands for the baseline technique \emph{Random Line Retrieval}:
+
+\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/success-partial-all.pdf}
+		\caption{Success of chunk retrievals for all techniques}
+		\label{fig:success-partial-all}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
+		\caption{Precision and recall of all techniques compared when training examples are in \emph{one} structural category}
+		\label{fig:recall-precision-singlecategory-all}
+\end{figure}
+
+\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
+		\caption{Precision and recall of all techniques compared when training examples are in \emph{more than one} structural categories}
+		\label{fig:recall-precision-multicategory-all}
+\end{figure}
+
 \end{document}

### 2019-12-02 thesis/txt/5-study.tex
update graphics to violin plots, adjust some text and make graphics color blind accessible

@@
 	\item True positives: $TP = desiredlines \cap retrievedlines$
-	%\item False positives: $FP = retrievedlines - desiredlines$
-	%\item True negatives: $TN = allloglines - (retrievedlines \cup desiredlines)$
-	%\item False negatives: $FN = desiredlines - retrievedlines$
-	\item Precision: $Precision = TP / retrievedlines$
-	\item Recall: $Recall = TP / desiredlines$
-	%\item F-Score:
-	\item Successful Retrieval: $true if Recall == 1$
+	\item Precision: $Precision =  \frac{\# TP}{\# retrievedlines}$
+	\item Recall: $Recall = \frac{\# TP}{\# desiredlines}$
+	\item Successful retrieval: $true\ if\ Recall = 1$
 \end{itemize}
@@
 Throughout the presentation and discussion of our results we keep these two metrics separate, as they might have a different weight when choosing a suitable technique for a task.
+We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
 
@@
 
-Figure~\ref{fig:precision-extraction-result-PBE} compares the precision of the PBE chunk retrieval runs with the training set size.
-For one example there is a high number of empty extraction outputs, meaning that the regular expression synthesized from this one training example could not be applied to the test example.
-For two or more training examples the chunk retrieval is in most cases either successful or no consistent program could be synthesized.
+Figure~\ref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of runs where PBE could synthesize a program consistent with all training examples.
+When the training set size increases from one to two, recall increases by 24\% and precision increases by 10\%.
+For two or more training examples the recall stays around 75\% and precision around 96\%.
 
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
-		\caption{Precision of chunk retrieval with PBE for increasing training set size}
-		\label{fig:precision-extraction-result-PBE}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+		\caption{Precision and recall of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set}
+		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
 \end{figure}
@@
 
-Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS\@.
+Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision and recall of chunk retrieval runs with CTS\@.
 The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
@@
 
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=0.5\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
-		\caption{Ratio of lines retrieved with KWS compared to retrieval size factor}
-		\label{fig:retrievalsizefactor-retrievalratio-KWS}
-\end{figure}
-
 \subsection{Keyword Search (KWS)}
@@
 Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for increasing number of structural categories in the training and test examples.
-There is no clear trend visible in precision and recall for an increasing amount of categories in the training and test examples
+For more than one structural category in the training and test examples the recall decreases about 20\% and the precision decreases about 6\%.
+For more than two structural categories no clear trend visible in precision and recall for an increasing amount of categories in the training and test examples.
 
-Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with KWS\@.
-The precision ranges from 19\% when retrieving half expected number of lines to 10\% when 2.5 times the expected number of lines.
+Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision and recall of chunk retrieval runs with KWS\@.
+The precision is 19\% when retrieving half expected number of lines. On average 9\% of the lines in the build log are retrieved then.
+When 2.5 times the expected number of lines, the precision decreases to 10\% and a quater of the lines in the build log are retrieved on average.
 The recall ranges from 58\% to 75\%.
-
-Figure~\ref{fig:retrievalsizefactor-retrievalratio-KWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS\@.
-When retrieving the average number of lines in the outputs of the training examples, 15\% of the log lines are retrieved on average.
-This proportion goes up to 25\% when retrieving 1.5 times more lines.
 

### 2019-12-02 thesis/txt/6-discussion.tex
update graphics to violin plots, adjust some text and make graphics color blind accessible

@@
 
-When the training examples are of the same structure, one to three examples are enough input for PROSE to synthesize a regular expression program.
+When the training examples are of the same structure, two examples are enough input for PROSE to synthesize a regular expression program with good recall.
 In our study, additional training examples did not improve the chunk retrieval.
@@
 \paragraph{Configuration and Input}
-Chunk retrieval using CTS also yields better results the fewer structural categories are present in the training examples.
-The number of training examples had no noticeable influence on the extraction quality in our study.
+Chunk retrieval using CTS also yields better results the fewer structural categories are present in the training and test examples.
+The number of training examples had no noticeable influence on precision or recall in our study.
 Information retrieval techniques like text similarity commonly learn on a higher number of examples than we used for our study.
@@
 \paragraph{Retrieval Output Usage}
-CTS has good precision and recall on average, though the quality of a chunk retrieval run is very hard to predict from the given result.
+CTS has good precision and recall on average, though the precision or recall of a chunk retrieval run is very hard to predict from the given result.
 Therefore, retrieval output from CTS is suited to be read by a human.
@@
 \paragraph{Configuration and Input}
-The number of structural categories in the training examples have little impact on the extraction quality of KWS\@.
+KWS has a higher recall than both other techniques for multiple structural categories present in the training and test examples.\@.
 This makes KWS a good technique if there is little prior knowledge on how the desired BLI is represented in the build log to be analyzed.
@@
 
-With at least two training examples KWS achieves good recall.
+With two training examples KWS achieves good recall.
 
@@
 If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
-We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the accuracy of the outcome and the user rather have output with low recall instead of no output at all.
+We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the precision or recall of the outcome and the user rather have output with low recall instead of no output at all.
 When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.
@@
   \midrule
-  Structural Categories & 1 & less is better & no influence \\
-  Training Set Size & 1 - 3 & no influence & > 2 \\ 
+  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
+  Training Set Size & 2 & no influence & 2 \\ 
   Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 

### 2019-12-02 thesis/txt/0-introduction.tex
fix decision tree graphic, remove list of listings, remove graphs for pretschner from introduction

@@
 Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
-Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion-fw}.
+Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion-fw}.%\\\\
 
-Following we show selected plots from the study results section. RLR stands for the baseline technique \emph{Random Line Retrieval}:
+% Following we show selected plots from the study results section. RLR stands for the baseline technique \emph{Random Line Retrieval}:
 
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques}
-		\label{fig:success-partial-all}
-\end{figure}
+% \begin{figure}[htbp]
+% 		\centering
+% 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/success-partial-all.pdf}
+% 		\caption{Success of chunk retrievals for all techniques}
+% 		\label{fig:success-partial-all}
+% \end{figure}
 
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision and recall of all techniques compared when training examples are in \emph{one} structural category}
-		\label{fig:recall-precision-singlecategory-all}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
+% 		\caption{Precision and recall of all techniques compared when training examples are in \emph{one} structural category}
+% 		\label{fig:recall-precision-singlecategory-all}
+% \end{figure}
 
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision and recall of all techniques compared when training examples are in \emph{more than one} structural categories}
-		\label{fig:recall-precision-multicategory-all}
-\end{figure}
+% \begin{figure}[htbp]
+% 		\centering
+% 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
+% 		\caption{Precision and recall of all techniques compared when training examples are in \emph{more than one} structural categories}
+% 		\label{fig:recall-precision-multicategory-all}
+% \end{figure}
 

### 2019-12-03 thesis/txt/3-data-set.tex
cleanup some graphics, incorporate easy Martijn Feedback

@@
 For each build log we manually labeled which substring describes why the build failed.
-Four our evaluation of the chunk retrieval techniques PBE, CTS and KWS we added search keywords and structural categories to each of the labeled substrings.
+For our evaluation of the chunk retrieval techniques PBE, CTS and KWS we added search keywords and structural categories to each of the labeled substrings.
 
@@
 Further, it presents the labeling process and how we validated the obtained data points.
-In our first validation study, a second person also labeled a sample of the build logs.
+In the first validation study, we compared the labeled data points with those of a second labeler on a sample of the build logs.
 For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled really describes the reason the build failed.
@@
 The \texttt{LogCollector} uses the \texttt{TravisRequester} to obtain the newest builds for a given repository.
-Wwe use a stratified sampling approach: \texttt{TravisRequester} saves the obtained builds in buckets according to their status.
+It uses a stratified sampling approach: \texttt{TravisRequester} saves the obtained builds in buckets according to their status.
 We encountered the following statuses during our data collection:
@@
 \texttt{TravisRequester} queries each build for the first job, which has the same state.
-For the selected jobs, the tool queries the Travis API V3 over HTTP to obtains the corresponding build log.
+For the selected jobs, the tool queries the Travis API V3 over HTTPS to obtains the corresponding build log.
 
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
-	\caption{Distribution of the categories in LogChunks}
-	\label{fig:categorycount-examplecount-dataset}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
+% 	\caption{Distribution of the categories in LogChunks}
+% 	\label{fig:categorycount-examplecount-dataset}
+% \end{figure}
 
@@
 There are no special limitations on the string itself, especially spaces are also allowed.
-Regular Expressions are not allowed.
 
@@
 We validate our collected data points in two different ways.
-A different labeler performed a second pass of labeling the build failure reason, keywords and categories on a subset of the data.
+A different labeler performed a second pass of labeling the build failure reason, keywords and structural categories on a subset of the data.
 In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set.
@@
 \paragraph{Method}
-A second labeler processed 30 random generated logs for each data point in \emph{LogChunks}.
-We followed the same labeling process as described in Section~\ref{labeling-process}.
+The second labeler processed 30 random generated logs for each data point in \emph{LogChunks}.
+We followed the same labeling process as described in Section~\ref{sec:labeling-process}.
 For the build failure reason and the keywords, we presented 30 randomly sampled build logs from distinct repositories in \emph{LogChunks}.
-As the structural categories are always relative to the other logs from the same repository we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.
+The labeled structural categories are relative to the other logs from the same repository.
+Therefore, we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.
 
@@
 \paragraph{Discussion}
-The results of this validation study show that there is overlap in the data from the two labelers, however also a high variation.
-We mainly attribute this to not specific enough instructions to the second labeler.
+The results of this validation study show that there is overlap in the data from both labelers, however also a high variation.
+We believe that the main cause for this is that our explanations to the second labeler were not extensive enough.
 There were implicit, inconsistent assumptions both labelers created during their work.
-In the following we describe the inconsistent assumptions between both labelers for each data point and the implications on our description of the data classes.
+In the following we describe these assumptions from both labelers for each data point and the implications on our description of the data classes.
 
 For the first data class, the reason the build failed, it was ambiguous whether the labeled substring should contain the information \emph{that} the build failed.
-This concerns statements like \texttt{The build exited with 1}.
-The second labeler included such statements, while the first one only focussed on the log parts describing \emph{why} the build failed, e.g.\ the name of the failing test case.
+This concerns statements like ``\texttt{The build exited with 1}''.
+One labeler included such statements, while the other one only focussed on the log parts describing \emph{why} the build failed, e.g.\ the name of the failing test case.
 
-While labeling the keywords a developer would use to search for the log part describing why the build failed, the first labeler allowed arbitrary, case-sensitive strings.
-In contrast to that, the second labeler focussed on actual \emph{words}, delimited by spaces or special characters, while ignoring capitalization.
-A second difference was that the first labeler was presented with all substrings from a repository, yielding more general keywords than the second labeler.
-Their keywords were in part specific to the failure itself and therefore would not have caught a log part describing a different reason for the build to fail in the test build log.
+While labeling the keywords a developer would use to search for the log part describing why the build failed, the one labeler allowed arbitrary strings appearing around the presented log part.
+In contrast to that, the other labeler focussed on actual \emph{words}, delimited by spaces or special characters.
+One labeler ignored capitalization, while the other one selected case-sensitive keywords.
+A third difference was that the first labeler was presented with all substrings from a repository, yielding more general keywords than the second labeler.
 
@@
 
-\paragraph{Introduction}
 For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
@@
 In this section, we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
+
 \paragraph{Method}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
-		\caption{Label correctness as validated by developers}
-		\label{fig:mails-extraction-correct}
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
+		\caption{Proportions of logs about which mails were answered, unanswered, not delivered or we could not find a corresponding mail address}
+		\label{fig:mails-answers-received-builds}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
-		\caption{Proportions of logs answered, undelivered and unanswered}
-		\label{fig:mails-answers-received-builds}
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
+		\caption{Label correctness as validated by developers}
+		\label{fig:mails-extraction-correct}
 	\end{minipage}\hfill
@@
 26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
-We manually inspected these negative answers and found that extractions were correct after all.
+We manually inspected these negative answers and found that some extractions were correct after all.
 This yields 12 log extractions in our example set that were not correct, shown in Figure~\ref{fig:mails-extraction-correct}.
@@
 This study highly strengthens the trust in the validity of the extracted build failure reasons in \emph{LogChunks}.
-The study received answers about 18\% of the logs labelled in our build log, of which, after manual correction, 91\% said our labelled extractions were accurate.
+The study received answers about 18\% of the logs from \emph{LogChunks}.
+After manual correction, 91\% of the received answers said our labelled extractions were accurate.
 
-Most of the initial ``incorrect'' answers we adjusted in them manual inspection, stated that the proposed extraction did not show the whole reason the build failed.
+Most of the initial ``incorrect'' answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
 This is because we had to trim long labeled extractions to keep the emails readable.
 
-One of our extractions only showed a warning and the developer propose to also include the line above, stating that warnings are treated as errors in the build.
-In others that were identified as ``incorrect'' we labelled the error message of an error that later ignored and did not lead to the build failing.
+One of our extractions only showed a warning and the developer proposed to also include the line above, stating that warnings are treated as errors in the build.
+In others that were identified as ``incorrect'', we labelled the error message of an error that later ignored and did not lead to the build failing.
 

### 2019-12-03 thesis/txt/1-related-work.tex
improving story of rw and smaller text fixes

@@
 \label{sec:rw}
-This section presents various research works adjacent or foundational to our work.
-To start, we describe studies about continuous integration (CI) and how they gather information about CI usage in software projects.
-Next, the section moves on to works about build log analysis and their augmentation, which are related to the techniques we analyze in this thesis.
-We differentiate our work from system log analysis and show how we classify build logs as semi-structured data.
-The section describes how chunk retrieval can be employed as a part of presented information extraction approaches.
-We introduce how information retrieval techniques, the basis for CTS, are used to improve software development.
-Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library, the foundation of PBE\@.
+This chapter presents various research works adjacent or foundational to our work.
+The first section presents existing work in the field of continuous integration (CI) and showcases how researchers analyze build logs.
+In the second section we describe the existing methods which are the foundation for the chunk retrieval we investigate.
 % moritz: nice formulation :)
@@
 \section{Continuous Integration and Build Logs}
+We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
+We explain how the researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
+Next, this section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
+The presented approaches are related to and can benefit from the techniques we analyze in this thesis.
+Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.
+% CI describes the practice of integrating, building and testing source code changes often and fast.
+% The tools involved in a CI build communicate their progress and status through a combined build log.
+% In Section~\ref{sec:bl-characteristics}, we describe CI builds and how
+
+% We investigate different techniques which developers and researchers can employ to retrieve information from CI build logs.
+% In this section we present
+
+% research about CI to show that it is a relevant topic in research
+
+% explain methods of those researchers, how they analyzed build logs and how the chunk retrieval techniques we investigate can support them.
+
+% we present existing research into analyzing verbose build logs to help developers intercating with them.
+
+% Following we classify build logs as semi structured data.  and differentiate our work from system log analysis.
+
 \subsection{Continuous Integration}
-This section starts with an overview on research into why CI is used and its impact on development.
-It presents analyses on why CI builds fail and how testing and static analysis tools are used within CI\@.
-We explain how researchers compose data sets for their work on CI and how chunk retrieval techniques can support them.
+The first paragraphs of this section present the results of past research into CI: its influence on the software engineering processes, the reasons for CI builds to fail and the role of testing and static analysis in CI builds.
+Later we describe how these researchers obtain the data sets these works are based on.
+We show how they analyze build logs and why the chunk retrieval techniques we investigate can support them to broaden their studies.
+% This section starts with an overview on research into why CI is used and its impact on development.
+% It presents analyses on why CI builds fail and how testing and static analysis tools are used within CI\@.
+% We explain how researchers compose data sets for their work on CI and how chunk retrieval techniques can support them.
 
 \paragraph{Motivation for CI and Impact of CI}
+Why teams choose to use CI and its impac on the software development process is explored by several existing works.
 Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
@@
 They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
-Vasilescu et al.~\cite{vasilescu2015quality} analyzed a broad rage of open source projects written in popular languages on GitHub.
-They compared their usage of CI with the successful merges of pull requests and found that CI increase the number of successful merges, internal as well as external contributions, and allows the team members to uncover more bugs.
-In a new study, Vasallo et al.~\cite{vassallo2019every} interview developers on how they determine why a CI build failed.
+Vasilescu et al.~\cite{vasilescu2015quality} analyze a broad rage of open source projects written in popular languages on GitHub.
+They compare their usage of CI with the successful merges of pull requests and find that CI increase the number of successful merges, internal as well as external contributions, and allows the team members to uncover more bugs.
+In a recent study, Vasallo et al.~\cite{vassallo2019every} interview developers on how they determine why a CI build failed.
 They model how these developers resolve failures.
-The first and most important steps when developers want to fix a build failure is locating the error within the build log.
+The first and most important steps when developers want to fix a build failure is to locate the error within the build log.
 Then the developers use the additional information provided with and around the error message to understand the details of the failures.
+This shows that the build log is a central source of information about a CI build.
 % Vassallo et al.~\cite{vassallo2018continuous} conducted a survey study on how ci influences developers to continuously refactor their code to fix ci quality analysis warnings.
@@
 \paragraph{Build Failures in CI}
-Various researchers looked into why CI builds fail and the impact of build failures on the development workflow.
-Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google.
-In addition most failures are resolved within two builds and a small percentage of error types account for most of the build failures.
-Rausch et al.~\cite{rausch2017empirical} analyzed CI builds of open source java procjects and categorize why builds failed.
-Most fail because of test  and for most porojects over half of failed biuilds follow another failed build.
-Found that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
-Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones.
-They determined that testing failures outweigh compilation errors.
+Various researchers look into why CI builds fail and the impact of build failures on the development workflow.
+Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
+In addition, most failures are resolved within two builds.
+Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and categorize why builds failed.
+Most builds fail because of failing tests.
+For most projects, over half of the failed builds follow another failed build.
+Their data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
+Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
+They determine that testing failures are more common than compilation errors.
 Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
@@
 \paragraph{Static Analysis and Testing in CI}
-Automated static analysis tools are the focus of Zampetti et al.~\cite{zampetti2017open} in ther study of java projects from GitHub.
-Their results show that static analysis in responsible for a small amount of build failures and mainly responsible for warned builds.
-Almost all projects use custom configurations for the static analysis, however the configuration rarely changes.
+Automated static analysis tools are the focus of Zampetti et al.~\cite{zampetti2017open} in their study of java projects from GitHub.
+Their results show that static analysis is responsible for a small amount of build failures and mainly responsible for warned builds.
+Almost all analyzed projects use custom configurations for the static analysis, however the configuration rarely changes.
 Failures because of static analysis warnings are fixed in a short time frame.
-Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
-They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.
+Beller et al.~\cite{beller2017oops} show that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
+They observe a high variety between programming langues, i.e. in the kind and number of tests which are run, as well as how often tests fail.
+The low failure rates on the CI server hint at code being tested before it is sent to the server.
 
@@
 The works presented in this section are based on either developer surveys or data sets, containing build metadata or build logs.
-Seo et al..~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
-Beller et al.\ created the \emph{TravisTorrent} data set~\cite{beller2017travistorrent} providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
+Seo et al.~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
+Beller et al.~\cite{beller2017travistorrent} created the \emph{TravisTorrent} data set providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
 TravisTorrent was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
@@
 \paragraph{Build Log Analysis in CI Research}
-For Seo et al.~\cite{seo2014programmers} the build logs were the primary data source for their analysis and they developed a custom parser to classify error messages reported by Java and C++ builds. 
-Vassallo et al.~\cite{vassallo2017a-tale} analyzed collected build logs by extraction error messages using regular expressions.
-The regular expressions were looking for keywords identified in a manual analysis.
+Several of the works we mentioned until now analyze build logs to obtain information about the CI builds. 
+For Seo et al.~\cite{seo2014programmers} the build logs are the primary data source for their study.
+They develop a custom parser to classify error messages reported by Java and C++ builds. 
+Vassallo et al.~\cite{vassallo2017a-tale} analyze collected build logs by extracting error messages using regular expressions.
+The regular expressions search for keywords identified in a manual analysis.
 The analysis of Ghaleb et al.~\cite{ghaleb2019studying} starts with manual categorization of build logs.
-They select keywords and strings that identify one of their noise categories and coded script to automatically classify logs based on these keywords.
-To validate the script results, they performed another manual classification.
-Beller et al.~\cite{beller2017oops} focus their analysis on java and ruby build logs for which they built custom parsers with regular expressions to extract the reason a build failed.
+They select keywords and strings that identify their noise categories and code a script to automatically classify logs based on these keywords.
+%To validate the script results, they performed another manual classification.
+Beller et al.~\cite{beller2017oops} focus their analysis on Java and Ruby build logs for which they build custom parsers with regular expressions to extract the reason a build failed.
 
 \paragraph{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs these researchers built parsers and regular expression based programs.
+To leverage the valuable information within build logs these researchers build parsers and regular expression based programs.
 This task of retrieving specific chunks of text from the build logs can be solved by the chunk retrieval techniques we compare in this thesis.
@@
 Build logs are a valuable data source for developers to find out why their build failed.
-Various researchers are looking into supporting developers to process the verbose build logs.
+Several researchers are looking into supporting developers to process the verbose build logs.
 Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
@@
 The hint generators leverage this structured access to the information within the build log to propose fixes.
-One of the hint generators for example queries stack overflow for discussions related to why the build failed.
+For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
 In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
@@
 The chunk retrieval techniques we compare in this thesis can be used to fill similar structured representations with information from build logs.
-As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, the main influence factor on the structure of a build log.
+As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.
 
-Amar et al.~\cite{amar2019mining} compare different approaches to reduce the portions of a log to be inspected by a developer.
-The techniques remove lines that appear both in passing and failing build logs and use a modified term frequency inverse document frequency weighting to identify term vectors likely to occur with failures.
+Amar et al.~\cite{amar2019mining} compare different approaches to reduce the portions of a log that a developer has to inspect.
+Their techniques remove lines that appear both in passing and failing build logs and use a modified term frequency inverse document frequency weighting to identify term vectors likely to occur with failures.
 They use the term vectors and cosine similarity to further filter the log portions only present in failing build logs.
-Their diff technique can be interpreted as a chunk retrieval technique, the targeted information is defined by the past failures used as basis for the weighted term vectors.
+Their diff technique can be interpreted as a chunk retrieval technique, where the targeted information is defined by the past failures used as basis for the weighted term vectors.
 
-Travis already provides a basic structuring of build logs within their log viewer using \emph{log folds}~\cite{travis2019logfolds}.
+Travis itself already provides build logs augmentation in the form of a basic structuring of the build logs within their log viewer using \emph{log folds}~\cite{travis2019logfolds}.
 They add fold identifiers around common commands and setup or teardown build phases and collapse the contained lines by default.
@@
 \label{sec:rw-semi-structured-data}
-Serge Abiteboul introduced a theory of semi-structured data in his report from 1997 about integrating data from several sources~\cite{abiteboul1997querying}.
-He proposes essential characteristics of semi-structured data, and we show how five of these map to the context of build logs.
+Serge Abiteboul introduces a theory of semi-structured data in his report from 1997 about integrating data from several sources~\cite{abiteboul1997querying}.
+He proposes essential characteristics of semi-structured data.
+In this section, we show how five of these map to the context of build logs.
 
@@
   We observed this in the logs we collected for the \emph{LogChunks} data set, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
-  You can see an example of this in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.
-  \item \textbf{is partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, e.g.\ natural language text in error messages.
-  \item can be described with an \textbf{analytical data guide} rather than a beforehand defined schema.
+  Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} present an example of this.
+  \item \textbf{is partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, such as natural language text in error messages.
+  \item can be described with an \textbf{analytical data guide} rather than a predefined schema.
   There is no fixed specification on how build tools structure their output.
@@
   \item \textbf{has a rapidly evolving schema}.
-  Modifications in the build configuration might change the tools involved in the build and therefore the composition of the build log.
+  Modifications in the build configuration can change the tools involved in the build and therefore the composition of the build log.
   Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adopt their log messages over time~\cite{yuan2012characterizing}.
@@
 A related field of log processing is the processing of system log files produced during runtime.
-A main difference in system logs is that they are fundamentally structured through events.
+A main difference between build logs and system logs is that system logs are fundamentally structured through events.
 Each line in the log file represents one event.
 The first goal in parsing system log files is to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
-Next the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
+Next, the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
 The output of a log parser is a structured log, composed of a list of timed events and the corresponding parameter values~\cite{he2016evaluation}.
 This structured log is then the input to various machine learning and data mining processes.
-They mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
-Xu et al.~\cite{xu2009detecting} leveraged the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
+Researchers mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
+Xu et al.~\cite{xu2009detecting} leverage the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
 
@@
 A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
-In this thesis we taka a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
-Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ through regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+In this thesis we take a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
+Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
 
@@
 % \section{Information Extraction and Retrieval Techniques}
+The techniques we investigate in this thesis are based on existing methods of Programming by Example, information extraction and information retrieval.
+This section presents different Programming by Example resources surrounding Microsoft's work on the PROSE library
+We explain its generic program synthesis algorithm and how PROSE synthesize text extraction programs, the foundation of PBE\@.
+In addition, we describe how chunk retrieval can be employed as a part of presented information extraction approaches.
+We introduce how information retrieval techniques, the basis for CTS, are used to improve software development.
 
-The chunk retrieval techniques we compare in this thesis use different techniques from the fields of information extraction and retrieval.
-This section presents existing approaches to extract structured information from semi-structured data and how these approaches differ from chunk retrieval.
-Further we illustrate how information retrieval techniques, basis for our chunk retrieval technique CTS, are used in software engineering research.
-
-\subsection{Information Extraction} %from Semi-Structured Documents
-\emph{Information extraction} techniques aim at structuring unstructured information to support subsequent processing.
-
-The PADS project~\cite{fisher2011the-pads} is centered around declaring grammars for the information contained in semi-structured documents.
-Based on this declarative data description various tools are generated like format converters, e.g.\ to XML, data adaptors to other tools, statistical analyzers and visualizers.
-Manually defined PADS grammars eliminate the need to develop a custom data extraction parser.
-Xi and Walker developed ANNE~\cite{xi2010a-context-free}, which can infer context-free PADS grammars from a few user annotations and the raw document data.
-Fisher et al.~\cite{fisher2008from} fully automated the generation of PADS grammars.
-They split the data into chunks, lines or documents, and further into tokens.
-Parentheses are used to infer hierarchical structure information.
-The system guesses grammar operators unifying single tokens or subexpressions, scores the resulting grammars and applies appropriate rewrite rules to refine the candidate grammars.
-
-The IEPAD tool created by Chang et al.~\cite{chang2003automatic} automatically identifies data extraction patterns in semi-structured web pages, without requiring user-labeled training examples.
-They split the semi-structured documents into tokens, discover repetitive patterns using occurrence-counting suffix trees and select the most regular and compact patterns to define extraction.
-
-Dan Smith and Mauricio Lopez~\cite{smith1997information} extract structured information from sets of semi-structured documents that contain similar information but are structured differently.
-The user provides rules of each piece of information, detailing in which section of the document it might be present.
-Identifying keywords and regular expressions determine whether the information is present and where it starts and ends.
-
-These information extraction approaches support parsing and structuring of entire files.
-We investigate chunk retrieval techniques which do not aim at inferring the whole structure of a build log.
-Instead, chunk retrieval focuses on extracting one specific information characterized by the user.
-
-\subsection{Information Retrieval}% in Software Engineering Research
-The process of automatically selecting unstructured documents related to a given \emph{search query} is called \emph{information retrieval}~\cite{schutze2008introduction}.
-
-In information retrieval, algorithms try to determine the general topic or conceptual information of the document.
-Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix and weighing the terms with tf-idf~\cite{lee1997document}.
-On the matrix the algorithms apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
-
-Information retrieval techniques are leveraged to improve software engineering in various areas.
-Antoniol et al.~\cite{antoniol2002recovering} query manual pages and requirements with program identifiers to create trace links between code and documentation.
-The same task is addressed by Marcus et al.~\cite{marcus2005recovery}, who also incorporate source code comments into their query.
-Panichella et al.~\cite{panichella2016parameterizing} and Runeson et al.~\cite{runeson2007detection} apply similar information retrieval techniques to detect duplicated bug reports.
-Salton et al.~\cite{salton1993approaches} retrieve text parts relevant for a given user query by calculating global document similarity scores and refining the output through local passage similarity.
-They also calculate similarity with term vectors.
-
-Our chunk retrieval technique CTS uses the same approach of term vectors to identify which lines to extract from a log file.
+% The chunk retrieval techniques we compare in this thesis use different techniques from the fields of information extraction and retrieval.
+% This section presents existing approaches to extract structured information from semi-structured data and how these approaches differ from chunk retrieval.
+% Further we illustrate how information retrieval techniques, basis for our chunk retrieval technique CTS, are used in software engineering research.
 
@@
 The PROSE framework is developed by Microsoft Research.
-The section next presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
-Further, we cover additional applications and extensions of the PROSE program synthesis and alternative research on generating regular expressions from examples.
+Next, this section presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
+Finally, we cover additional applications and extensions of the PROSE program synthesis and alternative research on generating regular expressions from examples.
 
@@
 The FlashMeta framework presented by Polozov and Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program synthesis in the Microsoft PROSE framework.
-FlashMeta separates the inductive synthesis algorithm from the domain specific capabilities of the desired program, by encoding the possible program space in a domain specific language (DSL).
+FlashMeta separates the inductive synthesis algorithm from the domain specific capabilities of the desired program by encoding the possible program space in a domain specific language (DSL).
 The user specifies the desired program behavior by providing in / output examples (I/O examples).
@@
 In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples.
-Negative input examples should not to be processed by the synthesized program.
+Negative input examples should not be processed by the synthesized program.
 
@@
 It enables a user to define text extraction programs for text, websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes text extraction programs from semi-structured text based on regular expressions.
+FlashExtract's instantiation for text synthesizes extraction programs from semi-structured text based on regular expressions.
 Users can extract multiple fields and structure them with hierarchy and sequence.
 FlashExtract synthesizes programs to extract each of the fields leveraging the information about hierarchical containment and sequentiality.
-It eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.
+It eliminates the need for the user to understand the entire structure of the processed document and decreases the effort of developing a suitable extraction program.
 
 The text instantiation of FlashExtract models the extraction of a single substring as a pair of two cut positions.
-A position is either specified by an absolute character index or a pair of two regular expression (regex).
-The first regex matches the substring directly before the characterized position, the second regex directly after.
-A regex in FlashExtract is a concatenation of tokens, e.g.\ standard character classes or string literals frequently occurring in the input examples.
+A position is either specified by an absolute character index or by a pair of two regular expressions.
+The first regular expression matches the substring directly before the characterized position, the second regular expression matches the substring directly after.
+A regular expression in FlashExtract is a concatenation of tokens, e.g.\ standard character classes or string literals frequently occurring in the input examples.
 
@@
 Their DSL for PROSE abstracts over variables and subexpressions by describing rewrite rules applied to the abstract syntax tree.
-The synthesized transformations proposes fixes for student assignments based on corrections from other students and to automates repetitive refactoring tasks.
+These synthesized transformations propose fixes for student assignments based on corrections from other students and to automate repetitive refactoring tasks.
 
-Raza and Gulwani~\cite{raza2017automated} present an automated algorithm that tries to predict data extraction programs from only input examples.
+Raza and Gulwani~\cite{raza2017automated} present an automated algorithm that attempts to predict data extraction programs from only input examples.
 Their tool can split system log statements into table columns or extract data from lists on webpages into spreadsheets.
@@
 In a program synthesis shorter and simpler program often receive a better ranking.
-Ellis and Gulwani~\cite{ellis2017learning} improve the accuracy of the PROSE program learner even further by also taking the execution traces of the program candidates into account.
+By also taking the execution traces of the program candidates into account, Ellis and Gulwani~\cite{ellis2017learning} improve the accuracy of the PROSE program learner even further.
 For example, a program that extracts overlapping substrings is ranked lower than a program without overlapping extractions.
@@
 \paragraph{User Interaction with Programming by Example}
-I/O examples are an ambiguous specification of a program and user confidence in the correctness of the synthesized program is important for a wide adoption of Programming by Example based systems~\cite{lau2009why-programming-by-demonstration}.
+I/O examples are an ambiguous specification of a program.
+As such, user confidence in the correctness of the synthesized program is important for a wide adoption of Programming by Example based systems~\cite{lau2009why-programming-by-demonstration}.
 Miller and Myers~\cite{miller2001outlier} uncover outliers in input data provided to a Programming by Example text editing task.
@@
 
+\subsection{Information Extraction} %from Semi-Structured Documents
+\emph{Information extraction} techniques aim at structuring unstructured information to support subsequent processing.
+We present existing approaches to extract information from semi-structured documents and how these approaches differ and can benefit from chunk retrieval.
+
+The PADS project~\cite{fisher2011the-pads} is centered around declaring grammars for the information contained in semi-structured documents.
+Based on this declarative data description various tools are generated.
+This includes tools such as format converters, e.g.\ to XML, data adaptors to other tools, statistical analyzers and visualizers.
+Manually defined PADS grammars eliminate the need to develop a custom data extraction parser.
+Xi and Walker developed ANNE~\cite{xi2010a-context-free}, which can infer context-free PADS grammars from a few user annotations and the raw document data.
+Fisher et al.~\cite{fisher2008from} fully automated the generation of PADS grammars.
+They split the data into chunks, lines or documents, and further into tokens.
+Parentheses are used to infer hierarchical structure information.
+The system guesses grammar operators unifying single tokens or subexpressions, scores the resulting grammars and applies appropriate rewrite rules to refine the candidate grammars.
+
+The IEPAD tool created by Chang et al.~\cite{chang2003automatic} automatically identifies data extraction patterns in semi-structured web pages, without requiring user-labeled training examples.
+They split the semi-structured documents into tokens, discover repetitive patterns using occurrence-counting suffix trees and select the most regular and compact patterns to define extraction.
+
+Smith and Lopez~\cite{smith1997information} extract structured information from sets of semi-structured documents that contain similar information but which are structured differently.
+The user provides rules for each piece of information, detailing in which section of the document it might be present.
+Identifying keywords and regular expressions determine whether the information is present and where it starts and ends.
+
+These information extraction approaches support parsing and structuring of entire files.
+We investigate chunk retrieval techniques which do not aim at inferring the whole structure of a build log.
+Instead, chunk retrieval focusses on extracting one specific information characterized by the user.
+
+\subsection{Information Retrieval}% in Software Engineering Research
+The process of automatically selecting unstructured documents related to a given \emph{search query} is called \emph{information retrieval}~\cite{schutze2008introduction}.
+In information retrieval, algorithms try to determine the general topic or conceptual information of a document.
+Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix and weighing the terms with tf-idf~\cite{lee1997document}.
+On the matrix the algorithms apply a similarity comparison like, for example,vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
+
+Information retrieval techniques are leveraged to improve software engineering in various areas.
+Antoniol et al.~\cite{antoniol2002recovering} query manual pages and requirements with program identifiers to create trace links between code and documentation.
+The same task is addressed by Marcus et al.~\cite{marcus2005recovery}, who also incorporate source code comments into their query.
+Panichella et al.~\cite{panichella2016parameterizing} and Runeson et al.~\cite{runeson2007detection} apply similar information retrieval techniques to detect duplicated bug reports.
+Salton et al.~\cite{salton1993approaches} retrieve text parts relevant for a given user query by calculating global document similarity scores and refining the output through local passage similarity.
+They also calculate similarity with term vectors.
+Our chunk retrieval technique CTS uses the same approach of term vectors to identify which lines to extract from a log file.
+
 \end{document}

### 2019-12-06 msr-paper/paper.tex
adding tse and msr templates

--- 2019-10-01 paper/paper_old.tex
@@
-%%
 %%
@@
 \setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
+\copyrightyear{2020}
+\acmYear{2020}
 \acmDOI{10.1145/1122445.1122456}
@@
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
-  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  June 03--05, 2018, Woodstock, NY}
+\acmConference[Seoul '20]{Seoul '20: Mining Software Repositories Data Showcase}{May 25--26, 2020}{Seoul, South Korea}
+\acmBooktitle{Seoul '20: Mining Software Repositories Data Showcase,
+  May 25--26, 2020, Seoul, South Korea}
 \acmPrice{15.00}
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Analyzing Build Logs Using Programming by Example}
+\title{Why Did My CI Build Fail?\\ -\\ LogChunks: A Data Set for Build Log Analysis}
 
 \author{Carolin Brandt}
+\author{Moritz Beller}
+\author{Annibale Panichella}
 
@@
 \begin{abstract}
-  ...
+Build failures are common in continuous integration (CI), but identifying the root cause of a failure is difficult.
+Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
+We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
+For each build log we manually labeled the log part (chunk) describing why the build failed.
+We validated the data set by surveying the developers of the projects which produced the builds.
+In addition, the data set categorizes the log chunks according to their format within the log text and provides keywords that a developer would use to search for the log chunks.
+\emph{LogChunks} can be the basis to assess further build log analysis techniques and studies about why CI builds fail.
+
+% This is the question developers ask when they want to fix a failing build and the question various researchers ask when they investigate continuous integration practices.
+% A common approach is to seek advice in the build's log file, which details the progress, results and errors of the tools involved in the build.
+% However, build logs are challenging to process as they are very verbose, at best semi-structured and highly variable between projects.
+
 \end{abstract}
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{ci, buildlogs, programming by example}
+\keywords{ci, build log analysis, build failure, chunk retrieval}
 
@@
 
-\secfunc{section function - \textbackslash secfunc} \\
-\mention{things to mention / reference - \textbackslash mention} \\
-\plan{what to write here - \textbackslash plan} \\
-\bp{actual bullet points - \textbackslash bp} \\
-\draft{final text drafty - \textbackslash draft} \\
-\review{final text review ready - \textbackslash review} \\
-\todo{ToDo - \textbackslash todo} \\
+\section{Introduction}
++ motivating: why is this data set important/special, what did other people do?
 
-\section{Introduction}
-\secfunc{why? what? research questions? purpose? hypothesis? wide $\rightarrow$ narrow
+Annibale proposed: what is the problem we are addressing?
 
-problem, done in literature, why not enough? our approach
-}
+\section{Data Schema and Access}
+data schema explanation: log, reason the build failed, keywords, structural categories
 
-\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the success build state is restored improves the overall productivity of developers.
+how to obtain and use (import) the data (github repo, csv?, database dump?)
 
-\plan{why are logs so difficult: mention heterogeneous, semi-structured (paper reference for that?), big data (reference paper about log sizes), in distributed systems probably distributed (really also for build log?)
-g
-to combat that users write tools to <extract / retrieve superbegriff> information from build logs.
+\section{Data Collection Process}
+repo / build / log sampling
 
-one possibility IR: classify specific part of program as similar to others (list IR technique) to see whether it is correlated to a failure.
-but not as good: not a real summarization technique, more what is similar to the last few times it failed.
+labeling process
 
-way to extract fine grained information: regular expressions which have to be written manually
+\section{Data Set Validation}
+sending mails to developers
 
-\todo{maybe other paragraph. here only half fitting?}
-}
+second labeling?
 
-During this assignment an engineer spends a lot of their time \todo{or: find percentage to cite} reading very long and verbose build logs, trying to retrieve the relevant information from between many uninteresting other lines.
-\todo{add anecdotal evidence, watchdog paper?}
+\section{Applications}
+\subsection{Chunk Retrieval Evaluation}
+short description of our study and results
 
-A way to support them would be to extract the desired information and present it in a structured way.
-One approach to realize such functionality are tools that employ handcrafted regular expressions to find the desired text parts within the build log.
-However, creating these regular expressions is tedious, mentally complicated and usually error-prone task.
-Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers.
-Our goal is to evaluate an alternative way of taking this burden of programmers.
-By simply giving examples of the desired extractions they should be able to define extraction programs.
+\subsection{Future Research Questions}
+\begin{itemize}
+  \item train information chunk retrieval techniques
+  \item train build log classification algorithms
+  \item look into what keywords tools use to mark failures / developers use to search for them
+\end{itemize}
 
-We implement \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples.
-After collecting a diverse set of build logs from Travis CI we design a meta-model of the contained information.
-We evaluate ALBE on logs from selected GitHub repositories on the accuracy of extraction for a varying number and selection of in-output-examples.
-Furthermore we compare the tool to classical information retrieval and plain keyword search.
-Our evaluation of ALBE shows that it is able to define extractions for various desired informations, that it shortens development time in comparison to manual regular expression construction and ...
-}
+\section{Limitations}
+limits: only one coherent text substring labeled, first description of build failure
 
-\todo{Research Questions!}
-
-\bp{ RQ1: how many and which kind of samples does pbe need to be competitive with existing methods? }
-
-\bp{ can pbe extraction replace or even exceed existing methods for our use case? }
-
-\bp{ What are the limitations of extractions? (only interesting when specified with PROSE library..)}
-
-\bp{ Adjustements / Improvements to PROSE for extracting specifically from build logs }
-
-\section{Related Work}
-
-\todo{More glue \& sentences that give an overview over the next paragraph}
-
-\subsection{Bulidlogs Analysis Tools}
-
-\review{
-Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs.
-They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts.
-They observed that highlighting the locality and context of an issue is helpful to programmers.
-We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.
-
-Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs.
-They further employed information retrieval techniques to identify the lines most likely hinting at the cause of the error.
-In contrast to that, our tool ALBE extracts specific parts of the build logs.
-As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
-}
-
-\subsection{Continuous Integration}
-
-\review{
-Various researchers have analyzed industrial and open source logs for failure reasons and their impact on development.
-Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google.
-In addition most failures are resolved within two builds.
-Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones.
-They determined that testing failures outweigh compilation errors.
-Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
-Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
-They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.
-
-All these researchers described building parsers in order to evaluate the studied build logs.
-Our work could support their research by easing the parser development and enable them to cover more languages and build tools easier.
-}
-
-\subsection{Information Extraction and Retrieval}
-
-\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources.
-Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix.
-On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
-For our use case, this could be applied by slicing the build logs into lines or small sections.
-Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
-Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}
-
-\review{
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework.
-It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples.
-Users can extract multiple fields and structure them with hierarchy and sequence.
-FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.
-
-We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information extraction.
-}
-
-\subsection{Semi-Structured Data}
-
-\draft{
-Software build logs are inherently semi-structured data. \todo{explain the different characteristics and relate to build logs}
-Serge Abiteboul~\cite{abiteboul1997querying} characterized semi-structured data as having an irregular, implicit, partial and rapidly evolving texture.
-}
-
-\section{Method}
-\secfunc{how? when? material? narrow}
-
-\todo{want?: flow of research figure}
-
-\todo{study design vs. study carry out}
-
-\begin{figure}
-	\includegraphics[width=0.5\textwidth, trim={0.5cm 5cm 3cm 2cm}, clip]{img/flow-of-research.pdf}
-	\caption{Flow of Research}
-\end{figure}
-
-\subsection{Data collection}
-
-\draft{
-In order to build a tool which facilitates information extraction from build logs we first had \todo{which time form here?
-past or present?} to get an impression on what kinds of build logs occur in projects, what possibly extractable information they contain and how structured or unstructured they are.
-}
-
-\subsubsection{Design} ...
-\bp{
-realistic image (for open source software) we sample from popular GitHub repositories that also use Travis CI.
-
-\draft{Obtaining the newest logs from them would entail sampling mostly logs of succeeding builds as the distribution of build states on a Travis CI repository is highly skewed towards successful builds~\cite{beller2017oops}.
-Therefore we stratify our collection of logs and select an equal amount of logs from each type of Travis CI build status.}
-}
-
-\subsubsection{Execution} ...
-\bp{
-built tool X \todo{data collection tool name, LogCollector?}
-
-queryed ghtorrent dataset from the first of April 2018 through google BigQuery
-
-poked Travis CI for active status of project and collected sampled builds through Travis ruby library
-
-downloaded logs through Travis Rest API \todo{look up version}
-}
-
-\subsection{Meta-Model}
-\bp{through manual examination of y of the build logs we collected designed a meta-model  of the contained/extractable/useful/interesting information}
-
-\todo{figure with meta-model}
-\begin{figure}
-	\includegraphics[width=0.5\textwidth, trim={0.5cm 4cm 3cm 0.5cm}, clip]{img/meta-model.pdf}
-	\caption{Meta-Model}
-\end{figure}
-
-\plan{explain (shortly? partly?) meta model classes}
-
-\subsection{Our Tool: ALBE \textemdash \ Analyzing Logs By Example}
-
-\plan{
-techstacky: C\#, dot net core, Microsoft PROSE library specifically their TextExtraction DSL
-
-samples \& learning: labeled data is in xml files, parsed (and shuffled) for examples, program learned for specific instruction
-
-interaction: user can analyze given file with program defined by specific exampleset, if there: describe how to use iteratively growing / shuffling learning process
-}
-
-\subsubsection{Capabilities} ...
-
-\plan{
-Example extractions: travis worker, android failure, what we do evaluations on
-}
-
-\subsubsection{Limitations} ...
-
-\plan{
-Travis worker both kinds at once, explain PROSE limitations on arbitrary OR regexes
-
-for all limitations: why? and how would we solve that?
-}
-
-\subsection{Evaluation}
-\bp{
-To evaluate our tool we did xyz, we wanted to measure: accuracy of extractions, impression on effort of creating such extraction, compare both to existing methods
-}
-
-\subsubsection{Extraction Accuracy}
-...
-
-\bp{we labelled x logs from project y using language z / build tool b. (do for one, maybe extend with further one)
-
-evaluated accuracy \todo{<define accuracy for us>} with growing number of 
-\begin{itemize}
-	\item random selected
-	\item chronologically sampled
-	\item hand selected 
-\end{itemize}
-samples.
-}
-
-\subsubsection{Compare to Traditional Methods}
-\paragraph{TravisTorrent} ...
-\bp{Beller et al.
-\mention{cite correct travistorrent paper} reported on manually constructing a parser with regular expressions for ruby \& Java and common build tools / output formats there, they can extract \todo{<explain there extractions, with example necessary?}
-
-android-failure example: decided not to implement as to complicated \todo{<- that kind of already belongs into results, how do we describe the \emph{method} of this comparison accurately??}
-}
-
-\paragraph{Manual Regex Construction} ...
-\plan{
-for something where I did not look at the synthesized program
-
-alternative: small study with other developers on manual vs. pbe extraction
-}
-
-\paragraph{IR paragraph stuff} ...
-\plan{
-maybe simple setup with lines implementing vector comparison on keywords ourselves -> how can we reuse the labeling for the c\# tool?
-}
-
-\paragraph{Keyword search} ...
-\plan{
-either: we give a list of keywords generally associated with the thing we want to extract (e.g. failure/error/..) -> write nicely how we brainstormed that
-
-or: small study of what developers would search for (maybe literature already did that?)
-
-or: relate to samples? search for already seen words from last failure
-}
-
-\section{Results}
-\secfunc{hard numbers! answers to research questions, narrow}
-
-\plan{graphs!, achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data}
-
-\section{Analysis / Discussion}
-\secfunc{interpretation, implication of answers and why does it matter, comparison to previous findings, narrow $\rightarrow$ wide}
-
-\plan{our tool works well for defined cases, limitations of tool/prose/regex usage in general, every x weeks extraction has to be rewritten to keep accuracy, well improved if only y new examples have to be added}
-
-\section{Conclusion and Future Work}
-\secfunc{summarize, results again, future research}
-
-\plan{repeat everything and results}
-
-\plan{future}
-
-\bp{make avaliable to other researchers
-
-integrate into travis
-
-\plan{as always} extend evaluation and data collection
-
-use dataset to evaluate against existing approaches
-
-}
+\section{Potential Improvements}
+extension: include more repositories, further classification of the build failures e.g.\ root cause, further validation
 
@@
 %% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
+
+% \begin{acks}
+% To Robert, for the bagels and explaining CMYK and color spaces.
+% \end{acks}
 
@@
 %% If your work has an appendix, this is the place to put it.
-\appendix
+% \appendix
 
-\section{Research Methods}
+% \section{Research Methods}
 
-\subsection{Part One}
+% \subsection{Part One}
 

### 2019-12-06 tse-paper/abstract.tex
adding tse and msr templates

Software builds from continuous integration produce detailed logs about the status and results of the various tools involved in the build.
These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps or understand the cause of a build failure.
However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
This makes it hard to process and analyze them.
In this paper, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
We conduct an empirical study by comparing these techniques on the \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.
Our findings show that none of the three techniques clearly outperforms the others.
We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.

### 2019-12-06 tse-paper/content.tex
adding tse and msr templates

basically like in thesis

\section{Related Work}
\begin{itemize}
	\item CI research? could show how researchers could use chunk retrieval for existing studies (then I would only mention studies that do build log analysis)
	\item build log augmentation (BART paper, ICSE Amar et al.)
	\item ``foundational techniques'', e.g. explaining how PROSE synthesis algorithm works, I would move to the explanation of the method
\end{itemize}

\section{Chunk Retrieval Techniques}
general: what is a chunk retrieval technique

should I include the "how is a build log generated" and (some of, one) the examples for retrievable information?

\subsection{Program Synthesis by Example (PBE)}
like in thesis
\subsection{Common Text Similarity (CTS)}
like in thesis
\subsection{Keyword Search (KWS)}
like in thesis

\section{Empirical Comparsion}
\subsection{Data Set}
short explanation of content and reference to the MSR paper
\subsection{Tool Implementation}
stating that (and in which languages) we implemented the techniques (will be very short, integrate somewhere else?)
\subsection{Study Design}
like in thesis
\subsection{Results}
like in thesis?

less plots! -> can I only mention the results and just not show the plots showing then?

\section{Discussion}
like in thesis - table and explanation
\subsection{Program Synthesis by Example (PBE)}
like in thesis
\subsection{Common Text Similarity (CTS)}
like in thesis
\subsection{Keyword Search (KWS)}
like in thesis
\subsection{Recommendation of a Suitable Technique}
like in thesis - decision tree

\section{Threats to Validity}
like in thesis

\section{Conclusion and Future Work}
like in thesis

### 2019-12-06 tse-paper/paper.tex
adding tse and msr templates

%% bare_jrnl_compsoc.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% Computer Society journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[10pt,journal,compsoc]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later. Note also the use of a CLASSOPTION conditional provided by
% IEEEtran.cls V1.7 and later.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

\usepackage{tabularx}
\usepackage{multicol}
\usepackage{booktabs}
\renewcommand{\arraystretch}{1.4}
\usepackage{makecell}

\usepackage[most]{tcolorbox}
\newtcolorbox{simplebox}[2][]{enhanced,
    sharp corners,
    colback=white,
    colbacktitle=white,
    coltitle=black,
    boxrule=1pt,
    left=8mm,
    right=8mm,
    bottom=2mm,
    top=4mm,
    boxed title style={colframe=white},
    attach boxed title to top center={yshift=-3mm}, 
    title=#2,#1}

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{How to Analyze Build Logs\\ ---\\ A~Comparative Study of Chunk~Retrieval~Techniques}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc 
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

\author{Carolin~Brandt,~\IEEEmembership{Member,~IEEE,}
        Moritz~Beller,~\IEEEmembership{Fellow,~OSA,}
        and~Annibale~Panichella,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: see http://www.michaelshell.org/contact.html
\IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% The publisher's ID mark at the bottom of the page is less important with
% Computer Society journal papers as those publications place the marks
% outside of the main text columns and, therefore, unlike regular IEEE
% journals, the available text space is not reduced by their presence.
% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% or like this to get the Computer Society new two part style.
%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark (Computer Society jorunal
% papers don't need this extra clearance.)

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
\input{abstract.tex}
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Computer Society, IEEE, IEEEtran, journal, continuous integration, build log analysis, chunk retrieval.
\end{IEEEkeywords}}

% make the title area
\maketitle

% To allow for easy dual compilation without having to reenter the
% abstract/keywords data, the \IEEEtitleabstractindextext text will
% not be used in maketitle, but will appear (i.e., to be "transported")
% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
% or transmag modes are not selected <OR> if conference mode is selected 
% - because all conference papers position the abstract like regular
% papers do.
\IEEEdisplaynontitleabstractindextext
% \IEEEdisplaynontitleabstractindextext has no effect when using
% compsoc or transmag under a non-conference mode.

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
% Computer Society journal (but not conference!) papers do something unusual
% with the very first section heading (almost always called "Introduction").
% They place it ABOVE the main text! IEEEtran.cls does not automatically do
% this for you, but you can achieve this effect with the provided
% \IEEEraisesectionheading{} command. Note the need to keep any \label that
% is to refer to the section immediately after \section in the above as
% \IEEEraisesectionheading puts \section within a raised box.

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps (small caps for compsoc).
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word. TODO
% \IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
% for IEEE Computer Society journal papers produced under \LaTeX\ using
% IEEEtran.cls version 1.8b and later.
% % You must have at least 2 lines in the paragraph with the drop letter
% % (should never be an issue)
% I wish you the best of success.

% \hfill mds

% \hfill August 26, 2015

% \subsection{Subsection Heading Here}
% Subsection text here.

% % needed in second column of first page if using \IEEEpubid
% %\IEEEpubidadjcol

% \subsubsection{Subsubsection Heading Here}
% Subsubsection text here.

\input{content.tex}

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.
% However, the Computer Society has been known to put floats at the bottom.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

% \section{Conclusion}
% The conclusion goes here.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

% \appendices
% \section{Proof of the First Zonklar Equation}
% Appendix one text goes here.

% % you can choose not to have a title for an appendix
% % if you want by leaving the argument blank
% \section{}
% Appendix two text goes here.

% use section* for acknowledgment
\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
  \section*{Acknowledgments}
\else
  % regular IEEE prefers the singular form
  \section*{Acknowledgment}
\fi

The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2019-12-09 msr-paper/paper.tex
rewriting introduction and making todos actual todos

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Why Did My CI Build Fail?\\ -\\ LogChunks: A Data Set for Build Log Analysis}
+\title{LogChunks: A Data Set for Build Log Analysis}
 
 \author{Carolin Brandt}
+\author{Annibale Panichella}
 \author{Moritz Beller}
-\author{Annibale Panichella}
 
@@
 \emph{LogChunks} can be the basis to assess further build log analysis techniques and studies about why CI builds fail.
-
-% This is the question developers ask when they want to fix a failing build and the question various researchers ask when they investigate continuous integration practices.
-% A common approach is to seek advice in the build's log file, which details the progress, results and errors of the tools involved in the build.
-% However, build logs are challenging to process as they are very verbose, at best semi-structured and highly variable between projects.
 
@@
 \section{Introduction}
-+ motivating: why is this data set important/special, what did other people do?
+Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
+CI builds produce build logs, reporting the progress and results of the steps within the build.
+These build logs contain a lot of valuable information for developers and researchers.
+They analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed.
+Developers examine timer reports to track how different stages of the build process perform.
+Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is avaliable to them.
+% CI builds report the progress and results of the steps within the build in build logs.
+% These are a valuable data source for developers and researchers.
+% Developers analyze them to identify why their build failed or to 
+The produced build logs are long and verbose~\cite{beller2017oops}, making them inadequate for direct cosumption.
+These two groups can only use the information within the build logs if they can adequately retrieve the log parts (chunks) describing the targeted information.
+% However, these two groups can only use the 
+% Build logs are a valuable data source for developers and researchers.
+% Developers read them to analyze why their build failed or how different stages of the build process perform.
+% Researchers can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
 
-Annibale proposed: what is the problem we are addressing?
+There are different techniques to retrieve information chunks from CI build logs.
+Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
+Such regular expressions are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
+Vassallo et al.\ wrote a custom parser for build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
+Recently, Amar et al.\ reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and a successful build~\cite{amar2019mining}.
 
-\section{Data Schema and Access}
-data schema explanation: log, reason the build failed, keywords, structural categories
+These approaches have various downsides and strengths:
+Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.
+Custom parsers are powerful though fragile towards changes in the log structure.
+The structure of build logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
+Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
+At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred over other alternatives.
+In addition, there is currently no data set available to evaluate and compare such chunk retrieval techniques for build logs.
 
-how to obtain and use (import) the data (github repo, csv?, database dump?)
+% Developers and researches currently have little support while choosing which technique to use for a task.
+% In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
+% One example set always contains build log in/output examples from the same software repository or project and for one specific build log information.
+They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
+% Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
+% The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
+% To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
 
-\section{Data Collection Process}
-repo / build / log sampling
+We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
+For each build log we manually labeled which substring describes why the build failed.
+The data set also provides keywords a developer would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
+% For our evaluation of the chunk retrieval techniques PBE, CTS and KWS we added search keywords and structural categories to each of the labeled substrings.
 
-labeling process
+In this paper, we illustrate potential use cases of \emph{LogChunks} and present our own comparison of three chunk retrieval techniques using the data set.
+Section \ref{sec:related-data-sets} describes related data sets and how \emph{LogChunks} differs from them.
+The following section introduces the data schema, how to access the data set, as well as limitations and potential improvements.
+We present our data collection in Section \ref{sec:data-collection}.
+To validate our labels we performed a second labeling of a sample of the data.
+In addition, we surveyed the developers, whose commits triggered the builds, whether our labeled log chunk describes why their build failed.
+Section \ref{sec:validation} presents the two validation studies.
+We conclude with Section \ref{sec:conclusion} and describe limitations as well as potential improvements of \emph{LogChunks}.
 
-\section{Data Set Validation}
-sending mails to developers
-
-second labeling?
+% First, we present related data sets and show how \emph{LogChunks} differs.
+% Second, this chapter describes our log collection process and details the data schema of \emph{LogChunks}.
+% Further, it presents the labeling process and how we validated the obtained data points.
+% In the first validation study, we compared the labeled data points with those of a second labeler on a sample of the build logs.
+% For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled really describes the reason the build failed.
 
@@
 \subsection{Chunk Retrieval Evaluation}
-short description of our study and results
+\todo{short description of our study and results}
 
 \subsection{Future Research Questions}
+\todo{
 \begin{itemize}
@@
 \end{itemize}
+}
 
-\section{Limitations}
-limits: only one coherent text substring labeled, first description of build failure
+\section{Related Data Sets}
+\label{sec:related-data-sets}
 
-\section{Potential Improvements}
-extension: include more repositories, further classification of the build failures e.g.\ root cause, further validation
+\subsection{TravisTorrent}
+The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI\@.
+It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc}, related data from GHTorrent~\cite{gousios2013ghtorrent}, the corresponding git repository and data obtained through analysis of the build logs.
+The data obtained through build logs contains the names of failing test cases, similar to the reason the build failed in \emph{LogChunks}.
+However, these values are obtained through a manually developed parser, which only supports specific Ruby test runners and Java Maven or JUnit logs.
+\emph{LogChunks} provides manually labeled data points on the description of the build failure reason for a much wider selection of programming languages.
+
+\subsection{Travis CI Build Log Data Set}
+Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected a large amount of Travis CI build logs from 130 github repositories to analyze their use of the Checkstyle plugin.
+They selected Maven repsitories that included the Checkstyle plugin and also used Travis CI\@.
+Their data set only provides the plain build logs, whereas \emph{LogChunks} provides manually analyzed build logs from Travis CI\@.
+
+\section{Data Schema and Access}
+\todo{data schema explanation: log, reason the build failed, keywords, structural categories
+
+how to obtain and use (import) the data (github repo, csv?, database dump?)}
+
+\label{sec:data-schema}
+For each repository, \emph{LogChunks} has a list of \emph{examples}.
+Each example consists of:
+\begin{itemize}
+	\item \textbf{Input:} the relative path to the input build log.
+	\item \textbf{BuildFailureReason:} the substring of the log describing the reason the build failed.
+	\item \textbf{Keywords:} keywords a developer would use to search for the BuildFailureReason.
+	\item \textbf{Category:} a categorization of the structural representation of the BuildFailureReason within the build log.
+				The category is relative to the other examples for the same repository.
+\end{itemize}
+Following, this section describes the BuildFailureReason, Keywords and Category in more detail.
+
+\paragraph{BuildFailureReason}
+The \emph{BuildFailureReason} is the substring of the build logs that describes why the build failed.
+This could be the failing test case, the description of a failed linter rule or a compiler error.
+The \emph{BuildFailureReason} is one continuous string cut from the build log.
+If there are multiple errors leading for the build to fail, the substring contains the first appearing continuous error descriptions.
+\emph{Continuous} means that no lines reporting of normal build behavior are interrupting the error descriptions.
+Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
+For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
+In these instances the \emph{BuildFailureReason} contains the lines describing that the build failed.
+
+\paragraph{Keywords}
+The \emph{Keywords} contain a list of one to three keywords appearing within the \emph{BuildFailureReason} or in the area around it in the build log.
+We aim to select keywords a developer would use to search for the \emph{BuildFailureReason} when inspecting the build log.
+
+\paragraph{Category}
+For each repository, we assign \emph{structural categories} to the examples.
+The structural category compares how the \emph{BuildFailureReasons} are represented within the build logs.
+Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'', surrounding lines filled with special characters or additional empty log lines.
+Two examples fall into the same structural categories if they are surrounded by similar markings.
+For most cases, two BuildFailureReason examples which fall into one category are outputted either within the same build phase or by the same build tool.
+For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
+
+\section{Data Collection Process}
+\label{sec:data-collection}
+\subsection{Log Collection}
+In the following we describe how we select the repositories, builds and Logs for \emph{LogChunks}.
+To collect the build logs we built the  \texttt{GHTorrentParser},\texttt{LogCollector} and \texttt{TravisRequester} using Ruby.
+
+\paragraph{Repository Sampling}
+First, we determine a set of repositories to query logs from.
+Our \texttt{GHTorrentParser} queries the \emph{GHTorrent}~\cite{gousios2013ghtorrent} data set for the most popular languages on GitHub~\cite{github2019website}.
+It then retrieves the most popular repositories for a given language.
+We define \emph{Popularity} as the number of watches.
+The \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, can then check for a given repository whether it uses Travis CI\@.
+
+For \emph{LogChunks} we queried GHTorrent from 01/04/2018 for the three most popular repositories of each of the 30 most popular languages.
+
+\paragraph{Build Sampling}
+The \texttt{LogCollector} uses the \texttt{TravisRequester} to obtain the newest builds for a given repository.
+It uses a stratified sampling approach: \texttt{TravisRequester} saves the obtained builds in buckets according to their status.
+We encountered the following statuses during our data collection: created, started, cancelled, passed, errored and failed.
+The user of \texttt{TravisRequester} configures how many builds should be checked and how many builds per status should be saved.
+
+To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to a 1000 builds per repository and kept ten for each status.
+We discarded all statuses except one, namely ``failed''~\cite{travis2009buildstatus}, to make the most use of Travis' existing categorization of build status.
+
+\paragraph{Log Sampling}
+For each build the \texttt{TravisRequester} then selects a log to download.
+Travis CI attributes logs to \emph{jobs}.
+A single build can consist of multiple jobs, e.g.\ building the same code version and executing tests in various different testing environments.
+A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
+\texttt{TravisRequester} queries each build for the first job, which has the same state.
+For the selected jobs, the tool queries the Travis API V3 over HTTPS to obtains the corresponding build log.
+
+We manually inspected the collected build logs and had to discard logs from three repositories.
+One had only one failed build, two others had empty build logs on Travis CI\@.
+In total we collected 797 logs from 80 repositories.
+
+\subsection{Labeling Process}
+\label{sec:labeling-process}
+
+\paragraph{BuildFailureReason}
+For each repository, the labeler skimmed through the build logs and tried to identify the first occurrence of a description why the build failed.
+They copied out the first continuous description as the BuildFailureReason.
+They preserved whitespace and special characters, as they might be crucial to detect the targeted substring.
+To support exact learning of regular expressions identifying the labeled substrings the labeler aimed to start and end the labeled substring at consistent locations around the fault description.
+
+\paragraph{Keywords}
+We presented the BuildFailureReason substring and ten lines above and below to the labeler.
+Their task was to note down three strings they would put into a document search function to find this failure description.
+The string should appear in or around the BuildFailureReason substring and is case-sensitive.
+There are no special limitations on the string itself, especially spaces are also allowed.
+
+\paragraph{Category}
+To label the \emph{structural categories} we again presented the BuildFailureReason and the surrounding context to the labeler for all logs from a repository.
+We asked them to assign numerical categories according to whether the BuildFailureReason substring had the same structural representation, i.e.\ the same surrounding or identifying characters.
+The labeler should start the categories with 0 and increase as new ones appear.
+For reproducibility we presented the logs in chronological build order.
+
+\section{Data Set Validation}
+\label{sec:validation}
+We validate our collected data points in two different ways.
+A different labeler performed a second pass of labeling the build failure reason, keywords and structural categories on a subset of the data.
+In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set.
+We asked them whether our retrieval of the log part describing the reason the build failed was correct.
+This sections describes these two validation studies.
+
+\subsection{Inter-Rater Reliability Study}
+To evaluate the validity of our labeled data points we perform a second labeling of a sample from \emph{LogChunks}.
+
+\paragraph{Method}
+The second labeler processed 30 random generated logs for each data point in \emph{LogChunks}.
+We followed the same labeling process as described in Section~\ref{sec:labeling-process}.
+For the build failure reason and the keywords, we presented 30 randomly sampled build logs from distinct repositories in \emph{LogChunks}.
+The labeled structural categories are relative to the other logs from the same repository.
+Therefore, we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.
+
+\paragraph{Results}
+For the first labeled data point, namely the substring describing why the build failed, the two labelers exactly agreed in six cases.
+In 15 cases the second labeler selected more lines than the first one, in five there was partial overlap and in 4 they completely disagreed.
+
+Regarding the keywords the two labelers completely agreed in nine cases and completely disagreed in two cases.
+In nine cases there was partial overlap in the keywords of the two labelers, in two the first labeler selected additional keywords compared to the second, while the second labeler labeled additional keywords in seven cases.
+
+When classifying the labeled substrings into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.
+
+\paragraph{Discussion}
+The results of this validation study show that there is overlap in the data from both labelers, however also a high variation.
+We believe that the main cause for this is that our explanations to the second labeler were not extensive enough.
+There were implicit, inconsistent assumptions both labelers created during their work.
+In the following we describe these assumptions from both labelers for each data point and the implications on our description of the data classes.
+
+For the first data class, the reason the build failed, it was ambiguous whether the labeled substring should contain the information \emph{that} the build failed.
+This concerns statements like ``\texttt{The build exited with 1}''.
+One labeler included such statements, while the other one only focussed on the log parts describing \emph{why} the build failed, e.g.\ the name of the failing test case.
+
+While labeling the keywords a developer would use to search for the log part describing why the build failed, the one labeler allowed arbitrary strings appearing around the presented log part.
+In contrast to that, the other labeler focussed on actual \emph{words}, delimited by spaces or special characters.
+One labeler ignored capitalization, while the other one selected case-sensitive keywords.
+A third difference was that the first labeler was presented with all substrings from a repository, yielding more general keywords than the second labeler.
+
+For the structural categories this validation study showed a high overlap.
+In our instructions to the second labeler we did not emphasize the \emph{structural} aspect enough.
+They sorted into categories along \emph{why} the build failed, putting failing tests from different test runners into the same category even though the failing tests were presented differently in the log.
+
+Our main learning from this study is that adequately communicating all decisions and assumptions on how data is labeled is important and difficult.
+We reviewed the misunderstandings and incorporated more thorough descriptions of our data classes in Section~\ref{sec:data-schema}.
+
+\subsection{Developer Survey}
+
+For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
+As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
+We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
+
+The person who probably knows best why a build failed is the one committing the changes which triggered the build.
+If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
+In this section, we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
+
+\paragraph{Method}
+Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
+We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
+The email included links to the corresponding commits, build overview and log file.
+We asked the receivers to fill out a short survey in case our extraction was not correct.
+Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
+In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
+As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
+
+\paragraph{Results}
+In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
+32 of these mails could not be delivered, e.g.\ because they were addressed at noreply mail addresses.
+These 32 mails related to 68 of the build logs.
+We received answers from 61 developers, responding about 144 build logs.
+Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.
+
+Of the 144 answers, 132 said our extraction was correct.
+26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
+We manually inspected these negative answers and found that some extractions were correct after all.
+This yields 12 log extractions in our example set that were not correct, shown in Figure~\ref{fig:mails-extraction-correct}.
+
+\paragraph{Discussion}
+This study highly strengthens the trust in the validity of the extracted build failure reasons in \emph{LogChunks}.
+The study received answers about 18\% of the logs from \emph{LogChunks}.
+After manual correction, 91\% of the received answers said our labelled extractions were accurate.
+
+Most of the initial ``incorrect'' answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
+This is because we had to trim long labeled extractions to keep the emails readable.
+
+One of our extractions only showed a warning and the developer proposed to also include the line above, stating that warnings are treated as errors in the build.
+In others that were identified as ``incorrect'', we labelled the error message of an error that later ignored and did not lead to the build failing.
+
+\section{Conclusion}
+\label{sec:conclusion}
+\subsection{Limitations}
+\todo{limits: only one coherent text substring labeled, first description of build failure}
+
+\subsection{Potential Improvements}
+\todo{extension: include more repositories, further classification of the build failures e.g.\ root cause, further validation}
 

### 2019-12-09 msr-paper/paper.tex
add citations to bib, add example image and write on applications

@@
 
+You can access \emph{LogChunks} on Zendoo: \todo{insert zendoo link}.
+
 % First, we present related data sets and show how \emph{LogChunks} differs.
@@
 \subsection{Chunk Retrieval Evaluation}
-\todo{short description of our study and results}
+We created \emph{LogChunks} to evaluate and compare different chunk retrieval techniques for build logs.
+The first investigated technique is based on synthesizing programs from examples using the Microsoft PROSE library.
+A user provides a small number of examples to describe which text part the program should extract.
+PROSE then synthesizes a program of regular expressions that is consistent with these examples.
+We compared this extraction technique to a text similarity approach, which selects the lines of a build log which are most similar to the ones in the given user examples.
+Lastly, we investigated searching for keywords that are associated with the given user examples.
 
-\subsection{Future Research Questions}
+The log chunks in this data set provided the examples for these techniques, the keywords were used to configure the keyword search.
+The structural categories enabled us to measure how structurally similar the examples have to be for a technique to be applicable.
+
+Our results show that program synthesis is well suited to retrieve information chunks from build logs when the targeted information is always presented in a structurally identical way and the user requires a high confidence in the precision and recall of the output.
+Using text similarity is advisable when precision is valued higher than recall and we recommend keyword search when recall is valued higher than precision.
+We present more detailed results, background and our study design in \todo{ref (preprint or so?) of full journal paper (or thesis?)}.
+
+\subsection{Potential Use Cases}
+\emph{LogChunks} can be the basis for a wide range of further research inquiries.
+This section presents a selection of further research ideas.
+
+\paragraph{Evaluate Information (Chunk) Retrival Techniques}
+In addition to the three techniques we investigated until now, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
+We can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason the build failed.
+
+\paragraph{Train Build Log Classification Algorithms}
+Various researchers are looking into why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
+They write custom parsers and classifiers to categorize why a build failed.
+\todo{more!}
+
 \todo{
 \begin{itemize}
-  \item train information chunk retrieval techniques
-  \item train build log classification algorithms
   \item look into what keywords tools use to mark failures / developers use to search for them
@@
 Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected a large amount of Travis CI build logs from 130 github repositories to analyze their use of the Checkstyle plugin.
-They selected Maven repsitories that included the Checkstyle plugin and also used Travis CI\@.
+They selected Maven repositories that included the Checkstyle plugin and also used Travis CI\@.
 Their data set only provides the plain build logs, whereas \emph{LogChunks} provides manually analyzed build logs from Travis CI\@.
 
-\section{Data Schema and Access}
-\todo{data schema explanation: log, reason the build failed, keywords, structural categories
+\section{Data Schema}
+\label{sec:data-schema}
 
-how to obtain and use (import) the data (github repo, csv?, database dump?)}
+\begin{figure}[tbp]
+	\centering
+	\includegraphics[width=0.45\textwidth, clip]{exampleXml.png}
+	\caption{One example from the php/php-src repository in \emph{LogChunks}}
+	\label{fig:dev-survey}
+\end{figure}
 
-\label{sec:data-schema}
 For each repository, \emph{LogChunks} has a list of \emph{examples}.
@@
 Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
-We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
+We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
+%Figure~\ref{fig:dev-mail} shows one of the mails sent out.
 The email included links to the corresponding commits, build overview and log file.
 We asked the receivers to fill out a short survey in case our extraction was not correct.
-Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
+%Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
 In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
@@
 We received answers from 61 developers, responding about 144 build logs.
-Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.
+%Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.
 
@@
 We manually inspected these negative answers and found that some extractions were correct after all.
-This yields 12 log extractions in our example set that were not correct, shown in Figure~\ref{fig:mails-extraction-correct}.
+This yields 12 log extractions in our example set that were not correct.%, shown in Figure~\ref{fig:mails-extraction-correct}.
 

### 2019-12-11 msr-paper/paper.tex
more glue text, potential use cases and conclusion, correcting some sections

@@
 \newcommand{\review}[1]{{\color{black}#1}}
-\newcommand{\todo}[1]{{\color{orange}#1}}
+\newcommand{\todo}[1]{{\color{orange}(#1)}}
+
+\usepackage{listings}
+
 %%
@@
 Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
-CI builds produce build logs, reporting the progress and results of the steps within the build.
+CI builds produce logs which report the progress and results of the steps within the build.
 These build logs contain a lot of valuable information for developers and researchers.
-They analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed.
 Developers examine timer reports to track how different stages of the build process perform.
-Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is avaliable to them.
-% CI builds report the progress and results of the steps within the build in build logs.
-% These are a valuable data source for developers and researchers.
-% Developers analyze them to identify why their build failed or to 
-The produced build logs are long and verbose~\cite{beller2017oops}, making them inadequate for direct cosumption.
-These two groups can only use the information within the build logs if they can adequately retrieve the log parts (chunks) describing the targeted information.
-% However, these two groups can only use the 
-% Build logs are a valuable data source for developers and researchers.
-% Developers read them to analyze why their build failed or how different stages of the build process perform.
-% Researchers can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
+Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
+Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
+
+Build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
+Therefore, developers and researchers can only use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.
 
@@
 
-% Developers and researches currently have little support while choosing which technique to use for a task.
-% In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
-% One example set always contains build log in/output examples from the same software repository or project and for one specific build log information.
-They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
-% Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
-% The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
-% To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
-
 We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
@@
 The data set also provides keywords a developer would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
-% For our evaluation of the chunk retrieval techniques PBE, CTS and KWS we added search keywords and structural categories to each of the labeled substrings.
 
@@
 Section \ref{sec:validation} presents the two validation studies.
-We conclude with Section \ref{sec:conclusion} and describe limitations as well as potential improvements of \emph{LogChunks}.
+To conclude we describe limitations as well as potential improvements of \emph{LogChunks}.
 
-You can access \emph{LogChunks} on Zendoo: \todo{insert zendoo link}.
-
-% First, we present related data sets and show how \emph{LogChunks} differs.
-% Second, this chapter describes our log collection process and details the data schema of \emph{LogChunks}.
-% Further, it presents the labeling process and how we validated the obtained data points.
-% In the first validation study, we compared the labeled data points with those of a second labeler on a sample of the build logs.
-% For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled really describes the reason the build failed.
+We published \emph{LogChunks} through Zendoo: \todo{insert zendoo link}.
 
 \section{Applications}
+This section possible use cases for \emph{LogChunks} and outlines how we previously applied it to compare different build log analysis techniques.
+
+\subsection{Potential Use Cases}
+\emph{LogChunks} can be the basis for a wide range of further studies:
+
+\paragraph{Evaluate Information (Chunk) Retrival Techniques}
+In addition to the three techniques we investigated until now, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
+We can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason the build failed.
+
+\paragraph{Support Build Log Classification Algorithms}
+Various researchers are looking into why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
+They write custom parsers and classifiers to categorize builds according to why a build failed.
+The manually labeled chunk describing why the build failed can show classification algorithms where in the build logs they can find the information relevant for the classification.
+
+\paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
+\emph{LogChunks} provides keywords that a developer would look for to search the chunk describing why the build failed.
+Analyzing these could help us understand how developers process build logs and which keywords a tool should use to mark an error description so developers quickly find it through text search.
+
+\paragraph{Studying Conversations about Build Failures}
+Some researchers are looking into conversations of developers surrounding CI builds and pull requests \todo{citation needed: nathan cassee did this in his master thesis (the paper on it is either rejected or not yet published), did not find others yet that do this}.
+The chunks describing why a build failed, or the results of chunk retrieval techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
+
 \subsection{Chunk Retrieval Evaluation}
 We created \emph{LogChunks} to evaluate and compare different chunk retrieval techniques for build logs.
-The first investigated technique is based on synthesizing programs from examples using the Microsoft PROSE library.
+The first technique is based on synthesizing programs from examples using the Microsoft PROSE library.
 A user provides a small number of examples to describe which text part the program should extract.
@@
 
-\subsection{Potential Use Cases}
-\emph{LogChunks} can be the basis for a wide range of further research inquiries.
-This section presents a selection of further research ideas.
-
-\paragraph{Evaluate Information (Chunk) Retrival Techniques}
-In addition to the three techniques we investigated until now, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
-We can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason the build failed.
-
-\paragraph{Train Build Log Classification Algorithms}
-Various researchers are looking into why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
-They write custom parsers and classifiers to categorize why a build failed.
-\todo{more!}
-
-\todo{
-\begin{itemize}
-  \item look into what keywords tools use to mark failures / developers use to search for them
-\end{itemize}
-}
-
 \section{Related Data Sets}
 \label{sec:related-data-sets}
+This section presents existing data sets of CI build logs and why \emph{LogChunks} is unique among them.
 
@@
 They selected Maven repositories that included the Checkstyle plugin and also used Travis CI\@.
-Their data set only provides the plain build logs, whereas \emph{LogChunks} provides manually analyzed build logs from Travis CI\@.
+Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
 
@@
 
-\begin{figure}[tbp]
-	\centering
-	\includegraphics[width=0.45\textwidth, clip]{exampleXml.png}
-	\caption{One example from the php/php-src repository in \emph{LogChunks}}
-	\label{fig:dev-survey}
-\end{figure}
+% \begin{figure}[tbp]
+% 	\centering
+% 	\includegraphics[width=0.45\textwidth, clip]{exampleXml.png}
+% 	\caption{One example from the php/php-src repository in \emph{LogChunks}}
+% 	\label{fig:dev-survey}
+% \end{figure}
 
-For each repository, \emph{LogChunks} has a list of \emph{examples}.
-Each example consists of:
+This section describes the file structure and the data schema of \emph{LogChunks}.
+We give a detailed explanation for the manually labeled data.
+
+\emph{LogChunks} has two top level folders, \texttt{logs} and \texttt{build-failure-reason}.
+Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
+
+The logs are organized in folders for each repository, identified through the repository slug: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater }.
+Within each repository folder the logs are separated according to build status.
+Currently \emph{LogChunks} only contains logs from \texttt{failed} builds.
+The build status folder contains the full logs in files named with the ID of the Travis CI build that produced the log.
+
+The folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
+The data set provides an XML file for each repository \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater .xml}) categorized according to the main language of the repository.
+The schema of these XML files is presented in Listing \ref{lst:examples}.
+
+\lstset{
+  language=XML,
+  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
+  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
+	frame=single
+}
+\begin{lstlisting}[caption={Example XML file from \emph{LogChunks}}, label=lst:examples, breaklines=true]
+<Examples>
+  <Log>C/php@php-src/failed/529279089.log</Log>
+    <Keywords>ERROR, FAIL, DIFF</Keywords>
+    <Category>0</Category>
+    <Chunk>001+ ** ERROR: process timed out **
+
+001- OK.
+========DONE========
+FAIL Bug #60120 (proc_open hangs when data in stdin/out/err is getting larger or equal to 2048) [ext/standard/tests/file/bug60120.phpt]</Chunk>
+  </Example>
+  ...
+</Examples>
+\end{lstlisting}
+
+For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
+Each \texttt{Example} consists of:
 \begin{itemize}
-	\item \textbf{Input:} the relative path to the input build log.
-	\item \textbf{BuildFailureReason:} the substring of the log describing the reason the build failed.
-	\item \textbf{Keywords:} keywords a developer would use to search for the BuildFailureReason.
-	\item \textbf{Category:} a categorization of the structural representation of the BuildFailureReason within the build log.
+	\item \texttt{Log:} the relative path to the input build log.
+	\item \texttt{Chunk:} the targeted information chunk. We are targeting the substring of the log that describes why the build failed.
+	\item \texttt{Keywords:} keywords a developer would use to search for the log chunk.
+	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
 				The category is relative to the other examples for the same repository.
 \end{itemize}
-Following, this section describes the BuildFailureReason, Keywords and Category in more detail.
+Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
 
-\paragraph{BuildFailureReason}
-The \emph{BuildFailureReason} is the substring of the build logs that describes why the build failed.
+\paragraph{Chunk --- reason the build failed}
+The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
 This could be the failing test case, the description of a failed linter rule or a compiler error.
-The \emph{BuildFailureReason} is one continuous string cut from the build log.
+The \texttt{Chunk} is one continuous string cut from the build log.
 If there are multiple errors leading for the build to fail, the substring contains the first appearing continuous error descriptions.
@@
 For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
-In these instances the \emph{BuildFailureReason} contains the lines describing that the build failed.
+In these instances the \texttt{Chunk} contains the lines describing that the build failed.
 
 \paragraph{Keywords}
-The \emph{Keywords} contain a list of one to three keywords appearing within the \emph{BuildFailureReason} or in the area around it in the build log.
-We aim to select keywords a developer would use to search for the \emph{BuildFailureReason} when inspecting the build log.
+The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
+We aim to select keywords a developer would use to search for the \texttt{Chunk} when inspecting the build log.
 
@@
 For each repository, we assign \emph{structural categories} to the examples.
-The structural category compares how the \emph{BuildFailureReasons} are represented within the build logs.
+The structural category compares how the \texttt{Chunk}s are represented within the build logs.
 Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'', surrounding lines filled with special characters or additional empty log lines.
 Two examples fall into the same structural categories if they are surrounded by similar markings.
-For most cases, two BuildFailureReason examples which fall into one category are outputted either within the same build phase or by the same build tool.
+For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
 For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
@@
 \section{Data Collection Process}
+This section presents how we gathered the logs for \emph{LogChunks} and our manual labeling process.
 \label{sec:data-collection}
+
 \subsection{Log Collection}
-In the following we describe how we select the repositories, builds and Logs for \emph{LogChunks}.
-To collect the build logs we built the  \texttt{GHTorrentParser},\texttt{LogCollector} and \texttt{TravisRequester} using Ruby.
+We describe how we select the repositories, builds and logs for \emph{LogChunks}.
+To collect the build logs we built the  \texttt{GHTorrentParser}, \texttt{LogCollector} and \texttt{TravisRequester} using Ruby.
 
@@
 
-To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to a 1000 builds per repository and kept ten for each status.
-We discarded all statuses except one, namely ``failed''~\cite{travis2009buildstatus}, to make the most use of Travis' existing categorization of build status.
+To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to a 1000 builds per repository and keep ten for each status.
+We discard all statuses except \emph{failed}~\cite{travis2009buildstatus}.
+A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
 
@@
 We manually inspected the collected build logs and had to discard logs from three repositories.
-One had only one failed build, two others had empty build logs on Travis CI\@.
+One had only a single failed build, two others had empty build logs on Travis CI\@.
 In total we collected 797 logs from 80 repositories.
@@
 \label{sec:labeling-process}
+After collecting a wide range of Travis CI build logs we manually labeled which text chunk describes why the build failed.
+Following that, we assigned search keywords and structural categories to each log chunk.
 
-\paragraph{BuildFailureReason}
+\paragraph{Chunk --- reason the build failed}
 For each repository, the labeler skimmed through the build logs and tried to identify the first occurrence of a description why the build failed.
-They copied out the first continuous description as the BuildFailureReason.
+They copied out the first continuous description as the \texttt{Chunk}.
 They preserved whitespace and special characters, as they might be crucial to detect the targeted substring.
@@
 \paragraph{Keywords}
-We presented the BuildFailureReason substring and ten lines above and below to the labeler.
+We presented the \texttt{Chunk} and ten lines above and below to the labeler.
 Their task was to note down three strings they would put into a document search function to find this failure description.
-The string should appear in or around the BuildFailureReason substring and is case-sensitive.
+The string should appear in or around the \texttt{Chunk} substring and is case-sensitive.
 There are no special limitations on the string itself, especially spaces are also allowed.
@@
 \paragraph{Category}
-To label the \emph{structural categories} we again presented the BuildFailureReason and the surrounding context to the labeler for all logs from a repository.
-We asked them to assign numerical categories according to whether the BuildFailureReason substring had the same structural representation, i.e.\ the same surrounding or identifying characters.
+To label the \emph{structural categories} we again presented the \texttt{Chunk} and the surrounding context to the labeler for all logs from a repository.
+We asked them to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation, i.e.\ the same surrounding or identifying characters.
 The labeler should start the categories with 0 and increase as new ones appear.
@@
 \subsection{Inter-Rater Reliability Study}
-To evaluate the validity of our labeled data points we perform a second labeling of a sample from \emph{LogChunks}.
+To evaluate the validity of our labeled data points we perform a second labeling of a sample of the data in \emph{LogChunks}.
 
@@
 Regarding the keywords the two labelers completely agreed in nine cases and completely disagreed in two cases.
-In nine cases there was partial overlap in the keywords of the two labelers, in two the first labeler selected additional keywords compared to the second, while the second labeler labeled additional keywords in seven cases.
+In nine cases there was partial overlap in the keywords of the two labelers, in two the first labeler selected additional keywords compared to the second, while the second labeler proposed additional keywords in seven cases.
 
@@
 For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
-As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
-We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
+As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
+We only took the logs into accont and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
 
 The person who probably knows best why a build failed is the one committing the changes which triggered the build.
-If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
-In this section, we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
+If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.
+We sent out mails to the original developers whose commits triggered the builds represented in \emph{LogChunks} and asked them whether the log chunk we labeled actually describes why the build failed.
+This section describes out survey and discusses our results.
 
@@
 Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
-We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
+We grouped all commits triggered by one developer and sent out a mail to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
 %Figure~\ref{fig:dev-mail} shows one of the mails sent out.
-The email included links to the corresponding commits, build overview and log file.
+The mail included links to the corresponding commits, build overview and log file.
 We asked the receivers to fill out a short survey in case our extraction was not correct.
@@
 \paragraph{Results}
-In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
-32 of these mails could not be delivered, e.g.\ because they were addressed at noreply mail addresses.
+In total we sent out mails to 246 developers, asking about 3.2 build logs per mail on average.
+32 of these mails could not be delivered, e.g.\ because they were addressed to \emph{noreply} mail addresses.
 These 32 mails related to 68 of the build logs.
@@
 Most of the initial ``incorrect'' answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
-This is because we had to trim long labeled extractions to keep the emails readable.
+This is because we had to trim long labeled extractions to keep the mails readable.
 
@@
 \section{Conclusion}
+In this paper we introduced the \emph{LogChunks} data set encompassing about 800 build logs from a wide range of projects using Travis CI.
+For each log we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.
+Still there are limitations to our data set, which we present in the following.
+We also propose several improvements and extensions to \emph{LogChunks}.
 \label{sec:conclusion}
-\subsection{Limitations}
-\todo{limits: only one coherent text substring labeled, first description of build failure}
 
-\subsection{Potential Improvements}
-\todo{extension: include more repositories, further classification of the build failures e.g.\ root cause, further validation}
+\paragraph{Chunk as One Consecutive Substring}
+The manually labeled \texttt{Chunk} in our data set aims to contain the log part describing why the build failed.
+However, it contains only one consecutive substring of the log text, whereas the reason a build failed could be described at multiple locations within the log.
+We could improve this by extending \emph{LogChunks} to contain multiple substrings of the log text.
+
+\paragraph{Include More Repositories and Logs}
+\emph{LogChunks} encompasses a wide range of repositories from various main development languages, though only 10 logs from each repository.
+This stems from the high effort necessary for the manual data labeling process.
+Including more logs and repositories into \emph{LogChunks} will strengthen it as a broad baseline for comparing build log analysis tools.
+
+\paragraph{Classification of the Build Failure Cause}
+Our data set contains the log chunks describing why a build failed but has no further classification according to the cause of the failure.
+As various researchers are investigating why CI builds fail, a useful extension would be to annotate cause of the build failure for each log.
+
+\paragraph{Other Targeted Information Chunks}
+Build log analysis is not limited to retrieving the chunk describing why a build failed.
+\emph{LogChunks} could be extended with further information targets such as descriptions of warnings, build infrastructure and more.
 

### 2019-12-11 msr-paper/paper.tex
adapt data set section of thesis

@@
 
-\paragraph{Chunk --- reason the build failed}
+\paragraph{Chunk Describing Why The Build Failed}
 The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
@@
 
-\paragraph{Chunk --- reason the build failed}
+\paragraph{Chunk Describing Why The Build Failed}
 For each repository, the labeler skimmed through the build logs and tried to identify the first occurrence of a description why the build failed.
@@
 \subsection{Developer Survey}
-
 For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
@@
 
-Most of the initial ``incorrect'' answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
+Most of the initial incorrect answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
 This is because we had to trim long labeled extractions to keep the mails readable.
@@
 One of our extractions only showed a warning and the developer proposed to also include the line above, stating that warnings are treated as errors in the build.
-In others that were identified as ``incorrect'', we labelled the error message of an error that later ignored and did not lead to the build failing.
+In others that were identified as incorrect, we labelled the error message of an error that later ignored and did not lead to the build failing.
 

### 2019-12-11 thesis/txt/3-data-set.tex
add citations to bib, add example image and write on applications
adapt data set section of thesis

@@
 \includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
-This chapter describes the creation of the \emph{LogChunks} data set.
-\emph{LogChunks} encompasses about 800 build logs produced by a wide variety of programming languages.
+This chapter describes the creation of the \emph{LogChunks} data set that we use in our empirical comparison of chunk retrieval techniques.
+\emph{LogChunks} is a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
 For each build log we manually labeled which substring describes why the build failed.
-For our evaluation of the chunk retrieval techniques PBE, CTS and KWS we added search keywords and structural categories to each of the labeled substrings.
+The data set also provides keywords a developer would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
 
-First, we present related data sets and show how \emph{LogChunks} differs.
-Second, this chapter describes our log collection process and details the data schema of \emph{LogChunks}.
-Further, it presents the labeling process and how we validated the obtained data points.
-In the first validation study, we compared the labeled data points with those of a second labeler on a sample of the build logs.
-For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled really describes the reason the build failed.
+We start this chapter by explaining why we created \emph{LogChunks} and how it enables us to compare the chunk retrieval techniques PBE, CTS and KWS\@.
+Then, we introduces related data sets and show how \emph{LogChunks} differs.
+The chapter describes the data schema of \emph{LogChunks} and our log collection process.
+Further, it presents the labeling process and how we validated the labeled data, including a survey of the original developers of the projects represented in \emph{LogChunks}.
+%In the first validation study, we compared the labeled data points with those of a second labeler on a sample of the build logs.
+%For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled really describes the reason the build failed.
 
 \section{Motivation}
-In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
+\todo{In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
 One example set always contains build log in/output examples from the same software repository or project and for one specific build log information.
@@
 The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
-To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
+To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.}
 
 \section{Related Data Sets}
+\label{sec:related-data-sets}
+This section presents existing data sets of CI build logs and why \emph{LogChunks} is unique among them.
 
-\paragraph{TravisTorrent}
+\subsection{TravisTorrent}
 The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI\@.
@@
 
-\paragraph{Travis CI Build Log Data Set}
+\subsection{Travis CI Build Log Data Set}
 Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected a large amount of Travis CI build logs from 130 github repositories to analyze their use of the Checkstyle plugin.
-They selected Maven repsitories that included the Checkstyle plugin and also used Travis CI\@.
-Their data set only provides the plain build logs, whereas \emph{LogChunks} provides manually analyzed build logs from Travis CI\@.
+They selected Maven repositories that included the Checkstyle plugin and also used Travis CI\@.
+Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
+
+\section{Data Schema}
+\label{sec:data-schema}
+This section describes the file structure and the data schema of \emph{LogChunks}.
+We give a detailed explanation for the manually labeled data.
+
+\emph{LogChunks} has two top level folders, \texttt{logs} and \texttt{build-failure-reason}.
+Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
+
+The logs are organized in folders for each repository, identified through the repository slug: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater }.
+Within each repository folder the logs are separated according to build status.
+Currently \emph{LogChunks} only contains logs from \texttt{failed} builds.
+The build status folder contains the full logs in files named with the ID of the Travis CI build that produced the log.
+
+The folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
+The data set provides an XML file for each repository \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater .xml}) categorized according to the main language of the repository.
+The schema of these XML files is presented in Listing \ref{lst:examples}.
+
+\lstset{
+  language=XML,
+  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
+  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
+	frame=single
+}
+\begin{lstlisting}[caption={Example XML file from \emph{LogChunks}}, label=lst:examples, breaklines=true]
+<Examples>
+  <Log>C/php@php-src/failed/529279089.log</Log>
+    <Keywords>ERROR, FAIL, DIFF</Keywords>
+    <Category>0</Category>
+    <Chunk>001+ ** ERROR: process timed out **
+
+001- OK.
+========DONE========
+FAIL Bug #60120 (proc_open hangs when data in stdin/out/err is getting larger or equal to 2048) [ext/standard/tests/file/bug60120.phpt]</Chunk>
+  </Example>
+  ...
+</Examples>
+\end{lstlisting}
+
+For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
+Each \texttt{Example} consists of:
+\begin{itemize}
+	\item \texttt{Log:} the relative path to the input build log.
+	\item \texttt{Chunk:} the targeted information chunk. We are targeting the substring of the log that describes why the build failed.
+	\item \texttt{Keywords:} keywords a developer would use to search for the log chunk.
+	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
+				The category is relative to the other examples for the same repository.
+\end{itemize}
+Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
+
+\paragraph{Chunk Describing Why The Build Failed}
+The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
+This could be the failing test case, the description of a failed linter rule or a compiler error.
+The \texttt{Chunk} is one continuous string cut from the build log.
+If there are multiple errors leading for the build to fail, the substring contains the first appearing continuous error descriptions.
+\emph{Continuous} means that no lines reporting of normal build behavior are interrupting the error descriptions.
+Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
+For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
+In these instances the \texttt{Chunk} contains the lines describing that the build failed.
+
+\paragraph{Keywords}
+The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
+We aim to select keywords a developer would use to search for the \texttt{Chunk} when inspecting the build log.
+
+\paragraph{Category}
+For each repository, we assign \emph{structural categories} to the examples.
+The structural category compares how the \texttt{Chunk}s are represented within the build logs.
+Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'', surrounding lines filled with special characters or additional empty log lines.
+Two examples fall into the same structural categories if they are surrounded by similar markings.
+For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
+For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
 
 \section{Log Collection}
-In the following we describe how we select the repositories, builds and Logs for \emph{LogChunks}.
-To collect the build logs we built the  \texttt{GHTorrentParser},\texttt{LogCollector} and \texttt{TravisRequester} using Ruby.
+We describe how we select the repositories, builds and logs for \emph{LogChunks}.
+To collect the build logs we built the  \texttt{GHTorrentParser}, \texttt{LogCollector} and \texttt{TravisRequester} using Ruby.
 
@@
 It uses a stratified sampling approach: \texttt{TravisRequester} saves the obtained builds in buckets according to their status.
-We encountered the following statuses during our data collection:
-\begin{multicols}{3}
-\begin{itemize}
-	\item created
-	\item started
-	\item cancelled
-	\item passed
-	\item errored
-	\item failed
-\end{itemize}
-\end{multicols}
+We encountered the following statuses during our data collection: created, started, cancelled, passed, errored and failed.
 The user of \texttt{TravisRequester} configures how many builds should be checked and how many builds per status should be saved.
 
-To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to a 1000 builds per repository and kept ten for each status.
-We discarded all statuses except one, namely ``failed''~\cite{travis2009buildstatus}, to make the most use of Travis' existing categorization of build status.
+To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to a 1000 builds per repository and keep ten for each status.
+We discard all statuses except \emph{failed}~\cite{travis2009buildstatus}.
+A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
 
@@
 We manually inspected the collected build logs and had to discard logs from three repositories.
-One had only one failed build, two others had empty build logs on Travis CI\@.
+One had only a single failed build, two others had empty build logs on Travis CI\@.
 In total we collected 797 logs from 80 repositories.
-
-\section{Data Schema}
-\label{sec:data-schema}
-For each repository, \emph{LogChunks} has a list of \emph{examples}.
-Each example consists of:
-\begin{itemize}
-	\item \textbf{Input:} the relative path to the input build log.
-	\item \textbf{BuildFailureReason:} the substring of the log describing the reason the build failed.
-	\item \textbf{Keywords:} keywords a developer would use to search for the BuildFailureReason.
-	\item \textbf{Category:} a categorization of the structural representation of the BuildFailureReason within the build log.
-				The category is relative to the other examples for the same repository.
-\end{itemize}
-Following, this section describes the BuildFailureReason, Keywords and Category in more detail.
-
-\paragraph{BuildFailureReason}
-The \emph{BuildFailureReason} is the substring of the build logs that describes why the build failed.
-This could be the failing test case, the description of a failed linter rule or a compiler error.
-The \emph{BuildFailureReason} is one continuous string cut from the build log.
-If there are multiple errors leading for the build to fail, the substring contains the first appearing continuous error descriptions.
-\emph{Continuous} means that no lines reporting of normal build behavior are interrupting the error descriptions.
-Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
-For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
-In these instances the \emph{BuildFailureReason} contains the lines describing that the build failed.
-
-\paragraph{Keywords}
-The \emph{Keywords} contain a list of one to three keywords appearing within the \emph{BuildFailureReason} or in the area around it in the build log.
-We aim to select keywords a developer would use to search for the \emph{BuildFailureReason} when inspecting the build log.
-
-\paragraph{Category}
-For each repository, we assign \emph{structural categories} to the examples.
-The structural category compares how the \emph{BuildFailureReasons} are represented within the build logs.
-Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'', surrounding lines filled with special characters or additional empty log lines.
-Two examples fall into the same structural categories if they are surrounded by similar markings.
-For most cases, two BuildFailureReason examples which fall into one category are outputted either within the same build phase or by the same build tool.
-For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
-
-% \begin{figure}[htbp]
-% 	\centering
-% 	\includegraphics[width=\textwidth, clip]{img/big-study/categories-dataset.pdf}
-% 	\caption{Distribution of the categories in LogChunks}
-% 	\label{fig:categorycount-examplecount-dataset}
-% \end{figure}
 
@@
 \label{sec:labeling-process}
+After collecting a wide range of Travis CI build logs we manually labeled which text chunk describes why the build failed.
+Following that, we assigned search keywords and structural categories to each log chunk.
 
-\paragraph{BuildFailureReason}
+\paragraph{Chunk Describing Why The Build Failed}
 For each repository, the labeler skimmed through the build logs and tried to identify the first occurrence of a description why the build failed.
-They copied out the first continuous description as the BuildFailureReason.
+They copied out the first continuous description as the \texttt{Chunk}.
 They preserved whitespace and special characters, as they might be crucial to detect the targeted substring.
@@
 \subsection{Developer Survey}
-
 For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
-As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
-We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
+As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
+We only took the logs into accont and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
 
 The person who probably knows best why a build failed is the one committing the changes which triggered the build.
-If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
-In this section, we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
+If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.
+We sent out mails to the original developers whose commits triggered the builds represented in \emph{LogChunks} and asked them whether the log chunk we labeled actually describes why the build failed.
+This section describes out survey and discusses our results.
 
@@
 Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
-We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
-The email included links to the corresponding commits, build overview and log file.
+We grouped all commits triggered by one developer and sent out a mail to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
+Figure~\ref{fig:dev-mail} shows one of the mails sent out.
+The mail included links to the corresponding commits, build overview and log file.
 We asked the receivers to fill out a short survey in case our extraction was not correct.
@@
 
-Most of the initial ``incorrect'' answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
-This is because we had to trim long labeled extractions to keep the emails readable.
+Most of the initial incorrect answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
+This is because we had to trim long labeled extractions to keep the mails readable.
 
 One of our extractions only showed a warning and the developer proposed to also include the line above, stating that warnings are treated as errors in the build.
-In others that were identified as ``incorrect'', we labelled the error message of an error that later ignored and did not lead to the build failing.
+In others that were identified as incorrect, we labelled the error message of an error that later ignored and did not lead to the build failing.
 

### 2019-12-11 msr-paper/paper.tex
shorten paper + fix bibliography for links

@@
 There are different techniques to retrieve information chunks from CI build logs.
-Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
+Beller et al.\ use regular expressions to analyze the reasons for build failures from Travis CI logs~\cite{beller2017oops}.
 Such regular expressions are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
@@
 We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
-For each build log we manually labeled which substring describes why the build failed.
+For each build log, we manually labeled which substring describes why the build failed.
 The data set also provides keywords a developer would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
 
-In this paper, we illustrate potential use cases of \emph{LogChunks} and present our own comparison of three chunk retrieval techniques using the data set.
-Section \ref{sec:related-data-sets} describes related data sets and how \emph{LogChunks} differs from them.
+In this paper, we illustrate potential use cases of \emph{LogChunks} and past studies using the data set.
+Section~\ref{sec:related-data-sets} describes related data sets and how \emph{LogChunks} differs from them.
 The following section introduces the data schema, how to access the data set, as well as limitations and potential improvements.
-We present our data collection in Section \ref{sec:data-collection}.
+We present our data collection in Section~\ref{sec:data-collection}.
 To validate our labels we performed a second labeling of a sample of the data.
 In addition, we surveyed the developers, whose commits triggered the builds, whether our labeled log chunk describes why their build failed.
-Section \ref{sec:validation} presents the two validation studies.
+Section~\ref{sec:validation} presents the two validation studies.
 To conclude we describe limitations as well as potential improvements of \emph{LogChunks}.
@@
 
-\section{Applications}
-This section possible use cases for \emph{LogChunks} and outlines how we previously applied it to compare different build log analysis techniques.
+%\section{Applications}
+%This section possible use cases for \emph{LogChunks} and outlines how we previously applied it to compare different build log analysis techniques.
+\section{Potential Use Cases}
 
-\subsection{Potential Use Cases}
+%\subsection{Potential Use Cases}
 \emph{LogChunks} can be the basis for a wide range of further studies:
 
-\paragraph{Evaluate Information (Chunk) Retrival Techniques}
-In addition to the three techniques we investigated until now, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
-We can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason the build failed.
+\paragraph{Evaluate Information (Chunk) Retrieval Techniques}
+We created \emph{LogChunks} to evaluate and compare different techniques to retrieve information chunks from build logs \todo{cite journal paper (or preprint?)}.
+The techniques we compared are based on program synthesis from examples, text similarity and searching for keywords.
+In addition that, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
+For example, we can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason the build failed.
 
@@
 \paragraph{Studying Conversations about Build Failures}
-Some researchers are looking into conversations of developers surrounding CI builds and pull requests \todo{citation needed: nathan cassee did this in his master thesis (the paper on it is either rejected or not yet published), did not find others yet that do this}.
+Some researchers are looking into conversations of developers surrounding CI builds and pull requests \todo{citation needed: nathan cassee (with Alexander Sebrenik) did this in his master thesis (paper got accepted, will get link when preprint is finished), did not find others yet that do this}.
 The chunks describing why a build failed, or the results of chunk retrieval techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
 
-\subsection{Chunk Retrieval Evaluation}
-We created \emph{LogChunks} to evaluate and compare different chunk retrieval techniques for build logs.
-The first technique is based on synthesizing programs from examples using the Microsoft PROSE library.
-A user provides a small number of examples to describe which text part the program should extract.
-PROSE then synthesizes a program of regular expressions that is consistent with these examples.
-We compared this extraction technique to a text similarity approach, which selects the lines of a build log which are most similar to the ones in the given user examples.
-Lastly, we investigated searching for keywords that are associated with the given user examples.
+% \subsection{Chunk Retrieval Evaluation}
+% We created \emph{LogChunks} to evaluate and compare different chunk retrieval techniques for build logs.
+% The first technique is based on synthesizing programs from examples using the Microsoft PROSE library.
+% A user provides a small number of examples to describe which text part the program should extract.
+% PROSE then synthesizes a program of regular expressions that is consistent with these examples.
+% We compared this extraction technique to a text similarity approach, which selects the lines of a build log which are most similar to the ones in the given user examples.
+% Lastly, we investigated searching for keywords that are associated with the given user examples.
 
-The log chunks in this data set provided the examples for these techniques, the keywords were used to configure the keyword search.
-The structural categories enabled us to measure how structurally similar the examples have to be for a technique to be applicable.
+% The log chunks in this data set provided the examples for these techniques, the keywords were used to configure the keyword search.
+% The structural categories enabled us to measure how structurally similar the examples have to be for a technique to be applicable.
 
-Our results show that program synthesis is well suited to retrieve information chunks from build logs when the targeted information is always presented in a structurally identical way and the user requires a high confidence in the precision and recall of the output.
-Using text similarity is advisable when precision is valued higher than recall and we recommend keyword search when recall is valued higher than precision.
-We present more detailed results, background and our study design in \todo{ref (preprint or so?) of full journal paper (or thesis?)}.
+% Our results show that program synthesis is well suited to retrieve information chunks from build logs when the targeted information is always presented in a structurally identical way and the user requires a high confidence in the precision and recall of the output.
+% Using text similarity is advisable when precision is valued higher than recall and we recommend keyword search when recall is valued higher than precision.
+% We present more detailed results, background and our study design in \todo{ref (preprint or so?) of full journal paper (or thesis?)}.
 
@@
 It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc}, related data from GHTorrent~\cite{gousios2013ghtorrent}, the corresponding git repository and data obtained through analysis of the build logs.
-The data obtained through build logs contains the names of failing test cases, similar to the reason the build failed in \emph{LogChunks}.
+The data obtained through build logs contains the names of failing test cases, similar to the chunk describing why the build failed in \emph{LogChunks}.
 However, these values are obtained through a manually developed parser, which only supports specific Ruby test runners and Java Maven or JUnit logs.
-\emph{LogChunks} provides manually labeled data points on the description of the build failure reason for a much wider selection of programming languages.
+\emph{LogChunks} provides manually labeled data points on the description of why the build failed for a much wider selection of programming languages.
 
 \subsection{Travis CI Build Log Data Set}
-Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected a large amount of Travis CI build logs from 130 github repositories to analyze their use of the Checkstyle plugin.
+Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected a large amount of Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
 They selected Maven repositories that included the Checkstyle plugin and also used Travis CI\@.
@@
 
-% \begin{figure}[tbp]
-% 	\centering
-% 	\includegraphics[width=0.45\textwidth, clip]{exampleXml.png}
-% 	\caption{One example from the php/php-src repository in \emph{LogChunks}}
-% 	\label{fig:dev-survey}
-% \end{figure}
-
 This section describes the file structure and the data schema of \emph{LogChunks}.
@@
 
-\emph{LogChunks} has two top level folders, \texttt{logs} and \texttt{build-failure-reason}.
+\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
 Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
 
-The logs are organized in folders for each repository, identified through the repository slug: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater }.
+The logs are organized in folders for each repository, identified by \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater }.
 Within each repository folder the logs are separated according to build status.
@@
 The folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
-The data set provides an XML file for each repository \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater .xml}) categorized according to the main language of the repository.
-The schema of these XML files is presented in Listing \ref{lst:examples}.
+The data set provides an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
+Listing~\ref{lst:examples} presents the schema of these XML files.
 
@@
 
-\paragraph{Chunk Describing Why The Build Failed}
+\paragraph{Chunk That Describes Why The Build Failed}
 The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
-This could be the failing test case, the description of a failed linter rule or a compiler error.
+This can be the failing test case, the description of a failed linter rule or a compiler error.
 The \texttt{Chunk} is one continuous string cut from the build log.
@@
 Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
-For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
-In these instances the \texttt{Chunk} contains the lines describing that the build failed.
+%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
+%In these instances the \texttt{Chunk} contains the lines describing that the build failed.
 
@@
 
-To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to a 1000 builds per repository and keep ten for each status.
+To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to 1000 builds per repository and keep ten for each status.
 We discard all statuses except \emph{failed}~\cite{travis2009buildstatus}.
@@
 \paragraph{Log Sampling}
-For each build the \texttt{TravisRequester} then selects a log to download.
+For each build, the \texttt{TravisRequester} then selects a log to download.
 Travis CI attributes logs to \emph{jobs}.
-A single build can consist of multiple jobs, e.g.\ building the same code version and executing tests in various different testing environments.
+A single build can consist of multiple jobs, e.g.\ building the same code version and executing tests in different testing environments.
 A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
@@
 
-\paragraph{Chunk Describing Why The Build Failed}
+\paragraph{Chunk That Describes Why The Build Failed}
 For each repository, the labeler skimmed through the build logs and tried to identify the first occurrence of a description why the build failed.
@@
 The labeler should start the categories with 0 and increase as new ones appear.
-For reproducibility we presented the logs in chronological build order.
+For reproducibility, we presented the logs in chronological build order.
 
@@
 \label{sec:validation}
-We validate our collected data points in two different ways.
-A different labeler performed a second pass of labeling the build failure reason, keywords and structural categories on a subset of the data.
-In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set.
-We asked them whether our retrieval of the log part describing the reason the build failed was correct.
-This sections describes these two validation studies.
+% We validate our collected data points in two different ways.
+% A different labeler performed a second pass of labeling the build failure reason, keywords and structural categories on a subset of the data.
+% In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set.
+% We asked them whether our retrieval of the log part describing the reason the build failed was correct.
+%This sections describes these two validation studies.
+Following we present the two studies we conduct to validate the labeled data in \emph{LogChunks}.
 
@@
 
-Regarding the keywords the two labelers completely agreed in nine cases and completely disagreed in two cases.
+Regarding the keywords, the two labelers completely agreed in nine cases and completely disagreed in two cases.
 In nine cases there was partial overlap in the keywords of the two labelers, in two the first labeler selected additional keywords compared to the second, while the second labeler proposed additional keywords in seven cases.
@@
 There were implicit, inconsistent assumptions both labelers created during their work.
-In the following we describe these assumptions from both labelers for each data point and the implications on our description of the data classes.
+% In the following we describe these assumptions from both labelers for each data point and the implications on our description of the data classes.
 
-For the first data class, the reason the build failed, it was ambiguous whether the labeled substring should contain the information \emph{that} the build failed.
-This concerns statements like ``\texttt{The build exited with 1}''.
-One labeler included such statements, while the other one only focussed on the log parts describing \emph{why} the build failed, e.g.\ the name of the failing test case.
+% For the first data class, the reason the build failed, it was ambiguous whether the labeled substring should contain the information \emph{that} the build failed.
+% This concerns statements like ``\texttt{The build exited with 1}''.
+% One labeler included such statements, while the other one only focussed on the log parts describing \emph{why} the build failed, e.g.\ the name of the failing test case.
 
-While labeling the keywords a developer would use to search for the log part describing why the build failed, the one labeler allowed arbitrary strings appearing around the presented log part.
-In contrast to that, the other labeler focussed on actual \emph{words}, delimited by spaces or special characters.
-One labeler ignored capitalization, while the other one selected case-sensitive keywords.
-A third difference was that the first labeler was presented with all substrings from a repository, yielding more general keywords than the second labeler.
+% While labeling the keywords a developer would use to search for the log part describing why the build failed, the one labeler allowed arbitrary strings appearing around the presented log part.
+% In contrast to that, the other labeler focussed on actual \emph{words}, delimited by spaces or special characters.
+% One labeler ignored capitalization, while the other one selected case-sensitive keywords.
+% A third difference was that the first labeler was presented with all substrings from a repository, yielding more general keywords than the second labeler.
 
-For the structural categories this validation study showed a high overlap.
-In our instructions to the second labeler we did not emphasize the \emph{structural} aspect enough.
-They sorted into categories along \emph{why} the build failed, putting failing tests from different test runners into the same category even though the failing tests were presented differently in the log.
-
+% For the structural categories this validation study showed a high overlap.
+% In our instructions to the second labeler we did not emphasize the \emph{structural} aspect enough.
+% They sorted into categories along \emph{why} the build failed, putting failing tests from different test runners into the same category even though the failing tests were presented differently in the log.
+%
 Our main learning from this study is that adequately communicating all decisions and assumptions on how data is labeled is important and difficult.
@@
 \subsection{Developer Survey}
-For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
+%For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
 As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
-We only took the logs into accont and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
-
-The person who probably knows best why a build failed is the one committing the changes which triggered the build.
-If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.
+%We only took the logs into account and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
+%
+%The person who probably knows best why a build failed is the one committing the changes which triggered the build.
+%If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.
 We sent out mails to the original developers whose commits triggered the builds represented in \emph{LogChunks} and asked them whether the log chunk we labeled actually describes why the build failed.
-This section describes out survey and discusses our results.
+This section describes our survey and discusses our results.
 
@@
 Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
-We grouped all commits triggered by one developer and sent out a mail to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
+We grouped all commits triggered by one developer and sent out an mail to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
 %Figure~\ref{fig:dev-mail} shows one of the mails sent out.
@@
 %Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
-In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
+In the survey, we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
 As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
@@
 The study received answers about 18\% of the logs from \emph{LogChunks}.
-After manual correction, 91\% of the received answers said our labelled extractions were accurate.
+After manual correction, 91\% of the received answers said our labeled extractions were accurate.
 
@@
 One of our extractions only showed a warning and the developer proposed to also include the line above, stating that warnings are treated as errors in the build.
-In others that were identified as incorrect, we labelled the error message of an error that later ignored and did not lead to the build failing.
+In others that were identified as incorrect, we labeled the error message of an error that later ignored and did not lead to the build failing.
 
 \section{Conclusion}
-In this paper we introduced the \emph{LogChunks} data set encompassing about 800 build logs from a wide range of projects using Travis CI.
-For each log we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.
-Still there are limitations to our data set, which we present in the following.
+In this paper, we introduced the \emph{LogChunks} data set encompassing about 800 build logs from a wide range of projects using Travis CI\@.
+For each log, we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.
+Still, there are limitations to our data set, which we present in the following.
 We also propose several improvements and extensions to \emph{LogChunks}.

### 2019-12-11 thesis/txt/3-data-set.tex
shorten paper + fix bibliography for links

@@
 
-\paragraph{Chunk Describing Why The Build Failed}
+\paragraph{Chunk That Describes Why The Build Failed}
 The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
@@
 As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
-We only took the logs into accont and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
+We only took the logs into account and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
 

### 2019-12-12 thesis/txt/3-data-set.tex
add F1 Score to plots

@@
 The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
-This could be the failing test case, the description of a failed linter rule or a compiler error.
+This can be the failing test case, the description of a failed linter rule or a compiler error.
 The \texttt{Chunk} is one continuous string cut from the build log.
@@
 Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
-We grouped all commits triggered by one developer and sent out a mail to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
+We grouped all commits triggered by one developer and sent out an mail to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
 Figure~\ref{fig:dev-mail} shows one of the mails sent out.
@@
 Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
-In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
+In the survey, we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
 As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
@@
 One of our extractions only showed a warning and the developer proposed to also include the line above, stating that warnings are treated as errors in the build.
-In others that were identified as incorrect, we labelled the error message of an error that later ignored and did not lead to the build failing.
+In others that were identified as incorrect, we labeled the error message of an error that later ignored and did not lead to the build failing.
 

### 2019-12-12 thesis/txt/5-study.tex
add F1 Score to plots

@@
 		\centering
-		\includegraphics[width=0.5\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
+		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
 		\caption{Results of chunk retrieval with PBE}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
 		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training and test set}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
 		\caption{Precision and recall of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
 		\caption{Precision and recall of chunk retrieval with CTS for increasing training set size}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
 		\caption{Precision and recall of chunk retrieval with CTS for increasing number of structural categories in the training and test set}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
 		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
 		\caption{Precision and recall of chunk retrieval with KWS for increasing training set size}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
 		\caption{Precision and recall of chunk retrieval with KWS for increasing number of structural categories in the training and test set}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
 		\caption{Precision and recall of chunk retrieval with KWS compared to retrieval size factor}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/success-partial-all.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
 		\caption{Success of chunk retrievals for all techniques}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-all.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-all.pdf}
 		\caption{Precision and recall of all techniques compared}
@@
 	\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
 		\caption{Precision and recall of all techniques compared when training examples are in \emph{one} structural category}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
 		\caption{Precision and recall of all techniques compared when training examples are in \emph{more than one} structural categories}

### 2019-12-13 thesis/txt/1-related-work.tex
adding various examples to rw, data set and study

@@
 \subsection{Continuous Integration}
+\label{sec:rw-ci}
 The first paragraphs of this section present the results of past research into CI: its influence on the software engineering processes, the reasons for CI builds to fail and the role of testing and static analysis in CI builds.
@@
 A main difference between build logs and system logs is that system logs are fundamentally structured through events.
-Each line in the log file represents one event.
+Each line in the log file represents one event with a set of fields: timestamp, verbosity level and raw message content~\cite{he2017towards}.
+Listing \ref{lst:system-log} shows example lines from a system log.
+
 The first goal in parsing system log files is to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
@@
 Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+
+\lstset{
+  morekeywords={INFO, WARN, 2008-11-09},
+  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
+  showspaces=false,
+  showstringspaces=false,
+  keywordstyle=\color{blue},
+	frame=single,
+  extendedchars=false,
+  texcl=false
+}
+\begin{figure}[]
+  \centering
+  \begin{lstlisting}[breaklines=true]
+2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet- Responder: Received block blk_3587508140051953248 of size 67108864 from /10.251.42.84
+2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140051953248 terminating
+  \end{lstlisting}  
+  \caption{System Log Statements, adapted example from~\cite{he2017towards}}
+  \label{lst:system-log}
+\end{figure}
 
@@
 A regular expression in FlashExtract is a concatenation of tokens, e.g.\ standard character classes or string literals frequently occurring in the input examples.
+Listing \ref{lst:prose-program} shows a text extraction program synthesized by FlashExtract.
+This program defines the first position as after a colon followed by a newline character and before a piece of text with all capital letters.
+It defines the second position as before two newline characters.
 
@@
 We apply the text instantiation of FlashExtract to the domain of build logs with our chunk retrieval technique PBE\@.
+
+\lstset{
+  language=caml,
+  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
+  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
+  showspaces=false,
+  showstringspaces=false,
+  stringstyle=\color{blue},
+  keywordstyle=\bfseries\color{black},
+	frame=single,
+  extendedchars=false,
+  escapeinside=//
+}
+\begin{figure}[]
+  \centering
+  \begin{lstlisting}[breaklines=true]
+let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
+  \end{lstlisting}  
+  \caption{Text extraction program synthesized by FlashExtract}
+  \label{lst:prose-program}
+\end{figure}
 

### 2019-12-13 thesis/txt/2-models.tex
adding various examples to rw, data set and study

@@
 \midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In / Output Examples      \\
-Common Text Similarity       & CTS     & Tf-idf \& cosine similarity, mean number of lines expected & Line        & Output Examples           \\
-Keyword Search               & KWS     & Keywords, mean number of lines expected                    & Line        & Keywords, Context Length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval Length          \\
-Diff Approach                &         & Line not present in successful log, information retrieval  & Line        & Successful Log File       \\
+Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In / output examples      \\
+Common Text Similarity       & CTS     & Tf-idf \& cosine similarity, mean number of lines expected & Line        & Output examples           \\
+Keyword Search               & KWS     & Keywords, mean number of lines expected                    & Line        & Keywords, context length  \\
+Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
+Diff Approach                &         & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
 \bottomrule
@@
 We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
-In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (CTS), the concrete implementation is described in~\ref{sec:impl-ts}.
+In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs, which we refer to as \emph{CTS}\@.
 
@@
 As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
-In the following we will explain how we use simple keyword search to retrieve information from CI build logs (KWS).
+In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.
 

### 2019-12-13 thesis/txt/3-data-set.tex
adding various examples to rw, data set and study

@@
 \emph{LogChunks} is a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
-For each build log we manually labeled which substring describes why the build failed.
+For each build log we manually label which substring describes why the build failed.
 The data set also provides keywords a developer would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
@@
 \section{Motivation}
-\todo{In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity.
-One example set always contains build log in/output examples from the same software repository or project and for one specific build log information.
-They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
-Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
-The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
-To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.}
+We create \emph{LogChunks} as a data set for our empirical comparison study of the three chunk retrieval techniques PBE, CTS and KWS\@.
+In the following, we motivate which repositories and build logs we collect and what data we label for each build log.
+
+\paragraph{Log Collection}
+Existing build log analysis approaches, like writing a custom parser and creating regular expressions, are specific to the build tools which create the targeted log output.
+In contrast to that, our findings about the chunk retrieval techniques should not be specific to a specific build tool.
+As the main development language in a repository influences the build tools, we want our comparison study and \emph{LogChunks} cover a wide array of development languages.
+This is why we selected GitHub repositories from 29 different main development languages for our data set.
+
+Examples configure the chunk retrieval techniques we investigate.
+As the structure of a build log changes from project to project, these examples are specific to one project.
+A user of a chunk retrieval technique has to manually create the examples for for each targeted information and project.
+If the effort of creating examples should not too high, e.g. as high as developing a custom extraction program.
+For that reason, we choose ten logs and examples per repository for \emph{LogChunks}.
+
+\paragraph{Targeted Log Chunk}
+To evaluate chunk retrieval techniques, we have to select an information chunk the techniques should target.
+The targeted information chunk should occur as a realistic use case for developers or researchers and should not be trivial for any of the studied techniques.
+
+As the targeted log chunk we choose the part of the log describing why the build failed.
+Developers examine build logs to identify the cause of a build failure so they can address the issue.
+As we described in Section \ref{sec:rw-ci}, various researchers analyze build logs for the reason the build failed.
+
+In addition, the log chunk describing why a build failed can be represented in different ways in build logs.
+The representation and content of this log chunk depends on the tool reporting the fault and a build can fail in various of the tools involved in the build.
+This makes it non-trivial for any of the three techniques to extract.
+An example of a log chunk easily extractable by all of the three techniques is the \emph{TravisTiming}, described in Section \ref{sec:bli}.
+Travis CI logs its timing statements in a always consistent structure, therefore it would be easy for PBE to synthesize a regular expression program to extract them.
+The same holds for search keywords identifying the lines which contain the \emph{TravisTiming} and selecting lines with similar text content.
+
+\paragraph{Additional Data: Keywords and Structural Categories}
+For each log chunk example we additionally annotated keywords a developer would use to search for this log chunk, as well as a categorization of the chunks into structural categories according to their format within the log.
+The technique KWS is configured by keywords instead of in/output examples like the other techniques.
+To make the evaluation more consistent an comparable we choose to annotate keywords to each log chunk example.
+We can then use these extended examples as a configuration for KWS.
+An increasing number of examples is then comparable to the user basing his given keywords on more previously seen build logs.
+
+For our second research question we want to investigate how structurally similar the training examples have to be for a chunk retrieval technique to be applicable.
+To measure this in our study we choose to categorize the examples according to their format within the log.
+Section \ref{sec:data-schema} gives examples of log chunks from the same and different structural categories.
+As we evaluate the techniques separately for separate projects, the categorization is relative to the project which produced the build log.
 
@@
   morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-	frame=single
+  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
+	frame=single,
+	escapeinside=**
 }
-\begin{lstlisting}[caption={Example XML file from \emph{LogChunks}}, label=lst:examples, breaklines=true]
+\begin{figure}[]
+	\centering
+\begin{lstlisting}[breaklines=true]
 <Examples>
@@
 
+	\caption{Example XML file from \emph{LogChunks}}
+	\label{lst:examples}
+\end{figure}
+
 For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
@@
 \begin{itemize}
-	\item \texttt{Log:} the relative path to the input build log.
-	\item \texttt{Chunk:} the targeted information chunk. We are targeting the substring of the log that describes why the build failed.
-	\item \texttt{Keywords:} keywords a developer would use to search for the log chunk.
-	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
+	\item \textbf{\texttt{Log:}} the relative path to the input build log.
+	\item \textbf{\texttt{Chunk:}} the targeted information chunk. We are targeting the substring of the log that describes why the build failed.
+	\item \textbf{\texttt{Keywords:}} keywords a developer would use to search for the log chunk.
+	\item \textbf{\texttt{Category:}} a categorization of the structural representation of the log chunk within the build log.
 				The category is relative to the other examples for the same repository.
@@
 \paragraph{Keywords}
-The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
+The \texttt{Keywords} contain a list of one to three strings appearing within the \texttt{Chunk} or in the area around it in the build log.
 We aim to select keywords a developer would use to search for the \texttt{Chunk} when inspecting the build log.
+Some example keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{failed}'', ``\texttt{[-]}'', ``\texttt{===================================}'' or ``\texttt{ERR!}''.
 
@@
 For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
+
+\begin{figure}[]
+	\centering
+\begin{lstlisting}[breaklines=true]
+[0K$ ./sapi/cli/php run-tests.php -P -d extension=`pwd`/modules/zend_test.so $(if [ $ENABLE_DEBUG == 0 ]; then ...
+*{\color{cyan}-=-=-=-=-=-}*
+Illegal switch 'j' specified!
+*{\color{cyan}-=-=-=-=-=-}*
+Synopsis:
+\end{lstlisting}
+
+	\caption{Log chunk with one line of context from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\label{lst:same-category}
+\end{figure}
+
+\begin{figure}[]
+	\centering
+\begin{lstlisting}[breaklines=true]
+========DIFF========
+*{\color{cyan}-=-=-=-=-=-}*
+005+     Parameter #1 [ <optional> $flags ]
+
+005-     Parameter #1 [ <optional> $ar_flags ]
+========DONE========
+FAIL Bug#71412 ArrayIterator reflection parameter info [ext/spl/tests/bug71412.phpt] 
+*{\color{cyan}-=-=-=-=-=-}*
+TEST 9895/13942 [2/2 concurrent test workers running]
+\end{lstlisting}
+
+	\caption{Log chunk with one line of context from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\label{lst:different-category}
+\end{figure}
 

### 2019-12-13 thesis/txt/5-study.tex
adding various examples to rw, data set and study

@@
 		\label{fig:failure-reason-PBE}
+\end{figure}
+
+\lstset{
+  morekeywords={Test Output, Desired Test Output},
+  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
+  showspaces=false,
+  showstringspaces=false,
+  keywordstyle=\color{blue},
+	frame=single,
+  extendedchars=false,
+  texcl=false
+}
+\begin{figure}[]
+  \centering
+  \begin{lstlisting}[breaklines=true]
+Test Output:
+Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
+        on line 86 of sass/components/dropdown.sass
+
+Desired Test Output:
+Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
+        on line 86 of sass/components/dropdown.sass
+        from line 5 of sass/components/_all.sass
+        from line 6 of bulma.sass
+  \end{lstlisting}  
+  \caption{Example for an unsuccessful retrieval, PBE retrieved only two of the four targeted lines}
+  \label{lst:system-log}
 \end{figure}

### 2019-12-13 thesis/txt/6-discussion.tex
adding various examples to rw, data set and study

@@
 
+\begin{table}[htbp]
+\centering
+\begin{tabularx}{\textwidth}{@{}llll@{}}
+  \toprule
+  & PBE & CTS & KWS \\
+  \midrule
+  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
+  Training Set Size & 2 & no influence & 2 \\ 
+  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
+  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
+  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
+  Output Consumption by & program & human & human \\ 
+  \bottomrule
+\end{tabularx}
+\caption{Recommendations for each of the investigated chunk retrieval techniques}
+\label{tab:single-technique-recommendations}
+\end{table}
+
 \subsection{Program Synthesis by Example (PBE)}
+
 \paragraph{Configuration and Input}
@@
 
+\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/crt-recommendation.pdf}
+		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
+		\label{fig:crt-recommendation}
+\end{figure}
+
 \section{Recommendations of Suitable Techniques}
-% This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS\@.
-% It recommends which technique to use depending on the available configuration and 
 After discussing three chunk retrieval techniques separately we now want to unify out results into one recommendation scheme.
@@
 
-\begin{table}[htbp]
-\centering
-\begin{tabularx}{\textwidth}{@{}llll@{}}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabularx}
-\caption{Recommendations for each of the investigated chunk retrieval techniques}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
-		\label{fig:crt-recommendation}
-\end{figure}
-
 \section{Threats to Validity}
-
 There are several threats to the validity of the conclusions of our work.

### 2019-12-15 thesis/mini/abstract.tex
literature research about CI and benefits
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text

@@
 
-It is just a small template, that is hopefully helpful for writing your thesis.
-First, it gives a short introduction to its usage and the personalizations.
-Finally, it presents several examples of frequently used pieces of layout.
+Software builds from continuous integration produce detailed logs about the status and results of the various tools involved in the build.
+These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps or understand the cause of a build failure.
+However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
+This makes it hard to process and analyze them.
+In this paper, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
+We conduct an empirical study by comparing these techniques on our \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.
+Our findings show that none of the three techniques clearly outperforms the others.
+We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.
 

### 2019-12-15 thesis/txt/0-introduction.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text

@@
 \begin{itemize}
-  \item A model of the contained and retrievable information in CI build logs.
-  \item A model to characterize chunk retrieval techniques from CI build logs.
+  %\item A model of the contained and retrievable information in CI build logs.
+  %\item A model to characterize chunk retrieval techniques from CI build logs.
   \item A tool unifying several chunk retrieval techniques namely:
@@
         \end{itemize}
-  \item A study comparing the effectiveness of the three implemented techniques.
+  %\item A study comparing the effectiveness of the three implemented techniques.
   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
@@
 Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
-Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
+%Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
 This tool is also used for the comparison described in Chapter~\ref{sec:study}.

### 2019-12-15 thesis/txt/2-models.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text

@@
 	\centering
-	\includegraphics[width=\textwidth, trim={0cm 15cm 0cm 0cm}, clip]{img/tool-log-contribution.pdf}
+	\includegraphics[page=1, width=0.8\textwidth, trim={5cm 0.5cm 0.5cm 0.5cm}, clip]{img/overview-graphics.pdf}
 	\caption{Contribution of different tools to the build log}
@@
 Therefore, build logs are semi-structured, as described in Section~\ref{sec:rw-semi-structured-data}.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
-	\caption{Information retrievable from build logs}
-	\label{fig:build-log-information}
-\end{figure}
 
@@
 Figure~\ref{fig:build-log-information} shows an overview of these information examples.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
+	\caption{Information retrievable from build logs}
+	\label{fig:build-log-information}
+\end{figure}
 
@@
 
+\section{Tool Implementation}
+For our comparison study we implemented PBE, CTS, KWS and RLR and a unifying interface.
+The unified interface is implemented in Ruby and calls the separate technique implementations over the command line.
+The implementation of PBE in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
+We implemented CTS, KWS and RLR using R and the text2vec library~\cite{text2vec2019webpage}.
+
 \end{document}

### 2019-12-15 thesis/txt/3-data-set.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text

@@
 \label{sec:data-set}
-\includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
+
 This chapter describes the creation of the \emph{LogChunks} data set that we use in our empirical comparison of chunk retrieval techniques.
@@
 %For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled really describes the reason the build failed.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[page=3, width=\textwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{img/overview-graphics.pdf}
+	\caption{Overview of \emph{LogChunks}}
+	\label{fig:lc-overview}
+\end{figure}
 
@@
 
-The logs are organized in folders for each repository, identified by \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater }.
+The logs are organized in folders for each repository.
 Within each repository folder the logs are separated according to build status.
@@
 The folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
-The data set provides an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
+The data set provides an XML file for each repository.
 Listing~\ref{lst:examples} presents the schema of these XML files.
@@
 Two examples fall into the same structural categories if they are surrounded by similar markings.
+Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
+In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
 For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
 For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
-
-\begin{figure}[]
-	\centering
-\begin{lstlisting}[breaklines=true]
-[0K$ ./sapi/cli/php run-tests.php -P -d extension=`pwd`/modules/zend_test.so $(if [ $ENABLE_DEBUG == 0 ]; then ...
-*{\color{cyan}-=-=-=-=-=-}*
-Illegal switch 'j' specified!
-*{\color{cyan}-=-=-=-=-=-}*
-Synopsis:
-\end{lstlisting}
-
-	\caption{Log chunk with one line of context from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
-	\label{lst:same-category}
-\end{figure}
 
@@
 \end{lstlisting}
+	\caption{Log chunk with one line of context from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\label{lst:same-category}
+\end{figure}
 
-	\caption{Log chunk with one line of context from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+\begin{figure}[]
+	\centering
+\begin{lstlisting}[breaklines=true]
+[0K$ ./sapi/cli/php run-tests.php -P -d extension=`pwd`/modules/zend_test.so $(if [ $ENABLE_DEBUG == 0 ]; then ...
+*{\color{cyan}-=-=-=-=-=-}*
+Illegal switch 'j' specified!
+*{\color{cyan}-=-=-=-=-=-}*
+Synopsis:
+\end{lstlisting}
+	\caption{Log chunk with one line of context from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
 	\label{lst:different-category}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/dev-mail.png}
-	\caption{An example of the mails we sent out to developers for validation of our labeled log part}
-	\label{fig:dev-mail}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/dev-survey.png}
-	\caption{Survey for the validation with developers}
-	\label{fig:dev-survey}
-\end{figure}
-
 \subsection{Developer Survey}
@@
 As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
-
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-mails.pdf}
-		\caption{Number of mails answered, unanswered and not delivered}
-		\label{fig:mails-answers-received-mails}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
-		\caption{Proportions of logs about which mails were answered, unanswered, not delivered or we could not find a corresponding mail address}
-		\label{fig:mails-answers-received-builds}
-	\end{minipage}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
-		\caption{Label correctness as validated by developers}
-		\label{fig:mails-extraction-correct}
-	\end{minipage}\hfill
-	\begin{minipage}{0.45\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/dev-mails/logs-per-mail.pdf}
-		\caption{Average number of logs per sent out mail}
-		\label{fig:mails-logs-per-mail}
-	\end{minipage}
-\end{figure}
 
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/dev-mail.png}
+	\caption{An example of the mails we sent out to developers for validation of our labeled log part}
+	\label{fig:dev-mail}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-mails.pdf}
+		\caption{Number of mails answered, unanswered and not delivered}
+		\label{fig:mails-answers-received-mails}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
+		\caption{Proportions of logs about which mails were answered, unanswered, not delivered or we could not find a corresponding mail address}
+		\label{fig:mails-answers-received-builds}
+	\end{minipage}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/dev-survey.png}
+	\caption{Survey for the validation with developers}
+	\label{fig:dev-survey}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
+		\caption{Label correctness as validated by developers}
+		\label{fig:mails-extraction-correct}
+	\end{minipage}\hfill
+	\begin{minipage}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/logs-per-mail.pdf}
+		\caption{Average number of logs per sent out mail}
+		\label{fig:mails-logs-per-mail}
+	\end{minipage}
+\end{figure}
+
 \end{document}

### 2019-12-15 thesis/txt/5-study.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text

@@
 	\centering
-	\includegraphics[width=\textwidth, clip]{img/study-design.pdf}
+	\includegraphics[page=2, width=\textwidth, trim={0cm 1cm 1.5cm 0.5cm}, clip]{img/overview-graphics.pdf}
 	\caption{Study design of our technique comparison study}
@@
 Therefore, we train on examples from past build logs and test on future build logs.
+
 \paragraph{RQ 2.1: Size of Training and Test Set}
@@
 The size of the test set is one.
+
 \paragraph{RQ 2.2: Recording Structural Categories}
 To determine how structurally similar the examples for the chunk retrieval techniques need to be, we record the structural categories of the examples in the training and test sets.
+
 \paragraph{RQ2.3: Accuracy Metrics}
@@
 \begin{itemize}
+	 \itemsep0.5em
 	\item True positives: $TP = desiredlines \cap retrievedlines$
@@
 	\item Recall: $Recall = \frac{\# TP}{\# desiredlines}$
+	\item F$_{1}$-score: $2 * \frac{Precision * Recall}{Precision + Recall}$
 	\item Successful retrieval: $true\ if\ Recall = 1$
@@
 
-Precision of a chunk retrieval describes which proportion of the retrieved lines were not targeted.
+Precision of a chunk retrieval describes which proportion of the retrieved lines were targeted.
 Recall of a chunk retrieval describes which proportion of the targeted lines were retrieved.
-Throughout the presentation and discussion of our results we keep these two metrics separate, as they might have a different weight when choosing a suitable technique for a task.
+Throughout the presentation and discussion of our results we show these two metrics separate, as they might have a different weight when choosing a suitable technique for a task.
+In addition, we calculate the F1-Score, the harmonic mean of precision and recall.
 We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
@@
 In 30 cases the synthesized program did not extract all of the desired lines and had an average recall of 28\%.
+We present example of such an \emph{unsuccessful retrieval} in Listing \ref{lst:pbe-unsuccessful}, where the synthesized regular expression program only retrieved two of the four targeted lines.
 In 173 cases the PROSE program synthesis could not synthesize a regular expression program that is consistent with all of the training examples.
 
-Figure~\ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training examples.
+Figure~\ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training and test examples.
 It shows that the program synthesis is more likely to succeed when there are few categories present in the training examples.
@@
 Figure~\ref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of runs where PBE could synthesize a program consistent with all training examples.
-When the training set size increases from one to two, recall increases by 24\% and precision increases by 10\%.
-For two or more training examples the recall stays around 75\% and precision around 96\%.
+When the training set size increases from one to two, recall and F$_{1}$-score increase by 25\%, precision increases by 10\%.
+For two or more training examples the recall and F$_{1}$-score stay around 75\% and precision around 96\%.
 
@@
   \caption{Example for an unsuccessful retrieval, PBE retrieved only two of the four targeted lines}
-  \label{lst:system-log}
+  \label{lst:pbe-unsuccessful}
 \end{figure}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-		\caption{Precision and recall of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set}
 		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
 \end{figure}
+
+\subsection{Common Text Similarity (CTS)}
+Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision, recall and F$_{1}$-score of chunk retrieval using CTS for an increasing number of training examples.
+When using one to five training examples, the size of the training set has no noticeable influence on precision, recall or F$_{1}$-score of the chunk retrieval with CTS.
+
+Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for an increasing number of structural categories in the training and test examples.
+With increasing category count, precision, recall and F$_{1}$-score decrease.
+Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.
+
+Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with CTS\@.
+The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
+The recall ranges from 30\% to 55\%.
+A retrieval size factor of 1 gives the best F$_{1}$-score with 51\%.
 
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision and recall of chunk retrieval with CTS for increasing training set size}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for increasing training set size}
 		\label{fig:recall-precision-examplecount-CTS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision and recall of chunk retrieval with CTS for increasing number of structural categories in the training and test set}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for increasing number of structural categories in the training and test set}
 		\label{fig:recall-precision-categorycount-CTS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
-		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS compared to retrieval size factors}
 		\label{fig:contextsizefactor-precision-recall-CTS}
 \end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision and recall of chunk retrieval using CTS for an increasing number of training examples.
-When using one to five training examples, the size of the training set has no noticeable influence on recall and precision of the chunk retrieval with CTS.
-
-Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for an increasing number of structural categories in the training and test examples.
-With increasing category count, precision and recall decrease.
-Especially for more than four categories present we have no chunk retrieval runs where all desired lines were extracted.
-
-Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision and recall of chunk retrieval runs with CTS\@.
-The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
-The recall ranges from 30\% to 55\%.
 
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision and recall of chunk retrieval with KWS for increasing training set size}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for increasing training set size}
 		\label{fig:recall-precision-examplecount-KWS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision and recall of chunk retrieval with KWS for increasing number of structural categories in the training and test set}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for increasing number of structural categories in the training and test set}
 		\label{fig:recall-precision-categorycount-KWS}
 \end{figure}
+
+\subsection{Keyword Search (KWS)}
+Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision, recall and F$_{1}$-score of chunk retrieval using KWS for different numbers of training examples.
+The recall increases by about 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
+The F$_{1}$-score stays around 26\%.
+
+Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for increasing number of structural categories in the training and test examples.
+For more than one structural category in the training and test examples the recall decreases about 20\% and the precision decreases about 6\%.
+For more than two structural categories no clear trend visible in precision, recall or F$_{1}$-score for an increasing amount of categories in the training and test examples.
+
+Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
+The precision is 19\% when retrieving half expected number of lines. On average 9\% of the lines in the build log are retrieved then.
+When 2.5 times the expected number of lines, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
+The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
 
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-		\caption{Precision and recall of chunk retrieval with KWS compared to retrieval size factor}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor}
 		\label{fig:contextsizefactor-precision-recall-KWS}
@@
 
-\subsection{Keyword Search (KWS)}
-Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision and recall of chunk retrieval using KWS for different numbers of training examples.
-The recall increases by about 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
+\subsection{Comparison of All Techniques}
+Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval of the different techniques in our study.
+CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
+With 38.25\%, KWS also has the highest number of successful extractions, followed by PBE with 34.5\%.
+PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.
 
-Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for increasing number of structural categories in the training and test examples.
-For more than one structural category in the training and test examples the recall decreases about 20\% and the precision decreases about 6\%.
-For more than two structural categories no clear trend visible in precision and recall for an increasing amount of categories in the training and test examples.
+The averaged precision, recall and F$_{1}$-score of all techniques is compared in Figure~\ref{fig:recall-precision-all}.
+The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
+PBE has the highest average precision with 95\%.
+Chunk retrieval with CTS has tmhe highest average F$_{1}$-score with 51\% and the second highest recall with 46\%.
+KWS has the smallest precision of the three chunk retrieval techniques.
+With 16\% it is still higher than the precision of the RLR baseline with 7\%.
+KWS has the highest recall of all techniques with 70\%.
 
-Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision and recall of chunk retrieval runs with KWS\@.
-The precision is 19\% when retrieving half expected number of lines. On average 9\% of the lines in the build log are retrieved then.
-When 2.5 times the expected number of lines, the precision decreases to 10\% and a quater of the lines in the build log are retrieved on average.
-The recall ranges from 58\% to 75\%.
+Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
+For more than one present category, the recall of PBE decreases greatly.
+For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.
 
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-all.pdf}
-		\caption{Precision and recall of all techniques compared}
+		\caption{Precision, recall and F$_{1}$-score of all techniques compared}
 		\label{fig:recall-precision-all}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision and recall of all techniques compared when training examples are in \emph{one} structural category}
+		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{one} structural category}
 		\label{fig:recall-precision-singlecategory-all}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision and recall of all techniques compared when training examples are in \emph{more than one} structural categories}
+		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{more than one} structural categories}
 		\label{fig:recall-precision-multicategory-all}
@@
 
-\subsection{Comparison of All Techniques}
-Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval of the different techniques in our study.
-CTS and KWS extract some of the desired lines in 79\% and 88.5\%.
-With 38.25\%, KWS also has the highest number of successful extractions, followed by PBE with 34.5\%.
-PBE has the lowest number of partial extraction with only 18 out of 400 chunk retrieval runs.
-
-The averaged precision and recall of all techniques is compared in Figure~\ref{fig:recall-precision-all}.
-The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
-Chunk retrieval with CTS has the highest average precision with 46\% and the second best recall with 45\%.
-KWS has the smallest precision of the three chunk retrieval techniques.
-With 16\% it is still higher than the precision of the RLR baseline with 7\%.
-KWS has the highest recall of all techniques with 70\%.
-
-Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
-For more than one present category, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.
-
 \end{document}

### 2019-12-15 thesis/txt/6-discussion.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text

@@
 
-Extracting the average number of lines present in the training examples seems to give the best balance of precision and recall for CTS\@.
+Extracting the average number of lines present in the training examples gives the best retrieval results for CTS, according to the F$_{1}$-score.
 
@@
 KWS has a higher recall than both other techniques for multiple structural categories present in the training and test examples.\@.
-This makes KWS a good technique if there is little prior knowledge on how the desired BLI is represented in the build log to be analyzed.
+This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.
 For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
@@
 
+\paragraph{Example of Using the Recommendation Scheme}
+To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we follow with describing two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.
+
+In our first example, a researcher studies whether there test failures in CI are caused by a small or by a large group of test cases.
+They gather CI build logs from various projects, which are their only available data source.
+The task of the researcher is to extract the name of the failing test case from each build log.
+When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test case is in the investigated build logs.
+As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, not predictable structural representations.
+The next question is whether they value precision over recall.
+As they have to manually inspect the results of both CTS and KWS, they choose recall over precision to avoid having to inspect the whole log in case the relevant information chunk was not retrieved.
+Therefore, our decision tree recommends them to use KWS\@.
+
+In case the researchers want to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
+Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each tes tool separately.
+
+In our second example, a software development team wants to monitor the performance of the phases within their CI build.
+They are using Travis CI, which measures the duration of build phases and documents them within the build log.
+As all log statements that report timing measurements are formatted the same way, the targeted log chunks are from one structural category.
+Therefore the development team can use PBE to retrieve the duration of a build phase as well as its name.
+
 \section{Threats to Validity}

### 2019-12-15 thesis/txt2/4-tool.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text

--- 2019-11-17 thesis/txt/4-tool.tex
@@
 \label{sec:implementation}
-To evaluate PBE, CTS and KWS on \emph{LogChunks} we implemented them and a unifying interface to retrieve chunks from build logs.
+To evaluate PBE, CTS and KWS on \emph{LogChunks} we implemented them and a unifying interface to retrieve information chunks from build logs.
 
@@
 
-The unified interface is implemented in Ruby and gives access to all the CTRs we implemented.
-This section describes how to use it to retrieve chunks for a build log or evaluate a CRT.
-% As we implemented the information retrieval techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interface.
-Our unified interface then in turn calls the various different IE techniques over the command line.
+The unified interface is implemented in Ruby and gives access to all the chunk retrieval techniques we implemented.
+This section describes how to use it to retrieve chunks for a build log or evaluate a chunk retrieval technique.
 
-To retrieve chunks from a build log use the option \texttt{-a analyze} with these options:
+To retrieve an chunk from a build log use the option \texttt{-a analyze} with these options:
 \begin{itemize}
@@
 For pbe, ir and random analysis only.
-See Section \ref{sec:example-set} for the definition of an example set.
+See Section~\ref{sec:example-set} for the definition of an example set.
     \item \texttt{-p} \textbf{Build Log Path} The path to the file to be analyzed.
@@
     \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
-    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section \ref{sec:example-set} for the definition of an example set.
+    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section~\ref{sec:example-set} for the definition of an example set.
     \item \texttt{-s} \textbf{Selection Technique} \texttt{chronological, random or manual} How the order of the examples should be selected during learning.
@@
 
-% We provide two different modes: \emph{analysis} and \emph{evaluation}.
-% The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting retrieval on the console output.
-The \emph{evaluation} takes an
-
-% unification tool, reference CLI somehow nicely?,
-
-% ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)
-
-%\section{Overall Implementation Remarks}
-% There are multiple implementation specialities that span over all languages, frameworks and implemented techniques.
-% The following section discusses preprocessing and escaping of the parsed build log files / example sets, as well as\textellipsis \todo{more?}
-
-% \subsection*{Preprocessing Log Text}
-% \label{sec:impl-preprocessing}
-
-%\section*{PBE}
-% \paragraph{Program Synthesis by Example (PBE)}
-% \label{sec:impl-pbe}
-% Our implementation of the PBE chunk retrieval in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
-% % The first technique we implemented was the PROSE regular expression program synthesis. As it is based on the PROSE library from Microsoft provided in C\# we also chose C\# for our tool. 
-% % implementation details :)
-
-% % C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)
-
-% \paragraph{Common Text Similarity (CTS)}
-% \label{sec:impl-ts}
-% We implemented the CTS chunk retrieval using R and the text2vec library.
-
-% % impl details,
-
-% % R, text2vec, tokenized vectors, impl of preprocessing?
-
-% % don't repeat from IE models section!
-
-% \paragraph{Keyword Search (KWs)}
-% \label{sec:impl-skws}
-% impl details,
-
-% R, simple!
-
 \end{document}

### 2019-12-16 msr-paper/paper.tex
change introduction story

@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{ci, build log analysis, build failure, chunk retrieval}
+\keywords{CI, Build Log Analysis, Build Failure, Chunk Retrieval}
 
@@
 These build logs contain a lot of valuable information for developers and researchers.
-Developers examine timer reports to track how different stages of the build process perform.
-Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
+%Developers examine time measurement log statements to track how different stages of the build process perform.
+%Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
 Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
@@
 Build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
-Therefore, developers and researchers can only use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.
+Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.
 
@@
 
-These approaches have various downsides and strengths:
+These approaches have various strengths and weaknesses:
 Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.

### 2019-12-16 thesis/txt/0-introduction.tex
change introduction story

@@
 
-CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
-The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
-Build logs are a valuable data source for developers and researchers.
-Developers read them to analyze why their build failed or how different stages of the build process perform.
-Researchers can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
-However, these two groups can only use the information within the build logs if they can adequately retrieve the information relevant to them.
+CI builds produce logs which report the progress and results of the steps within the build.
+These build logs contain a lot of valuable information for developers and researchers.
+Developers examine log statements of time measurements to track how different stages of the build process perform.
+Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
+Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed tests to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
 
-There are different techniques to retrieve information from CI build logs. Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
+Build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
+Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.
+
+% CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
+% The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
+% Build logs are a valuable data source for developers and researchers.
+% Developers read them to analyze why their build failed or how different stages of the build process perform.
+% Researchers can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
+% However, these two groups can only use the information within the build logs if they can adequately retrieve the information relevant to them.
+
+There are different techniques to retrieve information chunks from CI build logs.
+Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
 Such regular expressions are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
@@
 
-These approaches have various downsides and strengths:
+These approaches have various strengths and weaknesses:
 Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.
 Custom parsers are powerful though fragile towards changes in the log structure.
+The structure of build logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
 Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.

### 2019-12-16 msr-paper/paper.tex
incorporate andys feedback v1

@@
 \usepackage{listings}
+\usepackage{tabularx}
 
@@
 In addition, the data set categorizes the log chunks according to their format within the log text and provides keywords that a developer would use to search for the log chunks.
+The width and depth of the \emph{LogChunks} data set makes it an ideal basis to further explore build log analysis, which can ultimately increase our understanding of CI build failures.
 \emph{LogChunks} can be the basis to assess further build log analysis techniques and studies about why CI builds fail.
@@
 Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
-CI builds produce logs which report the progress and results of the steps within the build.
+Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
+A build on a CI server typically compiles and packages the software, executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.
+
+CI builds produce logs which report the results of the steps within the build.
 These build logs contain a lot of valuable information for developers and researchers.
@@
 Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
 Build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
@@
 
-In this paper, we illustrate potential use cases of \emph{LogChunks} and past studies using the data set.
+In this paper, we illustrate potential use cases of \emph{LogChunks}.% and our past study using the data set.
 Section~\ref{sec:related-data-sets} describes related data sets and how \emph{LogChunks} differs from them.
@@
 
-We published \emph{LogChunks} through Zendoo: \todo{insert zendoo link}.
+We published \emph{LogChunks} through Zenodo: \todo{insert zenodo link}.
 
@@
 The techniques we compared are based on program synthesis from examples, text similarity and searching for keywords.
-In addition that, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
+In addition to that, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
 For example, we can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason the build failed.
@@
 Analyzing these could help us understand how developers process build logs and which keywords a tool should use to mark an error description so developers quickly find it through text search.
+We could also recommend users which search keywords they should use to find why the build failed.
 
@@
 The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI\@.
-It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc}, related data from GHTorrent~\cite{gousios2013ghtorrent}, the corresponding git repository and data obtained through analysis of the build logs.
+It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc}, related data from GitHub~\cite{github2019website} through GHTorrent~\cite{gousios2013ghtorrent}, the corresponding git repository, and data obtained through analysis of the build logs.
 The data obtained through build logs contains the names of failing test cases, similar to the chunk describing why the build failed in \emph{LogChunks}.
@@
 Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
+	\caption{Overview of \emph{LogChunks}}
+	\label{fig:lc-overview}
+\end{figure}
 
@@
 Within each repository folder the logs are separated according to build status.
-Currently \emph{LogChunks} only contains logs from \texttt{failed} builds.
+Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
 The build status folder contains the full logs in files named with the ID of the Travis CI build that produced the log.
@@
 \end{lstlisting}
+	\caption{Example XML file from \emph{LogChunks}}
+	\label{lst:examples}
+\end{figure}
 
@@
 	\item \texttt{Log:} the relative path to the input build log.
-	\item \texttt{Chunk:} the targeted information chunk. We are targeting the substring of the log that describes why the build failed.
+	\item \texttt{Chunk:} the log chunk that describes why the build failed.
 	\item \texttt{Keywords:} keywords a developer would use to search for the log chunk.
@@
 Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
+
+\begin{figure*}[htbp]
+\centering
+\begin{tabularx}{\textwidth}{@{}lXlX@{}}
+  \toprule
+  & Description & Unit & Example \\
+  \midrule
+  Log & relative path to the input build log & Path to Text File & Haskell/koalaman@shellcheck/failed/501296412.log \\
+  Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
+    Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
+  Keywords & keywords a developer would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
+  Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
+  \bottomrule
+\end{tabularx}
+\caption{Recommendations for each of the investigated chunk retrieval techniques}
+\label{tab:single-technique-recommendations}
+\end{figure*}
 
@@
 We aim to select keywords a developer would use to search for the \texttt{Chunk} when inspecting the build log.
+Some example keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{failed}'', ``\texttt{[-]}'', ``\texttt{===================================}'' or ``\texttt{ERR!}''.
 
@@
 Two examples fall into the same structural categories if they are surrounded by similar markings.
+Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
+In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
 For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
 For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
+
+\begin{figure}[]
+	\centering
+\begin{lstlisting}[breaklines=true]
+========DIFF========
+*{\color{cyan}-=-=-=-=-=-}*
+005+     Parameter #1 [<optional> $flags]
+
+005-     Parameter #1 [<optional> $ar_flags]
+========DONE========
+FAIL Bug#71412 ArrayIterator reflection parameter info [ext/spl/tests/bug71412.phpt] 
+*{\color{cyan}-=-=-=-=-=-}*
+TEST 9895/13942 [2/2 test workers running]
+\end{lstlisting}
+	\caption{Log chunk with one line of context from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\label{lst:same-category}
+\end{figure}
+
+\begin{figure}[]
+	\centering
+\begin{lstlisting}[breaklines=true]
+[0K$ ./sapi/cli/php run-tests.php -P ...
+*{\color{cyan}-=-=-=-=-=-}*
+Illegal switch 'j' specified!
+*{\color{cyan}-=-=-=-=-=-}*
+Synopsis:
+\end{lstlisting}
+	\caption{Log chunk with one line of context from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\label{lst:different-category}
+\end{figure}
 
@@
 First, we determine a set of repositories to query logs from.
-Our \texttt{GHTorrentParser} queries the \emph{GHTorrent}~\cite{gousios2013ghtorrent} data set for the most popular languages on GitHub~\cite{github2019website}.
+Our \texttt{GHTorrentParser} queries the \emph{GHTorrent}~\cite{gousios2013ghtorrent} data set for the most popular languages on GitHub.
 It then retrieves the most popular repositories for a given language.
@@
 
-For \emph{LogChunks} we queried GHTorrent from 01/04/2018 for the three most popular repositories of each of the 30 most popular languages.
+For \emph{LogChunks} we queried GHTorrent on 01/04/2018 for the three most popular repositories of each of the 30 most popular languages.
+Among the selected repositories are, for example, \texttt{git/git},  \texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.
 
@@
 A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
-\texttt{TravisRequester} queries each build for the first job, which has the same state.
+\texttt{TravisRequester} queries each build for the first job which has the same state.
 For the selected jobs, the tool queries the Travis API V3 over HTTPS to obtains the corresponding build log.
@@
 These 32 mails related to 68 of the build logs.
-We received answers from 61 developers, responding about 144 build logs.
+We received answers from 61 developers, corresponding with 144 build logs.
 %Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.

### 2019-12-16 thesis/txt/5-study.tex
incorporate prof. knapps feedback on formulas

@@
 \paragraph{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($retrievedlines$).
-As oracle in our evaluation, we save the desired lines from the output of the test example ($desiredlines$).
+To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($\mathit{RetrievedLines}$).
+As oracle in our evaluation, we save the desired lines from the output of the test example ($\mathit{DesiredLines}$).
 
@@
 \begin{itemize}
-	 \itemsep0.5em
-	\item True positives: $TP = desiredlines \cap retrievedlines$
-	\item Precision: $Precision =  \frac{\# TP}{\# retrievedlines}$
-	\item Recall: $Recall = \frac{\# TP}{\# desiredlines}$
-	\item F$_{1}$-score: $2 * \frac{Precision * Recall}{Precision + Recall}$
-	\item Successful retrieval: $true\ if\ Recall = 1$
+	 \itemsep0.75em
+	\item True positives: $\mathit{DesiredLines} \cap \mathit{RetrievedLines}$
+	\item Precision: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{RetrievedLines}}$
+	\item Recall: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{DesiredLines}}$
+	\item F$_{1}$-score: $2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
+	\item Successful retrieval: $\mathit{true}\ \mathit{if}\ \mathit{Recall} = 1$
 \end{itemize}
@@
 Throughout the presentation and discussion of our results we show these two metrics separate, as they might have a different weight when choosing a suitable technique for a task.
-In addition, we calculate the F1-Score, the harmonic mean of precision and recall.
+In addition, we calculate the F1-score, the harmonic mean of precision and recall.
 We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.

### 2019-12-18 msr-paper/paper.tex
various corrections + acknowledgements

@@
 Build failures are common in continuous integration (CI), but identifying the root cause of a failure is difficult.
-Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
-We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
+To stimulate research in this area, we present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
 For each build log we manually labeled the log part (chunk) describing why the build failed.
 We validated the data set by surveying the developers of the projects which produced the builds.
-In addition, the data set categorizes the log chunks according to their format within the log text and provides keywords that a developer would use to search for the log chunks.
-The width and depth of the \emph{LogChunks} data set makes it an ideal basis to further explore build log analysis, which can ultimately increase our understanding of CI build failures.
-\emph{LogChunks} can be the basis to assess further build log analysis techniques and studies about why CI builds fail.
-
+Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
+The width and depth of the \emph{LogChunks} data set makes it an ideal basis to benchmark build log analysis techniques.
+Benchmarking different techniques will advance this research area and ultimately increase our understanding of CI build failures.
 \end{abstract}
@@
 Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
-A build on a CI server typically compiles and packages the software, executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.
-
 CI builds produce logs which report the results of the steps within the build.
@@
 Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-Build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
+
+The problem is, that build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
 Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.
@@
 At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred over other alternatives.
-In addition, there is currently no data set available to evaluate and compare such chunk retrieval techniques for build logs.
+In addition, there is currently no data set available to benchmark such build log analysis techniques.
 
@@
 
-In this paper, we illustrate potential use cases of \emph{LogChunks}.% and our past study using the data set.
-Section~\ref{sec:related-data-sets} describes related data sets and how \emph{LogChunks} differs from them.
-The following section introduces the data schema, how to access the data set, as well as limitations and potential improvements.
-We present our data collection in Section~\ref{sec:data-collection}.
-To validate our labels we performed a second labeling of a sample of the data.
-In addition, we surveyed the developers, whose commits triggered the builds, whether our labeled log chunk describes why their build failed.
-Section~\ref{sec:validation} presents the two validation studies.
-To conclude we describe limitations as well as potential improvements of \emph{LogChunks}.
+% andy: okay if no structure overview in 4 page paper, place too valuable
+% In this paper, we illustrate potential use cases of \emph{LogChunks}.% and our past study using the data set.
+% Section~\ref{sec:related-data-sets} describes related data sets and how \emph{LogChunks} differs from them.
+% The following section introduces the data schema, how to access the data set, as well as limitations and potential improvements.
+% We present our data collection in Section~\ref{sec:data-collection}.
+% To validate our labels we performed a second labeling of a sample of the data.
+% In addition, we surveyed the developers, whose commits triggered the builds, whether our labeled log chunk describes why their build failed.
+% Section~\ref{sec:validation} presents the two validation studies.
+% To conclude we describe limitations as well as potential improvements of \emph{LogChunks}.
 
@@
   \midrule
-  Log & relative path to the input build log & Path to Text File & Haskell/koalaman@shellcheck/failed/501296412.log \\
+  Log & relative path to the input build log & Path to Log File & Haskell/koalaman@shellcheck/failed/501296412.log \\
   Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
@@
 
-\section{Conclusion}
+\section{Summary}
 In this paper, we introduced the \emph{LogChunks} data set encompassing about 800 build logs from a wide range of projects using Travis CI\@.

### 2019-12-18 thesis/mini/abstract.tex
various corrections + acknowledgements

@@
 This makes it hard to process and analyze them.
-In this paper, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
+In this thesis, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
 We conduct an empirical study by comparing these techniques on our \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.

### 2019-12-18 thesis/mini/acknowledgments.tex
describe inter-rater reliability, conclusion and fw, add se logos
various corrections + acknowledgements

@@
 \noindent
+I would like to thank Moritz for his great support, detailed feedback and his invaluable teaching how to do proper research.
+I could not have imagined a better advisor for my master's thesis.
+
+\noindent
+Furthermore, I would like to thank Annibale for his helpful feedback and teaching me which is the proper vocabulary to describe my work.
+
+\noindent
+I want to pay my special regards to Prof. Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.
+
+\noindent
+I would like to acknowledge Martin, Martijn and Dominik for their thorough reviews.
+
+\noindent
+I am extremely grateful for my newfound friends, the fourth floor group and my colleagues from SERG.
+Thank you for welcoming me with open arms and sparking joy in my days.
+
+\noindent
+Lastly, I want to thank Michi and Taico.
+Thank you for your calming input, critical reflection, your relentless support and upcheering.
+
 %I want to thank Moritz Beller for: support when coming to delft, great support and detailed feedback.
-invaluable contribution to this work and the large amount of things I learned about reserach in these last five months
-% annibale for his neverending input on study ideas, his expertise on information retrieval
-% prof. pretschner for his feedback and critical questions on the whether my evaluation is actually meaningful
-% prof. knapp?
-% Taico for his relentless support, upcheering in the emotional valleys of throwing everything out of the window and listening to my enthusiastic detailed descriptions of ?
-% Michi for his calming input and critical reflection of my working ethics
-% my new founld colleagues from SERG (xavier, enrique, ayoushi, pouria, luis, joseph), sparking joy in lunch and coffee breaks, good breaks for my focussed mind
+invaluable contribution to this work and the large amount of things I learned about reserach in these last five months, aufbauendes feedback
+% annibale for his neverending input on study ideas, his expertise on information retrieval, telling me the proper vocabulary to use and unlimited study and plotting ideas
+% prof. pretschner for his feedback and critical questions on the whether my evaluation is actually meaningful and what problems I really solve
+% prof. knapp? sharp eyes with formulas and /aufbauend/ words
+% Michi for his calming input and critical reflection of my working ethics / balance.
+% A big thank you to Martin, Taico, Martijn and Michi for their reviews.
+% my new found colleagues from SERG (xavier, enrique, ayoushi, pouria, luis, joseph), sparking joy in lunch and coffee breaks and beer evenings
 % the fourth floor group in welcoming me in a new country as I was one of them and showing me that even when you go to a completely new place you can find awesome friends there as well
+% Lastly, Taico for his relentless support, upcheering in the emotional valleys of throwing everything out of the window and listening to my enthusiastic detailed descriptions of ?
 

### 2019-12-18 thesis/txt/0-introduction.tex
incorporate andys feedback v1
various corrections + acknowledgements

@@
 
-CI builds produce logs which report the progress and results of the steps within the build.
+CI builds produce logs which report the results of the steps within the build.
 These build logs contain a lot of valuable information for developers and researchers.
@@
 
-Build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
+The problem is, that build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
 Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.

### 2019-12-18 thesis/txt/3-data-set.tex
incorporate andys feedback v1
various corrections + acknowledgements

@@
 We create \emph{LogChunks} as a data set for our empirical comparison study of the three chunk retrieval techniques PBE, CTS and KWS\@.
-In the following, we motivate which repositories and build logs we collect and what data we label for each build log.
+In the following, we motivate which repositories and build logs we collect and which data we label for each build log.
 
@@
 Existing build log analysis approaches, like writing a custom parser and creating regular expressions, are specific to the build tools which create the targeted log output.
-In contrast to that, our findings about the chunk retrieval techniques should not be specific to a specific build tool.
-As the main development language in a repository influences the build tools, we want our comparison study and \emph{LogChunks} cover a wide array of development languages.
+In contrast to that, our findings about the chunk retrieval techniques should not be specific to a particular build tool.
+As the main development language in a repository influences the build tools, we want our comparison study and \emph{LogChunks} to cover a wide array of development languages.
 This is why we selected GitHub repositories from 29 different main development languages for our data set.
@@
 A user of a chunk retrieval technique has to manually create the examples for for each targeted information and project.
-If the effort of creating examples should not too high, e.g. as high as developing a custom extraction program.
+The effort of creating these examples should not be too high, e.g. as high as developing a custom extraction program.
 For that reason, we choose ten logs and examples per repository for \emph{LogChunks}.
@@
 \end{lstlisting}
-
 	\caption{Example XML file from \emph{LogChunks}}
@@
 \end{lstlisting}
-	\caption{Log chunk with one line of context from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\caption[Log chunk from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}]{Log chunk from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from one line of context}
 	\label{lst:same-category}
@@
 \end{lstlisting}
-	\caption{Log chunk with one line of context from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\caption[Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}]{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk one line of context}
 	\label{lst:different-category}

### 2019-12-18 thesis/txt/6-discussion.tex
various corrections + acknowledgements

@@
 \section{Recommendations of Suitable Techniques}
-After discussing three chunk retrieval techniques separately we now want to unify out results into one recommendation scheme.
-We present a decision tree, which asks questions to a developer or researcher who wants to retrieve information chunks from build logs.
-The answers lead the user to more questions or the recommended technique as leaf nodes.
+After discussing three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
+We present a decision tree, which developers and researchers who want to retrieve information chunks from build logs can follow.
+The decision tree is built up of questions which either lead to more questions or to a leaf node containing a recommended technique.
 Figure~\ref{fig:crt-recommendation} presents the decision tree.
@@
 \emph{Caveat!} This is a preliminary theory based on the results from our comparison study.
-The recommendations are therefore likely based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
+The recommendations are therefore based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
 This decision tree is the answer to our first research question about which criteria influence the suitability of a chunk retrieval technique.
@@
 If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
-We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the precision or recall of the outcome and the user rather have output with low recall instead of no output at all.
+We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the precision or recall of the outcome and the user would rather have output with low recall instead of no output at all.
 When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.
@@
 
-In our first example, a researcher studies whether there test failures in CI are caused by a small or by a large group of test cases.
+In our first example, a researcher studies whether test failures in CI are caused by a small or by a large group of test cases.
 They gather CI build logs from various projects, which are their only available data source.
-The task of the researcher is to extract the name of the failing test case from each build log.
-When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test case is in the investigated build logs.
+The task of the researcher is to extract the names of the failing test cases from each build log.
+When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test cases is in the investigated build logs.
 As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, not predictable structural representations.
@@
 In case the researchers want to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each tes tool separately.
+Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each test tool separately.
 
@@
 The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
-It only consists of build logs from open source and therefore it is not clear whether our results are generalizable to industry projects.
+It only consists of build logs from open source projects and therefore it is not clear whether our results are generalizable to industry projects.
 We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
@@
 \paragraph{Training Set Size}
-Especially the results for CTS might influenced by the fact that we only trained on one to five examples.
+Especially the results for CTS might be influenced by the fact that we only trained on one to five examples.
 We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.
@@
 Our comparison study shows fewer measurements with many structural categories than with one category.
-This stems from the fact that we use such a realistic data set which in many cases has only one or few structural categories.
+This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.
 % \bp{

### 2019-12-18 thesis/txt/7-conclusion.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text
various corrections + acknowledgements

@@
 \label{sec:conclusion-fw}
-The goal of this thesis is to support researches and developers when they decide how to analyze build logs.
+The goal of this thesis is to support researchers and developers when they decide how to analyze build logs.
 We implemented and compared three different chunk retrieval techniques on our \emph{LogChunks} data set.
@@
 
-In the following we describe various future research opportunities based on our work:
+There are various future research opportunities based on our work:
 \begin{itemize}
   \item \textbf{Further Analysis of the \emph{LogChunks} Data Set} We created the \emph{LogChunks} data set specifically for our comparison study, though it can be the basis for various further analyses of build log data.
-  The keywords, for example, can be investigated to answer which keywords do developers use to search for the reason the build failed within build logs.
+  The keywords, for example, can be investigated to answer which keywords developers use to search for the reason the build failed within build logs.
   \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
@@
     \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focussed on precision and recall.
-  In addition to that, we propose to investigate how useful these outputs are to developers through controlled experiments.
+  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focuses on precision and recall.
+  In addition to precision and recall, we propose to investigate how useful these outputs are to developers through controlled experiments.
 \end{itemize}

### 2019-12-19 msr-paper/paper.tex
incorporate andys feedback from meeting

@@
 \author{Annibale Panichella}
+\author{Andy Zaidman}
 \author{Moritz Beller}
@@
 The width and depth of the \emph{LogChunks} data set makes it an ideal basis to benchmark build log analysis techniques.
-Benchmarking different techniques will advance this research area and ultimately increase our understanding of CI build failures.
+Benchmarking different techniques will advance the research area of build log analysis and ultimately increase our understanding of CI build failures.
 \end{abstract}
@@
 %Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
-Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
+They analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
 
@@
 
+Following Sim et al., creating a benchmark gives us the chance to ``increase the scientific maturity of the area''~\cite{sim2003using} of build log analysis.
+
 We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
 For each build log, we manually labeled which substring describes why the build failed.
-The data set also provides keywords a developer would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
+The data set also provides keywords the authors would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
 
@@
 
-\paragraph{Evaluate Information (Chunk) Retrieval Techniques}
-We created \emph{LogChunks} to evaluate and compare different techniques to retrieve information chunks from build logs \todo{cite journal paper (or preprint?)}.
+\paragraph{Benchmarking Build Log Analysis Techniques}
+We created this data set to evaluate and compare different techniques to retrieve information chunks from build logs. %\todo{cite journal paper (or preprint?)}.
 The techniques we compared are based on program synthesis from examples, text similarity and searching for keywords.
@@
 \paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
-\emph{LogChunks} provides keywords that a developer would look for to search the chunk describing why the build failed.
-Analyzing these could help us understand how developers process build logs and which keywords a tool should use to mark an error description so developers quickly find it through text search.
+\emph{LogChunks} provides keywords that the authors would use to search for the chunk describing why the build failed.
+Analyzing these could help us understand how users process build logs and which keywords a tool should use to mark an error description so developers quickly find it through text search.
 We could also recommend users which search keywords they should use to find why the build failed.
@@
 The chunks describing why a build failed, or the results of chunk retrieval techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
+
+% Andy also proposed: automatic creation of issue reports on GitHub with extracted info: sounds okay, but build failures are to be fixed faster than a GH issue I would say
 
@@
 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
-	\item \texttt{Keywords:} keywords a developer would use to search for the log chunk.
+	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
@@
     Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
-  Keywords & keywords a developer would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
+  Keywords & keywords the authors would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
   Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
@@
 The \texttt{Chunk} is one continuous string cut from the build log.
-If there are multiple errors leading for the build to fail, the substring contains the first appearing continuous error descriptions.
-\emph{Continuous} means that no lines reporting of normal build behavior are interrupting the error descriptions.
-Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
+When the description \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes the description \emph{that} the build failed.
+%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
 %For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
@@
 The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
-We aim to select keywords a developer would use to search for the \texttt{Chunk} when inspecting the build log.
+We selected keywords the authors would use to search for the \texttt{Chunk} within the build log after analyzing about 800 build logs manually.
 Some example keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{failed}'', ``\texttt{[-]}'', ``\texttt{===================================}'' or ``\texttt{ERR!}''.
@@
 
+% TODO Moritz: this is to answer questions 'why did you not do this standard thing': maybe there is a better position and/or way of saying this?
+Calculating the standard measure for inter-rater agreement, Cohen's Kappa, is not applicable here.
+For the log chunk it cannot represent the impact of overlapping selections of the labelers and for the keywords and structural categories the values the labelers could assign were not fixed.
+
 \paragraph{Discussion}
@@
 26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
-We manually inspected these negative answers and found that some extractions were correct after all.
-This yields 12 log extractions in our example set that were not correct.%, shown in Figure~\ref{fig:mails-extraction-correct}.
+We manually inspected these negative answers and found that some stated that the proposed extraction did not show the whole description of why the build failed.
+This is because we had to trim long labeled extractions to keep the mails readable.
+After adjusting these answers, 12 log extractions in our example set that were not correct.%, shown in Figure~\ref{fig:mails-extraction-correct}.
 
@@
 After manual correction, 91\% of the received answers said our labeled extractions were accurate.
-
-Most of the initial incorrect answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
-This is because we had to trim long labeled extractions to keep the mails readable.
 
@@
 For each log, we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.
+
+\emph{LogChunks} advances the research field of build log analysis by introducing a benchmark to rigorously examine research contributions~\cite{sim2003using}.
+
 Still, there are limitations to our data set, which we present in the following.
@@
 The manually labeled \texttt{Chunk} in our data set aims to contain the log part describing why the build failed.
-However, it contains only one consecutive substring of the log text, whereas the reason a build failed could be described at multiple locations within the log.
+However, it contains only one continuous substring of the log text, whereas the reason a build failed could be described at multiple locations within the log.
 We could improve this by extending \emph{LogChunks} to contain multiple substrings of the log text.
@@
 \emph{LogChunks} could be extended with further information targets such as descriptions of warnings, build infrastructure and more.
+
+\paragraph{Validation of Search Keywords}
+The keywords \emph{LogChunks} provides are based on the experience of the authors gained from analyzing about 800 build logs.
+Next, we propose to evaluate whether these keywords would also be used by the actual project developers to find the log chunk describing why a build failed.
 

### 2019-12-19 msr-paper/paper.tex
shortening paper

@@
 We validated the data set by surveying the developers of the projects which produced the builds.
+The width and depth of the \emph{LogChunks} data set makes it an ideal basis to benchmark build log analysis techniques.
 Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
-The width and depth of the \emph{LogChunks} data set makes it an ideal basis to benchmark build log analysis techniques.
 Benchmarking different techniques will advance the research area of build log analysis and ultimately increase our understanding of CI build failures.
@@
 There are different techniques to retrieve information chunks from CI build logs.
-Beller et al.\ use regular expressions to analyze the reasons for build failures from Travis CI logs~\cite{beller2017oops}.
-Such regular expressions are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
-Vassallo et al.\ wrote a custom parser for build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
-Recently, Amar et al.\ reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and a successful build~\cite{amar2019mining}.
+Beller et al.\ use regular expressions to analyze logs from Travis CI~\cite{beller2017oops}.
+Such regular expressions are developed by looking at exemplary build logs.
+Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
+Vassallo et al.\ wrote a custom parser to gather information for build repair hints~\cite{vassallo2018un-break}.
+Recently, Amar et al.\ reduced the number of lines for a developer to inspect by creating a diff between logs from failed and successful builds~\cite{amar2019mining}.
 
@@
 Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
+
 At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred over other alternatives.
 In addition, there is currently no data set available to benchmark such build log analysis techniques.
-
-Following Sim et al., creating a benchmark gives us the chance to ``increase the scientific maturity of the area''~\cite{sim2003using} of build log analysis.
+Following Sim et al., a benchmark gives us the chance to ``increase the scientific maturity of the area''~\cite{sim2003using} of build log analysis by evaluating and comparing research contributions.
 
@@
 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
+	\caption{Overview of \emph{LogChunks}}
+	\label{fig:lc-overview}
+\end{figure}
+
 %\section{Applications}
@@
 \paragraph{Benchmarking Build Log Analysis Techniques}
-We created this data set to evaluate and compare different techniques to retrieve information chunks from build logs. %\todo{cite journal paper (or preprint?)}.
+We created this data set to compare different techniques to retrieve chunks from build logs. %\todo{cite journal paper (or preprint?)}.
 The techniques we compared are based on program synthesis from examples, text similarity and searching for keywords.
-In addition to that, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
-For example, we can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason the build failed.
+\emph{LogChunks} can be a benchmark to evaluate further build log analysis techniques.
+For example, we can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason a build failed.
 
@@
 They write custom parsers and classifiers to categorize builds according to why a build failed.
-The manually labeled chunk describing why the build failed can show classification algorithms where in the build logs they can find the information relevant for the classification.
+The manually labeled chunk describing why the build failed can show classification algorithms where in a build log they can find information relevant for the classification.
 
@@
 \emph{LogChunks} provides keywords that the authors would use to search for the chunk describing why the build failed.
-Analyzing these could help us understand how users process build logs and which keywords a tool should use to mark an error description so developers quickly find it through text search.
-We could also recommend users which search keywords they should use to find why the build failed.
+Analyzing these can help us understand how users process build logs and which keywords a tool should use to mark an error description.
+We can also recommend users which search keywords they should use to find why the build failed.
 
 \paragraph{Studying Conversations about Build Failures}
-Some researchers are looking into conversations of developers surrounding CI builds and pull requests \todo{citation needed: nathan cassee (with Alexander Sebrenik) did this in his master thesis (paper got accepted, will get link when preprint is finished), did not find others yet that do this}.
-The chunks describing why a build failed, or the results of chunk retrieval techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
+Researchers are looking into conversations of developers surrounding CI builds and pull requests \todo{citation pending}
+%TODO Caro: nathan cassee (with Alexander Sebrenik) did this in his master thesis (paper got accepted, will get link when preprint is finished), did not find others yet that do this}.
+The chunks describing why a build failed, or the results of build log analysis techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
 
@@
 The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI\@.
-It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc}, related data from GitHub~\cite{github2019website} through GHTorrent~\cite{gousios2013ghtorrent}, the corresponding git repository, and data obtained through analysis of the build logs.
-The data obtained through build logs contains the names of failing test cases, similar to the chunk describing why the build failed in \emph{LogChunks}.
-However, these values are obtained through a manually developed parser, which only supports specific Ruby test runners and Java Maven or JUnit logs.
-\emph{LogChunks} provides manually labeled data points on the description of why the build failed for a much wider selection of programming languages.
+It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc} and related data from GitHub~\cite{github2019website} through GHTorrent~\cite{gousios2013ghtorrent}.
+They provide the names of failing test cases.
+However, they obtained these through a manually developed parser, which only supports specific Ruby test runners and Java Maven or JUnit logs.
+\emph{LogChunks} provides manually labeled data on the description of why builds failed for a much wider selection of build tools.
 
 \subsection{Travis CI Build Log Data Set}
-Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected a large amount of Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
-They selected Maven repositories that included the Checkstyle plugin and also used Travis CI\@.
+Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
+They selected Maven repositories that included the Checkstyle plugin.
 Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
-	\caption{Overview of \emph{LogChunks}}
-	\label{fig:lc-overview}
-\end{figure}
 
@@
 Within each repository folder the logs are separated according to build status.
-Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
-The build status folder contains the full logs in files named with the ID of the Travis CI build that produced the log.
+%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
+The build status folder contains the full logs in files named with the ID of the build that produced the log.
 
@@
     <Chunk>001+ ** ERROR: process timed out **
-
 001- OK.
 ========DONE========
-FAIL Bug #60120 (proc_open hangs when data in stdin/out/err is getting larger or equal to 2048) [ext/standard/tests/file/bug60120.phpt]</Chunk>
+FAIL Bug #60120 (proc_open hangs when data in stdin/out/err is getting larger or equal to 2048)</Chunk>
   </Example>
@@
 For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
-Each \texttt{Example} consists of:
-\begin{itemize}
-	\item \texttt{Log:} the relative path to the input build log.
-	\item \texttt{Chunk:} the log chunk that describes why the build failed.
-	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
-	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
-				The category is relative to the other examples for the same repository.
-\end{itemize}
+Figure \ref{tab:data-in-example} presents the data within each example.
+% Each \texttt{Example} consists of:
+% \begin{itemize}
+% 	\item \texttt{Log:} the relative path to the input build log.
+% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
+% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
+% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
+% 				The category is relative to the other examples for the same repository.
+% \end{itemize}
 Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
@@
 \end{tabularx}
-\caption{Recommendations for each of the investigated chunk retrieval techniques}
-\label{tab:single-technique-recommendations}
+\caption{Data within an example in \emph{LogChunks}}
+\label{tab:data-in-example}
 \end{figure*}
@@
 The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
-This can be the failing test case, the description of a failed linter rule or a compiler error.
-The \texttt{Chunk} is one continuous string cut from the build log.
-When the description \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes the description \emph{that} the build failed.
+This can, for example, be the failing test case or a compiler error and is one continuous substring of the build log.
+When the reason \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes the description \emph{that} the build failed.
 %Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
@@
 The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
-We selected keywords the authors would use to search for the \texttt{Chunk} within the build log after analyzing about 800 build logs manually.
-Some example keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{failed}'', ``\texttt{[-]}'', ``\texttt{===================================}'' or ``\texttt{ERR!}''.
+We selected keywords the authors would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.
+Some keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{=DIFF=}'' or ``\texttt{ERR!}''.
 
 \paragraph{Category}
-For each repository, we assign \emph{structural categories} to the examples.
-The structural category compares how the \texttt{Chunk}s are represented within the build logs.
-Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'', surrounding lines filled with special characters or additional empty log lines.
-Two examples fall into the same structural categories if they are surrounded by similar markings.
+For each repository, we assign \emph{structural categories} to the chunks.
+The structural category compares how \texttt{Chunk}s are represented within the build log.
+Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'' or surrounding special characters.
+Two chunks fall into the same structural categories if they are surrounded by the same markings.
 Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
 In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
-For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
+%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
 For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
 
-\begin{figure}[]
+\begin{figure}[tbp]
 	\centering
@@
 005+     Parameter #1 [<optional> $flags]
-
 005-     Parameter #1 [<optional> $ar_flags]
 ========DONE========
-FAIL Bug#71412 ArrayIterator reflection parameter info [ext/spl/tests/bug71412.phpt] 
+FAIL Bug#71412 ArrayIterator reflection 
 *{\color{cyan}-=-=-=-=-=-}*
@@
 \end{lstlisting}
-	\caption{Log chunk with one line of context from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\caption{Log chunk from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
 	\label{lst:same-category}
@@
 
-\begin{figure}[]
+\begin{figure}[tbp]
 	\centering
@@
 \end{lstlisting}
-	\caption{Log chunk with one line of context from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\caption{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}}
+  %, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
 	\label{lst:different-category}
@@
 We describe how we select the repositories, builds and logs for \emph{LogChunks}.
-To collect the build logs we built the  \texttt{GHTorrentParser}, \texttt{LogCollector} and \texttt{TravisRequester} using Ruby.
+To collect the build logs we built the  \texttt{GHTorrentParser} and \texttt{TravisRequester} using Ruby.
 
 \paragraph{Repository Sampling}
-First, we determine a set of repositories to query logs from.
+%First, we determine a set of repositories to query logs from.
 Our \texttt{GHTorrentParser} queries the \emph{GHTorrent}~\cite{gousios2013ghtorrent} data set for the most popular languages on GitHub.
@@
 We define \emph{Popularity} as the number of watches.
-The \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, can then check for a given repository whether it uses Travis CI\@.
+The \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, then checks whether a given repository uses Travis CI\@.
 
 For \emph{LogChunks} we queried GHTorrent on 01/04/2018 for the three most popular repositories of each of the 30 most popular languages.
-Among the selected repositories are, for example, \texttt{git/git},  \texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.
+Among the resulting repositories are, for example, \texttt{git/git},  \texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.
 
 \paragraph{Build Sampling}
-The \texttt{LogCollector} uses the \texttt{TravisRequester} to obtain the newest builds for a given repository.
-It uses a stratified sampling approach: \texttt{TravisRequester} saves the obtained builds in buckets according to their status.
-We encountered the following statuses during our data collection: created, started, cancelled, passed, errored and failed.
+The \texttt{TravisRequester} obtains the newest builds for a given repository.
+We use a stratified sampling approach and save the obtained builds in buckets according to their status.
+%We encountered the following statuses during our data collection: created, started, cancelled, passed, errored and failed.
 The user of \texttt{TravisRequester} configures how many builds should be checked and how many builds per status should be saved.
 
-To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to 1000 builds per repository and keep ten for each status.
-We discard all statuses except \emph{failed}~\cite{travis2009buildstatus}.
-A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
+To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to 1000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
+%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
 
@@
 For each build, the \texttt{TravisRequester} then selects a log to download.
-Travis CI attributes logs to \emph{jobs}.
-A single build can consist of multiple jobs, e.g.\ building the same code version and executing tests in different testing environments.
-A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
-\texttt{TravisRequester} queries each build for the first job which has the same state.
-For the selected jobs, the tool queries the Travis API V3 over HTTPS to obtains the corresponding build log.
+Travis CI links logs to \emph{jobs}.
+A build can consist of multiple jobs, e.g.\ executing tests in different environments.
+%A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
+\texttt{TravisRequester} queries each build for the first job which has the same state and obtains the corresponding build log.
 
-We manually inspected the collected build logs and had to discard logs from three repositories.
-One had only a single failed build, two others had empty build logs on Travis CI\@.
-In total we collected 797 logs from 80 repositories.
+We inspected the collected build logs and discarded logs from three repositories.
+One had only one failed build, two others had empty build logs on Travis CI\@.
+In total we collected 797 logs from 80 repositories spanning 29 languages.
 
@@
 \paragraph{Chunk That Describes Why The Build Failed}
-For each repository, the labeler skimmed through the build logs and tried to identify the first occurrence of a description why the build failed.
-They copied out the first continuous description as the \texttt{Chunk}.
+For each repository, the labeler skimmed through the build logs and copied out the first occurrence of a description why the build failed.
+%They copied out the first continuous description as the \texttt{Chunk}.
 They preserved whitespace and special characters, as they might be crucial to detect the targeted substring.
-To support exact learning of regular expressions identifying the labeled substrings the labeler aimed to start and end the labeled substring at consistent locations around the fault description.
+To support learning of regular expressions identifying the labeled substrings the labeler aimed to start and end the labeled substring at consistent locations around the fault description.
 
@@
 We presented the \texttt{Chunk} and ten lines above and below to the labeler.
-Their task was to note down three strings they would put into a document search function to find this failure description.
-The string should appear in or around the \texttt{Chunk} substring and is case-sensitive.
-There are no special limitations on the string itself, especially spaces are also allowed.
+Their task was to note down three strings they would put into a search field to find this failure description.
+The strings should appear in or around the \texttt{Chunk} and is case-sensitive.
+There are no special limitations on the string itself, especially spaces are allowed.
 
 \paragraph{Category}
-To label the \emph{structural categories} we again presented the \texttt{Chunk} and the surrounding context to the labeler for all logs from a repository.
-We asked them to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation, i.e.\ the same surrounding or identifying characters.
+To label the \emph{structural categories} we presented the \texttt{Chunk} and the surrounding context to the labeler for all logs from a repository.
+We asked them to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation.
 The labeler should start the categories with 0 and increase as new ones appear.
-For reproducibility, we presented the logs in chronological build order.
+%For reproducibility, we presented the logs in chronological build order.
 
@@
 \paragraph{Method}
-The second labeler processed 30 random generated logs for each data point in \emph{LogChunks}.
 We followed the same labeling process as described in Section~\ref{sec:labeling-process}.
 For the build failure reason and the keywords, we presented 30 randomly sampled build logs from distinct repositories in \emph{LogChunks}.
-The labeled structural categories are relative to the other logs from the same repository.
+The structural categories are relative to other logs from the same repository.
 Therefore, we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.
@@
 \paragraph{Results}
-For the first labeled data point, namely the substring describing why the build failed, the two labelers exactly agreed in six cases.
-In 15 cases the second labeler selected more lines than the first one, in five there was partial overlap and in 4 they completely disagreed.
-
+For the substring describing why the build failed, the two labelers exactly agreed in six cases.
+In 15 cases the second labeler selected more lines, in five their selections overlapped and in four they completely disagreed.
 Regarding the keywords, the two labelers completely agreed in nine cases and completely disagreed in two cases.
-In nine cases there was partial overlap in the keywords of the two labelers, in two the first labeler selected additional keywords compared to the second, while the second labeler proposed additional keywords in seven cases.
-
-When classifying the labeled substrings into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.
+In nineteen cases there was  overlap in the keywords of the two labelers.%, in two the first labeler selected additional keywords compared to the second, while the second labeler proposed additional keywords in seven cases.
+When classifying the chunks into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.
 
 % TODO Moritz: this is to answer questions 'why did you not do this standard thing': maybe there is a better position and/or way of saying this?
-Calculating the standard measure for inter-rater agreement, Cohen's Kappa, is not applicable here.
+We found that calculating the standard measure for inter-rater agreement, Cohen's Kappa, is not applicable here.
 For the log chunk it cannot represent the impact of overlapping selections of the labelers and for the keywords and structural categories the values the labelers could assign were not fixed.
@@
 %
-Our main learning from this study is that adequately communicating all decisions and assumptions on how data is labeled is important and difficult.
-We reviewed the misunderstandings and incorporated more thorough descriptions of our data classes in Section~\ref{sec:data-schema}.
+Our main learning from this study is that it is important and difficult to adequately communicate all decisions and assumptions on how data is labeled.
+We reviewed the misunderstandings and incorporated more thorough descriptions in Section~\ref{sec:data-schema}.
 
@@
 %For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
-As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
+%As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
 %We only took the logs into account and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
@@
 \paragraph{Method}
-Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
-We grouped all commits triggered by one developer and sent out an mail to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
+Using the Travis API, we collect the commit information for each build represented in \emph{LogChunks}.
+We grouped all commits triggered by one developer and sent out an mail to them.%, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
 %Figure~\ref{fig:dev-mail} shows one of the mails sent out.
@@
 %Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
-In the survey, we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
-As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
+In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
+As some of the chunks we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
 
@@
 32 of these mails could not be delivered, e.g.\ because they were addressed to \emph{noreply} mail addresses.
-These 32 mails related to 68 of the build logs.
+%These 32 mails related to 68 of the build logs.
 We received answers from 61 developers, corresponding with 144 build logs.
@@
 Of the 144 answers, 132 said our extraction was correct.
-26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
-We manually inspected these negative answers and found that some stated that the proposed extraction did not show the whole description of why the build failed.
-This is because we had to trim long labeled extractions to keep the mails readable.
-After adjusting these answers, 12 log extractions in our example set that were not correct.%, shown in Figure~\ref{fig:mails-extraction-correct}.
+%26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
+We manually inspected the 26 negative answers and found that some stated that the proposed extraction did not show the whole description of why the build failed.
+This is because we had to trim long chunks to keep the mails readable.
+After adjusting these answers, 12 answers stated that our labeled log chunk was not correct.
 
 \paragraph{Discussion}
-This study highly strengthens the trust in the validity of the extracted build failure reasons in \emph{LogChunks}.
+This study highly strengthens the trust in the validity of the labeled log chunks.
 The study received answers about 18\% of the logs from \emph{LogChunks}.
-After manual correction, 91\% of the received answers said our labeled extractions were accurate.
+After manual correction, 91\% of the received answers said our labeled chunks were accurate.
 
-One of our extractions only showed a warning and the developer proposed to also include the line above, stating that warnings are treated as errors in the build.
-In others that were identified as incorrect, we labeled the error message of an error that later ignored and did not lead to the build failing.
+One of our extractions only showed a warning and the developer proposed to also include the line stating that warnings are treated as errors.
+In others that were identified as incorrect, we labeled the error message of an error that was later ignored.
 
 \section{Summary}
-In this paper, we introduced the \emph{LogChunks} data set encompassing about 800 build logs from a wide range of projects using Travis CI\@.
+\label{sec:conclusion}
+In this paper, we introduced the \emph{LogChunks} data set encompassing 797 build logs from 80 projects using Travis CI\@.
 For each log, we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.
@@
 
-Still, there are limitations to our data set, which we present in the following.
-We also propose several improvements and extensions to \emph{LogChunks}.
-\label{sec:conclusion}
+Still, there are limitations to our data set, which we present in the following, together with improvements and extensions to \emph{LogChunks}.
 
 \paragraph{Chunk as One Consecutive Substring}
-The manually labeled \texttt{Chunk} in our data set aims to contain the log part describing why the build failed.
-However, it contains only one continuous substring of the log text, whereas the reason a build failed could be described at multiple locations within the log.
-We could improve this by extending \emph{LogChunks} to contain multiple substrings of the log text.
+The manually labeled \texttt{Chunk} contains only one continuous substring of the log text.
+The reason a build failed could be described at multiple locations within the log.
+We propose to extend \emph{LogChunks} to contain multiple substrings of the log text.
 
@@
 \emph{LogChunks} encompasses a wide range of repositories from various main development languages, though only 10 logs from each repository.
-This stems from the high effort necessary for the manual data labeling process.
-Including more logs and repositories into \emph{LogChunks} will strengthen it as a broad baseline for comparing build log analysis tools.
+%This stems from the high effort necessary for the manual data labeling process.
+Including more logs and repositories into \emph{LogChunks} will strengthen it as a benchmark to compare build log analysis techniques.
 
 \paragraph{Classification of the Build Failure Cause}
-Our data set contains the log chunks describing why a build failed but has no further classification according to the cause of the failure.
-As various researchers are investigating why CI builds fail, a useful extension would be to annotate cause of the build failure for each log.
+Our data set contains no further classification according to the cause of the failure.
+As researchers are investigating why CI builds fail, a useful extension is to annotate cause of the build failure for each log.
 
@@
 Build log analysis is not limited to retrieving the chunk describing why a build failed.
-\emph{LogChunks} could be extended with further information targets such as descriptions of warnings, build infrastructure and more.
+\emph{LogChunks} can be extended with further information targets such as descriptions of warnings, build infrastructure and more.
 
 \paragraph{Validation of Search Keywords}
-The keywords \emph{LogChunks} provides are based on the experience of the authors gained from analyzing about 800 build logs.
-Next, we propose to evaluate whether these keywords would also be used by the actual project developers to find the log chunk describing why a build failed.
+The keywords \emph{LogChunks} provides are based on the experience of the authors gained from analyzing around 800 build logs.
+Next, we propose to evaluate whether these keywords would also be used by developers to find the log chunk describing why a build failed.
 

### 2019-12-19 msr-paper/paper.tex
bit more shortening to get under 4 pages :)

@@
 
-\begin{figure}[htbp]
+\begin{figure}[tbp]
 	\centering
@@
 
-This section describes the file structure and the data schema of \emph{LogChunks}.
-We give a detailed explanation for the manually labeled data.
-
-\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
-Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
-
-The logs are organized in folders for each repository, identified by \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater }.
-Within each repository folder the logs are separated according to build status.
+This section presents the file structure and the data schema of \emph{LogChunks}.
+%We give a description of the manually labeled data.
+%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
+%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
+The build logs are organized in folders for each language and repository.
+Within each repository folder, folders for each build status contain the log files named with the corresponding build ID.
+% the logs are separated according to build status.
 %Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
-The build status folder contains the full logs in files named with the ID of the build that produced the log.
+%The build status folder contains the full logs in files named with the ID of the build that produced the log.
 
@@
 Listing~\ref{lst:examples} presents the schema of these XML files.
+
+For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
+Figure \ref{tab:data-in-example} presents the data within each example.
+% Each \texttt{Example} consists of:
+% \begin{itemize}
+% 	\item \texttt{Log:} the relative path to the input build log.
+% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
+% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
+% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
+% 				The category is relative to the other examples for the same repository.
+% \end{itemize}
+Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
 
@@
 ========DONE========
-FAIL Bug #60120 (proc_open hangs when data in stdin/out/err is getting larger or equal to 2048)</Chunk>
+FAIL Bug #60120 (proc_open hangs)</Chunk>
   </Example>
@@
 \end{figure}
-
-For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
-Figure \ref{tab:data-in-example} presents the data within each example.
-% Each \texttt{Example} consists of:
-% \begin{itemize}
-% 	\item \texttt{Log:} the relative path to the input build log.
-% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
-% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
-% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
-% 				The category is relative to the other examples for the same repository.
-% \end{itemize}
-Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
 
@@
 The strings should appear in or around the \texttt{Chunk} and is case-sensitive.
-There are no special limitations on the string itself, especially spaces are allowed.
+There are no limitations on the search string, especially spaces are allowed.
 
@@
 We asked them to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation.
-The labeler should start the categories with 0 and increase as new ones appear.
+%The labeler should start the categories with 0 and increase as new ones appear.
 %For reproducibility, we presented the logs in chronological build order.
@@
 \paragraph{Results}
-In total we sent out mails to 246 developers, asking about 3.2 build logs per mail on average.
-32 of these mails could not be delivered, e.g.\ because they were addressed to \emph{noreply} mail addresses.
+In total we sent out mails to 246 developers.%, asking about 3.2 build logs per mail on average.
+32 of these mails could not be delivered, e.g.\ because they were addressed to \emph{noreply} addresses.
 %These 32 mails related to 68 of the build logs.

### 2019-12-23 tool/cleanup-dataset.rb
commit dataset cleanup code

@@ -1,0 +1,45 @@
+#!/usr/bin/env ruby
+
+# cleaning up the master thesis data set for a nice logchunks package
+
+# samples -> "logs" folder, remove misc folder, otherwise same
+
+# example-sets -> "remove and just take buildfailurereason"
+
+require 'nokogiri'
+require 'fileutils'
+
+if $PROGRAM_NAME == __FILE__
+  langs = Dir.entries('./build-failure-reason').select { |lang| not lang.start_with?('.') }
+  langs.each do |lang|
+    repos = Dir.entries("./build-failure-reason/#{lang}").select { |lang| not lang.start_with?('.') }
+    repos.each do |repo|
+      xml = Nokogiri::XML(open("./build-failure-reason/#{lang}/#{repo}")) do |config|
+        config.default_xml.noblanks
+      end
+      clean = Nokogiri::XML('', nil, "UTF-8")
+      examples = xml.at 'Examples'
+      clean.add_child(examples)
+
+      single_examples = clean.search 'ExampleDataOfString'
+      single_examples.each do |example|
+        example.name = 'Example'
+      end
+      input_paths = clean.search 'InputPath'
+      input_paths.each do |input|
+        input.name = 'Log'
+      end
+      outputs = clean.search 'Output'
+      outputs.each do |output|
+        output.name = 'Chunk'
+      end
+
+      path = "./cleaned/#{lang}/#{repo}"
+      dirname = File.dirname(path)
+      unless File.directory?(dirname)
+        FileUtils.mkdir_p(dirname)
+      end
+      File.write(path, clean.to_xml(:indent => 2))
+    end
+  end
+end

### 2019-12-23 thesis/mini/acknowledgments.tex
marting feedback 1

@@
 \noindent
-I would like to thank Moritz for his great support, detailed feedback and his invaluable teaching how to do proper research.
+I would like to thank Dr. Moritz Beller for his great support, his detailed feedback and his invaluable teaching how to do research.
 I could not have imagined a better advisor for my master's thesis.
@@
 \noindent
-Furthermore, I would like to thank Annibale for his helpful feedback and teaching me which is the proper vocabulary to describe my work.
+Furthermore, I would like to thank Prof. Annibale Panichella for his helpful feedback and teaching me the proper vocabulary to describe my work.
 
 \noindent
-I want to pay my special regards to Prof. Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.
+I want to pay my special regards to Prof. Alexander Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.
+I would like to thank Prof. Alexander Knapp for his sharp eyes for formulas and our reassuring conversations.
 
@@
 Lastly, I want to thank Michi and Taico.
-Thank you for your calming input, critical reflection, your relentless support and upcheering.
+Thank you for your calming input, your critical reflection, your relentless support and  your upcheering.
 

### 2019-12-23 thesis/txt/0-introduction.tex
marting feedback 1

@@
 Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
-Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
-A build on a CI server typically compiles and packages the software, executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.
+Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect defects early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
+A build on a CI server typically compiles and packages the software, executes tests~\cite{beller2017oops} and performs various kinds of static analyses~\cite{zampetti2017open}.
 
 CI builds produce logs which report the results of the steps within the build.
-These build logs contain a lot of valuable information for developers and researchers.
-Developers examine log statements of time measurements to track how different stages of the build process perform.
-Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
+These build logs contain valuable information for developers and researchers.
+Developers examine log statements of time measurements to track how steps of the build process perform.
+Researchers collect the commands triggering different build steps to reverse engineer the build configuration when only the log is available to them.
 Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed tests to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
@@
 The problem is, that build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
-Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.
-
-% CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
-% The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
-% Build logs are a valuable data source for developers and researchers.
-% Developers read them to analyze why their build failed or how different stages of the build process perform.
-% Researchers can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
-% However, these two groups can only use the information within the build logs if they can adequately retrieve the information relevant to them.
+Therefore, developers and researchers can only efficiently use the information within build logs if they can adequately retrieve those parts (chunks) of the log that describe the targeted information.
 
@@
 Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
-Such regular expressions are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
 Vassallo et al.\ wrote a custom parser for build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
@@
 These approaches have various strengths and weaknesses:
-Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.
+Regular expressions are exact but difficult to maintain.
+They are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
 Custom parsers are powerful though fragile towards changes in the log structure.
 The structure of build logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
-Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
-At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred over other alternatives.
-Developers and researches currently have little support while choosing which technique to use for a task.
+Taking a diff between the logs of failed and successful builds can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
 
-The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances each techniques is recommended over another.
+At the moment there is only anecdotal evidence on the performance of these techniques and on when a technique should be preferred over other alternatives.
+Developers and researches currently have little support when choosing which technique to use for a task.
+
+The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
 We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
-For \textbf{RQ1}, we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
+For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
 We implement and evaluate three chunk retrieval techniques:
@@
 \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-How many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is(\textbf{RQ2.3}).
-To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
+how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
+To evaluate PBE, CTS and KWS we create a data set, called \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
 Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
@@
 \end{itemize}
+
 We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in precision and recall of the chunk retrieval is required.
@@
 %Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
-This tool is also used for the comparison described in Chapter~\ref{sec:study}.
+Chapter~\ref{sec:study} explains the empirical comparison of the three techniques on \emph{LogChunks} and presents the study results.
 Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
-Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion-fw}.%\\\\
+Lastly,Chapter~\ref{sec:conclusion-fw} concludes and gives an overview of further research opportunities.%\\\\
 

### 2019-12-23 thesis/txt/1-related-work.tex
marting feedback 1

@@
 We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
-We explain how the researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
-Next, this section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
+We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifys their data collection.
+This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
 The presented approaches are related to and can benefit from the techniques we analyze in this thesis.
@@
 \label{sec:rw-ci}
-The first paragraphs of this section present the results of past research into CI: its influence on the software engineering processes, the reasons for CI builds to fail and the role of testing and static analysis in CI builds.
-Later we describe how these researchers obtain the data sets these works are based on.
+The first paragraphs of this section present the results of past research into CI: its influence on the software engineering processes, the reasons for CI builds to fail and the role of testing and of static analysis in CI builds.
+Later we describe how researchers obtain the data sets these works are based on.
 We show how they analyze build logs and why the chunk retrieval techniques we investigate can support them to broaden their studies.
@@
 \paragraph{Motivation for CI and Impact of CI}
-Why teams choose to use CI and its impac on the software development process is explored by several existing works.
+Why teams choose to use CI and its impact on the software development process is explored by several existing works.
 Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
-Developers use CI to ensure consistency and quality across different execution environments and increase confidence into the code they deploy.
+They find that, developers use CI to ensure consistency and quality across different execution environments and increase confidence in the code they deploy.
 Hilton et al.~\cite{hilton2016usage} also analyze how and why open source projects use CI\@.
-They observe CI usage in a broad range of projects, it supports them to catch bugs earlier and have more confidence in a successful build and shorten release cycles.
-Stahl and Bosch~\cite{staahl2014modeling} provide a holistic review of literature on automatic build environments in industry projects.
+They observe CI usage in a broad range of projects, it supports developers to catch bugs earlier and to shorten release cycles.
+Stahl and Bosch~\cite{staahl2014modeling} provide a review of literature on automatic build environments in industry projects.
 They propose a descriptive structure to model build flows, which they found to be highly different from project to project.
 Vasilescu et al.~\cite{vasilescu2015quality} analyze a broad rage of open source projects written in popular languages on GitHub.
-They compare their usage of CI with the successful merges of pull requests and find that CI increase the number of successful merges, internal as well as external contributions, and allows the team members to uncover more bugs.
-In a recent study, Vasallo et al.~\cite{vassallo2019every} interview developers on how they determine why a CI build failed.
-They model how these developers resolve failures.
-The first and most important steps when developers want to fix a build failure is to locate the error within the build log.
+They compare the usage of CI with the successful merges of pull requests and find that CI increase the number of successful merges and allows the team members to uncover more bugs.
+In a recent study, Vasallo et al.~\cite{vassallo2019every} interview developers on how they determine why a CI build failed and model how these developers resolve failures.
+Vasallo et al. find that, the first and most important steps when developers want to fix a build failure is to locate the error within the build log.
 Then the developers use the additional information provided with and around the error message to understand the details of the failures.
@@
 \paragraph{Build Failures in CI}
-Various researchers look into why CI builds fail and the impact of build failures on the development workflow.
+Various researchers look into why CI builds fail and into the impact of build failures on the development workflow.
 Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
-In addition, most failures are resolved within two builds.
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and categorize why builds failed.
-Most builds fail because of failing tests.
-For most projects, over half of the failed builds follow another failed build.
-Their data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
+In addition, they notice that most failures are resolved within two builds.
+Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and find that most builds fail because of failing tests.
+For most projects, over half of the failed builds follow a previous failed build.
+Rausch et al.'s data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
 Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
 They determine that testing failures are more common than compilation errors.
-Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects.
+Open source builds fail most often because of unit tests, whereas release preparations are the primary cause in industrial projects.
 
 \paragraph{Static Analysis and Testing in CI}
-Automated static analysis tools are the focus of Zampetti et al.~\cite{zampetti2017open} in their study of java projects from GitHub.
+Automated static analysis tools are the focus of Zampetti et al.~\cite{zampetti2017open} in their study of Java projects from GitHub.
 Their results show that static analysis is responsible for a small amount of build failures and mainly responsible for warned builds.
 Almost all analyzed projects use custom configurations for the static analysis, however the configuration rarely changes.
-Failures because of static analysis warnings are fixed in a short time frame.
-Beller et al.~\cite{beller2017oops} show that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds.
-They observe a high variety between programming langues, i.e. in the kind and number of tests which are run, as well as how often tests fail.
+Failures because of static analysis warnings are observed to be fixed in a short time frame.
+Beller et al.~\cite{beller2017oops} show that testing is central to continuous integration when evaluating Travis CI logs for Java and Ruby builds.
+They observe a high variation between programming langues, in the kind and number of tests which are run, as well as how often tests fail.
 The low failure rates on the CI server hint at code being tested before it is sent to the server.
@@
 \paragraph{Data Sets Powering CI Research}
-The works presented in this section are based on either developer surveys or data sets, containing build metadata or build logs.
+The works presented in this section are based on either developer surveys or data setsa containing build metadata or build logs.
 Seo et al.~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
 Beller et al.~\cite{beller2017travistorrent} created the \emph{TravisTorrent} data set providing access to build metadata from more than 1,000 projects from Travis CI~\cite{travisci2019webpage}.
-TravisTorrent was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
+\emph{TravisTorrent} was the basis for several of the works mentioned in this section~\cite{rausch2017empirical,zampetti2017open,vassallo2017a-tale,beller2017oops}.
 Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.

### 2019-12-26 msr-paper/paper.tex
martin feedback 2

@@
 <Examples>
+  <Example>
     <Log>C/php@php-src/failed/529279089.log</Log>
@@
 \end{lstlisting}
-	\caption{Log chunk from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
 	\label{lst:same-category}
@@
 \subsection{Inter-Rater Reliability Study}
-To evaluate the validity of our labeled data points we perform a second labeling of a sample of the data in \emph{LogChunks}.
+To evaluate the validity of our labeled data we perform a second labeling of a sample of the data in \emph{LogChunks}.
 
@@
 The mail included links to the corresponding commits, build overview and log file.
-We asked the receivers to fill out a short survey in case our extraction was not correct.
+We asked the developers to fill out a short survey in case our extraction was not correct.
 %Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
-In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
+In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why we were wrong.
 As some of the chunks we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.

### 2019-12-26 thesis/txt/1-related-work.tex
martin feedback 2

@@
 The analysis of Ghaleb et al.~\cite{ghaleb2019studying} starts with manual categorization of build logs.
-They select keywords and strings that identify their noise categories and code a script to automatically classify logs based on these keywords.
+They select keywords and strings that identify their targeted categories and code a script to automatically classify logs based on these keywords.
 %To validate the script results, they performed another manual classification.
@@
 \paragraph{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs these researchers build parsers and regular expression based programs.
+To leverage the valuable information within build logs the researchers presented in this section build parsers and regular expression-based programs.
 This task of retrieving specific chunks of text from the build logs can be solved by the chunk retrieval techniques we compare in this thesis.
 Our results can support researchers in choosing a suitable technique for their data set of build logs and the chunks they want to retrieve.
-By relieving them from building custom parsers we enable them to cover more languages and build tools in their studies.
+By relieving them from building custom parsers we enable them to cover a much wider range of languages and build tools in their studies.
 
@@
 Amar et al.~\cite{amar2019mining} compare different approaches to reduce the portions of a log that a developer has to inspect.
-Their techniques remove lines that appear both in passing and failing build logs and use a modified term frequency inverse document frequency weighting to identify term vectors likely to occur with failures.
-They use the term vectors and cosine similarity to further filter the log portions only present in failing build logs.
+Their techniques remove lines that appear both in passing and failing build logs and use a modified \emph{Term Frequency Inverse Document Frequency} (TF-IDF) weighting to identify term vectors likely to occur with failures.
+They use term vectors and cosine similarity to further filter the log portions only present in failing build logs.
 Their diff technique can be interpreted as a chunk retrieval technique, where the targeted information is defined by the past failures used as basis for the weighted term vectors.
 
-Travis itself already provides build logs augmentation in the form of a basic structuring of the build logs within their log viewer using \emph{log folds}~\cite{travis2019logfolds}.
+Travis itself already provides build log augmentation in the form of a basic structuring of the build logs within their log viewer using \emph{log folds}~\cite{travis2019logfolds}.
 They add fold identifiers around common commands and setup or teardown build phases and collapse the contained lines by default.
@@
   Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} present an example of this.
-  \item \textbf{is partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, such as natural language text in error messages.
+  \item \textbf{is partial}. Some parts are highly structured by e.g.\ special characters. Other parts are unstructured, such as natural language text in error messages.
   \item can be described with an \textbf{analytical data guide} rather than a predefined schema.
   There is no fixed specification on how build tools structure their output.
-  We afterwards extract structuring patterns in the produced output.
+  We later extract structuring patterns in the produced output.
   \item \textbf{has a rapidly evolving schema}.
   Modifications in the build configuration can change the tools involved in the build and therefore the composition of the build log.
-  Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adopt their log messages over time~\cite{yuan2012characterizing}.
+  Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adapt their log messages over time~\cite{yuan2012characterizing}.
 \end{itemize}
@@
 Abiteboul proposes an approach to overlay the semi-structured data with a structured layer.
-The additional layer can answer queries and give access to the semi-structured data relevant to the query.
-In contrast to that, this thesis takes a look at techniques to gater a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.
+The additional layer can answer queries and give access to the semi-structured data relevant to a query.
+In contrast to that, this thesis takes a look at techniques to gather a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/log42.png}
+	\caption{Excerpt from a build log showing a WarningMessage chunk.}
+	\label{fig:log-4}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/log52.png}
+	\caption{Excerpt from a build log showing another WarningMessage chunk.}
+	\label{fig:log-5}
+\end{figure}
 
@@
 A main difference between build logs and system logs is that system logs are fundamentally structured through events.
-Each line in the log file represents one event with a set of fields: timestamp, verbosity level and raw message content~\cite{he2017towards}.
-Listing \ref{lst:system-log} shows example lines from a system log.
+Each line in a log file represents one event with a set of fields: timestamp, verbosity level and raw message content~\cite{he2017towards}.
+Figure \ref{lst:system-log} shows example lines from a system log.
 
@@
   \end{lstlisting}  
-  \caption{System Log Statements, adapted example from~\cite{he2017towards}}
+  \caption{System Log Statements. Example adapted from~\cite{he2017towards}.}
   \label{lst:system-log}
@@
 The techniques we investigate in this thesis are based on existing methods of Programming by Example, information extraction and information retrieval.
-This section presents different Programming by Example resources surrounding Microsoft's work on the PROSE library
-We explain its generic program synthesis algorithm and how PROSE synthesize text extraction programs, the foundation of PBE\@.
+This section presents different Programming by Example resources surrounding Microsoft's work on the PROSE library.
+We explain its generic program synthesis algorithm and how PROSE synthesizes text extraction programs, the foundation of PBE\@.
 In addition, we describe how chunk retrieval can be employed as a part of presented information extraction approaches.
@@
 FlashMeta separates the inductive synthesis algorithm from the domain specific capabilities of the desired program by encoding the possible program space in a domain specific language (DSL).
-The user specifies the desired program behavior by providing in / output examples (I/O examples).
+The user specifies the desired program behavior by providing in/output examples (I/O examples).
 FlashMeta uses \emph{witness functions}, provided by the DSL, to divide the synthesis into smaller subtasks.
@@
 The DSL also provides the ranking characteristics.
-From the ranked VSA, FlashMeta can then return a ranked list of complete programs consistent with the users example.
+From the ranked VSA, FlashMeta can then return a ranked list of complete programs consistent with the user's example.
 
@@
 A regular expression in FlashExtract is a concatenation of tokens, e.g.\ standard character classes or string literals frequently occurring in the input examples.
-Listing \ref{lst:prose-program} shows a text extraction program synthesized by FlashExtract.
+Figure \ref{lst:prose-program} shows a text extraction program synthesized by FlashExtract.
 This program defines the first position as after a colon followed by a newline character and before a piece of text with all capital letters.
@@
   \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract}
+  \caption{Text extraction program synthesized by FlashExtract.}
   \label{lst:prose-program}
@@
 Their DSL for PROSE abstracts over variables and subexpressions by describing rewrite rules applied to the abstract syntax tree.
-These synthesized transformations propose fixes for student assignments based on corrections from other students and to automate repetitive refactoring tasks.
+These synthesized transformations can be used to propose fixes for student assignments based on corrections from other students and can also be used to automate repetitive refactoring tasks.
 
-Raza and Gulwani~\cite{raza2017automated} present an automated algorithm that attempts to predict data extraction programs from only input examples.
+Raza and Gulwani~\cite{raza2017automated} present an automated algorithm that attempts to predict data extraction programs only from input examples.
 Their tool can split system log statements into table columns or extract data from lists on webpages into spreadsheets.
 
-In a program synthesis shorter and simpler program often receive a better ranking.
+In program synthesis shorter and simpler program often receive a better ranking.
 By also taking the execution traces of the program candidates into account, Ellis and Gulwani~\cite{ellis2017learning} improve the accuracy of the PROSE program learner even further.
 For example, a program that extracts overlapping substrings is ranked lower than a program without overlapping extractions.
-They also weigh the produced output of applying a program to input only examples and prefer programs which produces output structurally similar to provided output examples.
+They also weigh the produced output of applying a program to input only examples and prefer programs which produce output structurally similar to provided output examples.
 
@@
 I/O examples are an ambiguous specification of a program.
-As such, user confidence in the correctness of the synthesized program is important for a wide adoption of Programming by Example based systems~\cite{lau2009why-programming-by-demonstration}.
+As such, user confidence in the correctness of the synthesized program is important for a wide adoption of Programming by Example-based systems~\cite{lau2009why-programming-by-demonstration}.
 Miller and Myers~\cite{miller2001outlier} uncover outliers in input data provided to a Programming by Example text editing task.
 For the PROSE framework, Mayer et al.~\cite{mayer2015user} compare two approaches for disambiguation by the user.
-With their first approach, the user can browse lower ranked program candidates in a tree like natural language transformation of the constructed VSA\@.
+With their first approach, the user can browse lower ranked program candidates in a tree-like natural language transformation of the constructed VSA\@.
 The second approach actively asks the user to resolve ambiguous output possibilities for input only examples.
@@
 The WHISK system by Stephen Soderland~\cite{soderland1999learning} learns text extraction regular expressions for semi-structured text.
-The system interleaves the learning process with the example annotation and reduces the number of required examples by presenting examples that eliminate ambiguities between learning candidates.
+The system interleaves the learning process with example annotation and reduces the number of required examples by presenting examples that eliminate ambiguities between learning candidates.
 
@@
 Fisher et al.~\cite{fisher2008from} fully automated the generation of PADS grammars.
-They split the data into chunks, lines or documents, and further into tokens.
+They split the data into chunks, documents or lines, and further into tokens.
 Parentheses are used to infer hierarchical structure information.
@@
 In information retrieval, algorithms try to determine the general topic or conceptual information of a document.
-Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix and weighing the terms with tf-idf~\cite{lee1997document}.
-On the matrix the algorithms apply a similarity comparison like, for example,vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
+Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix and weighing the terms with TF-IDF~\cite{lee1997document}.
+On the matrix the algorithms apply a similarity comparison such as, for example, vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}.
 

### 2019-12-26 thesis/txt/2-models.tex
martin feedback 2

@@
 This chapter first presents how a build log, which we take as input to the chunk retrieval, is created by a continuous integration (CI) build.
-Next, it describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
+Next, the chapter describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
 We illustrate why it is useful to extract the presented information chunks.
@@
 We present the three chunk retrieval techniques we investigate in this thesis:
-Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
+program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
 
@@
 	\includegraphics[width=\textwidth, clip]{img/build-overview.pdf}
-	\caption{The different entities related to a CI build}
+	\caption{The different entities related to a CI build.}
 	\label{fig:build-overview}
@@
 \label{sec:bl-characteristics}
-The idea of CI is to catch errors early, by integrating new software changes fast and often~\cite{humble2010continuous}.
+The idea of CI is to catch errors early by integrating software changes fast and often~\cite{humble2010continuous}.
 Companies link a CI server, e.g.\ Travis CI, to their source code repository.
@@
 Software tools involved in the build write out log messages to the console.
-They communicate progress updates, error and warning messages to the user~\cite{yuan2012characterizing}.
+They communicate progress updates, error messages and warning messages to the user~\cite{yuan2012characterizing}.
 We refer to to the concatenation of this output as \emph{build log}.
@@
 	\includegraphics[page=1, width=0.8\textwidth, trim={5cm 0.5cm 0.5cm 0.5cm}, clip]{img/overview-graphics.pdf}
-	\caption{Contribution of different tools to the build log}
+	\caption{Contribution of different tools to a build log.}
 	\label{fig:tool-log-contribution}
@@
 This section defines our concept of information retrievable from a CI build log.
-We use the introduced terms throughout the following sections and chapters to talk about the characteristics of chunk retrieval techniques.
+We use the introduced terms throughout the following sections and chapters to discuss about the characteristics of chunk retrieval techniques.
 To illustrate why chunk retrieval from build logs is useful, we present examples of information contained in Travis CI build logs and describe use cases for developers and researchers to retrieve them.
@@
 Chunks can be hierarchically ordered, determined by how their textual representations contain each other.
-As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section~\ref{sec:rw-semi-structured-data}, this section only presents hierarchical containment for chunks whose hierarchy we definitely know.
-Most chunks can appear in various hierarchical arrangements and are therefore not contained in any other type in our explanation.
+As this is an ad-hoc and a-posteriori structuring schema, as described in Section~\ref{sec:rw-semi-structured-data}, this section only presents hierarchical containment for chunks whose hierarchy is known.
+Most chunks can appear in various hierarchical arrangements and are therefore not contained in any other chunk.
 
@@
 	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
-	\caption{Information retrievable from build logs}
+	\caption{Information retrievable from build logs.}
 	\label{fig:build-log-information}
@@
 	\item \textbf{BuildPhase} Build logs can be divided into the sections produced by different tools.
-	      These build steps could be for example be a \textbf{TestPhase}, \textbf{LinterPhase}, \textbf{TravisWorker} or \textbf{GitFetch} are some that we encountered in the logs.
+	      These build steps could, for example, be a \textbf{TestPhase}, \textbf{LinterPhase}, \textbf{TravisWorker} or \textbf{GitFetch}.
 
 	\item \textbf{TravisPhase} Travis CI build logs consist of several build phases defined within the Travis CI configuration language.
-Within the build log each of these phases is framed by \lstinline{travis_fold:start:<travis phase name>} and \\ \lstinline{travis_fold:end:<travis phase name>}.
+Within the build log each phase is framed by \lstinline{travis_fold:start:<phase name>} and \lstinline{travis_fold:end:<phase name>}.
 
@@
 	      \begin{itemize}
-		      \item \textbf{TravisPhaseName} The string Travis CI uses to identify the phase within start and end statements.
+		      \item \textbf{TravisPhaseName} The string Travis CI uses to identify the phase in start and end statements.
 		      \item \textbf{TravisPhaseOutput} The output generated during the TravisPhase. The chunk presenting the \texttt{TravisPhaseOutput} is the string between the start and end statements.
 	      \end{itemize}
-				 Retrieving the names of the phases of a Travis CI build log could be used to afterward reconstruct an overview of the executed steps within a build.
+				 Retrieving the names of the phases of a Travis CI build log could be used to later reconstruct an overview of the executed steps within a build.
 	       Figure~\ref{fig:log-1} shows an example of a TravisPhase chunk and its components within a build log.
@@
 
-	\item \textbf{TravisWorker} Travis CI mentions for each build which machine is executing the build.
+	\item \textbf{TravisWorker} Travis CI logs which machine is executing each build.
 	      Retrieving this information from multiple build logs can help visualize the impact of the build server assignment algorithm.
@@
 	\item \textbf{ErrorMessage} Various tools involved in the build process output messages of errors that occurred during their execution.
-	      A developer can retrieve them understand why the build failed.
-	      Figure~\ref{fig:log-3} shows an example of and ErrorMessage chunk.
+	      A developer can retrieve them to understand why the build failed.
+	      Figure~\ref{fig:log-3} shows an example of an ErrorMessage chunk.
 
@@
 				Developers can collect and count them to encourage their team to resolve them.
-	      Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} show examples of WarningMessage chunks within build logs.
+	      Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} show two examples of WarningMessage chunks formatted differently in two build logs.
 
@@
 	\centering
+	\includegraphics[width=\textwidth, clip]{img/log12.png}
+	\caption{Excerpt from a build log showing a TravisTiming chunk and a TravisPhase chunk, containing the TravisPhaseName chunk and the TravisPhaseOutput chunk.}
+	\label{fig:log-1}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
 	\includegraphics[width=\textwidth, clip]{img/log02.png}
-	\caption{Excerpt from a build log showing a long TravisWorker chunk and a TravisSystemInfo chunk}
+	\caption{Excerpt from a build log showing a long TravisWorker chunk and a TravisSystemInfo chunk.}
 	\label{fig:log-0}
@@
 	\centering
-	\includegraphics[width=\textwidth, clip]{img/log12.png}
-	\caption{Excerpt from a build log showing a TravisTiming chunk and a TravisPhase chunk, containing the TravisPhaseName chunk and the TravisPhaseOutput chunk}
-	\label{fig:log-1}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
 	\includegraphics[width=\textwidth, clip]{img/log22.png}
-	\caption{Excerpt from a build log showing a short TravisWorker chunk}
+	\caption{Excerpt from a build log showing a short TravisWorker chunk.}
 	\label{fig:log-2}
@@
 	\includegraphics[width=\textwidth, clip]{img/log32.png}
-	\caption{Excerpt from a build log showing chunk an ErrorMessage, an ExitCode chunk and a TravisTriggeringCommand chunk}
+	\caption{Excerpt from a build log showing an ErrorMessage chunk, an ExitCode chunk and a TravisTriggeringCommand chunk.}
 	\label{fig:log-3}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/log42.png}
-	\caption{Excerpt from a build log showing a WarningMessage chunk}
-	\label{fig:log-4}
-\end{figure}
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/log52.png}
-	\caption{Excerpt from a build log showin another WarningMessage chunk}
-	\label{fig:log-5}
 \end{figure}
@@
 \centering
-\caption{Chunk Retrieval Techniques}
+\caption{Overview of the described chunk retrieval techniques.}
 \begin{tabularx}{\textwidth}{@{}XlXlX@{}} 
@@
 \midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In / output examples      \\
-Common Text Similarity       & CTS     & Tf-idf \& cosine similarity, mean number of lines expected & Line        & Output examples           \\
+Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
+Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, mean number of lines expected & Line        & Output examples           \\
 Keyword Search               & KWS     & Keywords, mean number of lines expected                    & Line        & Keywords, context length  \\
 Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                &         & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
+Diff Approach                & ---        & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
 \bottomrule
@@
 \label{sec:expl-pbe}
-\emph{Programming by Example} is a technique which synthesizes programs according to in and output examples provided by the user.
+\emph{Programming by Example} is a technique which synthesizes programs according to in- and output examples provided by the user.
 It enables users to create programs without a priori programming knowledge~\cite{mayer2015user}.
@@
 PBE reports an error back to the user if it could not synthesize a consistent program.
-The program synthesis builds on the Flash Extract DSL, which in turn uses the FlashMeta algorithm.
+The program synthesis builds on the FlashExtract DSL, which in turn uses the FlashMeta algorithm.
 Both are described in Section~\ref{sec:rw-prose}.
@@
 Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
-Next, the algorithm applies term frequency inverse document frequency to the matrix, a best practice for natural language queries~\cite{lee1997document}.
+Next, the algorithm applies TF-IDF to the matrix, a best practice for natural language queries~\cite{lee1997document}.
 
 \paragraph{Application}
-To retrieve the desired information from a build log, we parse the whole text and process it in the same way as the search query.
+To retrieve the desired information from a build log, we parse the whole text and process it in the same way as the output of the training examples.
 The algorithm calculates the cosine similarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
@@
 When developers are looking for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is searching for related keywords.
-This was one of the most common approaches we took when searching for the reason the build failed within a log while creating our \emph{LogChunks} data set.
+Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating our \emph{LogChunks} data set.
 As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
@@
 To better compare KWS with PBE and CTS, we also configure it through examples.
-We link each example with keywords, which appear in the desired output or close to it in the input build log.
+We link each example with keywords, which appear in the targeted chunk or close to it in the input build log.
 The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.

### 2019-12-26 thesis/txt/3-data-set.tex
martin feedback 2

@@
 For each build log we manually label which substring describes why the build failed.
-The data set also provides keywords a developer would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
+The data set also provides keywords we would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
 
 We start this chapter by explaining why we created \emph{LogChunks} and how it enables us to compare the chunk retrieval techniques PBE, CTS and KWS\@.
-Then, we introduces related data sets and show how \emph{LogChunks} differs.
+Then, we introduce related data sets and show how \emph{LogChunks} differs.
 The chapter describes the data schema of \emph{LogChunks} and our log collection process.
 Further, it presents the labeling process and how we validated the labeled data, including a survey of the original developers of the projects represented in \emph{LogChunks}.
-%In the first validation study, we compared the labeled data points with those of a second labeler on a sample of the build logs.
-%For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled really describes the reason the build failed.
 
@@
 	\includegraphics[page=3, width=\textwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{img/overview-graphics.pdf}
-	\caption{Overview of \emph{LogChunks}}
+	\caption{Overview of \emph{LogChunks}.}
 	\label{fig:lc-overview}
@@
 \paragraph{Log Collection}
-Existing build log analysis approaches, like writing a custom parser and creating regular expressions, are specific to the build tools which create the targeted log output.
+Existing build log analysis approaches, such as writing a custom parser and creating regular expressions, are specific to the build tools which create the targeted log output.
 In contrast to that, our findings about the chunk retrieval techniques should not be specific to a particular build tool.
@@
 Examples configure the chunk retrieval techniques we investigate.
-As the structure of a build log changes from project to project, these examples are specific to one project.
-A user of a chunk retrieval technique has to manually create the examples for for each targeted information and project.
+As the structure of a build log changes from project to project, examples on logs from one project are not suited to configure a retrieval on logs from another project that uses different build tools.
+Therefore, a user of a chunk retrieval technique has to manually create the examples for each targeted information and project.
 The effort of creating these examples should not be too high, e.g. as high as developing a custom extraction program.
-For that reason, we choose ten logs and examples per repository for \emph{LogChunks}.
+Our study should investigate how good the chunk retrieval techniques perform with a small number of training examples.
+For that reason, we choose to cover a wide range of 80 repositories and include only a few, namely ten, logs and examples per repository.
 
@@
 An example of a log chunk easily extractable by all of the three techniques is the \emph{TravisTiming}, described in Section \ref{sec:bli}.
-Travis CI logs its timing statements in a always consistent structure, therefore it would be easy for PBE to synthesize a regular expression program to extract them.
+Travis CI logs its timing statements in an always consistent structure, therefore it would be easy for PBE to synthesize a regular expression program to extract them.
 The same holds for search keywords identifying the lines which contain the \emph{TravisTiming} and selecting lines with similar text content.
@@
 \paragraph{Additional Data: Keywords and Structural Categories}
-For each log chunk example we additionally annotated keywords a developer would use to search for this log chunk, as well as a categorization of the chunks into structural categories according to their format within the log.
+For each log chunk example we additionally annotated keywords we would use to search for this log chunk, as well as a categorization of the chunks into structural categories according to their format within the log.
 The technique KWS is configured by keywords instead of in/output examples like the other techniques.
-To make the evaluation more consistent an comparable we choose to annotate keywords to each log chunk example.
+To make the evaluation more consistent and comparable we choose to annotate search keywords to each log chunk example.
 We can then use these extended examples as a configuration for KWS.
@@
 To measure this in our study we choose to categorize the examples according to their format within the log.
-Section \ref{sec:data-schema} gives examples of log chunks from the same and different structural categories.
+Section \ref{sec:data-schema} gives examples of log chunks from the same and from different structural categories.
 As we evaluate the techniques separately for separate projects, the categorization is relative to the project which produced the build log.
@@
 The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI\@.
-It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc}, related data from GHTorrent~\cite{gousios2013ghtorrent}, the corresponding git repository and data obtained through analysis of the build logs.
+It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc}, related data from GHTorrent~\cite{gousios2013ghtorrent}, the corresponding git repository and data obtained through analysis of build logs.
 The data obtained through build logs contains the names of failing test cases, similar to the chunk describing why the build failed in \emph{LogChunks}.
 However, these values are obtained through a manually developed parser, which only supports specific Ruby test runners and Java Maven or JUnit logs.
-\emph{LogChunks} provides manually labeled data points on the description of why the build failed for a much wider selection of programming languages.
+\emph{LogChunks} provides manually labeled data on the description of why the build failed for a much wider selection of programming languages.
 
@@
 The data set provides an XML file for each repository.
-Listing~\ref{lst:examples} presents the schema of these XML files.
+Figure~\ref{lst:examples} presents the schema of these XML files.
 
@@
 \end{lstlisting}
-	\caption{Example XML file from \emph{LogChunks}}
+	\caption{Example XML file from \emph{LogChunks}.}
 	\label{lst:examples}
@@
 	\item \textbf{\texttt{Chunk:}} the targeted information chunk. We are targeting the substring of the log that describes why the build failed.
-	\item \textbf{\texttt{Keywords:}} keywords a developer would use to search for the log chunk.
+	\item \textbf{\texttt{Keywords:}} keywords we would use to search for the log chunk.
 	\item \textbf{\texttt{Category:}} a categorization of the structural representation of the log chunk within the build log.
@@
 \end{itemize}
-Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
+In the following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
 
@@
 If there are multiple errors leading for the build to fail, the substring contains the first appearing continuous error descriptions.
-\emph{Continuous} means that no lines reporting of normal build behavior are interrupting the error descriptions.
-Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
-For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
-In these instances the \texttt{Chunk} contains the lines describing that the build failed.
+\emph{Continuous} means that no lines reporting normal build behavior are interrupting the error descriptions.
+When the reason \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes the description \emph{that} the build failed.
 
@@
 The \texttt{Keywords} contain a list of one to three strings appearing within the \texttt{Chunk} or in the area around it in the build log.
-We aim to select keywords a developer would use to search for the \texttt{Chunk} when inspecting the build log.
+We selected keywords we would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.
 Some example keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{failed}'', ``\texttt{[-]}'', ``\texttt{===================================}'' or ``\texttt{ERR!}''.
@@
 Two examples fall into the same structural categories if they are surrounded by similar markings.
-Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
-In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
+Figure \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
+In comparison to that, Figure \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
 For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
@@
 \end{lstlisting}
-	\caption[Log chunk from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}]{Log chunk from the \emph{same} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from one line of context}
+	\caption[Log chunk from the \emph{same} structural category as the log chunk presented in Figure \ref{lst:examples}.]{Log chunk from the \emph{same} structural category as the log chunk presented in Figure \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from one line of context.}
 	\label{lst:same-category}
@@
 \end{lstlisting}
-	\caption[Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}]{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk one line of context}
+	\caption[Log chunk from a \emph{different} structural category than the log chunk presented in Figure \ref{lst:examples}.]{Log chunk from a \emph{different} structural category than the log chunk presented in Figure \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk one line of context.}
 	\label{lst:different-category}
@@
 
-For \emph{LogChunks} we queried GHTorrent from 01/04/2018 for the three most popular repositories of each of the 30 most popular languages.
+For \emph{LogChunks} we queried GHTorrent on 01/04/2018 for the three most popular repositories of each of the 30 most popular languages.
+We found 80 repositories from 29 languages that use Travis CI\@.
+Among these repositories are, for example, \texttt{git/git}, \texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.
 
@@
 
-To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to 1000 builds per repository and keep ten for each status.
-We discard all statuses except \emph{failed}~\cite{travis2009buildstatus}.
+To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to 1000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
 A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
@@
 \texttt{TravisRequester} queries each build for the first job, which has the same state.
-For the selected jobs, the tool queries the Travis API V3 over HTTPS to obtains the corresponding build log.
+For the selected jobs, the tool queries the Travis API V3 over HTTPS to obtain the corresponding build log.
 
@@
 \section{Validation}
-We validate our collected data points in two different ways.
+We validate our collected data in two different ways.
 A different labeler performed a second pass of labeling the build failure reason, keywords and structural categories on a subset of the data.
@@
 \subsection{Inter-Rater Reliability Study}
-To evaluate the validity of our labeled data points we perform a second labeling of a sample of the data in \emph{LogChunks}.
+To evaluate the validity of our labeled data we performed a second labeling of a sample of the data in \emph{LogChunks}.
 
 \paragraph{Method}
-The second labeler processed 30 random generated logs for each data point in \emph{LogChunks}.
 We followed the same labeling process as described in Section~\ref{sec:labeling-process}.
 For the build failure reason and the keywords, we presented 30 randomly sampled build logs from distinct repositories in \emph{LogChunks}.
-The labeled structural categories are relative to the other logs from the same repository.
+The structural categories are relative to other logs from the same repository.
 Therefore, we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.
@@
 \paragraph{Results}
-For the first labeled data point, namely the substring describing why the build failed, the two labelers exactly agreed in six cases.
-In 15 cases the second labeler selected more lines than the first one, in five there was partial overlap and in 4 they completely disagreed.
-
-Regarding the keywords the two labelers completely agreed in nine cases and completely disagreed in two cases.
-In nine cases there was partial overlap in the keywords of the two labelers, in two the first labeler selected additional keywords compared to the second, while the second labeler proposed additional keywords in seven cases.
-
-When classifying the labeled substrings into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.
+For the substring describing why the build failed, the two labelers exactly agreed in six cases.
+In 15 cases the second labeler selected more lines, in five their selections overlapped and in four they completely disagreed.
+Regarding the keywords, the two labelers completely agreed in nine cases and completely disagreed in two cases.
+In nineteen cases there was overlap in the keywords of the two labelers.%, in two the first labeler selected additional keywords compared to the second, while the second labeler proposed additional keywords in seven cases.
+When classifying the chunks into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.
 
@@
 There were implicit, inconsistent assumptions both labelers created during their work.
-In the following we describe these assumptions from both labelers for each data point and the implications on our description of the data classes.
+In the following we describe these assumptions from both labelers and the implications on our description of the data classes.
 
@@
 
-Our main learning from this study is that adequately communicating all decisions and assumptions on how data is labeled is important and difficult.
+The main conclusion from this study is that adequately communicating all decisions and assumptions on how data is labeled is important and difficult.
 We reviewed the misunderstandings and incorporated more thorough descriptions of our data classes in Section~\ref{sec:data-schema}.
@@
 For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
-As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
-We only took the logs into account and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
+As we were not involved in the development of any of the projects within our data set we only relied on our previous experience with various build logs and systems.
+We only took the logs into account and did not check the related configurations, so it is possible that we extracted parts that do describe errors but that the respective step failing is ignored by the configuration and the build failed for another reason.
 
@@
 Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
-We grouped all commits triggered by one developer and sent out an mail to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
+We grouped all commits triggered by one developer and sent out an mail to each of the developers, asking whether the log chunk selected during our labeling was indeed describing the reason the build failed.
 Figure~\ref{fig:dev-mail} shows one of the mails sent out.
 The mail included links to the corresponding commits, build overview and log file.
-We asked the receivers to fill out a short survey in case our extraction was not correct.
+We asked the developers to fill out a short survey in case our chunk was not correct.
 Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
-In the survey, we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
-As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
+In the survey, we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe in their own words why we were wrong.
+As some of the chunks we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
 
@@
 We received answers from 61 developers, responding about 144 build logs.
-Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.
+Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails delivered and logs answered about, as well as those not delivered and unanswered.
 
-Of the 144 answers, 132 said our extraction was correct.
+Of the 144 log chunks we received answers about, 132 were marked as describing why the build failed.
 26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
-We manually inspected these negative answers and found that some extractions were correct after all.
-This yields 12 log extractions in our example set that were not correct, shown in Figure~\ref{fig:mails-extraction-correct}.
+We manually inspected the 26 negative answers and found that some stated that the proposed chunk did not show the whole description of why the build failed.
+This is because we had to trim long chunks to keep the mails readable.
+After adjusting these answers, 12 answers stated that our labeled log chunk was not correct, shown in Figure~\ref{fig:mails-extraction-correct}.
 
@@
 The study received answers about 18\% of the logs from \emph{LogChunks}.
-After manual correction, 91\% of the received answers said our labeled extractions were accurate.
+After manual correction, 91\% of the received answers said our labeled chunks were accurate.
 
-Most of the initial incorrect answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
-This is because we had to trim long labeled extractions to keep the mails readable.
-
-One of our extractions only showed a warning and the developer proposed to also include the line above, stating that warnings are treated as errors in the build.
-In others that were identified as incorrect, we labeled the error message of an error that later ignored and did not lead to the build failing.
+One of our chunks only showed a warning and the developer proposed to also include the line above, stating that warnings are treated as errors in the build.
+In others that were identified as incorrect, we labeled the error message of an error that was later ignored and did not lead to the build failing.
 
@@
 	\includegraphics[width=\textwidth, clip]{img/dev-mail.png}
-	\caption{An example of the mails we sent out to developers for validation of our labeled log part}
+	\caption{An example of the mails we sent out to developers for validation of our labeled log part.}
 	\label{fig:dev-mail}
@@
 		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-mails.pdf}
-		\caption{Number of mails answered, unanswered and not delivered}
+		\caption{Number of mails answered, unanswered and not delivered.}
 		\label{fig:mails-answers-received-mails}
@@
 		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
-		\caption{Proportions of logs about which mails were answered, unanswered, not delivered or we could not find a corresponding mail address}
+		\caption{Proportions of logs about which mails were answered, unanswered, not delivered or we could not find a corresponding mail address.}
 		\label{fig:mails-answers-received-builds}
@@
 	\includegraphics[width=\textwidth, clip]{img/dev-survey.png}
-	\caption{Survey for the validation with developers}
+	\caption{Survey for the validation with developers.}
 	\label{fig:dev-survey}
@@
 		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
-		\caption{Label correctness as validated by developers}
+		\caption{Label correctness as validated by developers.}
 		\label{fig:mails-extraction-correct}
@@
 		\includegraphics[width=\textwidth, clip]{img/dev-mails/logs-per-mail.pdf}
-		\caption{Average number of logs per sent out mail}
+		\caption{Average number of logs per mail sent out.}
 		\label{fig:mails-logs-per-mail}

### 2019-12-26 thesis/txt/5-study.tex
martin feedback 2

@@
 	\includegraphics[page=2, width=\textwidth, trim={0cm 1cm 1.5cm 0.5cm}, clip]{img/overview-graphics.pdf}
-	\caption{Study design of our technique comparison study}
+	\caption{Study design of our technique comparison study.}
 	\label{fig:study}
@@
 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
-		\caption{Results of chunk retrieval with PBE}
+		\caption{Results of chunk retrieval with PBE.}
 		\label{fig:failure-reason-PBE}
@@
   \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval, PBE retrieved only two of the four targeted lines}
+  \caption{Example for an unsuccessful retrieval, PBE retrieved only two of the four targeted lines.}
   \label{lst:pbe-unsuccessful}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training and test set}
+		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training and test set.}
 		\label{fig:failure-reason-categorycount-PBE}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set.}
 		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for increasing training set size}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for increasing training set size.}
 		\label{fig:recall-precision-examplecount-CTS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for increasing number of structural categories in the training and test set}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for increasing number of structural categories in the training and test set.}
 		\label{fig:recall-precision-categorycount-CTS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS compared to retrieval size factors}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS compared to retrieval size factors.}
 		\label{fig:contextsizefactor-precision-recall-CTS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for increasing training set size}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for increasing training set size.}
 		\label{fig:recall-precision-examplecount-KWS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for increasing number of structural categories in the training and test set}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for increasing number of structural categories in the training and test set.}
 		\label{fig:recall-precision-categorycount-KWS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
 		\label{fig:contextsizefactor-precision-recall-KWS}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques}
+		\caption{Success of chunk retrievals for all techniques.}
 		\label{fig:success-partial-all}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques compared}
+		\caption{Precision, recall and F$_{1}$-score of all techniques compared.}
 		\label{fig:recall-precision-all}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{one} structural category}
+		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{one} structural category.}
 		\label{fig:recall-precision-singlecategory-all}
@@
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{more than one} structural categories}
+		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{more than one} structural categories.}
 		\label{fig:recall-precision-multicategory-all}

### 2019-12-26 thesis/txt/6-discussion.tex
martin feedback 2

@@
 \end{tabularx}
-\caption{Recommendations for each of the investigated chunk retrieval techniques}
+\caption{Recommendations for each of the investigated chunk retrieval techniques.}
 \label{tab:single-technique-recommendations}
@@
 		\includegraphics[width=\textwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
+		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
 		\label{fig:crt-recommendation}

### 2019-12-26 thesis/mini/abstract.tex
martin feedback 3 + line ajustments and figure moving

--- 2019-05-02 thesis/mini/abstract.tex
@@
 
-It is just a small template, that is hopefully helpful for writing your thesis.
-First, it gives a short introduction to its usage and the personalizations.
-Finally, it presents several examples of frequently used pieces of layout.
+Continuous integration produces detailed logs about the status and results of the various tools involved in the build.
+These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps and understand the cause of a build failure.
+However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
+This makes it hard to process and analyze them.
+In this thesis, we evaluate and compare three different techniques that aim to retrieve specified log parts (chunks) from a build log, namely program synthesis by example, textual similarity and search keywords.
+We conduct an empirical study by comparing these techniques on our manually labeled \emph{LogChunks} data set of 797 Travis CI logs from 80 GitHub projects and a broad range of 29 programming languages.
+Our findings show that none of the three techniques in general outperforms the others.
+We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.
 

### 2019-12-26 thesis/txt/0-introduction.tex
martin feedback 2
martin feedback 3 + line ajustments and figure moving

@@
 Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
-Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect defects early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
+Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect defects early~\cite{vasilescu2015quality,duvall2007continuous} and to improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
 A build on a CI server typically compiles and packages the software, executes tests~\cite{beller2017oops} and performs various kinds of static analyses~\cite{zampetti2017open}.
@@
 Researchers collect the commands triggering different build steps to reverse engineer the build configuration when only the log is available to them.
-Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed tests to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
+Both groups analyze build logs for descriptions of compiler errors or failed tests to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
 
@@
 Regular expressions are exact but difficult to maintain.
-They are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
+They are developed by looking at a few exemplary build logs.
+Updating regular expressions whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
 Custom parsers are powerful though fragile towards changes in the log structure.
@@
 For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
+
 We implement and evaluate three chunk retrieval techniques:
@@
           \item the substring of the log describing the reason the build failed,
-          \item keywords developers would use to search for these substrings, and
+          \item keywords we would use to search for these substrings, and
           \item a categorization of the substrings according to their structural representation within the build log.

### 2019-12-26 thesis/txt/1-related-work.tex
martin feedback 3 + line ajustments and figure moving

@@
 Amar et al.~\cite{amar2019mining} compare different approaches to reduce the portions of a log that a developer has to inspect.
-Their techniques remove lines that appear both in passing and failing build logs and use a modified \emph{Term Frequency Inverse Document Frequency} (TF-IDF) weighting to identify term vectors likely to occur with failures.
-They use term vectors and cosine similarity to further filter the log portions only present in failing build logs.
+Their techniques remove lines that appear both in logs from passing and failing builds and use a modified \emph{Term Frequency Inverse Document Frequency} (TF-IDF) weighting to identify term vectors likely to occur with failures.
 Their diff technique can be interpreted as a chunk retrieval technique, where the targeted information is defined by the past failures used as basis for the weighted term vectors.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
@@
 \end{figure}
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=\textwidth, clip]{img/log52.png}
-	\caption{Excerpt from a build log showing another WarningMessage chunk.}
+	\caption{Excerpt from a build log showing a differently formatted WarningMessage chunk.}
 	\label{fig:log-5}
@@
 % \section{Information Extraction and Retrieval Techniques}
-The techniques we investigate in this thesis are based on existing methods of Programming by Example, information extraction and information retrieval.
-This section presents different Programming by Example resources surrounding Microsoft's work on the PROSE library.
+The techniques we investigate are based on existing methods of Programming by Example, information extraction and information retrieval.
+This section presents different Programming by Example resources surrounding the PROSE library.
 We explain its generic program synthesis algorithm and how PROSE synthesizes text extraction programs, the foundation of PBE\@.
@@
 The IEPAD tool created by Chang et al.~\cite{chang2003automatic} automatically identifies data extraction patterns in semi-structured web pages, without requiring user-labeled training examples.
-They split the semi-structured documents into tokens, discover repetitive patterns using occurrence-counting suffix trees and select the most regular and compact patterns to define extraction.
+They split the documents into tokens, discover repetitive patterns using occurrence-counting suffix trees and select the most regular and compact patterns to define extraction.
 

### 2019-12-26 thesis/txt/2-models.tex
martin feedback 3 + line ajustments and figure moving

@@
 
-\begin{table}[htbp]
+\begin{table}[H]
 \centering
@@
 Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, mean number of lines expected & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, mean number of lines expected                    & Line        & Keywords, context length  \\
+Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
+Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
 Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
@@
 \label{sec:expl-rlr}
-Literature mentions further build log analysis techniques.
-This section describes them with our notion of chunk retrieval techniques.
+%Literature mentions further build log analysis techniques.
+%This section describes them with our notion of chunk retrieval techniques.
 

### 2019-12-26 thesis/txt/3-data-set.tex
graphics corrections
martin feedback 3 + line ajustments and figure moving

@@
 
-\subsection{TravisTorrent}
+\paragraph{TravisTorrent}
 The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI\@.
@@
 
-\subsection{Travis CI Build Log Data Set}
+\paragraph{Travis CI Build Log Data Set}
 Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected a large amount of Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
@@
 We selected keywords we would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.
-Some example keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{failed}'', ``\texttt{[-]}'', ``\texttt{===================================}'' or ``\texttt{ERR!}''.
+Some example keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{failed}'', ``\texttt{[-]}'', ``\texttt{===================}'' or ``\texttt{ERR!}''.
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth, clip]{img/dev-mail.png}
-	\caption{An example of the mails we sent out to developers for validation of our labeled log part.}
-	\label{fig:dev-mail}
-\end{figure}
-
-\begin{figure}[htbp]
+\begin{figure}[p]
 	\centering
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
-		\caption{Proportions of logs about which mails were answered, unanswered, not delivered or we could not find a corresponding mail address.}
-		\label{fig:mails-answers-received-builds}
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/logs-per-mail.pdf}
+		\caption{Average number of logs per mail sent out.}
+		\label{fig:mails-logs-per-mail}
 	\end{minipage}
@@
 
-\begin{figure}[h]
+\begin{figure}[p]
 	\centering
-	\includegraphics[width=\textwidth, clip]{img/dev-survey.png}
-	\caption{Survey for the validation with developers.}
-	\label{fig:dev-survey}
+	\includegraphics[width=\textwidth, clip]{img/dev-mail.png}
+	\caption{An example of the mails we sent out to developers for validation of our labeled log part.}
+	\label{fig:dev-mail}
 \end{figure}
 
-\begin{figure}[htbp]
+\begin{figure}[p]
 	\centering
@@
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/dev-mails/logs-per-mail.pdf}
-		\caption{Average number of logs per mail sent out.}
-		\label{fig:mails-logs-per-mail}
+		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
+		\caption{Proportions of logs about which mails were answered, unanswered, not delivered or we could not find a corresponding mail address.}
+		\label{fig:mails-answers-received-builds}
 	\end{minipage}
@@
 
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=\textwidth, clip]{img/dev-survey.png}
+	\caption{Survey for the validation with developers.}
+	\label{fig:dev-survey}
+\end{figure}
+
 \end{document}

### 2019-12-26 thesis/txt/5-study.tex
martin feedback 3 + line ajustments and figure moving

@@
 \section{Study Design}
-For the comparison, we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},\ref{sec:expl-ts} and~\ref{sec:expl-skws}.
-RLR, explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
-We run four techniques on the Examples from \emph{LogChunks}.
+For the comparison, we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe}, \ref{sec:expl-ts} and \ref{sec:expl-skws}.
+Random Line Retrieval (RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
+We run four techniques on the examples from \emph{LogChunks}.
 \paragraph{Training and Test Set}
@@
 For each repository in \emph{LogChunks}, we split the examples chronologically into training and test set.
-Therefore, we train on examples from past build logs and test on future build logs.
+Therefore, we train on examples from past build logs and test on more recent build logs.
 
@@
 
-Precision of a chunk retrieval describes which proportion of the retrieved lines were targeted.
+Precision of a chunk retrieval describes which proportion of the retrieved lines were desired.
 Recall of a chunk retrieval describes which proportion of the targeted lines were retrieved.
-Throughout the presentation and discussion of our results we show these two metrics separate, as they might have a different weight when choosing a suitable technique for a task.
-In addition, we calculate the F1-score, the harmonic mean of precision and recall.
+Throughout the presentation and discussion of our results we show these two metrics separately, as they might have a different weight when choosing a suitable technique for a task.
+In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall.
 We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
@@
 
-\subsection{Program Synthesis by Example (PBE)}
-Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
-Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
-Figure~\ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
-In 30 cases the synthesized program did not extract all of the desired lines and had an average recall of 28\%.
-We present example of such an \emph{unsuccessful retrieval} in Listing \ref{lst:pbe-unsuccessful}, where the synthesized regular expression program only retrieved two of the four targeted lines.
-In 173 cases the PROSE program synthesis could not synthesize a regular expression program that is consistent with all of the training examples.
-
-Figure~\ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training and test examples.
-It shows that the program synthesis is more likely to succeed when there are few categories present in the training examples.
-When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all training examples.
-For three or more present categories PROSE could never synthesize a consistent program.
-
-Figure~\ref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of runs where PBE could synthesize a program consistent with all training examples.
-When the training set size increases from one to two, recall and F$_{1}$-score increase by 25\%, precision increases by 10\%.
-For two or more training examples the recall and F$_{1}$-score stay around 75\% and precision around 96\%.
-
-\begin{figure}[htbp]
+\begin{figure}[hb]
 		\centering
@@
 }
-\begin{figure}[]
+\begin{figure}[hb]
   \centering
@@
         on line 86 of sass/components/dropdown.sass   
-
 Desired Test Output:
@@
   \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval, PBE retrieved only two of the four targeted lines.}
+  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
   \label{lst:pbe-unsuccessful}
@@
 
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training and test set.}
-		\label{fig:failure-reason-categorycount-PBE}
-\end{figure}
+\subsection{Program Synthesis by Example (PBE)}
+Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
+Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
+In 89 further cases a program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output at all.
+In 30 of the 89 cases the synthesized program did not extract all of the desired lines.
+For these 30 cases, the average recall was 28\%.
+We present an example of such an \emph{unsuccessful retrieval} in Listing \ref{lst:pbe-unsuccessful}, where the synthesized regular expression program only retrieved two of the four targeted lines.
+In 173 of the 400 cases the PROSE program synthesis could not synthesize a regular expression program that is consistent with all of the training examples.
 
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set.}
-		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{figure}
+Figure~\ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training and test examples.
+It shows that the program synthesis is more likely to succeed when there are only a few categories present in the training examples.
+When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all training examples.
+For three or more present categories PROSE could never synthesize a consistent program.
+
+Figure~\ref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of the 227 runs where PBE could synthesize a program consistent with all training examples.
+When the training set size increases from one to two, recall and F$_{1}$-score increase by about 25\%, precision increases by about 10\%.
+For two or more training examples, recall and F$_{1}$-score stay around 75\% and precision around 96\%.
 
@@
 The recall ranges from 30\% to 55\%.
-A retrieval size factor of 1 gives the best F$_{1}$-score with 51\%.
+A retrieval size factor of 1 gives the best average F$_{1}$-score with 51\%.
 
-\begin{figure}[htbp]
+\begin{figure}[t]
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+		\caption{Results of chunk retrieval with PBE for an increasing number of structural categories in the training and test sets.}
+		\label{fig:failure-reason-categorycount-PBE}
+\end{figure}
+
+\begin{figure}[t]
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set.}
+		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
+\end{figure}
+
+\begin{figure}[hp]
 		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for increasing training set size.}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing training set size.}
 		\label{fig:recall-precision-examplecount-CTS}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[hp]
 		\centering
 		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for increasing number of structural categories in the training and test set.}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing number of structural categories in the training and test sets.}
 		\label{fig:recall-precision-categorycount-CTS}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[hp]
 		\centering
@@
 		\label{fig:contextsizefactor-precision-recall-CTS}
-\end{figure}
-
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{figure}
-
-\begin{figure}[htbp]
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for increasing number of structural categories in the training and test set.}
-		\label{fig:recall-precision-categorycount-KWS}
 \end{figure}
@@
 
-Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for increasing number of structural categories in the training and test examples.
-For more than one structural category in the training and test examples the recall decreases about 20\% and the precision decreases about 6\%.
-For more than two structural categories no clear trend visible in precision, recall or F$_{1}$-score for an increasing amount of categories in the training and test examples.
+Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for an increasing number of structural categories in the training and test examples.
+For more than one structural category in the training and test examples the recall decreases by about 20\% and the precision decreases about 6\%.
+For more than two structural categories no clear trend is visible in precision, recall or F$_{1}$-score for an increasing amount of categories in the training and test examples.
 
 Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
-The precision is 19\% when retrieving half expected number of lines. On average 9\% of the lines in the build log are retrieved then.
-When 2.5 times the expected number of lines, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
+The precision is 19\% when retrieving half of the expected number of lines. On average 9\% of the lines in the build log are retrieved then.
+When 2.5 times the expected number of lines are retrieved, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
 The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
 
-\begin{figure}[htbp]
+\begin{figure}[hp]
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for an increasing training set size.}
+		\label{fig:recall-precision-examplecount-KWS}
+\end{figure}
+
+\begin{figure}[hp]
+		\centering
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for an increasing number of structural categories in the training and test sets.}
+		\label{fig:recall-precision-categorycount-KWS}
+\end{figure}
+
+\begin{figure}[hp]
 		\centering
@@
 \subsection{Comparison of All Techniques}
-Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval of the different techniques in our study.
+Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval by the different techniques in our study.
 CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
-With 38.25\%, KWS also has the highest number of successful extractions, followed by PBE with 34.5\%.
+With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
 PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.
 
-The averaged precision, recall and F$_{1}$-score of all techniques is compared in Figure~\ref{fig:recall-precision-all}.
+The averaged precision, recall and F$_{1}$-score f all techniques is compared in Figure~\ref{fig:recall-precision-all}.
 The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
 PBE has the highest average precision with 95\%.
-Chunk retrieval with CTS has tmhe highest average F$_{1}$-score with 51\% and the second highest recall with 46\%.
+Chunk retrieval with CTS has the highest average F$_{1}$-score with 51\% and the second highest recall with 46\%.
 KWS has the smallest precision of the three chunk retrieval techniques.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[hp]
 	\centering

### 2019-12-26 thesis/txt/6-discussion.tex
martin feedback 3 + line ajustments and figure moving

@@
 It details for which types of input build logs, available training examples and consumption of the retrieved output each technique is suited.
-In the following section we discuss which of these criteria should influence the decision on a technique most.
+In the following section we discuss which of these criteria should influence the decision to use a certain technique most.
 Based on our empirical comparison, we present a decision tree between the three techniques we investigated.
@@
 This section discusses the study results for each of the analyzed chunk retrieval techniques separately.
-It gives recommendations on which kind of information chunk targets are best for each technique and for what kind of usage the output is suitable.
+It gives recommendations which kind of information chunk targets are best for each technique and for what kind of usage the respective output is suitable.
 
@@
 \paragraph{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and high recall.
-The tool clearly identifies a failing program synthesis or no output from the program applied to a build log.
-Therefore, if there is an output, the user can have high confidence it is the correct output.
-This makes output from PBE chunk retrieval well suited for consumption of other software components.
+If the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and a high recall.
+The tool clearly identifies a failing program synthesis or when no output from the program applied to a build log is obtained.
+Therefore, if there is an output, the user can have high confidence that it is the correct output.
+This makes output from PBE chunk retrieval well suited for consumption by other software components.
 
@@
 Chunk retrieval using CTS also yields better results the fewer structural categories are present in the training and test examples.
+
 The number of training examples had no noticeable influence on precision or recall in our study.
-Information retrieval techniques like text similarity commonly learn on a higher number of examples than we used for our study.
+Information retrieval techniques like text similarity commonly learn on a higher number of examples than used for our study.
 Future work is needed to investigate how many examples yield improvements in the chunk retrieval over a single training example.
@@
 \paragraph{Configuration and Input}
-KWS has a higher recall than both other techniques for multiple structural categories present in the training and test examples.\@.
+KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.\@.
 This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.
@@
 \section{Recommendations of Suitable Techniques}
-After discussing three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
+After discussing the three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
 We present a decision tree, which developers and researchers who want to retrieve information chunks from build logs can follow.
@@
 The recommendations are therefore based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
+
 This decision tree is the answer to our first research question about which criteria influence the suitability of a chunk retrieval technique.
@@
 
-If the information chunks are from multiple structural categories, meaning the are not represented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS\@.
+If the information chunks are from multiple structural categories, i.e.
+they are not represented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS\@.
 If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
-We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the precision or recall of the outcome and the user would rather have output with low recall instead of no output at all.
+We also recommend CTS when the representations are from one structural category, when the user does not require a high confidence in the precision or recall of the outcome and when the user would rather have output with low recall instead of no output at all.
 When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.
@@
 \paragraph{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we follow with describing two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.
+To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we describe two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.
 
@@
 When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test cases is in the investigated build logs.
-As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, not predictable structural representations.
+As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, non-predictable structural representations.
 The next question is whether they value precision over recall.
@@
 
-In case the researchers want to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
+In case the researcher wants to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
 Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each test tool separately.
@@
 Our results are highly dependent on our implementation of the investigated chunk retrieval techniques and the libraries we used.
-Our implementation of PBE is mainly based on the program synthesis provided by PROSE\@.
+Our implementation of PBE is severely based on the program synthesis provided by PROSE\@.
 Its limitations are therefore also mainly influenced by this library.
@@
 This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.
-% \bp{
-% chronologically selected examples -> very specific view, devs/users might pick more representative examples
 
-% very few evaluation runs with a high number of categories in configuring I/O examples -> because we chose to create such a ``realistic'' data set, from data set we see that many structural categories uncommon
-
-% some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed}
 \end{document}

### 2019-12-26 thesis/txt/7-conclusion.tex
martin feedback 3 + line ajustments and figure moving

@@
 \label{sec:conclusion-fw}
-The goal of this thesis is to support researchers and developers when they decide how to analyze build logs.
-We implemented and compared three different chunk retrieval techniques on our \emph{LogChunks} data set.
+The goal of this thesis was to support researchers and developers in their decision on how to analyze build logs.
+We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
 Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
-Secondary factors are confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.
+Secondary factors are the desired confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.
 
@@
 \begin{itemize}
-  \item \textbf{Further Analysis of the \emph{LogChunks} Data Set} We created the \emph{LogChunks} data set specifically for our comparison study, though it can be the basis for various further analyses of build log data.
-  The keywords, for example, can be investigated to answer which keywords developers use to search for the reason the build failed within build logs.
+  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set specifically for our comparative study, though it can be the basis for various further analyses of build log data.
+  The keywords, for example, can be investigated to answer which keywords are used to search for the reason the build failed within build logs.
   \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
-  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment agnostic analysis tools.
+  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment-agnostic analysis tools.
   \item \textbf{Comparison with more Chunk Retrieval Techniques} This thesis investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
-  Our study design can be reused to evaluate other build log analysis techniques.
+  Our study design can be reused to evaluate other build log analysis techniques, such as the diff and information retrieval approach by Amar et al.~\cite{amar2019mining}.
   \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
-  In a next step, each of these techniques could be refined and configured to better approach the domain of build logs.
-  The \emph{LogChunks} data set and our study results act as a baseline to evaluate further technique improvements.
+  In a next step, each of these techniques could be refined to better approach the domain of build logs.
+  The \emph{LogChunks} data set and our study results act as a baseline to benchmark such technique improvements.
   We propose the following improvements:
@@
       \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
-      We could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
+      One could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
       FlashExtract includes special tokens when enumerating possible regular expressions.
-      We could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
+      One could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
       \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
-      We propose to further investigate improvements in preprocessing of the log text, tokenization of the log lines into terms and stop words lists.
+      We propose to further investigate improvements in preprocessing of the log text, in tokenization of the log lines into terms and in stop words lists.
     \end{itemize}
   \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focuses on precision and recall.
-  In addition to precision and recall, we propose to investigate how useful these outputs are to developers through controlled experiments.
+  We propose to investigate how useful these outputs are to developers through controlled experiments.
 \end{itemize}

### 2019-12-27 thesis/mini/abstract.tex
thesis version printed

@@
 Continuous integration produces detailed logs about the status and results of the various tools involved in the build.
-These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps and understand the cause of a build failure.
+These build logs are a valuable data source for developers and researchers to inspect test results, to check the duration of build steps and to understand the cause of a build failure.
 However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
@@
 In this thesis, we evaluate and compare three different techniques that aim to retrieve specified log parts (chunks) from a build log, namely program synthesis by example, textual similarity and search keywords.
-We conduct an empirical study by comparing these techniques on our manually labeled \emph{LogChunks} data set of 797 Travis CI logs from 80 GitHub projects and a broad range of 29 programming languages.
+We conduct an empirical study by comparing these techniques on our manually labeled \emph{LogChunks} data set of 797 Travis CI build logs from a broad range of 80 projects.
 Our findings show that none of the three techniques in general outperforms the others.

### 2019-12-27 thesis/mini/acknowledgments.tex
thesis version printed

@@
 \noindent
-I would like to thank Dr. Moritz Beller for his great support, his detailed feedback and his invaluable teaching how to do research.
+I would like to thank Dr.\ Moritz Beller for his great support, his detailed feedback and his invaluable teaching on how to do research.
 I could not have imagined a better advisor for my master's thesis.
@@
 \noindent
-Furthermore, I would like to thank Prof. Annibale Panichella for his helpful feedback and teaching me the proper vocabulary to describe my work.
+Furthermore, I would like to thank Prof.\ Annibale Panichella for his helpful feedback and teaching me the proper vocabulary to describe my work.
 
 \noindent
-I want to pay my special regards to Prof. Alexander Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.
-I would like to thank Prof. Alexander Knapp for his sharp eyes for formulas and our reassuring conversations.
+I want to pay my special regards to Prof.\ Alexander Pretschner for his critical questions, leading me to continuously challenge my evaluation and the problems my work addresses.
+I would like to thank Prof.\ Alexander Knapp for his sharp eyes for formulas and our reassuring conversations.
 

### 2019-12-27 thesis/txt/1-related-work.tex
thesis version printed

@@
 The first section presents existing work in the field of continuous integration (CI) and showcases how researchers analyze build logs.
-In the second section we describe the existing methods which are the foundation for the chunk retrieval we investigate.
+In the second section we describe the existing methods which are the foundation for the chunk retrieval techniques we investigate.
 % moritz: nice formulation :)
@@
 We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
-We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifys their data collection.
+We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
 This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
@@
 \paragraph{Data Sets Powering CI Research}
-The works presented in this section are based on either developer surveys or data setsa containing build metadata or build logs.
+The works presented in this section are based on either developer surveys or data sets containing build metadata or build logs.
 Seo et al.~\cite{seo2014programmers} and Vassallo et al.~\cite{vassallo2017a-tale} based their analyses on sets of build logs collected from industry partners.
@@
 The user provides examples for the input and the corresponding output and a synthesis algorithm tries to create the program intended by the user.
-This section introduces the theoretical foundations of the program synthesis algorithm of the \emph{Program Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
+This section introduces the theoretical foundations of the program synthesis algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
 The PROSE framework is developed by Microsoft Research.

### 2019-12-27 thesis/txt/6-discussion.tex
thesis version printed

@@
 \paragraph{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.\@.
+KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
 This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.

### 2020-01-14 msr-paper/paper.tex
Edit abstract

@@
 \begin{abstract}
-Build failures are common in continuous integration (CI), but identifying the root cause of a failure is difficult.
-To stimulate research in this area, we present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
-For each build log we manually labeled the log part (chunk) describing why the build failed.
-We validated the data set by surveying the developers of the projects which produced the builds.
-The width and depth of the \emph{LogChunks} data set makes it an ideal basis to benchmark build log analysis techniques.
-Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
-Benchmarking different techniques will advance the research area of build log analysis and ultimately increase our understanding of CI build failures.
+Build logs are the textual by-products that a software build processes
+creates, often as part of a Continuous Integration (CI)
+pipeline. Build logs are a paramount source of information for
+developers when debugging into and understanding a build
+failures. Recently, attempts to partly automate this time-consuming,
+purely manual activity have come up, such as rule- or
+Information-Retrieval-based techniques.
+
+While still in their infancy, we believe that having a common dataset
+to be able to fairly compare different build log analysis techniques
+will advance the research area and ultimately increase our
+understanding of CI build failures. In this paper, we present
+\emph{LogChunks}, a collection of 797 fully annotated Travis CI build
+logs from 80 GitHub repositories in 29 programming languages. For each
+build log, LogChunks contains a manually labeled log part (chunk)
+describing why the build failed. We externally validated the data set
+with the developer who caused the original build failure.
+
+In our opinion, the width and depth of the \emph{LogChunks} data set
+makes it an ideal benchmark for automated build log analysis
+techniques.
 \end{abstract}

### 2020-01-14 msr-paper/paper.tex
Review until l300

@@
 Build logs are the textual by-products that a software build processes
-creates, often as part of a Continuous Integration (CI)
+creates, often as part of its Continuous Integration (CI)
 pipeline. Build logs are a paramount source of information for
@@
 purely manual activity have come up, such as rule- or
-Information-Retrieval-based techniques.
+information-retrieval-based techniques.
 
@@
 In our opinion, the width and depth of the \emph{LogChunks} data set
-makes it an ideal benchmark for automated build log analysis
+make it an ideal benchmark for automated build log analysis
 techniques.
@@
 CI builds produce logs which report the results of the steps within the build.
-These build logs contain a lot of valuable information for developers and researchers.
+These build logs contain a lot of valuable information for developers and researchers, for example:
 %Developers examine time measurement log statements to track how different stages of the build process perform.
 %Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
-They analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
+descriptions of compile errors, linter warnings or failed tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
 
-The problem is, that build logs are verbose and long~\cite{beller2017oops}, making them inadequate for direct consumption.
-Therefore, developers and researchers can only efficiently use the information within the build logs if they can adequately retrieve the parts (chunks) of the log that describe the targeted information.
+However, build logs are verbose and
+long~\cite{beller2017oops}---sometimes in excess of 50 MB of ASCII
+text for one build---, making them inadequate for direct consumption.
+Therefore, developers and researchers can only efficiently use the
+information within the build logs if we can at least
+semi-automatically retrieve the chunks of the log that describe the
+targeted information.
 
 There are different techniques to retrieve information chunks from CI build logs.
-Beller et al.\ use regular expressions to analyze logs from Travis CI~\cite{beller2017oops}.
+Beller et al. use a rule-based system of regular expressions to analyze logs from Travis CI~\cite{beller2017oops}.
 Such regular expressions are developed by looking at exemplary build logs.
-Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
 Vassallo et al.\ wrote a custom parser to gather information for build repair hints~\cite{vassallo2018un-break}.
@@
 
-These approaches have various strengths and weaknesses:
-Regular expressions are exact but difficult to maintain~\cite{michael2019regexes}.
-Custom parsers are powerful though fragile towards changes in the log structure.
-The structure of build logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
-Taking a diff between failed and successful logs can reduce the information to be processed, but the imprecise output needs to be interpreted by a developer~\cite{amar2019mining}.
+These approaches have various strengths and weaknesses: Regular
+expressions are exact, but tedious and error-prone to
+maintain~\cite{michael2019regexes}.  Custom parsers are powerful
+though fragile in light of changes in the log structure. Diffing
+between failed and successful logs can reduce the information to be
+processed, but is at best semi-automatic~\cite{amar2019mining}.
 
-At the moment there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred over other alternatives.
-In addition, there is currently no data set available to benchmark such build log analysis techniques.
-Following Sim et al., a benchmark gives us the chance to ``increase the scientific maturity of the area''~\cite{sim2003using} of build log analysis by evaluating and comparing research contributions.
+At the moment there is only anecdotal evidence on the performance of
+these techniques and when a technique should be preferred over its
+alternatives.  In fact, there is no data set available to support the
+creation of such a benchmark of build log analysis techniques.
+Following Sim et al., a benchmark gives us the chance to ``increase
+the scientific maturity of the area''~\cite{sim2003using} of build log
+analysis by evaluating and comparing research contributions.
 
-We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
-For each build log, we manually labeled which substring describes why the build failed.
-The data set also provides keywords the authors would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.
-
-% andy: okay if no structure overview in 4 page paper, place too valuable
-% In this paper, we illustrate potential use cases of \emph{LogChunks}.% and our past study using the data set.
-% Section~\ref{sec:related-data-sets} describes related data sets and how \emph{LogChunks} differs from them.
-% The following section introduces the data schema, how to access the data set, as well as limitations and potential improvements.
-% We present our data collection in Section~\ref{sec:data-collection}.
-% To validate our labels we performed a second labeling of a sample of the data.
-% In addition, we surveyed the developers, whose commits triggered the builds, whether our labeled log chunk describes why their build failed.
-% Section~\ref{sec:validation} presents the two validation studies.
-% To conclude we describe limitations as well as potential improvements of \emph{LogChunks}.
-
-We published \emph{LogChunks} through Zenodo: \todo{insert zenodo link}.
+Thus, in this paper, we present \emph{LogChunks},\footnote{LogChunks is
+  openly available on Zenodo: \todo{insert zenodo link}} a collection
+of 797 Travis CI build logs from 80 GitHub repositories spread over 29
+programming languages.  For each build log, we manually labeled chunk
+describing why the build failed.  The data set also provides keywords
+the authors would use to search for the labeled log chunk and
+categorizes the log chunks according to their format within the log.
 
@@
 \paragraph{Benchmarking Build Log Analysis Techniques}
-We created this data set to compare different techniques to retrieve chunks from build logs. %\todo{cite journal paper (or preprint?)}.
-The techniques we compared are based on program synthesis from examples, text similarity and searching for keywords.
-\emph{LogChunks} can be a benchmark to evaluate further build log analysis techniques.
-For example, we can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason a build failed.
+LogChunks is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
+\emph{LogChunks} can be a benchmark to evaluate other build log analysis techniques.
+For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.
 
 \paragraph{Support Build Log Classification Algorithms}
-Various researchers are looking into why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
+Various researchers are examining why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
 They write custom parsers and classifiers to categorize builds according to why a build failed.
-The manually labeled chunk describing why the build failed can show classification algorithms where in a build log they can find information relevant for the classification.
+The manually labeled chunk can help researchers locate the source for their classification algorithms and cross-validate their data.
 
@@
 We can also recommend users which search keywords they should use to find why the build failed.
+\todo{Isn't this pretty simple and not really worth a research paper? If it is too trivial, we should probably not mention it here.}
 
@@
 The chunks describing why a build failed, or the results of build log analysis techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
+\todo{Similar comment: This is a bit too narrow.
+But perhaps we can merge the two in one and say researchers doing research around the topic of build logs, such as ...
+user studies on keyword retrievala and conversations?}
 
-% Andy also proposed: automatic creation of issue reports on GitHub with extracted info: sounds okay, but build failures are to be fixed faster than a GH issue I would say
+\todo{ Andy also proposed: automatic creation of issue reports on GitHub with extracted info: sounds okay, but build failures are to be fixed faster than a GH issue I would say}
+\todo{I think this proposal is again too narrow: but what about further automatic on-ward processing? Even if small, perhaps reinforcement learning might be feasible ...}
 
@@
 \label{sec:related-data-sets}
-This section presents existing data sets of CI build logs and why \emph{LogChunks} is unique among them.
+This section presents existing data sets of CI build logs and how
+\emph{LogChunks} is different from them.
 
 \subsection{TravisTorrent}
-The \emph{TravisTorrent} data set~\cite{beller2017travistorrent} collects a broad range of metadata about builds on Travis CI\@.
-It combines data accessible through the public Travis CI API~\cite{travisci2019apidoc} and related data from GitHub~\cite{github2019website} through GHTorrent~\cite{gousios2013ghtorrent}.
-They provide the names of failing test cases.
-However, they obtained these through a manually developed parser, which only supports specific Ruby test runners and Java Maven or JUnit logs.
-\emph{LogChunks} provides manually labeled data on the description of why builds failed for a much wider selection of build tools.
+\emph{TravisTorrent}~\cite{beller2017travistorrent} collects a broad
+range of metadata about builds on Travis CI\@.  It combines data
+accessible through the public Travis CI and GitHub APIs and through
+GHTorrent~\cite{gousios2013ghtorrent}. Similar to LogChunks, among the
+metadata are the failing test cases.  However, TravisTorrent obtained
+these through a manually developed parser, which only supports
+specific Ruby test runners and Java Maven or JUnit logs. Anecdotally,
+many of the failing tests are at least incomplete and lack
+validation. By contrast, \emph{LogChunks} provides manually labeled
+data on the description of why builds failed for a much wider
+selection of build tools.
 
 \subsection{Travis CI Build Log Data Set}
+\todo{I would remove this as it is not really related because it does not contain labels?}
 Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
@@
 Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
+
+\todo{What about the related data set I showed you and Georgios also mentioned? (Forgot exact name but don't have Internet so cannot look it up.)}
 

### 2020-01-15 msr-paper/paper.tex
Done until L280

@@
 \usepackage{tabularx}
+\usepackage{cleveref}
 
@@
 \section{Introduction}
-Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
-Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
-CI builds produce logs which report the results of the steps within the build.
-These build logs contain a lot of valuable information for developers and researchers, for example:
-%Developers examine time measurement log statements to track how different stages of the build process perform.
-%Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
-descriptions of compile errors, linter warnings or failed tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
+Continuous Integration (CI) has become a common practice in software
+engineering~\cite{hilton2016usage}.  Many software projects use
+CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
+bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
+developer productivity~\cite{miller2008hundred,hilton2016usage} and
+communication~\cite{downs2012ambient}.  CI builds produce logs which
+report the results of the steps within the build.  These build logs
+contain a lot of valuable information for developers and researchers,
+for example: descriptions of compile errors, linter warnings or failed
+tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
 
-However, build logs are verbose and
-long~\cite{beller2017oops}---sometimes in excess of 50 MB of ASCII
-text for one build---, making them inadequate for direct consumption.
-Therefore, developers and researchers can only efficiently use the
-information within the build logs if we can at least
-semi-automatically retrieve the chunks of the log that describe the
-targeted information.
+However, build logs can be verbose and large---sometimes in excess of
+50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
+for direct human consumption. Therefore, to support developers and
+researchers in efficiently making use of the information within build
+logs, we must at least semi-automatically retrieve the chunks of the
+log that describe the targeted information.
 
-There are different techniques to retrieve information chunks from CI build logs.
-Beller et al. use a rule-based system of regular expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build logs.
-Vassallo et al.\ wrote a custom parser to gather information for build repair hints~\cite{vassallo2018un-break}.
-Recently, Amar et al.\ reduced the number of lines for a developer to inspect by creating a diff between logs from failed and successful builds~\cite{amar2019mining}.
+There are different techniques to retrieve information chunks from CI
+build logs. Beller et al. use a rule-based system of regular
+expressions to analyze logs from Travis CI~\cite{beller2017oops}.
+Such regular expressions are developed by looking at exemplary build
+logs.  Vassallo et al.\ wrote a custom parser to gather information
+for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
+al.\ reduced the number of lines for a developer to inspect by
+creating a diff between logs from failed and successful
+builds~\cite{amar2019mining}.
 
@@
 
-Thus, in this paper, we present \emph{LogChunks},\footnote{LogChunks is
-  openly available on Zenodo: \todo{insert zenodo link}} a collection
-of 797 Travis CI build logs from 80 GitHub repositories spread over 29
-programming languages.  For each build log, we manually labeled chunk
-describing why the build failed.  The data set also provides keywords
-the authors would use to search for the labeled log chunk and
+Thus, in this paper, we present \emph{LogChunks},\footnote{LogChunks
+  is openly available on Zenodo: \todo{insert zenodo link}} a
+collection of 797 Travis CI build logs from 80 GitHub repositories in
+29 programming languages.  For each build log, we manually labeled
+the chunk describing why the build failed.  The data set also provides
+keywords the authors would use to search for the labeled log chunk and
 categorizes the log chunks according to their format within the log.
 
+\todo{mention most popular repositories very briefly somewhere?}
+\todo{80x -> 80}
 \begin{figure}[tbp]
@@
 
-%\section{Applications}
-%This section possible use cases for \emph{LogChunks} and outlines how we previously applied it to compare different build log analysis techniques.
-\section{Potential Use Cases}
-
-%\subsection{Potential Use Cases}
-\emph{LogChunks} can be the basis for a wide range of further studies:
-
-\paragraph{Benchmarking Build Log Analysis Techniques}
-LogChunks is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
-\emph{LogChunks} can be a benchmark to evaluate other build log analysis techniques.
-For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.
-
-\paragraph{Support Build Log Classification Algorithms}
-Various researchers are examining why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
-They write custom parsers and classifiers to categorize builds according to why a build failed.
-The manually labeled chunk can help researchers locate the source for their classification algorithms and cross-validate their data.
-
-\paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
-\emph{LogChunks} provides keywords that the authors would use to search for the chunk describing why the build failed.
-Analyzing these can help us understand how users process build logs and which keywords a tool should use to mark an error description.
-We can also recommend users which search keywords they should use to find why the build failed.
-\todo{Isn't this pretty simple and not really worth a research paper? If it is too trivial, we should probably not mention it here.}
-
-\paragraph{Studying Conversations about Build Failures}
-Researchers are looking into conversations of developers surrounding CI builds and pull requests \todo{citation pending}
-%TODO Caro: nathan cassee (with Alexander Sebrenik) did this in his master thesis (paper got accepted, will get link when preprint is finished), did not find others yet that do this}.
-The chunks describing why a build failed, or the results of build log analysis techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
-\todo{Similar comment: This is a bit too narrow.
-But perhaps we can merge the two in one and say researchers doing research around the topic of build logs, such as ...
-user studies on keyword retrievala and conversations?}
-
-\todo{ Andy also proposed: automatic creation of issue reports on GitHub with extracted info: sounds okay, but build failures are to be fixed faster than a GH issue I would say}
-\todo{I think this proposal is again too narrow: but what about further automatic on-ward processing? Even if small, perhaps reinforcement learning might be feasible ...}
-
-% \subsection{Chunk Retrieval Evaluation}
-% We created \emph{LogChunks} to evaluate and compare different chunk retrieval techniques for build logs.
-% The first technique is based on synthesizing programs from examples using the Microsoft PROSE library.
-% A user provides a small number of examples to describe which text part the program should extract.
-% PROSE then synthesizes a program of regular expressions that is consistent with these examples.
-% We compared this extraction technique to a text similarity approach, which selects the lines of a build log which are most similar to the ones in the given user examples.
-% Lastly, we investigated searching for keywords that are associated with the given user examples.
-
-% The log chunks in this data set provided the examples for these techniques, the keywords were used to configure the keyword search.
-% The structural categories enabled us to measure how structurally similar the examples have to be for a technique to be applicable.
-
-% Our results show that program synthesis is well suited to retrieve information chunks from build logs when the targeted information is always presented in a structurally identical way and the user requires a high confidence in the precision and recall of the output.
-% Using text similarity is advisable when precision is valued higher than recall and we recommend keyword search when recall is valued higher than precision.
-% We present more detailed results, background and our study design in \todo{ref (preprint or so?) of full journal paper (or thesis?)}.
-
-\section{Related Data Sets}
-\label{sec:related-data-sets}
-This section presents existing data sets of CI build logs and how
-\emph{LogChunks} is different from them.
-
-\subsection{TravisTorrent}
-\emph{TravisTorrent}~\cite{beller2017travistorrent} collects a broad
-range of metadata about builds on Travis CI\@.  It combines data
-accessible through the public Travis CI and GitHub APIs and through
-GHTorrent~\cite{gousios2013ghtorrent}. Similar to LogChunks, among the
-metadata are the failing test cases.  However, TravisTorrent obtained
-these through a manually developed parser, which only supports
-specific Ruby test runners and Java Maven or JUnit logs. Anecdotally,
-many of the failing tests are at least incomplete and lack
-validation. By contrast, \emph{LogChunks} provides manually labeled
-data on the description of why builds failed for a much wider
-selection of build tools.
-
-\subsection{Travis CI Build Log Data Set}
-\todo{I would remove this as it is not really related because it does not contain labels?}
-Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
-They selected Maven repositories that included the Checkstyle plugin.
-Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
-
-\todo{What about the related data set I showed you and Georgios also mentioned? (Forgot exact name but don't have Internet so cannot look it up.)}
-
-\section{Data Schema}
-\label{sec:data-schema}
-
-This section presents the file structure and the data schema of \emph{LogChunks}.
-%We give a description of the manually labeled data.
-%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
-%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
-The build logs are organized in folders for each language and repository.
-Within each repository folder, folders for each build status contain the log files named with the corresponding build ID.
-% the logs are separated according to build status.
-%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
-%The build status folder contains the full logs in files named with the ID of the build that produced the log.
-
-The folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
-The data set provides an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
-Listing~\ref{lst:examples} presents the schema of these XML files.
-
-For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
-Figure \ref{tab:data-in-example} presents the data within each example.
-% Each \texttt{Example} consists of:
-% \begin{itemize}
-% 	\item \texttt{Log:} the relative path to the input build log.
-% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
-% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
-% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
-% 				The category is relative to the other examples for the same repository.
-% \end{itemize}
-Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
-
-\lstset{
-  language=XML,
-  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-	frame=single,
-	escapeinside=**
-}
-\begin{figure}[]
-	\centering
-\begin{lstlisting}[breaklines=true]
-<Examples>
-  <Example>
-    <Log>C/php@php-src/failed/529279089.log</Log>
-      <Keywords>ERROR, FAIL, DIFF</Keywords>
-      <Category>0</Category>
-      <Chunk>001+ ** ERROR: process timed out **
-001- OK.
-========DONE========
-FAIL Bug #60120 (proc_open hangs)</Chunk>
-  </Example>
-  ...
-</Examples>
-\end{lstlisting}
-	\caption{Example XML file from \emph{LogChunks}}
-	\label{lst:examples}
-\end{figure}
-
-\begin{figure*}[htbp]
-\centering
-\begin{tabularx}{\textwidth}{@{}lXlX@{}}
-  \toprule
-  & Description & Unit & Example \\
-  \midrule
-  Log & relative path to the input build log & Path to Log File & Haskell/koalaman@shellcheck/failed/501296412.log \\
-  Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
-    Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
-  Keywords & keywords the authors would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
-  Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
-  \bottomrule
-\end{tabularx}
-\caption{Data within an example in \emph{LogChunks}}
-\label{tab:data-in-example}
-\end{figure*}
-
-\paragraph{Chunk That Describes Why The Build Failed}
-The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
-This can, for example, be the failing test case or a compiler error and is one continuous substring of the build log.
-When the reason \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes the description \emph{that} the build failed.
-%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
-%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
-%In these instances the \texttt{Chunk} contains the lines describing that the build failed.
-
-\paragraph{Keywords}
-The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
-We selected keywords the authors would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.
-Some keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{=DIFF=}'' or ``\texttt{ERR!}''.
-
-\paragraph{Category}
-For each repository, we assign \emph{structural categories} to the chunks.
-The structural category compares how \texttt{Chunk}s are represented within the build log.
-Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'' or surrounding special characters.
-Two chunks fall into the same structural categories if they are surrounded by the same markings.
-Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
-In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
-%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
-For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
-
-\begin{figure}[tbp]
-	\centering
-\begin{lstlisting}[breaklines=true]
-========DIFF========
-*{\color{cyan}-=-=-=-=-=-}*
-005+     Parameter #1 [<optional> $flags]
-005-     Parameter #1 [<optional> $ar_flags]
-========DONE========
-FAIL Bug#71412 ArrayIterator reflection 
-*{\color{cyan}-=-=-=-=-=-}*
-TEST 9895/13942 [2/2 test workers running]
-\end{lstlisting}
-	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
-	\label{lst:same-category}
-\end{figure}
-
-\begin{figure}[tbp]
-	\centering
-\begin{lstlisting}[breaklines=true]
-[0K$ ./sapi/cli/php run-tests.php -P ...
-*{\color{cyan}-=-=-=-=-=-}*
-Illegal switch 'j' specified!
-*{\color{cyan}-=-=-=-=-=-}*
-Synopsis:
-\end{lstlisting}
-	\caption{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}}
-  %, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
-	\label{lst:different-category}
-\end{figure}
-
-\section{Data Collection Process}
+\section{Creating LogChunks}
 This section presents how we gathered the logs for \emph{LogChunks} and our manual labeling process.
@@
 \subsection{Log Collection}
-We describe how we select the repositories, builds and logs for \emph{LogChunks}.
-To collect the build logs we built the \texttt{GHTorrentParser} and \texttt{TravisRequester} using Ruby.
+In this section, we describe how we created \emph{LogChunks} along the
+overview in \Cref{fig:lc-overview}. All steps are automatized as Ruby
+scripts\todo{link to repo?} and highly configurable.
 
 \paragraph{Repository Sampling}
-%First, we determine a set of repositories to query logs from.
-Our \texttt{GHTorrentParser} queries the \emph{GHTorrent}~\cite{gousios2013ghtorrent} data set for the most popular languages on GitHub.
-It then retrieves the most popular repositories for a given language.
-We define \emph{Popularity} as the number of watches.
-The \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, then checks whether a given repository uses Travis CI\@.
+We first query \emph{GHTorrent}~\cite{gousios2013ghtorrent} for the
+most popular languages on GitHub, and subsequently, the most popular
+(by number of watchers) repositories for a given language. We measure
+popularity by the number of watchers.  We only select repositories
+which use Travis CI\@.
 
-For \emph{LogChunks} we queried GHTorrent on 01/04/2018 for the three most popular repositories of each of the 30 most popular languages.
-Among the resulting repositories are, for example, \texttt{git/git}, \texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.
+For \emph{LogChunks}, we queried GHTorrent on 2018-04-01 for the three
+most popular repositories of each of the 30 most popular languages.
+Among the resulting repositories are, for example, \texttt{git/git},
+\texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.
+
+\todo{we need some reasoning for most popular, our proxy for
+  popularity (watchers) -- as is often done, reference --, and ideally, how much
+  data we are including}
 
 \paragraph{Build Sampling}
-The \texttt{TravisRequester} obtains the newest builds for a given repository.
-We use a stratified sampling approach and save the obtained builds in buckets according to their status.
+We use a sampling approach using the build status as our stratum.
+\todo{What are our strata?}
 %We encountered the following statuses during our data collection: created, started, cancelled, passed, errored and failed.
-The user of \texttt{TravisRequester} configures how many builds should be checked and how many builds per status should be saved.
 
@@
 \paragraph{Log Sampling}
-For each build, the \texttt{TravisRequester} then selects a log to download.
-Travis CI links logs to \emph{jobs}.
-A build can consist of multiple jobs, e.g.\ executing tests in different environments.
-%A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
-\texttt{TravisRequester} queries each build for the first job which has the same state and obtains the corresponding build log.
+Travis CI build comprise of a number of jobs that actualize a build
+process in a defined environment. As such, the outcome from different
+jobs might be different. For each build in LogChunks, we download the
+first job which has the same state as the overall build.
 
@@
 
+%\section{Applications}
+%This section possible use cases for \emph{LogChunks} and outlines how we previously applied it to compare different build log analysis techniques.
+\section{Potential Use Cases}
+
+%\subsection{Potential Use Cases}
+\emph{LogChunks} can be the basis for a range of further studies:
+
+\paragraph{Benchmarking Build Log Analysis Techniques}
+LogChunks is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
+\emph{LogChunks} can be a benchmark to evaluate other build log analysis techniques.
+For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.
+
+\paragraph{Support Build Log Classification Algorithms}
+Various researchers are examining why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
+They write custom parsers and classifiers to categorize builds according to why a build failed.
+The manually labeled chunk can help researchers locate the source for their classification algorithms and cross-validate their data.
+
+\paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
+\emph{LogChunks} provides keywords that the authors would use to search for the chunk describing why the build failed.
+Analyzing these can help us understand how users process build logs and which keywords a tool should use to mark an error description.
+We can also recommend users which search keywords they should use to find why the build failed.
+\todo{Isn't this pretty simple and not really worth a research paper? If it is too trivial, we should probably not mention it here.}
+
+\paragraph{Studying Conversations about Build Failures}
+Researchers are looking into conversations of developers surrounding CI builds and pull requests \todo{citation pending}
+%TODO Caro: nathan cassee (with Alexander Sebrenik) did this in his master thesis (paper got accepted, will get link when preprint is finished), did not find others yet that do this}.
+The chunks describing why a build failed, or the results of build log analysis techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
+\todo{Similar comment: This is a bit too narrow.
+But perhaps we can merge the two in one and say researchers doing research around the topic of build logs, such as ...
+user studies on keyword retrievala and conversations?}
+
+\todo{ Andy also proposed: automatic creation of issue reports on GitHub with extracted info: sounds okay, but build failures are to be fixed faster than a GH issue I would say}
+\todo{I think this proposal is again too narrow: but what about further automatic on-ward processing? Even if small, perhaps reinforcement learning might be feasible ...}
+
+% \subsection{Chunk Retrieval Evaluation}
+% We created \emph{LogChunks} to evaluate and compare different chunk retrieval techniques for build logs.
+% The first technique is based on synthesizing programs from examples using the Microsoft PROSE library.
+% A user provides a small number of examples to describe which text part the program should extract.
+% PROSE then synthesizes a program of regular expressions that is consistent with these examples.
+% We compared this extraction technique to a text similarity approach, which selects the lines of a build log which are most similar to the ones in the given user examples.
+% Lastly, we investigated searching for keywords that are associated with the given user examples.
+
+% The log chunks in this data set provided the examples for these techniques, the keywords were used to configure the keyword search.
+% The structural categories enabled us to measure how structurally similar the examples have to be for a technique to be applicable.
+
+% Our results show that program synthesis is well suited to retrieve information chunks from build logs when the targeted information is always presented in a structurally identical way and the user requires a high confidence in the precision and recall of the output.
+% Using text similarity is advisable when precision is valued higher than recall and we recommend keyword search when recall is valued higher than precision.
+% We present more detailed results, background and our study design in \todo{ref (preprint or so?) of full journal paper (or thesis?)}.
+
+\section{Related Data Sets}
+\label{sec:related-data-sets}
+This section presents existing data sets of CI build logs and how
+\emph{LogChunks} differs from them.
+
+\subsection{TravisTorrent}
+\emph{TravisTorrent}~\cite{beller2017travistorrent} collects a broad
+range of metadata about Travis CI builds\@.  It combines data
+accessible through the public Travis CI and GitHub APIs and through
+GHTorrent~\cite{gousios2013ghtorrent}. Similar to LogChunks, among the
+metadata are the failing test cases. However, TravisTorrent obtained
+these through a manually developed parser, which only supports
+specific Ruby test runners and Java Maven or JUnit logs. Anecdotally,
+many of the failing tests are at least incomplete and lack
+validation. By contrast, \emph{LogChunks} provides manually labeled
+and two-fold cross-validated data of why builds failed, not only for
+failing tests like TravisTorrent, but for all possible build-failing
+errors.
+
+\subsection{Travis CI Build Log Data Set}
+\todo{I would remove this as it is not really related because it does not contain labels?}
+Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
+They selected Maven repositories that included the Checkstyle plugin.
+Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
+
+\todo{What about the related data set I showed you and Georgios also mentioned? (Forgot exact name but don't have Internet so cannot look it up.)}
+
+\section{Data Schema}
+\label{sec:data-schema}
+
+This section presents the internal structure and data schema of
+\emph{LogChunks}. In principle, LogChunks comprises automatically
+retrieved and manually cross-validated data.
+
+\subsection{Automatic data.}
+%We give a description of the manually labeled data.
+%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
+%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
+LogChunks comprises information on \todo{x} build logs, which are organized in folders for each language and repository.
+Within a repository folder, there are folders for each of the general build status ('successful', 'failed', ...), which contain the entire unaltered log files.
+% the logs are separated according to build status.
+%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
+%The build status folder contains the full logs in files named with the ID of the build that produced the log.
+For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
+Figure \ref{tab:data-in-example} presents the data within each example.
+
+The top-level folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
+The data set contains an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
+Listing~\ref{lst:examples} presents the schema of these XML files.
+
+% Each \texttt{Example} consists of:
+% \begin{itemize}
+% 	\item \texttt{Log:} the relative path to the input build log.
+% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
+% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
+% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
+% 				The category is relative to the other examples for the same repository.
+% \end{itemize}
+Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
+
+\lstset{
+  language=XML,
+  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
+  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
+	frame=single,
+	escapeinside=**
+}
+\begin{figure}[]
+	\centering
+\begin{lstlisting}[breaklines=true]
+<Examples>
+  <Example>
+    <Log>C/php@php-src/failed/529279089.log</Log>
+      <Keywords>ERROR, FAIL, DIFF</Keywords>
+      <Category>0</Category>
+      <Chunk>001+ ** ERROR: process timed out **
+001- OK.
+========DONE========
+FAIL Bug #60120 (proc_open hangs)</Chunk>
+  </Example>
+  ...
+</Examples>
+\end{lstlisting}
+	\caption{Example XML file from \emph{LogChunks}}
+	\label{lst:examples}
+\end{figure}
+
+\begin{figure*}[htbp]
+\centering
+\begin{tabularx}{\textwidth}{@{}lXlX@{}}
+  \toprule
+  & Description & Unit & Example \\
+  \midrule
+  Log & relative path to the input build log & Path to Log File & Haskell/koalaman@shellcheck/failed/501296412.log \\
+  Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
+    Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
+  Keywords & keywords the authors would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
+  Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
+  \bottomrule
+\end{tabularx}
+\caption{Data within an example in \emph{LogChunks}}
+\label{tab:data-in-example}
+\end{figure*}
+
+\paragraph{Chunk That Describes Why The Build Failed}
+The \texttt{Chunk} is the substring of the build log that describes why the build failed.
+This can, for example, be the failing test case or a compiler error and is one continuous substring of the build log.
+In cases where the reason \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes only the fact \emph{that} the build failed.
+%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
+%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
+%In these instances the \texttt{Chunk} contains the lines describing that the build failed.
+
+\paragraph{Keywords}
+The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
+We selected keywords the authors would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.
+Some keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{=DIFF=}'' or ``\texttt{ERR!}''.
+
+\paragraph{Category}
+For each repository, we assign \emph{structural categories} to the chunks.
+The structural category compares how \texttt{Chunk}s are represented within the build log.
+Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'' or surrounding special characters.
+Two chunks fall into the same structural categories if they are surrounded by the same markings.
+Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
+In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
+%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
+For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
+
+\begin{figure}[tbp]
+	\centering
+\begin{lstlisting}[breaklines=true]
+========DIFF========
+*{\color{cyan}-=-=-=-=-=-}*
+005+     Parameter #1 [<optional> $flags]
+005-     Parameter #1 [<optional> $ar_flags]
+========DONE========
+FAIL Bug#71412 ArrayIterator reflection 
+*{\color{cyan}-=-=-=-=-=-}*
+TEST 9895/13942 [2/2 test workers running]
+\end{lstlisting}
+	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\label{lst:same-category}
+\end{figure}
+
+\begin{figure}[tbp]
+	\centering
+\begin{lstlisting}[breaklines=true]
+[0K$ ./sapi/cli/php run-tests.php -P ...
+*{\color{cyan}-=-=-=-=-=-}*
+Illegal switch 'j' specified!
+*{\color{cyan}-=-=-=-=-=-}*
+Synopsis:
+\end{lstlisting}
+	\caption{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}}
+  %, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\label{lst:different-category}
+\end{figure}
+
 \section{Summary}
@@
 \paragraph{Include More Repositories and Logs}
-\emph{LogChunks} encompasses a wide range of repositories from various main development languages, though only 10 logs from each repository.
+\emph{LogChunks} encompasses a range of repositories from various main development languages, though only 10 logs from each repository.
 %This stems from the high effort necessary for the manual data labeling process.

### 2020-01-15 msr-paper/paper.tex
Done until l480

@@
 
-In our opinion, the width and depth of the \emph{LogChunks} data set
-make it an ideal benchmark for automated build log analysis
+The width and depth of the \emph{LogChunks} data set are intended to
+make it the default benchmark for automated build log analysis
 techniques.
@@
 \todo{mention most popular repositories very briefly somewhere?}
+\todo{Match subsection titles with descriptions in picture}
 \todo{80x -> 80}
@@
 \section{Creating LogChunks}
-This section presents how we gathered the logs for \emph{LogChunks} and our manual labeling process.
+This section presents how we gathered the logs and our manual labeling process.
 \label{sec:data-collection}
@@
 
-To sample the builds for \emph{LogChunks} we let \texttt{TravisRequester} check up to 1000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
+To sample the builds for \emph{LogChunks} we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
 %A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
@@
 \paragraph{Log Sampling}
-Travis CI build comprise of a number of jobs that actualize a build
-process in a defined environment. As such, the outcome from different
+Travis CI builds comprise a number of jobs that actualize a build
+process in different environments. Hence, the outcome from different
 jobs might be different. For each build in LogChunks, we download the
@@
 
-We inspected the collected build logs and discarded logs from three repositories.
-One had only one failed build, two others had empty build logs on Travis CI\@.
-In total we collected 797 logs from 80 repositories spanning 29 languages.
+\todo{what does it mean to only have one failed build? wouldn't you
+  exclude the entire repository then?}  We inspected the collected
+build logs and discarded logs from three repositories.  One had only
+one failed build, two others had empty build logs on Travis CI\@.  In
+total, we collected 797 logs from 80 repositories spanning 29
+languages.
 
@@
 \label{sec:labeling-process}
-After collecting a wide range of Travis CI build logs we manually labeled which text chunk describes why the build failed.
-Following that, we assigned search keywords and structural categories to each log chunk.
+After collecting build logs, the first author manually labeled which
+text chunk describes why the build failed.  Following that, she
+assigned search keywords and structural categories to each log chunk.
 
@@
 
-\section{Data Set Validation}
+\subsection{Validation}
 \label{sec:validation}
-% We validate our collected data points in two different ways.
-% A different labeler performed a second pass of labeling the build failure reason, keywords and structural categories on a subset of the data.
-% In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set.
-% We asked them whether our retrieval of the log part describing the reason the build failed was correct.
-%This sections describes these two validation studies.
-Following we present the two studies we conduct to validate the labeled data in \emph{LogChunks}.
+\todo{how is the validation embedded in the data set? is there a special flag for validated entries?}
+\todo{how many entries are validated?}
+
+We validate our collected data points via an initial inter-rater
+reliability study, and a cross-validation with developers.
 
 \subsection{Inter-Rater Reliability Study}
-To evaluate the validity of our labeled data we perform a second labeling of a sample of the data in \emph{LogChunks}.
+\todo{I am thinking to cut this ... it does not give much, results are a bit underwhelming (why not calculate kappa?), and the meat lies in the developer study anyway}
 
 \paragraph{Method}
-We followed the same labeling process as described in Section~\ref{sec:labeling-process}.
-For the build failure reason and the keywords, we presented 30 randomly sampled build logs from distinct repositories in \emph{LogChunks}.
+The second author of this paper performed the same labeling process as described in \Cref{sec:labeling-process}, on 30 randomly sampled build logs from distinct repostories.
+He extracted the build failure reason and the keywords.
 The structural categories are relative to other logs from the same repository.
@@
 \paragraph{Results}
+\todo{Can we shorten this?}
 For the substring describing why the build failed, the two labelers exactly agreed in six cases.
@@
 Regarding the keywords, the two labelers completely agreed in nine cases and completely disagreed in two cases.
-In nineteen cases there was overlap in the keywords of the two labelers.%, in two the first labeler selected additional keywords compared to the second, while the second labeler proposed additional keywords in seven cases.
+In nineteen cases was there overlap in the keywords of the two labelers.
 When classifying the chunks into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.
@@
 Our main learning from this study is that it is important and difficult to adequately communicate all decisions and assumptions on how data is labeled.
-We reviewed the misunderstandings and incorporated more thorough descriptions in Section~\ref{sec:data-schema}.
+We reviewed the misunderstandings and incorporated more thorough descriptions in \cref{sec:data-schema} to guide the design for our external validation.
 
-\subsection{Developer Survey}
+\subsection{Developer Validation}
 %For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
@@
 %If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.
-We sent out mails to the original developers whose commits triggered the builds represented in \emph{LogChunks} and asked them whether the log chunk we labeled actually describes why the build failed.
-This section describes our survey and discusses our results.
+
+In our second validation, we sent out emails to the original
+developers whose commits triggered the builds represented in
+\emph{LogChunks} and asked them whether the log chunk we labeled
+actually describes why the build failed.  This section describes our
+survey and discusses our results.
 
 \paragraph{Method}
-Using the Travis API, we collect the commit information for each build represented in \emph{LogChunks}.
-We grouped all commits triggered by one developer and sent out an mail to them.%, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
+Using the Travis API, we collected the commit information for each build represented in \emph{LogChunks}.
+We grouped all commits triggered by one developer and sent out an email to them.%, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
 %Figure~\ref{fig:dev-mail} shows one of the mails sent out.
-The mail included links to the corresponding commits, build overview and log file.
-We asked the developers to fill out a short survey in case our extraction was not correct.
+It included links to the corresponding commits, build overviewm and log file.
+We asked the developers to fill out a short form in case our extraction was not correct.
 %Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
-In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why we were wrong.
-As some of the chunks we labeled are many lines long, we trimmed all down to 10 lines to keep the mail readable.
+In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why our original extraction was incorrect.
 
 \paragraph{Results}
-In total we sent out mails to 246 developers.%, asking about 3.2 build logs per mail on average.
-32 of these mails could not be delivered, e.g.\ because they were addressed to \emph{noreply} addresses.
-%These 32 mails related to 68 of the build logs.
-We received answers from 61 developers, corresponding with 144 build logs.
-%Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.
+In total we sent out mails to 246 developers. 32 of these mails could
+not be delivered. We received answers from 61 developers, corresponding to
+144 build logs (response rate: 24.8\%).
 
-Of the 144 answers, 132 said our extraction was correct.
+Of the 144 answers, 132 indicated our extraction was correct.
 %26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
@@
 This is because we had to trim long chunks to keep the mails readable.
-After adjusting these answers, 12 answers stated that our labeled log chunk was not correct.
+
+After adjusting for these answers, 12 answers remained that stated that our labeled log chunk was not correct.
 
 \paragraph{Discussion}
-This study highly strengthens the trust in the validity of the labeled log chunks.
-The study received answers about 18\% of the logs from \emph{LogChunks}.
-After manual correction, 91\% of the received answers said our labeled chunks were accurate.
+We believe that our developer survey highly strengthens the trust in
+the validity of the labeled log chunks.  The study received answers
+for about 18\% of the data in \emph{LogChunks}.  After manual
+correction, 91\% of the received answers said our labeled chunks were
+accurate.  One possible threat regarding the high number of correct
+answers is that, since we show the error message we extracted, it
+might be operationally easier for developers to validate it, rather
+than search for it in a long log file. To alleviate this problem, we
+made it as easy to confirm as to reject an extracted log chunk. We
+only ask for more details (the correct log chunk) in a second step.
 
-One of our extractions only showed a warning and the developer proposed to also include the line stating that warnings are treated as errors.
-In others that were identified as incorrect, we labeled the error message of an error that was later ignored.
+One of our 12 incorrect extractions only showed a warning and the
+developer proposed to also include the line stating that warnings are
+treated as errors. In others, we labeled the error message of an error
+that was later ignored.
+
+\section{Data Schema}
+\label{sec:data-schema}
+
+This section presents the internal structure and data schema of
+\emph{LogChunks}. In principle, LogChunks comprises automatically
+retrieved and manually cross-validated data.
+
+%We give a description of the manually labeled data.
+%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
+%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
+LogChunks comprises information on \todo{x} build logs, which are organized in folders for each language and repository.
+Within a repository folder, there are folders for each of the general build status ('successful', 'failed', ...), which contain the entire unaltered log files.
+% the logs are separated according to build status.
+%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
+%The build status folder contains the full logs in files named with the ID of the build that produced the log.
+For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
+\Cref{tab:data-in-example} presents the data LogChunks contaians for an examplatory build from koalaman@shellcheck each example.
+
+The top-level folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
+The data set contains an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
+Listing~\ref{lst:examples} presents the schema of these XML files.
+
+% Each \texttt{Example} consists of:
+% \begin{itemize}
+% 	\item \texttt{Log:} the relative path to the input build log.
+% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
+% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
+% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
+% 				The category is relative to the other examples for the same repository.
+% \end{itemize}
+Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
+
+\lstset{
+  language=XML,
+  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
+  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
+	frame=single,
+	escapeinside=**
+}
+\begin{figure}[]
+	\centering
+\begin{lstlisting}[breaklines=true]
+<Examples>
+  <Example>
+    <Log>C/php@php-src/failed/529279089.log</Log>
+      <Keywords>ERROR, FAIL, DIFF</Keywords>
+      <Category>0</Category>
+      <Chunk>001+ ** ERROR: process timed out **
+001- OK.
+========DONE========
+FAIL Bug #60120 (proc_open hangs)</Chunk>
+  </Example>
+  ...
+</Examples>
+\end{lstlisting}
+	\caption{Example XML file from \emph{LogChunks} \todo{Isn't this exactly the same as Figure 2? Only keep one?}}
+	\label{lst:examples}
+\end{figure}
+
+\begin{figure*}[htbp]
+\centering
+\begin{tabularx}{\textwidth}{@{}lXlX@{}}
+  \toprule
+  Data & Description & Unit & Example \\
+  \midrule
+  Log & Relative path to the input build log & Path & \tt{Haskell/koalaman@shellcheck\newline/failed/501296412.log} \\
+  Chunk & Log chunk that describes why the build failed & String & \tt{shellcheck.hs:442:19: error:
+    Variable not in scope: doesPathExist :: [Char] -> IO Bool} \todo{is this strictly one?} \\ 
+  Keywords & Keywords the authors would use to search \todo{only search or also actually FIND it?} for the log chunk & List of Strings & \tt{Failures, FAILURE, FAILED} \\ 
+  Category & Categorization of the structural representation of the log chunk within the build log \todo{can you explain what this means?} & Integer & \tt{0}\\
+  \todo{what about validation info?}\\
+  \bottomrule
+\end{tabularx}
+\caption{Examplary, complete data excerpt from \emph{LogChunks} for a failed build in \tt{koalaman@shellcheck}.}
+\label{tab:data-in-example}
+\end{figure*}
+
+\paragraph{Chunk That Describes Why The Build Failed}
+The \texttt{Chunk} is the substring of the build log that describes why the build failed.
+This can, for example, be the failing test case or a compiler error and is one continuous substring of the build log.
+In cases where the reason \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes only the fact \emph{that} the build failed.
+%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
+%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
+%In these instances the \texttt{Chunk} contains the lines describing that the build failed.
+
+\paragraph{Keywords}
+The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
+We selected keywords the authors would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.
+Some keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{=DIFF=}'' or ``\texttt{ERR!}''.
+
+\paragraph{Category}
+For each repository, we assign \emph{structural categories} to the chunks.
+The structural category compares how \texttt{Chunk}s are represented within the build log.
+Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'' or surrounding special characters.
+Two chunks fall into the same structural categories if they are surrounded by the same markings.
+Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
+In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
+%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
+For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
+
+\begin{figure}[tbp]
+	\centering
+\begin{lstlisting}[breaklines=true]
+========DIFF========
+*{\color{cyan}-=-=-=-=-=-}*
+005+     Parameter #1 [<optional> $flags]
+005-     Parameter #1 [<optional> $ar_flags]
+========DONE========
+FAIL Bug#71412 ArrayIterator reflection 
+*{\color{cyan}-=-=-=-=-=-}*
+TEST 9895/13942 [2/2 test workers running]
+\end{lstlisting}
+	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\label{lst:same-category}
+\end{figure}
+
+\begin{figure}[tbp]
+	\centering
+\begin{lstlisting}[breaklines=true]
+[0K$ ./sapi/cli/php run-tests.php -P ...
+*{\color{cyan}-=-=-=-=-=-}*
+Illegal switch 'j' specified!
+*{\color{cyan}-=-=-=-=-=-}*
+Synopsis:
+\end{lstlisting}
+	\caption{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}}
+  %, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\label{lst:different-category}
+\end{figure}
 
@@
 
-\section{Data Schema}
-\label{sec:data-schema}
-
-This section presents the internal structure and data schema of
-\emph{LogChunks}. In principle, LogChunks comprises automatically
-retrieved and manually cross-validated data.
-
-\subsection{Automatic data.}
-%We give a description of the manually labeled data.
-%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
-%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
-LogChunks comprises information on \todo{x} build logs, which are organized in folders for each language and repository.
-Within a repository folder, there are folders for each of the general build status ('successful', 'failed', ...), which contain the entire unaltered log files.
-% the logs are separated according to build status.
-%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
-%The build status folder contains the full logs in files named with the ID of the build that produced the log.
-For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
-Figure \ref{tab:data-in-example} presents the data within each example.
-
-The top-level folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
-The data set contains an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
-Listing~\ref{lst:examples} presents the schema of these XML files.
-
-% Each \texttt{Example} consists of:
-% \begin{itemize}
-% 	\item \texttt{Log:} the relative path to the input build log.
-% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
-% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
-% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
-% 				The category is relative to the other examples for the same repository.
-% \end{itemize}
-Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
-
-\lstset{
-  language=XML,
-  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-	frame=single,
-	escapeinside=**
-}
-\begin{figure}[]
-	\centering
-\begin{lstlisting}[breaklines=true]
-<Examples>
-  <Example>
-    <Log>C/php@php-src/failed/529279089.log</Log>
-      <Keywords>ERROR, FAIL, DIFF</Keywords>
-      <Category>0</Category>
-      <Chunk>001+ ** ERROR: process timed out **
-001- OK.
-========DONE========
-FAIL Bug #60120 (proc_open hangs)</Chunk>
-  </Example>
-  ...
-</Examples>
-\end{lstlisting}
-	\caption{Example XML file from \emph{LogChunks}}
-	\label{lst:examples}
-\end{figure}
-
-\begin{figure*}[htbp]
-\centering
-\begin{tabularx}{\textwidth}{@{}lXlX@{}}
-  \toprule
-  & Description & Unit & Example \\
-  \midrule
-  Log & relative path to the input build log & Path to Log File & Haskell/koalaman@shellcheck/failed/501296412.log \\
-  Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
-    Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
-  Keywords & keywords the authors would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
-  Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
-  \bottomrule
-\end{tabularx}
-\caption{Data within an example in \emph{LogChunks}}
-\label{tab:data-in-example}
-\end{figure*}
-
-\paragraph{Chunk That Describes Why The Build Failed}
-The \texttt{Chunk} is the substring of the build log that describes why the build failed.
-This can, for example, be the failing test case or a compiler error and is one continuous substring of the build log.
-In cases where the reason \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes only the fact \emph{that} the build failed.
-%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
-%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
-%In these instances the \texttt{Chunk} contains the lines describing that the build failed.
-
-\paragraph{Keywords}
-The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
-We selected keywords the authors would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.
-Some keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{=DIFF=}'' or ``\texttt{ERR!}''.
-
-\paragraph{Category}
-For each repository, we assign \emph{structural categories} to the chunks.
-The structural category compares how \texttt{Chunk}s are represented within the build log.
-Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'' or surrounding special characters.
-Two chunks fall into the same structural categories if they are surrounded by the same markings.
-Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
-In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
-%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
-For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
-
-\begin{figure}[tbp]
-	\centering
-\begin{lstlisting}[breaklines=true]
-========DIFF========
-*{\color{cyan}-=-=-=-=-=-}*
-005+     Parameter #1 [<optional> $flags]
-005-     Parameter #1 [<optional> $ar_flags]
-========DONE========
-FAIL Bug#71412 ArrayIterator reflection 
-*{\color{cyan}-=-=-=-=-=-}*
-TEST 9895/13942 [2/2 test workers running]
-\end{lstlisting}
-	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
-	\label{lst:same-category}
-\end{figure}
-
-\begin{figure}[tbp]
-	\centering
-\begin{lstlisting}[breaklines=true]
-[0K$ ./sapi/cli/php run-tests.php -P ...
-*{\color{cyan}-=-=-=-=-=-}*
-Illegal switch 'j' specified!
-*{\color{cyan}-=-=-=-=-=-}*
-Synopsis:
-\end{lstlisting}
-	\caption{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}}
-  %, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
-	\label{lst:different-category}
-\end{figure}
-
 \section{Summary}

### 2020-01-16 msr-paper/paper.tex
Finish review

@@
 \todo{how is the validation embedded in the data set? is there a special flag for validated entries?}
-\todo{how many entries are validated?}
 
-We validate our collected data points via an initial inter-rater
-reliability study, and a cross-validation with developers.
+We validated our collected data points in an iterative fashion. First,
+we performed an initial inter-rater reliability study with a
+co-author, which informed the design of a cross-validation study in
+which we contacted over 200 developers.  Our main learning from the
+initial internal study was that it is important and difficult to
+adequately communicate all decisions and assumptions on how data is
+labeled.
 
-\subsection{Inter-Rater Reliability Study}
-\todo{I am thinking to cut this ... it does not give much, results are a bit underwhelming (why not calculate kappa?), and the meat lies in the developer study anyway}
-
-\paragraph{Method}
-The second author of this paper performed the same labeling process as described in \Cref{sec:labeling-process}, on 30 randomly sampled build logs from distinct repostories.
-He extracted the build failure reason and the keywords.
-The structural categories are relative to other logs from the same repository.
-Therefore, we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.
-
-\paragraph{Results}
-\todo{Can we shorten this?}
-For the substring describing why the build failed, the two labelers exactly agreed in six cases.
-In 15 cases the second labeler selected more lines, in five their selections overlapped and in four they completely disagreed.
-Regarding the keywords, the two labelers completely agreed in nine cases and completely disagreed in two cases.
-In nineteen cases was there overlap in the keywords of the two labelers.
-When classifying the chunks into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.
-
-% TODO Moritz: this is to answer questions 'why did you not do this standard thing': maybe there is a better position and/or way of saying this?
-We found that calculating the standard measure for inter-rater agreement, Cohen's Kappa, is not applicable here.
-For the log chunk it cannot represent the impact of overlapping selections of the labelers and for the keywords and structural categories the values the labelers could assign were not fixed.
-
-\paragraph{Discussion}
-The results of this validation study show that there is overlap in the data from both labelers, however also a high variation.
-We believe that the main cause for this is that our explanations to the second labeler were not extensive enough.
-There were implicit, inconsistent assumptions both labelers created during their work.
-% In the following we describe these assumptions from both labelers for each data point and the implications on our description of the data classes.
-
-% For the first data class, the reason the build failed, it was ambiguous whether the labeled substring should contain the information \emph{that} the build failed.
-% This concerns statements like ``\texttt{The build exited with 1}''.
-% One labeler included such statements, while the other one only focussed on the log parts describing \emph{why} the build failed, e.g.\ the name of the failing test case.
-
-% While labeling the keywords a developer would use to search for the log part describing why the build failed, the one labeler allowed arbitrary strings appearing around the presented log part.
-% In contrast to that, the other labeler focussed on actual \emph{words}, delimited by spaces or special characters.
-% One labeler ignored capitalization, while the other one selected case-sensitive keywords.
-% A third difference was that the first labeler was presented with all substrings from a repository, yielding more general keywords than the second labeler.
-
-% For the structural categories this validation study showed a high overlap.
-% In our instructions to the second labeler we did not emphasize the \emph{structural} aspect enough.
-% They sorted into categories along \emph{why} the build failed, putting failing tests from different test runners into the same category even though the failing tests were presented differently in the log.
-%
-Our main learning from this study is that it is important and difficult to adequately communicate all decisions and assumptions on how data is labeled.
-We reviewed the misunderstandings and incorporated more thorough descriptions in \cref{sec:data-schema} to guide the design for our external validation.
-
-\subsection{Developer Validation}
 %For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
@@
 for about 18\% of the data in \emph{LogChunks}.  After manual
-correction, 91\% of the received answers said our labeled chunks were
-accurate.  One possible threat regarding the high number of correct
-answers is that, since we show the error message we extracted, it
-might be operationally easier for developers to validate it, rather
+correction, 91\% of the received answers indicated our labeled chunks
+were accurate.  One possible threat regarding the high number of
+correct answers is that, since we show the error message we extracted,
+it might be operationally easier for developers to validate it, rather
 than search for it in a long log file. To alleviate this problem, we
@@
 
-% Each \texttt{Example} consists of:
-% \begin{itemize}
-% 	\item \texttt{Log:} the relative path to the input build log.
-% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
-% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
-% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
-% 				The category is relative to the other examples for the same repository.
-% \end{itemize}
 Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
@@
 
+\todo{Including Figure 3 as a running example}
 \paragraph{Chunk That Describes Why The Build Failed}
 The \texttt{Chunk} is the substring of the build log that describes why the build failed.
-This can, for example, be the failing test case or a compiler error and is one continuous substring of the build log.
-In cases where the reason \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes only the fact \emph{that} the build failed.
+This can, for example, be the failing test case or a compiler error.
+In cases where the reason \emph{why} the build failed is contained in a log file external to the main build log, the \texttt{Chunk} includes only the fact \emph{that} the build failed.\todo{what does this look like?} In \Cref{tab:data-in-example}, this is a compile error where a variable did not exist in the current scope.
+
 %Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
@@
 \paragraph{Keywords}
-The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
-We selected keywords the authors would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.
+The \texttt{Keywords} contain a list of one to three \todo{find different word to explain it with} keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
+We selected keywords the authors would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.\todo{This needs more explanation!
+Why these keywords (as opposed to others?)}
 Some keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{=DIFF=}'' or ``\texttt{ERR!}''.
@@
 
-\section{Summary}
-\label{sec:conclusion}
-In this paper, we introduced the \emph{LogChunks} data set encompassing 797 build logs from 80 projects using Travis CI\@.
-For each log, we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.
+\section{Future Extensions to LogChunks}
 
-\emph{LogChunks} advances the research field of build log analysis by introducing a benchmark to rigorously examine research contributions~\cite{sim2003using}.
-
-Still, there are limitations to our data set, which we present in the following, together with improvements and extensions to \emph{LogChunks}.
+In this section, we describe LogChunk's current limitations and future improvements and extensions we are planning.
 
@@
 As researchers are investigating why CI builds fail, a useful extension is to annotate cause of the build failure for each log.
+\todo{Example: such as this is due to tests, compilation, ...?}
 
@@
 \emph{LogChunks} can be extended with further information targets such as descriptions of warnings, build infrastructure and more.
+\todo{a rich description of all info contained in a build log?}
 
@@
 Next, we propose to evaluate whether these keywords would also be used by developers to find the log chunk describing why a build failed.
+
+\section{Summary}
+\label{sec:conclusion}
+In this paper, we introduce\emph{LogChunks}, a cross-validated data
+set encompassing 797 build logs from 80 projects using Travis CI\@.
+For each log, we annotated the log chunk describing why the build
+failed and provide keywords a developer would use to search for the
+log chunk as well as a categorization of the log chunks according to
+their format within the log. \emph{LogChunks} advances the research
+field of build log analysis by introducing a benchmark to rigorously
+examine research contributions~\cite{sim2003using} and opening various
+research possibilites that previously required tedious manual
+classification.
 

### 2020-01-24 msr-paper/paper.tex
addressing moritz feedback

@@
 understanding of CI build failures. In this paper, we present
-\emph{LogChunks}, a collection of 797 fully annotated Travis CI build
+\emph{LogChunks}, a collection of 797 annotated Travis CI build
 logs from 80 GitHub repositories in 29 programming languages. For each
@@
 describing why the build failed. We externally validated the data set
-with the developer who caused the original build failure.
+with the developers who caused the original build failure.
 
@@
   is openly available on Zenodo: \todo{insert zenodo link}} a
-collection of 797 Travis CI build logs from 80 GitHub repositories in
+collection of 797 Travis CI build logs from 80 highly popular GitHub repositories in
 29 programming languages.  For each build log, we manually labeled
@@
 
-\todo{mention most popular repositories very briefly somewhere?}
-\todo{Match subsection titles with descriptions in picture}
-\todo{80x -> 80}
 \begin{figure}[tbp]
@@
 \paragraph{Repository Sampling}
-We first query \emph{GHTorrent}~\cite{gousios2013ghtorrent} for the
+We target mature GitHub repositories that are using Travis CI\@.
+To avoid personal and toy projects we select popular projects based
+on the number of users that starred a project~\cite{kalliamvakou2016depth}.
+We query \emph{GHTorrent}~\cite{gousios2013ghtorrent} for the
 most popular languages on GitHub, and subsequently, the most popular
-(by number of watchers) repositories for a given language. We measure
-popularity by the number of watchers.  We only select repositories
-which use Travis CI\@.
+repositories for a given language.
 
@@
 
-\todo{we need some reasoning for most popular, our proxy for
-  popularity (watchers) -- as is often done, reference --, and ideally, how much
-  data we are including}
-
 \paragraph{Build Sampling}
-We use a sampling approach using the build status as our stratum.
-\todo{What are our strata?}
-%We encountered the following statuses during our data collection: created, started, cancelled, passed, errored and failed.
-
 To sample the builds for \emph{LogChunks} we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
@@
 
-\todo{what does it mean to only have one failed build? wouldn't you
-  exclude the entire repository then?}  We inspected the collected
+We inspected the collected
 build logs and discarded logs from three repositories.  One had only
@@
 
-\subsection{Labeling Process}
+\subsection{Manual Labeling}
 \label{sec:labeling-process}
@@
 
-\paragraph{Keywords}
+\paragraph{Search Keywords}
 We presented the \texttt{Chunk} and ten lines above and below to the labeler.
@@
 
-\paragraph{Category}
+\paragraph{Structural Category}
 To label the \emph{structural categories} we presented the \texttt{Chunk} and the surrounding context to the labeler for all logs from a repository.
@@
 \label{sec:validation}
-\todo{how is the validation embedded in the data set? is there a special flag for validated entries?}
 
@@
 Using the Travis API, we collected the commit information for each build represented in \emph{LogChunks}.
-We grouped all commits triggered by one developer and sent out an email to them.%, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
+We grouped all commits triggered by one developer and sent out an email to them. %, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
 %Figure~\ref{fig:dev-mail} shows one of the mails sent out.
-It included links to the corresponding commits, build overviewm and log file.
+It included links to the corresponding commits, build overview and log file.
 We asked the developers to fill out a short form in case our extraction was not correct.
@@
 \emph{LogChunks}. In principle, LogChunks comprises automatically
-retrieved and manually cross-validated data.
+retrieved logs, as well as manually labeled and cross-validated data.
 
@@
 %Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
-LogChunks comprises information on \todo{x} build logs, which are organized in folders for each language and repository.
-Within a repository folder, there are folders for each of the general build status ('successful', 'failed', ...), which contain the entire unaltered log files.
+LogChunks comprises information on 797 build logs, which are organized in folders for each language and repository.
+Within a repository folder, there is a folder for the general build status ('failed'), which contains the entire log files.
 % the logs are separated according to build status.
@@
 For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
-\Cref{tab:data-in-example} presents the data LogChunks contaians for an examplatory build from koalaman@shellcheck each example.
+\Cref{tab:data-in-example} presents the data LogChunks contains for an exemplary build from \texttt{php@php-src}.
 
@@
 The data set contains an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
-Listing~\ref{lst:examples} presents the schema of these XML files.
+\Cref{tab:data-in-example} gives an overview of the data within these XML files.
 
 Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
+
+\begin{figure*}[htbp]
+\centering
+\begin{tabularx}{\textwidth}{@{}lXlX@{}}
+  \toprule
+  Data & Description & Unit & Example \\
+  \midrule
+  Log & Relative path to the input build log & Unique Path & \tt{C/php@php-src/failed/529279089.log} \\
+  Chunk & Log chunk that describes why the build failed & String & \tt{001+ ** ERROR: process timed out **\newline
+001- OK.\newline
+========DONE========\newline
+FAIL Bug \#60120 (proc\_open hangs)} \\ 
+  Keywords & Keywords the authors would use to search for and find the log chunk & List of Strings & \tt{ERROR, FAIL, DIFF} \\ 
+  Category & Categorization of the structural representation of the log chunk within the build log & Integer & \tt{0}\\
+  \todo{what about validation info?}\\
+  \bottomrule
+\end{tabularx}
+\caption{Exemplary, complete data excerpt from \emph{LogChunks} for a failed build in \tt{php@php-src}.}
+\label{tab:data-in-example}
+\end{figure*}
+
+\paragraph{Chunk That Describes Why The Build Failed}
+The \texttt{Chunk} is the substring of the build log that describes why the build failed.
+This can, for example, be the failing test case or a compiler error.
+In cases where the reason \emph{why} the build failed is contained in a log file external to the main build log, the \texttt{Chunk} includes only the fact \emph{that} the build failed, for example ``\texttt{The command "test/run !" exited with 1.}''.
+In \Cref{tab:data-in-example}, the \texttt{Chunk} describes a compile error where a variable did not exist in the current scope.
+
+%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
+%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
+%In these instances the \texttt{Chunk} contains the lines describing that the build failed.
+
+\paragraph{Search Keywords}
+The \texttt{Keywords} contain a list of one to three freely chosen search strings appearing within the \texttt{Chunk} or in the area around it in the build log.
+We selected keywords the authors would use to search for the log \texttt{Chunk}, as we found them repeatedly next to failure describing chunks while analyzing about 800 build logs manually.
+Some keywords from \emph{LogChunks} are  ``\texttt{Error}'', ``\texttt{=DIFF=}'', ``\texttt{ERR!}'', or the keywords shown in \Cref{tab:data-in-example}.
+
+\paragraph{Structural Category}
+For each repository, we assign \emph{structural categories} to the chunks.
+The structural category compares how \texttt{Chunk}s are represented within the build log.
+Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'' or surrounding special characters.
+Two chunks fall into the same structural categories if they are surrounded by the same markings.
+Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from \Cref{tab:data-in-example}.
+In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
+%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
+For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
 
@@
 }
-\begin{figure}[]
-	\centering
-\begin{lstlisting}[breaklines=true]
-<Examples>
-  <Example>
-    <Log>C/php@php-src/failed/529279089.log</Log>
-      <Keywords>ERROR, FAIL, DIFF</Keywords>
-      <Category>0</Category>
-      <Chunk>001+ ** ERROR: process timed out **
-001- OK.
-========DONE========
-FAIL Bug #60120 (proc_open hangs)</Chunk>
-  </Example>
-  ...
-</Examples>
-\end{lstlisting}
-	\caption{Example XML file from \emph{LogChunks} \todo{Isn't this exactly the same as Figure 2? Only keep one?}}
-	\label{lst:examples}
-\end{figure}
-
-\begin{figure*}[htbp]
-\centering
-\begin{tabularx}{\textwidth}{@{}lXlX@{}}
-  \toprule
-  Data & Description & Unit & Example \\
-  \midrule
-  Log & Relative path to the input build log & Path & \tt{Haskell/koalaman@shellcheck\newline/failed/501296412.log} \\
-  Chunk & Log chunk that describes why the build failed & String & \tt{shellcheck.hs:442:19: error:
-    Variable not in scope: doesPathExist :: [Char] -> IO Bool} \todo{is this strictly one?} \\ 
-  Keywords & Keywords the authors would use to search \todo{only search or also actually FIND it?} for the log chunk & List of Strings & \tt{Failures, FAILURE, FAILED} \\ 
-  Category & Categorization of the structural representation of the log chunk within the build log \todo{can you explain what this means?} & Integer & \tt{0}\\
-  \todo{what about validation info?}\\
-  \bottomrule
-\end{tabularx}
-\caption{Examplary, complete data excerpt from \emph{LogChunks} for a failed build in \tt{koalaman@shellcheck}.}
-\label{tab:data-in-example}
-\end{figure*}
-
-\todo{Including Figure 3 as a running example}
-\paragraph{Chunk That Describes Why The Build Failed}
-The \texttt{Chunk} is the substring of the build log that describes why the build failed.
-This can, for example, be the failing test case or a compiler error.
-In cases where the reason \emph{why} the build failed is contained in a log file external to the main build log, the \texttt{Chunk} includes only the fact \emph{that} the build failed.\todo{what does this look like?} In \Cref{tab:data-in-example}, this is a compile error where a variable did not exist in the current scope.
-
-%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
-%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
-%In these instances the \texttt{Chunk} contains the lines describing that the build failed.
-
-\paragraph{Keywords}
-The \texttt{Keywords} contain a list of one to three \todo{find different word to explain it with} keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
-We selected keywords the authors would use to search for the log \texttt{Chunk} after analyzing about 800 build logs manually.\todo{This needs more explanation!
-Why these keywords (as opposed to others?)}
-Some keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{=DIFF=}'' or ``\texttt{ERR!}''.
-
-\paragraph{Category}
-For each repository, we assign \emph{structural categories} to the chunks.
-The structural category compares how \texttt{Chunk}s are represented within the build log.
-Build tools highlight their error messages with markings, e.g.\ starting each line with ``\texttt{ERROR}'' or surrounding special characters.
-Two chunks fall into the same structural categories if they are surrounded by the same markings.
-Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from Listing \ref{lst:examples}.
-In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
-%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
-For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
-
 \begin{figure}[tbp]
@@
 \end{lstlisting}
-	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in Listing \ref{lst:examples}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in \Cref{tab:data-in-example}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
 	\label{lst:same-category}
@@
 \end{lstlisting}
-	\caption{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \ref{lst:examples}}
+	\caption{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \Cref{tab:data-in-example}}
   %, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
@@
 \paragraph{Benchmarking Build Log Analysis Techniques}
-LogChunks is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
+\emph{LogChunks} is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
 \emph{LogChunks} can be a benchmark to evaluate other build log analysis techniques.
@@
 \paragraph{Support Build Log Classification Algorithms}
-Various researchers are examining why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
+Various researchers are emxamining why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
 They write custom parsers and classifiers to categorize builds according to why a build failed.
@@
 
-\paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
-\emph{LogChunks} provides keywords that the authors would use to search for the chunk describing why the build failed.
-Analyzing these can help us understand how users process build logs and which keywords a tool should use to mark an error description.
-We can also recommend users which search keywords they should use to find why the build failed.
-\todo{Isn't this pretty simple and not really worth a research paper? If it is too trivial, we should probably not mention it here.}
+\paragraph{Research about Build Logs}
+The data from \emph{LogChunks} can support research around the topic of build logs such as how users use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests.
+\todo{citation pending}
+%TODO Caro: nathan cassee (with Alexander Sebrenik) did this in his master thesis (paper got accepted, will get link when preprint is finished), did not find others yet that do this}.
 
-\paragraph{Studying Conversations about Build Failures}
-Researchers are looking into conversations of developers surrounding CI builds and pull requests \todo{citation pending}
-%TODO Caro: nathan cassee (with Alexander Sebrenik) did this in his master thesis (paper got accepted, will get link when preprint is finished), did not find others yet that do this}.
-The chunks describing why a build failed, or the results of build log analysis techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
-\todo{Similar comment: This is a bit too narrow.
+% \paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
+% \emph{LogChunks} provides keywords that the authors would use to search for the chunk describing why the build failed.
+% Analyzing these can help us understand how users process build logs and which keywords a tool should use to mark an error description.
+% We can also recommend users which search keywords they should use to find why the build failed.
+% \todo{Isn't this pretty simple and not really worth a research paper? If it is too trivial, we should probably not mention it here.}
+
+% \paragraph{Studying Conversations about Build Failures}
+% Researchers are looking into conversations of developers surrounding CI builds and pull requests 
+% The chunks describing why a build failed, or the results of build log analysis techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
+% \todo{Similar comment: This is a bit too narrow.
 But perhaps we can merge the two in one and say researchers doing research around the topic of build logs, such as ...
@@
 
-\todo{ Andy also proposed: automatic creation of issue reports on GitHub with extracted info: sounds okay, but build failures are to be fixed faster than a GH issue I would say}
-\todo{I think this proposal is again too narrow: but what about further automatic on-ward processing? Even if small, perhaps reinforcement learning might be feasible ...}
+\paragraph{Automatic Processing of Build Results}
+\emph{LogChunks} enables researchers to train algorithms that retrieve build failure descriptions from build logs and provide the basis for further automatic on-ward processing of the retrieved log chunks.
+
+% \todo{ Andy also proposed: automatic creation of issue reports on GitHub with extracted info: sounds okay, but build failures are to be fixed faster than a GH issue I would say}
+% \todo{I think this proposal is again too narrow: but what about further automatic on-ward processing? Even if small, perhaps reinforcement learning might be feasible ...}
 
@@
 
-\subsection{Travis CI Build Log Data Set}
-\todo{I would remove this as it is not really related because it does not contain labels?}
-Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
-They selected Maven repositories that included the Checkstyle plugin.
-Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
+\subsection{LogHub}
+\emph{LogHub}~\cite{zhu2019tools} is a collection of a wide range of system log data sets.
+It is the basis for various studies that compare different approaches to parse unstructured system log messages into structured data for further analysis.
+\emph{LogChunks} empowers research with a benchmark to compare different build log analysis techniques, similar to the role of \emph{LogHub} in the area of system log parsing.
 
-\todo{What about the related data set I showed you and Georgios also mentioned? (Forgot exact name but don't have Internet so cannot look it up.)}
+% \subsection{Travis CI Build Log Data Set}
+% \todo{I would remove this as it is not really related because it does not contain labels?}
+% Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
+% They selected Maven repositories that included the Checkstyle plugin.
+% Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
 
@@
 
-In this section, we describe LogChunk's current limitations and future improvements and extensions we are planning.
+In this section, we describe \emph{LogChunk}'s current limitations and future improvements and extensions we are planning.
 
@@
 \paragraph{Classification of the Build Failure Cause}
-Our data set contains no further classification according to the cause of the failure.
+Our data set contains no further classification according to the cause of the failure, such as due to tests, compilation or linter errors.
 As researchers are investigating why CI builds fail, a useful extension is to annotate cause of the build failure for each log.
-\todo{Example: such as this is due to tests, compilation, ...?}
 
@@
 Build log analysis is not limited to retrieving the chunk describing why a build failed.
-\emph{LogChunks} can be extended with further information targets such as descriptions of warnings, build infrastructure and more.
-\todo{a rich description of all info contained in a build log?}
+\emph{LogChunks} can be extended with labels for all information that is contained in the build log, such as descriptions of warnings, build infrastructure and more.
 
@@
 \label{sec:conclusion}
-In this paper, we introduce\emph{LogChunks}, a cross-validated data
+In this paper, we introduce \emph{LogChunks}, a cross-validated data
 set encompassing 797 build logs from 80 projects using Travis CI\@.

### 2020-01-27 msr-paper/paper.tex
insert link, cassee citation & clean up bibliography, minor abstract corrections

@@
 \author{Carolin Brandt}
+\affiliation{
+  \institution{Delft University of Technology}
+  \country{The Netherlands}
+}
+\email{c.e.brandt@tudelft.nl}
 \author{Annibale Panichella}
+\affiliation{
+  \institution{Delft University of Technology}
+  \country{The Netherlands}
+}
+\email{a.panichella@tudelft.nl}
 \author{Andy Zaidman}
+\affiliation{
+  \institution{Delft University of Technology}
+  \country{The Netherlands}
+}
+\email{a.e.zaidman@tudelft.nl}
 \author{Moritz Beller}
+\affiliation{Inventitech}
+\email{mmb@inventitech.com}
 
@@
 \begin{abstract}
-Build logs are the textual by-products that a software build processes
+Build logs are textual by-products that a software build process
 creates, often as part of its Continuous Integration (CI)
@@
 developers when debugging into and understanding a build
-failures. Recently, attempts to partly automate this time-consuming,
+failure. Recently, attempts to partly automate this time-consuming,
 purely manual activity have come up, such as rule- or
@@
 overview in \Cref{fig:lc-overview}. All steps are automatized as Ruby
-scripts\todo{link to repo?} and highly configurable.
+scripts\footnote{Data collection scripts avaliable on GitHub: http://tiny.cc/data-collection} and highly configurable.
 
@@
 \paragraph{Research about Build Logs}
-The data from \emph{LogChunks} can support research around the topic of build logs such as how users use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests.
-\todo{citation pending}
-%TODO Caro: nathan cassee (with Alexander Sebrenik) did this in his master thesis (paper got accepted, will get link when preprint is finished), did not find others yet that do this}.
+The data from \emph{LogChunks} can support research around the topic of build logs such as how users use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests~\cite{cassee2019silent}.
 

### 2020-01-28 msr-paper/paper.tex
Fix author info
Review

@@
 
-\author{Carolin Brandt}
+\author{Carolin Brandt, Annibale Panichella, Andy Zaidman, Moritz Beller}
+\email{{c.e.brandt,a.panichella,a.e.zaidman,m.m.beller}@tudelft.nl}
 \affiliation{
@@
 }
-\email{c.e.brandt@tudelft.nl}
-\author{Annibale Panichella}
-\affiliation{
-  \institution{Delft University of Technology}
-  \country{The Netherlands}
-}
-\email{a.panichella@tudelft.nl}
-\author{Andy Zaidman}
-\affiliation{
-  \institution{Delft University of Technology}
-  \country{The Netherlands}
-}
-\email{a.e.zaidman@tudelft.nl}
-\author{Moritz Beller}
-\affiliation{Inventitech}
-\email{mmb@inventitech.com}
 
@@
 
-\begin{figure}[tbp]
+\begin{figure*}[tbp]
 	\centering
-	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
+	\includegraphics[width=1.35\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
 	\caption{Overview of \emph{LogChunks}}
 	\label{fig:lc-overview}
-\end{figure}
+\end{figure*}
 
@@
 \subsection{Log Collection}
-In this section, we describe how we created \emph{LogChunks} along the
-overview in \Cref{fig:lc-overview}. All steps are automatized as Ruby
-scripts\footnote{Data collection scripts avaliable on GitHub: http://tiny.cc/data-collection} and highly configurable.
+In this section, we describe along the overview in
+\Cref{fig:lc-overview} how we created \emph{LogChunks}. All steps are
+automatized as Ruby scripts\footnote{Data collection scripts avaliable
+  on GitHub: http://tiny.cc/data-collection} and highly configurable.
 
@@
 \paragraph{Results}
-In total we sent out mails to 246 developers. 32 of these mails could
-not be delivered. We received answers from 61 developers, corresponding to
+In total, from \todo{x date} to \todo{y date}, we sent out mails to 246 developers. 32 of these mails could
+not be delivered.
+We performed the sending out in an iterative way, first with \todo{x} emails and then in a second batch the remaining \todo{y} emails, and used the first author's academic email address as thes ender.
+All emails were specific to each receipient, and we only sent one mail per recipient.
+We received answers from 61 developers, corresponding to
 144 build logs (response rate: 24.8\%).
+When comparing this response rate with other typical response rates known from Software Engineering, it is extremely high.
+We believe that our personalization and the ease of use for the responder are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer.
+Indeed, we only received \todo{z} replies from developers along the lines of ``done''.
 
@@
 
-\section{Data Schema}
-\label{sec:data-schema}
-
-This section presents the internal structure and data schema of
-\emph{LogChunks}. In principle, LogChunks comprises automatically
-retrieved logs, as well as manually labeled and cross-validated data.
-
-%We give a description of the manually labeled data.
-%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
-%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
-LogChunks comprises information on 797 build logs, which are organized in folders for each language and repository.
-Within a repository folder, there is a folder for the general build status ('failed'), which contains the entire log files.
-% the logs are separated according to build status.
-%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
-%The build status folder contains the full logs in files named with the ID of the build that produced the log.
-For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
-\Cref{tab:data-in-example} presents the data LogChunks contains for an exemplary build from \texttt{php@php-src}.
-
-The top-level folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
-The data set contains an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
-\Cref{tab:data-in-example} gives an overview of the data within these XML files.
-
-Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.
-
-\begin{figure*}[htbp]
+\begin{table*}[htbp]
 \centering
@@
   Category & Categorization of the structural representation of the log chunk within the build log & Integer & \tt{0}\\
-  \todo{what about validation info?}\\
   \bottomrule
@@
 \label{tab:data-in-example}
-\end{figure*}
+\end{table*}
+
+\section{Data Schema}
+\label{sec:data-schema}
+
+This section presents the internal structure and data schema of
+\emph{LogChunks}. In principle, LogChunks comprises automatically
+retrieved logs, as well as manually labeled and cross-validated data.
+
+%We give a description of the manually labeled data.
+%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
+%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
+LogChunks comprises information on 797 build logs, which are organized in folders for each language and repository.
+For each repository, \emph{LogChunks} has about 10 \texttt{Examples}.
+Within a repository folder, there is a folder \todo{foldername} \texttt{} for the general build status (`failed'), which contains the full log files in plain text.
+% the logs are separated according to build status.
+%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
+%The build status folder contains the full logs in files named with the ID of the build that produced the log.
+
+The folder \texttt{build-failure-reason} contains the manually labeled
+data of \emph{LogChunks}, one XML file for each repository: \\
+\texttt{\textless repository\_owner\textgreater @\textless
+  repository\_name\textgreater.xml}.  \Cref{tab:data-in-example} gives
+an overview of the data within these XML files on the example of one
+build from \texttt{php@php-src}. The remainder of this section defines
+in more detail the data embedded in the XML files, that is, the
+labeled log chunk, search keywords and structural categories.
 
@@
 This can, for example, be the failing test case or a compiler error.
-In cases where the reason \emph{why} the build failed is contained in a log file external to the main build log, the \texttt{Chunk} includes only the fact \emph{that} the build failed, for example ``\texttt{The command "test/run !" exited with 1.}''.
+In cases where the reason \emph{why} the build failed is contained in a log file external to the main build log, the \texttt{Chunk} includes only the fact \emph{that} the build failed, for example ``\texttt{The command "test/run !" exited with 1.}''
 In \Cref{tab:data-in-example}, the \texttt{Chunk} describes a compile error where a variable did not exist in the current scope.
@@
 \end{lstlisting}
-	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in \Cref{tab:data-in-example}, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
+	\caption{Log chunk from the \emph{same} structural category (\todo{name structural category}) as the log chunk presented in \Cref{tab:data-in-example}.
+\todo{We inserted the special marker} ``{\color{cyan}-=-=-=-=-=-}'' to separate the log chunk from its context.}
 	\label{lst:same-category}
@@
 \end{lstlisting}
-	\caption{Log chunk from a \emph{different} structural category than the log chunk presented in Listing \Cref{tab:data-in-example}}
+	\caption{Log chunk from a \emph{different} structural category (\todo{name structural category}) than the log chunk presented in \Cref{tab:data-in-example}.}
   %, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
@@
 \paragraph{Support Build Log Classification Algorithms}
-Various researchers are emxamining why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
-They write custom parsers and classifiers to categorize builds according to why a build failed.
+Various researchers examine why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
+They typically write custom parsers and classifiers to categorize builds according to why a build failed.
 The manually labeled chunk can help researchers locate the source for their classification algorithms and cross-validate their data.
 
-\paragraph{Research about Build Logs}
+\paragraph{Research on Build Logs}
 The data from \emph{LogChunks} can support research around the topic of build logs such as how users use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests~\cite{cassee2019silent}.
@@
 It is the basis for various studies that compare different approaches to parse unstructured system log messages into structured data for further analysis.
-\emph{LogChunks} empowers research with a benchmark to compare different build log analysis techniques, similar to the role of \emph{LogHub} in the area of system log parsing.
+\emph{LogChunks} is situated in a different area, build log analysis, which tend to be semi-structured, and could play a similar role to \emph{LogHub} in its area:
+empower research with a benchmark to compare different build log analysis techniques.
 

### 2020-01-28 msr-paper/paper.tex
Finish review

@@
 
+\usepackage{listings}
+\usepackage{tabularx}
+\usepackage{cleveref}
+\usepackage{xspace}
 % TODO remove XD
 \usepackage{xcolor}
+
 \newcommand{\secfunc}[1]{{\color{magenta}#1}}
@@
 \newcommand{\todo}[1]{{\color{orange}(#1)}}
-
-\usepackage{listings}
-\usepackage{tabularx}
-\usepackage{cleveref}
+\newcommand{\logchunks}{\emph{LogChunks}\xspace}
 
@@
 
-While still in their infancy, we believe that having a common dataset
-to be able to fairly compare different build log analysis techniques
-will advance the research area and ultimately increase our
-understanding of CI build failures. In this paper, we present
-\emph{LogChunks}, a collection of 797 annotated Travis CI build
-logs from 80 GitHub repositories in 29 programming languages. For each
-build log, LogChunks contains a manually labeled log part (chunk)
-describing why the build failed. We externally validated the data set
-with the developers who caused the original build failure.
+We believe that having a common dataset to be able to fairly compare
+different build log analysis techniques will advance the research
+area. It will ultimately increase our understanding of CI build
+failures. In this paper, we present \logchunks, a collection of 797
+annotated Travis CI build logs from 80 GitHub repositories in 29
+programming languages. For each build log, \logchunks contains a
+manually labeled log part (chunk) describing why the build failed. We
+externally validated the data set with the developers who caused the
+original build failure.
 
-The width and depth of the \emph{LogChunks} data set are intended to
+The width and depth of the \logchunks data set are intended to
 make it the default benchmark for automated build log analysis
@@
 
-Thus, in this paper, we present \emph{LogChunks},\footnote{LogChunks
+Thus, in this paper, we present \logchunks,\footnote{\logchunks
   is openly available on Zenodo: \todo{insert zenodo link}} a
@@
 	\includegraphics[width=1.35\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
-	\caption{Overview of \emph{LogChunks}}
+	\caption{Overview of \logchunks}
 	\label{fig:lc-overview}
@@
 
-\section{Creating LogChunks}
+\section{Creating \logchunks}
 This section presents how we gathered the logs and our manual labeling process.
@@
 In this section, we describe along the overview in
-\Cref{fig:lc-overview} how we created \emph{LogChunks}. All steps are
+\Cref{fig:lc-overview} how we created \logchunks. All steps are
 automatized as Ruby scripts\footnote{Data collection scripts avaliable
@@
 
-For \emph{LogChunks}, we queried GHTorrent on 2018-04-01 for the three
+For \logchunks, we queried GHTorrent on 2018-04-01 for the three
 most popular repositories of each of the 30 most popular languages.
@@
 \paragraph{Build Sampling}
-To sample the builds for \emph{LogChunks} we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
+To sample the builds for \logchunks we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
 %A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
@@
 process in different environments. Hence, the outcome from different
-jobs might be different. For each build in LogChunks, we download the
+jobs might be different. For each build in \logchunks, we download the
 first job which has the same state as the overall build.
@@
 
-%For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
+%For \logchunks we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
 %As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
@@
 developers whose commits triggered the builds represented in
-\emph{LogChunks} and asked them whether the log chunk we labeled
+\logchunks and asked them whether the log chunk we labeled
 actually describes why the build failed.  This section describes our
@@
 \paragraph{Method}
-Using the Travis API, we collected the commit information for each build represented in \emph{LogChunks}.
+Using the Travis API, we collected the commit information for each build represented in \logchunks.
 We grouped all commits triggered by one developer and sent out an email to them. %, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
@@
 the validity of the labeled log chunks.  The study received answers
-for about 18\% of the data in \emph{LogChunks}.  After manual
+for about 18\% of the data in \logchunks.  After manual
 correction, 91\% of the received answers indicated our labeled chunks
@@
 \end{tabularx}
-\caption{Exemplary, complete data excerpt from \emph{LogChunks} for a failed build in \tt{php@php-src}.}
+\caption{Exemplary, complete data excerpt from \logchunks for a failed build in \tt{php@php-src}.}
 \label{tab:data-in-example}
@@
 This section presents the internal structure and data schema of
-\emph{LogChunks}. In principle, LogChunks comprises automatically
+\logchunks. In principle, \logchunks comprises automatically
 retrieved logs, as well as manually labeled and cross-validated data.
@@
 %We give a description of the manually labeled data.
-%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
-%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
-LogChunks comprises information on 797 build logs, which are organized in folders for each language and repository.
-For each repository, \emph{LogChunks} has about 10 \texttt{Examples}.
+%\logchunks has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
+%Each contains folders representing the main languages of the repositories in \logchunks.
+\logchunks comprises information on 797 build logs, which are organized in folders for each language and repository.
+For each repository, \logchunks has about 10 \texttt{Examples}.
 Within a repository folder, there is a folder \todo{foldername} \texttt{} for the general build status (`failed'), which contains the full log files in plain text.
 % the logs are separated according to build status.
-%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
+%Currently, \logchunks only contains logs from \texttt{failed} builds.
 %The build status folder contains the full logs in files named with the ID of the build that produced the log.
@@
 The folder \texttt{build-failure-reason} contains the manually labeled
-data of \emph{LogChunks}, one XML file for each repository: \\
+data of \logchunks, one XML file for each repository: \\
 \texttt{\textless repository\_owner\textgreater @\textless
@@
 We selected keywords the authors would use to search for the log \texttt{Chunk}, as we found them repeatedly next to failure describing chunks while analyzing about 800 build logs manually.
-Some keywords from \emph{LogChunks} are  ``\texttt{Error}'', ``\texttt{=DIFF=}'', ``\texttt{ERR!}'', or the keywords shown in \Cref{tab:data-in-example}.
+Some keywords from \logchunks are  ``\texttt{Error}'', ``\texttt{=DIFF=}'', ``\texttt{ERR!}'', or the keywords shown in \Cref{tab:data-in-example}.
 
@@
 %\section{Applications}
-%This section possible use cases for \emph{LogChunks} and outlines how we previously applied it to compare different build log analysis techniques.
+%This section possible use cases for \logchunks and outlines how we previously applied it to compare different build log analysis techniques.
 \section{Potential Use Cases}
@@
 %\subsection{Potential Use Cases}
-\emph{LogChunks} can be the basis for a range of further studies:
+\logchunks can be the basis for a range of further studies:
 
 \paragraph{Benchmarking Build Log Analysis Techniques}
-\emph{LogChunks} is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
-\emph{LogChunks} can be a benchmark to evaluate other build log analysis techniques.
+\logchunks is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
+\logchunks can be a benchmark to evaluate other build log analysis techniques.
 For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.
@@
 \paragraph{Research on Build Logs}
-The data from \emph{LogChunks} can support research around the topic of build logs such as how users use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests~\cite{cassee2019silent}.
+The data from \logchunks can support research around the topic of build logs such as how developers use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests~\cite{cassee2019silent}.
 
 % \paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
-% \emph{LogChunks} provides keywords that the authors would use to search for the chunk describing why the build failed.
+% \logchunks provides keywords that the authors would use to search for the chunk describing why the build failed.
 % Analyzing these can help us understand how users process build logs and which keywords a tool should use to mark an error description.
@@
 \paragraph{Automatic Processing of Build Results}
-\emph{LogChunks} enables researchers to train algorithms that retrieve build failure descriptions from build logs and provide the basis for further automatic on-ward processing of the retrieved log chunks.
+\logchunks enables researchers to train algorithms that retrieve build failure descriptions from build logs.
+It can provide the basis for further automatic on-ward processing of the retrieved log chunks.
 
@@
 % \subsection{Chunk Retrieval Evaluation}
-% We created \emph{LogChunks} to evaluate and compare different chunk retrieval techniques for build logs.
+% We created \logchunks to evaluate and compare different chunk retrieval techniques for build logs.
 % The first technique is based on synthesizing programs from examples using the Microsoft PROSE library.
@@
 This section presents existing data sets of CI build logs and how
-\emph{LogChunks} differs from them.
+\logchunks differs from them.
 
@@
 accessible through the public Travis CI and GitHub APIs and through
-GHTorrent~\cite{gousios2013ghtorrent}. Similar to LogChunks, among the
+GHTorrent~\cite{gousios2013ghtorrent}. Similar to \logchunks, among the
 metadata are the failing test cases. However, TravisTorrent obtained
@@
 many of the failing tests are at least incomplete and lack
-validation. By contrast, \emph{LogChunks} provides manually labeled
+validation. By contrast, \logchunks provides manually labeled
 and two-fold cross-validated data of why builds failed, not only for
@@
 It is the basis for various studies that compare different approaches to parse unstructured system log messages into structured data for further analysis.
-\emph{LogChunks} is situated in a different area, build log analysis, which tend to be semi-structured, and could play a similar role to \emph{LogHub} in its area:
+\logchunks is situated in a different area, build log analysis, which tend to be semi-structured, and could play a similar role to \emph{LogHub} in its area:
 empower research with a benchmark to compare different build log analysis techniques.
@@
 % They selected Maven repositories that included the Checkstyle plugin.
-% Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.
+% Their data set only provides the plain build logs, whereas \logchunks additionally provides manually labeled data about the chunk describing why a build failed.
 
-\section{Future Extensions to LogChunks}
+\section{Future Extensions to \logchunks}
 
-In this section, we describe \emph{LogChunk}'s current limitations and future improvements and extensions we are planning.
+In this section, we describe current limitations and future improvements of \logchunks and extensions we are planning.
 
@@
 The reason a build failed could be described at multiple locations within the log.
-We propose to extend \emph{LogChunks} to contain multiple substrings of the log text.
+We propose to extend \logchunks to contain multiple substrings of the log text.
 
 \paragraph{Include More Repositories and Logs}
-\emph{LogChunks} encompasses a range of repositories from various main development languages, though only 10 logs from each repository.
+\logchunks encompasses a range of repositories from various main development languages, though only 10 logs from each repository.
 %This stems from the high effort necessary for the manual data labeling process.
-Including more logs and repositories into \emph{LogChunks} will strengthen it as a benchmark to compare build log analysis techniques.
+Including more logs and repositories into \logchunks will strengthen it as a benchmark to compare build log analysis techniques.
 
@@
 Build log analysis is not limited to retrieving the chunk describing why a build failed.
-\emph{LogChunks} can be extended with labels for all information that is contained in the build log, such as descriptions of warnings, build infrastructure and more.
+\logchunks can be extended with labels for all information that is contained in the build log, such as descriptions of warnings, build infrastructure and more.
 
 \paragraph{Validation of Search Keywords}
-The keywords \emph{LogChunks} provides are based on the experience of the authors gained from analyzing around 800 build logs.
+The keywords \logchunks provides are based on the experience of the authors gained from analyzing around 800 build logs.
 Next, we propose to evaluate whether these keywords would also be used by developers to find the log chunk describing why a build failed.
@@
 \label{sec:conclusion}
-In this paper, we introduce \emph{LogChunks}, a cross-validated data
+In this paper, we introduce \logchunks, a cross-validated data
 set encompassing 797 build logs from 80 projects using Travis CI\@.
@@
 log chunk as well as a categorization of the log chunks according to
-their format within the log. \emph{LogChunks} advances the research
+their format within the log. \logchunks advances the research
 field of build log analysis by introducing a benchmark to rigorously

### 2020-01-28 msr-paper/paper.tex
Remove a TODO, bring to 4 pages

@@
 co-author, which informed the design of a cross-validation study in
-which we contacted over 200 developers.  Our main learning from the
-initial internal study was that it is important and difficult to
-adequately communicate all decisions and assumptions on how data is
-labeled.
+which we contacted over 200 developers.  Our learnings from the
+initial internal study are that  1) it is important and difficult to
+adequately communicate all decisions and assumptions on how and which data is
+labeled and 2) that can be different legitimate view points on
+what log chunk consitutes the cardinal error and which key words best to use.
 
@@
 \label{tab:data-in-example}
+\vspace{-0.5cm}
 \end{table*}
@@
 \logchunks. In principle, \logchunks comprises automatically
-retrieved logs, as well as manually labeled and cross-validated data.
+retrieved and manually labeled and cross-validated logs.
 
@@
 \logchunks comprises information on 797 build logs, which are organized in folders for each language and repository.
-For each repository, \logchunks has about 10 \texttt{Examples}.
-Within a repository folder, there is a folder \todo{foldername} \texttt{} for the general build status (`failed'), which contains the full log files in plain text.
+For each repository, \logchunks has about 10 \texttt{Examples}. Every repository folder, contains the full log files for the build status `failed' in plain text.
 % the logs are separated according to build status.
@@
 labeled log chunk, search keywords and structural categories.
+Data from the developer validation study is in the file \texttt{developer-crossvalidation.csv}, the build id can be used as a unique identifier to match it with the other data.
 
@@
 \end{lstlisting}
-	\caption{Log chunk from the \emph{same} structural category (\todo{name structural category}) as the log chunk presented in \Cref{tab:data-in-example}.
+\vspace{-0.3cm}
+	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in \Cref{tab:data-in-example}.
 \todo{We inserted the special marker} ``{\color{cyan}-=-=-=-=-=-}'' to separate the log chunk from its context.}
@@
 \end{lstlisting}
-	\caption{Log chunk from a \emph{different} structural category (\todo{name structural category}) than the log chunk presented in \Cref{tab:data-in-example}.}
+\vspace{-0.3cm}
+	\caption{Log chunk from a \emph{different} structural category than the log chunk presented in \Cref{tab:data-in-example}.}
   %, ``{\color{cyan}-=-=-=-=-=-}'' separates the log chunk from the context}
 	\label{lst:different-category}
+        \vspace{-0.3cm}
 \end{figure}
@@
 %This stems from the high effort necessary for the manual data labeling process.
-Including more logs and repositories into \logchunks will strengthen it as a benchmark to compare build log analysis techniques.
+Including more logs and repositories will strengthen \logchunks as the go-to benchmark.
 

### 2020-01-31 msr-paper/paper.tex
fill in missing numbers, minor corrections, add zenodo link

@@
 \usepackage{xspace}
-% TODO remove XD
 \usepackage{xcolor}
 
-\newcommand{\secfunc}[1]{{\color{magenta}#1}}
-\newcommand{\mention}[1]{{\color{cyan}#1}}
-\newcommand{\plan}[1]{{\color{purple}#1}}
-\newcommand{\bp}[1]{{\color{violet}#1}}
-\newcommand{\draft}[1]{{\color{blue}#1}}
-\newcommand{\review}[1]{{\color{black}#1}}
-\newcommand{\todo}[1]{{\color{orange}(#1)}}
 \newcommand{\logchunks}{\emph{LogChunks}\xspace}
@@
 
-\author{Carolin Brandt, Annibale Panichella, Andy Zaidman, Moritz Beller}
+\author{Carolin E. Brandt, Annibale Panichella, Andy Zaidman, Moritz Beller}
 \email{{c.e.brandt,a.panichella,a.e.zaidman,m.m.beller}@tudelft.nl}
@@
 Thus, in this paper, we present \logchunks,\footnote{\logchunks
-  is openly available on Zenodo: \todo{insert zenodo link}} a
+  is openly available on Zenodo: https://zenodo.org/record/3632351} a
 collection of 797 Travis CI build logs from 80 highly popular GitHub repositories in
@@
 process in different environments. Hence, the outcome from different
-jobs might be different. For each build in \logchunks, we download the
-first job which has the same state as the overall build.
+jobs might be different. For each build in \logchunks, we download the log of the
+first job that has the same state as the overall build.
 
@@
 Their task was to note down three strings they would put into a search field to find this failure description.
-The strings should appear in or around the \texttt{Chunk} and is case-sensitive.
+The strings should appear in or around the \texttt{Chunk} and are case-sensitive.
 There are no limitations on the search string, especially spaces are allowed.
@@
 adequately communicate all decisions and assumptions on how and which data is
-labeled and 2) that can be different legitimate view points on
-what log chunk consitutes the cardinal error and which key words best to use.
+labeled and 2) that there can be different legitimate view points on
+what log chunk constitutes the cardinal error and which keywords best to use.
 
@@
 %Figure~\ref{fig:dev-mail} shows one of the mails sent out.
-It included links to the corresponding commits, build overview and log file.
+It included links to the corresponding commits, the build overview and the log file.
 We asked the developers to fill out a short form in case our extraction was not correct.
@@
 \paragraph{Results}
-In total, from \todo{x date} to \todo{y date}, we sent out mails to 246 developers. 32 of these mails could
+In total, from 2020-10-15 to 2020-10-17, we sent out mails to 246 developers. 32 of these mails could
 not be delivered.
-We performed the sending out in an iterative way, first with \todo{x} emails and then in a second batch the remaining \todo{y} emails, and used the first author's academic email address as thes ender.
-All emails were specific to each receipient, and we only sent one mail per recipient.
+We performed the sending out in three batches and used the first author's academic email address as the sender.
+All emails were specific to each recipient, and we only sent one mail per recipient.
 We received answers from 61 developers, corresponding to
@@
 We believe that our personalization and the ease of use for the responder are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer.
-Indeed, we only received \todo{z} replies from developers along the lines of ``done''.
+Indeed, we only received seven replies from developers along the lines of ``done''.
 
@@
 In cases where the reason \emph{why} the build failed is contained in a log file external to the main build log, the \texttt{Chunk} includes only the fact \emph{that} the build failed, for example ``\texttt{The command "test/run !" exited with 1.}''
-In \Cref{tab:data-in-example}, the \texttt{Chunk} describes a compile error where a variable did not exist in the current scope.
+In \Cref{tab:data-in-example}, the \texttt{Chunk} describes a failing test in which the tested process timed out.
 
@@
 \paragraph{Structural Category}
-For each repository, we assign \emph{structural categories} to the chunks.
+For each repository, we assign \emph{structural categories} to the \texttt{Chunk}s.
 The structural category compares how \texttt{Chunk}s are represented within the build log.
@@
 	\caption{Log chunk from the \emph{same} structural category as the log chunk presented in \Cref{tab:data-in-example}.
-\todo{We inserted the special marker} ``{\color{cyan}-=-=-=-=-=-}'' to separate the log chunk from its context.}
+We inserted the special marker ``{\color{cyan}-=-=-=-=-=-}'' to separate the log chunk from its context.}
 	\label{lst:same-category}
@@
 \paragraph{Benchmarking Build Log Analysis Techniques}
-\logchunks is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
+\logchunks is a spin-off from research in which we compared three different log chunk retrieval techniques prototypically. %\todo{cite journal paper (or preprint?)}.
 \logchunks can be a benchmark to evaluate other build log analysis techniques.

### 2020-01-31 msr-paper/paper.tex
Enable review mode
Add reference

@@
 %% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf]{acmart}
+\documentclass[sigconf,review]{acmart}
 
@@
 \author{Carolin E. Brandt, Annibale Panichella, Andy Zaidman, Moritz Beller}
-\email{{c.e.brandt,a.panichella,a.e.zaidman,m.m.beller}@tudelft.nl}
+\email{{c.e.brandt, a.panichella, a.e.zaidman, m.m.beller}@tudelft.nl}
 \affiliation{
@@
 
-We believe that having a common dataset to be able to fairly compare
+We believe that having a common data set to be able to fairly compare
 different build log analysis techniques will advance the research
@@
 
-Thus, in this paper, we present \logchunks,\footnote{\logchunks
-  is openly available on Zenodo: https://zenodo.org/record/3632351} a
-collection of 797 Travis CI build logs from 80 highly popular GitHub repositories in
-29 programming languages.  For each build log, we manually labeled
-the chunk describing why the build failed.  The data set also provides
-keywords the authors would use to search for the labeled log chunk and
-categorizes the log chunks according to their format within the log.
+Thus, in this paper, we present
+\logchunks~\cite{brandt_carolin_2020_3632351},\footnote{\logchunks is
+  openly available on Zenodo: https://zenodo.org/record/3632351} a
+collection of 797 labeled Travis CI build logs from 80 highly popular GitHub
+repositories in 29 programming languages with  we
+manually labeled the chunk describing why the build failed.  The data
+set also provides keywords the authors would use to search for the
+labeled log chunk and categorizes the log chunks according to their
+format within the log.
 
@@
 \Cref{fig:lc-overview} how we created \logchunks. All steps are
-automatized as Ruby scripts\footnote{Data collection scripts avaliable
-  on GitHub: http://tiny.cc/data-collection} and highly configurable.
+automatized as Ruby scripts\footnote{Data collection scripts and their original parametrization are included in the data set.} and highly configurable.
 
@@
 144 build logs (response rate: 24.8\%).
-When comparing this response rate with other typical response rates known from Software Engineering, it is extremely high.
+Compared to typical response rates known from Software Engineering~\cite{smith2013improving}, this is very high.
 We believe that our personalization and the ease of use for the responder are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer.
@@
 % \todo{I would remove this as it is not really related because it does not contain labels?}
-% Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
+% Loriot et al.~\cite{loriot2019data set, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
 % They selected Maven repositories that included the Checkstyle plugin.

### 2020-02-04 msr-paper/paper.tex
Include Andy feedback

@@
 \paragraph{Search Keywords}
-We presented the \texttt{Chunk} and ten lines above and below to the labeler.
-Their task was to note down three strings they would put into a search field to find this failure description.
+To extract the search keywords, we considered the \texttt{Chunk} and ten lines above and below.
+The labeler's task was to note down three strings they would search for (``grep'') to find this failure description.
 The strings should appear in or around the \texttt{Chunk} and are case-sensitive.
-There are no limitations on the search string, especially spaces are allowed.
+We made no limitations on the search string; particularly, spaces are allowed.
 
@@
 We validated our collected data points in an iterative fashion. First,
-we performed an initial inter-rater reliability study with a
-co-author, which informed the design of a cross-validation study in
-which we contacted over 200 developers.  Our learnings from the
+we performed an initial inter-rater reliability study with the second author of this paper. Our learnings from this
 initial internal study are that  1) it is important and difficult to
-adequately communicate all decisions and assumptions on how and which data is
-labeled and 2) that there can be different legitimate view points on
-what log chunk constitutes the cardinal error and which keywords best to use.
+adequately communicate all decisions and assumptions on how to and which data to
+lable and 2) there can be different legitimate viewpoints on
+which log chunk constitute the cardinal error and which keywords best to use. These learning informed the design of a seocnd, larger cross-validation study for which we contacted over 200 developers.
 
@@
 \paragraph{Results}
-In total, from 2020-10-15 to 2020-10-17, we sent out mails to 246 developers. 32 of these mails could
+In total, from 2020-10-15 to 2020-10-17, we sent out mails to 246 developers. Of these, 32 could
 not be delivered.
 We performed the sending out in three batches and used the first author's academic email address as the sender.
-All emails were specific to each recipient, and we only sent one mail per recipient.
+All emails were specific to each recipient.
+We only sent one mail per recipient.
 We received answers from 61 developers, corresponding to
-144 build logs (response rate: 24.8\%).
-Compared to typical response rates known from Software Engineering~\cite{smith2013improving}, this is very high.
+144 build logs with a response rate of 24.8\%.
+Compared to typical response rates to cold calling known from Software Engineering~\cite{smith2013improving}, this is very high.
 We believe that our personalization and the ease of use for the responder are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer.
-Indeed, we only received seven replies from developers along the lines of ``done''.
+Indeed, we only received seven replies from developers along the lines of ``done.''
 
-Of the 144 answers, 132 indicated our extraction was correct.
+Of the 144 answers, 118 initially indicated that our extraction was correct.
 %26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
 We manually inspected the 26 negative answers and found that some stated that the proposed extraction did not show the whole description of why the build failed.
-This is because we had to trim long chunks to keep the mails readable.
-
-After adjusting for these answers, 12 answers remained that stated that our labeled log chunk was not correct.
+This was because we chose to trim long chunks to keep the mails readable, and not a fault in our extraction per se.
+After adjusting for these answers, only 12 answers remained that stated that our labeled log chunk was not correct.
+This validates our dataset with an externally validated consensus on 94.4\% of the extracted data.
 
@@
 \logchunks comprises information on 797 build logs, which are organized in folders for each language and repository.
-For each repository, \logchunks has about 10 \texttt{Examples}. Every repository folder, contains the full log files for the build status `failed' in plain text.
+For each repository, \logchunks has about 10 \texttt{Examples}. Every repository folder contains the full log files for the build status `failed' in plain text.
 % the logs are separated according to build status.
@@
 \paragraph{Chunk as One Consecutive Substring}
-The manually labeled \texttt{Chunk} contains only one continuous substring of the log text.
+The \texttt{Chunk} contains only one continuous substring of the log text.
 The reason a build failed could be described at multiple locations within the log.
@@
 
-\paragraph{Other Targeted Information Chunks}
-Build log analysis is not limited to retrieving the chunk describing why a build failed.
+\paragraph{Other Information Chunks}
+Build log analysis is not limited to the chunk that describes why a build failed.
 \logchunks can be extended with labels for all information that is contained in the build log, such as descriptions of warnings, build infrastructure and more.

### 2020-02-04 msr-paper/paper.tex
mend

@@
 \Cref{fig:lc-overview} how we created \logchunks. All steps are
-automatized as Ruby scripts\footnote{Data collection scripts and their original parametrization are included in the data set.} and highly configurable.
+automatized as Ruby scripts\footnote{Data collection scripts and their original parameterization are included in the data set.} and highly configurable.
 
@@
 %They copied out the first continuous description as the \texttt{Chunk}.
-They preserved whitespace and special characters, as they might be crucial to detect the targeted substring.
+They preserved whitespaces and special characters, as they might be crucial to detect the targeted substring.
 To support learning of regular expressions identifying the labeled substrings the labeler aimed to start and end the labeled substring at consistent locations around the fault description.
@@
 adequately communicate all decisions and assumptions on how to and which data to
-lable and 2) there can be different legitimate viewpoints on
-which log chunk constitute the cardinal error and which keywords best to use. These learning informed the design of a seocnd, larger cross-validation study for which we contacted over 200 developers.
+label and 2) there can be different legitimate viewpoints on
+which log chunk constitute the cardinal error and which keywords best to use. These learning informed the design of a second, larger cross-validation study for which we contacted over 200 developers.
 
@@
 Compared to typical response rates to cold calling known from Software Engineering~\cite{smith2013improving}, this is very high.
-We believe that our personalization and the ease of use for the responder are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer.
+We believe that our personalization and the ease of use for the participant are the main reasons for this---simply clicking on a link to confirm or refute an answer is enough, there is no need to craft an answer.
 Indeed, we only received seven replies from developers along the lines of ``done.''
@@
 After adjusting for these answers, only 12 answers remained that stated that our labeled log chunk was not correct.
-This validates our dataset with an externally validated consensus on 94.4\% of the extracted data.
+This validates our data set with an externally validated consensus on 94.4\% of the extracted data.
 
@@
 \paragraph{Benchmarking Build Log Analysis Techniques}
-\logchunks is a spin-off from research in which we compared three different log chunk retrieval techniques prototypically. %\todo{cite journal paper (or preprint?)}.
+\logchunks is a spin-off from the first author's Master's Thesis in which she compared three different log chunk retrieval techniques prototypically. %\todo{cite journal paper (or preprint?)}.
 \logchunks can be a benchmark to evaluate other build log analysis techniques.
@@
 examine research contributions~\cite{sim2003using} and opening various
-research possibilites that previously required tedious manual
+research possibilities that previously required tedious manual
 classification.

### 2020-02-04 msr-paper/paper.tex
Small changes in the abstract
Minor corrections in the intro

@@
 %% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf,review]{acmart}
+\documentclass[sigconf]{acmart}
 
@@
 
-We believe that having a common data set to be able to fairly compare
-different build log analysis techniques will advance the research
+We believe that having a common data set to be able to compare
+different build log analysis techniques fairly will advance the research
 area. It will ultimately increase our understanding of CI build
@@
 developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
+communication~\cite{downs2012ambient}.  CI builds produce logs that
 report the results of the steps within the build.  These build logs
 contain a lot of valuable information for developers and researchers,
-for example: descriptions of compile errors, linter warnings or failed
+for example, descriptions of compile errors, linter warnings, or failed
 tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
@@
 logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
+to build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
 al.\ reduced the number of lines for a developer to inspect by
@@
 
-At the moment there is only anecdotal evidence on the performance of
-these techniques and when a technique should be preferred over its
+At the moment, there is only anecdotal evidence on the performance of
+these techniques, and when a technique should be preferred over its
 alternatives.  In fact, there is no data set available to support the
-creation of such a benchmark of build log analysis techniques.
+creation of such a benchmark for build log analysis techniques.
 Following Sim et al., a benchmark gives us the chance to ``increase

### 2020-02-06 msr-paper/paper.tex
My pass on the paper + added some comments

@@
 
-We believe that having a common data set to be able to compare
-different build log analysis techniques fairly will advance the research
+We believe that having a common data set that enables a fair comparison 
+of different build log analysis techniques will advance the research
 area. It will ultimately increase our understanding of CI build
@@
 original build failure. 
+\textcolor{red}{I am not sure about saying that the developers caused 
+a failure.}
 
@@
 automatized as Ruby scripts\footnote{Data collection scripts and their original parameterization are included in the data set.} and highly configurable.
+\smallskip
 
-\paragraph{Repository Sampling}
+\textit{Repository Sampling}
 We target mature GitHub repositories that are using Travis CI\@.
@@
 \texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.
+\smallskip
 
-\paragraph{Build Sampling}
+\textit{Build Sampling}.
 To sample the builds for \logchunks we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
 %A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
+\smallskip
 
-\paragraph{Log Sampling}
+\textit{Log Sampling}.
 Travis CI builds comprise a number of jobs that actualize a build
@@
 \label{sec:labeling-process}
-After collecting build logs, the first author manually labeled which
-text chunk describes why the build failed. Following that, she
-assigned search keywords and structural categories to each log chunk.
+After collecting build logs, the first author manually labeled the
+text chunk that describes why the build failed. Following that, she
+assigned search keywords and structural categories to each identified log chunk.
+\smallskip
 
-\paragraph{Chunk That Describes Why The Build Failed}
+\textit{Chunk That Describes Why The Build Failed}.
 For each repository, the labeler skimmed through the build logs and copied out the first occurrence of a description why the build failed.
 %They copied out the first continuous description as the \texttt{Chunk}.
-They preserved whitespaces and special characters, as they might be crucial to detect the targeted substring.
+They \textcolor{red}{Annibale: who/what is the subject here?
+I mean, does ``they'' refer to one person?} preserved whitespaces and special characters, as they might be crucial to detect the targeted substring.
 To support learning of regular expressions identifying the labeled substrings the labeler aimed to start and end the labeled substring at consistent locations around the fault description.
+\smallskip
 
-\paragraph{Search Keywords}
+\textit{Search Keywords}.
 To extract the search keywords, we considered the \texttt{Chunk} and ten lines above and below.
@@
 We made no limitations on the search string; particularly, spaces are allowed.
+\smallskip
 
-\paragraph{Structural Category}
+\textit{Structural Category}.
 To label the \emph{structural categories} we presented the \texttt{Chunk} and the surrounding context to the labeler for all logs from a repository.
 We asked them to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation.
+\textcolor{red}{Them?
+Up to now we refer to one labeler (one single person).}
 %The labeler should start the categories with 0 and increase as new ones appear.
@@
 survey and discusses our results.
+\smallskip
 
-\paragraph{Method}
+\textit{Method}.
 Using the Travis API, we collected the commit information for each build represented in \logchunks.
@@
 %Figure~\ref{fig:dev-mail} shows one of the mails sent out.
-It included links to the corresponding commits, the build overview and the log file.
+It included links to the corresponding commits, the build overview, and the log file.
 We asked the developers to fill out a short form in case our extraction was not correct.
@@
 In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why our original extraction was incorrect.
+\smallskip
 
-\paragraph{Results}
-In total, from 2020-10-15 to 2020-10-17, we sent out mails to 246 developers. Of these, 32 could
+\textit{Results}.
+In total, from 2020-10-15 to 2020-10-17, we sent out emails to 246 developers. Of these, 32 could
 not be delivered.
@@
 This validates our data set with an externally validated consensus on 94.4\% of the extracted data.
+\smallskip
 
-\paragraph{Discussion}
+\textit{Discussion}.
 We believe that our developer survey highly strengthens the trust in
@@
 
-One of our 12 incorrect extractions only showed a warning and the
+One of our 12 incorrect extractions only showed a warning, and the
 developer proposed to also include the line stating that warnings are
@@
 \logchunks comprises information on 797 build logs, which are organized in folders for each language and repository.
-For each repository, \logchunks has about 10 \texttt{Examples}. Every repository folder contains the full log files for the build status `failed' in plain text.
+For each repository, \logchunks has about ten \texttt{Examples}. Every repository folder contains the full logs for the build status `failed' in plain text.
 % the logs are separated according to build status.
@@
 in more detail the data embedded in the XML files, that is, the
-labeled log chunk, search keywords and structural categories.
+labeled log chunk, search keywords, and structural categories.
 Data from the developer validation study is in the file \texttt{developer-crossvalidation.csv}, the build id can be used as a unique identifier to match it with the other data.
+\smallskip
 
-\paragraph{Chunk That Describes Why The Build Failed}
+\textit{Chunk That Describes Why The Build Failed}.
 The \texttt{Chunk} is the substring of the build log that describes why the build failed.
@@
 %In these instances the \texttt{Chunk} contains the lines describing that the build failed.
+\smallskip
 
-\paragraph{Search Keywords}
+\textit{Search Keywords}.
 The \texttt{Keywords} contain a list of one to three freely chosen search strings appearing within the \texttt{Chunk} or in the area around it in the build log.
@@
 Some keywords from \logchunks are  ``\texttt{Error}'', ``\texttt{=DIFF=}'', ``\texttt{ERR!}'', or the keywords shown in \Cref{tab:data-in-example}.
+\smallskip
 
-\paragraph{Structural Category}
+\textit{Structural Category}.
 For each repository, we assign \emph{structural categories} to the \texttt{Chunk}s.
@@
 Listing \ref{lst:same-category} presents a log chunk from the same category as the log chunk from \Cref{tab:data-in-example}.
-In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
+In comparison to that, Listing \ref{lst:different-category} presents a log chunk that is formatted differently within the log file.
 %For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
@@
 \logchunks can be the basis for a range of further studies:
+\smallskip
 
-\paragraph{Benchmarking Build Log Analysis Techniques}
+\textit{Benchmarking Build Log Analysis Techniques}.
 \logchunks is a spin-off from the first author's Master's Thesis in which she compared three different log chunk retrieval techniques prototypically. %\todo{cite journal paper (or preprint?)}.
@@
 For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.
+\smallskip
 
-\paragraph{Support Build Log Classification Algorithms}
+\textit{Support Build Log Classification Algorithms}.
 Various researchers examine why CI builds fail and use build logs as a data source~\cite{seo2014programmers,vassallo2017a-tale}.
@@
 The manually labeled chunk can help researchers locate the source for their classification algorithms and cross-validate their data.
+\smallskip
 
-\paragraph{Research on Build Logs}
-The data from \logchunks can support research around the topic of build logs such as how developers use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests~\cite{cassee2019silent}.
+\textit{Research on Build Logs}.
+The data from \logchunks can support research around the topic of build logs, such as how developers use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests~\cite{cassee2019silent}.
 
@@
 user studies on keyword retrievala and conversations?}
+\smallskip
 
-\paragraph{Automatic Processing of Build Results}
+\textit{Automatic Processing of Build Results}.
 \logchunks enables researchers to train algorithms that retrieve build failure descriptions from build logs.
@@
 In this section, we describe current limitations and future improvements of \logchunks and extensions we are planning.
+\smallskip
 
-\paragraph{Chunk as One Consecutive Substring}
+\textit{Chunk as One Consecutive Substring}
 The \texttt{Chunk} contains only one continuous substring of the log text.
@@
 We propose to extend \logchunks to contain multiple substrings of the log text.
+\smallskip
 
-\paragraph{Include More Repositories and Logs}
+\textit{Include More Repositories and Logs}
 \logchunks encompasses a range of repositories from various main development languages, though only 10 logs from each repository.
@@
 Including more logs and repositories will strengthen \logchunks as the go-to benchmark.
+\smallskip
 
-\paragraph{Classification of the Build Failure Cause}
-Our data set contains no further classification according to the cause of the failure, such as due to tests, compilation or linter errors.
-As researchers are investigating why CI builds fail, a useful extension is to annotate cause of the build failure for each log.
+\textit{Classification of the Build Failure Cause}
+Our data set contains no further classification according to the cause of the failure, such as due to tests, compilation, or linter errors.
+As researchers are investigating why CI builds fail, a useful extension is to annotate the cause of the build failure for each log.
+\smallskip
 
-\paragraph{Other Information Chunks}
+\textit{Other Information Chunks}
 Build log analysis is not limited to the chunk that describes why a build failed.
 \logchunks can be extended with labels for all information that is contained in the build log, such as descriptions of warnings, build infrastructure and more.
+\smallskip
 
-\paragraph{Validation of Search Keywords}
+\textit{Validation of Search Keywords}
 The keywords \logchunks provides are based on the experience of the authors gained from analyzing around 800 build logs.
@@
 For each log, we annotated the log chunk describing why the build
-failed and provide keywords a developer would use to search for the
+failed and provided keywords a developer would use to search for the
 log chunk as well as a categorization of the log chunks according to

### 2020-02-06 msr-paper/paper.tex
Make paper fit 4 pages

--- 2020-02-04 msr-paper/paper.tex
@@
 \paragraph{Benchmarking Build Log Analysis Techniques}
-\logchunks is a spin-off from the first author's Master's Thesis in which she compared three different log chunk retrieval techniques prototypically. %\todo{cite journal paper (or preprint?)}.
+\logchunks originated from the first author's Master's Thesis in which she compared three different log chunk retrieval techniques. %\todo{cite journal paper (or preprint?)}.
 \logchunks can be a benchmark to evaluate other build log analysis techniques.
-For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.
+For example, one can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves build failure reasons.
 

### 2020-02-06 msr-paper/paper.tex

--- 2020-02-06 msr-paper/paper.tex
@@
 
-\textit{Benchmarking Build Log Analysis Techniques}.
-\logchunks is a spin-off from the first author's Master's Thesis in which she compared three different log chunk retrieval techniques prototypically. %\todo{cite journal paper (or preprint?)}.
+\paragraph{Benchmarking Build Log Analysis Techniques}
+\logchunks originated from the first author's Master's Thesis in which she compared three different log chunk retrieval techniques. %\todo{cite journal paper (or preprint?)}.
 \logchunks can be a benchmark to evaluate other build log analysis techniques.
-For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.
-\smallskip
+For example, one can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves build failure reasons.
 

### 2020-02-06 msr-paper/paper.tex
Revert "Minor corrections in the intro"
This reverts commit 6372569ccf80204bda3f0173fd9dd1722f6e2321.

--- 2020-02-06 msr-paper/paper.tex
@@
 developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs that
+communication~\cite{downs2012ambient}.  CI builds produce logs which
 report the results of the steps within the build.  These build logs
 contain a lot of valuable information for developers and researchers,
-for example, descriptions of compile errors, linter warnings, or failed
+for example: descriptions of compile errors, linter warnings or failed
 tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
@@
 logs.  Vassallo et al.\ wrote a custom parser to gather information
-to build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
+for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
 al.\ reduced the number of lines for a developer to inspect by
@@
 
-At the moment, there is only anecdotal evidence on the performance of
-these techniques, and when a technique should be preferred over its
+At the moment there is only anecdotal evidence on the performance of
+these techniques and when a technique should be preferred over its
 alternatives.  In fact, there is no data set available to support the
-creation of such a benchmark for build log analysis techniques.
+creation of such a benchmark of build log analysis techniques.
 Following Sim et al., a benchmark gives us the chance to ``increase

### 2020-02-06 msr-paper/paper.tex
Re-integrate some of Annibale's changes

--- 2020-02-06 msr-paper/paper.tex
@@
 
-We believe that having a common data set to be able to compare
+We believe that having a common data set to compare
 different build log analysis techniques fairly will advance the research
@@
 developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs that
-report the results of the steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers,
-for example, descriptions of compile errors, linter warnings, or failed
+communication~\cite{downs2012ambient}.  CI builds produce logs which
+report results of various sub-steps within the build.  These build logs
+contain a lot of valuable information for developers and researchers---for example, descriptions of compile errors, linter warnings or failed
 tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
@@
 %They copied out the first continuous description as the \texttt{Chunk}.
-They preserved whitespaces and special characters, as they might be crucial to detect the targeted substring.
+She preserved whitespaces and special characters, as these might be crucial to detect the targeted substring.
 To support learning of regular expressions identifying the labeled substrings the labeler aimed to start and end the labeled substring at consistent locations around the fault description.
@@
 To label the \emph{structural categories} we presented the \texttt{Chunk} and the surrounding context to the labeler for all logs from a repository.
-We asked them to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation.
+We asked the labeler to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation.
 %The labeler should start the categories with 0 and increase as new ones appear.
@@
 \paragraph{Results}
-In total, from 2020-10-15 to 2020-10-17, we sent out mails to 246 developers. Of these, 32 could
+In total, from 2020-10-15 to 2020-10-17, we sent out emails to 246 developers. Of these, 32 could
 not be delivered.

### 2020-02-14 msr-paper/paper.tex
Make link clickable

@@
 \logchunks~\cite{brandt_carolin_2020_3632351},\footnote{\logchunks is
-  openly available on Zenodo: https://zenodo.org/record/3632351} a
+  openly available on Zenodo: \url{https://zenodo.org/record/3632351}} a
 collection of 797 labeled Travis CI build logs from 80 highly popular GitHub

### 2020-03-02 tse-paper/content.tex
Add motivation

@@
+\textbf{Motivation.} The information stored in build logs can and has
+already been used for a variety of applications. One prominent dataset
+in the space, TravisTorrent, was featured as the MSR Data Challenge
+2017~\cite{msr17challenge}. To date, scientist and practitioners alike
+have used it and other, proprietary datasets to understand and
+cateogrize Continuous Integration build
+failures~\cite{islam2017insights}, to do research on testing
+practices~\cite{orellana2017differences}, to train classifiers to
+predict the build outcome and
+duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
+and to investigate static analysis tools in CI
+builds~\cite{zampetti2017open}. Therefore, being able to efficiently
+and correctly extract information from build logs is paramount to the
+future of a variety of fields depending on it.
+
 basically like in thesis

### 2020-03-03 tse-paper/content.tex
include loads of text and graphics from thesis, fix graphics, start adapting heading levels

@@
+Continuous Integration (CI) has become a common practice in software
+engineering~\cite{hilton2016usage}.  Many software projects use
+CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
+bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
+developer productivity~\cite{miller2008hundred,hilton2016usage} and
+communication~\cite{downs2012ambient}.  CI builds produce logs which
+report results of various sub-steps within the build.  These build logs
+contain a lot of valuable information for developers and researchers---for
+example, descriptions of compile errors, linter warnings or failed
+tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
+
 \textbf{Motivation.} The information stored in build logs can and has
@@
 
-basically like in thesis
+However, build logs can be verbose and large---sometimes in excess of
+50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
+for direct human consumption. Therefore, to support developers and
+researchers in efficiently making use of the information within build
+logs, we must at least semi-automatically retrieve the chunks of the
+log that describe the targeted information.
+
+There are different techniques to retrieve information chunks from CI
+build logs. Beller et al. use a rule-based system of regular
+expressions to analyze logs from Travis CI~\cite{beller2017oops}.
+Such regular expressions are developed by looking at exemplary build
+logs.  Vassallo et al.\ wrote a custom parser to gather information
+for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
+al.\ reduced the number of lines for a developer to inspect by
+creating a diff between logs from failed and successful
+builds~\cite{amar2019mining}.
+
+These approaches have various strengths and weaknesses: Regular
+expressions are exact, but tedious and error-prone to
+maintain~\cite{michael2019regexes}.  Custom parsers are powerful
+though fragile in light of changes in the log structure. Diffing
+between failed and successful logs can reduce the information to be
+processed, but is at best semi-automatic~\cite{amar2019mining}.
+
+At the moment there is only anecdotal evidence on the performance of these techniques and on when a technique should be preferred over other alternatives.
+Developers and researches currently have little support when choosing which technique to use for a task.
+
+The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
+We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
+For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
+
+We implement and evaluate three chunk retrieval techniques:
+\begin{itemize}
+  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
+  \item a common text similarity approach (referred to as CTS), and
+  \item keyword search (referred to as KWS).
+\end{itemize}
+\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
+\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
+how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
+To evaluate PBE, CTS and KWS we create a data set, called \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
+Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
+
+Our study of the three techniques on \emph{LogChunks} shows that
+\begin{itemize}
+  \item PBE yields very accurate results when trained with two examples from a single structural category.
+  \item CTS shows the best average precision, though precision and recall of a retrieval is hard to determine from the given result.
+  A small increase in the number of training examples has no noticeable influence.
+  Fewer structural categories improve precision and recall of the retrieval.
+  \item KWS has the highest recall of all techniques, however much lower precision.
+  It is the technique with the best recall when multiple structural categories are present in the training examples.
+\end{itemize}
+
+\paragraph{Our work contributes:}
+\begin{itemize}
+  \item A tool unifying several chunk retrieval techniques namely:
+        \begin{itemize}
+          \item program synthesis from examples using the Microsoft PROSE library (PBE),
+          \item a common information retrieval approach using text similarity (CTS), and
+          \item a keyword search approach (KWS).
+        \end{itemize}
+  \item A validated data set of about 800 logs from failed Travis CI builds manually-labelled with:
+        \begin{itemize}
+          \item the substring of the log describing the reason the build failed,
+          \item keywords we would use to search for these substrings, and
+          \item a categorization of the substrings according to their structural representation within the build log.
+        \end{itemize}
+  \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
+  \item Guidelines on choosing a suitable chunk retrieval technique.
+\end{itemize}
+
+We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in precision and recall of the chunk retrieval is required.
+CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
+In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
+However, its low precision requires a human to interpret the output of the chunk retrieval.
+
+\todo{structure overview of article}
 
@@
 
+\label{sec:rw}
+This chapter presents various research works adjacent or foundational to our work.
+The first section presents existing work in the field of continuous integration (CI) and showcases how researchers analyze build logs.
+In the second section we describe the existing methods which are the foundation for the chunk retrieval techniques we investigate.
+
+\subsection{Continuous Integration and Build Logs}
+We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
+We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
+This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
+The presented approaches are related to and can benefit from the techniques we analyze in this thesis.
+Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.
+
+\subsubsection{Build Failures in CI}
+Various researchers look into why CI builds fail and into the impact of build failures on the development workflow.
+Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
+In addition, they notice that most failures are resolved within two builds.
+Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and find that most builds fail because of failing tests.
+For most projects, over half of the failed builds follow a previous failed build.
+Rausch et al.'s data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
+Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
+They determine that testing failures are more common than compilation errors.
+Open source builds fail most often because of unit tests, whereas release preparations are the primary cause in industrial projects.
+
+\subsubsection{Supporting Log Analysis with Chunk Retrieval}
+To leverage the valuable information within build logs the researchers presented in this section build parsers and regular expression-based programs.
+This task of retrieving specific chunks of text from the build logs can be solved by the chunk retrieval techniques we compare in this thesis.
+Our results can support researchers in choosing a suitable technique for their data set of build logs and the chunks they want to retrieve.
+By relieving them from building custom parsers we enable them to cover a much wider range of languages and build tools in their studies.
+
+\subsection{Augmentation of Build Logs}
+\label{sec:rw-bl-analysis}
+Build logs are a valuable data source for developers to find out why their build failed.
+Several researchers are looking into supporting developers to process the verbose build logs.
+Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
+They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
+The hint generators leverage this structured access to the information within the build log to propose fixes.
+For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
+In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
+Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
+The chunk retrieval techniques we compare in this thesis can be used to fill similar structured representations with information from build logs.
+As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.
+
+Amar et al.~\cite{amar2019mining} compare different approaches to reduce the portions of a log that a developer has to inspect.
+Their techniques remove lines that appear both in logs from passing and failing builds and use a modified \emph{Term Frequency Inverse Document Frequency} (TF-IDF) weighting to identify term vectors likely to occur with failures.
+Their diff technique can be interpreted as a chunk retrieval technique, where the targeted information is defined by the past failures used as basis for the weighted term vectors.
+
+Travis itself already provides build log augmentation in the form of a basic structuring of the build logs within their log viewer using \emph{log folds}~\cite{travis2019logfolds}.
+They add fold identifiers around common commands and setup or teardown build phases and collapse the contained lines by default.
+
+\subsection{Build Logs as Semi-Structured Data}
+\label{sec:rw-semi-structured-data}
+Serge Abiteboul introduces a theory of semi-structured data in his report from 1997 about integrating data from several sources~\cite{abiteboul1997querying}.
+He proposes essential characteristics of semi-structured data.
+In this section, we show how five of these map to the context of build logs.
+
+The structure of build logs
+\begin{itemize}
+  \item \textbf{is implicit}.
+  We might not have access to explicit structuring elements or an explicit structure description.
+  Computation is required to infer the present structure.
+  \item \textbf{is irregular}.
+  Changes in the build process or execution environment might change the structure of a build log.
+  We observed this in the logs we collected for the \emph{LogChunks} data set, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
+  Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} present an example of this.
+  \item \textbf{is partial}. Some parts are highly structured by e.g.\ special characters. Other parts are unstructured, such as natural language text in error messages.
+  \item can be described with an \textbf{analytical data guide} rather than a predefined schema.
+  There is no fixed specification on how build tools structure their output.
+  We later extract structuring patterns in the produced output.
+  \item \textbf{has a rapidly evolving schema}.
+  Modifications in the build configuration can change the tools involved in the build and therefore the composition of the build log.
+  Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adapt their log messages over time~\cite{yuan2012characterizing}.
+\end{itemize}
+
+Abiteboul proposes an approach to overlay the semi-structured data with a structured layer.
+The additional layer can answer queries and give access to the semi-structured data relevant to a query.
+In contrast to that, this thesis takes a look at techniques to gather a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=\columnwidth, clip]{img/log42.png}
+	\caption{Excerpt from a build log showing a WarningMessage chunk.}
+	\label{fig:log-4}
+\end{figure}
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=\columnwidth, clip]{img/log52.png}
+	\caption{Excerpt from a build log showing a differently formatted WarningMessage chunk.}
+	\label{fig:log-5}
+\end{figure}
+
+\subsection{System Log Analysis}
+\label{sec:log-analysis}
+A related field of log processing is the processing of system log files produced during runtime.
+A main difference between build logs and system logs is that system logs are fundamentally structured through events.
+Each line in a log file represents one event with a set of fields: timestamp, verbosity level and raw message content~\cite{he2017towards}.
+Figure \ref{lst:system-log} shows example lines from a system log.
+
+The first goal in parsing system log files is to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
+Next, the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
+The output of a log parser is a structured log, composed of a list of timed events and the corresponding parameter values~\cite{he2016evaluation}.
+This structured log is then the input to various machine learning and data mining processes.
+Researchers mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
+Xu et al.~\cite{xu2009detecting} leverage the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
+
+The techniques developed for system log analysis can also be applied to build logs.
+One example is comparing execution traces to reference traces of intended behavior to detect anomalies.
+Amar et al.~\cite{amar2019mining} employed a similar approach to detect relevant lines in build logs.
+
+Classic log parsers interpret the whole log file into a sequence of events.
+A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
+In this thesis we take a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
+Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+
+\lstset{
+  morekeywords={INFO, WARN, 2008-11-09},
+  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
+  showspaces=false,
+  showstringspaces=false,
+  keywordstyle=\color{blue},
+	frame=single,
+  extendedchars=false,
+  texcl=false
+}
+\begin{figure}[!t]
+  \centering
+  \begin{lstlisting}[breaklines=true]
+2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet- Responder: Received block blk_3587508140051953248 of size 67108864 from /10.251.42.84
+2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140051953248 terminating
+  \end{lstlisting}  
+  \caption{System Log Statements. Example adapted from~\cite{he2017towards}.}
+  \label{lst:system-log}
+\end{figure}
+
+\subsection{Program Synthesis by Example}
+% \section{Information Extraction and Retrieval Techniques}
+The techniques we investigate are based on existing methods of Programming by Example, information extraction and information retrieval.
+This section presents different Programming by Example resources surrounding the PROSE library.
+We explain its generic program synthesis algorithm and how PROSE synthesizes text extraction programs, the foundation of PBE\@.
+\label{sec:rw-prose}
+Programming by Example enables end users to automate repetitive tasks.
+The user provides examples for the input and the corresponding output and a synthesis algorithm tries to create the program intended by the user.
+This section introduces the theoretical foundations of the program synthesis algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
+The PROSE framework is developed by Microsoft Research.
+Next, this section presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
+Finally, we cover additional applications and extensions of the PROSE program synthesis and alternative research on generating regular expressions from examples.
+
+\subsubsection{FlashMeta: Inductive Program Synthesis}
+The FlashMeta framework presented by Polozov and Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program synthesis in the Microsoft PROSE framework.
+FlashMeta separates the inductive synthesis algorithm from the domain specific capabilities of the desired program by encoding the possible program space in a domain specific language (DSL).
+The user specifies the desired program behavior by providing in/output examples (I/O examples).
+FlashMeta uses \emph{witness functions}, provided by the DSL, to divide the synthesis into smaller subtasks.
+For each of these subtasks it enumerates all possible programs that solve the subtask consistent with the set of I/O examples.
+A program is consistent with a set of I/O examples if, for each input example, it produces the corresponding output~\cite{mitchell1982generalization}.
+The possible subprograms are joined and stored in a \emph{version space algebra} (VSA)~\cite{mitchell1982generalization}.
+This a tree structure, which space-efficiently saves candidate programs for tasks by sharing common subexpressions.
+Next, FlashMeta ranks the enumerated programs according to which ones the user most likely intended.
+The DSL also provides the ranking characteristics.
+From the ranked VSA, FlashMeta can then return a ranked list of complete programs consistent with the user's example.
+
+In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples.
+Negative input examples should not be processed by the synthesized program.
+
+The different applications of PROSE presented in the following paragraphs were all eventually implemented as DSLs for the FlashMeta synthesis algorithm.
+
+\subsubsection{FlashExtract: Data Extraction by Example}
+Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL for the Microsoft PROSE framework.
+It enables a user to define text extraction programs for text, websites and spreadsheets by giving I/O examples.
+FlashExtract's instantiation for text synthesizes extraction programs from semi-structured text based on regular expressions.
+Users can extract multiple fields and structure them with hierarchy and sequence.
+FlashExtract synthesizes programs to extract each of the fields leveraging the information about hierarchical containment and sequentiality.
+It eliminates the need for the user to understand the entire structure of the processed document and decreases the effort of developing a suitable extraction program.
+
+The text instantiation of FlashExtract models the extraction of a single substring as a pair of two cut positions.
+A position is either specified by an absolute character index or by a pair of two regular expressions.
+The first regular expression matches the substring directly before the characterized position, the second regular expression matches the substring directly after.
+A regular expression in FlashExtract is a concatenation of tokens, e.g.\ standard character classes or string literals frequently occurring in the input examples.
+Figure \ref{lst:prose-program} shows a text extraction program synthesized by FlashExtract.
+This program defines the first position as after a colon followed by a newline character and before a piece of text with all capital letters.
+It defines the second position as before two newline characters.
+
+Apart from automatic completion in Excel spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for two other Microsoft product features:
+Microsoft's system log analysis tool Azure Monitor lets users define custom log fields~\cite{azure2019custom}.
+The ConvertFrom-String function in PowerShell allows a user to specify an example template to extract hierarchical data from a text document~\cite{powershell2019convert}.
+
+We apply the text instantiation of FlashExtract to the domain of build logs with our chunk retrieval technique PBE\@.
+
+\lstset{
+  language=caml,
+  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
+  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
+  showspaces=false,
+  showstringspaces=false,
+  stringstyle=\color{blue},
+  keywordstyle=\bfseries\color{black},
+	frame=single,
+  extendedchars=false,
+  escapeinside=//
+}
+\begin{figure}[!t]
+  \centering
+  \begin{lstlisting}[breaklines=true]
+let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
+  \end{lstlisting}  
+  \caption{Text extraction program synthesized by FlashExtract.}
+  \label{lst:prose-program}
+\end{figure}
+
 \section{Chunk Retrieval Techniques}
-general: what is a chunk retrieval technique
+\label{sec:techniques}
+This chapter introduces the concept of chunk retrieval techniques.
+We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
+This chapter first presents how a build log, which we take as input to the chunk retrieval, is created by a continuous integration (CI) build.
+Next, the chapter describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
+We illustrate why it is useful to extract the presented information chunks.
+The following section introduces our concept of chunk retrieval techniques.
+We present the three chunk retrieval techniques we investigate in this thesis:
+program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
 
-should I include the "how is a build log generated" and (some of, one) the examples for retrievable information?
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=\columnwidth, clip]{img/build-overview.pdf}
+	\caption{The different entities related to a CI build.}
+	\label{fig:build-overview}
+\end{figure}
+
+\subsection{Characteristics of Chunk Retrieval Techniques}
+\label{sec:blirt}
+For this thesis, we want to evaluate different techniques to retrieve information chunks from build logs, which we call \emph{chunk retrieval techniques}.
+The techniques we investigate do not require to parse the structure of a whole build log, but focus on extracting just one specific information.
+
+The user provides a \textit{configuration} that specifies which information the chunk retrieval should target and supplies the necessary information for the technique to identify the targeted information chunk in a build log.
+Each chunk retrieval has a specific \textit{granularity}, i.e.\ the smallest retrievable text piece and uses a specific \textit{identification technique} to select the log parts it retrieves.
+Each configuration addresses a specific \textit{scope}.
+The scope can be a specific project, a tool involved in the build, a programming language or global, when configuring a retrieval technique for all possible build logs.
+A \emph{run} of a chunk retrieval technique consumes a build log as a plain text file and produces a string output, which consists of substrings of the build log text.
+
+The following sections of this chapter introduce the three chunk retrieval techniques we investigate: program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
+Lastly we describe other techniques which can also be treated as chunk retrieval techniques.
+Table~\ref{tab:ctr} shows a comparison of the presented techniques.
+
+\begin{table}[]
+\centering
+\caption{Overview of the described chunk retrieval techniques.}
+\begin{tabularx}{\columnwidth}{@{}XlXlX@{}} 
+\toprule
+Name                         & Acronym & Identification Technique                                   & Granularity & Configuration             \\ 
+\midrule
+Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
+Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
+Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
+Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
+Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
+\bottomrule
+\end{tabularx}
+\label{tab:ctr}
+\end{table}
 
 \subsection{Program Synthesis by Example (PBE)}
-like in thesis
+\label{sec:expl-pbe}
+\emph{Programming by Example} is a technique which synthesizes programs according to in- and output examples provided by the user.
+It enables users to create programs without a priori programming knowledge~\cite{mayer2015user}.
+In the context of text extraction through regular expressions, Programming by Example relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
+In this work, we refer to our interpretation of Programming by Example as \emph{PBE}\@.
+We investigate the suitability of PBE to retrieve information chunks from build logs.
+In the following, we explain the configuration and application of PBE to chunk retrieval from CI build logs.
+
+\subsubsection{Configuration}
+In/output examples are the main driver of Programming by Example.
+We refer to in/output examples as \emph{examples}.
+When retrieving information chunks from build logs the \emph{input} is a whole build log, i.e.\ the whole text of the build log file.
+The \emph{output} is a substring of the log file text, representing the substring that should be retrieved by the synthesized program when given the corresponding input file.
+One or multiple examples, the training examples, configure a chunk retrieval with PBE: they define the substring of a build log that should be extracted.
+The PROSE program synthesis then tries to construct a regular expression program consistent with all training examples.
+A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
+PBE reports an error back to the user if it could not synthesize a consistent program.
+The program synthesis builds on the FlashExtract DSL, which in turn uses the FlashMeta algorithm.
+Both are described in Section~\ref{sec:rw-prose}.
+
+\subsubsection{Application}
+A run of PBE takes a build log file as input and applies the synthesized regular expression program.
+It then returns the substring of the build log matched by the program or an empty string if the program found no match.
+
 \subsection{Common Text Similarity (CTS)}
-like in thesis
+\label{sec:expl-ts}
+Text Similarity approaches are used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+One common and simple technique is the Vector Space Model~\cite{schutze2008introduction}.
+We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
+In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs, which we refer to as \emph{CTS}\@.
+
+\subsubsection{Configuration}
+To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@.
+The lines of the output strings of the training examples define our search query.
+The algorithm splits the search query into single lines and identifies tokens, in our case words.
+Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
+Next, the algorithm applies TF-IDF to the matrix, a best practice for natural language queries~\cite{lee1997document}.
+
+\subsubsection{Application}
+To retrieve the desired information from a build log, we parse the whole text and process it in the same way as the output of the training examples.
+The algorithm calculates the cosine similarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
+After summing up the similarities of each build log line to all search query lines, we sort the build log lines in decreasing similarity.
+The average number of lines in the outputs of the training examples determines how many of the most similar lines are returned as the output of the retrieval run.
+
 \subsection{Keyword Search (KWS)}
-like in thesis
+\label{sec:expl-skws}
+When developers are looking for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is searching for related keywords.
+Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating our \emph{LogChunks} data set.
+As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
+In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.
 
-\section{Empirical Comparsion}
-\subsection{Data Set}
-short explanation of content and reference to the MSR paper
+\subsubsection{Configuration}
+A set of keywords configures the chunk retrieval with KWS\@.
+To better compare KWS with PBE and CTS, we also configure it through examples.
+We link each example with keywords, which appear in the targeted chunk or close to it in the input build log.
+The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.
+
+\subsubsection{Application}
+For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the keywords.
+As keywords are often not directly describing the desired information, but rather appear close to the desired information, KWS also retrieves the lines around the found keyword.
+The number of surrounding lines retrieved is the average of lines in the output of the training examples.
+
+\subsection{Other Techniques}
+\label{sec:expl-rlr}
+%Literature mentions further build log analysis techniques.
+%This section describes them with our notion of chunk retrieval techniques.
+
+\subsubsection{Log Diff}
+Amar et al.\ use a technique based on line diffs and information retrieval to identify relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
+The configuration for the technique is the log from the last successful build and relevant past failures.
+This technique retrieves the lines from a build log that are not present in the successful build log and contain terms related to the given past failures.
+
+\subsubsection{Random Line Retrieval (RLR)}
+In our evaluation, we want to compare against a baseline of randomly extracted lines.
+The average number of lines in the outputs of the training examples is the configuration for random line retrieval (RLR).
+It retrieves this number of lines randomly sampled from the build log.
+
 \subsection{Tool Implementation}
-stating that (and in which languages) we implemented the techniques (will be very short, integrate somewhere else?)
-\subsection{Study Design}
-like in thesis
-\subsection{Results}
-like in thesis?
+For our comparison study we implemented PBE, CTS, KWS and RLR and a unifying interface.
+The unified interface is implemented in Ruby and calls the separate technique implementations over the command line.
+The implementation of PBE in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
+We implemented CTS, KWS and RLR using R and the text2vec library~\cite{text2vec2019webpage}.
 
-less plots! -> can I only mention the results and just not show the plots showing then?
+\section{Study Design}
+\label{sec:study}
+To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluate them on the \emph{LogChunks} data set.
+\todo{cite dataset}
+\todo{adapt glue text}
+This chapter describes our study design and which metrics we measure to answer our research questions.
+In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.
+
+\todo{move implementation here?}
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[page=2, width=\columnwidth, trim={0cm 1cm 1.5cm 0.5cm}, clip]{img/overview-graphics.pdf}
+	\caption{Study design of our technique comparison study.}
+	\label{fig:study}
+\end{figure}
+
+\begin{simplebox}{Research Questions}
+\begin{itemize}
+  \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
+  \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
+  \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
+  \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
+  \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
+\end{itemize}
+\end{simplebox}
+
+For the comparison, we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe}, \ref{sec:expl-ts} and \ref{sec:expl-skws}.
+Random Line Retrieval (RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
+We run four techniques on the examples from \emph{LogChunks}.
+
+\paragraph{Training and Test Set}
+We use \emph{LogChunks} as the data set for our study.
+For each one of 80 repositories it contains about 10 build logs, manually labeled with the substring describing the reason the build failed.
+In addition to that, it contains keywords to search for that substring and which structural category the substring belongs to.
+
+For each repository in \emph{LogChunks}, we split the examples chronologically into training and test set.
+Therefore, we train on examples from past build logs and test on more recent build logs.
+
+\paragraph{RQ 2.1: Size of Training and Test Set}
+To analyze how many examples the chunk retrieval techniques need to perform best, we evaluate the techniques with different training set sizes.
+We train each technique with one to five examples from each of the repositories within \emph{LogChunks}.
+The size of the test set is one.
+
+\paragraph{RQ 2.2: Recording Structural Categories}
+To determine how structurally similar the examples for the chunk retrieval techniques need to be, we record the structural categories of the examples in the training and test sets.
+
+\paragraph{RQ2.3: Accuracy Metrics}
+To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($\mathit{RetrievedLines}$).
+As oracle in our evaluation, we save the desired lines from the output of the test example ($\mathit{DesiredLines}$).
+
+We calculate the following metrics:
+\begin{itemize}
+	 \itemsep0.75em
+	\item True positives: $\mathit{DesiredLines} \cap \mathit{RetrievedLines}$
+	\item Precision: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{RetrievedLines}}$
+	\item Recall: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{DesiredLines}}$
+	\item F$_{1}$-score: $2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
+	\item Successful retrieval: $\mathit{true}\ \mathit{if}\ \mathit{Recall} = 1$
+\end{itemize}
+
+Precision of a chunk retrieval describes which proportion of the retrieved lines were desired.
+Recall of a chunk retrieval describes which proportion of the targeted lines were retrieved.
+Throughout the presentation and discussion of our results we show these two metrics separately, as they might have a different weight when choosing a suitable technique for a task.
+In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall.
+We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
+
+Recall and precision of CTS and KWS vary with the number of lines selected for retrieval.
+We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the training examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
+
+\section{Results}
+This section presents the results for PBE, CTS and KWS separately.
+Afterwards we compare the three techniques with each other and RLR as baseline.
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-PBE.pdf}
+		\caption{Results of chunk retrieval with PBE.}
+		\label{fig:failure-reason-PBE}
+\end{figure}
+
+\lstset{
+  morekeywords={Test Output, Desired Test Output},
+  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
+  showspaces=false,
+  showstringspaces=false,
+  keywordstyle=\color{blue},
+	frame=single,
+  extendedchars=false,
+  texcl=false
+}
+\begin{figure}[!t]
+  \centering
+  \begin{lstlisting}[breaklines=true]
+Test Output:
+Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
+        on line 86 of sass/components/dropdown.sass   
+Desired Test Output:
+Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
+        on line 86 of sass/components/dropdown.sass
+        from line 5 of sass/components/_all.sass
+        from line 6 of bulma.sass
+  \end{lstlisting}  
+  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
+  \label{lst:pbe-unsuccessful}
+\end{figure}
+
+\subsection{Program Synthesis by Example (PBE)}
+Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
+Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
+In 89 further cases a program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output at all.
+In 30 of the 89 cases the synthesized program did not extract all of the desired lines.
+For these 30 cases, the average recall was 28\%.
+We present an example of such an \emph{unsuccessful retrieval} in Listing \ref{lst:pbe-unsuccessful}, where the synthesized regular expression program only retrieved two of the four targeted lines.
+In 173 of the 400 cases the PROSE program synthesis could not synthesize a regular expression program that is consistent with all of the training examples.
+
+Figure~\ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training and test examples.
+It shows that the program synthesis is more likely to succeed when there are only a few categories present in the training examples.
+When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all training examples.
+For three or more present categories PROSE could never synthesize a consistent program.
+
+Figure~\ref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of the 227 runs where PBE could synthesize a program consistent with all training examples.
+When the training set size increases from one to two, recall and F$_{1}$-score increase by about 25\%, precision increases by about 10\%.
+For two or more training examples, recall and F$_{1}$-score stay around 75\% and precision around 96\%.
+
+\subsection{Common Text Similarity (CTS)}
+Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision, recall and F$_{1}$-score of chunk retrieval using CTS for an increasing number of training examples.
+When using one to five training examples, the size of the training set has no noticeable influence on precision, recall or F$_{1}$-score of the chunk retrieval with CTS.
+
+Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for an increasing number of structural categories in the training and test examples.
+With increasing category count, precision, recall and F$_{1}$-score decrease.
+Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.
+
+Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with CTS\@.
+The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
+The recall ranges from 30\% to 55\%.
+A retrieval size factor of 1 gives the best average F$_{1}$-score with 51\%.
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+		\caption{Results of chunk retrieval with PBE for an increasing number of structural categories in the training and test sets.}
+		\label{fig:failure-reason-categorycount-PBE}
+\end{figure}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set.}
+		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
+\end{figure}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing training set size.}
+		\label{fig:recall-precision-examplecount-CTS}
+\end{figure}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing number of structural categories in the training and test sets.}
+		\label{fig:recall-precision-categorycount-CTS}
+\end{figure}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS compared to retrieval size factors.}
+		\label{fig:contextsizefactor-precision-recall-CTS}
+\end{figure}
+
+\subsection{Keyword Search (KWS)}
+Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision, recall and F$_{1}$-score of chunk retrieval using KWS for different numbers of training examples.
+The recall increases by about 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
+The F$_{1}$-score stays around 26\%.
+
+Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for an increasing number of structural categories in the training and test examples.
+For more than one structural category in the training and test examples the recall decreases by about 20\% and the precision decreases about 6\%.
+For more than two structural categories no clear trend is visible in precision, recall or F$_{1}$-score for an increasing amount of categories in the training and test examples.
+
+Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
+The precision is 19\% when retrieving half of the expected number of lines. On average 9\% of the lines in the build log are retrieved then.
+When 2.5 times the expected number of lines are retrieved, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
+The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for an increasing training set size.}
+		\label{fig:recall-precision-examplecount-KWS}
+\end{figure}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for an increasing number of structural categories in the training and test sets.}
+		\label{fig:recall-precision-categorycount-KWS}
+\end{figure}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
+		\label{fig:contextsizefactor-precision-recall-KWS}
+\end{figure}
+
+\subsection{Comparison of All Techniques}
+Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval by the different techniques in our study.
+CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
+With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
+PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.
+
+The averaged precision, recall and F$_{1}$-score f all techniques is compared in Figure~\ref{fig:recall-precision-all}.
+The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
+PBE has the highest average precision with 95\%.
+Chunk retrieval with CTS has the highest average F$_{1}$-score with 51\% and the second highest recall with 46\%.
+KWS has the smallest precision of the three chunk retrieval techniques.
+With 16\% it is still higher than the precision of the RLR baseline with 7\%.
+KWS has the highest recall of all techniques with 70\%.
+
+Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
+For more than one present category, the recall of PBE decreases greatly.
+For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
+		\caption{Success of chunk retrievals for all techniques.}
+		\label{fig:success-partial-all}
+\end{figure}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-all.pdf}
+		\caption{Precision, recall and F$_{1}$-score of all techniques compared.}
+		\label{fig:recall-precision-all}
+\end{figure}
+
+\begin{figure}[!t]
+	\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
+		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{one} structural category.}
+		\label{fig:recall-precision-singlecategory-all}
+\end{figure}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
+		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{more than one} structural categories.}
+		\label{fig:recall-precision-multicategory-all}
+\end{figure}
 
 \section{Discussion}
-like in thesis - table and explanation
-\subsection{Program Synthesis by Example (PBE)}
-like in thesis
-\subsection{Common Text Similarity (CTS)}
-like in thesis
-\subsection{Keyword Search (KWS)}
-like in thesis
-\subsection{Recommendation of a Suitable Technique}
-like in thesis - decision tree
+\label{sec:discussion}
+
+This chapter presents the answers to our research questions:
+\begin{simplebox}{Research Questions}
+\begin{itemize}
+ \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
+  \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
+  \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
+  \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
+  \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
+\end{itemize}
+\end{simplebox}
+
+The first section discusses for PBE, CTS and KWS separately in which cases they perform best.
+It details for which types of input build logs, available training examples and consumption of the retrieved output each technique is suited.
+In the following section we discuss which of these criteria should influence the decision to use a certain technique most.
+Based on our empirical comparison, we present a decision tree between the three techniques we investigated.
+
+\subsection{Interpretation of Study Results}
+This section discusses the study results for each of the analyzed chunk retrieval techniques separately.
+It gives recommendations which kind of information chunk targets are best for each technique and for what kind of usage the respective output is suitable.
+
+\begin{table}[tbp]
+\centering
+\begin{tabularx}{\columnwidth}{@{}llll@{}}
+  \toprule
+  & PBE & CTS & KWS \\
+  \midrule
+  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
+  Training Set Size & 2 & no influence & 2 \\ 
+  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
+  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
+  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
+  Output Consumption by & program & human & human \\ 
+  \bottomrule
+\end{tabularx}
+\caption{Recommendations for each of the investigated chunk retrieval techniques.}
+\label{tab:single-technique-recommendations}
+\end{table}
+
+\subsubsection{Program Synthesis by Example (PBE)}
+
+\paragraph{Configuration and Input}
+Our study results show that chunk retrieval with PBE gives best results when the training examples are from one structural category.
+This means it is suited to retrieve information chunks that always have the same surrounding structure.
+To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.
+
+When the training examples are of the same structure, two examples are enough input for PROSE to synthesize a regular expression program with good recall.
+In our study, additional training examples did not improve the chunk retrieval.
+
+\paragraph{Retrieval Output Usage}
+If the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and a high recall.
+The tool clearly identifies a failing program synthesis or when no output from the program applied to a build log is obtained.
+Therefore, if there is an output, the user can have high confidence that it is the correct output.
+This makes output from PBE chunk retrieval well suited for consumption by other software components.
+
+\subsubsection{Common Text Similarity (CTS)}
+\paragraph{Configuration and Input}
+Chunk retrieval using CTS also yields better results the fewer structural categories are present in the training and test examples.
+
+The number of training examples had no noticeable influence on precision or recall in our study.
+Information retrieval techniques like text similarity commonly learn on a higher number of examples than used for our study.
+Future work is needed to investigate how many examples yield improvements in the chunk retrieval over a single training example.
+
+Extracting the average number of lines present in the training examples gives the best retrieval results for CTS, according to the F$_{1}$-score.
+
+\paragraph{Retrieval Output Usage}
+CTS has good precision and recall on average, though the precision or recall of a chunk retrieval run is very hard to predict from the given result.
+Therefore, retrieval output from CTS is suited to be read by a human.
+
+\subsubsection{Keyword Search (KWS)}
+\paragraph{Configuration and Input}
+KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
+This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.
+For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
+
+With two training examples KWS achieves good recall.
+
+Retrieving the average number of lines present in the outputs of the training examples around every found keyword yields reasonable recall.
+Selecting 1.5 times as many lines around every found keyword does improve the recall within our study but also increases the proportion of lines retrieved overall and therefore decreases precision.
+
+\paragraph{Retrieval Output Usage}
+Even though KWS has the highest recall of all three techniques, its precision is also the lowest.
+The output of a chunk retrieval with KWS is well suited to be read by humans.
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
+		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
+		\label{fig:crt-recommendation}
+\end{figure}
+
+\subsection{Recommendations of Suitable Techniques}
+After discussing the three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
+We present a decision tree, which developers and researchers who want to retrieve information chunks from build logs can follow.
+The decision tree is built up of questions which either lead to more questions or to a leaf node containing a recommended technique.
+Figure~\ref{fig:crt-recommendation} presents the decision tree.
+
+\emph{Caveat!} This is a preliminary theory based on the results from our comparison study.
+The recommendations are therefore based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
+
+This decision tree is the answer to our first research question about which criteria influence the suitability of a chunk retrieval technique.
+The earlier in the decision tree a criterion is noted, the more important it is when distinguishing the techniques.
+
+The first and most important aspect are the structural categories.
+Are the information chunks you would like to retrieve always presented in the same structural way within the build logs?
+Then the information chunks in all training examples and the analyzed build log are in the same structural category.
+
+If the information chunks are from multiple structural categories, i.e.
+they are not represented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS\@.
+If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
+We also recommend CTS when the representations are from one structural category, when the user does not require a high confidence in the precision or recall of the outcome and when the user would rather have output with low recall instead of no output at all.
+When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.
+
+\subsubsection{Example of Using the Recommendation Scheme}
+To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we describe two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.
+
+In our first example, a researcher studies whether test failures in CI are caused by a small or by a large group of test cases.
+They gather CI build logs from various projects, which are their only available data source.
+The task of the researcher is to extract the names of the failing test cases from each build log.
+When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test cases is in the investigated build logs.
+As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, non-predictable structural representations.
+The next question is whether they value precision over recall.
+As they have to manually inspect the results of both CTS and KWS, they choose recall over precision to avoid having to inspect the whole log in case the relevant information chunk was not retrieved.
+Therefore, our decision tree recommends them to use KWS\@.
+
+In case the researcher wants to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
+Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each test tool separately.
+
+In our second example, a software development team wants to monitor the performance of the phases within their CI build.
+They are using Travis CI, which measures the duration of build phases and documents them within the build log.
+As all log statements that report timing measurements are formatted the same way, the targeted log chunks are from one structural category.
+Therefore the development team can use PBE to retrieve the duration of a build phase as well as its name.
 
 \section{Threats to Validity}
-like in thesis
+There are several threats to the validity of the conclusions of our work.
+
+\subsection{Implementation}
+Our results are highly dependent on our implementation of the investigated chunk retrieval techniques and the libraries we used.
+Our implementation of PBE is severely based on the program synthesis provided by PROSE\@.
+Its limitations are therefore also mainly influenced by this library.
+For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
+This limitation was necessary to keep the synthesis performance reasonable.
+
+Our implementation of CTS is dependent on the library tex2vec and the way they split strings into word tokens.
+We intentionally chose a simple, minimally configured and tuned approach to compare against.
+Tuning the text similarity meta-parameters more to the specific use case of chunk retrieval from build logs would yield better chunk retrieval results.
+
+\subsection{Data Set}
+The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
+It only consists of build logs from open source projects and therefore it is not clear whether our results are generalizable to industry projects.
+We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
+This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI environment.
+
+\subsection{Training Set Size}
+Especially the results for CTS might be influenced by the fact that we only trained on one to five examples.
+We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.
+
+\subsection{Few Samples with Many Structural Categories}
+Our comparison study shows fewer measurements with many structural categories than with one category.
+This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.
 
 \section{Conclusion and Future Work}
-like in thesis
+\label{sec:conclusion-fw}
+The goal of this thesis was to support researchers and developers in their decision on how to analyze build logs.
+We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
+Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
+Secondary factors are the desired confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.
+
+There are various future research opportunities based on our work:
+\begin{itemize}
+  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set specifically for our comparative study, though it can be the basis for various further analyses of build log data.
+  The keywords, for example, can be investigated to answer which keywords are used to search for the reason the build failed within build logs.
+  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
+  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment-agnostic analysis tools.
+  \item \textbf{Comparison with more Chunk Retrieval Techniques} This thesis investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
+  Our study design can be reused to evaluate other build log analysis techniques, such as the diff and information retrieval approach by Amar et al.~\cite{amar2019mining}.
+  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
+  In a next step, each of these techniques could be refined to better approach the domain of build logs.
+  The \emph{LogChunks} data set and our study results act as a baseline to benchmark such technique improvements.
+  We propose the following improvements:
+    \begin{itemize}
+      \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
+      One could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
+      FlashExtract includes special tokens when enumerating possible regular expressions.
+      One could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
+      \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
+      We propose to further investigate improvements in preprocessing of the log text, in tokenization of the log lines into terms and in stop words lists.
+    \end{itemize}
+  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focuses on precision and recall.
+  We propose to investigate how useful these outputs are to developers through controlled experiments.
+\end{itemize}

### 2020-03-03 tse-paper/abstract.tex
include loads of text and graphics from thesis, fix graphics, start adapting heading levels

@@
-Software builds from continuous integration produce detailed logs about the status and results of the various tools involved in the build.
-These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps or understand the cause of a build failure.
-However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
-This makes it hard to process and analyze them.
-In this paper, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
-We conduct an empirical study by comparing these techniques on the \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.
-Our findings show that none of the three techniques clearly outperforms the others.
-We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.
+Build logs are textual by-products that a software build process
+creates, often as part of its Continuous Integration (CI)
+pipeline. Build logs are a paramount source of information for
+developers when debugging into and understanding a build
+failure. Recently, attempts to partly automate this time-consuming,
+purely manual activity have come up, such as rule- or
+information-retrieval-based techniques.
+
+We evaluate and compare three different techniques that aim to retrieve
+specified log parts (chunks) from a build log, namely program synthesis
+by example, textual similarity and search keywords.
+We conduct an empirical study by comparing these techniques on the manually
+labeled \emph{LogChunks} data set.
+Our findings show that none of the three techniques in general outperforms
+the others. We discuss under which circumstances each technique performs best
+and provide a recommendation on when developers or researchers should use which
+technique.
+
+% Software builds from continuous integration produce detailed logs about the status and results of the various tools involved in the build.
+% These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps or understand the cause of a build failure.
+% However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
+% This makes it hard to process and analyze them.
+% In this paper, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
+% We conduct an empirical study by comparing these techniques on the \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.
+% Our findings show that none of the three techniques clearly outperforms the others.
+% We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.

### 2020-03-05 msr-paper/paper.tex
include loads of text and graphics from thesis, fix graphics, start adapting heading levels
proposing some adjustments from reviewer feedback

@@
 \Cref{fig:lc-overview} how we created \logchunks. All steps are
-automatized as Ruby scripts\footnote{Data collection scripts and their original parameterization are included in the data set.} and highly configurable.
+automatized as Ruby scripts\footnote{Data collection scripts and their original 
+parameterization are included in the data set.} and highly configurable.
 
@@
 
-For \logchunks, we queried GHTorrent on 2018-04-01 for the three
-most popular repositories of each of the 30 most popular languages.
+For \logchunks, we queried GHTorrent from 2018-04-01 for the three
+most popular repositories of each of the 30 most popular languages
+to cover a broad range of development languages.
 Among the resulting repositories are, for example, \texttt{git/git},
@@
 \paragraph{Build Sampling}
-To sample the builds for \logchunks we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
+To sample the builds for \logchunks we keep the most recent ten of the status 
+\emph{failed}~\cite{travis2009buildstatus}. We check up to 1,000 builds per 
+repository to ensure predictable termination of the log collection.
 %A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
@@
 \paragraph{Results}
-In total, from 2020-10-15 to 2020-10-17, we sent out emails to 246 developers. Of these, 32 could
+In total, from 2019-10-15 to 2019-10-17, we sent out emails to 246 developers. Of these, 32 could
 not be delivered.

### 2020-03-09 tse-paper/content2.tex
try to concept new introduction, more heading fixes

CI important and widespreach

buildlogs valuable source of information, for devs and researchers

use for many applications -> msr mining chanllenge

though verbose and large -> inadequate for direct consumption

need to retrieve the parts of the logs relevant to 'user', introduce chunks work

-> tools used to retrieve log chunks

however! tedios to develop -> small range of languages spanned

This paper presents a novel technique to retrieve chunks from build logs based
on programming by example. In addition we design and execute an empirical study
on the \emph{LogChunks} data set
to gauge the performance of the novel technique (PBE).
We aim to compare PBE against a common text
similariy measure and keyword search. \todo{eeeeehm}
\todo{difficulty: quite different techniques which are employed to solve a similar
problem -> our contribution: a design and set of metrics to evaluate their performance}

This paper starts by detailing how we applied Programming by Example to the
area of chunk retrieval from build logs using the Microsoft PROSE library.
We present our learnings about the
training input, what you can expect from the output and for which use cases you
could apply Programming by Example in your own field.
Following we illustrate the design and results of our empirical comparison study.
We discuss the results and the methodological obstacles we were found when
trying to compare very diverse techniques addressing the same task.

\textbf{Our work contributes:}
\begin{itemize}
  \item 
\end{itemize}

\todo{RQs?}

\section{Retrieving Chunks from Logs with Programming by Example}
\todo{show and explain examples from defense talk}
Input: in/output examples
then: synthesis of regex program
output: regex program

\subsection{Wins}

\subsection{Caveats and Downsides}

\subsection{Applying Prgramming by Example to other areas}

\section{Empirical Comparsion}

### 2020-03-09 tse-paper/content.tex
try to concept new introduction, more heading fixes

@@
+\textbf{Motivation.}
 Continuous Integration (CI) has become a common practice in software
@@
 
-\textbf{Motivation.} The information stored in build logs can and has
+CI builds produce logs which report the results of the steps within the build. The information stored in build logs can and has
 already been used for a variety of applications. One prominent dataset
@@
 
-The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
-We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
+The goal of this paper is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
+We aim to characterize different chunk retrieval techniques.
 For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
@@
 
-\paragraph{Our work contributes:}
+\noindent
+\textbf{Our work contributes:}
 \begin{itemize}
@@
           \item a keyword search approach (KWS).
-        \end{itemize}
-  \item A validated data set of about 800 logs from failed Travis CI builds manually-labelled with:
-        \begin{itemize}
-          \item the substring of the log describing the reason the build failed,
-          \item keywords we would use to search for these substrings, and
-          \item a categorization of the substrings according to their structural representation within the build log.
         \end{itemize}
@@
 \section{Related Work}
-\begin{itemize}
-	\item CI research? could show how researchers could use chunk retrieval for existing studies (then I would only mention studies that do build log analysis)
-	\item build log augmentation (BART paper, ICSE Amar et al.)
-	\item ``foundational techniques'', e.g. explaining how PROSE synthesis algorithm works, I would move to the explanation of the method
-\end{itemize}
-
 \label{sec:rw}
-This chapter presents various research works adjacent or foundational to our work.
-The first section presents existing work in the field of continuous integration (CI) and showcases how researchers analyze build logs.
-In the second section we describe the existing methods which are the foundation for the chunk retrieval techniques we investigate.
-
-\subsection{Continuous Integration and Build Logs}
-We describe existing studies about CI to show that CI is a relevant topic within the software engineering research community.
 We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
 This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we analyze in this thesis.
+The presented approaches are related to and can benefit from the techniques we analyze in this paper.
 Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.
+% In this section we cover previous works on CI and how resarchers use the
+% information within build logs to investigate software engineering processes and
+% support developers.
 
-\subsubsection{Build Failures in CI}
+\subsection{Build Failures in CI}
 Various researchers look into why CI builds fail and into the impact of build failures on the development workflow.
+
 Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
 In addition, they notice that most failures are resolved within two builds.
+They based their analyses on sets of build logs collected from industry partners.
+They develop a custom parser to classify error messages reported by Java and C++ builds.
+
 Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and find that most builds fail because of failing tests.
@@
 Rausch et al.'s data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
+
 Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
@@
 Open source builds fail most often because of unit tests, whereas release preparations are the primary cause in industrial projects.
+Their data stems from analyzing build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent} with regular expressions.
 
-\subsubsection{Supporting Log Analysis with Chunk Retrieval}
+Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
+They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
+Their analysis starts with manual categorization of build logs.
+They select keywords and strings that identify their targeted categories and code a script to automatically classify logs based on these keywords.
+
+\noindent
+\textbf{Supporting Log Analysis with Chunk Retrieval}
 To leverage the valuable information within build logs the researchers presented in this section build parsers and regular expression-based programs.
-This task of retrieving specific chunks of text from the build logs can be solved by the chunk retrieval techniques we compare in this thesis.
+This task of retrieving specific chunks of text from the build logs can be solved by the chunk retrieval techniques we compare in this paper.
 Our results can support researchers in choosing a suitable technique for their data set of build logs and the chunks they want to retrieve.
@@
 Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this thesis can be used to fill similar structured representations with information from build logs.
+The chunk retrieval techniques we compare in this paper can be used to fill similar structured representations with information from build logs.
 As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.
@@
 The additional layer can answer queries and give access to the semi-structured data relevant to a query.
-In contrast to that, this thesis takes a look at techniques to gather a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.
+In contrast to that, this paper takes a look at techniques to gather a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.
 
@@
 A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
-In this thesis we take a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
+In this paper we take a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
 Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
@@
 The following section introduces our concept of chunk retrieval techniques.
-We present the three chunk retrieval techniques we investigate in this thesis:
+We present the three chunk retrieval techniques we investigate in this paper:
 program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
@@
 \label{sec:blirt}
-For this thesis, we want to evaluate different techniques to retrieve information chunks from build logs, which we call \emph{chunk retrieval techniques}.
+For this paper, we want to evaluate different techniques to retrieve information chunks from build logs, which we call \emph{chunk retrieval techniques}.
 The techniques we investigate do not require to parse the structure of a whole build log, but focus on extracting just one specific information.
@@
 In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.
-
-\todo{move implementation here?}
 
@@
 
-\paragraph{Configuration and Input}
+\noindent
+\textbf{Configuration and Input}
 Our study results show that chunk retrieval with PBE gives best results when the training examples are from one structural category.
@@
 
-\paragraph{Retrieval Output Usage}
+\noindent
+\textbf{Retrieval Output Usage}
 If the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and a high recall.
@@
 \subsubsection{Common Text Similarity (CTS)}
-\paragraph{Configuration and Input}
+\noindent
+\textbf{Configuration and Input}
 Chunk retrieval using CTS also yields better results the fewer structural categories are present in the training and test examples.
@@
 
-\paragraph{Retrieval Output Usage}
+\noindent
+\textbf{Retrieval Output Usage}
 CTS has good precision and recall on average, though the precision or recall of a chunk retrieval run is very hard to predict from the given result.
@@
 \subsubsection{Keyword Search (KWS)}
-\paragraph{Configuration and Input}
+\noindent
+\textbf{Configuration and Input}
 KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
@@
 
-\paragraph{Retrieval Output Usage}
+\noindent
+\textbf{Retrieval Output Usage}
 Even though KWS has the highest recall of all three techniques, its precision is also the lowest.
@@
 
-\emph{Caveat!} This is a preliminary theory based on the results from our comparison study.
+\noindent
+\textbf{Caveat!} This is a preliminary theory based on the results from our comparison study.
 The recommendations are therefore based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
@@
 
-\subsubsection{Example of Using the Recommendation Scheme}
+\noindent
+\textbf{Example of Using the Recommendation Scheme}
 To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we describe two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.
@@
 
-\subsection{Implementation}
+\noindent
+\textbf{Implementation}
 Our results are highly dependent on our implementation of the investigated chunk retrieval techniques and the libraries we used.
@@
 
-\subsection{Data Set}
+\noindent
+\textbf{Data Set}
 The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
@@
 
-\subsection{Training Set Size}
+\noindent
+\textbf{Training Set Size}
 Especially the results for CTS might be influenced by the fact that we only trained on one to five examples.
@@
 
-\subsection{Few Samples with Many Structural Categories}
+\noindent
+\textbf{Few Samples with Many Structural Categories}
 Our comparison study shows fewer measurements with many structural categories than with one category.
@@
 \label{sec:conclusion-fw}
-The goal of this thesis was to support researchers and developers in their decision on how to analyze build logs.
+The goal of this paper was to support researchers and developers in their decision on how to analyze build logs.
 We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
@@
   We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This thesis investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
+  \item \textbf{Comparison with more Chunk Retrieval Techniques} This paper investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
   Our study design can be reused to evaluate other build log analysis techniques, such as the diff and information retrieval approach by Amar et al.~\cite{amar2019mining}.

### 2020-03-09 tse-paper/content.tex
shortening

@@
 how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-To evaluate PBE, CTS and KWS we create a data set, called \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
+To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
 Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
@@
 
-We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in precision and recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
-However, its low precision requires a human to interpret the output of the chunk retrieval.
+We recommend PBE for use cases where the desired information is always
+represented in the same structural way and high confidence in precision and
+recall of the chunk retrieval is required.
+CTS is well suited when the representation of the desired information varies
+slightly and the output of the chunk retrieval is further processed by a human.
+In cases where the textual representation of the desired information in the log
+is unpredictable or varies greatly, KWS is the best technique to choose.
+However, its low precision requires a human to interpret the output of the chunk
+retrieval.
 
@@
 \label{sec:rw}
-We explain how researchers gather information about CI usage in software projects through build log analysis and why the chunk retrieval techniques we investigate simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we analyze in this paper.
-Further, we classify build logs as semi-structured data and differentiate our work from system log analysis.
-% In this section we cover previous works on CI and how resarchers use the
-% information within build logs to investigate software engineering processes and
-% support developers.
+We explain how researchers gather information about CI usage in software projects
+through build log analysis and why the chunk retrieval techniques we investigate
+simplifies their data collection.
+This section moves on to past works about augmenting build logs to make it easier
+for developers to inspect them.
+The presented approaches are related to and can benefit from the techniques we
+analyze in this paper.
+Further, we classify build logs as semi-structured data and differentiate our
+work from system log analysis.
 
@@
 \textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers presented in this section build parsers and regular expression-based programs.
-This task of retrieving specific chunks of text from the build logs can be solved by the chunk retrieval techniques we compare in this paper.
-Our results can support researchers in choosing a suitable technique for their data set of build logs and the chunks they want to retrieve.
-By relieving them from building custom parsers we enable them to cover a much wider range of languages and build tools in their studies.
+To leverage the valuable information within build logs the researchers presented
+in this section create parsers and regular expression-based programs.
+This task of retrieving specific chunks of text from the build logs can be
+solved by the chunk retrieval techniques we compare in this paper.
+Our results can support researchers in choosing a suitable technique for their
+data set of build logs and the chunks they want to retrieve.
+By relieving them from building custom parsers we enable them to cover a much
+wider range of languages and build tools in their studies.
 
@@
 They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
-The hint generators leverage this structured access to the information within the build log to propose fixes.
+%The hint generators leverage this structured access to the information within the build log to propose fixes.
 For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
 In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
-Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
+%Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
 The chunk retrieval techniques we compare in this paper can be used to fill similar structured representations with information from build logs.
@@
 They add fold identifiers around common commands and setup or teardown build phases and collapse the contained lines by default.
-
-\subsection{Build Logs as Semi-Structured Data}
-\label{sec:rw-semi-structured-data}
-Serge Abiteboul introduces a theory of semi-structured data in his report from 1997 about integrating data from several sources~\cite{abiteboul1997querying}.
-He proposes essential characteristics of semi-structured data.
-In this section, we show how five of these map to the context of build logs.
-
-The structure of build logs
-\begin{itemize}
-  \item \textbf{is implicit}.
-  We might not have access to explicit structuring elements or an explicit structure description.
-  Computation is required to infer the present structure.
-  \item \textbf{is irregular}.
-  Changes in the build process or execution environment might change the structure of a build log.
-  We observed this in the logs we collected for the \emph{LogChunks} data set, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
-  Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5} present an example of this.
-  \item \textbf{is partial}. Some parts are highly structured by e.g.\ special characters. Other parts are unstructured, such as natural language text in error messages.
-  \item can be described with an \textbf{analytical data guide} rather than a predefined schema.
-  There is no fixed specification on how build tools structure their output.
-  We later extract structuring patterns in the produced output.
-  \item \textbf{has a rapidly evolving schema}.
-  Modifications in the build configuration can change the tools involved in the build and therefore the composition of the build log.
-  Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adapt their log messages over time~\cite{yuan2012characterizing}.
-\end{itemize}
-
-Abiteboul proposes an approach to overlay the semi-structured data with a structured layer.
-The additional layer can answer queries and give access to the semi-structured data relevant to a query.
-In contrast to that, this paper takes a look at techniques to gather a specific, pre-specified information without the need to parse, understand or estimate the whole structure of a log.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\columnwidth, clip]{img/log42.png}
-	\caption{Excerpt from a build log showing a WarningMessage chunk.}
-	\label{fig:log-4}
-\end{figure}
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\columnwidth, clip]{img/log52.png}
-	\caption{Excerpt from a build log showing a differently formatted WarningMessage chunk.}
-	\label{fig:log-5}
-\end{figure}
 
@@
 This structured log is then the input to various machine learning and data mining processes.
-Researchers mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
-Xu et al.~\cite{xu2009detecting} leverage the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
+%Researchers mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
+%Xu et al.~\cite{xu2009detecting} leverage the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
 
@@
 Amar et al.~\cite{amar2019mining} employed a similar approach to detect relevant lines in build logs.
-
-Classic log parsers interpret the whole log file into a sequence of events.
-A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
-In this paper we take a different approach and focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
+%Classic log parsers interpret the whole log file into a sequence of events.
+%A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
+In this paper we focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
 Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
@@
   morekeywords={INFO, WARN, 2008-11-09},
+	basicstyle=\scriptsize,
   postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
@@
 \subsection{Program Synthesis by Example}
+\label{sec:rw-prose}
 % \section{Information Extraction and Retrieval Techniques}
-The techniques we investigate are based on existing methods of Programming by Example, information extraction and information retrieval.
-This section presents different Programming by Example resources surrounding the PROSE library.
-We explain its generic program synthesis algorithm and how PROSE synthesizes text extraction programs, the foundation of PBE\@.
-\label{sec:rw-prose}
+%The techniques we investigate are based on existing methods of Programming by Example.%, information extraction and information retrieval.
+%This section presents different Programming by Example resources surrounding the PROSE library.
+%We explain its generic program synthesis algorithm and how PROSE synthesizes text extraction programs, the foundation of PBE\@.
+
 Programming by Example enables end users to automate repetitive tasks.
-The user provides examples for the input and the corresponding output and a synthesis algorithm tries to create the program intended by the user.
-This section introduces the theoretical foundations of the program synthesis algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
+The user provides examples for the input and the corresponding output and a
+synthesis algorithm tries to create the program intended by the user.
+This section introduces the theoretical foundations of the program synthesis
+algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
 The PROSE framework is developed by Microsoft Research.
-Next, this section presents the FlashExtract DSL, which defines text extraction tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
-Finally, we cover additional applications and extensions of the PROSE program synthesis and alternative research on generating regular expressions from examples.
+Next, this section presents the FlashExtract DSL, which defines text extraction
+tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
 
@@
 
-In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples.
-Negative input examples should not be processed by the synthesized program.
+% In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples.
+% Negative input examples should not be processed by the synthesized program.
 
-The different applications of PROSE presented in the following paragraphs were all eventually implemented as DSLs for the FlashMeta synthesis algorithm.
+% The different applications of PROSE presented in the following paragraphs were all eventually implemented as DSLs for the FlashMeta synthesis algorithm.
 
@@
 Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL for the Microsoft PROSE framework.
-It enables a user to define text extraction programs for text, websites and spreadsheets by giving I/O examples.
+% It enables a user to define text extraction programs for text, websites and spreadsheets by giving I/O examples.
 FlashExtract's instantiation for text synthesizes extraction programs from semi-structured text based on regular expressions.
 Users can extract multiple fields and structure them with hierarchy and sequence.
-FlashExtract synthesizes programs to extract each of the fields leveraging the information about hierarchical containment and sequentiality.
-It eliminates the need for the user to understand the entire structure of the processed document and decreases the effort of developing a suitable extraction program.
+% FlashExtract synthesizes programs to extract each of the fields leveraging the information about hierarchical containment and sequentiality.
+% It eliminates the need for the user to understand the entire structure of the processed document and decreases the effort of developing a suitable extraction program.
 
-The text instantiation of FlashExtract models the extraction of a single substring as a pair of two cut positions.
+FlashExtract models the extraction of a single substring as a pair of two cut positions.
 A position is either specified by an absolute character index or by a pair of two regular expressions.
@@
   language=caml,
+	basicstyle=\scriptsize,
   morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
@@
 \label{sec:techniques}
-This chapter introduces the concept of chunk retrieval techniques.
+This section introduces the concept of chunk retrieval techniques.
 We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
-This chapter first presents how a build log, which we take as input to the chunk retrieval, is created by a continuous integration (CI) build.
-Next, the chapter describes retrievable information chunks in build logs and gives examples found in Travis CI build logs.
-We illustrate why it is useful to extract the presented information chunks.
-The following section introduces our concept of chunk retrieval techniques.
 We present the three chunk retrieval techniques we investigate in this paper:
@@
 	\includegraphics[width=\columnwidth, clip]{img/build-overview.pdf}
-	\caption{The different entities related to a CI build.}
+	\caption{The different entities related to a CI build. \todo{mention in text or remove}}
 	\label{fig:build-overview}
@@
 
-The following sections of this chapter introduce the three chunk retrieval techniques we investigate: program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
+The following sections of this section introduce the three chunk retrieval techniques we investigate: program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
 Lastly we describe other techniques which can also be treated as chunk retrieval techniques.
@@
 \label{sec:expl-pbe}
-\emph{Programming by Example} is a technique which synthesizes programs according to in- and output examples provided by the user.
-It enables users to create programs without a priori programming knowledge~\cite{mayer2015user}.
-In the context of text extraction through regular expressions, Programming by Example relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
-In this work, we refer to our interpretation of Programming by Example as \emph{PBE}\@.
-We investigate the suitability of PBE to retrieve information chunks from build logs.
-In the following, we explain the configuration and application of PBE to chunk retrieval from CI build logs.
+% \emph{Programming by Example} is a technique which synthesizes programs according
+% to in- and output examples provided by the user.
+% It enables users to create programs without a priori programming knowledge~\cite{mayer2015user}.
+% In the context of text extraction through regular expressions, Programming by Example relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
+% In this work, we refer to our interpretation of Programming by Example as \emph{PBE}\@.
+% We investigate the suitability of PBE to retrieve information chunks from build logs.
+% In the following, we explain the configuration and application of PBE to chunk retrieval from CI build logs.
 
 \subsubsection{Configuration}
-In/output examples are the main driver of Programming by Example.
-We refer to in/output examples as \emph{examples}.
-When retrieving information chunks from build logs the \emph{input} is a whole build log, i.e.\ the whole text of the build log file.
+In/output examples are the main driver of Programming by Example, we refer to them
+as \emph{examples}.
+The \emph{input} is a whole build log, i.e.\ the whole text of the build log file.
 The \emph{output} is a substring of the log file text, representing the substring that should be retrieved by the synthesized program when given the corresponding input file.
-One or multiple examples, the training examples, configure a chunk retrieval with PBE: they define the substring of a build log that should be extracted.
+One or multiple examples, the training set, configure a chunk retrieval with PBE:
+they define the substring of a build log that should be extracted.
 The PROSE program synthesis then tries to construct a regular expression program consistent with all training examples.
-A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
+% A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
 PBE reports an error back to the user if it could not synthesize a consistent program.
-The program synthesis builds on the FlashExtract DSL, which in turn uses the FlashMeta algorithm.
-Both are described in Section~\ref{sec:rw-prose}.
+% The program synthesis builds on the FlashExtract DSL, which in turn uses the FlashMeta algorithm.
+% Both are described in Section~\ref{sec:rw-prose}.
 
@@
 \label{sec:expl-ts}
-Text Similarity approaches are used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-One common and simple technique is the Vector Space Model~\cite{schutze2008introduction}.
-We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
-In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs, which we refer to as \emph{CTS}\@.
+% Text Similarity approaches are used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+% One common and simple technique is the Vector Space Model.
+% We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
+% In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs, which we refer to as \emph{CTS}\@.
 
 \subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@.
+To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@ and apply the Vector Space Model~\cite{schutze2008introduction}.
 The lines of the output strings of the training examples define our search query.
@@
 When developers are looking for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is searching for related keywords.
-Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating our \emph{LogChunks} data set.
-As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
-In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.
+Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set.
+% As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
+% In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.
 
@@
 
-\subsubsection{Log Diff}
+\noindent
+\textbf{Log Diff}
 Amar et al.\ use a technique based on line diffs and information retrieval to identify relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
@@
 
-\subsubsection{Random Line Retrieval (RLR)}
+\noindent
+\textbf{Random Line Retrieval (RLR)}
 In our evaluation, we want to compare against a baseline of randomly extracted lines.
@@
 \todo{adapt glue text}
-This chapter describes our study design and which metrics we measure to answer our research questions.
+This section describes our study design and which metrics we measure to answer our research questions.
 In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.
@@
 Random Line Retrieval (RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
-We run four techniques on the examples from \emph{LogChunks}.
+% We run four techniques on the examples from \emph{LogChunks}.
 
-\paragraph{Training and Test Set}
+\noindent
+\textbf{Training and Test Set}
 We use \emph{LogChunks} as the data set for our study.
@@
 
-\paragraph{RQ 2.1: Size of Training and Test Set}
+\noindent
+\textbf{RQ 2.1: Size of Training and Test Set}
 To analyze how many examples the chunk retrieval techniques need to perform best, we evaluate the techniques with different training set sizes.
@@
 
-\paragraph{RQ 2.2: Recording Structural Categories}
+\noindent
+\textbf{RQ 2.2: Recording Structural Categories}
 To determine how structurally similar the examples for the chunk retrieval techniques need to be, we record the structural categories of the examples in the training and test sets.
 
-\paragraph{RQ2.3: Accuracy Metrics}
+\noindent
+\textbf{RQ2.3: Accuracy Metrics}
 To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($\mathit{RetrievedLines}$).
@@
 Recall of a chunk retrieval describes which proportion of the targeted lines were retrieved.
-Throughout the presentation and discussion of our results we show these two metrics separately, as they might have a different weight when choosing a suitable technique for a task.
+% Throughout the presentation and discussion of our results we show these two metrics separately, as they might have a different weight when choosing a suitable technique for a task.
 In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall.
@@
 
-Recall and precision of CTS and KWS vary with the number of lines selected for retrieval.
-We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the training examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
+% Recall and precision of CTS and KWS vary with the number of lines selected for retrieval.
+% We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the training examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
 
@@
   morekeywords={Test Output, Desired Test Output},
+	basicstyle=\scriptsize,
   postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
@@
 
-Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with CTS\@.
-The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
-The recall ranges from 30\% to 55\%.
-A retrieval size factor of 1 gives the best average F$_{1}$-score with 51\%.
+% Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with CTS\@.
+% The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
+% The recall ranges from 30\% to 55\%.
+% A retrieval size factor of 1 gives the best average F$_{1}$-score with 51\%.
 
@@
 
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS compared to retrieval size factors.}
-		\label{fig:contextsizefactor-precision-recall-CTS}
-\end{figure}
+% \begin{figure}[!t]
+% 		\centering
+% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
+% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS compared to retrieval size factors.}
+% 		\label{fig:contextsizefactor-precision-recall-CTS}
+% \end{figure}
 
@@
 
-Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
-The precision is 19\% when retrieving half of the expected number of lines. On average 9\% of the lines in the build log are retrieved then.
-When 2.5 times the expected number of lines are retrieved, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
-The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
+% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
+% The precision is 19\% when retrieving half of the expected number of lines. On average 9\% of the lines in the build log are retrieved then.
+% When 2.5 times the expected number of lines are retrieved, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
+% The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
 
@@
 
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-		\label{fig:contextsizefactor-precision-recall-KWS}
-\end{figure}
+% \begin{figure}[!t]
+% 		\centering
+% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
+% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
+% 		\label{fig:contextsizefactor-precision-recall-KWS}
+% \end{figure}
 
@@
 
-The averaged precision, recall and F$_{1}$-score f all techniques is compared in Figure~\ref{fig:recall-precision-all}.
-The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
-PBE has the highest average precision with 95\%.
-Chunk retrieval with CTS has the highest average F$_{1}$-score with 51\% and the second highest recall with 46\%.
-KWS has the smallest precision of the three chunk retrieval techniques.
-With 16\% it is still higher than the precision of the RLR baseline with 7\%.
-KWS has the highest recall of all techniques with 70\%.
+% The averaged precision, recall and F$_{1}$-score f all techniques is compared in Figure~\ref{fig:recall-precision-all}.
+% The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
+% PBE has the highest average precision with 95\%.
+% Chunk retrieval with CTS has the highest average F$_{1}$-score with 51\% and the second highest recall with 46\%.
+% KWS has the smallest precision of the three chunk retrieval techniques.
+% With 16\% it is still higher than the precision of the RLR baseline with 7\%.
+% KWS has the highest recall of all techniques with 70\%.
 
@@
 
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques compared.}
-		\label{fig:recall-precision-all}
-\end{figure}
+% \begin{figure}[!t]
+% 		\centering
+% 		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-all.pdf}
+% 		\caption{Precision, recall and F$_{1}$-score of all techniques compared.}
+% 		\label{fig:recall-precision-all}
+% \end{figure}
 
@@
 
-This chapter presents the answers to our research questions:
+This section presents the answers to our research questions:
 \begin{simplebox}{Research Questions}
@@
 After discussing the three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
-We present a decision tree, which developers and researchers who want to retrieve information chunks from build logs can follow.
+In Figure~\ref{fig:crt-recommendation}, we present a decision tree, which developers and researchers who want to retrieve information chunks from build logs can follow.
 The decision tree is built up of questions which either lead to more questions or to a leaf node containing a recommended technique.
-Figure~\ref{fig:crt-recommendation} presents the decision tree.
 

### 2020-03-10 msr-paper/paper.tex
few more edits, smaller listing textsize

@@
 We believe that having a common data set to compare
-different build log analysis techniques fairly will advance the research
+different build log analysis techniques will advance the research
 area. It will ultimately increase our understanding of CI build
@@
 \Cref{fig:lc-overview} how we created \logchunks. All steps are
-automatized as Ruby scripts\footnote{Data collection scripts and their original 
-parameterization are included in the data set.} and highly configurable.
+automatized as Ruby scripts\footnote{Data collection scripts and their original parameterization are included in the data set.} and highly configurable.
 
@@
 \paragraph{Build Sampling}
-To sample the builds for \logchunks we keep the most recent ten of the status 
+To sample builds for \logchunks we keep the ten most recent builds of the status 
 \emph{failed}~\cite{travis2009buildstatus}. We check up to 1,000 builds per 
@@
   language=XML,
+  basicstyle=\footnotesize,
   morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
@@
 \paragraph{Automatic Processing of Build Results}
-\logchunks enables researchers to train algorithms that retrieve build failure descriptions from build logs.
-It can provide the basis for further automatic on-ward processing of the retrieved log chunks.
+\logchunks enables researchers to train algorithms that retrieve build failure
+descriptions from build logs. It can provide the basis for further automatic
+on-ward processing of the retrieved log chunks.
 

### 2020-03-10 msr-paper/paper.tex
remove commented out text
add copyright

@@
 %% complete the rights form.
-\setcopyright{acmcopyright}
 \copyrightyear{2020} 
 \acmYear{2020} 
-\acmDOI{10.1145/1122445.1122456}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Seoul '20]{Seoul '20: Mining Software Repositories Data Showcase}{May 25--26, 2020}{Seoul, South Korea}
-\acmBooktitle{Seoul '20: Mining Software Repositories Data Showcase,
-  May 25--26, 2020, Seoul, South Korea}
+\setcopyright{acmlicensed}
+\acmConference[MSR '20]{17th International Conference on Mining Software Repositories}{October 5--6, 2020}{Seoul, Republic of Korea}
+\acmBooktitle{17th International Conference on Mining Software Repositories (MSR '20), October 5--6, 2020, Seoul, Republic of Korea}
 \acmPrice{15.00}
-\acmISBN{978-1-4503-9999-9/18/06}
+\acmDOI{10.1145/3379597.3387485}
+\acmISBN{978-1-4503-7517-7/20/05}
 
@@
 \Cref{fig:lc-overview} how we created \logchunks. All steps are
-automatized as Ruby scripts\footnote{Data collection scripts and their original parameterization are included in the data set.} and highly configurable.
+automatized as Ruby scripts\footnote{Data collection scripts and their original
+parameterization are included in the data set.} and highly configurable.
 
@@
 repository to ensure predictable termination of the log collection.
-%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.
-
 \paragraph{Log Sampling}
@@
 For each repository, the labeler skimmed through the build logs and copied out the first occurrence of a description why the build failed.
-%They copied out the first continuous description as the \texttt{Chunk}.
 She preserved whitespaces and special characters, as these might be crucial to detect the targeted substring.
@@
 We asked the labeler to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation.
-%The labeler should start the categories with 0 and increase as new ones appear.
-%For reproducibility, we presented the logs in chronological build order.
 
@@
 
-%For \logchunks we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
-%As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
-%We only took the logs into account and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
-%
-%The person who probably knows best why a build failed is the one committing the changes which triggered the build.
-%If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.
-
 In our second validation, we sent out emails to the original
@@
 Using the Travis API, we collected the commit information for each build represented in \logchunks.
-We grouped all commits triggered by one developer and sent out an email to them. %, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
-%Figure~\ref{fig:dev-mail} shows one of the mails sent out.
+We grouped all commits triggered by one developer and sent out an email to them. 
 It included links to the corresponding commits, the build overview and the log file.
 We asked the developers to fill out a short form in case our extraction was not correct.
-%Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
 In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why our original extraction was incorrect.
@@
 Of the 144 answers, 118 initially indicated that our extraction was correct.
-%26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
 We manually inspected the 26 negative answers and found that some stated that the proposed extraction did not show the whole description of why the build failed.
@@
 
-%We give a description of the manually labeled data.
-%\logchunks has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
-%Each contains folders representing the main languages of the repositories in \logchunks.
 \logchunks comprises information on 797 build logs, which are organized in folders for each language and repository.
 For each repository, \logchunks has about 10 \texttt{Examples}. Every repository folder contains the full log files for the build status `failed' in plain text.
-% the logs are separated according to build status.
-%Currently, \logchunks only contains logs from \texttt{failed} builds.
-%The build status folder contains the full logs in files named with the ID of the build that produced the log.
 
@@
 
-%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
-%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
-%In these instances the \texttt{Chunk} contains the lines describing that the build failed.
-
 \paragraph{Search Keywords}
@@
 In comparison to that, Listing \ref{lst:different-category} presents a log chunk which is formatted differently within the log file.
-%For most cases, two \texttt{Chunk} examples that fall into one category are outputted either within the same build phase or by the same build tool.
 For each repository, the structural categories are represented as integers, starting at 0 and increased with the next appearing category in chronological build order.
@@
 
-%\section{Applications}
-%This section possible use cases for \logchunks and outlines how we previously applied it to compare different build log analysis techniques.
 \section{Potential Use Cases}
 
-%\subsection{Potential Use Cases}
 \logchunks can be the basis for a range of further studies:
@@
 
-% \paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
-% \logchunks provides keywords that the authors would use to search for the chunk describing why the build failed.
-% Analyzing these can help us understand how users process build logs and which keywords a tool should use to mark an error description.
-% We can also recommend users which search keywords they should use to find why the build failed.
-% \todo{Isn't this pretty simple and not really worth a research paper? If it is too trivial, we should probably not mention it here.}
-
-% \paragraph{Studying Conversations about Build Failures}
-% Researchers are looking into conversations of developers surrounding CI builds and pull requests 
-% The chunks describing why a build failed, or the results of build log analysis techniques trained on them, can support these researchers to detect when a conversation participant is referring to the build failure described in the log.
-% \todo{Similar comment: This is a bit too narrow.
-But perhaps we can merge the two in one and say researchers doing research around the topic of build logs, such as ...
-user studies on keyword retrievala and conversations?}
-
 \paragraph{Automatic Processing of Build Results}
@@
 on-ward processing of the retrieved log chunks.
-
-% \todo{ Andy also proposed: automatic creation of issue reports on GitHub with extracted info: sounds okay, but build failures are to be fixed faster than a GH issue I would say}
-% \todo{I think this proposal is again too narrow: but what about further automatic on-ward processing? Even if small, perhaps reinforcement learning might be feasible ...}
-
-% \subsection{Chunk Retrieval Evaluation}
-% We created \logchunks to evaluate and compare different chunk retrieval techniques for build logs.
-% The first technique is based on synthesizing programs from examples using the Microsoft PROSE library.
-% A user provides a small number of examples to describe which text part the program should extract.
-% PROSE then synthesizes a program of regular expressions that is consistent with these examples.
-% We compared this extraction technique to a text similarity approach, which selects the lines of a build log which are most similar to the ones in the given user examples.
-% Lastly, we investigated searching for keywords that are associated with the given user examples.
-
-% The log chunks in this data set provided the examples for these techniques, the keywords were used to configure the keyword search.
-% The structural categories enabled us to measure how structurally similar the examples have to be for a technique to be applicable.
-
-% Our results show that program synthesis is well suited to retrieve information chunks from build logs when the targeted information is always presented in a structurally identical way and the user requires a high confidence in the precision and recall of the output.
-% Using text similarity is advisable when precision is valued higher than recall and we recommend keyword search when recall is valued higher than precision.
-% We present more detailed results, background and our study design in \todo{ref (preprint or so?) of full journal paper (or thesis?)}.
 
@@
 empower research with a benchmark to compare different build log analysis techniques.
-
-% \subsection{Travis CI Build Log Data Set}
-% \todo{I would remove this as it is not really related because it does not contain labels?}
-% Loriot et al.~\cite{loriot2019data set, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
-% They selected Maven repositories that included the Checkstyle plugin.
-% Their data set only provides the plain build logs, whereas \logchunks additionally provides manually labeled data about the chunk describing why a build failed.
 

### 2020-03-11 tse-paper/content.tex
introduce Log Chnuks data set

@@
 \label{sec:study}
-To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluate them on the \emph{LogChunks} data set.
-\todo{cite dataset}
-\todo{adapt glue text}
+To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build
+logs we evaluate them on the \emph{LogChunks}~\cite{brandt2020logchunks} data set.
 This section describes our study design and which metrics we measure to answer our research questions.
 In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.
+
+\subsection{LogChunks}
+For this study we created the previously published data set \emph{LogChunks}.
+It encompasses 797 build logs from Travis CI, stemming from a broad range of 80
+GitHub repositories and 29 programming languages. For each file, the authors
+manually ``labeled the log part (chunk) describing why the build failed''~\cite{brandt2020logchunks}.
+We include keywords, which we would use to search for the selected chunk
+within the log. In addition, we categorized the log chunks according to their
+format within the log. If the chunks are surrounded by the same markings within
+the log we assign them the same structural category.
 

### 2020-03-12 tse-paper/content.tex
Fix build

@@
 \begin{itemize}
-  \item A tool unifying several chunk retrieval techniques namely:
+  \item A tool with three prototypical implementations of chunk retrieval techniques:
         \begin{itemize}
@@
 
-\todo{structure overview of article}
+%\todo{structure overview of article}
 
@@
 	\includegraphics[width=\columnwidth, clip]{img/build-overview.pdf}
-	\caption{The different entities related to a CI build. \todo{mention in text or remove}}
+	\caption{The different entities related to a CI build.
+        %\todo{mention in text or remove}
+        }
 	\label{fig:build-overview}
@@
 		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-PBE.pdf}
+		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
 		\caption{Results of chunk retrieval with PBE.}

### 2020-03-12 tse-paper/abstract.tex

@@
-Build logs are textual by-products that a software build process
+Build logs are the textual by-product that a software build process
 creates, often as part of its Continuous Integration (CI)
-pipeline. Build logs are a paramount source of information for
-developers when debugging into and understanding a build
-failure. Recently, attempts to partly automate this time-consuming,
-purely manual activity have come up, such as rule- or
+pipeline. Build logs can not only serve as a paramount source of
+information for developers to understand and debugging into build or
+test failures, but also for automated on-ward processing. Manually
+extracting the important chunks of information, though, is akin to
+finding a needle in a haystack. Recently, attempts to partly automate
+this time-consuming activity have come up, such as rule- or
 information-retrieval-based techniques.
-
-We evaluate and compare three different techniques that aim to retrieve
-specified log parts (chunks) from a build log, namely program synthesis
-by example, textual similarity and search keywords.
-We conduct an empirical study by comparing these techniques on the manually
-labeled \emph{LogChunks} data set.
+In this paper, we first sysmetically overview and categorize the existing methods to extract information chunks.
+We then develop prototypical implementations for three promising techniques, namely program synthesis
+by example, textual similarity and search keywords. We evaluate them in an empirical study on the manually
+labeled \emph{LogChunks} data set, which comprises more than x build logs in y languages.
 Our findings show that none of the three techniques in general outperforms

### 2020-03-12 msr-paper/paper.tex

@@
 report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for example, descriptions of compile errors, linter warnings or failed
+contain a lot of valuable information for developers and researchers---for example, descriptions of compile errors or failed
 tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
@@
 to cover a broad range of development languages.
-Among the resulting repositories are, for example, \texttt{git/git},
-\texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.
+Among the resulting repositories are, for example,
+\texttt{Microsoft/TypeScript}, \texttt{git/git} and \texttt{jwilm/alacritty}.
 

### 2020-03-13 tse-paper/abstract.tex
More corrections

--- 2019-12-06 tse-paper/abstract.tex
@@
-Software builds from continuous integration produce detailed logs about the status and results of the various tools involved in the build.
-These build logs are a valuable data source for developers and researchers to inspect test results, the duration of build steps or understand the cause of a build failure.
-However, build logs are very verbose, at best semi-structured and their structure differs highly between projects.
-This makes it hard to process and analyze them.
-In this paper, we evaluate and compare three different techniques that aim to retrieve specified text chunks from a build log, namely program synthesis by example, textual similarity and search keywords.
-We conduct an empirical study by comparing these techniques on the \emph{LogChunks} data set of 797 Travis CI logs from a diverse range of projects.
-Our findings show that none of the three techniques clearly outperforms the others.
-We discuss under which circumstances each technique performs best and provide a recommendation on when developers or researchers should use which technique.
+Build logs are a textual by-product that software build processes
+create, often as part of their Continuous Integration (CI)
+pipeline. Build logs can serve as a paramount source of
+information for developers to understand and debugg build or
+test failures. Manually
+extracting the important chunks of information, though, is akin to
+finding a needle in a haystack. Recently, researchers and practitioners have begun attempts to partly automate
+this time-consuming activity, with the proposition to not only ease developers' tasks but to enable a new class of automated on-ward processing applications.
+In this paper, we want to give a systematic overview of the state of the art of the emerging field of build log analysis.
+To this end, we first survey and categorize the existing methods to extract information chunks from build logs.
+We then develop prototypical implementations for three promising techniques, namely program synthesis
+by example, textual similarity and search keywords. Finally, we evaluate the three techniques in an empirical study on our manually
+labeled \emph{LogChunks} data set, which comprises 797 build logs in 29 languages.
+Our findings show that none of the three techniques in general outperforms
+the others, but rather, that each technique has its respective strengths and weaknesses. We discuss under which circumstances each technique performs best
+and provide a recommendation on when developers or researchers should use which
+technique.

### 2020-03-13 tse-paper/content.tex
More corrections

@@
 
-The goal of this paper is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
+The goal of this article is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
 We aim to characterize different chunk retrieval techniques.
@@
 \end{itemize}
+% TODO: Shortly describe each of these techniques
+
 \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
@@
 Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
+
+% TODO: Add structural category explanation
+% TODO: Add running example
 
@@
 In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS is the best technique to choose.
-However, its low precision requires a human to interpret the output of the chunk
-retrieval.
+is unpredictable or varies greatly, KWS ssems to be the best choice.
+However, its low precision---it extracts a context of multiple lines around a find---makes it generally unsuited for automatic on-ward processing and instead requires a human to interpret the output chunk.
 
@@
 The presented approaches are related to and can benefit from the techniques we
-analyze in this paper.
+analyze in this article.
 Further, we classify build logs as semi-structured data and differentiate our
@@
 \subsection{Build Failures in CI}
-Various researchers look into why CI builds fail and into the impact of build failures on the development workflow.
+Various researchers studied why CI builds fail and into the impact of build failures on the development workflow.
 
@@
 This task of retrieving specific chunks of text from the build logs can be
-solved by the chunk retrieval techniques we compare in this paper.
+solved by the chunk retrieval techniques we compare in this article.
 Our results can support researchers in choosing a suitable technique for their
@@
 %Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this paper can be used to fill similar structured representations with information from build logs.
+The chunk retrieval techniques we compare in this article can be used to fill similar structured representations with information from build logs.
 As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.
@@
 
-The first goal in parsing system log files is to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
+The first goal in analyzing system log files is ubiquitously to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
 Next, the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
-The output of a log parser is a structured log, composed of a list of timed events and the corresponding parameter values~\cite{he2016evaluation}.
+The output of a log parser is an ordered list of timed events and their corresponding parameter values~\cite{he2016evaluation}.
 This structured log is then the input to various machine learning and data mining processes.
@@
 %A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
-In this paper we focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
-Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.\ by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+In this article, we focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
+Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.
+by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
 
@@
 }
-\begin{figure}[!t]
+\begin{figure*}[!t]
   \centering
@@
   \end{lstlisting}  
-  \caption{System Log Statements. Example adapted from~\cite{he2017towards}.}
+  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
   \label{lst:system-log}
-\end{figure}
+\end{figure*}
 
@@
 
-Programming by Example enables end users to automate repetitive tasks.
-The user provides examples for the input and the corresponding output and a
-synthesis algorithm tries to create the program intended by the user.
+Programming by Example (PBE) is a form of generalized program synthesis that enables users to automate repetitive tasks, without them having to explicitly code a program.
+The users provide examples for the input and the desired output and a
+synthesis algorithm tries to create a program that transforms the input to the output, hopefully as close as possbile to the user's intention.
 This section introduces the theoretical foundations of the program synthesis
@@
 \label{sec:techniques}
-This section introduces the concept of chunk retrieval techniques.
+This section introduces key concepts of the three chunk retrieval techniques we study in this article, namely program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
 We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
-We present the three chunk retrieval techniques we investigate in this paper:
-program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).
 
@@
 \label{sec:blirt}
-For this paper, we want to evaluate different techniques to retrieve information chunks from build logs, which we call \emph{chunk retrieval techniques}.
-The techniques we investigate do not require to parse the structure of a whole build log, but focus on extracting just one specific information.
+In this article, we evaluate different techniques to automatically retrieve pieces of information that appear literally in the build logs, i.e., techniques that do not aggreagte, combine, or deducted information.
+We call such pieces of information from build logs \emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
+The techniques we investigate here do not require to parse the entire structure of build logs, but focus on extracting just one specific piece of information per configuration.
 
+With the term \textit{configuration,} we want to abstract over the training and parametrization that techniques require in different forms.
 The user provides a \textit{configuration} that specifies which information the chunk retrieval should target and supplies the necessary information for the technique to identify the targeted information chunk in a build log.
-Each chunk retrieval has a specific \textit{granularity}, i.e.\ the smallest retrievable text piece and uses a specific \textit{identification technique} to select the log parts it retrieves.
-Each configuration addresses a specific \textit{scope}.
-The scope can be a specific project, a tool involved in the build, a programming language or global, when configuring a retrieval technique for all possible build logs.
+Each chunk retrieval has a specific \textit{granularity}, i.e.,\ the smallest retrievable text piece and uses a specific \textit{identification technique} to select the log parts it retrieves.
+The granularity might be adjustable by configuration.
 A \emph{run} of a chunk retrieval technique consumes a build log as a plain text file and produces a string output, which consists of substrings of the build log text.
@@
 We use \emph{LogChunks} as the data set for our study.
-For each one of 80 repositories it contains about 10 build logs, manually labeled with the substring describing the reason the build failed.
-In addition to that, it contains keywords to search for that substring and which structural category the substring belongs to.
+For each of the 80 repositories in it, it contains 10 build logs, manually labeled with the substring describing the reason the build failed.
+Additionally, it contains keywords to search for that substring and which structural category the substring belongs to.
+% TODO (Caro): Add details how key words were extracted
 
+% TODO (Caro): Add more details. How was the split in numbers?
 For each repository in \emph{LogChunks}, we split the examples chronologically into training and test set.

### 2020-03-17 zip-replication-package.sh
add sh file to zip replication

@@ -1,0 +1,2 @@
+#! /bin/bash
+zip crt-replication.zip evaluation pbe-extraction-buildlogs r-extractions tool replication.md

### 2020-03-17 tse-paper/content.tex
Add Litsurvey protocol

@@
-\textbf{Motivation.}
 Continuous Integration (CI) has become a common practice in software
@@
 We implemented CTS, KWS and RLR using R and the text2vec library~\cite{text2vec2019webpage}.
+
+\section{Systematic Literature Survey}
+\label{sec:survey}
+From our own experience, we know that the field of analyzing build
+logs is relatively young, with perhaps the work on TravisTorrent the
+most cited and central one. We also know there have been scattered
+research efforts on build log analysis prior to it, mostly where the
+log analysis was a side-part of the article. To the best of our
+knowledge, there has not been an attempt to systematically overview
+and survey them, despite their forseeable future and current practical
+importance.
+
+\subsection{Methodology}
+In this first overview, we therefore want to survey as broad a
+population of papers, books, and other scientific publications as
+possible. One challenge is that no common nomenclature has been
+established yet (in fact, this is one of the goals of this
+article).
+
+Since we cannot take for granted that ``analyzing build logs'' is the
+cannonical term that other, isolated works have used, we instead
+decdided to leave out the potentially variable ``analysis'' part and
+instead focus on variations of the term ``build log''. This has the
+advantage of being biunique: We explicitly decided to include systems
+or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
+search for ``build log'' returns more than 2.2 million results
+(2020-03-15). We therefore refined our search criterions for the four
+different spelling possibilities of ``build log'' to exclude obvious
+non-related works. This left us with 1,552 combined search results
+(2020-03-15).
+
+To make handling so many search results feasible, the authors of the
+paper employed a two-pass filtering strategy:
+
+First, we filtered out articles based on 1) their title and 2) the
+contextual information Google Scholar displayed. Our strategy was to
+err on the side of caution, that is rather including a paper than
+not. We then unified the search results, removing duplicates. After
+this process, we were left with 271 (17\%) of the original search
+results.
+
+We did a second filter phase by downloading the remaining papers,
+reading their abstracts, and searching the full text for the
+occurrence of ``log''. If these papers contained traces of working
+with build logs, we included them in our survey.
+
+%todo: fill-in number
+Wtih these X remaining articles, we followed a limited backward
+snowball sampling for articles referenced in the paragraphs that
+mention the technique. Having added these papers to our literature
+set, we performed a full forward-snowball sampling for all papers in
+the set.
 

### 2020-03-17 tse-paper/content.tex
Add log

@@
 
-\subsection{Methodology}
+\subsection{Selection Protocol}
 In this first overview, we therefore want to survey as broad a
@@
 the set.
+
+\subsection{Article Classification}
+%todo
 

### 2020-03-18 zip-replication-package.sh
fix replication script

@@ -1,2 +1,2 @@
 #! /bin/bash
-zip crt-replication.zip evaluation pbe-extraction-buildlogs r-extractions tool replication.md
+zip -r crt-replication.zip evaluation pbe-extraction-buildlogs r-extractions tool replication.md

### 2020-03-18 tse-paper/content.tex
Prepare figures for inclusion

@@
 Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
+
+\begin{simplebox}{Research Questions}
+\begin{itemize}
+  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
+  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
+\end{itemize}
+\end{simplebox}
 
@@
 
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
-  \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
-  \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
-\end{itemize}
-\end{simplebox}
-
 For the comparison, we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe}, \ref{sec:expl-ts} and \ref{sec:expl-skws}.
@@
 
-\subsection{Program Synthesis by Example (PBE)}
-Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
-Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
-In 89 further cases a program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output at all.
-In 30 of the 89 cases the synthesized program did not extract all of the desired lines.
-For these 30 cases, the average recall was 28\%.
-We present an example of such an \emph{unsuccessful retrieval} in Listing \ref{lst:pbe-unsuccessful}, where the synthesized regular expression program only retrieved two of the four targeted lines.
-In 173 of the 400 cases the PROSE program synthesis could not synthesize a regular expression program that is consistent with all of the training examples.
-
-Figure~\ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training and test examples.
-It shows that the program synthesis is more likely to succeed when there are only a few categories present in the training examples.
-When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all training examples.
-For three or more present categories PROSE could never synthesize a consistent program.
-
-Figure~\ref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of the 227 runs where PBE could synthesize a program consistent with all training examples.
-When the training set size increases from one to two, recall and F$_{1}$-score increase by about 25\%, precision increases by about 10\%.
-For two or more training examples, recall and F$_{1}$-score stay around 75\% and precision around 96\%.
-
 \subsection{Common Text Similarity (CTS)}
-Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision, recall and F$_{1}$-score of chunk retrieval using CTS for an increasing number of training examples.
-When using one to five training examples, the size of the training set has no noticeable influence on precision, recall or F$_{1}$-score of the chunk retrieval with CTS.
-
-Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for an increasing number of structural categories in the training and test examples.
-With increasing category count, precision, recall and F$_{1}$-score decrease.
-Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with CTS\@.
-% The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
-% The recall ranges from 30\% to 55\%.
-% A retrieval size factor of 1 gives the best average F$_{1}$-score with 51\%.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-		\caption{Results of chunk retrieval with PBE for an increasing number of structural categories in the training and test sets.}
-		\label{fig:failure-reason-categorycount-PBE}
-\end{figure}
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set.}
-		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{figure}
 
@@
 
+\Cref{fig:recall-precision-examplecount-CTS} presents precision, recall and F$_{1}$-score of chunk retrieval using CTS for an increasing number of training examples.
+When using one to five training examples, the size of the training set has no noticeable influence on precision, recall or F$_{1}$-score of the chunk retrieval with CTS.
+
+\Cref{fig:recall-precision-categorycount-CTS} shows the same measurements for an increasing number of structural categories in the training and test examples.
+With increasing category count, precision, recall and F$_{1}$-score decrease.
+Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.
+
+% Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with CTS\@.
+% The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
+% The recall ranges from 30\% to 55\%.
+% A retrieval size factor of 1 gives the best average F$_{1}$-score with 51\%.
+
 % \begin{figure}[!t]
@@
 \subsection{Keyword Search (KWS)}
-Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision, recall and F$_{1}$-score of chunk retrieval using KWS for different numbers of training examples.
-The recall increases by about 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
-The F$_{1}$-score stays around 26\%.
-
-Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for an increasing number of structural categories in the training and test examples.
-For more than one structural category in the training and test examples the recall decreases by about 20\% and the precision decreases about 6\%.
-For more than two structural categories no clear trend is visible in precision, recall or F$_{1}$-score for an increasing amount of categories in the training and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
-% The precision is 19\% when retrieving half of the expected number of lines. On average 9\% of the lines in the build log are retrieved then.
-% When 2.5 times the expected number of lines are retrieved, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
-% The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
 
@@
 
+\Cref{fig:recall-precision-examplecount-KWS} presents precision, recall and F$_{1}$-score of chunk retrieval using KWS for different numbers of training examples.
+The recall increases by about 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
+The F$_{1}$-score stays around 26\%.
+
+\Cref{fig:recall-precision-categorycount-KWS} shows the same measurements for an increasing number of structural categories in the training and test examples.
+For more than one structural category in the training and test examples the recall decreases by about 20\% and the precision decreases about 6\%.
+For more than two structural categories no clear trend is visible in precision, recall or F$_{1}$-score for an increasing amount of categories in the training and test examples.
+
+% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
+% The precision is 19\% when retrieving half of the expected number of lines. On average 9\% of the lines in the build log are retrieved then.
+% When 2.5 times the expected number of lines are retrieved, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
+% The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
+
 % \begin{figure}[!t]
@@
 
+\subsection{Program Synthesis by Example (PBE)}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set.}
+		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
+\end{figure}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+		\caption{Results of chunk retrieval with PBE for an increasing number of structural categories in the training and test sets.}
+		\label{fig:failure-reason-categorycount-PBE}
+\end{figure}
+
+\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
+Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
+In 89 further cases a program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output at all.
+In 30 of the 89 cases the synthesized program did not extract all of the desired lines.
+For these 30 cases, the average recall was 28\%.
+We present an example of such an \emph{unsuccessful retrieval} in Listing \ref{lst:pbe-unsuccessful}, where the synthesized regular expression program only retrieved two of the four targeted lines.
+In 173 of the 400 cases the PROSE program synthesis could not synthesize a regular expression program that is consistent with all of the training examples.
+
+\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training and test examples.
+It shows that the program synthesis is more likely to succeed when there are only a few categories present in the training examples.
+When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all training examples.
+For three or more present categories PROSE could never synthesize a consistent program.
+
+\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of the 227 runs where PBE could synthesize a program consistent with all training examples.
+When the training set size increases from one to two, recall and F$_{1}$-score increase by about 25\%, precision increases by about 10\%.
+For two or more training examples, recall and F$_{1}$-score stay around 75\% and precision around 96\%.
+
 \subsection{Comparison of All Techniques}
-Figure~\ref{fig:success-partial-all} compares the success of all chunk retrieval by the different techniques in our study.
+\Cref{fig:success-partial-all} compares the success of all chunk retrieval by the different techniques in our study.
 CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
@@
 
-Figure~\ref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
+\Cref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
 For more than one present category, the recall of PBE decreases greatly.
@@
   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
-  \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
+
+  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
+  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
+  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
 \end{itemize}

### 2020-03-18 tse-paper/content.tex
First example of subfigures

@@
 
-\begin{figure}[!t]
+\begin{figure*}
+\begin{subfigure}[b]{\columnwidth}
 		\centering
 		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for an increasing training set size.}
+		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
 		\label{fig:recall-precision-examplecount-KWS}
-\end{figure}
-
-\begin{figure}[!t]
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[b]{\columnwidth}
 		\centering
 		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for an increasing number of structural categories in the training and test sets.}
+		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
 		\label{fig:recall-precision-categorycount-KWS}
-\end{figure}
+\end{subfigure}
+\caption{Results of chunk retrieval with  (KWS)}
+\end{figure*}
 
@@
 
-\begin{figure}[!t]
+\begin{figure*}
+\begin{subfigure}[!t]{\textwidth}
 		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set.}
+		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
 		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{figure}
+\end{subfigure}
 
-\begin{figure}[!t]
+\begin{subfigure}[!t]{\textwidth}
 		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-		\caption{Results of chunk retrieval with PBE for an increasing number of structural categories in the training and test sets.}
+		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+		\caption{Increasing number of structural categories in the training and test sets.}
 		\label{fig:failure-reason-categorycount-PBE}
-\end{figure}
+\end{subfigure}
+
+\caption{Results of chunk retrieval with Program Synthesis by Example (PBE)}
+\end{figure*}
 

### 2020-03-18 tse-paper/paper.tex
Add motivation
include loads of text and graphics from thesis, fix graphics, start adapting heading levels
Edit abstract
Add Litsurvey protocol
Prepare figures for inclusion
First example of subfigures

@@
 
+\usepackage{todonotes}
+%\setuptodonotes{inline, color=cyan!50}
+\usepackage{cleveref}
+%\usepackage{subfigure}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{mdframed,xcolor}
+
+\newenvironment{figureax}[1][htbp]% Redefine figure
+  {\oldfigure[#1]\mdframed[backgroundcolor=blue!15]}
+  {\endmdframed\endoldfigure}
+
 % *** Do not adjust lengths that control margins, column widths, etc. ***
@@
 % Do not put math or special symbols in the title.
-\title{How to Analyze Build Logs\\ ---\\ A~Comparative Study of Chunk~Retrieval~Techniques}
+\title{How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques}
 %
@@
 % http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
+\bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
+\bibliography{paper}
 

### 2020-03-19 tse-paper/content.tex
Add survey description protocol

@@
 First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. Our strategy was to
-err on the side of caution, that is rather including a paper than
-not. We then unified the search results, removing duplicates. After
-this process, we were left with 271 (17\%) of the original search
-results.
+contextual information Google Scholar displayed. We inlcuded only
+publications written in a language intelligible to the authors (that
+is, English or German), but only disregarded fewer than 1\% of search
+hits due to this criterion. Our strategy was to err on the side of
+caution, that is rather including a paper than not. We then unified
+the results of the four search queries based on the link as the
+identifying element, removing 60 articles that appeared in more than
+one search query. We noticed that some publishers (ACM, Springer,
+Google Books) augment a link to an article with a cutomized ID, which
+specifies the link source ({\tt casa\_token, oid}). We automatically
+removed it to find all true duplicates. After this process, we were
+left with 259 (17\%) of the original search results.
 
@@
 \begin{itemize}  
- \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
-  \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
+  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
+  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
 

### 2020-03-20 tse-paper/content.tex
adapt study overview picture journal paper
Store changes

@@
+% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
+
 Continuous Integration (CI) has become a common practice in software
@@
 \label{sec:survey}
+% TODO (Caro): Integrate Kitchenham's guidelines
 From our own experience, we know that the field of analyzing build
@@
 In this first overview, we therefore want to survey as broad a
-population of papers, books, and other scientific publications as
-possible. One challenge is that no common nomenclature has been
-established yet (in fact, this is one of the goals of this
-article).
+population of scientific material as possible. Note that we do not
+limit our sources to a handful of Software Engineering venues, as is
+often done, but survey all sources monitored by Google Scholar,
+including Bachelor's and Master's theses, academic slide decks, adn
+books. One challenge is that no common nomenclature has been
+established yet (in fact, this is one of the goals of this article).
 
@@
 instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to include systems
+advantage of being biunique: We explicitly decided to exclude systems
 or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar

### 2020-03-20 msr-paper/paper.tex

@@
 %%
-%\begin{CCSXML}
-%<ccs2012>
-% <concept>
-%  <concept_id>10010520.10010553.10010562</concept_id>
-%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-%  <concept_significance>500</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010575.10010755</concept_id>
-%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-%  <concept_significance>300</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010553.10010554</concept_id>
-%  <concept_desc>Computer systems organization~Robotics</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10003033.10003083.10003095</concept_id>
-%  <concept_desc>Networks~Network reliability</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-%</ccs2012>
-%\end{CCSXML}
-%
-%\ccsdesc[500]{Computer systems organization~Embedded systems}
-%\ccsdesc[300]{Computer systems organization~Redundancy}
-%\ccsdesc{Computer systems organization~Robotics}
-%\ccsdesc[100]{Networks~Network reliability}
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10011007.10011074</concept_id>
+<concept_desc>Software and its engineering~Software creation and management</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
 
+\ccsdesc[500]{Software and its engineering~Software creation and management}
 %%
@@
 	\centering
-	\includegraphics[width=1.35\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
+	\includegraphics[width=1.35\columnwidth, trim={2cm 2.75cm 2cm 0.75cm}, clip]{overview.pdf}
 	\caption{Overview of \logchunks}

### 2020-03-23 r-extractions/install_packages.R
Add various fixes

@@ -3,4 +3,5 @@ r["CRAN"] = "http://cran.us.r-project.org"
 options(repos = r)
 
 install.packages("optigrab", dependencies=TRUE)
-install.packages("wordcloud", dependencies=TRUE)
+install.packages("NLP", dependencies=TRUE)
+install.packages("XML")

### 2020-03-23 r-extractions/utilities.R

@@ -1,7 +1,6 @@
 suppressPackageStartupMessages({
   library(stringr)
   library(stringi)
-  library(wordcloud)
   library(NLP)
   library(XML)
 })

### 2020-03-23 tse-paper/content.tex
Paper edits

@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 	\centering
-	\includegraphics[page=2, width=\columnwidth, trim={0cm 1cm 1.5cm 0.5cm}, clip]{img/overview-graphics.pdf}
+	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
 	\caption{Study design of our technique comparison study.}
 	\label{fig:study}
-\end{figure}
+\end{figure*}
 
@@
 
+\newpage
 \subsection{Common Text Similarity (CTS)}
@@
 
+\newpage
 \subsection{Keyword Search (KWS)}
@@
 
+\newpage
 \subsection{Program Synthesis by Example (PBE)}
@@
 \subsection{Comparison of All Techniques}
-\Cref{fig:success-partial-all} compares the success of all chunk retrieval by the different techniques in our study.
+\Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
 CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.

### 2020-03-23 tse-paper/content.tex
Add text

@@
 %todo: fill-in number
-Wtih these X remaining articles, we followed a limited backward
-snowball sampling for articles referenced in the paragraphs that
-mention the technique. Having added these papers to our literature
-set, we performed a full forward-snowball sampling for all papers in
-the set.
+Wtih these X remaining articles, we followed a backward snowball
+sampling for other related work referenced in the paragraphs that
+mention the technique. This added four papers (five before duplicate
+elimination) to our literature set.
 

### 2020-03-24 tse-paper/content.tex
Complete Lit survey protocol

@@
 
-We did a second filter phase by downloading the remaining papers,
+We did a second filter phase by downloading the surviving papers,
 reading their abstracts, and searching the full text for the
@@
 
-%todo: fill-in number
-Wtih these X remaining articles, we followed a backward snowball
-sampling for other related work referenced in the paragraphs that
-mention the technique. This added four papers (five before duplicate
-elimination) to our literature set.
+Wtih these 259 remaining articles, we followed a backward snowball
+sampling for related work referenced in the paragraphs that mention
+the technique. This added two papers (five before duplicate
+elimination and second-pass filtering) to our literature set, both of
+which stem from the same first author, were borderline-includes, and
+had called build logs from the Linux kernel ``build traces.''
 

### 2020-03-24 tse-paper/content.tex
Include updated numbers

--- 2020-03-23 tse-paper/content.tex
@@
 
-\section{Systematic Literature Survey}
+\section{Systematic Literature Survey and Mapping}
 \label{sec:survey}
@@
 often done, but survey all sources monitored by Google Scholar,
-including Bachelor's and Master's theses, academic slide decks, adn
-books. One challenge is that no common nomenclature has been
+including Bachelor's and Master's theses, academic slide decks, and
+books. We use Google Scholar as opposed to Scopus or other databases,
+as it is the search engine for acdemic articles with the broadest and
+most current index, including preprints from sources such as
+arXiv. One challenge is that no common nomenclature has been
 established yet (in fact, this is one of the goals of this article).
@@
 
-We did a second filter phase by downloading the remaining papers,
-reading their abstracts, and searching the full text for the
-occurrence of ``log''. If these papers contained traces of working
-with build logs, we included them in our survey.
+Wtih these 259 remaining articles, we followed a backward snowball
+sampling for related work. This added three papers (five before
+duplicate elimination) to our literature set, coming to a total of 261
+articles.
 
-%todo: fill-in number
-Wtih these X remaining articles, we followed a backward snowball
-sampling for other related work referenced in the paragraphs that
-mention the technique. This added four papers (five before duplicate
-elimination) to our literature set.
+On the 261 artciles, We did a second filter phase by downloading the
+surviving papers, reading their abstracts, and searching the full text
+for the occurrence of ``log''. If these papers showed even traces of
+working with build logs, we included them in our survey. For the
+snowballed set, we included two of the three articles, both of which
+stem from the same first author, were borderline-includes, and had
+called build logs from the Linux kernel ``build traces.'' In total, we
+were left with 90 articles after this search.
 

### 2020-03-26 zip-replication-package.sh
replication zip creation for replication repo

@@ -1,2 +1,14 @@
 #! /bin/bash
-zip -r crt-replication.zip evaluation pbe-extraction-buildlogs r-extractions tool replication.md
+
+mkdir chunk-retrieval-replication
+
+cp -r evaluation chunk-retrieval-replication/evaluation
+cp -r pbe-extraction-buildlogs chunk-retrieval-replication/pbe-extraction-buildlogs
+cp -r r-extractions chunk-retrieval-replication/r-extractions
+cp -r tool chunk-retrieval-replication/tool
+cp replication.md chunk-retrieval-replication/readme.md
+cp .gitignore chunk-retrieval-replication/.gitignore
+
+zip -r chunk-retrieval-replication.zip chunk-retrieval-replication
+
+rm -rf chunk-retrieval-replication

### 2020-03-27 tse-paper/content.tex
Include lit overview schematic

@@
 
-\begin{table}[]
+\begin{table*}[]
 \centering
 \caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\columnwidth}{@{}XlXlX@{}} 
+\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
 \toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration             \\ 
+Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
 \midrule
@@
 \label{tab:ctr}
-\end{table}
+\end{table*}
 
@@
 knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current practical
-importance.
+and survey them, despite their forseeable future and current importance.
 
-\subsection{Selection Protocol}
-In this first overview, we therefore want to survey as broad a
-population of scientific material as possible. Note that we do not
-limit our sources to a handful of Software Engineering venues, as is
-often done, but survey all sources monitored by Google Scholar,
-including Bachelor's and Master's theses, academic slide decks, and
-books. We use Google Scholar as opposed to Scopus or other databases,
-as it is the search engine for acdemic articles with the broadest and
-most current index, including preprints from sources such as
-arXiv. One challenge is that no common nomenclature has been
-established yet (in fact, this is one of the goals of this article).
+\subsection{Study Selection}
+
+\begin{figure}[htb]
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
+		\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
+		\label{fig:lit-survey}
+\end{figure}
+\Cref{fig:lit-survey} presents an overview of our study selection.
+In this first literature overview study on analyzing build logs, we
+therefore want to survey as broad a population of scientific material
+as possible. Note that we do not limit our sources to specific
+Software Engineering venues, as is often done, but survey all sources
+monitored by Google Scholar, including Bachelor's and Master's theses,
+academic slide decks, and books. We use Google Scholar as opposed to
+Scopus or other databases, as it is the search engine for acdemic
+articles with the broadest and most current index, including preprints
+from sources such as arXiv. One challenge is that no common
+nomenclature has been established yet (in fact, this is one of the
+goals of this article).
 
@@
 
-To make handling so many search results feasible, the authors of the
-paper employed a two-pass filtering strategy:
+To make handling so many search results feasible, we employed a
+two-pass filtering strategy:
 

### 2020-03-27 tse-paper/content.tex
More adaptations
Fix table

@@
 \end{figure}
+
 \Cref{fig:lit-survey} presents an overview of our study selection.
@@
 
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
 \lstset{
@@
 \newpage
+\pagebreak
 \subsection{Common Text Similarity (CTS)}
 
-\begin{figure}[!t]
+\begin{figure*}
+\begin{subfigure}[t]{\columnwidth}
 		\centering
@@
 		\label{fig:recall-precision-examplecount-CTS}
-\end{figure}
 
-\begin{figure}[!t]
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[t]{\columnwidth}
 		\centering
@@
 		\label{fig:recall-precision-categorycount-CTS}
-\end{figure}
+\end{subfigure}
+\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
+\end{figure*}
 
@@
 \newpage
+\newpage
 \subsection{Keyword Search (KWS)}
@@
 \end{subfigure}
-\caption{Results of chunk retrieval with  (KWS)}
+\caption{Results of chunk retrieval with Keyword Search (KWS)}
 \end{figure*}
@@
 \newpage
+\newpage
 \subsection{Program Synthesis by Example (PBE)}
@@
 \begin{figure*}
-\begin{subfigure}[!t]{\textwidth}
+\begin{subfigure}[b]{\columnwidth}
 		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
                 		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
                 \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[b]{\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+                		\caption{Increasing number of structural categories in the training and test sets.}
 
-\begin{subfigure}[!t]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-		\caption{Increasing number of structural categories in the training and test sets.}
                 \label{fig:failure-reason-categorycount-PBE}
 \end{subfigure}
-
 \caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
 \end{figure*}
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
+		\caption{Results of chunk retrieval with PBE.}
+		\label{fig:failure-reason-PBE}
+\end{figure}
 
@@
 
+\pagebreak
 \subsection{Comparison of All Techniques}
@@
 
-\Cref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
+\Cref{fig:recall-precision-singlecategory-all} and \Cref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
 For more than one present category, the recall of PBE decreases greatly.
@@
 \begin{table}[tbp]
+\resizebox{\columnwidth}{!}{%
 \centering
-\begin{tabularx}{\columnwidth}{@{}llll@{}}
+\begin{tabular}{llll}
   \toprule
@@
   \bottomrule
-\end{tabularx}
+\end{tabular}%
+}
 \caption{Recommendations for each of the investigated chunk retrieval techniques.}

### 2020-03-29 tse-paper/content.tex
Huge review and redo

@@
 % TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
+% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
+% - Lots of effort
+% - not a generic solution
+% - how to analyze history where such plugins were not installed
+% - unclear which information you want
 
@@
   \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
-  \item a common text similarity approach (referred to as CTS), and
-  \item keyword search (referred to as KWS).
+  \item a common text similarity approach (CTS), and
+  \item keyword search (KWS), an ad-hoc method for finding fitting passages by searching the whole text for the occurrence of a specific trigger word.
 \end{itemize}
@@
 
+% TODO: Add running example?
 \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
@@
 To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
+% TODO: explain structural category based on running example from above?
 Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
@@
 is unpredictable or varies greatly, KWS ssems to be the best choice.
-However, its low precision---it extracts a context of multiple lines around a find---makes it generally unsuited for automatic on-ward processing and instead requires a human to interpret the output chunk.
-
-%\todo{structure overview of article}
+However, its low precision---it extracts a context of multiple lines around a finding---makes it generally unsuited for automatic on-ward processing and instead requires a human to further inspect and interpret the output chunk.
+
+\section{Systematic Literature Survey and Mapping}
+\label{sec:survey}
+
+\begin{figure}[htb]
+        \centering
+	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
+	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
+	\label{fig:lit-survey}
+\end{figure}
+
+% TODO (Caro): Integrate Kitchenham's guidelines
+From our own experience, we know that the field of analyzing build
+logs is relatively young, with perhaps the work on TravisTorrent the
+most cited and central one. We also know there have been scattered
+research efforts on build log analysis prior to it, mostly where the
+log analysis was a side-part of the article. To the best of our
+knowledge, there has not been an attempt to systematically overview
+and survey them, despite their forseeable future and current importance.
+
+\subsection{Study Selection}
+
+\Cref{fig:lit-survey} presents an overview of our study selection.
+In this first literature overview study on analyzing build logs, we
+therefore want to survey as broad a population of scientific material
+as possible. Note that we do not limit our sources to specific
+Software Engineering venues, as is often done, but survey all sources
+monitored by Google Scholar, including Bachelor's and Master's theses,
+academic slide decks, and books. We use Google Scholar as opposed to
+Scopus or other databases, as it is the search engine for acdemic
+articles with the broadest and most current index, including preprints
+from sources such as arXiv. One challenge is that no common
+nomenclature has been established yet (in fact, this is one of the
+goals of this article).
+
+Since we cannot take for granted that ``analyzing build logs'' is the
+cannonical term that other, isolated works have used, we instead
+decdided to leave out the potentially variable ``analysis'' part and
+instead focus on variations of the term ``build log''. This has the
+advantage of being biunique: We explicitly decided to exclude systems
+or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
+search for ``build log'' returns more than 2.2 million results
+(2020-03-15). We therefore refined our search criterions for the four
+different spelling possibilities of ``build log'' to exclude obvious
+non-related works. This left us with 1,552 combined search results
+(2020-03-15).
+
+To make handling so many search results feasible, we employed a
+two-pass filtering strategy:
+
+First, we filtered out articles based on 1) their title and 2) the
+contextual information Google Scholar displayed. We inlcuded only
+publications written in a language intelligible to the authors (that
+is, English or German), but only disregarded fewer than 1\% of search
+hits due to this criterion. Our strategy was to err on the side of
+caution, that is rather including a paper than not. We then unified
+the results of the four search queries based on the link as the
+identifying element, removing 60 articles that appeared in more than
+one search query. We noticed that some publishers (ACM, Springer,
+Google Books) augment a link to an article with a cutomized ID, which
+specifies the link source ({\tt casa\_token, oid}). We automatically
+removed it to find all true duplicates. After this process, we were
+left with 259 (17\%) of the original search results.
+
+Wtih these 259 remaining articles, we followed a backward snowball
+sampling for related work. This added three papers (five before
+duplicate elimination) to our literature set, coming to a total of 261
+articles.
+
+On the 261 artciles, We did a second filter phase by downloading the
+surviving papers, reading their abstracts, and searching the full text
+for the occurrence of ``log''. If these papers showed even traces of
+working with build logs, we included them in our survey. For the
+snowballed set, we included two of the three articles, both of which
+stem from the same first author, were borderline-includes, and had
+called build logs from the Linux kernel ``build traces.'' In total, we
+were left with 90 articles after this search.
+
+\subsection{Article Classification}
+%todo Caro: please write a draft for this :-)
+Having trimmed down the set of articles, we investigated them in depth.
 
 \section{Related Work}
+% TODO reorder rw by build retrieval technique rather than by paper
 \label{sec:rw}
@@
 Build logs are a valuable data source for developers to find out why their build failed.
-Several researchers are looking into supporting developers to process the verbose build logs.
+Several researchers investigate how to support developers in working with verbose build logs.
 Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
@@
 
-Programming by Example (PBE) is a form of generalized program synthesis that enables users to automate repetitive tasks, without them having to explicitly code a program.
-The users provide examples for the input and the desired output and a
-synthesis algorithm tries to create a program that transforms the input to the output, hopefully as close as possbile to the user's intention.
+Programming by Example (PBE) is a form of generalized program synthesis that enables users to automate repetitive tasks, without them having to explicitly codify a computer program.
+One has to provide prototypical examples of the input and the desired output.
+A
+synthesis algorithm tries to create a program (based on a regular language) that transforms the input to the output.
+The minimum working condition is for this when replayed on the examples inputs is to provide the specified output, but, hopefully, PBE is as close as possbile to the user's intention and thus also works on a different and larger set of inputs.
 This section introduces the theoretical foundations of the program synthesis
@@
 
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=\columnwidth, clip]{img/build-overview.pdf}
-	\caption{The different entities related to a CI build.
-        %\todo{mention in text or remove}
-        }
-	\label{fig:build-overview}
-\end{figure}
-
 \subsection{Characteristics of Chunk Retrieval Techniques}
@@
 We call such pieces of information from build logs \emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require to parse the entire structure of build logs, but focus on extracting just one specific piece of information per configuration.
-
-With the term \textit{configuration,} we want to abstract over the training and parametrization that techniques require in different forms.
-The user provides a \textit{configuration} that specifies which information the chunk retrieval should target and supplies the necessary information for the technique to identify the targeted information chunk in a build log.
-Each chunk retrieval has a specific \textit{granularity}, i.e.,\ the smallest retrievable text piece and uses a specific \textit{identification technique} to select the log parts it retrieves.
-The granularity might be adjustable by configuration.
-A \emph{run} of a chunk retrieval technique consumes a build log as a plain text file and produces a string output, which consists of substrings of the build log text.
-
-The following sections of this section introduce the three chunk retrieval techniques we investigate: program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
-Lastly we describe other techniques which can also be treated as chunk retrieval techniques.
-Table~\ref{tab:ctr} shows a comparison of the presented techniques.
+The techniques we investigate here do not require a formal lexer and parser to analyze the entire structure of build logs, but focus on ad-hoc extracting just one specific piece of information per configuration.
+
+With the term \textit{configuration,} we abstract over the training and parametrization that different techniques require in different forms.
+A configuration can be explicitly stated or implicitly dervied by learning through provided examples.
+It is therefore a manual specification of which information the chunk retrieval should target.
+It also supplies the necessary information for the technique to identify the targeted information chunk in a build log.
+Each chunk retrieval technqiue has a specific \textit{granularity}, i.e.,\ the smallest piece of text it can return (e.g., a line, or a word). The granularity might be adjustable by configuration.
+\emph{Running a chunk retrieval technique} means to execute a fully configured technique to consumes as input a build log in plain text format and to produce an array as output.
+The array consists of substrings of the build log text.
+
+\Cref{tab:ctr} shows a comparison of the presented techniques.
 
@@
 
+\subsection{Common Text Similarity (CTS)}
+\label{sec:expl-ts}
+% Text Similarity approaches are used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+% One common and simple technique is the Vector Space Model.
+% We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
+% In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs, which we refer to as \emph{CTS}\@.
+
+\subsubsection{Configuration}
+To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@
+% TODO Caro: More details on this. How do you 'apply' VSM? On what?
+and apply the Vector Space Model~\cite{schutze2008introduction}.
+The lines of the output strings of the training examples define our search query.
+The algorithm splits the search query into single lines and identifies tokens, in our case words.
+Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
+Finally, the algorithm applies TF-IDF to the matrix, a best practice for natural language queries~\cite{lee1997document}.
+
+\subsubsection{Application}
+To retrieve the desired information from a build log, we parse the whole text and process it in the same way as the output of the training examples.
+The algorithm calculates the cosine similarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
+After summing up the similarities of each build log line to all search query lines, we sort the build log lines in decreasing similarity.
+The average number of lines in the outputs of the training examples determines how many of the most similar lines are returned as the output of the retrieval run.
+
+\subsection{Keyword Search (KWS)}
+\label{sec:expl-skws}
+When developers scavenge for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is to search for related keywords.
+Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set~\cite{logchunks}.
+% As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
+% In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.
+
+\subsubsection{Configuration}
+A set of keywords configures the chunk retrieval with KWS\@.
+To better compare KWS with PBE and CTS, we also configure it through examples.
+We associate each example with keywords which appear in the targeted chunk or close to it.
+The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.
+% TODO Caro Please explain above sentence more precisely
+
+\subsubsection{Application}
+For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the keywords.
+As keywords are often not directly describing the desired information, but rather appear close to the desired information, KWS also retrieves the lines around the found keyword.
+The number of surrounding lines retrieved is the average of lines in the output of the training examples.
+
 \subsection{Program Synthesis by Example (PBE)}
@@
 \subsubsection{Configuration}
-In/output examples are the main driver of Programming by Example, we refer to them
+In- and output example pairs are the main driver of Programming by Example, we refer to them in short
 as \emph{examples}.
-The \emph{input} is a whole build log, i.e.\ the whole text of the build log file.
-The \emph{output} is a substring of the log file text, representing the substring that should be retrieved by the synthesized program when given the corresponding input file.
-One or multiple examples, the training set, configure a chunk retrieval with PBE:
+The \emph{input} is the text of the build log file.
+The \emph{output} is an array of substrings of the log file text, representing the substrings that should be retrieved by the synthesized program when given the corresponding input file.
+One or multiple examples, the training set, \emph{configure} a specific chunk retrieval with PBE:
 they define the substring of a build log that should be extracted.
-The PROSE program synthesis then tries to construct a regular expression program consistent with all training examples.
+The PROSE program synthesis then tries to construct a program consistent with all training examples.
 % A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
@@
 
+% TODO Caro: The following is very obvious and could apply to any technique. 
 \subsubsection{Application}
@@
 
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model.
-% We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
-% In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@ and apply the Vector Space Model~\cite{schutze2008introduction}.
-The lines of the output strings of the training examples define our search query.
-The algorithm splits the search query into single lines and identifies tokens, in our case words.
-Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
-Next, the algorithm applies TF-IDF to the matrix, a best practice for natural language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the whole text and process it in the same way as the output of the training examples.
-The algorithm calculates the cosine similarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
-After summing up the similarities of each build log line to all search query lines, we sort the build log lines in decreasing similarity.
-The average number of lines in the outputs of the training examples determines how many of the most similar lines are returned as the output of the retrieval run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers are looking for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is searching for related keywords.
-Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set.
-% As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
-% In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@.
-To better compare KWS with PBE and CTS, we also configure it through examples.
-We link each example with keywords, which appear in the targeted chunk or close to it in the input build log.
-The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the keywords.
-As keywords are often not directly describing the desired information, but rather appear close to the desired information, KWS also retrieves the lines around the found keyword.
-The number of surrounding lines retrieved is the average of lines in the output of the training examples.
+\subsection{Random Line Retrieval}
+\label{sec:r:rlr}
+
+In our evaluation, we want to compare against a baseline of randomly picking lines from the build log.
+RLR essentially mimicks the situation of guessing purely blindly which lines might be interesting.
+The only configuration option for RLR is the number of lines it should return.
+For a fair comparison to the other techniques (whose number of returned lines is dynamic), we configure RLR to return the average number of lines in the chunks of the training examples.
+% TODO Caro: some more details here?
 
@@
 This technique retrieves the lines from a build log that are not present in the successful build log and contain terms related to the given past failures.
-
-\noindent
-\textbf{Random Line Retrieval (RLR)}
-In our evaluation, we want to compare against a baseline of randomly extracted lines.
-The average number of lines in the outputs of the training examples is the configuration for random line retrieval (RLR).
-It retrieves this number of lines randomly sampled from the build log.
 
@@
 
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-% TODO (Caro): Integrate Kitchenham's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15).
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-Wtih these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles.
-
-On the 261 artciles, We did a second filter phase by downloading the
-surviving papers, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed even traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-%todo
-
 \section{Study Design}
 \label{sec:study}
-To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build
+
+% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
+	\caption{Study design of our technique comparison study.}
+	\label{fig:study}
+\end{figure*}
+
+To investigate which techqnique is best suited to retrieve chunks from CI build
 logs we evaluate them on the \emph{LogChunks}~\cite{brandt2020logchunks} data set.
@@
 
-\begin{figure*}[!t]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
 For the comparison, we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe}, \ref{sec:expl-ts} and \ref{sec:expl-skws}.
@@
 We use \emph{LogChunks} as the data set for our study.
-For each of the 80 repositories in it, it contains 10 build logs, manually labeled with the substring describing the reason the build failed.
-Additionally, it contains keywords to search for that substring and which structural category the substring belongs to.
-% TODO (Caro): Add details how key words were extracted
+For each of the 80 repositories in it, \emph{LogChunks} contains 10 build logs, manually labeled with the substring or \emph{chunk} describing the reason the build failed.
+Additionally, it contains (1) keywords useful to
+% TODO Caro uniquely?
+identify the substring in the log  and (2) which structural category the substring belongs to.
+% TODO (Caro): Add details how key words were extracted. Add example?
 
@@
 
-We calculate the following metrics:
-\begin{itemize}
-	 \itemsep0.75em
-	\item True positives: $\mathit{DesiredLines} \cap \mathit{RetrievedLines}$
-	\item Precision: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{RetrievedLines}}$
-	\item Recall: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{DesiredLines}}$
-	\item F$_{1}$-score: $2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
-	\item Successful retrieval: $\mathit{true}\ \mathit{if}\ \mathit{Recall} = 1$
+We calculate and define a number of metrics for the context of our evaluation.
+
+\vspace{0.2cm}
+\begin{itemize}[leftmargin=0.4cm]
+	 \itemsep1em
+	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap \mathit{RetrievedLines}$ \vspace{0.2cm}\\
+        True positives are lines that appear both in the output of a tool as well as what \textit{LogChunks} contains for each example. 
+        % TODO (Caro) What about when a line is replicated twice? I.e., Are line numbers part of this?
+	\item $\mbox{Precision} = \dfrac{|\mathit{True\ Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
+        Precision of a chunk retrieval describes which proportion of the retrieved lines were actually desired. 
+	\item $\mbox{Recall} = \dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$ \vspace{0.2cm} \\
+        Recall of a chunk retrieval describes which proportion of the desired lines were retrieved.
+	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$ \vspace{0.2cm}\\
+        In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall.
+We prefer F$_{1}$ to other aggregate measures such as accuracy because for a ``needle-in-the-haystack'' scenario, we do not want to bloat our results by correctly not finding lots of irrelevant log lines.
+	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\ \mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\ We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
 \end{itemize}
-
-Precision of a chunk retrieval describes which proportion of the retrieved lines were desired.
-Recall of a chunk retrieval describes which proportion of the targeted lines were retrieved.
-% Throughout the presentation and discussion of our results we show these two metrics separately, as they might have a different weight when choosing a suitable technique for a task.
-In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall.
-We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
 
@@
 
-\newpage
-\pagebreak
 \subsection{Common Text Similarity (CTS)}
-
+\label{sec:r:cts}
 \begin{figure*}
+\centering
+    \textbf{Common Text Similarity (CTS)}\par\medskip
 \begin{subfigure}[t]{\columnwidth}
@@
                 \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing training set size.}
+		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
 		\label{fig:recall-precision-examplecount-CTS}
@@
                 		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing number of structural categories in the training and test sets.}
+		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
 		\label{fig:recall-precision-categorycount-CTS}
@@
 
-% Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with CTS\@.
-% The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
-% The recall ranges from 30\% to 55\%.
-% A retrieval size factor of 1 gives the best average F$_{1}$-score with 51\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS compared to retrieval size factors.}
-% 		\label{fig:contextsizefactor-precision-recall-CTS}
-% \end{figure}
-
-\newpage
-\newpage
 \subsection{Keyword Search (KWS)}
-
+\label{sec:r:kws}
 \begin{figure*}
+\centering
+    \textbf{Keyword Search (KWS)}\par\medskip
 \begin{subfigure}[b]{\columnwidth}
@@
 
-\newpage
-\newpage
 \subsection{Program Synthesis by Example (PBE)}
-
+\label{sec:r:pbe}
 \begin{figure*}
+\centering
+    \textbf{Program Synthesis by Example (PBE)}\par\medskip
 \begin{subfigure}[b]{\columnwidth}
@@
                 		\caption{Increasing number of structural categories in the training and test sets.}
-
                 \label{fig:failure-reason-categorycount-PBE}
@@
 
-\begin{figure}[!t]
+\begin{figure}[tbp]
 		\centering
@@
 Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
-In 89 further cases a program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output at all.
-In 30 of the 89 cases the synthesized program did not extract all of the desired lines.
+In 89 further cases, an extraction program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output.
+In 30 of the 89 cases did the synthesized program only partially extract a subset of the desired lines.
 For these 30 cases, the average recall was 28\%.
-We present an example of such an \emph{unsuccessful retrieval} in Listing \ref{lst:pbe-unsuccessful}, where the synthesized regular expression program only retrieved two of the four targeted lines.
-In 173 of the 400 cases the PROSE program synthesis could not synthesize a regular expression program that is consistent with all of the training examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of structural categories present in the training and test examples.
-It shows that the program synthesis is more likely to succeed when there are only a few categories present in the training examples.
-When two structural categories are present, PROSE could in most cases not synthesize a program consistent with all training examples.
-For three or more present categories PROSE could never synthesize a consistent program.
+Listing \ref{lst:pbe-unsuccessful} shows an example of such an \emph{unsuccessful retrieval}, where the synthesized program only retrieved two of the four targeted lines.
+In 173 of the 400 cases could PROSE not synthesize program consistent with all of the training examples.
+
+\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs depend on the number of structural categories in the training and test examples.
+The figure demonstrates that program synthesis mostly returns exactly the desired output when there are is only one structural category present in the training examples.
+However, when two or more structural categories are simultaneously present in the examlpe set, PROSE could in most cases not synthesize a program consistent with all training examples.
+For four or more present categories PROSE could never synthesize a consistent program.
 
@@
 
-\pagebreak
+\subsection{Random Line Retrieval}
+\label{sec:r:rlr}
+
+In our evaluation, we want to compare against a baseline of randomly picking lines from the build log.
+Due to the fact no one would seriously consider RLR in real-world scenarios, we are omitting its detailed graphs here.
+However, its results follow intuitive expectations:
+% TODO Caro: shortly descibre RLR graphs ommitted
+
 \subsection{Comparison of All Techniques}
+In this section, we aggregate the results from \Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it each other.
+
 \Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
@@
 
-\Cref{fig:recall-precision-singlecategory-all} and \Cref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
-For more than one present category, the recall of PBE decreases greatly.
+\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
+For more than one category being present, the recall of PBE decreases greatly.
 For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.
@@
 
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-all.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of all techniques compared.}
-% 		\label{fig:recall-precision-all}
-% \end{figure}
-
-\begin{figure}[!t]
+\begin{figure*}
+\centering
+    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
+\begin{subfigure}[b]{\columnwidth}
 		\centering
                 		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{one} structural category.}
+		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
 		\label{fig:recall-precision-singlecategory-all}
-\end{figure}
-
-\begin{figure}[!t]
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[b]{\columnwidth}
+		\centering
                 		\centering
 		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques compared when training examples are in \emph{more than one} structural categories.}
+		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
 		\label{fig:recall-precision-multicategory-all}
-\end{figure}
+\end{subfigure}
+\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
+\end{figure*}
 
@@
 \label{sec:discussion}
+
+% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered
 
@@
 \textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best results when the training examples are from one structural category.
-This means it is suited to retrieve information chunks that always have the same surrounding structure.
+Our study results show that chunk retrieval with PBE gives best results when the training examples are structurally identical.
+This is because PROSE has difficulty synthesizing OR-based programs (see \Cref{sec:prose:impl}).
+PBE is thus suited to retrieve information chunks that always have the same surrounding or defining internal structure.
 To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.
 
-When the training examples are of the same structure, two examples are enough input for PROSE to synthesize a regular expression program with good recall.
+When the training examples are of the same structure, even one or two two examples are enough input for PROSE to synthesize a regular expression program with good recall.
 In our study, additional training examples did not improve the chunk retrieval.
+In fact, unless they were in some sense redudant, adding training examples above that even hindered the applicability of PBE.
 
@@
 \textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression program yields an output, PBE shows a high precision and a high recall.
+If the program synthesis succeeds and applying the regular expression program yields an output, PBE has high precision and recall.
 The tool clearly identifies a failing program synthesis or when no output from the program applied to a build log is obtained.
-Therefore, if there is an output, the user can have high confidence that it is the correct output.
-This makes output from PBE chunk retrieval well suited for consumption by other software components.
+Therefore, if there is an output, the user can have high confidence that it is the desired output.
+This preciseness makes output from PBE chunk retrieval well-suited for machine consumption.
 
@@
 \textbf{Configuration and Input}
-Chunk retrieval using CTS also yields better results the fewer structural categories are present in the training and test examples.
+Similar to PBE, chunk retrieval using CTS yields better results the fewer structural categories are present in the training and test examples.
 
@@
 
+% TODO Caro: I do not understand the following sentence.
 Extracting the average number of lines present in the training examples gives the best retrieval results for CTS, according to the F$_{1}$-score.
@@
 \textbf{Retrieval Output Usage}
+% TODO Caro: reforumlate this please
 CTS has good precision and recall on average, though the precision or recall of a chunk retrieval run is very hard to predict from the given result.
-Therefore, retrieval output from CTS is suited to be read by a human.
+Therefore, retrieval output from CTS is suited to be read by a human. This could include semi-automated procedures such as sending developers an email with the extracted build failure reason.
 
@@
 KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
-This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.
+This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log.
 For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
 
-With two training examples KWS achieves good recall.
+Going from one to two two training examples, KWS's recall improves
+siginficantly. However, further enlarging the training example count
+does not lead to further improvments.
 
@@
 \textbf{Retrieval Output Usage}
-Even though KWS has the highest recall of all three techniques, its precision is also the lowest.
-The output of a chunk retrieval with KWS is well suited to be read by humans.
-
-\begin{figure}[!t]
+While KWS has the highest recall of all three techniques, its precision is the lowest.
+The output of a chunk retrieval with KWS is well-suited to be read by humans, but ill-suited for consumption by automated tools.
+
+\begin{figure}[tb]
 		\centering
@@
 
-\subsection{Recommendations of Suitable Techniques}
+\subsection{Recommendation of Suitable Techniques}
 After discussing the three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
@@
 \noindent
-\textbf{Caveat!} This is a preliminary theory based on the results from our comparison study.
-The recommendations are therefore based on our implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
-
-This decision tree is the answer to our first research question about which criteria influence the suitability of a chunk retrieval technique.
+\textbf{Caveat!} This is a preliminary hypothesis based on the results from our comparison study.
+The recommendations could therefore be influenced by idiosyncrazies of our specific implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
+
+This decision tree in \Cref{fig:crt-recommendation} gives a nunanced answer to RQ2, about which criteria influence the suitability of a chunk retrieval technique.
 The earlier in the decision tree a criterion is noted, the more important it is when distinguishing the techniques.
@@
 The first and most important aspect are the structural categories.
-Are the information chunks you would like to retrieve always presented in the same structural way within the build logs?
+Are the information chunks one would like to retrieve always presented in the same structural way within the build logs?
 Then the information chunks in all training examples and the analyzed build log are in the same structural category.
@@
 When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.
+
+As a final recommendation, one could create a ``super analyzer'' by combining the different build log analysis techniques studied in this paper.
+Such a super analyzer would likely always first employ PBE (because of its high accuracy), followed by a combination of CTS and KWS.
+Other than initial setup and training time, there should be no downside to this approach if it is implemented in a transparent way to the underlying technique: the output of the super analyzer could include from which sub-tool it originated and thus facilitate automatic on-ward processing or interpretation of the result.
 
@@
 \textbf{Implementation}
-Our results are highly dependent on our implementation of the investigated chunk retrieval techniques and the libraries we used.
-Our implementation of PBE is severely based on the program synthesis provided by PROSE\@.
-Its limitations are therefore also mainly influenced by this library.
-For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
-This limitation was necessary to keep the synthesis performance reasonable.
-
-Our implementation of CTS is dependent on the library tex2vec and the way they split strings into word tokens.
+\label{sec:prose:impl}
+% TODO we need to say something about why we think that these limtiations do not actually harm our results
+Our results depend on the implementation of the investigated chunk retrieval techniques and the libraries we used.
+Our implementation of PBE is based on the program synthesis provided by PROSE\@.
+The idiosyncrazies of this framework influence our PBE results. Other frameworks similar to PROSE might have somewhat different strengths and weaknesses.
+For example, the need for examples from a single structural category stems from the fact that PROSE cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
+PROSE introduced this constraint to keep the synthesis performance reasonable.
+At the same time, this is clearly a current theoretical challenge of all PBE implementations, and we therefore attribute it to the technique itself, rather than the specific implementation.
+
+% TODO cite http://text2vec.org/
+Our implementation of CTS is dependent on the library {\tt text2vec} and the way it splits strings into word tokens.
+On the other hand, {\tt text2vec} is the de-facto standard library to do word embeddings in R.
 We intentionally chose a simple, minimally configured and tuned approach to compare against.
@@
 Our comparison study shows fewer measurements with many structural categories than with one category.
+% TODO Caro: Please explain the following further. Why does a realistic data set only have one or few structural categories?
 This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.
 
-\section{Conclusion and Future Work}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in their decision on how to analyze build logs.
-We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
-Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
-Secondary factors are the desired confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.
+\section{Future Work}
 
@@
 \begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set specifically for our comparative study, though it can be the basis for various further analyses of build log data.
+  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set \cite{} specifically for the comparative study in this paper, though it can be the basis for various further analyses of build log data.
   The keywords, for example, can be investigated to answer which keywords are used to search for the reason the build failed within build logs.
@@
 \end{itemize}
+
+\section{Conclusion}
+\label{sec:conclusion-fw}
+The goal of this paper was to support researchers and developers in their decision on how to analyze build logs.
+We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
+Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
+Secondary factors are the desired confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.
+
+As a final recommendation, one could create a ``super analyzer'' by combining the different build log analysis techniques studied in this paper.

### 2020-03-30 tse-paper/content.tex
Add intro plan
drafts for data extraction section

@@
+% TODO: Introduction structure
+% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
+
 % TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
+
 % TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
@@
 \subsection{Study Selection}
-
+% TODO shorten
 \Cref{fig:lit-survey} presents an overview of our study selection.
@@
 
+% TODO Caro cite guidelines
 Since we cannot take for granted that ``analyzing build logs'' is the
@@
 non-related works. This left us with 1,552 combined search results
-(2020-03-15).
+(2020-03-15). The full search queries are documented in our replication
+package \todo{cite/add replication package}.
 
@@
 Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). We automatically
+specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
 removed it to find all true duplicates. After this process, we were
@@
 
-Wtih these 259 remaining articles, we followed a backward snowball
+With these 259 remaining articles, we followed a backward snowball
 sampling for related work. This added three papers (five before
 duplicate elimination) to our literature set, coming to a total of 261
-articles.
-
-On the 261 artciles, We did a second filter phase by downloading the
-surviving papers, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed even traces of
+articles. % TODO Caro: update
+
+On the surviving artciles, we did a second filter phase by downloading the
+full articles, reading their abstracts, and searching the full text
+for the occurrence of ``log''. If these papers showed traces of
 working with build logs, we included them in our survey. For the
@@
 \subsection{Article Classification}
-%todo Caro: please write a draft for this :-)
+% TODO Caro: please write a draft for this :-)
 Having trimmed down the set of articles, we investigated them in depth.
+kept all articles that use logs from software builds as input to some kind of process.
+we wanted to characterize how researchers use buildlogs as input to any processes.
+Interesed in 
+\begin{itemize}
+  \item what kind of build logs they are using and the source of these logs.
+  \item what information they are retrieving from the logs, 
+  its kind (chunk/classification) and 
+  what they use the retrieved information for
+  \item which technique they are using to process the build logs,
+  in how much detail it is described and whether they published their tools
+\end{itemize}
+To objecifiy our data extraction we created a template of the targeted factors
+and performed a pilot on five articles. Two authors extracted the data from the
+five pilot articles and we held a consensus meeting to unify our understanding
+of the factors in the data extraction templates. The remaining articles were
+divided over these two authors. We inspected the articles as closesly as necessary,
+starting from occurences of ``log'' or ``build'' within the text.
+The full data extraction template and our results of this step can be found in
+our replication package \todo{cite}.
+
+In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
+For several cases, multiple articles extended others, though still reported on
+the same work with the respect to analyzing build logs.
+Of these we only considered the earliest article which reported on the processing
+of build logs.
+
+\subsection{Results}
+lots of:
+- categories + frequencies of answers
+
+\subsubsection{Retrieved Information}
+
+\subsubsection{Retrieval Technique}
+
+\subsubsection{Build Logs}
+
+\subsection{Discussion}
+various researchers analyzing build logs to support their research, tools developed
+to help developers \todo{motivational reference}.
+
+\subsubsection{Retrieved Information}
+why from build logs? 
+not avaliable in cleaner format
+much use for research, a bit of developer information / tools
+following: research so many logs that unfeasible to do manually, less focus on tools
+for devs (caveat! we excluded books and documentation on industrial tools -> many
+approaches there to make build logs digestible, tough many focus on general
+minimizing of the data presented, not retrieving specific chunks)
+
+\subsubsection{Retrieval Technique}
+broadly mentioned shortly, rarely explained in detail
+we follow that researchers often see this as an unimportant side fact
+work needed to be done to get the big work done
+
+\subsubsection{Build Logs}
+often focussed on specific logs, sometimes mentioned because of effort developing a parser
+other times also because other tools used in further research are limiting the scope
+(reference paper with PIT tool).
+many focus on maven because of it's prevalence also in respect to other tools
+much research done on travis ci logs b/c of their abundance and open availability
 
@@
 \section{Future Work}
+\todo{survey build logs tools in industry}
 

### 2020-03-31 tse-paper/content.tex
Add TODO
start on new structure in introduction

@@
 
-At the moment there is only anecdotal evidence on the performance of these techniques and on when a technique should be preferred over other alternatives.
-Developers and researches currently have little support when choosing which technique to use for a task.
-
-The goal of this article is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
-We aim to characterize different chunk retrieval techniques.
-For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
+\dots
+
+build logs valuable data source, but semi-structured and verbose,
+therefore need (automated) processing
+
+To gain an impression on how researchers are using information from build logs
+within their research and how they are gathering chunks from them to support
+developers in understanding build outcomes, we conducted a systematic mapping
+study.
+Our goal was to classify how and what for researchers use build logs as a source
+of data (\textbf{RQ1}).
+
+The outcomes of our study shows that there are various attempts to retrieve
+specific information from buildlogs. The resulting implementations are rarely
+available and therefore rarely reused. Because of the high development overhead
+of the custom parsers, many implementations are limited to small number of supported
+build tools.
+
+To address this, we implement three promising techniques for build log analysis.
+They retrieve specific chunks of targeted information and are configured by
+examples provided by the user.
+We conduct an empirical study on the \emph{LogChunks} \todo{cite} data set to
+gauge the performance of these chunk retrieval techniques and characterize
+when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
+
+% At the moment there is only anecdotal evidence on the performance of these
+% techniques and on when a technique should be preferred over other alternatives.
+% Developers and researches currently have little support when choosing which
+% technique to use for a task.
+
+% The goal of this article is to investigate different chunk retrieval techniques
+% for build logs and describe under which circumstances certain techniques can be
+% recommended over others.
+% We aim to characterize different chunk retrieval techniques.
+% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
+% influence the suitability of a chunk retrieval technique for CI build logs.
 
@@
 \begin{itemize}
-  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
-  \item a common text similarity approach (CTS), and
-  \item keyword search (KWS), an ad-hoc method for finding fitting passages by searching the whole text for the occurrence of a specific trigger word.
+  \item \textbf{Program Synthesis by Example (referred to as PBE)}
+  Based on 
+  \item \textbf{a common text similarity approach (CTS)}
+  \item \textbf{keyword search (KWS), an ad-hoc method for finding fitting passages by searching the whole text for the occurrence of a specific trigger word}
 \end{itemize}
@@
   \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
+  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
+  retrieval technique for build logs?
 \end{itemize}

### 2020-04-01 tse-paper/content.tex
explain techniques in intro, add running example and structural category example

@@
 % - unclear which information you want
+
+% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
+Finally, they are not really automatic
+
+\lstset{
+  morekeywords={},
+	basicstyle=\ttfamily\scriptsize,
+  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
+  showspaces=false,
+  showstringspaces=false,
+  stringstyle=\color{Plum},
+	frame=single,
+  extendedchars=false,
+  texcl=false,
+  aboveskip=\baselineskip,
+  belowskip=0pt
+}
 
@@
 
-\dots
-
-build logs valuable data source, but semi-structured and verbose,
-therefore need (automated) processing
-
 To gain an impression on how researchers are using information from build logs
@@
 examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} \todo{cite} data set to
+We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
 gauge the performance of these chunk retrieval techniques and characterize
 when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on 
-  \item \textbf{a common text similarity approach (CTS)}
-  \item \textbf{keyword search (KWS), an ad-hoc method for finding fitting passages by searching the whole text for the occurrence of a specific trigger word}
-\end{itemize}
-% TODO: Shortly describe each of these techniques
-
-% TODO: Add running example?
-\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% TODO: explain structural category based on running example from above?
-Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
 
@@
 \end{simplebox}
+
+% At the moment there is only anecdotal evidence on the performance of these
+% techniques and on when a technique should be preferred over other alternatives.
+% Developers and researches currently have little support when choosing which
+% technique to use for a task.
+
+% The goal of this article is to investigate different chunk retrieval techniques
+% for build logs and describe under which circumstances certain techniques can be
+% recommended over others.
+% We aim to characterize different chunk retrieval techniques.
+% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
+% influence the suitability of a chunk retrieval technique for CI build logs.
+
+We implement and evaluate three chunk retrieval techniques:
+\begin{itemize}
+  \item \textbf{Program Synthesis by Example (referred to as PBE)}
+  Based on user examples of build logs and targeted log chunks, PBE synthesizes
+  a regular expression matching the given chunks within the build logs.
+  \item \textbf{Common Text Similarity (CTS)}
+  Using the Vector Space Model, CTS selects those lines of a log which are
+  most similar to the lines present in example chunks provided by the user.
+  \item \textbf{Keyword Search (KWS)}
+  Ad-hoc method for finding fitting passages by searching the whole text for
+  the occurrence of specific trigger words.
+\end{itemize}
+
+\begin{figure}[!t]
+  \centering
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+FAILURE: Build failed with an exception.
+
+* What went wrong:
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
+Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
+> Task with path 'testDebug' not found in project ':app'.
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+
+* Try:
+  \end{lstlisting}  
+  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
+  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
+  \label{lst:chunk-example-1}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+FAILURE: Build failed with an exception.
+
+* What went wrong:
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
+Execution failed for task ':app:connectedAndroidTest'.
+> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+
+* Try:
+  \end{lstlisting}  
+  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
+  \label{lst:chunk-example-2}
+\end{figure}
+
+\lstset{
+  language=caml,
+  morekeywords={StartExtraction, RegexPosition, RegexPair, EndExtraction},
+  keywordstyle=\bfseries\color{black},
+  escapeinside=//
+}
+\begin{figure}[!t]
+  \centering
+  \begin{lstlisting}[breaklines=true]
+StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
+  \end{lstlisting}  
+  \caption{Simiplified regular expression produced by PBE when trained
+  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
+  \label{lst:prose-program-simplified}
+\end{figure}
+
+\lstset{
+  language=,
+  morekeywords={},
+  texcl=false
+}
+\begin{figure}[!t]
+  \centering
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+=== RUN   TestSeparator
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
+--- FAIL: TestSeparator (0.03s)
+    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+=== RUN   TestGenerateHTML
+  \end{lstlisting}  
+  \caption{Example of a log chunk. \todo{which build tool?}
+  \todo{move to where structural category explanation}}
+  \label{lst:chunk-example-3}
+\end{figure}
+
+The results of our empirical comparison study on the chunk retrieval techniques
+show that the structural representation of the targeted chunk greatly influences
+the performance of the chunk retrieval techinques.
+\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary log chunks
+from Android/Gradle build logs. Both chunks contain the information on why the
+corresponding build failed. When PBE is trained on these two examples it produces
+a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
+starts after a colon followed by a line separator and before a capital letter.
+It ends before two line separators, consistent with the two example chunks from
+\Cref{lst:chunk-example-1,lst:chunk-example-2}.
+This shows, that the characters structuring the text around the chunk are cruicial
+for regular expressions to identify the targeted log chunk. In fact, if the third
+example from \Cref{lst:chunk-example-3} with a different structural representation is added,
+PBE is not able to syntesize a program and returns ``\texttt{no program found}''
+
+% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
+% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
+% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
+% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
+% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
 
@@
 
-\noindent
-\textbf{Our work contributes:}
-\begin{itemize}
-  \item A tool with three prototypical implementations of chunk retrieval techniques:
-        \begin{itemize}
-          \item program synthesis from examples using the Microsoft PROSE library (PBE),
-          \item a common information retrieval approach using text similarity (CTS), and
-          \item a keyword search approach (KWS).
-        \end{itemize}
-  \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-  \item Guidelines on choosing a suitable chunk retrieval technique.
-\end{itemize}
+% \noindent
+% \textbf{Our work contributes:}
+% \begin{itemize}
+%   \item A tool with three prototypical implementations of chunk retrieval techniques:
+%         \begin{itemize}
+%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
+%           \item a common information retrieval approach using text similarity (CTS), and
+%           \item a keyword search approach (KWS).
+%         \end{itemize}
+%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
+%   \item Guidelines on choosing a suitable chunk retrieval technique.
+% \end{itemize}
 
@@
 (2020-03-15). The full search queries are documented in our replication
-package \todo{cite/add replication package}.
+package~\cite{brandt2020chunk-replication}.
 
@@
   morekeywords={INFO, WARN, 2008-11-09},
-	basicstyle=\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\color{blue},
-	frame=single,
-  extendedchars=false,
-  texcl=false
+  keywordstyle=\color{Plum},
+  escapeinside=**
 }
@@
   \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet- Responder: Received block blk_3587508140051953248 of size 67108864 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140051953248 terminating
+2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
+2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
   \end{lstlisting}  
@@
   language=caml,
-	basicstyle=\scriptsize,
   morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{blue},
   keywordstyle=\bfseries\color{black},
-	frame=single,
-  extendedchars=false,
   escapeinside=//
@@
 When developers scavenge for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is to search for related keywords.
-Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set~\cite{logchunks}.
+Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
 % As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
@@
 \subsection{Random Line Retrieval}
-\label{sec:r:rlr}
+\label{sec:expl-rlr}
 
@@
 \subsection{Other Techniques}
-\label{sec:expl-rlr}
 %Literature mentions further build log analysis techniques.
@@
 \lstset{
-  morekeywords={Test Output, Desired Test Output},
-	basicstyle=\scriptsize,
+  language=,
+  morekeywords={Test, Output, Desired},
+	basicstyle=\ttfamily\scriptsize,
   postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
@@
   showstringspaces=false,
-  keywordstyle=\color{blue},
+  keywordstyle=\textbf,
 	frame=single,

### 2020-04-01 tse-paper/content.tex
describe struc cats

@@
 
-CI builds produce logs which report the results of the steps within the build. The information stored in build logs can and has
+CI builds produce logs which report the results of the steps within the build.
+The information stored in build logs can and has
 already been used for a variety of applications. One prominent dataset
@@
 
-\lstset{
-  language=caml,
-  morekeywords={StartExtraction, RegexPosition, RegexPair, EndExtraction},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
+\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
+  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
 \begin{figure}[!t]
@@
 the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary log chunks
-from Android/Gradle build logs. Both chunks contain the information on why the
+\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
+from Android/Gradle build logs marked in blue.
+Both chunks contain the information on why the
 corresponding build failed. When PBE is trained on these two examples it produces
@@
 \Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are cruicial
-for regular expressions to identify the targeted log chunk. In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural representation is added,
-PBE is not able to syntesize a program and returns ``\texttt{no program found}''
+This shows, that the characters structuring the text around the chunk are
+cruicial for regular expressions to identify the targeted log chunk.
+In fact, if the third
+example from \Cref{lst:chunk-example-3} with a different structural
+representation is added, PBE is not able to syntesize a program and returns
+``\texttt{no program found}''.
+We express this difference in structural representation through dividing log
+chunks into structural categories. The chunks from
+\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
+category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
 
@@
 
-% TODO: Add structural category explanation
-% TODO: Add running example
-
 Our study of the three techniques on \emph{LogChunks} shows that
 \begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a single structural category.
-  \item CTS shows the best average precision, though precision and recall of a retrieval is hard to determine from the given result.
+  \item PBE yields very accurate results when trained with two examples from a
+  single structural category.
+  \item CTS shows the best average precision, though precision and recall of a
+  retrieval is hard to determine from the given result.
   A small increase in the number of training examples has no noticeable influence.
@@
   \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories are present in the training examples.
+  It is the technique with the best recall when multiple structural categories
+  are present in the training examples.
 \end{itemize}
@@
 In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS ssems to be the best choice.
-However, its low precision---it extracts a context of multiple lines around a finding---makes it generally unsuited for automatic on-ward processing and instead requires a human to further inspect and interpret the output chunk.
+is unpredictable or varies greatly, KWS seems to be the best choice. However,
+its low precision---it extracts a context of multiple lines around a
+finding---makes it generally unsuited for automatic on-ward processing and
+instead requires a human to further inspect and interpret the output chunk.
 

### 2020-04-01 tse-paper/content.tex
auto-wrap my old text for consistency

@@
 \subsection{Discussion}
-various researchers analyzing build logs to support their research, tools developed
-to help developers \todo{motivational reference}.
+various researchers analyzing build logs to support their research,
+tools developed to help developers \todo{motivational reference}.
 
 \subsubsection{Retrieved Information}
-why from build logs? 
-not avaliable in cleaner format
-much use for research, a bit of developer information / tools
-following: research so many logs that unfeasible to do manually, less focus on tools
-for devs (caveat! we excluded books and documentation on industrial tools -> many
-approaches there to make build logs digestible, tough many focus on general
-minimizing of the data presented, not retrieving specific chunks)
+why from build logs? not avaliable in cleaner format much use for
+research, a bit of developer information / tools following: research
+so many logs that unfeasible to do manually, less focus on tools for
+devs (caveat! we excluded books and documentation on industrial tools
+-> many approaches there to make build logs digestible, tough many
+focus on general minimizing of the data presented, not retrieving
+specific chunks)
 
 \subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail
-we follow that researchers often see this as an unimportant side fact
-work needed to be done to get the big work done
+broadly mentioned shortly, rarely explained in detail we follow that
+researchers often see this as an unimportant side fact work needed to
+be done to get the big work done
 
 \subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort developing a parser
-other times also because other tools used in further research are limiting the scope
-(reference paper with PIT tool).
-many focus on maven because of it's prevalence also in respect to other tools
-much research done on travis ci logs b/c of their abundance and open availability
+often focussed on specific logs, sometimes mentioned because of effort
+developing a parser other times also because other tools used in
+further research are limiting the scope (reference paper with PIT
+tool). many focus on maven because of it's prevalence also in respect
+to other tools much research done on travis ci logs b/c of their
+abundance and open availability
 
@@
 \subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
-In addition, they notice that most failures are resolved within two builds.
-They based their analyses on sets of build logs collected from industry partners.
-They develop a custom parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and find that most builds fail because of failing tests.
-For most projects, over half of the failed builds follow a previous failed build.
-Rausch et al.'s data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
-They determine that testing failures are more common than compilation errors.
-Open source builds fail most often because of unit tests, whereas release preparations are the primary cause in industrial projects.
-Their data stems from analyzing build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent} with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
-They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
-Their analysis starts with manual categorization of build logs.
-They select keywords and strings that identify their targeted categories and code a script to automatically classify logs based on these keywords.
+Various researchers studied why CI builds fail and into the impact of
+build failures on the development workflow.
+
+Seo et al.~\cite{seo2014programmers} find that a small group of error
+types such as dependency mismatches are the most prominent cause of
+build failures at Google. In addition, they notice that most failures
+are resolved within two builds. They based their analyses on sets of
+build logs collected from industry partners. They develop a custom
+parser to classify error messages reported by Java and C++ builds.
+
+Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
+source Java projects and find that most builds fail because of failing
+tests. For most projects, over half of the failed builds follow a
+previous failed build. Rausch et al.'s data shows that most failures
+occur in the second half of the build runtime, which can cause long
+delays in the feedback loop, especially when builds are automatically
+retried upon failure.
+
+Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
+in Java to industrial ones. They determine that testing failures are
+more common than compilation errors. Open source builds fail most
+often because of unit tests, whereas release preparations are the
+primary cause in industrial projects. Their data stems from analyzing
+build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
+with regular expressions.
+
+Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
+breakage data. They classify build failures from \emph{TravisTorrent}
+according to whether they were caused by an environmental failure or
+caused by a developer change. Their analysis starts with manual
+categorization of build logs. They select keywords and strings that
+identify their targeted categories and code a script to automatically
+classify logs based on these keywords.
 
@@
 \textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers presented
-in this section create parsers and regular expression-based programs.
-This task of retrieving specific chunks of text from the build logs can be
-solved by the chunk retrieval techniques we compare in this article.
-Our results can support researchers in choosing a suitable technique for their
-data set of build logs and the chunks they want to retrieve.
-By relieving them from building custom parsers we enable them to cover a much
-wider range of languages and build tools in their studies.
+To leverage the valuable information within build logs the researchers
+presented in this section create parsers and regular expression-based
+programs. This task of retrieving specific chunks of text from the
+build logs can be solved by the chunk retrieval techniques we compare
+in this article. Our results can support researchers in choosing a
+suitable technique for their data set of build logs and the chunks
+they want to retrieve. By relieving them from building custom parsers
+we enable them to cover a much wider range of languages and build
+tools in their studies.
 
@@
 \label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why their build failed.
-Several researchers investigate how to support developers in working with verbose build logs.
-Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
-They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
-%The hint generators leverage this structured access to the information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
-In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
-%Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used to fill similar structured representations with information from build logs.
-As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to reduce the portions of a log that a developer has to inspect.
-Their techniques remove lines that appear both in logs from passing and failing builds and use a modified \emph{Term Frequency Inverse Document Frequency} (TF-IDF) weighting to identify term vectors likely to occur with failures.
-Their diff technique can be interpreted as a chunk retrieval technique, where the targeted information is defined by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a basic structuring of the build logs within their log viewer using \emph{log folds}~\cite{travis2019logfolds}.
-They add fold identifiers around common commands and setup or teardown build phases and collapse the contained lines by default.
+Build logs are a valuable data source for developers to find out why
+their build failed. Several researchers investigate how to support
+developers in working with verbose build logs. Vassallo et
+al.~\cite{vassallo2018un-break} try to shorten the time it takes
+developers to understand build logs. They parse
+Maven~\cite{maven2019website} build logs into a structured
+representation and create hint generators.
+%The hint generators leverage this structured access to the
+%information within the build log to propose fixes.
+For example, one of the hint generators queries stack overflow for
+discussions related to why the build failed. In a qualitative study
+they observed that highlighting the locality and context of an issue
+is helpful to programmers.
+%Their tool BART is published as a Jenkins
+%Plugin~\cite{bart2019plugin}.
+The chunk retrieval techniques we compare in this article can be used
+to fill similar structured representations with information from build
+logs. As they simplify the construction of parsers they would enable
+developers and researchers to cover a wider array of build tools,
+which is the main influence factor on the structure of a build log.
+
+Amar et al.~\cite{amar2019mining} compare different approaches to
+reduce the portions of a log that a developer has to inspect. Their
+techniques remove lines that appear both in logs from passing and
+failing builds and use a modified \emph{Term Frequency Inverse
+Document Frequency} (TF-IDF) weighting to identify term vectors likely
+to occur with failures. Their diff technique can be interpreted as a
+chunk retrieval technique, where the targeted information is defined
+by the past failures used as basis for the weighted term vectors.
+
+Travis itself already provides build log augmentation in the form of a
+basic structuring of the build logs within their log viewer using
+\emph{log folds}~\cite{travis2019logfolds}. They add fold identifiers
+around common commands and setup or teardown build phases and collapse
+the contained lines by default.
 
@@
 \label{sec:log-analysis}
-A related field of log processing is the processing of system log files produced during runtime.
-A main difference between build logs and system logs is that system logs are fundamentally structured through events.
-Each line in a log file represents one event with a set of fields: timestamp, verbosity level and raw message content~\cite{he2017towards}.
-Figure \ref{lst:system-log} shows example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
-Next, the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
-The output of a log parser is an ordered list of timed events and their corresponding parameter values~\cite{he2016evaluation}.
-This structured log is then the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
-%Xu et al.~\cite{xu2009detecting} leverage the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied to build logs.
-One example is comparing execution traces to reference traces of intended behavior to detect anomalies.
-Amar et al.~\cite{amar2019mining} employed a similar approach to detect relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of events.
-%A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
-Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.
-by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+A related field of log processing is the processing of system log
+files produced during runtime. A main difference between build logs
+and system logs is that system logs are fundamentally structured
+through events. Each line in a log file represents one event with a
+set of fields: timestamp, verbosity level and raw message
+content~\cite{he2017towards}. Figure \ref{lst:system-log} shows
+example lines from a system log.
+
+The first goal in analyzing system log files is ubiquitously to
+separate constant and variable parts within a log
+message~\cite{nagappan2010abstracting,he2017towards}. Next, the log
+messages are clustered into log events, unifying messages with
+identical constant parts and varying parameters. The output of a log
+parser is an ordered list of timed events and their corresponding
+parameter values~\cite{he2016evaluation}. This structured log is then
+the input to various machine learning and data mining processes.
+%Researchers mine patterns for operational
+%profiling~\cite{nagappan2009efficiently},
+%debugging~\cite{oliner2012advances}, performance analytics or anomaly
+%detection~\cite{nagappan2010abstracting}. Xu et
+%al.~\cite{xu2009detecting} leverage the connection of log statements
+%to the source code producing them to separate messages into constant
+%and variable parts more accurately.
+
+The techniques developed for system log analysis can also be applied
+to build logs. One example is comparing execution traces to reference
+traces of intended behavior to detect anomalies. Amar et
+al.~\cite{amar2019mining} employed a similar approach to detect
+relevant lines in build logs.
+%Classic log parsers interpret the whole log file into a sequence of
+%events. A similar approach could also be applied to build logs to
+%determine the sequence of executed build steps or phases.
+In this article, we focus on extracting a single specified information
+from the build log as a whole with chunk retrieval techniques. Chunk
+retrieval techniques are used as a part of log parsing to retrieve the
+values of variable parts in a log message, e.g. by using regular
+expressions~\cite{nagappan2010abstracting,xu2009detecting}.
 
@@
 \label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques}
-%The techniques we investigate are based on existing methods of Programming by Example.%, information extraction and information retrieval.
-%This section presents different Programming by Example resources surrounding the PROSE library.
-%We explain its generic program synthesis algorithm and how PROSE synthesizes text extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program synthesis that enables users to automate repetitive tasks, without them having to explicitly codify a computer program.
-One has to provide prototypical examples of the input and the desired output.
-A
-synthesis algorithm tries to create a program (based on a regular language) that transforms the input to the output.
-The minimum working condition is for this when replayed on the examples inputs is to provide the specified output, but, hopefully, PBE is as close as possbile to the user's intention and thus also works on a different and larger set of inputs.
-This section introduces the theoretical foundations of the program synthesis
-algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research.
-Next, this section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
+% \section{Information Extraction and Retrieval Techniques} The
+% techniques we investigate are based on existing methods of
+% Programming by Example.%, information extraction and information
+% retrieval. This section presents different Programming by Example
+% resources surrounding the PROSE library. We explain its generic
+% program synthesis algorithm and how PROSE synthesizes text
+% extraction programs, the foundation of PBE\@.
+
+Programming by Example (PBE) is a form of generalized program
+synthesis that enables users to automate repetitive tasks, without
+them having to explicitly codify a computer program. One has to
+provide prototypical examples of the input and the desired output. A
+synthesis algorithm tries to create a program (based on a regular
+language) that transforms the input to the output. The minimum working
+condition is for this when replayed on the examples inputs is to
+provide the specified output, but, hopefully, PBE is as close as
+possbile to the user's intention and thus also works on a different
+and larger set of inputs. This section introduces the theoretical
+foundations of the program synthesis algorithm of the \emph{PROgram
+Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
+The PROSE framework is developed by Microsoft Research. Next, this
+section presents the FlashExtract DSL, which defines text extraction
+tasks within PROSE and is the basis for the implementation of our
+chunk retrieval technique PBE\@.
 
 \subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program synthesis in the Microsoft PROSE framework.
-FlashMeta separates the inductive synthesis algorithm from the domain specific capabilities of the desired program by encoding the possible program space in a domain specific language (DSL).
-The user specifies the desired program behavior by providing in/output examples (I/O examples).
-FlashMeta uses \emph{witness functions}, provided by the DSL, to divide the synthesis into smaller subtasks.
-For each of these subtasks it enumerates all possible programs that solve the subtask consistent with the set of I/O examples.
-A program is consistent with a set of I/O examples if, for each input example, it produces the corresponding output~\cite{mitchell1982generalization}.
-The possible subprograms are joined and stored in a \emph{version space algebra} (VSA)~\cite{mitchell1982generalization}.
-This a tree structure, which space-efficiently saves candidate programs for tasks by sharing common subexpressions.
-Next, FlashMeta ranks the enumerated programs according to which ones the user most likely intended.
-The DSL also provides the ranking characteristics.
-From the ranked VSA, FlashMeta can then return a ranked list of complete programs consistent with the user's example.
-
-% In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized program.
-
-% The different applications of PROSE presented in the following paragraphs were all eventually implemented as DSLs for the FlashMeta synthesis algorithm.
+The FlashMeta framework presented by Polozov and
+Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
+synthesis in the Microsoft PROSE framework. FlashMeta separates the
+inductive synthesis algorithm from the domain specific capabilities of
+the desired program by encoding the possible program space in a domain
+specific language (DSL). The user specifies the desired program
+behavior by providing in/output examples (I/O examples). FlashMeta
+uses \emph{witness functions}, provided by the DSL, to divide the
+synthesis into smaller subtasks. For each of these subtasks it
+enumerates all possible programs that solve the subtask consistent
+with the set of I/O examples. A program is consistent with a set of
+I/O examples if, for each input example, it produces the corresponding
+output~\cite{mitchell1982generalization}. The possible subprograms are
+joined and stored in a \emph{version space algebra}
+(VSA)~\cite{mitchell1982generalization}. This a tree structure, which
+space-efficiently saves candidate programs for tasks by sharing common
+subexpressions. Next, FlashMeta ranks the enumerated programs
+according to which ones the user most likely intended. The DSL also
+provides the ranking characteristics. From the ranked VSA, FlashMeta
+can then return a ranked list of complete programs consistent with the
+user's example.
+
+% In addition to I/O examples of the intended program, the user can
+% also provide examples with only input or negative input examples.
+% Negative input examples should not be processed by the synthesized
+% program.
+
+% The different applications of PROSE presented in the following
+% paragraphs were all eventually implemented as DSLs for the FlashMeta
+% synthesis algorithm.
 
 \subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text, websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs from semi-structured text based on regular expressions.
-Users can extract multiple fields and structure them with hierarchy and sequence.
-% FlashExtract synthesizes programs to extract each of the fields leveraging the information about hierarchical containment and sequentiality.
-% It eliminates the need for the user to understand the entire structure of the processed document and decreases the effort of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of two cut positions.
-A position is either specified by an absolute character index or by a pair of two regular expressions.
-The first regular expression matches the substring directly before the characterized position, the second regular expression matches the substring directly after.
-A regular expression in FlashExtract is a concatenation of tokens, e.g.\ standard character classes or string literals frequently occurring in the input examples.
-Figure \ref{lst:prose-program} shows a text extraction program synthesized by FlashExtract.
-This program defines the first position as after a colon followed by a newline character and before a piece of text with all capital letters.
-It defines the second position as before two newline characters.
-
-Apart from automatic completion in Excel spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for two other Microsoft product features:
-Microsoft's system log analysis tool Azure Monitor lets users define custom log fields~\cite{azure2019custom}.
-The ConvertFrom-String function in PowerShell allows a user to specify an example template to extract hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build logs with our chunk retrieval technique PBE\@.
+Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
+for the Microsoft PROSE framework.
+% It enables a user to define text extraction programs for text,
+% websites and spreadsheets by giving I/O examples.
+FlashExtract's instantiation for text synthesizes extraction programs
+from semi-structured text based on regular expressions. Users can
+extract multiple fields and structure them with hierarchy and
+sequence.
+% FlashExtract synthesizes programs to extract each of the fields
+% leveraging the information about hierarchical containment and
+% sequentiality. It eliminates the need for the user to understand the
+% entire structure of the processed document and decreases the effort
+% of developing a suitable extraction program.
+
+FlashExtract models the extraction of a single substring as a pair of
+two cut positions. A position is either specified by an absolute
+character index or by a pair of two regular expressions. The first
+regular expression matches the substring directly before the
+characterized position, the second regular expression matches the
+substring directly after. A regular expression in FlashExtract is a
+concatenation of tokens, e.g.\ standard character classes or string
+literals frequently occurring in the input examples. Figure
+\ref{lst:prose-program} shows a text extraction program synthesized by
+FlashExtract. This program defines the first position as after a colon
+followed by a newline character and before a piece of text with all
+capital letters. It defines the second position as before two newline
+characters.
+
+Apart from automatic completion in Excel
+spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for
+two other Microsoft product features: Microsoft's system log analysis
+tool Azure Monitor lets users define custom log
+fields~\cite{azure2019custom}. The ConvertFrom-String function in
+PowerShell allows a user to specify an example template to extract
+hierarchical data from a text document~\cite{powershell2019convert}.
+
+We apply the text instantiation of FlashExtract to the domain of build
+logs with our chunk retrieval technique PBE\@.
 
@@
 \label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval techniques we study in this article, namely program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
+This section introduces key concepts of the three chunk retrieval
+techniques we study in this article, namely program synthesis by
+example (PBE), common text similarity (CTS), and keyword search (KWS).
+We use these techniques to extract text chunks from build logs that
+represent a specific, targeted information.
 
@@
 \label{sec:blirt}
-In this article, we evaluate different techniques to automatically retrieve pieces of information that appear literally in the build logs, i.e., techniques that do not aggreagte, combine, or deducted information.
-We call such pieces of information from build logs \emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and parser to analyze the entire structure of build logs, but focus on ad-hoc extracting just one specific piece of information per configuration.
-
-With the term \textit{configuration,} we abstract over the training and parametrization that different techniques require in different forms.
-A configuration can be explicitly stated or implicitly dervied by learning through provided examples.
-It is therefore a manual specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to identify the targeted information chunk in a build log.
-Each chunk retrieval technqiue has a specific \textit{granularity}, i.e.,\ the smallest piece of text it can return (e.g., a line, or a word). The granularity might be adjustable by configuration.
-\emph{Running a chunk retrieval technique} means to execute a fully configured technique to consumes as input a build log in plain text format and to produce an array as output.
-The array consists of substrings of the build log text.
+In this article, we evaluate different techniques to automatically
+retrieve pieces of information that appear literally in the build
+logs, i.e., techniques that do not aggreagte, combine, or deducted
+information. We call such pieces of information from build logs
+\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
+The techniques we investigate here do not require a formal lexer and
+parser to analyze the entire structure of build logs, but focus on
+ad-hoc extracting just one specific piece of information per
+configuration.
+
+With the term \textit{configuration,} we abstract over the training
+and parametrization that different techniques require in different
+forms. A configuration can be explicitly stated or implicitly dervied
+by learning through provided examples. It is therefore a manual
+specification of which information the chunk retrieval should target.
+It also supplies the necessary information for the technique to
+identify the targeted information chunk in a build log. Each chunk
+retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
+smallest piece of text it can return (e.g., a line, or a word). The
+granularity might be adjustable by configuration. \emph{Running a
+chunk retrieval technique} means to execute a fully configured
+technique to consumes as input a build log in plain text format and to
+produce an array as output. The array consists of substrings of the
+build log text.
 
@@
 \label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model.
-% We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
-% In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs, which we refer to as \emph{CTS}\@.
+% Text Similarity approaches are used to filter unstructured textual
+% software
+% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+% One common and simple technique is the Vector Space Model. We
+% investigate when text similarity is a suitable technique to retrieve
+% information chunks from build logs. In the following we will explain
+% the concept of how we apply text similarity to information retrieval
+% from CI build logs, which we refer to as \emph{CTS}\@.
 
 \subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@
+To configure chunk retrieval though text similarity we chose to use
+the same concept of examples as for PBE\@
 % TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}.
-The lines of the output strings of the training examples define our search query.
-The algorithm splits the search query into single lines and identifies tokens, in our case words.
-Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
-Finally, the algorithm applies TF-IDF to the matrix, a best practice for natural language queries~\cite{lee1997document}.
+and apply the Vector Space Model~\cite{schutze2008introduction}. The
+lines of the output strings of the training examples define our search
+query. The algorithm splits the search query into single lines and
+identifies tokens, in our case words. Then we build a
+document-term-frequency matrix over the lines from the search query
+and prune very often or very rarely appearing words. Finally, the
+algorithm applies TF-IDF to the matrix, a best practice for natural
+language queries~\cite{lee1997document}.
 
 \subsubsection{Application}
-To retrieve the desired information from a build log, we parse the whole text and process it in the same way as the output of the training examples.
-The algorithm calculates the cosine similarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
-After summing up the similarities of each build log line to all search query lines, we sort the build log lines in decreasing similarity.
-The average number of lines in the outputs of the training examples determines how many of the most similar lines are returned as the output of the retrieval run.
+To retrieve the desired information from a build log, we parse the
+whole text and process it in the same way as the output of the
+training examples. The algorithm calculates the cosine
+similarity~\cite{korenius2007principal} to compare each line of the
+build log with each line of the search query. After summing up the
+similarities of each build log line to all search query lines, we sort
+the build log lines in decreasing similarity. The average number of
+lines in the outputs of the training examples determines how many of
+the most similar lines are returned as the output of the retrieval
+run.
 
@@
 \label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is to search for related keywords.
-Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
-% In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.
+When developers scavenge for a specific piece of information within a
+large amount of unstructured information, a first ad-hoc approach they
+use is to search for related keywords. Indeed, this was one of the
+most common approaches we took when searching for the reason the build
+failed within a log while creating the \emph{LogChunks} data
+set~\cite{brandt2020logchunks}.
+% As this is a technique readily available in many tools developers
+% use to view build logs, we study when such a keyword search is
+% suitable for retrieving information chunks from CI build logs. In
+% the following we will explain how we use simple keyword search to
+% retrieve information from CI build logs, which we refer to as
+% \emph{KWS}\@.
 
 \subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@.
-To better compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted chunk or close to it.
-The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.
+A set of keywords configures the chunk retrieval with KWS\@. To better
+compare KWS with PBE and CTS, we also configure it through examples.
+We associate each example with keywords which appear in the targeted
+chunk or close to it. The configuring keywords for KWS are the ones
+that appear most often in the keywords of all training examples.
 % TODO Caro Please explain above sentence more precisely
@@
 \subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the keywords.
-As keywords are often not directly describing the desired information, but rather appear close to the desired information, KWS also retrieves the lines around the found keyword.
-The number of surrounding lines retrieved is the average of lines in the output of the training examples.
+For a retrieval run, we take a whole build log file as input and
+search for all exact occurrences of the keywords. As keywords are
+often not directly describing the desired information, but rather
+appear close to the desired information, KWS also retrieves the lines
+around the found keyword. The number of surrounding lines retrieved is
+the average of lines in the output of the training examples.
 
@@
 \label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes programs according
-% to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming knowledge~\cite{mayer2015user}.
-% In the context of text extraction through regular expressions, Programming by Example relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
-% In this work, we refer to our interpretation of Programming by Example as \emph{PBE}\@.
-% We investigate the suitability of PBE to retrieve information chunks from build logs.
-% In the following, we explain the configuration and application of PBE to chunk retrieval from CI build logs.
+% \emph{Programming by Example} is a technique which synthesizes
+% programs according to in- and output examples provided by the user.
+% It enables users to create programs without a priori programming
+% knowledge~\cite{mayer2015user}. In the context of text extraction
+% through regular expressions, Programming by Example relieves the
+% developer from having to understand the whole document structure to
+% solve a single extraction task~\cite{le2014flashextract:}. In this
+% work, we refer to our interpretation of Programming by Example as
+% \emph{PBE}\@. We investigate the suitability of PBE to retrieve
+% information chunks from build logs. In the following, we explain the
+% configuration and application of PBE to chunk retrieval from CI
+% build logs.
 
 \subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by Example, we refer to them in short
-as \emph{examples}.
-The \emph{input} is the text of the build log file.
-The \emph{output} is an array of substrings of the log file text, representing the substrings that should be retrieved by the synthesized program when given the corresponding input file.
-One or multiple examples, the training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted.
-The PROSE program synthesis then tries to construct a program consistent with all training examples.
-% A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn uses the FlashMeta algorithm.
-% Both are described in Section~\ref{sec:rw-prose}.
-
-% TODO Caro: The following is very obvious and could apply to any technique. 
+In- and output example pairs are the main driver of Programming by
+Example, we refer to them in short as \emph{examples}. The
+\emph{input} is the text of the build log file. The \emph{output} is
+an array of substrings of the log file text, representing the
+substrings that should be retrieved by the synthesized program when
+given the corresponding input file. One or multiple examples, the
+training set, \emph{configure} a specific chunk retrieval with PBE:
+they define the substring of a build log that should be extracted. The
+PROSE program synthesis then tries to construct a program consistent
+with all training examples.
+% A program is consistent with an example if it returns the defined
+% output when executed on the defined
+% input~\cite{mitchell1982generalization}.
+PBE reports an error back to the user if it could not synthesize a
+consistent program.
+% The program synthesis builds on the FlashExtract DSL, which in turn
+% uses the FlashMeta algorithm. Both are described in
+% Section~\ref{sec:rw-prose}.
+
+% TODO Caro: The following is very obvious and could apply to any
+% technique. 
 \subsubsection{Application}
-A run of PBE takes a build log file as input and applies the synthesized regular expression program.
-It then returns the substring of the build log matched by the program or an empty string if the program found no match.
+A run of PBE takes a build log file as input and applies the
+synthesized regular expression program. It then returns the substring
+of the build log matched by the program or an empty string if the
+program found no match.
 
@@
 
-In our evaluation, we want to compare against a baseline of randomly picking lines from the build log.
-RLR essentially mimicks the situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should return.
-For a fair comparison to the other techniques (whose number of returned lines is dynamic), we configure RLR to return the average number of lines in the chunks of the training examples.
+In our evaluation, we want to compare against a baseline of randomly
+picking lines from the build log. RLR essentially mimicks the
+situation of guessing purely blindly which lines might be interesting.
+The only configuration option for RLR is the number of lines it should
+return. For a fair comparison to the other techniques (whose number of
+returned lines is dynamic), we configure RLR to return the average
+number of lines in the chunks of the training examples. 
 % TODO Caro: some more details here?
@@
 \subsection{Other Techniques}
-%Literature mentions further build log analysis techniques.
-%This section describes them with our notion of chunk retrieval techniques.
+%Literature mentions further build log analysis techniques. This
+%section describes them with our notion of chunk retrieval techniques.
 
@@
 \textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information retrieval to identify relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
-The configuration for the technique is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not present in the successful build log and contain terms related to the given past failures.
+Amar et al.\ use a technique based on line diffs and information
+retrieval to identify relevant lines from a failed build
+log~\cite{amar2019mining}, as we describe in more detail in
+Section~\ref{sec:rw-bl-analysis}. The configuration for the technique
+is the log from the last successful build and relevant past failures.
+This technique retrieves the lines from a build log that are not
+present in the successful build log and contain terms related to the
+given past failures.
 
 \subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a unifying interface.
-The unified interface is implemented in Ruby and calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
-We implemented CTS, KWS and RLR using R and the text2vec library~\cite{text2vec2019webpage}.
+For our comparison study we implemented PBE, CTS, KWS and RLR and a
+unifying interface. The unified interface is implemented in Ruby and
+calls the separate technique implementations over the command line.
+The implementation of PBE in C\# is based on the Microsoft PROSE
+library~\cite{prose2019webpage}. We implemented CTS, KWS and RLR using
+R and the text2vec library~\cite{text2vec2019webpage}.
 
@@
 
-To investigate which techqnique is best suited to retrieve chunks from CI build
-logs we evaluate them on the \emph{LogChunks}~\cite{brandt2020logchunks} data set.
-This section describes our study design and which metrics we measure to answer our research questions.
-In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.
+To investigate which techqnique is best suited to retrieve chunks from
+CI build logs we evaluate them on the
+\emph{LogChunks}~\cite{brandt2020logchunks} data set. This section
+describes our study design and which metrics we measure to answer our
+research questions. In the presentation of the results, we first focus
+on each of the three techniques and later compare them against each
+other.
 
 \subsection{LogChunks}
-For this study we created the previously published data set \emph{LogChunks}.
-It encompasses 797 build logs from Travis CI, stemming from a broad range of 80
-GitHub repositories and 29 programming languages. For each file, the authors
-manually ``labeled the log part (chunk) describing why the build failed''~\cite{brandt2020logchunks}.
-We include keywords, which we would use to search for the selected chunk
-within the log. In addition, we categorized the log chunks according to their
-format within the log. If the chunks are surrounded by the same markings within
-the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe}, \ref{sec:expl-ts} and \ref{sec:expl-skws}.
-Random Line Retrieval (RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
+For this study we created the previously published data set
+\emph{LogChunks}. It encompasses 797 build logs from Travis CI,
+stemming from a broad range of 80 GitHub repositories and 29
+programming languages. For each file, the authors manually ``labeled
+the log part (chunk) describing why the build
+failed''~\cite{brandt2020logchunks}. We include keywords, which we
+would use to search for the selected chunk within the log. In
+addition, we categorized the log chunks according to their format
+within the log. If the chunks are surrounded by the same markings
+within the log we assign them the same structural category.
+
+For the comparison, we evaluate the three chunk retrieval techniques
+PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
+\ref{sec:expl-ts} and \ref{sec:expl-skws}. Random Line Retrieval
+(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
+the comparison.
 % We run four techniques on the examples from \emph{LogChunks}.
@@
 \textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study.
-For each of the 80 repositories in it, \emph{LogChunks} contains 10 build logs, manually labeled with the substring or \emph{chunk} describing the reason the build failed.
-Additionally, it contains (1) keywords useful to
+We use \emph{LogChunks} as the data set for our study. For each of the
+80 repositories in it, \emph{LogChunks} contains 10 build logs,
+manually labeled with the substring or \emph{chunk} describing the
+reason the build failed. Additionally, it contains (1) keywords useful
+to
 % TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category the substring belongs to.
+identify the substring in the log  and (2) which structural category
+the substring belongs to.
 % TODO (Caro): Add details how key words were extracted. Add example?
@@
 % TODO (Caro): Add more details. How was the split in numbers?
-For each repository in \emph{LogChunks}, we split the examples chronologically into training and test set.
-Therefore, we train on examples from past build logs and test on more recent build logs.
+For each repository in \emph{LogChunks}, we split the examples
+chronologically into training and test set. Therefore, we train on
+examples from past build logs and test on more recent build logs.
 
@@
 \textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to perform best, we evaluate the techniques with different training set sizes.
-We train each technique with one to five examples from each of the repositories within \emph{LogChunks}.
-The size of the test set is one.
+To analyze how many examples the chunk retrieval techniques need to
+perform best, we evaluate the techniques with different training set
+sizes. We train each technique with one to five examples from each of
+the repositories within \emph{LogChunks}. The size of the test set is
+one.
 
@@
 \textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk retrieval techniques need to be, we record the structural categories of the examples in the training and test sets.
+To determine how structurally similar the examples for the chunk
+retrieval techniques need to be, we record the structural categories
+of the examples in the training and test sets.
 
@@
 \textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($\mathit{RetrievedLines}$).
-As oracle in our evaluation, we save the desired lines from the output of the test example ($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our evaluation.
+To measure the accuracy of the retrieved chunks we save the output
+lines of the chunk retrieval run on the input of the test example
+($\mathit{RetrievedLines}$). As oracle in our evaluation, we save the
+desired lines from the output of the test example
+($\mathit{DesiredLines}$).
+
+We calculate and define a number of metrics for the context of our
+evaluation.
 
 \vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm]
-	 \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap \mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a tool as well as what \textit{LogChunks} contains for each example. 
-        % TODO (Caro) What about when a line is replicated twice? I.e., Are line numbers part of this?
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\ Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of the retrieved lines were actually desired. 
-	\item $\mbox{Recall} = \dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$ \vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$ \vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall.
-We prefer F$_{1}$ to other aggregate measures such as accuracy because for a ``needle-in-the-haystack'' scenario, we do not want to bloat our results by correctly not finding lots of irrelevant log lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\ \mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\ We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
+\begin{itemize}[leftmargin=0.4cm] \itemsep1em
+	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap
+	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
+        True positives are lines that appear both in the output of a
+        tool as well as what \textit{LogChunks} contains for each
+        example. 
+        % TODO (Caro) What about when a line is replicated twice?
+        % I.e., Are line numbers part of this?
+	\item $\mbox{Precision} = \dfrac{|\mathit{True\
+	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
+        Precision of a chunk retrieval describes which proportion of
+        the retrieved lines were actually desired. 
+	\item $\mbox{Recall} =
+	\dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$
+	\vspace{0.2cm} \\
+        Recall of a chunk retrieval describes which proportion of the
+        desired lines were retrieved.
+	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
+	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
+	\vspace{0.2cm}\\
+        In addition, we calculate the F$_{1}$-score, the harmonic mean
+        of precision and recall. We prefer F$_{1}$ to other aggregate
+        measures such as accuracy because for a
+        ``needle-in-the-haystack'' scenario, we do not want to bloat
+        our results by correctly not finding lots of irrelevant log
+        lines.
+	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
+	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
+	We define a successful retrieval as one where all desired lines were
+	extracted, therefore when recall is one.
 \end{itemize}
 
-% Recall and precision of CTS and KWS vary with the number of lines selected for retrieval.
-% We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the training examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
+% Recall and precision of CTS and KWS vary with the number of lines
+% selected for retrieval. We evaluate the effect of varying the number
+% of extracted lines by multiplying the average number of lines
+% present in the training examples with a \emph{retrieval size factor}
+% from 0.5 to 2.5 in steps of 0.5.
 
@@
 This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as baseline.
+Afterwards we compare the three techniques with each other and RLR as
+baseline.
 
@@
 
-\Cref{fig:recall-precision-examplecount-CTS} presents precision, recall and F$_{1}$-score of chunk retrieval using CTS for an increasing number of training examples.
-When using one to five training examples, the size of the training set has no noticeable influence on precision, recall or F$_{1}$-score of the chunk retrieval with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same measurements for an increasing number of structural categories in the training and test examples.
-With increasing category count, precision, recall and F$_{1}$-score decrease.
-Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.
+\Cref{fig:recall-precision-examplecount-CTS} presents precision,
+recall and F$_{1}$-score of chunk retrieval using CTS for an
+increasing number of training examples. When using one to five
+training examples, the size of the training set has no noticeable
+influence on precision, recall or F$_{1}$-score of the chunk retrieval
+with CTS.
+
+\Cref{fig:recall-precision-categorycount-CTS} shows the same
+measurements for an increasing number of structural categories in the
+training and test examples. With increasing category count, precision,
+recall and F$_{1}$-score decrease. Especially for more than three
+categories present we have no chunk retrieval runs where all desired
+lines were extracted.
 
@@
 
-\Cref{fig:recall-precision-examplecount-KWS} presents precision, recall and F$_{1}$-score of chunk retrieval using KWS for different numbers of training examples.
-The recall increases by about 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
-The F$_{1}$-score stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same measurements for an increasing number of structural categories in the training and test examples.
-For more than one structural category in the training and test examples the recall decreases by about 20\% and the precision decreases about 6\%.
-For more than two structural categories no clear trend is visible in precision, recall or F$_{1}$-score for an increasing amount of categories in the training and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
-% The precision is 19\% when retrieving half of the expected number of lines. On average 9\% of the lines in the build log are retrieved then.
-% When 2.5 times the expected number of lines are retrieved, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
-% The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
+\Cref{fig:recall-precision-examplecount-KWS} presents precision,
+recall and F$_{1}$-score of chunk retrieval using KWS for different
+numbers of training examples. The recall increases by about 12\% when
+increasing the size of the training set to more than one example,
+while the precision stays constant at around 16\%. The F$_{1}$-score
+stays around 26\%.
+
+\Cref{fig:recall-precision-categorycount-KWS} shows the same
+measurements for an increasing number of structural categories in the
+training and test examples. For more than one structural category in
+the training and test examples the recall decreases by about 20\% and
+the precision decreases about 6\%. For more than two structural
+categories no clear trend is visible in precision, recall or
+F$_{1}$-score for an increasing amount of categories in the training
+and test examples.
+
+% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the
+% effect of the retrieval size factor on precision, recall and
+% F$_{1}$-score of chunk retrieval runs with KWS\@. The precision is
+% 19\% when retrieving half of the expected number of lines. On
+% average 9\% of the lines in the build log are retrieved then. When
+% 2.5 times the expected number of lines are retrieved, the precision
+% decreases to 10\% and a quarter of the lines in the build log are
+% retrieved on average. The recall ranges from 58\% to 75\% and the
+% F$_{1}$-score shows a constant decrease from 29\% to 17\%.
 
@@
 
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
-Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
-In 89 further cases, an extraction program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output.
-In 30 of the 89 cases did the synthesized program only partially extract a subset of the desired lines.
-For these 30 cases, the average recall was 28\%.
-Listing \ref{lst:pbe-unsuccessful} shows an example of such an \emph{unsuccessful retrieval}, where the synthesized program only retrieved two of the four targeted lines.
-In 173 of the 400 cases could PROSE not synthesize program consistent with all of the training examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs depend on the number of structural categories in the training and test examples.
-The figure demonstrates that program synthesis mostly returns exactly the desired output when there are is only one structural category present in the training examples.
-However, when two or more structural categories are simultaneously present in the examlpe set, PROSE could in most cases not synthesize a program consistent with all training examples.
-For four or more present categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of the 227 runs where PBE could synthesize a program consistent with all training examples.
-When the training set size increases from one to two, recall and F$_{1}$-score increase by about 25\%, precision increases by about 10\%.
-For two or more training examples, recall and F$_{1}$-score stay around 75\% and precision around 96\%.
+\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
+evaluation. Out of the 400 runs, 5 per each one of the 80 example
+sets, PBE extracted all the desired lines in 138 cases. In 89 further
+cases, an extraction program was also successfully synthesized, though
+in 59 of the 89 cases the synthesized program yielded no output. In 30
+of the 89 cases did the synthesized program only partially extract a
+subset of the desired lines. For these 30 cases, the average recall
+was 28\%. Listing \ref{lst:pbe-unsuccessful} shows an example of such
+an \emph{unsuccessful retrieval}, where the synthesized program only
+retrieved two of the four targeted lines. In 173 of the 400 cases
+could PROSE not synthesize program consistent with all of the training
+examples.
+
+\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
+runs depend on the number of structural categories in the training and
+test examples. The figure demonstrates that program synthesis mostly
+returns exactly the desired output when there are is only one
+structural category present in the training examples. However, when
+two or more structural categories are simultaneously present in the
+examlpe set, PROSE could in most cases not synthesize a program
+consistent with all training examples. For four or more present
+categories PROSE could never synthesize a consistent program.
+
+\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
+precision and recall of the 227 runs where PBE could synthesize a
+program consistent with all training examples. When the training set
+size increases from one to two, recall and F$_{1}$-score increase by
+about 25\%, precision increases by about 10\%. For two or more
+training examples, recall and F$_{1}$-score stay around 75\% and
+precision around 96\%.
 
@@
 
-In our evaluation, we want to compare against a baseline of randomly picking lines from the build log.
-Due to the fact no one would seriously consider RLR in real-world scenarios, we are omitting its detailed graphs here.
-However, its results follow intuitive expectations:
+In our evaluation, we want to compare against a baseline of randomly
+picking lines from the build log. Due to the fact no one would
+seriously consider RLR in real-world scenarios, we are omitting its
+detailed graphs here. However, its results follow intuitive
+expectations:
 % TODO Caro: shortly descibre RLR graphs ommitted
@@
 \subsection{Comparison of All Techniques}
-In this section, we aggregate the results from \Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
-CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
-With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
-PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is compared in Figure~\ref{fig:recall-precision-all}.
-% The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
-% PBE has the highest average precision with 95\%.
-% Chunk retrieval with CTS has the highest average F$_{1}$-score with 51\% and the second highest recall with 46\%.
-% KWS has the smallest precision of the three chunk retrieval techniques.
-% With 16\% it is still higher than the precision of the RLR baseline with 7\%.
-% KWS has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
-For more than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.
+In this section, we aggregate the results from
+\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it
+each other.
+
+\Cref{fig:success-partial-all} compares the success of chunk
+retrievals differentiated by techniques in our study. CTS and KWS
+extract some of the desired lines in 79\% and 88.5\% of the chunk
+retrieval runs. With 38.25\%, KWS also has the highest number of fully
+successful extractions, followed by PBE with 34.5\%. PBE has the
+lowest number of partial retrievals with only 18 out of 400 chunk
+retrieval runs.
+
+% The averaged precision, recall and F$_{1}$-score f all techniques is
+% compared in Figure~\ref{fig:recall-precision-all}. The recall of PBE
+% has a high skew towards one and zero, meaning in most cases either
+% the retrieval is successful or no relevant lines are extracted at
+% all. PBE has the highest average precision with 95\%. Chunk
+% retrieval with CTS has the highest average F$_{1}$-score with 51\%
+% and the second highest recall with 46\%. KWS has the smallest
+% precision of the three chunk retrieval techniques. With 16\% it is
+% still higher than the precision of the RLR baseline with 7\%. KWS
+% has the highest recall of all techniques with 70\%.
+
+\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
+show the influence of a single structural category present in the
+training examples compared to multiple categories present. For more
+than one category being present, the recall of PBE decreases greatly.
+For CTS and KWS the values also decrease, while RLR is not affected by
+the number of structural categories present.
 
@@
 
-The first section discusses for PBE, CTS and KWS separately in which cases they perform best.
-It details for which types of input build logs, available training examples and consumption of the retrieved output each technique is suited.
-In the following section we discuss which of these criteria should influence the decision to use a certain technique most.
-Based on our empirical comparison, we present a decision tree between the three techniques we investigated.
+The first section discusses for PBE, CTS and KWS separately in which
+cases they perform best. It details for which types of input build
+logs, available training examples and consumption of the retrieved
+output each technique is suited. In the following section we discuss
+which of these criteria should influence the decision to use a certain
+technique most. Based on our empirical comparison, we present a
+decision tree between the three techniques we investigated.
 
 \subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed chunk retrieval techniques separately.
-It gives recommendations which kind of information chunk targets are best for each technique and for what kind of usage the respective output is suitable.
+This section discusses the study results for each of the analyzed
+chunk retrieval techniques separately. It gives recommendations which
+kind of information chunk targets are best for each technique and for
+what kind of usage the respective output is suitable.
 
@@
 \textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best results when the training examples are structurally identical.
-This is because PROSE has difficulty synthesizing OR-based programs (see \Cref{sec:prose:impl}).
-PBE is thus suited to retrieve information chunks that always have the same surrounding or defining internal structure.
-To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.
-
-When the training examples are of the same structure, even one or two two examples are enough input for PROSE to synthesize a regular expression program with good recall.
-In our study, additional training examples did not improve the chunk retrieval.
-In fact, unless they were in some sense redudant, adding training examples above that even hindered the applicability of PBE.
+Our study results show that chunk retrieval with PBE gives best
+results when the training examples are structurally identical. This is
+because PROSE has difficulty synthesizing OR-based programs (see
+\Cref{sec:prose:impl}). PBE is thus suited to retrieve information
+chunks that always have the same surrounding or defining internal
+structure. To extract for example the reason a build failed, the log
+passage describing the failure would always have to be started and
+ended the same way.
+
+When the training examples are of the same structure, even one or two
+two examples are enough input for PROSE to synthesize a regular
+expression program with good recall. In our study, additional training
+examples did not improve the chunk retrieval. In fact, unless they
+were in some sense redudant, adding training examples above that even
+hindered the applicability of PBE.
 
@@
 \textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression program yields an output, PBE has high precision and recall.
-The tool clearly identifies a failing program synthesis or when no output from the program applied to a build log is obtained.
-Therefore, if there is an output, the user can have high confidence that it is the desired output.
-This preciseness makes output from PBE chunk retrieval well-suited for machine consumption.
+If the program synthesis succeeds and applying the regular expression
+program yields an output, PBE has high precision and recall. The tool
+clearly identifies a failing program synthesis or when no output from
+the program applied to a build log is obtained. Therefore, if there is
+an output, the user can have high confidence that it is the desired
+output. This preciseness makes output from PBE chunk retrieval
+well-suited for machine consumption.
 
@@
 \textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the fewer structural categories are present in the training and test examples.
-
-The number of training examples had no noticeable influence on precision or recall in our study.
-Information retrieval techniques like text similarity commonly learn on a higher number of examples than used for our study.
-Future work is needed to investigate how many examples yield improvements in the chunk retrieval over a single training example.
+Similar to PBE, chunk retrieval using CTS yields better results the
+fewer structural categories are present in the training and test
+examples.
+
+The number of training examples had no noticeable influence on
+precision or recall in our study. Information retrieval techniques
+like text similarity commonly learn on a higher number of examples
+than used for our study. Future work is needed to investigate how many
+examples yield improvements in the chunk retrieval over a single
+training example.
 
 % TODO Caro: I do not understand the following sentence.
-Extracting the average number of lines present in the training examples gives the best retrieval results for CTS, according to the F$_{1}$-score.
+Extracting the average number of lines present in the training
+examples gives the best retrieval results for CTS, according to the
+F$_{1}$-score.
 
@@
 % TODO Caro: reforumlate this please
-CTS has good precision and recall on average, though the precision or recall of a chunk retrieval run is very hard to predict from the given result.
-Therefore, retrieval output from CTS is suited to be read by a human. This could include semi-automated procedures such as sending developers an email with the extracted build failure reason.
+CTS has good precision and recall on average, though the precision or
+recall of a chunk retrieval run is very hard to predict from the given
+result. Therefore, retrieval output from CTS is suited to be read by a
+human. This could include semi-automated procedures such as sending
+developers an email with the extracted build failure reason.
 
@@
 \textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
-This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log.
-For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
+KWS has a higher recall than the two other techniques for multiple
+structural categories present in the training and test examples. This
+makes KWS a good technique if there is little prior knowledge on how
+the targeted log chunk is represented in the build log. For the
+example of extracting the reason the build failed, KWS is best suited
+if a build can fail in various steps logged by different tools and no
+pre-categorization of where the build failed is available.
 
@@
 
-Retrieving the average number of lines present in the outputs of the training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does improve the recall within our study but also increases the proportion of lines retrieved overall and therefore decreases precision.
+Retrieving the average number of lines present in the outputs of the
+training examples around every found keyword yields reasonable recall.
+Selecting 1.5 times as many lines around every found keyword does
+improve the recall within our study but also increases the proportion
+of lines retrieved overall and therefore decreases precision.
 
@@
 \textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its precision is the lowest.
-The output of a chunk retrieval with KWS is well-suited to be read by humans, but ill-suited for consumption by automated tools.
+While KWS has the highest recall of all three techniques, its
+precision is the lowest. The output of a chunk retrieval with KWS is
+well-suited to be read by humans, but ill-suited for consumption by
+automated tools.
 
@@
 \subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
-In Figure~\ref{fig:crt-recommendation}, we present a decision tree, which developers and researchers who want to retrieve information chunks from build logs can follow.
-The decision tree is built up of questions which either lead to more questions or to a leaf node containing a recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results from our comparison study.
-The recommendations could therefore be influenced by idiosyncrazies of our specific implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced answer to RQ2, about which criteria influence the suitability of a chunk retrieval technique.
-The earlier in the decision tree a criterion is noted, the more important it is when distinguishing the techniques.
-
-The first and most important aspect are the structural categories.
-Are the information chunks one would like to retrieve always presented in the same structural way within the build logs?
-Then the information chunks in all training examples and the analyzed build log are in the same structural category.
-
-If the information chunks are from multiple structural categories, i.e.
-they are not represented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS\@.
-If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
-We also recommend CTS when the representations are from one structural category, when the user does not require a high confidence in the precision or recall of the outcome and when the user would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by combining the different build log analysis techniques studied in this paper.
-Such a super analyzer would likely always first employ PBE (because of its high accuracy), followed by a combination of CTS and KWS.
-Other than initial setup and training time, there should be no downside to this approach if it is implemented in a transparent way to the underlying technique: the output of the super analyzer could include from which sub-tool it originated and thus facilitate automatic on-ward processing or interpretation of the result.
+After discussing the three chunk retrieval techniques separately we
+now want to unify our results into one recommendation scheme. In
+Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
+developers and researchers who want to retrieve information chunks
+from build logs can follow. The decision tree is built up of questions
+which either lead to more questions or to a leaf node containing a
+recommended technique.
+
+\noindent
+\textbf{Caveat!} This is a preliminary hypothesis based on the results
+from our comparison study. The recommendations could therefore be
+influenced by idiosyncrazies of our specific implementation of the
+chunk retrieval techniques as well as the logs in the \emph{LogChunks}
+data set.
+
+This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
+answer to RQ2, about which criteria influence the suitability of a
+chunk retrieval technique. The earlier in the decision tree a
+criterion is noted, the more important it is when distinguishing the
+techniques.
+
+The first and most important aspect are the structural categories. Are
+the information chunks one would like to retrieve always presented in
+the same structural way within the build logs? Then the information
+chunks in all training examples and the analyzed build log are in the
+same structural category.
+
+If the information chunks are from multiple structural categories,
+i.e. they are not represented in the same structural way within the
+build logs, and recall is more important than precision we recommend
+to use KWS\@. If the representations are from multiple structural
+categories and precision is more important than recall to the user we
+recommend CTS\@. We also recommend CTS when the representations are
+from one structural category, when the user does not require a high
+confidence in the precision or recall of the outcome and when the user
+would rather have output with low recall instead of no output at all.
+When the representations are from one structural category and the user
+wishes a high confidence in the correctness of the output or prefers
+no output over output with low recall, we recommend PBE\@.
+
+As a final recommendation, one could create a ``super analyzer'' by
+combining the different build log analysis techniques studied in this
+paper. Such a super analyzer would likely always first employ PBE
+(because of its high accuracy), followed by a combination of CTS and
+KWS. Other than initial setup and training time, there should be no
+downside to this approach if it is implemented in a transparent way to
+the underlying technique: the output of the super analyzer could
+include from which sub-tool it originated and thus facilitate
+automatic on-ward processing or interpretation of the result.
 
@@
 \textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we describe two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI are caused by a small or by a large group of test cases.
-They gather CI build logs from various projects, which are their only available data source.
-The task of the researcher is to extract the names of the failing test cases from each build log.
-When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test cases is in the investigated build logs.
-As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, non-predictable structural representations.
-The next question is whether they value precision over recall.
-As they have to manually inspect the results of both CTS and KWS, they choose recall over precision to avoid having to inspect the whole log in case the relevant information chunk was not retrieved.
-Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor the performance of the phases within their CI build.
-They are using Travis CI, which measures the duration of build phases and documents them within the build log.
-As all log statements that report timing measurements are formatted the same way, the targeted log chunks are from one structural category.
-Therefore the development team can use PBE to retrieve the duration of a build phase as well as its name.
+To illustrate how one would use our decision tree to find a suitable
+chunk retrieval technique we describe two concrete examples: a
+researcher investigating why CI builds fail and a software team
+wanting to monitor their build performance.
+
+In our first example, a researcher studies whether test failures in CI
+are caused by a small or by a large group of test cases. They gather
+CI build logs from various projects, which are their only available
+data source. The task of the researcher is to extract the names of the
+failing test cases from each build log. When they use our
+recommendation scheme to select a chunk retrieval technique, they
+first have to estimate how uniform the representation of the failing
+test cases is in the investigated build logs. As the researcher is
+covering a wide range of build tools and development languages, the
+log chunks they target are in various, non-predictable structural
+representations. The next question is whether they value precision
+over recall. As they have to manually inspect the results of both CTS
+and KWS, they choose recall over precision to avoid having to inspect
+the whole log in case the relevant information chunk was not
+retrieved. Therefore, our decision tree recommends them to use KWS\@.
+
+In case the researcher wants to avoid manually inspecting the
+retrieval results, they have to first separate the CI build logs
+according to the test tool responsible for logging the test results.
+Then the targeted log chunks are from one structural category and they
+can use PBE, trained with examples from each test tool separately.
+
+In our second example, a software development team wants to monitor
+the performance of the phases within their CI build. They are using
+Travis CI, which measures the duration of build phases and documents
+them within the build log. As all log statements that report timing
+measurements are formatted the same way, the targeted log chunks are
+from one structural category. Therefore the development team can use
+PBE to retrieve the duration of a build phase as well as its name.
 
 \section{Threats to Validity}
-There are several threats to the validity of the conclusions of our work.
+There are several threats to the validity of the conclusions of our
+work.
 
@@
 \label{sec:prose:impl}
-% TODO we need to say something about why we think that these limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk retrieval techniques and the libraries we used.
-Our implementation of PBE is based on the program synthesis provided by PROSE\@.
-The idiosyncrazies of this framework influence our PBE results. Other frameworks similar to PROSE might have somewhat different strengths and weaknesses.
-For example, the need for examples from a single structural category stems from the fact that PROSE cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
-PROSE introduced this constraint to keep the synthesis performance reasonable.
-At the same time, this is clearly a current theoretical challenge of all PBE implementations, and we therefore attribute it to the technique itself, rather than the specific implementation.
+% TODO we need to say something about why we think that these
+% limtiations do not actually harm our results
+Our results depend on the implementation of the investigated chunk
+retrieval techniques and the libraries we used. Our implementation of
+PBE is based on the program synthesis provided by PROSE\@. The
+idiosyncrazies of this framework influence our PBE results. Other
+frameworks similar to PROSE might have somewhat different strengths
+and weaknesses. For example, the need for examples from a single
+structural category stems from the fact that PROSE cannot learn
+regular expression programs with arbitrary boolean conjunctions and
+disjunctions~\cite{mayer2015user}. PROSE introduced this constraint to
+keep the synthesis performance reasonable. At the same time, this is
+clearly a current theoretical challenge of all PBE implementations,
+and we therefore attribute it to the technique itself, rather than the
+specific implementation.
 
 % TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec} and the way it splits strings into word tokens.
-On the other hand, {\tt text2vec} is the de-facto standard library to do word embeddings in R.
-We intentionally chose a simple, minimally configured and tuned approach to compare against.
-Tuning the text similarity meta-parameters more to the specific use case of chunk retrieval from build logs would yield better chunk retrieval results.
+Our implementation of CTS is dependent on the library {\tt text2vec}
+and the way it splits strings into word tokens. On the other hand,
+{\tt text2vec} is the de-facto standard library to do word embeddings
+in R. We intentionally chose a simple, minimally configured and tuned
+approach to compare against. Tuning the text similarity
+meta-parameters more to the specific use case of chunk retrieval from
+build logs would yield better chunk retrieval results.
 
@@
 \textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
-It only consists of build logs from open source projects and therefore it is not clear whether our results are generalizable to industry projects.
-We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
-This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI environment.
+The outcomes of our comparison study are highly dependent on the build
+logs from the \emph{LogChunks} data set. It only consists of build
+logs from open source projects and therefore it is not clear whether
+our results are generalizable to industry projects. We only collected
+build logs from Travis CI, however we chose to evaluate on an
+information chunk whose format is not dependent on Travis CI\@. This
+is because the reason the build failed is described within the build
+logs by the tools themselves and not the Travis CI environment.
 
@@
 \textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we only trained on one to five examples.
-We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.
+Especially the results for CTS might be influenced by the fact that we
+only trained on one to five examples. We chose this small training set
+size as the training examples have to be provided per repository and
+we expect a developer to not want to provide more examples than the
+small numbers we evaluated on.
 
@@
 \textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural categories than with one category.
-% TODO Caro: Please explain the following further. Why does a realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.
+Our comparison study shows fewer measurements with many structural
+categories than with one category.
+% TODO Caro: Please explain the following further. Why does a
+% realistic data set only have one or few structural categories?
+This stems from the fact that we use a realistic data set which in
+many cases has only one or few structural categories.
 
@@
 \begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set \cite{} specifically for the comparative study in this paper, though it can be the basis for various further analyses of build log data.
-  The keywords, for example, can be investigated to answer which keywords are used to search for the reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
-  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This paper investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
-  Our study design can be reused to evaluate other build log analysis techniques, such as the diff and information retrieval approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
-  In a next step, each of these techniques could be refined to better approach the domain of build logs.
-  The \emph{LogChunks} data set and our study results act as a baseline to benchmark such technique improvements.
-  We propose the following improvements:
+  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
+  \emph{LogChunks} data set \cite{} specifically for the comparative
+  study in this paper, though it can be the basis for various further
+  analyses of build log data. The keywords, for example, can be
+  investigated to answer which keywords are used to search for the
+  reason the build failed within build logs.
+  \item \textbf{Cross-Repository Build Log Analysis} We trained and
+  tested each chunk retrieval technique on examples from the same
+  repository. We propose to analyze how techniques could be trained
+  across repositories, building the cornerstones for build
+  environment-agnostic analysis tools.
+  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
+  paper investigates the three chunk retrieval techniques PBE, CTS and
+  KWS\@. Our study design can be reused to evaluate other build log
+  analysis techniques, such as the diff and information retrieval
+  approach by Amar et al.~\cite{amar2019mining}.
+  \item \textbf{Refinement of Retrieval Quality for each Technique} We
+  investigated basic configurations of existing techniques applied to
+  chunk retrieval from build logs. In a next step, each of these
+  techniques could be refined to better approach the domain of build
+  logs. The \emph{LogChunks} data set and our study results act as a
+  baseline to benchmark such technique improvements. We propose the
+  following improvements:
     \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
-      One could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
-      FlashExtract includes special tokens when enumerating possible regular expressions.
-      One could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
-      We propose to further investigate improvements in preprocessing of the log text, in tokenization of the log lines into terms and in stop words lists.
+      \item \textbf{Custom Ranking and Tokens for PBE} The program
+      synthesis through PROSE ranks possible programs according to
+      what the user most likely intended. One could adapt the ranking
+      rules provided by the FlashExtract DSL to fit common build log
+      chunk retrieval tasks. FlashExtract includes special tokens when
+      enumerating possible regular expressions. One could extend these
+      with tokens found in build logs, such as ``-'',``='',``ERROR''
+      or ``[OK''.
+      \item \textbf{Meta-Parameter Optimization for CTS} Information
+      retrieval techniques have various meta-parameters which can be
+      optimized for the specific use
+      case~\cite{panichella2016parameterizing}. We propose to further
+      investigate improvements in preprocessing of the log text, in
+      tokenization of the log lines into terms and in stop words
+      lists.
     \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focuses on precision and recall.
-  We propose to investigate how useful these outputs are to developers through controlled experiments.
+  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
+  analysis of the output produced by the chunk retrieval focuses on
+  precision and recall. We propose to investigate how useful these
+  outputs are to developers through controlled experiments.
 \end{itemize}
@@
 \label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in their decision on how to analyze build logs.
-We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
-Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
-Secondary factors are the desired confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by combining the different build log analysis techniques studied in this paper.
+The goal of this paper was to support researchers and developers in
+their decision on how to analyze build logs. We implemented and
+compared three different chunk retrieval techniques on our data set
+\emph{LogChunks}, composed of 797 manually labeled build logs from a
+broad range of 80 repositories. Our results show that the structural
+representation of the targeted information in the build logs is the
+main factor to consider when choosing a suitable technique. Secondary
+factors are the desired confidence into recall and precision of the
+produced output and whether precision or recall is more important for
+the task at hand.
+
+As a final recommendation, one could create a ``super analyzer'' by
+combining the different build log analysis techniques studied in this
+paper.

### 2020-04-01 tse-paper/content.tex
address all of the todos addressed to Caro

@@
 the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
+\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary log chunks
 from Android/Gradle build logs marked in blue.
@@
 
-% TODO (Caro): Integrate Kitchenham's guidelines
+% TODO (Caro): Integrate Petersen's guidelines
 From our own experience, we know that the field of analyzing build
@@
 duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO Caro: update
+articles. % TODO: update numbers
 
@@
 \subsection{Article Classification}
-% TODO Caro: please write a draft for this :-)
 Having trimmed down the set of articles, we investigated them in depth.
@@
 
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual
-% software
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model. We
-% investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs. In the following we will explain
-% the concept of how we apply text similarity to information retrieval
-% from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use
-the same concept of examples as for PBE\@
-% TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}. The
-lines of the output strings of the training examples define our search
-query. The algorithm splits the search query into single lines and
-identifies tokens, in our case words. Then we build a
-document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words. Finally, the
-algorithm applies TF-IDF to the matrix, a best practice for natural
-language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the output of the
-training examples. The algorithm calculates the cosine
-similarity~\cite{korenius2007principal} to compare each line of the
-build log with each line of the search query. After summing up the
-similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity. The average number of
-lines in the outputs of the training examples determines how many of
-the most similar lines are returned as the output of the retrieval
-run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad-hoc approach they
-use is to search for related keywords. Indeed, this was one of the
-most common approaches we took when searching for the reason the build
-failed within a log while creating the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers
-% use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs. In
-% the following we will explain how we use simple keyword search to
-% retrieve information from CI build logs, which we refer to as
-% \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@. To better
-compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted
-chunk or close to it. The configuring keywords for KWS are the ones
-that appear most often in the keywords of all training examples.
-% TODO Caro Please explain above sentence more precisely
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords. As keywords are
-often not directly describing the desired information, but rather
-appear close to the desired information, KWS also retrieves the lines
-around the found keyword. The number of surrounding lines retrieved is
-the average of lines in the output of the training examples.
-
 \subsection{Program Synthesis by Example (PBE)}
@@
 
+% TODO later: we should make sure to at least mention PROSE
+% _somewhere_, it's crucial for why PBE is how it is
 \subsubsection{Configuration}
@@
 
-% TODO Caro: The following is very obvious and could apply to any
+% TODO Moritz: you said: The following is very obvious and could apply to any
 % technique. 
+% kinda. It does give a descriptive error message on no match (and
+% that is not possible in other techniques)
+% otherwise yes, nothing interesting happens in the application of pbe
+% though for consistency we might need this section? or merge config/application?
 \subsubsection{Application}
@@
 synthesized regular expression program. It then returns the substring
-of the build log matched by the program or an empty string if the
+of the build log matched by the program or an error message if the
 program found no match.
+
+\subsection{Common Text Similarity (CTS)}
+\label{sec:expl-ts}
+% Text Similarity approaches are used to filter unstructured textual
+% software
+% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+% One common and simple technique is the Vector Space Model. We
+% investigate when text similarity is a suitable technique to retrieve
+% information chunks from build logs. In the following we will explain
+% the concept of how we apply text similarity to information retrieval
+% from CI build logs, which we refer to as \emph{CTS}\@.
+
+\subsubsection{Configuration}
+To configure chunk retrieval though text similarity we chose to use
+the same concept of examples as for PBE
+% TODO Moritz: your question was: More details on this. How do you
+% 'apply' VSM? On what?
+% all the following sentences in this subsubsection describe our way
+% of determining text similarity which as far as I understand and
+% Annibale said is the VSM. word tokens, tf-idf, similarity measure
+% I added a "as follows", think that is enough for explanation? 
+and apply the Vector Space Model~\cite{schutze2008introduction} as follows. The
+lines of the output strings of the training examples define our search
+query. The algorithm splits the search query into single lines and
+identifies tokens, in our case words. Then we build a
+document-term-frequency matrix over the lines from the search query
+and prune very often or very rarely appearing words. Finally, the
+algorithm applies TF-IDF to the matrix, a best practice for natural
+language queries~\cite{lee1997document}.
+
+\subsubsection{Application}
+To retrieve the desired information from a build log, we parse the
+whole text and process it in the same way as the output of the
+training examples. The algorithm calculates the cosine
+similarity~\cite{korenius2007principal} to compare each line of the
+build log with each line of the search query. After summing up the
+similarities of each build log line to all search query lines, we sort
+the build log lines in decreasing similarity. The average number of
+lines in the outputs of the training examples determines how many of
+the most similar lines are returned as the output of the retrieval
+run.
+
+\subsection{Keyword Search (KWS)}
+\label{sec:expl-skws}
+When developers scavenge for a specific piece of information within a
+large amount of unstructured information, a first ad-hoc approach they
+use is to search for related keywords. Indeed, this was one of the
+most common approaches we took when searching for the reason the build
+failed within a log while creating the \emph{LogChunks} data
+set~\cite{brandt2020logchunks}.
+% As this is a technique readily available in many tools developers
+% use to view build logs, we study when such a keyword search is
+% suitable for retrieving information chunks from CI build logs. In
+% the following we will explain how we use simple keyword search to
+% retrieve information from CI build logs, which we refer to as
+% \emph{KWS}\@.
+
+\subsubsection{Configuration}
+A set of keywords configures the chunk retrieval with KWS\@. To better
+compare KWS with PBE and CTS, we also configure it through examples.
+We associate each example with keywords which appear in the targeted
+chunk or close to it. 
+KWS then searches for those keywords which are tied to the greatest
+number of examples in the training set.
+If several keywords are associated with the same number of training
+examples, and no other keywords are associated with more training
+examples, KWS searches for all of these keywords.
+
+\subsubsection{Application}
+For a retrieval run, we take a whole build log file as input and
+search for all exact occurrences of the keywords. As keywords are
+often not directly describing the desired information, but rather
+appear close to the desired information, KWS also retrieves the lines
+around the found keyword. The number of surrounding lines retrieved is
+the average of lines in the output of the training examples.
 
@@
 \label{sec:expl-rlr}
-
 In our evaluation, we want to compare against a baseline of randomly
@@
 number of lines in the chunks of the training examples. 
-% TODO Caro: some more details here?
+% TODO Moritz: you said: some more details here?
+% I would not know of any details to add. It's really all we are doing
 
@@
 given past failures.
+
+% TODO: we could add more techniques from the lit. survey here
 
@@
 80 repositories in it, \emph{LogChunks} contains 10 build logs,
-manually labeled with the substring or \emph{chunk} describing the
+manually labeled with the \emph{chunk} describing the
 reason the build failed. Additionally, it contains (1) keywords useful
-to
-% TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category
+to identify the substring in the log  and (2) which structural category
 the substring belongs to.
-% TODO (Caro): Add details how key words were extracted. Add example?
-
-% TODO (Caro): Add more details. How was the split in numbers?
+% TODO Moritz: You said: Add details how key words were extracted. Add example?
+% how the keywords were put in logchunks does not fit here, that is
+% maybe answered 2 paragraphs above already?
+% how KWS uses the keywords is already described in the section
+% introducing the technique => I would scrap everything but the first
+% sentence directly above here :)
+
+% TODO Moritz: You said: Add more details. How was the split in numbers?
+% this is described in the following paragraph, should we merge them
+% (bc there are also no sub-RQs now) or is it close enough? :)
 For each repository in \emph{LogChunks}, we split the examples
@@
 
-\noindent
+\noindent % TODO: adapt if we change the research questions
 \textbf{RQ 2.1: Size of Training and Test Set}
@@
         example. 
-        % TODO (Caro) What about when a line is replicated twice?
-        % I.e., Are line numbers part of this?
+        % What about when a line is replicated twice?
+        % I.e., Are line numbers part of this? => no.
+        % not checked, but if lines are identical they also contain
+        % the same information so if someone asks we can defend I think
 	\item $\mbox{Precision} = \dfrac{|\mathit{True\
@@
 
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. Due to the fact no one would
-seriously consider RLR in real-world scenarios, we are omitting its
-detailed graphs here. However, its results follow intuitive
+In our evaluation, we compare against a baseline of randomly
+picking lines from the build log. Its results follow intuitive
 expectations:
-% TODO Caro: shortly descibre RLR graphs ommitted
+The precision ranges between 8\% and 5\%, the recall between 6\% and
+8\%. The size of the training set has no visible impact on either.
+An greater number of structural categories within the training and
+test sets decreased the precision of RLR from 7\% to 0\%, the recall
+increases from 6\%, for one structural category present, to 11\%, for
+three sturctural categories present and also drops to 0\% for more
+structural categories.
+Graphs of the results of the chunk retrieval with RLR from our study
+are included in our replication package~\cite{brandt2020chunk-replication}.
 
@@
 
-% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered
+% TODO update RQs
+% TODO incorporate these RQs into the text where they are being answered
 
@@
 
-% TODO Caro: I do not understand the following sentence.
-Extracting the average number of lines present in the training
-examples gives the best retrieval results for CTS, according to the
-F$_{1}$-score.
-
 \noindent
 \textbf{Retrieval Output Usage}
-% TODO Caro: reforumlate this please
-CTS has good precision and recall on average, though the precision or
-recall of a chunk retrieval run is very hard to predict from the given
-result. Therefore, retrieval output from CTS is suited to be read by a
-human. This could include semi-automated procedures such as sending
+CTS has good precision and recall on average, though with a high
+variation. This means that the quality of an output by CTS is hard to
+determine, which makes it unsuited for automatic  processing and requires a human to further inspect and interpret the output. This could include semi-automated procedures such as sending
 developers an email with the extracted build failure reason.
@@
 % realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in
-many cases has only one or few structural categories.
+This stems from the fact that we investigated the chunk retrieval
+techniques on a realistic data set, which showed to often have few
+structural categories within one project.
 
@@
   \item \textbf{Further Analysis of \emph{LogChunks}} We created the
-  \emph{LogChunks} data set \cite{} specifically for the comparative
+  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for the comparative
   study in this paper, though it can be the basis for various further

### 2020-04-02 tse-paper/0-introduction.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
 instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Kitchenham's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO Caro: update
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-% TODO Caro: please write a draft for this :-)
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research, tools developed
-to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? 
-not avaliable in cleaner format
-much use for research, a bit of developer information / tools
-following: research so many logs that unfeasible to do manually, less focus on tools
-for devs (caveat! we excluded books and documentation on industrial tools -> many
-approaches there to make build logs digestible, tough many focus on general
-minimizing of the data presented, not retrieving specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail
-we follow that researchers often see this as an unimportant side fact
-work needed to be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort developing a parser
-other times also because other tools used in further research are limiting the scope
-(reference paper with PIT tool).
-many focus on maven because of it's prevalence also in respect to other tools
-much research done on travis ci logs b/c of their abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
-work from system log analysis.
-
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
-In addition, they notice that most failures are resolved within two builds.
-They based their analyses on sets of build logs collected from industry partners.
-They develop a custom parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and find that most builds fail because of failing tests.
-For most projects, over half of the failed builds follow a previous failed build.
-Rausch et al.'s data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
-They determine that testing failures are more common than compilation errors.
-Open source builds fail most often because of unit tests, whereas release preparations are the primary cause in industrial projects.
-Their data stems from analyzing build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent} with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
-They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
-Their analysis starts with manual categorization of build logs.
-They select keywords and strings that identify their targeted categories and code a script to automatically classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers presented
-in this section create parsers and regular expression-based programs.
-This task of retrieving specific chunks of text from the build logs can be
-solved by the chunk retrieval techniques we compare in this article.
-Our results can support researchers in choosing a suitable technique for their
-data set of build logs and the chunks they want to retrieve.
-By relieving them from building custom parsers we enable them to cover a much
-wider range of languages and build tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why their build failed.
-Several researchers investigate how to support developers in working with verbose build logs.
-Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
-They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
-%The hint generators leverage this structured access to the information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
-In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
-%Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used to fill similar structured representations with information from build logs.
-As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to reduce the portions of a log that a developer has to inspect.
-Their techniques remove lines that appear both in logs from passing and failing builds and use a modified \emph{Term Frequency Inverse Document Frequency} (TF-IDF) weighting to identify term vectors likely to occur with failures.
-Their diff technique can be interpreted as a chunk retrieval technique, where the targeted information is defined by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a basic structuring of the build logs within their log viewer using \emph{log folds}~\cite{travis2019logfolds}.
-They add fold identifiers around common commands and setup or teardown build phases and collapse the contained lines by default.
-
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log files produced during runtime.
-A main difference between build logs and system logs is that system logs are fundamentally structured through events.
-Each line in a log file represents one event with a set of fields: timestamp, verbosity level and raw message content~\cite{he2017towards}.
-Figure \ref{lst:system-log} shows example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
-Next, the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
-The output of a log parser is an ordered list of timed events and their corresponding parameter values~\cite{he2016evaluation}.
-This structured log is then the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
-%Xu et al.~\cite{xu2009detecting} leverage the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied to build logs.
-One example is comparing execution traces to reference traces of intended behavior to detect anomalies.
-Amar et al.~\cite{amar2019mining} employed a similar approach to detect relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of events.
-%A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
-Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.
-by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
-  \end{lstlisting}  
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques}
-%The techniques we investigate are based on existing methods of Programming by Example.%, information extraction and information retrieval.
-%This section presents different Programming by Example resources surrounding the PROSE library.
-%We explain its generic program synthesis algorithm and how PROSE synthesizes text extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program synthesis that enables users to automate repetitive tasks, without them having to explicitly codify a computer program.
-One has to provide prototypical examples of the input and the desired output.
-A
-synthesis algorithm tries to create a program (based on a regular language) that transforms the input to the output.
-The minimum working condition is for this when replayed on the examples inputs is to provide the specified output, but, hopefully, PBE is as close as possbile to the user's intention and thus also works on a different and larger set of inputs.
-This section introduces the theoretical foundations of the program synthesis
-algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research.
-Next, this section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program synthesis in the Microsoft PROSE framework.
-FlashMeta separates the inductive synthesis algorithm from the domain specific capabilities of the desired program by encoding the possible program space in a domain specific language (DSL).
-The user specifies the desired program behavior by providing in/output examples (I/O examples).
-FlashMeta uses \emph{witness functions}, provided by the DSL, to divide the synthesis into smaller subtasks.
-For each of these subtasks it enumerates all possible programs that solve the subtask consistent with the set of I/O examples.
-A program is consistent with a set of I/O examples if, for each input example, it produces the corresponding output~\cite{mitchell1982generalization}.
-The possible subprograms are joined and stored in a \emph{version space algebra} (VSA)~\cite{mitchell1982generalization}.
-This a tree structure, which space-efficiently saves candidate programs for tasks by sharing common subexpressions.
-Next, FlashMeta ranks the enumerated programs according to which ones the user most likely intended.
-The DSL also provides the ranking characteristics.
-From the ranked VSA, FlashMeta can then return a ranked list of complete programs consistent with the user's example.
-
-% In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized program.
-
-% The different applications of PROSE presented in the following paragraphs were all eventually implemented as DSLs for the FlashMeta synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text, websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs from semi-structured text based on regular expressions.
-Users can extract multiple fields and structure them with hierarchy and sequence.
-% FlashExtract synthesizes programs to extract each of the fields leveraging the information about hierarchical containment and sequentiality.
-% It eliminates the need for the user to understand the entire structure of the processed document and decreases the effort of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of two cut positions.
-A position is either specified by an absolute character index or by a pair of two regular expressions.
-The first regular expression matches the substring directly before the characterized position, the second regular expression matches the substring directly after.
-A regular expression in FlashExtract is a concatenation of tokens, e.g.\ standard character classes or string literals frequently occurring in the input examples.
-Figure \ref{lst:prose-program} shows a text extraction program synthesized by FlashExtract.
-This program defines the first position as after a colon followed by a newline character and before a piece of text with all capital letters.
-It defines the second position as before two newline characters.
-
-Apart from automatic completion in Excel spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for two other Microsoft product features:
-Microsoft's system log analysis tool Azure Monitor lets users define custom log fields~\cite{azure2019custom}.
-The ConvertFrom-String function in PowerShell allows a user to specify an example template to extract hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
-\section{Chunk Retrieval Techniques}
-\label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval techniques we study in this article, namely program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically retrieve pieces of information that appear literally in the build logs, i.e., techniques that do not aggreagte, combine, or deducted information.
-We call such pieces of information from build logs \emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and parser to analyze the entire structure of build logs, but focus on ad-hoc extracting just one specific piece of information per configuration.
-
-With the term \textit{configuration,} we abstract over the training and parametrization that different techniques require in different forms.
-A configuration can be explicitly stated or implicitly dervied by learning through provided examples.
-It is therefore a manual specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to identify the targeted information chunk in a build log.
-Each chunk retrieval technqiue has a specific \textit{granularity}, i.e.,\ the smallest piece of text it can return (e.g., a line, or a word). The granularity might be adjustable by configuration.
-\emph{Running a chunk retrieval technique} means to execute a fully configured technique to consumes as input a build log in plain text format and to produce an array as output.
-The array consists of substrings of the build log text.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[]
-\centering
-\caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
-\toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
-\bottomrule
-\end{tabularx}
-\label{tab:ctr}
-\end{table*}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model.
-% We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
-% In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@
-% TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}.
-The lines of the output strings of the training examples define our search query.
-The algorithm splits the search query into single lines and identifies tokens, in our case words.
-Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
-Finally, the algorithm applies TF-IDF to the matrix, a best practice for natural language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the whole text and process it in the same way as the output of the training examples.
-The algorithm calculates the cosine similarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
-After summing up the similarities of each build log line to all search query lines, we sort the build log lines in decreasing similarity.
-The average number of lines in the outputs of the training examples determines how many of the most similar lines are returned as the output of the retrieval run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is to search for related keywords.
-Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
-% In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@.
-To better compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted chunk or close to it.
-The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.
-% TODO Caro Please explain above sentence more precisely
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the keywords.
-As keywords are often not directly describing the desired information, but rather appear close to the desired information, KWS also retrieves the lines around the found keyword.
-The number of surrounding lines retrieved is the average of lines in the output of the training examples.
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes programs according
-% to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming knowledge~\cite{mayer2015user}.
-% In the context of text extraction through regular expressions, Programming by Example relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
-% In this work, we refer to our interpretation of Programming by Example as \emph{PBE}\@.
-% We investigate the suitability of PBE to retrieve information chunks from build logs.
-% In the following, we explain the configuration and application of PBE to chunk retrieval from CI build logs.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by Example, we refer to them in short
-as \emph{examples}.
-The \emph{input} is the text of the build log file.
-The \emph{output} is an array of substrings of the log file text, representing the substrings that should be retrieved by the synthesized program when given the corresponding input file.
-One or multiple examples, the training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted.
-The PROSE program synthesis then tries to construct a program consistent with all training examples.
-% A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn uses the FlashMeta algorithm.
-% Both are described in Section~\ref{sec:rw-prose}.
-
-% TODO Caro: The following is very obvious and could apply to any technique. 
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the synthesized regular expression program.
-It then returns the substring of the build log matched by the program or an empty string if the program found no match.
-
-\subsection{Random Line Retrieval}
-\label{sec:expl-rlr}
-
-In our evaluation, we want to compare against a baseline of randomly picking lines from the build log.
-RLR essentially mimicks the situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should return.
-For a fair comparison to the other techniques (whose number of returned lines is dynamic), we configure RLR to return the average number of lines in the chunks of the training examples.
-% TODO Caro: some more details here?
-
-\subsection{Other Techniques}
-%Literature mentions further build log analysis techniques.
-%This section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information retrieval to identify relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
-The configuration for the technique is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not present in the successful build log and contain terms related to the given past failures.
-
-\subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a unifying interface.
-The unified interface is implemented in Ruby and calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
-We implemented CTS, KWS and RLR using R and the text2vec library~\cite{text2vec2019webpage}.
-
-\section{Study Design}
-\label{sec:study}
-
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-To investigate which techqnique is best suited to retrieve chunks from CI build
-logs we evaluate them on the \emph{LogChunks}~\cite{brandt2020logchunks} data set.
-This section describes our study design and which metrics we measure to answer our research questions.
-In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.
-
-\subsection{LogChunks}
-For this study we created the previously published data set \emph{LogChunks}.
-It encompasses 797 build logs from Travis CI, stemming from a broad range of 80
-GitHub repositories and 29 programming languages. For each file, the authors
-manually ``labeled the log part (chunk) describing why the build failed''~\cite{brandt2020logchunks}.
-We include keywords, which we would use to search for the selected chunk
-within the log. In addition, we categorized the log chunks according to their
-format within the log. If the chunks are surrounded by the same markings within
-the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe}, \ref{sec:expl-ts} and \ref{sec:expl-skws}.
-Random Line Retrieval (RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study.
-For each of the 80 repositories in it, \emph{LogChunks} contains 10 build logs, manually labeled with the substring or \emph{chunk} describing the reason the build failed.
-Additionally, it contains (1) keywords useful to
-% TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category the substring belongs to.
-% TODO (Caro): Add details how key words were extracted. Add example?
-
-% TODO (Caro): Add more details. How was the split in numbers?
-For each repository in \emph{LogChunks}, we split the examples chronologically into training and test set.
-Therefore, we train on examples from past build logs and test on more recent build logs.
-
-\noindent
-\textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to perform best, we evaluate the techniques with different training set sizes.
-We train each technique with one to five examples from each of the repositories within \emph{LogChunks}.
-The size of the test set is one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk retrieval techniques need to be, we record the structural categories of the examples in the training and test sets.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($\mathit{RetrievedLines}$).
-As oracle in our evaluation, we save the desired lines from the output of the test example ($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our evaluation.
-
-\vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm]
-	 \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap \mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a tool as well as what \textit{LogChunks} contains for each example. 
-        % TODO (Caro) What about when a line is replicated twice? I.e., Are line numbers part of this?
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\ Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of the retrieved lines were actually desired. 
-	\item $\mbox{Recall} = \dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$ \vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$ \vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall.
-We prefer F$_{1}$ to other aggregate measures such as accuracy because for a ``needle-in-the-haystack'' scenario, we do not want to bloat our results by correctly not finding lots of irrelevant log lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\ \mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\ We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
-\end{itemize}
-
-% Recall and precision of CTS and KWS vary with the number of lines selected for retrieval.
-% We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the training examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
-
-\section{Results}
-This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as baseline.
-
-\lstset{
-  language=,
-  morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass   
-Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass
-        from line 5 of sass/components/_all.sass
-        from line 6 of bulma.sass
-  \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
-  \label{lst:pbe-unsuccessful}
-\end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:r:cts}
-\begin{figure*}
-\centering
-    \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-CTS}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-CTS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-CTS} presents precision, recall and F$_{1}$-score of chunk retrieval using CTS for an increasing number of training examples.
-When using one to five training examples, the size of the training set has no noticeable influence on precision, recall or F$_{1}$-score of the chunk retrieval with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same measurements for an increasing number of structural categories in the training and test examples.
-With increasing category count, precision, recall and F$_{1}$-score decrease.
-Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:r:kws}
-\begin{figure*}
-\centering
-    \textbf{Keyword Search (KWS)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-KWS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-KWS} presents precision, recall and F$_{1}$-score of chunk retrieval using KWS for different numbers of training examples.
-The recall increases by about 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
-The F$_{1}$-score stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same measurements for an increasing number of structural categories in the training and test examples.
-For more than one structural category in the training and test examples the recall decreases by about 20\% and the precision decreases about 6\%.
-For more than two structural categories no clear trend is visible in precision, recall or F$_{1}$-score for an increasing amount of categories in the training and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
-% The precision is 19\% when retrieving half of the expected number of lines. On average 9\% of the lines in the build log are retrieved then.
-% When 2.5 times the expected number of lines are retrieved, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
-% The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-% 		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
-                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
-                \label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
-Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
-In 89 further cases, an extraction program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output.
-In 30 of the 89 cases did the synthesized program only partially extract a subset of the desired lines.
-For these 30 cases, the average recall was 28\%.
-Listing \ref{lst:pbe-unsuccessful} shows an example of such an \emph{unsuccessful retrieval}, where the synthesized program only retrieved two of the four targeted lines.
-In 173 of the 400 cases could PROSE not synthesize program consistent with all of the training examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs depend on the number of structural categories in the training and test examples.
-The figure demonstrates that program synthesis mostly returns exactly the desired output when there are is only one structural category present in the training examples.
-However, when two or more structural categories are simultaneously present in the examlpe set, PROSE could in most cases not synthesize a program consistent with all training examples.
-For four or more present categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of the 227 runs where PBE could synthesize a program consistent with all training examples.
-When the training set size increases from one to two, recall and F$_{1}$-score increase by about 25\%, precision increases by about 10\%.
-For two or more training examples, recall and F$_{1}$-score stay around 75\% and precision around 96\%.
-
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we want to compare against a baseline of randomly picking lines from the build log.
-Due to the fact no one would seriously consider RLR in real-world scenarios, we are omitting its detailed graphs here.
-However, its results follow intuitive expectations:
-% TODO Caro: shortly descibre RLR graphs ommitted
-
-\subsection{Comparison of All Techniques}
-In this section, we aggregate the results from \Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
-CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
-With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
-PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is compared in Figure~\ref{fig:recall-precision-all}.
-% The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
-% PBE has the highest average precision with 95\%.
-% Chunk retrieval with CTS has the highest average F$_{1}$-score with 51\% and the second highest recall with 46\%.
-% KWS has the smallest precision of the three chunk retrieval techniques.
-% With 16\% it is still higher than the precision of the RLR baseline with 7\%.
-% KWS has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
-For more than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
-		\label{fig:success-partial-all}
-\end{figure}
-
-\begin{figure*}
-\centering
-    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
-		\label{fig:recall-precision-singlecategory-all}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
-		\label{fig:recall-precision-multicategory-all}
-\end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}  
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
-\end{itemize}
-\end{simplebox}
-
-The first section discusses for PBE, CTS and KWS separately in which cases they perform best.
-It details for which types of input build logs, available training examples and consumption of the retrieved output each technique is suited.
-In the following section we discuss which of these criteria should influence the decision to use a certain technique most.
-Based on our empirical comparison, we present a decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed chunk retrieval techniques separately.
-It gives recommendations which kind of information chunk targets are best for each technique and for what kind of usage the respective output is suitable.
-
-\begin{table}[tbp]
-\resizebox{\columnwidth}{!}{%
-\centering
-\begin{tabular}{llll}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabular}%
-}
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\subsubsection{Program Synthesis by Example (PBE)}
-
-\noindent
-\textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best results when the training examples are structurally identical.
-This is because PROSE has difficulty synthesizing OR-based programs (see \Cref{sec:prose:impl}).
-PBE is thus suited to retrieve information chunks that always have the same surrounding or defining internal structure.
-To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.
-
-When the training examples are of the same structure, even one or two two examples are enough input for PROSE to synthesize a regular expression program with good recall.
-In our study, additional training examples did not improve the chunk retrieval.
-In fact, unless they were in some sense redudant, adding training examples above that even hindered the applicability of PBE.
-
-\noindent
-\textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression program yields an output, PBE has high precision and recall.
-The tool clearly identifies a failing program synthesis or when no output from the program applied to a build log is obtained.
-Therefore, if there is an output, the user can have high confidence that it is the desired output.
-This preciseness makes output from PBE chunk retrieval well-suited for machine consumption.
-
-\subsubsection{Common Text Similarity (CTS)}
-\noindent
-\textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the fewer structural categories are present in the training and test examples.
-
-The number of training examples had no noticeable influence on precision or recall in our study.
-Information retrieval techniques like text similarity commonly learn on a higher number of examples than used for our study.
-Future work is needed to investigate how many examples yield improvements in the chunk retrieval over a single training example.
-
-% TODO Caro: I do not understand the following sentence.
-Extracting the average number of lines present in the training examples gives the best retrieval results for CTS, according to the F$_{1}$-score.
-
-\noindent
-\textbf{Retrieval Output Usage}
-% TODO Caro: reforumlate this please
-CTS has good precision and recall on average, though the precision or recall of a chunk retrieval run is very hard to predict from the given result.
-Therefore, retrieval output from CTS is suited to be read by a human. This could include semi-automated procedures such as sending developers an email with the extracted build failure reason.
-
-\subsubsection{Keyword Search (KWS)}
-\noindent
-\textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
-This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log.
-For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
-
-Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does improve the recall within our study but also increases the proportion of lines retrieved overall and therefore decreases precision.
-
-\noindent
-\textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its precision is the lowest.
-The output of a chunk retrieval with KWS is well-suited to be read by humans, but ill-suited for consumption by automated tools.
-
-\begin{figure}[tb]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
-		\label{fig:crt-recommendation}
-\end{figure}
-
-\subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
-In Figure~\ref{fig:crt-recommendation}, we present a decision tree, which developers and researchers who want to retrieve information chunks from build logs can follow.
-The decision tree is built up of questions which either lead to more questions or to a leaf node containing a recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results from our comparison study.
-The recommendations could therefore be influenced by idiosyncrazies of our specific implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced answer to RQ2, about which criteria influence the suitability of a chunk retrieval technique.
-The earlier in the decision tree a criterion is noted, the more important it is when distinguishing the techniques.
-
-The first and most important aspect are the structural categories.
-Are the information chunks one would like to retrieve always presented in the same structural way within the build logs?
-Then the information chunks in all training examples and the analyzed build log are in the same structural category.
-
-If the information chunks are from multiple structural categories, i.e.
-they are not represented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS\@.
-If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
-We also recommend CTS when the representations are from one structural category, when the user does not require a high confidence in the precision or recall of the outcome and when the user would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by combining the different build log analysis techniques studied in this paper.
-Such a super analyzer would likely always first employ PBE (because of its high accuracy), followed by a combination of CTS and KWS.
-Other than initial setup and training time, there should be no downside to this approach if it is implemented in a transparent way to the underlying technique: the output of the super analyzer could include from which sub-tool it originated and thus facilitate automatic on-ward processing or interpretation of the result.
-
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we describe two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI are caused by a small or by a large group of test cases.
-They gather CI build logs from various projects, which are their only available data source.
-The task of the researcher is to extract the names of the failing test cases from each build log.
-When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test cases is in the investigated build logs.
-As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, non-predictable structural representations.
-The next question is whether they value precision over recall.
-As they have to manually inspect the results of both CTS and KWS, they choose recall over precision to avoid having to inspect the whole log in case the relevant information chunk was not retrieved.
-Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor the performance of the phases within their CI build.
-They are using Travis CI, which measures the duration of build phases and documents them within the build log.
-As all log statements that report timing measurements are formatted the same way, the targeted log chunks are from one structural category.
-Therefore the development team can use PBE to retrieve the duration of a build phase as well as its name.
-
-\section{Threats to Validity}
-There are several threats to the validity of the conclusions of our work.
-
-\noindent
-\textbf{Implementation}
-\label{sec:prose:impl}
-% TODO we need to say something about why we think that these limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk retrieval techniques and the libraries we used.
-Our implementation of PBE is based on the program synthesis provided by PROSE\@.
-The idiosyncrazies of this framework influence our PBE results. Other frameworks similar to PROSE might have somewhat different strengths and weaknesses.
-For example, the need for examples from a single structural category stems from the fact that PROSE cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
-PROSE introduced this constraint to keep the synthesis performance reasonable.
-At the same time, this is clearly a current theoretical challenge of all PBE implementations, and we therefore attribute it to the technique itself, rather than the specific implementation.
-
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec} and the way it splits strings into word tokens.
-On the other hand, {\tt text2vec} is the de-facto standard library to do word embeddings in R.
-We intentionally chose a simple, minimally configured and tuned approach to compare against.
-Tuning the text similarity meta-parameters more to the specific use case of chunk retrieval from build logs would yield better chunk retrieval results.
-
-\noindent
-\textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
-It only consists of build logs from open source projects and therefore it is not clear whether our results are generalizable to industry projects.
-We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
-This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI environment.
-
-\noindent
-\textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we only trained on one to five examples.
-We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.
-
-\noindent
-\textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural categories than with one category.
-% TODO Caro: Please explain the following further. Why does a realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.
-
-\section{Future Work}
-\todo{survey build logs tools in industry}
-
-There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set \cite{} specifically for the comparative study in this paper, though it can be the basis for various further analyses of build log data.
-  The keywords, for example, can be investigated to answer which keywords are used to search for the reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
-  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This paper investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
-  Our study design can be reused to evaluate other build log analysis techniques, such as the diff and information retrieval approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
-  In a next step, each of these techniques could be refined to better approach the domain of build logs.
-  The \emph{LogChunks} data set and our study results act as a baseline to benchmark such technique improvements.
-  We propose the following improvements:
-    \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
-      One could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
-      FlashExtract includes special tokens when enumerating possible regular expressions.
-      One could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
-      We propose to further investigate improvements in preprocessing of the log text, in tokenization of the log lines into terms and in stop words lists.
-    \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focuses on precision and recall.
-  We propose to investigate how useful these outputs are to developers through controlled experiments.
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in their decision on how to analyze build logs.
-We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
-Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
-Secondary factors are the desired confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by combining the different build log analysis techniques studied in this paper.

### 2020-04-02 tse-paper/1-lit-survey.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
-
-\lstset{
-  morekeywords={},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{Plum},
-	frame=single,
-  extendedchars=false,
-  texcl=false,
-  aboveskip=\baselineskip,
-  belowskip=0pt
-}
-
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within the build.
-The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
-study.
-Our goal was to classify how and what for researchers use build logs as a source
-of data (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
-build tools.
-
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
-examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
-\end{itemize}
-\end{simplebox}
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
-  a regular expression matching the given chunks within the build logs.
-  \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
-  \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
-  the occurrence of specific trigger words.
-\end{itemize}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
-  \end{lstlisting}  
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}  
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
-from Android/Gradle build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
-
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence.
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
-  are present in the training examples.
-\end{itemize}
-
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
-%         \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
-%           \item a keyword search approach (KWS).
-%         \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
-
-We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
-recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
 \section{Systematic Literature Survey and Mapping}
@@
 \subsection{Discussion}
-various researchers analyzing build logs to support their research, tools developed
-to help developers \todo{motivational reference}.
+various researchers analyzing build logs to support their research,
+tools developed to help developers \todo{motivational reference}.
 
 \subsubsection{Retrieved Information}
-why from build logs? 
-not avaliable in cleaner format
-much use for research, a bit of developer information / tools
-following: research so many logs that unfeasible to do manually, less focus on tools
-for devs (caveat! we excluded books and documentation on industrial tools -> many
-approaches there to make build logs digestible, tough many focus on general
-minimizing of the data presented, not retrieving specific chunks)
+why from build logs? not avaliable in cleaner format much use for
+research, a bit of developer information / tools following: research
+so many logs that unfeasible to do manually, less focus on tools for
+devs (caveat! we excluded books and documentation on industrial tools
+-> many approaches there to make build logs digestible, tough many
+focus on general minimizing of the data presented, not retrieving
+specific chunks)
 
 \subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail
-we follow that researchers often see this as an unimportant side fact
-work needed to be done to get the big work done
+broadly mentioned shortly, rarely explained in detail we follow that
+researchers often see this as an unimportant side fact work needed to
+be done to get the big work done
 
 \subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort developing a parser
-other times also because other tools used in further research are limiting the scope
-(reference paper with PIT tool).
-many focus on maven because of it's prevalence also in respect to other tools
-much research done on travis ci logs b/c of their abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
-work from system log analysis.
-
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error types such as dependency mismatches are the most prominent cause of build failures at Google.
-In addition, they notice that most failures are resolved within two builds.
-They based their analyses on sets of build logs collected from industry partners.
-They develop a custom parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open source Java projects and find that most builds fail because of failing tests.
-For most projects, over half of the failed builds follow a previous failed build.
-Rausch et al.'s data shows that most failures occur in the second half of the build runtime, which can cause long delays in the feedback loop, especially when builds are automatically retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects in Java to industrial ones.
-They determine that testing failures are more common than compilation errors.
-Open source builds fail most often because of unit tests, whereas release preparations are the primary cause in industrial projects.
-Their data stems from analyzing build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent} with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build breakage data.
-They classify build failures from \emph{TravisTorrent} according to whether they were caused by an environmental failure or caused by a developer change.
-Their analysis starts with manual categorization of build logs.
-They select keywords and strings that identify their targeted categories and code a script to automatically classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers presented
-in this section create parsers and regular expression-based programs.
-This task of retrieving specific chunks of text from the build logs can be
-solved by the chunk retrieval techniques we compare in this article.
-Our results can support researchers in choosing a suitable technique for their
-data set of build logs and the chunks they want to retrieve.
-By relieving them from building custom parsers we enable them to cover a much
-wider range of languages and build tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why their build failed.
-Several researchers investigate how to support developers in working with verbose build logs.
-Vassallo et al.~\cite{vassallo2018un-break} try to shorten the time it takes developers to understand build logs.
-They parse Maven~\cite{maven2019website} build logs into a structured representation and create hint generators.
-%The hint generators leverage this structured access to the information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for discussions related to why the build failed.
-In a qualitative study they observed that highlighting the locality and context of an issue is helpful to programmers.
-%Their tool BART is published as a Jenkins Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used to fill similar structured representations with information from build logs.
-As they simplify the construction of parsers they would enable developers and researchers to cover a wider array of build tools, which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to reduce the portions of a log that a developer has to inspect.
-Their techniques remove lines that appear both in logs from passing and failing builds and use a modified \emph{Term Frequency Inverse Document Frequency} (TF-IDF) weighting to identify term vectors likely to occur with failures.
-Their diff technique can be interpreted as a chunk retrieval technique, where the targeted information is defined by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a basic structuring of the build logs within their log viewer using \emph{log folds}~\cite{travis2019logfolds}.
-They add fold identifiers around common commands and setup or teardown build phases and collapse the contained lines by default.
-
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log files produced during runtime.
-A main difference between build logs and system logs is that system logs are fundamentally structured through events.
-Each line in a log file represents one event with a set of fields: timestamp, verbosity level and raw message content~\cite{he2017towards}.
-Figure \ref{lst:system-log} shows example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to separate constant and variable parts within a log message~\cite{nagappan2010abstracting,he2017towards}.
-Next, the log messages are clustered into log events, unifying messages with identical constant parts and varying parameters.
-The output of a log parser is an ordered list of timed events and their corresponding parameter values~\cite{he2016evaluation}.
-This structured log is then the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational profiling~\cite{nagappan2009efficiently}, debugging~\cite{oliner2012advances}, performance analytics or anomaly detection~\cite{nagappan2010abstracting}.
-%Xu et al.~\cite{xu2009detecting} leverage the connection of log statements to the source code producing them to separate messages into constant and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied to build logs.
-One example is comparing execution traces to reference traces of intended behavior to detect anomalies.
-Amar et al.~\cite{amar2019mining} employed a similar approach to detect relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of events.
-%A similar approach could also be applied to build logs to determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information from the build log as a whole with chunk retrieval techniques.
-Chunk retrieval techniques are used as a part of log parsing to retrieve the values of variable parts in a log message, e.g.
-by using regular expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
-  \end{lstlisting}  
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques}
-%The techniques we investigate are based on existing methods of Programming by Example.%, information extraction and information retrieval.
-%This section presents different Programming by Example resources surrounding the PROSE library.
-%We explain its generic program synthesis algorithm and how PROSE synthesizes text extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program synthesis that enables users to automate repetitive tasks, without them having to explicitly codify a computer program.
-One has to provide prototypical examples of the input and the desired output.
-A
-synthesis algorithm tries to create a program (based on a regular language) that transforms the input to the output.
-The minimum working condition is for this when replayed on the examples inputs is to provide the specified output, but, hopefully, PBE is as close as possbile to the user's intention and thus also works on a different and larger set of inputs.
-This section introduces the theoretical foundations of the program synthesis
-algorithm of the \emph{PROgram Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research.
-Next, this section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program synthesis in the Microsoft PROSE framework.
-FlashMeta separates the inductive synthesis algorithm from the domain specific capabilities of the desired program by encoding the possible program space in a domain specific language (DSL).
-The user specifies the desired program behavior by providing in/output examples (I/O examples).
-FlashMeta uses \emph{witness functions}, provided by the DSL, to divide the synthesis into smaller subtasks.
-For each of these subtasks it enumerates all possible programs that solve the subtask consistent with the set of I/O examples.
-A program is consistent with a set of I/O examples if, for each input example, it produces the corresponding output~\cite{mitchell1982generalization}.
-The possible subprograms are joined and stored in a \emph{version space algebra} (VSA)~\cite{mitchell1982generalization}.
-This a tree structure, which space-efficiently saves candidate programs for tasks by sharing common subexpressions.
-Next, FlashMeta ranks the enumerated programs according to which ones the user most likely intended.
-The DSL also provides the ranking characteristics.
-From the ranked VSA, FlashMeta can then return a ranked list of complete programs consistent with the user's example.
-
-% In addition to I/O examples of the intended program, the user can also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized program.
-
-% The different applications of PROSE presented in the following paragraphs were all eventually implemented as DSLs for the FlashMeta synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text, websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs from semi-structured text based on regular expressions.
-Users can extract multiple fields and structure them with hierarchy and sequence.
-% FlashExtract synthesizes programs to extract each of the fields leveraging the information about hierarchical containment and sequentiality.
-% It eliminates the need for the user to understand the entire structure of the processed document and decreases the effort of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of two cut positions.
-A position is either specified by an absolute character index or by a pair of two regular expressions.
-The first regular expression matches the substring directly before the characterized position, the second regular expression matches the substring directly after.
-A regular expression in FlashExtract is a concatenation of tokens, e.g.\ standard character classes or string literals frequently occurring in the input examples.
-Figure \ref{lst:prose-program} shows a text extraction program synthesized by FlashExtract.
-This program defines the first position as after a colon followed by a newline character and before a piece of text with all capital letters.
-It defines the second position as before two newline characters.
-
-Apart from automatic completion in Excel spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for two other Microsoft product features:
-Microsoft's system log analysis tool Azure Monitor lets users define custom log fields~\cite{azure2019custom}.
-The ConvertFrom-String function in PowerShell allows a user to specify an example template to extract hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
-\section{Chunk Retrieval Techniques}
-\label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval techniques we study in this article, namely program synthesis by example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that represent a specific, targeted information.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically retrieve pieces of information that appear literally in the build logs, i.e., techniques that do not aggreagte, combine, or deducted information.
-We call such pieces of information from build logs \emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and parser to analyze the entire structure of build logs, but focus on ad-hoc extracting just one specific piece of information per configuration.
-
-With the term \textit{configuration,} we abstract over the training and parametrization that different techniques require in different forms.
-A configuration can be explicitly stated or implicitly dervied by learning through provided examples.
-It is therefore a manual specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to identify the targeted information chunk in a build log.
-Each chunk retrieval technqiue has a specific \textit{granularity}, i.e.,\ the smallest piece of text it can return (e.g., a line, or a word). The granularity might be adjustable by configuration.
-\emph{Running a chunk retrieval technique} means to execute a fully configured technique to consumes as input a build log in plain text format and to produce an array as output.
-The array consists of substrings of the build log text.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[]
-\centering
-\caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
-\toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
-\bottomrule
-\end{tabularx}
-\label{tab:ctr}
-\end{table*}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model.
-% We investigate when text similarity is a suitable technique to retrieve information chunks from build logs.
-% In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use the same concept of examples as for PBE\@
-% TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}.
-The lines of the output strings of the training examples define our search query.
-The algorithm splits the search query into single lines and identifies tokens, in our case words.
-Then we build a document-term-frequency matrix over the lines from the search query and prune very often or very rarely appearing words.
-Finally, the algorithm applies TF-IDF to the matrix, a best practice for natural language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the whole text and process it in the same way as the output of the training examples.
-The algorithm calculates the cosine similarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
-After summing up the similarities of each build log line to all search query lines, we sort the build log lines in decreasing similarity.
-The average number of lines in the outputs of the training examples determines how many of the most similar lines are returned as the output of the retrieval run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a large amount of unstructured information, a first ad-hoc approach they use is to search for related keywords.
-Indeed, this was one of the most common approaches we took when searching for the reason the build failed within a log while creating the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers use to view build logs, we study when such a keyword search is suitable for retrieving information chunks from CI build logs.
-% In the following we will explain how we use simple keyword search to retrieve information from CI build logs, which we refer to as \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@.
-To better compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted chunk or close to it.
-The configuring keywords for KWS are the ones that appear most often in the keywords of all training examples.
-% TODO Caro Please explain above sentence more precisely
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and search for all exact occurrences of the keywords.
-As keywords are often not directly describing the desired information, but rather appear close to the desired information, KWS also retrieves the lines around the found keyword.
-The number of surrounding lines retrieved is the average of lines in the output of the training examples.
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes programs according
-% to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming knowledge~\cite{mayer2015user}.
-% In the context of text extraction through regular expressions, Programming by Example relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
-% In this work, we refer to our interpretation of Programming by Example as \emph{PBE}\@.
-% We investigate the suitability of PBE to retrieve information chunks from build logs.
-% In the following, we explain the configuration and application of PBE to chunk retrieval from CI build logs.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by Example, we refer to them in short
-as \emph{examples}.
-The \emph{input} is the text of the build log file.
-The \emph{output} is an array of substrings of the log file text, representing the substrings that should be retrieved by the synthesized program when given the corresponding input file.
-One or multiple examples, the training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted.
-The PROSE program synthesis then tries to construct a program consistent with all training examples.
-% A program is consistent with an example if it returns the defined output when executed on the defined input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn uses the FlashMeta algorithm.
-% Both are described in Section~\ref{sec:rw-prose}.
-
-% TODO Caro: The following is very obvious and could apply to any technique. 
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the synthesized regular expression program.
-It then returns the substring of the build log matched by the program or an empty string if the program found no match.
-
-\subsection{Random Line Retrieval}
-\label{sec:expl-rlr}
-
-In our evaluation, we want to compare against a baseline of randomly picking lines from the build log.
-RLR essentially mimicks the situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should return.
-For a fair comparison to the other techniques (whose number of returned lines is dynamic), we configure RLR to return the average number of lines in the chunks of the training examples.
-% TODO Caro: some more details here?
-
-\subsection{Other Techniques}
-%Literature mentions further build log analysis techniques.
-%This section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information retrieval to identify relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
-The configuration for the technique is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not present in the successful build log and contain terms related to the given past failures.
-
-\subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a unifying interface.
-The unified interface is implemented in Ruby and calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
-We implemented CTS, KWS and RLR using R and the text2vec library~\cite{text2vec2019webpage}.
-
-\section{Study Design}
-\label{sec:study}
-
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-To investigate which techqnique is best suited to retrieve chunks from CI build
-logs we evaluate them on the \emph{LogChunks}~\cite{brandt2020logchunks} data set.
-This section describes our study design and which metrics we measure to answer our research questions.
-In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.
-
-\subsection{LogChunks}
-For this study we created the previously published data set \emph{LogChunks}.
-It encompasses 797 build logs from Travis CI, stemming from a broad range of 80
-GitHub repositories and 29 programming languages. For each file, the authors
-manually ``labeled the log part (chunk) describing why the build failed''~\cite{brandt2020logchunks}.
-We include keywords, which we would use to search for the selected chunk
-within the log. In addition, we categorized the log chunks according to their
-format within the log. If the chunks are surrounded by the same markings within
-the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe}, \ref{sec:expl-ts} and \ref{sec:expl-skws}.
-Random Line Retrieval (RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study.
-For each of the 80 repositories in it, \emph{LogChunks} contains 10 build logs, manually labeled with the substring or \emph{chunk} describing the reason the build failed.
-Additionally, it contains (1) keywords useful to
-% TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category the substring belongs to.
-% TODO (Caro): Add details how key words were extracted. Add example?
-
-% TODO (Caro): Add more details. How was the split in numbers?
-For each repository in \emph{LogChunks}, we split the examples chronologically into training and test set.
-Therefore, we train on examples from past build logs and test on more recent build logs.
-
-\noindent
-\textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to perform best, we evaluate the techniques with different training set sizes.
-We train each technique with one to five examples from each of the repositories within \emph{LogChunks}.
-The size of the test set is one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk retrieval techniques need to be, we record the structural categories of the examples in the training and test sets.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($\mathit{RetrievedLines}$).
-As oracle in our evaluation, we save the desired lines from the output of the test example ($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our evaluation.
-
-\vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm]
-	 \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap \mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a tool as well as what \textit{LogChunks} contains for each example. 
-        % TODO (Caro) What about when a line is replicated twice? I.e., Are line numbers part of this?
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\ Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of the retrieved lines were actually desired. 
-	\item $\mbox{Recall} = \dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$ \vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$ \vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean of precision and recall.
-We prefer F$_{1}$ to other aggregate measures such as accuracy because for a ``needle-in-the-haystack'' scenario, we do not want to bloat our results by correctly not finding lots of irrelevant log lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\ \mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\ We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
-\end{itemize}
-
-% Recall and precision of CTS and KWS vary with the number of lines selected for retrieval.
-% We evaluate the effect of varying the number of extracted lines by multiplying the average number of lines present in the training examples with a \emph{retrieval size factor} from 0.5 to 2.5 in steps of 0.5.
-
-\section{Results}
-This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as baseline.
-
-\lstset{
-  language=,
-  morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass   
-Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass
-        from line 5 of sass/components/_all.sass
-        from line 6 of bulma.sass
-  \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
-  \label{lst:pbe-unsuccessful}
-\end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:r:cts}
-\begin{figure*}
-\centering
-    \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-CTS}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-CTS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-CTS} presents precision, recall and F$_{1}$-score of chunk retrieval using CTS for an increasing number of training examples.
-When using one to five training examples, the size of the training set has no noticeable influence on precision, recall or F$_{1}$-score of the chunk retrieval with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same measurements for an increasing number of structural categories in the training and test examples.
-With increasing category count, precision, recall and F$_{1}$-score decrease.
-Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:r:kws}
-\begin{figure*}
-\centering
-    \textbf{Keyword Search (KWS)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-KWS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-KWS} presents precision, recall and F$_{1}$-score of chunk retrieval using KWS for different numbers of training examples.
-The recall increases by about 12\% when increasing the size of the training set to more than one example, while the precision stays constant at around 16\%.
-The F$_{1}$-score stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same measurements for an increasing number of structural categories in the training and test examples.
-For more than one structural category in the training and test examples the recall decreases by about 20\% and the precision decreases about 6\%.
-For more than two structural categories no clear trend is visible in precision, recall or F$_{1}$-score for an increasing amount of categories in the training and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision, recall and F$_{1}$-score of chunk retrieval runs with KWS\@.
-% The precision is 19\% when retrieving half of the expected number of lines. On average 9\% of the lines in the build log are retrieved then.
-% When 2.5 times the expected number of lines are retrieved, the precision decreases to 10\% and a quarter of the lines in the build log are retrieved on average.
-% The recall ranges from 58\% to 75\% and the F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-% 		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
-                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
-                \label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
-Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
-In 89 further cases, an extraction program was also successfully synthesized, though in 59 of the 89 cases the synthesized program yielded no output.
-In 30 of the 89 cases did the synthesized program only partially extract a subset of the desired lines.
-For these 30 cases, the average recall was 28\%.
-Listing \ref{lst:pbe-unsuccessful} shows an example of such an \emph{unsuccessful retrieval}, where the synthesized program only retrieved two of the four targeted lines.
-In 173 of the 400 cases could PROSE not synthesize program consistent with all of the training examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs depend on the number of structural categories in the training and test examples.
-The figure demonstrates that program synthesis mostly returns exactly the desired output when there are is only one structural category present in the training examples.
-However, when two or more structural categories are simultaneously present in the examlpe set, PROSE could in most cases not synthesize a program consistent with all training examples.
-For four or more present categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows precision and recall of the 227 runs where PBE could synthesize a program consistent with all training examples.
-When the training set size increases from one to two, recall and F$_{1}$-score increase by about 25\%, precision increases by about 10\%.
-For two or more training examples, recall and F$_{1}$-score stay around 75\% and precision around 96\%.
-
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we want to compare against a baseline of randomly picking lines from the build log.
-Due to the fact no one would seriously consider RLR in real-world scenarios, we are omitting its detailed graphs here.
-However, its results follow intuitive expectations:
-% TODO Caro: shortly descibre RLR graphs ommitted
-
-\subsection{Comparison of All Techniques}
-In this section, we aggregate the results from \Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
-CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
-With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
-PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is compared in Figure~\ref{fig:recall-precision-all}.
-% The recall of PBE has a high skew towards one and zero, meaning in most cases either the retrieval is successful or no relevant lines are extracted at all.
-% PBE has the highest average precision with 95\%.
-% Chunk retrieval with CTS has the highest average F$_{1}$-score with 51\% and the second highest recall with 46\%.
-% KWS has the smallest precision of the three chunk retrieval techniques.
-% With 16\% it is still higher than the precision of the RLR baseline with 7\%.
-% KWS has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
-For more than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
-		\label{fig:success-partial-all}
-\end{figure}
-
-\begin{figure*}
-\centering
-    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
-		\label{fig:recall-precision-singlecategory-all}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
-		\label{fig:recall-precision-multicategory-all}
-\end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}  
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
-\end{itemize}
-\end{simplebox}
-
-The first section discusses for PBE, CTS and KWS separately in which cases they perform best.
-It details for which types of input build logs, available training examples and consumption of the retrieved output each technique is suited.
-In the following section we discuss which of these criteria should influence the decision to use a certain technique most.
-Based on our empirical comparison, we present a decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed chunk retrieval techniques separately.
-It gives recommendations which kind of information chunk targets are best for each technique and for what kind of usage the respective output is suitable.
-
-\begin{table}[tbp]
-\resizebox{\columnwidth}{!}{%
-\centering
-\begin{tabular}{llll}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabular}%
-}
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\subsubsection{Program Synthesis by Example (PBE)}
-
-\noindent
-\textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best results when the training examples are structurally identical.
-This is because PROSE has difficulty synthesizing OR-based programs (see \Cref{sec:prose:impl}).
-PBE is thus suited to retrieve information chunks that always have the same surrounding or defining internal structure.
-To extract for example the reason a build failed, the log passage describing the failure would always have to be started and ended the same way.
-
-When the training examples are of the same structure, even one or two two examples are enough input for PROSE to synthesize a regular expression program with good recall.
-In our study, additional training examples did not improve the chunk retrieval.
-In fact, unless they were in some sense redudant, adding training examples above that even hindered the applicability of PBE.
-
-\noindent
-\textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression program yields an output, PBE has high precision and recall.
-The tool clearly identifies a failing program synthesis or when no output from the program applied to a build log is obtained.
-Therefore, if there is an output, the user can have high confidence that it is the desired output.
-This preciseness makes output from PBE chunk retrieval well-suited for machine consumption.
-
-\subsubsection{Common Text Similarity (CTS)}
-\noindent
-\textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the fewer structural categories are present in the training and test examples.
-
-The number of training examples had no noticeable influence on precision or recall in our study.
-Information retrieval techniques like text similarity commonly learn on a higher number of examples than used for our study.
-Future work is needed to investigate how many examples yield improvements in the chunk retrieval over a single training example.
-
-% TODO Caro: I do not understand the following sentence.
-Extracting the average number of lines present in the training examples gives the best retrieval results for CTS, according to the F$_{1}$-score.
-
-\noindent
-\textbf{Retrieval Output Usage}
-% TODO Caro: reforumlate this please
-CTS has good precision and recall on average, though the precision or recall of a chunk retrieval run is very hard to predict from the given result.
-Therefore, retrieval output from CTS is suited to be read by a human. This could include semi-automated procedures such as sending developers an email with the extracted build failure reason.
-
-\subsubsection{Keyword Search (KWS)}
-\noindent
-\textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple structural categories present in the training and test examples.
-This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log.
-For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.
-
-Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does improve the recall within our study but also increases the proportion of lines retrieved overall and therefore decreases precision.
-
-\noindent
-\textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its precision is the lowest.
-The output of a chunk retrieval with KWS is well-suited to be read by humans, but ill-suited for consumption by automated tools.
-
-\begin{figure}[tb]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
-		\label{fig:crt-recommendation}
-\end{figure}
-
-\subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we now want to unify our results into one recommendation scheme.
-In Figure~\ref{fig:crt-recommendation}, we present a decision tree, which developers and researchers who want to retrieve information chunks from build logs can follow.
-The decision tree is built up of questions which either lead to more questions or to a leaf node containing a recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results from our comparison study.
-The recommendations could therefore be influenced by idiosyncrazies of our specific implementation of the chunk retrieval techniques as well as the logs in the \emph{LogChunks} data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced answer to RQ2, about which criteria influence the suitability of a chunk retrieval technique.
-The earlier in the decision tree a criterion is noted, the more important it is when distinguishing the techniques.
-
-The first and most important aspect are the structural categories.
-Are the information chunks one would like to retrieve always presented in the same structural way within the build logs?
-Then the information chunks in all training examples and the analyzed build log are in the same structural category.
-
-If the information chunks are from multiple structural categories, i.e.
-they are not represented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS\@.
-If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS\@.
-We also recommend CTS when the representations are from one structural category, when the user does not require a high confidence in the precision or recall of the outcome and when the user would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user wishes a high confidence in the correctness of the output or prefers no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by combining the different build log analysis techniques studied in this paper.
-Such a super analyzer would likely always first employ PBE (because of its high accuracy), followed by a combination of CTS and KWS.
-Other than initial setup and training time, there should be no downside to this approach if it is implemented in a transparent way to the underlying technique: the output of the super analyzer could include from which sub-tool it originated and thus facilitate automatic on-ward processing or interpretation of the result.
-
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we describe two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI are caused by a small or by a large group of test cases.
-They gather CI build logs from various projects, which are their only available data source.
-The task of the researcher is to extract the names of the failing test cases from each build log.
-When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test cases is in the investigated build logs.
-As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, non-predictable structural representations.
-The next question is whether they value precision over recall.
-As they have to manually inspect the results of both CTS and KWS, they choose recall over precision to avoid having to inspect the whole log in case the relevant information chunk was not retrieved.
-Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor the performance of the phases within their CI build.
-They are using Travis CI, which measures the duration of build phases and documents them within the build log.
-As all log statements that report timing measurements are formatted the same way, the targeted log chunks are from one structural category.
-Therefore the development team can use PBE to retrieve the duration of a build phase as well as its name.
-
-\section{Threats to Validity}
-There are several threats to the validity of the conclusions of our work.
-
-\noindent
-\textbf{Implementation}
-\label{sec:prose:impl}
-% TODO we need to say something about why we think that these limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk retrieval techniques and the libraries we used.
-Our implementation of PBE is based on the program synthesis provided by PROSE\@.
-The idiosyncrazies of this framework influence our PBE results. Other frameworks similar to PROSE might have somewhat different strengths and weaknesses.
-For example, the need for examples from a single structural category stems from the fact that PROSE cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
-PROSE introduced this constraint to keep the synthesis performance reasonable.
-At the same time, this is clearly a current theoretical challenge of all PBE implementations, and we therefore attribute it to the technique itself, rather than the specific implementation.
-
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec} and the way it splits strings into word tokens.
-On the other hand, {\tt text2vec} is the de-facto standard library to do word embeddings in R.
-We intentionally chose a simple, minimally configured and tuned approach to compare against.
-Tuning the text similarity meta-parameters more to the specific use case of chunk retrieval from build logs would yield better chunk retrieval results.
-
-\noindent
-\textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build logs from the \emph{LogChunks} data set.
-It only consists of build logs from open source projects and therefore it is not clear whether our results are generalizable to industry projects.
-We only collected build logs from Travis CI, however we chose to evaluate on an information chunk whose format is not dependent on Travis CI\@.
-This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI environment.
-
-\noindent
-\textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we only trained on one to five examples.
-We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.
-
-\noindent
-\textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural categories than with one category.
-% TODO Caro: Please explain the following further. Why does a realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in many cases has only one or few structural categories.
-
-\section{Future Work}
-\todo{survey build logs tools in industry}
-
-There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the \emph{LogChunks} data set \cite{} specifically for the comparative study in this paper, though it can be the basis for various further analyses of build log data.
-  The keywords, for example, can be investigated to answer which keywords are used to search for the reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and tested each chunk retrieval technique on examples from the same repository.
-  We propose to analyze how techniques could be trained across repositories, building the cornerstones for build environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This paper investigates the three chunk retrieval techniques PBE, CTS and KWS\@.
-  Our study design can be reused to evaluate other build log analysis techniques, such as the diff and information retrieval approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We investigated basic configurations of existing techniques applied to chunk retrieval from build logs.
-  In a next step, each of these techniques could be refined to better approach the domain of build logs.
-  The \emph{LogChunks} data set and our study results act as a baseline to benchmark such technique improvements.
-  We propose the following improvements:
-    \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program synthesis through PROSE ranks possible programs according to what the user most likely intended.
-      One could adapt the ranking rules provided by the FlashExtract DSL to fit common build log chunk retrieval tasks.
-      FlashExtract includes special tokens when enumerating possible regular expressions.
-      One could extend these with tokens found in build logs, such as ``-'',``='',``ERROR'' or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information retrieval techniques have various meta-parameters which can be optimized for the specific use case~\cite{panichella2016parameterizing}.
-      We propose to further investigate improvements in preprocessing of the log text, in tokenization of the log lines into terms and in stop words lists.
-    \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our analysis of the output produced by the chunk retrieval focuses on precision and recall.
-  We propose to investigate how useful these outputs are to developers through controlled experiments.
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in their decision on how to analyze build logs.
-We implemented and compared three different chunk retrieval techniques on our data set \emph{LogChunks}, composed of 797 manually labeled build logs from a broad range of 80 repositories.
-Our results show that the structural representation of the targeted information in the build logs is the main factor to consider when choosing a suitable technique.
-Secondary factors are the desired confidence into recall and precision of the produced output and whether precision or recall is more important for the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by combining the different build log analysis techniques studied in this paper.
+often focussed on specific logs, sometimes mentioned because of effort
+developing a parser other times also because other tools used in
+further research are limiting the scope (reference paper with PIT
+tool). many focus on maven because of it's prevalence also in respect
+to other tools much research done on travis ci logs b/c of their
+abundance and open availability

### 2020-04-02 tse-paper/2-rw.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
-
-\lstset{
-  morekeywords={},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{Plum},
-	frame=single,
-  extendedchars=false,
-  texcl=false,
-  aboveskip=\baselineskip,
-  belowskip=0pt
-}
-
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within the build.
-The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
-study.
-Our goal was to classify how and what for researchers use build logs as a source
-of data (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
-build tools.
-
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
-examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
-\end{itemize}
-\end{simplebox}
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
-  a regular expression matching the given chunks within the build logs.
-  \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
-  \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
-  the occurrence of specific trigger words.
-\end{itemize}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
-  \end{lstlisting}  
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}  
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
-from Android/Gradle build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
-
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence.
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
-  are present in the training examples.
-\end{itemize}
-
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
-%         \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
-%           \item a keyword search approach (KWS).
-%         \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
-
-We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
-recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Kitchenham's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO Caro: update
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-% TODO Caro: please write a draft for this :-)
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool). many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
-
 \section{Related Work}
@@
 \end{figure}
-
-\section{Chunk Retrieval Techniques}
-\label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval
-techniques we study in this article, namely program synthesis by
-example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that
-represent a specific, targeted information.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically
-retrieve pieces of information that appear literally in the build
-logs, i.e., techniques that do not aggreagte, combine, or deducted
-information. We call such pieces of information from build logs
-\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and
-parser to analyze the entire structure of build logs, but focus on
-ad-hoc extracting just one specific piece of information per
-configuration.
-
-With the term \textit{configuration,} we abstract over the training
-and parametrization that different techniques require in different
-forms. A configuration can be explicitly stated or implicitly dervied
-by learning through provided examples. It is therefore a manual
-specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log. Each chunk
-retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word). The
-granularity might be adjustable by configuration. \emph{Running a
-chunk retrieval technique} means to execute a fully configured
-technique to consumes as input a build log in plain text format and to
-produce an array as output. The array consists of substrings of the
-build log text.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[]
-\centering
-\caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
-\toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
-\bottomrule
-\end{tabularx}
-\label{tab:ctr}
-\end{table*}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual
-% software
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model. We
-% investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs. In the following we will explain
-% the concept of how we apply text similarity to information retrieval
-% from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use
-the same concept of examples as for PBE\@
-% TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}. The
-lines of the output strings of the training examples define our search
-query. The algorithm splits the search query into single lines and
-identifies tokens, in our case words. Then we build a
-document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words. Finally, the
-algorithm applies TF-IDF to the matrix, a best practice for natural
-language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the output of the
-training examples. The algorithm calculates the cosine
-similarity~\cite{korenius2007principal} to compare each line of the
-build log with each line of the search query. After summing up the
-similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity. The average number of
-lines in the outputs of the training examples determines how many of
-the most similar lines are returned as the output of the retrieval
-run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad-hoc approach they
-use is to search for related keywords. Indeed, this was one of the
-most common approaches we took when searching for the reason the build
-failed within a log while creating the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers
-% use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs. In
-% the following we will explain how we use simple keyword search to
-% retrieve information from CI build logs, which we refer to as
-% \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@. To better
-compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted
-chunk or close to it. The configuring keywords for KWS are the ones
-that appear most often in the keywords of all training examples.
-% TODO Caro Please explain above sentence more precisely
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords. As keywords are
-often not directly describing the desired information, but rather
-appear close to the desired information, KWS also retrieves the lines
-around the found keyword. The number of surrounding lines retrieved is
-the average of lines in the output of the training examples.
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes
-% programs according to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming
-% knowledge~\cite{mayer2015user}. In the context of text extraction
-% through regular expressions, Programming by Example relieves the
-% developer from having to understand the whole document structure to
-% solve a single extraction task~\cite{le2014flashextract:}. In this
-% work, we refer to our interpretation of Programming by Example as
-% \emph{PBE}\@. We investigate the suitability of PBE to retrieve
-% information chunks from build logs. In the following, we explain the
-% configuration and application of PBE to chunk retrieval from CI
-% build logs.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by
-Example, we refer to them in short as \emph{examples}. The
-\emph{input} is the text of the build log file. The \emph{output} is
-an array of substrings of the log file text, representing the
-substrings that should be retrieved by the synthesized program when
-given the corresponding input file. One or multiple examples, the
-training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted. The
-PROSE program synthesis then tries to construct a program consistent
-with all training examples.
-% A program is consistent with an example if it returns the defined
-% output when executed on the defined
-% input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a
-consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn
-% uses the FlashMeta algorithm. Both are described in
-% Section~\ref{sec:rw-prose}.
-
-% TODO Caro: The following is very obvious and could apply to any
-% technique. 
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the
-synthesized regular expression program. It then returns the substring
-of the build log matched by the program or an empty string if the
-program found no match.
-
-\subsection{Random Line Retrieval}
-\label{sec:expl-rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. RLR essentially mimicks the
-situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should
-return. For a fair comparison to the other techniques (whose number of
-returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples. 
-% TODO Caro: some more details here?
-
-\subsection{Other Techniques}
-%Literature mentions further build log analysis techniques. This
-%section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information
-retrieval to identify relevant lines from a failed build
-log~\cite{amar2019mining}, as we describe in more detail in
-Section~\ref{sec:rw-bl-analysis}. The configuration for the technique
-is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not
-present in the successful build log and contain terms related to the
-given past failures.
-
-\subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a
-unifying interface. The unified interface is implemented in Ruby and
-calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE
-library~\cite{prose2019webpage}. We implemented CTS, KWS and RLR using
-R and the text2vec library~\cite{text2vec2019webpage}.
-
-\section{Study Design}
-\label{sec:study}
-
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-To investigate which techqnique is best suited to retrieve chunks from
-CI build logs we evaluate them on the
-\emph{LogChunks}~\cite{brandt2020logchunks} data set. This section
-describes our study design and which metrics we measure to answer our
-research questions. In the presentation of the results, we first focus
-on each of the three techniques and later compare them against each
-other.
-
-\subsection{LogChunks}
-For this study we created the previously published data set
-\emph{LogChunks}. It encompasses 797 build logs from Travis CI,
-stemming from a broad range of 80 GitHub repositories and 29
-programming languages. For each file, the authors manually ``labeled
-the log part (chunk) describing why the build
-failed''~\cite{brandt2020logchunks}. We include keywords, which we
-would use to search for the selected chunk within the log. In
-addition, we categorized the log chunks according to their format
-within the log. If the chunks are surrounded by the same markings
-within the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}. Random Line Retrieval
-(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
-the comparison.
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study. For each of the
-80 repositories in it, \emph{LogChunks} contains 10 build logs,
-manually labeled with the substring or \emph{chunk} describing the
-reason the build failed. Additionally, it contains (1) keywords useful
-to
-% TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category
-the substring belongs to.
-% TODO (Caro): Add details how key words were extracted. Add example?
-
-% TODO (Caro): Add more details. How was the split in numbers?
-For each repository in \emph{LogChunks}, we split the examples
-chronologically into training and test set. Therefore, we train on
-examples from past build logs and test on more recent build logs.
-
-\noindent
-\textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to
-perform best, we evaluate the techniques with different training set
-sizes. We train each technique with one to five examples from each of
-the repositories within \emph{LogChunks}. The size of the test set is
-one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk
-retrieval techniques need to be, we record the structural categories
-of the examples in the training and test sets.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output
-lines of the chunk retrieval run on the input of the test example
-($\mathit{RetrievedLines}$). As oracle in our evaluation, we save the
-desired lines from the output of the test example
-($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our
-evaluation.
-
-\vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm] \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap
-	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a
-        tool as well as what \textit{LogChunks} contains for each
-        example. 
-        % TODO (Caro) What about when a line is replicated twice?
-        % I.e., Are line numbers part of this?
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\
-	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of
-        the retrieved lines were actually desired. 
-	\item $\mbox{Recall} =
-	\dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$
-	\vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the
-        desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
-	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
-	\vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean
-        of precision and recall. We prefer F$_{1}$ to other aggregate
-        measures such as accuracy because for a
-        ``needle-in-the-haystack'' scenario, we do not want to bloat
-        our results by correctly not finding lots of irrelevant log
-        lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
-	We define a successful retrieval as one where all desired lines were
-	extracted, therefore when recall is one.
-\end{itemize}
-
-% Recall and precision of CTS and KWS vary with the number of lines
-% selected for retrieval. We evaluate the effect of varying the number
-% of extracted lines by multiplying the average number of lines
-% present in the training examples with a \emph{retrieval size factor}
-% from 0.5 to 2.5 in steps of 0.5.
-
-\section{Results}
-This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as
-baseline.
-
-\lstset{
-  language=,
-  morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass   
-Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass
-        from line 5 of sass/components/_all.sass
-        from line 6 of bulma.sass
-  \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
-  \label{lst:pbe-unsuccessful}
-\end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:r:cts}
-\begin{figure*}
-\centering
-    \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-CTS}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-CTS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-CTS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using CTS for an
-increasing number of training examples. When using one to five
-training examples, the size of the training set has no noticeable
-influence on precision, recall or F$_{1}$-score of the chunk retrieval
-with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. With increasing category count, precision,
-recall and F$_{1}$-score decrease. Especially for more than three
-categories present we have no chunk retrieval runs where all desired
-lines were extracted.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:r:kws}
-\begin{figure*}
-\centering
-    \textbf{Keyword Search (KWS)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-KWS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-KWS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using KWS for different
-numbers of training examples. The recall increases by about 12\% when
-increasing the size of the training set to more than one example,
-while the precision stays constant at around 16\%. The F$_{1}$-score
-stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. For more than one structural category in
-the training and test examples the recall decreases by about 20\% and
-the precision decreases about 6\%. For more than two structural
-categories no clear trend is visible in precision, recall or
-F$_{1}$-score for an increasing amount of categories in the training
-and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the
-% effect of the retrieval size factor on precision, recall and
-% F$_{1}$-score of chunk retrieval runs with KWS\@. The precision is
-% 19\% when retrieving half of the expected number of lines. On
-% average 9\% of the lines in the build log are retrieved then. When
-% 2.5 times the expected number of lines are retrieved, the precision
-% decreases to 10\% and a quarter of the lines in the build log are
-% retrieved on average. The recall ranges from 58\% to 75\% and the
-% F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-% 		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
-                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
-                \label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
-evaluation. Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines in 138 cases. In 89 further
-cases, an extraction program was also successfully synthesized, though
-in 59 of the 89 cases the synthesized program yielded no output. In 30
-of the 89 cases did the synthesized program only partially extract a
-subset of the desired lines. For these 30 cases, the average recall
-was 28\%. Listing \ref{lst:pbe-unsuccessful} shows an example of such
-an \emph{unsuccessful retrieval}, where the synthesized program only
-retrieved two of the four targeted lines. In 173 of the 400 cases
-could PROSE not synthesize program consistent with all of the training
-examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
-runs depend on the number of structural categories in the training and
-test examples. The figure demonstrates that program synthesis mostly
-returns exactly the desired output when there are is only one
-structural category present in the training examples. However, when
-two or more structural categories are simultaneously present in the
-examlpe set, PROSE could in most cases not synthesize a program
-consistent with all training examples. For four or more present
-categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
-precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples. When the training set
-size increases from one to two, recall and F$_{1}$-score increase by
-about 25\%, precision increases by about 10\%. For two or more
-training examples, recall and F$_{1}$-score stay around 75\% and
-precision around 96\%.
-
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. Due to the fact no one would
-seriously consider RLR in real-world scenarios, we are omitting its
-detailed graphs here. However, its results follow intuitive
-expectations:
-% TODO Caro: shortly descibre RLR graphs ommitted
-
-\subsection{Comparison of All Techniques}
-In this section, we aggregate the results from
-\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it
-each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk
-retrievals differentiated by techniques in our study. CTS and KWS
-extract some of the desired lines in 79\% and 88.5\% of the chunk
-retrieval runs. With 38.25\%, KWS also has the highest number of fully
-successful extractions, followed by PBE with 34.5\%. PBE has the
-lowest number of partial retrievals with only 18 out of 400 chunk
-retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is
-% compared in Figure~\ref{fig:recall-precision-all}. The recall of PBE
-% has a high skew towards one and zero, meaning in most cases either
-% the retrieval is successful or no relevant lines are extracted at
-% all. PBE has the highest average precision with 95\%. Chunk
-% retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% and the second highest recall with 46\%. KWS has the smallest
-% precision of the three chunk retrieval techniques. With 16\% it is
-% still higher than the precision of the RLR baseline with 7\%. KWS
-% has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of a single structural category present in the
-training examples compared to multiple categories present. For more
-than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by
-the number of structural categories present.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
-		\label{fig:success-partial-all}
-\end{figure}
-
-\begin{figure*}
-\centering
-    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
-		\label{fig:recall-precision-singlecategory-all}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
-		\label{fig:recall-precision-multicategory-all}
-\end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}  
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
-\end{itemize}
-\end{simplebox}
-
-The first section discusses for PBE, CTS and KWS separately in which
-cases they perform best. It details for which types of input build
-logs, available training examples and consumption of the retrieved
-output each technique is suited. In the following section we discuss
-which of these criteria should influence the decision to use a certain
-technique most. Based on our empirical comparison, we present a
-decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed
-chunk retrieval techniques separately. It gives recommendations which
-kind of information chunk targets are best for each technique and for
-what kind of usage the respective output is suitable.
-
-\begin{table}[tbp]
-\resizebox{\columnwidth}{!}{%
-\centering
-\begin{tabular}{llll}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabular}%
-}
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\subsubsection{Program Synthesis by Example (PBE)}
-
-\noindent
-\textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best
-results when the training examples are structurally identical. This is
-because PROSE has difficulty synthesizing OR-based programs (see
-\Cref{sec:prose:impl}). PBE is thus suited to retrieve information
-chunks that always have the same surrounding or defining internal
-structure. To extract for example the reason a build failed, the log
-passage describing the failure would always have to be started and
-ended the same way.
-
-When the training examples are of the same structure, even one or two
-two examples are enough input for PROSE to synthesize a regular
-expression program with good recall. In our study, additional training
-examples did not improve the chunk retrieval. In fact, unless they
-were in some sense redudant, adding training examples above that even
-hindered the applicability of PBE.
-
-\noindent
-\textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression
-program yields an output, PBE has high precision and recall. The tool
-clearly identifies a failing program synthesis or when no output from
-the program applied to a build log is obtained. Therefore, if there is
-an output, the user can have high confidence that it is the desired
-output. This preciseness makes output from PBE chunk retrieval
-well-suited for machine consumption.
-
-\subsubsection{Common Text Similarity (CTS)}
-\noindent
-\textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the
-fewer structural categories are present in the training and test
-examples.
-
-The number of training examples had no noticeable influence on
-precision or recall in our study. Information retrieval techniques
-like text similarity commonly learn on a higher number of examples
-than used for our study. Future work is needed to investigate how many
-examples yield improvements in the chunk retrieval over a single
-training example.
-
-% TODO Caro: I do not understand the following sentence.
-Extracting the average number of lines present in the training
-examples gives the best retrieval results for CTS, according to the
-F$_{1}$-score.
-
-\noindent
-\textbf{Retrieval Output Usage}
-% TODO Caro: reforumlate this please
-CTS has good precision and recall on average, though the precision or
-recall of a chunk retrieval run is very hard to predict from the given
-result. Therefore, retrieval output from CTS is suited to be read by a
-human. This could include semi-automated procedures such as sending
-developers an email with the extracted build failure reason.
-
-\subsubsection{Keyword Search (KWS)}
-\noindent
-\textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple
-structural categories present in the training and test examples. This
-makes KWS a good technique if there is little prior knowledge on how
-the targeted log chunk is represented in the build log. For the
-example of extracting the reason the build failed, KWS is best suited
-if a build can fail in various steps logged by different tools and no
-pre-categorization of where the build failed is available.
-
-Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the
-training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does
-improve the recall within our study but also increases the proportion
-of lines retrieved overall and therefore decreases precision.
-
-\noindent
-\textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its
-precision is the lowest. The output of a chunk retrieval with KWS is
-well-suited to be read by humans, but ill-suited for consumption by
-automated tools.
-
-\begin{figure}[tb]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
-		\label{fig:crt-recommendation}
-\end{figure}
-
-\subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we
-now want to unify our results into one recommendation scheme. In
-Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
-developers and researchers who want to retrieve information chunks
-from build logs can follow. The decision tree is built up of questions
-which either lead to more questions or to a leaf node containing a
-recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results
-from our comparison study. The recommendations could therefore be
-influenced by idiosyncrazies of our specific implementation of the
-chunk retrieval techniques as well as the logs in the \emph{LogChunks}
-data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
-answer to RQ2, about which criteria influence the suitability of a
-chunk retrieval technique. The earlier in the decision tree a
-criterion is noted, the more important it is when distinguishing the
-techniques.
-
-The first and most important aspect are the structural categories. Are
-the information chunks one would like to retrieve always presented in
-the same structural way within the build logs? Then the information
-chunks in all training examples and the analyzed build log are in the
-same structural category.
-
-If the information chunks are from multiple structural categories,
-i.e. they are not represented in the same structural way within the
-build logs, and recall is more important than precision we recommend
-to use KWS\@. If the representations are from multiple structural
-categories and precision is more important than recall to the user we
-recommend CTS\@. We also recommend CTS when the representations are
-from one structural category, when the user does not require a high
-confidence in the precision or recall of the outcome and when the user
-would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user
-wishes a high confidence in the correctness of the output or prefers
-no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper. Such a super analyzer would likely always first employ PBE
-(because of its high accuracy), followed by a combination of CTS and
-KWS. Other than initial setup and training time, there should be no
-downside to this approach if it is implemented in a transparent way to
-the underlying technique: the output of the super analyzer could
-include from which sub-tool it originated and thus facilitate
-automatic on-ward processing or interpretation of the result.
-
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable
-chunk retrieval technique we describe two concrete examples: a
-researcher investigating why CI builds fail and a software team
-wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI
-are caused by a small or by a large group of test cases. They gather
-CI build logs from various projects, which are their only available
-data source. The task of the researcher is to extract the names of the
-failing test cases from each build log. When they use our
-recommendation scheme to select a chunk retrieval technique, they
-first have to estimate how uniform the representation of the failing
-test cases is in the investigated build logs. As the researcher is
-covering a wide range of build tools and development languages, the
-log chunks they target are in various, non-predictable structural
-representations. The next question is whether they value precision
-over recall. As they have to manually inspect the results of both CTS
-and KWS, they choose recall over precision to avoid having to inspect
-the whole log in case the relevant information chunk was not
-retrieved. Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the
-retrieval results, they have to first separate the CI build logs
-according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they
-can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor
-the performance of the phases within their CI build. They are using
-Travis CI, which measures the duration of build phases and documents
-them within the build log. As all log statements that report timing
-measurements are formatted the same way, the targeted log chunks are
-from one structural category. Therefore the development team can use
-PBE to retrieve the duration of a build phase as well as its name.
-
-\section{Threats to Validity}
-There are several threats to the validity of the conclusions of our
-work.
-
-\noindent
-\textbf{Implementation}
-\label{sec:prose:impl}
-% TODO we need to say something about why we think that these
-% limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk
-retrieval techniques and the libraries we used. Our implementation of
-PBE is based on the program synthesis provided by PROSE\@. The
-idiosyncrazies of this framework influence our PBE results. Other
-frameworks similar to PROSE might have somewhat different strengths
-and weaknesses. For example, the need for examples from a single
-structural category stems from the fact that PROSE cannot learn
-regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}. PROSE introduced this constraint to
-keep the synthesis performance reasonable. At the same time, this is
-clearly a current theoretical challenge of all PBE implementations,
-and we therefore attribute it to the technique itself, rather than the
-specific implementation.
-
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec}
-and the way it splits strings into word tokens. On the other hand,
-{\tt text2vec} is the de-facto standard library to do word embeddings
-in R. We intentionally chose a simple, minimally configured and tuned
-approach to compare against. Tuning the text similarity
-meta-parameters more to the specific use case of chunk retrieval from
-build logs would yield better chunk retrieval results.
-
-\noindent
-\textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build
-logs from the \emph{LogChunks} data set. It only consists of build
-logs from open source projects and therefore it is not clear whether
-our results are generalizable to industry projects. We only collected
-build logs from Travis CI, however we chose to evaluate on an
-information chunk whose format is not dependent on Travis CI\@. This
-is because the reason the build failed is described within the build
-logs by the tools themselves and not the Travis CI environment.
-
-\noindent
-\textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples. We chose this small training set
-size as the training examples have to be provided per repository and
-we expect a developer to not want to provide more examples than the
-small numbers we evaluated on.
-
-\noindent
-\textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural
-categories than with one category.
-% TODO Caro: Please explain the following further. Why does a
-% realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in
-many cases has only one or few structural categories.
-
-\section{Future Work}
-\todo{survey build logs tools in industry}
-
-There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
-  \emph{LogChunks} data set \cite{} specifically for the comparative
-  study in this paper, though it can be the basis for various further
-  analyses of build log data. The keywords, for example, can be
-  investigated to answer which keywords are used to search for the
-  reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and
-  tested each chunk retrieval technique on examples from the same
-  repository. We propose to analyze how techniques could be trained
-  across repositories, building the cornerstones for build
-  environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
-  paper investigates the three chunk retrieval techniques PBE, CTS and
-  KWS\@. Our study design can be reused to evaluate other build log
-  analysis techniques, such as the diff and information retrieval
-  approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We
-  investigated basic configurations of existing techniques applied to
-  chunk retrieval from build logs. In a next step, each of these
-  techniques could be refined to better approach the domain of build
-  logs. The \emph{LogChunks} data set and our study results act as a
-  baseline to benchmark such technique improvements. We propose the
-  following improvements:
-    \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program
-      synthesis through PROSE ranks possible programs according to
-      what the user most likely intended. One could adapt the ranking
-      rules provided by the FlashExtract DSL to fit common build log
-      chunk retrieval tasks. FlashExtract includes special tokens when
-      enumerating possible regular expressions. One could extend these
-      with tokens found in build logs, such as ``-'',``='',``ERROR''
-      or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information
-      retrieval techniques have various meta-parameters which can be
-      optimized for the specific use
-      case~\cite{panichella2016parameterizing}. We propose to further
-      investigate improvements in preprocessing of the log text, in
-      tokenization of the log lines into terms and in stop words
-      lists.
-    \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
-  analysis of the output produced by the chunk retrieval focuses on
-  precision and recall. We propose to investigate how useful these
-  outputs are to developers through controlled experiments.
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in
-their decision on how to analyze build logs. We implemented and
-compared three different chunk retrieval techniques on our data set
-\emph{LogChunks}, composed of 797 manually labeled build logs from a
-broad range of 80 repositories. Our results show that the structural
-representation of the targeted information in the build logs is the
-main factor to consider when choosing a suitable technique. Secondary
-factors are the desired confidence into recall and precision of the
-produced output and whether precision or recall is more important for
-the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper.

### 2020-04-02 tse-paper/3-techniques.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
-
-\lstset{
-  morekeywords={},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{Plum},
-	frame=single,
-  extendedchars=false,
-  texcl=false,
-  aboveskip=\baselineskip,
-  belowskip=0pt
-}
-
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within the build.
-The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
-study.
-Our goal was to classify how and what for researchers use build logs as a source
-of data (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
-build tools.
-
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
-examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
-\end{itemize}
-\end{simplebox}
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
-  a regular expression matching the given chunks within the build logs.
-  \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
-  \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
-  the occurrence of specific trigger words.
-\end{itemize}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
-  \end{lstlisting}  
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}  
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary log chunks
-from Android/Gradle build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
-
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence. 
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
-  are present in the training examples.
-\end{itemize}
-
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
-%         \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
-%           \item a keyword search approach (KWS).
-%         \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
-
-We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
-recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Petersen's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO: update numbers
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool). many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
-work from system log analysis.
-
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of
-build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error
-types such as dependency mismatches are the most prominent cause of
-build failures at Google. In addition, they notice that most failures
-are resolved within two builds. They based their analyses on sets of
-build logs collected from industry partners. They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects and find that most builds fail because of failing
-tests. For most projects, over half of the failed builds follow a
-previous failed build. Rausch et al.'s data shows that most failures
-occur in the second half of the build runtime, which can cause long
-delays in the feedback loop, especially when builds are automatically
-retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones. They determine that testing failures are
-more common than compilation errors. Open source builds fail most
-often because of unit tests, whereas release preparations are the
-primary cause in industrial projects. Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data. They classify build failures from \emph{TravisTorrent}
-according to whether they were caused by an environmental failure or
-caused by a developer change. Their analysis starts with manual
-categorization of build logs. They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers
-presented in this section create parsers and regular expression-based
-programs. This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article. Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve. By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why
-their build failed. Several researchers investigate how to support
-developers in working with verbose build logs. Vassallo et
-al.~\cite{vassallo2018un-break} try to shorten the time it takes
-developers to understand build logs. They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-%The hint generators leverage this structured access to the
-%information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed. In a qualitative study
-they observed that highlighting the locality and context of an issue
-is helpful to programmers.
-%Their tool BART is published as a Jenkins
-%Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs. As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect. Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures. Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a
-basic structuring of the build logs within their log viewer using
-\emph{log folds}~\cite{travis2019logfolds}. They add fold identifiers
-around common commands and setup or teardown build phases and collapse
-the contained lines by default.
-
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log
-files produced during runtime. A main difference between build logs
-and system logs is that system logs are fundamentally structured
-through events. Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}. Figure \ref{lst:system-log} shows
-example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to
-separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}. Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters. The output of a log
-parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}. This structured log is then
-the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational
-%profiling~\cite{nagappan2009efficiently},
-%debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}. Xu et
-%al.~\cite{xu2009detecting} leverage the connection of log statements
-%to the source code producing them to separate messages into constant
-%and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied
-to build logs. One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies. Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of
-%events. A similar approach could also be applied to build logs to
-%determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques. Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g. by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
-  \end{lstlisting}  
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques} The
-% techniques we investigate are based on existing methods of
-% Programming by Example.%, information extraction and information
-% retrieval. This section presents different Programming by Example
-% resources surrounding the PROSE library. We explain its generic
-% program synthesis algorithm and how PROSE synthesizes text
-% extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program
-synthesis that enables users to automate repetitive tasks, without
-them having to explicitly codify a computer program. One has to
-provide prototypical examples of the input and the desired output. A
-synthesis algorithm tries to create a program (based on a regular
-language) that transforms the input to the output. The minimum working
-condition is for this when replayed on the examples inputs is to
-provide the specified output, but, hopefully, PBE is as close as
-possbile to the user's intention and thus also works on a different
-and larger set of inputs. This section introduces the theoretical
-foundations of the program synthesis algorithm of the \emph{PROgram
-Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research. Next, this
-section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our
-chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and
-Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
-synthesis in the Microsoft PROSE framework. FlashMeta separates the
-inductive synthesis algorithm from the domain specific capabilities of
-the desired program by encoding the possible program space in a domain
-specific language (DSL). The user specifies the desired program
-behavior by providing in/output examples (I/O examples). FlashMeta
-uses \emph{witness functions}, provided by the DSL, to divide the
-synthesis into smaller subtasks. For each of these subtasks it
-enumerates all possible programs that solve the subtask consistent
-with the set of I/O examples. A program is consistent with a set of
-I/O examples if, for each input example, it produces the corresponding
-output~\cite{mitchell1982generalization}. The possible subprograms are
-joined and stored in a \emph{version space algebra}
-(VSA)~\cite{mitchell1982generalization}. This a tree structure, which
-space-efficiently saves candidate programs for tasks by sharing common
-subexpressions. Next, FlashMeta ranks the enumerated programs
-according to which ones the user most likely intended. The DSL also
-provides the ranking characteristics. From the ranked VSA, FlashMeta
-can then return a ranked list of complete programs consistent with the
-user's example.
-
-% In addition to I/O examples of the intended program, the user can
-% also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized
-% program.
-
-% The different applications of PROSE presented in the following
-% paragraphs were all eventually implemented as DSLs for the FlashMeta
-% synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
-for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text,
-% websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs
-from semi-structured text based on regular expressions. Users can
-extract multiple fields and structure them with hierarchy and
-sequence.
-% FlashExtract synthesizes programs to extract each of the fields
-% leveraging the information about hierarchical containment and
-% sequentiality. It eliminates the need for the user to understand the
-% entire structure of the processed document and decreases the effort
-% of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of
-two cut positions. A position is either specified by an absolute
-character index or by a pair of two regular expressions. The first
-regular expression matches the substring directly before the
-characterized position, the second regular expression matches the
-substring directly after. A regular expression in FlashExtract is a
-concatenation of tokens, e.g.\ standard character classes or string
-literals frequently occurring in the input examples. Figure
-\ref{lst:prose-program} shows a text extraction program synthesized by
-FlashExtract. This program defines the first position as after a colon
-followed by a newline character and before a piece of text with all
-capital letters. It defines the second position as before two newline
-characters.
-
-Apart from automatic completion in Excel
-spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for
-two other Microsoft product features: Microsoft's system log analysis
-tool Azure Monitor lets users define custom log
-fields~\cite{azure2019custom}. The ConvertFrom-String function in
-PowerShell allows a user to specify an example template to extract
-hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build
-logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
 \section{Chunk Retrieval Techniques}
@@
 R and the text2vec library~\cite{text2vec2019webpage}.
-
-\section{Study Design}
-\label{sec:study}
-
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-To investigate which techqnique is best suited to retrieve chunks from
-CI build logs we evaluate them on the
-\emph{LogChunks}~\cite{brandt2020logchunks} data set. This section
-describes our study design and which metrics we measure to answer our
-research questions. In the presentation of the results, we first focus
-on each of the three techniques and later compare them against each
-other.
-
-\subsection{LogChunks}
-For this study we created the previously published data set
-\emph{LogChunks}. It encompasses 797 build logs from Travis CI,
-stemming from a broad range of 80 GitHub repositories and 29
-programming languages. For each file, the authors manually ``labeled
-the log part (chunk) describing why the build
-failed''~\cite{brandt2020logchunks}. We include keywords, which we
-would use to search for the selected chunk within the log. In
-addition, we categorized the log chunks according to their format
-within the log. If the chunks are surrounded by the same markings
-within the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}. Random Line Retrieval
-(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
-the comparison.
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study. For each of the
-80 repositories in it, \emph{LogChunks} contains 10 build logs,
-manually labeled with the \emph{chunk} describing the
-reason the build failed. Additionally, it contains (1) keywords useful
-to identify the substring in the log  and (2) which structural category
-the substring belongs to.
-% TODO Moritz: You said: Add details how key words were extracted. Add example?
-% how the keywords were put in logchunks does not fit here, that is
-% maybe answered 2 paragraphs above already?
-% how KWS uses the keywords is already described in the section
-% introducing the technique => I would scrap everything but the first
-% sentence directly above here :)
-
-% TODO Moritz: You said: Add more details. How was the split in numbers?
-% this is described in the following paragraph, should we merge them
-% (bc there are also no sub-RQs now) or is it close enough? :)
-For each repository in \emph{LogChunks}, we split the examples
-chronologically into training and test set. Therefore, we train on
-examples from past build logs and test on more recent build logs.
-
-\noindent % TODO: adapt if we change the research questions
-\textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to
-perform best, we evaluate the techniques with different training set
-sizes. We train each technique with one to five examples from each of
-the repositories within \emph{LogChunks}. The size of the test set is
-one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk
-retrieval techniques need to be, we record the structural categories
-of the examples in the training and test sets.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output
-lines of the chunk retrieval run on the input of the test example
-($\mathit{RetrievedLines}$). As oracle in our evaluation, we save the
-desired lines from the output of the test example
-($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our
-evaluation.
-
-\vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm] \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap
-	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a
-        tool as well as what \textit{LogChunks} contains for each
-        example. 
-        % What about when a line is replicated twice?
-        % I.e., Are line numbers part of this? => no.
-        % not checked, but if lines are identical they also contain
-        % the same information so if someone asks we can defend I think
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\
-	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of
-        the retrieved lines were actually desired. 
-	\item $\mbox{Recall} =
-	\dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$
-	\vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the
-        desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
-	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
-	\vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean
-        of precision and recall. We prefer F$_{1}$ to other aggregate
-        measures such as accuracy because for a
-        ``needle-in-the-haystack'' scenario, we do not want to bloat
-        our results by correctly not finding lots of irrelevant log
-        lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
-	We define a successful retrieval as one where all desired lines were
-	extracted, therefore when recall is one.
-\end{itemize}
-
-% Recall and precision of CTS and KWS vary with the number of lines
-% selected for retrieval. We evaluate the effect of varying the number
-% of extracted lines by multiplying the average number of lines
-% present in the training examples with a \emph{retrieval size factor}
-% from 0.5 to 2.5 in steps of 0.5.
-
-\section{Results}
-This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as
-baseline.
-
-\lstset{
-  language=,
-  morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass   
-Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass
-        from line 5 of sass/components/_all.sass
-        from line 6 of bulma.sass
-  \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
-  \label{lst:pbe-unsuccessful}
-\end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:r:cts}
-\begin{figure*}
-\centering
-    \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-CTS}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-CTS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-CTS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using CTS for an
-increasing number of training examples. When using one to five
-training examples, the size of the training set has no noticeable
-influence on precision, recall or F$_{1}$-score of the chunk retrieval
-with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. With increasing category count, precision,
-recall and F$_{1}$-score decrease. Especially for more than three
-categories present we have no chunk retrieval runs where all desired
-lines were extracted.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:r:kws}
-\begin{figure*}
-\centering
-    \textbf{Keyword Search (KWS)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-KWS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-KWS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using KWS for different
-numbers of training examples. The recall increases by about 12\% when
-increasing the size of the training set to more than one example,
-while the precision stays constant at around 16\%. The F$_{1}$-score
-stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. For more than one structural category in
-the training and test examples the recall decreases by about 20\% and
-the precision decreases about 6\%. For more than two structural
-categories no clear trend is visible in precision, recall or
-F$_{1}$-score for an increasing amount of categories in the training
-and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the
-% effect of the retrieval size factor on precision, recall and
-% F$_{1}$-score of chunk retrieval runs with KWS\@. The precision is
-% 19\% when retrieving half of the expected number of lines. On
-% average 9\% of the lines in the build log are retrieved then. When
-% 2.5 times the expected number of lines are retrieved, the precision
-% decreases to 10\% and a quarter of the lines in the build log are
-% retrieved on average. The recall ranges from 58\% to 75\% and the
-% F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-% 		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
-                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
-                \label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
-evaluation. Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines in 138 cases. In 89 further
-cases, an extraction program was also successfully synthesized, though
-in 59 of the 89 cases the synthesized program yielded no output. In 30
-of the 89 cases did the synthesized program only partially extract a
-subset of the desired lines. For these 30 cases, the average recall
-was 28\%. Listing \ref{lst:pbe-unsuccessful} shows an example of such
-an \emph{unsuccessful retrieval}, where the synthesized program only
-retrieved two of the four targeted lines. In 173 of the 400 cases
-could PROSE not synthesize program consistent with all of the training
-examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
-runs depend on the number of structural categories in the training and
-test examples. The figure demonstrates that program synthesis mostly
-returns exactly the desired output when there are is only one
-structural category present in the training examples. However, when
-two or more structural categories are simultaneously present in the
-examlpe set, PROSE could in most cases not synthesize a program
-consistent with all training examples. For four or more present
-categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
-precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples. When the training set
-size increases from one to two, recall and F$_{1}$-score increase by
-about 25\%, precision increases by about 10\%. For two or more
-training examples, recall and F$_{1}$-score stay around 75\% and
-precision around 96\%.
-
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we compare against a baseline of randomly
-picking lines from the build log. Its results follow intuitive
-expectations:
-The precision ranges between 8\% and 5\%, the recall between 6\% and
-8\%. The size of the training set has no visible impact on either.
-An greater number of structural categories within the training and
-test sets decreased the precision of RLR from 7\% to 0\%, the recall
-increases from 6\%, for one structural category present, to 11\%, for
-three sturctural categories present and also drops to 0\% for more
-structural categories.
-Graphs of the results of the chunk retrieval with RLR from our study
-are included in our replication package~\cite{brandt2020chunk-replication}.
-
-\subsection{Comparison of All Techniques}
-In this section, we aggregate the results from
-\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it
-each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk
-retrievals differentiated by techniques in our study. CTS and KWS
-extract some of the desired lines in 79\% and 88.5\% of the chunk
-retrieval runs. With 38.25\%, KWS also has the highest number of fully
-successful extractions, followed by PBE with 34.5\%. PBE has the
-lowest number of partial retrievals with only 18 out of 400 chunk
-retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is
-% compared in Figure~\ref{fig:recall-precision-all}. The recall of PBE
-% has a high skew towards one and zero, meaning in most cases either
-% the retrieval is successful or no relevant lines are extracted at
-% all. PBE has the highest average precision with 95\%. Chunk
-% retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% and the second highest recall with 46\%. KWS has the smallest
-% precision of the three chunk retrieval techniques. With 16\% it is
-% still higher than the precision of the RLR baseline with 7\%. KWS
-% has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of a single structural category present in the
-training examples compared to multiple categories present. For more
-than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by
-the number of structural categories present.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
-		\label{fig:success-partial-all}
-\end{figure}
-
-\begin{figure*}
-\centering
-    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
-		\label{fig:recall-precision-singlecategory-all}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
-		\label{fig:recall-precision-multicategory-all}
-\end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% TODO update RQs
-% TODO incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}  
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
-\end{itemize}
-\end{simplebox}
-
-The first section discusses for PBE, CTS and KWS separately in which
-cases they perform best. It details for which types of input build
-logs, available training examples and consumption of the retrieved
-output each technique is suited. In the following section we discuss
-which of these criteria should influence the decision to use a certain
-technique most. Based on our empirical comparison, we present a
-decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed
-chunk retrieval techniques separately. It gives recommendations which
-kind of information chunk targets are best for each technique and for
-what kind of usage the respective output is suitable.
-
-\begin{table}[tbp]
-\resizebox{\columnwidth}{!}{%
-\centering
-\begin{tabular}{llll}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabular}%
-}
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\subsubsection{Program Synthesis by Example (PBE)}
-
-\noindent
-\textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best
-results when the training examples are structurally identical. This is
-because PROSE has difficulty synthesizing OR-based programs (see
-\Cref{sec:prose:impl}). PBE is thus suited to retrieve information
-chunks that always have the same surrounding or defining internal
-structure. To extract for example the reason a build failed, the log
-passage describing the failure would always have to be started and
-ended the same way.
-
-When the training examples are of the same structure, even one or two
-two examples are enough input for PROSE to synthesize a regular
-expression program with good recall. In our study, additional training
-examples did not improve the chunk retrieval. In fact, unless they
-were in some sense redudant, adding training examples above that even
-hindered the applicability of PBE.
-
-\noindent
-\textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression
-program yields an output, PBE has high precision and recall. The tool
-clearly identifies a failing program synthesis or when no output from
-the program applied to a build log is obtained. Therefore, if there is
-an output, the user can have high confidence that it is the desired
-output. This preciseness makes output from PBE chunk retrieval
-well-suited for machine consumption.
-
-\subsubsection{Common Text Similarity (CTS)}
-\noindent
-\textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the
-fewer structural categories are present in the training and test
-examples.
-
-The number of training examples had no noticeable influence on
-precision or recall in our study. Information retrieval techniques
-like text similarity commonly learn on a higher number of examples
-than used for our study. Future work is needed to investigate how many
-examples yield improvements in the chunk retrieval over a single
-training example.
-
-\noindent
-\textbf{Retrieval Output Usage}
-CTS has good precision and recall on average, though with a high
-variation. This means that the quality of an output by CTS is hard to
-determine, which makes it unsuited for automatic  processing and requires a human to further inspect and interpret the output. This could include semi-automated procedures such as sending
-developers an email with the extracted build failure reason.
-
-\subsubsection{Keyword Search (KWS)}
-\noindent
-\textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple
-structural categories present in the training and test examples. This
-makes KWS a good technique if there is little prior knowledge on how
-the targeted log chunk is represented in the build log. For the
-example of extracting the reason the build failed, KWS is best suited
-if a build can fail in various steps logged by different tools and no
-pre-categorization of where the build failed is available.
-
-Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the
-training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does
-improve the recall within our study but also increases the proportion
-of lines retrieved overall and therefore decreases precision.
-
-\noindent
-\textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its
-precision is the lowest. The output of a chunk retrieval with KWS is
-well-suited to be read by humans, but ill-suited for consumption by
-automated tools.
-
-\begin{figure}[tb]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
-		\label{fig:crt-recommendation}
-\end{figure}
-
-\subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we
-now want to unify our results into one recommendation scheme. In
-Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
-developers and researchers who want to retrieve information chunks
-from build logs can follow. The decision tree is built up of questions
-which either lead to more questions or to a leaf node containing a
-recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results
-from our comparison study. The recommendations could therefore be
-influenced by idiosyncrazies of our specific implementation of the
-chunk retrieval techniques as well as the logs in the \emph{LogChunks}
-data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
-answer to RQ2, about which criteria influence the suitability of a
-chunk retrieval technique. The earlier in the decision tree a
-criterion is noted, the more important it is when distinguishing the
-techniques.
-
-The first and most important aspect are the structural categories. Are
-the information chunks one would like to retrieve always presented in
-the same structural way within the build logs? Then the information
-chunks in all training examples and the analyzed build log are in the
-same structural category.
-
-If the information chunks are from multiple structural categories,
-i.e. they are not represented in the same structural way within the
-build logs, and recall is more important than precision we recommend
-to use KWS\@. If the representations are from multiple structural
-categories and precision is more important than recall to the user we
-recommend CTS\@. We also recommend CTS when the representations are
-from one structural category, when the user does not require a high
-confidence in the precision or recall of the outcome and when the user
-would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user
-wishes a high confidence in the correctness of the output or prefers
-no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper. Such a super analyzer would likely always first employ PBE
-(because of its high accuracy), followed by a combination of CTS and
-KWS. Other than initial setup and training time, there should be no
-downside to this approach if it is implemented in a transparent way to
-the underlying technique: the output of the super analyzer could
-include from which sub-tool it originated and thus facilitate
-automatic on-ward processing or interpretation of the result.
-
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable
-chunk retrieval technique we describe two concrete examples: a
-researcher investigating why CI builds fail and a software team
-wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI
-are caused by a small or by a large group of test cases. They gather
-CI build logs from various projects, which are their only available
-data source. The task of the researcher is to extract the names of the
-failing test cases from each build log. When they use our
-recommendation scheme to select a chunk retrieval technique, they
-first have to estimate how uniform the representation of the failing
-test cases is in the investigated build logs. As the researcher is
-covering a wide range of build tools and development languages, the
-log chunks they target are in various, non-predictable structural
-representations. The next question is whether they value precision
-over recall. As they have to manually inspect the results of both CTS
-and KWS, they choose recall over precision to avoid having to inspect
-the whole log in case the relevant information chunk was not
-retrieved. Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the
-retrieval results, they have to first separate the CI build logs
-according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they
-can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor
-the performance of the phases within their CI build. They are using
-Travis CI, which measures the duration of build phases and documents
-them within the build log. As all log statements that report timing
-measurements are formatted the same way, the targeted log chunks are
-from one structural category. Therefore the development team can use
-PBE to retrieve the duration of a build phase as well as its name.
-
-\section{Threats to Validity}
-There are several threats to the validity of the conclusions of our
-work.
-
-\noindent
-\textbf{Implementation}
-\label{sec:prose:impl}
-% TODO we need to say something about why we think that these
-% limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk
-retrieval techniques and the libraries we used. Our implementation of
-PBE is based on the program synthesis provided by PROSE\@. The
-idiosyncrazies of this framework influence our PBE results. Other
-frameworks similar to PROSE might have somewhat different strengths
-and weaknesses. For example, the need for examples from a single
-structural category stems from the fact that PROSE cannot learn
-regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}. PROSE introduced this constraint to
-keep the synthesis performance reasonable. At the same time, this is
-clearly a current theoretical challenge of all PBE implementations,
-and we therefore attribute it to the technique itself, rather than the
-specific implementation.
-
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec}
-and the way it splits strings into word tokens. On the other hand,
-{\tt text2vec} is the de-facto standard library to do word embeddings
-in R. We intentionally chose a simple, minimally configured and tuned
-approach to compare against. Tuning the text similarity
-meta-parameters more to the specific use case of chunk retrieval from
-build logs would yield better chunk retrieval results.
-
-\noindent
-\textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build
-logs from the \emph{LogChunks} data set. It only consists of build
-logs from open source projects and therefore it is not clear whether
-our results are generalizable to industry projects. We only collected
-build logs from Travis CI, however we chose to evaluate on an
-information chunk whose format is not dependent on Travis CI\@. This
-is because the reason the build failed is described within the build
-logs by the tools themselves and not the Travis CI environment.
-
-\noindent
-\textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples. We chose this small training set
-size as the training examples have to be provided per repository and
-we expect a developer to not want to provide more examples than the
-small numbers we evaluated on.
-
-\noindent
-\textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural
-categories than with one category.
-% TODO Caro: Please explain the following further. Why does a
-% realistic data set only have one or few structural categories?
-This stems from the fact that we investigated the chunk retrieval
-techniques on a realistic data set, which showed to often have few
-structural categories within one project.
-
-\section{Future Work}
-\todo{survey build logs tools in industry}
-
-There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
-  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for the comparative
-  study in this paper, though it can be the basis for various further
-  analyses of build log data. The keywords, for example, can be
-  investigated to answer which keywords are used to search for the
-  reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and
-  tested each chunk retrieval technique on examples from the same
-  repository. We propose to analyze how techniques could be trained
-  across repositories, building the cornerstones for build
-  environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
-  paper investigates the three chunk retrieval techniques PBE, CTS and
-  KWS\@. Our study design can be reused to evaluate other build log
-  analysis techniques, such as the diff and information retrieval
-  approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We
-  investigated basic configurations of existing techniques applied to
-  chunk retrieval from build logs. In a next step, each of these
-  techniques could be refined to better approach the domain of build
-  logs. The \emph{LogChunks} data set and our study results act as a
-  baseline to benchmark such technique improvements. We propose the
-  following improvements:
-    \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program
-      synthesis through PROSE ranks possible programs according to
-      what the user most likely intended. One could adapt the ranking
-      rules provided by the FlashExtract DSL to fit common build log
-      chunk retrieval tasks. FlashExtract includes special tokens when
-      enumerating possible regular expressions. One could extend these
-      with tokens found in build logs, such as ``-'',``='',``ERROR''
-      or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information
-      retrieval techniques have various meta-parameters which can be
-      optimized for the specific use
-      case~\cite{panichella2016parameterizing}. We propose to further
-      investigate improvements in preprocessing of the log text, in
-      tokenization of the log lines into terms and in stop words
-      lists.
-    \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
-  analysis of the output produced by the chunk retrieval focuses on
-  precision and recall. We propose to investigate how useful these
-  outputs are to developers through controlled experiments.
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in
-their decision on how to analyze build logs. We implemented and
-compared three different chunk retrieval techniques on our data set
-\emph{LogChunks}, composed of 797 manually labeled build logs from a
-broad range of 80 repositories. Our results show that the structural
-representation of the targeted information in the build logs is the
-main factor to consider when choosing a suitable technique. Secondary
-factors are the desired confidence into recall and precision of the
-produced output and whether precision or recall is more important for
-the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper.

### 2020-04-02 tse-paper/4-study-design.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
-
-\lstset{
-  morekeywords={},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{Plum},
-	frame=single,
-  extendedchars=false,
-  texcl=false,
-  aboveskip=\baselineskip,
-  belowskip=0pt
-}
-
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within the build.
-The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
-study.
-Our goal was to classify how and what for researchers use build logs as a source
-of data (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
-build tools.
-
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
-examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
-\end{itemize}
-\end{simplebox}
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
-  a regular expression matching the given chunks within the build logs.
-  \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
-  \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
-  the occurrence of specific trigger words.
-\end{itemize}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
-  \end{lstlisting}  
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}  
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary log chunks
-from Android/Gradle build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
-
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence. 
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
-  are present in the training examples.
-\end{itemize}
-
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
-%         \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
-%           \item a keyword search approach (KWS).
-%         \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
-
-We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
-recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Petersen's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO: update numbers
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool). many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
-work from system log analysis.
-
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of
-build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error
-types such as dependency mismatches are the most prominent cause of
-build failures at Google. In addition, they notice that most failures
-are resolved within two builds. They based their analyses on sets of
-build logs collected from industry partners. They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects and find that most builds fail because of failing
-tests. For most projects, over half of the failed builds follow a
-previous failed build. Rausch et al.'s data shows that most failures
-occur in the second half of the build runtime, which can cause long
-delays in the feedback loop, especially when builds are automatically
-retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones. They determine that testing failures are
-more common than compilation errors. Open source builds fail most
-often because of unit tests, whereas release preparations are the
-primary cause in industrial projects. Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data. They classify build failures from \emph{TravisTorrent}
-according to whether they were caused by an environmental failure or
-caused by a developer change. Their analysis starts with manual
-categorization of build logs. They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers
-presented in this section create parsers and regular expression-based
-programs. This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article. Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve. By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why
-their build failed. Several researchers investigate how to support
-developers in working with verbose build logs. Vassallo et
-al.~\cite{vassallo2018un-break} try to shorten the time it takes
-developers to understand build logs. They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-%The hint generators leverage this structured access to the
-%information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed. In a qualitative study
-they observed that highlighting the locality and context of an issue
-is helpful to programmers.
-%Their tool BART is published as a Jenkins
-%Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs. As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect. Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures. Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a
-basic structuring of the build logs within their log viewer using
-\emph{log folds}~\cite{travis2019logfolds}. They add fold identifiers
-around common commands and setup or teardown build phases and collapse
-the contained lines by default.
-
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log
-files produced during runtime. A main difference between build logs
-and system logs is that system logs are fundamentally structured
-through events. Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}. Figure \ref{lst:system-log} shows
-example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to
-separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}. Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters. The output of a log
-parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}. This structured log is then
-the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational
-%profiling~\cite{nagappan2009efficiently},
-%debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}. Xu et
-%al.~\cite{xu2009detecting} leverage the connection of log statements
-%to the source code producing them to separate messages into constant
-%and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied
-to build logs. One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies. Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of
-%events. A similar approach could also be applied to build logs to
-%determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques. Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g. by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
-  \end{lstlisting}  
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques} The
-% techniques we investigate are based on existing methods of
-% Programming by Example.%, information extraction and information
-% retrieval. This section presents different Programming by Example
-% resources surrounding the PROSE library. We explain its generic
-% program synthesis algorithm and how PROSE synthesizes text
-% extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program
-synthesis that enables users to automate repetitive tasks, without
-them having to explicitly codify a computer program. One has to
-provide prototypical examples of the input and the desired output. A
-synthesis algorithm tries to create a program (based on a regular
-language) that transforms the input to the output. The minimum working
-condition is for this when replayed on the examples inputs is to
-provide the specified output, but, hopefully, PBE is as close as
-possbile to the user's intention and thus also works on a different
-and larger set of inputs. This section introduces the theoretical
-foundations of the program synthesis algorithm of the \emph{PROgram
-Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research. Next, this
-section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our
-chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and
-Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
-synthesis in the Microsoft PROSE framework. FlashMeta separates the
-inductive synthesis algorithm from the domain specific capabilities of
-the desired program by encoding the possible program space in a domain
-specific language (DSL). The user specifies the desired program
-behavior by providing in/output examples (I/O examples). FlashMeta
-uses \emph{witness functions}, provided by the DSL, to divide the
-synthesis into smaller subtasks. For each of these subtasks it
-enumerates all possible programs that solve the subtask consistent
-with the set of I/O examples. A program is consistent with a set of
-I/O examples if, for each input example, it produces the corresponding
-output~\cite{mitchell1982generalization}. The possible subprograms are
-joined and stored in a \emph{version space algebra}
-(VSA)~\cite{mitchell1982generalization}. This a tree structure, which
-space-efficiently saves candidate programs for tasks by sharing common
-subexpressions. Next, FlashMeta ranks the enumerated programs
-according to which ones the user most likely intended. The DSL also
-provides the ranking characteristics. From the ranked VSA, FlashMeta
-can then return a ranked list of complete programs consistent with the
-user's example.
-
-% In addition to I/O examples of the intended program, the user can
-% also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized
-% program.
-
-% The different applications of PROSE presented in the following
-% paragraphs were all eventually implemented as DSLs for the FlashMeta
-% synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
-for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text,
-% websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs
-from semi-structured text based on regular expressions. Users can
-extract multiple fields and structure them with hierarchy and
-sequence.
-% FlashExtract synthesizes programs to extract each of the fields
-% leveraging the information about hierarchical containment and
-% sequentiality. It eliminates the need for the user to understand the
-% entire structure of the processed document and decreases the effort
-% of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of
-two cut positions. A position is either specified by an absolute
-character index or by a pair of two regular expressions. The first
-regular expression matches the substring directly before the
-characterized position, the second regular expression matches the
-substring directly after. A regular expression in FlashExtract is a
-concatenation of tokens, e.g.\ standard character classes or string
-literals frequently occurring in the input examples. Figure
-\ref{lst:prose-program} shows a text extraction program synthesized by
-FlashExtract. This program defines the first position as after a colon
-followed by a newline character and before a piece of text with all
-capital letters. It defines the second position as before two newline
-characters.
-
-Apart from automatic completion in Excel
-spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for
-two other Microsoft product features: Microsoft's system log analysis
-tool Azure Monitor lets users define custom log
-fields~\cite{azure2019custom}. The ConvertFrom-String function in
-PowerShell allows a user to specify an example template to extract
-hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build
-logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
-\section{Chunk Retrieval Techniques}
-\label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval
-techniques we study in this article, namely program synthesis by
-example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that
-represent a specific, targeted information.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically
-retrieve pieces of information that appear literally in the build
-logs, i.e., techniques that do not aggreagte, combine, or deducted
-information. We call such pieces of information from build logs
-\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and
-parser to analyze the entire structure of build logs, but focus on
-ad-hoc extracting just one specific piece of information per
-configuration.
-
-With the term \textit{configuration,} we abstract over the training
-and parametrization that different techniques require in different
-forms. A configuration can be explicitly stated or implicitly dervied
-by learning through provided examples. It is therefore a manual
-specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log. Each chunk
-retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word). The
-granularity might be adjustable by configuration. \emph{Running a
-chunk retrieval technique} means to execute a fully configured
-technique to consumes as input a build log in plain text format and to
-produce an array as output. The array consists of substrings of the
-build log text.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[]
-\centering
-\caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
-\toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
-\bottomrule
-\end{tabularx}
-\label{tab:ctr}
-\end{table*}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes
-% programs according to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming
-% knowledge~\cite{mayer2015user}. In the context of text extraction
-% through regular expressions, Programming by Example relieves the
-% developer from having to understand the whole document structure to
-% solve a single extraction task~\cite{le2014flashextract:}. In this
-% work, we refer to our interpretation of Programming by Example as
-% \emph{PBE}\@. We investigate the suitability of PBE to retrieve
-% information chunks from build logs. In the following, we explain the
-% configuration and application of PBE to chunk retrieval from CI
-% build logs.
-
-% TODO later: we should make sure to at least mention PROSE
-% _somewhere_, it's crucial for why PBE is how it is
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by
-Example, we refer to them in short as \emph{examples}. The
-\emph{input} is the text of the build log file. The \emph{output} is
-an array of substrings of the log file text, representing the
-substrings that should be retrieved by the synthesized program when
-given the corresponding input file. One or multiple examples, the
-training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted. The
-PROSE program synthesis then tries to construct a program consistent
-with all training examples.
-% A program is consistent with an example if it returns the defined
-% output when executed on the defined
-% input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a
-consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn
-% uses the FlashMeta algorithm. Both are described in
-% Section~\ref{sec:rw-prose}.
-
-% TODO Moritz: you said: The following is very obvious and could apply to any
-% technique. 
-% kinda. It does give a descriptive error message on no match (and
-% that is not possible in other techniques)
-% otherwise yes, nothing interesting happens in the application of pbe
-% though for consistency we might need this section? or merge config/application?
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the
-synthesized regular expression program. It then returns the substring
-of the build log matched by the program or an error message if the
-program found no match.
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual
-% software
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model. We
-% investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs. In the following we will explain
-% the concept of how we apply text similarity to information retrieval
-% from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use
-the same concept of examples as for PBE
-% TODO Moritz: your question was: More details on this. How do you
-% 'apply' VSM? On what?
-% all the following sentences in this subsubsection describe our way
-% of determining text similarity which as far as I understand and
-% Annibale said is the VSM. word tokens, tf-idf, similarity measure
-% I added a "as follows", think that is enough for explanation? 
-and apply the Vector Space Model~\cite{schutze2008introduction} as follows. The
-lines of the output strings of the training examples define our search
-query. The algorithm splits the search query into single lines and
-identifies tokens, in our case words. Then we build a
-document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words. Finally, the
-algorithm applies TF-IDF to the matrix, a best practice for natural
-language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the output of the
-training examples. The algorithm calculates the cosine
-similarity~\cite{korenius2007principal} to compare each line of the
-build log with each line of the search query. After summing up the
-similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity. The average number of
-lines in the outputs of the training examples determines how many of
-the most similar lines are returned as the output of the retrieval
-run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad-hoc approach they
-use is to search for related keywords. Indeed, this was one of the
-most common approaches we took when searching for the reason the build
-failed within a log while creating the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers
-% use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs. In
-% the following we will explain how we use simple keyword search to
-% retrieve information from CI build logs, which we refer to as
-% \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@. To better
-compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted
-chunk or close to it. 
-KWS then searches for those keywords which are tied to the greatest
-number of examples in the training set.
-If several keywords are associated with the same number of training
-examples, and no other keywords are associated with more training
-examples, KWS searches for all of these keywords.
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords. As keywords are
-often not directly describing the desired information, but rather
-appear close to the desired information, KWS also retrieves the lines
-around the found keyword. The number of surrounding lines retrieved is
-the average of lines in the output of the training examples.
-
-\subsection{Random Line Retrieval}
-\label{sec:expl-rlr}
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. RLR essentially mimicks the
-situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should
-return. For a fair comparison to the other techniques (whose number of
-returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples. 
-% TODO Moritz: you said: some more details here?
-% I would not know of any details to add. It's really all we are doing
-
-\subsection{Other Techniques}
-%Literature mentions further build log analysis techniques. This
-%section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information
-retrieval to identify relevant lines from a failed build
-log~\cite{amar2019mining}, as we describe in more detail in
-Section~\ref{sec:rw-bl-analysis}. The configuration for the technique
-is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not
-present in the successful build log and contain terms related to the
-given past failures.
-
-% TODO: we could add more techniques from the lit. survey here
-
-\subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a
-unifying interface. The unified interface is implemented in Ruby and
-calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE
-library~\cite{prose2019webpage}. We implemented CTS, KWS and RLR using
-R and the text2vec library~\cite{text2vec2019webpage}.
-
 \section{Study Design}
@@
 % from 0.5 to 2.5 in steps of 0.5.
-
-\section{Results}
-This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as
-baseline.
-
-\lstset{
-  language=,
-  morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass   
-Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass
-        from line 5 of sass/components/_all.sass
-        from line 6 of bulma.sass
-  \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
-  \label{lst:pbe-unsuccessful}
-\end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:r:cts}
-\begin{figure*}
-\centering
-    \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-CTS}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-CTS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-CTS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using CTS for an
-increasing number of training examples. When using one to five
-training examples, the size of the training set has no noticeable
-influence on precision, recall or F$_{1}$-score of the chunk retrieval
-with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. With increasing category count, precision,
-recall and F$_{1}$-score decrease. Especially for more than three
-categories present we have no chunk retrieval runs where all desired
-lines were extracted.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:r:kws}
-\begin{figure*}
-\centering
-    \textbf{Keyword Search (KWS)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-KWS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-KWS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using KWS for different
-numbers of training examples. The recall increases by about 12\% when
-increasing the size of the training set to more than one example,
-while the precision stays constant at around 16\%. The F$_{1}$-score
-stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. For more than one structural category in
-the training and test examples the recall decreases by about 20\% and
-the precision decreases about 6\%. For more than two structural
-categories no clear trend is visible in precision, recall or
-F$_{1}$-score for an increasing amount of categories in the training
-and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the
-% effect of the retrieval size factor on precision, recall and
-% F$_{1}$-score of chunk retrieval runs with KWS\@. The precision is
-% 19\% when retrieving half of the expected number of lines. On
-% average 9\% of the lines in the build log are retrieved then. When
-% 2.5 times the expected number of lines are retrieved, the precision
-% decreases to 10\% and a quarter of the lines in the build log are
-% retrieved on average. The recall ranges from 58\% to 75\% and the
-% F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-% 		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
-                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
-                \label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
-evaluation. Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines in 138 cases. In 89 further
-cases, an extraction program was also successfully synthesized, though
-in 59 of the 89 cases the synthesized program yielded no output. In 30
-of the 89 cases did the synthesized program only partially extract a
-subset of the desired lines. For these 30 cases, the average recall
-was 28\%. Listing \ref{lst:pbe-unsuccessful} shows an example of such
-an \emph{unsuccessful retrieval}, where the synthesized program only
-retrieved two of the four targeted lines. In 173 of the 400 cases
-could PROSE not synthesize program consistent with all of the training
-examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
-runs depend on the number of structural categories in the training and
-test examples. The figure demonstrates that program synthesis mostly
-returns exactly the desired output when there are is only one
-structural category present in the training examples. However, when
-two or more structural categories are simultaneously present in the
-examlpe set, PROSE could in most cases not synthesize a program
-consistent with all training examples. For four or more present
-categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
-precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples. When the training set
-size increases from one to two, recall and F$_{1}$-score increase by
-about 25\%, precision increases by about 10\%. For two or more
-training examples, recall and F$_{1}$-score stay around 75\% and
-precision around 96\%.
-
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we compare against a baseline of randomly
-picking lines from the build log. Its results follow intuitive
-expectations:
-The precision ranges between 8\% and 5\%, the recall between 6\% and
-8\%. The size of the training set has no visible impact on either.
-An greater number of structural categories within the training and
-test sets decreased the precision of RLR from 7\% to 0\%, the recall
-increases from 6\%, for one structural category present, to 11\%, for
-three sturctural categories present and also drops to 0\% for more
-structural categories.
-Graphs of the results of the chunk retrieval with RLR from our study
-are included in our replication package~\cite{brandt2020chunk-replication}.
-
-\subsection{Comparison of All Techniques}
-In this section, we aggregate the results from
-\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it
-each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk
-retrievals differentiated by techniques in our study. CTS and KWS
-extract some of the desired lines in 79\% and 88.5\% of the chunk
-retrieval runs. With 38.25\%, KWS also has the highest number of fully
-successful extractions, followed by PBE with 34.5\%. PBE has the
-lowest number of partial retrievals with only 18 out of 400 chunk
-retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is
-% compared in Figure~\ref{fig:recall-precision-all}. The recall of PBE
-% has a high skew towards one and zero, meaning in most cases either
-% the retrieval is successful or no relevant lines are extracted at
-% all. PBE has the highest average precision with 95\%. Chunk
-% retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% and the second highest recall with 46\%. KWS has the smallest
-% precision of the three chunk retrieval techniques. With 16\% it is
-% still higher than the precision of the RLR baseline with 7\%. KWS
-% has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of a single structural category present in the
-training examples compared to multiple categories present. For more
-than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by
-the number of structural categories present.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
-		\label{fig:success-partial-all}
-\end{figure}
-
-\begin{figure*}
-\centering
-    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
-		\label{fig:recall-precision-singlecategory-all}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
-		\label{fig:recall-precision-multicategory-all}
-\end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% TODO update RQs
-% TODO incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}  
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
-\end{itemize}
-\end{simplebox}
-
-The first section discusses for PBE, CTS and KWS separately in which
-cases they perform best. It details for which types of input build
-logs, available training examples and consumption of the retrieved
-output each technique is suited. In the following section we discuss
-which of these criteria should influence the decision to use a certain
-technique most. Based on our empirical comparison, we present a
-decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed
-chunk retrieval techniques separately. It gives recommendations which
-kind of information chunk targets are best for each technique and for
-what kind of usage the respective output is suitable.
-
-\begin{table}[tbp]
-\resizebox{\columnwidth}{!}{%
-\centering
-\begin{tabular}{llll}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabular}%
-}
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\subsubsection{Program Synthesis by Example (PBE)}
-
-\noindent
-\textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best
-results when the training examples are structurally identical. This is
-because PROSE has difficulty synthesizing OR-based programs (see
-\Cref{sec:prose:impl}). PBE is thus suited to retrieve information
-chunks that always have the same surrounding or defining internal
-structure. To extract for example the reason a build failed, the log
-passage describing the failure would always have to be started and
-ended the same way.
-
-When the training examples are of the same structure, even one or two
-two examples are enough input for PROSE to synthesize a regular
-expression program with good recall. In our study, additional training
-examples did not improve the chunk retrieval. In fact, unless they
-were in some sense redudant, adding training examples above that even
-hindered the applicability of PBE.
-
-\noindent
-\textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression
-program yields an output, PBE has high precision and recall. The tool
-clearly identifies a failing program synthesis or when no output from
-the program applied to a build log is obtained. Therefore, if there is
-an output, the user can have high confidence that it is the desired
-output. This preciseness makes output from PBE chunk retrieval
-well-suited for machine consumption.
-
-\subsubsection{Common Text Similarity (CTS)}
-\noindent
-\textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the
-fewer structural categories are present in the training and test
-examples.
-
-The number of training examples had no noticeable influence on
-precision or recall in our study. Information retrieval techniques
-like text similarity commonly learn on a higher number of examples
-than used for our study. Future work is needed to investigate how many
-examples yield improvements in the chunk retrieval over a single
-training example.
-
-\noindent
-\textbf{Retrieval Output Usage}
-CTS has good precision and recall on average, though with a high
-variation. This means that the quality of an output by CTS is hard to
-determine, which makes it unsuited for automatic  processing and requires a human to further inspect and interpret the output. This could include semi-automated procedures such as sending
-developers an email with the extracted build failure reason.
-
-\subsubsection{Keyword Search (KWS)}
-\noindent
-\textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple
-structural categories present in the training and test examples. This
-makes KWS a good technique if there is little prior knowledge on how
-the targeted log chunk is represented in the build log. For the
-example of extracting the reason the build failed, KWS is best suited
-if a build can fail in various steps logged by different tools and no
-pre-categorization of where the build failed is available.
-
-Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the
-training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does
-improve the recall within our study but also increases the proportion
-of lines retrieved overall and therefore decreases precision.
-
-\noindent
-\textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its
-precision is the lowest. The output of a chunk retrieval with KWS is
-well-suited to be read by humans, but ill-suited for consumption by
-automated tools.
-
-\begin{figure}[tb]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
-		\label{fig:crt-recommendation}
-\end{figure}
-
-\subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we
-now want to unify our results into one recommendation scheme. In
-Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
-developers and researchers who want to retrieve information chunks
-from build logs can follow. The decision tree is built up of questions
-which either lead to more questions or to a leaf node containing a
-recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results
-from our comparison study. The recommendations could therefore be
-influenced by idiosyncrazies of our specific implementation of the
-chunk retrieval techniques as well as the logs in the \emph{LogChunks}
-data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
-answer to RQ2, about which criteria influence the suitability of a
-chunk retrieval technique. The earlier in the decision tree a
-criterion is noted, the more important it is when distinguishing the
-techniques.
-
-The first and most important aspect are the structural categories. Are
-the information chunks one would like to retrieve always presented in
-the same structural way within the build logs? Then the information
-chunks in all training examples and the analyzed build log are in the
-same structural category.
-
-If the information chunks are from multiple structural categories,
-i.e. they are not represented in the same structural way within the
-build logs, and recall is more important than precision we recommend
-to use KWS\@. If the representations are from multiple structural
-categories and precision is more important than recall to the user we
-recommend CTS\@. We also recommend CTS when the representations are
-from one structural category, when the user does not require a high
-confidence in the precision or recall of the outcome and when the user
-would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user
-wishes a high confidence in the correctness of the output or prefers
-no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper. Such a super analyzer would likely always first employ PBE
-(because of its high accuracy), followed by a combination of CTS and
-KWS. Other than initial setup and training time, there should be no
-downside to this approach if it is implemented in a transparent way to
-the underlying technique: the output of the super analyzer could
-include from which sub-tool it originated and thus facilitate
-automatic on-ward processing or interpretation of the result.
-
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable
-chunk retrieval technique we describe two concrete examples: a
-researcher investigating why CI builds fail and a software team
-wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI
-are caused by a small or by a large group of test cases. They gather
-CI build logs from various projects, which are their only available
-data source. The task of the researcher is to extract the names of the
-failing test cases from each build log. When they use our
-recommendation scheme to select a chunk retrieval technique, they
-first have to estimate how uniform the representation of the failing
-test cases is in the investigated build logs. As the researcher is
-covering a wide range of build tools and development languages, the
-log chunks they target are in various, non-predictable structural
-representations. The next question is whether they value precision
-over recall. As they have to manually inspect the results of both CTS
-and KWS, they choose recall over precision to avoid having to inspect
-the whole log in case the relevant information chunk was not
-retrieved. Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the
-retrieval results, they have to first separate the CI build logs
-according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they
-can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor
-the performance of the phases within their CI build. They are using
-Travis CI, which measures the duration of build phases and documents
-them within the build log. As all log statements that report timing
-measurements are formatted the same way, the targeted log chunks are
-from one structural category. Therefore the development team can use
-PBE to retrieve the duration of a build phase as well as its name.
-
-\section{Threats to Validity}
-There are several threats to the validity of the conclusions of our
-work.
-
-\noindent
-\textbf{Implementation}
-\label{sec:prose:impl}
-% TODO we need to say something about why we think that these
-% limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk
-retrieval techniques and the libraries we used. Our implementation of
-PBE is based on the program synthesis provided by PROSE\@. The
-idiosyncrazies of this framework influence our PBE results. Other
-frameworks similar to PROSE might have somewhat different strengths
-and weaknesses. For example, the need for examples from a single
-structural category stems from the fact that PROSE cannot learn
-regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}. PROSE introduced this constraint to
-keep the synthesis performance reasonable. At the same time, this is
-clearly a current theoretical challenge of all PBE implementations,
-and we therefore attribute it to the technique itself, rather than the
-specific implementation.
-
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec}
-and the way it splits strings into word tokens. On the other hand,
-{\tt text2vec} is the de-facto standard library to do word embeddings
-in R. We intentionally chose a simple, minimally configured and tuned
-approach to compare against. Tuning the text similarity
-meta-parameters more to the specific use case of chunk retrieval from
-build logs would yield better chunk retrieval results.
-
-\noindent
-\textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build
-logs from the \emph{LogChunks} data set. It only consists of build
-logs from open source projects and therefore it is not clear whether
-our results are generalizable to industry projects. We only collected
-build logs from Travis CI, however we chose to evaluate on an
-information chunk whose format is not dependent on Travis CI\@. This
-is because the reason the build failed is described within the build
-logs by the tools themselves and not the Travis CI environment.
-
-\noindent
-\textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples. We chose this small training set
-size as the training examples have to be provided per repository and
-we expect a developer to not want to provide more examples than the
-small numbers we evaluated on.
-
-\noindent
-\textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural
-categories than with one category.
-% TODO Caro: Please explain the following further. Why does a
-% realistic data set only have one or few structural categories?
-This stems from the fact that we investigated the chunk retrieval
-techniques on a realistic data set, which showed to often have few
-structural categories within one project.
-
-\section{Future Work}
-\todo{survey build logs tools in industry}
-
-There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
-  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for the comparative
-  study in this paper, though it can be the basis for various further
-  analyses of build log data. The keywords, for example, can be
-  investigated to answer which keywords are used to search for the
-  reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and
-  tested each chunk retrieval technique on examples from the same
-  repository. We propose to analyze how techniques could be trained
-  across repositories, building the cornerstones for build
-  environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
-  paper investigates the three chunk retrieval techniques PBE, CTS and
-  KWS\@. Our study design can be reused to evaluate other build log
-  analysis techniques, such as the diff and information retrieval
-  approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We
-  investigated basic configurations of existing techniques applied to
-  chunk retrieval from build logs. In a next step, each of these
-  techniques could be refined to better approach the domain of build
-  logs. The \emph{LogChunks} data set and our study results act as a
-  baseline to benchmark such technique improvements. We propose the
-  following improvements:
-    \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program
-      synthesis through PROSE ranks possible programs according to
-      what the user most likely intended. One could adapt the ranking
-      rules provided by the FlashExtract DSL to fit common build log
-      chunk retrieval tasks. FlashExtract includes special tokens when
-      enumerating possible regular expressions. One could extend these
-      with tokens found in build logs, such as ``-'',``='',``ERROR''
-      or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information
-      retrieval techniques have various meta-parameters which can be
-      optimized for the specific use
-      case~\cite{panichella2016parameterizing}. We propose to further
-      investigate improvements in preprocessing of the log text, in
-      tokenization of the log lines into terms and in stop words
-      lists.
-    \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
-  analysis of the output produced by the chunk retrieval focuses on
-  precision and recall. We propose to investigate how useful these
-  outputs are to developers through controlled experiments.
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in
-their decision on how to analyze build logs. We implemented and
-compared three different chunk retrieval techniques on our data set
-\emph{LogChunks}, composed of 797 manually labeled build logs from a
-broad range of 80 repositories. Our results show that the structural
-representation of the targeted information in the build logs is the
-main factor to consider when choosing a suitable technique. Secondary
-factors are the desired confidence into recall and precision of the
-produced output and whether precision or recall is more important for
-the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper.

### 2020-04-02 tse-paper/5-results.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
-
-\lstset{
-  morekeywords={},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{Plum},
-	frame=single,
-  extendedchars=false,
-  texcl=false,
-  aboveskip=\baselineskip,
-  belowskip=0pt
-}
-
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within the build.
-The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
-study.
-Our goal was to classify how and what for researchers use build logs as a source
-of data (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
-build tools.
-
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
-examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
-\end{itemize}
-\end{simplebox}
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
-  a regular expression matching the given chunks within the build logs.
-  \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
-  \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
-  the occurrence of specific trigger words.
-\end{itemize}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
-  \end{lstlisting}  
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}  
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
-from Android/Gradle build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
-
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence.
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
-  are present in the training examples.
-\end{itemize}
-
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
-%         \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
-%           \item a keyword search approach (KWS).
-%         \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
-
-We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
-recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Kitchenham's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO Caro: update
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-% TODO Caro: please write a draft for this :-)
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool). many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
-work from system log analysis.
-
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of
-build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error
-types such as dependency mismatches are the most prominent cause of
-build failures at Google. In addition, they notice that most failures
-are resolved within two builds. They based their analyses on sets of
-build logs collected from industry partners. They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects and find that most builds fail because of failing
-tests. For most projects, over half of the failed builds follow a
-previous failed build. Rausch et al.'s data shows that most failures
-occur in the second half of the build runtime, which can cause long
-delays in the feedback loop, especially when builds are automatically
-retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones. They determine that testing failures are
-more common than compilation errors. Open source builds fail most
-often because of unit tests, whereas release preparations are the
-primary cause in industrial projects. Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data. They classify build failures from \emph{TravisTorrent}
-according to whether they were caused by an environmental failure or
-caused by a developer change. Their analysis starts with manual
-categorization of build logs. They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers
-presented in this section create parsers and regular expression-based
-programs. This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article. Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve. By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why
-their build failed. Several researchers investigate how to support
-developers in working with verbose build logs. Vassallo et
-al.~\cite{vassallo2018un-break} try to shorten the time it takes
-developers to understand build logs. They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-%The hint generators leverage this structured access to the
-%information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed. In a qualitative study
-they observed that highlighting the locality and context of an issue
-is helpful to programmers.
-%Their tool BART is published as a Jenkins
-%Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs. As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect. Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures. Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a
-basic structuring of the build logs within their log viewer using
-\emph{log folds}~\cite{travis2019logfolds}. They add fold identifiers
-around common commands and setup or teardown build phases and collapse
-the contained lines by default.
-
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log
-files produced during runtime. A main difference between build logs
-and system logs is that system logs are fundamentally structured
-through events. Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}. Figure \ref{lst:system-log} shows
-example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to
-separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}. Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters. The output of a log
-parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}. This structured log is then
-the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational
-%profiling~\cite{nagappan2009efficiently},
-%debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}. Xu et
-%al.~\cite{xu2009detecting} leverage the connection of log statements
-%to the source code producing them to separate messages into constant
-%and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied
-to build logs. One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies. Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of
-%events. A similar approach could also be applied to build logs to
-%determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques. Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g. by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
-  \end{lstlisting}  
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques} The
-% techniques we investigate are based on existing methods of
-% Programming by Example.%, information extraction and information
-% retrieval. This section presents different Programming by Example
-% resources surrounding the PROSE library. We explain its generic
-% program synthesis algorithm and how PROSE synthesizes text
-% extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program
-synthesis that enables users to automate repetitive tasks, without
-them having to explicitly codify a computer program. One has to
-provide prototypical examples of the input and the desired output. A
-synthesis algorithm tries to create a program (based on a regular
-language) that transforms the input to the output. The minimum working
-condition is for this when replayed on the examples inputs is to
-provide the specified output, but, hopefully, PBE is as close as
-possbile to the user's intention and thus also works on a different
-and larger set of inputs. This section introduces the theoretical
-foundations of the program synthesis algorithm of the \emph{PROgram
-Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research. Next, this
-section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our
-chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and
-Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
-synthesis in the Microsoft PROSE framework. FlashMeta separates the
-inductive synthesis algorithm from the domain specific capabilities of
-the desired program by encoding the possible program space in a domain
-specific language (DSL). The user specifies the desired program
-behavior by providing in/output examples (I/O examples). FlashMeta
-uses \emph{witness functions}, provided by the DSL, to divide the
-synthesis into smaller subtasks. For each of these subtasks it
-enumerates all possible programs that solve the subtask consistent
-with the set of I/O examples. A program is consistent with a set of
-I/O examples if, for each input example, it produces the corresponding
-output~\cite{mitchell1982generalization}. The possible subprograms are
-joined and stored in a \emph{version space algebra}
-(VSA)~\cite{mitchell1982generalization}. This a tree structure, which
-space-efficiently saves candidate programs for tasks by sharing common
-subexpressions. Next, FlashMeta ranks the enumerated programs
-according to which ones the user most likely intended. The DSL also
-provides the ranking characteristics. From the ranked VSA, FlashMeta
-can then return a ranked list of complete programs consistent with the
-user's example.
-
-% In addition to I/O examples of the intended program, the user can
-% also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized
-% program.
-
-% The different applications of PROSE presented in the following
-% paragraphs were all eventually implemented as DSLs for the FlashMeta
-% synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
-for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text,
-% websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs
-from semi-structured text based on regular expressions. Users can
-extract multiple fields and structure them with hierarchy and
-sequence.
-% FlashExtract synthesizes programs to extract each of the fields
-% leveraging the information about hierarchical containment and
-% sequentiality. It eliminates the need for the user to understand the
-% entire structure of the processed document and decreases the effort
-% of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of
-two cut positions. A position is either specified by an absolute
-character index or by a pair of two regular expressions. The first
-regular expression matches the substring directly before the
-characterized position, the second regular expression matches the
-substring directly after. A regular expression in FlashExtract is a
-concatenation of tokens, e.g.\ standard character classes or string
-literals frequently occurring in the input examples. Figure
-\ref{lst:prose-program} shows a text extraction program synthesized by
-FlashExtract. This program defines the first position as after a colon
-followed by a newline character and before a piece of text with all
-capital letters. It defines the second position as before two newline
-characters.
-
-Apart from automatic completion in Excel
-spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for
-two other Microsoft product features: Microsoft's system log analysis
-tool Azure Monitor lets users define custom log
-fields~\cite{azure2019custom}. The ConvertFrom-String function in
-PowerShell allows a user to specify an example template to extract
-hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build
-logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
-\section{Chunk Retrieval Techniques}
-\label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval
-techniques we study in this article, namely program synthesis by
-example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that
-represent a specific, targeted information.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically
-retrieve pieces of information that appear literally in the build
-logs, i.e., techniques that do not aggreagte, combine, or deducted
-information. We call such pieces of information from build logs
-\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and
-parser to analyze the entire structure of build logs, but focus on
-ad-hoc extracting just one specific piece of information per
-configuration.
-
-With the term \textit{configuration,} we abstract over the training
-and parametrization that different techniques require in different
-forms. A configuration can be explicitly stated or implicitly dervied
-by learning through provided examples. It is therefore a manual
-specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log. Each chunk
-retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word). The
-granularity might be adjustable by configuration. \emph{Running a
-chunk retrieval technique} means to execute a fully configured
-technique to consumes as input a build log in plain text format and to
-produce an array as output. The array consists of substrings of the
-build log text.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[]
-\centering
-\caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
-\toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
-\bottomrule
-\end{tabularx}
-\label{tab:ctr}
-\end{table*}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual
-% software
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model. We
-% investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs. In the following we will explain
-% the concept of how we apply text similarity to information retrieval
-% from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use
-the same concept of examples as for PBE\@
-% TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}. The
-lines of the output strings of the training examples define our search
-query. The algorithm splits the search query into single lines and
-identifies tokens, in our case words. Then we build a
-document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words. Finally, the
-algorithm applies TF-IDF to the matrix, a best practice for natural
-language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the output of the
-training examples. The algorithm calculates the cosine
-similarity~\cite{korenius2007principal} to compare each line of the
-build log with each line of the search query. After summing up the
-similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity. The average number of
-lines in the outputs of the training examples determines how many of
-the most similar lines are returned as the output of the retrieval
-run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad-hoc approach they
-use is to search for related keywords. Indeed, this was one of the
-most common approaches we took when searching for the reason the build
-failed within a log while creating the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers
-% use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs. In
-% the following we will explain how we use simple keyword search to
-% retrieve information from CI build logs, which we refer to as
-% \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@. To better
-compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted
-chunk or close to it. The configuring keywords for KWS are the ones
-that appear most often in the keywords of all training examples.
-% TODO Caro Please explain above sentence more precisely
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords. As keywords are
-often not directly describing the desired information, but rather
-appear close to the desired information, KWS also retrieves the lines
-around the found keyword. The number of surrounding lines retrieved is
-the average of lines in the output of the training examples.
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes
-% programs according to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming
-% knowledge~\cite{mayer2015user}. In the context of text extraction
-% through regular expressions, Programming by Example relieves the
-% developer from having to understand the whole document structure to
-% solve a single extraction task~\cite{le2014flashextract:}. In this
-% work, we refer to our interpretation of Programming by Example as
-% \emph{PBE}\@. We investigate the suitability of PBE to retrieve
-% information chunks from build logs. In the following, we explain the
-% configuration and application of PBE to chunk retrieval from CI
-% build logs.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by
-Example, we refer to them in short as \emph{examples}. The
-\emph{input} is the text of the build log file. The \emph{output} is
-an array of substrings of the log file text, representing the
-substrings that should be retrieved by the synthesized program when
-given the corresponding input file. One or multiple examples, the
-training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted. The
-PROSE program synthesis then tries to construct a program consistent
-with all training examples.
-% A program is consistent with an example if it returns the defined
-% output when executed on the defined
-% input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a
-consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn
-% uses the FlashMeta algorithm. Both are described in
-% Section~\ref{sec:rw-prose}.
-
-% TODO Caro: The following is very obvious and could apply to any
-% technique. 
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the
-synthesized regular expression program. It then returns the substring
-of the build log matched by the program or an empty string if the
-program found no match.
-
-\subsection{Random Line Retrieval}
-\label{sec:expl-rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. RLR essentially mimicks the
-situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should
-return. For a fair comparison to the other techniques (whose number of
-returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples. 
-% TODO Caro: some more details here?
-
-\subsection{Other Techniques}
-%Literature mentions further build log analysis techniques. This
-%section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information
-retrieval to identify relevant lines from a failed build
-log~\cite{amar2019mining}, as we describe in more detail in
-Section~\ref{sec:rw-bl-analysis}. The configuration for the technique
-is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not
-present in the successful build log and contain terms related to the
-given past failures.
-
-\subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a
-unifying interface. The unified interface is implemented in Ruby and
-calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE
-library~\cite{prose2019webpage}. We implemented CTS, KWS and RLR using
-R and the text2vec library~\cite{text2vec2019webpage}.
-
-\section{Study Design}
-\label{sec:study}
-
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-To investigate which techqnique is best suited to retrieve chunks from
-CI build logs we evaluate them on the
-\emph{LogChunks}~\cite{brandt2020logchunks} data set. This section
-describes our study design and which metrics we measure to answer our
-research questions. In the presentation of the results, we first focus
-on each of the three techniques and later compare them against each
-other.
-
-\subsection{LogChunks}
-For this study we created the previously published data set
-\emph{LogChunks}. It encompasses 797 build logs from Travis CI,
-stemming from a broad range of 80 GitHub repositories and 29
-programming languages. For each file, the authors manually ``labeled
-the log part (chunk) describing why the build
-failed''~\cite{brandt2020logchunks}. We include keywords, which we
-would use to search for the selected chunk within the log. In
-addition, we categorized the log chunks according to their format
-within the log. If the chunks are surrounded by the same markings
-within the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}. Random Line Retrieval
-(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
-the comparison.
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study. For each of the
-80 repositories in it, \emph{LogChunks} contains 10 build logs,
-manually labeled with the substring or \emph{chunk} describing the
-reason the build failed. Additionally, it contains (1) keywords useful
-to
-% TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category
-the substring belongs to.
-% TODO (Caro): Add details how key words were extracted. Add example?
-
-% TODO (Caro): Add more details. How was the split in numbers?
-For each repository in \emph{LogChunks}, we split the examples
-chronologically into training and test set. Therefore, we train on
-examples from past build logs and test on more recent build logs.
-
-\noindent
-\textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to
-perform best, we evaluate the techniques with different training set
-sizes. We train each technique with one to five examples from each of
-the repositories within \emph{LogChunks}. The size of the test set is
-one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk
-retrieval techniques need to be, we record the structural categories
-of the examples in the training and test sets.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output
-lines of the chunk retrieval run on the input of the test example
-($\mathit{RetrievedLines}$). As oracle in our evaluation, we save the
-desired lines from the output of the test example
-($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our
-evaluation.
-
-\vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm] \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap
-	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a
-        tool as well as what \textit{LogChunks} contains for each
-        example. 
-        % TODO (Caro) What about when a line is replicated twice?
-        % I.e., Are line numbers part of this?
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\
-	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of
-        the retrieved lines were actually desired. 
-	\item $\mbox{Recall} =
-	\dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$
-	\vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the
-        desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
-	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
-	\vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean
-        of precision and recall. We prefer F$_{1}$ to other aggregate
-        measures such as accuracy because for a
-        ``needle-in-the-haystack'' scenario, we do not want to bloat
-        our results by correctly not finding lots of irrelevant log
-        lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
-	We define a successful retrieval as one where all desired lines were
-	extracted, therefore when recall is one.
-\end{itemize}
-
-% Recall and precision of CTS and KWS vary with the number of lines
-% selected for retrieval. We evaluate the effect of varying the number
-% of extracted lines by multiplying the average number of lines
-% present in the training examples with a \emph{retrieval size factor}
-% from 0.5 to 2.5 in steps of 0.5.
-
 \section{Results}
@@
 \end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}  
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
-\end{itemize}
-\end{simplebox}
-
-The first section discusses for PBE, CTS and KWS separately in which
-cases they perform best. It details for which types of input build
-logs, available training examples and consumption of the retrieved
-output each technique is suited. In the following section we discuss
-which of these criteria should influence the decision to use a certain
-technique most. Based on our empirical comparison, we present a
-decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed
-chunk retrieval techniques separately. It gives recommendations which
-kind of information chunk targets are best for each technique and for
-what kind of usage the respective output is suitable.
-
-\begin{table}[tbp]
-\resizebox{\columnwidth}{!}{%
-\centering
-\begin{tabular}{llll}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabular}%
-}
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\subsubsection{Program Synthesis by Example (PBE)}
-
-\noindent
-\textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best
-results when the training examples are structurally identical. This is
-because PROSE has difficulty synthesizing OR-based programs (see
-\Cref{sec:prose:impl}). PBE is thus suited to retrieve information
-chunks that always have the same surrounding or defining internal
-structure. To extract for example the reason a build failed, the log
-passage describing the failure would always have to be started and
-ended the same way.
-
-When the training examples are of the same structure, even one or two
-two examples are enough input for PROSE to synthesize a regular
-expression program with good recall. In our study, additional training
-examples did not improve the chunk retrieval. In fact, unless they
-were in some sense redudant, adding training examples above that even
-hindered the applicability of PBE.
-
-\noindent
-\textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression
-program yields an output, PBE has high precision and recall. The tool
-clearly identifies a failing program synthesis or when no output from
-the program applied to a build log is obtained. Therefore, if there is
-an output, the user can have high confidence that it is the desired
-output. This preciseness makes output from PBE chunk retrieval
-well-suited for machine consumption.
-
-\subsubsection{Common Text Similarity (CTS)}
-\noindent
-\textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the
-fewer structural categories are present in the training and test
-examples.
-
-The number of training examples had no noticeable influence on
-precision or recall in our study. Information retrieval techniques
-like text similarity commonly learn on a higher number of examples
-than used for our study. Future work is needed to investigate how many
-examples yield improvements in the chunk retrieval over a single
-training example.
-
-% TODO Caro: I do not understand the following sentence.
-Extracting the average number of lines present in the training
-examples gives the best retrieval results for CTS, according to the
-F$_{1}$-score.
-
-\noindent
-\textbf{Retrieval Output Usage}
-% TODO Caro: reforumlate this please
-CTS has good precision and recall on average, though the precision or
-recall of a chunk retrieval run is very hard to predict from the given
-result. Therefore, retrieval output from CTS is suited to be read by a
-human. This could include semi-automated procedures such as sending
-developers an email with the extracted build failure reason.
-
-\subsubsection{Keyword Search (KWS)}
-\noindent
-\textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple
-structural categories present in the training and test examples. This
-makes KWS a good technique if there is little prior knowledge on how
-the targeted log chunk is represented in the build log. For the
-example of extracting the reason the build failed, KWS is best suited
-if a build can fail in various steps logged by different tools and no
-pre-categorization of where the build failed is available.
-
-Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the
-training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does
-improve the recall within our study but also increases the proportion
-of lines retrieved overall and therefore decreases precision.
-
-\noindent
-\textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its
-precision is the lowest. The output of a chunk retrieval with KWS is
-well-suited to be read by humans, but ill-suited for consumption by
-automated tools.
-
-\begin{figure}[tb]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
-		\label{fig:crt-recommendation}
-\end{figure}
-
-\subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we
-now want to unify our results into one recommendation scheme. In
-Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
-developers and researchers who want to retrieve information chunks
-from build logs can follow. The decision tree is built up of questions
-which either lead to more questions or to a leaf node containing a
-recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results
-from our comparison study. The recommendations could therefore be
-influenced by idiosyncrazies of our specific implementation of the
-chunk retrieval techniques as well as the logs in the \emph{LogChunks}
-data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
-answer to RQ2, about which criteria influence the suitability of a
-chunk retrieval technique. The earlier in the decision tree a
-criterion is noted, the more important it is when distinguishing the
-techniques.
-
-The first and most important aspect are the structural categories. Are
-the information chunks one would like to retrieve always presented in
-the same structural way within the build logs? Then the information
-chunks in all training examples and the analyzed build log are in the
-same structural category.
-
-If the information chunks are from multiple structural categories,
-i.e. they are not represented in the same structural way within the
-build logs, and recall is more important than precision we recommend
-to use KWS\@. If the representations are from multiple structural
-categories and precision is more important than recall to the user we
-recommend CTS\@. We also recommend CTS when the representations are
-from one structural category, when the user does not require a high
-confidence in the precision or recall of the outcome and when the user
-would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user
-wishes a high confidence in the correctness of the output or prefers
-no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper. Such a super analyzer would likely always first employ PBE
-(because of its high accuracy), followed by a combination of CTS and
-KWS. Other than initial setup and training time, there should be no
-downside to this approach if it is implemented in a transparent way to
-the underlying technique: the output of the super analyzer could
-include from which sub-tool it originated and thus facilitate
-automatic on-ward processing or interpretation of the result.
-
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable
-chunk retrieval technique we describe two concrete examples: a
-researcher investigating why CI builds fail and a software team
-wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI
-are caused by a small or by a large group of test cases. They gather
-CI build logs from various projects, which are their only available
-data source. The task of the researcher is to extract the names of the
-failing test cases from each build log. When they use our
-recommendation scheme to select a chunk retrieval technique, they
-first have to estimate how uniform the representation of the failing
-test cases is in the investigated build logs. As the researcher is
-covering a wide range of build tools and development languages, the
-log chunks they target are in various, non-predictable structural
-representations. The next question is whether they value precision
-over recall. As they have to manually inspect the results of both CTS
-and KWS, they choose recall over precision to avoid having to inspect
-the whole log in case the relevant information chunk was not
-retrieved. Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the
-retrieval results, they have to first separate the CI build logs
-according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they
-can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor
-the performance of the phases within their CI build. They are using
-Travis CI, which measures the duration of build phases and documents
-them within the build log. As all log statements that report timing
-measurements are formatted the same way, the targeted log chunks are
-from one structural category. Therefore the development team can use
-PBE to retrieve the duration of a build phase as well as its name.
-
-\section{Threats to Validity}
-There are several threats to the validity of the conclusions of our
-work.
-
-\noindent
-\textbf{Implementation}
-\label{sec:prose:impl}
-% TODO we need to say something about why we think that these
-% limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk
-retrieval techniques and the libraries we used. Our implementation of
-PBE is based on the program synthesis provided by PROSE\@. The
-idiosyncrazies of this framework influence our PBE results. Other
-frameworks similar to PROSE might have somewhat different strengths
-and weaknesses. For example, the need for examples from a single
-structural category stems from the fact that PROSE cannot learn
-regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}. PROSE introduced this constraint to
-keep the synthesis performance reasonable. At the same time, this is
-clearly a current theoretical challenge of all PBE implementations,
-and we therefore attribute it to the technique itself, rather than the
-specific implementation.
-
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec}
-and the way it splits strings into word tokens. On the other hand,
-{\tt text2vec} is the de-facto standard library to do word embeddings
-in R. We intentionally chose a simple, minimally configured and tuned
-approach to compare against. Tuning the text similarity
-meta-parameters more to the specific use case of chunk retrieval from
-build logs would yield better chunk retrieval results.
-
-\noindent
-\textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build
-logs from the \emph{LogChunks} data set. It only consists of build
-logs from open source projects and therefore it is not clear whether
-our results are generalizable to industry projects. We only collected
-build logs from Travis CI, however we chose to evaluate on an
-information chunk whose format is not dependent on Travis CI\@. This
-is because the reason the build failed is described within the build
-logs by the tools themselves and not the Travis CI environment.
-
-\noindent
-\textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples. We chose this small training set
-size as the training examples have to be provided per repository and
-we expect a developer to not want to provide more examples than the
-small numbers we evaluated on.
-
-\noindent
-\textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural
-categories than with one category.
-% TODO Caro: Please explain the following further. Why does a
-% realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in
-many cases has only one or few structural categories.
-
-\section{Future Work}
-\todo{survey build logs tools in industry}
-
-There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
-  \emph{LogChunks} data set \cite{} specifically for the comparative
-  study in this paper, though it can be the basis for various further
-  analyses of build log data. The keywords, for example, can be
-  investigated to answer which keywords are used to search for the
-  reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and
-  tested each chunk retrieval technique on examples from the same
-  repository. We propose to analyze how techniques could be trained
-  across repositories, building the cornerstones for build
-  environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
-  paper investigates the three chunk retrieval techniques PBE, CTS and
-  KWS\@. Our study design can be reused to evaluate other build log
-  analysis techniques, such as the diff and information retrieval
-  approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We
-  investigated basic configurations of existing techniques applied to
-  chunk retrieval from build logs. In a next step, each of these
-  techniques could be refined to better approach the domain of build
-  logs. The \emph{LogChunks} data set and our study results act as a
-  baseline to benchmark such technique improvements. We propose the
-  following improvements:
-    \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program
-      synthesis through PROSE ranks possible programs according to
-      what the user most likely intended. One could adapt the ranking
-      rules provided by the FlashExtract DSL to fit common build log
-      chunk retrieval tasks. FlashExtract includes special tokens when
-      enumerating possible regular expressions. One could extend these
-      with tokens found in build logs, such as ``-'',``='',``ERROR''
-      or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information
-      retrieval techniques have various meta-parameters which can be
-      optimized for the specific use
-      case~\cite{panichella2016parameterizing}. We propose to further
-      investigate improvements in preprocessing of the log text, in
-      tokenization of the log lines into terms and in stop words
-      lists.
-    \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
-  analysis of the output produced by the chunk retrieval focuses on
-  precision and recall. We propose to investigate how useful these
-  outputs are to developers through controlled experiments.
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in
-their decision on how to analyze build logs. We implemented and
-compared three different chunk retrieval techniques on our data set
-\emph{LogChunks}, composed of 797 manually labeled build logs from a
-broad range of 80 repositories. Our results show that the structural
-representation of the targeted information in the build logs is the
-main factor to consider when choosing a suitable technique. Secondary
-factors are the desired confidence into recall and precision of the
-produced output and whether precision or recall is more important for
-the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper.

### 2020-04-02 tse-paper/6-discussion.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
-
-\lstset{
-  morekeywords={},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{Plum},
-	frame=single,
-  extendedchars=false,
-  texcl=false,
-  aboveskip=\baselineskip,
-  belowskip=0pt
-}
-
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within the build.
-The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
-study.
-Our goal was to classify how and what for researchers use build logs as a source
-of data (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
-build tools.
-
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
-examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
-\end{itemize}
-\end{simplebox}
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
-  a regular expression matching the given chunks within the build logs.
-  \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
-  \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
-  the occurrence of specific trigger words.
-\end{itemize}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
-  \end{lstlisting}  
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}  
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
-from Android/Gradle build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
-
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence.
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
-  are present in the training examples.
-\end{itemize}
-
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
-%         \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
-%           \item a keyword search approach (KWS).
-%         \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
-
-We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
-recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Kitchenham's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO Caro: update
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-% TODO Caro: please write a draft for this :-)
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool). many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
-work from system log analysis.
-
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of
-build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error
-types such as dependency mismatches are the most prominent cause of
-build failures at Google. In addition, they notice that most failures
-are resolved within two builds. They based their analyses on sets of
-build logs collected from industry partners. They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects and find that most builds fail because of failing
-tests. For most projects, over half of the failed builds follow a
-previous failed build. Rausch et al.'s data shows that most failures
-occur in the second half of the build runtime, which can cause long
-delays in the feedback loop, especially when builds are automatically
-retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones. They determine that testing failures are
-more common than compilation errors. Open source builds fail most
-often because of unit tests, whereas release preparations are the
-primary cause in industrial projects. Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data. They classify build failures from \emph{TravisTorrent}
-according to whether they were caused by an environmental failure or
-caused by a developer change. Their analysis starts with manual
-categorization of build logs. They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers
-presented in this section create parsers and regular expression-based
-programs. This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article. Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve. By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why
-their build failed. Several researchers investigate how to support
-developers in working with verbose build logs. Vassallo et
-al.~\cite{vassallo2018un-break} try to shorten the time it takes
-developers to understand build logs. They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-%The hint generators leverage this structured access to the
-%information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed. In a qualitative study
-they observed that highlighting the locality and context of an issue
-is helpful to programmers.
-%Their tool BART is published as a Jenkins
-%Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs. As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect. Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures. Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a
-basic structuring of the build logs within their log viewer using
-\emph{log folds}~\cite{travis2019logfolds}. They add fold identifiers
-around common commands and setup or teardown build phases and collapse
-the contained lines by default.
-
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log
-files produced during runtime. A main difference between build logs
-and system logs is that system logs are fundamentally structured
-through events. Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}. Figure \ref{lst:system-log} shows
-example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to
-separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}. Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters. The output of a log
-parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}. This structured log is then
-the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational
-%profiling~\cite{nagappan2009efficiently},
-%debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}. Xu et
-%al.~\cite{xu2009detecting} leverage the connection of log statements
-%to the source code producing them to separate messages into constant
-%and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied
-to build logs. One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies. Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of
-%events. A similar approach could also be applied to build logs to
-%determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques. Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g. by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
-  \end{lstlisting}  
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques} The
-% techniques we investigate are based on existing methods of
-% Programming by Example.%, information extraction and information
-% retrieval. This section presents different Programming by Example
-% resources surrounding the PROSE library. We explain its generic
-% program synthesis algorithm and how PROSE synthesizes text
-% extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program
-synthesis that enables users to automate repetitive tasks, without
-them having to explicitly codify a computer program. One has to
-provide prototypical examples of the input and the desired output. A
-synthesis algorithm tries to create a program (based on a regular
-language) that transforms the input to the output. The minimum working
-condition is for this when replayed on the examples inputs is to
-provide the specified output, but, hopefully, PBE is as close as
-possbile to the user's intention and thus also works on a different
-and larger set of inputs. This section introduces the theoretical
-foundations of the program synthesis algorithm of the \emph{PROgram
-Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research. Next, this
-section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our
-chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and
-Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
-synthesis in the Microsoft PROSE framework. FlashMeta separates the
-inductive synthesis algorithm from the domain specific capabilities of
-the desired program by encoding the possible program space in a domain
-specific language (DSL). The user specifies the desired program
-behavior by providing in/output examples (I/O examples). FlashMeta
-uses \emph{witness functions}, provided by the DSL, to divide the
-synthesis into smaller subtasks. For each of these subtasks it
-enumerates all possible programs that solve the subtask consistent
-with the set of I/O examples. A program is consistent with a set of
-I/O examples if, for each input example, it produces the corresponding
-output~\cite{mitchell1982generalization}. The possible subprograms are
-joined and stored in a \emph{version space algebra}
-(VSA)~\cite{mitchell1982generalization}. This a tree structure, which
-space-efficiently saves candidate programs for tasks by sharing common
-subexpressions. Next, FlashMeta ranks the enumerated programs
-according to which ones the user most likely intended. The DSL also
-provides the ranking characteristics. From the ranked VSA, FlashMeta
-can then return a ranked list of complete programs consistent with the
-user's example.
-
-% In addition to I/O examples of the intended program, the user can
-% also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized
-% program.
-
-% The different applications of PROSE presented in the following
-% paragraphs were all eventually implemented as DSLs for the FlashMeta
-% synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
-for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text,
-% websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs
-from semi-structured text based on regular expressions. Users can
-extract multiple fields and structure them with hierarchy and
-sequence.
-% FlashExtract synthesizes programs to extract each of the fields
-% leveraging the information about hierarchical containment and
-% sequentiality. It eliminates the need for the user to understand the
-% entire structure of the processed document and decreases the effort
-% of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of
-two cut positions. A position is either specified by an absolute
-character index or by a pair of two regular expressions. The first
-regular expression matches the substring directly before the
-characterized position, the second regular expression matches the
-substring directly after. A regular expression in FlashExtract is a
-concatenation of tokens, e.g.\ standard character classes or string
-literals frequently occurring in the input examples. Figure
-\ref{lst:prose-program} shows a text extraction program synthesized by
-FlashExtract. This program defines the first position as after a colon
-followed by a newline character and before a piece of text with all
-capital letters. It defines the second position as before two newline
-characters.
-
-Apart from automatic completion in Excel
-spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for
-two other Microsoft product features: Microsoft's system log analysis
-tool Azure Monitor lets users define custom log
-fields~\cite{azure2019custom}. The ConvertFrom-String function in
-PowerShell allows a user to specify an example template to extract
-hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build
-logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
-\section{Chunk Retrieval Techniques}
-\label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval
-techniques we study in this article, namely program synthesis by
-example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that
-represent a specific, targeted information.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically
-retrieve pieces of information that appear literally in the build
-logs, i.e., techniques that do not aggreagte, combine, or deducted
-information. We call such pieces of information from build logs
-\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and
-parser to analyze the entire structure of build logs, but focus on
-ad-hoc extracting just one specific piece of information per
-configuration.
-
-With the term \textit{configuration,} we abstract over the training
-and parametrization that different techniques require in different
-forms. A configuration can be explicitly stated or implicitly dervied
-by learning through provided examples. It is therefore a manual
-specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log. Each chunk
-retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word). The
-granularity might be adjustable by configuration. \emph{Running a
-chunk retrieval technique} means to execute a fully configured
-technique to consumes as input a build log in plain text format and to
-produce an array as output. The array consists of substrings of the
-build log text.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[]
-\centering
-\caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
-\toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
-\bottomrule
-\end{tabularx}
-\label{tab:ctr}
-\end{table*}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual
-% software
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model. We
-% investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs. In the following we will explain
-% the concept of how we apply text similarity to information retrieval
-% from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use
-the same concept of examples as for PBE\@
-% TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}. The
-lines of the output strings of the training examples define our search
-query. The algorithm splits the search query into single lines and
-identifies tokens, in our case words. Then we build a
-document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words. Finally, the
-algorithm applies TF-IDF to the matrix, a best practice for natural
-language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the output of the
-training examples. The algorithm calculates the cosine
-similarity~\cite{korenius2007principal} to compare each line of the
-build log with each line of the search query. After summing up the
-similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity. The average number of
-lines in the outputs of the training examples determines how many of
-the most similar lines are returned as the output of the retrieval
-run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad-hoc approach they
-use is to search for related keywords. Indeed, this was one of the
-most common approaches we took when searching for the reason the build
-failed within a log while creating the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers
-% use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs. In
-% the following we will explain how we use simple keyword search to
-% retrieve information from CI build logs, which we refer to as
-% \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@. To better
-compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted
-chunk or close to it. The configuring keywords for KWS are the ones
-that appear most often in the keywords of all training examples.
-% TODO Caro Please explain above sentence more precisely
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords. As keywords are
-often not directly describing the desired information, but rather
-appear close to the desired information, KWS also retrieves the lines
-around the found keyword. The number of surrounding lines retrieved is
-the average of lines in the output of the training examples.
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes
-% programs according to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming
-% knowledge~\cite{mayer2015user}. In the context of text extraction
-% through regular expressions, Programming by Example relieves the
-% developer from having to understand the whole document structure to
-% solve a single extraction task~\cite{le2014flashextract:}. In this
-% work, we refer to our interpretation of Programming by Example as
-% \emph{PBE}\@. We investigate the suitability of PBE to retrieve
-% information chunks from build logs. In the following, we explain the
-% configuration and application of PBE to chunk retrieval from CI
-% build logs.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by
-Example, we refer to them in short as \emph{examples}. The
-\emph{input} is the text of the build log file. The \emph{output} is
-an array of substrings of the log file text, representing the
-substrings that should be retrieved by the synthesized program when
-given the corresponding input file. One or multiple examples, the
-training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted. The
-PROSE program synthesis then tries to construct a program consistent
-with all training examples.
-% A program is consistent with an example if it returns the defined
-% output when executed on the defined
-% input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a
-consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn
-% uses the FlashMeta algorithm. Both are described in
-% Section~\ref{sec:rw-prose}.
-
-% TODO Caro: The following is very obvious and could apply to any
-% technique. 
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the
-synthesized regular expression program. It then returns the substring
-of the build log matched by the program or an empty string if the
-program found no match.
-
-\subsection{Random Line Retrieval}
-\label{sec:expl-rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. RLR essentially mimicks the
-situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should
-return. For a fair comparison to the other techniques (whose number of
-returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples. 
-% TODO Caro: some more details here?
-
-\subsection{Other Techniques}
-%Literature mentions further build log analysis techniques. This
-%section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information
-retrieval to identify relevant lines from a failed build
-log~\cite{amar2019mining}, as we describe in more detail in
-Section~\ref{sec:rw-bl-analysis}. The configuration for the technique
-is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not
-present in the successful build log and contain terms related to the
-given past failures.
-
-\subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a
-unifying interface. The unified interface is implemented in Ruby and
-calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE
-library~\cite{prose2019webpage}. We implemented CTS, KWS and RLR using
-R and the text2vec library~\cite{text2vec2019webpage}.
-
-\section{Study Design}
-\label{sec:study}
-
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-To investigate which techqnique is best suited to retrieve chunks from
-CI build logs we evaluate them on the
-\emph{LogChunks}~\cite{brandt2020logchunks} data set. This section
-describes our study design and which metrics we measure to answer our
-research questions. In the presentation of the results, we first focus
-on each of the three techniques and later compare them against each
-other.
-
-\subsection{LogChunks}
-For this study we created the previously published data set
-\emph{LogChunks}. It encompasses 797 build logs from Travis CI,
-stemming from a broad range of 80 GitHub repositories and 29
-programming languages. For each file, the authors manually ``labeled
-the log part (chunk) describing why the build
-failed''~\cite{brandt2020logchunks}. We include keywords, which we
-would use to search for the selected chunk within the log. In
-addition, we categorized the log chunks according to their format
-within the log. If the chunks are surrounded by the same markings
-within the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}. Random Line Retrieval
-(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
-the comparison.
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study. For each of the
-80 repositories in it, \emph{LogChunks} contains 10 build logs,
-manually labeled with the substring or \emph{chunk} describing the
-reason the build failed. Additionally, it contains (1) keywords useful
-to
-% TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category
-the substring belongs to.
-% TODO (Caro): Add details how key words were extracted. Add example?
-
-% TODO (Caro): Add more details. How was the split in numbers?
-For each repository in \emph{LogChunks}, we split the examples
-chronologically into training and test set. Therefore, we train on
-examples from past build logs and test on more recent build logs.
-
-\noindent
-\textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to
-perform best, we evaluate the techniques with different training set
-sizes. We train each technique with one to five examples from each of
-the repositories within \emph{LogChunks}. The size of the test set is
-one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk
-retrieval techniques need to be, we record the structural categories
-of the examples in the training and test sets.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output
-lines of the chunk retrieval run on the input of the test example
-($\mathit{RetrievedLines}$). As oracle in our evaluation, we save the
-desired lines from the output of the test example
-($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our
-evaluation.
-
-\vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm] \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap
-	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a
-        tool as well as what \textit{LogChunks} contains for each
-        example. 
-        % TODO (Caro) What about when a line is replicated twice?
-        % I.e., Are line numbers part of this?
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\
-	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of
-        the retrieved lines were actually desired. 
-	\item $\mbox{Recall} =
-	\dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$
-	\vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the
-        desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
-	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
-	\vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean
-        of precision and recall. We prefer F$_{1}$ to other aggregate
-        measures such as accuracy because for a
-        ``needle-in-the-haystack'' scenario, we do not want to bloat
-        our results by correctly not finding lots of irrelevant log
-        lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
-	We define a successful retrieval as one where all desired lines were
-	extracted, therefore when recall is one.
-\end{itemize}
-
-% Recall and precision of CTS and KWS vary with the number of lines
-% selected for retrieval. We evaluate the effect of varying the number
-% of extracted lines by multiplying the average number of lines
-% present in the training examples with a \emph{retrieval size factor}
-% from 0.5 to 2.5 in steps of 0.5.
-
-\section{Results}
-This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as
-baseline.
-
-\lstset{
-  language=,
-  morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass   
-Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass
-        from line 5 of sass/components/_all.sass
-        from line 6 of bulma.sass
-  \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
-  \label{lst:pbe-unsuccessful}
-\end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:r:cts}
-\begin{figure*}
-\centering
-    \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-CTS}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-CTS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-CTS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using CTS for an
-increasing number of training examples. When using one to five
-training examples, the size of the training set has no noticeable
-influence on precision, recall or F$_{1}$-score of the chunk retrieval
-with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. With increasing category count, precision,
-recall and F$_{1}$-score decrease. Especially for more than three
-categories present we have no chunk retrieval runs where all desired
-lines were extracted.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:r:kws}
-\begin{figure*}
-\centering
-    \textbf{Keyword Search (KWS)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-KWS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-KWS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using KWS for different
-numbers of training examples. The recall increases by about 12\% when
-increasing the size of the training set to more than one example,
-while the precision stays constant at around 16\%. The F$_{1}$-score
-stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. For more than one structural category in
-the training and test examples the recall decreases by about 20\% and
-the precision decreases about 6\%. For more than two structural
-categories no clear trend is visible in precision, recall or
-F$_{1}$-score for an increasing amount of categories in the training
-and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the
-% effect of the retrieval size factor on precision, recall and
-% F$_{1}$-score of chunk retrieval runs with KWS\@. The precision is
-% 19\% when retrieving half of the expected number of lines. On
-% average 9\% of the lines in the build log are retrieved then. When
-% 2.5 times the expected number of lines are retrieved, the precision
-% decreases to 10\% and a quarter of the lines in the build log are
-% retrieved on average. The recall ranges from 58\% to 75\% and the
-% F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-% 		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
-                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
-                \label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
-evaluation. Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines in 138 cases. In 89 further
-cases, an extraction program was also successfully synthesized, though
-in 59 of the 89 cases the synthesized program yielded no output. In 30
-of the 89 cases did the synthesized program only partially extract a
-subset of the desired lines. For these 30 cases, the average recall
-was 28\%. Listing \ref{lst:pbe-unsuccessful} shows an example of such
-an \emph{unsuccessful retrieval}, where the synthesized program only
-retrieved two of the four targeted lines. In 173 of the 400 cases
-could PROSE not synthesize program consistent with all of the training
-examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
-runs depend on the number of structural categories in the training and
-test examples. The figure demonstrates that program synthesis mostly
-returns exactly the desired output when there are is only one
-structural category present in the training examples. However, when
-two or more structural categories are simultaneously present in the
-examlpe set, PROSE could in most cases not synthesize a program
-consistent with all training examples. For four or more present
-categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
-precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples. When the training set
-size increases from one to two, recall and F$_{1}$-score increase by
-about 25\%, precision increases by about 10\%. For two or more
-training examples, recall and F$_{1}$-score stay around 75\% and
-precision around 96\%.
-
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. Due to the fact no one would
-seriously consider RLR in real-world scenarios, we are omitting its
-detailed graphs here. However, its results follow intuitive
-expectations:
-% TODO Caro: shortly descibre RLR graphs ommitted
-
-\subsection{Comparison of All Techniques}
-In this section, we aggregate the results from
-\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it
-each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk
-retrievals differentiated by techniques in our study. CTS and KWS
-extract some of the desired lines in 79\% and 88.5\% of the chunk
-retrieval runs. With 38.25\%, KWS also has the highest number of fully
-successful extractions, followed by PBE with 34.5\%. PBE has the
-lowest number of partial retrievals with only 18 out of 400 chunk
-retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is
-% compared in Figure~\ref{fig:recall-precision-all}. The recall of PBE
-% has a high skew towards one and zero, meaning in most cases either
-% the retrieval is successful or no relevant lines are extracted at
-% all. PBE has the highest average precision with 95\%. Chunk
-% retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% and the second highest recall with 46\%. KWS has the smallest
-% precision of the three chunk retrieval techniques. With 16\% it is
-% still higher than the precision of the RLR baseline with 7\%. KWS
-% has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of a single structural category present in the
-training examples compared to multiple categories present. For more
-than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by
-the number of structural categories present.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
-		\label{fig:success-partial-all}
-\end{figure}
-
-\begin{figure*}
-\centering
-    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
-		\label{fig:recall-precision-singlecategory-all}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
-		\label{fig:recall-precision-multicategory-all}
-\end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
-\end{figure*}
-
 \section{Discussion}
@@
 PBE to retrieve the duration of a build phase as well as its name.
-
-\section{Threats to Validity}
-There are several threats to the validity of the conclusions of our
-work.
-
-\noindent
-\textbf{Implementation}
-\label{sec:prose:impl}
-% TODO we need to say something about why we think that these
-% limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk
-retrieval techniques and the libraries we used. Our implementation of
-PBE is based on the program synthesis provided by PROSE\@. The
-idiosyncrazies of this framework influence our PBE results. Other
-frameworks similar to PROSE might have somewhat different strengths
-and weaknesses. For example, the need for examples from a single
-structural category stems from the fact that PROSE cannot learn
-regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}. PROSE introduced this constraint to
-keep the synthesis performance reasonable. At the same time, this is
-clearly a current theoretical challenge of all PBE implementations,
-and we therefore attribute it to the technique itself, rather than the
-specific implementation.
-
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec}
-and the way it splits strings into word tokens. On the other hand,
-{\tt text2vec} is the de-facto standard library to do word embeddings
-in R. We intentionally chose a simple, minimally configured and tuned
-approach to compare against. Tuning the text similarity
-meta-parameters more to the specific use case of chunk retrieval from
-build logs would yield better chunk retrieval results.
-
-\noindent
-\textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build
-logs from the \emph{LogChunks} data set. It only consists of build
-logs from open source projects and therefore it is not clear whether
-our results are generalizable to industry projects. We only collected
-build logs from Travis CI, however we chose to evaluate on an
-information chunk whose format is not dependent on Travis CI\@. This
-is because the reason the build failed is described within the build
-logs by the tools themselves and not the Travis CI environment.
-
-\noindent
-\textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples. We chose this small training set
-size as the training examples have to be provided per repository and
-we expect a developer to not want to provide more examples than the
-small numbers we evaluated on.
-
-\noindent
-\textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural
-categories than with one category.
-% TODO Caro: Please explain the following further. Why does a
-% realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in
-many cases has only one or few structural categories.
-
-\section{Future Work}
-\todo{survey build logs tools in industry}
-
-There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
-  \emph{LogChunks} data set \cite{} specifically for the comparative
-  study in this paper, though it can be the basis for various further
-  analyses of build log data. The keywords, for example, can be
-  investigated to answer which keywords are used to search for the
-  reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and
-  tested each chunk retrieval technique on examples from the same
-  repository. We propose to analyze how techniques could be trained
-  across repositories, building the cornerstones for build
-  environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
-  paper investigates the three chunk retrieval techniques PBE, CTS and
-  KWS\@. Our study design can be reused to evaluate other build log
-  analysis techniques, such as the diff and information retrieval
-  approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We
-  investigated basic configurations of existing techniques applied to
-  chunk retrieval from build logs. In a next step, each of these
-  techniques could be refined to better approach the domain of build
-  logs. The \emph{LogChunks} data set and our study results act as a
-  baseline to benchmark such technique improvements. We propose the
-  following improvements:
-    \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program
-      synthesis through PROSE ranks possible programs according to
-      what the user most likely intended. One could adapt the ranking
-      rules provided by the FlashExtract DSL to fit common build log
-      chunk retrieval tasks. FlashExtract includes special tokens when
-      enumerating possible regular expressions. One could extend these
-      with tokens found in build logs, such as ``-'',``='',``ERROR''
-      or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information
-      retrieval techniques have various meta-parameters which can be
-      optimized for the specific use
-      case~\cite{panichella2016parameterizing}. We propose to further
-      investigate improvements in preprocessing of the log text, in
-      tokenization of the log lines into terms and in stop words
-      lists.
-    \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
-  analysis of the output produced by the chunk retrieval focuses on
-  precision and recall. We propose to investigate how useful these
-  outputs are to developers through controlled experiments.
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in
-their decision on how to analyze build logs. We implemented and
-compared three different chunk retrieval techniques on our data set
-\emph{LogChunks}, composed of 797 manually labeled build logs from a
-broad range of 80 repositories. Our results show that the structural
-representation of the targeted information in the build logs is the
-main factor to consider when choosing a suitable technique. Secondary
-factors are the desired confidence into recall and precision of the
-produced output and whether precision or recall is more important for
-the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper.

### 2020-04-02 tse-paper/7-threats.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
-
-\lstset{
-  morekeywords={},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{Plum},
-	frame=single,
-  extendedchars=false,
-  texcl=false,
-  aboveskip=\baselineskip,
-  belowskip=0pt
-}
-
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within the build.
-The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
-study.
-Our goal was to classify how and what for researchers use build logs as a source
-of data (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
-build tools.
-
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
-examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
-\end{itemize}
-\end{simplebox}
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
-  a regular expression matching the given chunks within the build logs.
-  \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
-  \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
-  the occurrence of specific trigger words.
-\end{itemize}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
-  \end{lstlisting}  
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}  
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
-from Android/Gradle build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
-
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence.
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
-  are present in the training examples.
-\end{itemize}
-
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
-%         \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
-%           \item a keyword search approach (KWS).
-%         \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
-
-We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
-recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Kitchenham's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO Caro: update
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-% TODO Caro: please write a draft for this :-)
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool). many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
-work from system log analysis.
-
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of
-build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error
-types such as dependency mismatches are the most prominent cause of
-build failures at Google. In addition, they notice that most failures
-are resolved within two builds. They based their analyses on sets of
-build logs collected from industry partners. They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects and find that most builds fail because of failing
-tests. For most projects, over half of the failed builds follow a
-previous failed build. Rausch et al.'s data shows that most failures
-occur in the second half of the build runtime, which can cause long
-delays in the feedback loop, especially when builds are automatically
-retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones. They determine that testing failures are
-more common than compilation errors. Open source builds fail most
-often because of unit tests, whereas release preparations are the
-primary cause in industrial projects. Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data. They classify build failures from \emph{TravisTorrent}
-according to whether they were caused by an environmental failure or
-caused by a developer change. Their analysis starts with manual
-categorization of build logs. They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers
-presented in this section create parsers and regular expression-based
-programs. This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article. Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve. By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why
-their build failed. Several researchers investigate how to support
-developers in working with verbose build logs. Vassallo et
-al.~\cite{vassallo2018un-break} try to shorten the time it takes
-developers to understand build logs. They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-%The hint generators leverage this structured access to the
-%information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed. In a qualitative study
-they observed that highlighting the locality and context of an issue
-is helpful to programmers.
-%Their tool BART is published as a Jenkins
-%Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs. As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect. Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures. Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a
-basic structuring of the build logs within their log viewer using
-\emph{log folds}~\cite{travis2019logfolds}. They add fold identifiers
-around common commands and setup or teardown build phases and collapse
-the contained lines by default.
-
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log
-files produced during runtime. A main difference between build logs
-and system logs is that system logs are fundamentally structured
-through events. Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}. Figure \ref{lst:system-log} shows
-example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to
-separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}. Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters. The output of a log
-parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}. This structured log is then
-the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational
-%profiling~\cite{nagappan2009efficiently},
-%debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}. Xu et
-%al.~\cite{xu2009detecting} leverage the connection of log statements
-%to the source code producing them to separate messages into constant
-%and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied
-to build logs. One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies. Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of
-%events. A similar approach could also be applied to build logs to
-%determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques. Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g. by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
-  \end{lstlisting}  
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques} The
-% techniques we investigate are based on existing methods of
-% Programming by Example.%, information extraction and information
-% retrieval. This section presents different Programming by Example
-% resources surrounding the PROSE library. We explain its generic
-% program synthesis algorithm and how PROSE synthesizes text
-% extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program
-synthesis that enables users to automate repetitive tasks, without
-them having to explicitly codify a computer program. One has to
-provide prototypical examples of the input and the desired output. A
-synthesis algorithm tries to create a program (based on a regular
-language) that transforms the input to the output. The minimum working
-condition is for this when replayed on the examples inputs is to
-provide the specified output, but, hopefully, PBE is as close as
-possbile to the user's intention and thus also works on a different
-and larger set of inputs. This section introduces the theoretical
-foundations of the program synthesis algorithm of the \emph{PROgram
-Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research. Next, this
-section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our
-chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and
-Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
-synthesis in the Microsoft PROSE framework. FlashMeta separates the
-inductive synthesis algorithm from the domain specific capabilities of
-the desired program by encoding the possible program space in a domain
-specific language (DSL). The user specifies the desired program
-behavior by providing in/output examples (I/O examples). FlashMeta
-uses \emph{witness functions}, provided by the DSL, to divide the
-synthesis into smaller subtasks. For each of these subtasks it
-enumerates all possible programs that solve the subtask consistent
-with the set of I/O examples. A program is consistent with a set of
-I/O examples if, for each input example, it produces the corresponding
-output~\cite{mitchell1982generalization}. The possible subprograms are
-joined and stored in a \emph{version space algebra}
-(VSA)~\cite{mitchell1982generalization}. This a tree structure, which
-space-efficiently saves candidate programs for tasks by sharing common
-subexpressions. Next, FlashMeta ranks the enumerated programs
-according to which ones the user most likely intended. The DSL also
-provides the ranking characteristics. From the ranked VSA, FlashMeta
-can then return a ranked list of complete programs consistent with the
-user's example.
-
-% In addition to I/O examples of the intended program, the user can
-% also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized
-% program.
-
-% The different applications of PROSE presented in the following
-% paragraphs were all eventually implemented as DSLs for the FlashMeta
-% synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
-for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text,
-% websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs
-from semi-structured text based on regular expressions. Users can
-extract multiple fields and structure them with hierarchy and
-sequence.
-% FlashExtract synthesizes programs to extract each of the fields
-% leveraging the information about hierarchical containment and
-% sequentiality. It eliminates the need for the user to understand the
-% entire structure of the processed document and decreases the effort
-% of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of
-two cut positions. A position is either specified by an absolute
-character index or by a pair of two regular expressions. The first
-regular expression matches the substring directly before the
-characterized position, the second regular expression matches the
-substring directly after. A regular expression in FlashExtract is a
-concatenation of tokens, e.g.\ standard character classes or string
-literals frequently occurring in the input examples. Figure
-\ref{lst:prose-program} shows a text extraction program synthesized by
-FlashExtract. This program defines the first position as after a colon
-followed by a newline character and before a piece of text with all
-capital letters. It defines the second position as before two newline
-characters.
-
-Apart from automatic completion in Excel
-spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for
-two other Microsoft product features: Microsoft's system log analysis
-tool Azure Monitor lets users define custom log
-fields~\cite{azure2019custom}. The ConvertFrom-String function in
-PowerShell allows a user to specify an example template to extract
-hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build
-logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
-\section{Chunk Retrieval Techniques}
-\label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval
-techniques we study in this article, namely program synthesis by
-example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that
-represent a specific, targeted information.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically
-retrieve pieces of information that appear literally in the build
-logs, i.e., techniques that do not aggreagte, combine, or deducted
-information. We call such pieces of information from build logs
-\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and
-parser to analyze the entire structure of build logs, but focus on
-ad-hoc extracting just one specific piece of information per
-configuration.
-
-With the term \textit{configuration,} we abstract over the training
-and parametrization that different techniques require in different
-forms. A configuration can be explicitly stated or implicitly dervied
-by learning through provided examples. It is therefore a manual
-specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log. Each chunk
-retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word). The
-granularity might be adjustable by configuration. \emph{Running a
-chunk retrieval technique} means to execute a fully configured
-technique to consumes as input a build log in plain text format and to
-produce an array as output. The array consists of substrings of the
-build log text.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[]
-\centering
-\caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
-\toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
-\bottomrule
-\end{tabularx}
-\label{tab:ctr}
-\end{table*}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual
-% software
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model. We
-% investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs. In the following we will explain
-% the concept of how we apply text similarity to information retrieval
-% from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use
-the same concept of examples as for PBE\@
-% TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}. The
-lines of the output strings of the training examples define our search
-query. The algorithm splits the search query into single lines and
-identifies tokens, in our case words. Then we build a
-document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words. Finally, the
-algorithm applies TF-IDF to the matrix, a best practice for natural
-language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the output of the
-training examples. The algorithm calculates the cosine
-similarity~\cite{korenius2007principal} to compare each line of the
-build log with each line of the search query. After summing up the
-similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity. The average number of
-lines in the outputs of the training examples determines how many of
-the most similar lines are returned as the output of the retrieval
-run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad-hoc approach they
-use is to search for related keywords. Indeed, this was one of the
-most common approaches we took when searching for the reason the build
-failed within a log while creating the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers
-% use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs. In
-% the following we will explain how we use simple keyword search to
-% retrieve information from CI build logs, which we refer to as
-% \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@. To better
-compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted
-chunk or close to it. The configuring keywords for KWS are the ones
-that appear most often in the keywords of all training examples.
-% TODO Caro Please explain above sentence more precisely
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords. As keywords are
-often not directly describing the desired information, but rather
-appear close to the desired information, KWS also retrieves the lines
-around the found keyword. The number of surrounding lines retrieved is
-the average of lines in the output of the training examples.
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes
-% programs according to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming
-% knowledge~\cite{mayer2015user}. In the context of text extraction
-% through regular expressions, Programming by Example relieves the
-% developer from having to understand the whole document structure to
-% solve a single extraction task~\cite{le2014flashextract:}. In this
-% work, we refer to our interpretation of Programming by Example as
-% \emph{PBE}\@. We investigate the suitability of PBE to retrieve
-% information chunks from build logs. In the following, we explain the
-% configuration and application of PBE to chunk retrieval from CI
-% build logs.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by
-Example, we refer to them in short as \emph{examples}. The
-\emph{input} is the text of the build log file. The \emph{output} is
-an array of substrings of the log file text, representing the
-substrings that should be retrieved by the synthesized program when
-given the corresponding input file. One or multiple examples, the
-training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted. The
-PROSE program synthesis then tries to construct a program consistent
-with all training examples.
-% A program is consistent with an example if it returns the defined
-% output when executed on the defined
-% input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a
-consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn
-% uses the FlashMeta algorithm. Both are described in
-% Section~\ref{sec:rw-prose}.
-
-% TODO Caro: The following is very obvious and could apply to any
-% technique. 
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the
-synthesized regular expression program. It then returns the substring
-of the build log matched by the program or an empty string if the
-program found no match.
-
-\subsection{Random Line Retrieval}
-\label{sec:expl-rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. RLR essentially mimicks the
-situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should
-return. For a fair comparison to the other techniques (whose number of
-returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples. 
-% TODO Caro: some more details here?
-
-\subsection{Other Techniques}
-%Literature mentions further build log analysis techniques. This
-%section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information
-retrieval to identify relevant lines from a failed build
-log~\cite{amar2019mining}, as we describe in more detail in
-Section~\ref{sec:rw-bl-analysis}. The configuration for the technique
-is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not
-present in the successful build log and contain terms related to the
-given past failures.
-
-\subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a
-unifying interface. The unified interface is implemented in Ruby and
-calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE
-library~\cite{prose2019webpage}. We implemented CTS, KWS and RLR using
-R and the text2vec library~\cite{text2vec2019webpage}.
-
-\section{Study Design}
-\label{sec:study}
-
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-To investigate which techqnique is best suited to retrieve chunks from
-CI build logs we evaluate them on the
-\emph{LogChunks}~\cite{brandt2020logchunks} data set. This section
-describes our study design and which metrics we measure to answer our
-research questions. In the presentation of the results, we first focus
-on each of the three techniques and later compare them against each
-other.
-
-\subsection{LogChunks}
-For this study we created the previously published data set
-\emph{LogChunks}. It encompasses 797 build logs from Travis CI,
-stemming from a broad range of 80 GitHub repositories and 29
-programming languages. For each file, the authors manually ``labeled
-the log part (chunk) describing why the build
-failed''~\cite{brandt2020logchunks}. We include keywords, which we
-would use to search for the selected chunk within the log. In
-addition, we categorized the log chunks according to their format
-within the log. If the chunks are surrounded by the same markings
-within the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}. Random Line Retrieval
-(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
-the comparison.
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study. For each of the
-80 repositories in it, \emph{LogChunks} contains 10 build logs,
-manually labeled with the substring or \emph{chunk} describing the
-reason the build failed. Additionally, it contains (1) keywords useful
-to
-% TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category
-the substring belongs to.
-% TODO (Caro): Add details how key words were extracted. Add example?
-
-% TODO (Caro): Add more details. How was the split in numbers?
-For each repository in \emph{LogChunks}, we split the examples
-chronologically into training and test set. Therefore, we train on
-examples from past build logs and test on more recent build logs.
-
-\noindent
-\textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to
-perform best, we evaluate the techniques with different training set
-sizes. We train each technique with one to five examples from each of
-the repositories within \emph{LogChunks}. The size of the test set is
-one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk
-retrieval techniques need to be, we record the structural categories
-of the examples in the training and test sets.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output
-lines of the chunk retrieval run on the input of the test example
-($\mathit{RetrievedLines}$). As oracle in our evaluation, we save the
-desired lines from the output of the test example
-($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our
-evaluation.
-
-\vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm] \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap
-	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a
-        tool as well as what \textit{LogChunks} contains for each
-        example. 
-        % TODO (Caro) What about when a line is replicated twice?
-        % I.e., Are line numbers part of this?
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\
-	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of
-        the retrieved lines were actually desired. 
-	\item $\mbox{Recall} =
-	\dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$
-	\vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the
-        desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
-	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
-	\vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean
-        of precision and recall. We prefer F$_{1}$ to other aggregate
-        measures such as accuracy because for a
-        ``needle-in-the-haystack'' scenario, we do not want to bloat
-        our results by correctly not finding lots of irrelevant log
-        lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
-	We define a successful retrieval as one where all desired lines were
-	extracted, therefore when recall is one.
-\end{itemize}
-
-% Recall and precision of CTS and KWS vary with the number of lines
-% selected for retrieval. We evaluate the effect of varying the number
-% of extracted lines by multiplying the average number of lines
-% present in the training examples with a \emph{retrieval size factor}
-% from 0.5 to 2.5 in steps of 0.5.
-
-\section{Results}
-This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as
-baseline.
-
-\lstset{
-  language=,
-  morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass   
-Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass
-        from line 5 of sass/components/_all.sass
-        from line 6 of bulma.sass
-  \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
-  \label{lst:pbe-unsuccessful}
-\end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:r:cts}
-\begin{figure*}
-\centering
-    \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-CTS}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-CTS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-CTS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using CTS for an
-increasing number of training examples. When using one to five
-training examples, the size of the training set has no noticeable
-influence on precision, recall or F$_{1}$-score of the chunk retrieval
-with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. With increasing category count, precision,
-recall and F$_{1}$-score decrease. Especially for more than three
-categories present we have no chunk retrieval runs where all desired
-lines were extracted.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:r:kws}
-\begin{figure*}
-\centering
-    \textbf{Keyword Search (KWS)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-KWS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-KWS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using KWS for different
-numbers of training examples. The recall increases by about 12\% when
-increasing the size of the training set to more than one example,
-while the precision stays constant at around 16\%. The F$_{1}$-score
-stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. For more than one structural category in
-the training and test examples the recall decreases by about 20\% and
-the precision decreases about 6\%. For more than two structural
-categories no clear trend is visible in precision, recall or
-F$_{1}$-score for an increasing amount of categories in the training
-and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the
-% effect of the retrieval size factor on precision, recall and
-% F$_{1}$-score of chunk retrieval runs with KWS\@. The precision is
-% 19\% when retrieving half of the expected number of lines. On
-% average 9\% of the lines in the build log are retrieved then. When
-% 2.5 times the expected number of lines are retrieved, the precision
-% decreases to 10\% and a quarter of the lines in the build log are
-% retrieved on average. The recall ranges from 58\% to 75\% and the
-% F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-% 		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
-                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
-                \label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
-evaluation. Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines in 138 cases. In 89 further
-cases, an extraction program was also successfully synthesized, though
-in 59 of the 89 cases the synthesized program yielded no output. In 30
-of the 89 cases did the synthesized program only partially extract a
-subset of the desired lines. For these 30 cases, the average recall
-was 28\%. Listing \ref{lst:pbe-unsuccessful} shows an example of such
-an \emph{unsuccessful retrieval}, where the synthesized program only
-retrieved two of the four targeted lines. In 173 of the 400 cases
-could PROSE not synthesize program consistent with all of the training
-examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
-runs depend on the number of structural categories in the training and
-test examples. The figure demonstrates that program synthesis mostly
-returns exactly the desired output when there are is only one
-structural category present in the training examples. However, when
-two or more structural categories are simultaneously present in the
-examlpe set, PROSE could in most cases not synthesize a program
-consistent with all training examples. For four or more present
-categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
-precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples. When the training set
-size increases from one to two, recall and F$_{1}$-score increase by
-about 25\%, precision increases by about 10\%. For two or more
-training examples, recall and F$_{1}$-score stay around 75\% and
-precision around 96\%.
-
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. Due to the fact no one would
-seriously consider RLR in real-world scenarios, we are omitting its
-detailed graphs here. However, its results follow intuitive
-expectations:
-% TODO Caro: shortly descibre RLR graphs ommitted
-
-\subsection{Comparison of All Techniques}
-In this section, we aggregate the results from
-\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it
-each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk
-retrievals differentiated by techniques in our study. CTS and KWS
-extract some of the desired lines in 79\% and 88.5\% of the chunk
-retrieval runs. With 38.25\%, KWS also has the highest number of fully
-successful extractions, followed by PBE with 34.5\%. PBE has the
-lowest number of partial retrievals with only 18 out of 400 chunk
-retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is
-% compared in Figure~\ref{fig:recall-precision-all}. The recall of PBE
-% has a high skew towards one and zero, meaning in most cases either
-% the retrieval is successful or no relevant lines are extracted at
-% all. PBE has the highest average precision with 95\%. Chunk
-% retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% and the second highest recall with 46\%. KWS has the smallest
-% precision of the three chunk retrieval techniques. With 16\% it is
-% still higher than the precision of the RLR baseline with 7\%. KWS
-% has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of a single structural category present in the
-training examples compared to multiple categories present. For more
-than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by
-the number of structural categories present.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
-		\label{fig:success-partial-all}
-\end{figure}
-
-\begin{figure*}
-\centering
-    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
-		\label{fig:recall-precision-singlecategory-all}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
-		\label{fig:recall-precision-multicategory-all}
-\end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}  
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
-\end{itemize}
-\end{simplebox}
-
-The first section discusses for PBE, CTS and KWS separately in which
-cases they perform best. It details for which types of input build
-logs, available training examples and consumption of the retrieved
-output each technique is suited. In the following section we discuss
-which of these criteria should influence the decision to use a certain
-technique most. Based on our empirical comparison, we present a
-decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed
-chunk retrieval techniques separately. It gives recommendations which
-kind of information chunk targets are best for each technique and for
-what kind of usage the respective output is suitable.
-
-\begin{table}[tbp]
-\resizebox{\columnwidth}{!}{%
-\centering
-\begin{tabular}{llll}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabular}%
-}
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\subsubsection{Program Synthesis by Example (PBE)}
-
-\noindent
-\textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best
-results when the training examples are structurally identical. This is
-because PROSE has difficulty synthesizing OR-based programs (see
-\Cref{sec:prose:impl}). PBE is thus suited to retrieve information
-chunks that always have the same surrounding or defining internal
-structure. To extract for example the reason a build failed, the log
-passage describing the failure would always have to be started and
-ended the same way.
-
-When the training examples are of the same structure, even one or two
-two examples are enough input for PROSE to synthesize a regular
-expression program with good recall. In our study, additional training
-examples did not improve the chunk retrieval. In fact, unless they
-were in some sense redudant, adding training examples above that even
-hindered the applicability of PBE.
-
-\noindent
-\textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression
-program yields an output, PBE has high precision and recall. The tool
-clearly identifies a failing program synthesis or when no output from
-the program applied to a build log is obtained. Therefore, if there is
-an output, the user can have high confidence that it is the desired
-output. This preciseness makes output from PBE chunk retrieval
-well-suited for machine consumption.
-
-\subsubsection{Common Text Similarity (CTS)}
-\noindent
-\textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the
-fewer structural categories are present in the training and test
-examples.
-
-The number of training examples had no noticeable influence on
-precision or recall in our study. Information retrieval techniques
-like text similarity commonly learn on a higher number of examples
-than used for our study. Future work is needed to investigate how many
-examples yield improvements in the chunk retrieval over a single
-training example.
-
-% TODO Caro: I do not understand the following sentence.
-Extracting the average number of lines present in the training
-examples gives the best retrieval results for CTS, according to the
-F$_{1}$-score.
-
-\noindent
-\textbf{Retrieval Output Usage}
-% TODO Caro: reforumlate this please
-CTS has good precision and recall on average, though the precision or
-recall of a chunk retrieval run is very hard to predict from the given
-result. Therefore, retrieval output from CTS is suited to be read by a
-human. This could include semi-automated procedures such as sending
-developers an email with the extracted build failure reason.
-
-\subsubsection{Keyword Search (KWS)}
-\noindent
-\textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple
-structural categories present in the training and test examples. This
-makes KWS a good technique if there is little prior knowledge on how
-the targeted log chunk is represented in the build log. For the
-example of extracting the reason the build failed, KWS is best suited
-if a build can fail in various steps logged by different tools and no
-pre-categorization of where the build failed is available.
-
-Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the
-training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does
-improve the recall within our study but also increases the proportion
-of lines retrieved overall and therefore decreases precision.
-
-\noindent
-\textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its
-precision is the lowest. The output of a chunk retrieval with KWS is
-well-suited to be read by humans, but ill-suited for consumption by
-automated tools.
-
-\begin{figure}[tb]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
-		\label{fig:crt-recommendation}
-\end{figure}
-
-\subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we
-now want to unify our results into one recommendation scheme. In
-Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
-developers and researchers who want to retrieve information chunks
-from build logs can follow. The decision tree is built up of questions
-which either lead to more questions or to a leaf node containing a
-recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results
-from our comparison study. The recommendations could therefore be
-influenced by idiosyncrazies of our specific implementation of the
-chunk retrieval techniques as well as the logs in the \emph{LogChunks}
-data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
-answer to RQ2, about which criteria influence the suitability of a
-chunk retrieval technique. The earlier in the decision tree a
-criterion is noted, the more important it is when distinguishing the
-techniques.
-
-The first and most important aspect are the structural categories. Are
-the information chunks one would like to retrieve always presented in
-the same structural way within the build logs? Then the information
-chunks in all training examples and the analyzed build log are in the
-same structural category.
-
-If the information chunks are from multiple structural categories,
-i.e. they are not represented in the same structural way within the
-build logs, and recall is more important than precision we recommend
-to use KWS\@. If the representations are from multiple structural
-categories and precision is more important than recall to the user we
-recommend CTS\@. We also recommend CTS when the representations are
-from one structural category, when the user does not require a high
-confidence in the precision or recall of the outcome and when the user
-would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user
-wishes a high confidence in the correctness of the output or prefers
-no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper. Such a super analyzer would likely always first employ PBE
-(because of its high accuracy), followed by a combination of CTS and
-KWS. Other than initial setup and training time, there should be no
-downside to this approach if it is implemented in a transparent way to
-the underlying technique: the output of the super analyzer could
-include from which sub-tool it originated and thus facilitate
-automatic on-ward processing or interpretation of the result.
-
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable
-chunk retrieval technique we describe two concrete examples: a
-researcher investigating why CI builds fail and a software team
-wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI
-are caused by a small or by a large group of test cases. They gather
-CI build logs from various projects, which are their only available
-data source. The task of the researcher is to extract the names of the
-failing test cases from each build log. When they use our
-recommendation scheme to select a chunk retrieval technique, they
-first have to estimate how uniform the representation of the failing
-test cases is in the investigated build logs. As the researcher is
-covering a wide range of build tools and development languages, the
-log chunks they target are in various, non-predictable structural
-representations. The next question is whether they value precision
-over recall. As they have to manually inspect the results of both CTS
-and KWS, they choose recall over precision to avoid having to inspect
-the whole log in case the relevant information chunk was not
-retrieved. Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the
-retrieval results, they have to first separate the CI build logs
-according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they
-can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor
-the performance of the phases within their CI build. They are using
-Travis CI, which measures the duration of build phases and documents
-them within the build log. As all log statements that report timing
-measurements are formatted the same way, the targeted log chunks are
-from one structural category. Therefore the development team can use
-PBE to retrieve the duration of a build phase as well as its name.
-
 \section{Threats to Validity}
@@
 categories than with one category.
-% TODO Caro: Please explain the following further. Why does a
-% realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in
-many cases has only one or few structural categories.
-
-\section{Future Work}
-\todo{survey build logs tools in industry}
-
-There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
-  \emph{LogChunks} data set \cite{} specifically for the comparative
-  study in this paper, though it can be the basis for various further
-  analyses of build log data. The keywords, for example, can be
-  investigated to answer which keywords are used to search for the
-  reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and
-  tested each chunk retrieval technique on examples from the same
-  repository. We propose to analyze how techniques could be trained
-  across repositories, building the cornerstones for build
-  environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
-  paper investigates the three chunk retrieval techniques PBE, CTS and
-  KWS\@. Our study design can be reused to evaluate other build log
-  analysis techniques, such as the diff and information retrieval
-  approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We
-  investigated basic configurations of existing techniques applied to
-  chunk retrieval from build logs. In a next step, each of these
-  techniques could be refined to better approach the domain of build
-  logs. The \emph{LogChunks} data set and our study results act as a
-  baseline to benchmark such technique improvements. We propose the
-  following improvements:
-    \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program
-      synthesis through PROSE ranks possible programs according to
-      what the user most likely intended. One could adapt the ranking
-      rules provided by the FlashExtract DSL to fit common build log
-      chunk retrieval tasks. FlashExtract includes special tokens when
-      enumerating possible regular expressions. One could extend these
-      with tokens found in build logs, such as ``-'',``='',``ERROR''
-      or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information
-      retrieval techniques have various meta-parameters which can be
-      optimized for the specific use
-      case~\cite{panichella2016parameterizing}. We propose to further
-      investigate improvements in preprocessing of the log text, in
-      tokenization of the log lines into terms and in stop words
-      lists.
-    \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
-  analysis of the output produced by the chunk retrieval focuses on
-  precision and recall. We propose to investigate how useful these
-  outputs are to developers through controlled experiments.
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in
-their decision on how to analyze build logs. We implemented and
-compared three different chunk retrieval techniques on our data set
-\emph{LogChunks}, composed of 797 manually labeled build logs from a
-broad range of 80 repositories. Our results show that the structural
-representation of the targeted information in the build logs is the
-main factor to consider when choosing a suitable technique. Secondary
-factors are the desired confidence into recall and precision of the
-produced output and whether precision or recall is more important for
-the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper.
+This stems from the fact that we investigated the chunk retrieval
+techniques on a realistic data set, which showed to often have few
+structural categories within one project.

### 2020-04-02 tse-paper/8-future-work.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
-
-\lstset{
-  morekeywords={},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{Plum},
-	frame=single,
-  extendedchars=false,
-  texcl=false,
-  aboveskip=\baselineskip,
-  belowskip=0pt
-}
-
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within the build.
-The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
-study.
-Our goal was to classify how and what for researchers use build logs as a source
-of data (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
-build tools.
-
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
-examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
-\end{itemize}
-\end{simplebox}
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
-  a regular expression matching the given chunks within the build logs.
-  \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
-  \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
-  the occurrence of specific trigger words.
-\end{itemize}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
-  \end{lstlisting}  
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}  
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
-from Android/Gradle build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
-
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence.
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
-  are present in the training examples.
-\end{itemize}
-
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
-%         \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
-%           \item a keyword search approach (KWS).
-%         \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
-
-We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
-recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Kitchenham's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO Caro: update
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-% TODO Caro: please write a draft for this :-)
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool). many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
-work from system log analysis.
-
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of
-build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error
-types such as dependency mismatches are the most prominent cause of
-build failures at Google. In addition, they notice that most failures
-are resolved within two builds. They based their analyses on sets of
-build logs collected from industry partners. They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects and find that most builds fail because of failing
-tests. For most projects, over half of the failed builds follow a
-previous failed build. Rausch et al.'s data shows that most failures
-occur in the second half of the build runtime, which can cause long
-delays in the feedback loop, especially when builds are automatically
-retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones. They determine that testing failures are
-more common than compilation errors. Open source builds fail most
-often because of unit tests, whereas release preparations are the
-primary cause in industrial projects. Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data. They classify build failures from \emph{TravisTorrent}
-according to whether they were caused by an environmental failure or
-caused by a developer change. Their analysis starts with manual
-categorization of build logs. They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers
-presented in this section create parsers and regular expression-based
-programs. This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article. Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve. By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why
-their build failed. Several researchers investigate how to support
-developers in working with verbose build logs. Vassallo et
-al.~\cite{vassallo2018un-break} try to shorten the time it takes
-developers to understand build logs. They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-%The hint generators leverage this structured access to the
-%information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed. In a qualitative study
-they observed that highlighting the locality and context of an issue
-is helpful to programmers.
-%Their tool BART is published as a Jenkins
-%Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs. As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect. Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures. Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a
-basic structuring of the build logs within their log viewer using
-\emph{log folds}~\cite{travis2019logfolds}. They add fold identifiers
-around common commands and setup or teardown build phases and collapse
-the contained lines by default.
-
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log
-files produced during runtime. A main difference between build logs
-and system logs is that system logs are fundamentally structured
-through events. Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}. Figure \ref{lst:system-log} shows
-example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to
-separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}. Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters. The output of a log
-parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}. This structured log is then
-the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational
-%profiling~\cite{nagappan2009efficiently},
-%debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}. Xu et
-%al.~\cite{xu2009detecting} leverage the connection of log statements
-%to the source code producing them to separate messages into constant
-%and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied
-to build logs. One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies. Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of
-%events. A similar approach could also be applied to build logs to
-%determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques. Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g. by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
-  \end{lstlisting}  
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques} The
-% techniques we investigate are based on existing methods of
-% Programming by Example.%, information extraction and information
-% retrieval. This section presents different Programming by Example
-% resources surrounding the PROSE library. We explain its generic
-% program synthesis algorithm and how PROSE synthesizes text
-% extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program
-synthesis that enables users to automate repetitive tasks, without
-them having to explicitly codify a computer program. One has to
-provide prototypical examples of the input and the desired output. A
-synthesis algorithm tries to create a program (based on a regular
-language) that transforms the input to the output. The minimum working
-condition is for this when replayed on the examples inputs is to
-provide the specified output, but, hopefully, PBE is as close as
-possbile to the user's intention and thus also works on a different
-and larger set of inputs. This section introduces the theoretical
-foundations of the program synthesis algorithm of the \emph{PROgram
-Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research. Next, this
-section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our
-chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and
-Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
-synthesis in the Microsoft PROSE framework. FlashMeta separates the
-inductive synthesis algorithm from the domain specific capabilities of
-the desired program by encoding the possible program space in a domain
-specific language (DSL). The user specifies the desired program
-behavior by providing in/output examples (I/O examples). FlashMeta
-uses \emph{witness functions}, provided by the DSL, to divide the
-synthesis into smaller subtasks. For each of these subtasks it
-enumerates all possible programs that solve the subtask consistent
-with the set of I/O examples. A program is consistent with a set of
-I/O examples if, for each input example, it produces the corresponding
-output~\cite{mitchell1982generalization}. The possible subprograms are
-joined and stored in a \emph{version space algebra}
-(VSA)~\cite{mitchell1982generalization}. This a tree structure, which
-space-efficiently saves candidate programs for tasks by sharing common
-subexpressions. Next, FlashMeta ranks the enumerated programs
-according to which ones the user most likely intended. The DSL also
-provides the ranking characteristics. From the ranked VSA, FlashMeta
-can then return a ranked list of complete programs consistent with the
-user's example.
-
-% In addition to I/O examples of the intended program, the user can
-% also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized
-% program.
-
-% The different applications of PROSE presented in the following
-% paragraphs were all eventually implemented as DSLs for the FlashMeta
-% synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
-for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text,
-% websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs
-from semi-structured text based on regular expressions. Users can
-extract multiple fields and structure them with hierarchy and
-sequence.
-% FlashExtract synthesizes programs to extract each of the fields
-% leveraging the information about hierarchical containment and
-% sequentiality. It eliminates the need for the user to understand the
-% entire structure of the processed document and decreases the effort
-% of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of
-two cut positions. A position is either specified by an absolute
-character index or by a pair of two regular expressions. The first
-regular expression matches the substring directly before the
-characterized position, the second regular expression matches the
-substring directly after. A regular expression in FlashExtract is a
-concatenation of tokens, e.g.\ standard character classes or string
-literals frequently occurring in the input examples. Figure
-\ref{lst:prose-program} shows a text extraction program synthesized by
-FlashExtract. This program defines the first position as after a colon
-followed by a newline character and before a piece of text with all
-capital letters. It defines the second position as before two newline
-characters.
-
-Apart from automatic completion in Excel
-spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for
-two other Microsoft product features: Microsoft's system log analysis
-tool Azure Monitor lets users define custom log
-fields~\cite{azure2019custom}. The ConvertFrom-String function in
-PowerShell allows a user to specify an example template to extract
-hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build
-logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
-\section{Chunk Retrieval Techniques}
-\label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval
-techniques we study in this article, namely program synthesis by
-example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that
-represent a specific, targeted information.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically
-retrieve pieces of information that appear literally in the build
-logs, i.e., techniques that do not aggreagte, combine, or deducted
-information. We call such pieces of information from build logs
-\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and
-parser to analyze the entire structure of build logs, but focus on
-ad-hoc extracting just one specific piece of information per
-configuration.
-
-With the term \textit{configuration,} we abstract over the training
-and parametrization that different techniques require in different
-forms. A configuration can be explicitly stated or implicitly dervied
-by learning through provided examples. It is therefore a manual
-specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log. Each chunk
-retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word). The
-granularity might be adjustable by configuration. \emph{Running a
-chunk retrieval technique} means to execute a fully configured
-technique to consumes as input a build log in plain text format and to
-produce an array as output. The array consists of substrings of the
-build log text.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[]
-\centering
-\caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
-\toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
-\bottomrule
-\end{tabularx}
-\label{tab:ctr}
-\end{table*}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual
-% software
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model. We
-% investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs. In the following we will explain
-% the concept of how we apply text similarity to information retrieval
-% from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use
-the same concept of examples as for PBE\@
-% TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}. The
-lines of the output strings of the training examples define our search
-query. The algorithm splits the search query into single lines and
-identifies tokens, in our case words. Then we build a
-document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words. Finally, the
-algorithm applies TF-IDF to the matrix, a best practice for natural
-language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the output of the
-training examples. The algorithm calculates the cosine
-similarity~\cite{korenius2007principal} to compare each line of the
-build log with each line of the search query. After summing up the
-similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity. The average number of
-lines in the outputs of the training examples determines how many of
-the most similar lines are returned as the output of the retrieval
-run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad-hoc approach they
-use is to search for related keywords. Indeed, this was one of the
-most common approaches we took when searching for the reason the build
-failed within a log while creating the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers
-% use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs. In
-% the following we will explain how we use simple keyword search to
-% retrieve information from CI build logs, which we refer to as
-% \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@. To better
-compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted
-chunk or close to it. The configuring keywords for KWS are the ones
-that appear most often in the keywords of all training examples.
-% TODO Caro Please explain above sentence more precisely
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords. As keywords are
-often not directly describing the desired information, but rather
-appear close to the desired information, KWS also retrieves the lines
-around the found keyword. The number of surrounding lines retrieved is
-the average of lines in the output of the training examples.
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes
-% programs according to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming
-% knowledge~\cite{mayer2015user}. In the context of text extraction
-% through regular expressions, Programming by Example relieves the
-% developer from having to understand the whole document structure to
-% solve a single extraction task~\cite{le2014flashextract:}. In this
-% work, we refer to our interpretation of Programming by Example as
-% \emph{PBE}\@. We investigate the suitability of PBE to retrieve
-% information chunks from build logs. In the following, we explain the
-% configuration and application of PBE to chunk retrieval from CI
-% build logs.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by
-Example, we refer to them in short as \emph{examples}. The
-\emph{input} is the text of the build log file. The \emph{output} is
-an array of substrings of the log file text, representing the
-substrings that should be retrieved by the synthesized program when
-given the corresponding input file. One or multiple examples, the
-training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted. The
-PROSE program synthesis then tries to construct a program consistent
-with all training examples.
-% A program is consistent with an example if it returns the defined
-% output when executed on the defined
-% input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a
-consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn
-% uses the FlashMeta algorithm. Both are described in
-% Section~\ref{sec:rw-prose}.
-
-% TODO Caro: The following is very obvious and could apply to any
-% technique. 
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the
-synthesized regular expression program. It then returns the substring
-of the build log matched by the program or an empty string if the
-program found no match.
-
-\subsection{Random Line Retrieval}
-\label{sec:expl-rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. RLR essentially mimicks the
-situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should
-return. For a fair comparison to the other techniques (whose number of
-returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples. 
-% TODO Caro: some more details here?
-
-\subsection{Other Techniques}
-%Literature mentions further build log analysis techniques. This
-%section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information
-retrieval to identify relevant lines from a failed build
-log~\cite{amar2019mining}, as we describe in more detail in
-Section~\ref{sec:rw-bl-analysis}. The configuration for the technique
-is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not
-present in the successful build log and contain terms related to the
-given past failures.
-
-\subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a
-unifying interface. The unified interface is implemented in Ruby and
-calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE
-library~\cite{prose2019webpage}. We implemented CTS, KWS and RLR using
-R and the text2vec library~\cite{text2vec2019webpage}.
-
-\section{Study Design}
-\label{sec:study}
-
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-To investigate which techqnique is best suited to retrieve chunks from
-CI build logs we evaluate them on the
-\emph{LogChunks}~\cite{brandt2020logchunks} data set. This section
-describes our study design and which metrics we measure to answer our
-research questions. In the presentation of the results, we first focus
-on each of the three techniques and later compare them against each
-other.
-
-\subsection{LogChunks}
-For this study we created the previously published data set
-\emph{LogChunks}. It encompasses 797 build logs from Travis CI,
-stemming from a broad range of 80 GitHub repositories and 29
-programming languages. For each file, the authors manually ``labeled
-the log part (chunk) describing why the build
-failed''~\cite{brandt2020logchunks}. We include keywords, which we
-would use to search for the selected chunk within the log. In
-addition, we categorized the log chunks according to their format
-within the log. If the chunks are surrounded by the same markings
-within the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}. Random Line Retrieval
-(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
-the comparison.
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study. For each of the
-80 repositories in it, \emph{LogChunks} contains 10 build logs,
-manually labeled with the substring or \emph{chunk} describing the
-reason the build failed. Additionally, it contains (1) keywords useful
-to
-% TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category
-the substring belongs to.
-% TODO (Caro): Add details how key words were extracted. Add example?
-
-% TODO (Caro): Add more details. How was the split in numbers?
-For each repository in \emph{LogChunks}, we split the examples
-chronologically into training and test set. Therefore, we train on
-examples from past build logs and test on more recent build logs.
-
-\noindent
-\textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to
-perform best, we evaluate the techniques with different training set
-sizes. We train each technique with one to five examples from each of
-the repositories within \emph{LogChunks}. The size of the test set is
-one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk
-retrieval techniques need to be, we record the structural categories
-of the examples in the training and test sets.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output
-lines of the chunk retrieval run on the input of the test example
-($\mathit{RetrievedLines}$). As oracle in our evaluation, we save the
-desired lines from the output of the test example
-($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our
-evaluation.
-
-\vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm] \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap
-	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a
-        tool as well as what \textit{LogChunks} contains for each
-        example. 
-        % TODO (Caro) What about when a line is replicated twice?
-        % I.e., Are line numbers part of this?
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\
-	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of
-        the retrieved lines were actually desired. 
-	\item $\mbox{Recall} =
-	\dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$
-	\vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the
-        desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
-	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
-	\vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean
-        of precision and recall. We prefer F$_{1}$ to other aggregate
-        measures such as accuracy because for a
-        ``needle-in-the-haystack'' scenario, we do not want to bloat
-        our results by correctly not finding lots of irrelevant log
-        lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
-	We define a successful retrieval as one where all desired lines were
-	extracted, therefore when recall is one.
-\end{itemize}
-
-% Recall and precision of CTS and KWS vary with the number of lines
-% selected for retrieval. We evaluate the effect of varying the number
-% of extracted lines by multiplying the average number of lines
-% present in the training examples with a \emph{retrieval size factor}
-% from 0.5 to 2.5 in steps of 0.5.
-
-\section{Results}
-This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as
-baseline.
-
-\lstset{
-  language=,
-  morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass   
-Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass
-        from line 5 of sass/components/_all.sass
-        from line 6 of bulma.sass
-  \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
-  \label{lst:pbe-unsuccessful}
-\end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:r:cts}
-\begin{figure*}
-\centering
-    \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-CTS}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-CTS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-CTS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using CTS for an
-increasing number of training examples. When using one to five
-training examples, the size of the training set has no noticeable
-influence on precision, recall or F$_{1}$-score of the chunk retrieval
-with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. With increasing category count, precision,
-recall and F$_{1}$-score decrease. Especially for more than three
-categories present we have no chunk retrieval runs where all desired
-lines were extracted.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:r:kws}
-\begin{figure*}
-\centering
-    \textbf{Keyword Search (KWS)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-KWS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-KWS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using KWS for different
-numbers of training examples. The recall increases by about 12\% when
-increasing the size of the training set to more than one example,
-while the precision stays constant at around 16\%. The F$_{1}$-score
-stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. For more than one structural category in
-the training and test examples the recall decreases by about 20\% and
-the precision decreases about 6\%. For more than two structural
-categories no clear trend is visible in precision, recall or
-F$_{1}$-score for an increasing amount of categories in the training
-and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the
-% effect of the retrieval size factor on precision, recall and
-% F$_{1}$-score of chunk retrieval runs with KWS\@. The precision is
-% 19\% when retrieving half of the expected number of lines. On
-% average 9\% of the lines in the build log are retrieved then. When
-% 2.5 times the expected number of lines are retrieved, the precision
-% decreases to 10\% and a quarter of the lines in the build log are
-% retrieved on average. The recall ranges from 58\% to 75\% and the
-% F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-% 		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
-                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
-                \label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
-evaluation. Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines in 138 cases. In 89 further
-cases, an extraction program was also successfully synthesized, though
-in 59 of the 89 cases the synthesized program yielded no output. In 30
-of the 89 cases did the synthesized program only partially extract a
-subset of the desired lines. For these 30 cases, the average recall
-was 28\%. Listing \ref{lst:pbe-unsuccessful} shows an example of such
-an \emph{unsuccessful retrieval}, where the synthesized program only
-retrieved two of the four targeted lines. In 173 of the 400 cases
-could PROSE not synthesize program consistent with all of the training
-examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
-runs depend on the number of structural categories in the training and
-test examples. The figure demonstrates that program synthesis mostly
-returns exactly the desired output when there are is only one
-structural category present in the training examples. However, when
-two or more structural categories are simultaneously present in the
-examlpe set, PROSE could in most cases not synthesize a program
-consistent with all training examples. For four or more present
-categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
-precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples. When the training set
-size increases from one to two, recall and F$_{1}$-score increase by
-about 25\%, precision increases by about 10\%. For two or more
-training examples, recall and F$_{1}$-score stay around 75\% and
-precision around 96\%.
-
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. Due to the fact no one would
-seriously consider RLR in real-world scenarios, we are omitting its
-detailed graphs here. However, its results follow intuitive
-expectations:
-% TODO Caro: shortly descibre RLR graphs ommitted
-
-\subsection{Comparison of All Techniques}
-In this section, we aggregate the results from
-\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it
-each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk
-retrievals differentiated by techniques in our study. CTS and KWS
-extract some of the desired lines in 79\% and 88.5\% of the chunk
-retrieval runs. With 38.25\%, KWS also has the highest number of fully
-successful extractions, followed by PBE with 34.5\%. PBE has the
-lowest number of partial retrievals with only 18 out of 400 chunk
-retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is
-% compared in Figure~\ref{fig:recall-precision-all}. The recall of PBE
-% has a high skew towards one and zero, meaning in most cases either
-% the retrieval is successful or no relevant lines are extracted at
-% all. PBE has the highest average precision with 95\%. Chunk
-% retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% and the second highest recall with 46\%. KWS has the smallest
-% precision of the three chunk retrieval techniques. With 16\% it is
-% still higher than the precision of the RLR baseline with 7\%. KWS
-% has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of a single structural category present in the
-training examples compared to multiple categories present. For more
-than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by
-the number of structural categories present.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
-		\label{fig:success-partial-all}
-\end{figure}
-
-\begin{figure*}
-\centering
-    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
-		\label{fig:recall-precision-singlecategory-all}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
-		\label{fig:recall-precision-multicategory-all}
-\end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}  
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
-\end{itemize}
-\end{simplebox}
-
-The first section discusses for PBE, CTS and KWS separately in which
-cases they perform best. It details for which types of input build
-logs, available training examples and consumption of the retrieved
-output each technique is suited. In the following section we discuss
-which of these criteria should influence the decision to use a certain
-technique most. Based on our empirical comparison, we present a
-decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed
-chunk retrieval techniques separately. It gives recommendations which
-kind of information chunk targets are best for each technique and for
-what kind of usage the respective output is suitable.
-
-\begin{table}[tbp]
-\resizebox{\columnwidth}{!}{%
-\centering
-\begin{tabular}{llll}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabular}%
-}
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\subsubsection{Program Synthesis by Example (PBE)}
-
-\noindent
-\textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best
-results when the training examples are structurally identical. This is
-because PROSE has difficulty synthesizing OR-based programs (see
-\Cref{sec:prose:impl}). PBE is thus suited to retrieve information
-chunks that always have the same surrounding or defining internal
-structure. To extract for example the reason a build failed, the log
-passage describing the failure would always have to be started and
-ended the same way.
-
-When the training examples are of the same structure, even one or two
-two examples are enough input for PROSE to synthesize a regular
-expression program with good recall. In our study, additional training
-examples did not improve the chunk retrieval. In fact, unless they
-were in some sense redudant, adding training examples above that even
-hindered the applicability of PBE.
-
-\noindent
-\textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression
-program yields an output, PBE has high precision and recall. The tool
-clearly identifies a failing program synthesis or when no output from
-the program applied to a build log is obtained. Therefore, if there is
-an output, the user can have high confidence that it is the desired
-output. This preciseness makes output from PBE chunk retrieval
-well-suited for machine consumption.
-
-\subsubsection{Common Text Similarity (CTS)}
-\noindent
-\textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the
-fewer structural categories are present in the training and test
-examples.
-
-The number of training examples had no noticeable influence on
-precision or recall in our study. Information retrieval techniques
-like text similarity commonly learn on a higher number of examples
-than used for our study. Future work is needed to investigate how many
-examples yield improvements in the chunk retrieval over a single
-training example.
-
-% TODO Caro: I do not understand the following sentence.
-Extracting the average number of lines present in the training
-examples gives the best retrieval results for CTS, according to the
-F$_{1}$-score.
-
-\noindent
-\textbf{Retrieval Output Usage}
-% TODO Caro: reforumlate this please
-CTS has good precision and recall on average, though the precision or
-recall of a chunk retrieval run is very hard to predict from the given
-result. Therefore, retrieval output from CTS is suited to be read by a
-human. This could include semi-automated procedures such as sending
-developers an email with the extracted build failure reason.
-
-\subsubsection{Keyword Search (KWS)}
-\noindent
-\textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple
-structural categories present in the training and test examples. This
-makes KWS a good technique if there is little prior knowledge on how
-the targeted log chunk is represented in the build log. For the
-example of extracting the reason the build failed, KWS is best suited
-if a build can fail in various steps logged by different tools and no
-pre-categorization of where the build failed is available.
-
-Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the
-training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does
-improve the recall within our study but also increases the proportion
-of lines retrieved overall and therefore decreases precision.
-
-\noindent
-\textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its
-precision is the lowest. The output of a chunk retrieval with KWS is
-well-suited to be read by humans, but ill-suited for consumption by
-automated tools.
-
-\begin{figure}[tb]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
-		\label{fig:crt-recommendation}
-\end{figure}
-
-\subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we
-now want to unify our results into one recommendation scheme. In
-Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
-developers and researchers who want to retrieve information chunks
-from build logs can follow. The decision tree is built up of questions
-which either lead to more questions or to a leaf node containing a
-recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results
-from our comparison study. The recommendations could therefore be
-influenced by idiosyncrazies of our specific implementation of the
-chunk retrieval techniques as well as the logs in the \emph{LogChunks}
-data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
-answer to RQ2, about which criteria influence the suitability of a
-chunk retrieval technique. The earlier in the decision tree a
-criterion is noted, the more important it is when distinguishing the
-techniques.
-
-The first and most important aspect are the structural categories. Are
-the information chunks one would like to retrieve always presented in
-the same structural way within the build logs? Then the information
-chunks in all training examples and the analyzed build log are in the
-same structural category.
-
-If the information chunks are from multiple structural categories,
-i.e. they are not represented in the same structural way within the
-build logs, and recall is more important than precision we recommend
-to use KWS\@. If the representations are from multiple structural
-categories and precision is more important than recall to the user we
-recommend CTS\@. We also recommend CTS when the representations are
-from one structural category, when the user does not require a high
-confidence in the precision or recall of the outcome and when the user
-would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user
-wishes a high confidence in the correctness of the output or prefers
-no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper. Such a super analyzer would likely always first employ PBE
-(because of its high accuracy), followed by a combination of CTS and
-KWS. Other than initial setup and training time, there should be no
-downside to this approach if it is implemented in a transparent way to
-the underlying technique: the output of the super analyzer could
-include from which sub-tool it originated and thus facilitate
-automatic on-ward processing or interpretation of the result.
-
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable
-chunk retrieval technique we describe two concrete examples: a
-researcher investigating why CI builds fail and a software team
-wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI
-are caused by a small or by a large group of test cases. They gather
-CI build logs from various projects, which are their only available
-data source. The task of the researcher is to extract the names of the
-failing test cases from each build log. When they use our
-recommendation scheme to select a chunk retrieval technique, they
-first have to estimate how uniform the representation of the failing
-test cases is in the investigated build logs. As the researcher is
-covering a wide range of build tools and development languages, the
-log chunks they target are in various, non-predictable structural
-representations. The next question is whether they value precision
-over recall. As they have to manually inspect the results of both CTS
-and KWS, they choose recall over precision to avoid having to inspect
-the whole log in case the relevant information chunk was not
-retrieved. Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the
-retrieval results, they have to first separate the CI build logs
-according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they
-can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor
-the performance of the phases within their CI build. They are using
-Travis CI, which measures the duration of build phases and documents
-them within the build log. As all log statements that report timing
-measurements are formatted the same way, the targeted log chunks are
-from one structural category. Therefore the development team can use
-PBE to retrieve the duration of a build phase as well as its name.
-
-\section{Threats to Validity}
-There are several threats to the validity of the conclusions of our
-work.
-
-\noindent
-\textbf{Implementation}
-\label{sec:prose:impl}
-% TODO we need to say something about why we think that these
-% limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk
-retrieval techniques and the libraries we used. Our implementation of
-PBE is based on the program synthesis provided by PROSE\@. The
-idiosyncrazies of this framework influence our PBE results. Other
-frameworks similar to PROSE might have somewhat different strengths
-and weaknesses. For example, the need for examples from a single
-structural category stems from the fact that PROSE cannot learn
-regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}. PROSE introduced this constraint to
-keep the synthesis performance reasonable. At the same time, this is
-clearly a current theoretical challenge of all PBE implementations,
-and we therefore attribute it to the technique itself, rather than the
-specific implementation.
-
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec}
-and the way it splits strings into word tokens. On the other hand,
-{\tt text2vec} is the de-facto standard library to do word embeddings
-in R. We intentionally chose a simple, minimally configured and tuned
-approach to compare against. Tuning the text similarity
-meta-parameters more to the specific use case of chunk retrieval from
-build logs would yield better chunk retrieval results.
-
-\noindent
-\textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build
-logs from the \emph{LogChunks} data set. It only consists of build
-logs from open source projects and therefore it is not clear whether
-our results are generalizable to industry projects. We only collected
-build logs from Travis CI, however we chose to evaluate on an
-information chunk whose format is not dependent on Travis CI\@. This
-is because the reason the build failed is described within the build
-logs by the tools themselves and not the Travis CI environment.
-
-\noindent
-\textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples. We chose this small training set
-size as the training examples have to be provided per repository and
-we expect a developer to not want to provide more examples than the
-small numbers we evaluated on.
-
-\noindent
-\textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural
-categories than with one category.
-% TODO Caro: Please explain the following further. Why does a
-% realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in
-many cases has only one or few structural categories.
-
 \section{Future Work}
@@
 \end{itemize}
-
-\section{Conclusion}
-\label{sec:conclusion-fw}
-The goal of this paper was to support researchers and developers in
-their decision on how to analyze build logs. We implemented and
-compared three different chunk retrieval techniques on our data set
-\emph{LogChunks}, composed of 797 manually labeled build logs from a
-broad range of 80 repositories. Our results show that the structural
-representation of the targeted information in the build logs is the
-main factor to consider when choosing a suitable technique. Secondary
-factors are the desired confidence into recall and precision of the
-produced output and whether precision or recall is more important for
-the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper.

### 2020-04-02 tse-paper/content.tex
split into separate files per section

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
-
-\lstset{
-  morekeywords={},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  stringstyle=\color{Plum},
-	frame=single,
-  extendedchars=false,
-  texcl=false,
-  aboveskip=\baselineskip,
-  belowskip=0pt
-}
-
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within the build.
-The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
-study.
-Our goal was to classify how and what for researchers use build logs as a source
-of data (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
-build tools.
-
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
-examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
-
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
-\end{itemize}
-\end{simplebox}
-
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
-
-We implement and evaluate three chunk retrieval techniques:
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
-  a regular expression matching the given chunks within the build logs.
-  \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
-  \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
-  the occurrence of specific trigger words.
-\end{itemize}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}  
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
-  \end{lstlisting}  
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}  
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-e:xample-2} show two exemplary log chunks
-from Android/Gradle build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
-
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence.
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
-  are present in the training examples.
-\end{itemize}
-
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
-%         \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
-%           \item a keyword search approach (KWS).
-%         \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
-
-We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
-recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Kitchenham's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO Caro: update
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-% TODO Caro: please write a draft for this :-)
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool). many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
-work from system log analysis.
-
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of
-build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error
-types such as dependency mismatches are the most prominent cause of
-build failures at Google. In addition, they notice that most failures
-are resolved within two builds. They based their analyses on sets of
-build logs collected from industry partners. They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects and find that most builds fail because of failing
-tests. For most projects, over half of the failed builds follow a
-previous failed build. Rausch et al.'s data shows that most failures
-occur in the second half of the build runtime, which can cause long
-delays in the feedback loop, especially when builds are automatically
-retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones. They determine that testing failures are
-more common than compilation errors. Open source builds fail most
-often because of unit tests, whereas release preparations are the
-primary cause in industrial projects. Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data. They classify build failures from \emph{TravisTorrent}
-according to whether they were caused by an environmental failure or
-caused by a developer change. Their analysis starts with manual
-categorization of build logs. They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers
-presented in this section create parsers and regular expression-based
-programs. This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article. Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve. By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why
-their build failed. Several researchers investigate how to support
-developers in working with verbose build logs. Vassallo et
-al.~\cite{vassallo2018un-break} try to shorten the time it takes
-developers to understand build logs. They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-%The hint generators leverage this structured access to the
-%information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed. In a qualitative study
-they observed that highlighting the locality and context of an issue
-is helpful to programmers.
-%Their tool BART is published as a Jenkins
-%Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs. As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect. Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures. Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a
-basic structuring of the build logs within their log viewer using
-\emph{log folds}~\cite{travis2019logfolds}. They add fold identifiers
-around common commands and setup or teardown build phases and collapse
-the contained lines by default.
-
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log
-files produced during runtime. A main difference between build logs
-and system logs is that system logs are fundamentally structured
-through events. Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}. Figure \ref{lst:system-log} shows
-example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to
-separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}. Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters. The output of a log
-parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}. This structured log is then
-the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational
-%profiling~\cite{nagappan2009efficiently},
-%debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}. Xu et
-%al.~\cite{xu2009detecting} leverage the connection of log statements
-%to the source code producing them to separate messages into constant
-%and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied
-to build logs. One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies. Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of
-%events. A similar approach could also be applied to build logs to
-%determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques. Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g. by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
-  \end{lstlisting}  
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques} The
-% techniques we investigate are based on existing methods of
-% Programming by Example.%, information extraction and information
-% retrieval. This section presents different Programming by Example
-% resources surrounding the PROSE library. We explain its generic
-% program synthesis algorithm and how PROSE synthesizes text
-% extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program
-synthesis that enables users to automate repetitive tasks, without
-them having to explicitly codify a computer program. One has to
-provide prototypical examples of the input and the desired output. A
-synthesis algorithm tries to create a program (based on a regular
-language) that transforms the input to the output. The minimum working
-condition is for this when replayed on the examples inputs is to
-provide the specified output, but, hopefully, PBE is as close as
-possbile to the user's intention and thus also works on a different
-and larger set of inputs. This section introduces the theoretical
-foundations of the program synthesis algorithm of the \emph{PROgram
-Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research. Next, this
-section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our
-chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and
-Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
-synthesis in the Microsoft PROSE framework. FlashMeta separates the
-inductive synthesis algorithm from the domain specific capabilities of
-the desired program by encoding the possible program space in a domain
-specific language (DSL). The user specifies the desired program
-behavior by providing in/output examples (I/O examples). FlashMeta
-uses \emph{witness functions}, provided by the DSL, to divide the
-synthesis into smaller subtasks. For each of these subtasks it
-enumerates all possible programs that solve the subtask consistent
-with the set of I/O examples. A program is consistent with a set of
-I/O examples if, for each input example, it produces the corresponding
-output~\cite{mitchell1982generalization}. The possible subprograms are
-joined and stored in a \emph{version space algebra}
-(VSA)~\cite{mitchell1982generalization}. This a tree structure, which
-space-efficiently saves candidate programs for tasks by sharing common
-subexpressions. Next, FlashMeta ranks the enumerated programs
-according to which ones the user most likely intended. The DSL also
-provides the ranking characteristics. From the ranked VSA, FlashMeta
-can then return a ranked list of complete programs consistent with the
-user's example.
-
-% In addition to I/O examples of the intended program, the user can
-% also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized
-% program.
-
-% The different applications of PROSE presented in the following
-% paragraphs were all eventually implemented as DSLs for the FlashMeta
-% synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
-for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text,
-% websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs
-from semi-structured text based on regular expressions. Users can
-extract multiple fields and structure them with hierarchy and
-sequence.
-% FlashExtract synthesizes programs to extract each of the fields
-% leveraging the information about hierarchical containment and
-% sequentiality. It eliminates the need for the user to understand the
-% entire structure of the processed document and decreases the effort
-% of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of
-two cut positions. A position is either specified by an absolute
-character index or by a pair of two regular expressions. The first
-regular expression matches the substring directly before the
-characterized position, the second regular expression matches the
-substring directly after. A regular expression in FlashExtract is a
-concatenation of tokens, e.g.\ standard character classes or string
-literals frequently occurring in the input examples. Figure
-\ref{lst:prose-program} shows a text extraction program synthesized by
-FlashExtract. This program defines the first position as after a colon
-followed by a newline character and before a piece of text with all
-capital letters. It defines the second position as before two newline
-characters.
-
-Apart from automatic completion in Excel
-spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for
-two other Microsoft product features: Microsoft's system log analysis
-tool Azure Monitor lets users define custom log
-fields~\cite{azure2019custom}. The ConvertFrom-String function in
-PowerShell allows a user to specify an example template to extract
-hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build
-logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}  
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
-\section{Chunk Retrieval Techniques}
-\label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval
-techniques we study in this article, namely program synthesis by
-example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that
-represent a specific, targeted information.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically
-retrieve pieces of information that appear literally in the build
-logs, i.e., techniques that do not aggreagte, combine, or deducted
-information. We call such pieces of information from build logs
-\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and
-parser to analyze the entire structure of build logs, but focus on
-ad-hoc extracting just one specific piece of information per
-configuration.
-
-With the term \textit{configuration,} we abstract over the training
-and parametrization that different techniques require in different
-forms. A configuration can be explicitly stated or implicitly dervied
-by learning through provided examples. It is therefore a manual
-specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log. Each chunk
-retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word). The
-granularity might be adjustable by configuration. \emph{Running a
-chunk retrieval technique} means to execute a fully configured
-technique to consumes as input a build log in plain text format and to
-produce an array as output. The array consists of substrings of the
-build log text.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[]
-\centering
-\caption{Overview of the described chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
-\toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
-\bottomrule
-\end{tabularx}
-\label{tab:ctr}
-\end{table*}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual
-% software
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model. We
-% investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs. In the following we will explain
-% the concept of how we apply text similarity to information retrieval
-% from CI build logs, which we refer to as \emph{CTS}\@.
-
-\subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use
-the same concept of examples as for PBE\@
-% TODO Caro: More details on this. How do you 'apply' VSM? On what?
-and apply the Vector Space Model~\cite{schutze2008introduction}. The
-lines of the output strings of the training examples define our search
-query. The algorithm splits the search query into single lines and
-identifies tokens, in our case words. Then we build a
-document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words. Finally, the
-algorithm applies TF-IDF to the matrix, a best practice for natural
-language queries~\cite{lee1997document}.
-
-\subsubsection{Application}
-To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the output of the
-training examples. The algorithm calculates the cosine
-similarity~\cite{korenius2007principal} to compare each line of the
-build log with each line of the search query. After summing up the
-similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity. The average number of
-lines in the outputs of the training examples determines how many of
-the most similar lines are returned as the output of the retrieval
-run.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
-When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad-hoc approach they
-use is to search for related keywords. Indeed, this was one of the
-most common approaches we took when searching for the reason the build
-failed within a log while creating the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers
-% use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs. In
-% the following we will explain how we use simple keyword search to
-% retrieve information from CI build logs, which we refer to as
-% \emph{KWS}\@.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@. To better
-compare KWS with PBE and CTS, we also configure it through examples.
-We associate each example with keywords which appear in the targeted
-chunk or close to it. The configuring keywords for KWS are the ones
-that appear most often in the keywords of all training examples.
-% TODO Caro Please explain above sentence more precisely
-
-\subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords. As keywords are
-often not directly describing the desired information, but rather
-appear close to the desired information, KWS also retrieves the lines
-around the found keyword. The number of surrounding lines retrieved is
-the average of lines in the output of the training examples.
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes
-% programs according to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming
-% knowledge~\cite{mayer2015user}. In the context of text extraction
-% through regular expressions, Programming by Example relieves the
-% developer from having to understand the whole document structure to
-% solve a single extraction task~\cite{le2014flashextract:}. In this
-% work, we refer to our interpretation of Programming by Example as
-% \emph{PBE}\@. We investigate the suitability of PBE to retrieve
-% information chunks from build logs. In the following, we explain the
-% configuration and application of PBE to chunk retrieval from CI
-% build logs.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by
-Example, we refer to them in short as \emph{examples}. The
-\emph{input} is the text of the build log file. The \emph{output} is
-an array of substrings of the log file text, representing the
-substrings that should be retrieved by the synthesized program when
-given the corresponding input file. One or multiple examples, the
-training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted. The
-PROSE program synthesis then tries to construct a program consistent
-with all training examples.
-% A program is consistent with an example if it returns the defined
-% output when executed on the defined
-% input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a
-consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn
-% uses the FlashMeta algorithm. Both are described in
-% Section~\ref{sec:rw-prose}.
-
-% TODO Caro: The following is very obvious and could apply to any
-% technique. 
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the
-synthesized regular expression program. It then returns the substring
-of the build log matched by the program or an empty string if the
-program found no match.
-
-\subsection{Random Line Retrieval}
-\label{sec:expl-rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. RLR essentially mimicks the
-situation of guessing purely blindly which lines might be interesting.
-The only configuration option for RLR is the number of lines it should
-return. For a fair comparison to the other techniques (whose number of
-returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples. 
-% TODO Caro: some more details here?
-
-\subsection{Other Techniques}
-%Literature mentions further build log analysis techniques. This
-%section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information
-retrieval to identify relevant lines from a failed build
-log~\cite{amar2019mining}, as we describe in more detail in
-Section~\ref{sec:rw-bl-analysis}. The configuration for the technique
-is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not
-present in the successful build log and contain terms related to the
-given past failures.
-
-\subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a
-unifying interface. The unified interface is implemented in Ruby and
-calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE
-library~\cite{prose2019webpage}. We implemented CTS, KWS and RLR using
-R and the text2vec library~\cite{text2vec2019webpage}.
-
-\section{Study Design}
-\label{sec:study}
-
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-To investigate which techqnique is best suited to retrieve chunks from
-CI build logs we evaluate them on the
-\emph{LogChunks}~\cite{brandt2020logchunks} data set. This section
-describes our study design and which metrics we measure to answer our
-research questions. In the presentation of the results, we first focus
-on each of the three techniques and later compare them against each
-other.
-
-\subsection{LogChunks}
-For this study we created the previously published data set
-\emph{LogChunks}. It encompasses 797 build logs from Travis CI,
-stemming from a broad range of 80 GitHub repositories and 29
-programming languages. For each file, the authors manually ``labeled
-the log part (chunk) describing why the build
-failed''~\cite{brandt2020logchunks}. We include keywords, which we
-would use to search for the selected chunk within the log. In
-addition, we categorized the log chunks according to their format
-within the log. If the chunks are surrounded by the same markings
-within the log we assign them the same structural category.
-
-For the comparison, we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}. Random Line Retrieval
-(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
-the comparison.
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study. For each of the
-80 repositories in it, \emph{LogChunks} contains 10 build logs,
-manually labeled with the substring or \emph{chunk} describing the
-reason the build failed. Additionally, it contains (1) keywords useful
-to
-% TODO Caro uniquely?
-identify the substring in the log  and (2) which structural category
-the substring belongs to.
-% TODO (Caro): Add details how key words were extracted. Add example?
-
-% TODO (Caro): Add more details. How was the split in numbers?
-For each repository in \emph{LogChunks}, we split the examples
-chronologically into training and test set. Therefore, we train on
-examples from past build logs and test on more recent build logs.
-
-\noindent
-\textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to
-perform best, we evaluate the techniques with different training set
-sizes. We train each technique with one to five examples from each of
-the repositories within \emph{LogChunks}. The size of the test set is
-one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk
-retrieval techniques need to be, we record the structural categories
-of the examples in the training and test sets.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output
-lines of the chunk retrieval run on the input of the test example
-($\mathit{RetrievedLines}$). As oracle in our evaluation, we save the
-desired lines from the output of the test example
-($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our
-evaluation.
-
-\vspace{0.2cm}
-\begin{itemize}[leftmargin=0.4cm] \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap
-	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
-        True positives are lines that appear both in the output of a
-        tool as well as what \textit{LogChunks} contains for each
-        example. 
-        % TODO (Caro) What about when a line is replicated twice?
-        % I.e., Are line numbers part of this?
-	\item $\mbox{Precision} = \dfrac{|\mathit{True\
-	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
-        Precision of a chunk retrieval describes which proportion of
-        the retrieved lines were actually desired. 
-	\item $\mbox{Recall} =
-	\dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$
-	\vspace{0.2cm} \\
-        Recall of a chunk retrieval describes which proportion of the
-        desired lines were retrieved.
-	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
-	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
-	\vspace{0.2cm}\\
-        In addition, we calculate the F$_{1}$-score, the harmonic mean
-        of precision and recall. We prefer F$_{1}$ to other aggregate
-        measures such as accuracy because for a
-        ``needle-in-the-haystack'' scenario, we do not want to bloat
-        our results by correctly not finding lots of irrelevant log
-        lines.
-	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
-	We define a successful retrieval as one where all desired lines were
-	extracted, therefore when recall is one.
-\end{itemize}
-
-% Recall and precision of CTS and KWS vary with the number of lines
-% selected for retrieval. We evaluate the effect of varying the number
-% of extracted lines by multiplying the average number of lines
-% present in the training examples with a \emph{retrieval size factor}
-% from 0.5 to 2.5 in steps of 0.5.
-
-\section{Results}
-This section presents the results for PBE, CTS and KWS separately.
-Afterwards we compare the three techniques with each other and RLR as
-baseline.
-
-\lstset{
-  language=,
-  morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
-  keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass   
-Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
-        on line 86 of sass/components/dropdown.sass
-        from line 5 of sass/components/_all.sass
-        from line 6 of bulma.sass
-  \end{lstlisting}  
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
-  \label{lst:pbe-unsuccessful}
-\end{figure}
-
-\subsection{Common Text Similarity (CTS)}
-\label{sec:r:cts}
-\begin{figure*}
-\centering
-    \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-CTS}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-CTS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-CTS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using CTS for an
-increasing number of training examples. When using one to five
-training examples, the size of the training set has no noticeable
-influence on precision, recall or F$_{1}$-score of the chunk retrieval
-with CTS.
-
-\Cref{fig:recall-precision-categorycount-CTS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. With increasing category count, precision,
-recall and F$_{1}$-score decrease. Especially for more than three
-categories present we have no chunk retrieval runs where all desired
-lines were extracted.
-
-\subsection{Keyword Search (KWS)}
-\label{sec:r:kws}
-\begin{figure*}
-\centering
-    \textbf{Keyword Search (KWS)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
-		\label{fig:recall-precision-examplecount-KWS}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
-		\label{fig:recall-precision-categorycount-KWS}
-\end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
-\end{figure*}
-
-\Cref{fig:recall-precision-examplecount-KWS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using KWS for different
-numbers of training examples. The recall increases by about 12\% when
-increasing the size of the training set to more than one example,
-while the precision stays constant at around 16\%. The F$_{1}$-score
-stays around 26\%.
-
-\Cref{fig:recall-precision-categorycount-KWS} shows the same
-measurements for an increasing number of structural categories in the
-training and test examples. For more than one structural category in
-the training and test examples the recall decreases by about 20\% and
-the precision decreases about 6\%. For more than two structural
-categories no clear trend is visible in precision, recall or
-F$_{1}$-score for an increasing amount of categories in the training
-and test examples.
-
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the
-% effect of the retrieval size factor on precision, recall and
-% F$_{1}$-score of chunk retrieval runs with KWS\@. The precision is
-% 19\% when retrieving half of the expected number of lines. On
-% average 9\% of the lines in the build log are retrieved then. When
-% 2.5 times the expected number of lines are retrieved, the precision
-% decreases to 10\% and a quarter of the lines in the build log are
-% retrieved on average. The recall ranges from 58\% to 75\% and the
-% F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-% 		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
-% 		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
-                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
-                \label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
-evaluation. Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines in 138 cases. In 89 further
-cases, an extraction program was also successfully synthesized, though
-in 59 of the 89 cases the synthesized program yielded no output. In 30
-of the 89 cases did the synthesized program only partially extract a
-subset of the desired lines. For these 30 cases, the average recall
-was 28\%. Listing \ref{lst:pbe-unsuccessful} shows an example of such
-an \emph{unsuccessful retrieval}, where the synthesized program only
-retrieved two of the four targeted lines. In 173 of the 400 cases
-could PROSE not synthesize program consistent with all of the training
-examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
-runs depend on the number of structural categories in the training and
-test examples. The figure demonstrates that program synthesis mostly
-returns exactly the desired output when there are is only one
-structural category present in the training examples. However, when
-two or more structural categories are simultaneously present in the
-examlpe set, PROSE could in most cases not synthesize a program
-consistent with all training examples. For four or more present
-categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
-precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples. When the training set
-size increases from one to two, recall and F$_{1}$-score increase by
-about 25\%, precision increases by about 10\%. For two or more
-training examples, recall and F$_{1}$-score stay around 75\% and
-precision around 96\%.
-
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. Due to the fact no one would
-seriously consider RLR in real-world scenarios, we are omitting its
-detailed graphs here. However, its results follow intuitive
-expectations:
-% TODO Caro: shortly descibre RLR graphs ommitted
-
-\subsection{Comparison of All Techniques}
-In this section, we aggregate the results from
-\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it
-each other.
-
-\Cref{fig:success-partial-all} compares the success of chunk
-retrievals differentiated by techniques in our study. CTS and KWS
-extract some of the desired lines in 79\% and 88.5\% of the chunk
-retrieval runs. With 38.25\%, KWS also has the highest number of fully
-successful extractions, followed by PBE with 34.5\%. PBE has the
-lowest number of partial retrievals with only 18 out of 400 chunk
-retrieval runs.
-
-% The averaged precision, recall and F$_{1}$-score f all techniques is
-% compared in Figure~\ref{fig:recall-precision-all}. The recall of PBE
-% has a high skew towards one and zero, meaning in most cases either
-% the retrieval is successful or no relevant lines are extracted at
-% all. PBE has the highest average precision with 95\%. Chunk
-% retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% and the second highest recall with 46\%. KWS has the smallest
-% precision of the three chunk retrieval techniques. With 16\% it is
-% still higher than the precision of the RLR baseline with 7\%. KWS
-% has the highest recall of all techniques with 70\%.
-
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of a single structural category present in the
-training examples compared to multiple categories present. For more
-than one category being present, the recall of PBE decreases greatly.
-For CTS and KWS the values also decrease, while RLR is not affected by
-the number of structural categories present.
-
-\begin{figure}[!t]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
-		\label{fig:success-partial-all}
-\end{figure}
-
-\begin{figure*}
-\centering
-    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
-		\label{fig:recall-precision-singlecategory-all}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-                		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
-		\label{fig:recall-precision-multicategory-all}
-\end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
-\end{figure*}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% TODO Rather than giving them once (``friss und stirb''), better to incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}  
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
-\end{itemize}
-\end{simplebox}
-
-The first section discusses for PBE, CTS and KWS separately in which
-cases they perform best. It details for which types of input build
-logs, available training examples and consumption of the retrieved
-output each technique is suited. In the following section we discuss
-which of these criteria should influence the decision to use a certain
-technique most. Based on our empirical comparison, we present a
-decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed
-chunk retrieval techniques separately. It gives recommendations which
-kind of information chunk targets are best for each technique and for
-what kind of usage the respective output is suitable.
-
-\begin{table}[tbp]
-\resizebox{\columnwidth}{!}{%
-\centering
-\begin{tabular}{llll}
-  \toprule
-  & PBE & CTS & KWS \\
-  \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\ 
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
-  Output Consumption by & program & human & human \\ 
-  \bottomrule
-\end{tabular}%
-}
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
-\label{tab:single-technique-recommendations}
-\end{table}
-
-\subsubsection{Program Synthesis by Example (PBE)}
-
-\noindent
-\textbf{Configuration and Input}
-Our study results show that chunk retrieval with PBE gives best
-results when the training examples are structurally identical. This is
-because PROSE has difficulty synthesizing OR-based programs (see
-\Cref{sec:prose:impl}). PBE is thus suited to retrieve information
-chunks that always have the same surrounding or defining internal
-structure. To extract for example the reason a build failed, the log
-passage describing the failure would always have to be started and
-ended the same way.
-
-When the training examples are of the same structure, even one or two
-two examples are enough input for PROSE to synthesize a regular
-expression program with good recall. In our study, additional training
-examples did not improve the chunk retrieval. In fact, unless they
-were in some sense redudant, adding training examples above that even
-hindered the applicability of PBE.
-
-\noindent
-\textbf{Retrieval Output Usage}
-If the program synthesis succeeds and applying the regular expression
-program yields an output, PBE has high precision and recall. The tool
-clearly identifies a failing program synthesis or when no output from
-the program applied to a build log is obtained. Therefore, if there is
-an output, the user can have high confidence that it is the desired
-output. This preciseness makes output from PBE chunk retrieval
-well-suited for machine consumption.
-
-\subsubsection{Common Text Similarity (CTS)}
-\noindent
-\textbf{Configuration and Input}
-Similar to PBE, chunk retrieval using CTS yields better results the
-fewer structural categories are present in the training and test
-examples.
-
-The number of training examples had no noticeable influence on
-precision or recall in our study. Information retrieval techniques
-like text similarity commonly learn on a higher number of examples
-than used for our study. Future work is needed to investigate how many
-examples yield improvements in the chunk retrieval over a single
-training example.
-
-% TODO Caro: I do not understand the following sentence.
-Extracting the average number of lines present in the training
-examples gives the best retrieval results for CTS, according to the
-F$_{1}$-score.
-
-\noindent
-\textbf{Retrieval Output Usage}
-% TODO Caro: reforumlate this please
-CTS has good precision and recall on average, though the precision or
-recall of a chunk retrieval run is very hard to predict from the given
-result. Therefore, retrieval output from CTS is suited to be read by a
-human. This could include semi-automated procedures such as sending
-developers an email with the extracted build failure reason.
-
-\subsubsection{Keyword Search (KWS)}
-\noindent
-\textbf{Configuration and Input}
-KWS has a higher recall than the two other techniques for multiple
-structural categories present in the training and test examples. This
-makes KWS a good technique if there is little prior knowledge on how
-the targeted log chunk is represented in the build log. For the
-example of extracting the reason the build failed, KWS is best suited
-if a build can fail in various steps logged by different tools and no
-pre-categorization of where the build failed is available.
-
-Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the
-training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does
-improve the recall within our study but also increases the proportion
-of lines retrieved overall and therefore decreases precision.
-
-\noindent
-\textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its
-precision is the lowest. The output of a chunk retrieval with KWS is
-well-suited to be read by humans, but ill-suited for consumption by
-automated tools.
-
-\begin{figure}[tb]
-		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
-		\label{fig:crt-recommendation}
-\end{figure}
-
-\subsection{Recommendation of Suitable Techniques}
-After discussing the three chunk retrieval techniques separately we
-now want to unify our results into one recommendation scheme. In
-Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
-developers and researchers who want to retrieve information chunks
-from build logs can follow. The decision tree is built up of questions
-which either lead to more questions or to a leaf node containing a
-recommended technique.
-
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results
-from our comparison study. The recommendations could therefore be
-influenced by idiosyncrazies of our specific implementation of the
-chunk retrieval techniques as well as the logs in the \emph{LogChunks}
-data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
-answer to RQ2, about which criteria influence the suitability of a
-chunk retrieval technique. The earlier in the decision tree a
-criterion is noted, the more important it is when distinguishing the
-techniques.
-
-The first and most important aspect are the structural categories. Are
-the information chunks one would like to retrieve always presented in
-the same structural way within the build logs? Then the information
-chunks in all training examples and the analyzed build log are in the
-same structural category.
-
-If the information chunks are from multiple structural categories,
-i.e. they are not represented in the same structural way within the
-build logs, and recall is more important than precision we recommend
-to use KWS\@. If the representations are from multiple structural
-categories and precision is more important than recall to the user we
-recommend CTS\@. We also recommend CTS when the representations are
-from one structural category, when the user does not require a high
-confidence in the precision or recall of the outcome and when the user
-would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user
-wishes a high confidence in the correctness of the output or prefers
-no output over output with low recall, we recommend PBE\@.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper. Such a super analyzer would likely always first employ PBE
-(because of its high accuracy), followed by a combination of CTS and
-KWS. Other than initial setup and training time, there should be no
-downside to this approach if it is implemented in a transparent way to
-the underlying technique: the output of the super analyzer could
-include from which sub-tool it originated and thus facilitate
-automatic on-ward processing or interpretation of the result.
-
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
-To illustrate how one would use our decision tree to find a suitable
-chunk retrieval technique we describe two concrete examples: a
-researcher investigating why CI builds fail and a software team
-wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI
-are caused by a small or by a large group of test cases. They gather
-CI build logs from various projects, which are their only available
-data source. The task of the researcher is to extract the names of the
-failing test cases from each build log. When they use our
-recommendation scheme to select a chunk retrieval technique, they
-first have to estimate how uniform the representation of the failing
-test cases is in the investigated build logs. As the researcher is
-covering a wide range of build tools and development languages, the
-log chunks they target are in various, non-predictable structural
-representations. The next question is whether they value precision
-over recall. As they have to manually inspect the results of both CTS
-and KWS, they choose recall over precision to avoid having to inspect
-the whole log in case the relevant information chunk was not
-retrieved. Therefore, our decision tree recommends them to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the
-retrieval results, they have to first separate the CI build logs
-according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they
-can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor
-the performance of the phases within their CI build. They are using
-Travis CI, which measures the duration of build phases and documents
-them within the build log. As all log statements that report timing
-measurements are formatted the same way, the targeted log chunks are
-from one structural category. Therefore the development team can use
-PBE to retrieve the duration of a build phase as well as its name.
-
-\section{Threats to Validity}
-There are several threats to the validity of the conclusions of our
-work.
-
-\noindent
-\textbf{Implementation}
-\label{sec:prose:impl}
-% TODO we need to say something about why we think that these
-% limtiations do not actually harm our results
-Our results depend on the implementation of the investigated chunk
-retrieval techniques and the libraries we used. Our implementation of
-PBE is based on the program synthesis provided by PROSE\@. The
-idiosyncrazies of this framework influence our PBE results. Other
-frameworks similar to PROSE might have somewhat different strengths
-and weaknesses. For example, the need for examples from a single
-structural category stems from the fact that PROSE cannot learn
-regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}. PROSE introduced this constraint to
-keep the synthesis performance reasonable. At the same time, this is
-clearly a current theoretical challenge of all PBE implementations,
-and we therefore attribute it to the technique itself, rather than the
-specific implementation.
-
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec}
-and the way it splits strings into word tokens. On the other hand,
-{\tt text2vec} is the de-facto standard library to do word embeddings
-in R. We intentionally chose a simple, minimally configured and tuned
-approach to compare against. Tuning the text similarity
-meta-parameters more to the specific use case of chunk retrieval from
-build logs would yield better chunk retrieval results.
-
-\noindent
-\textbf{Data Set}
-The outcomes of our comparison study are highly dependent on the build
-logs from the \emph{LogChunks} data set. It only consists of build
-logs from open source projects and therefore it is not clear whether
-our results are generalizable to industry projects. We only collected
-build logs from Travis CI, however we chose to evaluate on an
-information chunk whose format is not dependent on Travis CI\@. This
-is because the reason the build failed is described within the build
-logs by the tools themselves and not the Travis CI environment.
-
-\noindent
-\textbf{Training Set Size}
-Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples. We chose this small training set
-size as the training examples have to be provided per repository and
-we expect a developer to not want to provide more examples than the
-small numbers we evaluated on.
-
-\noindent
-\textbf{Few Samples with Many Structural Categories}
-Our comparison study shows fewer measurements with many structural
-categories than with one category.
-% TODO Caro: Please explain the following further. Why does a
-% realistic data set only have one or few structural categories?
-This stems from the fact that we use a realistic data set which in
-many cases has only one or few structural categories.
-
-\section{Future Work}
-\todo{survey build logs tools in industry}
-
-There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
-  \emph{LogChunks} data set \cite{} specifically for the comparative
-  study in this paper, though it can be the basis for various further
-  analyses of build log data. The keywords, for example, can be
-  investigated to answer which keywords are used to search for the
-  reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and
-  tested each chunk retrieval technique on examples from the same
-  repository. We propose to analyze how techniques could be trained
-  across repositories, building the cornerstones for build
-  environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
-  paper investigates the three chunk retrieval techniques PBE, CTS and
-  KWS\@. Our study design can be reused to evaluate other build log
-  analysis techniques, such as the diff and information retrieval
-  approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We
-  investigated basic configurations of existing techniques applied to
-  chunk retrieval from build logs. In a next step, each of these
-  techniques could be refined to better approach the domain of build
-  logs. The \emph{LogChunks} data set and our study results act as a
-  baseline to benchmark such technique improvements. We propose the
-  following improvements:
-    \begin{itemize}
-      \item \textbf{Custom Ranking and Tokens for PBE} The program
-      synthesis through PROSE ranks possible programs according to
-      what the user most likely intended. One could adapt the ranking
-      rules provided by the FlashExtract DSL to fit common build log
-      chunk retrieval tasks. FlashExtract includes special tokens when
-      enumerating possible regular expressions. One could extend these
-      with tokens found in build logs, such as ``-'',``='',``ERROR''
-      or ``[OK''.
-      \item \textbf{Meta-Parameter Optimization for CTS} Information
-      retrieval techniques have various meta-parameters which can be
-      optimized for the specific use
-      case~\cite{panichella2016parameterizing}. We propose to further
-      investigate improvements in preprocessing of the log text, in
-      tokenization of the log lines into terms and in stop words
-      lists.
-    \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
-  analysis of the output produced by the chunk retrieval focuses on
-  precision and recall. We propose to investigate how useful these
-  outputs are to developers through controlled experiments.
-\end{itemize}
+\input{0-introduction.tex}
+\input{1-lit-survey.tex}
+%\input{2-rw.tex}
+\input{3-techniques.tex}
+\input{4-study-design.tex}
+\input{5-results.tex}
+\input{6-discussion.tex}
+\input{7-threats.tex}
+\input{8-future-work.tex}
 

### 2020-04-02 tse-paper/content.tex
Run long lines

--- 2020-04-01 tse-paper/content.tex
@@
-% TODO: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques exist 2) we implement (for a lack of readily available implementations) and compare the most promising ones 3) we draw conclusions for when to use which technique
-
-% TODO: Include term predictive CI, link to FB paper and https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
-% TODO: What about the alternate solution, installing plugins to report precise data? Ie., maven plugins
+% Todo: Introduction structure
+% 0) we introduce & define the problem 1) we survey which techniques
+exist 2) we implement (for a lack of readily available implementations)
+and compare the most promising ones 3) we draw conclusions for when to
+use which technique
+
+% TODO: Include term predictive CI, link to FB paper and
+https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
+
+% TODO: What about the alternate solution, installing plugins to report
+precise data? Ie., maven plugins
 % - Lots of effort
@@
 
-% TODO It would be futile to compare our techniques with one of the existing manual regex parsers, as (a) as our literature survey showed, their scope is mainly limited to the Java ecosystem and (b) whether they would work or not would be randomly based on whether the project we select exhibits features their regular expressions were trained for.
+% TODO It would be futile to compare our techniques with one of the
+existing manual regex parsers, as (a) as our literature survey showed,
+their scope is mainly limited to the Java ecosystem and (b) whether
+they would work or not would be randomly based on whether the project
+we select exhibits features their regular expressions were trained for.
 Finally, they are not really automatic
@@
 Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.  Many software projects use
+engineering~\cite{hilton2016usage}.
+Many software projects use
 CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
@@
 developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.  CI builds produce logs which
-report results of various sub-steps within the build.  These build logs
+communication~\cite{downs2012ambient}.
+CI builds produce logs which
+report results of various sub-steps within the build.
+These build logs
 contain a lot of valuable information for developers and researchers---for
@@
 
-CI builds produce logs which report the results of the steps within the build.
+CI builds produce logs which report the results of the steps within
+the build.
 The information stored in build logs can and has
-already been used for a variety of applications. One prominent dataset
+already been used for a variety of applications.
+One prominent dataset
 in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}. To date, scientist and practitioners alike
+2017~\cite{msr17challenge}.
+To date, scientist and practitioners alike
 have used it and other, proprietary datasets to understand and
@@
 and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}. Therefore, being able to efficiently
+builds~\cite{zampetti2017open}.
+Therefore, being able to efficiently
 and correctly extract information from build logs is paramount to the
@@
 50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
-for direct human consumption. Therefore, to support developers and
+for direct human consumption.
+Therefore, to support developers and
 researchers in efficiently making use of the information within build
@@
 There are different techniques to retrieve information chunks from CI
-build logs. Beller et al. use a rule-based system of regular
+build logs.
+Beller et al.
+use a rule-based system of regular
 expressions to analyze logs from Travis CI~\cite{beller2017oops}.
 Such regular expressions are developed by looking at exemplary build
-logs.  Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.  Recently, Amar et
+logs.
+Vassallo et al.\ wrote a custom parser to gather information
+for build repair hints~\cite{vassallo2018un-break}.
+Recently, Amar et
 al.\ reduced the number of lines for a developer to inspect by
@@
 expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.  Custom parsers are powerful
-though fragile in light of changes in the log structure. Diffing
+maintain~\cite{michael2019regexes}.
+Custom parsers are powerful
+though fragile in light of changes in the log structure.
+Diffing
 between failed and successful logs can reduce the information to be
@@
 
-To gain an impression on how researchers are using information from build logs
-within their research and how they are gathering chunks from them to support
-developers in understanding build outcomes, we conducted a systematic mapping
+To gain an impression on how researchers are using information from
+build logs
+within their research and how they are gathering chunks from them
+to support
+developers in understanding build outcomes, we conducted a systematic
+mapping
 study.
-Our goal was to classify how and what for researchers use build logs as a source
+Our goal was to classify how and what for researchers use build logs as
+a source
 of data (\textbf{RQ1}).
 
-The outcomes of our study shows that there are various attempts to retrieve
-specific information from buildlogs. The resulting implementations are rarely
-available and therefore rarely reused. Because of the high development overhead
-of the custom parsers, many implementations are limited to small number of supported
+The outcomes of our study shows that there are various attempts to
+retrieve
+specific information from buildlogs.
+The resulting implementations are rarely
+available and therefore rarely reused.
+Because of the high development overhead
+of the custom parsers, many implementations are limited to small number
+of supported
 build tools.
 
-To address this, we implement three promising techniques for build log analysis.
-They retrieve specific chunks of targeted information and are configured by
+To address this, we implement three promising techniques for build
+log analysis.
+They retrieve specific chunks of targeted information and are configured
+by
 examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data set~\cite{brandt2020logchunks} to
+We conduct an empirical study on the \emph{LogChunks} data
+set~\cite{brandt2020logchunks} to
 gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).
+when one of the techniques should be preferred over other alternatives
+(\textbf{RQ2}).
 
@@
 
-% At the moment there is only anecdotal evidence on the performance of these
-% techniques and on when a technique should be preferred over other alternatives.
-% Developers and researches currently have little support when choosing which
+% At the moment there is only anecdotal evidence on the performance
+of these
+% techniques and on when a technique should be preferred over other
+alternatives.
+% Developers and researches currently have little support when choosing
+which
 % technique to use for a task.
 
-% The goal of this article is to investigate different chunk retrieval techniques
-% for build logs and describe under which circumstances certain techniques can be
+% The goal of this article is to investigate different chunk retrieval
+techniques
+% for build logs and describe under which circumstances certain techniques
+can be
 % recommended over others.
 % We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
-% influence the suitability of a chunk retrieval technique for CI build logs.
+% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which
+criteria
+% influence the suitability of a chunk retrieval technique for CI
+build logs.
 
@@
   \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE synthesizes
+  Based on user examples of build logs and targeted log chunks, PBE
+  synthesizes
   a regular expression matching the given chunks within the build logs.
@@
   Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by the user.
+  most similar to the lines present in example chunks provided by
+  the user.
   \item \textbf{Keyword Search (KWS)}
-  Ad-hoc method for finding fitting passages by searching the whole text for
+  Ad-hoc method for finding fitting passages by searching the whole
+  text for
   the occurrence of specific trigger words.
@@
   \end{lstlisting}
-  \caption{Example of a log chunk explaining why an Android/Gradle build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me long ago that this was something your analyzer cannot extract
+  \caption{Example of a log chunk explaining why an Android/Gradle
+  build failed.}
+  % TODO Moritz: we can relate this to travistorrent maybe, you told me
+  long ago that this was something your analyzer cannot extract
   \label{lst:chunk-example-1}
@@
 Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException: java.lang.RuntimeException: ...
+> com.android.builder.testing.api.DeviceException:
+java.lang.RuntimeException: ...
   \end{lstlisting}
@@
   \end{lstlisting}
-  \caption{Another example of a log chunk explaining why an Android/Gradle build failed.}
+  \caption{Another example of a log chunk explaining why an Android/Gradle
+  build failed.}
   \label{lst:chunk-example-2}
@@
 
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition, RegexPair,
+\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
+RegexPair,
   EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
@@
   \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator", "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/", "Line Separator/{\color{Plum}$\circ$}/Line Separator"))
+StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator",
+"ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/",
+"Line Separator/{\color{Plum}$\circ$}/Line Separator"))
   \end{lstlisting}
@@
 --- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
+    repo\_test.go:75: expected entry to be in form of `* [link] -
+    description.`, got '* ...
   \end{lstlisting}
@@
   \end{lstlisting}
-  \caption{Example of a log chunk. \todo{which build tool?}
-  \todo{move to where structural category explanation}}
+  \caption{Example of a log chunk.
+%\todo{which build tool?}
+%  \todo{move to where structural category explanation}
+}
   \label{lst:chunk-example-3}
@@
 
-The results of our empirical comparison study on the chunk retrieval techniques
-show that the structural representation of the targeted chunk greatly influences
+The results of our empirical comparison study on the chunk retrieval
+techniques
+show that the structural representation of the targeted chunk greatly
+influences
 the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary log chunks
+\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary
+log chunks
 from Android/Gradle build logs marked in blue.
 Both chunks contain the information on why the
-corresponding build failed. When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}. The retrieval
-starts after a colon followed by a line separator and before a capital letter.
-It ends before two line separators, consistent with the two example chunks from
+corresponding build failed.
+When PBE is trained on these two examples it produces
+a regular expression similar to \Cref{lst:prose-program-simplified}.
+The retrieval
+starts after a colon followed by a line separator and before a capital
+letter.
+It ends before two line separators, consistent with the two example
+chunks from
 \Cref{lst:chunk-example-1,lst:chunk-example-2}.
@@
 example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and returns
+representation is added, PBE is not able to syntesize a program and
+returns
 ``\texttt{no program found}''.
-We express this difference in structural representation through dividing log
-chunks into structural categories. The chunks from
+We express this difference in structural representation through
+dividing log
+chunks into structural categories.
+The chunks from
 \Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a different one.
-
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
-% how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is (\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set, which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.
+category, while the chunk from \Cref{lst:chunk-example-3} is in a
+different one.
+
+% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited
+to retrieve information from continuous integration build logs.
+% \textbf{RQ2} is refined into sub-questions along with the criteria
+resulting from \textbf{RQ1} and compares their instantiations for the
+three techniques:
+% how many training examples a technique needs to perform best
+(\textbf{RQ2.1}), how structurally diverse the examples can
+be (\textbf{RQ2.2}) and how accurate the retrieved output is
+(\textbf{RQ2.3}).
+% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set,
+which encompasses about 800 log files from 80 repositories.
+% Each log is labeled with the log part describing the reason a build
+failed, keywords to search for this log part and a categorization of
+the labeled log part according to its structural representation within
+the log.
 
@@
 \begin{itemize}
-  \item PBE yields very accurate results when trained with two examples from a
+  \item PBE yields very accurate results when trained with two examples
+  from a
   single structural category.
-  \item CTS shows the best average precision, though precision and recall of a
+  \item CTS shows the best average precision, though precision and recall
+  of a
   retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable influence. 
-  Fewer structural categories improve precision and recall of the retrieval.
-  \item KWS has the highest recall of all techniques, however much lower precision.
-  It is the technique with the best recall when multiple structural categories
+  A small increase in the number of training examples has no noticeable
+  influence.
+
+  Fewer structural categories improve precision and recall of the
+  retrieval.
+  \item KWS has the highest recall of all techniques, however much
+  lower precision.
+  It is the technique with the best recall when multiple structural
+  categories
   are present in the training examples.
@@
 % \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk retrieval techniques:
+%   \item A tool with three prototypical implementations of chunk
+retrieval techniques:
 %	  \begin{itemize}
-%           \item program synthesis from examples using the Microsoft PROSE library (PBE),
-%           \item a common information retrieval approach using text similarity (CTS), and
+%	    \item program synthesis from examples using the Microsoft
+PROSE library (PBE),
+%	    \item a common information retrieval approach using text
+similarity (CTS), and
 %	    \item a keyword search approach (KWS).
 %	  \end{itemize}
-%   \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
+%   \item Recommendations for the configuration of each of the
+investigated chunk retrieval techniques.
 %   \item Guidelines on choosing a suitable chunk retrieval technique.
@@
 We recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision and
+represented in the same structural way and high confidence in precision
+and
 recall of the chunk retrieval is required.
-CTS is well suited when the representation of the desired information varies
-slightly and the output of the chunk retrieval is further processed by a human.
-In cases where the textual representation of the desired information in the log
-is unpredictable or varies greatly, KWS seems to be the best choice. However,
+CTS is well suited when the representation of the desired information
+varies
+slightly and the output of the chunk retrieval is further processed by
+a human.
+In cases where the textual representation of the desired information in
+the log
+is unpredictable or varies greatly, KWS seems to be the best choice.
+However,
 its low precision---it extracts a context of multiple lines around a
 finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output chunk.
-
-\section{Systematic Literature Survey and Mapping}
-\label{sec:survey}
-
-\begin{figure}[htb]
-        \centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
-
-% TODO (Caro): Integrate Petersen's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one. We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
-log analysis was a side-part of the article. To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
-
-\subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible. Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books. We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv. One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''. This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
-(2020-03-15). We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
-non-related works. This left us with 1,552 combined search results
-(2020-03-15). The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
-To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered out articles based on 1) their title and 2) the
-contextual information Google Scholar displayed. We inlcuded only
-publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion. Our strategy was to err on the side of
-caution, that is rather including a paper than not. We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query. We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}). \todo{overly specific?} We automatically
-removed it to find all true duplicates. After this process, we were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
-sampling for related work. This added three papers (five before
-duplicate elimination) to our literature set, coming to a total of 261
-articles. % TODO: update numbers
-
-On the surviving artciles, we did a second filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
-for the occurrence of ``log''. If these papers showed traces of
-working with build logs, we included them in our survey. For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
-were left with 90 articles after this search.
-
-\subsection{Article Classification}
-Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some kind of process.
-we wanted to characterize how researchers use buildlogs as input to any processes.
-Interesed in 
-\begin{itemize}
-  \item what kind of build logs they are using and the source of these logs.
-  \item what information they are retrieving from the logs, 
-  its kind (chunk/classification) and 
-  what they use the retrieved information for
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their tools
-\end{itemize}
-To objecifiy our data extraction we created a template of the targeted factors
-and performed a pilot on five articles. Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our understanding
-of the factors in the data extraction templates. The remaining articles were
-divided over these two authors. We inspected the articles as closesly as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
-The full data extraction template and our results of this step can be found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push those to the last pass?}.
-For several cases, multiple articles extended others, though still reported on
-the same work with the respect to analyzing build logs.
-Of these we only considered the earliest article which reported on the processing
-of build logs.
-
-\subsection{Results}
-lots of:
-- categories + frequencies of answers
-
-\subsubsection{Retrieved Information}
-
-\subsubsection{Retrieval Technique}
-
-\subsubsection{Build Logs}
-
-\subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool). many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
+instead requires a human to further inspect and interpret the output
+chunk.
 
@@
 \label{sec:rw}
-We explain how researchers gather information about CI usage in software projects
-through build log analysis and why the chunk retrieval techniques we investigate
+We explain how researchers gather information about CI usage in software
+projects
+through build log analysis and why the chunk retrieval techniques we
+investigate
 simplifies their data collection.
-This section moves on to past works about augmenting build logs to make it easier
+This section moves on to past works about augmenting build logs to make
+it easier
 for developers to inspect them.
-The presented approaches are related to and can benefit from the techniques we
+The presented approaches are related to and can benefit from the
+techniques we
 analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate our
+Further, we classify build logs as semi-structured data and differentiate
+our
 work from system log analysis.
@@
 types such as dependency mismatches are the most prominent cause of
-build failures at Google. In addition, they notice that most failures
-are resolved within two builds. They based their analyses on sets of
-build logs collected from industry partners. They develop a custom
+build failures at Google.
+In addition, they notice that most failures
+are resolved within two builds.
+They based their analyses on sets of
+build logs collected from industry partners.
+They develop a custom
 parser to classify error messages reported by Java and C++ builds.
@@
 source Java projects and find that most builds fail because of failing
-tests. For most projects, over half of the failed builds follow a
-previous failed build. Rausch et al.'s data shows that most failures
+tests.
+For most projects, over half of the failed builds follow a
+previous failed build.
+Rausch et al.'s data shows that most failures
 occur in the second half of the build runtime, which can cause long
@@
 Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones. They determine that testing failures are
-more common than compilation errors. Open source builds fail most
+in Java to industrial ones.
+They determine that testing failures are
+more common than compilation errors.
+Open source builds fail most
 often because of unit tests, whereas release preparations are the
-primary cause in industrial projects. Their data stems from analyzing
+primary cause in industrial projects.
+Their data stems from analyzing
 build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
@@
 Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data. They classify build failures from \emph{TravisTorrent}
+breakage data.
+They classify build failures from \emph{TravisTorrent}
 according to whether they were caused by an environmental failure or
-caused by a developer change. Their analysis starts with manual
-categorization of build logs. They select keywords and strings that
+caused by a developer change.
+Their analysis starts with manual
+categorization of build logs.
+They select keywords and strings that
 identify their targeted categories and code a script to automatically
@@
 presented in this section create parsers and regular expression-based
-programs. This task of retrieving specific chunks of text from the
+programs.
+This task of retrieving specific chunks of text from the
 build logs can be solved by the chunk retrieval techniques we compare
-in this article. Our results can support researchers in choosing a
+in this article.
+Our results can support researchers in choosing a
 suitable technique for their data set of build logs and the chunks
-they want to retrieve. By relieving them from building custom parsers
+they want to retrieve.
+By relieving them from building custom parsers
 we enable them to cover a much wider range of languages and build
@@
 Build logs are a valuable data source for developers to find out why
-their build failed. Several researchers investigate how to support
-developers in working with verbose build logs. Vassallo et
+their build failed.
+Several researchers investigate how to support
+developers in working with verbose build logs.
+Vassallo et
 al.~\cite{vassallo2018un-break} try to shorten the time it takes
-developers to understand build logs. They parse
+developers to understand build logs.
+They parse
 Maven~\cite{maven2019website} build logs into a structured
@@
 For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed. In a qualitative study
+discussions related to why the build failed.
+In a qualitative study
 they observed that highlighting the locality and context of an issue
@@
 to fill similar structured representations with information from build
-logs. As they simplify the construction of parsers they would enable
+logs.
+As they simplify the construction of parsers they would enable
 developers and researchers to cover a wider array of build tools,
@@
 Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect. Their
+reduce the portions of a log that a developer has to inspect.
+Their
 techniques remove lines that appear both in logs from passing and
@@
 Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures. Their diff technique can be interpreted as a
+to occur with failures.
+Their diff technique can be interpreted as a
 chunk retrieval technique, where the targeted information is defined
@@
 basic structuring of the build logs within their log viewer using
-\emph{log folds}~\cite{travis2019logfolds}. They add fold identifiers
+\emph{log folds}~\cite{travis2019logfolds}.
+They add fold identifiers
 around common commands and setup or teardown build phases and collapse
@@
 A related field of log processing is the processing of system log
-files produced during runtime. A main difference between build logs
+files produced during runtime.
+A main difference between build logs
 and system logs is that system logs are fundamentally structured
-through events. Each line in a log file represents one event with a
+through events.
+Each line in a log file represents one event with a
 set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}. Figure \ref{lst:system-log} shows
+content~\cite{he2017towards}.
+Figure \ref{lst:system-log} shows
 example lines from a system log.
@@
 separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}. Next, the log
+message~\cite{nagappan2010abstracting,he2017towards}.
+Next, the log
 messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters. The output of a log
+identical constant parts and varying parameters.
+The output of a log
 parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}. This structured log is then
+parameter values~\cite{he2016evaluation}.
+This structured log is then
 the input to various machine learning and data mining processes.
@@
 %debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}. Xu et
+%detection~\cite{nagappan2010abstracting}.
+Xu et
 %al.~\cite{xu2009detecting} leverage the connection of log statements
@@
 The techniques developed for system log analysis can also be applied
-to build logs. One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies. Amar et
+to build logs.
+One example is comparing execution traces to reference
+traces of intended behavior to detect anomalies.
+Amar et
 al.~\cite{amar2019mining} employed a similar approach to detect
@@
 %Classic log parsers interpret the whole log file into a sequence of
-%events. A similar approach could also be applied to build logs to
+%events.
+A similar approach could also be applied to build logs to
 %determine the sequence of executed build steps or phases.
 In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques. Chunk
+from the build log as a whole with chunk retrieval techniques.
+Chunk
 retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g. by using regular
+values of variable parts in a log message, e.g.
+by using regular
 expressions~\cite{nagappan2010abstracting,xu2009detecting}.
@@
   \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140 terminating
+2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received
+block blk_3587508140 of size 67108 from /10.251.42.84
+2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140
+terminating
   \end{lstlisting}
-  \caption{System Log excerpt. Example adapted from~\cite{he2017towards}.}
+  \caption{System Log excerpt.
+Example adapted from~\cite{he2017towards}.}
   \label{lst:system-log}
@@
 % Programming by Example.%, information extraction and information
-% retrieval. This section presents different Programming by Example
-% resources surrounding the PROSE library. We explain its generic
+% retrieval.
+This section presents different Programming by Example
+% resources surrounding the PROSE library.
+We explain its generic
 % program synthesis algorithm and how PROSE synthesizes text
@@
 synthesis that enables users to automate repetitive tasks, without
-them having to explicitly codify a computer program. One has to
-provide prototypical examples of the input and the desired output. A
+them having to explicitly codify a computer program.
+One has to
+provide prototypical examples of the input and the desired output.
+A
 synthesis algorithm tries to create a program (based on a regular
-language) that transforms the input to the output. The minimum working
+language) that transforms the input to the output.
+The minimum working
 condition is for this when replayed on the examples inputs is to
@@
 possbile to the user's intention and thus also works on a different
-and larger set of inputs. This section introduces the theoretical
+and larger set of inputs.
+This section introduces the theoretical
 foundations of the program synthesis algorithm of the \emph{PROgram
 Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research. Next, this
+The PROSE framework is developed by Microsoft Research.
+Next, this
 section presents the FlashExtract DSL, which defines text extraction
@@
 Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
-synthesis in the Microsoft PROSE framework. FlashMeta separates the
+synthesis in the Microsoft PROSE framework.
+FlashMeta separates the
 inductive synthesis algorithm from the domain specific capabilities of
 the desired program by encoding the possible program space in a domain
-specific language (DSL). The user specifies the desired program
-behavior by providing in/output examples (I/O examples). FlashMeta
+specific language (DSL).
+The user specifies the desired program
+behavior by providing in/output examples (I/O examples).
+FlashMeta
 uses \emph{witness functions}, provided by the DSL, to divide the
-synthesis into smaller subtasks. For each of these subtasks it
+synthesis into smaller subtasks.
+For each of these subtasks it
 enumerates all possible programs that solve the subtask consistent
-with the set of I/O examples. A program is consistent with a set of
+with the set of I/O examples.
+A program is consistent with a set of
 I/O examples if, for each input example, it produces the corresponding
-output~\cite{mitchell1982generalization}. The possible subprograms are
+output~\cite{mitchell1982generalization}.
+The possible subprograms are
 joined and stored in a \emph{version space algebra}
-(VSA)~\cite{mitchell1982generalization}. This a tree structure, which
+(VSA)~\cite{mitchell1982generalization}.
+This a tree structure, which
 space-efficiently saves candidate programs for tasks by sharing common
-subexpressions. Next, FlashMeta ranks the enumerated programs
-according to which ones the user most likely intended. The DSL also
-provides the ranking characteristics. From the ranked VSA, FlashMeta
+subexpressions.
+Next, FlashMeta ranks the enumerated programs
+according to which ones the user most likely intended.
+The DSL also
+provides the ranking characteristics.
+From the ranked VSA, FlashMeta
 can then return a ranked list of complete programs consistent with the
@@
 FlashExtract's instantiation for text synthesizes extraction programs
-from semi-structured text based on regular expressions. Users can
+from semi-structured text based on regular expressions.
+Users can
 extract multiple fields and structure them with hierarchy and
@@
 % leveraging the information about hierarchical containment and
-% sequentiality. It eliminates the need for the user to understand the
+% sequentiality.
+It eliminates the need for the user to understand the
 % entire structure of the processed document and decreases the effort
@@
 FlashExtract models the extraction of a single substring as a pair of
-two cut positions. A position is either specified by an absolute
-character index or by a pair of two regular expressions. The first
+two cut positions.
+A position is either specified by an absolute
+character index or by a pair of two regular expressions.
+The first
 regular expression matches the substring directly before the
 characterized position, the second regular expression matches the
-substring directly after. A regular expression in FlashExtract is a
+substring directly after.
+A regular expression in FlashExtract is a
 concatenation of tokens, e.g.\ standard character classes or string
-literals frequently occurring in the input examples. Figure
+literals frequently occurring in the input examples.
+Figure
 \ref{lst:prose-program} shows a text extraction program synthesized by
-FlashExtract. This program defines the first position as after a colon
+FlashExtract.
+This program defines the first position as after a colon
 followed by a newline character and before a piece of text with all
-capital letters. It defines the second position as before two newline
+capital letters.
+It defines the second position as before two newline
 characters.
@@
 tool Azure Monitor lets users define custom log
-fields~\cite{azure2019custom}. The ConvertFrom-String function in
+fields~\cite{azure2019custom}.
+The ConvertFrom-String function in
 PowerShell allows a user to specify an example template to extract
@@
   language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair, StartToPosRegion},
+  morekeywords={PosToEndRegion, RegexPosition, RegexPair,
+  StartToPosRegion},
   keywordstyle=\bfseries\color{black},
@@
   \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s, RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/", "Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
+let s = v in let s = PosToEndRegion(s, RegexPosition(s,
+RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in
+StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/",
+"Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
   \end{lstlisting}
@@
 logs, i.e., techniques that do not aggreagte, combine, or deducted
-information. We call such pieces of information from build logs
+information.
+We call such pieces of information from build logs
 \emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
@@
 and parametrization that different techniques require in different
-forms. A configuration can be explicitly stated or implicitly dervied
-by learning through provided examples. It is therefore a manual
+forms.
+A configuration can be explicitly stated or implicitly dervied
+by learning through provided examples.
+It is therefore a manual
 specification of which information the chunk retrieval should target.
 It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log. Each chunk
+identify the targeted information chunk in a build log.
+Each chunk
 retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word). The
-granularity might be adjustable by configuration. \emph{Running a
+smallest piece of text it can return (e.g., a line, or a word).
+The
+granularity might be adjustable by configuration.
+\emph{Running a
 chunk retrieval technique} means to execute a fully configured
 technique to consumes as input a build log in plain text format and to
-produce an array as output. The array consists of substrings of the
+produce an array as output.
+The array consists of substrings of the
 build log text.
@@
 \toprule
-Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
+Name                         & Acronym & Identification Technique
+& Granularity & Configuration & Source            \\
 \midrule
-Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
-Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
-Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
-Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
-Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
+Program Synthesis by Example & PBE     & Regular expression program
+& Character   & In/output examples      \\
+Common Text Similarity       & CTS     & TF-IDF \& cosine similarity,
+expected number of lines & Line        & Output examples           \\
+Keyword Search               & KWS     & Keywords, expected number of
+lines                    & Line        & Keywords, context length  \\
+Random Line Retrieval        & RLR     & Random sample
+& Line        & Retrieval length          \\
+Diff Approach                & ---     & Line not present in successful
+log, information retrieval  & Line        & Logs from failing and
+successful builds      \\
 \bottomrule
@@
 % It enables users to create programs without a priori programming
-% knowledge~\cite{mayer2015user}. In the context of text extraction
+% knowledge~\cite{mayer2015user}.
+In the context of text extraction
 % through regular expressions, Programming by Example relieves the
 % developer from having to understand the whole document structure to
-% solve a single extraction task~\cite{le2014flashextract:}. In this
+% solve a single extraction task~\cite{le2014flashextract:}.
+In this
 % work, we refer to our interpretation of Programming by Example as
-% \emph{PBE}\@. We investigate the suitability of PBE to retrieve
-% information chunks from build logs. In the following, we explain the
+% \emph{PBE}\@.
+We investigate the suitability of PBE to retrieve
+% information chunks from build logs.
+In the following, we explain the
 % configuration and application of PBE to chunk retrieval from CI
@@
 In- and output example pairs are the main driver of Programming by
-Example, we refer to them in short as \emph{examples}. The
-\emph{input} is the text of the build log file. The \emph{output} is
+Example, we refer to them in short as \emph{examples}.
+The
+\emph{input} is the text of the build log file.
+The \emph{output} is
 an array of substrings of the log file text, representing the
 substrings that should be retrieved by the synthesized program when
-given the corresponding input file. One or multiple examples, the
+given the corresponding input file.
+One or multiple examples, the
 training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted. The
+they define the substring of a build log that should be extracted.
+The
 PROSE program synthesis then tries to construct a program consistent
@@
 % The program synthesis builds on the FlashExtract DSL, which in turn
-% uses the FlashMeta algorithm. Both are described in
+% uses the FlashMeta algorithm.
+Both are described in
 % Section~\ref{sec:rw-prose}.
 
-% TODO Moritz: you said: The following is very obvious and could apply to any
+% TODO Moritz: you said: The following is very obvious and could apply
+to any
 % technique.
-% kinda. It does give a descriptive error message on no match (and
+
+% kinda.
+It does give a descriptive error message on no match (and
 % that is not possible in other techniques)
 % otherwise yes, nothing interesting happens in the application of pbe
-% though for consistency we might need this section? or merge config/application?
+% though for consistency we might need this section? or merge
+config/application?
 \subsubsection{Application}
 A run of PBE takes a build log file as input and applies the
-synthesized regular expression program. It then returns the substring
+synthesized regular expression program.
+It then returns the substring
 of the build log matched by the program or an error message if the
@@
 % software
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model. We
+%
+artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+% One common and simple technique is the Vector Space Model.
+We
 % investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs. In the following we will explain
+% information chunks from build logs.
+In the following we will explain
 % the concept of how we apply text similarity to information retrieval
@@
 the same concept of examples as for PBE
-% TODO Moritz: your question was: More details on this. How do you
+% TODO Moritz: your question was: More details on this.
+How do you
 % 'apply' VSM? On what?
@@
 % of determining text similarity which as far as I understand and
-% Annibale said is the VSM. word tokens, tf-idf, similarity measure
+% Annibale said is the VSM.
+word tokens, tf-idf, similarity measure
 % I added a "as follows", think that is enough for explanation?
-and apply the Vector Space Model~\cite{schutze2008introduction} as follows. The
+and apply the Vector Space Model~\cite{schutze2008introduction}
+as follows.
+The
 lines of the output strings of the training examples define our search
-query. The algorithm splits the search query into single lines and
-identifies tokens, in our case words. Then we build a
+query.
+The algorithm splits the search query into single lines and
+identifies tokens, in our case words.
+Then we build a
 document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words. Finally, the
+and prune very often or very rarely appearing words.
+Finally, the
 algorithm applies TF-IDF to the matrix, a best practice for natural
@@
 whole text and process it in the same way as the output of the
-training examples. The algorithm calculates the cosine
+training examples.
+The algorithm calculates the cosine
 similarity~\cite{korenius2007principal} to compare each line of the
-build log with each line of the search query. After summing up the
+build log with each line of the search query.
+After summing up the
 similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity. The average number of
+the build log lines in decreasing similarity.
+The average number of
 lines in the outputs of the training examples determines how many of
@@
 large amount of unstructured information, a first ad-hoc approach they
-use is to search for related keywords. Indeed, this was one of the
+use is to search for related keywords.
+Indeed, this was one of the
 most common approaches we took when searching for the reason the build
@@
 % use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs. In
+% suitable for retrieving information chunks from CI build logs.
+In
 % the following we will explain how we use simple keyword search to
@@
 \subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@. To better
+A set of keywords configures the chunk retrieval with KWS\@.
+To better
 compare KWS with PBE and CTS, we also configure it through examples.
@@
 chunk or close to it.
+
 KWS then searches for those keywords which are tied to the greatest
@@
 For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords. As keywords are
+search for all exact occurrences of the keywords.
+As keywords are
 often not directly describing the desired information, but rather
 appear close to the desired information, KWS also retrieves the lines
-around the found keyword. The number of surrounding lines retrieved is
+around the found keyword.
+The number of surrounding lines retrieved is
 the average of lines in the output of the training examples.
@@
 In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log. RLR essentially mimicks the
+picking lines from the build log.
+RLR essentially mimicks the
 situation of guessing purely blindly which lines might be interesting.
 The only configuration option for RLR is the number of lines it should
-return. For a fair comparison to the other techniques (whose number of
+return.
+For a fair comparison to the other techniques (whose number of
 returned lines is dynamic), we configure RLR to return the average
 number of lines in the chunks of the training examples.
+
 % TODO Moritz: you said: some more details here?
-% I would not know of any details to add. It's really all we are doing
+% I would not know of any details to add.
+It's really all we are doing
 
 \subsection{Other Techniques}
-%Literature mentions further build log analysis techniques. This
+%Literature mentions further build log analysis techniques.
+This
 %section describes them with our notion of chunk retrieval techniques.
@@
 log~\cite{amar2019mining}, as we describe in more detail in
-Section~\ref{sec:rw-bl-analysis}. The configuration for the technique
+Section~\ref{sec:rw-bl-analysis}.
+The configuration for the technique
 is the log from the last successful build and relevant past failures.
@@
 
-% TODO: we could add more techniques from the lit. survey here
+% TODO: we could add more techniques from the lit.
+survey here
 
@@
 For our comparison study we implemented PBE, CTS, KWS and RLR and a
-unifying interface. The unified interface is implemented in Ruby and
+unifying interface.
+The unified interface is implemented in Ruby and
 calls the separate technique implementations over the command line.
 The implementation of PBE in C\# is based on the Microsoft PROSE
-library~\cite{prose2019webpage}. We implemented CTS, KWS and RLR using
+library~\cite{prose2019webpage}.
+We implemented CTS, KWS and RLR using
 R and the text2vec library~\cite{text2vec2019webpage}.
@@
 
-% TODO Caro: I find this figure still very confusing :'(, due to a lack of structure. If you want me to, I can give it a go?
+% TODO Caro: I find this figure still very confusing :'(, due to a lack
+of structure.
+If you want me to, I can give it a go?
 \begin{figure*}[tb]
 	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm}, clip]{img/study.pdf}
+	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm},
+	clip]{img/study.pdf}
 	\caption{Study design of our technique comparison study.}
@@
 CI build logs we evaluate them on the
-\emph{LogChunks}~\cite{brandt2020logchunks} data set. This section
+\emph{LogChunks}~\cite{brandt2020logchunks} data set.
+This section
 describes our study design and which metrics we measure to answer our
-research questions. In the presentation of the results, we first focus
+research questions.
+In the presentation of the results, we first focus
 on each of the three techniques and later compare them against each
@@
 For this study we created the previously published data set
-\emph{LogChunks}. It encompasses 797 build logs from Travis CI,
+\emph{LogChunks}.
+It encompasses 797 build logs from Travis CI,
 stemming from a broad range of 80 GitHub repositories and 29
-programming languages. For each file, the authors manually ``labeled
+programming languages.
+For each file, the authors manually ``labeled
 the log part (chunk) describing why the build
-failed''~\cite{brandt2020logchunks}. We include keywords, which we
-would use to search for the selected chunk within the log. In
+failed''~\cite{brandt2020logchunks}.
+We include keywords, which we
+would use to search for the selected chunk within the log.
+In
 addition, we categorized the log chunks according to their format
-within the log. If the chunks are surrounded by the same markings
+within the log.
+If the chunks are surrounded by the same markings
 within the log we assign them the same structural category.
@@
 PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}. Random Line Retrieval
+\ref{sec:expl-ts} and \ref{sec:expl-skws}.
+Random Line Retrieval
 (RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
@@
 \textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study. For each of the
+We use \emph{LogChunks} as the data set for our study.
+For each of the
 80 repositories in it, \emph{LogChunks} contains 10 build logs,
 manually labeled with the \emph{chunk} describing the
-reason the build failed. Additionally, it contains (1) keywords useful
+reason the build failed.
+Additionally, it contains (1) keywords useful
 to identify the substring in the log  and (2) which structural category
 the substring belongs to.
-% TODO Moritz: You said: Add details how key words were extracted. Add example?
+% TODO Moritz: You said: Add details how key words were extracted.
+Add example?
 % how the keywords were put in logchunks does not fit here, that is
@@
 
-% TODO Moritz: You said: Add more details. How was the split in numbers?
+% TODO Moritz: You said: Add more details.
+How was the split in numbers?
 % this is described in the following paragraph, should we merge them
@@
 For each repository in \emph{LogChunks}, we split the examples
-chronologically into training and test set. Therefore, we train on
+chronologically into training and test set.
+Therefore, we train on
 examples from past build logs and test on more recent build logs.
@@
 perform best, we evaluate the techniques with different training set
-sizes. We train each technique with one to five examples from each of
-the repositories within \emph{LogChunks}. The size of the test set is
+sizes.
+We train each technique with one to five examples from each of
+the repositories within \emph{LogChunks}.
+The size of the test set is
 one.
@@
 lines of the chunk retrieval run on the input of the test example
-($\mathit{RetrievedLines}$). As oracle in our evaluation, we save the
+($\mathit{RetrievedLines}$).
+As oracle in our evaluation, we save the
 desired lines from the output of the test example
@@
 	example.
+
 	% What about when a line is replicated twice?
@@
 	the retrieved lines were actually desired.
+
 	\item $\mbox{Recall} =
@@
 	In addition, we calculate the F$_{1}$-score, the harmonic mean
-        of precision and recall. We prefer F$_{1}$ to other aggregate
+	of precision and recall.
+We prefer F$_{1}$ to other aggregate
 	measures such as accuracy because for a
@@
 	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
-	We define a successful retrieval as one where all desired lines were
+	We define a successful retrieval as one where all desired
+	lines were
 	extracted, therefore when recall is one.
@@
 % Recall and precision of CTS and KWS vary with the number of lines
-% selected for retrieval. We evaluate the effect of varying the number
+% selected for retrieval.
+We evaluate the effect of varying the number
 % of extracted lines by multiplying the average number of lines
@@
 Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
+Error: Invalid CSS after "2.3em": expected expression (e.g.
+1px, bold), was ";"
 	on line 86 of sass/components/dropdown.sass
 Desired Test Output:
-Error: Invalid CSS after "2.3em": expected expression (e.g. 1px, bold), was ";"
+Error: Invalid CSS after "2.3em": expected expression (e.g.
+1px, bold), was ";"
 	on line 86 of sass/components/dropdown.sass
@@
   \end{lstlisting}
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only two of the four targeted lines).}
+  \caption{Example for an unsuccessful retrieval (PBE retrieved only
+  two of the four targeted lines).}
   \label{lst:pbe-unsuccessful}
@@
 		\centering
-                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
+		\caption{Precision, recall and F$_{1}$-score for an
+		increasing training set size.}
 		\label{fig:recall-precision-examplecount-CTS}
@@
 		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
+				\includegraphics[width=\columnwidth,
+				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
+		\caption{Precision, recall and F$_{1}$-score for
+		an increasing number of structural categories in the
+		training and test sets.}
 		\label{fig:recall-precision-categorycount-CTS}
@@
 recall and F$_{1}$-score of chunk retrieval using CTS for an
-increasing number of training examples. When using one to five
+increasing number of training examples.
+When using one to five
 training examples, the size of the training set has no noticeable
@@
 measurements for an increasing number of structural categories in the
-training and test examples. With increasing category count, precision,
-recall and F$_{1}$-score decrease. Especially for more than three
+training and test examples.
+With increasing category count, precision,
+recall and F$_{1}$-score decrease.
+Especially for more than three
 categories present we have no chunk retrieval runs where all desired
@@
 		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
+		\caption{Precision, recall and F$_{1}$-score for an
+		increasing training set size.}
 		\label{fig:recall-precision-examplecount-KWS}
@@
 		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
+		\caption{Precision, recall and F$_{1}$-score for
+		an increasing number of structural categories in the
+		training and test sets.}
 		\label{fig:recall-precision-categorycount-KWS}
@@
 recall and F$_{1}$-score of chunk retrieval using KWS for different
-numbers of training examples. The recall increases by about 12\% when
+numbers of training examples.
+The recall increases by about 12\% when
 increasing the size of the training set to more than one example,
-while the precision stays constant at around 16\%. The F$_{1}$-score
+while the precision stays constant at around 16\%.
+The F$_{1}$-score
 stays around 26\%.
@@
 measurements for an increasing number of structural categories in the
-training and test examples. For more than one structural category in
+training and test examples.
+For more than one structural category in
 the training and test examples the recall decreases by about 20\% and
-the precision decreases about 6\%. For more than two structural
+the precision decreases about 6\%.
+For more than two structural
 categories no clear trend is visible in precision, recall or
@@
 % effect of the retrieval size factor on precision, recall and
-% F$_{1}$-score of chunk retrieval runs with KWS\@. The precision is
-% 19\% when retrieving half of the expected number of lines. On
-% average 9\% of the lines in the build log are retrieved then. When
+% F$_{1}$-score of chunk retrieval runs with KWS\@.
+%The precision is
+% 19\% when retrieving half of the expected number of lines.
+%On
+% average 9\% of the lines in the build log are retrieved then.
+%When
 % 2.5 times the expected number of lines are retrieved, the precision
 % decreases to 10\% and a quarter of the lines in the build log are
-% retrieved on average. The recall ranges from 58\% to 75\% and the
+% retrieved on average.
+%The recall ranges from 58\% to 75\% and the
 % F$_{1}$-score shows a constant decrease from 29\% to 17\%.
@@
 %		\centering
-% 		\includegraphics[width=\columnwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-% 		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS compared to retrieval size factor.}
+%		\includegraphics[width=\columnwidth,
+%clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
+%		\caption{Precision, recall and F$_{1}$-score of chunk
+%retrieval with KWS compared to retrieval size factor.}
 %		\label{fig:contextsizefactor-precision-recall-KWS}
@@
 		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+				\caption{Precision, recall and
+				F$_{1}$-score when PBE could synthesize
+				a consistent program compared with the
+				size of the training set.}
 		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
@@
 		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-                		\caption{Increasing number of structural categories in the training and test sets.}
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+				\caption{Increasing number of structural
+				categories in the training and test sets.}
 		\label{fig:failure-reason-categorycount-PBE}
 \end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
+\caption{Results of chunk retrieval with  Program Synthesis by Example
+(PBE)}
 \end{figure*}
@@
 		\centering
-		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
+		\includegraphics[width=0.75\columnwidth,
+		clip]{img/big-study/failure-reason-pbe.pdf}
 		\caption{Results of chunk retrieval with PBE.}
@@
 \Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
-evaluation. Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines in 138 cases. In 89 further
+evaluation.
+Out of the 400 runs, 5 per each one of the 80 example
+sets, PBE extracted all the desired lines in 138 cases.
+In 89 further
 cases, an extraction program was also successfully synthesized, though
-in 59 of the 89 cases the synthesized program yielded no output. In 30
+in 59 of the 89 cases the synthesized program yielded no output.
+In 30
 of the 89 cases did the synthesized program only partially extract a
-subset of the desired lines. For these 30 cases, the average recall
-was 28\%. Listing \ref{lst:pbe-unsuccessful} shows an example of such
+subset of the desired lines.
+For these 30 cases, the average recall
+was 28\%.
+Listing \ref{lst:pbe-unsuccessful} shows an example of such
 an \emph{unsuccessful retrieval}, where the synthesized program only
-retrieved two of the four targeted lines. In 173 of the 400 cases
+retrieved two of the four targeted lines.
+In 173 of the 400 cases
 could PROSE not synthesize program consistent with all of the training
@@
 runs depend on the number of structural categories in the training and
-test examples. The figure demonstrates that program synthesis mostly
+test examples.
+The figure demonstrates that program synthesis mostly
 returns exactly the desired output when there are is only one
-structural category present in the training examples. However, when
+structural category present in the training examples.
+However, when
 two or more structural categories are simultaneously present in the
 examlpe set, PROSE could in most cases not synthesize a program
-consistent with all training examples. For four or more present
+consistent with all training examples.
+For four or more present
 categories PROSE could never synthesize a consistent program.
@@
 precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples. When the training set
+program consistent with all training examples.
+When the training set
 size increases from one to two, recall and F$_{1}$-score increase by
-about 25\%, precision increases by about 10\%. For two or more
+about 25\%, precision increases by about 10\%.
+For two or more
 training examples, recall and F$_{1}$-score stay around 75\% and
@@
 In our evaluation, we compare against a baseline of randomly
-picking lines from the build log. Its results follow intuitive
+picking lines from the build log.
+Its results follow intuitive
 expectations:
 The precision ranges between 8\% and 5\%, the recall between 6\% and
-8\%. The size of the training set has no visible impact on either.
+8\%.
+The size of the training set has no visible impact on either.
 An greater number of structural categories within the training and
@@
 Graphs of the results of the chunk retrieval with RLR from our study
-are included in our replication package~\cite{brandt2020chunk-replication}.
+are included in our replication
+package~\cite{brandt2020chunk-replication}.
 
@@
 \Cref{fig:success-partial-all} compares the success of chunk
-retrievals differentiated by techniques in our study. CTS and KWS
+retrievals differentiated by techniques in our study.
+CTS and KWS
 extract some of the desired lines in 79\% and 88.5\% of the chunk
-retrieval runs. With 38.25\%, KWS also has the highest number of fully
-successful extractions, followed by PBE with 34.5\%. PBE has the
+retrieval runs.
+With 38.25\%, KWS also has the highest number of fully
+successful extractions, followed by PBE with 34.5\%.
+PBE has the
 lowest number of partial retrievals with only 18 out of 400 chunk
@@
 % The averaged precision, recall and F$_{1}$-score f all techniques is
-% compared in Figure~\ref{fig:recall-precision-all}. The recall of PBE
+% compared in Figure~\ref{fig:recall-precision-all}.
+The recall of PBE
 % has a high skew towards one and zero, meaning in most cases either
 % the retrieval is successful or no relevant lines are extracted at
-% all. PBE has the highest average precision with 95\%. Chunk
+% all.
+PBE has the highest average precision with 95\%.
+Chunk
 % retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% and the second highest recall with 46\%. KWS has the smallest
-% precision of the three chunk retrieval techniques. With 16\% it is
-% still higher than the precision of the RLR baseline with 7\%. KWS
+% and the second highest recall with 46\%.
+KWS has the smallest
+% precision of the three chunk retrieval techniques.
+With 16\% it is
+% still higher than the precision of the RLR baseline with 7\%.
+KWS
 % has the highest recall of all techniques with 70\%.
@@
 show the influence of a single structural category present in the
-training examples compared to multiple categories present. For more
+training examples compared to multiple categories present.
+For more
 than one category being present, the recall of PBE decreases greatly.
@@
 		\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/success-partial-all.pdf}
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/success-partial-all.pdf}
 		\caption{Success of chunk retrievals for all techniques.}
@@
 		\centering
-                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{one} structural category.}
+				\includegraphics[width=\columnwidth,
+				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
+		\caption{Precision, recall and F$_{1}$-score of all
+		techniques when training examples are in \emph{one}
+		structural category.}
 		\label{fig:recall-precision-singlecategory-all}
@@
 				\centering
-		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all techniques when training examples are in \emph{more than one} structural categories.}
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-multicategory-all.pdf}
+		\caption{Precision, recall and F$_{1}$-score of all
+		techniques when training examples are in \emph{more than
+		one} structural categories.}
 		\label{fig:recall-precision-multicategory-all}
 \end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural category count.}
+\caption{Comparison of all chunk retrieval techniques, split by structural
+category count.}
 \end{figure*}
@@
   \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?}
+  \item[\textbf{RQ2:}] Which criteria influence the suitability of a
+  chunk retrieval technique for build logs?
+
+  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS,
+  and KWS need to perform best?
+  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples
+  for PBE, CTS and KWS need to be for the techniques to be applicable?
+  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS,
+  and KWS?}
 \end{itemize}
@@
 The first section discusses for PBE, CTS and KWS separately in which
-cases they perform best. It details for which types of input build
+cases they perform best.
+It details for which types of input build
 logs, available training examples and consumption of the retrieved
-output each technique is suited. In the following section we discuss
+output each technique is suited.
+In the following section we discuss
 which of these criteria should influence the decision to use a certain
-technique most. Based on our empirical comparison, we present a
+technique most.
+Based on our empirical comparison, we present a
 decision tree between the three techniques we investigated.
@@
 This section discusses the study results for each of the analyzed
-chunk retrieval techniques separately. It gives recommendations which
+chunk retrieval techniques separately.
+It gives recommendations which
 kind of information chunk targets are best for each technique and for
@@
   \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
+  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\
+  multiple okay} \\
   Training Set Size & 2 & no influence & 2 \\
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
+  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium &
+  low \\
+  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium &
+  high \\
+  \makecell[l]{Confidence in \\ Output Correctness} & high & low &
+  \makecell[l]{low (precision) \\ high (recall)} \\
   Output Consumption by & program & human & human \\
@@
 }
-\caption{Recommendations for each of the investigated chunk retrieval techniques.}
+\caption{Recommendations for each of the investigated chunk retrieval
+techniques.}
 \label{tab:single-technique-recommendations}
@@
 Our study results show that chunk retrieval with PBE gives best
-results when the training examples are structurally identical. This is
+results when the training examples are structurally identical.
+This is
 because PROSE has difficulty synthesizing OR-based programs (see
-\Cref{sec:prose:impl}). PBE is thus suited to retrieve information
+\Cref{sec:prose:impl}).
+PBE is thus suited to retrieve information
 chunks that always have the same surrounding or defining internal
-structure. To extract for example the reason a build failed, the log
+structure.
+To extract for example the reason a build failed, the log
 passage describing the failure would always have to be started and
@@
 two examples are enough input for PROSE to synthesize a regular
-expression program with good recall. In our study, additional training
-examples did not improve the chunk retrieval. In fact, unless they
+expression program with good recall.
+In our study, additional training
+examples did not improve the chunk retrieval.
+In fact, unless they
 were in some sense redudant, adding training examples above that even
@@
 If the program synthesis succeeds and applying the regular expression
-program yields an output, PBE has high precision and recall. The tool
+program yields an output, PBE has high precision and recall.
+The tool
 clearly identifies a failing program synthesis or when no output from
-the program applied to a build log is obtained. Therefore, if there is
+the program applied to a build log is obtained.
+Therefore, if there is
 an output, the user can have high confidence that it is the desired
-output. This preciseness makes output from PBE chunk retrieval
+output.
+This preciseness makes output from PBE chunk retrieval
 well-suited for machine consumption.
@@
 The number of training examples had no noticeable influence on
-precision or recall in our study. Information retrieval techniques
+precision or recall in our study.
+Information retrieval techniques
 like text similarity commonly learn on a higher number of examples
-than used for our study. Future work is needed to investigate how many
+than used for our study.
+Future work is needed to investigate how many
 examples yield improvements in the chunk retrieval over a single
@@
 CTS has good precision and recall on average, though with a high
-variation. This means that the quality of an output by CTS is hard to
-determine, which makes it unsuited for automatic  processing and requires a human to further inspect and interpret the output. This could include semi-automated procedures such as sending
+variation.
+This means that the quality of an output by CTS is hard to
+determine, which makes it unsuited for automatic  processing and requires
+a human to further inspect and interpret the output.
+This could include semi-automated procedures such as sending
 developers an email with the extracted build failure reason.
@@
 KWS has a higher recall than the two other techniques for multiple
-structural categories present in the training and test examples. This
+structural categories present in the training and test examples.
+This
 makes KWS a good technique if there is little prior knowledge on how
-the targeted log chunk is represented in the build log. For the
+the targeted log chunk is represented in the build log.
+For the
 example of extracting the reason the build failed, KWS is best suited
@@
 Going from one to two two training examples, KWS's recall improves
-siginficantly. However, further enlarging the training example count
+siginficantly.
+However, further enlarging the training example count
 does not lead to further improvments.
@@
 While KWS has the highest recall of all three techniques, its
-precision is the lowest. The output of a chunk retrieval with KWS is
+precision is the lowest.
+The output of a chunk retrieval with KWS is
 well-suited to be read by humans, but ill-suited for consumption by
@@
 		\centering
-		\includegraphics[width=\columnwidth, clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk retrieval techniques.}
+		\includegraphics[width=\columnwidth,
+		clip]{img/crt-recommendation.pdf}
+		\caption{Our preliminary recommendation scheme for chunk
+		retrieval techniques.}
 		\label{fig:crt-recommendation}
@@
 After discussing the three chunk retrieval techniques separately we
-now want to unify our results into one recommendation scheme. In
+now want to unify our results into one recommendation scheme.
+In
 Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
 developers and researchers who want to retrieve information chunks
-from build logs can follow. The decision tree is built up of questions
+from build logs can follow.
+The decision tree is built up of questions
 which either lead to more questions or to a leaf node containing a
@@
 \textbf{Caveat!} This is a preliminary hypothesis based on the results
-from our comparison study. The recommendations could therefore be
+from our comparison study.
+The recommendations could therefore be
 influenced by idiosyncrazies of our specific implementation of the
@@
 answer to RQ2, about which criteria influence the suitability of a
-chunk retrieval technique. The earlier in the decision tree a
+chunk retrieval technique.
+The earlier in the decision tree a
 criterion is noted, the more important it is when distinguishing the
@@
 
-The first and most important aspect are the structural categories. Are
+The first and most important aspect are the structural categories.
+Are
 the information chunks one would like to retrieve always presented in
@@
 If the information chunks are from multiple structural categories,
-i.e. they are not represented in the same structural way within the
+i.e.
+they are not represented in the same structural way within the
 build logs, and recall is more important than precision we recommend
-to use KWS\@. If the representations are from multiple structural
+to use KWS\@.
+If the representations are from multiple structural
 categories and precision is more important than recall to the user we
-recommend CTS\@. We also recommend CTS when the representations are
+recommend CTS\@.
+We also recommend CTS when the representations are
 from one structural category, when the user does not require a high
@@
 combining the different build log analysis techniques studied in this
-paper. Such a super analyzer would likely always first employ PBE
+paper.
+Such a super analyzer would likely always first employ PBE
 (because of its high accuracy), followed by a combination of CTS and
-KWS. Other than initial setup and training time, there should be no
+KWS.
+Other than initial setup and training time, there should be no
 downside to this approach if it is implemented in a transparent way to
@@
 In our first example, a researcher studies whether test failures in CI
-are caused by a small or by a large group of test cases. They gather
+are caused by a small or by a large group of test cases.
+They gather
 CI build logs from various projects, which are their only available
-data source. The task of the researcher is to extract the names of the
-failing test cases from each build log. When they use our
+data source.
+The task of the researcher is to extract the names of the
+failing test cases from each build log.
+When they use our
 recommendation scheme to select a chunk retrieval technique, they
 first have to estimate how uniform the representation of the failing
-test cases is in the investigated build logs. As the researcher is
+test cases is in the investigated build logs.
+As the researcher is
 covering a wide range of build tools and development languages, the
 log chunks they target are in various, non-predictable structural
-representations. The next question is whether they value precision
-over recall. As they have to manually inspect the results of both CTS
+representations.
+The next question is whether they value precision
+over recall.
+As they have to manually inspect the results of both CTS
 and KWS, they choose recall over precision to avoid having to inspect
 the whole log in case the relevant information chunk was not
-retrieved. Therefore, our decision tree recommends them to use KWS\@.
+retrieved.
+Therefore, our decision tree recommends them to use KWS\@.
 
@@
 In our second example, a software development team wants to monitor
-the performance of the phases within their CI build. They are using
+the performance of the phases within their CI build.
+They are using
 Travis CI, which measures the duration of build phases and documents
-them within the build log. As all log statements that report timing
+them within the build log.
+As all log statements that report timing
 measurements are formatted the same way, the targeted log chunks are
-from one structural category. Therefore the development team can use
+from one structural category.
+Therefore the development team can use
 PBE to retrieve the duration of a build phase as well as its name.
@@
 Our results depend on the implementation of the investigated chunk
-retrieval techniques and the libraries we used. Our implementation of
-PBE is based on the program synthesis provided by PROSE\@. The
-idiosyncrazies of this framework influence our PBE results. Other
+retrieval techniques and the libraries we used.
+Our implementation of
+PBE is based on the program synthesis provided by PROSE\@.
+The
+idiosyncrazies of this framework influence our PBE results.
+Other
 frameworks similar to PROSE might have somewhat different strengths
-and weaknesses. For example, the need for examples from a single
+and weaknesses.
+For example, the need for examples from a single
 structural category stems from the fact that PROSE cannot learn
 regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}. PROSE introduced this constraint to
-keep the synthesis performance reasonable. At the same time, this is
+disjunctions~\cite{mayer2015user}.
+PROSE introduced this constraint to
+keep the synthesis performance reasonable.
+At the same time, this is
 clearly a current theoretical challenge of all PBE implementations,
@@
 Our implementation of CTS is dependent on the library {\tt text2vec}
-and the way it splits strings into word tokens. On the other hand,
+and the way it splits strings into word tokens.
+On the other hand,
 {\tt text2vec} is the de-facto standard library to do word embeddings
-in R. We intentionally chose a simple, minimally configured and tuned
-approach to compare against. Tuning the text similarity
+in R.
+We intentionally chose a simple, minimally configured and tuned
+approach to compare against.
+Tuning the text similarity
 meta-parameters more to the specific use case of chunk retrieval from
@@
 The outcomes of our comparison study are highly dependent on the build
-logs from the \emph{LogChunks} data set. It only consists of build
+logs from the \emph{LogChunks} data set.
+It only consists of build
 logs from open source projects and therefore it is not clear whether
-our results are generalizable to industry projects. We only collected
+our results are generalizable to industry projects.
+We only collected
 build logs from Travis CI, however we chose to evaluate on an
-information chunk whose format is not dependent on Travis CI\@. This
+information chunk whose format is not dependent on Travis CI\@.
+This
 is because the reason the build failed is described within the build
@@
 Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples. We chose this small training set
+only trained on one to five examples.
+We chose this small training set
 size as the training examples have to be provided per repository and
@@
 categories than with one category.
-% TODO Caro: Please explain the following further. Why does a
-% realistic data set only have one or few structural categories?
 This stems from the fact that we investigated the chunk retrieval
@@
   \item \textbf{Further Analysis of \emph{LogChunks}} We created the
-  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for the comparative
+  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
+  the comparative
   study in this paper, though it can be the basis for various further
-  analyses of build log data. The keywords, for example, can be
+  analyses of build log data.
+The keywords, for example, can be
   investigated to answer which keywords are used to search for the
@@
   tested each chunk retrieval technique on examples from the same
-  repository. We propose to analyze how techniques could be trained
+  repository.
+We propose to analyze how techniques could be trained
   across repositories, building the cornerstones for build
@@
   paper investigates the three chunk retrieval techniques PBE, CTS and
-  KWS\@. Our study design can be reused to evaluate other build log
+  KWS\@.
+Our study design can be reused to evaluate other build log
   analysis techniques, such as the diff and information retrieval
@@
   investigated basic configurations of existing techniques applied to
-  chunk retrieval from build logs. In a next step, each of these
+  chunk retrieval from build logs.
+In a next step, each of these
   techniques could be refined to better approach the domain of build
-  logs. The \emph{LogChunks} data set and our study results act as a
-  baseline to benchmark such technique improvements. We propose the
+  logs.
+The \emph{LogChunks} data set and our study results act as a
+  baseline to benchmark such technique improvements.
+We propose the
   following improvements:
@@
       synthesis through PROSE ranks possible programs according to
-      what the user most likely intended. One could adapt the ranking
+      what the user most likely intended.
+One could adapt the ranking
       rules provided by the FlashExtract DSL to fit common build log
-      chunk retrieval tasks. FlashExtract includes special tokens when
-      enumerating possible regular expressions. One could extend these
+      chunk retrieval tasks.
+FlashExtract includes special tokens when
+      enumerating possible regular expressions.
+One could extend these
       with tokens found in build logs, such as ``-'',``='',``ERROR''
@@
       optimized for the specific use
-      case~\cite{panichella2016parameterizing}. We propose to further
+      case~\cite{panichella2016parameterizing}.
+We propose to further
       investigate improvements in preprocessing of the log text, in
@@
   analysis of the output produced by the chunk retrieval focuses on
-  precision and recall. We propose to investigate how useful these
+  precision and recall.
+We propose to investigate how useful these
   outputs are to developers through controlled experiments.

### 2020-04-02 tse-paper/fixlong.sh

@@ -1,0 +1,7 @@
+#!/bin/sh
+# Remove carriage returns (keeping line feeds)
+tr -d \\r |
+# Start sentences on a new line
+sed 's/\.  */.\n/g' |
+# Fold (but don't join) remaining long lines
+fmt -s

### 2020-04-03 tse-paper/content.tex
fix comments, move todos to code

@@
 % 0) we introduce & define the problem 1) we survey which techniques
-exist 2) we implement (for a lack of readily available implementations)
-and compare the most promising ones 3) we draw conclusions for when to
-use which technique
+% exist 2) we implement (for a lack of readily available implementations)
+% and compare the most promising ones 3) we draw conclusions for when to
+% use which technique
 
 % TODO: Include term predictive CI, link to FB paper and
-https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
+% https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
 
 % TODO: What about the alternate solution, installing plugins to report
-precise data? Ie., maven plugins
+% precise data? Ie., maven plugins
 % - Lots of effort
@@
 % TODO It would be futile to compare our techniques with one of the
-existing manual regex parsers, as (a) as our literature survey showed,
-their scope is mainly limited to the Java ecosystem and (b) whether
-they would work or not would be randomly based on whether the project
-we select exhibits features their regular expressions were trained for.
-Finally, they are not really automatic
+% existing manual regex parsers, as (a) as our literature survey showed,
+% their scope is mainly limited to the Java ecosystem and (b) whether
+% they would work or not would be randomly based on whether the project
+% we select exhibits features their regular expressions were trained for.
+% Finally, they are not really automatic
 
@@
 
-% At the moment there is only anecdotal evidence on the performance
-of these
-% techniques and on when a technique should be preferred over other
-alternatives.
-% Developers and researches currently have little support when choosing
-which
-% technique to use for a task.
-
-% The goal of this article is to investigate different chunk retrieval
-techniques
-% for build logs and describe under which circumstances certain techniques
-can be
-% recommended over others.
-% We aim to characterize different chunk retrieval techniques.
-% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which
-criteria
-% influence the suitability of a chunk retrieval technique for CI
-build logs.
+% % At the moment there is only anecdotal evidence on the performance
+% of these
+% % techniques and on when a technique should be preferred over other
+% alternatives.
+% % Developers and researches currently have little support when choosing
+% which
+% % technique to use for a task.
+
+% % The goal of this article is to investigate different chunk retrieval
+% techniques
+% % for build logs and describe under which circumstances certain techniques
+% can be
+% % recommended over others.
+% % We aim to characterize different chunk retrieval techniques.
+% % For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which
+% criteria
+% % influence the suitability of a chunk retrieval technique for CI
+% build logs.
 
@@
   % TODO Moritz: we can relate this to travistorrent maybe, you told me
-  long ago that this was something your analyzer cannot extract
+  % long ago that this was something your analyzer cannot extract
   \label{lst:chunk-example-1}
@@
 --- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] -
-    description.`, got '* ...
+    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
   \end{lstlisting}
@@
   \caption{Example of a log chunk.
-%\todo{which build tool?}
-%  \todo{move to where structural category explanation}
+% TODO: which build tool?
+% TODO: move to where structural category explanation
 }
@@
 
-% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited
-to retrieve information from continuous integration build logs.
-% \textbf{RQ2} is refined into sub-questions along with the criteria
-resulting from \textbf{RQ1} and compares their instantiations for the
-three techniques:
-% how many training examples a technique needs to perform best
-(\textbf{RQ2.1}), how structurally diverse the examples can
-be (\textbf{RQ2.2}) and how accurate the retrieved output is
-(\textbf{RQ2.3}).
-% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set,
-which encompasses about 800 log files from 80 repositories.
-% Each log is labeled with the log part describing the reason a build
-failed, keywords to search for this log part and a categorization of
-the labeled log part according to its structural representation within
-the log.
+% % \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited
+% to retrieve information from continuous integration build logs.
+% % \textbf{RQ2} is refined into sub-questions along with the criteria
+% resulting from \textbf{RQ1} and compares their instantiations for the
+% three techniques:
+% % how many training examples a technique needs to perform best
+% (\textbf{RQ2.1}), how structurally diverse the examples can
+% be (\textbf{RQ2.2}) and how accurate the retrieved output is
+% (\textbf{RQ2.3}).
+% % To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set,
+% which encompasses about 800 log files from 80 repositories.
+% % Each log is labeled with the log part describing the reason a build
+% failed, keywords to search for this log part and a categorization of
+% the labeled log part according to its structural representation within
+% the log.
 
@@
 
-% \noindent
-% \textbf{Our work contributes:}
-% \begin{itemize}
-%   \item A tool with three prototypical implementations of chunk
-retrieval techniques:
-%	  \begin{itemize}
-%	    \item program synthesis from examples using the Microsoft
-PROSE library (PBE),
-%	    \item a common information retrieval approach using text
-similarity (CTS), and
-%	    \item a keyword search approach (KWS).
-%	  \end{itemize}
-%   \item Recommendations for the configuration of each of the
-investigated chunk retrieval techniques.
-%   \item Guidelines on choosing a suitable chunk retrieval technique.
-% \end{itemize}
+% % \noindent
+% % \textbf{Our work contributes:}
+% % \begin{itemize}
+% %   \item A tool with three prototypical implementations of chunk
+% retrieval techniques:
+% %	  \begin{itemize}
+% %	    \item program synthesis from examples using the Microsoft
+% PROSE library (PBE),
+% %	    \item a common information retrieval approach using text
+% similarity (CTS), and
+% %	    \item a keyword search approach (KWS).
+% %	  \end{itemize}
+% %   \item Recommendations for the configuration of each of the
+% investigated chunk retrieval techniques.
+% %   \item Guidelines on choosing a suitable chunk retrieval technique.
+% % \end{itemize}
 
@@
 %detection~\cite{nagappan2010abstracting}.
-Xu et
+% Xu et
 %al.~\cite{xu2009detecting} leverage the connection of log statements
@@
 %events.
-A similar approach could also be applied to build logs to
+% A similar approach could also be applied to build logs to
 %determine the sequence of executed build steps or phases.
@@
 \label{sec:rw-prose}
-% \section{Information Extraction and Retrieval Techniques} The
-% techniques we investigate are based on existing methods of
-% Programming by Example.%, information extraction and information
-% retrieval.
-This section presents different Programming by Example
-% resources surrounding the PROSE library.
-We explain its generic
-% program synthesis algorithm and how PROSE synthesizes text
-% extraction programs, the foundation of PBE\@.
+% % \section{Information Extraction and Retrieval Techniques} The
+% % techniques we investigate are based on existing methods of
+% % Programming by Example.%, information extraction and information
+% % retrieval.
+% This section presents different Programming by Example
+% % resources surrounding the PROSE library.
+% We explain its generic
+% % program synthesis algorithm and how PROSE synthesizes text
+% % extraction programs, the foundation of PBE\@.
 
@@
 % sequentiality.
-It eliminates the need for the user to understand the
+% It eliminates the need for the user to understand the
 % entire structure of the processed document and decreases the effort
@@
 
-With the term \textit{configuration,} we abstract over the training
+With the term \textit{configuration}, we abstract over the training
 and parametrization that different techniques require in different
@@
 \label{sec:expl-pbe}
-% \emph{Programming by Example} is a technique which synthesizes
-% programs according to in- and output examples provided by the user.
-% It enables users to create programs without a priori programming
-% knowledge~\cite{mayer2015user}.
-In the context of text extraction
-% through regular expressions, Programming by Example relieves the
-% developer from having to understand the whole document structure to
-% solve a single extraction task~\cite{le2014flashextract:}.
-In this
-% work, we refer to our interpretation of Programming by Example as
-% \emph{PBE}\@.
-We investigate the suitability of PBE to retrieve
-% information chunks from build logs.
-In the following, we explain the
-% configuration and application of PBE to chunk retrieval from CI
-% build logs.
+% % \emph{Programming by Example} is a technique which synthesizes
+% % programs according to in- and output examples provided by the user.
+% % It enables users to create programs without a priori programming
+% % knowledge~\cite{mayer2015user}.
+% In the context of text extraction
+% % through regular expressions, Programming by Example relieves the
+% % developer from having to understand the whole document structure to
+% % solve a single extraction task~\cite{le2014flashextract:}.
+% In this
+% % work, we refer to our interpretation of Programming by Example as
+% % \emph{PBE}\@.
+% We investigate the suitability of PBE to retrieve
+% % information chunks from build logs.
+% In the following, we explain the
+% % configuration and application of PBE to chunk retrieval from CI
+% % build logs.
 
@@
 with all training examples.
-% A program is consistent with an example if it returns the defined
-% output when executed on the defined
-% input~\cite{mitchell1982generalization}.
-PBE reports an error back to the user if it could not synthesize a
-consistent program.
-% The program synthesis builds on the FlashExtract DSL, which in turn
-% uses the FlashMeta algorithm.
-Both are described in
-% Section~\ref{sec:rw-prose}.
+% % A program is consistent with an example if it returns the defined
+% % output when executed on the defined
+% % input~\cite{mitchell1982generalization}.
+% PBE reports an error back to the user if it could not synthesize a
+% consistent program.
+% % The program synthesis builds on the FlashExtract DSL, which in turn
+% % uses the FlashMeta algorithm.
+% Both are described in
+% % Section~\ref{sec:rw-prose}.
 
 % TODO Moritz: you said: The following is very obvious and could apply
-to any
-% technique.
-
-% kinda.
-It does give a descriptive error message on no match (and
-% that is not possible in other techniques)
-% otherwise yes, nothing interesting happens in the application of pbe
-% though for consistency we might need this section? or merge
-config/application?
+% to any
+% % technique.
+
+% % kinda.
+% It does give a descriptive error message on no match (and
+% % that is not possible in other techniques)
+% % otherwise yes, nothing interesting happens in the application of pbe
+% % though for consistency we might need this section? or merge
+% config/application?
 \subsubsection{Application}
@@
 \label{sec:expl-ts}
-% Text Similarity approaches are used to filter unstructured textual
-% software
-%
-artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-% One common and simple technique is the Vector Space Model.
-We
-% investigate when text similarity is a suitable technique to retrieve
-% information chunks from build logs.
-In the following we will explain
-% the concept of how we apply text similarity to information retrieval
-% from CI build logs, which we refer to as \emph{CTS}\@.
+% % Text Similarity approaches are used to filter unstructured textual
+% % software
+% %
+% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+% % One common and simple technique is the Vector Space Model.
+% We
+% % investigate when text similarity is a suitable technique to retrieve
+% % information chunks from build logs.
+% In the following we will explain
+% % the concept of how we apply text similarity to information retrieval
+% % from CI build logs, which we refer to as \emph{CTS}\@.
 
@@
 % TODO Moritz: your question was: More details on this.
-How do you
+% How do you
 % 'apply' VSM? On what?
@@
 % Annibale said is the VSM.
-word tokens, tf-idf, similarity measure
+% word tokens, tf-idf, similarity measure
 % I added a "as follows", think that is enough for explanation?
@@
 % suitable for retrieving information chunks from CI build logs.
-In
+% In
 % the following we will explain how we use simple keyword search to
@@
 % I would not know of any details to add.
-It's really all we are doing
+%It's really all we are doing
 
@@
 %Literature mentions further build log analysis techniques.
-This
+%This
 %section describes them with our notion of chunk retrieval techniques.
@@
 % TODO Moritz: You said: Add details how key words were extracted.
-Add example?
+% Add example?
 % how the keywords were put in logchunks does not fit here, that is
@@
 % TODO Moritz: You said: Add more details.
-How was the split in numbers?
+% How was the split in numbers?
 % this is described in the following paragraph, should we merge them
@@
 % selected for retrieval.
-We evaluate the effect of varying the number
+% We evaluate the effect of varying the number
 % of extracted lines by multiplying the average number of lines
@@
 
-% The averaged precision, recall and F$_{1}$-score f all techniques is
-% compared in Figure~\ref{fig:recall-precision-all}.
-The recall of PBE
-% has a high skew towards one and zero, meaning in most cases either
-% the retrieval is successful or no relevant lines are extracted at
-% all.
-PBE has the highest average precision with 95\%.
-Chunk
-% retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% and the second highest recall with 46\%.
-KWS has the smallest
-% precision of the three chunk retrieval techniques.
-With 16\% it is
-% still higher than the precision of the RLR baseline with 7\%.
-KWS
-% has the highest recall of all techniques with 70\%.
+% % The averaged precision, recall and F$_{1}$-score f all techniques is
+% % compared in Figure~\ref{fig:recall-precision-all}.
+% The recall of PBE
+% % has a high skew towards one and zero, meaning in most cases either
+% % the retrieval is successful or no relevant lines are extracted at
+% % all.
+% PBE has the highest average precision with 95\%.
+% Chunk
+% % retrieval with CTS has the highest average F$_{1}$-score with 51\%
+% % and the second highest recall with 46\%.
+% KWS has the smallest
+% % precision of the three chunk retrieval techniques.
+% With 16\% it is
+% % still higher than the precision of the RLR baseline with 7\%.
+% KWS
+% % has the highest recall of all techniques with 70\%.
 
@@
 \section{Future Work}
-\todo{survey build logs tools in industry}
+% TODO: survey build logs tools in industry
 

### 2020-04-03 tse-paper/content.tex
fix my fmt setup, add lit survey text back

@@
 % TODO: Include term predictive CI, link to FB paper and
-% https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
+%https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
 
@@
 % techniques
-% % for build logs and describe under which circumstances certain techniques
+% % for build logs and describe under which circumstances certain
+% techniques
 % can be
@@
 
+\section{Systematic Literature Survey and Mapping}
+\label{sec:survey}
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
+	\caption{Our literature selection process, following
+	\cite{petersen2015guidelines}.}
+	\label{fig:lit-survey}
+\end{figure}
+
+% TODO (Caro): Integrate Petersen's guidelines
+From our own experience, we know that the field of analyzing build
+logs is relatively young, with perhaps the work on TravisTorrent the
+most cited and central one.
+We also know there have been scattered
+research efforts on build log analysis prior to it, mostly where the
+log analysis was a side-part of the article.
+To the best of our
+knowledge, there has not been an attempt to systematically overview
+and survey them, despite their forseeable future and current importance.
+
+\subsection{Study Selection}
+% TODO shorten
+\Cref{fig:lit-survey} presents an overview of our study selection.
+In this first literature overview study on analyzing build logs, we
+therefore want to survey as broad a population of scientific material
+as possible.
+Note that we do not limit our sources to specific
+Software Engineering venues, as is often done, but survey all sources
+monitored by Google Scholar, including Bachelor's and Master's theses,
+academic slide decks, and books.
+We use Google Scholar as opposed to
+Scopus or other databases, as it is the search engine for acdemic
+articles with the broadest and most current index, including preprints
+from sources such as arXiv.
+One challenge is that no common
+nomenclature has been established yet (in fact, this is one of the
+goals of this article).
+
+% TODO Caro cite guidelines
+Since we cannot take for granted that ``analyzing build logs'' is the
+cannonical term that other, isolated works have used, we instead
+decdided to leave out the potentially variable ``analysis'' part and
+instead focus on variations of the term ``build log''.
+This has the
+advantage of being biunique: We explicitly decided to exclude systems
+or event logs (see \Cref{sec:rw}).
+On the other hand, a Google Scholar
+search for ``build log'' returns more than 2.2 million results
+(2020-03-15).
+We therefore refined our search criterions for the four
+different spelling possibilities of ``build log'' to exclude obvious
+non-related works.
+This left us with 1,552 combined search results
+(2020-03-15).
+The full search queries are documented in our replication
+package~\cite{brandt2020chunk-replication}.
+
+To make handling so many search results feasible, we employed a
+two-pass filtering strategy:
+
+First, we filtered out articles based on 1) their title and 2) the
+contextual information Google Scholar displayed.
+We inlcuded only
+publications written in a language intelligible to the authors (that
+is, English or German), but only disregarded fewer than 1\% of search
+hits due to this criterion.
+Our strategy was to err on the side of
+caution, that is rather including a paper than not.
+We then unified
+the results of the four search queries based on the link as the
+identifying element, removing 60 articles that appeared in more than
+one search query.
+We noticed that some publishers (ACM, Springer,
+Google Books) augment a link to an article with a cutomized ID, which
+specifies the link source ({\tt casa\_token, oid}).
+\todo{overly specific?} We automatically
+removed it to find all true duplicates.
+After this process, we were
+left with 259 (17\%) of the original search results.
+
+With these 259 remaining articles, we followed a backward snowball
+sampling for related work.
+This added three papers (five before
+duplicate elimination) to our literature set, coming to a total of 261
+articles.
+% TODO: update numbers
+
+On the surviving artciles, we did a second filter phase by downloading the
+full articles, reading their abstracts, and searching the full text
+for the occurrence of ``log''.
+If these papers showed traces of
+working with build logs, we included them in our survey.
+For the
+snowballed set, we included two of the three articles, both of which
+stem from the same first author, were borderline-includes, and had
+called build logs from the Linux kernel ``build traces.'' In total, we
+were left with 90 articles after this search.
+
+\subsection{Article Classification}
+Having trimmed down the set of articles, we investigated them in depth.
+kept all articles that use logs from software builds as input to some
+kind of process.
+we wanted to characterize how researchers use buildlogs as input to
+any processes.
+Interesed in
+\begin{itemize}
+  \item what kind of build logs they are using and the source of these
+  logs.
+  \item what information they are retrieving from the logs,
+  its kind (chunk/classification) and
+  what they use the retrieved information for
+  \item which technique they are using to process the build logs,
+  in how much detail it is described and whether they published their
+  tools
+\end{itemize}
+To objecifiy our data extraction we created a template of the targeted
+factors
+and performed a pilot on five articles.
+Two authors extracted the data from the
+five pilot articles and we held a consensus meeting to unify our
+understanding
+of the factors in the data extraction templates.
+The remaining articles were
+divided over these two authors.
+We inspected the articles as closesly as necessary,
+starting from occurences of ``log'' or ``build'' within the text.
+The full data extraction template and our results of this step can be
+found in
+our replication package \todo{cite}.
+
+In this pass we further identified x duplicate articles \todo{do we push
+those to the last pass?}.
+For several cases, multiple articles extended others, though still
+reported on
+the same work with the respect to analyzing build logs.
+Of these we only considered the earliest article which reported on
+the processing
+of build logs.
+
+\subsection{Results}
+lots of:
+- categories + frequencies of answers
+
+\subsubsection{Retrieved Information}
+
+\subsubsection{Retrieval Technique}
+
+\subsubsection{Build Logs}
+
+\subsection{Discussion}
+various researchers analyzing build logs to support their research,
+tools developed to help developers \todo{motivational reference}.
+
+\subsubsection{Retrieved Information}
+why from build logs? not avaliable in cleaner format much use for
+research, a bit of developer information / tools following: research
+so many logs that unfeasible to do manually, less focus on tools for
+devs (caveat! we excluded books and documentation on industrial tools
+-> many approaches there to make build logs digestible, tough many
+focus on general minimizing of the data presented, not retrieving
+specific chunks)
+
+\subsubsection{Retrieval Technique}
+broadly mentioned shortly, rarely explained in detail we follow that
+researchers often see this as an unimportant side fact work needed to
+be done to get the big work done
+
+\subsubsection{Build Logs}
+often focussed on specific logs, sometimes mentioned because of effort
+developing a parser other times also because other tools used in
+further research are limiting the scope (reference paper with PIT
+tool).
+many focus on maven because of it's prevalence also in respect
+to other tools much research done on travis ci logs b/c of their
+abundance and open availability
+
 \section{Related Work}
@@
 % %
-% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+%artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
 % % One common and simple technique is the Vector Space Model.
@@
 The goal of this paper was to support researchers and developers in
-their decision on how to analyze build logs. We implemented and
+their decision on how to analyze build logs.
+We implemented and
 compared three different chunk retrieval techniques on our data set
 \emph{LogChunks}, composed of 797 manually labeled build logs from a
-broad range of 80 repositories. Our results show that the structural
+broad range of 80 repositories.
+Our results show that the structural
 representation of the targeted information in the build logs is the
-main factor to consider when choosing a suitable technique. Secondary
+main factor to consider when choosing a suitable technique.
+Secondary
 factors are the desired confidence into recall and precision of the

### 2020-04-03 tse-paper/content.tex
move todos to tex

@@
 specifies the link source ({\tt casa\_token, oid}).
-\todo{overly specific?} We automatically
+% TODO: {overly specific?}
+We automatically
 removed it to find all true duplicates.
@@
 found in
-our replication package \todo{cite}.
-
-In this pass we further identified x duplicate articles \todo{do we push
-those to the last pass?}.
+our replication package % TODO: {cite}.
+
+In this pass we further identified x duplicate articles % TODO: {do we push
+% those to the last pass?}.
 For several cases, multiple articles extended others, though still
@@
 various researchers analyzing build logs to support their research,
-tools developed to help developers \todo{motivational reference}.
+tools developed to help developers % TODO: {motivational reference}.
 

### 2020-04-03 tse-paper/abstract.tex
small corrections introduction, Closes #20

@@
 create, often as part of their Continuous Integration (CI)
-pipeline. Build logs can serve as a paramount source of
-information for developers to understand and debugg build or
-test failures. Manually
+pipeline.
+Build logs can serve as a paramount source of
+information for developers to understand and debug build or
+test failures.
+Manually
 extracting the important chunks of information, though, is akin to
-finding a needle in a haystack. Recently, researchers and practitioners have begun attempts to partly automate
-this time-consuming activity, with the proposition to not only ease developers' tasks but to enable a new class of automated on-ward processing applications.
-In this paper, we want to give a systematic overview of the state of the art of the emerging field of build log analysis.
-To this end, we first survey and categorize the existing methods to extract information chunks from build logs.
-We then develop prototypical implementations for three promising techniques, namely program synthesis
-by example, textual similarity and search keywords. Finally, we evaluate the three techniques in an empirical study on our manually
-labeled \emph{LogChunks} data set, which comprises 797 build logs in 29 languages.
+finding a needle in a haystack.
+Recently, researchers and practitioners have begun attempts to partly
+automate
+this time-consuming activity, with the proposition to not only ease
+developers' and researcher's tasks but to enable a new class of automated
+on-ward processing applications.
+In this paper, we want to give a systematic overview of the state of
+the art of the emerging field of build log analysis.
+To this end, we first survey and categorize the existing methods to
+extract information from build logs.
+We then develop prototypical implementations for three promising
+techniques, namely program synthesis
+by example, textual similarity and search keywords.
+Finally, we evaluate the three techniques in an empirical study on
+our manually
+labeled \emph{LogChunks} data set, which comprises 797 build logs in
+29 languages.
 Our findings show that none of the three techniques in general outperforms
-the others, but rather, that each technique has its respective strengths and weaknesses. We discuss under which circumstances each technique performs best
-and provide a recommendation on when developers or researchers should use which
-technique.
+the others, but rather, that each technique has its respective strengths
+and weaknesses.
+We discuss under which circumstances each technique performs best
+and provide a recommendation on when developers or researchers should
+use which technique.

### 2020-04-03 tse-paper/content.tex
small corrections introduction, Closes #20

@@
 To gain an impression on how researchers are using information from
-build logs
-within their research and how they are gathering chunks from them
-to support
-developers in understanding build outcomes, we conducted a systematic
-mapping
-study.
-Our goal was to classify how and what for researchers use build logs as
-a source
-of data (\textbf{RQ1}).
+build logs within their research to support
+developers, we conducted a systematic mapping study.
+Our goal was to classify how, and what for, researchers use build logs as
+a source of data (\textbf{RQ1}).
 
 The outcomes of our study shows that there are various attempts to
-retrieve
-specific information from buildlogs.
-The resulting implementations are rarely
-available and therefore rarely reused.
+retrieve specific information from buildlogs.
+The resulting implementations are rarely available and therefore rarely reused.
 Because of the high development overhead
 of the custom parsers, many implementations are limited to small number
-of supported
-build tools.
+of supported build tools.
 
@@
 log analysis.
-They retrieve specific chunks of targeted information and are configured
-by
-examples provided by the user.
+They retrieve specific chunks of targeted information and are trained
+with examples provided by the user.
 We conduct an empirical study on the \emph{LogChunks} data
@@
   \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and targeted log chunks, PBE
+  Based on user examples of build logs and chunks, PBE
   synthesizes
@@
   \end{lstlisting}
-  \caption{Example of a log chunk explaining why an Android/Gradle
+  \caption{Example of a log chunk explaining why an Android
   build failed.}
@@
   \end{lstlisting}
-  \caption{Another example of a log chunk explaining why an Android/Gradle
+  \caption{Another example of a log chunk explaining why an Android
   build failed.}
@@
   \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/{\color{Plum}$\circ$}/Line Separator",
+StartExtraction(RegexPair("Colon/$\circ$/Line Separator",
 "ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/",
-"Line Separator/{\color{Plum}$\circ$}/Line Separator"))
+"Line Separator/$\circ$/Line Separator"))
   \end{lstlisting}
@@
   \end{lstlisting}
-  \caption{Example of a log chunk.
-% TODO: which build tool?
-% TODO: move to where structural category explanation
-}
+  \caption{Example of a log chunk showing a linter error}
   \label{lst:chunk-example-3}
@@
 \Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary
-log chunks
-from Android/Gradle build logs marked in blue.
+log chunks from Android build logs marked in blue.
 Both chunks contain the information on why the
 corresponding build failed.
-When PBE is trained on these two examples it produces
-a regular expression similar to \Cref{lst:prose-program-simplified}.
+When PBE is trained with these two examples it produces
+a regular expression program similar to the one presented in
+\Cref{lst:prose-program-simplified}.
 The retrieval
-starts after a colon followed by a line separator and before a capital
+starts after a colon and a line separator and before a capital
 letter.
 It ends before two line separators, consistent with the two example
-chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2}.
+chunks from \Cref{lst:chunk-example-1,lst:chunk-example-2}.
 This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify the targeted log chunk.
-In fact, if the third
-example from \Cref{lst:chunk-example-3} with a different structural
-representation is added, PBE is not able to syntesize a program and
-returns
+cruicial for regular expressions to identify a log chunk.
+In fact, if the third example from \Cref{lst:chunk-example-3} with a
+different structural representation is added to the training set,
+PBE is not able to syntesize a program and returns
 ``\texttt{no program found}''.
 We express this difference in structural representation through
-dividing log
-chunks into structural categories.
-The chunks from
-\Cref{lst:chunk-example-1,lst:chunk-example-2} are in the same structural
-category, while the chunk from \Cref{lst:chunk-example-3} is in a
-different one.
+dividing log chunks into structural categories.
+The chunks from \Cref{lst:chunk-example-1,lst:chunk-example-2}
+are in the \emph{same structural category}, while the chunk from
+\Cref{lst:chunk-example-3} is in a \emph{different structural category}.
 
@@
 
-Our study of the three techniques on \emph{LogChunks} shows that
-\begin{itemize}
-  \item PBE yields very accurate results when trained with two examples
-  from a
-  single structural category.
-  \item CTS shows the best average precision, though precision and recall
-  of a
-  retrieval is hard to determine from the given result.
-  A small increase in the number of training examples has no noticeable
-  influence.
-
-  Fewer structural categories improve precision and recall of the
-  retrieval.
-  \item KWS has the highest recall of all techniques, however much
-  lower precision.
-  It is the technique with the best recall when multiple structural
-  categories
-  are present in the training examples.
-\end{itemize}
+% Our study of the three techniques on \emph{LogChunks} shows that
+% \begin{itemize}
+%   \item PBE yields very accurate results when trained with two examples
+%   from a
+%   single structural category.
+%   \item CTS shows the best average precision, though precision and recall
+%   of a
+%   retrieval is hard to determine from the given result.
+%   A small increase in the number of training examples has no noticeable
+%   influence.
+
+%   Fewer structural categories improve precision and recall of the
+%   retrieval.
+%   \item KWS has the highest recall of all techniques, however much
+%   lower precision.
+%   It is the technique with the best recall when multiple structural
+%   categories
+%   are present in the training examples.
+% \end{itemize}
 
@@
 
-We recommend PBE for use cases where the desired information is always
+Following the results from our comparison study,
+recommend PBE for use cases where the desired information is always
 represented in the same structural way and high confidence in precision
-and
-recall of the chunk retrieval is required.
+and recall of the chunk retrieval is required.
+Results produced by PBE are suited for automatic on-ward processing.
 CTS is well suited when the representation of the desired information
@@
 We also know there have been scattered
-research efforts on build log analysis prior to it, mostly where the
+research efforts on build log analysis, mostly where the
 log analysis was a side-part of the article.
@@
 knowledge, there has not been an attempt to systematically overview
-and survey them, despite their forseeable future and current importance.
+and survey approaches for processing build logs,
+despite their forseeable future and current importance.
 
@@
 Note that we do not limit our sources to specific
-Software Engineering venues, as is often done, but survey all sources
+Software Engineering venues, as is often
+done~\cite{petersen2015guidelines}, but survey all sources
 monitored by Google Scholar, including Bachelor's and Master's theses,
@@
 from sources such as arXiv.
+% TODO: maybe remove. this screams snowballing needed
 One challenge is that no common
@@
 % TODO Caro cite guidelines
-Since we cannot take for granted that ``analyzing build logs'' is the
-cannonical term that other, isolated works have used, we instead
-decdided to leave out the potentially variable ``analysis'' part and
-instead focus on variations of the term ``build log''.
-This has the
-advantage of being biunique: We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}).
-On the other hand, a Google Scholar
-search for ``build log'' returns more than 2.2 million results
+Our Google Scholar
+search for variations ``build log'' returns more than 2.2 million results
 (2020-03-15).
@@
 non-related works.
+We explicitly decided to exclude systems
+or event logs (see \Cref{sec:rw}).
 This left us with 1,552 combined search results

### 2020-04-03 tse-paper/content.tex
adaptations to lit survey draft

@@
 
-First, we filtered out articles based on 1) their title and 2) the
+First, we filtered out articles based on (1) their title and (2) the
 contextual information Google Scholar displayed.
@@
 publications written in a language intelligible to the authors (that
-is, English or German), but only disregarded fewer than 1\% of search
-hits due to this criterion.
+is, English or German), which disregarded fewer than 1\% of search
+hits.
 Our strategy was to err on the side of
@@
 one search query.
-We noticed that some publishers (ACM, Springer,
-Google Books) augment a link to an article with a cutomized ID, which
-specifies the link source ({\tt casa\_token, oid}).
-% TODO: {overly specific?}
-We automatically
-removed it to find all true duplicates.
-After this process, we were
+We automatically removed all duplicates and were
 left with 259 (17\%) of the original search results.
@@
 If these papers showed traces of
-working with build logs, we included them in our survey.
-For the
-snowballed set, we included two of the three articles, both of which
-stem from the same first author, were borderline-includes, and had
-called build logs from the Linux kernel ``build traces.'' In total, we
+working with build logs, we included them in our survey. In total, we
 were left with 90 articles after this search.
@@
 Having trimmed down the set of articles, we investigated them in depth.
-kept all articles that use logs from software builds as input to some
-kind of process.
+We kept all articles that use logs from software builds as input to
+some kind of process.
 we wanted to characterize how researchers use buildlogs as input to
 any processes.
-Interesed in
+We were interesed in
 \begin{itemize}
@@
 To objecifiy our data extraction we created a template of the targeted
-factors
-and performed a pilot on five articles.
-Two authors extracted the data from the
-five pilot articles and we held a consensus meeting to unify our
-understanding
-of the factors in the data extraction templates.
+factors and performed a pilot.
+Two authors extracted the data from five articles and we held a
+consensus meeting to unify our understanding
+of the data extraction template.
 The remaining articles were
 divided over these two authors.
-We inspected the articles as closesly as necessary,
+We inspected the articles as closely as necessary,
 starting from occurences of ``log'' or ``build'' within the text.
 The full data extraction template and our results of this step can be
-found in
-our replication package % TODO: {cite}.
+found in our replication package~\cite{brandt2020chunk-replication}.
 
@@
 reported on
-the same work with the respect to analyzing build logs.
+the same work with the respect to processing build logs.
 Of these we only considered the earliest article which reported on

### 2020-04-03 tse-paper/content.tex
small fixes in study sections

@@
 \label{sec:rw-prose}
-% % \section{Information Extraction and Retrieval Techniques} The
+% % \section){Information Extraction and Retrieval Techniques} The
 % % techniques we investigate are based on existing methods of
@@
 \label{sec:techniques}
+% TODO: rework! extend / relate to further techniques
 This section introduces key concepts of the three chunk retrieval
@@
 
-% TODO Caro: I find this figure still very confusing :'(, due to a lack
-of structure.
-If you want me to, I can give it a go?
+% TODO Caro: redo
 \begin{figure*}[tb]
@@
 
-To investigate which techqnique is best suited to retrieve chunks from
-CI build logs we evaluate them on the
-\emph{LogChunks}~\cite{brandt2020logchunks} data set.
+To investigate which technique is best suited to retrieve chunks from
+CI build logs we evaluate the three chunk retrieval techniques
+PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
+\ref{sec:expl-ts} and \ref{sec:expl-skws}.
+Random Line Retrieval
+(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
+the comparison.
 This section
@@
 
-For the comparison, we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}.
-Random Line Retrieval
-(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
-the comparison.
 % We run four techniques on the examples from \emph{LogChunks}.
@@
 \textbf{Training and Test Set}
-We use \emph{LogChunks} as the data set for our study.
-For each of the
-80 repositories in it, \emph{LogChunks} contains 10 build logs,
-manually labeled with the \emph{chunk} describing the
-reason the build failed.
-Additionally, it contains (1) keywords useful
-to identify the substring in the log  and (2) which structural category
-the substring belongs to.
 % TODO Moritz: You said: Add details how key words were extracted.
@@
 \textbf{RQ 2.1: Size of Training and Test Set}
-To analyze how many examples the chunk retrieval techniques need to
-perform best, we evaluate the techniques with different training set
-sizes.
+We evaluate the techniques with different training set
+sizes, to analyze how many examples the chunk retrieval techniques need to
+perform best.
 We train each technique with one to five examples from each of
 the repositories within \emph{LogChunks}.
-The size of the test set is
-one.
+The size of the test set is one.
 
@@
 \textbf{RQ 2.2: Recording Structural Categories}
-To determine how structurally similar the examples for the chunk
-retrieval techniques need to be, we record the structural categories
-of the examples in the training and test sets.
+We record the structural categories
+of the examples in the training and test sets, to determine how
+structurally similar the examples for the chunk
+retrieval techniques need to be.
 
@@
 \textbf{RQ2.3: Accuracy Metrics}
-To measure the accuracy of the retrieved chunks we save the output
-lines of the chunk retrieval run on the input of the test example
-($\mathit{RetrievedLines}$).
+we save the output lines of the chunk retrieval run on the input
+of the test example ($\mathit{RetrievedLines}$), to measure the
+accuracy of the retrieved chunks 
 As oracle in our evaluation, we save the
@@
 \begin{itemize}[leftmargin=0.4cm] \itemsep1em
-	\item $|\mbox{True positives}| = \mathit{DesiredLines} \cap
+	\item $|\mbox{True\ Positives}| = \mathit{DesiredLines} \cap
 	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
 	True positives are lines that appear both in the output of a
-	tool as well as what \textit{LogChunks} contains for each
-	example.
+	tool as well as what \textit{LogChunks} contains for the
+  test example.
 
@@
 	\item $\mbox{Recall} =
-	\dfrac{|\mathit{TruePositives}|}{|\mathit{DesiredLines}|}$
+	\dfrac{|\mathit{True\ Positives}|}{|\mathit{DesiredLines}|}$
 	\vspace{0.2cm} \\
@@
 
-% Recall and precision of CTS and KWS vary with the number of lines
-% selected for retrieval.
-% We evaluate the effect of varying the number
-% of extracted lines by multiplying the average number of lines
-% present in the training examples with a \emph{retrieval size factor}
-% from 0.5 to 2.5 in steps of 0.5.
-
 \section{Results}
-This section presents the results for PBE, CTS and KWS separately.
+This section presents the separate results for each chunk retrieval
+technique. We start with CTS, KWS and RLR, as their results are easiest to
+understand.
 Afterwards we compare the three techniques with each other and RLR as
@@
   morekeywords={Test, Output, Desired},
-	basicstyle=\ttfamily\scriptsize,
-  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
-  showspaces=false,
-  showstringspaces=false,
   keywordstyle=\textbf,
-	frame=single,
-  extendedchars=false,
-  texcl=false
+	frame=single
 }
@@
 		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an
-		increasing training set size.}
+		\caption{Compared with the training set size.}
 		\label{fig:recall-precision-examplecount-CTS}
@@
 				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for
-		an increasing number of structural categories in the
+		\caption{Compared with the number of structural categories in the
 		training and test sets.}
@@
 \end{subfigure}
-\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
+\caption{Precision, recall and F$_{1}$-score of chunk
+retrieval with Common Text Similarity (CTS)}
 \end{figure*}
@@
 		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for an
-		increasing training set size.}
+		\caption{Compared with the training set size.}
 		\label{fig:recall-precision-examplecount-KWS}
@@
 		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Precision, recall and F$_{1}$-score for
-		an increasing number of structural categories in the
+		\caption{Compared with the number of structural categories in the
 		training and test sets.}
@@
 \end{subfigure}
-\caption{Results of chunk retrieval with Keyword Search (KWS)}
+\caption{Precision, recall and F$_{1}$-score of chunk retrieval with
+Keyword Search (KWS)}
 \end{figure*}
@@
 
-% Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the
-% effect of the retrieval size factor on precision, recall and
-% F$_{1}$-score of chunk retrieval runs with KWS\@.
-%The precision is
-% 19\% when retrieving half of the expected number of lines.
-%On
-% average 9\% of the lines in the build log are retrieved then.
-%When
-% 2.5 times the expected number of lines are retrieved, the precision
-% decreases to 10\% and a quarter of the lines in the build log are
-% retrieved on average.
-%The recall ranges from 58\% to 75\% and the
-% F$_{1}$-score shows a constant decrease from 29\% to 17\%.
-
-% \begin{figure}[!t]
-%		\centering
-%		\includegraphics[width=\columnwidth,
-%clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
-%		\caption{Precision, recall and F$_{1}$-score of chunk
-%retrieval with KWS compared to retrieval size factor.}
-%		\label{fig:contextsizefactor-precision-recall-KWS}
-% \end{figure}
+\subsection{Random Line Retrieval}
+\label{sec:r:rlr}
+
+In our evaluation, we compare against a baseline of randomly
+picking lines from the build log.
+Its results follow intuitive
+expectations:
+The precision ranges between 8\% and 5\%, the recall between 6\% and
+8\%.
+The size of the training set has no visible impact on either.
+An larger number of structural categories within the training and
+test sets decreased the precision of RLR from 7\% to 0\%, the recall
+increases from 6\%, for one structural category present, to 11\%, for
+three sturctural categories present and also drops to 0\% for more
+structural categories.
+Graphs of the results of the chunk retrieval with RLR from our study
+are included in our replication
+package~\cite{brandt2020chunk-replication}.
 
@@
 		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-				\caption{Increasing number of structural
-				categories in the training and test sets.}
+				\caption{Successfulness of retrieval compared with the number of
+        structural categories in the training and test sets.}
 		\label{fig:failure-reason-categorycount-PBE}
@@
 
-\subsection{Random Line Retrieval}
-\label{sec:r:rlr}
-
-In our evaluation, we compare against a baseline of randomly
-picking lines from the build log.
-Its results follow intuitive
-expectations:
-The precision ranges between 8\% and 5\%, the recall between 6\% and
-8\%.
-The size of the training set has no visible impact on either.
-An greater number of structural categories within the training and
-test sets decreased the precision of RLR from 7\% to 0\%, the recall
-increases from 6\%, for one structural category present, to 11\%, for
-three sturctural categories present and also drops to 0\% for more
-structural categories.
-Graphs of the results of the chunk retrieval with RLR from our study
-are included in our replication
-package~\cite{brandt2020chunk-replication}.
-
 \subsection{Comparison of All Techniques}
-In this section, we aggregate the results from
-\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr} and put them next to it
-each other.
+Next, we aggregate the results from
+\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr}.
 
@@
 				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all
-		techniques when training examples are in \emph{one}
+		\caption{Training and test examples are in \emph{one}
 		structural category.}
@@
 		clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Precision, recall and F$_{1}$-score of all
-		techniques when training examples are in \emph{more than
+		\caption{Training and test examples are in \emph{more than
 		one} structural categories.}
@@
 \end{subfigure}
-\caption{Comparison of all chunk retrieval techniques, split by structural
-category count.}
+\caption{Precision, recall and F$_{1}$-score of all
+techniques compared, split by structural category count.}
 \end{figure*}

### 2020-04-06 tse-paper/content.tex
incl. xcolors in travis
adapted numbers in literature survey part, also moving back duplicates to original duplicate removal within first pass/filter, closes #25

@@
+% \section{Introduction}
 % Todo: Introduction structure
@@
 retrieve specific information from buildlogs.
-The resulting implementations are rarely available and therefore rarely reused.
+The resulting implementations are rarely available and therefore rarely
+reused.
 Because of the high development overhead
@@
 %   single structural category.
-%   \item CTS shows the best average precision, though precision and recall
+%   \item CTS shows the best average precision, though precision and
+recall
 %   of a
@@
 from sources such as arXiv.
-% TODO: maybe remove. this screams snowballing needed
+% TODO: maybe remove, this screams snowballing needed
 One challenge is that no common
@@
 one search query.
-We automatically removed all duplicates and were
-left with 259 (17\%) of the original search results.
-
-With these 259 remaining articles, we followed a backward snowball
+We removed further duplicates based on the title and were
+left with 256 (16\%) of the original search results.
+% removed duplicates of data extraction pass already here
+
+With these 256 remaining articles, we followed a backward snowball
 sampling for related work.
-This added three papers (five before
+This added five papers (eight before
 duplicate elimination) to our literature set, coming to a total of 261
 articles.
-% TODO: update numbers
 
@@
 If these papers showed traces of
-working with build logs, we included them in our survey. In total, we
-were left with 90 articles after this search.
+working with build logs, we included them in our survey.
+In total, we
+were left with 87 articles after this search.
 
@@
 We kept all articles that use logs from software builds as input to
-some kind of process.
-we wanted to characterize how researchers use buildlogs as input to
+some kind of process and excluded another 15 articles.
+For several cases, multiple articles extended others, though still
+reported on
+the same work with the respect to processing build logs.
+Of these we only considered the earliest article which reported on
+the processing of build logs.
+This excluded 11 articles from our survey.
+In sum, we further classify 61 articles.
+
+We wanted to characterize how researchers use buildlogs as input to
 any processes.
@@
 of the data extraction template.
-The remaining articles were
-divided over these two authors.
+The remaining articles were divided over these two authors.
 We inspected the articles as closely as necessary,
 starting from occurences of ``log'' or ``build'' within the text.
+
 The full data extraction template and our results of this step can be
 found in our replication package~\cite{brandt2020chunk-replication}.
-
-In this pass we further identified x duplicate articles % TODO: {do we push
-% those to the last pass?}.
-For several cases, multiple articles extended others, though still
-reported on
-the same work with the respect to processing build logs.
-Of these we only considered the earliest article which reported on
-the processing
-of build logs.
 
@@
 This section presents the separate results for each chunk retrieval
-technique. We start with CTS, KWS and RLR, as their results are easiest to
+technique.
+We start with CTS, KWS and RLR, as their results are easiest to
 understand.
@@
 				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Compared with the number of structural categories in the
+		\caption{Compared with the number of structural categories
+		in the
 		training and test sets.}
@@
 		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Compared with the number of structural categories in the
+		\caption{Compared with the number of structural categories
+		in the
 		training and test sets.}
@@
 		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-				\caption{Successfulness of retrieval compared with the number of
+				\caption{Successfulness of retrieval
+				compared with the number of
 	structural categories in the training and test sets.}

### 2020-04-06 tse-paper/content.tex
Add graphs from GSheets
Refs #23

--- 2020-04-03 tse-paper/content.tex
@@
 from sources such as arXiv.
-% TODO: maybe remove. this screams snowballing needed
+% TODO: maybe remove.
+this screams snowballing needed
 One challenge is that no common
@@
 If these papers showed traces of
-working with build logs, we included them in our survey. In total, we
+working with build logs, we included them in our survey.
+In total, we
 were left with 90 articles after this search.
@@
 
-In this pass we further identified x duplicate articles % TODO: {do we push
+In this pass we further identified x duplicate articles % TODO: {do
+we push
 % those to the last pass?}.
@@
 - categories + frequencies of answers
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/techniques.pdf}
+		\caption{Frequency of different technique labels for
+		labels $>1$ occurence.}
+		\label{fig:litsur:techniques}
+\end{figure}
 

### 2020-04-06 tse-paper/content.tex
describe results of literature survey

--- 2020-04-06 tse-paper/content.tex
@@
 %   \item CTS shows the best average precision, though precision and
-recall
+% recall
 %   of a
@@
 found in our replication package~\cite{brandt2020chunk-replication}.
+Note that for most questions we allowed assigning multiple values, e.g.
+if
+two kinds of informations were targeted during a build log analysis.
 
 \subsection{Results}
-lots of:
-- categories + frequencies of answers
+In the following, we will present the results of our literature survey.
+Starting with the information that was targeted and what it was employed
+for, over the techniques used until the origin of the build logs
+which were
+analyzed.
+
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/techniques.pdf}
+		\caption{Frequency of different technique labels for
+		labels $>1$ occurence.}
+		\label{fig:litsur:techniques}
+\end{figure}
+
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/info_target.pdf}
+		\caption{Frequency of different targeted information
+		labels for
+		labels $>1$ occurence.}
+		\label{fig:litsur:info_target}
+\end{figure}
+
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/use.pdf}
+		\caption{Frequency of different usage of output labels for
+		labels $>1$ occurence.}
+		\label{fig:litsur:use}
+\end{figure}
+
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/log_producer.pdf}
+		\caption{Frequency of different log producer labels for
+		labels $>1$ occurence.}
+		\label{fig:litsur:log_producer}
+\end{figure}
 
 \subsubsection{Retrieved Information}
+The information that was targeted is presented in
+\Cref{fig:litsur:info_target} varied from article to article.
+Most prominent was the search for errors (39\%) that occured within
+the build process, followed by extracting the executed or the failing
+tests
+(both 11\%).
+
+In most cases (51\%), a chunk was retrieved from the log, whereas 36\%
+of the articles classified the articles into categories.
+Other types of processing (e.g.
+counting lines, summarization) were only
+done in one case each.
+
+The majority of articles (46\%) used the outcome of their build log
+analysis
+for research purpopses, as shown in \Cref{fig:litsur:use}.
+Further uses were giving feedback to developers (10\%) or automatic
+on-ward
+processing of the retrieved information (8\%).
 
 \subsubsection{Retrieval Technique}
+\Cref{fig:lisur:techniques} presents the techniques which the articles
+described for processing build logs.
+43 of the 61 articles we inspected touched on how they are analyzing build
+logs.
+However, only 16 of these described their method in detail.
+
+The most mentioned method (34\%) was using a parser, where we also
+included
+rather unprecise statements like ``we parse the build logs''.
+25\% of the articles described the use of regular expressions and 20\%
+inspected the logs manually.
+Another 8\% employed machine learning techniques such as natural language
+processing or information retrieval techniques.
+
+25\% of the articles claimed their implementation is available, however we
+saw very low reuse of build log analysis tools within our survey.
+Five articles employed the tools used to create
+\emph{TravisTorrent}~\cite{beller2017travistorrent}, two used the
+\emph{Maven Log Analyzer}, % TODO: cite
+another two the \emph{MAKAO} tool.
+% TODO: cite
 
 \subsubsection{Build Logs}
+Of the articles we surveyed, 30\% analyzed build logs produced by
+Maven~\cite{maven2019website}, 16\% ones produced by Gradle % TODO: cite
+and 10\% logs produced by Ant.
+% TODO: cite
+The distribution of supported build tools is shown in
+\Cref{fig:litsur:log_producer}.
+Only 7\% of the proposed methods claimed to be language-agnostic, while
+several described they are covering multiple source build tools.
+The majority of articles (42\%) targeted logs from a source which was not
+targeted by any second article.
+
+The main platform that build logs were collected from is Travis
+CI, % TODO cite.
+which was used in 38\% of cases.
+18\% of the articles processed logs from TravisTorrent and 8\% included
+build logs from industrial projects.
+
+The number of logs analyzed varied greatly and we were not always able to
+extract it confidently.
+Articles reported processing from two up to 122 million logs.
+
+31\% of the surveyed articles claimed to have published their data to
+enable further research.
 

### 2020-04-06 tse-paper/content.tex
Add new table. Improve existing figures.

@@
 
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=\columnwidth,
-		clip]{img/lit-sur/techniques.pdf}
-		\caption{Frequency of different technique labels for
-		labels $>1$ occurence.}
-		\label{fig:litsur:techniques}
-\end{figure}
-
-\begin{figure}[tbp]
+\begin{table*}[]
+\centering
+\caption{Overview of buildlog analysis techniques.}
+\begin{tabularx}{\textwidth}{@{}lXX@{}}
+\toprule
+Name			     & Source(s)	& Frequency 	  \\
+\midrule
+Parser  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}	\\
+Regular expression  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}	\\
+Manual inspection  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}	\\
+Machine Learning  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}	\\
+Natural Language Processing  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}	\\
+Information Retrieval  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}	\\
+Analysis  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}	\\
+Keyword Search  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}	\\
+Scan  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}	\\
+Other  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}	\\
+\bottomrule
+\end{tabularx}
+\label{tab:obat}
+\end{table*}
+
+\begin{figure}[tbhp]
 		\centering
@@
 		clip]{img/lit-sur/info_target.pdf}
-		\caption{Frequency of different targeted information
-		labels for
-		labels $>1$ occurence.}
+		\caption{Information targeted in build log analysis.}
 		\label{fig:litsur:info_target}
@@
 
-\begin{figure}[tbp]
+\begin{figure}[tbhp]
 		\centering
@@
 		clip]{img/lit-sur/use.pdf}
-		\caption{Frequency of different usage of output labels for
-		labels $>1$ occurence.}
+		\caption{Purpose of build log analysis.}
 		\label{fig:litsur:use}
@@
 
-\begin{figure}[tbp]
+\begin{figure}[tbhp]
 		\centering
 		\includegraphics[width=\columnwidth,
-		clip]{img/lit-sur/log_producer.pdf}
-		\caption{Frequency of different log producer labels for
-		labels $>1$ occurence.}
+		clip]{img/lit-sur/log_producer_long-cropped.pdf}
+		\caption{Frequency of supported log producer.}
 		\label{fig:litsur:log_producer}
@@
 \centering
-\caption{Overview of the described chunk retrieval techniques.}
+\caption{Chunk retrieval techniques.}
 \begin{tabularx}{\textwidth}{@{}XlXlXX@{}}

### 2020-04-06 tse-paper/content.tex
add new overview & study graphic

@@
 
+\begin{figure*}[htb]
+	\centering
+	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
+	clip]{img/overview.pdf}
+	\caption{Our Research Workflow.}
+	\label{fig:overview}
+\end{figure*}
+
 To address this, we implement three promising techniques for build
@@
 (\textbf{RQ2}).
+
+\Cref{fig:overview} gives an overview of our research steps.
 
@@
 	\centering
-	\includegraphics[width=\textwidth, trim={0.4cm 8.4cm 1.2cm 0.3cm},
+	\includegraphics[width=\textwidth, trim={0.5cm 1.3cm 0.2cm 0.3cm},
   clip]{img/study.pdf}
-	\caption{Study design of our technique comparison study.}
+	\caption{Design of our technique comparison study.}
 	\label{fig:study}
@@
 		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Compared with the training set size.}
+		\caption{Compared with the training set size.\\ \,}
+    % top-aligning captions
 		\label{fig:recall-precision-examplecount-KWS}
@@
 		\caption{Training and test examples are in \emph{one}
-		structural category.}
+		structural category.\\ \,}
+    % top-aligning captions
 		\label{fig:recall-precision-singlecategory-all}

### 2020-04-07 tse-paper/content.tex
Build view techniques

--- 2020-04-06 tse-paper/content.tex
@@
 
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=\columnwidth,
-		clip]{img/lit-sur/techniques.pdf}
-		\caption{Frequency of different technique labels for
-		labels $>1$ occurence.}
-		\label{fig:litsur:techniques}
-\end{figure}
-
-\begin{figure}[tbp]
+\begin{table*}[]
+\centering
+\caption{Overview of buildlog analysis techniques.}
+\begin{tabularx}{\textwidth}{@{}lXX@{}}
+\toprule
+Name			     & Source(s)	& Frequency	  \\
+\midrule
+Parser	& &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
+\\
+Regular expression  & &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
+\\
+Manual inspection  & &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
+\\
+Machine Learning  & &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
+\\
+Natural Language Processing  & &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+Information Retrieval  & &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+Analysis  & &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+Keyword Search	& &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+Scan  & &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
+\\
+Other  & &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
+\\
+\bottomrule
+\end{tabularx}
+\label{tab:obat}
+\end{table*}
+
+\begin{figure}[tbhp]
 		\centering
@@
 				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Training and test examples are in \emph{one}
+		\caption{Training and test examples in \emph{one}
 		structural category.}
@@
 		clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Training and test examples are in \emph{more than
+		\caption{Training and test examples in \emph{more than
 		one} structural categories.}

### 2020-04-07 tse-paper/content.tex

@@
 				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Training and test examples in \emph{one}
-		structural category.}
+		\caption{Training and test examples are in \emph{one}
+		structural category.\\ \,}
+    % top-aligning captions
 		\label{fig:recall-precision-singlecategory-all}

### 2020-04-07 tse-paper/content.tex
Align big comparison plot
Fix captions

@@
 		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
-		\caption{Compared with the training set size.}
+		\caption{training set size.}
 		\label{fig:recall-precision-examplecount-CTS}
@@
 				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
-		\caption{Compared with the number of structural categories
-		in the
-		training and test sets.}
+		\caption{structural category count
+		in training and test set.}
 		\label{fig:recall-precision-categorycount-CTS}
@@
 \caption{Precision, recall and F$_{1}$-score of chunk
-retrieval with Common Text Similarity (CTS)}
+retrieval with Common Text Similarity (CTS) compared by \ldots}
 \end{figure*}
@@
 		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{Compared with the training set size.\\ \,}
+		\caption{training set size.\\ \,}
     % top-aligning captions
@@
 		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
-		\caption{Compared with the number of structural categories
-		in the
-		training and test sets.}
+		\caption{structural category count
+		in training and test sets.}
 		\label{fig:recall-precision-categorycount-KWS}
@@
 \caption{Precision, recall and F$_{1}$-score of chunk retrieval with
-Keyword Search (KWS)}
+Keyword Search (KWS) compared by \ldots}
 \end{figure*}
@@
 				\caption{Successfulness of retrieval
-				compared with the number of
-	structural categories in the training and test sets.}
+				compared by structural category count in training and test sets.}
 		\label{fig:failure-reason-categorycount-PBE}
@@
 		clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Training and test examples in \emph{more than
-		one} structural categories.}
+		\caption{Training and test examples are in $>1$ structural
+		category.}
 		\label{fig:recall-precision-multicategory-all}

### 2020-04-07 tse-paper/content.tex
Align lit survey figure with text

@@
 % TODO (Caro): Integrate Petersen's guidelines
-From our own experience, we know that the field of analyzing build
-logs is relatively young, with perhaps the work on TravisTorrent the
-most cited and central one.
-We also know there have been scattered
+The field of analyzing build
+logs is relatively young; we know there have been scattered
 research efforts on build log analysis, mostly where the
@@
 knowledge, there has not been an attempt to systematically overview
-and survey approaches for processing build logs,
-despite their forseeable future and current importance.
+and survey approaches for processing build logs.
 
@@
 In this first literature overview study on analyzing build logs, we
-therefore want to survey as broad a population of scientific material
-as possible.
-Note that we do not limit our sources to specific
-Software Engineering venues, as is often
-done~\cite{petersen2015guidelines}, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's theses,
-academic slide decks, and books.
-We use Google Scholar as opposed to
-Scopus or other databases, as it is the search engine for acdemic
-articles with the broadest and most current index, including preprints
-from sources such as arXiv.
+ survey as broad a population of scientific material as possible. We
+ do not limit our sources to specific Software Engineering venues, as
+ is often done~\cite{petersen2015guidelines}, but survey all sources
+ monitored by Google Scholar, including Bachelor's and Master's
+ theses, academic slide decks, and books, since the field of build log
+ analysis is so young.  We use Google Scholar as opposed to Scopus or
+ other databases, as it is the search engine for acdemic articles with
+ the broadest and most current index, including preprints from sources
+ such as arXiv.
 % TODO: maybe remove, this screams snowballing needed
@@
 
-First, we filtered out articles based on (1) their title and (2) the
+First, we filtered articles based on (1) their title and (2) the
 contextual information Google Scholar displayed.
@@
 hits.
-Our strategy was to err on the side of
+Our strategy for this round was to err on the side of
 caution, that is rather including a paper than not.
@@
 With these 256 remaining articles, we followed a backward snowball
-sampling for related work.
+sampling for related work. This meant that we added an article if referred in them in the context of log analysis. 
 This added five papers (eight before
@@
 
-On the surviving artciles, we did a second filter phase by downloading the
+Subsequently, we did a second, finer filter phase by downloading the
 full articles, reading their abstracts, and searching the full text
@@
 some kind of process and excluded another 15 articles.
-For several cases, multiple articles extended others, though still
-reported on
-the same work with the respect to processing build logs.
+For several cases, multiple articles were extensions of others.
 Of these we only considered the earliest article which reported on
@@
 This excluded 11 articles from our survey.
-In sum, we further classify 61 articles.
+In sum, we further classified 61 articles.
 
@@
 				\caption{Successfulness of retrieval
-				compared by structural category count in training and test sets.}
+				compared by structural category count
+				in training and test sets.}
 		\label{fig:failure-reason-categorycount-PBE}
@@
 				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Training and test examples are in \emph{one}
+		\caption{Training and test examples in \emph{one}
 		structural category.\\ \,}
@@
 		clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Training and test examples are in $>1$ structural
+		\caption{Training and test examples in $>1$ structural
 		category.}

### 2020-04-07 tse-paper/content.tex
Make links clickable
start on discussion draft, bit of rw moving

@@
 
+\lstset{
+  morekeywords={INFO, WARN, 2008-11-09},
+  keywordstyle=\color{Plum},
+  escapeinside=**
+}
+\begin{figure*}[!t]
+  \centering
+  \begin{lstlisting}[breaklines=true]
+2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received
+block blk_3587508140 of size 67108 from /10.251.42.84
+2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140
+terminating
+  \end{lstlisting}
+  \caption{System Log excerpt.
+Example adapted from~\cite{he2017towards}.}
+  \label{lst:system-log}
+\end{figure*}
+
 \subsection{Study Selection}
@@
 In this first literature overview study on analyzing build logs, we
- survey as broad a population of scientific material as possible. We
+ survey as broad a population of scientific material as possible.
+We
  do not limit our sources to specific Software Engineering venues, as
@@
  theses, academic slide decks, and books, since the field of build log
- analysis is so young.  We use Google Scholar as opposed to Scopus or
+ analysis is so young.
+We use Google Scholar as opposed to Scopus or
  other databases, as it is the search engine for acdemic articles with
@@
 We explicitly decided to exclude systems
-or event logs (see \Cref{sec:rw}).
+or event logs (see \Cref{sec:system-log-analysis}).
 This left us with 1,552 combined search results
@@
 With these 256 remaining articles, we followed a backward snowball
-sampling for related work. This meant that we added an article if referred in them in the context of log analysis. 
+sampling for related work.
+This meant that we added an article if referred in them in the context
+of log analysis.
+
 This added five papers (eight before
@@
 were left with 87 articles after this search.
+
+\subsection{Distinction from System Log Analysis}
+\label{sec:system-log-analysis}
+A related field of build log analysis is the processing of system log
+files produced during runtime.
+A main difference between build logs
+and system logs is that system logs are fundamentally structured
+through events.
+Each line in a log file represents one event with a
+set of fields: timestamp, verbosity level and raw message
+content~\cite{he2017towards}.
+Figure \ref{lst:system-log} shows
+example lines from a system log.
+
+The first goal in analyzing system log files is ubiquitously to
+separate constant and variable parts within a log
+message~\cite{nagappan2010abstracting,he2017towards}.
+Next, the log
+messages are clustered into log events, unifying messages with
+identical constant parts and varying parameters.
+The output of a log
+parser is an ordered list of timed events and their corresponding
+parameter values~\cite{he2016evaluation}.
+This structured log is then
+the input to various machine learning and data mining processes.
+%Researchers mine patterns for operational
+%profiling~\cite{nagappan2009efficiently},
+%debugging~\cite{oliner2012advances}, performance analytics or anomaly
+%detection~\cite{nagappan2010abstracting}.
+% Xu et
+%al.~\cite{xu2009detecting} leverage the connection of log statements
+%to the source code producing them to separate messages into constant
+%and variable parts more accurately.
+
+The techniques developed for system log analysis can also be applied
+to build logs.
+One example is comparing execution traces to reference
+traces of intended behavior to detect anomalies.
+Amar et
+al.~\cite{amar2019mining} employed a similar approach to detect
+relevant lines in build logs.
+%Classic log parsers interpret the whole log file into a sequence of
+%events.
+% A similar approach could also be applied to build logs to
+%determine the sequence of executed build steps or phases.
+In this article, we focus on extracting a single specified information
+from the build log as a whole with chunk retrieval techniques.
+Chunk
+retrieval techniques are used as a part of log parsing to retrieve the
+values of variable parts in a log message, e.g.
+by using regular
+expressions~\cite{nagappan2010abstracting,xu2009detecting}.
 
@@
 for, over the techniques used until the origin of the build logs
-which were
-analyzed.
+which were analyzed.
 
@@
 the build process, followed by extracting the executed or the failing
-tests
-(both 11\%).
+tests (both 11\%).
 
@@
 The majority of articles (46\%) used the outcome of their build log
-analysis
-for research purpopses, as shown in \Cref{fig:litsur:use}.
+analysis for research purpopses, as shown in \Cref{fig:litsur:use}.
 Further uses were giving feedback to developers (10\%) or automatic
-on-ward
-processing of the retrieved information (8\%).
+on-ward processing of the retrieved information (8\%).
 
@@
 \subsubsection{Build Logs}
+The distribution of supported build tools is shown in
+\Cref{fig:litsur:log_producer}.
 Of the articles we surveyed, 30\% analyzed build logs produced by
@@
 % TODO: cite
-The distribution of supported build tools is shown in
-\Cref{fig:litsur:log_producer}.
+Sometimes this limitation to a specific build tool is motivated by
+% TODO: PIT tool, often: much variety in log format only time for
+one parser
+
 Only 7\% of the proposed methods claimed to be language-agnostic, while
@@
 \subsection{Discussion}
-various researchers analyzing build logs to support their research,
-tools developed to help developers % TODO: {motivational reference}.
+Our literature survey sheds light on how build log analysis is used within
+computer science research.
+We saw that various researchers process build logs to support their
+research, often because the logs provide more or the necessary information
+to the researchers.
+% TODO cite 'Autmoated localization for unreproducible builds
+Automated approaches are necessary as many studies target a large
+number of
+builds.
+Most of the articles which explicitly mention a manual analysis of
+the logs
+only restrict their work to few logs or take a ``representative sample to
+make manual analysis feasible''.
+% TODO cite: a study of build inflation in 30 mil CPAN builds
 
@@
 
+% TODO Caro: integrate as anecdotes in lit results
 \subsection{Build Failures in CI}
@@
 
-\subsection{System Log Analysis}
-\label{sec:log-analysis}
-A related field of log processing is the processing of system log
-files produced during runtime.
-A main difference between build logs
-and system logs is that system logs are fundamentally structured
-through events.
-Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}.
-Figure \ref{lst:system-log} shows
-example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to
-separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}.
-Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters.
-The output of a log
-parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}.
-This structured log is then
-the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational
-%profiling~\cite{nagappan2009efficiently},
-%debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}.
-% Xu et
-%al.~\cite{xu2009detecting} leverage the connection of log statements
-%to the source code producing them to separate messages into constant
-%and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied
-to build logs.
-One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies.
-Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of
-%events.
-% A similar approach could also be applied to build logs to
-%determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques.
-Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g.
-by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
-
-\lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
-  escapeinside=**
-}
-\begin{figure*}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received
-block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140
-terminating
-  \end{lstlisting}
-  \caption{System Log excerpt.
-Example adapted from~\cite{he2017towards}.}
-  \label{lst:system-log}
-\end{figure*}
-
+% TODO: Caro: integrate into pbe description
 \subsection{Program Synthesis by Example}
@@
 % TODO: rework! extend / relate to further techniques
+% (should follow from discussion)
 This section introduces key concepts of the three chunk retrieval
@@
 % TODO: we could add more techniques from the lit.
-survey here
+% survey here
 

### 2020-04-07 tse-paper/content.tex
add sources of literature survey

@@
 
-\section{Systematic Literature Survey and Mapping}
+\section{Systematic Literature Mapping Survey}
 \label{sec:survey}
@@
 \caption{Overview of buildlog analysis techniques.}
-\begin{tabularx}{\textwidth}{@{}lXX@{}}
+\begin{tabularx}{\textwidth}{@{}lXl@{}}
 \toprule
@@
 \midrule
-Parser	& &
+Parser	&
+\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
+&
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
 \\
-Regular expression  & &
+Regular expression  &
+\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
+&
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
 \\
-Manual inspection  & &
+Manual inspection  &
+\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2019study,cassee2019impact}
+&
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
 \\
-Machine Learning  & &
+Machine Learning  &
+\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
+&
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
 \\
-Natural Language Processing  & &
+\makecell[cl]{Natural Language \\ Processing}  &
+\cite{hassan2017change,lou2019history,schulz2017active} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
-Information Retrieval  & &
+Information Retrieval  &
+\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
-Analysis  & &
+Analysis  &
+\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
-Keyword Search	& &
+Keyword Search	&
+\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
-Scan  & &
+Scan  & \cite{clemencic2014new,hibbard2001visualization} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
 \\
-Other  & &
+Other  &
+\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
+&
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
+\\
+None identified  &
+\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
+&
 \\
@@
 \end{tabularx}
-\label{tab:obat}
+\label{tab:litsur:techniques}
 \end{table*}
+
+% TODO one source might contribute multiple times to 'other'
 
@@
 \subsubsection{Retrieval Technique}
-\Cref{fig:lisur:techniques} presents the techniques which the articles
+\Cref{tab:litsur:techniques} presents the techniques which the articles
 described for processing build logs.

### 2020-04-08 tse-paper/content.tex
writing study discussion draft, pbe and cts glue text, build log analysis in industry, subfigure for chunk examples

@@
 
-\begin{figure}[!t]
-  \centering
+\begin{figure*}[!t]
+  \centering
+\begin{subfigure}[t]{\columnwidth}
   \begin{lstlisting}[breaklines=true,frame=tlr]
@@
   \end{lstlisting}
-  \caption{Example of a log chunk explaining why an Android
-  build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me
-  % long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example-1}
-\end{figure}
-
-\begin{figure}[!t]
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[t]{\columnwidth}
   \centering
@@
   \end{lstlisting}
-  \caption{Another example of a log chunk explaining why an Android
+\end{subfigure}
+  \caption{Two examples of log chunks explaining why an Android
   build failed.}
-  \label{lst:chunk-example-2}
-\end{figure}
+  % TODO Moritz: we can relate this to travistorrent maybe, you told me
+  % long ago that this was something your analyzer cannot extract
+  \label{lst:chunk-example}
+\end{figure*}
 
@@
   \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example-1,lst:chunk-example-2}}
+  with examples from \Cref{lst:chunk-example}}
   \label{lst:prose-program-simplified}
@@
 the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example-1,lst:chunk-example-2} show two exemplary
+\Cref{lst:chunk-example} shows two exemplary
 log chunks from Android build logs marked in blue.
@@
 It ends before two line separators, consistent with the two example
-chunks from \Cref{lst:chunk-example-1,lst:chunk-example-2}.
+chunks from \Cref{lst:chunk-example}.
 This shows, that the characters structuring the text around the chunk are
@@
 dividing log chunks into structural categories.
-The chunks from \Cref{lst:chunk-example-1,lst:chunk-example-2}
+The chunks from \Cref{lst:chunk-example}
 are in the \emph{same structural category}, while the chunk from
@@
 Manual inspection  &
-\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2019study,cassee2019impact}
+\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
 &
@@
 \emph{TravisTorrent}~\cite{beller2017travistorrent}, two used the
-\emph{Maven Log Analyzer}, % TODO: cite
-another two the \emph{MAKAO} tool.
-% TODO: cite
+\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
+another two the
+\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.
 
@@
 Of the articles we surveyed, 30\% analyzed build logs produced by
-Maven~\cite{maven2019website}, 16\% ones produced by Gradle % TODO: cite
-and 10\% logs produced by Ant.
-% TODO: cite
+Maven~\cite{maven2019website}, 16\% ones produced by
+Gradle~\cite{gradle2020website}
+and 10\% logs produced by Ant~\cite{ant2020website}.
+
 Sometimes this limitation to a specific build tool is motivated by
-% TODO: PIT tool, often: much variety in log format only time for
-one parser
+aspects separate from the build log analysis.
+For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
+build logs because they also chose the PIT tool to calculate coverage
+and mutation score.
+A larger amount of the articles within our survey, however, limit
+themselves to few build tools because their log format varies and
+therefore ``parsers must be specialized to each build and test
+framework''~\cite{tomassi2019bugswarm}.
 
@@
 The main platform that build logs were collected from is Travis
-CI, % TODO cite.
+CI~\cite{travisci2019webpage},
 which was used in 38\% of cases.
@@
 computer science research.
+In this section we will summarize our findings and relate them to the
+approach we are taking to improve build log analysis with chunk
+retrieval techniques.
+
 We saw that various researchers process build logs to support their
 research, often because the logs provide more or the necessary information
-to the researchers.
-% TODO cite 'Autmoated localization for unreproducible builds
+to the researchers~\cite{ren2018automated}.
+Most of the articles which explicitly mention a manual analysis of
+the logs only restrict their work to few logs or take a
+``representative sample to make manual analysis
+feasible''~\cite{zolfagharinia2017not}.
 Automated approaches are necessary as many studies target a large
-number of
-builds.
-Most of the articles which explicitly mention a manual analysis of
-the logs
-only restrict their work to few logs or take a ``representative sample to
-make manual analysis feasible''.
-% TODO cite: a study of build inflation in 30 mil CPAN builds
-
-\subsubsection{Retrieved Information}
-why from build logs? not avaliable in cleaner format much use for
-research, a bit of developer information / tools following: research
-so many logs that unfeasible to do manually, less focus on tools for
-devs (caveat! we excluded books and documentation on industrial tools
--> many approaches there to make build logs digestible, tough many
-focus on general minimizing of the data presented, not retrieving
-specific chunks)
-
-\subsubsection{Retrieval Technique}
-broadly mentioned shortly, rarely explained in detail we follow that
-researchers often see this as an unimportant side fact work needed to
-be done to get the big work done
-
-\subsubsection{Build Logs}
-often focussed on specific logs, sometimes mentioned because of effort
-developing a parser other times also because other tools used in
-further research are limiting the scope (reference paper with PIT
-tool).
-many focus on maven because of it's prevalence also in respect
-to other tools much research done on travis ci logs b/c of their
-abundance and open availability
+number of builds.
+The chunk retrieval techniques we investigate within this article are
+automated, apart from their configuration through training examples.
+
+We have observed very little reuse of build log analysis tools.
+This can stem from the fact that publishing replication packages and
+research prototypes became popular only in recent years or from the
+high specialization of the developed tools in regards to supported
+build environments and targeted information.
+Several articles noted the variety in log formats for different build
+environments, which requires customizing build log techniques for
+every supported build environment.
+We implement build environment agonostic build log analysis
+techniques, which are customized to a specific project by
+the training examples which the user provides.
+In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
+data set we chose for our evaluation covers a broad range of build
+environments.
+Further, the training examples also specify the log chunk targeted by the
+retrieval, which enable our chunk retrieval techniques to retrieve a
+broad range of information from build logs.
+
+Urli et al.~\cite{urli2018design} strongly discouraged from parsing
+build logs for information as it is ``too error prone'', other
+articles pointed to the effort of developing a custom tool.
+Regular expressions are known to be tedious to
+maintain~\cite{michael2019regexes}.
+For this reason, we are focussing % TODO: less development time,
+% only giving examples
+
+% \subsubsection{Retrieved Information}
+% why from build logs? not avaliable in cleaner format much use for
+% research, a bit of developer information / tools following: research
+% so many logs that unfeasible to do manually, less focus on tools for
+% devs (caveat! we excluded books and documentation on industrial tools
+% -> many approaches there to make build logs digestible, tough many
+% focus on general minimizing of the data presented, not retrieving
+% specific chunks)
+
+% \subsubsection{Retrieval Technique}
+% broadly mentioned shortly, rarely explained in detail we follow that
+% researchers often see this as an unimportant side fact work needed to
+% be done to get the big work done
+
+% \subsubsection{Build Logs}
+% often focussed on specific logs, sometimes mentioned because of effort
+% developing a parser other times also because other tools used in
+% further research are limiting the scope (reference paper with PIT
+% tool).
+% many focus on maven because of it's prevalence also in respect
+% to other tools much research done on travis ci logs b/c of their
+% abundance and open availability
 
@@
 \label{sec:expl-pbe}
-% % \emph{Programming by Example} is a technique which synthesizes
-% % programs according to in- and output examples provided by the user.
+The area of \emph{Programming by Example} aims to capture the
+intent of the user through examples which they provide.
+Leveraging this apprach, we implemented a chunk retrieval technique
+for build logs.
+Our implementation is based and highly influenced by the
+\emph{Microsoft PROSE library}~\cite{prose2019webpage}.
+The PROSE library is powered by the generic program synthesis framework
+\emph{FlashMeta}~\cite{polozov2015flashmeta:} and the specialized
+text extraction DSL \emph{FlashExtract}~\cite{le2014flashextract:}.
+Both enable us to synthesize regular expression programs
+consistent~\cite{mitchell1982generalization} with a set of in-
+and output examples given by the user.
+The usage of example enables the user to configure a chunk
+retrieval without understanding the whole structure of
+the build log.
 % % It enables users to create programs without a priori programming
@@
 Example, we refer to them in short as \emph{examples}.
-The
-\emph{input} is the text of the build log file.
+The \emph{input} is the text of the build log file.
 The \emph{output} is
@@
 they define the substring of a build log that should be extracted.
-The
-PROSE program synthesis then tries to construct a program consistent
-with all training examples.
+The PROSE program synthesis then tries to construct a program
+consistent with all training examples.
+\Cref{lst:prose-program-simplified} presents a simplified version
+of a program learned from the examples in \Cref{lst:chunk-example}.
 % % A program is consistent with an example if it returns the defined
@@
 % % technique.
-
 % % kinda.
@@
 \label{sec:expl-ts}
-% % Text Similarity approaches are used to filter unstructured textual
-% % software
+Text Similarity approaches are widely used to filter unstructured
+textual software artifacts
+~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+We investigate a chunk retrieval technique based on the common
+and simple Vector Space Model~\cite{schutze2008introduction}.
+The aim is to retrieve those lines from a build log which are most
+similar to examples given by the user.
+% Text Similarity approaches are used to filter unstructured textual
+% software artifacts.
+% One common technique
 % %
-%artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+%artifacts.
 % % One common and simple technique is the Vector Space Model.
@@
 
-% TODO cite http://text2vec.org/
-Our implementation of CTS is dependent on the library {\tt text2vec}
+Our implementation of CTS is dependent on the library
+{\tt text2vec}~\cite{text2vec2019webpage}
 and the way it splits strings into word tokens.
@@
 \section{Future Work}
-% TODO: survey build logs tools in industry
 
@@
 \begin{itemize}
+  \item \textbf{Systematic Survey of Industry Approaches for Build
+  Log Analysis} Our survey is limited to academic work and articles.
+  However, handling build logs is a challenge for a wide range of
+  practitioners as well.
+  We propose to investigate the methods used in industry to analyze
+  build logs.
+  An example is the Jenkins \emph{build-failure-analyzer}
+  plugin~\cite{jenkins2020failure-analyzer} or automatically
+  inferred test results in Azure~\cite{azure2020inferred}.
   \item \textbf{Further Analysis of \emph{LogChunks}} We created the

### 2020-04-08 tse-paper/content.tex
move / remove rw parts

@@
 
+Seo et al.~\cite{seo2014programmers}
+They based their analyses on sets of
+build logs collected from industry partners.
+They develop a custom
+parser to classify error messages reported by Java and C++ builds.
+
+Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
+source Java projects
+
+Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
+in Java to industrial ones.
+Their data stems from analyzing
+build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
+with regular expressions.
+
+Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
+breakage data.
+They classify build failures from \emph{TravisTorrent}
+Their analysis starts with manual
+categorization of build logs.
+They select keywords and strings that
+identify their targeted categories and code a script to automatically
+classify logs based on these keywords.
+% TODO note which technique words we assined here
+
+This task of retrieving specific chunks of text from the
+build logs can be solved by the chunk retrieval techniques we compare
+in this article.
+Our results can support researchers in choosing a
+suitable technique for their data set of build logs and the chunks
+they want to retrieve.
+By relieving them from building custom parsers
+we enable them to cover a much wider range of languages and build
+tools in their studies.
+
+Vassallo et
+al.~\cite{vassallo2018un-break}
+They parse
+Maven~\cite{maven2019website} build logs into a structured
+representation and create hint generators.
+For example, one of the hint generators queries stack overflow for
+discussions related to why the build failed.
+The chunk retrieval techniques we compare in this article can be used
+to fill similar structured representations with information from build
+logs.
+As they simplify the construction of parsers they would enable
+developers and researchers to cover a wider array of build tools,
+which is the main influence factor on the structure of a build log.
+
+Amar et al.~\cite{amar2019mining} compare different approaches to
+reduce the portions of a log that a developer has to inspect.
+Their
+techniques remove lines that appear both in logs from passing and
+failing builds and use a modified \emph{Term Frequency Inverse
+Document Frequency} (TF-IDF) weighting to identify term vectors likely
+to occur with failures.
+Their diff technique can be interpreted as a
+chunk retrieval technique, where the targeted information is defined
+by the past failures used as basis for the weighted term vectors.
+
 \subsubsection{Build Logs}
@@
 % abundance and open availability
-
-\section{Related Work}
-% TODO reorder rw by build retrieval technique rather than by paper
-\label{sec:rw}
-We explain how researchers gather information about CI usage in software
-projects
-through build log analysis and why the chunk retrieval techniques we
-investigate
-simplifies their data collection.
-This section moves on to past works about augmenting build logs to make
-it easier
-for developers to inspect them.
-The presented approaches are related to and can benefit from the
-techniques we
-analyze in this article.
-Further, we classify build logs as semi-structured data and differentiate
-our
-work from system log analysis.
-
-% TODO Caro: integrate as anecdotes in lit results
-\subsection{Build Failures in CI}
-Various researchers studied why CI builds fail and into the impact of
-build failures on the development workflow.
-
-Seo et al.~\cite{seo2014programmers} find that a small group of error
-types such as dependency mismatches are the most prominent cause of
-build failures at Google.
-In addition, they notice that most failures
-are resolved within two builds.
-They based their analyses on sets of
-build logs collected from industry partners.
-They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects and find that most builds fail because of failing
-tests.
-For most projects, over half of the failed builds follow a
-previous failed build.
-Rausch et al.'s data shows that most failures
-occur in the second half of the build runtime, which can cause long
-delays in the feedback loop, especially when builds are automatically
-retried upon failure.
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones.
-They determine that testing failures are
-more common than compilation errors.
-Open source builds fail most
-often because of unit tests, whereas release preparations are the
-primary cause in industrial projects.
-Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data.
-They classify build failures from \emph{TravisTorrent}
-according to whether they were caused by an environmental failure or
-caused by a developer change.
-Their analysis starts with manual
-categorization of build logs.
-They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-
-\noindent
-\textbf{Supporting Log Analysis with Chunk Retrieval}
-To leverage the valuable information within build logs the researchers
-presented in this section create parsers and regular expression-based
-programs.
-This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article.
-Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve.
-By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-\subsection{Augmentation of Build Logs}
-\label{sec:rw-bl-analysis}
-Build logs are a valuable data source for developers to find out why
-their build failed.
-Several researchers investigate how to support
-developers in working with verbose build logs.
-Vassallo et
-al.~\cite{vassallo2018un-break} try to shorten the time it takes
-developers to understand build logs.
-They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-%The hint generators leverage this structured access to the
-%information within the build log to propose fixes.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed.
-In a qualitative study
-they observed that highlighting the locality and context of an issue
-is helpful to programmers.
-%Their tool BART is published as a Jenkins
-%Plugin~\cite{bart2019plugin}.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs.
-As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect.
-Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures.
-Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.
-
-Travis itself already provides build log augmentation in the form of a
-basic structuring of the build logs within their log viewer using
-\emph{log folds}~\cite{travis2019logfolds}.
-They add fold identifiers
-around common commands and setup or teardown build phases and collapse
-the contained lines by default.
-
-% TODO: Caro: integrate into pbe description
-\subsection{Program Synthesis by Example}
-\label{sec:rw-prose}
-% % \section){Information Extraction and Retrieval Techniques} The
-% % techniques we investigate are based on existing methods of
-% % Programming by Example.%, information extraction and information
-% % retrieval.
-% This section presents different Programming by Example
-% % resources surrounding the PROSE library.
-% We explain its generic
-% % program synthesis algorithm and how PROSE synthesizes text
-% % extraction programs, the foundation of PBE\@.
-
-Programming by Example (PBE) is a form of generalized program
-synthesis that enables users to automate repetitive tasks, without
-them having to explicitly codify a computer program.
-One has to
-provide prototypical examples of the input and the desired output.
-A
-synthesis algorithm tries to create a program (based on a regular
-language) that transforms the input to the output.
-The minimum working
-condition is for this when replayed on the examples inputs is to
-provide the specified output, but, hopefully, PBE is as close as
-possbile to the user's intention and thus also works on a different
-and larger set of inputs.
-This section introduces the theoretical
-foundations of the program synthesis algorithm of the \emph{PROgram
-Synthesis using Examples} (PROSE) framework~\cite{prose2019webpage}.
-The PROSE framework is developed by Microsoft Research.
-Next, this
-section presents the FlashExtract DSL, which defines text extraction
-tasks within PROSE and is the basis for the implementation of our
-chunk retrieval technique PBE\@.
-
-\subsubsection{FlashMeta: Inductive Program Synthesis}
-The FlashMeta framework presented by Polozov and
-Gulwani~\cite{polozov2015flashmeta:} is the backbone of the program
-synthesis in the Microsoft PROSE framework.
-FlashMeta separates the
-inductive synthesis algorithm from the domain specific capabilities of
-the desired program by encoding the possible program space in a domain
-specific language (DSL).
-The user specifies the desired program
-behavior by providing in/output examples (I/O examples).
-FlashMeta
-uses \emph{witness functions}, provided by the DSL, to divide the
-synthesis into smaller subtasks.
-For each of these subtasks it
-enumerates all possible programs that solve the subtask consistent
-with the set of I/O examples.
-A program is consistent with a set of
-I/O examples if, for each input example, it produces the corresponding
-output~\cite{mitchell1982generalization}.
-The possible subprograms are
-joined and stored in a \emph{version space algebra}
-(VSA)~\cite{mitchell1982generalization}.
-This a tree structure, which
-space-efficiently saves candidate programs for tasks by sharing common
-subexpressions.
-Next, FlashMeta ranks the enumerated programs
-according to which ones the user most likely intended.
-The DSL also
-provides the ranking characteristics.
-From the ranked VSA, FlashMeta
-can then return a ranked list of complete programs consistent with the
-user's example.
-
-% In addition to I/O examples of the intended program, the user can
-% also provide examples with only input or negative input examples.
-% Negative input examples should not be processed by the synthesized
-% program.
-
-% The different applications of PROSE presented in the following
-% paragraphs were all eventually implemented as DSLs for the FlashMeta
-% synthesis algorithm.
-
-\subsubsection{FlashExtract: Data Extraction by Example}
-Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
-for the Microsoft PROSE framework.
-% It enables a user to define text extraction programs for text,
-% websites and spreadsheets by giving I/O examples.
-FlashExtract's instantiation for text synthesizes extraction programs
-from semi-structured text based on regular expressions.
-Users can
-extract multiple fields and structure them with hierarchy and
-sequence.
-% FlashExtract synthesizes programs to extract each of the fields
-% leveraging the information about hierarchical containment and
-% sequentiality.
-% It eliminates the need for the user to understand the
-% entire structure of the processed document and decreases the effort
-% of developing a suitable extraction program.
-
-FlashExtract models the extraction of a single substring as a pair of
-two cut positions.
-A position is either specified by an absolute
-character index or by a pair of two regular expressions.
-The first
-regular expression matches the substring directly before the
-characterized position, the second regular expression matches the
-substring directly after.
-A regular expression in FlashExtract is a
-concatenation of tokens, e.g.\ standard character classes or string
-literals frequently occurring in the input examples.
-Figure
-\ref{lst:prose-program} shows a text extraction program synthesized by
-FlashExtract.
-This program defines the first position as after a colon
-followed by a newline character and before a piece of text with all
-capital letters.
-It defines the second position as before two newline
-characters.
-
-Apart from automatic completion in Excel
-spreadsheets~\cite{excel2019flashfill}, FlashExtract is the basis for
-two other Microsoft product features: Microsoft's system log analysis
-tool Azure Monitor lets users define custom log
-fields~\cite{azure2019custom}.
-The ConvertFrom-String function in
-PowerShell allows a user to specify an example template to extract
-hierarchical data from a text document~\cite{powershell2019convert}.
-
-We apply the text instantiation of FlashExtract to the domain of build
-logs with our chunk retrieval technique PBE\@.
-
-\lstset{
-  language=caml,
-  morekeywords={PosToEndRegion, RegexPosition, RegexPair,
-  StartToPosRegion},
-  keywordstyle=\bfseries\color{black},
-  escapeinside=//
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true]
-let s = v in let s = PosToEndRegion(s, RegexPosition(s,
-RegexPair("Colon/$\circ$/Line Separator", "ALL CAPS"), 1)) in
-StartToPosRegion(s, RegexPosition(s, RegexPair("/$\varepsilon$/",
-"Line Separator/{\color{blue}$\circ$}/Line Separator"), 1))
-  \end{lstlisting}
-  \caption{Text extraction program synthesized by FlashExtract.}
-  \label{lst:prose-program}
-\end{figure}
-
 \section{Chunk Retrieval Techniques}
@@
 \subsection{Other Techniques}
+% TODO: we could add more techniques from the lit.
+% survey here
+% TODO: probably remove
 %Literature mentions further build log analysis techniques.
@@
 retrieval to identify relevant lines from a failed build
-log~\cite{amar2019mining}, as we describe in more detail in
-Section~\ref{sec:rw-bl-analysis}.
+log~\cite{amar2019mining}.
 The configuration for the technique
@@
 given past failures.
-
-% TODO: we could add more techniques from the lit.
-% survey here
 
@@
 paper.
+
+Seo et al.~\cite{seo2014programmers}
+They based their analyses on sets of
+build logs collected from industry partners.
+They develop a custom
+parser to classify error messages reported by Java and C++ builds.
+
+Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
+source Java projects
+
+Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
+in Java to industrial ones.
+Their data stems from analyzing
+build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
+with regular expressions.
+
+Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
+breakage data.
+They classify build failures from \emph{TravisTorrent}
+Their analysis starts with manual
+categorization of build logs.
+They select keywords and strings that
+identify their targeted categories and code a script to automatically
+classify logs based on these keywords.
+% TODO note which technique words we assined here
+
+This task of retrieving specific chunks of text from the
+build logs can be solved by the chunk retrieval techniques we compare
+in this article.
+Our results can support researchers in choosing a
+suitable technique for their data set of build logs and the chunks
+they want to retrieve.
+By relieving them from building custom parsers
+we enable them to cover a much wider range of languages and build
+tools in their studies.
+
+Vassallo et
+al.~\cite{vassallo2018un-break}
+They parse
+Maven~\cite{maven2019website} build logs into a structured
+representation and create hint generators.
+For example, one of the hint generators queries stack overflow for
+discussions related to why the build failed.
+The chunk retrieval techniques we compare in this article can be used
+to fill similar structured representations with information from build
+logs.
+As they simplify the construction of parsers they would enable
+developers and researchers to cover a wider array of build tools,
+which is the main influence factor on the structure of a build log.
+
+Amar et al.~\cite{amar2019mining} compare different approaches to
+reduce the portions of a log that a developer has to inspect.
+Their
+techniques remove lines that appear both in logs from passing and
+failing builds and use a modified \emph{Term Frequency Inverse
+Document Frequency} (TF-IDF) weighting to identify term vectors likely
+to occur with failures.
+Their diff technique can be interpreted as a
+chunk retrieval technique, where the targeted information is defined
+by the past failures used as basis for the weighted term vectors.

### 2020-04-09 tse-paper/content.tex
Xupdated graphics, adding anecdotal results to literature study

@@
 		\centering
-		\includegraphics[width=\columnwidth,
-		clip]{img/lit-sur/log_producer_long-cropped.pdf}
+		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
+		1.5cm 0.5cm},
+		clip]{img/lit-sur/log_producer_annotated.pdf}
 		\caption{Frequency of supported log producer.}
@@
 tests (both 11\%).
-
-In most cases (51\%), a chunk was retrieved from the log, whereas 36\%
-of the articles classified the articles into categories.
-Other types of processing (e.g.
-counting lines, summarization) were only
-done in one case each.
+There were also numerous cases which targeted more specialized
+information, such as the environments used during the
+build~\cite{zolfagharinia2017not}, packages
+installed~\cite{selberg2012use} or hints to source files which are
+related to build failures~\cite{ren2018automated}.
+
+In most cases (51\%), a chunk was retrieved from the log.
+Cemencic and Couturier~\cite{clemencic2014new}, for example,
+scan build logs for compilation errors, while Zhang et
+al.~\cite{zhang2016android} retrieve the duration of
+tasks within the build.
+
+The articles classified the build logs into categories in 36\% of
+the cases.
+Didrik Lindqvist~\cite{lindqvist2019detection} used build logs to
+distuinguish failures caused by
+developers from those caused by infrastructure, while
+Kavaler et al.~\cite{kavaler2019tool} idenfity projects that use
+automated static analysis tools.
+Other types of information (e.g.
+counting lines, summarization) were only retrieved
+in one case each.
 
@@
 processing or information retrieval techniques.
+For example,
+Seo et al.~\cite{seo2014programmers} developed a custom
+parser to classify error messages, while Vassallo et
+al.~\cite{vassallo2017a-tale} analyzed build logs with regular
+expressions.
+Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
+They start with manual categorization of the build logs and select
+search strings that identify their targeted categories.
+Based on the search strings they create a script which automatically
+classifies the remaining logs.
+%TODO: they are not actually in our survey, the talk about 'test logs'
+Amar et al.~\cite{amar2019mining} compare different approaches to
+reduce the number of lines to be inspected by the developer.
+Their best performing technique creates a diff between the logs from a
+successful and a failed build and ranks the remaining lines using
+Information Retrieval (IR) techniques.
 
@@
 
-Seo et al.~\cite{seo2014programmers}
-They based their analyses on sets of
-build logs collected from industry partners.
-They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones.
-Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data.
-They classify build failures from \emph{TravisTorrent}
-Their analysis starts with manual
-categorization of build logs.
-They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-% TODO note which technique words we assined here
-
-This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article.
-Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve.
-By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-Vassallo et
-al.~\cite{vassallo2018un-break}
-They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs.
-As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect.
-Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures.
-Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.
+% Seo et al.~\cite{seo2014programmers}
+% They based their analyses on sets of
+% build logs collected from industry partners.
+% They	reported by Java and C++ builds.
+
+% Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
+% source Java projects
+
+% Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
+% in Java to industrial ones.
+% Their data stems from analyzing
+% build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
+% with regular expressions.
+
+% Vassallo et
+% al.~\cite{vassallo2018un-break}
+% They parse
+% Maven~\cite{maven2019website} build logs into a structured
+% representation and create hint generators.
+% For example, one of the hint generators queries stack overflow for
+% discussions related to why the build failed.
 
@@
 enable further research.
+However we found no clear reuse of build log data sets with the
+exception of TravisTorrent~\cite{beller2017travistorrent}, which was
+analyzed by Vassallo et al.~\cite{vassallo2017a-tale},
+Ghaleb et al.~\cite{ghaleb2019studying} and several other studies.
 
@@
 % only giving examples
+
+This task of retrieving specific chunks of text from the
+build logs can be solved by the chunk retrieval techniques we compare
+in this article.
+Our results can support researchers in choosing a
+suitable technique for their data set of build logs and the chunks
+they want to retrieve.
+By relieving them from building custom parsers
+we enable them to cover a much wider range of languages and build
+tools in their studies.
 
@@
 	\centering
-	\includegraphics[width=\textwidth, trim={0.5cm 1.3cm 0.2cm 0.3cm},
+	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
   clip]{img/study.pdf}
@@
 		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
-		\caption{training set size.\\ \,}
-    % top-aligning captions
+		\caption{training set size.}
 		\label{fig:recall-precision-examplecount-KWS}
@@
 		\caption{Training and test examples in \emph{one}
-		structural category.\\ \,}
-    % top-aligning captions
+		structural category.}
 		\label{fig:recall-precision-singlecategory-all}
@@
 paper.
-
-Seo et al.~\cite{seo2014programmers}
-They based their analyses on sets of
-build logs collected from industry partners.
-They develop a custom
-parser to classify error messages reported by Java and C++ builds.
-
-Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-source Java projects
-
-Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-in Java to industrial ones.
-Their data stems from analyzing
-build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-with regular expressions.
-
-Ghaleb et al.~\cite{ghaleb2019studying} aim to identify noise in build
-breakage data.
-They classify build failures from \emph{TravisTorrent}
-Their analysis starts with manual
-categorization of build logs.
-They select keywords and strings that
-identify their targeted categories and code a script to automatically
-classify logs based on these keywords.
-% TODO note which technique words we assined here
-
-This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article.
-Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve.
-By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-Vassallo et
-al.~\cite{vassallo2018un-break}
-They parse
-Maven~\cite{maven2019website} build logs into a structured
-representation and create hint generators.
-For example, one of the hint generators queries stack overflow for
-discussions related to why the build failed.
-The chunk retrieval techniques we compare in this article can be used
-to fill similar structured representations with information from build
-logs.
-As they simplify the construction of parsers they would enable
-developers and researchers to cover a wider array of build tools,
-which is the main influence factor on the structure of a build log.
-
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the portions of a log that a developer has to inspect.
-Their
-techniques remove lines that appear both in logs from passing and
-failing builds and use a modified \emph{Term Frequency Inverse
-Document Frequency} (TF-IDF) weighting to identify term vectors likely
-to occur with failures.
-Their diff technique can be interpreted as a
-chunk retrieval technique, where the targeted information is defined
-by the past failures used as basis for the weighted term vectors.

### 2020-04-09 tse-paper/abstract.tex
Finished abstract
Closes #36

--- 2020-03-13 tse-paper/abstract.tex
@@
-Build logs are a textual by-product that software build processes
+Build logs are a textual by-product that automatic software build processes
 create, often as part of their Continuous Integration (CI)
-pipeline. Build logs can serve as a paramount source of
-information for developers to understand and debugg build or
-test failures. Manually
+pipeline.
+Build logs can serve as a paramount source of
+information for developers to understand and debug depdency, compilation, or
+test failures.
+Manually
 extracting the important chunks of information, though, is akin to
-finding a needle in a haystack. Recently, researchers and practitioners have begun attempts to partly automate
-this time-consuming activity, with the proposition to not only ease developers' tasks but to enable a new class of automated on-ward processing applications.
-In this paper, we want to give a systematic overview of the state of the art of the emerging field of build log analysis.
-To this end, we first survey and categorize the existing methods to extract information chunks from build logs.
-We then develop prototypical implementations for three promising techniques, namely program synthesis
-by example, textual similarity and search keywords. Finally, we evaluate the three techniques in an empirical study on our manually
-labeled \emph{LogChunks} data set, which comprises 797 build logs in 29 languages.
+finding a needle in a haystack.
+Recently, researchers and practitioners have started attempts to partly
+automate
+this time-consuming activity, with the proposition to not only ease
+developers' and researchers task of finding this needle but also to enable a novel class of
+on-ward processing applications.
+In this paper, we give the first systematic overview of the emerging field of build log analysis.
+In a large-scale literature mapping study, we first survey and categorize the existing methods to
+extract information from build logs.
+In the second part of the paper, we then develop prototypical implementations of the three most promising
+techniques, namely program synthesis
+by example, textual similarity, and keyword search.
+Finally, we evaluate the techniques in an empirical study on
+the manually
+labeled \emph{LogChunks} data set, which comprises 797 build logs in
+29 languages.
 Our findings show that none of the three techniques in general outperforms
-the others, but rather, that each technique has its respective strengths and weaknesses. We discuss under which circumstances each technique performs best
-and provide a recommendation on when developers or researchers should use which
-technique.
+the others, but rather, that each technique has its respective strengths
+and weaknesses.
+We discuss under which circumstances each technique performs best
+and provide a recommendation scheme for when developers or researchers might 
+use which technique.

### 2020-04-09 tse-paper/content.tex
Fix layout of Table 1
@lacinoire We can discuss whether we want this, or we abbreviate
long words in column 1 to have everything even-sized

@@
 
-\begin{table*}[]
+\begin{table*}[tbhp]
 \centering
@@
 Parser	&
-\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
+{\smallish \cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}}
 &
@@
 \\
-\makecell[cl]{Natural Language \\ Processing}  &
+\makecell[cl]{{\smallish Natural Language Processing}}  &
 \cite{hassan2017change,lou2019history,schulz2017active} &
@@
 
-\begin{figure}[tbhp]
+\begin{figure}
+\centering
+\begin{subfigure}[t]{\columnwidth}
 		\centering
@@
 		\label{fig:litsur:info_target}
-\end{figure}
-
-\begin{figure}[tbhp]
+
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[t]{\columnwidth}
 		\centering
@@
 		\label{fig:litsur:use}
+
+\end{subfigure}
+
+\caption{Multi-label categorization of the 61 relevant articles.}
 \end{figure}
 
-\begin{figure}[tbhp]
-		\centering
-		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
+\begin{figure*}[tbhp]
+		\centering
+		\includegraphics[width=0.7\textwidth, trim={1.1cm 0.4cm
 		1.5cm 0.5cm},
 		clip]{img/lit-sur/log_producer_annotated.pdf}
-		\caption{Frequency of supported log producer.}
+		\caption{Frequency of supported log producers.}
 		\label{fig:litsur:log_producer}
-\end{figure}
+\end{figure*}
 

### 2020-04-09 tse-paper/content.tex
Bodge alignment issue

@@
 \toprule
-Name			     & Source(s)	& Frequency	  \\
+Name			     & Sources	& Frequency	  \\
 \midrule
 Parser	&
-{\smallish \cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}}
+~{\smallish
+\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}}
 &
@@
 \\
-Regular expression  &
-\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
+Regular expression  
+&\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
 &

### 2020-04-14 tse-paper/content.tex
lacheck corrections

@@
 However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
+50 MB of ASCII text~\cite{beller2017oops}---making them inadequate
 for direct human consumption.
@@
 build logs.
-Beller et al.
-use a rule-based system of regular
+Beller et al.\ use a rule-based system of regular
 expressions to analyze logs from Travis CI~\cite{beller2017oops}.
@@
   \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
+Could not determine the dependencies of task ':app:jacocoTestDebugReport'.
 > Task with path 'testDebug' not found in project ':app'.
@@
 content~\cite{he2017towards}.
-Figure \ref{lst:system-log} shows
+\Cref{lst:system-log} shows
 example lines from a system log.
@@
 retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g.
-by using regular
+values of variable parts in a log message, e.g.\ by using regular
 expressions~\cite{nagappan2010abstracting,xu2009detecting}.
@@
 found in our replication package~\cite{brandt2020chunk-replication}.
-Note that for most questions we allowed assigning multiple values, e.g.
-if
+Note that for most questions we allowed assigning multiple values,
+e.g.\ if
 two kinds of informations were targeted during a build log analysis.
@@
 automated static analysis tools.
-Other types of information (e.g.
-counting lines, summarization) were only retrieved
+Other types of information (e.g.\ counting
+lines, summarization) were only retrieved
 in one case each.
@@
 Text Similarity approaches are widely used to filter unstructured
-textual software artifacts
-~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+textual software artifacts~\cite{runeson2007detection,
+marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
 We investigate a chunk retrieval technique based on the common
@@
 was 28\%.
-Listing \ref{lst:pbe-unsuccessful} shows an example of such
+\Cref{lst:pbe-unsuccessful} shows an example of such
 an \emph{unsuccessful retrieval}, where the synthesized program only
@@
 If the information chunks are from multiple structural categories,
-i.e.
-they are not represented in the same structural way within the
+i.e.\ they are not represented in the same structural way within the
 build logs, and recall is more important than precision we recommend
@@
 (because of its high accuracy), followed by a combination of CTS and
-KWS.
+KWS\@.
 Other than initial setup and training time, there should be no

### 2020-04-14 tse-paper/content.tex
update RQs

@@
 
-\begin{simplebox}{Research Questions}
+\begin{simplebox}{\textbf{RQ1:} What is the state-of-research on build
+log analysis?}
 \begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
+  \item[\textbf{RQ1.1:}] Which information is targeted?
+  \item[\textbf{RQ1.2:}] Which techniques are used?
+  \item[\textbf{RQ1.3:}] Which build logs are analyzed?
+\end{itemize}
+\end{simplebox}
+
+\begin{simplebox}{\textbf{RQ2:} When are PBE\, CTS or KWS suited to
+retrieve chunks from build logs?}
+\begin{itemize}
+  \item[\textbf{RQ2.1:}] How many examples does a technique need to
+  perform best?
+  \item[\textbf{RQ2.2:}] How structurally similar do the examples
+  need for a technique to be applicable?
+  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
 \end{itemize}

### 2020-04-14 tse-paper/paper.tex
Fix table
Huge review and redo
explain techniques in intro, add running example and structural category example
Run long lines
fix comments, move todos to code
small corrections introduction, Closes #20
Make links clickable
Fix layout of Table 1
@lacinoire We can discuss whether we want this, or we abbreviate
long words in column 1 to have everything even-sized
Bodge alignment issue
update RQs

@@
   % normal IEEE
-  \usepackage{cite}
+  \usepackage[noadjust]{cite}
 \fi
@@
 
+\usepackage[dvipsnames]{xcolor}
 \usepackage{tabularx}
@@
 \usepackage{makecell}
+\usepackage{relsize}
 
@@
 \newtcolorbox{simplebox}[2][]{enhanced,
+    minipage boxed title,
     sharp corners,
@@
     boxed title style={colframe=white},
-    attach boxed title to top center={yshift=-3mm}, 
+    attach boxed title to top center={yshift=-3mm,yshifttext=-1mm},
     title=#2,#1}
 
-\usepackage{todonotes}
-%\setuptodonotes{inline, color=cyan!50}
+\usepackage[hidelinks,bookmarks=false]{hyperref}
 \usepackage{cleveref}
-%\usepackage{subfigure}
 \usepackage{caption}
 \usepackage{subcaption}
-\usepackage{mdframed,xcolor}
+\usepackage{mdframed}
+\usepackage{enumitem}
 
-\newenvironment{figureax}[1][htbp]% Redefine figure
-  {\oldfigure[#1]\mdframed[backgroundcolor=blue!15]}
-  {\endmdframed\endoldfigure}
+\newcommand{\smallish}{\fontsize{6.15pt}{20pt}\selectfont}
 

### 2020-04-15 tse-paper/content.tex
small changes to introduction (more ideas but wanna know Moritz' plans), start on update lit survey

--- 2020-04-14 tse-paper/content.tex
@@
 
-To gain an impression on how researchers are using information from
-build logs within their research to support
-developers, we conducted a systematic mapping study.
-Our goal was to classify how, and what for, researchers use build logs as
-a source of data (\textbf{RQ1}).
+% TODO: 4 sentence description of the steps in graphic?
+\Cref{fig:overview} gives an overview of our research steps.
+We conducted a systematic mapping study,
+to gain an impression on how researchers are using information from
+build logs within their research or to support
+developers.
+% We implemented three promising techniques that retrieve
+% chunks of text from build logs and can be adapted to
+% a specific project and use case by giving examples of build logs and
+% correpsonding chunks.
+% We evaluated the
+Our goal was to clarify the state-of-research on build log
+analysis (\textbf{RQ1}).
 
@@
 
-\Cref{fig:overview} gives an overview of our research steps.
-
-\begin{simplebox}{Research Questions}
+\begin{simplebox}[minipage boxed title*=-5cm]{Research Questions}
 \begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
-  retrieval technique for build logs?
+  \item[\textbf{RQ1:}] What is the state-of-research on build
+  log analysis?
+  \item[\textbf{RQ2:}] When are PBE, CTS or KWS suited to
+  retrieve chunks from build logs?
 \end{itemize}
 \end{simplebox}
+
+% TODO: move down to where mentioned in detail
+% \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
+% {\textbf{RQ1:} What is the state-of-research on build
+% log analysis?}
+% \begin{itemize}
+%   \item[\textbf{RQ1.1:}] Which information is targeted?
+%   \item[\textbf{RQ1.2:}] Which techniques are used?
+%   \item[\textbf{RQ1.3:}] Which build logs are analyzed?
+% \end{itemize}
+% \end{simplebox}
+
+% \begin{simplebox}[minipage boxed title*=-2.5cm,
+% attach boxed title to top center={yshift=-6mm}]
+% {\textbf{RQ2:} When are PBE{,} CTS or KWS suited to
+% retrieve chunks from build logs?}
+% \begin{itemize}
+%   \item[\textbf{RQ2.1:}] How many examples does a technique need to
+%   perform best?
+%   \item[\textbf{RQ2.2:}] How structurally similar do the examples
+%   need for a technique to be applicable?
+%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
+% \end{itemize}
+% \end{simplebox}
 
@@
 \end{itemize}
+
+Following the results from our comparison study,
+recommend PBE for use cases where the desired information is always
+represented in the same structural way and high confidence in precision
+and recall of the chunk retrieval is required.
+Results produced by PBE are suited for automatic on-ward processing.
+CTS is well suited when the representation of the desired information
+varies
+slightly and the output of the chunk retrieval is further processed by
+a human.
+In cases where the textual representation of the desired information in
+the log
+is unpredictable or varies greatly, KWS seems to be the best choice.
+However,
+its low precision---it extracts a context of multiple lines around a
+finding---makes it generally unsuited for automatic on-ward processing and
+instead requires a human to further inspect and interpret the output
+chunk.
 
@@
 
+% TODO: this could move to the chunk retrieval techniques section
 The results of our empirical comparison study on the chunk retrieval
@@
 
-Following the results from our comparison study,
-recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision
-and recall of the chunk retrieval is required.
-Results produced by PBE are suited for automatic on-ward processing.
-CTS is well suited when the representation of the desired information
-varies
-slightly and the output of the chunk retrieval is further processed by
-a human.
-In cases where the textual representation of the desired information in
-the log
-is unpredictable or varies greatly, KWS seems to be the best choice.
-However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output
-chunk.
-
 \section{Systematic Literature Mapping Survey}
@@
 
-% TODO (Caro): Integrate Petersen's guidelines
 The field of analyzing build
-logs is relatively young; we know there have been scattered
-research efforts on build log analysis, mostly where the
-log analysis was a side-part of the article.
+logs is relatively young; We have seen scattered
+research efforts on build log analysis.
+However,the processing of build logs was often
+a side-part of the article.
 To the best of our
@@
 and survey approaches for processing build logs.
+We conducted a systematic mapping study to determine the
+state-of-research on build log analysis following the guidelines
+by Petersen et al.~\cite{petersen2015guidelines}.
+
+In the following section, we explain how build log analysis differs
+from system log analysis.
 
@@
 \end{figure*}
+
+\subsection{Distinction from System Log Analysis}
+\label{sec:system-log-analysis}
+A related field of build log analysis is the processing of system log
+files produced during runtime.
+A main difference between build logs
+and system logs is that system logs are fundamentally structured
+through events.
+Each line in a log file represents one event with a
+set of fields: timestamp, verbosity level and raw message
+content~\cite{he2017towards}.
+\Cref{lst:system-log} shows
+example lines from a system log.
+
+The first goal in analyzing system log files is ubiquitously to
+separate constant and variable parts within a log
+message~\cite{nagappan2010abstracting,he2017towards}.
+Next, the log
+messages are clustered into log events, unifying messages with
+identical constant parts and varying parameters.
+The output of a log
+parser is an ordered list of timed events and their corresponding
+parameter values~\cite{he2016evaluation}.
+This structured log is then
+the input to various machine learning and data mining processes.
+
+The techniques developed for system log analysis can also be applied
+to build logs.
+One example is comparing execution traces to reference
+traces of intended behavior to detect anomalies.
+Amar et
+al.~\cite{amar2019mining} employed a similar approach to detect
+relevant lines in build logs.
+In this article, we focus on extracting a single specified information
+from the build log as a whole with chunk retrieval techniques.
+Chunk
+retrieval techniques are used as a part of log parsing to retrieve the
+values of variable parts in a log message, e.g.\ by using regular
+expressions~\cite{nagappan2010abstracting,xu2009detecting}.
 
@@
 were left with 87 articles after this search.
-
-\subsection{Distinction from System Log Analysis}
-\label{sec:system-log-analysis}
-A related field of build log analysis is the processing of system log
-files produced during runtime.
-A main difference between build logs
-and system logs is that system logs are fundamentally structured
-through events.
-Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
-content~\cite{he2017towards}.
-\Cref{lst:system-log} shows
-example lines from a system log.
-
-The first goal in analyzing system log files is ubiquitously to
-separate constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}.
-Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters.
-The output of a log
-parser is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}.
-This structured log is then
-the input to various machine learning and data mining processes.
-%Researchers mine patterns for operational
-%profiling~\cite{nagappan2009efficiently},
-%debugging~\cite{oliner2012advances}, performance analytics or anomaly
-%detection~\cite{nagappan2010abstracting}.
-% Xu et
-%al.~\cite{xu2009detecting} leverage the connection of log statements
-%to the source code producing them to separate messages into constant
-%and variable parts more accurately.
-
-The techniques developed for system log analysis can also be applied
-to build logs.
-One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies.
-Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
-%Classic log parsers interpret the whole log file into a sequence of
-%events.
-% A similar approach could also be applied to build logs to
-%determine the sequence of executed build steps or phases.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques.
-Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g.\ by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
 

### 2020-04-15 tse-paper/paper.tex
small changes to introduction (more ideas but wanna know Moritz' plans), start on update lit survey

@@
 \newtcolorbox{simplebox}[2][]{enhanced,
-    minipage boxed title,
+    minipage boxed title*,
     sharp corners,
@@
     boxed title style={colframe=white},
-    attach boxed title to top center={yshift=-3mm,yshifttext=-1mm},
+    attach boxed title to top center={yshift=-3mm},
+    center title,
     title=#2,#1}

### 2020-04-15 tse-paper/content.tex
correct first half of lit survey

@@
 
-% TODO: move down to where mentioned in detail
+% also moved down to where mentioned in detail
+% left copy here for convenience
+
 % \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
@@
 
-\begin{figure}[htb]
+\begin{figure}[hb]
 	\centering
@@
 state-of-research on build log analysis following the guidelines
-by Petersen et al.~\cite{petersen2015guidelines}.
+by Petersen et al.~\cite{petersen2008systematic,petersen2015guidelines}.
 
@@
 from system log analysis.
+Further, we describe how we selected the articles for our literature
+survey and the data extraction from the resulting articles.
+We present our results on how buildlogs are analyzed in literature
+and discuss the implecations of these findings on our research.
 
@@
 }
-\begin{figure*}[!t]
+\begin{figure*}[!tb]
   \centering
@@
 relevant lines in build logs.
-In this article, we focus on extracting a single specified information
-from the build log as a whole with chunk retrieval techniques.
-Chunk
-retrieval techniques are used as a part of log parsing to retrieve the
-values of variable parts in a log message, e.g.\ by using regular
-expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+However, many of the techniques developed to analyze system logs
+leverage their inherent event structure.
+As build logs lack this sturcture, we focussed our literature
+survey on articles that as a source of information.
+% In this article, we focus on extracting a single specified information
+% from the build log as a whole with chunk retrieval techniques.
+% Chunk
+% retrieval techniques are used as a part of log parsing to retrieve the
+% values of variable parts in a log message, e.g.\ by using regular
+% expressions~\cite{nagappan2010abstracting,xu2009detecting}.
 
 \subsection{Study Selection}
-% TODO shorten
-\Cref{fig:lit-survey} presents an overview of our study selection.
-In this first literature overview study on analyzing build logs, we
- survey as broad a population of scientific material as possible.
-We
- do not limit our sources to specific Software Engineering venues, as
+\Cref{fig:lit-survey} presents an overview of our study selection
+process.
+Since the field of build log analysis is so young, we
+surveyed a population of scientific material as broad as possible.
+We did not limit our sources to specific Software Engineering venues, as
 is often done~\cite{petersen2015guidelines}, but survey all sources
 monitored by Google Scholar, including Bachelor's and Master's
- theses, academic slide decks, and books, since the field of build log
- analysis is so young.
+theses and academic slide decks.
 We use Google Scholar as opposed to Scopus or
 other databases, as it is the search engine for acdemic articles with
- the broadest and most current index, including preprints from sources
- such as arXiv.
-% TODO: maybe remove, this screams snowballing needed
-One challenge is that no common
-nomenclature has been established yet (in fact, this is one of the
-goals of this article).
-
-% TODO Caro cite guidelines
-Our Google Scholar
-search for variations ``build log'' returns more than 2.2 million results
-(2020-03-15).
-We therefore refined our search criterions for the four
-different spelling possibilities of ``build log'' to exclude obvious
+the broadest and most current index, including preprints.
+
+Our Google Scholar search for variations of ``build log''
+returns more than 2.2 million results (2020-03-15).
+We refined our search criterions to exclude obvious
 non-related works.
-We explicitly decided to exclude systems
+For example, we decided to exclude systems
 or event logs (see \Cref{sec:system-log-analysis}).
-This left us with 1,552 combined search results
+This left us with 1,552 search results
 (2020-03-15).
@@
 hits.
-Our strategy for this round was to err on the side of
-caution, that is rather including a paper than not.
 We then unified
@@
 sampling for related work.
-This meant that we added an article if referred in them in the context
-of log analysis.
-
+If one one of the articles referenced a new article in the context
+of build log analysis we added the new to our literature set.
 This added five papers (eight before
-duplicate elimination) to our literature set, coming to a total of 261
+duplicate elimination), coming to a total of 261
 articles.
 
-Subsequently, we did a second, finer filter phase by downloading the
+Subsequently, we performed a second, finer filter phase by downloading the
 full articles, reading their abstracts, and searching the full text
@@
 In total, we
-were left with 87 articles after this search.
+were left with 87 articles after the two filtering phases.
+
+\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
+{\textbf{RQ1:} What is the state-of-research on build
+log analysis?}
+\begin{itemize}
+  \item[\textbf{RQ1.1:}] Which information is targeted?
+  \item[\textbf{RQ1.2:}] Which techniques are used?
+  \item[\textbf{RQ1.3:}] Which build logs are analyzed?
+\end{itemize}
+\end{simplebox}
 
@@
 Having trimmed down the set of articles, we investigated them in depth.
-We kept all articles that use logs from software builds as input to
-some kind of process and excluded another 15 articles.
-For several cases, multiple articles were extensions of others.
-Of these we only considered the earliest article which reported on
-the processing of build logs.
-This excluded 11 articles from our survey.
-In sum, we further classified 61 articles.
 
@@
 \begin{itemize}
-  \item what kind of build logs they are using and the source of these
-  logs.
-  \item what information they are retrieving from the logs,
-  its kind (chunk/classification) and
-  what they use the retrieved information for
+  \item what information they are retrieving from the logs and
+  what they use the retrieved information for (\textbf{RQ1.1})
   \item which technique they are using to process the build logs,
   in how much detail it is described and whether they published their
-  tools
+  tools (\textbf{RQ1.2})
+  \item what kind of build logs they are using and the origin of these
+  logs.
+(\textbf{RQ1.3})
 \end{itemize}
 To objecifiy our data extraction we created a template of the targeted
-factors and performed a pilot.
+factors and performed a pilot, as reccommended by Petersen et
+al.~\cite{petersen2015guidelines}.
 Two authors extracted the data from five articles and we held a
@@
 
+Relevant for our survey were all articles that
+use logs from software builds as input to
+some kind of process.
+This excluded 15 articles from our study.
+For several cases, multiple articles were extensions of others.
+Of these, we only considered the earliest article which reported on
+the processing of build logs.
+This excluded another 11 articles.
+In sum, we further extracted data from 61 articles.
+
 The full data extraction template and our results of this step can be
@@
 e.g.\ if
-two kinds of informations were targeted during a build log analysis.
+two kinds of information were targeted during a build log analysis.
 
@@
 In the following, we will present the results of our literature survey.
-Starting with the information that was targeted and what it was employed
-for, over the techniques used until the origin of the build logs
+We present the information within the build logs that was targeted,
+the retrieval techniques used and the origin of the build logs
 which were analyzed.
@@
 \centering
-\caption{Overview of buildlog analysis techniques.}
+\caption{Overview of build log analysis techniques.}
 \begin{tabularx}{\textwidth}{@{}lXl@{}}
@@
 
+\begin{simplebox}[minipage boxed title*=-2.5cm,
+attach boxed title to top center={yshift=-6mm}]
+{\textbf{RQ2:} When are PBE{,} CTS or KWS suited to
+retrieve chunks from build logs?}
+\begin{itemize}
+  \item[\textbf{RQ2.1:}] How many examples does a technique need to
+  perform best?
+  \item[\textbf{RQ2.2:}] How structurally similar do the examples
+  need for a technique to be applicable?
+  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
+\end{itemize}
+\end{simplebox}
+
 % TODO Caro: redo
@@
 \label{sec:discussion}
-
-% TODO update RQs
-% TODO incorporate these RQs into the text where they are being answered
-
-This section presents the answers to our research questions:
-\begin{simplebox}{Research Questions}
-\begin{itemize}
-  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
-  \item[\textbf{RQ2:}] Which criteria influence the suitability of a
-  chunk retrieval technique for build logs?
-
-  {\small \item[\textbf{~~ RQ2.1:}] How many examples do PBE, CTS,
-  and KWS need to perform best?
-  \item[\textbf{~~ RQ2.2:}] How structurally similar do the examples
-  for PBE, CTS and KWS need to be for the techniques to be applicable?
-  \item[\textbf{~~ RQ2.3:}] How accurate are the retrievals of PBE, CTS,
-  and KWS?}
-\end{itemize}
-\end{simplebox}
 

### 2020-04-15 tse-paper/content.tex
improve study results

@@
 \subsubsection{Retrieved Information}
-The information that was targeted is presented in
-\Cref{fig:litsur:info_target} varied from article to article.
-Most prominent was the search for errors (39\%) that occured within
-the build process, followed by extracting the executed or the failing
+The information that was targeted varied from article to article.
+Most prominent was the search for errors (39\%) which occured within
+the build process, as presented in \Cref{fig:litsur:info_target}.
+This is followed by extracting the executed or the failing
 tests (both 11\%).
@@
 In most cases (51\%), a chunk was retrieved from the log.
-Cemencic and Couturier~\cite{clemencic2014new}, for example,
-scan build logs for compilation errors, while Zhang et
-al.~\cite{zhang2016android} retrieve the duration of
-tasks within the build.
-
-The articles classified the build logs into categories in 36\% of
-the cases.
-Didrik Lindqvist~\cite{lindqvist2019detection} used build logs to
-distuinguish failures caused by
-developers from those caused by infrastructure, while
-Kavaler et al.~\cite{kavaler2019tool} idenfity projects that use
-automated static analysis tools.
+Build logs were scanned for compilation
+errors~\cite{clemencic2014new} or
+the duration of tasks within the build~\cite{zhang2016android}.
+36\% of the articles classified the build logs into categories.
+For instance distinguishing failures caused by developers from
+failures casued
+by infrastructure errors~\cite{lindqvist2019detection} or
+whether projects use automated statc analysis
+tools~\cite{kavaler2019tool}.
 Other types of information (e.g.\ counting
@@
 \subsubsection{Retrieval Technique}
-\Cref{tab:litsur:techniques} presents the techniques which the articles
+\Cref{tab:litsur:techniques} presents the techniques that the articles
 described for processing build logs.
-43 of the 61 articles we inspected touched on how they are analyzing build
+43 of the 61 articles we inspected mentioned how they are analyzing build
 logs.
@@
 processing or information retrieval techniques.
-For example,
+To give examples,
 Seo et al.~\cite{seo2014programmers} developed a custom
@@
 classifies the remaining logs.
-%TODO: they are not actually in our survey, the talk about 'test logs'
-Amar et al.~\cite{amar2019mining} compare different approaches to
-reduce the number of lines to be inspected by the developer.
-Their best performing technique creates a diff between the logs from a
-successful and a failed build and ranks the remaining lines using
-Information Retrieval (IR) techniques.
-
-25\% of the articles claimed their implementation is available, however we
+
+25\% of the articles claimed their implementation is available,
+however we
 saw very low reuse of build log analysis tools within our survey.
 Five articles employed the tools used to create
-\emph{TravisTorrent}~\cite{beller2017travistorrent}, two used the
+\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
+orellana2017differences,zhao2018comparing} or
+an extended version of them~\cite{rott2019empirische,
+shi2018evaluating},
+two used the
 \emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
@@
 Of the articles we surveyed, 30\% analyzed build logs produced by
-Maven~\cite{maven2019website}, 16\% ones produced by
+Maven~\cite{maven2019website}, 16\% analyzed logs produced by
 Gradle~\cite{gradle2020website}
-and 10\% logs produced by Ant~\cite{ant2020website}.
+and 10\% analyzed logs produced by Ant~\cite{ant2020website}.
 

### 2020-04-15 tse-paper/content.tex
improve chunk retrieval techniques section

@@
 \label{sec:techniques}
-% TODO: rework! extend / relate to further techniques
-% (should follow from discussion)
 This section introduces key concepts of the three chunk retrieval
@@
 example (PBE), common text similarity (CTS), and keyword search (KWS).
-We use these techniques to extract text chunks from build logs that
-represent a specific, targeted information.
+
+\Cref{tab:ctr} shows a comparison of the presented techniques.
 
@@
 retrieve pieces of information that appear literally in the build
-logs, i.e., techniques that do not aggreagte, combine, or deducted
-information.
+logs.
+%, i.e., techniques that do not aggreagte, combine, or deducted
+%information.
 We call such pieces of information from build logs
@@
 
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
 \begin{table*}[]
@@
 & Line	      & Retrieval length	  \\
-Diff Approach		     & ---     & Line not present in successful
-log, information retrieval  & Line	  & Logs from failing and
-successful builds      \\
 \bottomrule
@@
 \label{sec:expl-pbe}
-The area of \emph{Programming by Example} aims to capture the
+The concept of \emph{Programming by Example} aims to capture the
 intent of the user through examples which they provide.
@@
 the build log.
-% % It enables users to create programs without a priori programming
-% % knowledge~\cite{mayer2015user}.
-% In the context of text extraction
-% % through regular expressions, Programming by Example relieves the
-% % developer from having to understand the whole document structure to
-% % solve a single extraction task~\cite{le2014flashextract:}.
-% In this
-% % work, we refer to our interpretation of Programming by Example as
-% % \emph{PBE}\@.
-% We investigate the suitability of PBE to retrieve
-% % information chunks from build logs.
-% In the following, we explain the
-% % configuration and application of PBE to chunk retrieval from CI
-% % build logs.
-
-% TODO later: we should make sure to at least mention PROSE
-% _somewhere_, it's crucial for why PBE is how it is
+
 \subsubsection{Configuration}
@@
 The \emph{output} is
-an array of substrings of the log file text, representing the
-substrings that should be retrieved by the synthesized program when
+a substring of the log file text, representing the
+substring that should be retrieved by the synthesized program when
 given the corresponding input file.
@@
 consistent with all training examples.
+If PROSE cannot synthesize a program, e.g.\
+because the regular expression
+necessary would be too complicated to synthesize, PBE returns the
+error message ``no program found''.
 \Cref{lst:prose-program-simplified} presents a simplified version
 of a program learned from the examples in \Cref{lst:chunk-example}.
-% % A program is consistent with an example if it returns the defined
-% % output when executed on the defined
-% % input~\cite{mitchell1982generalization}.
-% PBE reports an error back to the user if it could not synthesize a
-% consistent program.
-% % The program synthesis builds on the FlashExtract DSL, which in turn
-% % uses the FlashMeta algorithm.
-% Both are described in
-% % Section~\ref{sec:rw-prose}.
+% TODO Caro: check that these figures are latest inserted here
 
@@
 We investigate a chunk retrieval technique based on the common
-and simple Vector Space Model~\cite{schutze2008introduction}.
+Vector Space Model~\cite{schutze2008introduction}.
 The aim is to retrieve those lines from a build log which are most
 similar to examples given by the user.
-% Text Similarity approaches are used to filter unstructured textual
-% software artifacts.
-% One common technique
-% %
-%artifacts.
-% % One common and simple technique is the Vector Space Model.
-% We
-% % investigate when text similarity is a suitable technique to retrieve
-% % information chunks from build logs.
-% In the following we will explain
-% % the concept of how we apply text similarity to information retrieval
-% % from CI build logs, which we refer to as \emph{CTS}\@.
 
@@
 and apply the Vector Space Model~\cite{schutze2008introduction}
-as follows.
-The
-lines of the output strings of the training examples define our search
-query.
+as follows:
+The lines of the output strings of the training examples define our
+search query.
 The algorithm splits the search query into single lines and
@@
 To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the output of the
-training examples.
+whole text and process it in the same way as the search query.
 The algorithm calculates the cosine
@@
 Indeed, this was one of the
-most common approaches we took when searching for the reason the build
-failed within a log while creating the \emph{LogChunks} data
+most common approaches we took when searching for the reason a build
+failed while creating the \emph{LogChunks} data
 set~\cite{brandt2020logchunks}.
-% As this is a technique readily available in many tools developers
-% use to view build logs, we study when such a keyword search is
-% suitable for retrieving information chunks from CI build logs.
-% In
-% the following we will explain how we use simple keyword search to
-% retrieve information from CI build logs, which we refer to as
-% \emph{KWS}\@.
 
@@
 picking lines from the build log.
-RLR essentially mimicks the
-situation of guessing purely blindly which lines might be interesting.
+RLR mimicks the
+situation of guessing blindly which lines might be interesting.
 The only configuration option for RLR is the number of lines it should
@@
 
-\subsection{Other Techniques}
-% TODO: we could add more techniques from the lit.
-% survey here
-% TODO: probably remove
-%Literature mentions further build log analysis techniques.
-%This
-%section describes them with our notion of chunk retrieval techniques.
-
-\noindent
-\textbf{Log Diff}
-Amar et al.\ use a technique based on line diffs and information
-retrieval to identify relevant lines from a failed build
-log~\cite{amar2019mining}.
-The configuration for the technique
-is the log from the last successful build and relevant past failures.
-This technique retrieves the lines from a build log that are not
-present in the successful build log and contain terms related to the
-given past failures.
-
 \subsection{Tool Implementation}
-For our comparison study we implemented PBE, CTS, KWS and RLR and a
-unifying interface.
+For our comparison study we implemented each of the chunk retrieval
+techniques and a unifying interface.
 The unified interface is implemented in Ruby and
@@
 CI build logs we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},
-\ref{sec:expl-ts} and \ref{sec:expl-skws}.
-Random Line Retrieval
-(RLR), explained in Section~\ref{sec:expl-rlr}, acts as a baseline for
+PBE, CTS and KWS.
+Random Line Retrieval (RLR), acts as a baseline for
 the comparison.
-This section
+The following section
 describes our study design and which metrics we measure to answer our

### 2020-04-15 tse-paper/content.tex
move listings to files to protect them from autoformat

@@
   \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Execution failed for task ':app:connectedAndroidTest'.
-> com.android.builder.testing.api.DeviceException:
-java.lang.RuntimeException: ...
-  \end{lstlisting}
+  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk1.txt}
   \vspace{-\baselineskip}
@@
   \centering
-  \begin{lstlisting}[breaklines=true]
-StartExtraction(RegexPair("Colon/$\circ$/Line Separator",
-"ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/",
-"Line Separator/$\circ$/Line Separator"))
-  \end{lstlisting}
+  \lstinputlisting[breaklines=true]{listings/prose.txt}
   \caption{Simiplified regular expression produced by PBE when trained
@@
   \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
---- FAIL: TestSeparator (0.03s)
-    repo\_test.go:75: expected entry to be in form of `* [link] -
-    description.`, got '* ...
-  \end{lstlisting}
+  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk2.txt}
   \vspace{-\baselineskip}
@@
 \lstset{
-  morekeywords={INFO, WARN, 2008-11-09},
-  keywordstyle=\color{Plum},
+  morekeywords={INFO, WARN, 2008, 11, 09},
+  alsoletter=-20819,
+  keywordstyle=\bfseries\color{Plum},
   escapeinside=**
@@
   \centering
-  \begin{lstlisting}[breaklines=true]
-2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received
-block blk_3587508140 of size 67108 from /10.251.42.84
-2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140
-terminating
-  \end{lstlisting}
+  \lstinputlisting[breaklines=true]{listings/syslog.txt}
   \caption{System Log excerpt.

### 2020-04-16 tse-paper/content.tex
add corrections ttv - conclusion

@@
 
+\addtolength{\tabcolsep}{-5pt}
 \begin{table*}[tbhp]
+\tinyish
 \centering
@@
 Parser	&
-~{\smallish
-\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}}
+\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
 &
@@
 \\
-\makecell[cl]{{\smallish Natural Language Processing}}	&
+\makecell[cl]{Natural Language Processing}	&
 \cite{hassan2017change,lou2019history,schulz2017active} &
@@
 \end{table*}
-
+\addtolength{\tabcolsep}{5pt}
 % TODO one source might contribute multiple times to 'other'
@@
 
-\noindent
 \textbf{Implementation}
-\label{sec:prose:impl}
 % TODO we need to say something about why we think that these
@@
 
-\noindent
 \textbf{Data Set}
@@
 logs from the \emph{LogChunks} data set.
-It only consists of build
+It consists of build
 logs from open source projects and therefore it is not clear whether
-our results are generalizable to industry projects.
-We only collected
-build logs from Travis CI, however we chose to evaluate on an
-information chunk whose format is not dependent on Travis CI\@.
+our results apply to industry projects that use build tools
+not popular in open source development.
+However, \emph{LogChunks} covers a wide array of build tools,
+we believe that our findings can be generalized.
+We collected build logs from Travis CI.
+Yet, the format of the log chunk we chose
+for our evaluation is not dependent on Travis CI\@.
 This
@@
 
-\noindent
 \textbf{Training Set Size}
@@
 small numbers we evaluated on.
-
-\noindent
+The fact that PBE and CTS performed best with already two training
+examples shows that our training set size is large enough to
+compare the three techniques we presented.
+
 \textbf{Few Samples with Many Structural Categories}
 Our comparison study shows fewer measurements with many structural
-categories than with one category.
+categories than with one structural category category
+(50.25\% one, 33.75\% two, 13.75\% more than two).
 This stems from the fact that we investigated the chunk retrieval
-techniques on a realistic data set, which showed to often have few
+techniques on a real-world data set, where there were mostly few
 structural categories within one project.
+In addition, a third of the measurements were conducted with two
+structural categories present and these already showed the negative
+effect of the number of structural categories on the performance
+of the chunk retrieval techniques.
 
@@
   precision and recall.
-We propose to investigate how useful these
+  The next step would be to investigate how useful these
   outputs are to developers through controlled experiments.
@@
 their decision on how to analyze build logs.
-We implemented and
-compared three different chunk retrieval techniques on our data set
+We conducted a systematic mapping study to uncover the
+state-of-research on build log analysis.
+We implemented	three promising chunk retrieval techniques and
+compared them on our data set
 \emph{LogChunks}, composed of 797 manually labeled build logs from a

### 2020-04-16 tse-paper/content.tex
corrections big study dicussion

@@
 
-\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
-{\textbf{RQ1:} What is the state-of-research on build
-log analysis?}
-\begin{itemize}
-  \item[\textbf{RQ1.1:}] Which information is targeted?
-  \item[\textbf{RQ1.2:}] Which techniques are used?
-  \item[\textbf{RQ1.3:}] Which build logs are analyzed?
-\end{itemize}
-\end{simplebox}
-
 \subsection{Article Classification}
@@
 two kinds of information were targeted during a build log analysis.
+
+\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
+{\textbf{RQ1:} What is the state-of-research on build
+log analysis?}
+\begin{itemize}
+  \item[\textbf{RQ1.1:}] Which information is targeted?
+  \item[\textbf{RQ1.2:}] Which techniques are used?
+  \item[\textbf{RQ1.3:}] Which build logs are analyzed?
+\end{itemize}
+\end{simplebox}
 
@@
 
-The first section discusses for PBE, CTS and KWS separately in which
-cases they perform best.
-It details for which types of input build
+For the interpretation of our study results we look at each chunk
+retrieval technique separately and give recommendations for
+which types of input build
 logs, available training examples and consumption of the retrieved
 output each technique is suited.
-In the following section we discuss
+Following that, we discuss
 which of these criteria should influence the decision to use a certain
-technique most.
+chunk retrieval technique most.
 Based on our empirical comparison, we present a
@@
 \subsection{Interpretation of Study Results}
-This section discusses the study results for each of the analyzed
-chunk retrieval techniques separately.
-It gives recommendations which
-kind of information chunk targets are best for each technique and for
-what kind of usage the respective output is suitable.
+\Cref{tab:single-technique-recommendations} summarizes the
+recommendations which we discuss
+in this section.
 
@@
 This is
-because PROSE has difficulty synthesizing OR-based programs (see
-\Cref{sec:prose:impl}).
+because PROSE has difficulty synthesizing OR-based
+programs~\cite{mayer2015user}.
 PBE is thus suited to retrieve information
-chunks that always have the same surrounding or defining internal
+chunks that always have the same defining surrounding or internal
 structure.
@@
 
-When the training examples are of the same structure, even one or two
+When the training examples are of the same structure, one or two
 two examples are enough input for PROSE to synthesize a regular
@@
 examples did not improve the chunk retrieval.
-In fact, unless they
-were in some sense redudant, adding training examples above that even
-hindered the applicability of PBE.
+% In fact, unless they
+% were in some sense redudant, adding training examples above that even
+% hindered the applicability of PBE.
 
@@
 The tool
-clearly identifies a failing program synthesis or when no output from
-the program applied to a build log is obtained.
-Therefore, if there is
+clearly identifies a failing synthesis or when the regular expression
+finds no match on a build log.
+Therefore, if PBE produces
 an output, the user can have high confidence that it is the desired
@@
 This preciseness makes output from PBE chunk retrieval
-well-suited for machine consumption.
+well-suited for machine consumption and therefore automatic on-ward
+processing.
 
@@
 
-Going from one to two two training examples, KWS's recall improves
-siginficantly.
-However, further enlarging the training example count
-does not lead to further improvments.
-
-Retrieving the average number of lines present in the outputs of the
-training examples around every found keyword yields reasonable recall.
-Selecting 1.5 times as many lines around every found keyword does
-improve the recall within our study but also increases the proportion
-of lines retrieved overall and therefore decreases precision.
+Going from one to two training examples, KWS's recall improves
+significantly.
+However, further enlarging the training set
+does not lead to further improvements.
 
@@
 now want to unify our results into one recommendation scheme.
-In
-Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
-developers and researchers who want to retrieve information chunks
-from build logs can follow.
+Figure~\ref{fig:crt-recommendation} presents a decision tree
+to answer our second research question;
+If researchers or developers want to retrieve chunks from build logs,
+they can follow the decision tree to identify the technique
+suited best for their use case.
 The decision tree is built up of questions
@@
 
-\noindent
-\textbf{Caveat!} This is a preliminary hypothesis based on the results
+\begin{simplebox}[minipage boxed title*=-7cm]{Caveat!}
+This is a preliminary hypothesis based on the results
 from our comparison study.
@@
 influenced by idiosyncrazies of our specific implementation of the
-chunk retrieval techniques as well as the logs in the \emph{LogChunks}
+chunk retrieval techniques as well as the \emph{LogChunks}
 data set.
-
-This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
-answer to RQ2, about which criteria influence the suitability of a
-chunk retrieval technique.
-The earlier in the decision tree a
-criterion is noted, the more important it is when distinguishing the
-techniques.
+\end{simplebox}
 
 The first and most important aspect are the structural categories.
-Are
-the information chunks one would like to retrieve always presented in
+Are the targeted log chunks always presented in
 the same structural way within the build logs? Then the information
@@
 
-If the information chunks are from multiple structural categories,
-i.e.\ they are not represented in the same structural way within the
-build logs, and recall is more important than precision we recommend
+If the information chunks are from multiple structural categories
+and recall is more important than precision we recommend
 to use KWS\@.
-If the representations are from multiple structural
-categories and precision is more important than recall to the user we
+If precision is more important than recall to the user we
 recommend CTS\@.
-We also recommend CTS when the representations are
+We also recommend CTS when the log chunks are
 from one structural category, when the user does not require a high
-confidence in the precision or recall of the outcome and when the user
+confidence in the precision or recall of the outcome and when one
 would rather have output with low recall instead of no output at all.
@@
 
-\noindent
-\textbf{Example of Using the Recommendation Scheme}
+\subsection{Examples of Using the Recommendation Scheme}
 To illustrate how one would use our decision tree to find a suitable
-chunk retrieval technique we describe two concrete examples: a
-researcher investigating why CI builds fail and a software team
-wanting to monitor their build performance.
-
-In our first example, a researcher studies whether test failures in CI
+chunk retrieval technique we describe two concrete examples: a software
+team
+wanting to monitor their build performance and a
+researcher investigating why builds fail.
+
+In our first example, a software development team wants to monitor
+the performance of the phases within their CI build.
+They are using
+Travis CI, which measures the duration of build phases and documents
+this within the build log.
+As all log statements that report timing
+measurements are formatted the same way, the targeted log chunks are
+from one structural category.
+Therefore the development team can use
+PBE to retrieve the duration of a build phase.
+
+In our second example, a researcher studies whether test failures
 are caused by a small or by a large group of test cases.
@@
 As the researcher is
-covering a wide range of build tools and development languages, the
+covering a wide range of test tools, the
 log chunks they target are in various, non-predictable structural
@@
 retrieved.
-Therefore, our decision tree recommends them to use KWS\@.
+Therefore, our decision tree recommends to the researcher to use KWS\@.
 
@@
 can use PBE, trained with examples from each test tool separately.
-
-In our second example, a software development team wants to monitor
-the performance of the phases within their CI build.
-They are using
-Travis CI, which measures the duration of build phases and documents
-them within the build log.
-As all log statements that report timing
-measurements are formatted the same way, the targeted log chunks are
-from one structural category.
-Therefore the development team can use
-PBE to retrieve the duration of a build phase as well as its name.
 
@@
 There are various future research opportunities based on our work:
-\begin{itemize}
-  \item \textbf{Systematic Survey of Industry Approaches for Build
-  Log Analysis} Our survey is limited to academic work and articles.
+
+\textbf{Systematic Survey of Industry Approaches for Build
+Log Analysis}
+Our survey is limited to academic work and articles.
 However, handling build logs is a challenge for a wide range of
@@
 inferred test results in Azure~\cite{azure2020inferred}.
-  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
+
+\textbf{Further Analysis of \emph{LogChunks}}
+We created the
 \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
@@
 reason the build failed within build logs.
-  \item \textbf{Cross-Repository Build Log Analysis} We trained and
+
+\textbf{Cross-Repository Build Log Analysis}
+We trained and
 tested each chunk retrieval technique on examples from the same
@@
 environment-agnostic analysis tools.
-  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
+
+\textbf{Comparison with more Chunk Retrieval Techniques}
+This
 paper investigates the three chunk retrieval techniques PBE, CTS and
@@
 approach by Amar et al.~\cite{amar2019mining}.
-  \item \textbf{Refinement of Retrieval Quality for each Technique} We
+
+\textbf{Refinement of Retrieval Quality for each Technique} We
 investigated basic configurations of existing techniques applied to
@@
 \end{itemize}
-  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
+
+\textbf{Usability Analysis of Chunk Retrieval Output}
+Our
 analysis of the output produced by the chunk retrieval focuses on
@@
 outputs are to developers through controlled experiments.
-\end{itemize}
 

### 2020-04-16 tse-paper/content.tex
corrections study results and graphs
closes #39, closes #42

@@
 technique.
-We start with CTS, KWS and RLR, as their results are easiest to
-understand.
 Afterwards we compare the three techniques with each other and RLR as
 baseline.
+
+\subsection{Program Synthesis by Example (PBE)}
+\label{sec:r:pbe}
+
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/failure-reason-pbe.pdf}
+		\caption{Results of chunk retrieval with PBE.}
+		\label{fig:failure-reason-PBE}
+\end{figure}
 
@@
 
+\begin{figure*}
+\centering
+    \textbf{Program Synthesis by Example (PBE)}\par\medskip
+\begin{subfigure}[b]{\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+				\caption{Successfulness of retrieval
+				compared by structural category count
+				in training and test sets.}
+		\label{fig:failure-reason-categorycount-PBE}
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[b]{\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+				\caption{Precision, recall and
+				F$_{1}$-score when PBE could synthesize
+				a consistent program compared with the
+				size of the training set.}
+		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
+\end{subfigure}
+\caption{Results of chunk retrieval with  Program Synthesis by Example
+(PBE)}
+\end{figure*}
+
+\Cref{fig:failure-reason-PBE} presents the results of the chunk
+retrieval with PBE.
+Out of the 400 runs, 5 per each one of the 80 example
+sets, PBE extracted all the desired lines successfully in 138 cases.
+In 59 cases, a regular expression program could be synthesized, though
+it did not find a match on the test build log.
+In 30 cases the synthesized program only extracted a
+subset of the desired lines.
+For these 30 cases, the average recall
+was 28\%.
+\Cref{lst:pbe-unsuccessful} shows how an example of such
+an \emph{unsuccessful retrieval}, where the synthesized program only
+retrieved two of the four targeted lines.
+In 173 of the 400 cases
+could PROSE not synthesize program consistent with all of the training
+examples.
+
+\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
+runs depend on the number of structural categories in the training and
+test examples.
+The figure demonstrates that program synthesis mostly
+returns exactly the desired output when there are is only one
+structural category present in the training and test examples.
+However, when
+two or more structural categories are simultaneously present,
+PROSE could in most cases not synthesize a program.
+For four or more present
+categories PROSE could never synthesize a consistent program.
+
+\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
+precision and recall of the 227 runs where PBE could synthesize a
+program consistent with all training examples.
+When the training set
+size increases from one to two, recall and F$_{1}$-score increase by
+about 25\%, precision increases by about 10\%.
+For two or more
+training examples, recall and F$_{1}$-score stay around 75\% and
+precision around 96\%.
+
 \subsection{Common Text Similarity (CTS)}
@@
     \textbf{Common Text Similarity (CTS)}\par\medskip
-\begin{subfigure}[t]{\columnwidth}
+\begin{subfigure}[tb]{\columnwidth}
 		\centering
@@
 \end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
+\begin{subfigure}[tb]{\columnwidth}
 		\centering
@@
 recall and F$_{1}$-score decrease.
-Especially for more than three
-categories present we have no chunk retrieval runs where all desired
-lines were extracted.
+% Especially for more than four
+% categories present we have no chunk retrieval runs where all desired
+% lines were extracted.
 
@@
 categories no clear trend is visible in precision, recall or
-F$_{1}$-score for an increasing amount of categories in the training
-and test examples.
+F$_{1}$-score.
 
@@
 increases from 6\%, for one structural category present, to 11\%, for
-three sturctural categories present and also drops to 0\% for more
+three structural categories present and also drops to 0\% for more
 structural categories.
-Graphs of the results of the chunk retrieval with RLR from our study
+Graphs of these results of the chunk retrieval with RLR
 are included in our replication
 package~\cite{brandt2020chunk-replication}.
-
-\subsection{Program Synthesis by Example (PBE)}
-\label{sec:r:pbe}
-\begin{figure*}
-\centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth,
-		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-				\caption{Precision, recall and
-				F$_{1}$-score when PBE could synthesize
-				a consistent program compared with the
-				size of the training set.}
-		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth,
-		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
-				\caption{Successfulness of retrieval
-				compared by structural category count
-				in training and test sets.}
-		\label{fig:failure-reason-categorycount-PBE}
-\end{subfigure}
-\caption{Results of chunk retrieval with  Program Synthesis by Example
-(PBE)}
-\end{figure*}
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=0.75\columnwidth,
-		clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
-		\label{fig:failure-reason-PBE}
-\end{figure}
-
-\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
-evaluation.
-Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines in 138 cases.
-In 89 further
-cases, an extraction program was also successfully synthesized, though
-in 59 of the 89 cases the synthesized program yielded no output.
-In 30
-of the 89 cases did the synthesized program only partially extract a
-subset of the desired lines.
-For these 30 cases, the average recall
-was 28\%.
-\Cref{lst:pbe-unsuccessful} shows an example of such
-an \emph{unsuccessful retrieval}, where the synthesized program only
-retrieved two of the four targeted lines.
-In 173 of the 400 cases
-could PROSE not synthesize program consistent with all of the training
-examples.
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
-runs depend on the number of structural categories in the training and
-test examples.
-The figure demonstrates that program synthesis mostly
-returns exactly the desired output when there are is only one
-structural category present in the training examples.
-However, when
-two or more structural categories are simultaneously present in the
-examlpe set, PROSE could in most cases not synthesize a program
-consistent with all training examples.
-For four or more present
-categories PROSE could never synthesize a consistent program.
-
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
-precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples.
-When the training set
-size increases from one to two, recall and F$_{1}$-score increase by
-about 25\%, precision increases by about 10\%.
-For two or more
-training examples, recall and F$_{1}$-score stay around 75\% and
-precision around 96\%.
 
@@
 CTS and KWS
-extract some of the desired lines in 79\% and 88.5\% of the chunk
-retrieval runs.
-With 38.25\%, KWS also has the highest number of fully
+extract at least some of the desired lines in 79\% and 88.5\%
+of the chunk retrieval runs.
+With 38.25\%, KWS also has the highest proportion of fully
 successful extractions, followed by PBE with 34.5\%.
@@
 				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
-		\caption{Training and test examples in \emph{one}
+		\caption{Training and test examples in 1
 		structural category.}
@@
 		clip]{img/big-study/recall-precision-multicategory-all.pdf}
-		\caption{Training and test examples in $>1$ structural
+		\caption{Training and test examples in \textgreater
+		1 structural
 		category.}

### 2020-04-16 tse-paper/content.tex
write more in lit sur discussion, relates to #40

@@
 
-\begin{figure}[hb]
+\begin{figure}[htbp]
 	\centering
@@
 survey and the data extraction from the resulting articles.
-We present our results on how buildlogs are analyzed in literature
-and discuss the implecations of these findings on our research.
+We present our results on how build logs are analyzed in literature
+and discuss the implications of these findings on our research.
 
@@
 }
-\begin{figure*}[!tb]
+\begin{figure*}[htbp]
   \centering
@@
 leverage their inherent event structure.
-As build logs lack this sturcture, we focussed our literature
+As build logs lack this structure, we focussed our literature
 survey on articles that as a source of information.
@@
 We use Google Scholar as opposed to Scopus or
-other databases, as it is the search engine for acdemic articles with
+other databases, as it is the search engine for academic articles with
 the broadest and most current index, including preprints.
@@
 contextual information Google Scholar displayed.
-We inlcuded only
+We included only
 publications written in a language intelligible to the authors (that
@@
 
-We wanted to characterize how researchers use buildlogs as input to
+We wanted to characterize how researchers use build logs as input to
 any processes.
-We were interesed in
+We were interested in
 \begin{itemize}
@@
 \end{itemize}
-To objecifiy our data extraction we created a template of the targeted
-factors and performed a pilot, as reccommended by Petersen et
+To objectifiy our data extraction we created a template of the targeted
+factors and performed a pilot, as recommended by Petersen et
 al.~\cite{petersen2015guidelines}.
@@
 We inspected the articles as closely as necessary,
-starting from occurences of ``log'' or ``build'' within the text.
+starting from occurrences of ``log'' or ``build'' within the text.
 
@@
 \end{simplebox}
-
-\subsection{Results}
-In the following, we will present the results of our literature survey.
-We present the information within the build logs that was targeted,
-the retrieval techniques used and the origin of the build logs
-which were analyzed.
 
@@
 
-\begin{figure*}[tbhp]
-		\centering
-		\includegraphics[width=0.7\textwidth, trim={1.1cm 0.4cm
+\begin{figure}[tbhp]
+		\centering
+		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
 		1.5cm 0.5cm},
@@
 		\label{fig:litsur:log_producer}
-\end{figure*}
+\end{figure}
+
+\subsection{Results}
+In the following, we will present the results of our literature survey.
+We present the information within the build logs that was targeted,
+the retrieval techniques used and the origin of the build logs
+which were analyzed.
 
@@
 The information that was targeted varied from article to article.
-Most prominent was the search for errors (39\%) which occured within
+Most prominent was the search for errors (39\%) which occurred within
 the build process, as presented in \Cref{fig:litsur:info_target}.
@@
 For instance distinguishing failures caused by developers from
-failures casued
+failures caused
 by infrastructure errors~\cite{lindqvist2019detection} or
-whether projects use automated statc analysis
+whether projects use automated static analysis
 tools~\cite{kavaler2019tool}.
@@
 The majority of articles (46\%) used the outcome of their build log
-analysis for research purpopses, as shown in \Cref{fig:litsur:use}.
+analysis for research purposes, as shown in \Cref{fig:litsur:use}.
 Further uses were giving feedback to developers (10\%) or automatic
@@
 included
-rather unprecise statements like ``we parse the build logs''.
+rather imprecise statements like ``we parse the build logs''.
 25\% of the articles described the use of regular expressions and 20\%
@@
 
-% Seo et al.~\cite{seo2014programmers}
-% They based their analyses on sets of
-% build logs collected from industry partners.
-% They	reported by Java and C++ builds.
-
-% Rausch et al.~\cite{rausch2017empirical} analyze CI builds of open
-% source Java projects
-
-% Vassallo et al.~\cite{vassallo2017a-tale} compare open source projects
-% in Java to industrial ones.
-% Their data stems from analyzing
-% build logs from \emph{TravisTorrent}~\cite{beller2017travistorrent}
-% with regular expressions.
-
-% Vassallo et
-% al.~\cite{vassallo2018un-break}
-% They parse
-% Maven~\cite{maven2019website} build logs into a structured
-% representation and create hint generators.
-% For example, one of the hint generators queries stack overflow for
-% discussions related to why the build failed.
-
 \subsubsection{Build Logs}
@@
 computer science research.
-In this section we will summarize our findings and relate them to the
+Hereafter we will summarize our findings and relate them to the
 approach we are taking to improve build log analysis with chunk
@@
 every supported build environment.
-We implement build environment agonostic build log analysis
+\Cref{fig:litsur:log_producer} shows that few build environments are
+targeted by many studies and tools (A).
+The majority of build environments was however only targeted by one
+article each (B).
+From this we follow that, while custom parsers are beneficial for the
+small group of environments targeted by many (A), all and especially
+the rarer investigated environments (B) would benefit from a generic
+solution.
+We implement build environment agnostic build log analysis
 techniques, which are customized to a specific project by
@@
 environments.
-Further, the training examples also specify the log chunk targeted by the
-retrieval, which enable our chunk retrieval techniques to retrieve a
-broad range of information from build logs.
+% Further, the training examples also specify the log chunk targeted
+by the
+% retrieval, which enable our chunk retrieval techniques to retrieve a
+% broad range of information from build logs.
+
+The articles within our study mainly tried to retrieve or classify
+errors or reasons for the build to fail from the logs.
+Therefore we chose the log chunk ``describing why the build failed''
+~\cite{brandt2020logchunks} for our empirical comparison study
+of chunk retrieval techniques.
+The techniques we implement are in principle agnostic to the targeted
+log chunk, thus we believe our results can be generalized to other
+kinds of log chunks.
 
@@
 maintain~\cite{michael2019regexes}.
-For this reason, we are focussing % TODO: less development time,
-% only giving examples
-
-This task of retrieving specific chunks of text from the
-build logs can be solved by the chunk retrieval techniques we compare
-in this article.
-Our results can support researchers in choosing a
-suitable technique for their data set of build logs and the chunks
-they want to retrieve.
-By relieving them from building custom parsers
-we enable them to cover a much wider range of languages and build
-tools in their studies.
-
-% \subsubsection{Retrieved Information}
-% why from build logs? not avaliable in cleaner format much use for
-% research, a bit of developer information / tools following: research
-% so many logs that unfeasible to do manually, less focus on tools for
-% devs (caveat! we excluded books and documentation on industrial tools
-% -> many approaches there to make build logs digestible, tough many
-% focus on general minimizing of the data presented, not retrieving
-% specific chunks)
-
-% \subsubsection{Retrieval Technique}
-% broadly mentioned shortly, rarely explained in detail we follow that
-% researchers often see this as an unimportant side fact work needed to
-% be done to get the big work done
-
-% \subsubsection{Build Logs}
-% often focussed on specific logs, sometimes mentioned because of effort
-% developing a parser other times also because other tools used in
-% further research are limiting the scope (reference paper with PIT
-% tool).
-% many focus on maven because of it's prevalence also in respect
-% to other tools much research done on travis ci logs b/c of their
-% abundance and open availability
+For this reason, we are focussing on techniques that are configured
+through examples consisting of logs and corresponding chunks.
+These examples are provided by the user and can simply be
+exchanged whenever new cases are introduced.
+
+% This task of retrieving specific chunks of text from the
+% build logs can be solved by the chunk retrieval techniques we compare
+% in this article.
+% Our results can support researchers in choosing a
+% suitable technique for their data set of build logs and the chunks
+% they want to retrieve.
+% By relieving them from building custom parsers
+% we enable them to cover a much wider range of languages and build
+% tools in their studies.
+
+In summary, this literature study shows the need for build log
+analysis techniques that are build-environment agnostic, automated
+and can be configured with small effort.
+We achieve this by developing three techniques for which the
+information to be retrieved is specified through examples or keywords.
+
+We propose the notion of chunk retrieval techniques which retrieve
+a substring, that describes a specific information, from a build log.
+Generally these can also be used to classify build logs and therefore
+cover the great majority of the type of log analysis we saw within
+our survey.
+
+We implement three chunk retrieval techniques based on approaches
+described by several articles:
+PBE mimics regular expressions and parsers while simplifying
+their development.
+We chose text similarity (CTS) as a common information retrieval
+technique, and implement the ad-hoc approach of
+searching for specific strings or keywords within KWS\@.
+
+Our evaluation of the three chunk retrieval techniques is done on the
+\emph{LogChunks} data set, because it encompasses a broad range of
+build environments which enables us to measure the generic
+applicability of our techniques.
+The targeted chunks are describing error messages or
+``the reason the build failed'', which was also the information
+most targeted by the articles in our survey.
+
 \section{Chunk Retrieval Techniques}
@@
 
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
-In this article, we evaluate different techniques to automatically
-retrieve pieces of information that appear literally in the build
-logs.
-%, i.e., techniques that do not aggreagte, combine, or deducted
-%information.
-We call such pieces of information from build logs
-\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
-The techniques we investigate here do not require a formal lexer and
-parser to analyze the entire structure of build logs, but focus on
-ad-hoc extracting just one specific piece of information per
-configuration.
-
-With the term \textit{configuration}, we abstract over the training
-and parametrization that different techniques require in different
-forms.
-A configuration can be explicitly stated or implicitly dervied
-by learning through provided examples.
-It is therefore a manual
-specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log.
-Each chunk
-retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word).
-The
-granularity might be adjustable by configuration.
-\emph{Running a
-chunk retrieval technique} means to execute a fully configured
-technique to consumes as input a build log in plain text format and to
-produce an array as output.
-The array consists of substrings of the
-build log text.
-
-\begin{table*}[]
+\begin{table*}[htbp]
 \centering
 \caption{Chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}XlXlXX@{}}
+\begin{tabularx}{\textwidth}{@{}llXll@{}}
 \toprule
 Name			     & Acronym & Identification Technique
-& Granularity & Configuration & Source		  \\
+& Granularity & Configuration \\
 \midrule
@@
 
+\subsection{Characteristics of Chunk Retrieval Techniques}
+\label{sec:blirt}
+In this article, we evaluate different techniques to automatically
+retrieve pieces of information that appear literally in the build
+logs.
+%, i.e., techniques that do not aggregate, combine, or deducted
+%information.
+We call such pieces of information from build logs
+\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
+The techniques we investigate here do not require a formal lexer and
+parser to analyze the entire structure of build logs, but focus on
+ad-hoc extracting just one specific piece of information per
+configuration.
+
+With the term \textit{configuration}, we abstract over the training
+and parametrization that different techniques require in different
+forms.
+A configuration can be explicitly stated or implicitly derived
+by learning through provided examples.
+It is therefore a manual
+specification of which information the chunk retrieval should target.
+It also supplies the necessary information for the technique to
+identify the targeted information chunk in a build log.
+Each chunk
+retrieval technique has a specific \textit{granularity}, i.e.,\ the
+smallest piece of text it can return (e.g., a line, or a word).
+The
+granularity might be adjustable by configuration.
+\emph{Running a
+chunk retrieval technique} means to execute a fully configured
+technique to consumes as input a build log in plain text format and to
+produce an array as output.
+The array consists of substrings of the
+build log text.
+
 \subsection{Program Synthesis by Example (PBE)}
@@
 intent of the user through examples which they provide.
-Leveraging this apprach, we implemented a chunk retrieval technique
+Leveraging this approach, we implemented a chunk retrieval technique
 for build logs.
@@
 picking lines from the build log.
-RLR mimicks the
+RLR mimics the
 situation of guessing blindly which lines might be interesting.

### 2020-04-17 tse-paper/content.tex
add more details to study design, relates to #41

@@
 analysis techniques that are build-environment agnostic, automated
-and can be configured with small effort.
+and can be configured by the user with little effort.
 We achieve this by developing three techniques for which the
@@
 \subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:blirt}
+\label{sec:crt-characteristics}
 In this article, we evaluate different techniques to automatically
@@
 
+To investigate when our chunk retrieval techniques are suited to
+analyze build logs (\textbf{RQ2}), we perform an empirical comparison
+study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
+In particular we are interested in how many examples a technique
+should be trained with for best performance (\textbf{RQ2.1}),
+how similar the structural representation of the targeted log chunks
+has to be (\textbf{RQ2.2}) and how reliable the quality of the
+produced outputs are (\textbf{RQ2.3}).
+
 \begin{simplebox}[minipage boxed title*=-2.5cm,
@@
 
-% TODO Caro: redo
+In the following we present the data set we created for this study,
+our study process (presented in \Cref{fig:study}) and the metrics
+we measure to answer our research questions.
+
 \begin{figure*}[tb]
@@
 \end{figure*}
-
-To investigate which technique is best suited to retrieve chunks from
-CI build logs we evaluate the three chunk retrieval techniques
-PBE, CTS and KWS.
-Random Line Retrieval (RLR), acts as a baseline for
-the comparison.
-The following section
-describes our study design and which metrics we measure to answer our
-research questions.
-In the presentation of the results, we first focus
-on each of the three techniques and later compare them against each
-other.
 
@@
 failed''~\cite{brandt2020logchunks}.
-We include keywords, which we
+We included keywords, which we
 would use to search for the selected chunk within the log.
@@
 within the log.
-If the chunks are surrounded by the same markings
-within the log we assign them the same structural category.
-
-% We run four techniques on the examples from \emph{LogChunks}.
-
-\noindent
-\textbf{Training and Test Set}
-% TODO Moritz: You said: Add details how key words were extracted.
-% Add example?
-% how the keywords were put in logchunks does not fit here, that is
-% maybe answered 2 paragraphs above already?
-% how KWS uses the keywords is already described in the section
-% introducing the technique => I would scrap everything but the first
-% sentence directly above here :)
-
-% TODO Moritz: You said: Add more details.
-% How was the split in numbers?
-% this is described in the following paragraph, should we merge them
-% (bc there are also no sub-RQs now) or is it close enough? :)
-For each repository in \emph{LogChunks}, we split the examples
-chronologically into training and test set.
-Therefore, we train on
-examples from past build logs and test on more recent build logs.
-
-\noindent % TODO: adapt if we change the research questions
-\textbf{RQ 2.1: Size of Training and Test Set}
-We evaluate the techniques with different training set
-sizes, to analyze how many examples the chunk retrieval techniques need to
-perform best.
-We train each technique with one to five examples from each of
-the repositories within \emph{LogChunks}.
-The size of the test set is one.
-
-\noindent
-\textbf{RQ 2.2: Recording Structural Categories}
-We record the structural categories
-of the examples in the training and test sets, to determine how
-structurally similar the examples for the chunk
-retrieval techniques need to be.
-
-\noindent
-\textbf{RQ2.3: Accuracy Metrics}
-we save the output lines of the chunk retrieval run on the input
-of the test example ($\mathit{RetrievedLines}$), to measure the
-accuracy of the retrieved chunks
-As oracle in our evaluation, we save the
-desired lines from the output of the test example
+If the chunks were surrounded by the same markings
+within the log we assigned them the same structural category.
+
+\subsection{Study Process}
+We begin by selecting all examples in \emph{LogChunks}
+that correspond to one GitHub repository---end therefore the
+same build environment (1).
+One to five examples make up the training set (2).
+We vary its size to measure how many examples are needed to
+confidently configure a technique.
+The training set is so small, because the examples have to be
+manually created by a user.
+A larger training set would oppose our goal of providing techniques
+that can be configured with little effort.
+The example chronologically after the training set makes up the
+test set (3).
+In this way, we train on examples from past build logs and test on
+more recent logs.
+We chose a training set size of 1, as users of our techniques
+should receive reliable results on every build log they analyze.
+As a next step, we configure the chunk retrieval technique with
+the examples from the training set (4) and apply the technique to the
+training set (5), which produces the retrieval output (6).
+Based on this, we collect the following measurements (7):
+\begin{itemize}
+  \item The size of training set (\textbf{RQ2.1}),
+  \item the number of structural categories in the training set
+  (\textbf{RQ2.2})
+  \item the lines of the retrieval output ($\mathit{RetrievedLines}$),
+  and our oracle, the output defined in the test example
   ($\mathit{DesiredLines}$).
-
-We calculate and define a number of metrics for the context of our
-evaluation.
+  From these we calculate accuracy metrics (\textbf{RQ2.1}).
+\end{itemize}
+
+\textbf{Accuracy Metrics}
+We calculate a number of accuracy metrics to measure how well
+the chunk retrieval techniques perform in our evaluation:
 
@@
 	% the same information so if someone asks we can defend I think
+
 	\item $\mbox{Precision} = \dfrac{|\mathit{True\
@@
 	desired lines were retrieved.
+
 	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
@@
 	measures such as accuracy because for a
-	``needle-in-the-haystack'' scenario, we do not want to bloat
+	``needle-in-the-haystack'' scenario, we want to avoid bloating
 	our results by correctly not finding lots of irrelevant log
 	lines.
+
 	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
+	\mathit{Recall} = 1, \mathit{false\ otherwise}$ \vspace{0.05cm}\\
 	We define a successful retrieval as one where all desired
@@
 \end{itemize}
+
+This concludes one execution within our evaluation.
+We conduct one run for each of the four chunk retrieval techniques,
+for each of the eighty repositories in \emph{LogChunks} (8)
+and for each of the five training set sizes (2).
+In total we perform 1600 runs, 400 for each of the chunk retrieval
+techniques PBE, CTS, KWS and RLR.
+
+Our implementation of the techniques, as well as our evaluation
+harness and the code we used to process our results is offered
+for inspection and reproduction in our replication package
+~\cite{brandt2020chunk-replication}.
 

### 2020-04-17 tse-paper/content.tex
move chunk example to section about techniques

@@
 chunk.
-
-\begin{figure*}[!t]
-  \centering
-\begin{subfigure}[t]{\columnwidth}
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Could not determine the dependencies of task ':app:jacocoTestDebugReport'.
-> Task with path 'testDebug' not found in project ':app'.
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-FAILURE: Build failed with an exception.
-
-* What went wrong:
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk1.txt}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-
-* Try:
-  \end{lstlisting}
-\end{subfigure}
-  \caption{Two examples of log chunks explaining why an Android
-  build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me
-  % long ago that this was something your analyzer cannot extract
-  \label{lst:chunk-example}
-\end{figure*}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
-RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!t]
-  \centering
-  \lstinputlisting[breaklines=true]{listings/prose.txt}
-  \caption{Simiplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[!t]
-  \centering
-  \begin{lstlisting}[breaklines=true,frame=tlr]
-=== RUN   TestSeparator
-  \end{lstlisting}
-  \vspace{-\baselineskip}
-  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk2.txt}
-  \vspace{-\baselineskip}
-  \begin{lstlisting}[breaklines=true,frame=blr]
-=== RUN   TestGenerateHTML
-  \end{lstlisting}
-  \caption{Example of a log chunk showing a linter error}
-  \label{lst:chunk-example-3}
-\end{figure}
-
-% TODO: this could move to the chunk retrieval techniques section
-The results of our empirical comparison study on the chunk retrieval
-techniques
-show that the structural representation of the targeted chunk greatly
-influences
-the performance of the chunk retrieval techinques.
-\Cref{lst:chunk-example} shows two exemplary
-log chunks from Android build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed.
-When PBE is trained with these two examples it produces
-a regular expression program similar to the one presented in
-\Cref{lst:prose-program-simplified}.
-The retrieval
-starts after a colon and a line separator and before a capital
-letter.
-It ends before two line separators, consistent with the two example
-chunks from \Cref{lst:chunk-example}.
-This shows, that the characters structuring the text around the chunk are
-cruicial for regular expressions to identify a log chunk.
-In fact, if the third example from \Cref{lst:chunk-example-3} with a
-different structural representation is added to the training set,
-PBE is not able to syntesize a program and returns
-``\texttt{no program found}''.
-We express this difference in structural representation through
-dividing log chunks into structural categories.
-The chunks from \Cref{lst:chunk-example}
-are in the \emph{same structural category}, while the chunk from
-\Cref{lst:chunk-example-3} is in a \emph{different structural category}.
 
@@
 
+\subsection{Chunk Retrieval Example}
+\begin{figure*}[!htbp]
+  \centering
+\begin{subfigure}[!htbp]{\columnwidth}
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+FAILURE: Build failed with an exception.
+
+* What went wrong:
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
+Could not determine the dependencies of task ':app:jacocoTestDebugReport'.
+> Task with path 'testDebug' not found in project ':app'.
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+
+* Try:
+  \end{lstlisting}
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[!htbp]{\columnwidth}
+  \centering
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+FAILURE: Build failed with an exception.
+
+* What went wrong:
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk1.txt}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+
+* Try:
+  \end{lstlisting}
+\end{subfigure}
+  \caption{Two examples of log chunks explaining why an Android
+  build failed.}
+  % TODO Moritz: we can relate this to travistorrent maybe, you told me
+  % long ago that this was something your analyzer cannot extract
+  \label{lst:chunk-example}
+\end{figure*}
+
+\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
+RegexPair,
+  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
+\begin{figure}[!htbp]
+  \centering
+  \lstinputlisting[breaklines=true]{listings/prose.txt}
+  \caption{Simplified regular expression produced by PBE when trained
+  with examples from \Cref{lst:chunk-example}}
+  \label{lst:prose-program-simplified}
+\end{figure}
+
+\lstset{
+  language=,
+  morekeywords={},
+  texcl=false
+}
+\begin{figure}[!htbp]
+  \centering
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+=== RUN   TestSeparator
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk2.txt}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+=== RUN   TestGenerateHTML
+  \end{lstlisting}
+  \caption{Example of a log chunk showing a linter error}
+  \label{lst:chunk-example-3}
+\end{figure}
+
+To illustrate the chunk retrieval techniques further, we want to give
+an example of real-world log chunks and how the techniques can
+retrieve them from build logs.
+\Cref{lst:chunk-example} shows two exemplary
+log chunks from Android build logs marked in blue.
+Both chunks contain the information on why the
+corresponding build failed, the information most often targeted by
+other articles which analyze build logs.
+
+When PBE is trained with these two examples it produces
+a regular expression program similar to the one presented in
+\Cref{lst:prose-program-simplified}.
+The retrieval
+starts after a colon and a line separator and before a capital
+letter.
+It ends before two line separators, consistent with the two example
+chunks from \Cref{lst:chunk-example}.
+This shows, that the characters structuring the text around the chunk are
+crucial for regular expressions to identify a log chunk.
+In fact, if the third example from \Cref{lst:chunk-example-3} with a
+different structural representation is added to the training set,
+PBE is not able to synthesize a program and returns
+``\texttt{no program found}''.
+We later express this difference in structural representation through
+dividing log chunks into \emph{structural categories}.
+The chunks from \Cref{lst:chunk-example}
+are in the \emph{same structural category}, while the chunk from
+\Cref{lst:chunk-example-3} is in a
+\emph{different structural category}.
+The results of our empirical comparison study on the chunk retrieval
+techniques
+show that the structural representation of the targeted chunk greatly
+influences
+the performance of the chunk retrieval techniques.
+
+CTS will rank the lines from the analyzed build log which are most
+similar to the chunks in the training examples,
+marked blue in \Cref{lst:chunk-example}.
+It will then return the two lines ranked highest, as the chunks in
+the training examples have on average two lines.
+
+KWS is configured with keywords that appear close to the chunk within
+the build log.
+For the examples from \Cref{lst:chunk-example} these could be
+``FAILURE'', ``wrong'' or ``failed''.
+The example from \Cref{lst:chunk-example-3} could be found with
+``FAIL''.
+If KWS would be trained with all three examples and the afformentioned
+associated keywords, it would search for the three keywords from
+\Cref{lst:chunk-example}, as they appear twice, most often within
+the training set of three examples.
+
 \subsection{Tool Implementation}
@@
 Based on this, we collect the following measurements (7):
-\begin{itemize}
+\begin{itemize}[leftmargin=0.4cm] \itemsep1em
   \item The size of training set (\textbf{RQ2.1}),
@@
 following improvements:
-\begin{itemize}
+\begin{itemize}[leftmargin=0.4cm] \itemsep1em
   \item \textbf{Custom Ranking and Tokens for PBE} The program

### 2020-04-17 tse-paper/content.tex
adapt authors
caros for now last text edits

@@
 \subsection{Discussion}
+\label{sec:lit-sur:discussion}
 Our literature survey sheds light on how build log analysis is used within
@@
 to the researchers~\cite{ren2018automated}.
-Most of the articles which explicitly mention a manual analysis of
-the logs only restrict their work to few logs or take a
+Articles which explicitly mention a manual analysis of
+the logs, mostly restrict their work to few logs or take a
 ``representative sample to make manual analysis
@@
 number of builds.
-The chunk retrieval techniques we investigate within this article are
-automated, apart from their configuration through training examples.
+% The chunk retrieval techniques we investigate within this article are
+% automated, apart from their configuration through training examples.
 
@@
 build environments and targeted information.
+
 Several articles noted the variety in log formats for different build
@@
 solution.
-We implement build environment agnostic build log analysis
-techniques, which are customized to a specific project by
-the training examples which the user provides.
-In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
-data set we chose for our evaluation covers a broad range of build
-environments.
-% Further, the training examples also specify the log chunk targeted
-by the
-% retrieval, which enable our chunk retrieval techniques to retrieve a
-% broad range of information from build logs.
-
-The articles within our study mainly tried to retrieve or classify
-errors or reasons for the build to fail from the logs.
-Therefore we chose the log chunk ``describing why the build failed''
-~\cite{brandt2020logchunks} for our empirical comparison study
-of chunk retrieval techniques.
-The techniques we implement are in principle agnostic to the targeted
-log chunk, thus we believe our results can be generalized to other
-kinds of log chunks.
+% We implement build environment agnostic build log analysis
+% techniques, which are customized to a specific project by
+% the training examples which the user provides.
+% In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
+% data set we chose for our evaluation covers a broad range of build
+% environments.
+% % Further, the training examples also specify the log chunk targeted
+% by the
+% % retrieval, which enable our chunk retrieval techniques to retrieve
+% % a broad range of information from build logs.
 
@@
 maintain~\cite{michael2019regexes}.
-For this reason, we are focussing on techniques that are configured
-through examples consisting of logs and corresponding chunks.
-These examples are provided by the user and can simply be
-exchanged whenever new cases are introduced.
 
@@
 In summary, this literature study shows the need for build log
-analysis techniques that are build-environment agnostic, automated
+analysis techniques that are automated, build-environment agnostic
 and can be configured by the user with little effort.
-We achieve this by developing three techniques for which the
-information to be retrieved is specified through examples or keywords.
+% We achieve this by developing three techniques for which the
+% information to be retrieved is specified through examples or keywords.
+
+For this reason, we are focussing on techniques that run automatic
+after being configured through examples or keywords.
+Examples consist of logs and corresponding chunks.
+The examples and keywords are provided by the user and can simply be
+exchanged whenever new cases are introduced.
 
@@
 
+% The articles within our study mainly tried to retrieve or classify
+% errors or reasons for the build to fail from the logs.
+% Therefore we chose the log chunk ``describing why the build failed''
+% ~\cite{brandt2020logchunks} for our empirical comparison study
+% of chunk retrieval techniques.
+% The techniques we implement are in principle agnostic to the targeted
+% log chunk, thus we believe our results can be generalized to other
+% kinds of log chunks.
+
 \section{Chunk Retrieval Techniques}
@@
 example (PBE), common text similarity (CTS), and keyword search (KWS).
+In addition we present our comparison baseline of random line
+retrieval (RLR), illustrate the techniques on a concrete example
+of log chunks and sketch out implementation.
 
@@
 
-\subsection{Random Line Retrieval}
+\subsection{Random Line Retrieval (RLR)}
 \label{sec:expl-rlr}
@@
 \subsection{Chunk Retrieval Example}
+\label{seC:crt-example}
+
 \begin{figure*}[!htbp]
@@
 To illustrate the chunk retrieval techniques further, we want to give
-an example of real-world log chunks and how the techniques can
-retrieve them from build logs.
-\Cref{lst:chunk-example} shows two exemplary
-log chunks from Android build logs marked in blue.
-Both chunks contain the information on why the
-corresponding build failed, the information most often targeted by
-other articles which analyze build logs.
-
-When PBE is trained with these two examples it produces
+an example of real-world log LogChunks.
+\Cref{lst:chunk-example} shows two excerpts
+from Android build logs.
+Marked in blue are the chunks
+which contain the information on why the
+corresponding build failed.
+
+When PBE is trained with these two examples, it produces
 a regular expression program similar to the one presented in
@@
 letter.
-It ends before two line separators, consistent with the two example
+It ends before two line separators,
+which is consistent with the two example
 chunks from \Cref{lst:chunk-example}.
@@
 crucial for regular expressions to identify a log chunk.
-In fact, if the third example from \Cref{lst:chunk-example-3} with a
-different structural representation is added to the training set,
+In fact, if the third example from \Cref{lst:chunk-example-3},
+which has a
+different structural representation, is added to the training set,
 PBE is not able to synthesize a program and returns
@@
 
-CTS will rank the lines from the analyzed build log which are most
-similar to the chunks in the training examples,
-marked blue in \Cref{lst:chunk-example}.
+CTS will rank the lines from an analyzed build log which are most
+similar to the chunks in the training examples
+from \Cref{lst:chunk-example}.
 It will then return the two lines ranked highest, as the chunks in
@@
 ``FAILURE'', ``wrong'' or ``failed''.
-The example from \Cref{lst:chunk-example-3} could be found with
-``FAIL''.
-If KWS would be trained with all three examples and the afformentioned
+The example from \Cref{lst:chunk-example-3} could be found
+by searching for ``FAIL''.
+If KWS would be trained with all three examples and the aforementioned
 associated keywords, it would search for the three keywords from
-\Cref{lst:chunk-example}, as they appear twice, most often within
+\Cref{lst:chunk-example}, as they appear twice---most often within
 the training set of three examples.
@@
 R and the text2vec library~\cite{text2vec2019webpage}.
+They can be found in our replication
+package~\cite{brandt2020chunk-replication} together which have
+our techniques installed and ready to use.
 
@@
 In particular we are interested in how many examples a technique
-should be trained with for best performance (\textbf{RQ2.1}),
+should be trained with (\textbf{RQ2.1}),
 how similar the structural representation of the targeted log chunks
 has to be (\textbf{RQ2.2}) and how reliable the quality of the
-produced outputs are (\textbf{RQ2.3}).
+produced outputs is (\textbf{RQ2.3}).
 
@@
 If the chunks were surrounded by the same markings
-within the log we assigned them the same structural category.
+within the log we assigned them the \emph{same structural category},
+as described in \Cref{sec:crt-example}.
 
@@
 We begin by selecting all examples in \emph{LogChunks}
-that correspond to one GitHub repository---end therefore the
+that correspond to one GitHub repository---and thus the
 same build environment (1).
@@
 A larger training set would oppose our goal of providing techniques
-that can be configured with little effort.
+that can be configured with little effort
+(see \Cref{sec:lit-sur:discussion}).
 The example chronologically after the training set makes up the
@@
 more recent logs.
-We chose a training set size of 1, as users of our techniques
+We chose a test set size of 1, as users of our techniques
 should receive reliable results on every build log they analyze.
-As a next step, we configure the chunk retrieval technique with
+In the next step, we configure a chunk retrieval technique with
 the examples from the training set (4) and apply the technique to the
@@
 Based on this, we collect the following measurements (7):
-\begin{itemize}[leftmargin=0.4cm] \itemsep1em
-  \item The size of training set (\textbf{RQ2.1}),
-  \item the number of structural categories in the training set
-  (\textbf{RQ2.2})
-  \item the lines of the retrieval output ($\mathit{RetrievedLines}$),
-  and our oracle, the output defined in the test example
+the size of training set (\textbf{RQ2.1}),
+the number of structural categories in the training
+set (\textbf{RQ2.2}),
+the lines of the retrieval output ($\mathit{RetrievedLines}$),
+and our oracle: the output defined in the test example
 ($\mathit{DesiredLines}$).
-  From these we calculate accuracy metrics (\textbf{RQ2.1}).
-\end{itemize}
-
-\textbf{Accuracy Metrics}
-We calculate a number of accuracy metrics to measure how well
-the chunk retrieval techniques perform in our evaluation:
+From these we calculate accuracy metrics (\textbf{RQ2.3}):
 

### 2020-04-17 tse-paper/content.tex
Add new intro

--- 2020-04-17 tse-paper/content.tex
@@
 
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.
-Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.
-CI builds produce logs which
-report results of various sub-steps within the build.
-These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within
-the build.
-The information stored in build logs can and has
-already been used for a variety of applications.
-One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}.
-To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
-builds~\cite{zampetti2017open}.
-Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text~\cite{beller2017oops}---making them inadequate
-for direct human consumption.
-Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs.
-Beller et al.\ use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.
-Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.
-Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.
-Custom parsers are powerful
-though fragile in light of changes in the log structure.
-Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-% TODO: 4 sentence description of the steps in graphic?
-\Cref{fig:overview} gives an overview of our research steps.
-We conducted a systematic mapping study,
-to gain an impression on how researchers are using information from
-build logs within their research or to support
-developers.
-% We implemented three promising techniques that retrieve
-% chunks of text from build logs and can be adapted to
-% a specific project and use case by giving examples of build logs and
-% correpsonding chunks.
-% We evaluated the
-Our goal was to clarify the state-of-research on build log
-analysis (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to
-retrieve specific information from buildlogs.
-The resulting implementations are rarely available and therefore rarely
-reused.
-Because of the high development overhead
-of the custom parsers, many implementations are limited to small number
-of supported build tools.
-
-\begin{figure*}[htb]
-	\centering
-	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
-	clip]{img/overview.pdf}
-	\caption{Our Research Workflow.}
-	\label{fig:overview}
-\end{figure*}
-
-To address this, we implement three promising techniques for build
-log analysis.
-They retrieve specific chunks of targeted information and are trained
-with examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data
-set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives
-(\textbf{RQ2}).
-
-\begin{simplebox}[minipage boxed title*=-5cm]{Research Questions}
+Within the past two decades, Continuous Integration (CI) has become a
+ubiquitous best practice to streamline the build process of software
+projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}. Build
+logs are a textual by-product that automatic software build processes
+create. As a ``treasure trove'' of information, they contain results
+not only of the elemntary steps to ``make'' a project---such as
+retrieving and resolving dependencies, compiling, and testing the
+software---but also about anciliary quality assurance steps such as
+automated, static analysis tools.
+
+When a build or one of its sub steps fails, developers typically
+scavenge the log for the source of the error. This manual activity is
+tedious and prone to error~\cite{santolucito2018statically}. As a
+single build log can be over 50 megabytes large~\cite{beller2017oops},
+it finding a piece of information in it is akin to searching for a
+needle in a haystack.  In addition, due to their information richness,
+build logs enable a plethora of other applications: with the help of
+build logs, we can better understand and cateogrize Continuous
+Integration failures and compile
+errors~\cite{islam2017insights,seo2014programmers}, differentiate
+testing practices~\cite{orellana2017differences,vassallo2017a-tale},
+train classifiers to predict the build outcome and
+duration~\cite{ni2017cost,bisong2017built,machalica2019predictive}, or
+investigate static analysis tools in CI
+builds~\cite{zampetti2017open}. Manual analysis of build logs does not
+scale to the number of build logs and amount of information that such
+sophisticated applications require. Therefore, being able to
+automatically extract pieces of information from build logs
+is not only paramount to such applications, but can also help
+developers debug a broken build.
+
+However, despite its paramount role, the process of how to analyze
+build logs has so far received little attention, bringing us to our first research question:
+\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}
 \begin{itemize}
-  \item[\textbf{RQ1:}] What is the state-of-research on build
+  \item[\textbf{RQ1:}] What are the state-of-the-art techniques on build
   log analysis?
-  \item[\textbf{RQ2:}] When are PBE, CTS or KWS suited to
-  retrieve chunks from build logs?
  \end{itemize}
@@
 
-% also moved down to where mentioned in detail
-% left copy here for convenience
-
-% \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
-% {\textbf{RQ1:} What is the state-of-research on build
-% log analysis?}
-% \begin{itemize}
-%   \item[\textbf{RQ1.1:}] Which information is targeted?
-%   \item[\textbf{RQ1.2:}] Which techniques are used?
-%   \item[\textbf{RQ1.3:}] Which build logs are analyzed?
-% \end{itemize}
-% \end{simplebox}
-
-% \begin{simplebox}[minipage boxed title*=-2.5cm,
-% attach boxed title to top center={yshift=-6mm}]
-% {\textbf{RQ2:} When are PBE{,} CTS or KWS suited to
-% retrieve chunks from build logs?}
-% \begin{itemize}
-%   \item[\textbf{RQ2.1:}] How many examples does a technique need to
-%   perform best?
-%   \item[\textbf{RQ2.2:}] How structurally similar do the examples
-%   need for a technique to be applicable?
-%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
-% \end{itemize}
-% \end{simplebox}
-
-% % At the moment there is only anecdotal evidence on the performance
-% of these
-% % techniques and on when a technique should be preferred over other
-% alternatives.
-% % Developers and researches currently have little support when choosing
-% which
-% % technique to use for a task.
-
-% % The goal of this article is to investigate different chunk retrieval
-% techniques
-% % for build logs and describe under which circumstances certain
-% techniques
-% can be
-% % recommended over others.
-% % We aim to characterize different chunk retrieval techniques.
-% % For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which
-% criteria
-% % influence the suitability of a chunk retrieval technique for CI
-% build logs.
-
-We implement and evaluate three chunk retrieval techniques:
+In this article, as first step (\Cref{fig:overview}), we show that
+less than half of the 61 works which rely on build log analysis
+describe how they performed it, and even fewer did so in detail, let
+alone made their implementation available. Even so, the literature
+survey finds three main strategies to extract information chunks from
+build logs: Using 1) a set of manually curated regular expressions,
+similar to TravisTorrentI~\cite{beller2017oops}, 2) a list of keywords
+to identify regions of interest in the build log, and 3)
+% TODO (Caro): Provide better description
+doing text-similarity.
+
+Even though these three approaches to retrieve information chunks from
+build logs have different strengths and weaknesses, the literature
+survey shows that their use is often arbitrary and that there is
+usually no discussion on why to use one over the other. Developers and
+researchers not only seem to lack awareness of which techniques exist
+(RQ1), but also guidelines on when to employ which. As a consequence,
+in RQ2 we ask:
+
+\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}
+\begin{itemize}
+  \item[\textbf{RQ2:}] What are the comparative strengths and weaknesses of the top-3 build log anaylsis techniques?
+\end{itemize}
+\end{simplebox}
+
+To answer this question, we implement three automatic techniques for
+build log analysis based on the three stratgies at large (step 2):
+
 \begin{itemize}
@@
 
-Following the results from our comparison study,
-recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision
-and recall of the chunk retrieval is required.
-Results produced by PBE are suited for automatic on-ward processing.
-CTS is well suited when the representation of the desired information
-varies
+In step 3, we conduct an empirical study to gauge the performance of
+these chunk retrieval techniques under a variety of conditions in
+real-world projects. Finally, we develop guidelines (step 4) on when
+one of the techniques might be perferrential to its alternatives.
+
+\begin{figure*}[htb]
+	\centering
+	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
+	clip]{img/overview.pdf}
+	\caption{Research Design.}
+	\label{fig:overview}
+\end{figure*}
+
+We recommend PBE for use cases where the desired information is always
+represented in the same structural way and high confidence in
+precision and recall of the chunk retrieval is required.  Results
+produced by PBE are suited for automatic on-ward processing.  CTS is
+well suited when the representation of the desired information varies
 slightly and the output of the chunk retrieval is further processed by
-a human.
-In cases where the textual representation of the desired information in
-the log
-is unpredictable or varies greatly, KWS seems to be the best choice.
-However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output
-chunk.
+a human.  In cases where the textual representation of the desired
+information in the log is unpredictable or varies greatly, KWS seems
+to be the best choice.  However, its low precision---it extracts a
+context of multiple lines around a finding---makes it generally
+unsuited for automatic on-ward processing and instead requires a human
+to further inspect and interpret the output chunk.
 
@@
 
+\subsection{Not intro anymore}
 % TODO: this could move to the chunk retrieval techniques section
@@
 	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Our literature selection process, following
+	\caption{Literature selection process, following
 	\cite{petersen2015guidelines}.}
@@
 analysis techniques that are build-environment agnostic, automated
-and can be configured by the user with little effort.
+and can be configured with small effort.
 We achieve this by developing three techniques for which the
@@
 \subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:crt-characteristics}
+\label{sec:blirt}
 In this article, we evaluate different techniques to automatically
@@
 
-To investigate when our chunk retrieval techniques are suited to
-analyze build logs (\textbf{RQ2}), we perform an empirical comparison
-study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
-In particular we are interested in how many examples a technique
-should be trained with for best performance (\textbf{RQ2.1}),
-how similar the structural representation of the targeted log chunks
-has to be (\textbf{RQ2.2}) and how reliable the quality of the
-produced outputs are (\textbf{RQ2.3}).
-
 \begin{simplebox}[minipage boxed title*=-2.5cm,
@@
 
-In the following we present the data set we created for this study,
-our study process (presented in \Cref{fig:study}) and the metrics
-we measure to answer our research questions.
-
+% TODO Caro: redo
 \begin{figure*}[tb]
@@
 \end{figure*}
+
+To investigate which technique is best suited to retrieve chunks from
+CI build logs we evaluate the three chunk retrieval techniques
+PBE, CTS and KWS.
+Random Line Retrieval (RLR), acts as a baseline for
+the comparison.
+The following section
+describes our study design and which metrics we measure to answer our
+research questions.
+In the presentation of the results, we first focus
+on each of the three techniques and later compare them against each
+other.
 
@@
 failed''~\cite{brandt2020logchunks}.
-We included keywords, which we
+We include keywords, which we
 would use to search for the selected chunk within the log.
@@
 within the log.
-If the chunks were surrounded by the same markings
-within the log we assigned them the same structural category.
-
-\subsection{Study Process}
-We begin by selecting all examples in \emph{LogChunks}
-that correspond to one GitHub repository---end therefore the
-same build environment (1).
-One to five examples make up the training set (2).
-We vary its size to measure how many examples are needed to
-confidently configure a technique.
-The training set is so small, because the examples have to be
-manually created by a user.
-A larger training set would oppose our goal of providing techniques
-that can be configured with little effort.
-The example chronologically after the training set makes up the
-test set (3).
-In this way, we train on examples from past build logs and test on
-more recent logs.
-We chose a training set size of 1, as users of our techniques
-should receive reliable results on every build log they analyze.
-As a next step, we configure the chunk retrieval technique with
-the examples from the training set (4) and apply the technique to the
-training set (5), which produces the retrieval output (6).
-Based on this, we collect the following measurements (7):
-\begin{itemize}
-  \item The size of training set (\textbf{RQ2.1}),
-  \item the number of structural categories in the training set
-  (\textbf{RQ2.2})
-  \item the lines of the retrieval output ($\mathit{RetrievedLines}$),
-  and our oracle, the output defined in the test example
+If the chunks are surrounded by the same markings
+within the log we assign them the same structural category.
+
+% We run four techniques on the examples from \emph{LogChunks}.
+
+\noindent
+\textbf{Training and Test Set}
+% TODO Moritz: You said: Add details how key words were extracted.
+% Add example?
+% how the keywords were put in logchunks does not fit here, that is
+% maybe answered 2 paragraphs above already?
+% how KWS uses the keywords is already described in the section
+% introducing the technique => I would scrap everything but the first
+% sentence directly above here :)
+
+% TODO Moritz: You said: Add more details.
+% How was the split in numbers?
+% this is described in the following paragraph, should we merge them
+% (bc there are also no sub-RQs now) or is it close enough? :)
+For each repository in \emph{LogChunks}, we split the examples
+chronologically into training and test set.
+Therefore, we train on
+examples from past build logs and test on more recent build logs.
+
+\noindent % TODO: adapt if we change the research questions
+\textbf{RQ 2.1: Size of Training and Test Set}
+We evaluate the techniques with different training set
+sizes, to analyze how many examples the chunk retrieval techniques need to
+perform best.
+We train each technique with one to five examples from each of
+the repositories within \emph{LogChunks}.
+The size of the test set is one.
+
+\noindent
+\textbf{RQ 2.2: Recording Structural Categories}
+We record the structural categories
+of the examples in the training and test sets, to determine how
+structurally similar the examples for the chunk
+retrieval techniques need to be.
+
+\noindent
+\textbf{RQ2.3: Accuracy Metrics}
+we save the output lines of the chunk retrieval run on the input
+of the test example ($\mathit{RetrievedLines}$), to measure the
+accuracy of the retrieved chunks
+As oracle in our evaluation, we save the
+desired lines from the output of the test example
 ($\mathit{DesiredLines}$).
-  From these we calculate accuracy metrics (\textbf{RQ2.1}).
-\end{itemize}
-
-\textbf{Accuracy Metrics}
-We calculate a number of accuracy metrics to measure how well
-the chunk retrieval techniques perform in our evaluation:
+
+We calculate and define a number of metrics for the context of our
+evaluation.
 
@@
 	% the same information so if someone asks we can defend I think
-
 	\item $\mbox{Precision} = \dfrac{|\mathit{True\
@@
 	desired lines were retrieved.
-
 	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
@@
 	measures such as accuracy because for a
-	``needle-in-the-haystack'' scenario, we want to avoid bloating
+	``needle-in-the-haystack'' scenario, we do not want to bloat
 	our results by correctly not finding lots of irrelevant log
 	lines.
-
 	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$ \vspace{0.05cm}\\
+	\mathit{Recall} = 1, \mathit{false\ otherwise}$  \vspace{0.2cm} \\
 	We define a successful retrieval as one where all desired
@@
 \end{itemize}
-
-This concludes one execution within our evaluation.
-We conduct one run for each of the four chunk retrieval techniques,
-for each of the eighty repositories in \emph{LogChunks} (8)
-and for each of the five training set sizes (2).
-In total we perform 1600 runs, 400 for each of the chunk retrieval
-techniques PBE, CTS, KWS and RLR.
-
-Our implementation of the techniques, as well as our evaluation
-harness and the code we used to process our results is offered
-for inspection and reproduction in our replication package
-~\cite{brandt2020chunk-replication}.
 

### 2020-04-17 tse-paper/content.tex
Formatting

--- 2020-04-17 tse-paper/content.tex
@@
 
-Continuous Integration (CI) has become a common practice in software
-engineering~\cite{hilton2016usage}.
-Many software projects use
-CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
-bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
-developer productivity~\cite{miller2008hundred,hilton2016usage} and
-communication~\cite{downs2012ambient}.
-CI builds produce logs which
-report results of various sub-steps within the build.
-These build logs
-contain a lot of valuable information for developers and researchers---for
-example, descriptions of compile errors, linter warnings or failed
-tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.
-
-CI builds produce logs which report the results of the steps within
-the build.
-The information stored in build logs can and has
-already been used for a variety of applications.
-One prominent dataset
-in the space, TravisTorrent, was featured as the MSR Data Challenge
-2017~\cite{msr17challenge}.
-To date, scientist and practitioners alike
-have used it and other, proprietary datasets to understand and
-cateogrize Continuous Integration build
-failures~\cite{islam2017insights}, to do research on testing
-practices~\cite{orellana2017differences}, to train classifiers to
-predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive},
-and to investigate static analysis tools in CI
+Within the past two decades, Continuous Integration (CI) has become a
+ubiquitous best practice to streamline the build process of software
+projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}.
+Build
+logs are a textual by-product that automatic software build processes
+create.
+As a ``treasure trove'' of information, they contain results
+not only of the elemntary steps to ``make'' a project---such as
+retrieving and resolving dependencies, compiling, and testing the
+software---but also about anciliary quality assurance steps such as
+automated, static analysis tools.
+
+When a build or one of its sub steps fails, developers typically
+scavenge the log for the source of the error.
+This manual activity is
+tedious and prone to error~\cite{santolucito2018statically}.
+As a
+single build log can be over 50 megabytes large~\cite{beller2017oops},
+it finding a piece of information in it is akin to searching for a
+needle in a haystack.
+In addition, due to their information richness,
+build logs enable a plethora of other applications: with the help of
+build logs, we can better understand and cateogrize Continuous
+Integration failures and compile
+errors~\cite{islam2017insights,seo2014programmers}, differentiate
+testing practices~\cite{orellana2017differences,vassallo2017a-tale},
+train classifiers to predict the build outcome and
+duration~\cite{ni2017cost,bisong2017built,machalica2019predictive}, or
+investigate static analysis tools in CI
 builds~\cite{zampetti2017open}.
-Therefore, being able to efficiently
-and correctly extract information from build logs is paramount to the
-future of a variety of fields depending on it.
-
-However, build logs can be verbose and large---sometimes in excess of
-50 MB of ASCII text~\cite{beller2017oops}---making them inadequate
-for direct human consumption.
-Therefore, to support developers and
-researchers in efficiently making use of the information within build
-logs, we must at least semi-automatically retrieve the chunks of the
-log that describe the targeted information.
-
-There are different techniques to retrieve information chunks from CI
-build logs.
-Beller et al.\ use a rule-based system of regular
-expressions to analyze logs from Travis CI~\cite{beller2017oops}.
-Such regular expressions are developed by looking at exemplary build
-logs.
-Vassallo et al.\ wrote a custom parser to gather information
-for build repair hints~\cite{vassallo2018un-break}.
-Recently, Amar et
-al.\ reduced the number of lines for a developer to inspect by
-creating a diff between logs from failed and successful
-builds~\cite{amar2019mining}.
-
-These approaches have various strengths and weaknesses: Regular
-expressions are exact, but tedious and error-prone to
-maintain~\cite{michael2019regexes}.
-Custom parsers are powerful
-though fragile in light of changes in the log structure.
-Diffing
-between failed and successful logs can reduce the information to be
-processed, but is at best semi-automatic~\cite{amar2019mining}.
-
-% TODO: 4 sentence description of the steps in graphic?
-\Cref{fig:overview} gives an overview of our research steps.
-We conducted a systematic mapping study,
-to gain an impression on how researchers are using information from
-build logs within their research or to support
-developers.
-% We implemented three promising techniques that retrieve
-% chunks of text from build logs and can be adapted to
-% a specific project and use case by giving examples of build logs and
-% correpsonding chunks.
-% We evaluated the
-Our goal was to clarify the state-of-research on build log
-analysis (\textbf{RQ1}).
-
-The outcomes of our study shows that there are various attempts to
-retrieve specific information from buildlogs.
-The resulting implementations are rarely available and therefore rarely
-reused.
-Because of the high development overhead
-of the custom parsers, many implementations are limited to small number
-of supported build tools.
-
-\begin{figure*}[htb]
-	\centering
-	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
-	clip]{img/overview.pdf}
-	\caption{Our Research Workflow.}
-	\label{fig:overview}
-\end{figure*}
-
-To address this, we implement three promising techniques for build
-log analysis.
-They retrieve specific chunks of targeted information and are trained
-with examples provided by the user.
-We conduct an empirical study on the \emph{LogChunks} data
-set~\cite{brandt2020logchunks} to
-gauge the performance of these chunk retrieval techniques and characterize
-when one of the techniques should be preferred over other alternatives
-(\textbf{RQ2}).
-
-\begin{simplebox}[minipage boxed title*=-5cm]{Research Questions}
+Manual analysis of build logs does not
+scale to the number of build logs and amount of information that such
+sophisticated applications require.
+Therefore, being able to
+automatically extract pieces of information from build logs
+is not only paramount to such applications, but can also help
+developers debug a broken build.
+
+However, despite its paramount role, the process of how to analyze
+build logs has so far received little attention, bringing us to our
+first research question:
+\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}
+
 \begin{itemize}
-  \item[\textbf{RQ1:}] What is the state-of-research on build
+  \item[\textbf{RQ1:}] What are the state-of-the-art techniques on build
   log analysis?
-  \item[\textbf{RQ2:}] When are PBE, CTS or KWS suited to
-  retrieve chunks from build logs?
  \end{itemize}
@@
 
-% also moved down to where mentioned in detail
-% left copy here for convenience
-
-% \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
-% {\textbf{RQ1:} What is the state-of-research on build
-% log analysis?}
-% \begin{itemize}
-%   \item[\textbf{RQ1.1:}] Which information is targeted?
-%   \item[\textbf{RQ1.2:}] Which techniques are used?
-%   \item[\textbf{RQ1.3:}] Which build logs are analyzed?
-% \end{itemize}
-% \end{simplebox}
-
-% \begin{simplebox}[minipage boxed title*=-2.5cm,
-% attach boxed title to top center={yshift=-6mm}]
-% {\textbf{RQ2:} When are PBE{,} CTS or KWS suited to
-% retrieve chunks from build logs?}
-% \begin{itemize}
-%   \item[\textbf{RQ2.1:}] How many examples does a technique need to
-%   perform best?
-%   \item[\textbf{RQ2.2:}] How structurally similar do the examples
-%   need for a technique to be applicable?
-%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
-% \end{itemize}
-% \end{simplebox}
-
-% % At the moment there is only anecdotal evidence on the performance
-% of these
-% % techniques and on when a technique should be preferred over other
-% alternatives.
-% % Developers and researches currently have little support when choosing
-% which
-% % technique to use for a task.
-
-% % The goal of this article is to investigate different chunk retrieval
-% techniques
-% % for build logs and describe under which circumstances certain
-% techniques
-% can be
-% % recommended over others.
-% % We aim to characterize different chunk retrieval techniques.
-% % For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which
-% criteria
-% % influence the suitability of a chunk retrieval technique for CI
-% build logs.
-
-We implement and evaluate three chunk retrieval techniques:
+In this article, as first step (\Cref{fig:overview}), we show that
+less than half of the 61 works which rely on build log analysis
+describe how they performed it, and even fewer did so in detail, let
+alone made their implementation available.
+Even so, the literature
+survey finds three main strategies to extract information chunks from
+build logs: Using 1) a set of manually curated regular expressions,
+similar to TravisTorrent~\cite{beller2017oops}, 2) a list of keywords
+to identify regions of interest in the build log, and 3)
+% TODO (Caro): Provide better description
+doing text-similarity.
+
+Even though these three approaches to retrieve information chunks from
+build logs have different strengths and weaknesses, the literature
+survey shows that their use is often arbitrary and that there is
+usually no discussion on why to use one over the other.
+Developers and
+researchers not only seem to lack awareness of which techniques exist
+(RQ1), but also guidelines on when to employ which.
+As a consequence,
+in RQ2 we ask:
+
+\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}
+\begin{itemize}
+  \item[\textbf{RQ2:}] What are the comparative strengths and weaknesses
+  of the top-3 build log anaylsis techniques?
+\end{itemize}
+\end{simplebox}
+
+To answer this question, we implement three automatic techniques for
+build log analysis based on the three stratgies at large (step 2):
+
 \begin{itemize}
@@
 
-Following the results from our comparison study,
-recommend PBE for use cases where the desired information is always
-represented in the same structural way and high confidence in precision
-and recall of the chunk retrieval is required.
-Results produced by PBE are suited for automatic on-ward processing.
-CTS is well suited when the representation of the desired information
-varies
+In step 3, we conduct an empirical study to gauge the performance of
+these chunk retrieval techniques under a variety of conditions in
+real-world projects.
+Finally, we develop guidelines (step 4) on when
+one of the techniques might be perferrential to its alternatives.
+
+\begin{figure*}[htb]
+	\centering
+	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
+	clip]{img/overview.pdf}
+	\caption{Research Design.}
+	\label{fig:overview}
+\end{figure*}
+
+We recommend PBE for use cases where the desired information is always
+represented in the same structural way and high confidence in
+precision and recall of the chunk retrieval is required.
+Results
+produced by PBE are suited for automatic on-ward processing.
+CTS is
+well suited when the representation of the desired information varies
 slightly and the output of the chunk retrieval is further processed by
 a human.
-In cases where the textual representation of the desired information in
-the log
-is unpredictable or varies greatly, KWS seems to be the best choice.
-However,
-its low precision---it extracts a context of multiple lines around a
-finding---makes it generally unsuited for automatic on-ward processing and
-instead requires a human to further inspect and interpret the output
-chunk.
+In cases where the textual representation of the desired
+information in the log is unpredictable or varies greatly, KWS seems
+to be the best choice.
+However, its low precision---it extracts a
+context of multiple lines around a finding---makes it generally
+unsuited for automatic on-ward processing and instead requires a human
+to further inspect and interpret the output chunk.
 

### 2020-04-17 tse-paper/paper.tex
correct first half of lit survey
add corrections ttv - conclusion

@@
 \newcommand{\smallish}{\fontsize{6.15pt}{20pt}\selectfont}
+\newcommand{\tinyish}{\fontsize{6.5pt}{6.15pt}\selectfont}
 
@@
 % Do not put math or special symbols in the title.
-\title{How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques}
+\title{How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques}
 %
@@
 \author{Carolin~Brandt,~\IEEEmembership{Member,~IEEE,}
-        Moritz~Beller,~\IEEEmembership{Fellow,~OSA,}
-        and~Annibale~Panichella,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
-of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-GA, 30332.\protect\\
-% note need leading \protect in front of \\ to get a newline within \thanks as
-% \\ is fragile and will error, could use \hfil\break instead.
-E-mail: see http://www.michaelshell.org/contact.html
-\IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
-\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
+        Moritz~Beller,~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
+% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
+% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
+% GA, 30332.\protect\\
+% % note need leading \protect in front of \\ to get a newline within \thanks as
+% % \\ is fragile and will error, could use \hfil\break instead.
+% E-mail: see http://www.michaelshell.org/contact.html
+% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
+\thanks{Manuscript received May 1, 2020; revised August 26, 2015.}}
 
@@
 \begin{IEEEkeywords}
-Computer Society, IEEE, IEEEtran, journal, continuous integration, build log analysis, chunk retrieval.
+Computer Society, IEEE, IEEEtran, Journal, Continuous Integration, 
+Build Log Analysis, Chunk Retrieval.
 \end{IEEEkeywords}}
@@
 % use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-  \section*{Acknowledgment}
-\fi
+% \ifCLASSOPTIONcompsoc
+%   % The Computer Society usually uses the plural form
+%   \section*{Acknowledgments}
+% \else
+%   % regular IEEE prefers the singular form
+%   \section*{Acknowledgment}
+% \fi
 
-The authors would like to thank...
+% The authors would like to thank...
 
@@
 
-\begin{IEEEbiography}{Michael Shell}
+\begin{IEEEbiography}{Carolin E. Brandt}
+Biography text here.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}{Moritz Beller}
 Biography text here.
@@
 % if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
+% \begin{IEEEbiographynophoto}{John Doe}
+% Biography text here.
+% \end{IEEEbiographynophoto}
 
@@
 
-\begin{IEEEbiographynophoto}{Jane Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
+% \begin{IEEEbiographynophoto}{Jane Doe}
+% Biography text here.
+% \end{IEEEbiographynophoto}
 

### 2020-04-20 tse-paper/abstract.tex
first round of edits on new introduction

@@
 the manually
-labeled \emph{LogChunks} data set, which comprises 797 build logs in
-29 languages.
+labeled \emph{LogChunks} data set, which comprises 797 build logs 
+from a wide range of build environments.
 Our findings show that none of the three techniques in general outperforms

### 2020-04-20 tse-paper/content.tex
Move figure
first round of edits on new introduction

@@
 As a ``treasure trove'' of information, they contain results
-not only of the elemntary steps to ``make'' a project---such as
+not only of the elementary steps to ``make'' a project---such as
 retrieving and resolving dependencies, compiling, and testing the
-software---but also about anciliary quality assurance steps such as
-automated, static analysis tools.
-
-When a build or one of its sub steps fails, developers typically
+software---but also about ancillary quality assurance steps such as
+automated static analysis tools.
+
+When a build or one of its steps fails, developers typically
 scavenge the log for the source of the error.
@@
 single build log can be over 50 megabytes large~\cite{beller2017oops},
-it finding a piece of information in it is akin to searching for a
+finding a piece of information in it is akin to searching for a
 needle in a haystack.
@@
 build logs enable a plethora of other applications: with the help of
-build logs, we can better understand and cateogrize Continuous
-Integration failures and compile
+build logs, we can better understand and categorize CI
+failures and compile
 errors~\cite{islam2017insights,seo2014programmers}, differentiate
@@
 automatically extract pieces of information from build logs
-is not only paramount to such applications, but can also help
+is not only paramount to applications such as the above mentioned
+ones, but can also help
 developers debug a broken build.
 
-However, despite its paramount role, the process of how to analyze
+\begin{figure*}[htb]
+	\centering
+	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
+	clip]{img/overview.pdf}
+	\caption{Research Design.}
+	\label{fig:overview}
+\end{figure*}
+
+Despite its paramount role, the process of analyzing
 build logs has so far received little attention, bringing us to our
 first research question:
-\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}
-
-\begin{itemize}
-  \item[\textbf{RQ1:}] What are the state-of-the-art techniques on build
-  log analysis?
- \end{itemize}
+\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
+1}}
+What are the state-of-the-research techniques on build log analysis?
 \end{simplebox}
@@
 less than half of the 61 works which rely on build log analysis
-describe how they performed it, and even fewer did so in detail, let
-alone made their implementation available.
-Even so, the literature
-survey finds three main strategies to extract information chunks from
-build logs: Using 1) a set of manually curated regular expressions,
-similar to TravisTorrent~\cite{beller2017oops}, 2) a list of keywords
-to identify regions of interest in the build log, and 3)
-% TODO (Caro): Provide better description
-doing text-similarity.
+describe how they performed it.
+Even fewer did so in detail or
+made their implementation available.
+Through the literature
+survey we identify three prevalent strategies to
+analyze build logs: Using 1) a set of
+manually curated regular expressions,
+similar to TravisTorrent~\cite{beller2017oops},
+2) information
+retrieval techniques,
+and 3) a list of search keywords
+to identify regions of interest in the build log.
 
@@
 
-\begin{simplebox}[minipage boxed title*=-5cm]{Research Question}
-\begin{itemize}
-  \item[\textbf{RQ2:}] What are the comparative strengths and weaknesses
-  of the top-3 build log anaylsis techniques?
-\end{itemize}
+\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
+2}}
+What are the comparative strengths and weaknesses
+of promising build log analysis techniques?
 \end{simplebox}
@@
 To answer this question, we implement three automatic techniques for
-build log analysis based on the three stratgies at large (step 2):
+build log analysis based on the identified strategies (step 2):
 
@@
 In step 3, we conduct an empirical study to gauge the performance of
-these chunk retrieval techniques under a variety of conditions in
-real-world projects.
+these chunk retrieval techniques in
+real-world projects under a variety of conditions.
+Our study is based on the \emph{LogChunks} data
+set~\cite{brandt2020logchunks} which encompasses build logs from
+80 popular open source projects and a broad range of
+build environments.
 Finally, we develop guidelines (step 4) on when
-one of the techniques might be perferrential to its alternatives.
-
-\begin{figure*}[htb]
-	\centering
-	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
-	clip]{img/overview.pdf}
-	\caption{Research Design.}
-	\label{fig:overview}
-\end{figure*}
+one of the techniques might be preferential to its alternatives.
 
@@
 
-% % \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited
-% to retrieve information from continuous integration build logs.
-% % \textbf{RQ2} is refined into sub-questions along with the criteria
-% resulting from \textbf{RQ1} and compares their instantiations for the
-% three techniques:
-% % how many training examples a technique needs to perform best
-% (\textbf{RQ2.1}), how structurally diverse the examples can
-% be (\textbf{RQ2.2}) and how accurate the retrieved output is
-% (\textbf{RQ2.3}).
-% % To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set,
-% which encompasses about 800 log files from 80 repositories.
-% % Each log is labeled with the log part describing the reason a build
-% failed, keywords to search for this log part and a categorization of
-% the labeled log part according to its structural representation within
-% the log.
-
-% Our study of the three techniques on \emph{LogChunks} shows that
-% \begin{itemize}
-%   \item PBE yields very accurate results when trained with two examples
-%   from a
-%   single structural category.
-%   \item CTS shows the best average precision, though precision and
-% recall
-%   of a
-%   retrieval is hard to determine from the given result.
-%   A small increase in the number of training examples has no noticeable
-%   influence.
-
-%   Fewer structural categories improve precision and recall of the
-%   retrieval.
-%   \item KWS has the highest recall of all techniques, however much
-%   lower precision.
-%   It is the technique with the best recall when multiple structural
-%   categories
-%   are present in the training examples.
-% \end{itemize}
-
-% % \noindent
-% % \textbf{Our work contributes:}
-% % \begin{itemize}
-% %   \item A tool with three prototypical implementations of chunk
-% retrieval techniques:
-% %	  \begin{itemize}
-% %	    \item program synthesis from examples using the Microsoft
-% PROSE library (PBE),
-% %	    \item a common information retrieval approach using text
-% similarity (CTS), and
-% %	    \item a keyword search approach (KWS).
-% %	  \end{itemize}
-% %   \item Recommendations for the configuration of each of the
-% investigated chunk retrieval techniques.
-% %   \item Guidelines on choosing a suitable chunk retrieval technique.
-% % \end{itemize}
+To enable retracing of our research, we provide a detailed replication
+package~\cite{brandt2020chunk-replication}.
 
@@
 \label{sec:survey}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Literature selection process, following
-	\cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
 
@@
 
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
+	\caption{Literature selection process, following
+	\cite{petersen2015guidelines}.}
+	\label{fig:lit-survey}
+\end{figure}
+
 \lstset{
@@
 }
-\begin{figure*}[htbp]
+\begin{figure}[b]
   \centering
@@
   \label{lst:system-log}
-\end{figure*}
+\end{figure}
 
@@
 \end{itemize}
-To objectifiy our data extraction we created a template of the targeted
+To objectify our data extraction we created a template of the targeted
 factors and performed a pilot, as recommended by Petersen et
@@
 \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
-{\textbf{RQ1:} What is the state-of-research on build
-log analysis?}
-\begin{itemize}
+{\textbf{RQ1:} What are the state-of-the-research
+techniques on build log analysis?}
+\begin{itemize}[leftmargin=2cm]
   \item[\textbf{RQ1.1:}] Which information is targeted?
@@
 \addtolength{\tabcolsep}{5pt}
-% TODO one source might contribute multiple times to 'other'
 
@@
 \caption{Multi-label categorization of the 61 relevant articles.}
-\end{figure}
-
-\begin{figure}[tbhp]
-		\centering
-		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
-		1.5cm 0.5cm},
-		clip]{img/lit-sur/log_producer_annotated.pdf}
-		\caption{Frequency of supported log producers.}
-		\label{fig:litsur:log_producer}
 \end{figure}
@@
 25\% of the articles claimed their implementation is available,
-however we
+however, we
 saw very low reuse of build log analysis tools within our survey.
@@
 Ghaleb et al.~\cite{ghaleb2019studying} and several other studies.
+
+\begin{figure}[tbhp]
+		\centering
+		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
+		1.5cm 0.5cm},
+		clip]{img/lit-sur/log_producer_annotated.pdf}
+		\caption{Frequency of supported log producers.}
+		\label{fig:litsur:log_producer}
+\end{figure}
 
@@
 \label{sec:techniques}
-This section introduces key concepts of the three chunk retrieval
-techniques we study in this article, namely program synthesis by
-example (PBE), common text similarity (CTS), and keyword search (KWS).
-In addition we present our comparison baseline of random line
-retrieval (RLR), illustrate the techniques on a concrete example
-of log chunks and sketch out implementation.
-
-\Cref{tab:ctr} shows a comparison of the presented techniques.
-
-\begin{table*}[htbp]
+
+\begin{table*}[htb]
 \centering
@@
 \end{table*}
+
+This section introduces key concepts of the three chunk retrieval
+techniques we study in this article, namely program synthesis by
+example (PBE), common text similarity (CTS), and keyword search (KWS).
+In addition we present our comparison baseline of random line
+retrieval (RLR), illustrate the techniques on a concrete example
+of log chunks and sketch out implementation.
+
+\Cref{tab:ctr} shows a comparison of the presented techniques.
 
@@
 of a program learned from the examples in \Cref{lst:chunk-example}.
-% TODO Caro: check that these figures are latest inserted here
 
@@
 \subsection{Chunk Retrieval Example}
-\label{seC:crt-example}
-
-\begin{figure*}[!htbp]
-  \centering
-\begin{subfigure}[!htbp]{\columnwidth}
+\label{sec:crt-example}
+
+\begin{figure}[tbp]
+  \centering
+\begin{subfigure}[tbp]{\columnwidth}
   \begin{lstlisting}[breaklines=true,frame=tlr]
@@
 \end{subfigure}\hspace{\fill}
-\begin{subfigure}[!htbp]{\columnwidth}
+\begin{subfigure}[tbp]{\columnwidth}
   \centering
@@
   \label{lst:chunk-example}
-\end{figure*}
+\end{figure}
 
@@
   EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[!htbp]
+\begin{figure}[tbp]
   \centering
@@
 }
-\begin{figure}[!htbp]
+\begin{figure}[tbp]
   \centering
@@
 
-\begin{simplebox}[minipage boxed title*=-2.5cm,
+\begin{simplebox}[minipage boxed title*=-1.5cm,
 attach boxed title to top center={yshift=-6mm}]
-{\textbf{RQ2:} When are PBE{,} CTS or KWS suited to
-retrieve chunks from build logs?}
-\begin{itemize}
+{\textbf{RQ2:} What are the comparative strengths and weaknesses
+of promising build log analysis techniques?}
+\begin{itemize}[leftmargin=1.2cm]
   \item[\textbf{RQ2.1:}] How many examples does a technique need to
@@
 	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}$ \vspace{0.05cm}\\
+	\mathit{Recall} = 1, \mathit{false\ otherwise}\vspace{0.1cm}$
+
 	We define a successful retrieval as one where all desired
@@
 \end{itemize}
-
 This concludes one execution within our evaluation.
@@
 % In fact, unless they
-% were in some sense redudant, adding training examples above that even
+% were in some sense redundant, adding training examples above that even
 % hindered the applicability of PBE.
@@
 The recommendations could therefore be
-influenced by idiosyncrazies of our specific implementation of the
+influenced by idiosyncrasies of our specific implementation of the
 chunk retrieval techniques as well as the \emph{LogChunks}
@@
 \textbf{Implementation}
-% TODO we need to say something about why we think that these
-% limtiations do not actually harm our results
 Our results depend on the implementation of the investigated chunk
@@
 The
-idiosyncrazies of this framework influence our PBE results.
+idiosyncrasies of this framework influence our PBE results.
 Other
@@
 following improvements:
-\begin{itemize}[leftmargin=0.4cm] \itemsep1em
+\begin{itemize}[leftmargin=0.4cm]
   \item \textbf{Custom Ranking and Tokens for PBE} The program

### 2020-04-20 tse-paper/paper.tex
first round of edits on new introduction

@@
     boxrule=1pt,
-    left=8mm,
-    right=8mm,
+    left=5mm,
+    right=5mm,
     bottom=2mm,
@@
 
-\author{Carolin~Brandt,~\IEEEmembership{Member,~IEEE,}
-        Moritz~Beller,~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
+\author{Carolin~Brandt,%~\IEEEmembership{Member,~IEEE,}
+        Moritz~Beller,%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
 % \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department

### 2020-04-21 tse-paper/content.tex
grammarly

@@
 1}}
-What are the state-of-the-research techniques on build log analysis?
+What are the state-of-the-research techniques for build log analysis?
 \end{simplebox}
 
-In this article, as first step (\Cref{fig:overview}), we show that
+In this article, as the first step (\Cref{fig:overview}), we show that
 less than half of the 61 works which rely on build log analysis
@@
 set~\cite{brandt2020logchunks} which encompasses build logs from
-80 popular open source projects and a broad range of
+80 popular open-source projects and a broad range of
 build environments.
@@
 
-To enable retracing of our research, we provide a detailed replication
+To enable the retracing of our research, we provide a detailed replication
 package~\cite{brandt2020chunk-replication}.
@@
 research efforts on build log analysis.
-However,the processing of build logs was often
+However, the processing of build logs was often
 a side-part of the article.
@@
 files produced during runtime.
-A main difference between build logs
+The main difference between build logs
 and system logs is that system logs are fundamentally structured
@@
 returns more than 2.2 million results (2020-03-15).
-We refined our search criterions to exclude obvious
+We refined our search criteria to exclude obvious
 non-related works.
@@
 sampling for related work.
-If one one of the articles referenced a new article in the context
+If one of the articles referenced a new article in the context
 of build log analysis we added the new to our literature set.
@@
 Subsequently, we performed a second, finer filter phase by downloading the
-full articles, reading their abstracts, and searching the full text
+full articles, reading their abstracts and searching the full text
 for the occurrence of ``log''.
@@
 This excluded 15 articles from our study.
-For several cases, multiple articles were extensions of others.
+In several cases, multiple articles were extensions of others.
 Of these, we only considered the earliest article which reported on
@@
 {\textbf{RQ1:} What are the state-of-the-research
-techniques on build log analysis?}
+techniques for build log analysis?}
 \begin{itemize}[leftmargin=2cm]
@@
 36\% of the articles classified the build logs into categories.
-For instance distinguishing failures caused by developers from
+For instance, distinguishing failures caused by developers from
 failures caused
@@
 search strings that identify their targeted categories.
-Based on the search strings they create a script which automatically
+Based on the search strings they create a script that automatically
 classifies the remaining logs.
@@
 however, we
-saw very low reuse of build log analysis tools within our survey.
+saw a very low reuse of build log analysis tools within our survey.
 Five articles employed the tools used to create
@@
 several described they are covering multiple source build tools.
-The majority of articles (42\%) targeted logs from a source which was not
+The majority of articles (42\%) targeted logs from a source that was not
 targeted by any second article.
@@
 CI~\cite{travisci2019webpage},
-which was used in 38\% of cases.
+which was used in 38\% cases.
 18\% of the articles processed logs from TravisTorrent and 8\% included
@@
 enable further research.
-However we found no clear reuse of build log data sets with the
+However, we found no clear reuse of build log data sets with the
 exception of TravisTorrent~\cite{beller2017travistorrent}, which was
@@
 article each (B).
-From this we follow that, while custom parsers are beneficial for the
+From this, we follow that, while custom parsers are beneficial for the
 small group of environments targeted by many (A), all and especially
@@
 
-For this reason, we are focussing on techniques that run automatic
+For this reason, we are focussing on techniques that run automatically
 after being configured through examples or keywords.
@@
 a substring, that describes a specific information, from a build log.
-Generally these can also be used to classify build logs and therefore
+Generally, these can also be used to classify build logs and therefore
 cover the great majority of the type of log analysis we saw within
@@
 Our evaluation of the three chunk retrieval techniques is done on the
-\emph{LogChunks} data set, because it encompasses a broad range of
+\emph{LogChunks} data set because it encompasses a broad range of
 build environments which enables us to measure the generic
@@
 example (PBE), common text similarity (CTS), and keyword search (KWS).
-In addition we present our comparison baseline of random line
+In addition, we present our comparison baseline of random line
 retrieval (RLR), illustrate the techniques on a concrete example
@@
 \emph{Running a
-chunk retrieval technique} means to execute a fully configured
+chunk retrieval technique} means executing a fully configured
 technique to consumes as input a build log in plain text format and to
@@
 \subsection{Program Synthesis by Example (PBE)}
-\label{sec:expl-pbe}
 The concept of \emph{Programming by Example} aims to capture the
@@
 \subsection{Common Text Similarity (CTS)}
-\label{sec:expl-ts}
 Text Similarity approaches are widely used to filter unstructured
@@
 \subsubsection{Configuration}
-To configure chunk retrieval though text similarity we chose to use
+To configure chunk retrieval through text similarity we chose to use
 the same concept of examples as for PBE
@@
 \subsection{Keyword Search (KWS)}
-\label{sec:expl-skws}
 When developers scavenge for a specific piece of information within a
@@
 \subsection{Tool Implementation}
-For our comparison study we implemented each of the chunk retrieval
+For our comparison study, we implemented each of the chunk retrieval
 techniques and a unifying interface.
@@
 They can be found in our replication
-package~\cite{brandt2020chunk-replication} together which have
+package~\cite{brandt2020chunk-replication} together
+with Docker images which have
 our techniques installed and ready to use.
@@
 study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
-In particular we are interested in how many examples a technique
+In particular, we are interested in how many examples a technique
 should be trained with (\textbf{RQ2.1}),
@@
 
-In the following we present the data set we created for this study,
+In the following, we present the data set we created for this study,
 our study process (presented in \Cref{fig:study}) and the metrics
@@
 \subsection{LogChunks}
-For this study we created the previously published data set
+For this study, we created the previously published data set
 \emph{LogChunks}.
@@
 If the chunks were surrounded by the same markings
-within the log we assigned them the \emph{same structural category},
+within the log, we assigned them the \emph{same structural category},
 as described in \Cref{sec:crt-example}.
@@
 confidently configure a technique.
-The training set is so small, because the examples have to be
+The training set is so small because the examples have to be
 manually created by a user.
@@
 Based on this, we collect the following measurements (7):
-the size of training set (\textbf{RQ2.1}),
+the size of the training set (\textbf{RQ2.1}),
 the number of structural categories in the training
@@
 technique.
-Afterwards we compare the three techniques with each other and RLR as
+Afterwards, we compare the three techniques with each other and RLR as
 baseline.
@@
 The size of the training set has no visible impact on either.
-An larger number of structural categories within the training and
+A larger number of structural categories within the training and
 test sets decreased the precision of RLR from 7\% to 0\%, the recall
@@
 
-For the interpretation of our study results we look at each chunk
+For the interpretation of our study results, we look at each chunk
 retrieval technique separately and give recommendations for
@@
 This
-makes KWS a good technique if there is little prior knowledge on how
+makes KWS a good technique if there is little prior knowledge of how
 the targeted log chunk is represented in the build log.
@@
 We also recommend CTS when the log chunks are
-from one structural category, when the user does not require a high
+from one structural category, when the user does not require high
 confidence in the precision or recall of the outcome and when one
@@
 When the representations are from one structural category and the user
-wishes a high confidence in the correctness of the output or prefers
+wishes high confidence in the correctness of the output or prefers
 no output over output with low recall, we recommend PBE\@.
@@
 KWS\@.
-Other than initial setup and training time, there should be no
+Other than initial setup and training time, there is no
 downside to this approach if it is implemented in a transparent way to
@@
   One could extend these
-  with tokens found in build logs, such as ``-'',``='',``ERROR''
+  with tokens found in build logs, such as ``-'',
+	``='', ``ERROR''
   or ``[OK''.

### 2020-04-22 tse-paper/abstract.tex
First feedback and review integrated

--- 2020-04-09 tse-paper/abstract.tex
@@
-Build logs are a textual by-product that automatic software build processes
+Build logs are the textual by-products that automatic software build processes
 create, often as part of their Continuous Integration (CI)
@@
 Manually
-extracting the important chunks of information, though, is akin to
+extracting the important chunks of information in a build log, though, is akin to
 finding a needle in a haystack.
-Recently, researchers and practitioners have started attempts to partly
+Recently, practitioners and researchers have started attempts to partly
 automate
-this time-consuming activity, with the proposition to not only ease
-developers' and researchers task of finding this needle but also to enable a novel class of
-on-ward processing applications.
-In this paper, we give the first systematic overview of the emerging field of build log analysis.
+this time-consuming activity, to not only ease
+developers' task of finding this needle but also to enable a novel class of
+automated on-ward processing applications.
+In this paper, we give a systematic overview of the emerging field of build log analysis.
 In a large-scale literature mapping study, we first survey and categorize the existing methods to
-extract information from build logs.
-In the second part of the paper, we then develop prototypical implementations of the three most promising
-techniques, namely program synthesis
+extract information chunks from build logs.
+In the second part of the paper, we develop prototypical implementations of the three most promising
+techniques we found, namely program synthesis
 by example, textual similarity, and keyword search.
 Finally, we evaluate the techniques in an empirical study on
-the manually
-labeled \emph{LogChunks} data set, which comprises 797 build logs in
-29 languages.
+the \emph{LogChunks} data set, which comprises 797 build logs 
+from a wide range of different projects and programming languages.
 Our findings show that none of the three techniques in general outperforms

### 2020-04-22 tse-paper/content.tex
First feedback and review integrated

@@
 projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}.
-Build
-logs are a textual by-product that automatic software build processes
-create.
-As a ``treasure trove'' of information, they contain results
-not only of the elementary steps to ``make'' a project---such as
-retrieving and resolving dependencies, compiling, and testing the
-software---but also about ancillary quality assurance steps such as
-automated static analysis tools.
+Build logs are a textual by-product that automatic software build
+processes create.  As a treasure trove of information~\cite{meyer},
+build logs contain trace outputs of not only the elementary steps to
+``make'' a project---such as retrieving and resolving dependencies and
+compiling---but also about ancillary quality assurance steps---such as
+testing the software and running automated static analysis tools. The
+contents of build logs can be highly variable depending on which tools
+are involved in the build process and how they are
+configured. The format of logs changes as projects and build tools evolve over time. Typically, though, they are at least a semi-structured and
+somewhat stable journal of the commands executed during the build and
+their results.
 
 When a build or one of its steps fails, developers typically
-scavenge the log for the source of the error.
+scavenge the logs for information related to the source of the error.
 This manual activity is
@@
 single build log can be over 50 megabytes large~\cite{beller2017oops},
-finding a piece of information in it is akin to searching for a
+finding the small chunk of information in it which is linked to the error, is akin to searching for a
 needle in a haystack.
-In addition, due to their information richness,
-build logs enable a plethora of other applications: with the help of
+In addition to helping understand and fix build failures, the information richness of build logs enables a plethora of other applications: with the help of
 build logs, we can better understand and categorize CI
@@
 builds~\cite{zampetti2017open}.
-Manual analysis of build logs does not
+
+However, manual analysis of build logs does not
 scale to the number of build logs and amount of information that such
-sophisticated applications require.
-Therefore, being able to
-automatically extract pieces of information from build logs
-is not only paramount to applications such as the above mentioned
-ones, but can also help
-developers debug a broken build.
+sophisticated applications require. Moreover, being able to
+automatically extract relevant pieces of information from build logs can also help
+developers debug a broken build more quickly without having to browse the entire build log.
 
@@
 
-Despite its paramount role, the process of analyzing
-build logs has so far received little attention, bringing us to our
-first research question:
+Despite its central role for helping developers and the enablement of
+on-ward applications of build logs, the process of how to
+automatically analyze build logs has thus far received little
+attention as a separate research topic, bringing us to our first
+research question:
 \begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
 1}}
-What are the state-of-the-research techniques for build log analysis?
+What are the state-of-the-research techniques to analyze build logs?
 \end{simplebox}
 
-In this article, as the first step (\Cref{fig:overview}), we show that
+To answer this question, we start our investigation by performing an extensive literature study (\Cref{fig:overview}).
+It shows that
 less than half of the 61 works which rely on build log analysis
-describe how they performed it.
-Even fewer did so in detail or
+describe in detail how they performed it, and even fewer
 made their implementation available.
-Through the literature
-survey we identify three prevalent strategies to
+The literature
+survey identifies three prevalent strategies to
 analyze build logs: Using 1) a set of
@@
 retrieval techniques,
+% TODO: Can you shortly explain the technique here?
 and 3) a list of search keywords
@@
 build logs have different strengths and weaknesses, the literature
-survey shows that their use is often arbitrary and that there is
-usually no discussion on why to use one over the other.
-Developers and
-researchers not only seem to lack awareness of which techniques exist
-(RQ1), but also guidelines on when to employ which.
+survey shows that their use often seems arbitrary.
 As a consequence,
@@
 
-To answer this question, we implement three automatic techniques for
-build log analysis based on the identified strategies (step 2):
+To answer this question, in the second step of our study
+(\Cref{fig:overview}), we build and compare three
+implementations that each stand protoypical for one of the idenitied
+strategies to analyze build logs:
 
@@
   \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on user examples of build logs and chunks, PBE
+  Based on manually supplied example pairs of build logs and chunks, PBE automatically
   synthesizes
-  a regular expression matching the given chunks within the build logs.
+  a regular expression extracting the given chunks within the build logs.
   \item \textbf{Common Text Similarity (CTS)}
-  Using the Vector Space Model, CTS selects those lines of a log which are
-  most similar to the lines present in example chunks provided by
-  the user.
+  % TODO what is the vector space model
+  Using the Vector Space Model, CTS selects lines of a log which are
+  most similar to the lines present in manually supplied example chunks.
   \item \textbf{Keyword Search (KWS)}
+  % TODO what is an ad-hoc method?
   Ad-hoc method for finding fitting passages by searching the whole
-  text for
+  text of a build log for
   the occurrence of specific trigger words.
@@
 
-In step 3, we conduct an empirical study to gauge the performance of
+In the third step, we conduct an empirical study to gauge the performance of
 these chunk retrieval techniques in
@@
 Our study is based on the \emph{LogChunks} data
-set~\cite{brandt2020logchunks} which encompasses build logs from
-80 popular open-source projects and a broad range of
-build environments.
-Finally, we develop guidelines (step 4) on when
-one of the techniques might be preferential to its alternatives.
-
+set~\cite{brandt2020logchunks}, which encompasses build logs from
+80 popular open-source projects and a broad range of different
+build tools and programming languages.
+
+Finally, we develop a set of guidelines (step 4) on how to choose a technique given a goal.
 We recommend PBE for use cases where the desired information is always
@@
 CTS is
-well suited when the representation of the desired information varies
+well-suited when the representation of the desired information varies
 slightly and the output of the chunk retrieval is further processed by
@@
 unsuited for automatic on-ward processing and instead requires a human
-to further inspect and interpret the output chunk.
-
-To enable the retracing of our research, we provide a detailed replication
-package~\cite{brandt2020chunk-replication}.
+to further inspect and interpret the output chunk. A hybrid-solution combining the three techniques might be the best allround solution.
+
+In short, this article contributes
+\begin{itemize}
+\item the first systematic study of the emerging field of build log analysis.
+\item three prototypical open-sourced implementations of the most promising chunk retrieval techniques.
+\item a large-scale empirical study comparing the three techniques.
+\item systematic guidelines on when to use which technique.
+\item a detailed replication package~\cite{brandt2020chunk-replication}.
+\end{itemize}
 
@@
 
-The field of analyzing build
-logs is relatively young; We have seen scattered
-research efforts on build log analysis.
-However, the processing of build logs was often
-a side-part of the article.
-To the best of our
-knowledge, there has not been an attempt to systematically overview
-and survey approaches for processing build logs.
-We conducted a systematic mapping study to determine the
-state-of-research on build log analysis following the guidelines
-by Petersen et al.~\cite{petersen2008systematic,petersen2015guidelines}.
-
-In the following section, we explain how build log analysis differs
-from system log analysis.
-Further, we describe how we selected the articles for our literature
-survey and the data extraction from the resulting articles.
-We present our results on how build logs are analyzed in literature
-and discuss the implications of these findings on our research.
+In this section, we survey the emerging field of build log
+analysis. We first start with a differentiation to the related field of general system log analysis. Then, we describe the methodology and results of a systematic mapping study to
+determine the state-of-research on build log analysis following the
+guidelines by Petersen et
+al.~\cite{petersen2008systematic,petersen2015guidelines}. 
+We close by summarizing how build logs are commonly
+analyzed in literature and discuss the implications of these findings.
 
@@
 \label{sec:system-log-analysis}
-A related field of build log analysis is the processing of system log
-files produced during runtime.
-The main difference between build logs
-and system logs is that system logs are fundamentally structured
+A field related to build log analysis is the processing of system log
+files produced during runtime of the system. The first difference here is that build logs are produced during runtime of the build of the system, not the system itself.
+In terms of the contents of the logs, the main difference is that system logs are fundamentally structured
 through events.
@@
 
-The first goal in analyzing system log files is ubiquitously to
+The first goal in analyzing system log files is generally to
 separate constant and variable parts within a log
@@
 messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters.
-The output of a log
-parser is an ordered list of timed events and their corresponding
+identical constant parts and varying parameters. Then, a log parser works on this intermediate representation.
+Its output is an ordered list of timed events and their corresponding
 parameter values~\cite{he2016evaluation}.
-This structured log is then
-the input to various machine learning and data mining processes.
-
-The techniques developed for system log analysis can also be applied
-to build logs.
+This structured log can serve as input to various machine learning and data mining processes.
+
+In principle, one can apply the techniques developed for system log analysis
+to parts of the build logs that have this same structure.
+% TODO this explanation is not understandable. It needs to better embedded in the surrounding text
 One example is comparing execution traces to reference
@@
 relevant lines in build logs.
-However, many of the techniques developed to analyze system logs
+However, almost all of the techniques developed to analyze system logs
 leverage their inherent event structure.
-As build logs lack this structure, we focussed our literature
-survey on articles that as a source of information.
+Build logs generally lack this structure and thus require different bespoke approaches.
 % In this article, we focus on extracting a single specified information
@@
 
+% TODO In general, we should reference petersen2015guidelines a bit
+% more. I.e., following the suggestions by Petersen or something, to
+% show how we followed their protocol. This comment applies to the rest of this section
+
 \subsection{Study Selection}
@@
 process.
-Since the field of build log analysis is so young, we
-surveyed a population of scientific material as broad as possible.
-We did not limit our sources to specific Software Engineering venues, as
-is often done~\cite{petersen2015guidelines}, but survey all sources
+Since the field of build log analysis is relatively young, we
+surveyed as broad a population of scientific material as possible.
+We did not limit our sources to specific Software Engineering venues~\cite{petersen2015guidelines}, but survey all sources
 monitored by Google Scholar, including Bachelor's and Master's
@@
 We use Google Scholar as opposed to Scopus or
-other databases, as it is the search engine for academic articles with
+other databases because it is the search engine for academic articles with
 the broadest and most current index, including preprints.
 
-Our Google Scholar search for variations of ``build log''
-returns more than 2.2 million results (2020-03-15).
-We refined our search criteria to exclude obvious
-non-related works.
-For example, we decided to exclude systems
+An initial Google Scholar search for variations of ``build log''
+returned more than 2.2 million results (2020-03-15), many of which stem from unrelated fields such as construction and wood working.
+We refined our search criteria to exclude such obvious
+non-related fields and also to exclude works on systems
 or event logs (see \Cref{sec:system-log-analysis}).
@@
 (2020-03-15).
-The full search queries are documented in our replication
-package~\cite{brandt2020chunk-replication}.
-
+Our replication package documents the full search queries~\cite{brandt2020chunk-replication}.
 To make handling so many search results feasible, we employed a
-two-pass filtering strategy:
-
-First, we filtered articles based on (1) their title and (2) the
+three-pass filtering strategy:
+
+First, we filtered articles based on (a) their title and (b) the
 contextual information Google Scholar displayed.
-We included only
-publications written in a language intelligible to the authors (that
-is, English or German), which disregarded fewer than 1\% of search
+We included works at large that seemed to bear a resemblence to software engineering and building software.
+We excluded wroks written in a language unintelligible to the authors (i.e., not English or German), which disregarded fewer than 1\% of search
 hits.
@@
 % removed duplicates of data extraction pass already here
-
 With these 256 remaining articles, we followed a backward snowball
 sampling for related work.
-If one of the articles referenced a new article in the context
-of build log analysis we added the new to our literature set.
-This added five papers (eight before
-duplicate elimination), coming to a total of 261
-articles.
+If an article referenced a new work in the context
+of build log analysis, we added the new one to our literature set.
+This added five articles (eight before
+duplicate elimination), leading to a total of 261
+works.
 
 Subsequently, we performed a second, finer filter phase by downloading the
-full articles, reading their abstracts and searching the full text
-for the occurrence of ``log''.
-If these papers showed traces of
-working with build logs, we included them in our survey.
+full text of the works, reading their abstracts, and searching the full text
+for the occurrence of ``log.''
+If a work showed traces of
+working with build logs, we included it in our survey.
 In total, we
-were left with 87 articles after the two filtering phases.
+were left with 87 works after the second filtering phases.
 
 \subsection{Article Classification}
-Having trimmed down the set of articles, we investigated them in depth.
-
-We wanted to characterize how researchers use build logs as input to
-any processes.
-We were interested in
+Having trimmed down the set of articles by 95\%, we investigated the remaining ones in depth.
+We wanted to characterize how research uses build logs.
+
+% TODO (resolved): RQs mentioned before explicitly stated
+Specifically, we were interested in
 \begin{itemize}
-  \item what information they are retrieving from the logs and
-  what they use the retrieved information for (\textbf{RQ1.1})
-  \item which technique they are using to process the build logs,
-  in how much detail it is described and whether they published their
-  tools (\textbf{RQ1.2})
-  \item what kind of build logs they are using and the origin of these
+  \item what information is retrieved from the logs and
+  what the retrieved information is used for (\textbf{RQ1.1})
+  \item which techniques are used to process the build logs,
+  in how much detail they are described, and whether they are published as tools (\textbf{RQ1.2})
+  \item what kind of build logs are used and the origin of these
   logs.
@@
 \end{itemize}
-To objectify our data extraction we created a template of the targeted
-factors and performed a pilot, as recommended by Petersen et
-al.~\cite{petersen2015guidelines}.
-Two authors extracted the data from five articles and we held a
-consensus meeting to unify our understanding
-of the data extraction template.
-The remaining articles were divided over these two authors.
-We inspected the articles as closely as necessary,
-starting from occurrences of ``log'' or ``build'' within the text.
-
-Relevant for our survey were all articles that
-use logs from software builds as input to
-some kind of process.
-This excluded 15 articles from our study.
-In several cases, multiple articles were extensions of others.
-Of these, we only considered the earliest article which reported on
-the processing of build logs.
-This excluded another 11 articles.
-In sum, we further extracted data from 61 articles.
-
-The full data extraction template and our results of this step can be
-found in our replication package~\cite{brandt2020chunk-replication}.
-Note that for most questions we allowed assigning multiple values,
-e.g.\ if
-two kinds of information were targeted during a build log analysis.
-
+
+This lead us to the following research questions:
 \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
 {\textbf{RQ1:} What are the state-of-the-research
-techniques for build log analysis?}
+techniques to analyze build logs?}
 \begin{itemize}[leftmargin=2cm]
@@
 \end{simplebox}
+
+Since we had been careful to include rather than exclude borderline works, this deeper evaluation excluded another 15 articles from the 87 works left after the second filter phase.
+Multiple articles were extensions of others.
+Of these, we only considered the earliest article which reported on
+the processing of build logs.
+This excluded another 11 articles.
+In sum, we extracted data from 61 articles.
+
+To guide the data extraction we created a template.
+The template form contained questions to answer RQ 1.1 through RQ 1.3, for example ``Is the technique explained in sufficient detail?'' and ``What is the source of the build logs?'' As recommended by Petersen et
+al.~\cite{petersen2015guidelines}, we started the mapping study with a pilot study:
+both authors extracted  data from the same five articles and held a
+consensus meeting to unify their understanding
+of the data extraction template.
+We divided the remaining 46 articles evenly between the two authors and inspected them as closely as necessary to fill out the template with confidence,
+starting from occurrences of ``log'' or ``build'' within the article's text.
+For questions that did not require a boolean answer, we allowed assigning multiple tags or categories as the first part (``preparation phase'') of a virtual open card sorting~\cite{zimmermann2016card}.
+% TODO: add more concrete example, such as use of retrieved x: developer feedback, build data set
+Once we had classified all works, we went into the second phase (``execution phase'') in which we found synonyms, and grouped tags together.
+
+%The full data extraction template and our results of this step can be
+%found in our replication package~\cite{brandt2020chunk-replication}.
+
+% TODO (resolved): RQs just appeared unconnected out of the blue
 
@@
 \subsection{Results}
-In the following, we will present the results of our literature survey.
-We present the information within the build logs that was targeted,
-the retrieval techniques used and the origin of the build logs
-which were analyzed.
-
-\subsubsection{Retrieved Information}
-The information that was targeted varied from article to article.
-Most prominent was the search for errors (39\%) which occurred within
-the build process, as presented in \Cref{fig:litsur:info_target}.
-This is followed by extracting the executed or the failing
+In this section, we present the results of the analysis phase of the
+literature mapping along RQ 1.1 through RQ 1.3.
+
+% TODO repeat the question in the subsection title?
+\subsubsection{Retrieved Information (RQ 1.1)}
+% TODO General ref to Figure 4 missing: We answer this question along data in Figure 4, and ... ?
+
+The precise information targeted in the build logs varied from article to article.
+\Cref{fig:litsur:info_target} gives an overview over the frequency of the targeted information. Most prominent was the search for errors (39\%), followed by extracting the executed or the failing
 tests (both 11\%).
-There were also numerous cases which targeted more specialized
+There were also numerous works which targeted more specialized
 information, such as the environments used during the
 build~\cite{zolfagharinia2017not}, packages
-installed~\cite{selberg2012use} or hints to source files which are
-related to build failures~\cite{ren2018automated}.
-
+installed~\cite{selberg2012use}, or hints to source files which 
+relate to build failures~\cite{ren2018automated}.
+
+% TODO It is unclear where this comes from. Also, wouldn't it perhaps be better to continue with Figure 4.b directly?
 In most cases (51\%), a chunk was retrieved from the log.
@@
 tools~\cite{kavaler2019tool}.
-Other types of information (e.g.\ counting
+Other types of information (e.g.,\ counting
 lines, summarization) were only retrieved
@@
 analysis for research purposes, as shown in \Cref{fig:litsur:use}.
+% TOOD What does this mean? Give an example: to drive further research, for example to categorize the types of compile errors encountered at Google~\cite{}.
 Further uses were giving feedback to developers (10\%) or automatic
-on-ward processing of the retrieved information (8\%).
-
-\subsubsection{Retrieval Technique}
+on-ward processing of the retrieved information (8\%)
+% TODO for example to ...
+.
+
+% TODO repeat the question in the subsection title?
+\subsubsection{Retrieval Technique (RQ 1.2)}
 \Cref{tab:litsur:techniques} presents the techniques that the articles
+% TODO: lets use analyzing build logs canonically? Please search text to eliminate occurrences of processing?
 described for processing build logs.
+% TODO This is weird. Last number we have from above is 51.
 43 of the 61 articles we inspected mentioned how they are analyzing build
@@
 included
-rather imprecise statements like ``we parse the build logs''.
+rather imprecise statements like ``we parse the build logs.''
+% TODO include citation?
+% TOOD maybe make the point here that it is questionable whether this includes a comprehensive tokenizer, lexer etc.
+based solution and that parsing in many cases really meant regexp.
+If we could figure that out, then we would assign it to regexp instead.
 25\% of the articles described the use of regular expressions and 20\%
 inspected the logs manually.
-Another 8\% employed machine learning techniques such as natural language
+Another 8\% employed machine learning such as natural language
 processing or information retrieval techniques.
-To give examples,
+For example,
 Seo et al.~\cite{seo2014programmers} developed a custom
@@
 Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
-They start with manual categorization of the build logs and select
-search strings that identify their targeted categories.
-Based on the search strings they create a script that automatically
+They started with manual categorizing build logs and selecting
+search strings that identify the target category.
+Based on the search strings they created a script that automatically
 classifies the remaining logs.
 
-25\% of the articles claimed their implementation is available,
-however, we
-saw a very low reuse of build log analysis tools within our survey.
+Only 25\% of the articles claimed their implementation is available. Moreover, we
+saw some reuse of the few available build log analysis tools.
 Five articles employed the tools used to create
@@
 an extended version of them~\cite{rott2019empirische,
-shi2018evaluating},
+shi2018evaluating} (based on regular expressions),
 two used the
-\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
+\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
+% TODO: based on which technique?,
 another two the
-\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.
+\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool
+% TODO: based on which technique?
+.
 
 \subsubsection{Build Logs}
+% TODO using passive where it is unneccessary
 The distribution of supported build tools is shown in
@@
 
+% TODO remove first part of this paragraph?
 Sometimes this limitation to a specific build tool is motivated by
@@
 several described they are covering multiple source build tools.
-The majority of articles (42\%) targeted logs from a source that was not
-targeted by any second article.
-
+The majority of articles (42\%) targeted logs from a source that no second article
+targeted.
+
+% TODO death by passive
 The main platform that build logs were collected from is Travis
@@
 
+% perhaps remove?
 The number of logs analyzed varied greatly and we were not always able to
@@
 However, we found no clear reuse of build log data sets with the
-exception of TravisTorrent~\cite{beller2017travistorrent}, which was
-analyzed by Vassallo et al.~\cite{vassallo2017a-tale},
-Ghaleb et al.~\cite{ghaleb2019studying} and several other studies.
-
+exception of TravisTorrent~\cite{beller2017travistorrent}, which 
+Vassallo et al.~\cite{vassallo2017a-tale},
+Ghaleb et al.~\cite{ghaleb2019studying}, and several other studies reused.
+
+% TODO A and B should possibly be overlapping, otherwise there is an area where neither A nor B makes sense?
 \begin{figure}[tbhp]
@@
 \label{sec:lit-sur:discussion}
-Our literature survey sheds light on how build log analysis is used within
-computer science research.
-Hereafter we will summarize our findings and relate them to the
-approach we are taking to improve build log analysis with chunk
-retrieval techniques.
-
-We saw that various researchers process build logs to support their
-research, often because the logs provide more or the necessary information
-to the researchers~\cite{ren2018automated}.
-Articles which explicitly mention a manual analysis of
-the logs, mostly restrict their work to few logs or take a
-``representative sample to make manual analysis
-feasible''~\cite{zolfagharinia2017not}.
-Automated approaches are necessary as many studies target a large
-number of builds.
+
+% TODO: this section is crucial. maybe we can highlight important findings, by categorizing them either as further subsubsections or making it bold in the text?
+% TODO: find values for X and Y
+Our literature survey shows that despite its relatively young age
+(first occurrence of a paper on the topic in X), \textbf{build log analysis is
+a widely established technique} in the literature, with Y articles on it.
+
+% TODO: this reads very hands-off and researchy.
+% I don't understand the first sentence and would simply cut it.
+We saw that various researchers process build logs, often because the logs  provide more or the necessary
+information to the researchers~\cite{ren2018automated}.  \textbf{Most log analysis is automated.} Automated approaches are necessary as many studies target a large
+number of builds. Articles
+which explicitly mention a manual analysis of the logs, mostly
+restrict their work to few logs or take a ``representative sample to
+make manual analysis feasible''~\cite{zolfagharinia2017not}.
 % The chunk retrieval techniques we investigate within this article are
@@
 
-We have observed very little reuse of build log analysis tools.
+% TODO: draw a conclusion together with figure 5: if reuse were higher, lots of effort could be saved?
+% discussion about popularity of replication packages adds nothing to this paper.
+We observed very little reuse of build log analysis tools.
 This can stem from the fact that publishing replication packages and
@@
 every supported build environment.
-\Cref{fig:litsur:log_producer} shows that few build environments are
-targeted by many studies and tools (A).
+\Cref{fig:litsur:log_producer} shows that many studies and tools target only a few distinct build environments (roughly, area A).
+% TODO: passive ...
 The majority of build environments was however only targeted by one
 article each (B).
-From this, we follow that, while custom parsers are beneficial for the
-small group of environments targeted by many (A), all and especially
-the rarer investigated environments (B) would benefit from a generic
+From this, we follow: (a) there is a nichè for custom parsers or even specialized plugins integrated into the build process to make post-factum parsing of logs redundant.
+Plugins  similar to, for example, the Maven plugin to report test executions Bell et al.
+wrote, still have the disadvantage of not being able to work on historic builds.
+(b) the large tail of seldomly-investigated environments would benefit from the existance of a more generic
 solution.
@@
 
+% TODO this is disconnected, at least here
 Urli et al.~\cite{urli2018design} strongly discouraged from parsing
@@
 
-In summary, this literature study shows the need for build log
+In summary, the results of the literature study show the need for build log
 analysis techniques that are automated, build-environment agnostic
+% TODO who is the user?
 and can be configured by the user with little effort.
@@
 
+% TODO: the following paragraphs have nothing to do with a discussion of the literature survey results.
+% what we need is some derivation of the three techniques 1) regex 2) cts 3) kws, best repeated here in the discussion and then from the lit survey above, section 2.4.2
 For this reason, we are focussing on techniques that run automatically

### 2020-04-22 tse-paper/paper.tex
First feedback and review integrated

@@
 \author{Carolin~Brandt,%~\IEEEmembership{Member,~IEEE,}
-        Moritz~Beller,%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
+        Moritz~Beller%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
 % \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
@@
 \begin{IEEEkeywords}
-Computer Society, IEEE, IEEEtran, Journal, Continuous Integration, 
-Build Log Analysis, Chunk Retrieval.
+Build Log Analysis, Chunk Retrieval, Continuous Integration
 \end{IEEEkeywords}}

### 2020-04-22 tse-paper/content.tex
Mega review done

@@
 Build logs are a textual by-product that automatic software build
-processes create.  As a treasure trove of information~\cite{meyer},
+processes create.
+As a treasure trove of information~\cite{meyer},
 build logs contain trace outputs of not only the elementary steps to
@@
 compiling---but also about ancillary quality assurance steps---such as
-testing the software and running automated static analysis tools. The
+testing the software and running automated static analysis tools.
+The
 contents of build logs can be highly variable depending on which tools
 are involved in the build process and how they are
-configured. The format of logs changes as projects and build tools evolve over time. Typically, though, they are at least a semi-structured and
+configured.
+The format of logs changes as projects and build tools evolve over time.
+Typically, though, they are at least a semi-structured and
 somewhat stable journal of the commands executed during the build and
@@
 single build log can be over 50 megabytes large~\cite{beller2017oops},
-finding the small chunk of information in it which is linked to the error, is akin to searching for a
+finding the small chunk of information in it which is linked to the error,
+is akin to searching for a
 needle in a haystack.
-In addition to helping understand and fix build failures, the information richness of build logs enables a plethora of other applications: with the help of
+In addition to helping understand and fix build failures, the information
+richness of build logs enables a plethora of other applications: with
+the help of
 build logs, we can better understand and categorize CI
@@
 scale to the number of build logs and amount of information that such
-sophisticated applications require. Moreover, being able to
-automatically extract relevant pieces of information from build logs can also help
-developers debug a broken build more quickly without having to browse the entire build log.
+sophisticated applications require.
+Moreover, being able to
+automatically extract relevant pieces of information from build logs
+can also help
+developers debug a broken build more quickly without having to browse
+the entire build log.
 
@@
 
-To answer this question, we start our investigation by performing an extensive literature study (\Cref{fig:overview}).
+To answer this question, we start our investigation by performing an
+extensive literature study (\Cref{fig:overview}).
 It shows that
@@
   \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on manually supplied example pairs of build logs and chunks, PBE automatically
+  Based on manually supplied example pairs of build logs and chunks,
+  PBE automatically
   synthesizes
@@
   \item \textbf{Common Text Similarity (CTS)}
-  % TODO what is the vector space model
+  % TODO what is the vector space model?
   Using the Vector Space Model, CTS selects lines of a log which are
@@
 
-In the third step, we conduct an empirical study to gauge the performance of
+In the third step, we conduct an empirical study to gauge the performance
+of
 these chunk retrieval techniques in
@@
 
-Finally, we develop a set of guidelines (step 4) on how to choose a technique given a goal.
+Finally, we develop a set of guidelines (step 4) on how to choose a
+technique given a goal.
 We recommend PBE for use cases where the desired information is always
@@
 unsuited for automatic on-ward processing and instead requires a human
-to further inspect and interpret the output chunk. A hybrid-solution combining the three techniques might be the best allround solution.
+to further inspect and interpret the output chunk.
+A hybrid-solution combining the three techniques might be the best
+allround solution.
 
@@
 \begin{itemize}
-\item the first systematic study of the emerging field of build log analysis.
-\item three prototypical open-sourced implementations of the most promising chunk retrieval techniques.
-\item a large-scale empirical study comparing the three techniques.
+\item the first systematic study of the emerging field of build log
+analysis.
+\item three prototypical open-sourced implementations of the most
+promising chunk retrieval techniques.
+\item a large empirical study comparing the three techniques.
 \item systematic guidelines on when to use which technique.
@@
 In this section, we survey the emerging field of build log
-analysis. We first start with a differentiation to the related field of general system log analysis. Then, we describe the methodology and results of a systematic mapping study to
+analysis.
+We first start with a differentiation to the related field of general
+system log analysis.
+Then, we describe the methodology and results of a systematic mapping
+study to
 determine the state-of-research on build log analysis following the
@@
 al.~\cite{petersen2008systematic,petersen2015guidelines}.
+
 We close by summarizing how build logs are commonly
@@
 \label{sec:system-log-analysis}
-A field related to build log analysis is the processing of system log
-files produced during runtime of the system. The first difference here is that build logs are produced during runtime of the build of the system, not the system itself.
-In terms of the contents of the logs, the main difference is that system logs are fundamentally structured
+A field related to build log analysis is the processing of system logs produced during runtime of the system.
+The first difference here is that build logs are produced during runtime
+of the build of the system, not the system itself.
+In terms of the contents of the logs, the main difference is that system
+logs are fundamentally structured
 through events.
@@
 messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters. Then, a log parser works on this intermediate representation.
+identical constant parts and varying parameters.
+Then, a log parser works on this intermediate representation.
 Its output is an ordered list of timed events and their corresponding
 parameter values~\cite{he2016evaluation}.
-This structured log can serve as input to various machine learning and data mining processes.
-
-In principle, one can apply the techniques developed for system log analysis
+This structured log can serve as input to various machine learning and
+data mining processes.
+
+In principle, one can apply the techniques developed for system log
+analysis
 to parts of the build logs that have this same structure.
-% TODO this explanation is not understandable. It needs to better embedded in the surrounding text
+% TODO this explanation is not understandable.
+It needs to better embedded in the surrounding text
 One example is comparing execution traces to reference
@@
 leverage their inherent event structure.
-Build logs generally lack this structure and thus require different bespoke approaches.
+Build logs generally lack this structure and thus require different
+bespoke approaches.
 % In this article, we focus on extracting a single specified information
@@
 
-% TODO In general, we should reference petersen2015guidelines a bit
-% more. I.e., following the suggestions by Petersen or something, to
-% show how we followed their protocol. This comment applies to the rest of this section
-
 \subsection{Study Selection}
@@
 surveyed as broad a population of scientific material as possible.
-We did not limit our sources to specific Software Engineering venues~\cite{petersen2015guidelines}, but survey all sources
+We did not limit our sources to specific Software Engineering
+venues~\cite{petersen2015guidelines}, but survey all sources
 monitored by Google Scholar, including Bachelor's and Master's
@@
 An initial Google Scholar search for variations of ``build log''
-returned more than 2.2 million results (2020-03-15), many of which stem from unrelated fields such as construction and wood working.
+returned more than 2.2 million results (2020-03-15), many of which stem
+from unrelated fields such as construction and wood working.
 We refined our search criteria to exclude such obvious
@@
 (2020-03-15).
-Our replication package documents the full search queries~\cite{brandt2020chunk-replication}.
+Our replication package documents the full search
+queries~\cite{brandt2020chunk-replication}.
 To make handling so many search results feasible, we employed a
@@
 contextual information Google Scholar displayed.
-We included works at large that seemed to bear a resemblence to software engineering and building software.
-We excluded wroks written in a language unintelligible to the authors (i.e., not English or German), which disregarded fewer than 1\% of search
+We included works at large that seemed to bear a resemblence to software
+engineering and building software.
+We excluded wroks written in a language unintelligible to the authors
+(i.e., not English or German), which disregarded fewer than 1\% of search
 hits.
@@
 Subsequently, we performed a second, finer filter phase by downloading the
-full text of the works, reading their abstracts, and searching the full text
+full text of the works, reading their abstracts, and searching the
+full text
 for the occurrence of ``log.''
@@
 \subsection{Article Classification}
-Having trimmed down the set of articles by 95\%, we investigated the remaining ones in depth.
+Having trimmed down the set of articles by 95\%, we investigated the
+remaining ones in depth.
 We wanted to characterize how research uses build logs.
@@
   \item which techniques are used to process the build logs,
-  in how much detail they are described, and whether they are published as tools (\textbf{RQ1.2})
+  in how much detail they are described, and whether they are published
+  as tools (\textbf{RQ1.2})
   \item what kind of build logs are used and the origin of these
@@
 
-Since we had been careful to include rather than exclude borderline works, this deeper evaluation excluded another 15 articles from the 87 works left after the second filter phase.
+Since we had been careful to include rather than exclude borderline
+works, this deeper evaluation excluded another 15 articles from the 87
+works left after the second filter phase.
 Multiple articles were extensions of others.
@@
 To guide the data extraction we created a template.
-The template form contained questions to answer RQ 1.1 through RQ 1.3, for example ``Is the technique explained in sufficient detail?'' and ``What is the source of the build logs?'' As recommended by Petersen et
-al.~\cite{petersen2015guidelines}, we started the mapping study with a pilot study:
+The template form contained questions to answer RQ 1.1 through RQ 1.3,
+for example ``Is the technique explained in sufficient detail?'' and
+``What is the source of the build logs?'' As recommended by Petersen et
+al.~\cite{petersen2015guidelines}, we started the mapping study with a
+pilot study:
 both authors extracted	data from the same five articles and held a
@@
 of the data extraction template.
-We divided the remaining 46 articles evenly between the two authors and inspected them as closely as necessary to fill out the template with confidence,
-starting from occurrences of ``log'' or ``build'' within the article's text.
-For questions that did not require a boolean answer, we allowed assigning multiple tags or categories as the first part (``preparation phase'') of a virtual open card sorting~\cite{zimmermann2016card}.
-% TODO: add more concrete example, such as use of retrieved x: developer feedback, build data set
-Once we had classified all works, we went into the second phase (``execution phase'') in which we found synonyms, and grouped tags together.
+We divided the remaining 46 articles evenly between the two authors
+and inspected them as closely as necessary to fill out the template
+with confidence,
+starting from occurrences of ``log'' or ``build'' within the article's
+text.
+For questions that did not require a boolean answer, we allowed assigning
+multiple tags or categories as the first part (``preparation phase'')
+of a virtual open card sorting~\cite{zimmermann2016card}.
+
+% TODO: add more concrete example, such as use of retrieved x: developer
+feedback, build data set
+Once we had classified all works, we went into the second phase
+(``execution phase'') in which we  grouped tags
+together and found synonyms.
 
@@
 
+% TODO: vertical alignment of rows with text to middle so they are aligned with pictograms on the right?
 \addtolength{\tabcolsep}{-5pt}
@@
 \subsubsection{Retrieved Information (RQ 1.1)}
-% TODO General ref to Figure 4 missing: We answer this question along data in Figure 4, and ... ?
-
-The precise information targeted in the build logs varied from article to article.
-\Cref{fig:litsur:info_target} gives an overview over the frequency of the targeted information. Most prominent was the search for errors (39\%), followed by extracting the executed or the failing
+% TODO General ref to Figure 4 missing: We answer this question along
+% data in Figure 4, and ...
+% ?
+
+The precise information targeted in the build logs varied from article
+to article.
+\Cref{fig:litsur:info_target} gives an overview over the frequency of
+the targeted information.
+Most prominent was the search for errors (39\%), followed by extracting
+the executed or the failing
 tests (both 11\%).
@@
 
-% TODO It is unclear where this comes from. Also, wouldn't it perhaps be better to continue with Figure 4.b directly?
+% TODO It is unclear where this comes from.
+% TODO Also, wouldn't it perhaps be better to continue with Figure 4.b directly?
 In most cases (51\%), a chunk was retrieved from the log.
@@
 analysis for research purposes, as shown in \Cref{fig:litsur:use}.
-% TOOD What does this mean? Give an example: to drive further research, for example to categorize the types of compile errors encountered at Google~\cite{}.
+% TOOD What does this mean? Give an example: to drive further research,
+for example to categorize the types of compile errors encountered at
+Google~\cite{}.
 Further uses were giving feedback to developers (10\%) or automatic
@@
 \Cref{tab:litsur:techniques} presents the techniques that the articles
-% TODO: lets use analyzing build logs canonically? Please search text to eliminate occurrences of processing?
+% TODO: lets use analyzing build logs canonically? Please search text
+to eliminate occurrences of processing?
 described for processing build logs.
-% TODO This is weird. Last number we have from above is 51.
+% TODO This is weird.
+Last number we have from above is 51.
 43 of the 61 articles we inspected mentioned how they are analyzing build
@@
 % TODO include citation?
-% TOOD maybe make the point here that it is questionable whether this includes a comprehensive tokenizer, lexer etc.
+% TOOD maybe make the point here that it is questionable whether this
+includes a comprehensive tokenizer, lexer etc.
 based solution and that parsing in many cases really meant regexp.
@@
 
-Only 25\% of the articles claimed their implementation is available. Moreover, we
+Only 25\% of the articles claimed their implementation is available.
+Moreover, we
 saw some reuse of the few available build log analysis tools.
@@
 several described they are covering multiple source build tools.
-The majority of articles (42\%) targeted logs from a source that no second article
+The majority of articles (42\%) targeted logs from a source that no
+second article
 targeted.
@@
 
-% perhaps remove?
+% TODO perhaps remove this paragraph?
 The number of logs analyzed varied greatly and we were not always able to
@@
 
-% TODO A and B should possibly be overlapping, otherwise there is an area where neither A nor B makes sense?
+% TODO A and B should possibly be overlapping, otherwise there is an
+% area where neither A nor B makes sense?
 \begin{figure}[tbhp]
@@
 \label{sec:lit-sur:discussion}
-
-% TODO: this section is crucial. maybe we can highlight important findings, by categorizing them either as further subsubsections or making it bold in the text?
+% TODO we are extracting failures in the following studies, which is mainly what
+% literature does, too, right? Highlight here and mention later again
+
+% TODO: this section is crucial.
+% maybe we can highlight important findings, by categorizing them either
+% as further subsubsections or making it bold in the text?
 % TODO: find values for X and Y
 Our literature survey shows that despite its relatively young age
-(first occurrence of a paper on the topic in X), \textbf{build log analysis is
-a widely established technique} in the literature, with Y articles on it.
+(first occurrence of a paper on the topic in 2001, vast majority after
+2016), \textbf{build log analysis is a widely established technique}
+in the literature, with Y articles on it.
 
@@
 % I don't understand the first sentence and would simply cut it.
-We saw that various researchers process build logs, often because the logs  provide more or the necessary
-information to the researchers~\cite{ren2018automated}.  \textbf{Most log analysis is automated.} Automated approaches are necessary as many studies target a large
-number of builds. Articles
+We saw that various researchers process build logs, often because the
+logs  provide more or the necessary
+information to the researchers~\cite{ren2018automated}.
+\textbf{Most log analysis is automated.} Automated approaches are
+necessary as many studies target a large
+number of builds.
+Articles
 which explicitly mention a manual analysis of the logs, mostly
@@
 
-% TODO: draw a conclusion together with figure 5: if reuse were higher, lots of effort could be saved?
-% discussion about popularity of replication packages adds nothing to this paper.
+% TODO: draw a conclusion together with figure 5: if reuse were higher,
+lots of effort could be saved?
+% discussion about popularity of replication packages adds nothing to
+this paper.
 We observed very little reuse of build log analysis tools.
@@
 every supported build environment.
-\Cref{fig:litsur:log_producer} shows that many studies and tools target only a few distinct build environments (roughly, area A).
+\Cref{fig:litsur:log_producer} shows that many studies and tools target
+only a few distinct build environments (roughly, area A).
 % TODO: passive ...
@@
 article each (B).
-From this, we follow: (a) there is a nichè for custom parsers or even specialized plugins integrated into the build process to make post-factum parsing of logs redundant.
-Plugins  similar to, for example, the Maven plugin to report test executions Bell et al.
-wrote, still have the disadvantage of not being able to work on historic builds.
-(b) the large tail of seldomly-investigated environments would benefit from the existance of a more generic
+From this, we follow: (a) there is a nichè for custom parsers or even
+specialized plugins integrated into the build process to make post-factum
+parsing of logs redundant.
+Plugins  similar to, for example, the Maven plugin to report test
+executions Bell et al.
+wrote, still have the disadvantage of not being able to work on historic
+builds.
+(b) the large tail of seldomly-investigated environments would benefit
+from the existance of a more generic
 solution.
@@
 Urli et al.~\cite{urli2018design} strongly discouraged from parsing
-build logs for information as it is ``too error prone'', other
+build logs for information as it is ``too error prone,'' other
 articles pointed to the effort of developing a custom tool.
@@
 
-In summary, the results of the literature study show the need for build log
+In summary, the results of the literature study show the need for
+build log
 analysis techniques that are automated, build-environment agnostic
@@
 
-% TODO: the following paragraphs have nothing to do with a discussion of the literature survey results.
-% what we need is some derivation of the three techniques 1) regex 2) cts 3) kws, best repeated here in the discussion and then from the lit survey above, section 2.4.2
+% TODO: the following paragraphs have nothing to do with a discussion
+of the literature survey results.
+% what we need is some derivation of the three techniques 1) regex 2)
+cts 3) kws, best repeated here in the discussion and then from the lit
+survey above, section 2.4.2
 For this reason, we are focussing on techniques that run automatically
@@
 The targeted chunks are describing error messages or
-``the reason the build failed'', which was also the information
+``the reason the build failed,'' which was also the information
 most targeted by the articles in our survey.
@@
 
-\Cref{tab:ctr} shows a comparison of the presented techniques.
+% TODO this is not enough for Table 3. Where does it come from?
+% How did it originate? Also: never single sentence abstracts
+\Cref{tab:ctr} shows a comparison of the implemented techniques.
+
+% TODO Somehow, we have to find a better place for this. We have been
+% using the term 'chunk retrieval' beforehand already -- this
+% definition now comes to late. The first paragraph should already
+% apply to the literature mapping, the second of course only applies
+% here.
 
@@
 for build logs.
-Our implementation is based and highly influenced by the
-\emph{Microsoft PROSE library}~\cite{prose2019webpage}.
+Our implementation is based on the
+\emph{PROSE library}~\cite{prose2019webpage}.
 The PROSE library is powered by the generic program synthesis framework
@@
 In- and output example pairs are the main driver of Programming by
-Example, we refer to them in short as \emph{examples}.
+Example; we refer to them in short as \emph{examples}.
 The \emph{input} is the text of the build log file.
@@
 consistent with all training examples.
-If PROSE cannot synthesize a program, e.g.\
+If PROSE cannot synthesize a program, e.g.,\
 because the regular expression
 necessary would be too complicated to synthesize, PBE returns the
-error message ``no program found''.
+error message ``no program found.''
+% TODO Figure 7 should not come before Figure 6. Figure 6 and 7 should be
+% introduced first. This is best-practice anyway: Whenever you mention
+% a figure/table the standard sentence should always be: Figure X shows Y,
+% on the vertical axis Z and on the horizontal axis D.
+
 \Cref{lst:prose-program-simplified} presents a simplified version
@@
 % config/application?
+% TODO Why does it return an error message? Shouldn't it also return
+% <empty string>? Does it not rather return an error message if no
+% program can be synthesized?
 \subsubsection{Application}
@@
 We investigate a chunk retrieval technique based on the common
+% TODO: the ominuous Vector Space Model again ...
 Vector Space Model~\cite{schutze2008introduction}.
@@
 % I added a "as follows", think that is enough for explanation?
+% TODO: I think it is good, but the VSM is still unexplained. We need a
+% (at least) 1-sentence introduction to it, at its first reference
 and apply the Vector Space Model~\cite{schutze2008introduction}
@@
 \label{sec:expl-rlr}
-In our evaluation, we want to compare against a baseline of randomly
-picking lines from the build log.
+% TODO: could you add two-three more references to the results of RLR in
+% the discussion, to show how even seemingly low numbers are much better
+% than RLR?
+
+To fully comprehend how difficult a task build log analysis really is without any a-priori knowledge, we include a comparison with a base line generated by Random Line Retrieval (RLR), that is,
+picking lines randomly from the build log.
 RLR mimics the
@@
 The only configuration option for RLR is the number of lines it should
-return.
+retrieve.
 For a fair comparison to the other techniques (whose number of
 returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples.
+number of lines in the chunks of the training examples, thus arguably giving it a slight advantage.
 
@@
 %It's really all we are doing
-
+% TODO: You are right, nothing more is necessary
+
+% TODO: these next two sections do not belong under this section -- they are not a chunk retrieval technique. One way to fix it would be to rename the section.
 \subsection{Chunk Retrieval Example}
@@
 PBE is not able to synthesize a program and returns
-``\texttt{no program found}''.
+``\texttt{no program found}.''
 We later express this difference in structural representation through
@@
 For the examples from \Cref{lst:chunk-example} these could be
-``FAILURE'', ``wrong'' or ``failed''.
+``FAILURE,'' ``wrong,'' or ``failed''.
 The example from \Cref{lst:chunk-example-3} could be found
-by searching for ``FAIL''.
-If KWS would be trained with all three examples and the aforementioned
+by searching for ``FAIL.''
+If KWS was to be trained with all three examples and the aforementioned
 associated keywords, it would search for the three keywords from
@@
 calls the separate technique implementations over the command line.
-The implementation of PBE in C\# is based on the Microsoft PROSE
-library~\cite{prose2019webpage}.
-We implemented CTS, KWS and RLR using
+We implemented PBE in C\# based on the Microsoft PROSE
+library~\cite{prose2019webpage} and CTS, KWS, and RLR using
 R and the text2vec library~\cite{text2vec2019webpage}.
-They can be found in our replication
+% TODO and passive again ...
+The source code of the implementation can be found in our replication
 package~\cite{brandt2020chunk-replication} together
-with Docker images which have
-our techniques installed and ready to use.
+with ready-to-use Docker images.
 
 \section{Study Design}
+
+% TODO This section is not structured well. First, it misses an
+% explanation of the bigger study design.  Second, What is the difference between Study Process and
+% Study Design? Third, the LogChunks section appears out of nowhere
+% and is not related to the section title (different abstraction
+% level).  Perhaps a solution would be to be a bit inspired by this
+% paper:
+% https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
+% There is a research design section (which we are missing) and a
+% Research Method section (which is a mixture of the current section
+% titled Log Chunks and Study Process)
+
 \label{sec:study}
 
-To investigate when our chunk retrieval techniques are suited to
+To investigate when the chunk retrieval techniques are suited to
 analyze build logs (\textbf{RQ2}), we perform an empirical comparison
@@
 has to be (\textbf{RQ2.2}) and how reliable the quality of the
-produced outputs is (\textbf{RQ2.3}).
+produced outputs is (\textbf{RQ2.3}). This leads us to the following research questions:
 
@@
 \subsection{LogChunks}
-For this study, we created the previously published data set
-\emph{LogChunks}.
+To conduct the study in this paper, we created the 
+\emph{LogChunks}  data set~\cite{brandt2020logchunks}.
 It encompasses 797 build logs from Travis CI,
@@
 the log part (chunk) describing why the build
-failed''~\cite{brandt2020logchunks}.
+failed''.
 We included keywords, which we
@@
 \subsection{Study Process}
+% TODO: I think you need to introduce a concept that makes clear what one
+% ``folder'' consists of ...
+% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
+% we operate on all repos in LogChunks?
 We begin by selecting all examples in \emph{LogChunks}
 that correspond to one GitHub repository---and thus the
+% TODO () is meant to reference the figure, but this the figure is not actually mentioned.
 same build environment (1).
+% TODO: What does this mean? Of what nature are the examples? How were they chosen?
+% Isn't it rather the case that for each repository, we built traning sets of size 1, 2,
+% ... 5 build logs?
 One to five examples make up the training set (2).
+% TODO passive ...
 We vary its size to measure how many examples are needed to
@@
 (see \Cref{sec:lit-sur:discussion}).
+% TODO: The example? why only one? And what is an example? An example build log?
+% Then it would be good to say so.
 The example chronologically after the training set makes up the
@@
 should receive reliable results on every build log they analyze.
+% TODO and why is this important? Doesn't everyone want such stability of results?
 In the next step, we configure a chunk retrieval technique with
@@
 \end{itemize}
+
+% This is a weird position for this paragraph
+% TODO What is ``this'' referring to? You just defined a bunch of equations.
 This concludes one execution within our evaluation.
+% TODO run vs. execution above.
 We conduct one run for each of the four chunk retrieval techniques,
@@
 and for each of the five training set sizes (2).
-In total we perform 1600 runs, 400 for each of the chunk retrieval
-techniques PBE, CTS, KWS and RLR.
-
-Our implementation of the techniques, as well as our evaluation
-harness and the code we used to process our results is offered
-for inspection and reproduction in our replication package
-~\cite{brandt2020chunk-replication}.
+In total we perform 1600 runs, 400 for each of the implemented chunk retrieval
+technique.
 
 \section{Results}
-This section presents the separate results for each chunk retrieval
-technique.
-Afterwards, we compare the three techniques with each other and RLR as
+This section first presents the results for each chunk retrieval
+technique separately.
+Afterwards, we compare the three techniques with each other and to RLR as a
 baseline.
@@
 
-\Cref{fig:failure-reason-PBE} presents the results of the chunk
+% TODO Say something about this being a pecularity of PBE ...
+\Cref{fig:failure-reason-PBE} shows the results of chunk
 retrieval with PBE.
-Out of the 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all the desired lines successfully in 138 cases.
+Out of the overall 400 runs, 5 per each one of the 80 example
+sets, PBE extracted all desired lines successfully in 138 cases.
 In 59 cases, a regular expression program could be synthesized, though
-it did not find a match on the test build log.
-In 30 cases the synthesized program only extracted a
+it did not find match on the test build log.
+In 30 cases, the synthesized program only extracted a
 subset of the desired lines.
@@
 was 28\%.
+% TODO: Perhaps we should call it partially successful? Let's
+% discuss this in a meeting
 \Cref{lst:pbe-unsuccessful} shows how an example of such
-an \emph{unsuccessful retrieval}, where the synthesized program only
+an \emph{unsuccessful retrieval} looks like. In it, the synthesized program only
 retrieved two of the four targeted lines.
 In 173 of the 400 cases
-could PROSE not synthesize program consistent with all of the training
+could PROSE not synthesize a program consistent with all of the training
 examples.
+
+% TODO introudce this fig at large. Soemthing like: Zooming in
+% on only the successful retrievals from (...), Fig ... shows ...
 
@@
 
+% TODO what about referencing the combined figure at first: something like shows the results of CTS on two beanplots of ... and ...., and then the subfigure
+% TODO this goes for all techniques
 \Cref{fig:recall-precision-examplecount-CTS} presents precision,
@@
 For more than two structural
-categories no clear trend is visible in precision, recall or
+categories no clear trend is visible in precision, recall, or
 F$_{1}$-score.
 
+% TODO Perhaps, above in our section about logchunks, we would need some
+% basic empirical stats -- e.g., how long are the files and how much
+% do we usually extract from the log
 \subsection{Random Line Retrieval}
@@
 
-In our evaluation, we compare against a baseline of randomly
-picking lines from the build log.
-Its results follow intuitive
-expectations:
-The precision ranges between 8\% and 5\%, the recall between 6\% and
+The baseline of randomly
+picking lines from build logs delivers the expected low and ``random'' results: precision ranges between 8\% and 5\% and recall between 6\% and
 8\%.
-The size of the training set has no visible impact on either.
-A larger number of structural categories within the training and
-test sets decreased the precision of RLR from 7\% to 0\%, the recall
+% TODO (resolved) visible is a tricky word here since the reader can specifically
+% NOT see this
+% TODO impact on what?
+As expected, the size of the training set has no impact on.
+% TODO (resolved) this explanation implies causality where there is none. 
+With a larger number of structural categories within the training and
+test sets, the precision of RLR decreases from 7\% to 0\%. Its recall
 increases from 6\%, for one structural category present, to 11\%, for
-three structural categories present and also drops to 0\% for more
+three structural categories present and drops to 0\% again for more
 structural categories. 
@@
 \subsection{Comparison of All Techniques}
-Next, we aggregate the results from
+In this section, we aggreagte and compare the results from
 \Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr}.
 
+% TODO 
 \Cref{fig:success-partial-all} compares the success of chunk
 retrievals differentiated by techniques in our study.
+% TODO It shows on the vertical axis the number of ?runs? ... and on the horizontal ...
 CTS and KWS
@@
 
+% TODO ``being present'' sounds cumbersome (and the other one is grammatically flawed)
+% , what about just removing it?
 \Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of a single structural category present in the
-training examples compared to multiple categories present.
+show the influence of a single structural category being present in the
+training examples compared to multiple categories being present.
 For more
 than one category being present, the recall of PBE decreases greatly.
+% TODO this is not a meaningful comparsion to RLR. One would be to say that
+% all of these techniques beat RLR handsdown
 For CTS and KWS the values also decrease, while RLR is not affected by
@@
 
+% TODO This sentence is too long and complicated for an intro (and something
+% is broken in it, too)
+% TODO decision tree -> recommendation schema? You can use the more specific decision
+% tree when referencing the figure.
 For the interpretation of our study results, we look at each chunk
@@
 \subsection{Interpretation of Study Results}
+% TODO This is bad style. Begin the section by saying what you do in there
+% Then at the end, say that you summarized it in Table 3 (or include Table 3
+% in the discussion throughout the text.)
 \Cref{tab:single-technique-recommendations} summarizes the
@@
   \toprule
-  & PBE & CTS & KWS \\
+  & \textbf{PBE} & \textbf{CTS} & \textbf{KWS} \\
   \midrule
-  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\
+  \textbf{Structural categories} & 1 & less is better & \makecell[l]{best 1 \\
   multiple okay} \\
-  Training Set Size & 2 & no influence & 2 \\
-  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium &
+  \midrule
+  \textbf{Training set size} & 2 & no influence & 2 \\
+    \midrule
+  \textbf{Precision} & \makecell[l]{high \\ (if synthesis succeeds)} & medium &
   low \\
-  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium &
+    \midrule
+  \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} & medium &
   high \\
-  \makecell[l]{Confidence in \\ Output Correctness} & high & low &
-  \makecell[l]{low (precision) \\ high (recall)} \\
-  Output Consumption by & program & human & human \\
+    \midrule
+  \makecell[l]{\textbf{Confidence in} \\ \textbf{Output correctness}} & high & low &
+  \makecell[l]{low (precision) \\ high (recall)} \\     \midrule 
+  \textbf{Output consumer} & program & human & human \\
   \bottomrule
@@
 \noindent
-\textbf{Configuration and Input}
+\textbf{Configuration and Input.}
 Our study results show that chunk retrieval with PBE gives best
@@
 examples did not improve the chunk retrieval.
+% TODO: Why uncomment the following? Is it not true? I think it is crucial.
 % In fact, unless they
@@
 \noindent
-\textbf{Retrieval Output Usage}
+\textbf{Retrieval Output Usage.}
 If the program synthesis succeeds and applying the regular expression
@@
 \noindent
-\textbf{Configuration and Input}
+\textbf{Configuration and Input.}
 Similar to PBE, chunk retrieval using CTS yields better results the
@@
 \noindent
-\textbf{Retrieval Output Usage}
+\textbf{Retrieval Output Usage.}
 CTS has good precision and recall on average, though with a high
@@
 \noindent
-\textbf{Configuration and Input}
+\textbf{Configuration and Input.}
 KWS has a higher recall than the two other techniques for multiple
@@
 \textbf{Retrieval Output Usage}
-While KWS has the highest recall of all three techniques, its
+While KWS has the highest reca.ll of all three techniques, its
 precision is the lowest.
@@
 \subsection{Recommendation of Suitable Techniques}
+% TODO Make intor less generic?
 After discussing the three chunk retrieval techniques separately we
 now want to unify our results into one recommendation scheme.
-Figure~\ref{fig:crt-recommendation} presents a decision tree
+% TODO Try to inductiviely let the figure emerge from the text, not this
+% ``here is the figure; eat it''.
+% C: ``How should I do this?''
+% Already a better solution would be at the end of this section: We
+% summarized these conditions in the decision tree in Fig ...
+\Cref{fig:crt-recommendation} presents a decision tree
 to answer our second research question;
@@
 
+% TODO this is too prominent and the style is reserved for RQs ...
+% shouldn't it also better be in threats to validity?
 \begin{simplebox}[minipage boxed title*=-7cm]{Caveat!}
@@
 
+% TODO for what?
 The first and most important aspect are the structural categories.
@@
 to use KWS\@.
-If precision is more important than recall to the user we
+If precision is more important than recall, we
 recommend CTS\@.
@@
 
-\subsection{Examples of Using the Recommendation Scheme}
+\subsection{Using the Recommendation Scheme}
+% TODO Perhaps add introduction from recommendation scheme here?
+
+% TODO this is very nice again, perhaps a tiny bit on the trivial side.
+% Do reference Figure 17 more, thoguh
 To illustrate how one would use our decision tree to find a suitable
@@
 from one structural category.
-Therefore the development team can use
+Therefore, the development team can use
 PBE to retrieve the duration of a build phase.
 
-In our second example, a researcher studies whether test failures
-are caused by a small or by a large group of test cases.
+In our second example, a researcher wants to investigate whether a small or large group of test cases
+causes build failures.
+% TODO They?
 They gather
-CI build logs from various projects, which are their only available
-data source.
+CI build logs from various projects.
 The task of the researcher is to extract the names of the
 failing test cases from each build log.
+% TODO They?
 When they use our
@@
 retrieved.
-Therefore, our decision tree recommends to the researcher to use KWS\@.
+Therefore, our decision tree recommends the researcher to use KWS\@.
 
@@
 
-\textbf{Implementation}
+\textbf{Implementation.}
 Our results depend on the implementation of the investigated chunk
@@
 
-\textbf{Data Set}
+% TODO something like overall, we argue that our implementations and their
+% weaknesses stand prototypical for the techniques and tried to limit
+% idiosyncrazies as much as possible (give example)
+
+\textbf{Data Set.}
 The outcomes of our comparison study are highly dependent on the build
@@
 not popular in open source development.
-However, \emph{LogChunks} covers a wide array of build tools,
-we believe that our findings can be generalized.
+However, since \emph{LogChunks} covers a wide array of build tools and programming languages,
+we believe that our findings do generalize.
 We collected build logs from Travis CI.
 Yet, the format of the log chunk we chose
-for our evaluation is not dependent on Travis CI\@.
+for our evaluation is largely independent of Travis CI\@.
 This
@@
 
-\textbf{Training Set Size}
+\textbf{Training Set Size.}
 Especially the results for CTS might be influenced by the fact that we
@@
 \section{Future Work}
+% TODO Actually, this future work is very, *very* good. It might be
+% the best future work I have ever read in an article.
+% One idea would be to sell it as such and tie a bit back to our
+% first literature sruvey. You can say you give a roadmap to guide
+% future research in the field, and sell it in abstract and intro!
 
@@
 \textbf{Systematic Survey of Industry Approaches for Build
-Log Analysis}
+Log Analysis.}
 Our survey is limited to academic work and articles.
@@
 
-\textbf{Further Analysis of \emph{LogChunks}}
+\textbf{Further Analysis of \emph{LogChunks}.}
 We created the
@@
 
-\textbf{Cross-Repository Build Log Analysis}
+\textbf{Cross-Repository Build Log Analysis.}
 We trained and
@@
 across repositories, building the cornerstones for build
-environment-agnostic analysis tools.
-
-\textbf{Comparison with more Chunk Retrieval Techniques}
+environment-agnostic analysis tools. This has the advantage of creating
+a default build log analyzer that would work without any pre-training.
+
+\textbf{Comparison with more Chunk Retrieval Techniques.}
 This
@@
 
-\textbf{Refinement of Retrieval Quality for each Technique} We
+\textbf{Refinement of Retrieval Quality for each Technique.} We
 investigated basic configurations of existing techniques applied to
@@
 \begin{itemize}[leftmargin=0.4cm]
-  \item \textbf{Custom Ranking and Tokens for PBE} The program
+  \item \textbf{Custom Ranking and Tokens for PBE.} The program
   synthesis through PROSE ranks possible programs according to
@@
   One could extend these
-  with tokens found in build logs, such as ``-'',
-	``='', ``ERROR''
+  with tokens found in build logs, such as ``-,''
+	``=,'' ``ERROR,''
   or ``[OK''.
-  \item \textbf{Meta-Parameter Optimization for CTS} Information
+  \item \textbf{Meta-Parameter Optimization for CTS.} Information
   retrieval techniques have various meta-parameters which can be
@@
 
-\textbf{Usability Analysis of Chunk Retrieval Output}
+\textbf{Usability Analysis of Chunk Retrieval Output.}
 Our
@@
 precision and recall.
-The next step would be to investigate how useful these
-outputs are to developers through controlled experiments.
+A next step could be to investigate how useful these
+outputs really are to developers through controlled experiments or user studies.
 
@@
 \label{sec:conclusion-fw}
+% TODO conclusion should be a bit longer and a little bit more in
+% detail. Mention general accuracy measures (techniques performed
+% up to in F1 score, which is x times better than RLR)
+% TODO could also mention future research here: Finally, we gave an
+% outline to guide future research efforts in the area of build log
+% analysis.
 The goal of this paper was to support researchers and developers in
 their decision on how to analyze build logs.
-We conducted a systematic mapping study to uncover the
+To this end, we conducted a systematic mapping study to uncover the
 state-of-research on build log analysis.
 We implemented	three promising chunk retrieval techniques and
-compared them on our data set
-\emph{LogChunks}, composed of 797 manually labeled build logs from a
-broad range of 80 repositories.
+compared their performance on the \emph{LogChunks} data set.
 Our results show that the structural
@@
 the task at hand.
-
-As a final recommendation, one could create a ``super analyzer'' by
-combining the different build log analysis techniques studied in this
-paper.

### 2020-04-22 tse-paper/paper.tex
Mega review done

@@
 % The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
+\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~14, No.~8, August~2015}%
 {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}

### 2020-04-23 tse-paper/content.tex
easy fixes and prio

@@
 % \section{Introduction}
-% Todo: Introduction structure
-% 0) we introduce & define the problem 1) we survey which techniques
-% exist 2) we implement (for a lack of readily available implementations)
-% and compare the most promising ones 3) we draw conclusions for when to
-% use which technique
-
 % TODO: Include term predictive CI, link to FB paper and
@@
   \item \textbf{Common Text Similarity (CTS)}
-  % TODO what is the vector space model?
-  Using the Vector Space Model, CTS selects lines of a log which are
+  CTS selects lines of a log which are
   most similar to the lines present in manually supplied example chunks.
   \item \textbf{Keyword Search (KWS)}
-  % TODO what is an ad-hoc method?
-  Ad-hoc method for finding fitting passages by searching the whole
+  KWS finds fitting passages by searching the whole
   text of a build log for
@@
 \label{sec:system-log-analysis}
-A field related to build log analysis is the processing of system logs produced during runtime of the system.
+A field related to build log analysis is the analysis of system
+logs which are produced during runtime of the system.
 The first difference here is that build logs are produced during runtime
@@
 % TODO this explanation is not understandable.
-It needs to better embedded in the surrounding text
+%It needs to better embedded in the surrounding text
 One example is comparing execution traces to reference
@@
 (2020-03-15).
-Our replication package documents the full search
-queries~\cite{brandt2020chunk-replication}.
+% Our replication package documents the full search
+% queries~\cite{brandt2020chunk-replication}.
 To make handling so many search results feasible, we employed a
@@
 contextual information Google Scholar displayed.
-We included works at large that seemed to bear a resemblence to software
+We included works at large that seemed to bear a resemblance to software
 engineering and building software.
-We excluded wroks written in a language unintelligible to the authors
+We excluded works written in a language unintelligible to the authors
 (i.e., not English or German), which disregarded fewer than 1\% of search
@@
 
-% TODO (resolved): RQs mentioned before explicitly stated
 Specifically, we were interested in
@@
 Of these, we only considered the earliest article which reported on
-the processing of build logs.
+the analyzing of build logs.
 This excluded another 11 articles.
@@
 % TODO: add more concrete example, such as use of retrieved x: developer
-feedback, build data set
+%feedback, build data set
 Once we had classified all works, we went into the second phase
@@
 
-% TODO (resolved): RQs just appeared unconnected out of the blue
-
-% TODO: vertical alignment of rows with text to middle so they are aligned with pictograms on the right?
 \addtolength{\tabcolsep}{-5pt}
@@
 \begin{tabularx}{\textwidth}{@{}lXl@{}}
+
 \toprule
@@
 \midrule
-Parser	&
+
+\raisebox{0.8mm}{Parser} &
+\raisebox{0.8mm}{
 \cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
-&
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
 \\
-Regular expression
-&\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
-&
+
+\raisebox{0.8mm}{Regular expression} &
+\raisebox{0.8mm}{
+\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
 \\
-Manual inspection  &
+
+\raisebox{0.8mm}{Manual inspection} &
+\raisebox{0.8mm}{
 \cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
-&
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
 \\
-Machine Learning  &
+
+\raisebox{0.8mm}{Machine Learning} &
+\raisebox{0.8mm}{
 \cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
-&
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
 \\
-\makecell[cl]{Natural Language Processing}	&
-\cite{hassan2017change,lou2019history,schulz2017active} &
+
+\raisebox{0.8mm}{Natural Language Processing}	&
+\raisebox{0.8mm}{
+\cite{hassan2017change,lou2019history,schulz2017active}
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
-Information Retrieval  &
-\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
+
+\raisebox{0.8mm}{Information Retrieval} &
+\raisebox{0.8mm}{
+\cite{hassan2017change,lindqvist2019detection,ren2018automated}
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
-Analysis  &
-\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
+
+\raisebox{0.8mm}{Analysis} &
+\raisebox{0.8mm}{
+\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
-Keyword Search	&
-\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
+
+\raisebox{0.8mm}{Keyword Search} &
+\raisebox{0.8mm}{
+\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool}
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
-Scan  & \cite{clemencic2014new,hibbard2001visualization} &
+
+\raisebox{0.8mm}{Scan} &
+\raisebox{0.8mm}{
+\cite{clemencic2014new,hibbard2001visualization}
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
 \\
-Other  &
+
+\raisebox{0.8mm}{Other} &
+\raisebox{0.8mm}{
 \cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
-&
+} &
 \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
 \\
-None identified  &
+
+\raisebox{0.8mm}{None identified} &
+\raisebox{0.8mm}{
 \cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
-&
+} &
 \\
-\bottomrule
+
+\specialrule{\heavyrulewidth}{0pt}{2pt}
+
 \end{tabularx}
@@
 
-% TODO repeat the question in the subsection title?
-\subsubsection{Retrieved Information (RQ 1.1)}
+\subsubsection{Which information is targeted? (RQ 1.1)}
 % TODO General ref to Figure 4 missing: We answer this question along
@@
 % TODO It is unclear where this comes from.
-% TODO Also, wouldn't it perhaps be better to continue with Figure 4.b directly?
+% TODO Also, wouldn't it perhaps be better to continue with Figure
+4.b directly?
 In most cases (51\%), a chunk was retrieved from the log.
@@
 analysis for research purposes, as shown in \Cref{fig:litsur:use}.
-% TOOD What does this mean? Give an example: to drive further research,
+% TODO What does this mean? Give an example: to drive further research,
+FIXME
 for example to categorize the types of compile errors encountered at
-Google~\cite{}.
+Google~\cite{seo2014programmers}.
 Further uses were giving feedback to developers (10\%) or automatic
@@
 % TODO for example to ...
+FIXME
 .
 
-% TODO repeat the question in the subsection title?
-\subsubsection{Retrieval Technique (RQ 1.2)}
+\subsubsection{Which techniques are used? (RQ 1.2)}
 \Cref{tab:litsur:techniques} presents the techniques that the articles
-% TODO: lets use analyzing build logs canonically? Please search text
-to eliminate occurrences of processing?
-described for processing build logs.
-% TODO This is weird.
-Last number we have from above is 51.
-43 of the 61 articles we inspected mentioned how they are analyzing build
-logs.
+described for analyzing build logs.
+43 of the 61 articles we inspected mentioned how they are analyzing
+build logs.
 However, only 16 of these described their method in detail.
@@
 included
-rather imprecise statements like ``we parse the build logs.''
-% TODO include citation?
-% TOOD maybe make the point here that it is questionable whether this
-includes a comprehensive tokenizer, lexer etc.
+rather imprecise statements like ``we parse the build logs''
+~\cite{rahman2018impact}.
+% TODO maybe make the point here that it is questionable whether this
+%includes a comprehensive tokenizer, lexer etc.
 based solution and that parsing in many cases really meant regexp.
@@
 an extended version of them~\cite{rott2019empirische,
-shi2018evaluating} (based on regular expressions),
+shi2018evaluating}
+% (based on regular expressions),
 two used the
 \emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
-% TODO: based on which technique?,
+% based on which technique?,  (based on regular expressions)
 another two the
 \emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool
-% TODO: based on which technique?
+% based on which technique?  (a parser for the output of make files)
 .
-
-\subsubsection{Build Logs}
-% TODO using passive where it is unneccessary
-The distribution of supported build tools is shown in
-\Cref{fig:litsur:log_producer}.
+% I don't think the based on..
+adds something here.
+
+% It's all kinda regex.
+Even if we say 'parser' it's often regex in the background
+
+\subsubsection{Which build logs are analyzed? (RQ 1.3)}
+\Cref{fig:litsur:log_producer} shows the distribution of supported
+build tools.
 Of the articles we surveyed, 30\% analyzed build logs produced by
@@
 % TODO remove first part of this paragraph?
-Sometimes this limitation to a specific build tool is motivated by
-aspects separate from the build log analysis.
+Sometimes, aspects separate from the build log analysis motivate
+this limitation to a specific build tool.
 For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
@@
 
-% TODO death by passive
-The main platform that build logs were collected from is Travis
-CI~\cite{travisci2019webpage},
-which was used in 38\% cases.
+In 38\% of cases, the articles collected build logs from Travis
+CI~\cite{travisci2019webpage}.
 18\% of the articles processed logs from TravisTorrent and 8\% included
@@
 % TODO perhaps remove this paragraph?
+% yes it is very unspecific.
+however then we have 0 reference
+% to how many logs are analyzed
+% a central point in our argumentation for automation
 The number of logs analyzed varied greatly and we were not always able to
 extract it confidently.
-Articles reported processing from two up to 122 million logs.
+Articles reported analyzing from two up to 122 million logs.
 
@@
 \label{sec:lit-sur:discussion}
-% TODO we are extracting failures in the following studies, which is mainly what
+% TODO we are extracting failures in the following studies, which is
+mainly what
 % literature does, too, right? Highlight here and mention later again
@@
 % TODO: draw a conclusion together with figure 5: if reuse were higher,
-lots of effort could be saved?
+%lots of effort could be saved?
 % discussion about popularity of replication packages adds nothing to
@@
 (b) the large tail of seldomly-investigated environments would benefit
-from the existance of a more generic
+from the existence of a more generic
 solution.
@@
 % TODO: the following paragraphs have nothing to do with a discussion
-of the literature survey results.
+%of the literature survey results.
 % what we need is some derivation of the three techniques 1) regex 2)
-cts 3) kws, best repeated here in the discussion and then from the lit
-survey above, section 2.4.2
+%cts 3) kws, best repeated here in the discussion and then from the lit
+%survey above, section 2.4.2
 For this reason, we are focussing on techniques that run automatically
@@
 
-% TODO this is not enough for Table 3. Where does it come from?
+% TODO this is not enough for Table 3.
+Where does it come from?
 % How did it originate? Also: never single sentence abstracts
@@
 
-% TODO Somehow, we have to find a better place for this. We have been
+% TODO Somehow, we have to find a better place for this.
+We have been
 % using the term 'chunk retrieval' beforehand already -- this
-% definition now comes to late. The first paragraph should already
+% definition now comes to late.
+The first paragraph should already
 % apply to the literature mapping, the second of course only applies
@@
 error message ``no program found.''
-% TODO Figure 7 should not come before Figure 6. Figure 6 and 7 should be
-% introduced first. This is best-practice anyway: Whenever you mention
-% a figure/table the standard sentence should always be: Figure X shows Y,
-% on the vertical axis Z and on the horizontal axis D.
-
-\Cref{lst:prose-program-simplified} presents a simplified version
-of a program learned from the examples in \Cref{lst:chunk-example}.
 
@@
 % program can be synthesized?
+% TODO Moritz: a regular expression can match an empty string
+% and that is different from not finding a match
+% it returns error messages in both cases
 \subsubsection{Application}
@@
 marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-We investigate a chunk retrieval technique based on the common
-% TODO: the ominuous Vector Space Model again ...
-Vector Space Model~\cite{schutze2008introduction}.
-The aim is to retrieve those lines from a build log which are most
+We investigate a chunk retrieval technique that
+retrieve those lines from a build log which are most
 similar to examples given by the user.
@@
 the same concept of examples as for PBE
-% TODO Moritz: your question was: More details on this.
+% Moritz: your question was: More details on this.
 % How do you
@@
 % I added a "as follows", think that is enough for explanation?
-% TODO: I think it is good, but the VSM is still unexplained. We need a
+% Moritz: I think it is good, but the VSM is still unexplained.
+We need a
 % (at least) 1-sentence introduction to it, at its first reference
+% TODO Moritz: I removed all other references, this is now the first one.
+% I hope I got your comment right and now the first and only reference
+% is explained :)
 and apply the Vector Space Model~\cite{schutze2008introduction}
@@
 
-To fully comprehend how difficult a task build log analysis really is without any a-priori knowledge, we include a comparison with a base line generated by Random Line Retrieval (RLR), that is,
+To fully comprehend how difficult a task build log analysis really
+is without any a-priori knowledge, we include a comparison with a
+base line generated by Random Line Retrieval (RLR), that is,
 picking lines randomly from the build log.
@@
 returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples, thus arguably giving it a slight advantage.
-
-% TODO Moritz: you said: some more details here?
-% I would not know of any details to add.
-%It's really all we are doing
-% TODO: You are right, nothing more is necessary
-
-% TODO: these next two sections do not belong under this section -- they are not a chunk retrieval technique. One way to fix it would be to rename the section.
+number of lines in the chunks of the training examples, thus arguably
+giving it a slight advantage.
+
+% TODO: these next two sections do not belong under this section --
+they are not a chunk retrieval technique.
+One way to fix it would be to rename the section.
 \subsection{Chunk Retrieval Example}
@@
   build failed.}
-  % TODO Moritz: we can relate this to travistorrent maybe, you told me
-  % long ago that this was something your analyzer cannot extract
   \label{lst:chunk-example}
@@
 R and the text2vec library~\cite{text2vec2019webpage}.
-% TODO and passive again ...
-The source code of the implementation can be found in our replication
-package~\cite{brandt2020chunk-replication} together
-with ready-to-use Docker images.
 
@@
 
-% TODO This section is not structured well. First, it misses an
-% explanation of the bigger study design.  Second, What is the difference between Study Process and
+% TODO This section is not structured well.
+First, it misses an
+% explanation of the bigger study design.
+Second, What is the difference between Study Process and
 % Study Design? Third, the LogChunks section appears out of nowhere
 % and is not related to the section title (different abstraction
-% level).  Perhaps a solution would be to be a bit inspired by this
+% level).
+Perhaps a solution would be to be a bit inspired by this
 % paper:
-% https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
+%
+https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
 % There is a research design section (which we are missing) and a
@@
 has to be (\textbf{RQ2.2}) and how reliable the quality of the
-produced outputs is (\textbf{RQ2.3}). This leads us to the following research questions:
+produced outputs is (\textbf{RQ2.3}).
+This leads us to the following research questions:
 
@@
 that correspond to one GitHub repository---and thus the
-% TODO () is meant to reference the figure, but this the figure is not actually mentioned.
+% TODO () is meant to reference the figure, but this the figure is not
+actually mentioned.
 same build environment (1).
-% TODO: What does this mean? Of what nature are the examples? How were they chosen?
-% Isn't it rather the case that for each repository, we built traning sets of size 1, 2,
-% ... 5 build logs?
+% TODO: What does this mean? Of what nature are the examples? How were
+they chosen?
+% Isn't it rather the case that for each repository, we built traning
+sets of size 1, 2,
+% ...
+5 build logs?
 One to five examples make up the training set (2).
@@
 (see \Cref{sec:lit-sur:discussion}).
-% TODO: The example? why only one? And what is an example? An example build log?
+% TODO: The example? why only one? And what is an example? An example
+build log?
 % Then it would be good to say so.
@@
 should receive reliable results on every build log they analyze.
-% TODO and why is this important? Doesn't everyone want such stability of results?
+% TODO and why is this important? Doesn't everyone want such stability
+of results?
 In the next step, we configure a chunk retrieval technique with
@@
 % This is a weird position for this paragraph
-% TODO What is ``this'' referring to? You just defined a bunch of equations.
+% TODO What is ``this'' referring to? You just defined a bunch of
+equations.
 This concludes one execution within our evaluation.
-% TODO run vs. execution above.
+% TODO run vs.
+execution above.
 We conduct one run for each of the four chunk retrieval techniques,
@@
 and for each of the five training set sizes (2).
-In total we perform 1600 runs, 400 for each of the implemented chunk retrieval
+In total we perform 1600 runs, 400 for each of the implemented chunk
+retrieval
 technique.
@@
 technique separately.
-Afterwards, we compare the three techniques with each other and to RLR as a
+Afterwards, we compare the three techniques with each other and to RLR
+as a
 baseline.
@@
 \Cref{lst:pbe-unsuccessful} shows how an example of such
-an \emph{unsuccessful retrieval} looks like. In it, the synthesized program only
+an \emph{unsuccessful retrieval} looks like.
+In it, the synthesized program only
 retrieved two of the four targeted lines.
@@
 
-% TODO introudce this fig at large. Soemthing like: Zooming in
-% on only the successful retrievals from (...), Fig ... shows ...
+% TODO introudce this fig at large.
+Soemthing like: Zooming in
+% on only the successful retrievals from (...), Fig ...
+shows ...
 
@@
 
-% TODO what about referencing the combined figure at first: something like shows the results of CTS on two beanplots of ... and ...., and then the subfigure
+% TODO what about referencing the combined figure at first: something
+like shows the results of CTS on two beanplots of ...
+and ...., and then the subfigure
 % TODO this goes for all techniques
@@
 The baseline of randomly
-picking lines from build logs delivers the expected low and ``random'' results: precision ranges between 8\% and 5\% and recall between 6\% and
-8\%.
-% TODO (resolved) visible is a tricky word here since the reader can specifically
-% NOT see this
-% TODO impact on what?
-As expected, the size of the training set has no impact on.
-% TODO (resolved) this explanation implies causality where there is none. 
+picking lines from build logs delivers the expected low and
+``random'' results: precision ranges between 8\% and 5\% and
+recall between 6\% and 8\%.
+As expected, the size of the training set has no impact on precision
+or recall of retrieving chunks with RLR.
 With a larger number of structural categories within the training and
-test sets, the precision of RLR decreases from 7\% to 0\%. Its recall
+test sets, the precision of RLR decreases from 7\% to 0\%.
+Its recall
 increases from 6\%, for one structural category present, to 11\%, for
@@
 structural categories.
-Graphs of these results of the chunk retrieval with RLR
-are included in our replication
-package~\cite{brandt2020chunk-replication}.
 
 \subsection{Comparison of All Techniques}
-In this section, we aggreagte and compare the results from
+In this section, we aggregate and compare the results from
 \Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr}.
@@
 retrievals differentiated by techniques in our study.
-% TODO It shows on the vertical axis the number of ?runs? ... and on the horizontal ...
+% TODO It shows on the vertical axis the number of ?runs? ...
+and on the horizontal ...
 CTS and KWS
@@
 
-% % The averaged precision, recall and F$_{1}$-score f all techniques is
-% % compared in Figure~\ref{fig:recall-precision-all}.
-% The recall of PBE
-% % has a high skew towards one and zero, meaning in most cases either
-% % the retrieval is successful or no relevant lines are extracted at
-% % all.
-% PBE has the highest average precision with 95\%.
-% Chunk
-% % retrieval with CTS has the highest average F$_{1}$-score with 51\%
-% % and the second highest recall with 46\%.
-% KWS has the smallest
-% % precision of the three chunk retrieval techniques.
-% With 16\% it is
-% % still higher than the precision of the RLR baseline with 7\%.
-% KWS
-% % has the highest recall of all techniques with 70\%.
-
-% TODO ``being present'' sounds cumbersome (and the other one is grammatically flawed)
-% , what about just removing it?
 \Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of a single structural category being present in the
-training examples compared to multiple categories being present.
+show the influence of all training and test examples being from the
+same structural category compared to being multiple categories
 For more
 than one category being present, the recall of PBE decreases greatly.
-% TODO this is not a meaningful comparsion to RLR. One would be to say that
+% TODO this is not a meaningful comparsion to RLR.
+One would be to say that
 % all of these techniques beat RLR handsdown
@@
 
-% TODO This sentence is too long and complicated for an intro (and something
-% is broken in it, too)
-% TODO decision tree -> recommendation schema? You can use the more specific decision
+% TODO decision tree -> recommendation schema? You can use the more
+specific decision
 % tree when referencing the figure.
 For the interpretation of our study results, we look at each chunk
-retrieval technique separately and give recommendations for
-which types of input build
-logs, available training examples and consumption of the retrieved
-output each technique is suited.
+retrieval technique separately.
+We give recommendations for
+which types of log chunks and how many training examples
+each technique is suited, and
+how their output can be used further.
 Following that, we discuss
@@
 \subsection{Interpretation of Study Results}
-% TODO This is bad style. Begin the section by saying what you do in there
-% Then at the end, say that you summarized it in Table 3 (or include Table 3
+% TODO This is bad style.
+Begin the section by saying what you do in there
+% Then at the end, say that you summarized it in Table 3 (or include
+Table 3
 % in the discussion throughout the text.)
@@
   \midrule
-  \textbf{Structural categories} & 1 & less is better & \makecell[l]{best 1 \\
+  \textbf{Structural categories} & 1 & less is better & \makecell[l]{best
+  1 \\
   multiple okay} \\
@@
     \midrule
-  \textbf{Precision} & \makecell[l]{high \\ (if synthesis succeeds)} & medium &
+  \textbf{Precision} & \makecell[l]{high \\ (if synthesis succeeds)} &
+  medium &
   low \\
     \midrule
-  \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} & medium &
+  \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} &
+  medium &
   high \\
     \midrule
-  \makecell[l]{\textbf{Confidence in} \\ \textbf{Output correctness}} & high & low &
+  \makecell[l]{\textbf{Confidence in} \\ \textbf{Output correctness}}
+  & high & low &
   \makecell[l]{low (precision) \\ high (recall)} \\	\midrule
@@
 Our study results show that chunk retrieval with PBE gives best
-results when the training examples are structurally identical.
+results when the log chunks are structurally identical.
 This is
@@
 When the training examples are of the same structure, one or two
-two examples are enough input for PROSE to synthesize a regular
+two training examples are enough input for PROSE to synthesize a regular
 expression program with good recall.
 In our study, additional training
-examples did not improve the chunk retrieval.
-% TODO: Why uncomment the following? Is it not true? I think it is crucial.
+examples from the same structural category
+did not improve the chunk retrieval.
+% Moritz: Why uncomment the following? Is it not true?
+% I think it is crucial.
 % In fact, unless they
@@
 % hindered the applicability of PBE.
+% TODO: it's true.
+Though this is because of the structural categories
+% which we discuss not in this paragraph but the one above.
 
@@
 \textbf{Retrieval Output Usage}
-While KWS has the highest reca.ll of all three techniques, its
+While KWS has the highest recall of all three techniques, its
 precision is the lowest.
@@
 
-% TODO this is too prominent and the style is reserved for RQs ...
 % shouldn't it also better be in threats to validity?
-\begin{simplebox}[minipage boxed title*=-7cm]{Caveat!}
+% it is as well.
+back for my thesis you said we should put it
+% directly here to make it more prominent avoid angry critics
+% I think it's good here
+% but it's also self-contained so feel free to comment it out
+\textbf{Caveat!}
 This is a preliminary hypothesis based on the results
@@
 data set.
-\end{simplebox}
-
-% TODO for what?
-The first and most important aspect are the structural categories.
+
+The first and most important aspect that influences a choice for
+a chunk retrieval technique are the structural categories.
 Are the targeted log chunks always presented in
@@
 
-In our second example, a researcher wants to investigate whether a small or large group of test cases
+In our second example, a researcher wants to investigate whether a small
+or large group of test cases
 causes build failures.
-% TODO They?
 They gather
@@
 failing test cases from each build log.
-% TODO They?
 When they use our
@@
 not popular in open source development.
-However, since \emph{LogChunks} covers a wide array of build tools and programming languages,
+However, since \emph{LogChunks} covers a wide array of build tools and
+programming languages,
 we believe that our findings do generalize.
@@
 \section{Future Work}
-% TODO Actually, this future work is very, *very* good. It might be
+% TODO Actually, this future work is very, *very* good.
+It might be
 % the best future work I have ever read in an article.
 % One idea would be to sell it as such and tie a bit back to our
-% first literature sruvey. You can say you give a roadmap to guide
+% first literature sruvey.
+You can say you give a roadmap to guide
 % future research in the field, and sell it in abstract and intro!
@@
 across repositories, building the cornerstones for build
-environment-agnostic analysis tools. This has the advantage of creating
+environment-agnostic analysis tools.
+This has the advantage of creating
 a default build log analyzer that would work without any pre-training.
@@
 A next step could be to investigate how useful these
-outputs really are to developers through controlled experiments or user studies.
+outputs really are to developers through controlled experiments or
+user studies.
 
@@
 % TODO conclusion should be a bit longer and a little bit more in
-% detail. Mention general accuracy measures (techniques performed
+% detail.
+Mention general accuracy measures (techniques performed
 % up to in F1 score, which is x times better than RLR)

### 2020-04-23 tse-paper/content.tex
oxford comma

@@
 
-Despite its central role for helping developers and the enablement of
-on-ward applications of build logs, the process of how to
+Despite its central role for helping developers and for enabling
+applications for on-ward processing of build logs,
+the process of how to
 automatically analyze build logs has thus far received little
@@
 less than half of the 61 works which rely on build log analysis
-describe in detail how they performed it, and even fewer
+describe in detail how they performed it.
+Even fewer
 made their implementation available.
@@
 context of multiple lines around a finding---makes it generally
-unsuited for automatic on-ward processing and instead requires a human
+unsuited for automatic on-ward processing.
+Instead, KWS requires a human
 to further inspect and interpret the output chunk.
 A hybrid-solution combining the three techniques might be the best
-allround solution.
+all-round solution.
 
@@
 Each line in a log file represents one event with a
-set of fields: timestamp, verbosity level and raw message
+set of fields: timestamp, verbosity level, and raw message
 content~\cite{he2017towards}.
@@
 venues~\cite{petersen2015guidelines}, but survey all sources
-monitored by Google Scholar, including Bachelor's and Master's
-theses and academic slide decks.
+monitored by Google Scholar, including Bachelor's theses, Master's
+theses, and academic slide decks.
 We use Google Scholar as opposed to Scopus or
@@
 The template form contained questions to answer RQ 1.1 through RQ 1.3,
-for example ``Is the technique explained in sufficient detail?'' and
-``What is the source of the build logs?'' As recommended by Petersen et
+for example ``Is the technique explained in detail?'' and
+``What is the source of the build logs?''.
+As recommended by Petersen et
 al.~\cite{petersen2015guidelines}, we started the mapping study with a
@@
 % TODO Also, wouldn't it perhaps be better to continue with Figure
-4.b directly?
+%4.b directly?
 In most cases (51\%), a chunk was retrieved from the log.
@@
 % TODO What does this mean? Give an example: to drive further research,
-FIXME
+%FIXME
 for example to categorize the types of compile errors encountered at
@@
 % TODO for example to ...
-FIXME
+%FIXME
 .
@@
 %includes a comprehensive tokenizer, lexer etc.
-based solution and that parsing in many cases really meant regexp.
+%based solution and that parsing in many cases really meant regexp.
 If we could figure that out, then we would assign it to regexp instead.
@@
 % I don't think the based on..
-adds something here.
-
+%adds something here.
 % It's all kinda regex.
-Even if we say 'parser' it's often regex in the background
+%Even if we say 'parser' it's often regex in the background
 
@@
 % yes it is very unspecific.
-however then we have 0 reference
+%however then we have 0 reference
 % to how many logs are analyzed
@@
 %lots of effort could be saved?
-% discussion about popularity of replication packages adds nothing to
-this paper.
 We observed very little reuse of build log analysis tools.
-This can stem from the fact that publishing replication packages and
-research prototypes became popular only in recent years or from the
+This can stem from the
 high specialization of the developed tools in regards to supported
@@
 From this, we follow: (a) there is a nichè for custom parsers or even
-specialized plugins integrated into the build process to make post-factum
+specialized plugins integrated into the build process to make
+post-factum
 parsing of logs redundant.
@@
 executions Bell et al.
+%TODO cite
 wrote, still have the disadvantage of not being able to work on historic
@@
 We chose text similarity (CTS) as a common information retrieval
-technique, and implement the ad-hoc approach of
+technique and implement the ad-hoc approach of
 searching for specific strings or keywords within KWS\@.
@@
 retrieval (RLR), illustrate the techniques on a concrete example
-of log chunks and sketch out implementation.
+of log chunks and sketch out their implementation.
 
@@
 % TODO Somehow, we have to find a better place for this.
-We have been
+%We have been
 % using the term 'chunk retrieval' beforehand already -- this
 % definition now comes to late.
-The first paragraph should already
+%The first paragraph should already
 % apply to the literature mapping, the second of course only applies
@@
 We call such pieces of information from build logs
-\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
+\emph{chunks} and the techniques \emph{chunk retrieval techniques}.
 The techniques we investigate here do not require a formal lexer and
@@
 % TODO: these next two sections do not belong under this section --
-they are not a chunk retrieval technique.
-One way to fix it would be to rename the section.
+%they are not a chunk retrieval technique.
+%One way to fix it would be to rename the section.
 \subsection{Chunk Retrieval Example}
@@
 % TODO This section is not structured well.
-First, it misses an
+%First, it misses an
 % explanation of the bigger study design.
-Second, What is the difference between Study Process and
+%Second, What is the difference between Study Process and
 % Study Design? Third, the LogChunks section appears out of nowhere
@@
 % level).
-Perhaps a solution would be to be a bit inspired by this
+%Perhaps a solution would be to be a bit inspired by this
 % paper:
-%
-https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
+%https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
 % There is a research design section (which we are missing) and a
@@
 how similar the structural representation of the targeted log chunks
-has to be (\textbf{RQ2.2}) and how reliable the quality of the
+has to be (\textbf{RQ2.2}), and how reliable the quality of the
 produced outputs is (\textbf{RQ2.3}).
@@
 In the following, we present the data set we created for this study,
-our study process (presented in \Cref{fig:study}) and the metrics
+our study process (presented in \Cref{fig:study}), and the metrics
 we measure to answer our research questions.
@@
 % TODO () is meant to reference the figure, but this the figure is not
-actually mentioned.
+%actually mentioned.
 same build environment (1).
 % TODO: What does this mean? Of what nature are the examples? How were
-they chosen?
+%they chosen?
 % Isn't it rather the case that for each repository, we built traning
-sets of size 1, 2,
+%ets of size 1, 2,
 % ...
-5 build logs?
+%5 build logs?
 One to five examples make up the training set (2).
@@
 % TODO: The example? why only one? And what is an example? An example
-build log?
+%build log?
 % Then it would be good to say so.
@@
 % TODO What is ``this'' referring to? You just defined a bunch of
-equations.
+%equations.
 This concludes one execution within our evaluation.
 % TODO run vs.
-execution above.
+%execution above.
 We conduct one run for each of the four chunk retrieval techniques,
@@
 Afterwards, we compare the three techniques with each other and to RLR
-as a
-baseline.
+as a baseline.
 
@@
 		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
-				\caption{Precision, recall and
+				\caption{Precision, recall, and
 				F$_{1}$-score when PBE could synthesize
@@
 % TODO introudce this fig at large.
-Soemthing like: Zooming in
+%Soemthing like: Zooming in
 % on only the successful retrievals from (...), Fig ...
-shows ...
+%shows ...
 
@@
 When the training set
-size increases from one to two, recall and F$_{1}$-score increase by
+size increases from one to two, recall, and F$_{1}$-score increase by
 about 25\%, precision increases by about 10\%.
 For two or more
-training examples, recall and F$_{1}$-score stay around 75\% and
+training examples, recall, and F$_{1}$-score stay around 75\% and
 precision around 96\%.
@@
 \end{subfigure}
-\caption{Precision, recall and F$_{1}$-score of chunk
+\caption{Precision, recall, and F$_{1}$-score of chunk
 retrieval with Common Text Similarity (CTS) compared by \ldots}
@@
 % TODO what about referencing the combined figure at first: something
-like shows the results of CTS on two beanplots of ...
-and ...., and then the subfigure
+%like shows the results of CTS on two beanplots of ...
+%and ...., and then the subfigure
 % TODO this goes for all techniques
 \Cref{fig:recall-precision-examplecount-CTS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using CTS for an
+recall, and F$_{1}$-score of chunk retrieval using CTS for an
 increasing number of training examples.
@@
 With increasing category count, precision,
-recall and F$_{1}$-score decrease.
+recall, and F$_{1}$-score decrease.
 % Especially for more than four
@@
 \end{subfigure}
-\caption{Precision, recall and F$_{1}$-score of chunk retrieval with
+\caption{Precision, recall, and F$_{1}$-score of chunk retrieval with
 Keyword Search (KWS) compared by \ldots}
@@
 \Cref{fig:recall-precision-examplecount-KWS} presents precision,
-recall and F$_{1}$-score of chunk retrieval using KWS for different
+recall, and F$_{1}$-score of chunk retrieval using KWS for different
 numbers of training examples.
@@
 picking lines from build logs delivers the expected low and
-``random'' results: precision ranges between 8\% and 5\% and
+``random'' results: precision ranges between 8\% and 5\%,
 recall between 6\% and 8\%.
@@
 \subsection{Comparison of All Techniques}
+%TODO too short
 In this section, we aggregate and compare the results from
@@
 % TODO this is not a meaningful comparsion to RLR.
-One would be to say that
+%One would be to say that
 % all of these techniques beat RLR handsdown
@@
 \end{subfigure}
-\caption{Precision, recall and F$_{1}$-score of all
+\caption{Precision, recall, and F$_{1}$-score of all
 techniques compared, split by structural category count.}
@@
 % TODO decision tree -> recommendation schema? You can use the more
-specific decision
+%specific decision
 % tree when referencing the figure.
@@
 which types of log chunks and how many training examples
-each technique is suited, and
+each technique is suited, as well as
 how their output can be used further.
@@
 % TODO This is bad style.
-Begin the section by saying what you do in there
+%Begin the section by saying what you do in there
 % Then at the end, say that you summarized it in Table 3 (or include
-Table 3
+%Table 3
 % in the discussion throughout the text.)
@@
 \subsection{Recommendation of Suitable Techniques}
-% TODO Make intor less generic?
+% TODO Make intro less generic?
 After discussing the three chunk retrieval techniques separately we
@@
 in R.
-We intentionally chose a simple, minimally configured and tuned
+We intentionally chose a simple, minimally configured or tuned
 approach to compare against.
@@
 % TODO Actually, this future work is very, *very* good.
-It might be
+%It might be
 % the best future work I have ever read in an article.
@@
 % first literature sruvey.
-You can say you give a roadmap to guide
+%You can say you give a roadmap to guide
 % future research in the field, and sell it in abstract and intro!
@@
 This
-paper investigates the three chunk retrieval techniques PBE, CTS and
+paper investigates the three chunk retrieval techniques PBE, CTS, and
 KWS\@.
@@
 approach by Amar et al.~\cite{amar2019mining}.
+% TODO: mention an actual chunk retrieval technique from the survey
+% if possible
 
@@
 % detail.
-Mention general accuracy measures (techniques performed
+%Mention general accuracy measures (techniques performed
 % up to in F1 score, which is x times better than RLR)

### 2020-04-23 tse-paper/content.tex
replace lots of ours

@@
 automatically analyze build logs has thus far received little
-attention as a separate research topic, bringing us to our first
+attention as a separate research topic, bringing us to the first
 research question:
@@
 
-To answer this question, we start our investigation by performing an
+To answer this question, we start the investigation by performing an
 extensive literature study (\Cref{fig:overview}).
@@
 
-To answer this question, in the second step of our study
+To answer this question, in the second step of the study
 (\Cref{fig:overview}), we build and compare three
@@
 \subsection{Study Selection}
-\Cref{fig:lit-survey} presents an overview of our study selection
+\Cref{fig:lit-survey} presents an overview of the study selection
 process.
@@
 surveyed as broad a population of scientific material as possible.
-We did not limit our sources to specific Software Engineering
+We did not limit the sources to specific Software Engineering
 venues~\cite{petersen2015guidelines}, but survey all sources
@@
 from unrelated fields such as construction and wood working.
-We refined our search criteria to exclude such obvious
+We refined the search criteria to exclude such obvious
 non-related fields and also to exclude works on systems
@@
 If an article referenced a new work in the context
-of build log analysis, we added the new one to our literature set.
+of build log analysis, we added the new one to the literature set.
 This added five articles (eight before
@@
 If a work showed traces of
-working with build logs, we included it in our survey.
+working with build logs, we included it in the survey.
 In total, we
@@
 and mutation score.
-A larger amount of the articles within our survey, however, limit
+A larger amount of the articles within the survey, however, limit
 themselves to few build tools because their log format varies and
@@
 build environments which enables us to measure the generic
-applicability of our techniques.
+applicability of the techniques.
 The targeted chunks are describing error messages or
@@
 example (PBE), common text similarity (CTS), and keyword search (KWS).
-In addition, we present our comparison baseline of random line
+In addition, we present a comparison baseline of random line
 retrieval (RLR), illustrate the techniques on a concrete example
@@
 % TODO this is not enough for Table 3.
-Where does it come from?
+%Where does it come from?
 % How did it originate? Also: never single sentence abstracts
@@
 % Moritz: I think it is good, but the VSM is still unexplained.
-We need a
+%We need a
 % (at least) 1-sentence introduction to it, at its first reference
@@
 The algorithm splits the search query into single lines and
-identifies tokens, in our case words.
+identifies tokens, in this case words.
 Then we build a
@@
 \emph{different structural category}.
-The results of our empirical comparison study on the chunk retrieval
+The results of the empirical comparison study on the chunk retrieval
 techniques
@@
 \subsection{Tool Implementation}
-For our comparison study, we implemented each of the chunk retrieval
+For the comparison study, we implemented each of the chunk retrieval
 techniques and a unifying interface.
@@
   clip]{img/study.pdf}
-	\caption{Design of our technique comparison study.}
+	\caption{Design of the technique comparison study.}
 	\label{fig:study}
@@
 more recent logs.
-We chose a test set size of 1, as users of our techniques
+We chose a test set size of 1, as users of the techniques
 should receive reliable results on every build log they analyze.
 % TODO and why is this important? Doesn't everyone want such stability
-of results?
+%of results?
 In the next step, we configure a chunk retrieval technique with
@@
 the lines of the retrieval output ($\mathit{RetrievedLines}$),
-and our oracle: the output defined in the test example
+and the oracle: the output defined in the test example
 ($\mathit{DesiredLines}$).
@@
 % tree when referencing the figure.
-For the interpretation of our study results, we look at each chunk
+For the interpretation of the study results, we look at each chunk
 retrieval technique separately.
@@
 chunk retrieval technique most.
-Based on our empirical comparison, we present a
+Based on the empirical comparison, we present a
 decision tree between the three techniques we investigated.
@@
 expression program with good recall.
-In our study, additional training
+In the study, additional training
 examples from the same structural category
@@
 The number of training examples had no noticeable influence on
-precision or recall in our study.
+precision or recall.
 Information retrieval techniques
 like text similarity commonly learn on a higher number of examples
-than used for our study.
-Future work is needed to investigate how many
+than we chose in the study.
+Future work should investigate how many
 examples yield improvements in the chunk retrieval over a single
@@
 After discussing the three chunk retrieval techniques separately we
-now want to unify our results into one recommendation scheme.
+now want to unify the results into one recommendation scheme.
 % TODO Try to inductiviely let the figure emerge from the text, not this
@@
 \Cref{fig:crt-recommendation} presents a decision tree
-to answer our second research question;
+to answer the second research question;
 If researchers or developers want to retrieve chunks from build logs,
@@
 % Do reference Figure 17 more, thoguh
-To illustrate how one would use our decision tree to find a suitable
+To illustrate how one would use the decision tree to find a suitable
 chunk retrieval technique we describe two concrete examples: a software
@@
 
-In our first example, a software development team wants to monitor
+In the first example, a software development team wants to monitor
 the performance of the phases within their CI build.
@@
 
-In our second example, a researcher wants to investigate whether a small
+In the second example, a researcher wants to investigate whether a small
 or large group of test cases
@@
 retrieved.
-Therefore, our decision tree recommends the researcher to use KWS\@.
+Therefore, the decision tree recommends the researcher to use KWS\@.
 
@@
 The
-idiosyncrasies of this framework influence our PBE results.
+idiosyncrasies of this framework influence the PBE results.
 Other
@@
 \textbf{Data Set.}
-The outcomes of our comparison study are highly dependent on the build
+The outcomes of the comparison study are highly dependent on the build
 logs from the \emph{LogChunks} data set.
@@
 programming languages,
-we believe that our findings do generalize.
+we believe that the findings do generalize.
 We collected build logs from Travis CI.
 Yet, the format of the log chunk we chose
-for our evaluation is largely independent of Travis CI\@.
+for the evaluation is largely independent of Travis CI\@.
 This
@@
 The fact that PBE and CTS performed best with already two training
-examples shows that our training set size is large enough to
+examples shows that the training set size is large enough to
 compare the three techniques we presented.
@@
 
-There are various future research opportunities based on our work:
+There are various future research opportunities based on the
+work we presented:
 

### 2020-04-23 tse-paper/content.tex
passives

@@
 (\Cref{fig:overview}), we build and compare three
-implementations that each stand protoypical for one of the idenitied
+implementations that each stand prototypical for one of the identified
 strategies to analyze build logs:
@@
 %based solution and that parsing in many cases really meant regexp.
-If we could figure that out, then we would assign it to regexp instead.
+%If we could figure that out, then we would assign it to regexp instead.
 25\% of the articles described the use of regular expressions and 20\%
@@
 build tools.
-Of the articles we surveyed, 30\% analyzed build logs produced by
-Maven~\cite{maven2019website}, 16\% analyzed logs produced by
-Gradle~\cite{gradle2020website}
-and 10\% analyzed logs produced by Ant~\cite{ant2020website}.
+Of the articles we surveyed, 30\% analyzed
+Maven~\cite{maven2019website} build logs,
+16\% analyzed Gradle~\cite{gradle2020website} logs
+and 10\% analyzed Ant~\cite{ant2020website} logs.
 
@@
 % TODO who is the user?
-and can be configured by the user with little effort.
+and can be configured by a user with little effort.
 % We achieve this by developing three techniques for which the
@@
 Examples consist of logs and corresponding chunks.
-The examples and keywords are provided by the user and can simply be
+The user provides these examples and keywords, which can simply be
 exchanged whenever new cases are introduced.
@@
 
-Our evaluation of the three chunk retrieval techniques is done on the
+We evaluate the three chunk retrieval techniques on the
 \emph{LogChunks} data set because it encompasses a broad range of
@@
 smallest piece of text it can return (e.g., a line, or a word).
-The
-granularity might be adjustable by configuration.
+% The
+% granularity might be adjustable by configuration.
 \emph{Running a
@@
 for build logs.
-Our implementation is based on the
-\emph{PROSE library}~\cite{prose2019webpage}.
-The PROSE library is powered by the generic program synthesis framework
+The \emph{PROSE library}~\cite{prose2019webpage} is the basis of
+our implementation.
+This library builds on the generic program synthesis framework
 \emph{FlashMeta}~\cite{polozov2015flashmeta:} and the specialized
@@
 a substring of the log file text, representing the
-substring that should be retrieved by the synthesized program when
+substring that the synthesized program should retrieve when
 given the corresponding input file.
@@
 because the regular expression
-necessary would be too complicated to synthesize, PBE returns the
+necessary is too complicated to synthesize, PBE returns the
 error message ``no program found.''
 
-% TODO Moritz: you said: The following is very obvious and could apply
+% Moritz: The following is very obvious and could apply
 % to any
@@
 % config/application?
-% TODO Why does it return an error message? Shouldn't it also return
+% Why does it return an error message? Shouldn't it also return
 % <empty string>? Does it not rather return an error message if no
@@
 is without any a-priori knowledge, we include a comparison with a
-base line generated by Random Line Retrieval (RLR), that is,
-picking lines randomly from the build log.
+base line of
+picking lines randomly from the build log (RLR).
 RLR mimics the
-situation of guessing blindly which lines might be interesting.
+situation of guessing blindly which lines are interesting.
 The only configuration option for RLR is the number of lines it should
@@
 
-When PBE is trained with these two examples, it produces
+When we train PBE with these two examples, it produces
 a regular expression program similar to the one presented in
@@
 crucial for regular expressions to identify a log chunk.
-In fact, if the third example from \Cref{lst:chunk-example-3},
+In fact, if we add the third example from \Cref{lst:chunk-example-3},
 which has a
-different structural representation, is added to the training set,
+different structural representation, to the training set,
 PBE is not able to synthesize a program and returns
@@
 
-KWS is configured with keywords that appear close to the chunk within
-the build log.
+Keywords that appear close to the chunk within
+the build log configure the technique KWS\@.
 For the examples from \Cref{lst:chunk-example} these could be
@@
 by searching for ``FAIL.''
-If KWS was to be trained with all three examples and the aforementioned
+If we train KWS with all three examples and the aforementioned
 associated keywords, it would search for the three keywords from
@@
 techniques and a unifying interface.
-The unified interface is implemented in Ruby and
+The unified interface is written in Ruby and
 calls the separate technique implementations over the command line.
@@
 sets, PBE extracted all desired lines successfully in 138 cases.
-In 59 cases, a regular expression program could be synthesized, though
+In 59 cases, PBE could synthesize a regular expression program, though
 it did not find match on the test build log.
@@
 The figure demonstrates that program synthesis mostly
-returns exactly the desired output when there are is only one
+returns exactly the desired output when there is only one
 structural category present in the training and test examples.
@@
 For more than two structural
-categories no clear trend is visible in precision, recall, or
+categories there is no clear trend in precision, recall, or
 F$_{1}$-score.
@@
 To extract for example the reason a build failed, the log
-passage describing the failure would always have to be started and
-ended the same way.
+passage describing the failure would always have to start and
+end the same way.
 
@@
 % it is as well.
-back for my thesis you said we should put it
+%back for my thesis you said we should put it
 % directly here to make it more prominent avoid angry critics
@@
 retrieval techniques and the libraries we used.
-Our implementation of
-PBE is based on the program synthesis provided by PROSE\@.
+The program synthesis provided by PROSE is the basis for our
+implementation of PBE\@.
 The
@@
 
-Our implementation of CTS is dependent on the library
+The library
 {\tt text2vec}~\cite{text2vec2019webpage}
-and the way it splits strings into word tokens.
+and the way it splits strings into word tokens is influencing
+our implementation of CTS\@.
 On the other hand,
@@
 \textbf{Data Set.}
-The outcomes of the comparison study are highly dependent on the build
-logs from the \emph{LogChunks} data set.
-It consists of build
+The build logs from the \emph{LogChunks} data set highly affect
+the outcomes of the comparison study.
+\emph{LogChunks} consists of build
 logs from open source projects and therefore it is not clear whether
@@
 We chose this small training set
-size as the training examples have to be provided per repository and
-we expect a developer to not want to provide more examples than the
+size as a user has to provide the training examples
+per repository or project.
+We expect a developer or a researcher
+to not want to provide more examples than the
 small numbers we evaluated on.
-The fact that PBE and CTS performed best with already two training
+% TODO maybe reference back to little effort technique in lit discus.
+The fact that PBE and KWS performed best with already two training
 examples shows that the training set size is large enough to
-compare the three techniques we presented.
+compare the three techniques.
 
@@
 Our
-analysis of the output produced by the chunk retrieval focuses on
+analysis of the chunk retrieval output focuses on
 precision and recall.

### 2020-04-24 tse-paper/content.tex
mention fw and update intro argumentation

@@
 The literature
-survey identifies three prevalent strategies to
-analyze build logs: Using 1) a set of
-manually curated regular expressions,
-similar to TravisTorrent~\cite{beller2017oops},
-2) information
-retrieval techniques,
-% TODO: Can you shortly explain the technique here?
-and 3) a list of search keywords
-to identify regions of interest in the build log.
-
-Even though these three approaches to retrieve information chunks from
+survey identifies various strategies to
+analyze build logs such as:
+custom built parsers, regular expressions, manual inspection,
+natural language processing, information retrieval or searching
+for keywords.
+%Using 1) a set of
+% manually curated regular expressions,
+% similar to TravisTorrent~\cite{beller2017oops},
+% 2) information
+% retrieval techniques,
+% % todo: Can you shortly explain the technique here?
+% and 3) a list of search keywords
+% to identify regions of interest in the build log.
+
+Even though these three approaches to analyze
 build logs have different strengths and weaknesses, the literature
@@
 As a consequence,
-in RQ2 we ask:
+in the second research question we ask:
 
@@
 To answer this question, in the second step of the study
-(\Cref{fig:overview}), we build and compare three
+(\Cref{fig:overview}), we choose three promising
+techniques to analyze build logs by retrieving substrings
+(chunks) that describe a specific information.
+
+We build and compare three
 implementations that each stand prototypical for one of the identified
@@
   Based on manually supplied example pairs of build logs and chunks,
-  PBE automatically
-  synthesizes
+  PBE automatically synthesizes
   a regular expression extracting the given chunks within the build logs.
+  % these second sentences about what the techniques stand for could
+  % also be merged to a paragraph after the itemize
+  PBE mimics regular expressions and parsers while
+  simplifying their development.
   \item \textbf{Common Text Similarity (CTS)}
+  Text similarity is a common information retrieval technique.
   CTS selects lines of a log which are
   most similar to the lines present in manually supplied example chunks.
+  As a common information retrieval technique, our text similarity
+  approach stands for the machine learning approaches identified in
+  the literature survey.
   \item \textbf{Keyword Search (KWS)}
@@
   the occurrence of specific trigger words.
+  Keyword Search was explicitly mentioned by several articles in the
+  literature survey.
 \end{itemize}
 
-In the third step, we conduct an empirical study to gauge the performance
-of
-these chunk retrieval techniques in
+In the third step (\Cref{fig:overview}),
+we conduct an empirical study to gauge the performance
+of these chunk retrieval techniques in
 real-world projects under a variety of conditions.
@@
 
-Finally, we develop a set of guidelines (step 4) on how to choose a
+We develop a set of guidelines (step 4, \Cref{fig:overview})
+on how to choose a
 technique given a goal.
@@
 precision and recall of the chunk retrieval is required.
-Results
-produced by PBE are suited for automatic on-ward processing.
+The results PBE produces are suited for automatic on-ward processing.
 CTS is
@@
 all-round solution.
+Finally, we give a roadmap to guide future research in the field
+of build log analysis.
 
@@
 analysis.
-\item three prototypical open-sourced implementations of the most
+\item three prototypical open-sourced implementations of
 promising chunk retrieval techniques.
@@
 \item systematic guidelines on when to use which technique.
+% TODO: is the future work good enough to put in contributions?
 \item a detailed replication package~\cite{brandt2020chunk-replication}.
@@
 \section{Future Work}
-% TODO Actually, this future work is very, *very* good.
+% Actually, this future work is very, *very* good.
 %It might be

### 2020-04-24 tse-paper/content.tex
bit of brainstorming and corrections

@@
 analysis.
-We first start with a differentiation to the related field of general
+We start with a differentiation to the related field of general
 system log analysis.
@@
 The first difference here is that build logs are produced during runtime
-of the build of the system, not the system itself.
+of the build of the system, not during runtime of the system itself.
 In terms of the contents of the logs, the main difference is that system
@@
 
-In principle, one can apply the techniques developed for system log
-analysis
-to parts of the build logs that have this same structure.
-% TODO this explanation is not understandable.
-%It needs to better embedded in the surrounding text
-One example is comparing execution traces to reference
-traces of intended behavior to detect anomalies.
-Amar et
-al.~\cite{amar2019mining} employed a similar approach to detect
-relevant lines in build logs.
+Some of the techniques developed to parse system logs can operate
+on build logs as well, such as methods to retrieve the
+values of variable parts in a log message, e.g.\ by using regular
+expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+% This is the easiest example matching here
+% amar et al are not in our literature survey
 However, almost all of the techniques developed to analyze system logs
@@
 bespoke approaches.
+% if included: this explanation is not understandable.
+% It needs to better embedded in the surrounding text
+% One example is comparing execution traces to reference
+% traces of intended behavior to detect anomalies.
+% Amar et
+% al.~\cite{amar2019mining} employed a similar approach to detect
+% relevant lines in build logs.
 % In this article, we focus on extracting a single specified information
@@
 % Chunk
-% retrieval techniques are used as a part of log parsing to retrieve the
-% values of variable parts in a log message, e.g.\ by using regular
-% expressions~\cite{nagappan2010abstracting,xu2009detecting}.
+% retrieval techniques are used as a part of log parsing
 
@@
 of a virtual open card sorting~\cite{zimmermann2016card}.
-
-% TODO: add more concrete example, such as use of retrieved x: developer
-%feedback, build data set
+An example for this is the source of the analyzed build logs,
+where we assigned tags such as ``Travis CI'',
+``Industrial'', ``Google'', or
+``self built''.
 Once we had classified all works, we went into the second phase
@@
 together and found synonyms.
-
-%The full data extraction template and our results of this step can be
-%found in our replication package~\cite{brandt2020chunk-replication}.
+% the following adds to the example but is maybe unneeded / too much
+For instance, in the case of the build log source we grouped
+``Travis'' and ``travis ci'' together and assigned ``Industrial'' to
+all articles that used build logs provided by a company.
+
+The full data extraction template and our results of this step can be
+found in our replication package~\cite{brandt2020chunk-replication}.
 
@@
 % TODO we are extracting failures in the following studies, which is
-mainly what
+%mainly what
 % literature does, too, right? Highlight here and mention later again
@@
 
+% TODO CARO
+% start by defining in more detail what a chunk retrieval technique is
+% or: characteristics that distinguishe them / to specify them further
+% (To Moritz: we have short definitions before, the first time we use
+% 'chunk', this is far to detailed to be earlier than here)
+% Following that we present each of the techniques in detail.
+
 This section introduces key concepts of the three chunk retrieval
@@
 
-% TODO this is not enough for Table 3.
+% TODO CARO this is not enough for Table 3.
 %Where does it come from?
@@
 \Cref{tab:ctr} shows a comparison of the implemented techniques.
-
-% TODO Somehow, we have to find a better place for this.
+% TODO CARO move to end of characteristics section and say that it is
+% summary of the techniques along the aspects introducted
+% can lead reading / understanding of the future sections
+
+% TODO QUESTION Somehow, we have to find a better place for this.
 %We have been
@@
 % than RLR?
+% TODO QUESTION: should I add those here? as references to the disc?
+% or in the discussion? (you also already added some)
+% In general: I think we talk a lot about RLR and it gets wordy.
 
@@
 %One way to fix it would be to rename the section.
+% TODO QUESTION: Caro show whole structure
+% -> introduction to crts, investigated techniques, ???
+
 \subsection{Chunk Retrieval Example}
@@
 One to five examples make up the training set (2).
-% TODO passive ...
-We vary its size to measure how many examples are needed to
+We vary its size to measure how many examples we need to
 confidently configure a technique.
@@
 %of results?
+% motivation why only one test example.
+we can also leave that out
+% and answer if we are asked about it
 In the next step, we configure a chunk retrieval technique with
@@
 %equations.
-This concludes one execution within our evaluation.
-% TODO run vs.
-%execution above.
+This concludes one run within our evaluation.
 We conduct one run for each of the four chunk retrieval techniques,
@@
 % discuss this in a meeting
+% TODO QUESTION: yes we can :)
 \Cref{lst:pbe-unsuccessful} shows how an example of such
@@
 % TODO this goes for all techniques
+% TODO QUESTION: yes, though then we have more redundant text
+% that repeats everywhere and is already in the captions
+% -> should we add it for the first time we include a type of figure?
 \Cref{fig:recall-precision-examplecount-CTS} presents precision,
@@
 %TODO too short
+% TODO CARO give outlook on results here
 In this section, we aggregate and compare the results from
@@
 
-% TODO
+% TODO CARO? check type of graph introduced
 \Cref{fig:success-partial-all} compares the success of chunk
@@
 % TODO It shows on the vertical axis the number of ?runs? ...
-and on the horizontal ...
+% and on the horizontal ...
 CTS and KWS
@@
 %One would be to say that
-% all of these techniques beat RLR handsdown
+% all of these techniques beat RLR handsdown -> discussion!
+% TODO QUESTOIN: well they don't in this picture (PBE, multiple sc)
+% maybe we can say that one figure earlier?
 For CTS and KWS the values also decrease, while RLR is not affected by
@@
 \subsection{Interpretation of Study Results}
-% TODO This is bad style.
+% TODO CARO
 %Begin the section by saying what you do in there
@@
 did not improve the chunk retrieval.
+% TODO QUESTION: maybe discuss this
 % Moritz: Why uncomment the following? Is it not true?
@@
 % TODO: it's true.
-Though this is because of the structural categories
+% Though this is because of the structural categories
 % which we discuss not in this paragraph but the one above.
@@
 \subsection{Recommendation of Suitable Techniques}
-% TODO Make intro less generic?
+% TODO CARO Make intro less generic?
 After discussing the three chunk retrieval techniques separately we
@@
 % C: ``How should I do this?''
+% TODO CARO
 % Already a better solution would be at the end of this section: We
 % summarized these conditions in the decision tree in Fig ...
+% also reference to the parts of the figure during the explanation
 \Cref{fig:crt-recommendation} presents a decision tree
@@
 
+% TODO QUESTION
 % shouldn't it also better be in threats to validity?
@@
 \subsection{Using the Recommendation Scheme}
+% TODO QUESTION: which one do you mean here?
 % TODO Perhaps add introduction from recommendation scheme here?
@@
 % TODO this is very nice again, perhaps a tiny bit on the trivial side.
-% Do reference Figure 17 more, thoguh
+% TODO CARO Do reference Figure 17 more, thoguh
 To illustrate how one would use the decision tree to find a suitable
@@
 % One idea would be to sell it as such and tie a bit back to our
-% first literature sruvey.
+% first literature survey.
 %You can say you give a roadmap to guide
@@
 \label{sec:conclusion-fw}
-% TODO conclusion should be a bit longer and a little bit more in
+% TODO CARO conclusion should be a bit longer and a little bit more in
 % detail.

### 2020-04-24 tse-paper/content.tex
Inline abstract

@@
 2}}
-What are the comparative strengths and weaknesses
-of promising build log analysis techniques?
+How do build log analysis techniques compare against each other?
 \end{simplebox}
@@
 \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
-{\textbf{RQ1:} What are the state-of-the-research
-techniques to analyze build logs?}
+{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
+% TODO (resolved): All of these are passive
+% TODO Swap RQ 1.2 and RQ 1.1 (logical order?)
 \begin{itemize}[leftmargin=2cm]
-  \item[\textbf{RQ1.1:}] Which information is targeted?
-  \item[\textbf{RQ1.2:}] Which techniques are used?
-  \item[\textbf{RQ1.3:}] Which build logs are analyzed?
+  \item[\textbf{RQ1.1:}] Which information in build logs is of interest?
+  \item[\textbf{RQ1.2:}] Which extraction techniques exist?
+  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to analysis?
 \end{itemize}
@@
 high specialization of the developed tools in regards to supported
+% TODO: build environments is used a bunch (also in the following), but
+% never defined.
 build environments and targeted information.
@@
 % using the term 'chunk retrieval' beforehand already -- this
-% definition now comes to late.
+% definition now comes too late.
 %The first paragraph should already
@@
 % % that is not possible in other techniques)
+% TODO Caro: Can you given an example of such an error message?
 % % otherwise yes, nothing interesting happens in the application of pbe
@@
 % it returns error messages in both cases
+% TODO: Ok, but what is the point of matching on an empty string (if I understand what you mean)? you would not normally define such an extraction?
+% If this distinction is important it needs to be made more clear 
 \subsubsection{Application}
@@
 attach boxed title to top center={yshift=-6mm}]
-{\textbf{RQ2:} What are the comparative strengths and weaknesses
-of promising build log analysis techniques?}
+{\textbf{RQ2:} How do build log analysis techniques compare against each other?}
 \begin{itemize}[leftmargin=1.2cm]
@@
 examples from the same structural category
-did not improve the chunk retrieval.
-% TODO QUESTION: maybe discuss this
-% Moritz: Why uncomment the following? Is it not true?
-% I think it is crucial.
-% In fact, unless they
-% were in some sense redundant, adding training examples above that even
-% hindered the applicability of PBE.
-% TODO: it's true.
-% Though this is because of the structural categories
-% which we discuss not in this paragraph but the one above.
+did not improve the chunk retrieval. In fact, unless they
+were in some sense redundant, adding more training examples even
+hindered the applicability of PBE.
 
@@
 
-\textbf{Few Samples with Many Structural Categories}
+\textbf{Few Samples with Many Structural Categories.}
 Our comparison study shows fewer measurements with many structural
-categories than with one structural category category
-(50.25\% one, 33.75\% two, 13.75\% more than two).
-This stems from the fact that we investigated the chunk retrieval
-techniques on a real-world data set, where there were mostly few
-structural categories within one project.
-In addition, a third of the measurements were conducted with two
-structural categories present and these already showed the negative
-effect of the number of structural categories on the performance
-of the chunk retrieval techniques.
+categories than with one structural category category (50.25\% one,
+33.75\% two, 13.75\% more than two).  This stems from the fact that we
+investigated the chunk retrieval techniques on a real-world data set,
+where there were mostly few structural categories within one project.
+In addition, the third of the measurements we conducted with two
+structural categories already showed the negative effect of an
+increasing number of structural categories on the performance of the
+chunk retrieval techniques.
 
@@
 % analysis.
-The goal of this paper was to support researchers and developers in
-their decision on how to analyze build logs.
-To this end, we conducted a systematic mapping study to uncover the
-state-of-research on build log analysis.
-We implemented three promising chunk retrieval techniques and
-compared their performance on the \emph{LogChunks} data set.
-Our results show that the structural
-representation of the targeted information in the build logs is the
-main factor to consider when choosing a suitable technique.
-Secondary
-factors are the desired confidence into recall and precision of the
-produced output and whether precision or recall is more important for
-the task at hand.
+The goal of this paper is to support practitioners and researchers in
+their decision on how to analyze build logs. To this end, we first
+conducted a systematic mapping study to map out the available build
+log analysis techniques.  We then
+implemented three promising chunk retrieval techniques and compared
+their performance on the \emph{LogChunks} data set.  Our results show
+that the structural representation of the targeted information in the
+build logs is the main factor to consider when choosing a suitable
+technique.  Secondary factors are the desired confidence in recall and
+precision of the produced output and whether precision or recall is
+more important for the task at hand.

### 2020-04-24 tse-paper/paper.tex
easy fixes and prio
Inline abstract

@@
 
-\author{Carolin~Brandt,%~\IEEEmembership{Member,~IEEE,}
+\author{Carolin~E.~Brandt, %~\IEEEmembership{Member,~IEEE,}
         Moritz~Beller%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
@@
 \begin{abstract}
-\input{abstract.tex}
+Build logs are the textual by-products that automatic software build processes
+create, often as part of their Continuous Integration (CI)
+pipeline.
+Build logs can serve as a paramount source of
+information for developers to understand and debug depdency, compilation, or
+test failures.
+Manually
+extracting the important chunks of information in a build log, though, is akin to
+finding a needle in a haystack.
+Recently, practitioners and researchers have started attempts to partly
+automate
+this time-consuming activity, to not only ease
+developers' task of finding this needle but also to enable a novel class of
+automated on-ward processing applications.
+In this paper, we give a systematic overview of the emerging field of build log analysis.
+In a large-scale literature mapping study, we first survey and categorize the existing methods to
+extract information chunks from build logs.
+In the second part of the paper, we develop prototypical implementations of the three most promising
+techniques we found, namely program synthesis
+by example, textual similarity, and keyword search.
+Finally, we evaluate the techniques in an empirical study on
+the \emph{LogChunks} data set, which comprises 797 build logs 
+from a wide range of different projects and programming languages.
+Our findings show that none of the three techniques in general outperforms
+the others, but rather, that each technique has its respective strengths
+and weaknesses.
+We discuss under which circumstances each technique performs best
+and provide a recommendation scheme for when developers or researchers might 
+use which technique.
+We close with a roadmap of important open problems in the
+emerging field of
+build log analysis.
 \end{abstract}

### 2020-04-24 tse-paper/content.tex
Finish intro (left some more TODOs)

@@
 automatically extract relevant pieces of information from build logs
-can also help
+can help
 developers debug a broken build more quickly without having to browse
@@
 
-Despite its central role for helping developers and for enabling
-applications for on-ward processing of build logs,
+Despite its central role in helping developers and in enabling
+novel, on-ward processing applications,
 the process of how to
-automatically analyze build logs has thus far received little
-attention as a separate research topic, bringing us to the first
+automatically analyze build logs has thus far not been systematically overviewed as a research topic, bringing us to the first
 research question:
@@
 1}}
-What are the state-of-the-research techniques to analyze build logs?
+What is the state-of-the-research on analyzing build logs?
 \end{simplebox}
 
-To answer this question, we start the investigation by performing an
-extensive literature study (\Cref{fig:overview}).
-It shows that
-less than half of the 61 works which rely on build log analysis
-describe in detail how they performed it.
-Even fewer
-made their implementation available.
+To answer this question, we start our investigation---pictured in \Cref{fig:overview}---with an
+extensive literature study (step 1).
 The literature
 survey identifies various strategies to
-analyze build logs such as:
-custom built parsers, regular expressions, manual inspection,
-natural language processing, information retrieval or searching
+analyze build logs, among which are developing
+custom parsers, using regular expressions, doing manual inspections,
+natural language processing, information retrieval, or searching
 for keywords.
+Unfortunately, our survey also shows that
+less than half of the 61 works which rely on build log analysis
+describe it in sufficient detail and that
+% TODO fill-in X
+only X independent implementations are available, one of which stems from the second author of this paper. Out of these implementations, all are based on either a custom parser or regular expressions.
 %Using 1) a set of
@@
 
+%% \begin{itemize}
+%%   \item \textbf{(referred to as PBE)}
+%%   Based on manually supplied example pairs of build logs and chunks,
+%%   PBE automatically synthesizes
+%%   a regular expression extracting the given chunks within the build logs.
+%%   % these second sentences about what the techniques stand for could
+%%   % also be merged to a paragraph after the itemize
+%%   PBE mimics regular expressions and parsers while
+%%   simplifying their development.
+%%   \item \textbf{Common Text Similarity (CTS)}
+%%   Text similarity is a common information retrieval technique.
+%%   CTS selects lines of a log which are
+%%   most similar to the lines present in manually supplied example chunks.
+%%   As a common information retrieval technique, our text similarity
+%%   approach stands for the machine learning approaches identified in
+%%   the literature survey.
+%%   \item \textbf{Keyword Search (KWS)}
+%%   KWS finds fitting passages by searching the whole
+%%   text of a build log for
+%%   the occurrence of specific trigger words.
+%%   Keyword Search was explicitly mentioned by several articles in the
+%%   literature survey.
+%% \end{itemize}
+
+% TODO caro: maybe convert this into a proper ordered list?
+As a consequence, we took it upon ourselves (step 2) to provide implementations of the three most promising automatic build log analysis techniques we observed in the literature survey:
+a technique 1) able to automatically synthesize regular expressions, called \emph{Program Synthesis by Example (PBE)}, 2) based on natural language processing, doing \emph{Common Text Similarity (CTS)}  and 3) inspired by information-retrieval employing \emph{Keyword Search (KWS)}.
 Even though these three approaches to analyze
@@
 
-To answer this question, in the second step of the study
-(\Cref{fig:overview}), we choose three promising
-techniques to analyze build logs by retrieving substrings
-(chunks) that describe a specific information.
-
-We build and compare three
-implementations that each stand prototypical for one of the identified
-strategies to analyze build logs:
-
-\begin{itemize}
-  \item \textbf{Program Synthesis by Example (referred to as PBE)}
-  Based on manually supplied example pairs of build logs and chunks,
-  PBE automatically synthesizes
-  a regular expression extracting the given chunks within the build logs.
-  % these second sentences about what the techniques stand for could
-  % also be merged to a paragraph after the itemize
-  PBE mimics regular expressions and parsers while
-  simplifying their development.
-  \item \textbf{Common Text Similarity (CTS)}
-  Text similarity is a common information retrieval technique.
-  CTS selects lines of a log which are
-  most similar to the lines present in manually supplied example chunks.
-  As a common information retrieval technique, our text similarity
-  approach stands for the machine learning approaches identified in
-  the literature survey.
-  \item \textbf{Keyword Search (KWS)}
-  KWS finds fitting passages by searching the whole
-  text of a build log for
-  the occurrence of specific trigger words.
-  Keyword Search was explicitly mentioned by several articles in the
-  literature survey.
-\end{itemize}
-
-In the third step (\Cref{fig:overview}),
-we conduct an empirical study to gauge the performance
+To answer this question, in the third step  of \Cref{fig:overview},
+we conduct an empirical study assessing the performance
 of these chunk retrieval techniques in
@@
 80 popular open-source projects and a broad range of different
-build tools and programming languages.
-
-We develop a set of guidelines (step 4, \Cref{fig:overview})
-on how to choose a
-technique given a goal.
+build tools and programming languages. Our results show that there is no technique that in general outperforms the others. However, 
+% TODO 1-2 sentences about results, inclduing some accuracy measures
+
+Finally, due to this ambiguity, we develop a set of guidelines (\Cref{fig:overview}, step 4)
+on how to choose the most suitable build log analysis
+technique for the task at hand.
 We recommend PBE for use cases where the desired information is always
@@
 \item systematic guidelines on when to use which technique.
-% TODO: is the future work good enough to put in contributions?
-\item a detailed replication package~\cite{brandt2020chunk-replication}.
+\item a detailed research map to inspire future contributions to the field.
+\item a replication package~\cite{brandt2020chunk-replication}.
 \end{itemize}
@@
 % TODO (resolved): All of these are passive
-% TODO Swap RQ 1.2 and RQ 1.1 (logical order?)
-\begin{itemize}[leftmargin=2cm]
-  \item[\textbf{RQ1.1:}] Which information in build logs is of interest?
+% TODO (resolved) Swap RQ 1.2 and RQ 1.1 (logical order?)
+\begin{itemize}[leftmargin=1cm]
+  \item[\textbf{RQ1.1:}] What information is extracted from build logs?
   \item[\textbf{RQ1.2:}] Which extraction techniques exist?
-  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to analysis?
+  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
+  analysis?
 \end{itemize}
@@
 \\
-
+% TODO: We need to mention in the text describing the Table what we mean by ``Analysis''
 \raisebox{0.8mm}{Analysis} &
@@
 % it returns error messages in both cases
-% TODO: Ok, but what is the point of matching on an empty string (if I understand what you mean)? you would not normally define such an extraction?
+% TODO: Ok, but what is the point of matching on an empty string
+(if I understand what you mean)? you would not normally define such
+an extraction?
 % If this distinction is important it needs to be made more clear
@@
 attach boxed title to top center={yshift=-6mm}]
-{\textbf{RQ2:} How do build log analysis techniques compare against each other?}
+{\textbf{RQ2:} How do build log analysis techniques compare against
+each other?}
 \begin{itemize}[leftmargin=1.2cm]
@@
 examples from the same structural category
-did not improve the chunk retrieval. In fact, unless they
+did not improve the chunk retrieval.
+In fact, unless they
 were in some sense redundant, adding more training examples even
@@
 % but it's also self-contained so feel free to comment it out
+
+% TODO we can't just have a paragraph in a scientific paper start with Caveat, I think ;-) Also, we should say why we THINK this is not the case. Otherwise we weaken our work unduly
 \textbf{Caveat!}
@@
 categories than with one structural category category (50.25\% one,
-33.75\% two, 13.75\% more than two).  This stems from the fact that we
+33.75\% two, 13.75\% more than two).
+This stems from the fact that we
 investigated the chunk retrieval techniques on a real-world data set,
@@
 The goal of this paper is to support practitioners and researchers in
-their decision on how to analyze build logs. To this end, we first
+their decision on how to analyze build logs.
+To this end, we first
 conducted a systematic mapping study to map out the available build
-log analysis techniques.  We then
+log analysis techniques.
+We then
 implemented three promising chunk retrieval techniques and compared
-their performance on the \emph{LogChunks} data set.  Our results show
+their performance on the \emph{LogChunks} data set.
+Our results show
 that the structural representation of the targeted information in the
 build logs is the main factor to consider when choosing a suitable
-technique.  Secondary factors are the desired confidence in recall and
+technique.
+Secondary factors are the desired confidence in recall and
 precision of the produced output and whether precision or recall is

### 2020-04-24 tse-paper/paper.tex
Finish intro (left some more TODOs)

@@
 Finally, we evaluate the techniques in an empirical study on
-the \emph{LogChunks} data set, which comprises 797 build logs 
+almost 800 build logs 
 from a wide range of different projects and programming languages.

### 2020-04-24 tse-paper/content.tex
Fix left-over comments

@@
 the process of how to
-automatically analyze build logs has thus far not been systematically overviewed as a research topic, bringing us to the first
+automatically analyze build logs has thus far not been systematically
+overviewed as a research topic, bringing us to the first
 research question:
@@
 
-To answer this question, we start our investigation---pictured in \Cref{fig:overview}---with an
+To answer this question, we start our investigation---pictured in
+\Cref{fig:overview}---with an
 extensive literature study (step 1).
@@
 % TODO fill-in X
-only X independent implementations are available, one of which stems from the second author of this paper. Out of these implementations, all are based on either a custom parser or regular expressions.
+only X independent implementations are available, one of which stems
+from the second author of this paper.
+Out of these implementations, all are based on either a custom parser
+or regular expressions.
 %Using 1) a set of
@@
 %%   PBE automatically synthesizes
-%%   a regular expression extracting the given chunks within the build logs.
+%%   a regular expression extracting the given chunks within the build
+%% logs.
 %%   % these second sentences about what the techniques stand for could
@@
 %%   CTS selects lines of a log which are
-%%   most similar to the lines present in manually supplied example chunks.
+%%   most similar to the lines present in manually supplied example
+%% chunks.
 %%   As a common information retrieval technique, our text similarity
@@
 % TODO caro: maybe convert this into a proper ordered list?
-As a consequence, we took it upon ourselves (step 2) to provide implementations of the three most promising automatic build log analysis techniques we observed in the literature survey:
-a technique 1) able to automatically synthesize regular expressions, called \emph{Program Synthesis by Example (PBE)}, 2) based on natural language processing, doing \emph{Common Text Similarity (CTS)}  and 3) inspired by information-retrieval employing \emph{Keyword Search (KWS)}.
+As a consequence, we took it upon ourselves (step 2) to provide
+implementations of the three most promising automatic build log analysis
+techniques we observed in the literature survey:
+a technique 1) able to automatically synthesize regular expressions,
+called \emph{Program Synthesis by Example (PBE)}, 2) based on natural
+language processing, doing \emph{Common Text Similarity (CTS)}	and 3)
+inspired by information-retrieval employing \emph{Keyword Search (KWS)}.
 Even though these three approaches to analyze
@@
 Our study is based on the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}, which encompasses build logs from
+set~\cite{brandt2020logchunks}, which encompasses 797 build logs from
 80 popular open-source projects and a broad range of different
-build tools and programming languages. Our results show that there is no technique that in general outperforms the others. However, 
+build tools and programming languages.
+Our results show that there is no technique that in general outperforms
+the others.
+However,
 % TODO 1-2 sentences about results, inclduing some accuracy measures
 
-Finally, due to this ambiguity, we develop a set of guidelines (\Cref{fig:overview}, step 4)
+Finally, due to this ambiguity, we develop a set of guidelines
+(\Cref{fig:overview}, step 4)
 on how to choose the most suitable build log analysis
@@
 \item systematic guidelines on when to use which technique.
-\item a detailed research map to inspire future contributions to the field.
+\item a detailed research map to inspire future contributions to the
+field.
 \item a replication package~\cite{brandt2020chunk-replication}.
@@
 \\
-% TODO: We need to mention in the text describing the Table what we mean by ``Analysis''
+% TODO: We need to mention in the text describing the Table what we mean
+by ``Analysis''
 \raisebox{0.8mm}{Analysis} &
@@
 
-% TODO we can't just have a paragraph in a scientific paper start with Caveat, I think ;-) Also, we should say why we THINK this is not the case. Otherwise we weaken our work unduly
+% TODO we can't just have a paragraph in a scientific paper start with
+Caveat, I think ;-) Also, we should say why we THINK this is not the case.
+Otherwise we weaken our work unduly
 \textbf{Caveat!}

### 2020-04-24 tse-paper/content.tex
Integrate TODO

@@
-% \section{Introduction}
-% TODO: Include term predictive CI, link to FB paper and
-%https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730
-
 % TODO: What about the alternate solution, installing plugins to report
@@
 
-When a build or one of its steps fails, developers typically
-scavenge the logs for information related to the source of the error.
-This manual activity is
-tedious and prone to error~\cite{santolucito2018statically}.
-As a
-single build log can be over 50 megabytes large~\cite{beller2017oops},
-finding the small chunk of information in it which is linked to the error,
-is akin to searching for a
-needle in a haystack.
-In addition to helping understand and fix build failures, the information
-richness of build logs enables a plethora of other applications: with
-the help of
-build logs, we can better understand and categorize CI
-failures and compile
+When a build or one of its steps fails, developers typically scavenge
+the logs for information related to the source of the error.  This
+manual activity is tedious and prone to
+error~\cite{santolucito2018statically}.  As a single build log can be
+over 50 megabytes large~\cite{beller2017oops}, finding the small chunk
+of information in it which is linked to the error, is akin to
+searching for a needle in a haystack.  In addition to helping
+understand and fix build failures, the information richness of build
+logs enables a plethora of other applications: with the help of build
+logs, we can better understand and categorize CI failures and compile
 errors~\cite{islam2017insights,seo2014programmers}, differentiate
 testing practices~\cite{orellana2017differences,vassallo2017a-tale},
-train classifiers to predict the build outcome and
-duration~\cite{ni2017cost,bisong2017built,machalica2019predictive}, or
-investigate static analysis tools in CI
+train classifiers to do ``predictive CI'' on the build or test outcome
+and
+duration~\cite{ni2017cost,bisong2017built,haghighatkhah2018test,machalica2019predictive},
+or investigate static analysis tools in CI
 builds~\cite{zampetti2017open}.
@@
 a technique 1) able to automatically synthesize regular expressions,
-called \emph{Program Synthesis by Example (PBE)}, 2) based on natural
-language processing, doing \emph{Common Text Similarity (CTS)}	and 3)
-inspired by information-retrieval employing \emph{Keyword Search (KWS)}.
-Even though these three approaches to analyze
-build logs have different strengths and weaknesses, the literature
+called \emph{Program Synthesis by Example (PBE)}, 2) based on information retrieval, using \emph{Common Text Similarity (CTS)}	and 3)
+inspired by the manual adhoc-search for key parts in the log, employing \emph{Keyword Search (KWS)}.
+Even though these three approaches---regular expressions, text similarity, keyword search---
+have different strengths and weaknesses, the literature
 survey shows that their use often seems arbitrary.
@@
 
-To answer this question, in the third step  of \Cref{fig:overview},
+To answer this question, as a third step,
 we conduct an empirical study assessing the performance
@@
 for example ``Is the technique explained in detail?'' and
-``What is the source of the build logs?''.
+``What is the source of the build logs?''
 As recommended by Petersen et
@@
 Our literature survey shows that despite its relatively young age
-(first occurrence of a paper on the topic in 2001, vast majority after
-2016), \textbf{build log analysis is a widely established technique}
-in the literature, with Y articles on it.
+(first mentioned in a paper in 2001, vast majority after
+2016), \textbf{build log analysis is an established technique}
+in the literature, with 61 articles making use of it.
 
@@
 article each (B).
-From this, we follow: (a) there is a nichè for custom parsers or even
+From this, we follow: (a) there is a niche for custom parsers or even
 specialized plugins integrated into the build process to make
@@
 % it returns error messages in both cases
-% TODO: Ok, but what is the point of matching on an empty string
+% TODO: Ok, but what is the point of matching on an empty string?
 (if I understand what you mean)? you would not normally define such
@@
 % is explained :)
+% TODO Slightly better, but I still have a problem with this -- what
+% exactly is the vector
+% space model here?
+% At a minimum, the text should mention what the vector is and how the model is used
 and apply the Vector Space Model~\cite{schutze2008introduction}
@@
 crucial for regular expressions to identify a log chunk.
-In fact, if we add the third example from \Cref{lst:chunk-example-3},
-which has a
-different structural representation, to the training set,
+In fact, if we add the third example from \Cref{lst:chunk-example-3} (which has a
+different structural representation) to the training set,
 PBE is not able to synthesize a program and returns
@@
 library~\cite{prose2019webpage} and CTS, KWS, and RLR using
-R and the text2vec library~\cite{text2vec2019webpage}.
+R and the {\tt text2vec} library~\cite{text2vec2019webpage}.
 
@@
 % motivation why only one test example.
-we can also leave that out
+%we can also leave that out
 % and answer if we are asked about it
@@
 % -> should we add it for the first time we include a type of figure?
+% TODO Yes, that sounds good. You might even say Figure 12-15 show two
+% plots in the short text under the section heading. It just makes the
+% text flow so much better.
 \Cref{fig:recall-precision-examplecount-CTS} presents precision,
@@
 \noindent
-\textbf{Retrieval Output Usage}
+\textbf{Retrieval Output Usage.}
 While KWS has the highest recall of all three techniques, its
@@
 % TODO we can't just have a paragraph in a scientific paper start with
-Caveat, I think ;-) Also, we should say why we THINK this is not the case.
-Otherwise we weaken our work unduly
+% Caveat, I think ;-) Also, we should say why we THINK this is not the case.
+% Otherwise we weaken our work unduly
 \textbf{Caveat!}
@@
 more important for the task at hand.
+
+Finally, we gave an
+outline to guide future research efforts in the area of build log
+analysis. Important themes are
+% TODO Caro complete :-)

### 2020-04-24 tse-paper/content.tex
merge

@@
 When a build or one of its steps fails, developers typically scavenge
-the logs for information related to the source of the error.  This
+the logs for information related to the source of the error.
+This
 manual activity is tedious and prone to
-error~\cite{santolucito2018statically}.  As a single build log can be
+error~\cite{santolucito2018statically}.
+As a single build log can be
 over 50 megabytes large~\cite{beller2017oops}, finding the small chunk
 of information in it which is linked to the error, is akin to
-searching for a needle in a haystack.  In addition to helping
+searching for a needle in a haystack.
+In addition to helping
 understand and fix build failures, the information richness of build
@@
 a technique 1) able to automatically synthesize regular expressions,
-called \emph{Program Synthesis by Example (PBE)}, 2) based on information retrieval, using \emph{Common Text Similarity (CTS)}	and 3)
-inspired by the manual adhoc-search for key parts in the log, employing \emph{Keyword Search (KWS)}.
-Even though these three approaches---regular expressions, text similarity, keyword search---
+called \emph{Program Synthesis by Example (PBE)}, 2) based on information
+retrieval, using \emph{Common Text Similarity (CTS)}  and 3)
+inspired by the manual adhoc-search for key parts in the log, employing
+\emph{Keyword Search (KWS)}.
+Even though these three approaches---regular expressions, text similarity,
+keyword search---
 have different strengths and weaknesses, the literature
@@
 
+% TODO: the following paragraphs have nothing to do with a discussion
+
 In summary, the results of the literature study show the need for
@@
 
-% TODO: the following paragraphs have nothing to do with a discussion
 %of the literature survey results.
@@
 % space model here?
-% At a minimum, the text should mention what the vector is and how the model is used
+% At a minimum, the text should mention what the vector is and how the
+model is used
 and apply the Vector Space Model~\cite{schutze2008introduction}
@@
 crucial for regular expressions to identify a log chunk.
-In fact, if we add the third example from \Cref{lst:chunk-example-3} (which has a
+In fact, if we add the third example from \Cref{lst:chunk-example-3}
+(which has a
 different structural representation) to the training set,
@@
 % motivation why only one test example.
-%we can also leave that out
+% we can also leave that out
 % and answer if we are asked about it
@@
 % -> should we add it for the first time we include a type of figure?
-% TODO Yes, that sounds good. You might even say Figure 12-15 show two
-% plots in the short text under the section heading. It just makes the
+% TODO Yes, that sounds good.
+You might even say Figure 12-15 show two
+% plots in the short text under the section heading.
+It just makes the
 % text flow so much better.
@@
 % TODO we can't just have a paragraph in a scientific paper start with
-% Caveat, I think ;-) Also, we should say why we THINK this is not the case.
+% Caveat, I think ;-) Also, we should say why we THINK this is not
+the case.
 % Otherwise we weaken our work unduly
@@
 outline to guide future research efforts in the area of build log
-analysis. Important themes are
+analysis.
+Important themes are
 % TODO Caro complete :-)

### 2020-04-25 tse-paper/content.tex
lit survey improvements

@@
+%\section{introduction}
 % TODO: What about the alternate solution, installing plugins to report
@@
 describe it in sufficient detail and that
-% TODO fill-in X
-only X independent implementations are available, one of which stems
+% TODO Moritz: 14 is still quite big, it's 'impl available' when we saw
+% no overlap.
+Decide whether you want to keep this in :)
+only 14 independent implementations are available, one of which stems
 from the second author of this paper.
@@
 % retrieval techniques,
-% % todo: Can you shortly explain the technique here?
+% % Can you shortly explain the technique here?
 % and 3) a list of search keywords
@@
 analysis.
-We start with a differentiation to the related field of general
+We start with a differentiation to the related field of
 system log analysis.
-Then, we describe the methodology and results of a systematic mapping
+% ref to fig 2 so it can be here and above fig 3
+Then, we describe the methodology (\Cref{fig:lit-survey})
+and results of a systematic mapping
 study to
@@
 al.~\cite{petersen2008systematic,petersen2015guidelines}.
-
 We close by summarizing how build logs are commonly
@@
 % removed duplicates of data extraction pass already here
+
 With these 256 remaining articles, we followed a backward snowball
@@
 % TODO (resolved): All of these are passive
-% TODO (resolved) Swap RQ 1.2 and RQ 1.1 (logical order?)
+% it says resolved, but they still are?
+% I exchanged 'extracted' with targeted / analysis
+% 'information retrieved' or 'information extracted' will give us
+% this is not IR neither IE discussions again
 \begin{itemize}[leftmargin=1cm]
-  \item[\textbf{RQ1.1:}] What information is extracted from build logs?
-  \item[\textbf{RQ1.2:}] Which extraction techniques exist?
+  \item[\textbf{RQ1.1:}] What information is targeted in build logs?
+  \item[\textbf{RQ1.2:}] Which analysis techniques exist?
   \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
@@
 of the data extraction template.
-We divided the remaining 46 articles evenly between the two authors
-and inspected them as closely as necessary to fill out the template
+We divided the remaining 56 articles evenly between the two authors
+and inspected each as closely as necessary to fill out the template
 with confidence,
@@
 text.
+
 For questions that did not require a boolean answer, we allowed assigning
@@
 all articles that used build logs provided by a company.
-
 The full data extraction template and our results of this step can be
@@
 % TODO: We need to mention in the text describing the Table what we mean
-by ``Analysis''
+%by ``Analysis''
 \raisebox{0.8mm}{Analysis} &
@@
 
-\subsubsection{Which information is targeted? (RQ 1.1)}
-% TODO General ref to Figure 4 missing: We answer this question along
-% data in Figure 4, and ...
-% ?
+\subsubsection{What information is targeted in build logs? (RQ 1.1)}
 
@@
 
-% TODO It is unclear where this comes from.
-% TODO Also, wouldn't it perhaps be better to continue with Figure
-%4.b directly?
-In most cases (51\%), a chunk was retrieved from the log.
-Build logs were scanned for compilation
+\Cref{fig:litsur:use} shows the reason for the
+investigated articles to analyze build logs.
+The majority of articles (46\%) used the outcome of their build log
+analysis to drive further research.
+Seo et al.~\cite{seo2014programmers}, for example,
+categorized the types of compile errors encountered at
+Google.
+Other articles (10\%) used the gained insights to give feedback to
+developers.
+For 8\% of the articles the retrieved information was the input
+to a next automatic on-ward processing step.
+Articles chose
+tests that should be part of a reduced but still effective test
+suite~\cite{shi2018evaluating} or filled a data structure with
+build information, an information source for further tools aiming
+to fix a failing build~\cite{vassallo2018un-break}.
+
+We also identified the type of information which the articles
+retrieved from the build logs.
+In most cases (51\%), the researchers retrieved a chunk of text.
+They scanned build logs for compilation
 errors~\cite{clemencic2014new} or
@@
 36\% of the articles classified the build logs into categories.
-For instance, distinguishing failures caused by developers from
+For instance, they distinguish failures caused by developers from
 failures caused
 by infrastructure errors~\cite{lindqvist2019detection} or
-whether projects use automated static analysis
+determine whether projects use automated static analysis
 tools~\cite{kavaler2019tool}.
@@
 
-The majority of articles (46\%) used the outcome of their build log
-analysis for research purposes, as shown in \Cref{fig:litsur:use}.
-% TODO What does this mean? Give an example: to drive further research,
-%FIXME
-for example to categorize the types of compile errors encountered at
-Google~\cite{seo2014programmers}.
-Further uses were giving feedback to developers (10\%) or automatic
-on-ward processing of the retrieved information (8\%)
-% TODO for example to ...
-%FIXME
-.
-
-\subsubsection{Which techniques are used? (RQ 1.2)}
+\subsubsection{Which analysis techniques exist? (RQ 1.2)}
 \Cref{tab:litsur:techniques} presents the techniques that the articles
@@
 ~\cite{rahman2018impact}.
-% TODO maybe make the point here that it is questionable whether this
-%includes a comprehensive tokenizer, lexer etc.
-%based solution and that parsing in many cases really meant regexp.
-%If we could figure that out, then we would assign it to regexp instead.
+For such imprecise statements it was often not clear if they describe
+a complex parser (including a tokenizer, lexer, etc.) or refer to a
+simpler parsing tool based on regular expressions.
+If we saw evidence for the latter, we assigned the tag
+``regular expression'' instead of the tag ``parser''.
 25\% of the articles described the use of regular expressions and 20\%
@@
 an extended version of them~\cite{rott2019empirische,
-shi2018evaluating}
-% (based on regular expressions),
-two used the
+shi2018evaluating}, two used the
 \emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
-% based on which technique?,  (based on regular expressions)
 another two the
-\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool
-% based on which technique?  (a parser for the output of make files)
-.
-% I don't think the based on..
-%adds something here.
-% It's all kinda regex.
-%Even if we say 'parser' it's often regex in the background
-
-\subsubsection{Which build logs are analyzed? (RQ 1.3)}
+\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.
+
+\subsubsection{Which kinds of build logs are subject to
+  analysis? (RQ 1.3)}
 \Cref{fig:litsur:log_producer} shows the distribution of supported
@@
 
-% TODO remove first part of this paragraph?
+A large amount of the articles within the survey, analyze build logs
+from a small number of build tools.
+In most cases, this is because the format of build logs changes
+~\cite{staahl2014modeling} and
+therefore ``parsers must be specialized to each build and test
+framework''~\cite{tomassi2019bugswarm}.
+% remove following part of this paragraph?
+% I think it is a nice anecdote but not super necessary yes.
 Sometimes, aspects separate from the build log analysis motivate
-this limitation to a specific build tool.
+their limitation to a specific build tool.
 For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
@@
 and mutation score.
-A larger amount of the articles within the survey, however, limit
-themselves to few build tools because their log format varies and
-therefore ``parsers must be specialized to each build and test
-framework''~\cite{tomassi2019bugswarm}.
 
@@
 
-% TODO perhaps remove this paragraph?
-% yes it is very unspecific.
-%however then we have 0 reference
-% to how many logs are analyzed
-% a central point in our argumentation for automation
-The number of logs analyzed varied greatly and we were not always able to
+% perhaps remove this paragraph?
+% C: made it more specific, this is the only reference in the result
+% which supports 'we need automatic because so many logs are analy'
+The number of logs analyzed varied greatly between the articles
+and we were not always able to
 extract it confidently.
-Articles reported analyzing from two up to 122 million logs.
+23 of the articles analyzed more than a thousand build logs, some
+investigated up to 122 million logs.
 
@@
 Vassallo et al.~\cite{vassallo2017a-tale},
-Ghaleb et al.~\cite{ghaleb2019studying}, and several other studies reused.
+Ghaleb et al.~\cite{ghaleb2019studying},
+and several other articles studied.
 
@@
 solution.
+% TODO this is disconnected, at least here
+Urli et al.~\cite{urli2018design} strongly discouraged from parsing
+build logs for information as it is ``too error prone,'' other
+articles pointed to the effort of developing a custom tool.
+Regular expressions are known to be tedious to
+maintain~\cite{michael2019regexes}.
+
 % We implement build environment agnostic build log analysis
@@
 
-% TODO this is disconnected, at least here
-Urli et al.~\cite{urli2018design} strongly discouraged from parsing
-build logs for information as it is ``too error prone,'' other
-articles pointed to the effort of developing a custom tool.
-Regular expressions are known to be tedious to
-maintain~\cite{michael2019regexes}.
-
 % This task of retrieving specific chunks of text from the
@@
 % tools in their studies.
-
-% TODO: the following paragraphs have nothing to do with a discussion
-
-In summary, the results of the literature study show the need for
-build log
-analysis techniques that are automated, build-environment agnostic
-% TODO who is the user?
-and can be configured by a user with little effort.
-% We achieve this by developing three techniques for which the
-% information to be retrieved is specified through examples or keywords.
-
-%of the literature survey results.
-% what we need is some derivation of the three techniques 1) regex 2)
-%cts 3) kws, best repeated here in the discussion and then from the lit
-%survey above, section 2.4.2
-For this reason, we are focussing on techniques that run automatically
-after being configured through examples or keywords.
-Examples consist of logs and corresponding chunks.
-The user provides these examples and keywords, which can simply be
-exchanged whenever new cases are introduced.
-
-We propose the notion of chunk retrieval techniques which retrieve
-a substring, that describes a specific information, from a build log.
-Generally, these can also be used to classify build logs and therefore
-cover the great majority of the type of log analysis we saw within
-our survey.
-
-We implement three chunk retrieval techniques based on approaches
-described by several articles:
-PBE mimics regular expressions and parsers while simplifying
-their development.
-We chose text similarity (CTS) as a common information retrieval
-technique and implement the ad-hoc approach of
-searching for specific strings or keywords within KWS\@.
-
-We evaluate the three chunk retrieval techniques on the
-\emph{LogChunks} data set because it encompasses a broad range of
-build environments which enables us to measure the generic
-applicability of the techniques.
-The targeted chunks are describing error messages or
-``the reason the build failed,'' which was also the information
-most targeted by the articles in our survey.
-
-% The articles within our study mainly tried to retrieve or classify
-% errors or reasons for the build to fail from the logs.
-% Therefore we chose the log chunk ``describing why the build failed''
-% ~\cite{brandt2020logchunks} for our empirical comparison study
-% of chunk retrieval techniques.
-% The techniques we implement are in principle agnostic to the targeted
-% log chunk, thus we believe our results can be generalized to other
-% kinds of log chunks.
 
@@
 % here.
+
+\subsection{The case for chunk retrieval on build logs}
+
+% TODO: the following paragraphs have nothing to do with a discussion
+
+In summary, the results of the literature study show the need for
+build log
+analysis techniques that are automated, build-environment agnostic
+% TODO who is the user?
+and can be configured by a user with little effort.
+% We achieve this by developing three techniques for which the
+% information to be retrieved is specified through examples or keywords.
+
+%of the literature survey results.
+% what we need is some derivation of the three techniques 1) regex 2)
+%cts 3) kws, best repeated here in the discussion and then from the lit
+%survey above, section 2.4.2
+For this reason, we are focussing on techniques that run automatically
+after being configured through examples or keywords.
+Examples consist of logs and corresponding chunks.
+The user provides these examples and keywords, which can simply be
+exchanged whenever new cases are introduced.
+
+We propose the notion of chunk retrieval techniques which retrieve
+a substring, that describes a specific information, from a build log.
+Generally, these can also be used to classify build logs and therefore
+cover the great majority of the type of log analysis we saw within
+our survey.
+
+We implement three chunk retrieval techniques based on approaches
+described by several articles:
+PBE mimics regular expressions and parsers while simplifying
+their development.
+We chose text similarity (CTS) as a common information retrieval
+technique and implement the ad-hoc approach of
+searching for specific strings or keywords within KWS\@.
+
+We evaluate the three chunk retrieval techniques on the
+\emph{LogChunks} data set because it encompasses a broad range of
+build environments which enables us to measure the generic
+applicability of the techniques.
+The targeted chunks are describing error messages or
+``the reason the build failed,'' which was also the information
+most targeted by the articles in our survey.
+
+% The articles within our study mainly tried to retrieve or classify
+% errors or reasons for the build to fail from the logs.
+% Therefore we chose the log chunk ``describing why the build failed''
+% ~\cite{brandt2020logchunks} for our empirical comparison study
+% of chunk retrieval techniques.
+% The techniques we implement are in principle agnostic to the targeted
+% log chunk, thus we believe our results can be generalized to other
+% kinds of log chunks.
 
@@
 % TODO: Ok, but what is the point of matching on an empty string?
-(if I understand what you mean)? you would not normally define such
-an extraction?
+%(if I understand what you mean)? you would not normally define such
+%an extraction?
 % If this distinction is important it needs to be made more clear
+
+% TODO CARO: make more clear that not matching is an error cause
+% pattern didn't match?
 \subsubsection{Application}
@@
 % At a minimum, the text should mention what the vector is and how the
-model is used
+% model is used
 and apply the Vector Space Model~\cite{schutze2008introduction}
@@
 \subsection{Study Process}
+% FIXME introduce term example
+% FIXME mention study figure
 % TODO: I think you need to introduce a concept that makes clear what one
@@
 % TODO Yes, that sounds good.
-You might even say Figure 12-15 show two
+% FIXME CARO You might even say Figure 12-15 show two
 % plots in the short text under the section heading.
-It just makes the
+% It just makes the
 % text flow so much better.

### 2020-04-25 tse-paper/content.tex
new draft texts for lit discussion and chunk retrieval techniques

@@
 
-% TODO A and B should possibly be overlapping, otherwise there is an
-% area where neither A nor B makes sense?
+% when we argue about this later we leave out the middle so A and B
+% match.
+whe then say that the long tail benefits from the generic
+% solution.
+Yes all benefit, but I think it's simpler like this.
 \begin{figure}[tbhp]
@@
 \label{sec:lit-sur:discussion}
-% TODO we are extracting failures in the following studies, which is
-%mainly what
-% literature does, too, right? Highlight here and mention later again
-
-% TODO: this section is crucial.
-% maybe we can highlight important findings, by categorizing them either
-% as further subsubsections or making it bold in the text?
-% TODO: find values for X and Y
+
 Our literature survey shows that despite its relatively young age
@@
 
-% TODO: this reads very hands-off and researchy.
-% I don't understand the first sentence and would simply cut it.
-We saw that various researchers process build logs, often because the
-logs provide more or the necessary
-information to the researchers~\cite{ren2018automated}.
+% TODO we are extracting failures in the following studies, which is
+%mainly what
+% literature does, too, right? Highlight here and mention later again
+
+% TODO: this section is crucial.
+% maybe we can highlight important findings, by categorizing them either
+% as further subsubsections or making it bold in the text?
+
+We saw that various researchers analyze build logs, often because the
+logs are the only available source for the
+information they need for their studies~\cite{ren2018automated,
+seo2014programmers,beller2017oops,zampetti2017open,rausch2017empirical}.
+
+\textbf{most analysis aims to find out why the build failed}
+
+\textbf{most techniques retrieve chunks from build logs}
+
 \textbf{Most log analysis is automated.} Automated approaches are
-necessary as many studies target a large
-number of builds.
+necessary as many studies target a large number of builds.
 Articles
@@
 make manual analysis feasible''~\cite{zolfagharinia2017not}.
-% The chunk retrieval techniques we investigate within this article are
-% automated, apart from their configuration through training examples.
-
-% TODO: draw a conclusion together with figure 5: if reuse were higher,
-%lots of effort could be saved?
-We observed very little reuse of build log analysis tools.
+\textbf{Developing automated analysis tools requires a lot of effort.}
+Urli et al.~\cite{urli2018design} strongly discouraged from parsing
+build logs for information as it is ``too error prone,'' other
+articles pointed to the effort of developing a custom tool.
+Regular expressions are known to be tedious to
+maintain~\cite{michael2019regexes}.
+
+We observed \textbf{very little reuse of build log analysis tools.}
 This can stem from the
@@
 
+% TODO: draw a conclusion together with figure 5: if reuse were higher,
+%lots of effort could be saved?
 Several articles noted the variety in log formats for different build
@@
 every supported build environment.
-\Cref{fig:litsur:log_producer} shows that many studies and tools target
-only a few distinct build environments (roughly, area A).
-% TODO: passive ...
+% The following two sentences are passive, however flipped around
+% have a different meaning (we want build env -> study count)
+\Cref{fig:litsur:log_producer} shows that only a few distinct
+build environments are the target of
+many studies and tools (roughly, area A).
 The majority of build environments was however only targeted by one
-article each (B).
-From this, we follow: (a) there is a niche for custom parsers or even
+article each (roughly, area B).
+From this we follow, that the large tail of
+\textbf{seldomly-investigated
+environments would benefit from the
+existence of a more generic solution.}
+
+% TODO we argue this in the intro!
+% problem: we have no data on this
+\textbf{techniques vary and seem rather randomly applied}
+
+\textbf{modifying the build output is not helpful}, as well as returning
+precise data through other documents than the log.
+This requires access to the build configuration, is also specific to
+the used build environment and prohibits the analysis of
+historical data.
+
+\textbf{TODO embed custom plugin discussion}
+% TODO very disconnected here
+From this, we follow: 1) there is a niche for custom parsers or even
 specialized plugins integrated into the build process to make
@@
 %TODO cite
-wrote, still have the disadvantage of not being able to work on historic
+wrote, have the disadvantage of not being able to work on historic
 builds.
-(b) the large tail of seldomly-investigated environments would benefit
+2) the large tail of seldomly-investigated environments would benefit
 from the existence of a more generic
 solution.
-% TODO this is disconnected, at least here
-Urli et al.~\cite{urli2018design} strongly discouraged from parsing
-build logs for information as it is ``too error prone,'' other
-articles pointed to the effort of developing a custom tool.
-Regular expressions are known to be tedious to
-maintain~\cite{michael2019regexes}.
 
@@
 \label{sec:techniques}
+%TODO here we sell our techniques as superior.
+match in intro?
+%TODO: really? currently the discussion does not show this 'need'!
+The outcome of our literature survey shows the need for a new
+generation of techniques to analyze build logs.
+In this section we argue how our research sets the first step to
+address this need by introducing three techniques that retrieve
+specific substrings (chunks) from build logs.
+We present defining characteristics of these so called \emph{chunk
+retrieval techniques} and present the techniques we developed in
+detail.
+At the end we illustrate how the techniques operate on a concrete
+example and sketch out their implementation.
 
@@
 \end{tabularx}
-\label{tab:ctr}
+\label{tab:techniques}
 \end{table*}
 
-% TODO CARO
-% start by defining in more detail what a chunk retrieval technique is
-% or: characteristics that distinguishe them / to specify them further
-% (To Moritz: we have short definitions before, the first time we use
-% 'chunk', this is far to detailed to be earlier than here)
-% Following that we present each of the techniques in detail.
-
-This section introduces key concepts of the three chunk retrieval
-techniques we study in this article, namely program synthesis by
-example (PBE), common text similarity (CTS), and keyword search (KWS).
-In addition, we present a comparison baseline of random line
-retrieval (RLR), illustrate the techniques on a concrete example
-of log chunks and sketch out their implementation.
-
-% TODO CARO this is not enough for Table 3.
-%Where does it come from?
-% How did it originate? Also: never single sentence abstracts
-\Cref{tab:ctr} shows a comparison of the implemented techniques.
-% TODO CARO move to end of characteristics section and say that it is
-% summary of the techniques along the aspects introducted
-% can lead reading / understanding of the future sections
-
-% TODO QUESTION Somehow, we have to find a better place for this.
-%We have been
-% using the term 'chunk retrieval' beforehand already -- this
-% definition now comes too late.
-%The first paragraph should already
-% apply to the literature mapping, the second of course only applies
-% here.
-
 \subsection{The case for chunk retrieval on build logs}
-
-% TODO: the following paragraphs have nothing to do with a discussion
-
+% FIXME Caro
 In summary, the results of the literature study show the need for
 build log
-analysis techniques that are automated, build-environment agnostic
-% TODO who is the user?
-and can be configured by a user with little effort.
-% We achieve this by developing three techniques for which the
-% information to be retrieved is specified through examples or keywords.
-
-%of the literature survey results.
+analysis techniques that are \emph{automated},
+\emph{build-environment agnostic}
+and can be \emph{configured with little effort}.
+
 % what we need is some derivation of the three techniques 1) regex 2)
@@
 after being configured through examples or keywords.
-Examples consist of logs and corresponding chunks.
+\emph{Examples consist of logs and corresponding chunks.}
 The user provides these examples and keywords, which can simply be
@@
 
-We propose the notion of chunk retrieval techniques which retrieve
-a substring, that describes a specific information, from a build log.
-Generally, these can also be used to classify build logs and therefore
-cover the great majority of the type of log analysis we saw within
+To analyze build logs,
+we propose to use chunk retrieval techniques.
+These retrieve a substring,
+that describes a specific information, from a build log.
+Generally, chunk retrieval techniques
+can also be used to classify build logs, e.g.\ by checking
+which substring was retrieved.
+Therefore, chunk retrieval techniques
+cover the great majority of the types of log analysis we saw within
 our survey.
@@
 We implement three chunk retrieval techniques based on approaches
-described by several articles:
+previously described by several articles:
 PBE mimics regular expressions and parsers while simplifying
@@
 
-We evaluate the three chunk retrieval techniques on the
-\emph{LogChunks} data set because it encompasses a broad range of
+To evaluate and compare the three chunk retrieval techniques
+we create a data set with logs from failed builds and corresponding
+chunks that describe error messages or
+``the reason the build failed.''
+This was also the information
+most targeted by the articles in our survey
+In addition to that, our data set encompasses a broad range of
 build environments which enables us to measure the generic
 applicability of the techniques.
-The targeted chunks are describing error messages or
-``the reason the build failed,'' which was also the information
-most targeted by the articles in our survey.
 
@@
 \label{sec:crt-characteristics}
-In this article, we evaluate different techniques to automatically
-retrieve pieces of information that appear literally in the build
-logs.
-%, i.e., techniques that do not aggregate, combine, or deducted
-%information.
-We call such pieces of information from build logs
-\emph{chunks} and the techniques \emph{chunk retrieval techniques}.
+Next, we will present our definition of chunk retrieval techniques
+which automatically
+retrieve pieces of information that appear literally in build
+logs, i.e., techniques that do not aggregate, combine, or deduct
+information.
+We call such pieces of information in build logs
+\emph{chunks}.
+% and the techniques \emph{chunk retrieval techniques}.
 The techniques we investigate here do not require a formal lexer and
@@
 % granularity might be adjustable by configuration.
+
 \emph{Running a
@@
 build log text.
+\Cref{tab:techniques} summarizes and distinguishes the techniques
+we present along the
+characteristics described above.
 
@@
 
-% Moritz: The following is very obvious and could apply
-% to any
-% % technique.
-% % kinda.
-% It does give a descriptive error message on no match (and
-% % that is not possible in other techniques)
-% TODO Caro: Can you given an example of such an error message?
-% % otherwise yes, nothing interesting happens in the application of pbe
-% % though for consistency we might need this section? or merge
-% config/application?
-% Why does it return an error message? Shouldn't it also return
-% <empty string>? Does it not rather return an error message if no
-% program can be synthesized?
-% TODO Moritz: a regular expression can match an empty string
-% and that is different from not finding a match
-% it returns error messages in both cases
-% TODO: Ok, but what is the point of matching on an empty string?
-%(if I understand what you mean)? you would not normally define such
-%an extraction?
-% If this distinction is important it needs to be made more clear
-
-% TODO CARO: make more clear that not matching is an error cause
-% pattern didn't match?
 \subsubsection{Application}
@@
 It then returns the substring
-of the build log matched by the program or an error message if the
-program found no match.
+of the build log matched by the program.
+% I hope this is fine, you can also cut this sentence if it still
+% bothers you :)
+If the program finds no match because the analyzed build logs
+does not contain the structure defined by the training examples,
+PBE returns an error message.
 
@@
 To configure chunk retrieval through text similarity we chose to use
-the same concept of examples as for PBE
-% Moritz: your question was: More details on this.
-% How do you
-% 'apply' VSM? On what?
-% all the following sentences in this subsubsection describe our way
-% of determining text similarity which as far as I understand and
-% Annibale said is the VSM.
-% word tokens, tf-idf, similarity measure
-% I added a "as follows", think that is enough for explanation?
-% Moritz: I think it is good, but the VSM is still unexplained.
-%We need a
-% (at least) 1-sentence introduction to it, at its first reference
-% TODO Moritz: I removed all other references, this is now the first one.
-% I hope I got your comment right and now the first and only reference
-% is explained :)
-% TODO Slightly better, but I still have a problem with this -- what
-% exactly is the vector
-% space model here?
-% At a minimum, the text should mention what the vector is and how the
-% model is used
-and apply the Vector Space Model~\cite{schutze2008introduction}
-as follows:
-The lines of the output strings of the training examples define our
+the same concept of examples as for PBE.
+The lines of the output strings of the training examples define the
 search query.
-The algorithm splits the search query into single lines and
-identifies tokens, in this case words.
-Then we build a
-document-term-frequency matrix over the lines from the search query
-and prune very often or very rarely appearing words.
+We represent each line as a term vector where each entry counts
+how often a word appears within the line.
+These vectors exist in a space ith as many dimensions as different
+words appear in the log text.
+This Vector Space Model~\cite{schutze2008introduction} defines
+text lines as more similar if they contain the same words in the same
+frequencies, meaning their term vectors point in a similar direction
+in the vector space.
+We use the cosine function to calculate the angle between two
+term vectors.
+The smaller the angle between term vectors, the more similar are the
+corresponding lines.
+This is called \emph{cosine similarity}~\cite{korenius2007principal}.
+
+To improve the similarity calculation, we prune very often or
+very rarely appearing words.
 Finally, the
-algorithm applies TF-IDF to the matrix, a best practice for natural
+algorithm weighs the vectors using TF-IDF, a best practice for natural
 language queries~\cite{lee1997document}.

### 2020-04-25 tse-paper/content.tex
new study explanation draft

@@
 
-\section{Study Design}
+% TODO -- this is a wrong title -- !!
+% TODO find better one
+\section{Empirical Comparison Study}
 
@@
 
-In the following, we present the data set we created for this study,
-our study process (presented in \Cref{fig:study}), and the metrics
-we measure to answer our research questions.
-
 \begin{figure*}[tb]
@@
   clip]{img/study.pdf}
+  % TODO wrong caption!!! find adequate one
 	\caption{Design of the technique comparison study.}
@@
 
-\subsection{LogChunks}
+% TODO this might need some glue / intro text
+
+\subsection{LogChunks Data Set}
+\label{sec:logchunks}
 To conduct the study in this paper, we created the
@@
 programming languages.
-For each file, the authors manually ``labeled
+For each file, we manually ``labeled
 the log part (chunk) describing why the build
@@
 
-\subsection{Study Process}
-% FIXME introduce term example
-% FIXME mention study figure
+This, the build log text, the corresponding chunk,
+the search keywords, and the assigned structural categories
+make up one \emph{example}.
+Examples are the basic units in the training and test sets of our
+empirical comparison study.
+
+% TODO: find better title!!!!
+\subsection{Study Execution}
+\Cref{fig:study} gives an overview over the steps within our empirical
+comparison study.
+In the following, we each of the steps and the metrics
+we measure to answer our research quest
+
 % TODO: I think you need to introduce a concept that makes clear what one
-% ``folder'' consists of ...
-% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
-% we operate on all repos in LogChunks?
-We begin by selecting all examples in \emph{LogChunks}
-that correspond to one GitHub repository---and thus the
-% TODO () is meant to reference the figure, but this the figure is not
-%actually mentioned.
-same build environment (1).
-% TODO: What does this mean? Of what nature are the examples? How were
-%they chosen?
-% Isn't it rather the case that for each repository, we built traning
-%ets of size 1, 2,
-% ...
-%5 build logs?
-One to five examples make up the training set (2).
+% ``folder'' consists of ...ions.
+
+We apply every one of the four chunk retrieval techniques
+% TODO Check abstraction level: leave out acronyms?
+(PBE, CTS, KWS, and RLR) on all 80 repositories represented in
+\emph{LogChunks} \circlenum{1}.
+For each repository, we select training sets of size 1, 2, \dots 5
+examples \circlenum{2}.
+% For this, we select all examples in \emph{LogChunks}
+% (as defined in \Cref{sec:logchunks})
+% We begin by selecting all examples
+% that correspond to one GitHub repository---and thus the
+% same build environment (1).
 We vary its size to measure how many examples we need to
@@
 (see \Cref{sec:lit-sur:discussion}).
-% TODO: The example? why only one? And what is an example? An example
-%build log?
-% Then it would be good to say so.
-The example chronologically after the training set makes up the
-test set (3).
+% TODO: The example? why only one?
+The test set consists of an example based on the build log produced
+chronologically after the build logs in the training set \circlenum{3}.
 In this way, we train on examples from past build logs and test on
 more recent logs.
-We chose a test set size of 1, as users of the techniques
-should receive reliable results on every build log they analyze.
-% TODO and why is this important? Doesn't everyone want such stability
+% We chose a test set size of 1, as users of the techniques
+% should receive reliable results on every build log they analyze.
+% M: and why is this important? Doesn't everyone want such stability
 %of results?
-% motivation why only one test example.
+% C: motivation why only one test example.
 % we can also leave that out
@@
 	True positives are lines that appear both in the output of a
-	tool as well as what \textit{LogChunks} contains for the
+	technique as well as the chnuk defined in the
   test example.
@@
 
-% This is a weird position for this paragraph
-% TODO What is ``this'' referring to? You just defined a bunch of
-%equations.
-This concludes one run within our evaluation.
-We conduct one run for each of the four chunk retrieval techniques,
-for each of the eighty repositories in \emph{LogChunks} (8)
-and for each of the five training set sizes (2).
-In total we perform 1600 runs, 400 for each of the implemented chunk
-retrieval
-technique.
-
 \section{Results}
+% TODO check abstraction level: mention PBE, CTS etc?
 This section first presents the results for each chunk retrieval
 technique separately.
-Afterwards, we compare the three techniques with each other and to RLR
-as a baseline.
+Afterwards, we compare the three techniques with each other and to a
+random baseline.
 

### 2020-04-25 tse-paper/content.tex
update study figure to fit new text

@@
 	\centering
-	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
+	\includegraphics[width=\textwidth, trim={1.6cm 2.5cm 0.2cm 4.8cm},
   clip]{img/study.pdf}
@@
 In the next step, we configure a chunk retrieval technique with
-the examples from the training set (4) and apply the technique to the
-training set (5), which produces the retrieval output (6).
-Based on this, we collect the following measurements (7):
+the examples from the training set \circlenum{4} and apply the technique
+to the
+training set \circlenum{5}, which produces the retrieval output
+\circlenum{6}.
+Based on this, we collect the following measurements \circlenum{7}:
 the size of the training set (\textbf{RQ2.1}),
@@
 	True positives are lines that appear both in the output of a
-	technique as well as the chnuk defined in the
+	technique as well as the chunk defined in the
   test example.
@@
 % Caveat, I think ;-) Also, we should say why we THINK this is not
-the case.
+%the case.
 % Otherwise we weaken our work unduly

### 2020-04-26 tse-paper/content.tex
status from before the meeting today

@@
 }
+
+\tableofcontents
 
@@
 describe it in sufficient detail and that
-% TODO Moritz: 14 is still quite big, it's 'impl available' when we saw
+% C: 14 is still quite big, it's 'impl available' when we saw
 % no overlap.
@@
 {\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
-% TODO (resolved): All of these are passive
-% it says resolved, but they still are?
+% M: All of these are passive
+% C: it says resolved, but they still are?
 % I exchanged 'extracted' with targeted / analysis
@@
 %TODO here we sell our techniques as superior.
-match in intro?
+% match in intro?
 %TODO: really? currently the discussion does not show this 'need'!
@@
 
-\subsection{The case for chunk retrieval on build logs}
-% FIXME Caro
+\subsection{The Case for Chunk Retrieval on Build Logs}
 In summary, the results of the literature study show the need for
@@
 \label{sec:expl-rlr}
-% TODO: could you add two-three more references to the results of RLR in
-% the discussion, to show how even seemingly low numbers are much better
-% than RLR?
-% TODO QUESTION: should I add those here? as references to the disc?
-% or in the discussion? (you also already added some)
-% In general: I think we talk a lot about RLR and it gets wordy.
 
@@
 giving it a slight advantage.
-
-% TODO: these next two sections do not belong under this section --
-%they are not a chunk retrieval technique.
-%One way to fix it would be to rename the section.
-% TODO QUESTION: Caro show whole structure
-% -> introduction to crts, investigated techniques, ???
 
@@
 % TODO -- this is a wrong title -- !!
-% TODO find better one
+% find better one
 \section{Empirical Comparison Study}
 
-% TODO This section is not structured well.
-%First, it misses an
-% explanation of the bigger study design.
 %Second, What is the difference between Study Process and
@@
 % level).
-%Perhaps a solution would be to be a bit inspired by this
-% paper:
-%https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
-% There is a research design section (which we are missing) and a
-% Research Method section (which is a mixture of the current section
-% titled Log Chunks and Study Process)
 
@@
 In the following, we each of the steps and the metrics
-we measure to answer our research quest
-
-% TODO: I think you need to introduce a concept that makes clear what one
-% ``folder'' consists of ...ions.
+we measure to answer our research questions.
 
@@
 (see \Cref{sec:lit-sur:discussion}).
-% TODO: The example? why only one?
 The test set consists of an example based on the build log produced
@@
 	We define a successful retrieval as one where all desired
-	lines were
-	extracted, therefore when recall is one.
+	lines were extracted, therefore when recall is one.
+  % TODO introduce partially successful and (new) unsuccessful
 \end{itemize}
@@
   \end{lstlisting}
-  \caption{Example for an unsuccessful retrieval (PBE retrieved only
+  \caption{Example for a partially successful retrieval
+  (PBE retrieved only
   two of the four targeted lines).}
@@
 
-% TODO Say something about this being a pecularity of PBE ...
+% actually, we could cut this figure and move it's explanation
+% to the next one (this is an aggregation of the next one)
+% however, having them separate eases the entry into the results a bit
+% and we have explanation of the categories before the more complicated
+% aspect of the change with more structural categories
 \Cref{fig:failure-reason-PBE} shows the results of chunk
 retrieval with PBE.
+It shows how many of the retrieval runs were successful or
+partially successful, as well as the number of runs where the
+synthesized program did not match on the analyzed build log or where
+no program could be synthesized.
+% The last two results stem from the regular expressions and their
+% synthesis, therefore only apply to PBE.
 Out of the overall 400 runs, 5 per each one of the 80 example
@@
 In 59 cases, PBE could synthesize a regular expression program, though
-it did not find match on the test build log.
+it did not match on the test build log.
 In 30 cases, the synthesized program only extracted a
@@
 was 28\%.
-% TODO: Perhaps we should call it partially successful? Let's
-% discuss this in a meeting
-% TODO QUESTION: yes we can :)
 \Cref{lst:pbe-unsuccessful} shows how an example of such
-an \emph{unsuccessful retrieval} looks like.
+an \emph{partially successful retrieval} looks like.
 In it, the synthesized program only
@@
 
-% TODO introudce this fig at large.
-%Soemthing like: Zooming in
-% on only the successful retrievals from (...), Fig ...
-%shows ...
-
-\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
+\Cref{fig:failure-reason-categorycount-PBE} shows how
+the results of PBE
 runs depend on the number of structural categories in the training and
 test examples.
+% It shows the categories from above change depending on how many
+% structural categories are present.
 The figure demonstrates that program synthesis mostly
@@
 
-\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
-precision and recall of the 227 runs where PBE could synthesize a
-program consistent with all training examples.
+Zooming in on only the 227 runs where PBE could synthesize a program,
+\Cref{fig:recall-precision-examplecount-sythesisworked-PBE}
+presents violin plots of the precision, the recall
+and the F$_{1}$-score
+of these runs compared with the number of examples in the training set.
+The black horizontal lines show the average of these measurements.
 When the training set
@@
 \label{sec:r:cts}
+
 \begin{figure*}
@@
 retrieval with Common Text Similarity (CTS) compared by \ldots}
+\label{fig:results-CTS}
 \end{figure*}
 
-% TODO what about referencing the combined figure at first: something
-%like shows the results of CTS on two beanplots of ...
-%and ...., and then the subfigure
-% TODO this goes for all techniques
-% TODO QUESTION: yes, though then we have more redundant text
-% that repeats everywhere and is already in the captions
-% -> should we add it for the first time we include a type of figure?
-% TODO Yes, that sounds good.
-% FIXME CARO You might even say Figure 12-15 show two
+% You might even say Figure 12-15 show two
 % plots in the short text under the section heading.
@@
 % text flow so much better.
-\Cref{fig:recall-precision-examplecount-CTS} presents precision,
-recall, and F$_{1}$-score of chunk retrieval using CTS for an
+
+% The following sections are each quite short...
+% we could merge them, but then it loses consistency with the other
+% result subsections where each plot gets an own paragraph
+
+\Cref{fig:results-CTS} shows violin plots
+of the precision,
+recall, and F$_{1}$-score of the chunk retrieval runs with CTS.
+%The black horizontal lines show the average of these measurements.
+
+\Cref{fig:recall-precision-examplecount-CTS} presents the
+measurements for an
 increasing number of training examples.
@@
 
-\Cref{fig:recall-precision-categorycount-CTS} shows the same
+\Cref{fig:recall-precision-categorycount-CTS} shows the
 measurements for an increasing number of structural categories in the
@@
 Keyword Search (KWS) compared by \ldots}
+\label{fig:results-KWS}
 \end{figure*}
 
-\Cref{fig:recall-precision-examplecount-KWS} presents precision,
-recall, and F$_{1}$-score of chunk retrieval using KWS for different
+\Cref{fig:results-KWS} shows violin plots
+of the precision,
+recall, and F$_{1}$-score of the chunk retrieval runs with KWS.
+%The black horizontal lines show the average of these measurements.
+
+\Cref{fig:recall-precision-examplecount-KWS} presents these
+measurements for different
 numbers of training examples.
@@
 
-% TODO Perhaps, above in our section about logchunks, we would need some
+% M: Perhaps, above in our section about logchunks, we would need some
 % basic empirical stats -- e.g., how long are the files and how much
 % do we usually extract from the log
+% C: yup, that would be nice
+% sadly, it's quite a bit of work to get those :/
+% maybe I/We'll do it at the end
 \subsection{Random Line Retrieval}
@@
 \subsection{Comparison of All Techniques}
-%TODO too short
-% TODO CARO give outlook on results here
-In this section, we aggregate and compare the results from
-\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr}.
-
-% TODO CARO? check type of graph introduced
-\Cref{fig:success-partial-all} compares the success of chunk
-retrievals differentiated by techniques in our study.
-% TODO It shows on the vertical axis the number of ?runs? ...
-% and on the horizontal ...
+In this section, we compare the results of all four chunk retrieval
+techniques and show the impact of structural categories on precision,
+recall and F$_{1}$-scores of the different techniques.
+
+% absolute results? is there a nice word for these results
+\Cref{fig:success-partial-all} compares the results all of chunk
+retrievals techniques in our study.
+It shows how many runs per technique were successful, partially
+successful or unsuccessful in retrieving the chunk defined in the
+test example.
 CTS and KWS
@@
 retrieval runs.
+All techniques clearly outperform the random baseline (RLR).
 
@@
 than one category being present, the recall of PBE decreases greatly.
-% TODO this is not a meaningful comparsion to RLR.
-%One would be to say that
-% all of these techniques beat RLR handsdown -> discussion!
-% TODO QUESTOIN: well they don't in this picture (PBE, multiple sc)
-% maybe we can say that one figure earlier?
 For CTS and KWS the values also decrease, while RLR is not affected by
 the number of structural categories present.
+Again, all techniques---except for PBE with multiple structural
+categories---yield better retrievals than RLR.
 
@@
 
-% TODO decision tree -> recommendation schema? You can use the more
-%specific decision
-% tree when referencing the figure.
 For the interpretation of the study results, we look at each chunk
 retrieval technique separately.
-We give recommendations for
+Next, we discuss
+which criteria should influence the decision to use a certain
+chunk retrieval technique most.
+Based on the empirical comparison, we present a
+decision tree between the three techniques we investigated.
+
+\subsection{Interpretation of Study Results}
+Following from the results of the empirical study,
+we give recommendations for
 which types of log chunks and how many training examples
@@
 how their output can be used further.
-Following that, we discuss
-which of these criteria should influence the decision to use a certain
-chunk retrieval technique most.
-Based on the empirical comparison, we present a
-decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-% TODO CARO
-%Begin the section by saying what you do in there
-% Then at the end, say that you summarized it in Table 3 (or include
-%Table 3
-% in the discussion throughout the text.)
-\Cref{tab:single-technique-recommendations} summarizes the
-recommendations which we discuss
-in this section.
+We summarize these recommendations in
+\Cref{tab:single-technique-recommendations}.
 
@@
 \textbf{Configuration and Input.}
-Our study results show that chunk retrieval with PBE gives best
+The study results show that chunk retrieval with PBE gives best
 results when the log chunks are structurally identical.
@@
 		clip]{img/crt-recommendation.pdf}
-		\caption{Our preliminary recommendation scheme for chunk
+		\caption{Our decision tree for chunk
 		retrieval techniques.}
@@
 \subsection{Recommendation of Suitable Techniques}
-% TODO CARO Make intro less generic?
-After discussing the three chunk retrieval techniques separately we
-now want to unify the results into one recommendation scheme.
-% TODO Try to inductiviely let the figure emerge from the text, not this
-% ``here is the figure; eat it''.
-% C: ``How should I do this?''
-% TODO CARO
-% Already a better solution would be at the end of this section: We
-% summarized these conditions in the decision tree in Fig ...
-% also reference to the parts of the figure during the explanation
-\Cref{fig:crt-recommendation} presents a decision tree
-to answer the second research question;
+We saw, that each of the techniques is suited for different types of
+log chunks and the output of each is suited for different uses.
+Now, we unify these results into conditions to answer
+our second research questions;
 If researchers or developers want to retrieve chunks from build logs,
-they can follow the decision tree to identify the technique
+they can follow these conditions to identify the technique
 suited best for their use case.
-The decision tree is built up of questions
+% I want to ref the figure early bc I believe the text is easier
+% to follow when looking at the figure as well
+We summarize these conditions in the decision tree in
+\Cref{fig:crt-recommendation}.
+It is built up of questions
 which either lead to more questions or to a leaf node containing a
 recommended technique.
-
-% TODO QUESTION
-% shouldn't it also better be in threats to validity?
-% it is as well.
-%back for my thesis you said we should put it
-% directly here to make it more prominent avoid angry critics
-% I think it's good here
-% but it's also self-contained so feel free to comment it out
-
-% TODO we can't just have a paragraph in a scientific paper start with
+At the end of this section we give two concrete examples on how to
+apply our decision tree.
+
+% we can't just have a paragraph in a scientific paper start with
 % Caveat, I think ;-) Also, we should say why we THINK this is not
@@
 % Otherwise we weaken our work unduly
-\textbf{Caveat!}
-This is a preliminary hypothesis based on the results
-from our comparison study.
-The recommendations could therefore be
-influenced by idiosyncrasies of our specific implementation of the
-chunk retrieval techniques as well as the \emph{LogChunks}
-data set.
+% Of course we can! xD
+% Agree with the rest.
+It's in TtV, quite close actually
+% so I'll comment this out
+% also #moreselling :D
+% \textbf{Caveat!}
+% This is a preliminary hypothesis based on the results
+% from our comparison study.
+% The recommendations could therefore be
+% influenced by idiosyncrasies of our specific implementation of the
+% chunk retrieval techniques as well as the \emph{LogChunks}
+% data set.
 
@@
 same structural category.
+This is why the first question in \Cref{fig:crt-recommendation} asks
+how many structural categories the targeted log chunks have.
 
@@
 If precision is more important than recall, we
-recommend CTS\@.
+recommend CTS, as \Cref{fig:crt-recommendation} shows on the
+right half of the decision tree.
 We also recommend CTS when the log chunks are
@@
 would rather have output with low recall instead of no output at all.
-When the representations are from one structural category and the user
+On the leftmost path of the decision tree,
+when the representations are from one structural category and the user
 wishes high confidence in the correctness of the output or prefers
@@
 
-\subsection{Using the Recommendation Scheme}
-% TODO QUESTION: which one do you mean here?
-% TODO Perhaps add introduction from recommendation scheme here?
-
-% TODO this is very nice again, perhaps a tiny bit on the trivial side.
-% TODO CARO Do reference Figure 17 more, thoguh
+\subsection{Using the Decision Tree}
 To illustrate how one would use the decision tree to find a suitable
@@
 from one structural category.
-Therefore, the development team can use
+Therefore, following the leftmost path in
+\Cref{fig:crt-recommendation},
+the development team should use
 PBE to retrieve the duration of a build phase.
@@
 failing test cases from each build log.
-When they use our
-recommendation scheme to select a chunk retrieval technique, they
+When they use the
+decision tree to select a chunk retrieval technique, they
 first have to estimate how uniform the representation of the failing
@@
 retrieved.
-Therefore, the decision tree recommends the researcher to use KWS\@.
+Therefore, following the rightmost path in
+\Cref{fig:crt-recommendation},
+the decision tree recommends the researcher to use KWS\@.
 
@@
 size as a user has to provide the training examples
-per repository or project.
-We expect a developer or a researcher
-to not want to provide more examples than the
-small numbers we evaluated on.
-% TODO maybe reference back to little effort technique in lit discus.
+per repository or project and one of the central aims of the chunk
+retrieval techniques is that they can be set up wit little effort.
 The fact that PBE and KWS performed best with already two training
@@
 % up to in F1 score, which is x times better than RLR)
-% TODO could also mention future research here: Finally, we gave an
-% outline to guide future research efforts in the area of build log
-% analysis.
 The goal of this paper is to support practitioners and researchers in

### 2020-04-26 tse-paper/content.tex
Fix BibTeX

@@
 
-Within the past two decades, Continuous Integration (CI) has become a
+In the past two decades, Continuous Integration (CI) has become a
 ubiquitous best practice to streamline the build process of software
@@
 The
-contents of build logs can be highly variable depending on which tools
-are involved in the build process and how they are
-configured.
-The format of logs changes as projects and build tools evolve over time.
+contents and format of build logs can vary highly depending on which tools
+are involved in the build process, how they are
+configured, and as projects and build tools evolve over time~\cite{}.
 Typically, though, they are at least a semi-structured and

### 2020-04-26 tse-paper/content.tex
Include review until page 2

@@
 are involved in the build process, how they are
-configured, and as projects and build tools evolve over time~\cite{}.
+configured, and as projects and build tools evolve over time~\cite{staahl2014modeling}.
 Typically, though, they are at least a semi-structured and
@@
 over 50 megabytes large~\cite{beller2017oops}, finding the small chunk
-of information in it which is linked to the error, is akin to
-searching for a needle in a haystack.
+of information in it which is linked to the actual error, is akin to
+searching for a needle in a haystack. The large numbers of unrelated, but amibguous warnings that many build logs regularly contain, further compounds this problem.
 In addition to helping
@@
 duration~\cite{ni2017cost,bisong2017built,haghighatkhah2018test,machalica2019predictive},
-or investigate static analysis tools in CI
+or investigate the role of automated static analysis tools (ASATs, \cite{beller2016analyzing}) in CI
 builds~\cite{zampetti2017open}.
@@
 custom parsers, using regular expressions, doing manual inspections,
-natural language processing, information retrieval, or searching
-for keywords.
+searching for keywords, or performing natural language processing.
+However, there is currently no guidance on when to use which of these approaches.
 Unfortunately, our survey also shows that
@@
 describe it in sufficient detail and that
-% C: 14 is still quite big, it's 'impl available' when we saw
-% no overlap.
-Decide whether you want to keep this in :)
-only 14 independent implementations are available, one of which stems
-from the second author of this paper.
-Out of these implementations, all are based on either a custom parser
+the few available implementations are all based on either a custom parser
 or regular expressions.
+These two approaches in particular are problematic, as their creation and maintenane is manual and expensive, does not generalize across build logs from different build environments, and is, as the experience of TravisTorrent has shown, prone to error.
+In fact, some even ``strongly discourage'' the creation of such
+bespoke parsers~\cite{urli2018design}. In summary, the outcome of our literature survey shows the need for a new
+generation of automated techniques to analyze build logs, which are documented in detail and which are openly available, together with guidance on when to use which tool.
+
 %Using 1) a set of
@@
 % TODO caro: maybe convert this into a proper ordered list?
-As a consequence, we took it upon ourselves (step 2) to provide
-implementations of the three most promising automatic build log analysis
-techniques we observed in the literature survey:
+To fill this gap, we adapted and implemented three novel, prototypical implementations to
+automatically analyze build logs. The ideas behind the implementations are based on promising approaches adopted from other research fields and automatic build log analysis
+techniques:
 a technique 1) able to automatically synthesize regular expressions,
@@
 \emph{Keyword Search (KWS)}.
-Even though these three approaches---regular expressions, text similarity,
+These three approaches---regular expressions, text similarity,
 keyword search---
-have different strengths and weaknesses, the literature
-survey shows that their use often seems arbitrary.
+have different strengths and weaknesses.
 As a consequence,
@@
 2}}
-How do build log analysis techniques compare against each other?
+How do build log analysis techniques compare?
 \end{simplebox}
@@
 However,
-% TODO 1-2 sentences about results, inclduing some accuracy measures
+% TODO Caro: 1-2 sentences about results, inclduing some accuracy measures
 
@@
 to further inspect and interpret the output chunk.
-A hybrid-solution combining the three techniques might be the best
+A hybrid solution combining the three techniques might be the best
 all-round solution.
@@
 analysis.
-We start with a differentiation to the related field of
+We start with a differentiation to the field of
 system log analysis.
@@
 logs which are produced during runtime of the system.
-The first difference here is that build logs are produced during runtime
+The first difference is that build logs are produced during runtime
 of the build of the system, not during runtime of the system itself.
@@
 attach boxed title to top center={yshift=-6mm}]
-{\textbf{RQ2:} How do build log analysis techniques compare against
-each other?}
+{\textbf{RQ2:} How do build log analysis techniques compare?}
 \begin{itemize}[leftmargin=1.2cm]

### 2020-04-27 tse-paper/content.tex
update graphics and pbe partially successful listing, include all notes for me from last meeting

@@
 are involved in the build process, how they are
-configured, and as projects and build tools evolve over time~\cite{staahl2014modeling}.
+configured, and as projects and build tools evolve over
+time~\cite{staahl2014modeling}.
 Typically, though, they are at least a semi-structured and
@@
 of information in it which is linked to the actual error, is akin to
-searching for a needle in a haystack. The large numbers of unrelated, but amibguous warnings that many build logs regularly contain, further compounds this problem.
+searching for a needle in a haystack.
+The large numbers of unrelated, but amibguous warnings that many build
+logs regularly contain, further compounds this problem.
 In addition to helping
@@
 duration~\cite{ni2017cost,bisong2017built,haghighatkhah2018test,machalica2019predictive},
-or investigate the role of automated static analysis tools (ASATs, \cite{beller2016analyzing}) in CI
+or investigate the role of automated static analysis tools (ASATs,
+\cite{beller2016analyzing}) in CI
 builds~\cite{zampetti2017open}.
@@
 searching for keywords, or performing natural language processing.
-However, there is currently no guidance on when to use which of these approaches.
+However, there is currently no guidance on when to use which of these
+approaches.
 Unfortunately, our survey also shows that
@@
 or regular expressions.
-These two approaches in particular are problematic, as their creation and maintenane is manual and expensive, does not generalize across build logs from different build environments, and is, as the experience of TravisTorrent has shown, prone to error.
+These two approaches in particular are problematic, as their creation
+and maintenane is manual and expensive, does not generalize across build
+logs from different build environments, and is, as the experience of
+TravisTorrent has shown, prone to error.
 In fact, some even ``strongly discourage'' the creation of such
-bespoke parsers~\cite{urli2018design}. In summary, the outcome of our literature survey shows the need for a new
-generation of automated techniques to analyze build logs, which are documented in detail and which are openly available, together with guidance on when to use which tool.
+bespoke parsers~\cite{urli2018design}.
+In summary, the outcome of our literature survey shows the need for a new
+generation of automated techniques to analyze build logs, which are
+documented in detail and which are openly available, together with
+guidance on when to use which tool.
 
@@
 % TODO caro: maybe convert this into a proper ordered list?
-To fill this gap, we adapted and implemented three novel, prototypical implementations to
-automatically analyze build logs. The ideas behind the implementations are based on promising approaches adopted from other research fields and automatic build log analysis
+To fill this gap, we adapted and implemented three novel, prototypical
+implementations to
+automatically analyze build logs.
+The ideas behind the implementations are based on promising approaches
+adopted from other research fields and automatic build log analysis
 techniques:
@@
 
-% when we argue about this later we leave out the middle so A and B
-% match.
-whe then say that the long tail benefits from the generic
-% solution.
-Yes all benefit, but I think it's simpler like this.
+% TODO Caro: adapt as discussed
 \begin{figure}[tbhp]
@@
 
+	% actually that is now giving recall another (nicer) name
+	% improved if we just talk about recall later?
 	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
 	\mathit{Recall} = 1, \mathit{false\ otherwise}\vspace{0.1cm}$
+	Partially Successful retrieval = $\mathit{true}\ \mathit{iff}\
+	0 < \mathit{Recall} < 1, \mathit{false\ otherwise}\vspace{0.1cm}$
+	Unsuccessful retrieval = $\mathit{true}\ \mathit{iff}\
+	\mathit{Recall} = 0, \mathit{false\ otherwise}\vspace{0.1cm}$
 
@@
 	lines were extracted, therefore when recall is one.
-  % TODO introduce partially successful and (new) unsuccessful
+	A retrieval is partially successful if at least some of the
+	desired lines were extracted.
+	If the retrieved lines contain none of the desired lines
+	a retrieval was unsuccessful.
 \end{itemize}
@@
   \centering
-  \begin{lstlisting}[breaklines=true]
-Test Output:
+\begin{subfigure}[b]{\columnwidth}
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+[0K$ test/sass-compile-tester.sh
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[backgroundcolor=\color{Yellow!60},breaklines=true,frame=rl]
 Error: Invalid CSS after "2.3em": expected expression (e.g.
 1px, bold), was ";"
-	on line 86 of sass/components/dropdown.sass
-Desired Test Output:
+	on line 86 of sass/components/dropdown.
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+	from line 5 of sass/components/_all.sass
+  \end{lstlisting}
+	\caption{Yellow: chunk retrieval output ($RetrievedLines$)}
+	\label{lst:pbe-part-success-output}
+\end{subfigure}
+
+\begin{subfigure}[b]{\columnwidth}
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+[0K$ test/sass-compile-tester.sh
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
 Error: Invalid CSS after "2.3em": expected expression (e.g.
@@
   \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+  Use --trace for backtrace.
+  \end{lstlisting}
+	\caption{Blue: targeted chunk ($DesiredLines$)}
+	\label{lst:pbe-part-success-desired}
+\end{subfigure}
   \caption{Example for a partially successful retrieval
@@
 sets, PBE extracted all desired lines successfully in 138 cases.
+In 18 cases, the synthesized program only extracted a
+subset of the desired lines, while in 12 cases it extracted none of
+the desired lines.
+For these 18 partially successful, the average recall
+was 47\%.
+\Cref{lst:pbe-unsuccessful} shows how an example of such
+a partially successful retrieval looks like.
+In it, the synthesized program only
+retrieved two (\Cref{lst:pbe-part-success-output})
+of the four (\Cref{lst:pbe-part-success-desired}) targeted lines.
 In 59 cases, PBE could synthesize a regular expression program, though
 it did not match on the test build log.
-In 30 cases, the synthesized program only extracted a
-subset of the desired lines.
-For these 30 cases, the average recall
-was 28\%.
-\Cref{lst:pbe-unsuccessful} shows how an example of such
-an \emph{partially successful retrieval} looks like.
-In it, the synthesized program only
-retrieved two of the four targeted lines.
 In 173 of the 400 cases
@@
 recall, and F$_{1}$-score of the chunk retrieval runs with CTS.
-%The black horizontal lines show the average of these measurements.
+The black horizontal lines show the average of these measurements.
+If the figure shows no violin plot for a category, we only have one
+data point or all data points have the same value.
 
@@
 recall, and F$_{1}$-score of the chunk retrieval runs with KWS.
-%The black horizontal lines show the average of these measurements.
+The black horizontal lines show the average of these measurements.
+If the figure shows no violin plot for a category, we only have one
+data point or all data points have the same value.
 
@@
 
+% capitalized headings / left title column
+% tried it out, I think it looks better with the rest lowercase
 \begin{table}[tbp]
@@
   \midrule
-  \textbf{Structural categories} & 1 & less is better & \makecell[l]{best
+  \textbf{Structural Categories} & 1 & less is better & \makecell[l]{best
   1 \\
@@
   \midrule
-  \textbf{Training set size} & 2 & no influence & 2 \\
+  \textbf{Training Set Size} & 2 & no influence & 2 \\
     \midrule
@@
     \midrule
-  \makecell[l]{\textbf{Confidence in} \\ \textbf{Output correctness}}
+  \makecell[l]{\textbf{Confidence in} \\ \textbf{Output Correctness}}
   & high & low &
   \makecell[l]{low (precision) \\ high (recall)} \\	\midrule
-  \textbf{Output consumer} & program & human & human \\
+  \textbf{Output Consumer} & program & human & human \\
   \bottomrule
@@
 % Agree with the rest.
-It's in TtV, quite close actually
+% It's in TtV, quite close actually
 % so I'll comment this out
@@
 Our study design can be reused to evaluate other build log
-analysis techniques, such as the diff and information retrieval
-approach by Amar et al.~\cite{amar2019mining}.
-% TODO: mention an actual chunk retrieval technique from the survey
-% if possible
+analysis techniques, such as the parser Tomassi et al.
+used to create
+BugSwarm~\cite{tomassi2019bugswarm} or the regex-based approach
+Beller et al.
+used to create TravisTorrent~\cite{beller2017oops}.
 
@@
 % detail.
-%Mention general accuracy measures (techniques performed
-% up to in F1 score, which is x times better than RLR)
+ TODO Mention general accuracy measures (techniques performed
+up to in F1 score, which is x times better than RLR)
 The goal of this paper is to support practitioners and researchers in

### 2020-04-28 tse-paper/content.tex
Review included incl page 3

@@
 content~\cite{he2017towards}.
-\Cref{lst:system-log} shows
-example lines from a system log.
+\Cref{lst:system-log} depicts two
+examplary lines from such a system log.
 
 The first goal in analyzing system log files is generally to
-separate constant and variable parts within a log
+separate the constant and variable parts within a log
 message~\cite{nagappan2010abstracting,he2017towards}.
@@
 on build logs as well, such as methods to retrieve the
-values of variable parts in a log message, e.g.\ by using regular
+values of variable parts in a log message, e.g.\, by using regular
 expressions~\cite{nagappan2010abstracting,xu2009detecting}.
@@
 
-\subsection{Study Selection}
-\Cref{fig:lit-survey} presents an overview of the study selection
-process.
+\subsection{Literature Selection}
+The first step in a systematic literature study is to establish which works one wants to cover and how to find them~\cite{kitchenham2009systematic}.
 Since the field of build log analysis is relatively young, we
@@
 We did not limit the sources to specific Software Engineering
-venues~\cite{petersen2015guidelines}, but survey all sources
+venues~\cite{petersen2015guidelines}, but included all sources
 monitored by Google Scholar, including Bachelor's theses, Master's
@@
 We use Google Scholar as opposed to Scopus or
-other databases because it is the search engine for academic articles with
+other databases because it is the search engine for scholarly material with
 the broadest and most current index, including preprints.
 
-An initial Google Scholar search for variations of ``build log''
-returned more than 2.2 million results (2020-03-15), many of which stem
-from unrelated fields such as construction and wood working.
+\Cref{fig:lit-survey} gives an overview of the study selection
+process. An initial Google Scholar search for variations of ``build log''
+returned more than 2.2 million results on the 15th of March 2020, many of which stem
+from unrelated fields such as construction or wood working.
 We refined the search criteria to exclude such obvious
-non-related fields and also to exclude works on systems
+non-related fields and to exclude works on systems
 or event logs (see \Cref{sec:system-log-analysis}).
-This left us with 1,552 search results
-(2020-03-15).
+This left us with 1,552 search results.
 % Our replication package documents the full search
@@
 First, we filtered articles based on (a) their title and (b) the
-contextual information Google Scholar displayed.
+contextual information Google Scholar displayed on its search results overview page.
 We included works at large that seemed to bear a resemblance to software
 engineering and building software.
-We excluded works written in a language unintelligible to the authors
+Following Kitchham's protocol~\cite{kitchenham2009systematic}, we excluded works written in a language unintelligible to the authors
 (i.e., not English or German), which disregarded fewer than 1\% of search
@@
 
-Subsequently, we performed a second, finer filter phase by downloading the
-full text of the works, reading their abstracts, and searching the
+Second, we performed a finer filter phase by (1) reading their abstracts, and (2) downloading the
+full text of the works and searching the
 full text
@@
 If a work showed traces of
-working with build logs, we included it in the survey.
+working with build logs, we included it for the next filter phase.
 In total, we
@@
 
-\subsection{Article Classification}
+Third, since we had been careful to include rather than exclude borderline
+works, a deeper evaluation excluded another 15 articles from the 87
+works left after the second filter phase.
+Multiple articles were extensions of others.
+Of these, we only considered the earliest article which reported on
+the analyzing of build logs.
+This excluded another 11 articles.
+In sum, we extracted data from 61 articles.
+
+\subsection{Literature Classification}
 Having trimmed down the set of articles by 95\%, we investigated the
-remaining ones in depth.
-We wanted to characterize how research uses build logs.
-
+remaining ones in-depth.
+We wanted to characterize how research works with build logs.
+
+% TODO  everything is in passive in the following
 Specifically, we were interested in
@@
 % C: it says resolved, but they still are?
+% M: Only the first one still is (don't know how to convert it), the others
+% are not?
 % I exchanged 'extracted' with targeted / analysis
@@
 
-Since we had been careful to include rather than exclude borderline
-works, this deeper evaluation excluded another 15 articles from the 87
-works left after the second filter phase.
-Multiple articles were extensions of others.
-Of these, we only considered the earliest article which reported on
-the analyzing of build logs.
-This excluded another 11 articles.
-In sum, we extracted data from 61 articles.
-
-To guide the data extraction we created a template.
-The template form contained questions to answer RQ 1.1 through RQ 1.3,
+To support the data extraction we created a template that we filled out for each of the 61 works.
+The template contained questions to answer RQ 1.1 through RQ 1.3,
 for example ``Is the technique explained in detail?'' and
@@
 al.~\cite{petersen2015guidelines}, we started the mapping study with a
-pilot study:
+pilot:
 both authors extracted data from the same five articles and held a
@@
 We divided the remaining 56 articles evenly between the two authors
-and inspected each as closely as necessary to fill out the template
+and inspected each articlex as closely as necessary to fill out the template
 with confidence,
@@
 of a virtual open card sorting~\cite{zimmermann2016card}.
-An example for this is the source of the analyzed build logs,
-where we assigned tags such as ``Travis CI'',
-``Industrial'', ``Google'', or
-``self built''.
-Once we had classified all works, we went into the second phase
-(``execution phase'') in which we grouped tags
+An example for this is the question ``What is the source of the build log?'',
+where we assigned tags such as ``Travis CI,''
+``Industrial,'' ``Google,'' or
+``self-built.''
+Once we had classified all works, we went into the second phase of card sorting
+(``execution phase''), in which we grouped tags
 together and found synonyms.
@@
 For instance, in the case of the build log source we grouped
-``Travis'' and ``travis ci'' together and assigned ``Industrial'' to
+``Travis'' and ``Travis CI'' together and assigned ``Industrial'' to
 all articles that used build logs provided by a company.
-The full data extraction template and our results of this step can be
-found in our replication package~\cite{brandt2020chunk-replication}.
-
+The replication package contains the data extraction template and all results of this step~\cite{brandt2020chunk-replication}.
+
+\subsection{Descriptive Study Statistics}
+To be done.
+
+\subsection{Results}
 \addtolength{\tabcolsep}{-5pt}
@@
 
-\subsection{Results}
 In this section, we present the results of the analysis phase of the
@@
 \subsubsection{What information is targeted in build logs? (RQ 1.1)}
-
 The precise information targeted in the build logs varied from article

### 2020-04-28 tse-paper/paper.tex
new study explanation draft
Fix BibTeX
Review included incl page 3

@@
 \newcommand{\tinyish}{\fontsize{6.5pt}{6.15pt}\selectfont}
+\newcommand{\circlenum}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
 
@@
 % Do not put math or special symbols in the title.
-\title{How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques}
+
+% TODO: No spaces before/after ---
+\title{How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques}
 %
@@
 use which technique.
-We close with a roadmap of important open problems in the
-emerging field of
+We close with a roadmap of important open problems in the field of
 build log analysis.

### 2020-04-28 tse-paper/content.tex
Implement more fixes

@@
 \subsection{Literature Selection}
-The first step in a systematic literature study is to establish which works one wants to cover and how to find them~\cite{kitchenham2009systematic}.
+The first step in a systematic literature study is to
+establish which works one wants to cover and how to find
+them~\cite{kitchenham2009systematic}.
 Since the field of build log analysis is relatively young, we
@@
 We use Google Scholar as opposed to Scopus or
-other databases because it is the search engine for scholarly material with
+other databases because it is the search engine for scholarly material
+with
 the broadest and most current index, including preprints.
@@
 \Cref{fig:lit-survey} gives an overview of the study selection
-process. An initial Google Scholar search for variations of ``build log''
-returned more than 2.2 million results on the 15th of March 2020, many of which stem
+process.
+An initial Google Scholar search for variations of ``build log''
+returned more than 2.2 million results on the 15th of March 2020, many
+of which stem
 from unrelated fields such as construction or wood working.
@@
 First, we filtered articles based on (a) their title and (b) the
-contextual information Google Scholar displayed on its search results overview page.
+contextual information Google Scholar displayed on its search results
+overview page.
 We included works at large that seemed to bear a resemblance to software
 engineering and building software.
-Following Kitchham's protocol~\cite{kitchenham2009systematic}, we excluded works written in a language unintelligible to the authors
+Following Kitchham's protocol~\cite{kitchenham2009systematic}, we excluded
+works written in a language unintelligible to the authors
 (i.e., not English or German), which disregarded fewer than 1\% of search
@@
 
-Second, we performed a finer filter phase by (1) reading their abstracts, and (2) downloading the
+Second, we performed a finer filter phase by (1) reading their abstracts,
+and (2) downloading the
 full text of the works and searching the
@@
 % C: it says resolved, but they still are?
-% M: Only the first one still is (don't know how to convert it), the others
+% M: Only the first one still is (don't know how to convert it),
+% the others
 % are not?
@@
 
-To support the data extraction we created a template that we filled out for each of the 61 works.
+To support the data extraction we created a template that we filled out
+for each of the 61 works.
 The template contained questions to answer RQ 1.1 through RQ 1.3,
@@
 We divided the remaining 56 articles evenly between the two authors
-and inspected each articlex as closely as necessary to fill out the template
+and inspected each articlex as closely as necessary to fill out the
+template
 with confidence,
@@
 of a virtual open card sorting~\cite{zimmermann2016card}.
-An example for this is the question ``What is the source of the build log?'',
+An example for this is the question ``What is the source of the build
+log?'',
 where we assigned tags such as ``Travis CI,''
@@
 ``self-built.''
-Once we had classified all works, we went into the second phase of card sorting
+Once we had classified all works, we went into the second phase of
+card sorting
 (``execution phase''), in which we grouped tags
@@
 all articles that used build logs provided by a company.
-The replication package contains the data extraction template and all results of this step~\cite{brandt2020chunk-replication}.
+The replication package contains the data extraction template and all
+results of this step~\cite{brandt2020chunk-replication}.
+
+\subsection{Results}
+\addtolength{\tabcolsep}{-5pt}
+
+In this section, we give a general overview over our paper population
+and then present the results of the analysis phase of the literature
+mapping along RQ 1.1 through RQ 1.3.
 
@@
 To be done.
-
-\subsection{Results}
-\addtolength{\tabcolsep}{-5pt}
-\begin{table*}[tbhp]
-\tinyish
-\centering
-\caption{Overview of build log analysis techniques.}
-\begin{tabularx}{\textwidth}{@{}lXl@{}}
-
-\toprule
-Name			     & Sources	& Frequency	  \\
-\midrule
-
-\raisebox{0.8mm}{Parser} &
-\raisebox{0.8mm}{
-\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
-\\
-
-\raisebox{0.8mm}{Regular expression} &
-\raisebox{0.8mm}{
-\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
-\\
-
-\raisebox{0.8mm}{Manual inspection} &
-\raisebox{0.8mm}{
-\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
-\\
-
-\raisebox{0.8mm}{Machine Learning} &
-\raisebox{0.8mm}{
-\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
-\\
-
-\raisebox{0.8mm}{Natural Language Processing}	&
-\raisebox{0.8mm}{
-\cite{hassan2017change,lou2019history,schulz2017active}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
-\\
-
-\raisebox{0.8mm}{Information Retrieval} &
-\raisebox{0.8mm}{
-\cite{hassan2017change,lindqvist2019detection,ren2018automated}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
-\\
-% TODO: We need to mention in the text describing the Table what we mean
-%by ``Analysis''
-\raisebox{0.8mm}{Analysis} &
-\raisebox{0.8mm}{
-\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
-\\
-
-\raisebox{0.8mm}{Keyword Search} &
-\raisebox{0.8mm}{
-\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
-\\
-
-\raisebox{0.8mm}{Scan} &
-\raisebox{0.8mm}{
-\cite{clemencic2014new,hibbard2001visualization}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
-\\
-
-\raisebox{0.8mm}{Other} &
-\raisebox{0.8mm}{
-\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
-\\
-
-\raisebox{0.8mm}{None identified} &
-\raisebox{0.8mm}{
-\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
-} &
-\\
-
-\specialrule{\heavyrulewidth}{0pt}{2pt}
-
-\end{tabularx}
-\label{tab:litsur:techniques}
-\end{table*}
-\addtolength{\tabcolsep}{5pt}
+% TODO moritz: age of papers (graph), kind of
+% publication (master, paper)
+% published (y, n)
+
+\subsubsection{What information is targeted in build logs? (RQ 1.1)}
 
@@
 \caption{Multi-label categorization of the 61 relevant articles.}
+\label{fig:litsur_r}
 \end{figure}
 
-In this section, we present the results of the analysis phase of the
-literature mapping along RQ 1.1 through RQ 1.3.
-
-\subsubsection{What information is targeted in build logs? (RQ 1.1)}
-The precise information targeted in the build logs varied from article
-to article.
+In this section, we describe what sort of information papers usually
+extract from build logs, along the results depicted
+in \Cref{fig:litsur_r}.
+
 \Cref{fig:litsur:info_target} gives an overview over the frequency of
 the targeted information.
+The precise information targeted in the build logs varied from article
+to article, with a relatively long tail.
 Most prominent was the search for errors (39\%), followed by extracting
@@
 developers.
-For 8\% of the articles the retrieved information was the input
-to a next automatic on-ward processing step.
-Articles chose
+For 8\% of the articles was the retrieved information the input
+to a next automatic on-ward processing step:
+articles chose
 tests that should be part of a reduced but still effective test
@@
 
+% TODO Moritz: add missing figure
 We also identified the type of information which the articles
@@
 \subsubsection{Which analysis techniques exist? (RQ 1.2)}
+\begin{table*}[tbhp]
+\tinyish
+\centering
+\caption{Overview of build log analysis techniques.}
+\begin{tabularx}{\textwidth}{@{}lXl@{}}
+
+\toprule
+Name			     & Sources	& Frequency	  \\
+\midrule
+
+\raisebox{0.8mm}{Parser} &
+\raisebox{0.8mm}{
+\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
+\\
+
+\raisebox{0.8mm}{Regular expression} &
+\raisebox{0.8mm}{
+\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
+\\
+
+\raisebox{0.8mm}{Manual inspection} &
+\raisebox{0.8mm}{
+\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
+\\
+
+\raisebox{0.8mm}{Machine Learning} &
+\raisebox{0.8mm}{
+\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
+\\
+
+\raisebox{0.8mm}{Natural Language Processing}	&
+\raisebox{0.8mm}{
+\cite{hassan2017change,lou2019history,schulz2017active}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+
+\raisebox{0.8mm}{Information Retrieval} &
+\raisebox{0.8mm}{
+\cite{hassan2017change,lindqvist2019detection,ren2018automated}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+% TODO: We need to mention in the text describing the Table what we mean
+%by ``Analysis''
+\raisebox{0.8mm}{Analysis} &
+\raisebox{0.8mm}{
+\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+
+\raisebox{0.8mm}{Keyword Search} &
+\raisebox{0.8mm}{
+\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+
+\raisebox{0.8mm}{Scan} &
+\raisebox{0.8mm}{
+\cite{clemencic2014new,hibbard2001visualization}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
+\\
+
+\raisebox{0.8mm}{Other} &
+\raisebox{0.8mm}{
+\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
+\\
+
+\raisebox{0.8mm}{None identified} &
+\raisebox{0.8mm}{
+\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
+} &
+\\
+
+\specialrule{\heavyrulewidth}{0pt}{2pt}
+
+\end{tabularx}
+\label{tab:litsur:techniques}
+\end{table*}
+\addtolength{\tabcolsep}{5pt}
+
 \Cref{tab:litsur:techniques} presents the techniques that the articles
@@
 If we saw evidence for the latter, we assigned the tag
-``regular expression'' instead of the tag ``parser''.
+``regular expression'' instead of the tag ``parser.''
 25\% of the articles described the use of regular expressions and 20\%
-inspected the logs manually.
-Another 8\% employed machine learning such as natural language
-processing or information retrieval techniques.
-For example,
+inspected the logs manually. For example,
 Seo et al.~\cite{seo2014programmers} developed a custom
@@
 classifies the remaining logs.
+Another 8\% employed machine learning such as natural language
+processing or information retrieval techniques.
 

### 2020-04-28 tse-paper/content.tex
addressing some todos and writing longer conclusion

@@
 searching for a needle in a haystack.
-The large numbers of unrelated, but amibguous warnings that many build
+The large numbers of unrelated, but ambiguous warnings that many build
 logs regularly contain, further compounds this problem.
@@
 and
-duration~\cite{ni2017cost,bisong2017built,haghighatkhah2018test,machalica2019predictive},
+duration~\cite{ni2017cost,bisong2017built,haghighatkhah2018test,
+machalica2019predictive},
 or investigate the role of automated static analysis tools (ASATs,
@@
 These two approaches in particular are problematic, as their creation
-and maintenane is manual and expensive, does not generalize across build
+and maintenance is manual and expensive, does not generalize across build
 logs from different build environments, and is, as the experience of
@@
 
-% TODO caro: maybe convert this into a proper ordered list?
+% M: maybe convert this into a proper ordered list?
+% TODO Moritz: not sure what you mean here ?
+% I agree that the non-itemized looks better than before
 To fill this gap, we adapted and implemented three novel, prototypical
@@
 the others.
-However,
-% TODO Caro: 1-2 sentences about results, inclduing some accuracy measures
+PBE has the best average precision of 95\%, while KWS has the largest
+recall with 70\% on average.
+However, CTS shows the best F$_{1}$-score
+of 51\% and all of the three techniques
+clearly outperform a random baseline.
 
@@
 
-% TODO something like overall, we argue that our implementations and their
-% weaknesses stand prototypical for the techniques and tried to limit
-% idiosyncrazies as much as possible (give example)
+% kinda uncreative..
+not sure what another example would be?
+% not sure if this adds much on top of the sentences further up
+Overall, we believe our implementations and their weaknesses stand
+prototypical for the techniques.
+We tried to limit idiosyncrasies as much as possible, by choosing
+standard approaches and configurations.
 
@@
 \label{sec:conclusion-fw}
-% TODO CARO conclusion should be a bit longer and a little bit more in
-% detail.
- TODO Mention general accuracy measures (techniques performed
-up to in F1 score, which is x times better than RLR)
+
 The goal of this paper is to support practitioners and researchers in
@@
 log analysis techniques.
-We then
-implemented three promising chunk retrieval techniques and compared
-their performance on the \emph{LogChunks} data set.
-Our results show
+We saw that while build log analysis is widely used, it is often
+a side-part of the article and implementations are rarely reused.
+This shows the need for a new generation of generic and automated
+build log analysis techniques that need little effort to set up.
+Based
+on common approaches we saw during the literature survey,
+we implemented three promising techniques to retrieve specific
+substrings (chunks) from build logs:
+PBE synthesizes regular expression programs based on examples of logs
+and corresponding chunks, CTS leverages a common text similarity
+measure to retrieve those lines which are most similar to example
+chunks, and KWS finds the targeted parts of a build log by searching
+for identifying keywords.
+We evaluated the performance of these chunk retrieval techniques on the
+\emph{LogChunks} data set and saw varying results.
+CTS had the highest average F$_{1}$-score with 51\%, while the other
+techniques showed higher average scores for precision (95\%, PBE)
+and recall (70\%, KWS).
+To guide researchers and developers on which technique to use for their
+we summarized our results in a decision tree.
+We found
 that the structural representation of the targeted information in the
-build logs is the main factor to consider when choosing a suitable
+build logs is the main factor a user should consider when they
+choose a suitable
 technique.
@@
 more important for the task at hand.
-
 Finally, we gave an
@@
 analysis.
-Important themes are
-% TODO Caro complete :-)
+Important themes are a systematic investigation of industry approaches,
+benchmarks of existing build log analysis approaches and further
+refinement of the chunk retrieval techniques we proposed.

### 2020-04-28 tse-paper/content.tex
Review until page 6

--- 2020-04-28 tse-paper/content.tex
@@
 \subsubsection{What information is targeted in build logs? (RQ 1.1)}
-
+\label{sec:rq11}
 \begin{figure}
@@
 25\% of the articles described the use of regular expressions and 20\%
-inspected the logs manually. For example,
+inspected the logs manually.
+For example,
 Seo et al.~\cite{seo2014programmers} developed a custom
@@
 orellana2017differences,zhao2018comparing} or
-an extended version of them~\cite{rott2019empirische,
+an updated version of them~\cite{rott2019empirische,
 shi2018evaluating}, two used the
-\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
-another two the
-\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.
+\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}, and
+another two 
+\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao}.
 
@@
 Of the articles we surveyed, 30\% analyzed
-Maven~\cite{maven2019website} build logs,
-16\% analyzed Gradle~\cite{gradle2020website} logs
-and 10\% analyzed Ant~\cite{ant2020website} logs.
-
-A large amount of the articles within the survey, analyze build logs
+Mave~\cite{maven2019website},
+16\% analyzed Gradle~\cite{gradle2020website},
+and 10\% analyzed Ant build logs~\cite{ant2020website}.
+
+A large amount of the articles analyze build logs
 from a small number of build tools.
@@
 ~\cite{staahl2014modeling} and
-therefore ``parsers must be specialized to each build and test
-framework''~\cite{tomassi2019bugswarm}.
-% remove following part of this paragraph?
-% I think it is a nice anecdote but not super necessary yes.
+therefore \textbf{``parsers must be specialized to each build and test
+framework''}~\cite{tomassi2019bugswarm}.
 Sometimes, aspects separate from the build log analysis motivate
-their limitation to a specific build tool.
-For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
+the limitation to a specific build tool.
+For example, Shi et al. focussed on Maven
 build logs because they also chose the PIT tool to calculate coverage
-and mutation score.
+and mutation score~\cite{shi2018evaluating}. PIT is only available as a Maven plugin.
 
@@
 several described they are covering multiple source build tools.
-The majority of articles (42\%) targeted logs from a source that no
+The majority of articles (42\%) used logs from a source that no
 second article
 targeted.
-
 In 38\% of cases, the articles collected build logs from Travis
-CI~\cite{travisci2019webpage}.
-18\% of the articles processed logs from TravisTorrent and 8\% included
+CI~\cite{travisci2019webpage};
+18\% of the articles processed logs from TravisTorrent; and 8\% included
 build logs from industrial projects.
-
-% perhaps remove this paragraph?
-% C: made it more specific, this is the only reference in the result
-% which supports 'we need automatic because so many logs are analy'
 The number of logs analyzed varied greatly between the articles
@@
 investigated up to 122 million logs.
-
-31\% of the surveyed articles claimed to have published their data to
+Of the surveyed articles, 31\% claim to have published their data to
 enable further research.
@@
 % TODO Caro: adapt as discussed
+% TODO: I think the axes labels are also unncessary for this graph.
+%Our other graphs in the lit survey do not have them, either.
 \begin{figure}[tbhp]
@@
 post-factum
-parsing of logs redundant.
-Plugins  similar to, for example, the Maven plugin to report test
-executions Bell et al.
-%TODO cite
-wrote, have the disadvantage of not being able to work on historic
-builds.
+parsing of logs redundant. Their advantage is that they can precisely report the information which is required.
+A downside of plugins, which are integrated into the CI flow similar to Deflaker by Bell et al.~\cite{bell2018deflaker}, is that they are unable to work on historic
+builds, i.e., before the moment they were being deployed and that if information has not been recorded from the beginning but turns out to be important, it is impossible to retrieve later.
 2) the large tail of seldomly-investigated environments would benefit
@@
 detail.
+% TODO At the end of what?
 At the end we illustrate how the techniques operate on a concrete
@@
 analysis techniques that are \emph{automated},
-\emph{build-environment agnostic}
+\emph{agnostic of the build environment}
 and can be \emph{configured with little effort}.
@@
 \emph{Examples consist of logs and corresponding chunks.}
-The user provides these examples and keywords, which can simply be
-exchanged whenever new cases are introduced.
+The user provides these examples and keywords, which are easy to adapt whenever the user adds new examples.
 
@@
 previously described by several articles:
-PBE mimics regular expressions and parsers while simplifying
+PBE mimics regular expressions, while simplifying
 their development.
@@
 This was also the information
-most targeted by the articles in our survey
+most targeted by the articles in our survey (see \Cref{sec:rq11}).
 In addition to that, our data set encompasses a broad range of
@@
 \subsection{Characteristics of Chunk Retrieval Techniques}
+% TODO Caro: Wouldn't this place perhaps be better to contain
+%the pargraph about why chunk log techniques are more general
+% than other approaches?
+
 \label{sec:crt-characteristics}
-Next, we will present our definition of chunk retrieval techniques
-which automatically
+In this section, we formalize our use of chunk retrieval techniques. By this word, we refer to techniques that automatically
 retrieve pieces of information that appear literally in build

### 2020-04-28 tse-paper/content.tex
Autoformat

@@
 shi2018evaluating}, two used the
-\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}, and
+\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
+and
 another two
@@
 the limitation to a specific build tool.
-For example, Shi et al. focussed on Maven
+For example, Shi et al.
+focussed on Maven
 build logs because they also chose the PIT tool to calculate coverage
-and mutation score~\cite{shi2018evaluating}. PIT is only available as a Maven plugin.
+and mutation score~\cite{shi2018evaluating}.
+PIT is only available as a Maven plugin.
 
@@
 post-factum
-parsing of logs redundant. Their advantage is that they can precisely report the information which is required.
-A downside of plugins, which are integrated into the CI flow similar to Deflaker by Bell et al.~\cite{bell2018deflaker}, is that they are unable to work on historic
-builds, i.e., before the moment they were being deployed and that if information has not been recorded from the beginning but turns out to be important, it is impossible to retrieve later.
+parsing of logs redundant.
+Their advantage is that they can precisely report the information which
+is required.
+A downside of plugins, which are integrated into the CI flow similar to
+Deflaker by Bell et al.~\cite{bell2018deflaker}, is that they are unable
+to work on historic
+builds, i.e., before the moment they were being deployed and that if
+information has not been recorded from the beginning but turns out to
+be important, it is impossible to retrieve later.
 2) the large tail of seldomly-investigated environments would benefit
@@
 \emph{Examples consist of logs and corresponding chunks.}
-The user provides these examples and keywords, which are easy to adapt whenever the user adds new examples.
+The user provides these examples and keywords, which are easy to adapt
+whenever the user adds new examples.
 
@@
 \label{sec:crt-characteristics}
-In this section, we formalize our use of chunk retrieval techniques. By this word, we refer to techniques that automatically
+In this section, we formalize our use of chunk retrieval techniques.
+By this word, we refer to techniques that automatically
 retrieve pieces of information that appear literally in build

### 2020-04-28 tse-paper/content.tex
Fix some blibs

@@
 The concept of \emph{Programming by Example} aims to capture the
-intent of the user through examples which they provide.
+intent of the user through examples which they provide in an automatically generated program.
 Leveraging this approach, we implemented a chunk retrieval technique
@@
 text extraction DSL \emph{FlashExtract}~\cite{le2014flashextract:}.
-Both enable us to synthesize regular expression programs
+Both enable \emph{PROSE} to synthesize regular expression programs
 consistent~\cite{mitchell1982generalization} with a set of in-
-and output examples given by the user.
+and output examples.
 The usage of example enables the user to configure a chunk
@@
 because the regular expression
-necessary is too complicated to synthesize, PBE returns the
+necessary is too complicated to be synthesized, PBE returns the
 error message ``no program found.''
@@
 If the program finds no match because the analyzed build logs
-does not contain the structure defined by the training examples,
+do not contain the structure the training examples define,
 PBE returns an error message.
@@
 We investigate a chunk retrieval technique that
-retrieve those lines from a build log which are most
+retrieves those lines from a build log which are most
 similar to examples given by the user.
@@
 Finally, the
+% TODO TF-IDF undefined
 algorithm weighs the vectors using TF-IDF, a best practice for natural
@@
 lines in the outputs of the training examples determines how many of
-the most similar lines are returned as the output of the retrieval
+the most similar lines our approach returns as the output of the retrieval
 run.
@@
 compare KWS with PBE and CTS, we also configure it through examples.
+% TODO: unclear
 We associate each example with keywords which appear in the targeted
@@
 
+% TODO: unclear. or do you mean: same number == all searched for ?
 KWS then searches for those keywords which are tied to the greatest
@@
 The number of surrounding lines retrieved is
-the average of lines in the output of the training examples.
+the average of lines in the specification output of the training examples.
 
@@
 
-To fully comprehend how difficult a task build log analysis really
+To fully comprehend how difficult a task build log analysis 
 is without any a-priori knowledge, we include a comparison with a
 base line of
-picking lines randomly from the build log (RLR).
+picking lines at random from the build log (RLR).
 RLR mimics the
@@
 number of lines in the chunks of the training examples, thus arguably
-giving it a slight advantage.
+giving it a slight advantage over guessing without previous knowledge.
 
@@
 
+% TODO: want to?
+% real-world log LogChunks ?
 To illustrate the chunk retrieval techniques further, we want to give
@@
 different structural representation) to the training set,
-PBE is not able to synthesize a program and returns
+PBE is not able to synthesize a program anymore and returns
 ``\texttt{no program found}.''
@@
 It will then return the two lines ranked highest, as the chunks in
-the training examples have on average two lines.
+the training examples have on average 2.0 lines.
 
@@
 For the examples from \Cref{lst:chunk-example} these could be
-``FAILURE,'' ``wrong,'' or ``failed''.
+``FAILURE,'' ``wrong,'' or ``failed.''
 The example from \Cref{lst:chunk-example-3} could be found
@@
 To investigate when the chunk retrieval techniques are suited to
-analyze build logs (\textbf{RQ2}), we perform an empirical comparison
+analyze build logs, we perform an empirical comparison
 study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
@@
 	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}\vspace{0.1cm}$
+	\mathit{Recall} = 1, \mathit{false\ otherwise}\vspace{0.1cm}
+        \\$
 	Partially Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	0 < \mathit{Recall} < 1, \mathit{false\ otherwise}\vspace{0.1cm}$
+	0 < \mathit{Recall} < 1, \mathit{false\ otherwise}\vspace{0.1cm}
+        \\$
 	Unsuccessful retrieval = $\mathit{true}\ \mathit{iff}\
@@
 retrieval with Common Text Similarity (CTS) compared by \ldots}
+% TODO: where are the bean plots?
 \label{fig:results-CTS}
@@
 
+% TODO 
 % You might even say Figure 12-15 show two
@@
 The first and most important aspect that influences a choice for
-a chunk retrieval technique are the structural categories.
-Are the targeted log chunks always presented in
+a chunk retrieval technique are the structural categories. In other words,
+are the targeted log chunks always presented in
 the same structural way within the build logs? Then the information

### 2020-04-28 tse-paper/content.tex
Make code subfigures

@@
 of a virtual open card sorting~\cite{zimmermann2016card}.
-An example for this is the question ``What is the source of the build
+An example of this is the question ``What is the source of the build
 log?'',
@@
 The concept of \emph{Programming by Example} aims to capture the
-intent of the user through examples which they provide in an automatically generated program.
+intent of the user through examples which they provide in an automatically
+generated program.
 Leveraging this approach, we implemented a chunk retrieval technique
@@
 
-% TODO: unclear. or do you mean: same number == all searched for ?
+% TODO: unclear.
+or do you mean: same number == all searched for ?
 KWS then searches for those keywords which are tied to the greatest
@@
   \end{lstlisting}
-\end{subfigure}
     \caption{Two examples of log chunks explaining why an Android
@@
   \label{lst:chunk-example}
-\end{figure}
-
-\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
-RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
-\begin{figure}[tbp]
-  \centering
-  \lstinputlisting[breaklines=true]{listings/prose.txt}
-  \caption{Simplified regular expression produced by PBE when trained
-  with examples from \Cref{lst:chunk-example}}
-  \label{lst:prose-program-simplified}
-\end{figure}
-
-\lstset{
-  language=,
-  morekeywords={},
-  texcl=false
-}
-\begin{figure}[tbp]
-  \centering
+\end{subfigure}
+
+\begin{subfigure}[tbp]{\columnwidth}
   \begin{lstlisting}[breaklines=true,frame=tlr]
@@
   \end{lstlisting}
-  \caption{Example of a log chunk showing a linter error}
+  \caption{Example of a log chunk showing a linter error.}
   \label{lst:chunk-example-3}
+\end{subfigure}
+
+\caption{Examplary log excerpts.}
+\label{lst:logexamples}
+\end{figure}
+
+\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
+RegexPair,
+  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
+\begin{figure}[tbp]
+  \centering
+  \lstinputlisting[breaklines=true]{listings/prose.txt}
+  \caption{Simplified regular expression produced by PBE when trained
+  with examples from \Cref{lst:chunk-example}.}
+  \label{lst:prose-program-simplified}
 \end{figure}
@@
 }
-\begin{figure}[!t]
+\begin{figure}[tbp]
   \centering
@@
 \end{subfigure}
-  \caption{Example for a partially successful retrieval
+  \caption{Example of a partially successful retrieval
   (PBE retrieved only
   two of the four targeted lines).}
+  % TODO: shouldn't the label be partially successful? ;-)
   \label{lst:pbe-unsuccessful}
@@
 The first and most important aspect that influences a choice for
-a chunk retrieval technique are the structural categories. In other words,
+a chunk retrieval technique are the structural categories.
+In other words,
 are the targeted log chunks always presented in

### 2020-04-28 tse-paper/content.tex
improve lit discussion and emp comparison study explanation

@@
 %\section{introduction}
-% TODO: What about the alternate solution, installing plugins to report
-% precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% TODO It would be futile to compare our techniques with one of the
+
+% Good point, but we don't really need it anywhere:
+%
+% It would be futile to compare our techniques with one of the
 % existing manual regex parsers, as (a) as our literature survey showed,
@@
 projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}.
-Build logs are a textual by-product that automatic software build
-processes create.
+Build logs are a textual by-product that these automatic software
+builds create.
 As a treasure trove of information~\cite{meyer},
@@
 over 50 megabytes large~\cite{beller2017oops}, finding the small chunk
-of information in it which is linked to the actual error, is akin to
+of information which is linked to the actual error, is akin to
 searching for a needle in a haystack.
-The large numbers of unrelated, but ambiguous warnings that many build
-logs regularly contain, further compounds this problem.
+The large numbers of unrelated, but ambiguous
+warnings, which many build
+logs regularly contain, further compound this problem.
 In addition to helping
@@
 the process of how to
-automatically analyze build logs has thus far not been systematically
+%automatically
+% ^ we survey manual as well, though leaving it out includes too much
+systematically
+analyze build logs has thus far not been systematically
 overviewed as a research topic, bringing us to the first
@@
 \Cref{fig:overview}---with an
-extensive literature study (step 1).
-The literature
-survey identifies various strategies to
+extensive literature survey (step 1).
+The survey identifies various strategies to
 analyze build logs, among which are developing
@@
 and maintenance is manual and expensive, does not generalize across build
-logs from different build environments, and is, as the experience of
+% TODO Moritz: should we say 'our' experience? or 'one authors'?
+% the latter might be too cumbersome
+logs from different build tools, and is, as the experience of
 TravisTorrent has shown, prone to error.
 In fact, some even ``strongly discourage'' the creation of such
-bespoke parsers~\cite{urli2018design}.
+parsers~\cite{urli2018design}.
 In summary, the outcome of our literature survey shows the need for a new
 generation of automated techniques to analyze build logs, which are
-documented in detail and which are openly available, together with
-guidance on when to use which tool.
+openly available and documented in detail, together with
+guidance on when to use which technique.
 
@@
 
-% M: maybe convert this into a proper ordered list?
-% TODO Moritz: not sure what you mean here ?
-% I agree that the non-itemized looks better than before
+% turned into an itemize again cause the 'sentence' around it was
+% rather broken and itemish anyways
 To fill this gap, we adapted and implemented three novel, prototypical
 implementations to
-automatically analyze build logs.
+automatically analyze build logs (step 2).
 The ideas behind the implementations are based on promising approaches
-adopted from other research fields and automatic build log analysis
-techniques:
-a technique 1) able to automatically synthesize regular expressions,
-called \emph{Program Synthesis by Example (PBE)}, 2) based on information
-retrieval, using \emph{Common Text Similarity (CTS)}  and 3)
-inspired by the manual adhoc-search for key parts in the log, employing
-\emph{Keyword Search (KWS)}.
-These three approaches---regular expressions, text similarity,
-keyword search---
-have different strengths and weaknesses.
+adopted from other research fields and existing build log analysis
+techniques.
+In this article, we present three techniques that analyze a build log
+by retrieving a substring (chunk) that describes a
+specific information:
+\begin{itemize}
+	\item \emph{Program Synthesis by Example (PBE)}, a technique
+	able to
+	automatically synthesize regular expressions,
+	\item a technique based on information
+	retrieval, using \emph{Common Text Similarity (CTS)}
+	\item inspired by the manual adhoc-search for key parts in the
+	log, a
+	technique employing \emph{Keyword Search (KWS)}
+\end{itemize}
+% a technique 1) able to automatically synthesize regular expressions,
+% called \emph{Program Synthesis by Example (PBE)}, a technique
+% 2) based on information
+% retrieval, using \emph{Common Text Similarity (CTS)}	and 3)
+% inspired by the manual adhoc-search for key parts in the log, a
+% technique employing \emph{Keyword Search (KWS)}.
+These three approaches---synthesized regular expressions,
+text similarity,
+keyword search---have
+different strengths and weaknesses.
 As a consequence,
@@
 
-To answer this question, as a third step,
+To answer this question
 we conduct an empirical study assessing the performance
 of these chunk retrieval techniques in
-real-world projects under a variety of conditions.
-Our study is based on the \emph{LogChunks} data
+real-world projects under a variety of conditions (step 3).
+The study is based on the \emph{LogChunks} data
 set~\cite{brandt2020logchunks}, which encompasses 797 build logs from
@@
 of 51\% and all of the three techniques
-clearly outperform a random baseline.
-
-Finally, due to this ambiguity, we develop a set of guidelines
-(\Cref{fig:overview}, step 4)
+clearly surpass a random baseline.
+
+Due to this ambiguity, we develop a set of guidelines
 on how to choose the most suitable build log analysis
-technique for the task at hand.
+technique for the task at hand (step 4).
 We recommend PBE for use cases where the desired information is always
@@
 However, its low precision---it extracts a
-context of multiple lines around a finding---makes it generally
+context of multiple lines around a found keyword---makes it generally
 unsuited for automatic on-ward processing.
@@
 \begin{itemize}
-\item the first systematic study of the emerging field of build log
+\item the first systematic survey of the emerging field of build log
 analysis.
@@
 field.
-\item a replication package~\cite{brandt2020chunk-replication}.
+% (resolved) only point with no adjective
+\item a documented replication package~\cite{brandt2020chunk-replication}.
 \end{itemize}
@@
 \Cref{lst:system-log} depicts two
-examplary lines from such a system log.
+exemplary lines from such a system log.
 
@@
 \subsection{Literature Selection}
-The first step in a systematic literature study is to
+The first step in a systematic literature survey is to
 establish which works one wants to cover and how to find
@@
 
-\Cref{fig:lit-survey} gives an overview of the study selection
+\Cref{fig:lit-survey} gives an overview of the literature selection
 process.
@@
 engineering and building software.
-Following Kitchham's protocol~\cite{kitchenham2009systematic}, we excluded
+Following Kitchenham's protocol~\cite{kitchenham2009systematic},
+we excluded
 works written in a language unintelligible to the authors
@@
 
-% TODO	everything is in passive in the following
 Specifically, we were interested in
 \begin{itemize}
-  \item what information is retrieved from the logs and
-  what the retrieved information is used for (\textbf{RQ1.1})
-  \item which techniques are used to process the build logs,
-  in how much detail they are described, and whether they are published
-  as tools (\textbf{RQ1.2})
-  \item what kind of build logs are used and the origin of these
-  logs.
-(\textbf{RQ1.3})
+  \item what information the researchers retrieve from build logs and
+  what this information is used for (\textbf{RQ1.1}),
+  \item which techniques they to process the build logs,
+  in how much detail the techniques are described,
+	and whether their implemented tools are published
+  (\textbf{RQ1.2}),
+  \item what kind of build logs the researchers analyze
+	and the origin of these logs (\textbf{RQ1.3}).
 \end{itemize}
@@
 {\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
-% M: All of these are passive
-% C: it says resolved, but they still are?
-% M: Only the first one still is (don't know how to convert it),
-% the others
-% are not?
-% I exchanged 'extracted' with targeted / analysis
-% 'information retrieved' or 'information extracted' will give us
-% this is not IR neither IE discussions again
 \begin{itemize}[leftmargin=1cm]
@@
 As recommended by Petersen et
-al.~\cite{petersen2015guidelines}, we started the mapping study with a
+al.~\cite{petersen2015guidelines}, we started the mapping survey with a
 pilot:
@@
 We divided the remaining 56 articles evenly between the two authors
-and inspected each articlex as closely as necessary to fill out the
+and inspected each article as closely as necessary to fill out the
 template
@@
 
-\subsection{Descriptive Study Statistics}
+\subsubsection{Descriptive Study Statistics}
 To be done.
@@
 \\
-% TODO: We need to mention in the text describing the Table what we mean
-%by ``Analysis''
+
 \raisebox{0.8mm}{Analysis} &
@@
 
+Of the 61 articles we inspected, 43 mentioned how they analyzed
+build logs.
+However, only 16 of these described their method in detail.
 \Cref{tab:litsur:techniques} presents the techniques that the articles
 described for analyzing build logs.
-43 of the 61 articles we inspected mentioned how they are analyzing
-build logs.
-However, only 16 of these described their method in detail.
 
@@
 processing or information retrieval techniques.
+The rather general tags ``analysis'' and ``scan'' in
+\Cref{tab:litsur:techniques}, stem---similar to the imprecise
+statements about parsing---from the
+words authors used to describe their techniques.
+%such as
+%``automatically analyzed [the build logs]''.
 
@@
 extract it confidently.
-23 of the articles analyzed more than a thousand build logs, some
+23 of the articles analyzed more than a thousand build logs, while one
 investigated up to 122 million logs.
@@
 
+% ----- descriptive / general -----
 Our literature survey shows that despite its relatively young age
@@
 
-% TODO we are extracting failures in the following studies, which is
-%mainly what
-% literature does, too, right? Highlight here and mention later again
-
-% TODO: this section is crucial.
-% maybe we can highlight important findings, by categorizing them either
-% as further subsubsections or making it bold in the text?
-
 We saw that various researchers analyze build logs, often because the
@@
 
-\textbf{most analysis aims to find out why the build failed}
-
-\textbf{most techniques retrieve chunks from build logs}
-
+% ----- information RQ 1.1 -----
+In regards to the information which was targeted, \textbf{most build log
+analysis approaches aim to retrieve the reason a build failed} by
+targeting ``errors'' or ``failing tests''.
+% which is what we also do in LogChunks
+\textbf{The majority of approaches retrieves specific chunks of
+text from the logs.}
+
+% ----- technique RQ 1.2 -----
 \textbf{Most log analysis is automated.} Automated approaches are
@@
 make manual analysis feasible''~\cite{zolfagharinia2017not}.
-\textbf{Developing automated analysis tools requires a lot of effort.}
+We observed \textbf{very little reuse of build log analysis tools},
+even though
+\textbf{developing automated analysis tools requires a lot of effort}.
 Urli et al.~\cite{urli2018design} strongly discouraged from parsing
-build logs for information as it is ``too error prone,'' other
+build logs for information as it is ``too error prone,'' while other
 articles pointed to the effort of developing a custom tool.
@@
 maintain~\cite{michael2019regexes}.
-
-We observed \textbf{very little reuse of build log analysis tools.}
-This can stem from the
-high specialization of the developed tools in regards to supported
-% TODO: build environments is used a bunch (also in the following), but
-% never defined.
-build environments and targeted information.
-
-% TODO: draw a conclusion together with figure 5: if reuse were higher,
-%lots of effort could be saved?
+% not sure if we can state that (no data on this, more 'impression')
+In addition, we rarely saw articles justifying why they use a certain
+technique to analyze build logs as there is a general \emph{lack of
+guidance on when to use which technique}.
+
+% ----- kinds of build logs RQ1.3 -----
 Several articles noted the variety in log formats for different build
-environments, which requires customizing build log techniques for
-every supported build environment.
+tools, which requires customizing build log techniques for
+every supported build tool.
 % The following two sentences are passive, however flipped around
-% have a different meaning (we want build env -> study count)
+% have a different meaning (we want build tool -> study count)
 \Cref{fig:litsur:log_producer} shows that only a few distinct
-build environments are the target of
+build tools are the target of
 many studies and tools (roughly, area A).
-The majority of build environments was however only targeted by one
+The majority of build tools was however only targeted by one
 article each (roughly, area B).
@@
 existence of a more generic solution.}
-
-% TODO we argue this in the intro!
-% problem: we have no data on this
-\textbf{techniques vary and seem rather randomly applied}
-
-\textbf{modifying the build output is not helpful}, as well as returning
-precise data through other documents than the log.
-This requires access to the build configuration, is also specific to
-the used build environment and prohibits the analysis of
-historical data.
-
-\textbf{TODO embed custom plugin discussion}
-% TODO very disconnected here
-From this, we follow: 1) there is a niche for custom parsers or even
-specialized plugins integrated into the build process to make
-post-factum
-parsing of logs redundant.
+In most cases, \textbf{researchers analyze build logs from open
+source projects}, obtained through Travis CI.
+In addition, we saw several articles that targeted the logs of only
+one specific software project.
+
+% ----- custom build tools -----
+
+% What about the alternate solution, installing plugins to report
+% precise data? Ie., maven plugins
+% - Lots of effort
+% - not a generic solution
+% - how to analyze history where such plugins were not installed
+% - unclear which information you want
+
+% TODO Moritz: is this okay (here)?
+% maybe it's better to add it to Threats to Validity with the heading:
+% \texbf{Modifying the Build Process.}
+An alternative to analyzing build logs, would be to integrate plugins
+that report precise data about the build process, such as the JUnit
+plugin for Jenkins~\cite{jenkins2020junit-plugin}.
+However, such plugins are not available for all build tools and they
+do not enable the analysis of historical data---builds that ran before
+the plugin was installed cannot be analyzed.
+In addition to that, when using such a plugin, one would have to know
+beforehand which information should be reported from a build, whereas
+build log analysis enables us to analyze the wide range of information
+already baked into the build logs.
 Their advantage is that they can precisely report the information which
@@
 be important, it is impossible to retrieve later.
-2) the large tail of seldomly-investigated environments would benefit
-from the existence of a more generic
-solution.
-
-% We implement build environment agnostic build log analysis
+
+% \textbf{modifying the build output is not helpful}, as well as returning
+% precise data through other documents than the log.
+% This requires access to the build configuration, is also specific to
+% the used build tool and prohibits the analysis of
+% historical data.
+
+% \textbf{ embed custom plugin discussion}
+% %  very disconnected here
+% From this, we follow: 1) there is a niche for custom parsers or even
+% specialized plugins integrated into the build process to make
+% post-factum
+% parsing of logs redundant.
+% Plugins  similar to, for example, the Maven plugin to report test
+% executions Bell et al.
+% % cite
+% wrote, have the disadvantage of not being able to work on historic
+% builds.
+% 2) the large tail of seldomly-investigated environments would benefit
+% from the existence of a more generic
+% solution.
+
+% We implement build tool agnostic build log analysis
 % techniques, which are customized to a specific project by
@@
 
+% Alt:
+%\section{Analyzing Build Logs with Chunk Retrieval Techniques}
 \section{Chunk Retrieval Techniques}
 \label{sec:techniques}
-%TODO here we sell our techniques as superior.
-% match in intro?
 %TODO: really? currently the discussion does not show this 'need'!
@@
 
-\subsection{The Case for Chunk Retrieval on Build Logs}
-In summary, the results of the literature study show the need for
+\subsection{A New Generation of Build Log Analysis Techniques}
+In summary, the results of the literature survey show the need for
 build log
@@
 whenever the user adds new examples.
+A user---a developer or a researcher who wants to analyze
+build logs---provides these examples and keywords, which can simply be
 
@@
 To evaluate and compare the three chunk retrieval techniques
-we create a data set with logs from failed builds and corresponding
+we create a data set with logs from failed builds on Travis
+CI---the most-used source of build logs within our survey.
+For each log we marked the corresponding
 chunks that describe error messages or
 ``the reason the build failed.''
-This was also the information
+This was the information
 most targeted by the articles in our survey (see \Cref{sec:rq11}).
 In addition to that, our data set encompasses a broad range of
-build environments which enables us to measure the generic
+build tools which enables us to measure the generic
 applicability of the techniques.
@@
 
-To fully comprehend how difficult a task build log analysis
+To fully comprehend how difficult the task of build log analysis really
 is without any a-priori knowledge, we include a comparison with a
@@
 returned lines is dynamic), we configure RLR to return the average
-number of lines in the chunks of the training examples, thus arguably
+number of lines in the chunks of the training examples.
 giving it a slight advantage over guessing without previous knowledge.
 
-\subsection{Chunk Retrieval Example}
+\subsection{Concrete Example}
 \label{sec:crt-example}
@@
 To illustrate the chunk retrieval techniques further, we want to give
-an example of real-world log LogChunks.
+an example of how the chunk retrieval techniques retrieve chunks from
+real-world build logs.
 \Cref{lst:chunk-example} shows two excerpts
@@
 In fact, if we add the third example from \Cref{lst:chunk-example-3}
-(which has a
-different structural representation) to the training set,
+to the training set (which has a
+different structural representation),
 PBE is not able to synthesize a program anymore and returns
@@
 We later express this difference in structural representation through
-dividing log chunks into \emph{structural categories}.
+separating log chunks into \emph{structural categories}.
 The chunks from \Cref{lst:chunk-example}
@@
 \emph{different structural category}.
+% TODO Moritz: is this fitting here?
+% or too much 'foreshadowing' too far down in the hierachy
 The results of the empirical comparison study on the chunk retrieval
@@
 % find better one
-\section{Empirical Comparison Study}
-
-%Second, What is the difference between Study Process and
-% Study Design? Third, the LogChunks section appears out of nowhere
-% and is not related to the section title (different abstraction
-% level).
-
+\section{Empirical Comparison Study Design}
 \label{sec:study}
 
-To investigate when the chunk retrieval techniques are suited to
-analyze build logs, we perform an empirical comparison
-study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
+\begin{figure*}[tb]
+	\centering
+	\includegraphics[width=\textwidth, trim={1.6cm 2.5cm 0.2cm 4.8cm},
+  clip]{img/study.pdf}
+  % TODO wrong caption!!! find adequate one
+	\caption{Design of the technique comparison study.}
+	\label{fig:study}
+\end{figure*}
+
+In the literature survey we saw that few articles justify why they
+use a certain build log analysis technique and concluded, that there
+is a lack of guidance on when to use which technique.
+% add (see \Cref{sec:lit-sur:discussion}) ?
+To address this lack of guidance we conduct an empirical study
+comparing the three novel chunk retrieval techniques we presented in
+\Cref{sec:techniques}.
+We vary the conditions under which we train and run the techniques
+to answer when a technique performs best and which conditions should
+influence the choice for one technique over the others.
+
 In particular, we are interested in how many examples a technique
@@
 
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={1.6cm 2.5cm 0.2cm 4.8cm},
-  clip]{img/study.pdf}
-  % TODO wrong caption!!! find adequate one
-	\caption{Design of the technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
-% TODO this might need some glue / intro text
+In the following we will introduce the data set we created for this
+study and describe the design of our comparison study.
 
@@
 the log part (chunk) describing why the build
-failed''.
+failed''---the information targeted by most of the articles from our
+literature survey.
 We included keywords, which we
@@
 % TODO: find better title!!!!
-\subsection{Study Execution}
-\Cref{fig:study} gives an overview over the steps within our empirical
-comparison study.
-In the following, we each of the steps and the metrics
+\subsection{Study Method}
+
+ gives an overview over the steps within .
+In the following, we explain each of the steps of our study
+(see \Cref{fig:study})
+and introduce the metrics
 we measure to answer our research questions.
 
-We apply every one of the four chunk retrieval techniques
-% TODO Check abstraction level: leave out acronyms?
-(PBE, CTS, KWS, and RLR) on all 80 repositories represented in
+We apply each of the chunk retrieval techniques
+on all of the 80 repositories represented in
 \emph{LogChunks} \circlenum{1}.
@@
 examples \circlenum{2}.
-% For this, we select all examples in \emph{LogChunks}
-% (as defined in \Cref{sec:logchunks})
-% We begin by selecting all examples
-% that correspond to one GitHub repository---and thus the
-% same build environment (1).
-We vary its size to measure how many examples we need to
+We vary the training set size to measure how many examples we need to
 confidently configure a technique.
@@
 (see \Cref{sec:lit-sur:discussion}).
+
 The test set consists of an example based on the build log produced
 chronologically after the build logs in the training set \circlenum{3}.
-In this way, we train on examples from past build logs and test on
+This way, we train on examples from past build logs and test on
 more recent logs.
@@
 % and answer if we are asked about it
+
 In the next step, we configure a chunk retrieval technique with
@@
 \circlenum{6}.
+
 Based on this, we collect the following measurements \circlenum{7}:
@@
 	A retrieval is partially successful if at least some of the
-	desired lines were extracted.
-	If the retrieved lines contain none of the desired lines
+	desired lines were extracted,
+	and if the retrieved lines contain none of the desired lines
 	a retrieval was unsuccessful.
@@
 \section{Results}
-% TODO check abstraction level: mention PBE, CTS etc?
-This section first presents the results for each chunk retrieval
+The empirical comparison study yielded diverse results for the
+different chunk retrieval techniques
+In this section, we first present the results for each chunk retrieval
 technique separately.
@@
 % maybe I/We'll do it at the end
-\subsection{Random Line Retrieval}
+\subsection{Random Line Retrieval (RLR)}
 \label{sec:r:rlr}
@@
 program yields an output, PBE has high precision and recall.
-The tool
+The technique
 clearly identifies a failing synthesis or when the regular expression
@@
 example of extracting the reason the build failed, KWS is best suited
-if a build can fail in various steps logged by different tools and no
+if a build can fail in various steps logged by different build
+tools and no
 pre-categorization of where the build failed is available.
@@
 the underlying technique: the output of the super analyzer could
-include from which sub-tool it originated and thus facilitate
+include from which sub-technique it originated and thus facilitate
 automatic on-ward processing or interpretation of the result.
 
-\subsection{Using the Decision Tree}
+\subsection{Exemplary Recommendation}
 To illustrate how one would use the decision tree to find a suitable
@@
 To this end, we first
-conducted a systematic mapping study to map out the available build
+conducted a systematic mapping survey to map out the available build
 log analysis techniques.

### 2020-04-28 tse-paper/content.tex
some fixes I merged away

@@
 is required.
+
+% TODO merge nicely
 A downside of plugins, which are integrated into the CI flow similar to
@@
 detail.
-% TODO At the end of what?
-At the end we illustrate how the techniques operate on a concrete
+At the end of this section we illustrate how the techniques
+operate on a concrete
 example and sketch out their implementation.
@@
 base line of
-picking lines at random from the build log (RLR).
+picking lines at random from the build log.
 RLR mimics the
@@
 
-% TODO: want to?
-% real-world log LogChunks ?
-To illustrate the chunk retrieval techniques further, we want to give
+To illustrate the chunk retrieval techniques further, we give
 an example of how the chunk retrieval techniques retrieve chunks from
@@
   two of the four targeted lines).}
-  % TODO: shouldn't the label be partially successful? ;-)
-  \label{lst:pbe-unsuccessful}
+  \label{lst:pbe-partially-successful}
 \end{figure}
@@
 was 47\%.
-\Cref{lst:pbe-unsuccessful} shows how an example of such
+\Cref{lst:pbe-partially-successful} shows how an example of such
 a partially successful retrieval looks like.

### 2020-04-29 tse-paper/content.tex
Add todos for Caro and myself
spellchecker fixes

@@
 
-In the past two decades, Continuous Integration (CI) has become a
+\IEEEPARstart{I}{n}
+the past two decades, Continuous Integration (CI) has become a
 ubiquitous best practice to streamline the build process of software
@@
 % turned into an itemize again cause the 'sentence' around it was
-% rather broken and itemish anyways
+% rather broken and item-ish anyways
 To fill this gap, we adapted and implemented three novel, prototypical
@@
 	retrieval, using \emph{Common Text Similarity (CTS)}
-	\item inspired by the manual adhoc-search for key parts in the
+	\item inspired by the manual ad hoc search for key parts in the
 	log, a
@@
 % retrieval, using \emph{Common Text Similarity (CTS)}	and 3)
-% inspired by the manual adhoc-search for key parts in the log, a
+% inspired by the manual ad hoc search for key parts in the log, a
 % technique employing \emph{Keyword Search (KWS)}.
@@
 Of the articles we surveyed, 30\% analyzed
-Mave~\cite{maven2019website},
+Maven~\cite{maven2019website},
 16\% analyzed Gradle~\cite{gradle2020website},
@@
 % TODO Caro: adapt as discussed
-% TODO: I think the axes labels are also unncessary for this graph.
+% TODO Caro: I think the axes labels are also unnecessary for this graph.
 %Our other graphs in the lit survey do not have them, either.
@@
 
-% TODO merge nicely
+% TODO Caro: merge nicely
 A downside of plugins, which are integrated into the CI flow similar to
@@
 %survey above, section 2.4.2
+% TODO Caro: merge!
 For this reason, we are focussing on techniques that run automatically
@@
 We chose text similarity (CTS) as a common information retrieval
-technique and implement the ad-hoc approach of
+technique and implement the ad hoc approach of
 searching for specific strings or keywords within KWS\@.
@@
 % TODO Caro: Wouldn't this place perhaps be better to contain
-%the pargraph about why chunk log techniques are more general
+%the paragraph about why chunk log techniques are more general
 % than other approaches?
@@
 parser to analyze the entire structure of build logs, but focus on
-ad-hoc extracting just one specific piece of information per
+ad hoc extracting just one specific piece of information per
 configuration.
@@
 Finally, the
-% TODO TF-IDF undefined
+% TODO Caro: TF-IDF undefined
 algorithm weighs the vectors using TF-IDF, a best practice for natural
@@
 When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad-hoc approach they
+large amount of unstructured information, a first ad hoc approach they
 use is to search for related keywords.
@@
 compare KWS with PBE and CTS, we also configure it through examples.
-% TODO: unclear
+% TODO Caro: unclear
 We associate each example with keywords which appear in the targeted
@@
 
-% TODO: unclear.
+% TODO Caro: unclear.
 or do you mean: same number == all searched for ?
@@
 
+% TODO Moritz: reference these in text properly
+
+\lstset{escapeinside=//}
 \begin{figure}[tbp]
@@
   \vspace{-\baselineskip}
+  % TODO Caro: Adapt frame= option to close frame properly
   \begin{lstlisting}[breaklines=true,frame=blr]
@@
 
-\caption{Examplary log excerpts.}
+\caption{Exemplary log excerpts.}
 \label{lst:logexamples}
@@
 RegexPair,
-  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
+  EndExtraction}, keywordstyle=\bfseries\color{black}}
 \begin{figure}[tbp]
@@
 % TODO Moritz: is this fitting here?
-% or too much 'foreshadowing' too far down in the hierachy
+% or too much 'foreshadowing' too far down in the hierarchy
 The results of the empirical comparison study on the chunk retrieval
@@
 retrieval with Common Text Similarity (CTS) compared by \ldots}
-% TODO: where are the bean plots?
+% TODO Caro: check: where are the bean plots?
 \label{fig:results-CTS}
@@
 
-% TODO
+% TODO Caro: check
 % You might even say Figure 12-15 show two
@@
 % so I'll comment this out
-% also #moreselling :D
+% also #more selling :D
 % \textbf{Caveat!}

### 2020-04-29 tse-paper/content.tex
integrate Taico's Feedback

@@
 Despite its central role in helping developers and in enabling
-novel, on-ward processing applications,
+novel, onward processing applications,
 the process of how to
@@
 research question:
+% TODO Discuss: is -research fine? or state-of-the-art more common and
+% still not missused (because industry m)
 \begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
@@
 or regular expressions.
-These two approaches in particular are problematic, as their creation
+These two approaches are problematic, as their creation
 and maintenance is manual and expensive, does not generalize across build
-% TODO Moritz: should we say 'our' experience? or 'one authors'?
+% TODO Discuss/Moritz: should we say 'our' experience? or
+% 'one authors'?
 % the latter might be too cumbersome
-logs from different build tools, and is, as the experience of
-TravisTorrent has shown, prone to error.
+logs from different build tools, and is prone to errors,
+as the experience of
+TravisTorrent has shown~\cite{beller2017travistorrent}.
 In fact, some even ``strongly discourage'' the creation of such
@@
 These three approaches---synthesized regular expressions,
-text similarity,
+text similarity, and
 keyword search---have
@@
 precision and recall of the chunk retrieval is required.
-The results PBE produces are suited for automatic on-ward processing.
+The results PBE produces are suited for automatic onward processing.
 CTS is
@@
 context of multiple lines around a found keyword---makes it generally
-unsuited for automatic on-ward processing.
+unsuited for automatic onward processing.
 Instead, KWS requires a human
@@
 
-In this section, we give a general overview over our paper population
-and then present the results of the analysis phase of the literature
-mapping along RQ 1.1 through RQ 1.3.
+In this section, we give a general overview over our paper population.
+We then present the results of the analysis phase, along the
+RQs 1.1 through 1.3.
 
@@
 
-In this section, we describe what sort of information papers usually
-extract from build logs, along the results depicted
-in \Cref{fig:litsur_r}.
+In this section, we describe what sort of information the articles in
+our survey usually retrieved from build logs.
+These results are depicted in \Cref{fig:litsur_r}.
 
@@
 For 8\% of the articles was the retrieved information the input
-to a next automatic on-ward processing step:
+to a next automatic onward processing step:
 articles chose
@@
 Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
-They started with manual categorizing build logs and selecting
+They started with a manual categorization of build logs and selected
 search strings that identify the target category.
@@
 article each (roughly, area B).
-From this we follow, that the large tail of
+From this we follow that the large tail of
 \textbf{seldomly-investigated
@@
 that report precise data about the build process, such as the JUnit
-plugin for Jenkins~\cite{jenkins2020junit-plugin}.
+plugin for Jenkins~\cite{jenkins2020junit-plugin} or
+Deflaker by Bell et al.~\cite{bell2018deflaker}.
 However, such plugins are not available for all build tools and they
 do not enable the analysis of historical data---builds that ran before
-the plugin was installed cannot be analyzed.
+the plugin was deployed cannot be analyzed.
 In addition to that, when using such a plugin, one would have to know
@@
 
-% TODO Caro: merge nicely
-A downside of plugins, which are integrated into the CI flow similar to
-Deflaker by Bell et al.~\cite{bell2018deflaker}, is that they are unable
-to work on historic
-builds, i.e., before the moment they were being deployed and that if
-information has not been recorded from the beginning but turns out to
-be important, it is impossible to retrieve later.
+% A downside of plugins, which are integrated into the CI flow similar to
+% Deflaker by Bell et al.~\cite{bell2018deflaker}, is that they are unable
+% to work on historic
+% builds, i.e., before the moment they were being deployed and that if
+% information has not been recorded from the beginning but turns out to
+% be important, it is impossible to retrieve later.i
 
@@
 %survey above, section 2.4.2
-% TODO Caro: merge!
 For this reason, we are focussing on techniques that run automatically
@@
 \emph{Examples consist of logs and corresponding chunks.}
-The user provides these examples and keywords, which are easy to adapt
-whenever the user adds new examples.
 A user---a developer or a researcher who wants to analyze
-build logs---provides these examples and keywords, which can simply be
+build logs---provides these examples and keywords, which are easy to
+adapt whenever the analysis needs to be maintained.
 
@@
 training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the substring of a build log that should be extracted.
+they define the chunk of a build log that should be retrieved.
 The PROSE program synthesis then tries to construct a program
@@
 % bothers you :)
-If the program finds no match because the analyzed build logs
-do not contain the structure the training examples define,
-PBE returns an error message.
+% no match is a category later in the results section
+If the program finds no match because the analyzed build log
+does not contain the structure that the training examples define,
+PBE returns the error message ``no match found''.
 
@@
 Finally, the
-% TODO Caro: TF-IDF undefined
-algorithm weighs the vectors using TF-IDF, a best practice for natural
+algorithm weighs the vectors using \emph{term frequency-inverse
+document frequency}, a best practice for natural
 language queries~\cite{lee1997document}.
@@
 compare KWS with PBE and CTS, we also configure it through examples.
-% TODO Caro: unclear
-We associate each example with keywords which appear in the targeted
+We associate a list of keywords with each example.
+The keywords should appear in the targeted
 chunk or close to it.
-
-% TODO Caro: unclear.
-or do you mean: same number == all searched for ?
-KWS then searches for those keywords which are tied to the greatest
-number of examples in the training set.
-If several keywords are associated with the same number of training
-examples, and no other keywords are associated with more training
-examples, KWS searches for all of these keywords.
+Then, we merge these lists and use the most commonly occuring
+keywords for the search with KWS.
 
@@
 For a retrieval run, we take a whole build log file as input and
-search for all exact occurrences of the keywords.
+search for all exact occurrences of the search keywords.
 As keywords are
@@
 \label{sec:expl-rlr}
-
 To fully comprehend how difficult the task of build log analysis really
-is without any a-priori knowledge, we include a comparison with a
-base line of
+is without any a priori knowledge, we include a comparison with a
+baseline of
 picking lines at random from the build log.
@@
 number of lines in the chunks of the training examples.
-giving it a slight advantage over guessing without previous knowledge.
 
@@
 chunks from \Cref{lst:chunk-example}.
-This shows, that the characters structuring the text around the chunk are
+This shows that the characters structuring the text around the chunk are
 crucial for regular expressions to identify a log chunk.
@@
 
-Keywords that appear close to the chunk within
+Keywords that appear in or close to the chunk within
 the build log configure the technique KWS\@.
@@
 
-% TODO -- this is a wrong title -- !!
-% find better one
-\section{Empirical Comparison Study Design}
+\section{Empirical Comparison Study}
 \label{sec:study}
@@
   clip]{img/study.pdf}
-  % TODO wrong caption!!! find adequate one
-	\caption{Design of the technique comparison study.}
+	\caption{Study design of the technique comparison study.}
 	\label{fig:study}
@@
 In the literature survey we saw that few articles justify why they
-use a certain build log analysis technique and concluded, that there
+use a certain build log analysis technique and concluded that there
 is a lack of guidance on when to use which technique.
@@
 programming languages.
-For each file, we manually ``labeled
-the log part (chunk) describing why the build
-failed''---the information targeted by most of the articles from our
+For each file, we manually marked
+the chunk that describes why the build
+failed---the information targeted by most of the articles from our
 literature survey.
-We included keywords, which we
+To be able to configure the keyword search technique,
+the data set associates each chunk with keywords that we
 would use to search for the selected chunk within the log.
@@
 
-% TODO: find better title!!!!
-\subsection{Study Method}
-
- gives an overview over the steps within .
+\subsection{Study Design}
+
 In the following, we explain each of the steps of our study
 (see \Cref{fig:study})
-and introduce the metrics
+and introduce the metrics that
 we measure to answer our research questions.
@@
 For each repository, we select training sets of size 1, 2, \dots 5
-examples \circlenum{2}.
+\circlenum{2}.
 We vary the training set size to measure how many examples we need to
@@
 retrieval with Common Text Similarity (CTS) compared by \ldots}
-% TODO Caro: check: where are the bean plots?
 \label{fig:results-CTS}
 \end{figure*}
-
-% TODO Caro: check
-% You might even say Figure 12-15 show two
-% plots in the short text under the section heading.
-% It just makes the
-% text flow so much better.
 
@@
 % result subsections where each plot gets an own paragraph
-
 \Cref{fig:results-CTS} shows violin plots
@@
 The black horizontal lines show the average of these measurements.
-If the figure shows no violin plot for a category, we only have one
-data point or all data points have the same value.
+For some measurements, the violin plot is not visible because there is
+only one available data point or all data points have the same value.
 
@@
 
-\Cref{fig:results-KWS} shows violin plots
-of the precision,
-recall, and F$_{1}$-score of the chunk retrieval runs with KWS.
-The black horizontal lines show the average of these measurements.
-If the figure shows no violin plot for a category, we only have one
+We present the precision,
+recall, and F$_{1}$-score of the chunk retrieval runs with KWS in
+\Cref{fig:results-KWS}.
+Violin plots show the distribution the values of each measurement,
+while the black horizontal lines show their average.
+If the figure shows no violin plot for a measurement, we only have one
 data point or all data points have the same value.
@@
 \label{sec:r:rlr}
-
 The baseline of randomly
 picking lines from build logs delivers the expected low and
-``random'' results: precision ranges between 8\% and 5\%,
+``random'' results: precision ranges between 5\% and 8\%,
 recall between 6\% and 8\%.
@@
 With a larger number of structural categories within the training and
-test sets, the precision of RLR decreases from 7\% to 0\%.
-Its recall
-increases from 6\%, for one structural category present, to 11\%, for
-three structural categories present and drops to 0\% again for more
-structural categories.
+test sets, the precision of RLR decreases from 7\% to 0\%, while
+the recall varies between 0\% end 11\%.
 
@@
 This preciseness makes output from PBE chunk retrieval
-well-suited for machine consumption and therefore automatic on-ward
+well-suited for machine consumption and therefore automatic onward
 processing.
@@
 \subsection{Recommendation of Suitable Techniques}
-We saw, that each of the techniques is suited for different types of
+We saw that each of the techniques is suited for different types of
 log chunks and the output of each is suited for different uses.
@@
 include from which sub-technique it originated and thus facilitate
-automatic on-ward processing or interpretation of the result.
+automatic onward processing or interpretation of the result.
 
@@
 % kinda uncreative..
-not sure what another example would be?
+% not sure what another example would be?
 % not sure if this adds much on top of the sentences further up
@@
 	``=,'' ``ERROR,''
-  or ``[OK''.
+  or ``[OK]''.
   \item \textbf{Meta-Parameter Optimization for CTS.} Information
@@
 We saw that while build log analysis is widely used, it is often
-a side-part of the article and implementations are rarely reused.
+a side part of an article and implementations are rarely reused.
 This shows the need for a new generation of generic and automated
@@
 more important for the task at hand.
+% TODO Caro: bring more across why it is so important that this field
+% and the research there continues
 Finally, we gave an

### 2020-04-29 tse-paper/paper.tex
improve lit discussion and emp comparison study explanation
spellchecker fixes
integrate Taico's Feedback

@@
 
-% TODO: No spaces before/after ---
 \title{How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques}
@@
 Build logs can serve as a paramount source of
-information for developers to understand and debug depdency, compilation, or
+information for developers to understand and debug dependency, compilation, or
 test failures.
@@
 In this paper, we give a systematic overview of the emerging field of build log analysis.
-In a large-scale literature mapping study, we first survey and categorize the existing methods to
+In a large-scale literature mapping survey, we first survey and categorize the existing methods to
 extract information chunks from build logs.
@@
 % Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word. TODO
+% and "HIS" in caps to complete the first word.
 % \IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''

### 2020-04-29 tse-paper/content.tex
reformulate techniques argumentation, improve conclusion

@@
 }
-
-\tableofcontents
 
@@
 
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
+	\caption{Literature selection process, following
+	\cite{petersen2015guidelines}.}
+	\label{fig:lit-survey}
+\end{figure}
+
 \section{Systematic Literature Mapping Survey}
@@
 analyzed in literature and discuss the implications of these findings.
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Literature selection process, following
-	\cite{petersen2015guidelines}.}
-	\label{fig:lit-survey}
-\end{figure}
 
@@
 
-% TODO Caro: adapt as discussed
-% TODO Caro: I think the axes labels are also unnecessary for this graph.
-%Our other graphs in the lit survey do not have them, either.
 \begin{figure}[tbhp]
 		\centering
-		\includegraphics[width=\columnwidth, trim={1.1cm 0.4cm
+		\includegraphics[width=\columnwidth, trim={1.5cm 0.4cm
 		1.5cm 0.5cm},
 		clip]{img/lit-sur/log_producer_annotated.pdf}
-		\caption{Frequency of supported log producers.}
+		\caption{Frequency of supported build tools.}
 		\label{fig:litsur:log_producer}
@@
 \label{sec:techniques}
-%TODO: really? currently the discussion does not show this 'need'!
-The outcome of our literature survey shows the need for a new
-generation of techniques to analyze build logs.
-In this section we argue how our research sets the first step to
-address this need by introducing three techniques that retrieve
-specific substrings (chunks) from build logs.
-We present defining characteristics of these so called \emph{chunk
-retrieval techniques} and present the techniques we developed in
-detail.
-At the end of this section we illustrate how the techniques
+
+In summary, the outcome of the literature survey show the need for
+build log
+analysis techniques that are \emph{automated},
+\emph{agnostic of the build environment}
+and can be \emph{configured with little effort}.
+
+To address this need,
+we propose a set of so called \emph{chunk retrieval techniques},
+which retrieve a specific substring (called chunk)
+from a build log.
+The techniques we propose run automatically
+and can be easily configured through examples.
+An example in this case consists of a build log together with the
+chunk that should be retrieved.
+A user---a developer or a researcher who wants to analyze
+build logs---provides these examples, which are easy to
+adapt whenever the analysis technique needs
+to support new cases.
+
+We designed and implemented three chunk retrieval
+techniques based on approaches
+previously described by several articles:
+PBE mimics regular expressions, while simplifying
+their development.
+We chose text similarity (CTS) as a common information retrieval
+technique and implement the ad hoc approach of
+searching for specific strings or keywords within KWS\@.
+
+In this section, we define our notion of chunk
+retrieval techniques and present each of the techniques
+we developed in detail.
+Following that, we illustrate how the techniques
 operate on a concrete
@@
 
-\subsection{A New Generation of Build Log Analysis Techniques}
-In summary, the results of the literature survey show the need for
-build log
-analysis techniques that are \emph{automated},
-\emph{agnostic of the build environment}
-and can be \emph{configured with little effort}.
-
-% what we need is some derivation of the three techniques 1) regex 2)
-%cts 3) kws, best repeated here in the discussion and then from the lit
-%survey above, section 2.4.2
-For this reason, we are focussing on techniques that run automatically
-after being configured through examples or keywords.
-\emph{Examples consist of logs and corresponding chunks.}
-A user---a developer or a researcher who wants to analyze
-build logs---provides these examples and keywords, which are easy to
-adapt whenever the analysis needs to be maintained.
-
-To analyze build logs,
-we propose to use chunk retrieval techniques.
-These retrieve a substring,
-that describes a specific information, from a build log.
-Generally, chunk retrieval techniques
-can also be used to classify build logs, e.g.\ by checking
-which substring was retrieved.
-Therefore, chunk retrieval techniques
-cover the great majority of the types of log analysis we saw within
-our survey.
-
-We implement three chunk retrieval techniques based on approaches
-previously described by several articles:
-PBE mimics regular expressions, while simplifying
-their development.
-We chose text similarity (CTS) as a common information retrieval
-technique and implement the ad hoc approach of
-searching for specific strings or keywords within KWS\@.
-
-To evaluate and compare the three chunk retrieval techniques
-we create a data set with logs from failed builds on Travis
-CI---the most-used source of build logs within our survey.
-For each log we marked the corresponding
-chunks that describe error messages or
-``the reason the build failed.''
-This was the information
-most targeted by the articles in our survey (see \Cref{sec:rq11}).
-In addition to that, our data set encompasses a broad range of
-build tools which enables us to measure the generic
-applicability of the techniques.
-
-% The articles within our study mainly tried to retrieve or classify
-% errors or reasons for the build to fail from the logs.
-% Therefore we chose the log chunk ``describing why the build failed''
-% ~\cite{brandt2020logchunks} for our empirical comparison study
-% of chunk retrieval techniques.
-% The techniques we implement are in principle agnostic to the targeted
-% log chunk, thus we believe our results can be generalized to other
-% kinds of log chunks.
-
 \subsection{Characteristics of Chunk Retrieval Techniques}
-% TODO Caro: Wouldn't this place perhaps be better to contain
-%the paragraph about why chunk log techniques are more general
-% than other approaches?
-
 \label{sec:crt-characteristics}
@@
 \emph{chunks}.
-% and the techniques \emph{chunk retrieval techniques}.
+
+Generally, chunk retrieval techniques
+can also be used to classify build logs, e.g.\ by checking
+which substring was retrieved.
+Therefore, chunk retrieval techniques
+cover the great majority of the types of log analysis we saw within
+our survey.
+
 The techniques we investigate here do not require a formal lexer and
@@
 chunk or close to it.
-Then, we merge these lists and use the most commonly occuring
+Then, we merge these lists and use the most commonly occurring
 keywords for the search with KWS.
@@
   \vspace{-\baselineskip}
-  % TODO Caro: Adapt frame= option to close frame properly
   \begin{lstlisting}[breaklines=true,frame=blr]
@@
 
-In the following we will introduce the data set we created for this
+In the following, we introduce the data set we created for this
 study and describe the design of our comparison study.
@@
 \emph{LogChunks} data set~\cite{brandt2020logchunks}.
-It encompasses 797 build logs from Travis CI,
-stemming from a broad range of 80 GitHub repositories and 29
+From Travis CI---the most-used source of build logs within
+according to our literature survey---we collected
+797 build logs that
+stem from a broad range of 80 GitHub repositories and 29
 programming languages.
-For each file, we manually marked
+This wide variety of projects, and the large number of different build
+tools they employ, enables us to measure the generic
+applicability of the chunk retrieval techniques.
+
+For each build log, we manually marked
 the chunk that describes why the build
-failed---the information targeted by most of the articles from our
+failed---the information targeted by most of the articles in our
 literature survey.
@@
 	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 1, \mathit{false\ otherwise}\vspace{0.1cm}
-	\\$
-	Partially Successful retrieval = $\mathit{true}\ \mathit{iff}\
-	0 < \mathit{Recall} < 1, \mathit{false\ otherwise}\vspace{0.1cm}
-	\\$
+	\mathit{Recall} = 1, \vspace{0.1cm}\\$
+	Partially successful retrieval = $\mathit{true}\ \mathit{iff}\
+	0<\mathit{Recall}<1, \vspace{0.1cm}\\$
 	Unsuccessful retrieval = $\mathit{true}\ \mathit{iff}\
-	\mathit{Recall} = 0, \mathit{false\ otherwise}\vspace{0.1cm}$
+	\mathit{Recall} = 0, \vspace{0.1cm}$
 
@@
 their decision on how to analyze build logs.
-To this end, we first
+To this end, we
 conducted a systematic mapping survey to map out the available build
 log analysis techniques.
-We saw that while build log analysis is widely used, it is often
+We saw that, while build log analysis is widely used, it is often
 a side part of an article and implementations are rarely reused.
@@
 build log analysis techniques that need little effort to set up.
-Based
-on common approaches we saw during the literature survey,
-we implemented three promising techniques to retrieve specific
-substrings (chunks) from build logs:
+
+Based on common approaches we observed in literature,
+we implemented three promising chunk retrieval techniques:
 PBE synthesizes regular expression programs based on examples of logs
@@
 measure to retrieve those lines which are most similar to example
-chunks, and KWS finds the targeted parts of a build log by searching
+chunks, and KWS finds the targeted chunks in a build log by searching
 for identifying keywords.
+
 We evaluated the performance of these chunk retrieval techniques on the
@@
 and recall (70\%, KWS).
-To guide researchers and developers on which technique to use for their
+
+To guide researchers and developers on which technique suits their
+use case,
 we summarized our results in a decision tree.
@@
 build logs is the main factor a user should consider when they
-choose a suitable
+choose a
 technique.
@@
 more important for the task at hand.
-% TODO Caro: bring more across why it is so important that this field
-% and the research there continues
+
 Finally, we gave an

### 2020-04-29 tse-paper/content.tex
Address a TODO

@@
 does not contain the structure that the training examples define,
-PBE returns the error message ``no match found''.
+PBE returns the error message ``no match found.''
 
@@
 
-% TODO Moritz: reference these in text properly
-
 \lstset{escapeinside=//}
@@
 an example of how the chunk retrieval techniques retrieve chunks from
-real-world build logs.
+real-world build logs in \Cref{lst:logexamples}. Marked in blue are the chunks
+which contain the information on why the
+corresponding build failed.
+
 \Cref{lst:chunk-example} shows two excerpts
 from Android build logs.
-Marked in blue are the chunks
-which contain the information on why the
-corresponding build failed.
-
 When we train PBE with these two examples, it produces

### 2020-04-30 tse-paper/content.tex
corrections to lit survey start

@@
 manual activity is tedious and prone to
-error~\cite{santolucito2018statically}.
+errors~\cite{santolucito2018statically}.
 As a single build log can be
@@
 machalica2019predictive},
-or investigate the role of automated static analysis tools (ASATs,
-\cite{beller2016analyzing}) in CI
+or investigate the role of automated static analysis tools (ASATs)
+in CI
 builds~\cite{zampetti2017open}.
@@
 
-In this section, we survey the emerging field of build log
-analysis.
-We start with a differentiation to the field of
+We performed a systematic mapping study on the emerging field of
+build log analysis,
+to determine how various researchers analyze build logs.
+We start this section by explaining how build log analysis differs
+from the more established field of
 system log analysis.
@@
 Then, we describe the methodology (\Cref{fig:lit-survey})
-and results of a systematic mapping
-study to
-determine the state-of-research on build log analysis following the
+and results of our systematic mapping
+survey following the
 guidelines by Petersen et
 al.~\cite{petersen2008systematic,petersen2015guidelines}.
-We close by summarizing how build logs are commonly
-analyzed in literature and discuss the implications of these findings.
+% We close by summarizing how build logs are commonly
+% analyzed in literature and discuss the implications of these findings.
 
@@
 \label{sec:system-log-analysis}
-A field related to build log analysis is the analysis of system
-logs which are produced during runtime of the system.
-The first difference is that build logs are produced during runtime
-of the build of the system, not during runtime of the system itself.
+A field related to build log analysis is the analysis of system logs.
+These system logs are produced during the runtime of a system, while
+build logs are produced during the runtime of the build of the system.
 In terms of the contents of the logs, the main difference is that system
@@
 
-The first goal in analyzing system log files is generally to
+When analyzing system log files, the first goal is generally to
 separate the constant and variable parts within a log
@@
 identical constant parts and varying parameters.
-Then, a log parser works on this intermediate representation.
-Its output is an ordered list of timed events and their corresponding
+The output is an ordered list of timed events and their corresponding
 parameter values~\cite{he2016evaluation}.
@@
 We refined the search criteria to exclude such obvious
-non-related fields and to exclude works on systems
-or event logs (see \Cref{sec:system-log-analysis}).
+non-related fields and to exclude works on system
+logs (see \Cref{sec:system-log-analysis}).
 This left us with 1,552 search results.
@@
 contextual information Google Scholar displayed on its search results
-overview page.
+page.
 We included works at large that seemed to bear a resemblance to software
@@
 hits.
-We then unified
-the results of the four search queries based on the link as the
-identifying element, removing 60 articles that appeared in more than
-one search query.
-We removed further duplicates based on the title and were
-left with 256 (16\%) of the original search results.
-% removed duplicates of data extraction pass already here
+% 'four' not clear and it gets lost that there are multiple search queries
+% therefore I'll cut this part completely
+% We then unified
+% the results of the four search queries based on the link as the
+% identifying element, removing 60 articles that appeared in more than
+% one search query.
+We removed duplicates based on the title and were
+left with 256 articles (16\% of the original search results).
 
@@
 
+% TODO Caro: check article vs.
+work occurrences, balance use
 Third, since we had been careful to include rather than exclude borderline
@@
 This excluded another 11 articles.
-In sum, we extracted data from 61 articles.
+In sum, we classified 61 articles in detail.
 
@@
 remaining ones in-depth.
-We wanted to characterize how research works with build logs.
+Our aim is to characterize how researchers work with build logs.
 
@@
   \item what information the researchers retrieve from build logs and
-  what this information is used for (\textbf{RQ1.1}),
-  \item which techniques they to process the build logs,
+  what they use this information for (\textbf{RQ1.1}),
+  \item which techniques they employ to process the build logs,
   in how much detail the techniques are described,
@@
   (\textbf{RQ1.2}),
-  \item what kind of build logs the researchers analyze
+  \item which kinds of build logs the researchers analyze
 	and the origin of these logs (\textbf{RQ1.3}).
@@
 
-To support the data extraction we created a template that we filled out
+To support the data extraction we created a template which we filled out
 for each of the 61 works.
@@
 for example ``Is the technique explained in detail?'' and
-``What is the source of the build logs?''
+``What is the source of the build logs?''.
 As recommended by Petersen et
@@
 
-\Cref{fig:litsur:use} shows the reason for the
-investigated articles to analyze build logs.
-The majority of articles (46\%) used the outcome of their build log
-analysis to drive further research.
-Seo et al.~\cite{seo2014programmers}, for example,
-categorized the types of compile errors encountered at
-Google.
-Other articles (10\%) used the gained insights to give feedback to
-developers.
-For 8\% of the articles was the retrieved information the input
-to a next automatic onward processing step:
-articles chose
-tests that should be part of a reduced but still effective test
-suite~\cite{shi2018evaluating} or filled a data structure with
-build information, an information source for further tools aiming
-to fix a failing build~\cite{vassallo2018un-break}.
-
 % TODO Moritz: add missing figure
+% C: this (to be 4b) is closer to 4a, therefore I moved it up
+% and the use/purpose down (to be 4c then)
 We also identified the type of information which the articles
@@
 
+\Cref{fig:litsur:use} shows the reason for the
+investigated articles to analyze build logs.
+The majority of articles (46\%) used the outcome of their build log
+analysis to drive further research.
+Seo et al.~\cite{seo2014programmers}, for example,
+categorized the types of compile errors encountered at
+Google.
+Other articles (10\%) used the gained insights to give feedback to
+developers.
+For 8\% of the articles the retrieved information was the input
+to a next automatic onward processing step:
+articles chose
+tests that should be part of a reduced but still effective test
+suite~\cite{shi2018evaluating} or filled a data structure with
+build information, an information source for further tools aiming
+to fix a failing build~\cite{vassallo2018un-break}.
+
 \subsubsection{Which analysis techniques exist? (RQ 1.2)}
@@
 build logs.
+% TODO Caro: check method vs.
+technique
 However, only 16 of these described their method in detail.
-\Cref{tab:litsur:techniques} presents the techniques that the articles
-described for analyzing build logs.
-
+We summarize the techniques that the articles
+described for analyzing build logs in \Cref{tab:litsur:techniques}.
+
+% TODO Caro: test \emph{parser}, regex, manually, etc...
 The most mentioned method (34\%) was using a parser, where we also
@@
 If we saw evidence for the latter, we assigned the tag
-``regular expression'' instead of the tag ``parser.''
+``Regular Expression'' instead of the tag ``Parser.''
 25\% of the articles described the use of regular expressions and 20\%
@@
 classifies the remaining logs.
-Another 8\% employed machine learning such as natural language
+Another 8\% of the investigated articles
+employed machine learning such as natural language
 processing or information retrieval techniques.
@@
 an example of how the chunk retrieval techniques retrieve chunks from
-real-world build logs in \Cref{lst:logexamples}. Marked in blue are the chunks
+real-world build logs in \Cref{lst:logexamples}.
+Marked in blue are the chunks
 which contain the information on why the

### 2020-04-30 tse-paper/content.tex
Make RQ1 fit one line

@@
 1}}
-What is the state-of-the-research on analyzing build logs?
+What is the state-of-research to analyze build logs?
 \end{simplebox}
@@
 \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
-{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
+{\textbf{RQ1:} What is the state-of-research to analyze build logs?}
 \begin{itemize}[leftmargin=1cm]

### 2020-04-30 tse-paper/content.tex
add todays review and todos for me

@@
 \label{sec:survey}
+% tense: past
 
@@
 \label{sec:system-log-analysis}
+% tense: present
+
 A field related to build log analysis is the analysis of system logs.
@@
 \subsection{Literature Selection}
+% tense: past
+
 The first step in a systematic literature survey is to
@@
 
-% TODO Caro: check article vs.
-work occurrences, balance use
+% TODO Caro: check article vs work occurrences, balance use
 Third, since we had been careful to include rather than exclude borderline
@@
 \subsection{Results}
+% tense: past
 \addtolength{\tabcolsep}{-5pt}
@@
 build logs.
-% TODO Caro: check method vs.
-technique
+% TODO Caro: check method vs technique
 However, only 16 of these described their method in detail.
@@
   analysis? (RQ 1.3)}
-\Cref{fig:litsur:log_producer} shows the distribution of supported
-build tools.
-Of the articles we surveyed, 30\% analyzed
+As the structure of build logs can change greatly depending on the
+build tools contributing to it~\cite{staahl2014modeling},
+we were interested in which (variety) build tools are
+investigate in literature.
+\Cref{fig:litsur:log_producer} shows the distribution of
+build tools whose logs were analyzed by the articles in our survey.
+Of the articles, 30\% analyzed
 Maven~\cite{maven2019website},
@@
 
-A large amount of the articles analyze build logs
+A large fraction of the articles analyze build logs
 from a small number of build tools.
-In most cases, this is because the format of build logs changes
-~\cite{staahl2014modeling} and
-therefore \textbf{``parsers must be specialized to each build and test
-framework''}~\cite{tomassi2019bugswarm}.
+In most cases, this is because the format of build logs
+% TODO Caro: check for tilde after space or newline
+changes and
+therefore ``parsers must be specialized to each build and test
+framework''~\cite{tomassi2019bugswarm}.
 Sometimes, aspects separate from the build log analysis motivate
@@
 focussed on Maven
-build logs because they also chose the PIT tool to calculate coverage
+build logs because they also chose the PIT tool~\cite{coles2016pit}
+to calculate coverage
 and mutation score~\cite{shi2018evaluating}.
 PIT is only available as a Maven plugin.
-
-Only 7\% of the proposed methods claimed to be language-agnostic, while
+Only 7\% of the proposed methods claimed to be
+build tool-agnostic, while
 several described they are covering multiple source build tools.
-The majority of articles (42\%) used logs from a source that no
-second article
-targeted.
+The majority of articles (42\%) analyzed logs produced by a build tool
+that no second article supported.
+
 In 38\% of cases, the articles collected build logs from Travis
@@
 extract it confidently.
+
 23 of the articles analyzed more than a thousand build logs, while one
@@
 \label{sec:lit-sur:discussion}
-
+% tense: present
+
+% TODO Caro: try emph instead of textbf
 % ----- descriptive / general -----
@@
 % ----- information RQ 1.1 -----
-In regards to the information which was targeted, \textbf{most build log
+In regards to the information that is targeted, \textbf{most build log
 analysis approaches aim to retrieve the reason a build failed} by
@@
 Articles
-which explicitly mention a manual analysis of the logs, mostly
+that explicitly mention a manual analysis of the logs, mostly
 restrict their work to few logs or take a ``representative sample to
@@
 We observed \textbf{very little reuse of build log analysis tools},
-even though
+even though articles reported that
 \textbf{developing automated analysis tools requires a lot of effort}.
@@
 In addition, we rarely saw articles justifying why they use a certain
-technique to analyze build logs as there is a general \emph{lack of
+technique to analyze build logs as there is a general \textbf{lack of
 guidance on when to use which technique}.
@@
 existence of a more generic solution.}
-In most cases, \textbf{researchers analyze build logs from open
-source projects}, obtained through Travis CI.
-In addition, we saw several articles that targeted the logs of only
-one specific software project.
+% In most cases, \textbf{researchers analyze build logs from open
+% source projects}, obtained through Travis CI.
+% In addition, we saw several articles that targeted the logs of only
+% one specific software project.
 
@@
 the plugin was deployed cannot be analyzed.
-In addition to that, when using such a plugin, one would have to know
+In addition to that, when using such a plugin, one has to decide
 beforehand which information should be reported from a build, whereas
-build log analysis enables us to analyze the wide range of information
+build log analysis enables us to leverage the wide range of information
 already baked into the build logs.
@@
 \label{sec:techniques}
-
-In summary, the outcome of the literature survey show the need for
+% tense: past? except for general definitions / statements
+
+In summary, the outcome of the literature survey shows the need for
 build log
 analysis techniques that are \emph{automated},
-\emph{agnostic of the build environment}
+\emph{build tool-agnostic}
 and can be \emph{configured with little effort}.
@@
 previously described by several articles:
-PBE mimics regular expressions, while simplifying
+\emph{Program Synthesis by Example (PBE)}
+mimics regular expressions, while simplifying
 their development.
-We chose text similarity (CTS) as a common information retrieval
-technique and implement the ad hoc approach of
-searching for specific strings or keywords within KWS\@.
-
-In this section, we define our notion of chunk
+From the field of information retrieval, we leverage a
+\emph{Common Text Similarity (CTS)} approach
+and implement the ad hoc approach of
+searching for specific strings as \emph{Keyword Search (KWS)}.
+
+In this section, we define our concept of chunk
 retrieval techniques and present each of the techniques
@@
 \label{sec:crt-characteristics}
-In this section, we formalize our use of chunk retrieval techniques.
-By this word, we refer to techniques that automatically
+Before introducing each of the techniques, we formalize
+we formalize our concept of chunk retrieval techniques.
+By this phrase, we refer to techniques that automatically
 retrieve pieces of information that appear literally in build
@@
 which substring was retrieved.
-Therefore, chunk retrieval techniques
+Therefore, they
 cover the great majority of the types of log analysis we saw within
@@
 \emph{Running a
-chunk retrieval technique} means executing a fully configured
-technique to consumes as input a build log in plain text format and to
-produce an array as output.
-The array consists of substrings of the
+chunk retrieval technique} means applying a fully configured
+technique to a build log in plain text format.
+The technique then outputs a list that consists of substrings of the
 build log text.
-\Cref{tab:techniques} summarizes and distinguishes the techniques
-we present along the
-characteristics described above.
+In \Cref{tab:techniques}, we summarize and distinguish the techniques
+we present along the characteristics described above.
 
 \subsection{Program Synthesis by Example (PBE)}
-The concept of \emph{Programming by Example} aims to capture the
-intent of the user through examples which they provide in an automatically
-generated program.
-Leveraging this approach, we implemented a chunk retrieval technique
+The concept of \emph{Programming by Example} aims to automatically
+generate a program, by capturing the
+intent of the user through examples that the user provides.
+Leveraging this approach, we designed a chunk retrieval technique
 for build logs.
@@
 text extraction DSL \emph{FlashExtract}~\cite{le2014flashextract:}.
-Both enable \emph{PROSE} to synthesize regular expression programs
-consistent~\cite{mitchell1982generalization} with a set of in-
-and output examples.
-The usage of example enables the user to configure a chunk
-retrieval without understanding the whole structure of
-the build log.
+% Both enable \emph{PROSE} to synthesize regular expression programs
+% consistent~\cite{mitchell1982generalization} with a set of in-
+% and output examples.
+% The usage of example enables the user to configure a chunk
+% retrieval without understanding the whole structure of
+% the build log.
 
@@
 The PROSE program synthesis then tries to construct a program
-consistent with all training examples.
+consistent with all training
+examples~\cite{mitchell1982generalization}.
 If PROSE cannot synthesize a program, e.g.,\
@@
 marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-We investigate a chunk retrieval technique that
+These approaches fall into the broader area of information retrieval
+techniques, which several of the articles from our literature survey
+used to analyze build logs.
+Similar to these approaches, we designed a chunk retrieval
+technique that
 retrieves those lines from a build log which are most
@@
 \subsubsection{Configuration}
-To configure chunk retrieval through text similarity we chose to use
+To configure CTS we chose to use
 the same concept of examples as for PBE.
-The lines of the output strings of the training examples define the
+The lines of the targeted chunks from the training examples define the
 search query.
-We represent each line as a term vector where each entry counts
+We represent each line as a term vector where every entry counts
 how often a word appears within the line.
-These vectors exist in a space ith as many dimensions as different
+These vectors exist in a space with as many dimensions as different
 words appear in the log text.
@@
 text lines as more similar if they contain the same words in the same
-frequencies, meaning their term vectors point in a similar direction
+frequencies, making their term vectors point in a similar direction
 in the vector space.
@@
 The algorithm calculates the cosine
-similarity~\cite{korenius2007principal} to compare each line of the
+similarity to compare each line of the
 build log with each line of the search query.
@@
 The average number of
-lines in the outputs of the training examples determines how many of
+lines in the chunks of the training examples determines how many of
 the most similar lines our approach returns as the output of the retrieval
@@
 set~\cite{brandt2020logchunks}.
+To investigate the performance of this approach, we
+designed a chunk retrieval technique based on keyword search.
 
@@
 The number of surrounding lines retrieved is
-the average of lines in the specification output of the training examples.
+the average number of lines in the chunks of the training examples.
 

### 2020-04-30 tse-paper/content.tex
method -> technique, address some more todos

@@
 research question:
-% TODO Discuss: is -research fine? or state-of-the-art more common and
-% still not missused (because industry m)
 \begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
@@
 Some of the techniques developed to parse system logs can operate
-on build logs as well, such as methods to retrieve the
+on build logs as well, such as approaches to retrieve the
 values of variable parts in a log message, e.g.\, by using regular
@@
 build logs.
-% TODO Caro: check method vs technique
-However, only 16 of these described their method in detail.
+However, only 16 of these described their technique in detail.
 We summarize the techniques that the articles
@@
 
-% TODO Caro: test \emph{parser}, regex, manually, etc...
-The most mentioned method (34\%) was using a parser, where we also
+The most mentioned technique (34\%) was using a parser, where we also
 included
-rather imprecise statements like ``we parse the build logs''
-~\cite{rahman2018impact}.
+rather imprecise statements like ``we parse the build
+logs''~\cite{rahman2018impact}.
 For such imprecise statements it was often not clear if they describe
@@
 In most cases, this is because the format of build logs
-% TODO Caro: check for tilde after space or newline
 changes and
@@
 PIT is only available as a Maven plugin.
-Only 7\% of the proposed methods claimed to be
+Only 7\% of the proposed techniques claimed to be
 build tool-agnostic, while
@@
 
-% TODO Caro: try emph instead of textbf
 % ----- descriptive / general -----
@@
 practitioners as well.
-We propose to investigate the methods used in industry to analyze
+We propose to investigate the techniques used in industry to analyze
 build logs.

### 2020-04-30 tse-paper/content.tex
Add new figure and text for lit survey

--- 2020-04-30 tse-paper/content.tex
@@
 				\includegraphics[width=\columnwidth,
+				clip]{img/lit-sur/kind.pdf}
+		\caption{Class of information analyzed.}
+		\label{fig:litsur:kind}
+
+\end{subfigure}
+\begin{subfigure}[t]{\columnwidth}
+		\centering
+				\includegraphics[width=\columnwidth,
 				clip]{img/lit-sur/use.pdf}
@@
 our survey usually retrieved from build logs.
-These results are depicted in \Cref{fig:litsur_r}.
+\Cref{fig:litsur_r} depicts these results.
 
@@
 
-% TODO Moritz: add missing figure
-% C: this (to be 4b) is closer to 4a, therefore I moved it up
-% and the use/purpose down (to be 4c then)
-We also identified the type of information which the articles
-retrieved from the build logs.
-In most cases (51\%), the researchers retrieved a chunk of text.
-They scanned build logs for compilation
-errors~\cite{clemencic2014new} or
-the duration of tasks within the build~\cite{zhang2016android}.
-36\% of the articles classified the build logs into categories.
-For instance, they distinguish failures caused by developers from
-failures caused
-by infrastructure errors~\cite{lindqvist2019detection} or
-determine whether projects use automated static analysis
+\Cref{fig:litsur:kind} depicts that there are two widely used ways to
+extract information from build logs: either chunks (53\%) or
+classifications (41\%).
+Uses for chunks were extracting compilation errors,
+test failures, or the duration of build
+tasks~\cite{clemencic2014new,zhang2016android}.
+Examples for
+classifications were distinguishing failures caused by developers from
+failures caused by infrastructure errors~\cite{lindqvist2019detection}
+or determining whether projects use automated static analysis
 tools~\cite{kavaler2019tool}.
-Other types of information (e.g.,\ counting
-lines, summarization) were only retrieved
-in one case each.
+Categorization is the more abstract representation, chunks
+contain more information and could be turned into a categorization.
 
 \Cref{fig:litsur:use} shows the reason for the
-investigated articles to analyze build logs.
+investigated articles to analyze build logs, and the result also explains
+the prevalence of classification.
 The majority of articles (46\%) used the outcome of their build log
-analysis to drive further research.
+analysis to drive further research---and it is science aims to try to
+classify and abstract.
 Seo et al.~\cite{seo2014programmers}, for example,

### 2020-04-30 tse-paper/content.tex
Add publication year figure

@@
 In this article, we present three techniques that analyze a build log
-by retrieving a substring (chunk) that describes a
-specific information:
+by retrieving a substring (chunk):
 \begin{itemize}
@@
 In this section, we give a general overview over our paper population.
-We then present the results of the analysis phase, along the
-RQs 1.1 through 1.3.
+We then present the results of the analysis phase along RQs 1.1 through 1.3.
 
@@
 To be done.
+
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/years.pdf}
+		\caption{Number of works analyzing build logs per year.}
+		\label{fig:failure-reason-PBE}
+\end{figure}
+
 % TODO moritz: age of papers (graph), kind of

### 2020-04-30 tse-paper/content.tex
Finish descriptive statistics

@@
 % the latter might be too cumbersome
+% Moritz: I have added a link to the disqus site of TT
+% (where this originates from and would leave it in the
+% current state)? Ok with you?
 logs from different build tools, and is prone to errors,
 as the experience of
-TravisTorrent has shown~\cite{beller2017travistorrent}.
+TravisTorrent has shown~\cite{beller2017travistorrent,travistorrentquestions}.
 In fact, some even ``strongly discourage'' the creation of such
@@
 \subsection{Literature Selection}
+\label{sec:litsel}
 % tense: past
@@
 In this section, we give a general overview over our paper population.
-We then present the results of the analysis phase along RQs 1.1 through 1.3.
+We then present the results of the analysis phase along RQs 1.1 through
+1.3.
 
 \subsubsection{Descriptive Study Statistics}
-To be done.
+After the third filtering phase, we finally included 61 works in the literature survey.
+The majority of these are scientific articles (81\%), of which all but three have been peer-reviewed and published (94\%).
+The remaining works are theses (14\%), two books, and one slide deck.
+
+\Cref{fig:failure-reason-PBE} depicts the year of appearance of these works.
+Although we applied no filtering by year in our initial search queries (see \Cref{sec:litsel}), the earliest work in our literature corpus stems only from 2001.
+There are various scattered works in the years between then and 2016, when the field of build log analysis started to grow rapidly.
 
@@
 \end{figure}
-
-% TODO moritz: age of papers (graph), kind of
-% publication (master, paper)
-% published (y, n)
 
@@
 % \texbf{Modifying the Build Process.}
+% Moritz: I think best to decided once we read the paper
+% top to bottom. For now, it seems ok
+
 An alternative to analyzing build logs, would be to integrate plugins
@@
 % or too much 'foreshadowing' too far down in the hierarchy
+% Would recommend to delete -- it simply follows later
 The results of the empirical comparison study on the chunk retrieval
@@
 show the influence of all training and test examples being from the
-same structural category compared to being multiple categories
+same structural category compared to being from multiple categories.
 For more
@@
 
-\begin{figure}[tb]
+\subsection{Recommendation of Suitable Techniques}
+
+\begin{figure}[bt]
 		\centering
@@
 		clip]{img/crt-recommendation.pdf}
-		\caption{Our decision tree for chunk
+		\caption{Decision tree for chunk
 		retrieval techniques.}
@@
 
-\subsection{Recommendation of Suitable Techniques}
 We saw that each of the techniques is suited for different types of

### 2020-05-01 tse-paper/content.tex
Improve number style
address my todos

@@
 and maintenance is manual and expensive, does not generalize across build
-% TODO Discuss/Moritz: should we say 'our' experience? or
-% 'one authors'?
-% the latter might be too cumbersome
-% Moritz: I have added a link to the disqus site of TT
-% (where this originates from and would leave it in the
-% current state)? Ok with you?
 logs from different build tools, and is prone to errors,
 as the experience of
-TravisTorrent has shown~\cite{beller2017travistorrent,travistorrentquestions}.
+TravisTorrent has
+shown~\cite{beller2017travistorrent,travistorrentquestions}.
 In fact, some even ``strongly discourage'' the creation of such
@@
 
-First, we filtered articles based on (a) their title and (b) the
+First, we filtered works based on (a) their title and (b) the
 contextual information Google Scholar displayed on its search results
@@
 % 'four' not clear and it gets lost that there are multiple search queries
-% therefore I'll cut this part completely
+% therefore I'll cut this part completely:
 % We then unified
 % the results of the four search queries based on the link as the
-% identifying element, removing 60 articles that appeared in more than
+% identifying element, removing 60 works that appeared in more than
 % one search query.
 We removed duplicates based on the title and were
-left with 256 articles (16\% of the original search results).
-
-With these 256 remaining articles, we followed a backward snowball
+left with 256 works (16\% of the original search results).
+
+With these 256 remaining works, we followed a backward snowball
 sampling for related work.
-If an article referenced a new work in the context
+If a work referenced a new work in the context
 of build log analysis, we added the new one to the literature set.
-This added five articles (eight before
+This added five works (eight before
 duplicate elimination), leading to a total of 261
@@
 
-% TODO Caro: check article vs work occurrences, balance use
 Third, since we had been careful to include rather than exclude borderline
-works, a deeper evaluation excluded another 15 articles from the 87
+works, a deeper evaluation excluded another 15 works from the 87
 works left after the second filter phase.
-Multiple articles were extensions of others.
-Of these, we only considered the earliest article which reported on
+Multiple works were extensions of others.
+Of these, we only considered the earliest work which reported on
 the analyzing of build logs.
-This excluded another 11 articles.
-In sum, we classified 61 articles in detail.
+This excluded another 11 works.
+In sum, we classified 61 works in detail.
 
 \subsection{Literature Classification}
-Having trimmed down the set of articles by 95\%, we investigated the
+Having trimmed down the set of works by 95\%, we investigated the
 remaining ones in-depth.
@@
 pilot:
-both authors extracted data from the same five articles and held a
+both authors extracted data from the same five works and held a
 consensus meeting to unify their understanding
 of the data extraction template.
-We divided the remaining 56 articles evenly between the two authors
-and inspected each article as closely as necessary to fill out the
+We divided the remaining 56 works evenly between the two authors
+and inspected each works as closely as necessary to fill out the
 template
 with confidence,
-starting from occurrences of ``log'' or ``build'' within the article's
+starting from occurrences of ``log'' or ``build'' within the works's
 text.
@@
 ``Travis'' and ``Travis CI'' together and assigned ``Industrial'' to
-all articles that used build logs provided by a company.
+all works that used build logs provided by a company.
 The replication package contains the data extraction template and all
@@
 \subsubsection{Descriptive Study Statistics}
-After the third filtering phase, we finally included 61 works in the literature survey.
-The majority of these are scientific articles (81\%), of which all but three have been peer-reviewed and published (94\%).
+After the third filtering phase, we finally included 61 works in the
+literature survey.
+The majority of these are scientific articles (81\%), of which all but
+three have been peer-reviewed and published (94\%).
 The remaining works are theses (14\%), two books, and one slide deck.
 
-\Cref{fig:failure-reason-PBE} depicts the year of appearance of these works.
-Although we applied no filtering by year in our initial search queries (see \Cref{sec:litsel}), the earliest work in our literature corpus stems only from 2001.
-There are various scattered works in the years between then and 2016, when the field of build log analysis started to grow rapidly.
+\Cref{fig:lit-years} depicts the year of appearance of these
+works.
+Although we applied no filtering by year in our initial search queries
+(see \Cref{sec:litsel}), the earliest work in our literature corpus
+stems only from 2001.
+There are various scattered works in the years between then and 2016,
+when the field of build log analysis started to grow rapidly.
 
@@
 		\caption{Number of works analyzing build logs per year.}
-		\label{fig:failure-reason-PBE}
+		\label{fig:lit-years}
 \end{figure}
@@
 
-\caption{Multi-label categorization of the 61 relevant articles.}
+\caption{Multi-label categorization of the 61 relevant works.}
 \label{fig:litsur_r}
@@
 
-In this section, we describe what sort of information the articles in
+In this section, we describe what sort of information the works in
 our survey usually retrieved from build logs.
@@
 the targeted information.
-The precise information targeted in the build logs varied from article
-to article, with a relatively long tail.
+The precise information targeted in the build logs varied from work
+to work, with a relatively long tail.
 Most prominent was the search for errors (39\%), followed by extracting
@@
 \Cref{fig:litsur:use} shows the reason for the
-investigated articles to analyze build logs, and the result also explains
+investigated works to analyze build logs, and the result also explains
 the prevalence of classification.
-The majority of articles (46\%) used the outcome of their build log
+The majority of works (46\%) used the outcome of their build log
 analysis to drive further research---and it is science aims to try to
@@
 Google.
-Other articles (10\%) used the gained insights to give feedback to
+Other works (10\%) used the gained insights to give feedback to
 developers.
-For 8\% of the articles the retrieved information was the input
+For 8\% of the works the retrieved information was the input
 to a next automatic onward processing step:
-articles chose
+works chose
 tests that should be part of a reduced but still effective test
@@
 
-Of the 61 articles we inspected, 43 mentioned how they analyzed
+Of the 61 works we inspected, 43 mentioned how they analyzed
 build logs.
 However, only 16 of these described their technique in detail.
-We summarize the techniques that the articles
+We summarize the techniques that the works
 described for analyzing build logs in \Cref{tab:litsur:techniques}.
@@
 ``Regular Expression'' instead of the tag ``Parser.''
-25\% of the articles described the use of regular expressions and 20\%
+25\% of the works described the use of regular expressions and 20\%
 inspected the logs manually.
@@
 classifies the remaining logs.
-Another 8\% of the investigated articles
+Another 8\% of the investigated works
 employed machine learning such as natural language
@@
 
-Only 25\% of the articles claimed their implementation is available.
+Only 25\% of the works claimed their implementation is available.
 Moreover, we
 saw some reuse of the few available build log analysis tools.
-Five articles employed the tools used to create
+Five works employed the tools used to create
 \emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
@@
 \Cref{fig:litsur:log_producer} shows the distribution of
-build tools whose logs were analyzed by the articles in our survey.
-Of the articles, 30\% analyzed
+build tools whose logs were analyzed by the works in our survey.
+Of the works, 30\% analyzed
 Maven~\cite{maven2019website},
@@
 
-A large fraction of the articles analyze build logs
+A large fraction of the works analyze build logs
 from a small number of build tools.
@@
 several described they are covering multiple source build tools.
-The majority of articles (42\%) analyzed logs produced by a build tool
-that no second article supported.
-
-In 38\% of cases, the articles collected build logs from Travis
+The majority of works (42\%) analyzed logs produced by a build tool
+that no second work investigated.
+
+In 38\% of cases, the works collected build logs from Travis
 CI~\cite{travisci2019webpage};
-18\% of the articles processed logs from TravisTorrent; and 8\% included
+18\% of the works analyzed logs from TravisTorrent; and 8\% included
 build logs from industrial projects.
-The number of logs analyzed varied greatly between the articles
+The number of logs analyzed varied greatly between the works
 and we were not always able to
@@
 
-23 of the articles analyzed more than a thousand build logs, while one
+23 of the works analyzed more than a thousand build logs, while one
 investigated up to 122 million logs.
-Of the surveyed articles, 31\% claim to have published their data to
+Of the surveyed works, 31\% claim to have published their data to
 enable further research.
@@
 Ghaleb et al.~\cite{ghaleb2019studying},
-and several other articles studied.
+and several other works studied.
 
@@
 2016), \textbf{build log analysis is an established technique}
-in the literature, with 61 articles making use of it.
+in the literature, with 61 works making use of it.
 
@@
 necessary as many studies target a large number of builds.
-Articles
+works
 that explicitly mention a manual analysis of the logs, mostly
@@
 We observed \textbf{very little reuse of build log analysis tools},
-even though articles reported that
+even though works reported that
 \textbf{developing automated analysis tools requires a lot of effort}.
@@
 build logs for information as it is ``too error prone,'' while other
-articles pointed to the effort of developing a custom tool.
+works pointed to the effort of developing a custom tool.
 Regular expressions are known to be tedious to
@@
 % not sure if we can state that (no data on this, more 'impression')
-In addition, we rarely saw articles justifying why they use a certain
+In addition, we rarely saw works justifying why they use a certain
 technique to analyze build logs as there is a general \textbf{lack of
@@
 % ----- kinds of build logs RQ1.3 -----
-Several articles noted the variety in log formats for different build
+Several works noted the variety in log formats for different build
 tools, which requires customizing build log techniques for
@@
 The majority of build tools was however only targeted by one
-article each (roughly, area B).
+work each (roughly, area B).
 From this we follow that the large tail of
@@
 % source projects}, obtained through Travis CI.
-% In addition, we saw several articles that targeted the logs of only
+% In addition, we saw several works that targeted the logs of only
 % one specific software project.
@@
 % Moritz: I think best to decided once we read the paper
-% top to bottom. For now, it seems ok
+% top to bottom.
+%For now, it seems ok
 
@@
 techniques based on approaches
-previously described by several articles:
+previously described by several works:
 \emph{Program Synthesis by Example (PBE)}
@@
 These approaches fall into the broader area of information retrieval
-techniques, which several of the articles from our literature survey
+techniques, which several of the works from our literature survey
 used to analyze build logs.
@@
 \emph{different structural category}.
-% TODO Moritz: is this fitting here?
-% or too much 'foreshadowing' too far down in the hierarchy
-% Would recommend to delete -- it simply follows later
-The results of the empirical comparison study on the chunk retrieval
-techniques
-show that the structural representation of the targeted chunk greatly
-influences
-the performance of the chunk retrieval techniques.
 
@@
 
-In the literature survey we saw that few articles justify why they
+In the literature survey we saw that few works justify why they
 use a certain build log analysis technique and concluded that there
@@
 the chunk that describes why the build
-failed---the information targeted by most of the articles in our
+failed---the information targeted by most of the works in our
 literature survey.
@@
 We saw that, while build log analysis is widely used, it is often
-a side part of an article and implementations are rarely reused.
+a side part of an work and implementations are rarely reused.
 This shows the need for a new generation of generic and automated

### 2020-05-01 tse-paper/content.tex
corrections to second half

@@
 \Cref{fig:litsur:use} shows the reason for the
+% TODO: isn't this discussion already?
 investigated works to analyze build logs, and the result also explains
@@
 It also supplies the necessary information for the technique to
-identify the targeted information chunk in a build log.
+identify the targeted chunk in a build log.
 Each chunk
@@
 an example of how the chunk retrieval techniques retrieve chunks from
-real-world build logs in \Cref{lst:logexamples}.
+the real-world build logs in \Cref{lst:logexamples}.
 Marked in blue are the chunks
@@
 
+% TODO: decide if keep or redo
+% if keep, Caro do noted improvements
 \begin{figure*}[tb]
@@
 \emph{LogChunks} data set~\cite{brandt2020logchunks}.
-From Travis CI---the most-used source of build logs within
+From Travis CI---the most-used source of build logs
 according to our literature survey---we collected
 797 build logs that
-stem from a broad range of 80 GitHub repositories and 29
+stem from a broad range of 80 GitHub projects and 29
 programming languages.
@@
 We apply each of the chunk retrieval techniques
-on all of the 80 repositories represented in
+on all of the 80 projects in
 \emph{LogChunks} \circlenum{1}.
-For each repository, we select training sets of size 1, 2, \dots 5
+For each project, we select training sets of size 1, 2, \dots 5
 \circlenum{2}.
@@
   We prefer F$_{1}$ to other aggregate
-	measures such as accuracy because for a
+	measures such as accuracy because of the
 	``needle-in-the-haystack'' scenario, we want to avoid bloating
@@
 technique separately.
-Afterwards, we compare the three techniques with each other and to a
+Afterwards, we compare the three techniques with each other and with a
 random baseline.
@@
   \vspace{-\baselineskip}
-  \begin{lstlisting}[backgroundcolor=\color{Yellow!60},breaklines=true,frame=rl]
-Error: Invalid CSS after "2.3em": expected expression (e.g.
-1px, bold), was ";"
-	on line 86 of sass/components/dropdown.
-  \end{lstlisting}
+  \lstinputlisting[backgroundcolor=\color{Yellow!60},breaklines=true,frame=rl]
+	{listings/chunk3.txt}
   \vspace{-\baselineskip}
@@
   \vspace{-\baselineskip}
+  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
+	{listings/chunk3.txt}
+  \vspace{-\baselineskip}
   \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
-Error: Invalid CSS after "2.3em": expected expression (e.g.
-1px, bold), was ";"
-	on line 86 of sass/components/dropdown.sass
 	from line 5 of sass/components/_all.sass
@@
 retrieval with PBE.
-It shows how many of the retrieval runs were successful or
-partially successful, as well as the number of runs where the
+It shows how many of the retrieval runs were successful,
+partially successful, or unsuccessful,
+as well as the number of runs where the
 synthesized program did not match on the analyzed build log or where
@@
 % synthesis, therefore only apply to PBE.
-Out of the overall 400 runs, 5 per each one of the 80 example
-sets, PBE extracted all desired lines successfully in 138 cases.
+Out of the 400 runs, 5 per each one of the 80 projects,
+PBE extracted all desired lines successfully in 138 cases.
 In 18 cases, the synthesized program only extracted a
@@
 the desired lines.
-For these 18 partially successful, the average recall
+For the 18 partially successful runs, the average recall
 was 47\%.
-\Cref{lst:pbe-partially-successful} shows how an example of such
-a partially successful retrieval looks like.
+\Cref{lst:pbe-partially-successful} shows an example of such
+a partially successful retrieval.
 In it, the synthesized program only
@@
 In 59 cases, PBE could synthesize a regular expression program, though
-it did not match on the test build log.
+the program did not match on the test build log.
 In 173 of the 400 cases
@@
 \Cref{fig:recall-precision-examplecount-sythesisworked-PBE}
-presents violin plots of the precision, the recall
+presents violin plots and averages of the precision, the recall
 and the F$_{1}$-score
 of these runs compared with the number of examples in the training set.
-The black horizontal lines show the average of these measurements.
 When the training set
@@
 If the figure shows no violin plot for a measurement, we only have one
-data point or all data points have the same value.
+data point available or all values are the same.
 
@@
 increasing the size of the training set to more than one example,
-while the precision stays constant at around 16\%.
+while the precision stays constant around 16\%.
 The F$_{1}$-score
@@
 test sets, the precision of RLR decreases from 7\% to 0\%, while
-the recall varies between 0\% end 11\%.
+the recall varies between 0\% and 11\%.
 
@@
 
-\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
-show the influence of all training and test examples being from the
-same structural category compared to being from multiple categories.
+\Cref{fig:category-all}
+shows the influence of all training and test examples being from the
+same structural category
+(\Cref{fig:recall-precision-singlecategory-all})
+compared to being from multiple categories
+(\Cref{fig:recall-precision-multicategory-all}).
 For more
-than one category being present, the recall of PBE decreases greatly.
+than one category present, the recall of PBE decreases greatly.
 For CTS and KWS the values also decrease, while RLR is not affected by
@@
 techniques compared, split by structural category count.}
+\label{fig:category-all}
 \end{figure*}
@@
 Now, we unify these results into conditions to answer
-our second research questions;
+our second research question;
 If researchers or developers want to retrieve chunks from build logs,
@@
 recommended technique.
-At the end of this section we give two concrete examples on how to
+In the next section we give two concrete examples on how to
 apply our decision tree.
@@
 a chunk retrieval technique are the structural categories.
-In other words,
+In other words:
 are the targeted log chunks always presented in
-the same structural way within the build logs? Then the information
+the same structural way within the build logs?
+Then the
 chunks in all training examples and the analyzed build log are in the
@@
 
-If the information chunks are from multiple structural categories
+If the chunks are from multiple structural categories
 and recall is more important than precision we recommend
@@
 On the leftmost path of the decision tree,
-when the representations are from one structural category and the user
+when the chunks are from one structural category and the user
 wishes high confidence in the correctness of the output or prefers
@@
 
-In the second example, a researcher wants to investigate whether a small
-or large group of test cases
-causes build failures.
+In the second example, a researcher wants to investigate whether
+small or large groups of test cases
+cause CI build failures.
 They gather
@@
 and KWS, they choose recall over precision to avoid having to inspect
-the whole log in case the relevant information chunk was not
-retrieved.
+the whole log in case the relevant chunk---the name of the failing
+test case---was not retrieved.
 Therefore, following the rightmost path in
@@
 size as a user has to provide the training examples
-per repository or project and one of the central aims of the chunk
+per project and one of the central aims of the chunk
 retrieval techniques is that they can be set up wit little effort.
@@
 
-\textbf{Cross-Repository Build Log Analysis.}
+\textbf{Cross-Project Build Log Analysis.}
 We trained and
 tested each chunk retrieval technique on examples from the same
-repository.
+project.
 We propose to analyze how techniques could be trained
-across repositories, building the cornerstones for build
+across projects, building the cornerstones for build
 environment-agnostic analysis tools.
@@
 We saw that, while build log analysis is widely used, it is often
-a side part of an work and implementations are rarely reused.
+a side part of a work and implementations are rarely reused.
 This shows the need for a new generation of generic and automated
@@
 refinement of the chunk retrieval techniques we proposed.
+We strongly believe that further research into the techniques to
+analyze build logs will support researchers and developers alike to
+leverage the vast amounts of valuable information
+hidden within build logs.

### 2020-05-01 tse-paper/content.tex
Smaller consistency fixes.

@@
 	clip]{img/overview.pdf}
-	\caption{Research Design.}
+	\caption{Research design.}
 	\label{fig:overview}
@@
 	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Literature selection process, following
-	\cite{petersen2015guidelines}.}
+	\caption{Literature selection (following Petersen et al.~\cite{petersen2015guidelines}).}
 	\label{fig:lit-survey}
@@
 
-\begin{figure}[tbhp]
+\begin{figure}[tbp]
 		\centering
@@
 		clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{Results of chunk retrieval with PBE.}
+		\caption{High-level results of chunk retrieval with Program Synthesis by Example (PBE).}
 		\label{fig:failure-reason-PBE}
@@
   \end{lstlisting}
-	\caption{Yellow: chunk retrieval output ($RetrievedLines$)}
+	\caption{Actual chunk retrieval output ($RetrievedLines$ in yellow).}
 	\label{lst:pbe-part-success-output}
@@
   \end{lstlisting}
-	\caption{Blue: targeted chunk ($DesiredLines$)}
+	\caption{Targeted chunk ($DesiredLines$ in blue).}
 	\label{lst:pbe-part-success-desired}
@@
 		clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals for all techniques.}
+		\caption{Success of chunk retrievals across all techniques.}
 		\label{fig:success-partial-all}
@@
 
-% capitalized headings / left title column
-% tried it out, I think it looks better with the rest lowercase
 \begin{table}[tbp]
+\caption{Recommendations for each of the investigated chunk retrieval
+techniques.}
+\label{tab:single-technique-recommendations}
+
 \resizebox{\columnwidth}{!}{%
@@
 }
-\caption{Recommendations for each of the investigated chunk retrieval
-techniques.}
-\label{tab:single-technique-recommendations}
 \end{table}

### 2020-05-01 tse-paper/content.tex
More small fixes.

@@
 \Cref{fig:overview}---with an
-extensive literature survey (step 1).
+extensive literature survey (step \circlenum{1}).
 The survey identifies various strategies to
@@
 implementations to
-automatically analyze build logs (step 2).
+automatically analyze build logs (step \circlenum{2}).
 The ideas behind the implementations are based on promising approaches
@@
 of these chunk retrieval techniques in
-real-world projects under a variety of conditions (step 3).
+real-world projects under a variety of conditions (step \circlenum{3}).
 The study is based on the \emph{LogChunks} data
@@
 on how to choose the most suitable build log analysis
-technique for the task at hand (step 4).
+technique for the task at hand (step \circlenum{4}).
 We recommend PBE for use cases where the desired information is always
@@
 	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
-	\caption{Literature selection (following Petersen et al.~\cite{petersen2015guidelines}).}
+	\caption{Literature selection (following Petersen et
+	al.~\cite{petersen2015guidelines}).}
 	\label{fig:lit-survey}
@@
   \lstinputlisting[breaklines=true]{listings/syslog.txt}
-  \caption{System Log excerpt.
-Example adapted from~\cite{he2017towards}.}
+  \caption{System log excerpt (adapted from He et al.~\cite{he2017towards}).}
   \label{lst:system-log}
@@
 		clip]{img/big-study/failure-reason-pbe.pdf}
-		\caption{High-level results of chunk retrieval with Program Synthesis by Example (PBE).}
+		\caption{High-level results of chunk retrieval with
+		Program Synthesis by Example (PBE).}
 		\label{fig:failure-reason-PBE}
@@
   \end{lstlisting}
-	\caption{Actual chunk retrieval output ($RetrievedLines$ in yellow).}
+	\caption{Actual chunk retrieval output ($RetrievedLines$
+	in yellow).}
 	\label{lst:pbe-part-success-output}
@@
 		clip]{img/big-study/success-partial-all.pdf}
-		\caption{Success of chunk retrievals across all techniques.}
+		\caption{Success of chunk retrievals across all
+		techniques.}
 		\label{fig:success-partial-all}

### 2020-05-01 tse-paper/content.tex
Extensive review until Section 3

@@
 compiling---but also about ancillary quality assurance steps---such as
-testing the software and running automated static analysis tools.
+testing the software and running automated static analysis tools~\cite{beller2017oops}.
 The
@@
 over 50 megabytes large~\cite{beller2017oops}, finding the small chunk
-of information which is linked to the actual error, is akin to
+of information linked to the actual error, is akin to
 searching for a needle in a haystack.
-The large numbers of unrelated, but ambiguous
-warnings, which many build
-logs regularly contain, further compound this problem.
+The large number of unrelated, but ambiguous
+warnings which many build
+logs regularly contain further compounds this problem.
 In addition to helping
@@
 
+% TODO Caro: I moved it to the intro
+% --- please check how it works for you
+Retrospectively analyzing the build logs is not the only solution to the problem---an alternate would be to integrate live plugins into the build process
+ such as the JUnit
+plugin for Jenkins~\cite{jenkins2020junit-plugin} or
+Deflaker by Bell et al.~\cite{bell2018deflaker}. 
+Their advantage is that they can precisely report the information which
+is required.
+However, such plugins are not available for all build tools, they are non-trivial to implement one-off solutions, and they
+do not enable the analysis of historical builds. When using such a plugin, one has to decide
+beforehand which information should be reported, whereas
+build log analysis enables us to leverage all information
+present in the build logs. Moreover, build log analyis is the more general soltuion. While they serve an important niche, custom plugins do not make build log analysis redundant.
+
 Despite its central role in helping developers and in enabling
@@
 the process of how to
+% TODO
 %automatically
 % ^ we survey manual as well, though leaving it out includes too much
-systematically
+% systematically twice -- avoid this
 analyze build logs has thus far not been systematically
@@
 
-To answer this question, we start our investigation---pictured in
+To answer this question, we start the investigation in this paper---pictured in
 \Cref{fig:overview}---with an
@@
 searching for keywords, or performing natural language processing.
-However, there is currently no guidance on when to use which of these
+
+However, it also identifies that there is currently no guidance on when to use which of these
 approaches.
@@
 
-%Using 1) a set of
-% manually curated regular expressions,
-% similar to TravisTorrent~\cite{beller2017oops},
-% 2) information
-% retrieval techniques,
-% % Can you shortly explain the technique here?
-% and 3) a list of search keywords
-% to identify regions of interest in the build log.
-
-%% \begin{itemize}
-%%   \item \textbf{(referred to as PBE)}
-%%   Based on manually supplied example pairs of build logs and chunks,
-%%   PBE automatically synthesizes
-%%   a regular expression extracting the given chunks within the build
-%% logs.
-%%   % these second sentences about what the techniques stand for could
-%%   % also be merged to a paragraph after the itemize
-%%   PBE mimics regular expressions and parsers while
-%%   simplifying their development.
-%%   \item \textbf{Common Text Similarity (CTS)}
-%%   Text similarity is a common information retrieval technique.
-%%   CTS selects lines of a log which are
-%%   most similar to the lines present in manually supplied example
-%% chunks.
-%%   As a common information retrieval technique, our text similarity
-%%   approach stands for the machine learning approaches identified in
-%%   the literature survey.
-%%   \item \textbf{Keyword Search (KWS)}
-%%   KWS finds fitting passages by searching the whole
-%%   text of a build log for
-%%   the occurrence of specific trigger words.
-%%   Keyword Search was explicitly mentioned by several articles in the
-%%   literature survey.
-%% \end{itemize}
-
-% turned into an itemize again cause the 'sentence' around it was
-% rather broken and item-ish anyways
-To fill this gap, we adapted and implemented three novel, prototypical
+To fill this gap, we created three novel, prototypical
 implementations to
@@
 adopted from other research fields and existing build log analysis
-techniques.
-In this article, we present three techniques that analyze a build log
-by retrieving a substring (chunk):
+techniques by retrieving a substring (chunk) from the build log:
 \begin{itemize}
@@
 	\item a technique based on information
-	retrieval, using \emph{Common Text Similarity (CTS)}
+	retrieval, using \emph{Common Text Similarity (CTS)},
 	\item inspired by the manual ad hoc search for key parts in the
 	log, a
-	technique employing \emph{Keyword Search (KWS)}
+	technique employing \emph{Keyword Search (KWS)}.
 \end{itemize}
-% a technique 1) able to automatically synthesize regular expressions,
-% called \emph{Program Synthesis by Example (PBE)}, a technique
-% 2) based on information
-% retrieval, using \emph{Common Text Similarity (CTS)}	and 3)
-% inspired by the manual ad hoc search for key parts in the log, a
-% technique employing \emph{Keyword Search (KWS)}.
-These three approaches---synthesized regular expressions,
-text similarity, and
-keyword search---have
+
+These three approaches have
 different strengths and weaknesses.
@@
 build tools and programming languages.
-Our results show that there is no technique that in general outperforms
+Our results show that all of the three techniques
+clearly surpass a random baseline, but have different strengths and weaknesses. There is no technique that in general outperforms
 the others.
-PBE has the best average precision of 95\%, while KWS has the largest
+PBE has the best average precision of 95\%, while KWS has the highest
 recall with 70\% on average.
 However, CTS shows the best F$_{1}$-score
-of 51\% and all of the three techniques
-clearly surpass a random baseline.
+of 51\%.
 
@@
 field.
-% (resolved) only point with no adjective
 \item a documented replication package~\cite{brandt2020chunk-replication}.
@@
 
-We performed a systematic mapping study on the emerging field of
-build log analysis,
-to determine how various researchers analyze build logs.
-We start this section by explaining how build log analysis differs
-from the more established field of
+In this section, we report on the state-of-research in the emerging field of build log analysis by means of a systematic mapping study.
+We start with a differentiation of build log analysis 
+from the older field of
 system log analysis.
@@
   \lstinputlisting[breaklines=true]{listings/syslog.txt}
-  \caption{System log excerpt (adapted from He et al.~\cite{he2017towards}).}
+  \caption{System log excerpt (adapted from He et
+  al.~\cite{he2017towards}).}
   \label{lst:system-log}
@@
 separate the constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}.
-Next, the log
+message~\cite{nagappan2010abstracting,he2017towards}.  Next, the log
 messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters.
-The output is an ordered list of timed events and their corresponding
-parameter values~\cite{he2016evaluation}.
-This structured log can serve as input to various machine learning and
-data mining processes.
+identical constant parts and varying parameters.  The output is an
+ordered list of timed events and their corresponding parameter
+values~\cite{he2016evaluation}.  This structured log can serve as
+input to various machine learning and data mining processes. Apart
+from a large body of research on system logs, an equally mature amount of commercial-grade and
+opensource tooling exists to analyze system logs---such as, for example, Elasticsearch, Logstash and Kiabana (the so-called ELK stack)~\cite{sanjappa2017analysis,bajer2017building}.
 
@@
 % amar et al are not in our literature survey
-However, almost all of the techniques developed to analyze system logs
-leverage their inherent event structure.
-Build logs generally lack this structure and thus require different
-bespoke approaches.
+However, the number of
+system logs generated mandates that scalability and efficiency play a
+much more important role than for build logs.
+In addition, almost all of the techniques developed to analyze system logs
+leverage their inherent event structure.   Build logs generally lack this
+structure and thus require different bespoke approaches.
 % if included: this explanation is not understandable.
@@
 process.
-An initial Google Scholar search for variations of ``build log''
+An initial Google Scholar search for ``build log''
 returned more than 2.2 million results on the 15th of March 2020, many
@@
 
-Second, we performed a finer filter phase by (1) reading their abstracts,
+Second, we performed a finer filter phase by (1) reading abstracts,
 and (2) downloading the
-full text of the works and searching the
-full text
-for the occurrence of ``log.''
+full text of the works and searching it
+for the occurrence of the term ``log.''
 If a work showed traces of
-working with build logs, we included it for the next filter phase.
+working with build logs, we passed it onto the final filter phase.
 In total, we
-were left with 87 works after the second filtering phases.
+were left with 87 works after the second filtering phase.
 
@@
 This excluded another 11 works.
-In sum, we classified 61 works in detail.
+In sum, we included and classified 61 works in detail.
 
@@
 remaining ones in-depth.
-Our aim is to characterize how researchers work with build logs.
+Our aim was to characterize how researchers work with build logs.
 
@@
 We divided the remaining 56 works evenly between the two authors
-and inspected each works as closely as necessary to fill out the
+and inspected each work as closely as necessary to fill out the
 template
 with confidence,
-starting from occurrences of ``log'' or ``build'' within the works's
-text.
+starting from occurrences of ``log'' or ``build'' within the full
+text of the work.
 
@@
 An example of this is the question ``What is the source of the build
-log?'',
+log?,''
 where we assigned tags such as ``Travis CI,''
 ``Industrial,'' ``Google,'' or
-``self-built.''
+``Self-built.''
 Once we had classified all works, we went into the second phase of
@@
 ``Travis'' and ``Travis CI'' together and assigned ``Industrial'' to
-all works that used build logs provided by a company.
+all works that used build logs from a company.
 The replication package contains the data extraction template and all
@@
 
-In this section, we give a general overview over our paper population.
+In this section, we first give a general overview over our paper population.
 We then present the results of the analysis phase along RQs 1.1 through
@@
 In this section, we describe what sort of information the works in
-our survey usually retrieved from build logs.
+our survey usually retrieve from build logs.
 \Cref{fig:litsur_r} depicts these results.
@@
 
-\Cref{fig:litsur:use} shows the reason for the
+\Cref{fig:litsur:use} shows the aim for the
 % TODO: isn't this discussion already?
+% Moritz: Not sure what is meant by that?
 investigated works to analyze build logs, and the result also explains
-the prevalence of classification.
+the prevalence of classification in \Cref{fig:litsur:kind}.
 The majority of works (46\%) used the outcome of their build log
-analysis to drive further research---and it is science aims to try to
+analysis to drive further research---and it is science's aim to
 classify and abstract.
@@
 developers.
-For 8\% of the works the retrieved information was the input
+For 8\% of the works was the retrieved information the input
 to a next automatic onward processing step:
 works chose
-tests that should be part of a reduced but still effective test
+tests that should be part of a reduced, but still effective test
 suite~\cite{shi2018evaluating} or filled     a data structure with
@@
 
-The most mentioned technique (34\%) was using a parser, where we also
+The most mentioned technique (34\%) was using a parser. In this tag, we also
 included
@@
 logs''~\cite{rahman2018impact}.
-For such imprecise statements it was often not clear if they describe
-a complex parser (including a tokenizer, lexer, etc.) or refer to a
+For such imprecise statements it was often not clear if they described
+a complex parser (including a tokenizer, lexer, etc.) or refered to a
 simpler parsing tool based on regular expressions.
@@
 saw some reuse of the few available build log analysis tools.
+% TODO The numbers here might look a bit strange
+% --- we say five but really it is six works we reference.
+% I assume this is because of only including the oldest ref?
+% Still, I think we need to fix the inconsistency.
 Five works employed the tools used to create
@@
   analysis? (RQ 1.3)}
-As the structure of build logs can change greatly depending on the
-build tools contributing to it~\cite{staahl2014modeling},
-we were interested in which (variety) build tools are
-investigate in literature.
+As the structure of build logs can change greatly depending on which
+build tools output to it~\cite{staahl2014modeling},
+we were interested in which build tools are
+investigated in the literature.
 \Cref{fig:litsur:log_producer} shows the distribution of
@@
 build tool-agnostic, while
-several described they are covering multiple source build tools.
+several described that they cover multiple build tools.
 The majority of works (42\%) analyzed logs produced by a build tool
@@
 extract it confidently.
-
 23 of the works analyzed more than a thousand build logs, while one
@@
 Ghaleb et al.~\cite{ghaleb2019studying},
-and several other works studied.
+% TODO  include the several others as references?
+and several others have studied.
 
@@
 (first mentioned in a paper in 2001, vast majority after
-2016), \textbf{build log analysis is an established technique}
-in the literature, with 61 works making use of it.
-
+2016), \textbf{build log analysis is already an established technique,} with 61 works in different venues making use of it for a variety of purposes.
 We saw that various researchers analyze build logs, often because the
@@
 analysis approaches aim to retrieve the reason a build failed} by
-targeting ``errors'' or ``failing tests''.
+targeting ``errors'' or ``failing tests.''
 % which is what we also do in LogChunks
 \textbf{The majority of approaches retrieves specific chunks of
-text from the logs.}
+text from the logs.} Chunks in some sense are the overarching concept to the almost equally used categorization, as a categorization can usually be deducted from chunks, but not vice versa.
 
@@
 \textbf{Most log analysis is automated.} Automated approaches are
-necessary as many studies target a large number of builds.
-works
-that explicitly mention a manual analysis of the logs, mostly
-restrict their work to few logs or take a ``representative sample to
+necessary because many studies target a large number of builds.
+Works
+that explicitly mention manual analysis of the logs, mostly
+restrict themselves to few logs or take a ``representative sample to
 make manual analysis feasible''~\cite{zolfagharinia2017not}.
@@
 works pointed to the effort of developing a custom tool.
-Regular expressions are known to be tedious to
+We know from other research lines that regular expressions, the second most popular way to analyze log files (\Cref{tab:litsur:techniques}), are tedious to
 maintain~\cite{michael2019regexes}.
-% not sure if we can state that (no data on this, more 'impression')
 In addition, we rarely saw works justifying why they use a certain
 technique to analyze build logs as there is a general \textbf{lack of
-guidance on when to use which technique}.
+guidance on when to use which technique.}
 
@@
 every supported build tool.
-% The following two sentences are passive, however flipped around
-% have a different meaning (we want build tool -> study count)
-\Cref{fig:litsur:log_producer} shows that only a few distinct
-build tools are the target of
-many studies and tools (roughly, area A).
-The majority of build tools was however only targeted by one
-work each (roughly, area B).
-From this we follow that the large tail of
+\Cref{fig:litsur:log_producer} shows that there are only a handful of build tools whose build logs more than one study analyzed, mainly in the Java ecosystem (area \circlenum{A}).
+Many works target a unique build tool that did not appear in any other study (area \circlenum{B}).
 \textbf{seldomly-investigated
@@
 %For now, it seems ok
-
-An alternative to analyzing build logs, would be to integrate plugins
-that report precise data about the build process, such as the JUnit
-plugin for Jenkins~\cite{jenkins2020junit-plugin} or
-Deflaker by Bell et al.~\cite{bell2018deflaker}.
-However, such plugins are not available for all build tools and they
-do not enable the analysis of historical data---builds that ran before
-the plugin was deployed cannot be analyzed.
-In addition to that, when using such a plugin, one has to decide
-beforehand which information should be reported from a build, whereas
-build log analysis enables us to leverage the wide range of information
-already baked into the build logs.
-Their advantage is that they can precisely report the information which
-is required.
+% Needs to go Threats or intro
 

### 2020-05-01 tse-paper/paper.tex
Finish descriptive statistics
Improve number style
Extensive review until Section 3

@@
 \newcommand{\smallish}{\fontsize{6.15pt}{20pt}\selectfont}
-\newcommand{\tinyish}{\fontsize{6.5pt}{6.15pt}\selectfont}
-\newcommand{\circlenum}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
+\newcommand{\tinyish}{\fontsize{6.4pt}{6.15pt}\selectfont}
+\newcommand\circlenum[1]{\raisebox{1.2pt}{\textcircled{\hspace{0.35pt}\scriptsize{\raisebox{-.4pt}{#1}}}}}
+%\newcommand{\circlenum}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
 
@@
 this time-consuming activity, to not only ease
-developers' task of finding this needle but also to enable a novel class of
-automated on-ward processing applications.
+developers' debugging task but also to enable a novel class of
+automated onward processing applications.
 In this paper, we give a systematic overview of the emerging field of build log analysis.
-In a large-scale literature mapping survey, we first survey and categorize the existing methods to
+In a broad literature mapping survey, we first survey and categorize the existing methods to
 extract information chunks from build logs.
-In the second part of the paper, we develop prototypical implementations of the three most promising
-techniques we found, namely program synthesis
+In the second part of the paper, we then develop prototypical implementations of three promising
+techniques to analyze build logsx, namely program synthesis
 by example, textual similarity, and keyword search.

### 2020-05-01 tse-paper/content.tex
More random fixes.

@@
 compiling---but also about ancillary quality assurance steps---such as
-testing the software and running automated static analysis tools~\cite{beller2017oops}.
+testing the software and running automated static analysis
+tools~\cite{beller2017oops}.
 The
@@
 % --- please check how it works for you
-Retrospectively analyzing the build logs is not the only solution to the problem---an alternate would be to integrate live plugins into the build process
+Retrospectively analyzing the build logs is not the only solution to
+the problem---an alternate would be to integrate live plugins into the
+build process
  such as the JUnit
@@
 Deflaker by Bell et al.~\cite{bell2018deflaker}.
+
 Their advantage is that they can precisely report the information which
 is required.
-However, such plugins are not available for all build tools, they are non-trivial to implement one-off solutions, and they
-do not enable the analysis of historical builds. When using such a plugin, one has to decide
+However, such plugins are not available for all build tools, they are
+non-trivial to implement one-off solutions, and they
+do not enable the analysis of historical builds.
+When using such a plugin, one has to decide
 beforehand which information should be reported, whereas
 build log analysis enables us to leverage all information
-present in the build logs. Moreover, build log analyis is the more general soltuion. While they serve an important niche, custom plugins do not make build log analysis redundant.
+present in the build logs.
+Moreover, build log analyis is the more general soltuion.
+While they serve an important niche, custom plugins do not make build
+log analysis redundant.
 
@@
 
-To answer this question, we start the investigation in this paper---pictured in
+To answer this question, we start the investigation in this
+paper---pictured in
 \Cref{fig:overview}---with an
@@
 
-However, it also identifies that there is currently no guidance on when to use which of these
+However, it also identifies that there is currently no guidance on when
+to use which of these
 approaches.
@@
 Our results show that all of the three techniques
-clearly surpass a random baseline, but have different strengths and weaknesses. There is no technique that in general outperforms
+clearly surpass a random baseline, but have different strengths and
+weaknesses.
+There is no technique that in general outperforms
 the others.
@@
 
-In this section, we report on the state-of-research in the emerging field of build log analysis by means of a systematic mapping study.
+In this section, we report on the state-of-research in the emerging
+field of build log analysis by means of a systematic mapping study.
 We start with a differentiation of build log analysis
@@
 separate the constant and variable parts within a log
-message~\cite{nagappan2010abstracting,he2017towards}.  Next, the log
+message~\cite{nagappan2010abstracting,he2017towards}.
+Next, the log
 messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters.  The output is an
+identical constant parts and varying parameters.
+The output is an
 ordered list of timed events and their corresponding parameter
-values~\cite{he2016evaluation}.  This structured log can serve as
-input to various machine learning and data mining processes. Apart
-from a large body of research on system logs, an equally mature amount of commercial-grade and
-opensource tooling exists to analyze system logs---such as, for example, Elasticsearch, Logstash and Kiabana (the so-called ELK stack)~\cite{sanjappa2017analysis,bajer2017building}.
+values~\cite{he2016evaluation}.
+This structured log can serve as
+input to various machine learning and data mining processes.
+Apart
+from a large body of research on system logs, an equally mature amount
+of commercial-grade and
+opensource tooling exists to analyze system logs---such as, for
+example, Elasticsearch, Logstash and Kiabana (the so-called ELK
+stack)~\cite{sanjappa2017analysis,bajer2017building}.
 
@@
 In addition, almost all of the techniques developed to analyze system logs
-leverage their inherent event structure.   Build logs generally lack this
+leverage their inherent event structure.
+Build logs generally lack this
 structure and thus require different bespoke approaches.
@@
 
-In this section, we first give a general overview over our paper population.
+In this section, we first give a general overview over our paper
+population.
 We then present the results of the analysis phase along RQs 1.1 through
@@
 \subsubsection{Descriptive Study Statistics}
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/years.pdf}
+		\caption{Number of works analyzing build logs per year.}
+		\label{fig:lit-years}
+\end{figure}
+
 After the third filtering phase, we finally included 61 works in the
@@
 when the field of build log analysis started to grow rapidly.
-
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=\columnwidth,
-		clip]{img/lit-sur/years.pdf}
-		\caption{Number of works analyzing build logs per year.}
-		\label{fig:lit-years}
-\end{figure}
 
@@
 
-The most mentioned technique (34\%) was using a parser. In this tag, we also
+The most mentioned technique (34\%) was using a parser.
+In this tag, we also
 included
@@
 (first mentioned in a paper in 2001, vast majority after
-2016), \textbf{build log analysis is already an established technique,} with 61 works in different venues making use of it for a variety of purposes.
+2016), \emph{build log analysis is already an established technique,}
+with 61 works in different venues making use of it for a variety of
+purposes.
 We saw that various researchers analyze build logs, often because the
@@
 % ----- information RQ 1.1 -----
-In regards to the information that is targeted, \textbf{most build log
+In regards to the information that is targeted, \emph{most build log
 analysis approaches aim to retrieve the reason a build failed} by
@@
 % which is what we also do in LogChunks
-\textbf{The majority of approaches retrieves specific chunks of
-text from the logs.} Chunks in some sense are the overarching concept to the almost equally used categorization, as a categorization can usually be deducted from chunks, but not vice versa.
+\emph{The majority of approaches retrieves specific chunks of
+text from the logs.} Chunks in some sense are the overarching concept to
+the almost equally used categorization, as a categorization can usually
+be deducted from chunks, but not vice versa.
 
 % ----- technique RQ 1.2 -----
-\textbf{Most log analysis is automated.} Automated approaches are
+\emph{Most log analysis is automated.} Automated approaches are
 necessary because many studies target a large number of builds.
@@
 make manual analysis feasible''~\cite{zolfagharinia2017not}.
-We observed \textbf{very little reuse of build log analysis tools},
+We observed \emph{very little reuse of build log analysis tools},
 even though works reported that
-\textbf{developing automated analysis tools requires a lot of effort}.
+\emph{developing automated analysis tools requires a lot of effort}.
 Urli et al.~\cite{urli2018design} strongly discouraged from parsing
@@
 works pointed to the effort of developing a custom tool.
-We know from other research lines that regular expressions, the second most popular way to analyze log files (\Cref{tab:litsur:techniques}), are tedious to
+We know from other research lines that regular expressions, the second
+most popular way to analyze log files (\Cref{tab:litsur:techniques}),
+are tedious to
 maintain~\cite{michael2019regexes}.
 In addition, we rarely saw works justifying why they use a certain
-technique to analyze build logs as there is a general \textbf{lack of
+technique to analyze build logs as there is a general \emph{lack of
 guidance on when to use which technique.}
@@
 every supported build tool.
-\Cref{fig:litsur:log_producer} shows that there are only a handful of build tools whose build logs more than one study analyzed, mainly in the Java ecosystem (area \circlenum{A}).
-Many works target a unique build tool that did not appear in any other study (area \circlenum{B}).
-\textbf{seldomly-investigated
+\Cref{fig:litsur:log_producer} shows that there are only a handful of
+build tools whose build logs more than one study analyzed, mainly in
+the Java ecosystem (area \circlenum{A}).
+Many works target a unique build tool that did not appear in any other
+study (area \circlenum{B}).
+
+\emph{seldomly-investigated
 environments would benefit from the
 existence of a more generic solution.}
-% In most cases, \textbf{researchers analyze build logs from open
+% In most cases, \emph{researchers analyze build logs from open
 % source projects}, obtained through Travis CI.
@@
 
+%% REVIEW MARKER
 % Alt:
@@
 \caption{Results of chunk retrieval with Program Synthesis by Example
-(PBE)}
+(PBE).}
 \end{figure*}

### 2020-05-01 tse-paper/content.tex
Add content
Small fix
Add new motivating section

@@
 
+% TODO Moritz: is this okay (here)?
+% maybe it's better to add it to Threats to Validity with the heading:
+% \texbf{Modifying the Build Process.}
+% Moritz: I think best to decided once we read the paper
+% top to bottom.
+%For now, it seems ok
+% Needs to go Threats or intro
 % TODO Caro: I moved it to the intro
@@
 purposes.
-We saw that various researchers analyze build logs, often because the
-logs are the only available source for the
+We saw that various researchers analyze build logs, with the
+logs often being the only available source for the
 information they need for their studies~\cite{ren2018automated,
@@
 \emph{The majority of approaches retrieves specific chunks of
-text from the logs.} Chunks in some sense are the overarching concept to
-the almost equally used categorization, as a categorization can usually
-be deducted from chunks, but not vice versa.
+text from the logs.} Chunks are the overarching concept to
+the almost equally much used categorization: one can deduce a categorization from chunks, but not vice versa.
 
@@
 study (area \circlenum{B}).
-
-\emph{seldomly-investigated
+We follow that \emph{many seldomly-investigated
 environments would benefit from the
 existence of a more generic solution.}
+
+% TODO passive ...
+The literature survey shows the need for
+build log
+analysis techniques that are \emph{automated},
+\emph{build tool-agnostic}
+and can be \emph{configured with little effort}.
+
 % In most cases, \emph{researchers analyze build logs from open
@@
 % - unclear which information you want
-
-% TODO Moritz: is this okay (here)?
-% maybe it's better to add it to Threats to Validity with the heading:
-% \texbf{Modifying the Build Process.}
-% Moritz: I think best to decided once we read the paper
-% top to bottom.
-%For now, it seems ok
-% Needs to go Threats or intro
 
@@
 
-In summary, the outcome of the literature survey shows the need for
-build log
-analysis techniques that are \emph{automated},
-\emph{build tool-agnostic}
-and can be \emph{configured with little effort}.
-
-To address this need,
-we propose a set of so called \emph{chunk retrieval techniques},
-which retrieve a specific substring (called chunk)
-from a build log.
+% TODO This introduction is weird
+In this section, we formally define the concept of chunk
+retrievals from build logs. Then, we motivate and present the choice of three such techqniues that we implemented for this study in detail.
+
+In this section,
+we propose three so-called \emph{chunk retrieval techniques},
+which retrieve a specific substring (chunk)
+from a build log
+% TODO passive ....
 The techniques we propose run automatically
 and can be easily configured through examples.
+% TODO this should go under characteristics and not be in an introduction to the section ...
 An example in this case consists of a build log together with the
@@
 
-We designed and implemented three chunk retrieval
-techniques based on approaches
-previously described by several works:
-\emph{Program Synthesis by Example (PBE)}
-mimics regular expressions, while simplifying
-their development.
-From the field of information retrieval, we leverage a
-\emph{Common Text Similarity (CTS)} approach
-and implement the ad hoc approach of
-searching for specific strings as \emph{Keyword Search (KWS)}.
-
-In this section, we define our concept of chunk
-retrieval techniques and present each of the techniques
-we developed in detail.
-Following that, we illustrate how the techniques
-operate on a concrete
-example and sketch out their implementation.
-
-\begin{table*}[htb]
-\centering
-\caption{Chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}llXll@{}}
-\toprule
-Name			     & Acronym & Identification Technique
-& Granularity & Configuration \\
-\midrule
-Program Synthesis by Example & PBE     & Regular expression program
-& Character   & In/output examples	\\
-Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
-expected number of lines & Line        & Output examples	   \\
-Keyword Search		     & KWS     & Keywords, expected number of
-lines			 & Line        & Keywords, context length  \\
-Random Line Retrieval	     & RLR     & Random sample
-& Line	      & Retrieval length	  \\
-\bottomrule
-\end{tabularx}
-\label{tab:techniques}
-\end{table*}
-
 \subsection{Characteristics of Chunk Retrieval Techniques}
 \label{sec:crt-characteristics}
-Before introducing each of the techniques, we formalize
-we formalize our concept of chunk retrieval techniques.
-By this phrase, we refer to techniques that automatically
-retrieve pieces of information that appear literally in build
+% TODO (resolved) Never define a concept with the
+% words used in the term
+% Use a thesaurus to find synonyms
+
+With the term ``chunk retrieval technique,'' we refer to a way of automatically extracting strings that appear literally in build
 logs, i.e., techniques that do not aggregate, combine, or deduct
@@
 Generally, chunk retrieval techniques
-can also be used to classify build logs, e.g.\ by checking
+can also be used to classify build logs, e.g.\, by checking
 which substring was retrieved.
 Therefore, they
-cover the great majority of the types of log analysis we saw within
-our survey.
+cover the great majority of the types of log analysis we saw in \Cref{sec:lit-sur:discussion}.
 
@@
 build log text.
+
+\subsection{Choice of Chunk Retrieval Techniques}
+For this article, we designed and implemented three automated chunk
+retrieval techniques. The strategies that underlie them were inspired
+based on techniques we found in the literature survey and other
+research fields. 
 In \Cref{tab:techniques}, we summarize and distinguish the techniques
 we present along the characteristics described above.
+
+Techniques based on custom parsers (\#1
+in \Cref{tab:litsur:techniques}) are inadquate for our comparison,
+since their creation is manual and such a technique would not
+generalize on the wide varitey of build logs we are interested in. The
+closest we could come to the second entry, regular expression, is a
+technique to automatically derive them: In particular, we implement a
+technique based on
+\emph{Program Synthesis by Example (PBE)}. This 
+mimics regular expressions, the second most frequently occurring whose while simplifying
+their development.
+
+To work effectively with build logs, many humans anecdotally search
+(``grep'') the logs for key phrases such as ``fail.'' Papers often
+resorted to such a strategy when doing manual analysis (\#2
+in \Cref{tab:litsur:techniques}), describing it with the word
+``scan.'' Imitating this ad hoc approach of searching for specific
+strings, we automatize it as \emph{Keyword Search (KWS)}.
+
+Finally, from the fields of information retrieval and natural language
+processing, we leverage a
+\emph{Common Text Similarity (CTS)} approach. The reason for it is that the relevant, failing parts of build logs often looks similar to each other, even if the exact failure reason might differ.
+
+\begin{table*}[htb]
+\centering
+\caption{Chunk retrieval techniques.}
+\begin{tabularx}{\textwidth}{@{}llXll@{}}
+\toprule
+Name & Acronym & Identification Technique & Granularity &
+Configuration \\
+\midrule
+Program Synthesis by Example & PBE     & Regular expression program
+& Character   & In/output examples	\\
+% TODO: TF-IDF still not defined
+Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
+expected number of lines & Line        & Output examples	   \\
+Keyword Search		     & KWS     & Keywords, expected number of
+lines			 & Line        & Keywords, context length  \\
+Random Line Retrieval	     & RLR     & Random sample
+& Line	      & Retrieval length	  \\
+\bottomrule
+\end{tabularx}
+\label{tab:techniques}
+\end{table*}
 
@@
 the chunk that describes why the build
+% TODO add back ref
 failed---the information targeted by most of the works in our

### 2020-05-01 tse-paper/content.tex
Lines
Done deduction

@@
 text from the logs.} Chunks are the overarching concept to
-the almost equally much used categorization: one can deduce a categorization from chunks, but not vice versa.
+the almost equally much used categorization: one can deduce a
+categorization from chunks, but not vice versa.
 
@@
 In this section, we formally define the concept of chunk
-retrievals from build logs. Then, we motivate and present the choice of three such techqniues that we implemented for this study in detail.
+retrievals from build logs.
+Then, we motivate and present the choice of three such techqniues that
+we implemented for this study in detail.
 
@@
 and can be easily configured through examples.
-% TODO this should go under characteristics and not be in an introduction to the section ...
+% TODO this should go under characteristics and not be in an introduction
+to the section ...
 An example in this case consists of a build log together with the
@@
 
-With the term ``chunk retrieval technique,'' we refer to a way of automatically extracting strings that appear literally in build
+With the term ``chunk retrieval technique,'' we refer to a way of
+automatically extracting strings that appear literally in build
 logs, i.e., techniques that do not aggregate, combine, or deduct
@@
 Therefore, they
-cover the great majority of the types of log analysis we saw in \Cref{sec:lit-sur:discussion}.
+cover the great majority of the types of log analysis we saw in
+\Cref{sec:lit-sur:discussion}.
 
@@
 For this article, we designed and implemented three automated chunk
-retrieval techniques. The strategies that underlie them were inspired
+retrieval techniques.
+The strategies that underlie them were inspired
 based on techniques we found in the literature survey and other
@@
 since their creation is manual and such a technique would not
-generalize on the wide varitey of build logs we are interested in. The
+generalize to the wide varitey of build logs we are interested in.
+The
 closest we could come to the second entry, regular expression, is a
-technique to automatically derive them: In particular, we implement a
+technique to automatically derive them: in particular, we implement a
 technique based on
-\emph{Program Synthesis by Example (PBE)}. This 
-mimics regular expressions, the second most frequently occurring whose while simplifying
-their development.
+\emph{Program Synthesis by Example (PBE)}.
+This mimics regular expressions, while simplifying their development.
 
@@
 resorted to such a strategy when doing manual analysis (\#2
-in \Cref{tab:litsur:techniques}), describing it with the word
-``scan.'' Imitating this ad hoc approach of searching for specific
-strings, we automatize it as \emph{Keyword Search (KWS)}.
+in \Cref{tab:litsur:techniques}), describing it with the word ``scan''
+or other paraphrases. Imitating this ad hoc approach of searching for
+specific strings, we automatize it as \emph{Keyword Search (KWS)}.
 
@@
 processing, we leverage a
-\emph{Common Text Similarity (CTS)} approach. The reason for it is that the relevant, failing parts of build logs often looks similar to each other, even if the exact failure reason might differ.
+\emph{Common Text Similarity (CTS)} approach.
+The reason for it is that the relevant, failing parts of build logs
+often looks similar to each other, even if the exact failure reason
+might differ.
 

### 2020-05-01 tse-paper/content.tex
Commenting out

@@
 
-%% REVIEW MARKER
 % Alt:
@@
 
-% TODO This introduction is weird
 In this section, we formally define the concept of chunk
@@
 
-In this section,
-we propose three so-called \emph{chunk retrieval techniques},
-which retrieve a specific substring (chunk)
-from a build log
-% TODO passive ....
-The techniques we propose run automatically
-and can be easily configured through examples.
-% TODO this should go under characteristics and not be in an introduction
-to the section ...
-An example in this case consists of a build log together with the
-chunk that should be retrieved.
-A user---a developer or a researcher who wants to analyze
-build logs---provides these examples, which are easy to
-adapt whenever the analysis technique needs
-to support new cases.
+% TODO Caro: Not sure what to do with this ...
+%% In this section,
+%% we propose three so-called \emph{chunk retrieval techniques},
+%% which retrieve a specific substring (chunk)
+%% from a build log
+%% % TODO passive ....
+%% The techniques we propose run automatically
+%% and can be easily configured through examples.
+%% % TODO this should go under characteristics and not be in an introduction
+%% to the section ...
+%% An example in this case consists of a build log together with the
+%% chunk that should be retrieved.
+%% A user---a developer or a researcher who wants to analyze
+%% build logs---provides these examples, which are easy to
+%% adapt whenever the analysis technique needs
+%% to support new cases.
 
@@
 in \Cref{tab:litsur:techniques}), describing it with the word ``scan''
-or other paraphrases. Imitating this ad hoc approach of searching for
+or other paraphrases.
+Imitating this ad hoc approach of searching for
 specific strings, we automatize it as \emph{Keyword Search (KWS)}.

### 2020-05-01 tse-paper/content.tex
address comments, spellchecking

@@
 
-% TODO Moritz: is this okay (here)?
-% maybe it's better to add it to Threats to Validity with the heading:
-% \texbf{Modifying the Build Process.}
-% Moritz: I think best to decided once we read the paper
-% top to bottom.
-%For now, it seems ok
-% Needs to go Threats or intro
-% TODO Caro: I moved it to the intro
-% --- please check how it works for you
 Retrospectively analyzing the build logs is not the only solution to
@@
 present in the build logs.
-Moreover, build log analyis is the more general soltuion.
+Moreover, build log analysis is the more general solution.
 While they serve an important niche, custom plugins do not make build
@@
 the process of how to
-% TODO
-%automatically
-% ^ we survey manual as well, though leaving it out includes too much
-% systematically twice -- avoid this
+automatically
 analyze build logs has thus far not been systematically
@@
 of commercial-grade and
-opensource tooling exists to analyze system logs---such as, for
+open source tooling exists to analyze system logs---such as, for
 example, Elasticsearch, Logstash and Kiabana (the so-called ELK
@@
 \Cref{fig:litsur:use} shows the aim for the
-% TODO: isn't this discussion already?
-% Moritz: Not sure what is meant by that?
 investigated works to analyze build logs, and the result also explains
@@
 For such imprecise statements it was often not clear if they described
-a complex parser (including a tokenizer, lexer, etc.) or refered to a
+a complex parser (including a tokenizer, lexer, etc.) or referred to a
 simpler parsing tool based on regular expressions.
@@
 saw some reuse of the few available build log analysis tools.
-% TODO The numbers here might look a bit strange
-% --- we say five but really it is six works we reference.
-% I assume this is because of only including the oldest ref?
-% Still, I think we need to fix the inconsistency.
 Five works employed the tools used to create
-\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
+\emph{TravisTorrent}~\cite{beller2017oops,
 orellana2017differences,zhao2018comparing} or
@@
 another two
-\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao}.
+\emph{MAKAO}~\cite{wen2018blimp,adams2007design}.
 
@@
 Ghaleb et al.~\cite{ghaleb2019studying},
-% TODO	include the several others as references?
-and several others have studied.
+and several others have studied~\cite{hassan2017change,
+hassan2019tackling,hassan2017automatic,orellana2017differences,
+haghighatkhah2018test,madeyski2017continuous,ghaleb2019empirical,
+santolucito2018statically,gallaba2018noise,shi2018evaluating}.
 
@@
 
-% TODO passive ...
 The literature survey shows the need for
@@
 \emph{build tool-agnostic}
-and can be \emph{configured with little effort}.
+and that a user can \emph{configure with little effort}.
 
@@
 retrievals from build logs.
-Then, we motivate and present the choice of three such techqniues that
+Then, we motivate and present the choice of three such techniques that
 we implemented for this study in detail.
 
-% TODO Caro: Not sure what to do with this ...
+% TOO Caro: Not sure what to do with this ...
 %% In this section,
@@
 %% from a build log
-%% % TODO passive ....
+%% % TOO passive ....
 %% The techniques we propose run automatically
 %% and can be easily configured through examples.
-%% % TODO this should go under characteristics and not be in an introduction
+%% % TOO this should go under characteristics and not be in an
+% introduction
 %% to the section ...
@@
 \label{sec:crt-characteristics}
-% TODO (resolved) Never define a concept with the
-% words used in the term
-% Use a thesaurus to find synonyms
 
@@
 Techniques based on custom parsers (\#1
-in \Cref{tab:litsur:techniques}) are inadquate for our comparison,
+in \Cref{tab:litsur:techniques}) are inadequate for our comparison,
 since their creation is manual and such a technique would not
-generalize to the wide varitey of build logs we are interested in.
+generalize to the wide variety of build logs we are interested in.
 The
@@
 & Character   & In/output examples	\\
-% TODO: TF-IDF still not defined
 Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
@@
 algorithm weighs the vectors using \emph{term frequency-inverse
-document frequency}, a best practice for natural
+document frequency (TF-IDF)}, a best practice for natural
 language queries~\cite{lee1997document}.
@@
 the chunk that describes why the build
-% TODO add back ref
 failed---the information targeted by most of the works in our
-literature survey.
+literature survey (see \Cref{sec:lit-sur:discussion}).
 To be able to configure the keyword search technique,

### 2020-05-04 tse-paper/content.tex
Lots of feedback and review

@@
 \addtolength{\tabcolsep}{-5pt}
+\label{sec:litsurresults}
 
@@
 Then, we motivate and present the choice of three such techniques that
-we implemented for this study in detail.
+we implemented and evaluated for this study.
 
@@
 \emph{Running a
-chunk retrieval technique} means applying a fully configured
-technique to a build log in plain text format.
-The technique then outputs a list that consists of substrings of the
+chunk retrieval technique} means
+% TODO what does it mean ``to apply?''
+applying a fully configured
+technique to a build log.
+The technique then outputs a (possibly empty) list of substrings of the
 build log text.
@@
 \subsection{Choice of Chunk Retrieval Techniques}
-For this article, we designed and implemented three automated chunk
-retrieval techniques.
-The strategies that underlie them were inspired
-based on techniques we found in the literature survey and other
-research fields.
-In \Cref{tab:techniques}, we summarize and distinguish the techniques
-we present along the characteristics described above.
-
-Techniques based on custom parsers (\#1
-in \Cref{tab:litsur:techniques}) are inadequate for our comparison,
-since their creation is manual and such a technique would not
-generalize to the wide variety of build logs we are interested in.
-The
-closest we could come to the second entry, regular expression, is a
-technique to automatically derive them: in particular, we implement a
-technique based on
-\emph{Program Synthesis by Example (PBE)}.
-This mimics regular expressions, while simplifying their development.
-
-To work effectively with build logs, many humans anecdotally search
-(``grep'') the logs for key phrases such as ``fail.'' Papers often
-resorted to such a strategy when doing manual analysis (\#2
-in \Cref{tab:litsur:techniques}), describing it with the word ``scan''
-or other paraphrases.
-Imitating this ad hoc approach of searching for
-specific strings, we automatize it as \emph{Keyword Search (KWS)}.
-
-Finally, from the fields of information retrieval and natural language
-processing, we leverage a
-\emph{Common Text Similarity (CTS)} approach.
-The reason for it is that the relevant, failing parts of build logs
-often looks similar to each other, even if the exact failure reason
-might differ.
 
@@
 
+For this article, we designed and implemented three automated chunk
+retrieval techniques.  Our findings of techniques in the literature
+survey (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
+particular) inspired the strategies that underlie them.
+\Cref{tab:techniques} summarizes the techniques, which describe in detail in the following.
+
+Techniques based on custom parsers (\#1
+in \Cref{tab:litsur:techniques}) are inadequate for our comparison,
+since their creation is manual and one parser would never generalize
+to the wide variety of build logs we are interested in.  The closest
+we could come to the second most popular entry, regular expression, is
+a technique to automatically derive them: in particular, we implement
+a technique based on
+\emph{Program Synthesis by Example (PBE)}.
+It uses regular expressions internally, while simplifying their
+development.
+
+To work effectively with build logs, many humans anecdotally search
+(``grep'') the logs for key phrases such as ``fail.'' Researchers often
+resorted to such a strategy when doing manual analysis (\#2
+in \Cref{tab:litsur:techniques}), describing it with the word ``scan''
+or other paraphrases.
+Imitating this ad hoc approach of searching for
+specific strings, we automatize it as \emph{Keyword Search (KWS)}.
+
+% TODO Caro, can you check this? Also I did not find any literature
+% references to CTS. It does not seem to be a common technique?
+% Where does the name come from then?
+Finally, from the fields of information retrieval (IR) and natural language
+processing (NLP), we leverage a
+\emph{Common Text Similarity (CTS)} approach.
+The inspiration behind it---apart from literature indicating the use
+of IR and NLP (\Cref{tab:litsur:techniques})--- is that the relevant,
+failing parts of build logs often looks similar to each other, even if
+the exact failure reason might differ.
+
 \subsection{Program Synthesis by Example (PBE)}
-The concept of \emph{Programming by Example} aims to automatically
+The idea behind \emph{Programming by Example} is to automatically
 generate a program, by capturing the
@@
 for build logs.
-The \emph{PROSE library}~\cite{prose2019webpage} is the basis of
+The \emph{PROSE library}~\cite{prose2019webpage} forms the basis for
 our implementation.
@@
 \subsubsection{Configuration}
-In- and output example pairs are the main driver of Programming by
-Example; we refer to them in short as \emph{examples}.
-The \emph{input} is the text of the build log file.
+In- and output example pairs are the main driver of PBE; 
+The \emph{input} is the full text of the build log file.
 The \emph{output} is
@@
 If PROSE cannot synthesize a program, e.g.,\
-because the regular expression
-necessary is too complicated to be synthesized, PBE returns the
+because the required regular expression
+is too complicated to be synthesized, PBE returns the
 error message ``no program found.''
@@
 of the build log matched by the program.
-% I hope this is fine, you can also cut this sentence if it still
-% bothers you :)
-% no match is a category later in the results section
 If the program finds no match because the analyzed build log
@@
 retrieves those lines from a build log which are most
-similar to examples given by the user.
+similar to the specified examples.
 
 \subsubsection{Configuration}
-To configure CTS we chose to use
-the same concept of examples as for PBE.
-The lines of the targeted chunks from the training examples define the
-search query.
-We represent each line as a term vector where every entry counts
-how often a word appears within the line.
-These vectors exist in a space with as many dimensions as different
-words appear in the log text.
-This Vector Space Model~\cite{schutze2008introduction} defines
-text lines as more similar if they contain the same words in the same
-frequencies, making their term vectors point in a similar direction
-in the vector space.
-We use the cosine function to calculate the angle between two
-term vectors.
-The smaller the angle between term vectors, the more similar are the
-corresponding lines.
-This is called \emph{cosine similarity}~\cite{korenius2007principal}.
+To configure CTS we chose to use the same concept of examples as for
+PBE: lines of the targeted chunks from the training examples define
+the search query.  Using a Vector Space
+Model~\cite{schutze2008introduction} (VSM), an algebraic model for
+representing textual documents, we encode each line as a separate term
+vector. The terms that make up the dictionary are simply all words
+that appear in the example logs, where we separate words by spaces.
+% TODO Caro: complete above sentence if we separate by anything else
+The vectors comprise points counting
+how many times a word out of the dictionary appears in the specific
+line at hand.
+
+The idea behind a representation in the VSM is that text lines as more
+similar if they contain the same words in similar frequencies,
+making their term vectors point in a similar direction in vector
+space.  We use \emph{cosine similarity}~\cite{korenius2007principal}
+to calculate the angle between two term vectors.  The smaller the
+angle between term vectors is, the more similar are the corresponding
+lines.
 
@@
 \subsubsection{Application}
-To retrieve the desired information from a build log, we parse the
-whole text and process it in the same way as the search query.
+To retrieve the desired information from a build log, we encode every line of the input build log in VSM.
 The algorithm calculates the cosine
@@
 use is to search for related keywords.
-Indeed, this was one of the
-most common approaches we took when searching for the reason a build
-failed while creating the \emph{LogChunks} data
-set~\cite{brandt2020logchunks}.
-To investigate the performance of this approach, we
-designed a chunk retrieval technique based on keyword search.
+%% TODO Caro: I took this out as it interrupts reading flow. Do you
+%% agree?
+%% Indeed, this was one of the
+%% most common approaches we took when searching for the reason a build
+%% failed while creating the \emph{LogChunks} data
+%% set~\cite{brandt2020logchunks}.
+To investigate the performance of this approach, we designed a chunk
+retrieval technique mimcing this human behavior based on keyword
+search.
 
@@
 compare KWS with PBE and CTS, we also configure it through examples.
-We associate a list of keywords with each example.
-The keywords should appear in the targeted
-chunk or close to it.
-Then, we merge these lists and use the most commonly occurring
-keywords for the search with KWS.
+% TODO (resolved) associate is very abstract and tells us
+% less about what is going on than the new version
+From each example, we extract a list of keywords that we hope should
+also appear in, or close to, the targeted chunk of new input.
+Finally, we merge the lists from all examples to build one unified
+list of the most commonly occurring keywords for the search with KWS.
 
 \subsubsection{Application}
-For a retrieval run, we take a whole build log file as input and
+For a retrieval run, we take an entire build log file as input and
 search for all exact occurrences of the search keywords.
@@
 often not directly describing the desired information, but rather
-appear close to the desired information, KWS also retrieves the lines
+appear close to it, KWS also retrieves a context of lines
 around the found keyword.
@@
 retrieve.
-For a fair comparison to the other techniques (whose number of
+For a comparison to the other techniques (whose number of
+% TODO Caro: but wait, this is not really true for KWS, right?
 returned lines is dynamic), we configure RLR to return the average
@@
 
-To illustrate the chunk retrieval techniques further, we give
-an example of how the chunk retrieval techniques retrieve chunks from
-the real-world build logs in \Cref{lst:logexamples}.
-Marked in blue are the chunks
-which contain the information on why the
+In this section, we illustrate how the different chunk retrieval
+techniques work practically on the example of the build logs
+in \Cref{lst:logexamples}. Marked in blue in \Cref{lst:logexamples}
+are the chunks we target. They contain the information on why the
 corresponding build failed.
-
 \Cref{lst:chunk-example} shows two excerpts
-from Android build logs.
-When we train PBE with these two examples, it produces
-a regular expression program similar to the one presented in
+from Android build logs. The chunk to be retrieved starts after a
+colon and a line separator and before a capital letter.  It ends
+before two line separators. All these characteristics are consistent
+with the two example chunks
+from \Cref{lst:chunk-example}. \Cref{lst:chunk-example-3} is very
+different. For example, it does not have the two extraneous newlines
+after the chunk.
+
+% TODO Caro: I like this explanation of structural categories and
+% would leave it here (slightly adapted), but I think
+% struct. categ. should be mentioned earlier -- not sure if you know a
+% better place, but how about sec. 3.1? i don't think people should
+% have to read an example section -- which they might skip -- to
+% get to know of this important concept!
+
+When we train PBE with the two examples from \Cref{lst:chunk-example},
+it produces a regular expression program similar to the one presented
+in
 \Cref{lst:prose-program-simplified}.
-The retrieval
-starts after a colon and a line separator and before a capital
-letter.
-It ends before two line separators,
-which is consistent with the two example
-chunks from \Cref{lst:chunk-example}.
 This shows that the characters structuring the text around the chunk are
 crucial for regular expressions to identify a log chunk.
-In fact, if we add the third example from \Cref{lst:chunk-example-3}
+In fact, if we add the third example from 
 to the training set (which has a
@@
 the training examples have on average 2.0 lines.
+% TODO Caro: How well does it deal with the third example?
 
@@
 \subsection{Tool Implementation}
-For the comparison study, we implemented each of the chunk retrieval
-techniques and a unifying interface.
-The unified interface is written in Ruby and
-calls the separate technique implementations over the command line.
+For the comparison study, we implemented the three chunk retrieval
+techniques described in this section and a unifying interface.
 We implemented PBE in C\# based on the Microsoft PROSE
@@
 
-In the literature survey we saw that few works justify why they
-use a certain build log analysis technique and concluded that there
-is a lack of guidance on when to use which technique.
+In the literature survey, we noted that previous work seemed to choose
+a log analysis technique arbitrarly and that is a lack of guidance on
+when to use which technique.
 % add (see \Cref{sec:lit-sur:discussion}) ?
-To address this lack of guidance we conduct an empirical study
+To address this, in this section, we conduct an empirical study
 comparing the three novel chunk retrieval techniques we presented in
 \Cref{sec:techniques}.
-We vary the conditions under which we train and run the techniques
-to answer when a technique performs best and which conditions should
-influence the choice for one technique over the others.
 
@@
 has to be (\textbf{RQ2.2}), and how reliable the quality of the
-produced outputs is (\textbf{RQ2.3}).
+produced retrievals is (\textbf{RQ2.3}).
 This leads us to the following research questions:
@@
 
-In the following, we introduce the data set we created for this
-study and describe the design of our comparison study.
+In the following, we first introduce the data set we created for this
+study, and then describe the study design and its
+results.
 
@@
 \emph{LogChunks} data set~\cite{brandt2020logchunks}.
-From Travis CI---the most-used source of build logs
-according to our literature survey---we collected
-797 build logs that
-stem from a broad range of 80 GitHub projects and 29
-programming languages.
-This wide variety of projects, and the large number of different build
-tools they employ, enables us to measure the generic
-applicability of the chunk retrieval techniques.
-
-For each build log, we manually marked
+We collected 797 build logs that
+from 80 GitHub projects and 29
+programming languages on Travis CI, the most-used source of build logs
+according to our literature survey.
+This wide variety of projects and the large number of different build
+tools they employ enables us to measure the generic
+applicability of chunk retrieval techniques.
+
+For each build log in \emph{LogChunks}, we manually marked
 the chunk that describes why the build
@@
 To be able to configure the keyword search technique,
-the data set associates each chunk with keywords that we
+% TODO (resolved) the data set cannot associate anything 
+we associated each chunk in the data set with keywords that we
 would use to search for the selected chunk within the log.
@@
 within the log.
-If the chunks were surrounded by the same markings
+% TODO Are surrounding markings really the only structural
+% category element? I doubt that
+If the chunks were, for example, surrounded by the same markings
 within the log, we assigned them the \emph{same structural category},
@@
 
-This, the build log text, the corresponding chunk,
-the search keywords, and the assigned structural categories
-make up one \emph{example}.
-Examples are the basic units in the training and test sets of our
-empirical comparison study.
+% TODO what does this refer to here? Make it clearer.
+%It would refer to the strcutrual categories but
+% that is already in the list?
+
+% TODO couldn't it also be chunks? why corresponding?
+As explained in \Cref{sec:crt-characteristics}, examples are the basic
+unit by which we configure each technique.  The full build log text,
+chunk(s), search keywords, and the assigned structural categories make
+up one \emph{example} in \emph{LogChunks}.
 
@@
 
-In the following, we explain each of the steps of our study
-(see \Cref{fig:study})
+In the following, we explain the individual steps of our study design
 and introduce the metrics that
-we measure to answer our research questions.
-
-We apply each of the chunk retrieval techniques
+we measure to answer RQ2.
+
+% TODO Didn't we above define ``run'' instead of apply?
+% Shouldn't we then also use it here?
+% TODO wow, this starts already super confusing
+We run each of the three chunk retrieval techniques
 on all of the 80 projects in
@@
 
-Based on this, we collect the following measurements \circlenum{7}:
+Based on this, we collect retrieval performance measurements \circlenum{7} for
 the size of the training set (\textbf{RQ2.1}),
@@
 
-\section{Results}
+\subsection{Results}
 The empirical comparison study yielded diverse results for the
@@
 
-\subsection{Program Synthesis by Example (PBE)}
+\subsubsection{Program Synthesis by Example (PBE)}
 \label{sec:r:pbe}
@@
 
-\subsection{Common Text Similarity (CTS)}
+\subsubsection{Common Text Similarity (CTS)}
 \label{sec:r:cts}
@@
 
-\subsection{Keyword Search (KWS)}
+\subsubsection{Keyword Search (KWS)}
 \label{sec:r:kws}
@@
 % maybe I/We'll do it at the end
-\subsection{Random Line Retrieval (RLR)}
+\subsubsection{Random Line Retrieval (RLR)}
 \label{sec:r:rlr}
@@
 
-\subsection{Comparison of All Techniques}
+\subsubsection{Comparison of All Techniques}
 In this section, we compare the results of all four chunk retrieval

### 2020-05-04 tse-paper/content.tex
Ran reindent
Review

@@
 \subsection{Choice of Chunk Retrieval Techniques}
+\label{sec:choice}
 
@@
 For this article, we designed and implemented three automated chunk
-retrieval techniques.  Our findings of techniques in the literature
+retrieval techniques.
+Our findings of techniques in the literature
 survey (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
 particular) inspired the strategies that underlie them.
-\Cref{tab:techniques} summarizes the techniques, which describe in detail in the following.
+\Cref{tab:techniques} summarizes the techniques, which describe in detail
+in the following.
 
@@
 since their creation is manual and one parser would never generalize
-to the wide variety of build logs we are interested in.  The closest
+to the wide variety of build logs we are interested in.
+The closest
 we could come to the second most popular entry, regular expression, is
@@
 % TODO Caro, can you check this? Also I did not find any literature
-% references to CTS. It does not seem to be a common technique?
+% references to CTS.
+It does not seem to be a common technique?
 % Where does the name come from then?
-Finally, from the fields of information retrieval (IR) and natural language
+Finally, from the fields of information retrieval (IR) and natural
+language
 processing (NLP), we leverage a
@@
 PBE: lines of the targeted chunks from the training examples define
-the search query.  Using a Vector Space
+the search query.
+Using a Vector Space
 Model~\cite{schutze2008introduction} (VSM), an algebraic model for
 representing textual documents, we encode each line as a separate term
-vector. The terms that make up the dictionary are simply all words
+vector.
+The terms that make up the dictionary are simply all words
 that appear in the example logs, where we separate words by spaces.
@@
 making their term vectors point in a similar direction in vector
-space.  We use \emph{cosine similarity}~\cite{korenius2007principal}
-to calculate the angle between two term vectors.  The smaller the
+space.
+We use \emph{cosine similarity}~\cite{korenius2007principal}
+to calculate the angle between two term vectors.
+The smaller the
 angle between term vectors is, the more similar are the corresponding
@@
 \subsubsection{Application}
-To retrieve the desired information from a build log, we encode every line of the input build log in VSM.
+To retrieve the desired information from a build log, we encode every
+line of the input build log in VSM.
 The algorithm calculates the cosine
@@
 use is to search for related keywords.
-%% TODO Caro: I took this out as it interrupts reading flow. Do you
+%% TODO Caro: I took this out as it interrupts reading flow.
+%% Do you
 %% agree?
@@
 techniques work practically on the example of the build logs
-in \Cref{lst:logexamples}. Marked in blue in \Cref{lst:logexamples}
-are the chunks we target. They contain the information on why the
+in \Cref{lst:logexamples}.
+Marked in blue in \Cref{lst:logexamples}
+are the chunks we target.
+They contain the information on why the
 corresponding build failed.
 \Cref{lst:chunk-example} shows two excerpts
-from Android build logs. The chunk to be retrieved starts after a
-colon and a line separator and before a capital letter.  It ends
-before two line separators. All these characteristics are consistent
+from Android build logs.
+The chunk to be retrieved starts after a
+colon and a line separator and before a capital letter.
+It ends
+before two line separators.
+All these characteristics are consistent
 with the two example chunks
-from \Cref{lst:chunk-example}. \Cref{lst:chunk-example-3} is very
-different. For example, it does not have the two extraneous newlines
+from \Cref{lst:chunk-example}.
+\Cref{lst:chunk-example-3} is very
+different.
+For example, it does not have the two extraneous newlines
 after the chunk.
@@
 % would leave it here (slightly adapted), but I think
-% struct. categ. should be mentioned earlier -- not sure if you know a
-% better place, but how about sec. 3.1? i don't think people should
+% struct.
+categ.
+should be mentioned earlier -- not sure if you know a
+% better place, but how about sec.
+3.1? i don't think people should
 % have to read an example section -- which they might skip -- to
@@
 \begin{itemize}[leftmargin=1.2cm]
-  \item[\textbf{RQ2.1:}] How many examples does a technique need to
-  perform best?
-  \item[\textbf{RQ2.2:}] How structurally similar do the examples
-  need for a technique to be applicable?
+  \item[\textbf{RQ2.1:}] With how many examples does a technique perform best?
+  \item[\textbf{RQ2.2:}] How structurally variable can configuration examples be?
   \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
@@
 study, and then describe the study design and its
-results.
+results. We answer these RQs separately for each technique.
 
@@
 As explained in \Cref{sec:crt-characteristics}, examples are the basic
-unit by which we configure each technique.  The full build log text,
+unit by which we configure each technique.
+The full build log text,
 chunk(s), search keywords, and the assigned structural categories make
@@
 
-Based on this, we collect retrieval performance measurements \circlenum{7} for
+Based on this, we collect retrieval performance measurements \circlenum{7}
+for
 the size of the training set (\textbf{RQ2.1}),
@@
 \subsection{Results}
-The empirical comparison study yielded diverse results for the
-different chunk retrieval techniques
 In this section, we first present the results for each chunk retrieval
@@
 
-\section{Discussion}
+\subsection{Discussion}
 \label{sec:discussion}
 
-For the interpretation of the study results, we look at each chunk
-retrieval technique separately.
-Next, we discuss
-which criteria should influence the decision to use a certain
-chunk retrieval technique most.
-Based on the empirical comparison, we present a
-decision tree between the three techniques we investigated.
-
-\subsection{Interpretation of Study Results}
-Following from the results of the empirical study,
+Following from the results of the empirical study, in this section,
 we give recommendations for
@@
 
-\subsection{Recommendation of Suitable Techniques}
-
+\subsection{Usage Recommendation}
+In this section, we derive a decision tree to help practitioners and
+researchers choose a suitable chunk retrieval technique. We then
+illustrate its use on two examples.
+
+\subsubsection{Derivation of Decision Tree}
 \begin{figure}[bt]
@@
 
-We saw that each of the techniques is suited for different types of
-log chunks and the output of each is suited for different uses.
-Now, we unify these results into conditions to answer
-our second research question;
-If researchers or developers want to retrieve chunks from build logs,
-they can follow these conditions to identify the technique
-suited best for their use case.
-% I want to ref the figure early bc I believe the text is easier
-% to follow when looking at the figure as well
-We summarize these conditions in the decision tree in
+Abstractly, we have learned that every chunk retrieval technique
+differs in its suitability depending on the kinds of logs it should
+operate on and the sort of output one expects.  In this section, we
+unify these findings, culminating in the creation of a decision tree
+to help developers and researchers choose an adequate technique in
 \Cref{fig:crt-recommendation}.
-It is built up of questions
-which either lead to more questions or to a leaf node containing a
-recommended technique.
-In the next section we give two concrete examples on how to
-apply our decision tree.
-
-% we can't just have a paragraph in a scientific paper start with
-% Caveat, I think ;-) Also, we should say why we THINK this is not
-%the case.
-% Otherwise we weaken our work unduly
-% Of course we can! xD
-% Agree with the rest.
-% It's in TtV, quite close actually
-% so I'll comment this out
-% also #more selling :D
-% \textbf{Caveat!}
-% This is a preliminary hypothesis based on the results
-% from our comparison study.
-% The recommendations could therefore be
-% influenced by idiosyncrasies of our specific implementation of the
-% chunk retrieval techniques as well as the \emph{LogChunks}
-% data set.
-
-The first and most important aspect that influences a choice for
-a chunk retrieval technique are the structural categories.
-In other words:
-are the targeted log chunks always presented in
-the same structural way within the build logs?
-Then the
-chunks in all training examples and the analyzed build log are in the
-same structural category.
-This is why the first question in \Cref{fig:crt-recommendation} asks
-how many structural categories the targeted log chunks have.
-
-If the chunks are from multiple structural categories
-and recall is more important than precision we recommend
-to use KWS\@.
+
+The first and most important aspect that influences the decision for a
+chunk retrieval technique is the presence of different structural
+categories in the log (or lack therefore).  Are the targeted log
+chunks always present in the same structural way within the build logs
+(first question in \Cref{fig:crt-recommendation})?  If so, the chunks
+in all training examples and the analyzed build log are in the same
+structural category
+%TODO ... and what? PBE is the best technique?
+If the chunks are from multiple structural categories and recall is
+more important than precision, we recommend to use KWS\@.
+% TODO because ?
+
 If precision is more important than recall, we
@@
 from one structural category, when the user does not require high
-confidence in the precision or recall of the outcome and when one
+confidence in the precision or recall of the outcome, and when one
 would rather have output with low recall instead of no output at all.
@@
 when the chunks are from one structural category and the user
-wishes high confidence in the correctness of the output or prefers
+needs high confidence in the correctness of the output or prefers
 no output over output with low recall, we recommend PBE\@.
@@
 combining the different build log analysis techniques studied in this
-paper.
-Such a super analyzer would likely always first employ PBE
+paper.  Such a super analyzer would likely always first employ PBE
 (because of its high accuracy), followed by a combination of CTS and
-KWS\@.
-Other than initial setup and training time, there is no
-downside to this approach if it is implemented in a transparent way to
-the underlying technique: the output of the super analyzer could
-include from which sub-technique it originated and thus facilitate
-automatic onward processing or interpretation of the result.
-
-\subsection{Exemplary Recommendation}
+KWS\@.  Other than initial setup and training time, there is no
+downside to this approach if it is implemented in a transparent way:
+the output of the super analyzer could include from which
+sub-technique it originated and thus facilitate automatic onward
+processing or interpretation of the result.
+
+\subsubsection{Example Use Cases}
 To illustrate how one would use the decision tree to find a suitable
-chunk retrieval technique we describe two concrete examples: a software
+chunk retrieval technique we describe here two concrete examples: a software
 team
 wanting to monitor their build performance and a
-researcher investigating why builds fail.
+group of researchers investigating why builds fail.
 
@@
 small or large groups of test cases
-cause CI build failures.
+cause CI failures.
 They gather
 CI build logs from various projects.
-The task of the researcher is to extract the names of the
-failing test cases from each build log.
+Their aim is to extract the names of the
+failing test cases from the build logs.
 When they use the
@@
 test cases is in the investigated build logs.
-As the researcher is
+As the researchers are
 covering a wide range of test tools, the
@@
 \Cref{fig:crt-recommendation},
-the decision tree recommends the researcher to use KWS\@.
-
-In case the researcher wants to avoid manually inspecting the
-retrieval results, they have to first separate the CI build logs
-according to the test tool responsible for logging the test results.
-Then the targeted log chunks are from one structural category and they
-can use PBE, trained with examples from each test tool separately.
+the decision tree recommends the researcher to use KWS\@.  An
+alternate, potentially more laborious but also more precise solution
+could be for researchers to first separate the CI build logs by the
+test tool responsible for logging the test results.  Then, the
+targeted log chunks are from one structural category and they can use
+PBE, trained with examples from each test tool separately.
 
 \section{Threats to Validity}
-There are several threats to the validity of the conclusions of our
-work.
+In this section, we outline threats to the validity of our work and
+show how we mitigated them.
+
+% TODO Caro: fill in the maven analyzer plugin and others.
+\textbf{Limitation to Scholarly Articles.} We limited our literature survey to scholarly articles.
+However, the field of build log analysis is extremely relevant to practitioners, too.
+While it is difficult to systematically sight all such non-scientific material, we ran several Google search queries related to build log analysis and evaluted them informally.
+Our findings include the Jenkins build log analyzer and a web page on which Microsoft details how its CI service, Azure Pipes, uses a PBE-approach for certain log formats such as Python.
+This inspired the choice of PBE in \Cref{sec:choice}.
 
@@
 retrieval techniques and the libraries we used.
-The program synthesis provided by PROSE is the basis for our
-implementation of PBE\@.
-The
-idiosyncrasies of this framework influence the PBE results.
-Other
+
+The program synthesis
+provided by PROSE is the basis for our implementation of PBE\@.  The
+idiosyncrasies of this framework influence the PBE results.  Other
 frameworks similar to PROSE might have somewhat different strengths
-and weaknesses.
-For example, the need for examples from a single
+and weaknesses.  For example, the need for examples from a single
 structural category stems from the fact that PROSE cannot learn
 regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}.
-PROSE introduced this constraint to
-keep the synthesis performance reasonable.
-At the same time, this is
-clearly a current theoretical challenge of all PBE implementations,
+disjunctions~\cite{mayer2015user}.  PROSE introduced this constraint
+to keep the synthesis performance reasonable.  At the same time, this
+is clearly a current theoretical challenge of all PBE implementations,
 and we therefore attribute it to the technique itself, rather than the
@@
 
-The library
+Similarly, the library
 {\tt text2vec}~\cite{text2vec2019webpage}
@@
 
+% TODO (resolved)
 % kinda uncreative..
@@
 % not sure if this adds much on top of the sentences further up
+%% Yup, it's super cool and I expanded it a bit
 Overall, we believe our implementations and their weaknesses stand
-prototypical for the techniques.
-We tried to limit idiosyncrasies as much as possible, by choosing
-standard approaches and configurations.
+prototypical for the techniques.  We tried to limit idiosyncrasies as
+much as possible, by choosing standard approaches and minimizing
+configuration, instead of parameterizing and fine-tuning methods
+specific to our data set.
 
 \textbf{Data Set.}
-The build logs from the \emph{LogChunks} data set highly affect
+Just like the implementations, the specific build logs from the \emph{LogChunks} data set affect
 the outcomes of the comparison study.
 \emph{LogChunks} consists of build
-logs from open source projects and therefore it is not clear whether
-our results apply to industry projects that use build tools
-not popular in open source development.
-However, since \emph{LogChunks} covers a wide array of build tools and
-programming languages,
-we believe that the findings do generalize.
-We collected build logs from Travis CI.
-Yet, the format of the log chunk we chose
-for the evaluation is largely independent of Travis CI\@.
-This
-is because the reason the build failed is described within the build
-logs by the tools themselves and not the Travis CI environment.
+logs from open source projects and therefore it is unclear to which
+degree our results apply to industry projects that use build tools not
+popular in open source development.  However, since \emph{LogChunks}
+covers a wide array of build tools and programming languages, we
+believe that the findings do generalize. In addition, build log output
+of such a tool would need to be wildly different from how the over 27
+tools covered in our study do it---this seems unlikely.
+
+We collected build logs from
+Travis CI.  Yet, the format of the log chunk we chose for the
+evaluation is largely independent of Travis CI\@, because the reason
+the build failed is described within the build logs by the tools
+themselves and not the Travis CI environment.
 
@@
 Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples.
-We chose this small training set
-size as a user has to provide the training examples
-per project and one of the central aims of the chunk
-retrieval techniques is that they can be set up wit little effort.
-The fact that PBE and KWS performed best with already two training
-examples shows that the training set size is large enough to
-compare the three techniques.
+only trained on one to five examples.  We chose this small training
+set size as a human has to provide the training examples and one of
+the central aims of the chunk retrieval techniques is that they can be
+set up wit little effort.  The fact that KWS and CTS performed best
+with already two training examples indicates that the maximum training
+set size of five is sufficiently large for research evaluation.
 
 \textbf{Few Samples with Many Structural Categories.}
-Our comparison study shows fewer measurements with many structural
+Our comparison study includes fewer measurements with many structural
 categories than with one structural category category (50.25\% one,
-33.75\% two, 13.75\% more than two).
-This stems from the fact that we
-investigated the chunk retrieval techniques on a real-world data set,
-where there were mostly few structural categories within one project.
-In addition, the third of the measurements we conducted with two
-structural categories already showed the negative effect of an
-increasing number of structural categories on the performance of the
-chunk retrieval techniques.
+% TODO This does not add up to 1. Please no decimals,
+% we do not need so much precision here. Also tell % of what?
+33.75\% two, 13.75\% more than two).  This distribution mirrors the
+structural categories in a real-world data set, where there were
+mostly few structural categories within one project.  In addition, the
+third of the measurements we conducted with two structural categories
+already showed the negative effect of an increasing number of
+structural categories on the performance of the chunk retrieval
+techniques.
 
 \section{Future Work}
-% Actually, this future work is very, *very* good.
-%It might be
-% the best future work I have ever read in an article.
-% One idea would be to sell it as such and tie a bit back to our
-% first literature survey.
-%You can say you give a roadmap to guide
-% future research in the field, and sell it in abstract and intro!
-
-There are various future research opportunities based on the
-work we presented:
+In this section, we describe what we believe are fruitful future
+research directions in the field of build log analysis. We base our
+assessment on the results of the literature survey and combine it with
+findings from our technique comparsion study.
 
 \textbf{Systematic Survey of Industry Approaches for Build
-Log Analysis.}
-Our survey is limited to academic work and articles.
-However, handling build logs is a challenge for a wide range of
-practitioners as well.
-We propose to investigate the techniques used in industry to analyze
-build logs.
-An example is the Jenkins \emph{build-failure-analyzer}
-plugin~\cite{jenkins2020failure-analyzer} or automatically
-inferred test results in Azure~\cite{azure2020inferred}.
+Log Analysis.}  Our survey is limited to scholarly material.  However,
+handling build logs is a challenge for a wide range of practitioners
+as well.  We propose to investigate the techniques used in industry to
+analyze build logs.  An example is the
+Jenkins \emph{build-failure-analyzer}
+plugin~\cite{jenkins2020failure-analyzer} or automatically inferred
+test results in Azure~\cite{azure2020inferred}. Such a study might
+also need to tackle the more abstract problem of how to survey
+non-scholarly material systematically, which might be an important
+contribution to Software Engineering research.
 
@@
 analyses of build log data.
+% TODO Passive overflow
 The keywords, for example, can be
@@
 \textbf{Comparison with more Chunk Retrieval Techniques.}
-This
-paper investigates the three chunk retrieval techniques PBE, CTS, and
+In this article, we investigated the three chunk retrieval techniques PBE, CTS, and
 KWS\@.
@@
 
-\textbf{Refinement of Retrieval Quality for each Technique.} We
+\textbf{Refinement of Retrieval Quality.} We
 investigated basic configurations of existing techniques applied to
@@
 In a next step, each of these
-techniques could be refined to better approach the domain of build
+techniques could be refined to better customize it to the domain of build
 logs.
@@
 \begin{itemize}[leftmargin=0.4cm]
-  \item \textbf{Custom Ranking and Tokens for PBE.} The program
+  \item \textbf{Custom Ranking and Tokens for PBE.} Program
   synthesis through PROSE ranks possible programs according to
@@
 	``=,'' ``ERROR,''
-  or ``[OK]''.
+  or ``[OK]'' to improve results.
   \item \textbf{Meta-Parameter Optimization for CTS.} Information
@@
   investigate improvements in preprocessing of the log text, in
-  tokenization of the log lines into terms and in stop words
+  tokenization of the log lines into terms, and in stop words
   lists.
@@
 The goal of this paper is to support practitioners and researchers in
-their decision on how to analyze build logs.
-To this end, we
+their decision on how to analyze build logs.  To this end, we
 conducted a systematic mapping survey to map out the available build
-log analysis techniques.
-We saw that, while build log analysis is widely used, it is often
-a side part of a work and implementations are rarely reused.
-This shows the need for a new generation of generic and automated
-build log analysis techniques that need little effort to set up.
+log analysis techniques.  We saw that build log analysis is an
+emerging field. At the same time, articles largely do not justify why
+they use a certain technique, nor do they document it in detail or
+open-sourced its implementation. Moreover, the survey showed that,
+while there is a niche for custom parsers and plugins for very popular
+tools such as the Java ecosystem, there is a wide variety of build
+tool and enviroment combinations for which the creation of such
+bespoke tooling is unlikely.  Overall, we showed the need for a new
+generation of generic and automated build log analysis techniques that
+need little effort to set up, both for practitioners as well as
+researchers.
 
@@
 CTS had the highest average F$_{1}$-score with 51\%, while the other
-techniques showed higher average scores for precision (95\%, PBE)
-and recall (70\%, KWS).
+techniques showed higher average scores for precision (95\%, PBE) and
+recall (70\%, KWS). Overall, all technqiues vastly outperformed a
+baseline of random line retrieval.
 
@@
 that the structural representation of the targeted information in the
-build logs is the main factor a user should consider when they
-choose a
+build logs is the main factor one should consider when 
+choosing a build log analysis
 technique.
@@
 Important themes are a systematic investigation of industry approaches,
-benchmarks of existing build log analysis approaches and further
+benchmarks of existing build log analysis approaches, and further
 refinement of the chunk retrieval techniques we proposed.
@@
 analyze build logs will support researchers and developers alike to
-leverage the vast amounts of valuable information
-hidden within build logs.
+leverage the vast amounts of valuable information hidden
+in build logs.

### 2020-05-04 tse-paper/content.tex
And lines

@@
 \begin{itemize}[leftmargin=1.2cm]
-  \item[\textbf{RQ2.1:}] With how many examples does a technique perform best?
-  \item[\textbf{RQ2.2:}] How structurally variable can configuration examples be?
+  \item[\textbf{RQ2.1:}] With how many examples does a technique
+  perform best?
+  \item[\textbf{RQ2.2:}] How structurally variable can configuration
+  examples be?
   \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
@@
 study, and then describe the study design and its
-results. We answer these RQs separately for each technique.
+results.
+We answer these RQs separately for each technique.
 
@@
 In this section, we derive a decision tree to help practitioners and
-researchers choose a suitable chunk retrieval technique. We then
+researchers choose a suitable chunk retrieval technique.
+We then
 illustrate its use on two examples.
@@
 differs in its suitability depending on the kinds of logs it should
-operate on and the sort of output one expects.  In this section, we
+operate on and the sort of output one expects.
+In this section, we
 unify these findings, culminating in the creation of a decision tree
@@
 chunk retrieval technique is the presence of different structural
-categories in the log (or lack therefore).  Are the targeted log
+categories in the log (or lack therefore).
+Are the targeted log
 chunks always present in the same structural way within the build logs
@@
 structural category
-%TODO ... and what? PBE is the best technique?
+%TODO ...
+and what? PBE is the best technique?
 If the chunks are from multiple structural categories and recall is
@@
 combining the different build log analysis techniques studied in this
-paper.  Such a super analyzer would likely always first employ PBE
+paper.
+Such a super analyzer would likely always first employ PBE
 (because of its high accuracy), followed by a combination of CTS and
-KWS\@.  Other than initial setup and training time, there is no
+KWS\@.
+Other than initial setup and training time, there is no
 downside to this approach if it is implemented in a transparent way:
@@
 To illustrate how one would use the decision tree to find a suitable
-chunk retrieval technique we describe here two concrete examples: a software
+chunk retrieval technique we describe here two concrete examples:
+a software
 team
@@
 \Cref{fig:crt-recommendation},
-the decision tree recommends the researcher to use KWS\@.  An
+the decision tree recommends the researcher to use KWS\@.
+An
 alternate, potentially more laborious but also more precise solution
 could be for researchers to first separate the CI build logs by the
-test tool responsible for logging the test results.  Then, the
+test tool responsible for logging the test results.
+Then, the
 targeted log chunks are from one structural category and they can use
@@
 % TODO Caro: fill in the maven analyzer plugin and others.
-\textbf{Limitation to Scholarly Articles.} We limited our literature survey to scholarly articles.
-However, the field of build log analysis is extremely relevant to practitioners, too.
-While it is difficult to systematically sight all such non-scientific material, we ran several Google search queries related to build log analysis and evaluted them informally.
-Our findings include the Jenkins build log analyzer and a web page on which Microsoft details how its CI service, Azure Pipes, uses a PBE-approach for certain log formats such as Python.
+\textbf{Limitation to Scholarly Articles.} We limited our literature
+survey to scholarly articles.
+However, the field of build log analysis is extremely relevant to
+practitioners, too.
+While it is difficult to systematically sight all such non-scientific
+material, we ran several Google search queries related to build log
+analysis and evaluted them informally.
+Our findings include the Jenkins build log analyzer and a web page
+on which Microsoft details how its CI service, Azure Pipes, uses a
+PBE-approach for certain log formats such as Python.
 This inspired the choice of PBE in \Cref{sec:choice}.
@@
 The program synthesis
-provided by PROSE is the basis for our implementation of PBE\@.  The
-idiosyncrasies of this framework influence the PBE results.  Other
+provided by PROSE is the basis for our implementation of PBE\@.
+The
+idiosyncrasies of this framework influence the PBE results.
+Other
 frameworks similar to PROSE might have somewhat different strengths
-and weaknesses.  For example, the need for examples from a single
+and weaknesses.
+For example, the need for examples from a single
 structural category stems from the fact that PROSE cannot learn
 regular expression programs with arbitrary boolean conjunctions and
-disjunctions~\cite{mayer2015user}.  PROSE introduced this constraint
-to keep the synthesis performance reasonable.  At the same time, this
+disjunctions~\cite{mayer2015user}.
+PROSE introduced this constraint
+to keep the synthesis performance reasonable.
+At the same time, this
 is clearly a current theoretical challenge of all PBE implementations,
@@
 Overall, we believe our implementations and their weaknesses stand
-prototypical for the techniques.  We tried to limit idiosyncrasies as
+prototypical for the techniques.
+We tried to limit idiosyncrasies as
 much as possible, by choosing standard approaches and minimizing
@@
 \textbf{Data Set.}
-Just like the implementations, the specific build logs from the \emph{LogChunks} data set affect
+Just like the implementations, the specific build logs from the
+\emph{LogChunks} data set affect
 the outcomes of the comparison study.
@@
 degree our results apply to industry projects that use build tools not
-popular in open source development.  However, since \emph{LogChunks}
+popular in open source development.
+However, since \emph{LogChunks}
 covers a wide array of build tools and programming languages, we
-believe that the findings do generalize. In addition, build log output
+believe that the findings do generalize.
+In addition, build log output
 of such a tool would need to be wildly different from how the over 27
@@
 We collected build logs from
-Travis CI.  Yet, the format of the log chunk we chose for the
+Travis CI.
+Yet, the format of the log chunk we chose for the
 evaluation is largely independent of Travis CI\@, because the reason
@@
 Especially the results for CTS might be influenced by the fact that we
-only trained on one to five examples.  We chose this small training
+only trained on one to five examples.
+We chose this small training
 set size as a human has to provide the training examples and one of
 the central aims of the chunk retrieval techniques is that they can be
-set up wit little effort.  The fact that KWS and CTS performed best
+set up wit little effort.
+The fact that KWS and CTS performed best
 with already two training examples indicates that the maximum training
@@
 categories than with one structural category category (50.25\% one,
-% TODO This does not add up to 1. Please no decimals,
-% we do not need so much precision here. Also tell % of what?
-33.75\% two, 13.75\% more than two).  This distribution mirrors the
+% TODO This does not add up to 1.
+Please no decimals,
+% we do not need so much precision here.
+Also tell % of what?
+33.75\% two, 13.75\% more than two).
+This distribution mirrors the
 structural categories in a real-world data set, where there were
-mostly few structural categories within one project.  In addition, the
+mostly few structural categories within one project.
+In addition, the
 third of the measurements we conducted with two structural categories
@@
 In this section, we describe what we believe are fruitful future
-research directions in the field of build log analysis. We base our
+research directions in the field of build log analysis.
+We base our
 assessment on the results of the literature survey and combine it with
@@
 \textbf{Systematic Survey of Industry Approaches for Build
-Log Analysis.}  Our survey is limited to scholarly material.  However,
+Log Analysis.}	Our survey is limited to scholarly material.
+However,
 handling build logs is a challenge for a wide range of practitioners
-as well.  We propose to investigate the techniques used in industry to
-analyze build logs.  An example is the
+as well.
+We propose to investigate the techniques used in industry to
+analyze build logs.
+An example is the
 Jenkins \emph{build-failure-analyzer}
 plugin~\cite{jenkins2020failure-analyzer} or automatically inferred
-test results in Azure~\cite{azure2020inferred}. Such a study might
+test results in Azure~\cite{azure2020inferred}.
+Such a study might
 also need to tackle the more abstract problem of how to survey
@@
 \textbf{Comparison with more Chunk Retrieval Techniques.}
-In this article, we investigated the three chunk retrieval techniques PBE, CTS, and
+In this article, we investigated the three chunk retrieval techniques PBE,
+CTS, and
 KWS\@.
@@
 The goal of this paper is to support practitioners and researchers in
-their decision on how to analyze build logs.  To this end, we
+their decision on how to analyze build logs.
+To this end, we
 conducted a systematic mapping survey to map out the available build
-log analysis techniques.  We saw that build log analysis is an
-emerging field. At the same time, articles largely do not justify why
+log analysis techniques.
+We saw that build log analysis is an
+emerging field.
+At the same time, articles largely do not justify why
 they use a certain technique, nor do they document it in detail or
-open-sourced its implementation. Moreover, the survey showed that,
+open-sourced its implementation.
+Moreover, the survey showed that,
 while there is a niche for custom parsers and plugins for very popular
@@
 tool and enviroment combinations for which the creation of such
-bespoke tooling is unlikely.  Overall, we showed the need for a new
+bespoke tooling is unlikely.
+Overall, we showed the need for a new
 generation of generic and automated build log analysis techniques that
@@
 techniques showed higher average scores for precision (95\%, PBE) and
-recall (70\%, KWS). Overall, all technqiues vastly outperformed a
+recall (70\%, KWS).
+Overall, all technqiues vastly outperformed a
 baseline of random line retrieval.

### 2020-05-05 tse-paper/content.tex
mark where we answer RQs 2.x

@@
 % tense: past
-\addtolength{\tabcolsep}{-5pt}
+
 \label{sec:litsurresults}
@@
 \subsubsection{Which analysis techniques exist? (RQ 1.2)}
+
+\addtolength{\tabcolsep}{-5pt}
 \begin{table*}[tbhp]
@@
 % TODO what does it mean ``to apply?''
+% C: run vs apply / show 332 heading / maybe take only run
 applying a fully configured
@@
 % references to CTS.
-It does not seem to be a common technique?
+% It does not seem to be a common technique?
 % Where does the name come from then?
+
+% C: text similarity and three letter acronyms
 Finally, from the fields of information retrieval (IR) and natural
@@
 %% set~\cite{brandt2020logchunks}.
+
+% C: motivation for KWS in LogChunks Paper
+% yeah we can maybe leave that out here (move to 'choice for crt'?)
+
 To investigate the performance of this approach, we designed a chunk
-retrieval technique mimcing this human behavior based on keyword
+retrieval technique mimicking this human behavior based on keyword
 search.
@@
 % less about what is going on than the new version
+
+% hope........
+% C: explain pure technique vs evaluate-able technique vs comparable
+% maybe! we can just replace the hope, or even refer to or logchunks
+% experience here / later
 From each example, we extract a list of keywords that we hope should
@@
 For a comparison to the other techniques (whose number of
-% TODO Caro: but wait, this is not really true for KWS, right?
+% M: but wait, this is not really true for KWS, right?
+% TODO Moritz: C: sure it is.
+
+% for KWS we vary the number of lines we extract around a found word
 returned lines is dynamic), we configure RLR to return the average
@@
 % struct.
-categ.
-should be mentioned earlier -- not sure if you know a
+%categ.
+%should be mentioned earlier -- not sure if you know a
 % better place, but how about sec.
-3.1? i don't think people should
+%3.1? i don't think people should
 % have to read an example section -- which they might skip -- to
 % get to know of this important concept!
+
+% C: indeed it's a bit too important to skip
+% though can we reasonably explain this without introducing the
+% exact techniques first?
+% we can also try to start with the example section
 
@@
 % TODO Caro: How well does it deal with the third example?
+% TS has so much magic & this example never ran in our study
+% note: I include no notice of how 'good' it runs here
+% if we look at the used words: they are very different in both examples
 
@@
 
-% TODO: decide if keep or redo
-% if keep, Caro do noted improvements
+% TODO Moritz: redo figure
+% depending on the size of changes / keeping figure uniformity
+% we can also do 'pair-animating'
 \begin{figure*}[tb]
@@
 In the literature survey, we noted that previous work seemed to choose
-a log analysis technique arbitrarly and that is a lack of guidance on
+a log analysis technique arbitrarily and that is a lack of guidance on
 when to use which technique.
@@
 {\textbf{RQ2:} How do build log analysis techniques compare?}
+% TODO: can we say 'training examples' in 22?
 \begin{itemize}[leftmargin=1.2cm]
-  \item[\textbf{RQ2.1:}] With how many examples does a technique
-  perform best?
-  \item[\textbf{RQ2.2:}] How structurally variable can configuration
+  \item[\textbf{RQ2.1:}] With how many training examples does a
+	technique perform best?
+  \item[\textbf{RQ2.2:}] How structurally variable can training
   examples be?
@@
 To be able to configure the keyword search technique,
-% TODO (resolved) the data set cannot associate anything
 we associated each chunk in the data set with keywords that we
@@
 % category element? I doubt that
+% C: ?
 If the chunks were, for example, surrounded by the same markings
@@
 % that is already in the list?
+% C: are you talking about the following or the previous paragraph?
+% the following one is a more explicit definition of 'example' as
+% used in the study
 
 % TODO couldn't it also be chunks? why corresponding?
+% C: you took that out already? a (maybe unecessary) specification
+% it is always ONE chunk !
 As explained in \Cref{sec:crt-characteristics}, examples are the basic
@@
 The full build log text,
-chunk(s), search keywords, and the assigned structural categories make
+the chunk, the search keywords, and the assigned
+structural category make
 up one \emph{example} in \emph{LogChunks}.
@@
 % Shouldn't we then also use it here?
+% C: see discussion further above about run vs apply
+% if we adapt the headings (332 and so on) we can use run
 % TODO wow, this starts already super confusing
+% C: T.T
 We run each of the three chunk retrieval techniques
@@
 \centering
-\begin{tabular}{llll}
+\begin{tabular}{lllll}
   \toprule
-  & \textbf{PBE} & \textbf{CTS} & \textbf{KWS} \\
+  & & \textbf{PBE} & \textbf{CTS} & \textbf{KWS} \\
+
 	\midrule
-  \textbf{Structural Categories} & 1 & less is better & \makecell[l]{best
-  1 \\
-  multiple okay} \\
+
+	\textbf{RQ2.1} & \textbf{Training Set Size} & 2 & no influence &
+	2 \\
+
   \midrule
-  \textbf{Training Set Size} & 2 & no influence & 2 \\
+
+	\textbf{RQ2.2} & \textbf{Structural Categories} & 1 & less
+	is better
+	& \makecell[l]{best 1 \\ multiple okay} \\
+
 	\midrule
-  \textbf{Precision} & \makecell[l]{high \\ (if synthesis succeeds)} &
-  medium &
-  low \\
-    \midrule
-  \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} &
-  medium &
-  high \\
-    \midrule
-  \makecell[l]{\textbf{Confidence in} \\ \textbf{Output Correctness}}
+
+  \multirow{6}{*}{\textbf{RQ2.3}} & \textbf{Precision} &
+	\makecell[l]{high \\ (if synthesis succeeds)} &
+  medium & low \\
+
+	\cmidrule{2-5}
+
+  & \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} &
+  medium & high \\
+
+	\cmidrule{2-5}
+
+  & \makecell[l]{\textbf{Confidence in} \\ \textbf{Output Correctness}}
   & high & low &
-  \makecell[l]{low (precision) \\ high (recall)} \\	\midrule
-  \textbf{Output Consumer} & program & human & human \\
+  \makecell[l]{low (precision) \\ high (recall)} \\
+
+	\cmidrule{2-5}
+
+  & \textbf{Output Consumer} & program & human & human \\
   \bottomrule
@@
 \noindent
-\textbf{Configuration and Input.}
+\textbf{With how many training examples does PBE perform best? (RQ2.1).}
+When the training examples are of the same structure, one or two
+two training examples are enough input for PROSE to synthesize a regular
+expression program with good recall.
+In the study, additional training
+examples from the same structural category
+did not improve the chunk retrieval.
+In fact, unless they
+were in some sense redundant, adding more training examples even
+hindered the applicability of PBE.
+
+\noindent
+\textbf{How structurally variable can training examples be? (RQ2.2).}
 The study results show that chunk retrieval with PBE gives best
@@
 
-When the training examples are of the same structure, one or two
-two training examples are enough input for PROSE to synthesize a regular
-expression program with good recall.
-In the study, additional training
-examples from the same structural category
-did not improve the chunk retrieval.
-In fact, unless they
-were in some sense redundant, adding more training examples even
-hindered the applicability of PBE.
-
 \noindent
-\textbf{Retrieval Output Usage.}
+\textbf{How accurate are the retrievals of PBE? (RQ2.3).}
 If the program synthesis succeeds and applying the regular expression
@@
 \subsubsection{Common Text Similarity (CTS)}
+
 \noindent
-\textbf{Configuration and Input.}
-Similar to PBE, chunk retrieval using CTS yields better results the
-fewer structural categories are present in the training and test
-examples.
-
+\textbf{With how many training examples does CTS perform best? (RQ2.1).}
 The number of training examples had no noticeable influence on
@@
 \noindent
-\textbf{Retrieval Output Usage.}
+\textbf{How structurally variable can training examples be? (RQ2.2).}
+CTS yields better results the
+fewer structural categories are present in the training and test
+examples.
+
+\noindent
+\textbf{How accurate are the retrievals of CTS? (RQ2.3).}
 CTS has good precision and recall on average, though with a high
@@
 \noindent
-\textbf{Configuration and Input.}
+\textbf{With how many training examples does KWS perform best? (RQ2.1).}
+Going from one to two training examples, KWS's recall improves
+significantly.
+However, further enlarging the training set
+does not lead to further improvements.
+
+\noindent
+\textbf{How structurally variable can training examples be? (RQ2.2).}
 KWS has a higher recall than the two other techniques for multiple
@@
 
-Going from one to two training examples, KWS's recall improves
-significantly.
-However, further enlarging the training set
-does not lead to further improvements.
-
 \noindent
-\textbf{Retrieval Output Usage.}
+\textbf{How accurate are the retrievals of KWS? (RQ2.3).}
 While KWS has the highest recall of all three techniques, its
@@
 %TODO ...
-and what? PBE is the best technique?
+%and what? PBE is the best technique?
+% C: this is more a clearer 'introduction' to structural categories
+% if we believe this to be explained well enough here we can also
+% leave it out
+
+% TODO Caro: check that this does not get a mini paragraph
 If the chunks are from multiple structural categories and recall is
@@
 % TODO because ?
+% C: looking for reference to tree figure or to results section?
 
@@
 % TODO Caro: fill in the maven analyzer plugin and others.
+% C: aha did we evaluate them?...
+% C: so I'll add a few more and anecdotally say what each does?
+% the list will be in now way complete but maybe give an impression
+% as if we are close to what industry says.
 \textbf{Limitation to Scholarly Articles.} We limited our literature
@@
 material, we ran several Google search queries related to build log
-analysis and evaluted them informally.
+analysis and evaluated them informally.
 Our findings include the Jenkins build log analyzer and a web page
@@
 This inspired the choice of PBE in \Cref{sec:choice}.
+% TODO Caro: end with claim that we are still close to
+% industry approaches
 
@@
 
-% TODO (resolved)
-% kinda uncreative..
-% not sure what another example would be?
-% not sure if this adds much on top of the sentences further up
-%% Yup, it's super cool and I expanded it a bit
 Overall, we believe our implementations and their weaknesses stand
@@
 Our comparison study includes fewer measurements with many structural
-categories than with one structural category category (50.25\% one,
-% TODO This does not add up to 1.
-Please no decimals,
-% we do not need so much precision here.
-Also tell % of what?
-33.75\% two, 13.75\% more than two).
+categories than with one structural category category.
+50\% of the measurements were conducted with one structural category
+in the training and test sets
+(34\% with two, 16\% with more than two categories).
+% TODO check resolved: Also tell % of what?
 This distribution mirrors the
@@
 assessment on the results of the literature survey and combine it with
-findings from our technique comparsion study.
+findings from our technique comparison study.
 
@@
 analyses of build log data.
-% TODO Passive overflow
-The keywords, for example, can be
-investigated to answer which keywords are used to search for the
-reason the build failed within build logs.
+For example, we can investigate the keywords to answer which
+keywords developers use to mark errors that lead to a build failure
+within build logs.
 
@@
 recall (70\%, KWS).
-Overall, all technqiues vastly outperformed a
+Overall, all techniques vastly outperformed a
 baseline of random line retrieval.

### 2020-05-05 tse-paper/content.tex
meeting todo notes and easy heading changes, apply -> run

@@
 
-\subsubsection{What information is targeted in build logs? (RQ 1.1)}
+\subsubsection{What information is targeted in build logs (RQ 1.1)?}
 \label{sec:rq11}
@@
 
-\subsubsection{Which analysis techniques exist? (RQ 1.2)}
+\subsubsection{Which analysis techniques exist (RQ 1.2)?}
 
@@
 \subsubsection{Which kinds of build logs are subject to
-  analysis? (RQ 1.3)}
+  analysis (RQ 1.3)?}
 As the structure of build logs can change greatly depending on which
@@
 chunk retrieval technique} means
-% TODO what does it mean ``to apply?''
-% C: run vs apply / show 332 heading / maybe take only run
-applying a fully configured
+executing a fully configured
 technique to a build log.
@@
 
-% TODO Caro, can you check this? Also I did not find any literature
-% references to CTS.
-% It does not seem to be a common technique?
-% Where does the name come from then?
-
-% C: text similarity and three letter acronyms
 Finally, from the fields of information retrieval (IR) and natural
@@
 
-\subsubsection{Configuration}
+\subsubsection{Configuring}
 In- and output example pairs are the main driver of PBE;
@@
 
-\subsubsection{Application}
-A run of PBE takes a build log file as input and applies the
-synthesized regular expression program.
+\subsubsection{Running}
+A run of PBE takes a build log file as input and executes the
+synthesized regular expression program on it.
 It then returns the substring
@@
 
-\subsubsection{Configuration}
+\subsubsection{Configuring}
 To configure CTS we chose to use the same concept of examples as for
@@
 
-\subsubsection{Application}
+\subsubsection{Running}
 To retrieve the desired information from a build log, we encode every
@@
 %% set~\cite{brandt2020logchunks}.
+% ganz raus
 
@@
 
-\subsubsection{Configuration}
+\subsubsection{Configuring}
 A set of keywords configures the chunk retrieval with KWS\@.
@@
 % maybe! we can just replace the hope, or even refer to or logchunks
-% experience here / later
-From each example, we extract a list of keywords that we hope should
-also appear in, or close to, the targeted chunk of new input.
+% experience here / later TODO expect fix sentence!
+% TODO CARO extract a list of kewords that expecti nt the spec input and
+From each example, we extract a list of keywords that appeared in the
+training examples and that we exect to appear
+in, or close to, the targeted chunk of new input.
 Finally, we merge the lists from all examples to build one unified
@@
 
-\subsubsection{Application}
+\subsubsection{Running}
 For a retrieval run, we take an entire build log file as input and
@@
 retrieve.
-For a comparison to the other techniques (whose number of
-% M: but wait, this is not really true for KWS, right?
-% TODO Moritz: C: sure it is.
-
-% for KWS we vary the number of lines we extract around a found word
-returned lines is dynamic), we configure RLR to return the average
+For a fair comparison to the other techniques (whose number of
+returned lines is largely determined by the training set),
+we configure RLR to return the average
 number of lines in the chunks of the training examples.
@@
 ``\texttt{no program found}.''
+% adapt because already introduced word TODO Caro
+% evtl kann man diesen satz rausnehmen
 We later express this difference in structural representation through
@@
 {\textbf{RQ2:} How do build log analysis techniques compare?}
-% TODO: can we say 'training examples' in 22?
 \begin{itemize}[leftmargin=1.2cm]
@@
 within the log.
-% TODO Are surrounding markings really the only structural
-% category element? I doubt that
-% C: ?
 If the chunks were, for example, surrounded by the same markings
@@
 
-% TODO what does this refer to here? Make it clearer.
-%It would refer to the strcutrual categories but
-% that is already in the list?
-% C: are you talking about the following or the previous paragraph?
-% the following one is a more explicit definition of 'example' as
-% used in the study
-
-% TODO couldn't it also be chunks? why corresponding?
-% C: you took that out already? a (maybe unecessary) specification
-% it is always ONE chunk !
 As explained in \Cref{sec:crt-characteristics}, examples are the basic
@@
 
-% TODO Didn't we above define ``run'' instead of apply?
-% Shouldn't we then also use it here?
-% C: see discussion further above about run vs apply
-% if we adapt the headings (332 and so on) we can use run
-% TODO wow, this starts already super confusing
-% C: T.T
 We run each of the three chunk retrieval techniques
@@
 In the next step, we configure a chunk retrieval technique with
-the examples from the training set \circlenum{4} and apply the technique
-to the
+the examples from the training set \circlenum{4} and run the technique
+on the
 training set \circlenum{5}, which produces the retrieval output
@@
 \noindent
-\textbf{With how many training examples does PBE perform best? (RQ2.1).}
+\textbf{With how many training examples does PBE perform best (RQ2.1)?}
 When the training examples are of the same structure, one or two
@@
 \noindent
-\textbf{How structurally variable can training examples be? (RQ2.2).}
+\textbf{How structurally variable can training examples be (RQ2.2)?}
 The study results show that chunk retrieval with PBE gives best
@@
 \noindent
-\textbf{How accurate are the retrievals of PBE? (RQ2.3).}
-If the program synthesis succeeds and applying the regular expression
+\textbf{How accurate are the retrievals of PBE (RQ2.3)?}
+If the program synthesis succeeds and running the regular expression
 program yields an output, PBE has high precision and recall.
@@
 \noindent
-\textbf{With how many training examples does CTS perform best? (RQ2.1).}
+\textbf{With how many training examples does CTS perform best (RQ2.1)?}
 The number of training examples had no noticeable influence on
@@
 \noindent
-\textbf{How structurally variable can training examples be? (RQ2.2).}
+\textbf{How structurally variable can training examples be (RQ2.2)?}
 CTS yields better results the
@@
 \noindent
-\textbf{How accurate are the retrievals of CTS? (RQ2.3).}
+\textbf{How accurate are the retrievals of CTS (RQ2.3)?}
 CTS has good precision and recall on average, though with a high
@@
 \noindent
-\textbf{With how many training examples does KWS perform best? (RQ2.1).}
+\textbf{With how many training examples does KWS perform best (RQ2.1)?}
 Going from one to two training examples, KWS's recall improves
@@
 \noindent
-\textbf{How structurally variable can training examples be? (RQ2.2).}
+\textbf{How structurally variable can training examples be (RQ2.2)?}
 KWS has a higher recall than the two other techniques for multiple
@@
 \noindent
-\textbf{How accurate are the retrievals of KWS? (RQ2.3).}
+\textbf{How accurate are the retrievals of KWS (RQ2.3)?}
 While KWS has the highest recall of all three techniques, its
@@
 chunks always present in the same structural way within the build logs
-(first question in \Cref{fig:crt-recommendation})?  If so, the chunks
+?  If so, the chunks
 in all training examples and the analyzed build log are in the same
-structural category
+structural category (first question in \Cref{fig:crt-recommendation})
+% TODO move up pbe then cts and then kws
 %TODO ...
@@
 Our findings include the Jenkins build log analyzer and a web page
-on which Microsoft details how its CI service, Azure Pipes, uses a
-PBE-approach for certain log formats such as Python.
+on which Microsoft details how its CI service, Azure Pipelines, uses a
+PBE approach for certain log formats such as Python.
 This inspired the choice of PBE in \Cref{sec:choice}.
@@
 (34\% with two, 16\% with more than two categories).
-% TODO check resolved: Also tell % of what?
 This distribution mirrors the

### 2020-05-05 r-extractions/information-retrieval.R

@@ -77,6 +77,7 @@ run_learning_step <- function(train_examples, test_examples, step_results) {
       doc_proportion_max = 0.7,
       doc_proportion_min = 0
     )
+  
   vectorizer <- vocab_vectorizer(pruned_vocab)
   
   dtm_train <- create_dtm(it_train, vectorizer)

### 2020-05-05 tse-paper/content.tex
address todos

@@
 \emph{chunks}.
+Depending on the format of the chunks within the build log we
+separate them into different \emph{structural categories}.
 
@@
 The terms that make up the dictionary are simply all words
-that appear in the example logs, where we separate words by spaces.
-% TODO Caro: complete above sentence if we separate by anything else
+that appear in the example logs, where we separate words by spaces and
+punctuation.
 The vectors comprise points counting
@@
 use is to search for related keywords.
-%% TODO Caro: I took this out as it interrupts reading flow.
-%% Do you
-%% agree?
-%% Indeed, this was one of the
-%% most common approaches we took when searching for the reason a build
-%% failed while creating the \emph{LogChunks} data
-%% set~\cite{brandt2020logchunks}.
-% ganz raus
-
-% C: motivation for KWS in LogChunks Paper
-% yeah we can maybe leave that out here (move to 'choice for crt'?)
-
 To investigate the performance of this approach, we designed a chunk
@@
 compare KWS with PBE and CTS, we also configure it through examples.
-% TODO (resolved) associate is very abstract and tells us
-% less about what is going on than the new version
-
-% hope........
-% C: explain pure technique vs evaluate-able technique vs comparable
-% maybe! we can just replace the hope, or even refer to or logchunks
-% experience here / later TODO expect fix sentence!
-% TODO CARO extract a list of kewords that expecti nt the spec input and
 From each example, we extract a list of keywords that appeared in the
-training examples and that we exect to appear
-in, or close to, the targeted chunk of new input.
+training examples and that we expect to appear
+in, or close to, the targeted chunk in a new build log.
 Finally, we merge the lists from all examples to build one unified
@@
 
-% TODO Caro: I like this explanation of structural categories and
-% would leave it here (slightly adapted), but I think
-% struct.
-%categ.
-%should be mentioned earlier -- not sure if you know a
-% better place, but how about sec.
-%3.1? i don't think people should
-% have to read an example section -- which they might skip -- to
-% get to know of this important concept!
-
-% C: indeed it's a bit too important to skip
-% though can we reasonably explain this without introducing the
-% exact techniques first?
-% we can also try to start with the example section
-
 When we train PBE with the two examples from \Cref{lst:chunk-example},
@@
 ``\texttt{no program found}.''
-% adapt because already introduced word TODO Caro
-% evtl kann man diesen satz rausnehmen
-We later express this difference in structural representation through
-separating log chunks into \emph{structural categories}.
 The chunks from \Cref{lst:chunk-example}
@@
 
+If we train CTS with the example chunks from
+\Cref{lst:chunk-example},
 CTS will rank the lines from an analyzed build log which are most
-similar to the chunks in the training examples
-from \Cref{lst:chunk-example}.
+similar to the chunks in the training examples.
 It will then return the two lines ranked highest, as the chunks in
 the training examples have on average 2.0 lines.
-% TODO Caro: How well does it deal with the third example?
-% TS has so much magic & this example never ran in our study
-% note: I include no notice of how 'good' it runs here
-% if we look at the used words: they are very different in both examples
+In this example,
+CTS will have difficulty extracting the lines from
+\Cref{lst:chunk-example-3} as there are no words that appear
+in both the training and the test chunks.
+The same applies if we train with the first chunk from
+\Cref{lst:chunk-example} and try to retrieve the second chunk,
+as the only shared word is ``task''.
 
@@
 Are the targeted log
-chunks always present in the same structural way within the build logs
-?  If so, the chunks
+chunks always present in the same structural way
+within the build logs? If so, the chunks
 in all training examples and the analyzed build log are in the same
-structural category (first question in \Cref{fig:crt-recommendation})
-% TODO move up pbe then cts and then kws
-%TODO ...
-%and what? PBE is the best technique?
-% C: this is more a clearer 'introduction' to structural categories
-% if we believe this to be explained well enough here we can also
-% leave it out
-
-% TODO Caro: check that this does not get a mini paragraph
-If the chunks are from multiple structural categories and recall is
-more important than precision, we recommend to use KWS\@.
-% TODO because ?
-% C: looking for reference to tree figure or to results section?
-
-If precision is more important than recall, we
-recommend CTS, as \Cref{fig:crt-recommendation} shows on the
-right half of the decision tree.
-We also recommend CTS when the log chunks are
-from one structural category, when the user does not require high
-confidence in the precision or recall of the outcome, and when one
-would rather have output with low recall instead of no output at all.
+structural category (first question in \Cref{fig:crt-recommendation}).
+
 On the leftmost path of the decision tree,
@@
 no output over output with low recall, we recommend PBE\@.
+If the user does not
+require high confidence in the correctness of the output and prefers
+to receive some output even with low recall, we recommend CTS\@.
+
+On the rightmost path of the decision tree,
+if the chunks are from multiple structural categories and recall is
+more important than precision, we recommend to use KWS\@.
+If precision is more important than recall, we
+recommend CTS\@.
 
@@
 
-% TODO Caro: fill in the maven analyzer plugin and others.
-% C: aha did we evaluate them?...
-% C: so I'll add a few more and anecdotally say what each does?
-% the list will be in now way complete but maybe give an impression
-% as if we are close to what industry says.
+% M: fill in the maven analyzer plugin and others.
+% C: added to the jenkins bl analyzer, though I left out th maven
+% analyzer cause it has 1 star on github so kinda not 'industry' grade
 \textbf{Limitation to Scholarly Articles.} We limited our literature
@@
 analysis and evaluated them informally.
-Our findings include the Jenkins build log analyzer and a web page
+Our findings include the Jenkins build log
+analyzer~\cite{jenkins2020failure-analyzer}, where a user can
+define custom regular expressions to parse a build log, and a web page
 on which Microsoft details how its CI service, Azure Pipelines, uses a
@@
 This inspired the choice of PBE in \Cref{sec:choice}.
-% TODO Caro: end with claim that we are still close to
-% industry approaches
+Our impression is that non-scientific tools are often based on
+parsing with the help of regular expressions---similar to the
+techniques mentioned in scientific literature and the PBE technique
+we proposed.
 

### 2020-05-05 tse-paper/content.tex
spellchecking

@@
 open source tooling exists to analyze system logs---such as, for
-example, Elasticsearch, Logstash and Kiabana (the so-called ELK
+example, Elasticsearch, Logstash and Kibana (the so-called ELK
 stack)~\cite{sanjappa2017analysis,bajer2017building}.
@@
 tools such as the Java ecosystem, there is a wide variety of build
-tool and enviroment combinations for which the creation of such
+tool and environment combinations for which the creation of such
 bespoke tooling is unlikely.

### 2020-05-05 tse-paper/content.tex
Fix text similarity

@@
 	\item a technique based on information
-	retrieval, using \emph{Common Text Similarity (CTS)},
+	retrieval, which we call \emph{Common Text Similarity (CTS)},
 	\item inspired by the manual ad hoc search for key parts in the
@@
 language
-processing (NLP), we leverage a
-\emph{Common Text Similarity (CTS)} approach.
-The inspiration behind it---apart from literature indicating the use
-of IR and NLP (\Cref{tab:litsur:techniques})--- is that the relevant,
-failing parts of build logs often looks similar to each other, even if
-the exact failure reason might differ.
+processing (NLP, see \Cref{tab:litsur:techniques}), we leverage widely-used text similarity measures and call this approach \emph{Common Text Similarity (CTS)}.
+The intuition behind it is that the relevant,
+failing parts of build logs often look similar to each other, even if
+the exact failure reasons might differ.
 

### 2020-05-05 tse-paper/content.tex
Include minor fixes

@@
 language
-processing (NLP, see \Cref{tab:litsur:techniques}), we leverage widely-used text similarity measures and call this approach \emph{Common Text Similarity (CTS)}.
+processing (NLP, see \Cref{tab:litsur:techniques}), we leverage
+a widely-used text similarity measure and call this approach \emph{Common
+Text Similarity (CTS)}.
 The intuition behind it is that the relevant,
@@
 The terms that make up the dictionary are simply all words
-that appear in the example logs, where we separate words by spaces and
+that appear in the example logs. We separate words by spaces and
 punctuation.
@@
 \section{Future Work}
-In this section, we describe what we believe are fruitful future
+In this section, we give an outline of fruitful future
 research directions in the field of build log analysis.
 We base our
-assessment on the results of the literature survey and combine it with
+suggestions on the results of the literature survey and the
 findings from our technique comparison study.
@@
 
+One could also interpret the techniques we implemented
+differently. For example, for CTS, we look for similarity between the
+lines we want to extract. One could find similarity between the
+context that surrounds them, instead of the actual chunk to be
+extracted. The intuition behind this approach would be that often the
+error chunk is variable, but the context around it is
+stable---essentially the principle by which extraction by PBE
+works. Such a version of ``inverse CTS'' might yield better retrieval
+results.
+
 \textbf{Refinement of Retrieval Quality.} We
@@
 logs.
-The \emph{LogChunks} data set and our study results act as a
+The \emph{LogChunks} data set and our study results can act as a
 baseline to benchmark such technique improvements.
@@
   One could adapt the ranking
-  rules provided by the FlashExtract DSL to fit common build log
+  rules provided by the \emph{FlashExtract} DSL to fit common build log
   chunk retrieval tasks.
-  FlashExtract includes special tokens when
-  enumerating possible regular expressions.
+  \emph{FlashExtract} includes special tokens when
+  enumerating possible regular expressions~\cite{le2014flashextract:}.
   One could extend these
@@
   lists.
+
+  For CTS, we currently have no concept of semantic
+  similarity. Therefore, the synonyms ``Fail'' and ``Failure'' would
+  fall into two different frequency counts. Using a
+  wordnet~\cite{pedersen2004wordnet} or other NLP techniques to
+  capture synonyms might improve similarity measure between related
+  lines, and therefore overall performance of CTS.
 \end{itemize}

### 2020-05-05 tse-paper/content.tex
Add algorithm

@@
 The terms that make up the dictionary are simply all words
-that appear in the example logs. We separate words by spaces and
+that appear in the example logs.
+We separate words by spaces and
 punctuation.
@@
 
-% TODO Moritz: redo figure
-% depending on the size of changes / keeping figure uniformity
-% we can also do 'pair-animating'
-\begin{figure*}[tb]
-	\centering
-	\includegraphics[width=\textwidth, trim={1.6cm 2.5cm 0.2cm 4.8cm},
-  clip]{img/study.pdf}
-	\caption{Study design of the technique comparison study.}
-	\label{fig:study}
-\end{figure*}
-
 In the literature survey, we noted that previous work seemed to choose
@@
 
-\subsection{Study Design}
-
-In the following, we explain the individual steps of our study design
+\subsection{Procedure}
+
+% TODO Caro: Not 100% sure about the 6. I had a set of rlogs before
+% that, but then I think you only always retrieve 1 build
+% log. However, I also looked into the LogChunks data set and saw more
+% than 6 logs per project sometimes ...
+
+% TODO: In addition, if there
+% are more than 6 logs per project, aren't we missing another
+% indirection in the algorithm?
+
+\begin{figure*}[tb]
+\begin{algorithmic}[1]
+\ForEach{technique $\in\{PBE,CTS,KWS,RLR\}$}
+ \ForEach{project  $\in$ \emph{LogChunks}} \Comment{$|\emph{LogChunks}|$=80}
+  \For{$i\gets 1, 5$} 
+   \State $logs \gets getBuildLogsByTime(project, i)$  \Comment{Logs returned ordered by time of creation.}
+   \State $rlog \gets  getBuildLogsByTime(project, 6)$
+   \State $n \gets |structuralCategories(logs)|$
+   \State
+   \State $train(technique, logs)$
+       \State $retrievedLines \gets run(technique, rlog)$
+       \State $metrics \gets calculateMetrics(retrievedLines, desiredLines(rlog))$
+       \State
+       \State $saveMetrics(technique, project, n, i, metrics)$
+
+  \EndFor
+ \EndFor
+ \State $aggregateMetrics(technique)$
+\EndFor
+\end{algorithmic}
+
+	\caption{Study procedure of the empirical chunk retrieval comparison study.}
+	\label{fig:study}
+\end{figure*}
+
+In the following, we explain our study design
 and introduce the metrics that
-we measure to answer RQ2.
-
-We run each of the three chunk retrieval techniques
-on all of the 80 projects in
-\emph{LogChunks} \circlenum{1}.
-For each project, we select training sets of size 1, 2, \dots 5
-\circlenum{2}.
+we measure to answer RQ2. \Cref{fig:study} depicts the individual steps of our study as an algorithmic procedure.
+
+For each chunk retrieval technique and each project, we create training example sets consisting of 1, 2, \dots 5 examples (lines \circlenum{1}--\circlenum{3}).
 We vary the training set size to measure how many examples we need to
-confidently configure a technique.
-The training set is so small because the examples have to be
-manually created by a user.
-A larger training set would oppose our goal of providing techniques
-that can be configured with little effort
-(see \Cref{sec:lit-sur:discussion}).
-
-The test set consists of an example based on the build log produced
-chronologically after the build logs in the training set \circlenum{3}.
+confidently configure a technique, adressing \textbf{RQ2.1}.
+
+The test set consists of the first build log produced
+chronologically after the build logs in the training set \circlenum{5}.
 This way, we train on examples from past build logs and test on
-more recent logs.
-% We chose a test set size of 1, as users of the techniques
-% should receive reliable results on every build log they analyze.
-% M: and why is this important? Doesn't everyone want such stability
-%of results?
-% C: motivation why only one test example.
-% we can also leave that out
-% and answer if we are asked about it
-
-In the next step, we configure a chunk retrieval technique with
-the examples from the training set \circlenum{4} and run the technique
+a more recent log, just as one would apply these techniques in the real world.
+
+In line \circlenum{6}, we obtain how many different structural categories are present in the trained logs and store this to be able to answer \textbf{RQ2.2}.
+
+In the next step, we configure the chosen chunk retrieval technique with
+the examples from the training set \circlenum{8} and run the technique
 on the
-training set \circlenum{5}, which produces the retrieval output
-\circlenum{6}.
-
-Based on this, we collect retrieval performance measurements \circlenum{7}
-for
-the size of the training set (\textbf{RQ2.1}),
-the number of structural categories in the training
-set (\textbf{RQ2.2}),
-the lines of the retrieval output ($\mathit{RetrievedLines}$),
-and the oracle: the output defined in the test example
-($\mathit{DesiredLines}$).
-From these we calculate accuracy metrics (\textbf{RQ2.3}):
+training set, producing the retrieval output \circlenum{9}.
+
+Based on this, we calculate the following metrics in \emph{calculateMetrics}, addressing \textbf{RQ2.3}:
 
@@
 \end{itemize}
+\vspace{0.2cm}
+
+\noindent
+Finally, we aggregate the results to be able to reason per technique \circlenum{15}, completing our study design to answer \textbf{RQ2} overall.
 
 \subsection{Results}
-In this section, we first present the results for each chunk retrieval
+In this section, we first present the metrics for each chunk retrieval
 technique separately.
@@
 One could also interpret the techniques we implemented
-differently. For example, for CTS, we look for similarity between the
-lines we want to extract. One could find similarity between the
+differently.
+For example, for CTS, we look for similarity between the
+lines we want to extract.
+One could find similarity between the
 context that surrounds them, instead of the actual chunk to be
-extracted. The intuition behind this approach would be that often the
+extracted.
+The intuition behind this approach would be that often the
 error chunk is variable, but the context around it is
 stable---essentially the principle by which extraction by PBE
-works. Such a version of ``inverse CTS'' might yield better retrieval
+works.
+Such a version of ``inverse CTS'' might yield better retrieval
 results.
@@
   For CTS, we currently have no concept of semantic
-  similarity. Therefore, the synonyms ``Fail'' and ``Failure'' would
-  fall into two different frequency counts. Using a
+  similarity.
+Therefore, the synonyms ``Fail'' and ``Failure'' would
+  fall into two different frequency counts.
+Using a
   wordnet~\cite{pedersen2004wordnet} or other NLP techniques to
@@
 bespoke tooling is unlikely.
-Overall, we showed the need for a new
+Overall, this study showed the need for a new
 generation of generic and automated build log analysis techniques that

### 2020-05-05 tse-paper/paper.tex
mark where we answer RQs 2.x
Add algorithm

@@
 %
-%\usepackage{algorithmic}
+\usepackage{algorithm}% http://ctan.org/pkg/algorithms
+\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
 % algorithmic.sty was written by Peter Williams and Rogerio Brito.
@@
 % http://www.ctan.org/pkg/algorithmicx
+
+\usepackage{etoolbox}
+\algnewcommand\algorithmicforeach{\textbf{for each}}
+\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
+
+\makeatletter
+% start with some helper code
+% This is the vertical rule that is inserted
+\newcommand*{\algrule}[1][\algorithmicindent]{%
+  \makebox[#1][l]{%
+    \hspace*{.2em}% <------------- This is where the rule starts from
+    \vrule height .75\baselineskip depth .25\baselineskip
+  }
+}
+
+\newcount\ALG@printindent@tempcnta
+\def\ALG@printindent{%
+    \ifnum \theALG@nested>0% is there anything to print
+    \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
+    % do nothing
+    \else
+    \unskip
+    % draw a rule for each indent level
+    \ALG@printindent@tempcnta=1
+    \loop
+    \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
+    \advance \ALG@printindent@tempcnta 1
+    \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax
+    \repeat
+    \fi
+    \fi
+}
+% the following line injects our new indent handling code in place of the default spacing
+\patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
+\patchcmd{\ALG@doentity}{\item[]\nointerlineskip}{}{}{} % no spurious vertical space
+% end vertical rule patch for algorithmicx
+\makeatother
 
@@
 \usepackage{multicol}
+\usepackage{multirow}
 \usepackage{booktabs}

### 2020-05-05 tse-paper/content.tex
Cosmetic improvements and consolidation

@@
 
-% TODO Caro: Not 100% sure about the 6. I had a set of rlogs before
+% TODO Caro: Not 100% sure about the 6 in the
+% algorithm below.
+% I had a set of rlogs before
 % that, but then I think you only always retrieve 1 build
-% log. However, I also looked into the LogChunks data set and saw more
+% log.
+% However, I also looked into the LogChunks data set and saw more
 % than 6 logs per project sometimes ...
@@
 \ForEach{technique $\in\{PBE,CTS,KWS,RLR\}$}
- \ForEach{project  $\in$ \emph{LogChunks}} \Comment{$|\emph{LogChunks}|$=80}
+ \ForEach{project  $\in$ \emph{LogChunks}}
+ \Comment{$|\emph{LogChunks}|$=80}
   \For{$i\gets 1, 5$}
-   \State $logs \gets getBuildLogsByTime(project, i)$  \Comment{Logs returned ordered by time of creation.}
+   \State $logs \gets getBuildLogsByTime(project, i)$  \Comment{Logs
+   returned ordered by time of creation.}
    \State $rlog \gets  getBuildLogsByTime(project, 6)$
@@
        \State $retrievedLines \gets run(technique, rlog)$
-       \State $metrics \gets calculateMetrics(retrievedLines, desiredLines(rlog))$
+       \State $metrics \gets calculateMetrics(retrievedLines,
+       desiredLines(rlog))$
        \State
@@
 
-	\caption{Study procedure of the empirical chunk retrieval comparison study.}
+	\caption{Study procedure of the empirical chunk retrieval
+	comparison study.}
 	\label{fig:study}
@@
 and introduce the metrics that
-we measure to answer RQ2. \Cref{fig:study} depicts the individual steps of our study as an algorithmic procedure.
-
-For each chunk retrieval technique and each project, we create training example sets consisting of 1, 2, \dots 5 examples (lines \circlenum{1}--\circlenum{3}).
+we measure to answer RQ2.
+\Cref{fig:study} depicts the individual steps of our study as an
+algorithmic procedure.
+
+For each chunk retrieval technique and each project, we create
+training example sets consisting of 1, 2, \dots 5 examples (lines
+\circlenum{1}--\circlenum{3}).
 We vary the training set size to measure how many examples we need to
@@
 This way, we train on examples from past build logs and test on
-a more recent log, just as one would apply these techniques in the real world.
-
-In line \circlenum{6}, we obtain how many different structural categories are present in the trained logs and store this to be able to answer \textbf{RQ2.2}.
+a more recent log, just as one would apply these techniques in the
+real world.
+
+In line \circlenum{6}, we obtain how many different structural categories
+are present in the trained logs and store this to be able to answer
+\textbf{RQ2.2}.
 
@@
 
-Based on this, we calculate the following metrics in \emph{calculateMetrics}, addressing \textbf{RQ2.3}:
+Based on this, we calculate the following metrics in
+\emph{calculateMetrics}, addressing \textbf{RQ2.3}:
 
@@
 \begin{itemize}[leftmargin=0.4cm] \itemsep1em
-	\item $|\mbox{True\ Positives}| = \mathit{DesiredLines} \cap
-	\mathit{RetrievedLines}$ \vspace{0.2cm}\\
+	\item $|\mbox{True\ Positives}| = \mathit{desiredLines} \cap
+	\mathit{retrievedLines}$ \vspace{0.2cm}\\
 	True positives are lines that appear both in the output of a
@@
 	\item $\mbox{Precision} = \dfrac{|\mathit{True\
-	Positives}|}{|\mathit{RetrievedLines}|}$ \vspace{0.21cm} \\
+	Positives}|}{|\mathit{retrievedLines}|}$ \vspace{0.21cm} \\
 	Precision of a chunk retrieval describes which proportion of
@@
 	\item $\mbox{Recall} =
-	\dfrac{|\mathit{True\ Positives}|}{|\mathit{DesiredLines}|}$
+	\dfrac{|\mathit{True\ Positives}|}{|\mathit{desiredLines}|}$
 	\vspace{0.2cm} \\
@@
 \noindent
-Finally, we aggregate the results to be able to reason per technique \circlenum{15}, completing our study design to answer \textbf{RQ2} overall.
+Finally, we aggregate the results to be able to reason per technique
+\circlenum{15}, completing our study design to answer \textbf{RQ2}
+overall.
 
@@
   \end{lstlisting}
-	\caption{Actual chunk retrieval output ($RetrievedLines$
+	\caption{Actual chunk retrieval output ($retrievedLines$
 	in yellow).}
@@
   \end{lstlisting}
-	\caption{Targeted chunk ($DesiredLines$ in blue).}
+	\caption{Targeted chunk ($desiredLines$ in blue).}
 	\label{lst:pbe-part-success-desired}

### 2020-05-05 tse-paper/content.tex
Optical fine tuning and section renaming.
Align and re-name sub sections (gerund was strange)

@@
 
-\subsubsection{Configuring}
+\subsubsection{Configuration}
 In- and output example pairs are the main driver of PBE;
@@
 
-\subsubsection{Running}
+\subsubsection{Chunk Retrieval Run}
 A run of PBE takes a build log file as input and executes the
@@
 
-\subsubsection{Configuring}
+\subsubsection{Configuration}
 To configure CTS we chose to use the same concept of examples as for
@@
 
-\subsubsection{Running}
+\subsubsection{Chunk Retrieval Run}
 To retrieve the desired information from a build log, we encode every
@@
 
-\subsubsection{Configuring}
+\subsubsection{Configuration}
 A set of keywords configures the chunk retrieval with KWS\@.
@@
 
-\subsubsection{Running}
+\subsubsection{Chunk Retrieval Run}
 For a retrieval run, we take an entire build log file as input and
@@
 
-\section{Empirical Comparison Study}
+\section{Chunk Retrieval Comparison}
 \label{sec:study}
-
-In the literature survey, we noted that previous work seemed to choose
-a log analysis technique arbitrarily and that is a lack of guidance on
-when to use which technique.
-% add (see \Cref{sec:lit-sur:discussion}) ?
-To address this, in this section, we conduct an empirical study
-comparing the three novel chunk retrieval techniques we presented in
-\Cref{sec:techniques}.
-
-In particular, we are interested in how many examples a technique
-should be trained with (\textbf{RQ2.1}),
-how similar the structural representation of the targeted log chunks
-has to be (\textbf{RQ2.2}), and how reliable the quality of the
-produced retrievals is (\textbf{RQ2.3}).
-This leads us to the following research questions:
-
-\begin{simplebox}[minipage boxed title*=-1.5cm,
-attach boxed title to top center={yshift=-6mm}]
-{\textbf{RQ2:} How do build log analysis techniques compare?}
-\begin{itemize}[leftmargin=1.2cm]
-  \item[\textbf{RQ2.1:}] With how many training examples does a
-	technique perform best?
-  \item[\textbf{RQ2.2:}] How structurally variable can training
-  examples be?
-  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
-\end{itemize}
-\end{simplebox}
-
-In the following, we first introduce the data set we created for this
-study, and then describe the study design and its
-results.
-We answer these RQs separately for each technique.
-
-\subsection{LogChunks Data Set}
-\label{sec:logchunks}
-To conduct the study in this paper, we created the
-\emph{LogChunks} data set~\cite{brandt2020logchunks}.
-We collected 797 build logs that
-from 80 GitHub projects and 29
-programming languages on Travis CI, the most-used source of build logs
-according to our literature survey.
-This wide variety of projects and the large number of different build
-tools they employ enables us to measure the generic
-applicability of chunk retrieval techniques.
-
-For each build log in \emph{LogChunks}, we manually marked
-the chunk that describes why the build
-failed---the information targeted by most of the works in our
-literature survey (see \Cref{sec:lit-sur:discussion}).
-To be able to configure the keyword search technique,
-we associated each chunk in the data set with keywords that we
-would use to search for the selected chunk within the log.
-In
-addition, we categorized the log chunks according to their format
-within the log.
-If the chunks were, for example, surrounded by the same markings
-within the log, we assigned them the \emph{same structural category},
-as described in \Cref{sec:crt-example}.
-
-As explained in \Cref{sec:crt-characteristics}, examples are the basic
-unit by which we configure each technique.
-The full build log text,
-the chunk, the search keywords, and the assigned
-structural category make
-up one \emph{example} in \emph{LogChunks}.
-
-\subsection{Procedure}
 
@@
 
-	\caption{Study procedure of the empirical chunk retrieval
-	comparison study.}
+	\caption{Study procedure.}
 	\label{fig:study}
 \end{figure*}
+
+In the literature survey, we noted that previous work seemed to choose
+a log analysis technique arbitrarily and that is a lack of guidance on
+when to use which technique.
+% add (see \Cref{sec:lit-sur:discussion}) ?
+To address this, in this section, we conduct an empirical study
+comparing the three novel chunk retrieval techniques we presented in
+\Cref{sec:techniques}.
+
+In particular, we are interested in how many examples a technique
+should be trained with (\textbf{RQ2.1}),
+how similar the structural representation of the targeted log chunks
+has to be (\textbf{RQ2.2}), and how reliable the quality of the
+produced retrievals is (\textbf{RQ2.3}).
+This leads us to the following research questions:
+
+\begin{simplebox}[minipage boxed title*=-1.5cm,
+attach boxed title to top center={yshift=-6mm}]
+{\textbf{RQ2:} How do build log analysis techniques compare?}
+\begin{itemize}[leftmargin=1.2cm]
+  \item[\textbf{RQ2.1:}] With how many training examples does a
+	technique perform best?
+  \item[\textbf{RQ2.2:}] How structurally variable can training
+  examples be?
+  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
+\end{itemize}
+\end{simplebox}
+
+In the following, we first introduce the data set we created for this
+study, and then describe the study design and its
+results.
+We answer these RQs separately for each technique.
+
+\subsection{LogChunks Data Set}
+\label{sec:logchunks}
+To conduct the study in this paper, we created the
+\emph{LogChunks} data set~\cite{brandt2020logchunks}.
+We collected 797 build logs that
+from 80 GitHub projects and 29
+programming languages on Travis CI, the most-used source of build logs
+according to our literature survey.
+This wide variety of projects and the large number of different build
+tools they employ enables us to measure the generic
+applicability of chunk retrieval techniques.
+
+For each build log in \emph{LogChunks}, we manually marked
+the chunk that describes why the build
+failed---the information targeted by most of the works in our
+literature survey (see \Cref{sec:lit-sur:discussion}).
+To be able to configure the keyword search technique,
+we associated each chunk in the data set with keywords that we
+would use to search for the selected chunk within the log.
+In
+addition, we categorized the log chunks according to their format
+within the log.
+If the chunks were, for example, surrounded by the same markings
+within the log, we assigned them the \emph{same structural category},
+as described in \Cref{sec:crt-example}.
+
+As explained in \Cref{sec:crt-characteristics}, examples are the basic
+unit by which we configure each technique.
+The full build log text,
+the chunk, the search keywords, and the assigned
+structural category make
+up one \emph{example} in \emph{LogChunks}.
+
+\subsection{Study Procedure}
 

### 2020-05-05 tse-paper/content.tex
speaking variable names & consistent cursiveness

@@
 \begin{algorithmic}[1]
-\ForEach{technique $\in\{PBE,CTS,KWS,RLR\}$}
- \ForEach{project  $\in$ \emph{LogChunks}}
+\ForEach{$technique \in\{PBE,CTS,KWS,RLR\}$}
+ \ForEach{$project  \in \emph{LogChunks}$}
  \Comment{$|\emph{LogChunks}|$=80}
-  \For{$i\gets 1, 5$}
-   \State $logs \gets getBuildLogsByTime(project, i)$  \Comment{Logs
+  \For{$i \in\{1,2,3,4,5\}$}
+   \State $training\_logs \gets getBuildLogsByTime(project, 0, i)$
+   \Comment{Logs
    returned ordered by time of creation.}
-   \State $rlog \gets  getBuildLogsByTime(project, 6)$
-   \State $n \gets |structuralCategories(logs)|$
+   \State $test\_log \gets  getBuildLogByTime(project, i)$
+   \State $n \gets |structuralCategories(test\_logs)|$
    \State
-   \State $train(technique, logs)$
-       \State $retrievedLines \gets run(technique, rlog)$
+   \State $train(technique, training\_logs)$
+       \State $retrievedLines \gets run(technique, test\_log)$
        \State $metrics \gets calculateMetrics(retrievedLines,
-       desiredLines(rlog))$
+       desiredLines(test\_log))$
        \State
@@
 
-In the following, we explain our study design
+In the following, we explain our study procedure
 and introduce the metrics that
@@
 We vary the training set size to measure how many examples we need to
-confidently configure a technique, adressing \textbf{RQ2.1}.
+confidently configure a technique, addressing \textbf{RQ2.1}.
 
@@
 on the
-training set, producing the retrieval output \circlenum{9}.
+test set, producing the retrieval output \circlenum{9}.
 

### 2020-05-07 tse-paper/content.tex
remove addressed todo
closes #43 Programming by Example, travis include pacage for algorithm

@@
 \begin{itemize}
-	\item \emph{Program Synthesis by Example (PBE)}, a technique
+	\item \emph{Programming by Example (PBE)}, a technique
 	able to
@@
 \midrule
-Program Synthesis by Example & PBE     & Regular expression program
+Programming by Example & PBE	 & Regular expression program
 & Character   & In/output examples	\\
@@
 a technique based on
-\emph{Program Synthesis by Example (PBE)}.
+\emph{Programming by Example (PBE)}.
 It uses regular expressions internally, while simplifying their
@@
 
-\subsection{Program Synthesis by Example (PBE)}
+\subsection{Programming by Example (PBE)}
 The idea behind \emph{Programming by Example} is to automatically
@@
 
-% TODO Caro: Not 100% sure about the 6 in the
-% algorithm below.
-% I had a set of rlogs before
-% that, but then I think you only always retrieve 1 build
-% log.
-% However, I also looked into the LogChunks data set and saw more
-% than 6 logs per project sometimes ...
-
-% TODO: In addition, if there
-% are more than 6 logs per project, aren't we missing another
-% indirection in the algorithm?
-
 \begin{figure*}[tb]
@@
 
-\subsubsection{Program Synthesis by Example (PBE)}
+\subsubsection{Programming by Example (PBE)}
 \label{sec:r:pbe}
@@
 		\caption{High-level results of chunk retrieval with
-		Program Synthesis by Example (PBE).}
+		Programming by Example (PBE).}
 		\label{fig:failure-reason-PBE}
@@
 \centering
-    \textbf{Program Synthesis by Example (PBE)}\par\medskip
+    \textbf{Programming by Example (PBE)}\par\medskip
 \begin{subfigure}[b]{\columnwidth}
@@
 \end{subfigure}
-\caption{Results of chunk retrieval with Program Synthesis by Example
+\caption{Results of chunk retrieval with Programming by Example
 (PBE).}
@@
 % structural categories are present.
-The figure demonstrates that program synthesis mostly
+The figure demonstrates that programming by example mostly
 returns exactly the desired output when there is only one
@@
 
-\subsubsection{Program Synthesis by Example (PBE)}
+\subsubsection{Programming by Example (PBE)}
 

### 2020-05-07 tse-paper/content.tex
closes #51, closes #49, closes #46

@@
 algorithm weighs the vectors using \emph{term frequency-inverse
-document frequency (TF-IDF)}, a best practice for natural
-language queries~\cite{lee1997document}.
+document frequency (TF-IDF)}, an established technique to give a higher
+impact to words that occur in a smaller number of
+documents~\cite{lee1997document}.
 
@@
 
+The runtime of the evaluation varied from technique to technique.
+The 400 runs of PBE took 19 hours to complete on a dedicated server.
+This is due to the long time needed for the program synthesis to
+complete, which increases the more training examples are used and
+ranges from about 10 to 30 minutes.
+Running a configured technique takes a similar amount of time for all
+techniques.
+Executing the 400 evaluation run for CTS took 15 minutes, for KWS 25
+minutes and for RLR 5 minutes.
+
 \begin{figure}[!t]
@@
 chunk retrieval technique we describe here two concrete examples:
-a software
-team
-wanting to monitor their build performance and a
+a software team monitoring build performance and a
 group of researchers investigating why builds fail.
@@
 They are using
-Travis CI, which measures the duration of build phases and documents
-this within the build log.
-As all log statements that report timing
-measurements are formatted the same way, the targeted log chunks are
-from one structural category.
+Travis CI, which documents the duration of build phases
+within the build log.
+As all relevant log statements are formatted the same way,
+the targeted log chunks are from one structural category.
 Therefore, following the leftmost path in
 \Cref{fig:crt-recommendation},
-the development team should use
-PBE to retrieve the duration of a build phase.
-
-In the second example, a researcher wants to investigate whether
-small or large groups of test cases
-cause CI failures.
-They gather
-CI build logs from various projects.
-Their aim is to extract the names of the
-failing test cases from the build logs.
-When they use the
-decision tree to select a chunk retrieval technique, they
-first have to estimate how uniform the representation of the failing
-test cases is in the investigated build logs.
-As the researchers are
-covering a wide range of test tools, the
-log chunks they target are in various, non-predictable structural
+they should use PBE.
+
+In the second example, researchers wants to investigate the names
+of test cases that cause build failures.
+Their study should cover a wide range of test tools, therefore are the
+log chunks they target in various, non-predictable structural
 representations.
-The next question is whether they value precision
-over recall.
 As they have to manually inspect the results of both CTS
-and KWS, they choose recall over precision to avoid having to inspect
-the whole log in case the relevant chunk---the name of the failing
-test case---was not retrieved.
+and KWS, they prefer higher recall over higher precision to
+avoid inspecting
+the whole log in case the relevant chunk was not retrieved.
 Therefore, following the rightmost path in
@@
 the decision tree recommends the researcher to use KWS\@.
-An
-alternate, potentially more laborious but also more precise solution
-could be for researchers to first separate the CI build logs by the
-test tool responsible for logging the test results.
+
+An alternate, more precise solution
+could be for researchers to first separate the build logs by the
+test tool responsible for logging the results.
 Then, the

### 2020-05-07 tse-paper/content.tex
Fix established technique
Closes #44

@@
 % ----- descriptive / general -----
-Our literature survey shows that despite its relatively young age
-(first mentioned in a paper in 2001, vast majority after
-2016), \emph{build log analysis is already an established technique,}
+Our literature survey shows that \emph{there is a rapidly growing body of works using build log analysis,}
 with 61 works in different venues making use of it for a variety of

### 2020-05-07 tse-paper/content.tex
Extracting
Closes #45

@@
 % ----- descriptive / general -----
-Our literature survey shows that \emph{there is a rapidly growing body of works using build log analysis,}
+Our literature survey shows that \emph{there is a rapidly growing body
+of works using build log analysis,}
 with 61 works in different venues making use of it for a variety of
@@
 parser to analyze the entire structure of build logs, but focus on
-ad hoc extracting just one specific piece of information per
+ad hoc extraction of just one specific information piece per
 configuration.

### 2020-05-07 tse-paper/content.tex
Include why Violin plots
Closes #47

@@
 of these runs compared with the number of examples in the training set.
+We chose violin plots to show spread in distributions of values.
+Specifically, we see an hour glass shape for training set size 1.
+In this case, it means that for recall (and F$_1$-score) there are about as many observations with low recall as there are with high.
+This is a striking difference to set size 2, where we have mostly correct extractions.
 When the training set

### 2020-05-07 tse-paper/content.tex
Lines
Include 80/20
Closes #48

@@
 confidently configure a technique, addressing \textbf{RQ2.1}.
+While this is atypical for an IR-based technique such as CTS---where the default is to split the whole corpus at a given percentage, often 80/20---we did this for the specific task of build logs.
+We want to find out how many examples one has to manually specify with a lot of effort~\Cref{sec:lit-sur:discussion} and at which point techniques become efficient.
 
@@
 Specifically, we see an hour glass shape for training set size 1.
-In this case, it means that for recall (and F$_1$-score) there are about as many observations with low recall as there are with high.
-This is a striking difference to set size 2, where we have mostly correct extractions.
+In this case, it means that for recall (and F$_1$-score) there are about
+as many observations with low recall as there are with high.
+This is a striking difference to set size 2, where we have mostly
+correct extractions.
 When the training set

### 2020-05-08 tse-paper/content.tex
Reformat
Add approaches
Closes #50

@@
 
-To fill this gap, we created three novel, prototypical
-implementations to
-automatically analyze build logs (step \circlenum{2}).
-The ideas behind the implementations are based on promising approaches
-adopted from other research fields and existing build log analysis
-techniques by retrieving a substring (chunk) from the build log:
+To fill this gap, we created three novel, prototypical implementations
+to automatically analyze build logs (step \circlenum{2}) by retrieving a substring (chunk)
+from the build log.  Our
+implementations are based on the most widely used approaches
+from the literature survey and as such, are meant to serve as
+the ``smallest common denominator,'' with as little tuning and optimization as possible to stand protoypical for the ideas they represent:
 \begin{itemize}
@@
 \item a large empirical study comparing the three techniques.
-\item systematic guidelines on when to use which technique.
+\item guidelines on when to use which technique.
 \item a detailed research map to inspire future contributions to the
@@
 particular) inspired the strategies that underlie them.
-\Cref{tab:techniques} summarizes the techniques, which describe in detail
-in the following.
+\Cref{tab:techniques} summarizes the techniques, which we describe here in detail.
 
@@
 the exact failure reasons might differ.
+
+Other techniques, specifically ones based on deep learning, are
+thinkable, but we did not evaluate them in this article since they did
+not emerge from the literature survey. Moreover, they typically
+require lots of training and tuning. However, our premise was to ease
+the creation of build log analysis for developers. First having to
+label thousands of logs on their project before they can start to
+analyze build logs is therfore infeasible. Similarly, as a manual
+effort, the \emph{LogChunks} data set is not big enough to support the
+training of such supervised techniques. Finding a way to train them in
+an unsupervised fashion would rapidly increase their applicability and
+appeal to build log analysis.
 
@@
 confidently configure a technique, addressing \textbf{RQ2.1}.
-While this is atypical for an IR-based technique such as CTS---where the default is to split the whole corpus at a given percentage, often 80/20---we did this for the specific task of build logs.
-We want to find out how many examples one has to manually specify with a lot of effort~\Cref{sec:lit-sur:discussion} and at which point techniques become efficient.
+While this is atypical for an IR-based technique such as CTS---where
+the default is to split the whole corpus at a given percentage, often
+80/20---we did this for the specific task of build logs.
+We want to find out how many examples one has to manually specify with a
+lot of effort~\Cref{sec:lit-sur:discussion} and at which point techniques
+become efficient.
 
@@
 Our study design can be reused to evaluate other build log
-analysis techniques, such as the parser Tomassi et al.
-used to create
+analysis techniques, such as for example deep learning-based techniques (discussed in \Cref{sec:choice}) or manually-written programs such as the parser Tomassi et al.
+created for
 BugSwarm~\cite{tomassi2019bugswarm} or the regex-based approach
 Beller et al.
-used to create TravisTorrent~\cite{beller2017oops}.
+created for TravisTorrent~\cite{beller2017oops}.
 

### 2020-05-08 tse-paper/content.tex
novelty statement, try linebreaks

@@
 To fill this gap, we created three novel, prototypical implementations
-to automatically analyze build logs (step \circlenum{2}) by retrieving a substring (chunk)
-from the build log.  Our
+to automatically analyze build logs (step \circlenum{2}) by retrieving
+a substring (chunk)
+from the build log.
+Our
 implementations are based on the most widely used approaches
 from the literature survey and as such, are meant to serve as
-the ``smallest common denominator,'' with as little tuning and optimization as possible to stand protoypical for the ideas they represent:
+the ``smallest common denominator,'' with as little tuning and
+optimization as possible to stand prototypical for the ideas
+they represent:
 \begin{itemize}
@@
 structure and thus require different bespoke approaches.
-% if included: this explanation is not understandable.
-% It needs to better embedded in the surrounding text
-% One example is comparing execution traces to reference
-% traces of intended behavior to detect anomalies.
-% Amar et
-% al.~\cite{amar2019mining} employed a similar approach to detect
-% relevant lines in build logs.
-% In this article, we focus on extracting a single specified information
-% from the build log as a whole with chunk retrieval techniques.
-% Chunk
-% retrieval techniques are used as a part of log parsing
 
@@
 and that a user can \emph{configure with little effort}.
-
-% In most cases, \emph{researchers analyze build logs from open
-% source projects}, obtained through Travis CI.
-% In addition, we saw several works that targeted the logs of only
-% one specific software project.
-
-% ----- custom build tools -----
-
-% What about the alternate solution, installing plugins to report
-% precise data? Ie., maven plugins
-% - Lots of effort
-% - not a generic solution
-% - how to analyze history where such plugins were not installed
-% - unclear which information you want
-
-% A downside of plugins, which are integrated into the CI flow similar to
-% Deflaker by Bell et al.~\cite{bell2018deflaker}, is that they are unable
-% to work on historic
-% builds, i.e., before the moment they were being deployed and that if
-% information has not been recorded from the beginning but turns out to
-% be important, it is impossible to retrieve later.i
-
-% \textbf{modifying the build output is not helpful}, as well as returning
-% precise data through other documents than the log.
-% This requires access to the build configuration, is also specific to
-% the used build tool and prohibits the analysis of
-% historical data.
-
-% \textbf{ embed custom plugin discussion}
-% %  very disconnected here
-% From this, we follow: 1) there is a niche for custom parsers or even
-% specialized plugins integrated into the build process to make
-% post-factum
-% parsing of logs redundant.
-% Plugins  similar to, for example, the Maven plugin to report test
-% executions Bell et al.
-% % cite
-% wrote, have the disadvantage of not being able to work on historic
-% builds.
-% 2) the large tail of seldomly-investigated environments would benefit
-% from the existence of a more generic
-% solution.
-
-% We implement build tool agnostic build log analysis
-% techniques, which are customized to a specific project by
-% the training examples which the user provides.
-% In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
-% data set we chose for our evaluation covers a broad range of build
-% environments.
-% % Further, the training examples also specify the log chunk targeted
-% by the
-% % retrieval, which enable our chunk retrieval techniques to retrieve
-% % a broad range of information from build logs.
-
-% This task of retrieving specific chunks of text from the
-% build logs can be solved by the chunk retrieval techniques we compare
-% in this article.
-% Our results can support researchers in choosing a
-% suitable technique for their data set of build logs and the chunks
-% they want to retrieve.
-% By relieving them from building custom parsers
-% we enable them to cover a much wider range of languages and build
-% tools in their studies.
-
-% Alt:
-%\section{Analyzing Build Logs with Chunk Retrieval Techniques}
 \section{Chunk Retrieval Techniques}
 \label{sec:techniques}
-% tense: past? except for general definitions / statements
 
@@
 we implemented and evaluated for this study.
-
-% TOO Caro: Not sure what to do with this ...
-%% In this section,
-%% we propose three so-called \emph{chunk retrieval techniques},
-%% which retrieve a specific substring (chunk)
-%% from a build log
-%% % TOO passive ....
-%% The techniques we propose run automatically
-%% and can be easily configured through examples.
-%% % TOO this should go under characteristics and not be in an
-% introduction
-%% to the section ...
-%% An example in this case consists of a build log together with the
-%% chunk that should be retrieved.
-%% A user---a developer or a researcher who wants to analyze
-%% build logs---provides these examples, which are easy to
-%% adapt whenever the analysis technique needs
-%% to support new cases.
 
@@
 particular) inspired the strategies that underlie them.
-\Cref{tab:techniques} summarizes the techniques, which we describe here in detail.
+\Cref{tab:techniques} summarizes the techniques, which we describe here
+in detail.
 
@@
 thinkable, but we did not evaluate them in this article since they did
-not emerge from the literature survey. Moreover, they typically
-require lots of training and tuning. However, our premise was to ease
-the creation of build log analysis for developers. First having to
+not emerge from the literature survey.
+Moreover, they typically
+require lots of training and tuning.
+However, our premise was to ease
+the creation of build log analysis for developers.
+First having to
 label thousands of logs on their project before they can start to
-analyze build logs is therfore infeasible. Similarly, as a manual
+analyze build logs is therefore infeasible.
+Similarly, as a manual
 effort, the \emph{LogChunks} data set is not big enough to support the
-training of such supervised techniques. Finding a way to train them in
+training of such supervised techniques.
+Finding a way to train them in
 an unsupervised fashion would rapidly increase their applicability and
@@
 Our study design can be reused to evaluate other build log
-analysis techniques, such as for example deep learning-based techniques (discussed in \Cref{sec:choice}) or manually-written programs such as the parser Tomassi et al.
+analysis techniques, such as for example deep learning-based
+techniques (discussed in \Cref{sec:choice}) or manually-written
+programs such as the parser Tomassi et al.
 created for

### 2021-02-16 tse-paper/paper_old_tse.tex
moving template tse → emse

--- 2020-05-08 tse-paper/content.tex
@@
+%% bare_jrnl_compsoc.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% Computer Society journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress]{cite}
+\else
+  % normal IEEE
+  \usepackage[noadjust]{cite}
+\fi
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+%
+% Note that some packages require special options to format as the Computer
+% Society requires. In particular, Computer Society  papers do not use
+% compressed citation ranges as is done in typical IEEE papers
+% (e.g., [1]-[4]). Instead, they list every citation separately in order
+% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
+% package with the nocompress option which is supported by cite.sty v4.0
+% and later. Note also the use of a CLASSOPTION conditional provided by
+% IEEEtran.cls V1.7 and later.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+%\usepackage{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
+%
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+\usepackage{algorithm}% http://ctan.org/pkg/algorithms
+\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
+
+\usepackage{etoolbox}
+\algnewcommand\algorithmicforeach{\textbf{for each}}
+\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
+
+\makeatletter
+% start with some helper code
+% This is the vertical rule that is inserted
+\newcommand*{\algrule}[1][\algorithmicindent]{%
+  \makebox[#1][l]{%
+    \hspace*{.2em}% <------------- This is where the rule starts from
+    \vrule height .75\baselineskip depth .25\baselineskip
+  }
+}
+
+\newcount\ALG@printindent@tempcnta
+\def\ALG@printindent{%
+    \ifnum \theALG@nested>0% is there anything to print
+    \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
+    % do nothing
+    \else
+    \unskip
+    % draw a rule for each indent level
+    \ALG@printindent@tempcnta=1
+    \loop
+    \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
+    \advance \ALG@printindent@tempcnta 1
+    \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax
+    \repeat
+    \fi
+    \fi
+}
+% the following line injects our new indent handling code in place of the default spacing
+\patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
+\patchcmd{\ALG@doentity}{\item[]\nointerlineskip}{}{}{} % no spurious vertical space
+% end vertical rule patch for algorithmicx
+\makeatother
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a sans serif font rather
+% than the serif font used in traditional IEEE formatting and thus the need
+% to invoke different subfig.sty package options depending on whether
+% compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
+% Axel Sommerfeldt. This package may be useful when used in conjunction with 
+% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
+% submissions have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.4.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/pkg/endfloat
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
+
+\usepackage[dvipsnames]{xcolor}
+\usepackage{tabularx}
+\usepackage{multicol}
+\usepackage{multirow}
+\usepackage{booktabs}
+\renewcommand{\arraystretch}{1.4}
+\usepackage{makecell}
+\usepackage{relsize}
+
+\usepackage[most]{tcolorbox}
+\newtcolorbox{simplebox}[2][]{enhanced,
+    minipage boxed title*,
+    sharp corners,
+    colback=white,
+    colbacktitle=white,
+    coltitle=black,
+    boxrule=1pt,
+    left=5mm,
+    right=5mm,
+    bottom=2mm,
+    top=4mm,
+    boxed title style={colframe=white},
+    attach boxed title to top center={yshift=-3mm},
+    center title,
+    title=#2,#1}
+
+\usepackage[hidelinks,bookmarks=false]{hyperref}
+\usepackage{cleveref}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{mdframed}
+\usepackage{enumitem}
+
+\newcommand{\smallish}{\fontsize{6.15pt}{20pt}\selectfont}
+\newcommand{\tinyish}{\fontsize{6.4pt}{6.15pt}\selectfont}
+\newcommand\circlenum[1]{\raisebox{1.2pt}{\textcircled{\hspace{0.35pt}\scriptsize{\raisebox{-.4pt}{#1}}}}}
+%\newcommand{\circlenum}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
+\begin{document}
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
+
+\title{How to Analyze Build Logs---A~Systematic Survey and Comparative Study of Chunk~Retrieval~Techniques}
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
+%
+%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
+% lists the Computer Society journals use for "first footnote" author
+% affiliations. Use \IEEEcompsocthanksitem which works much like \item
+% for each affiliation group. When not in compsoc mode,
+% \IEEEcompsocitemizethanks becomes like \thanks and
+% \IEEEcompsocthanksitem becomes a line break with idention. This
+% facilitates dual compilation, although admittedly the differences in the
+% desired content of \author between the different types of papers makes a
+% one-size-fits-all approach a daunting prospect. For instance, compsoc 
+% journal papers have the author affiliations above the "Manuscript
+% received ..."  text while in non-compsoc journals this is reversed. Sigh.
+
+\author{Carolin~E.~Brandt, %~\IEEEmembership{Member,~IEEE,}
+        Moritz~Beller%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
+% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
+% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
+% GA, 30332.\protect\\
+% % note need leading \protect in front of \\ to get a newline within \thanks as
+% % \\ is fragile and will error, could use \hfil\break instead.
+% E-mail: see http://www.michaelshell.org/contact.html
+% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
+\thanks{Manuscript received May 8, 2020.}}
+
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+% 
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~14, No.~8, August~2015}%
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% The publisher's ID mark at the bottom of the page is less important with
+% Computer Society journal papers as those publications place the marks
+% outside of the main text columns and, therefore, unlike regular IEEE
+% journals, the available text space is not reduced by their presence.
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+% or like this to get the Computer Society new two part style.
+%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
+%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark (Computer Society jorunal
+% papers don't need this extra clearance.)
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% for Computer Society papers, we must declare the abstract and index terms
+% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
+% command as these need to go into the title area created by \maketitle.
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
+\IEEEtitleabstractindextext{%
+\begin{abstract}
+Build logs are the textual by-products that automatic software build processes
+create, often as part of their Continuous Integration (CI)
+pipeline.
+Build logs can serve as a paramount source of
+information for developers to understand and debug dependency, compilation, or
+test failures.
+Manually
+extracting the important chunks of information in a build log, though, is akin to
+finding a needle in a haystack.
+Recently, practitioners and researchers have started attempts to partly
+automate
+this time-consuming activity, to not only ease
+developers' debugging task but also to enable a novel class of
+automated onward processing applications.
+In this paper, we give a systematic overview of the emerging field of build log analysis.
+In a broad literature mapping survey, we first survey and categorize the existing methods to
+extract information chunks from build logs.
+In the second part of the paper, we then develop prototypical implementations of three promising
+techniques to analyze build logsx, namely program synthesis
+by example, textual similarity, and keyword search.
+Finally, we evaluate the techniques in an empirical study on
+almost 800 build logs 
+from a wide range of different projects and programming languages.
+Our findings show that none of the three techniques in general outperforms
+the others, but rather, that each technique has its respective strengths
+and weaknesses.
+We discuss under which circumstances each technique performs best
+and provide a recommendation scheme for when developers or researchers might 
+use which technique.
+We close with a roadmap of important open problems in the field of
+build log analysis.
+\end{abstract}
+
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+Build Log Analysis, Chunk Retrieval, Continuous Integration
+\end{IEEEkeywords}}
+
+% make the title area
+\maketitle
+
+% To allow for easy dual compilation without having to reenter the
+% abstract/keywords data, the \IEEEtitleabstractindextext text will
+% not be used in maketitle, but will appear (i.e., to be "transported")
+% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
+% or transmag modes are not selected <OR> if conference mode is selected 
+% - because all conference papers position the abstract like regular
+% papers do.
+\IEEEdisplaynontitleabstractindextext
+% \IEEEdisplaynontitleabstractindextext has no effect when using
+% compsoc or transmag under a non-conference mode.
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
+\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
+% Computer Society journal (but not conference!) papers do something unusual
+% with the very first section heading (almost always called "Introduction").
+% They place it ABOVE the main text! IEEEtran.cls does not automatically do
+% this for you, but you can achieve this effect with the provided
+% \IEEEraisesectionheading{} command. Note the need to keep any \label that
+% is to refer to the section immediately after \section in the above as
+% \IEEEraisesectionheading puts \section within a raised box.
+
+% The very first letter is a 2 line initial drop letter followed
+% by the rest of the first word in caps (small caps for compsoc).
+% 
+% form to use if the first word consists of a single letter:
+% \IEEEPARstart{A}{demo} file is ....
+% 
+% form to use if you need the single drop letter followed by
+% normal text (unknown if ever used by the IEEE):
+% \IEEEPARstart{A}{}demo file is ....
+% 
+% Some journals put the first two words in caps:
+% \IEEEPARstart{T}{his demo} file is ....
+% 
+% Here we have the typical use of a "T" for an initial drop letter
+% and "HIS" in caps to complete the first word.
+% \IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
+% for IEEE Computer Society journal papers produced under \LaTeX\ using
+% IEEEtran.cls version 1.8b and later.
+% % You must have at least 2 lines in the paragraph with the drop letter
+% % (should never be an issue)
+% I wish you the best of success.
+
+% \hfill mds
+
+% \hfill August 26, 2015
+
+% \subsection{Subsection Heading Here}
+% Subsection text here.
+
+% % needed in second column of first page if using \IEEEpubid
+% %\IEEEpubidadjcol
 %\section{introduction}
@@
 techniques.
-Executing the 400 evaluation run for CTS took 15 minutes, for KWS 25
+Executing the 400 evaluation runs for CTS took 15 minutes, for KWS 25
 minutes and for RLR 5 minutes.
@@
 in build logs.
+
+% An example of a floating figure using the graphicx package.
+% Note that \label must occur AFTER (or within) \caption.
+% For figures, \caption should occur after the \includegraphics.
+% Note that IEEEtran v1.7 and later has special internal code that
+% is designed to preserve the operation of \label within \caption
+% even when the captionsoff option is in effect. However, because
+% of issues like this, it may be the safest practice to put all your
+% \label just after \caption rather than within \caption{}.
+%
+% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
+% option should be used if it is desired that the figures are to be
+% displayed while in draft mode.
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=2.5in]{myfigure}
+% where an .eps filename suffix will be assumed under latex, 
+% and a .pdf suffix will be assumed for pdflatex; or what has been declared
+% via \DeclareGraphicsExtensions.
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure}
+
+% Note that the IEEE typically puts floats only at the top, even when this
+% results in a large percentage of a column being occupied by floats.
+% However, the Computer Society has been known to put floats at the bottom.
+
+% An example of a double column floating figure using two subfigures.
+% (The subfig.sty package must be loaded for this to work.)
+% The subfigure \label commands are set within each subfloat command,
+% and the \label for the overall figure must come after \caption.
+% \hfil is used as a separator to get equal spacing.
+% Watch out that the combined width of all the subfigures on a 
+% line do not exceed the text width or a line break will occur.
+%
+%\begin{figure*}[!t]
+%\centering
+%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
+%\label{fig_first_case}}
+%\hfil
+%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
+%\label{fig_second_case}}
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure*}
+%
+% Note that often IEEE papers with subfigures do not employ subfigure
+% captions (using the optional argument to \subfloat[]), but instead will
+% reference/describe all of them (a), (b), etc., within the main caption.
+% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
+% labels, the optional argument to \subfloat must be present. If a
+% subcaption is not desired, just leave its contents blank,
+% e.g., \subfloat[].
+
+% An example of a floating table. Note that, for IEEE style tables, the
+% \caption command should come BEFORE the table and, given that table
+% captions serve much like titles, are usually capitalized except for words
+% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
+% and up, which are usually not capitalized unless they are the first or
+% last word of the caption. Table text will default to \footnotesize as
+% the IEEE normally uses this smaller font for tables.
+% The \label must come after \caption as always.
+%
+%\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+%\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+%\caption{An Example of a Table}
+%\label{table_example}
+%\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+%\begin{tabular}{|c||c|}
+%\hline
+%One & Two\\
+%\hline
+%Three & Four\\
+%\hline
+%\end{tabular}
+%\end{table}
+
+% Note that the IEEE does not put floats in the very first column
+% - or typically anywhere on the first page for that matter. Also,
+% in-text middle ("here") positioning is typically not used, but it
+% is allowed and encouraged for Computer Society conferences (but
+% not Computer Society journals). Most IEEE journals/conferences use
+% top floats exclusively. 
+% Note that, LaTeX2e, unlike IEEE journals/conferences, places
+% footnotes above bottom floats. This can be corrected via the
+% \fnbelowfloat command of the stfloats package.
+
+% \section{Conclusion}
+% The conclusion goes here.
+
+% if have a single appendix:
+%\appendix[Proof of the Zonklar Equations]
+% or
+%\appendix  % for no appendix heading
+% do not use \section anymore after \appendix, only \section*
+% is possibly needed
+
+% use appendices with more than one appendix
+% then use \section to start each appendix
+% you must declare a \section before using any
+% \subsection or using \label (\appendices by itself
+% starts a section numbered zero.)
+%
+
+% \appendices
+% \section{Proof of the First Zonklar Equation}
+% Appendix one text goes here.
+
+% % you can choose not to have a title for an appendix
+% % if you want by leaving the argument blank
+% \section{}
+% Appendix two text goes here.
+
+% use section* for acknowledgment
+% \ifCLASSOPTIONcompsoc
+%   % The Computer Society usually uses the plural form
+%   \section*{Acknowledgments}
+% \else
+%   % regular IEEE prefers the singular form
+%   \section*{Acknowledgment}
+% \fi
+
+% The authors would like to thank...
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+\bibliography{paper}
+
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+% \begin{IEEEbiography}{Carolin E. Brandt}
+% Biography text here.
+% \end{IEEEbiography}
+
+% \begin{IEEEbiography}{Moritz Beller}
+% Biography text here.
+% \end{IEEEbiography}
+
+% if you will not have a photo at all:
+% \begin{IEEEbiographynophoto}{John Doe}
+% Biography text here.
+% \end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+% \begin{IEEEbiographynophoto}{Jane Doe}
+% Biography text here.
+% \end{IEEEbiographynophoto}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
+% that's all folks
+\end{document}

### 2021-02-17 tse-paper/paper.tex
closes #53
Title
Closes #52
cite → citep

@@
-%% bare_jrnl_compsoc.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% Computer Society journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[10pt,journal,compsoc]{IEEEtran}
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
 %
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
+% This is a general template file for the LaTeX package SVJour3
+% for Springer journals.          Springer Heidelberg 2010/09/16
 %
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
+% Copy it to a new file with a new name and use it as the basis
+% for your article. Delete % signs as needed.
 %
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
-  \usepackage[noadjust]{cite}
-\fi
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
+% This template includes a few options for different layouts and
+% content for various journals. Please consult a previous issue of
+% your journal as needed.
 %
-% Note that some packages require special options to format as the Computer
-% Society requires. In particular, Computer Society  papers do not use
-% compressed citation ranges as is done in typical IEEE papers
-% (e.g., [1]-[4]). Instead, they list every citation separately in order
-% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
-% package with the nocompress option which is supported by cite.sty v4.0
-% and later. Note also the use of a CLASSOPTION conditional provided by
-% IEEEtran.cls V1.7 and later.
-
-% *** GRAPHICS RELATED PACKAGES ***
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-\ifCLASSINFOpdf
-  \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
+% First comes an example EPS file -- just ignore it and
+% proceed on the \documentclass line
+% your LaTeX will extract the file if required
+\begin{filecontents*}{example.eps}
+%!PS-Adobe-3.0 EPSF-3.0
+%%BoundingBox: 19 19 221 221
+%%CreationDate: Mon Sep 29 1997
+%%Creator: programmed by hand (JK)
+%%EndComments
+gsave
+newpath
+  20 20 moveto
+  20 220 lineto
+  220 220 lineto
+  220 20 lineto
+closepath
+2 setlinewidth
+gsave
+  .4 setgray fill
+grestore
+stroke
+grestore
+\end{filecontents*}
 %
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
+\RequirePackage{fix-cm}
 %
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[smallextended,
+  envcountsect,]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
 %
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
+\smartqed  % flush right qed marks, e.g. at end of proof
 %
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
+\usepackage{graphicx}
 %
+% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
+%\usepackage{latexsym}
+% etc.
+
+% algorithmic from the tse template:
 \usepackage{algorithm}% http://ctan.org/pkg/algorithms
@@
 
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a sans serif font rather
-% than the serif font used in traditional IEEE formatting and thus the need
-% to invoke different subfig.sty package options depending on whether
-% compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
 \usepackage[dvipsnames]{xcolor}
@@
 \usepackage{enumitem}
+\usepackage{natbib}
 
@@
 \newcommand\circlenum[1]{\raisebox{1.2pt}{\textcircled{\hspace{0.35pt}\scriptsize{\raisebox{-.4pt}{#1}}}}}
-%\newcommand{\circlenum}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
+
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
+%
+% Insert the name of "your journal" with
+% \journalname{myjournal}
+%
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-
-\title{How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-%
-%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
-% lists the Computer Society journals use for "first footnote" author
-% affiliations. Use \IEEEcompsocthanksitem which works much like \item
-% for each affiliation group. When not in compsoc mode,
-% \IEEEcompsocitemizethanks becomes like \thanks and
-% \IEEEcompsocthanksitem becomes a line break with idention. This
-% facilitates dual compilation, although admittedly the differences in the
-% desired content of \author between the different types of papers makes a
-% one-size-fits-all approach a daunting prospect. For instance, compsoc 
-% journal papers have the author affiliations above the "Manuscript
-% received ..."  text while in non-compsoc journals this is reversed. Sigh.
-
-\author{Carolin~E.~Brandt, %~\IEEEmembership{Member,~IEEE,}
-        Moritz~Beller%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
-% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
-% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-% GA, 30332.\protect\\
-% % note need leading \protect in front of \\ to get a newline within \thanks as
-% % \\ is fragile and will error, could use \hfil\break instead.
-% E-mail: see http://www.michaelshell.org/contact.html
-% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
-\thanks{Manuscript received May 1, 2020; revised August 26, 2015.}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~14, No.~8, August~2015}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% The publisher's ID mark at the bottom of the page is less important with
-% Computer Society journal papers as those publications place the marks
-% outside of the main text columns and, therefore, unlike regular IEEE
-% journals, the available text space is not reduced by their presence.
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% or like this to get the Computer Society new two part style.
-%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
-%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark (Computer Society jorunal
-% papers don't need this extra clearance.)
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% for Computer Society papers, we must declare the abstract and index terms
-% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
-% command as these need to go into the title area created by \maketitle.
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\IEEEtitleabstractindextext{%
+
+\title{How to Analyze Build Logs%\thanks{Grants or other notes
+%about the article that should go on the front page should be
+%placed here. General acknowledgments should be placed at the end of the article.}
+}
+\subtitle{A~Systematic Survey and Comparative Study of Chunk~Retrieval~Techniques}
+
+%\titlerunning{Short form of title}        % if too long for running head
+
+\author{Carolin~Brandt        \and
+        Moritz~Beller %etc.
+}
+
+%\authorrunning{Short form of author list} % if too long for running head
+
+\institute{Carolin Brandt \at
+              Delft University of Technology \\
+              % Tel.: +123-45-678910\\
+              % Fax: +123-45-678910\\
+              \email{c.e.brandt@tudelft.nl}           %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+           \and
+           Moritz Beller \at
+              Facebook \\
+              \email{moritz.beller@gmail.com}
+}
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
+
+\maketitle
+
 \begin{abstract}
@@
 build log analysis.
+\keywords{Build Log Analysis \and Chunk Retrieval \and Continuous Integration}
 \end{abstract}
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Build Log Analysis, Chunk Retrieval, Continuous Integration
-\end{IEEEkeywords}}
-
-% make the title area
-\maketitle
-
-% To allow for easy dual compilation without having to reenter the
-% abstract/keywords data, the \IEEEtitleabstractindextext text will
-% not be used in maketitle, but will appear (i.e., to be "transported")
-% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
-% or transmag modes are not selected <OR> if conference mode is selected 
-% - because all conference papers position the abstract like regular
-% papers do.
-\IEEEdisplaynontitleabstractindextext
-% \IEEEdisplaynontitleabstractindextext has no effect when using
-% compsoc or transmag under a non-conference mode.
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
+\lstset{
+  morekeywords={},
+	basicstyle=\ttfamily\scriptsize,
+  postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space},
+  showspaces=false,
+  showstringspaces=false,
+  stringstyle=\color{Plum},
+	frame=single,
+  extendedchars=false,
+  texcl=false,
+  aboveskip=\baselineskip,
+  belowskip=0pt
+}
+
+\section{Introduction}\label{sec:introduction}
+In the past two decades, Continuous Integration (CI) has become a
+ubiquitous best practice to streamline the build process of software
+projects~\citep{hilton2016usage,beller2017oops,staahl2014modeling}.
+Build logs are a textual by-product that these automatic software
+builds create.
+As a treasure trove of information~\citep{meyer},
+build logs contain trace outputs of not only the elementary steps to
+``make'' a project---such as retrieving and resolving dependencies and
+compiling---but also about ancillary quality assurance steps---such as
+testing the software and running automated static analysis
+tools~\citep{beller2017oops}.
+The
+contents and format of build logs can vary highly depending on which tools
+are involved in the build process, how they are
+configured, and as projects and build tools evolve over
+time~\citep{staahl2014modeling}.
+Typically, though, they are at least a semi-structured and
+somewhat stable journal of the commands executed during the build and
+their results.
+
+When a build or one of its steps fails, developers typically scavenge
+the logs for information related to the source of the error.
+This
+manual activity is tedious and prone to
+errors~\citep{santolucito2018statically}.
+As a single build log can be
+over 50 megabytes large~\citep{beller2017oops}, finding the small chunk
+of information linked to the actual error, is akin to
+searching for a needle in a haystack.
+The large number of unrelated, but ambiguous
+warnings which many build
+logs regularly contain further compounds this problem.
+In addition to helping
+understand and fix build failures, the information richness of build
+logs enables a plethora of other applications: with the help of build
+logs, we can better understand and categorize CI failures and compile
+errors~\citep{islam2017insights,seo2014programmers}, differentiate
+testing practices~\citep{orellana2017differences,vassallo2017a-tale},
+train classifiers to do ``predictive CI'' on the build or test outcome
+and
+duration~\citep{ni2017cost,bisong2017built,haghighatkhah2018test,
+machalica2019predictive},
+or investigate the role of automated static analysis tools (ASATs)
+in CI
+builds~\citep{zampetti2017open}.
+
+However, manual analysis of build logs does not
+scale to the number of build logs and amount of information that such
+sophisticated applications require.
+Moreover, being able to
+automatically extract relevant pieces of information from build logs
+can help
+developers debug a broken build more quickly without having to browse
+the entire build log.
+
+\begin{figure*}[htb]
+	\centering
+	\includegraphics[width=\textwidth, trim={1.2cm 10.5cm 1.2cm 0cm},
+	clip]{img/overview.pdf}
+	\caption{Research design.}
+	\label{fig:overview}
+\end{figure*}
+
+Retrospectively analyzing the build logs is not the only solution to
+the problem---an alternate would be to integrate live plugins into the
+build process
+ such as the JUnit
+plugin for Jenkins~\citep{jenkins2020junit-plugin} or
+Deflaker by Bell et al.~\citep{bell2018deflaker}.
+
+Their advantage is that they can precisely report the information which
+is required.
+However, such plugins are not available for all build tools, they are
+non-trivial to implement one-off solutions, and they
+do not enable the analysis of historical builds.
+When using such a plugin, one has to decide
+beforehand which information should be reported, whereas
+build log analysis enables us to leverage all information
+present in the build logs.
+Moreover, build log analysis is the more general solution.
+While they serve an important niche, custom plugins do not make build
+log analysis redundant.
+
+Despite its central role in helping developers and in enabling
+novel, onward processing applications,
+the process of how to
+automatically
+analyze build logs has thus far not been systematically
+overviewed as a research topic, bringing us to the first
+research question:
+\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
+1}}
+What is the state-of-research to analyze build logs?
+\end{simplebox}
+
+To answer this question, we start the investigation in this
+paper---pictured in
+\Cref{fig:overview}---with an
+extensive literature survey (step \circlenum{1}).
+The survey identifies various strategies to
+analyze build logs, among which are developing
+custom parsers, using regular expressions, doing manual inspections,
+searching for keywords, or performing natural language processing.
+
+However, it also identifies that there is currently no guidance on when
+to use which of these
+approaches.
+Unfortunately, our survey also shows that
+less than half of the 61 works which rely on build log analysis
+describe it in sufficient detail and that
+the few available implementations are all based on either a custom parser
+or regular expressions.
+These two approaches are problematic, as their creation
+and maintenance is manual and expensive, does not generalize across build
+logs from different build tools, and is prone to errors,
+as the experience of
+TravisTorrent has
+shown~\citep{beller2017travistorrent,travistorrentquestions}.
+In fact, some even ``strongly discourage'' the creation of such
+parsers~\citep{urli2018design}.
+In summary, the outcome of our literature survey shows the need for a new
+generation of automated techniques to analyze build logs, which are
+openly available and documented in detail, together with
+guidance on when to use which technique.
+
+To fill this gap, we created three novel, prototypical implementations
+to automatically analyze build logs (step \circlenum{2}) by retrieving
+a substring (chunk)
+from the build log.
+Our
+implementations are based on the most widely used approaches
+from the literature survey and as such, are meant to serve as
+the ``smallest common denominator,'' with as little tuning and
+optimization as possible to stand prototypical for the ideas
+they represent:
+\begin{itemize}
+	\item \emph{Programming by Example (PBE)}, a technique
+	able to
+	automatically synthesize regular expressions,
+	\item a technique based on information
+	retrieval, which we call \emph{Common Text Similarity (CTS)},
+	\item inspired by the manual ad hoc search for key parts in the
+	log, a
+	technique employing \emph{Keyword Search (KWS)}.
+\end{itemize}
+
+These three approaches have
+different strengths and weaknesses.
+As a consequence,
+in the second research question we ask:
+
+\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
+2}}
+How do build log analysis techniques compare?
+\end{simplebox}
+
+To answer this question
+we conduct an empirical study assessing the performance
+of these chunk retrieval techniques in
+real-world projects under a variety of conditions (step \circlenum{3}).
+The study is based on the \emph{LogChunks} data
+set~\citep{brandt2020logchunks}, which encompasses 797 build logs from
+80 popular open-source projects and a broad range of different
+build tools and programming languages.
+Our results show that all of the three techniques
+clearly surpass a random baseline, but have different strengths and
+weaknesses.
+There is no technique that in general outperforms
+the others.
+PBE has the best average precision of 95\%, while KWS has the highest
+recall with 70\% on average.
+However, CTS shows the best F$_{1}$-score
+of 51\%.
+
+Due to this ambiguity, we develop a set of guidelines
+on how to choose the most suitable build log analysis
+technique for the task at hand (step \circlenum{4}).
+We recommend PBE for use cases where the desired information is always
+represented in the same structural way and high confidence in
+precision and recall of the chunk retrieval is required.
+The results PBE produces are suited for automatic onward processing.
+CTS is
+well-suited when the representation of the desired information varies
+slightly and the output of the chunk retrieval is further processed by
+a human.
+In cases where the textual representation of the desired
+information in the log is unpredictable or varies greatly, KWS seems
+to be the best choice.
+However, its low precision---it extracts a
+context of multiple lines around a found keyword---makes it generally
+unsuited for automatic onward processing.
+Instead, KWS requires a human
+to further inspect and interpret the output chunk.
+A hybrid solution combining the three techniques might be the best
+all-round solution.
+Finally, we give a roadmap to guide future research in the field
+of build log analysis.
+
+In short, this article contributes
+\begin{itemize}
+\item the first systematic survey of the emerging field of build log
+analysis.
+\item three prototypical open-sourced implementations of
+promising chunk retrieval techniques.
+\item a large empirical study comparing the three techniques.
+\item guidelines on when to use which technique.
+\item a detailed research map to inspire future contributions to the
+field.
+\item a documented replication package~\citep{brandt2020chunk-replication}.
+\end{itemize}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
+	\caption{Literature selection (following Petersen et
+	al.~\citep{petersen2015guidelines}).}
+	\label{fig:lit-survey}
+\end{figure}
+
+\section{Systematic Literature Mapping Survey}
+\label{sec:survey}
+% tense: past
+
+In this section, we report on the state-of-research in the emerging
+field of build log analysis by means of a systematic mapping study.
+We start with a differentiation of build log analysis
+from the older field of
+system log analysis.
+% ref to fig 2 so it can be here and above fig 3
+Then, we describe the methodology (\Cref{fig:lit-survey})
+and results of our systematic mapping
+survey following the
+guidelines by Petersen et
+al.~\citep{petersen2008systematic,petersen2015guidelines}.
+% We close by summarizing how build logs are commonly
+% analyzed in literature and discuss the implications of these findings.
+
+\lstset{
+  morekeywords={INFO, WARN, 2008, 11, 09},
+  alsoletter=-20819,
+  keywordstyle=\bfseries\color{Plum},
+  escapeinside=**
+}
+\begin{figure}[b]
+  \centering
+  \lstinputlisting[breaklines=true]{listings/syslog.txt}
+  \caption{System log excerpt (adapted from He et
+  al.~\citep{he2017towards}).}
+  \label{lst:system-log}
+\end{figure}
+
+\subsection{Distinction from System Log Analysis}
+\label{sec:system-log-analysis}
+% tense: present
+
+A field related to build log analysis is the analysis of system logs.
+These system logs are produced during the runtime of a system, while
+build logs are produced during the runtime of the build of the system.
+In terms of the contents of the logs, the main difference is that system
+logs are fundamentally structured
+through events.
+Each line in a log file represents one event with a
+set of fields: timestamp, verbosity level, and raw message
+content~\citep{he2017towards}.
+\Cref{lst:system-log} depicts two
+exemplary lines from such a system log.
+
+When analyzing system log files, the first goal is generally to
+separate the constant and variable parts within a log
+message~\citep{nagappan2010abstracting,he2017towards}.
+Next, the log
+messages are clustered into log events, unifying messages with
+identical constant parts and varying parameters.
+The output is an
+ordered list of timed events and their corresponding parameter
+values~\citep{he2016evaluation}.
+This structured log can serve as
+input to various machine learning and data mining processes.
+Apart
+from a large body of research on system logs, an equally mature amount
+of commercial-grade and
+open source tooling exists to analyze system logs---such as, for
+example, Elasticsearch, Logstash and Kibana (the so-called ELK
+stack)~\citep{sanjappa2017analysis,bajer2017building}.
+
+Some of the techniques developed to parse system logs can operate
+on build logs as well, such as approaches to retrieve the
+values of variable parts in a log message, e.g.\, by using regular
+expressions~\citep{nagappan2010abstracting,xu2009detecting}.
+% This is the easiest example matching here
+% amar et al are not in our literature survey
+However, the number of
+system logs generated mandates that scalability and efficiency play a
+much more important role than for build logs.
+In addition, almost all of the techniques developed to analyze system logs
+leverage their inherent event structure.
+Build logs generally lack this
+structure and thus require different bespoke approaches.
+
+\subsection{Literature Selection}
+\label{sec:litsel}
+% tense: past
+
+The first step in a systematic literature survey is to
+establish which works one wants to cover and how to find
+them~\citep{kitchenham2009systematic}.
+Since the field of build log analysis is relatively young, we
+surveyed as broad a population of scientific material as possible.
+We did not limit the sources to specific Software Engineering
+venues~\citep{petersen2015guidelines}, but included all sources
+monitored by Google Scholar, including Bachelor's theses, Master's
+theses, and academic slide decks.
+We use Google Scholar as opposed to Scopus or
+other databases because it is the search engine for scholarly material
+with
+the broadest and most current index, including preprints.
+
+\Cref{fig:lit-survey} gives an overview of the literature selection
+process.
+An initial Google Scholar search for ``build log''
+returned more than 2.2 million results on the 15th of March 2020, many
+of which stem
+from unrelated fields such as construction or wood working.
+We refined the search criteria to exclude such obvious
+non-related fields and to exclude works on system
+logs (see \Cref{sec:system-log-analysis}).
+This left us with 1,552 search results.
+% Our replication package documents the full search
+% queries~\citep{brandt2020chunk-replication}.
+To make handling so many search results feasible, we employed a
+three-pass filtering strategy:
+
+First, we filtered works based on (a) their title and (b) the
+contextual information Google Scholar displayed on its search results
+page.
+We included works at large that seemed to bear a resemblance to software
+engineering and building software.
+Following Kitchenham's protocol~\citep{kitchenham2009systematic},
+we excluded
+works written in a language unintelligible to the authors
+(i.e., not English or German), which disregarded fewer than 1\% of search
+hits.
+% 'four' not clear and it gets lost that there are multiple search queries
+% therefore I'll cut this part completely:
+% We then unified
+% the results of the four search queries based on the link as the
+% identifying element, removing 60 works that appeared in more than
+% one search query.
+We removed duplicates based on the title and were
+left with 256 works (16\% of the original search results).
+
+With these 256 remaining works, we followed a backward snowball
+sampling for related work.
+If a work referenced a new work in the context
+of build log analysis, we added the new one to the literature set.
+This added five works (eight before
+duplicate elimination), leading to a total of 261
+works.
+
+Second, we performed a finer filter phase by (1) reading abstracts,
+and (2) downloading the
+full text of the works and searching it
+for the occurrence of the term ``log.''
+If a work showed traces of
+working with build logs, we passed it onto the final filter phase.
+In total, we
+were left with 87 works after the second filtering phase.
+
+Third, since we had been careful to include rather than exclude borderline
+works, a deeper evaluation excluded another 15 works from the 87
+works left after the second filter phase.
+Multiple works were extensions of others.
+Of these, we only considered the earliest work which reported on
+the analyzing of build logs.
+This excluded another 11 works.
+In sum, we included and classified 61 works in detail.
+
+\subsection{Literature Classification}
+Having trimmed down the set of works by 95\%, we investigated the
+remaining ones in-depth.
+Our aim was to characterize how researchers work with build logs.
+
+Specifically, we were interested in
+\begin{itemize}
+  \item what information the researchers retrieve from build logs and
+  what they use this information for (\textbf{RQ1.1}),
+  \item which techniques they employ to process the build logs,
+  in how much detail the techniques are described,
+	and whether their implemented tools are published
+  (\textbf{RQ1.2}),
+  \item which kinds of build logs the researchers analyze
+	and the origin of these logs (\textbf{RQ1.3}).
+\end{itemize}
+
+This lead us to the following research questions:
+\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
+{\textbf{RQ1:} What is the state-of-research to analyze build logs?}
+\begin{itemize}[leftmargin=1cm]
+  \item[\textbf{RQ1.1:}] What information is targeted in build logs?
+  \item[\textbf{RQ1.2:}] Which analysis techniques exist?
+  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
+  analysis?
+\end{itemize}
+\end{simplebox}
+
+To support the data extraction we created a template which we filled out
+for each of the 61 works.
+The template contained questions to answer RQ 1.1 through RQ 1.3,
+for example ``Is the technique explained in detail?'' and
+``What is the source of the build logs?''
+As recommended by Petersen et
+al.~\citep{petersen2015guidelines}, we started the mapping survey with a
+pilot:
+both authors extracted data from the same five works and held a
+consensus meeting to unify their understanding
+of the data extraction template.
+We divided the remaining 56 works evenly between the two authors
+and inspected each work as closely as necessary to fill out the
+template
+with confidence,
+starting from occurrences of ``log'' or ``build'' within the full
+text of the work.
+
+For questions that did not require a boolean answer, we allowed assigning
+multiple tags or categories as the first part (``preparation phase'')
+of a virtual open card sorting~\citep{zimmermann2016card}.
+An example of this is the question ``What is the source of the build
+log?,''
+where we assigned tags such as ``Travis CI,''
+``Industrial,'' ``Google,'' or
+``Self-built.''
+Once we had classified all works, we went into the second phase of
+card sorting
+(``execution phase''), in which we grouped tags
+together and found synonyms.
+% the following adds to the example but is maybe unneeded / too much
+For instance, in the case of the build log source we grouped
+``Travis'' and ``Travis CI'' together and assigned ``Industrial'' to
+all works that used build logs from a company.
+The replication package contains the data extraction template and all
+results of this step~\citep{brandt2020chunk-replication}.
+
+\subsection{Results}
+% tense: past
+
+\label{sec:litsurresults}
+
+In this section, we first give a general overview over our paper
+population.
+We then present the results of the analysis phase along RQs 1.1 through
+1.3.
+
+\subsubsection{Descriptive Study Statistics}
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/years.pdf}
+		\caption{Number of works analyzing build logs per year.}
+		\label{fig:lit-years}
+\end{figure}
+
+After the third filtering phase, we finally included 61 works in the
+literature survey.
+The majority of these are scientific articles (81\%), of which all but
+three have been peer-reviewed and published (94\%).
+The remaining works are theses (14\%), two books, and one slide deck.
+
+\Cref{fig:lit-years} depicts the year of appearance of these
+works.
+Although we applied no filtering by year in our initial search queries
+(see \Cref{sec:litsel}), the earliest work in our literature corpus
+stems only from 2001.
+There are various scattered works in the years between then and 2016,
+when the field of build log analysis started to grow rapidly.
+
+\subsubsection{What information is targeted in build logs (RQ 1.1)?}
+\label{sec:rq11}
+\begin{figure}
+\centering
+\begin{subfigure}[t]{\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/info_target.pdf}
+		\caption{Information targeted in build log analysis.}
+		\label{fig:litsur:info_target}
+
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[t]{\columnwidth}
+		\centering
+				\includegraphics[width=\columnwidth,
+				clip]{img/lit-sur/kind.pdf}
+		\caption{Class of information analyzed.}
+		\label{fig:litsur:kind}
+
+\end{subfigure}
+\begin{subfigure}[t]{\columnwidth}
+		\centering
+				\includegraphics[width=\columnwidth,
+				clip]{img/lit-sur/use.pdf}
+		\caption{Purpose of build log analysis.}
+		\label{fig:litsur:use}
+
+\end{subfigure}
+
+\caption{Multi-label categorization of the 61 relevant works.}
+\label{fig:litsur_r}
+\end{figure}
+
+In this section, we describe what sort of information the works in
+our survey usually retrieve from build logs.
+\Cref{fig:litsur_r} depicts these results.
+
+\Cref{fig:litsur:info_target} gives an overview over the frequency of
+the targeted information.
+The precise information targeted in the build logs varied from work
+to work, with a relatively long tail.
+Most prominent was the search for errors (39\%), followed by extracting
+the executed or the failing
+tests (both 11\%).
+There were also numerous works which targeted more specialized
+information, such as the environments used during the
+build~\citep{zolfagharinia2017not}, packages
+installed~\citep{selberg2012use}, or hints to source files which
+relate to build failures~\citep{ren2018automated}.
+
+\Cref{fig:litsur:kind} depicts that there are two widely used ways to
+extract information from build logs: either chunks (53\%) or
+classifications (41\%).
+Uses for chunks were extracting compilation errors,
+test failures, or the duration of build
+tasks~\citep{clemencic2014new,zhang2016android}.
+Examples for
+classifications were distinguishing failures caused by developers from
+failures caused by infrastructure errors~\citep{lindqvist2019detection}
+or determining whether projects use automated static analysis
+tools~\citep{kavaler2019tool}.
+Categorization is the more abstract representation, chunks
+contain more information and could be turned into a categorization.
+
+\Cref{fig:litsur:use} shows the aim for the
+investigated works to analyze build logs, and the result also explains
+the prevalence of classification in \Cref{fig:litsur:kind}.
+The majority of works (46\%) used the outcome of their build log
+analysis to drive further research---and it is science's aim to
+classify and abstract.
+Seo et al.~\citep{seo2014programmers}, for example,
+categorized the types of compile errors encountered at
+Google.
+Other works (10\%) used the gained insights to give feedback to
+developers.
+For 8\% of the works was the retrieved information the input
+to a next automatic onward processing step:
+works chose
+tests that should be part of a reduced, but still effective test
+suite~\citep{shi2018evaluating} or filled     a data structure with
+build information, an information source for further tools aiming
+to fix a failing build~\citep{vassallo2018un-break}.
+
+\subsubsection{Which analysis techniques exist (RQ 1.2)?}
+
+\addtolength{\tabcolsep}{-5pt}
+\begin{table*}[tbhp]
+\tinyish
+\centering
+\caption{Overview of build log analysis techniques.}
+\begin{tabularx}{\textwidth}{@{}lXl@{}}
+
+\toprule
+Name			     & Sources	& Frequency	  \\
+\midrule
+
+\raisebox{0.8mm}{Parser} &
+\raisebox{0.8mm}{
+\citep{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
+\\
+
+\raisebox{0.8mm}{Regular expression} &
+\raisebox{0.8mm}{
+\citep{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
+\\
+
+\raisebox{0.8mm}{Manual inspection} &
+\raisebox{0.8mm}{
+\citep{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
+\\
+
+\raisebox{0.8mm}{Machine Learning} &
+\raisebox{0.8mm}{
+\citep{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
+\\
+
+\raisebox{0.8mm}{Natural Language Processing}	&
+\raisebox{0.8mm}{
+\citep{hassan2017change,lou2019history,schulz2017active}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+
+\raisebox{0.8mm}{Information Retrieval} &
+\raisebox{0.8mm}{
+\citep{hassan2017change,lindqvist2019detection,ren2018automated}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+
+\raisebox{0.8mm}{Analysis} &
+\raisebox{0.8mm}{
+\citep{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+
+\raisebox{0.8mm}{Keyword Search} &
+\raisebox{0.8mm}{
+\citep{brandyberry2006continuous,zhang2019large,kavaler2019tool}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\\
+
+\raisebox{0.8mm}{Scan} &
+\raisebox{0.8mm}{
+\citep{clemencic2014new,hibbard2001visualization}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
+\\
+
+\raisebox{0.8mm}{Other} &
+\raisebox{0.8mm}{
+\citep{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
+} &
+\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
+\\
+
+\raisebox{0.8mm}{None identified} &
+\raisebox{0.8mm}{
+\citep{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
+} &
+\\
+
+\specialrule{\heavyrulewidth}{0pt}{2pt}
+
+\end{tabularx}
+\label{tab:litsur:techniques}
+\end{table*}
+\addtolength{\tabcolsep}{5pt}
+
+Of the 61 works we inspected, 43 mentioned how they analyzed
+build logs.
+However, only 16 of these described their technique in detail.
+We summarize the techniques that the works
+described for analyzing build logs in \Cref{tab:litsur:techniques}.
+
+The most mentioned technique (34\%) was using a parser.
+In this tag, we also
+included
+rather imprecise statements like ``we parse the build
+logs''~\citep{rahman2018impact}.
+For such imprecise statements it was often not clear if they described
+a complex parser (including a tokenizer, lexer, etc.) or referred to a
+simpler parsing tool based on regular expressions.
+If we saw evidence for the latter, we assigned the tag
+``Regular Expression'' instead of the tag ``Parser.''
+25\% of the works described the use of regular expressions and 20\%
+inspected the logs manually.
+For example,
+Seo et al.~\citep{seo2014programmers} developed a custom
+parser to classify error messages, while Vassallo et
+al.~\citep{vassallo2017a-tale} analyzed build logs with regular
+expressions.
+Ghaleb et al.~\citep{ghaleb2019studying} used a compound approach.
+They started with a manual categorization of build logs and selected
+search strings that identify the target category.
+Based on the search strings they created a script that automatically
+classifies the remaining logs.
+Another 8\% of the investigated works
+employed machine learning such as natural language
+processing or information retrieval techniques.
+The rather general tags ``analysis'' and ``scan'' in
+\Cref{tab:litsur:techniques}, stem---similar to the imprecise
+statements about parsing---from the
+words authors used to describe their techniques.
+%such as
+%``automatically analyzed [the build logs]''.
+
+Only 25\% of the works claimed their implementation is available.
+Moreover, we
+saw some reuse of the few available build log analysis tools.
+Five works employed the tools used to create
+\emph{TravisTorrent}~\citep{beller2017oops,
+orellana2017differences,zhao2018comparing} or
+an updated version of them~\citep{rott2019empirische,
+shi2018evaluating}, two used the
+\emph{Maven Log Analyzer}~\citep{macho2018automatically,gallaba2018noise},
+and
+another two
+\emph{MAKAO}~\citep{wen2018blimp,adams2007design}.
+
+\subsubsection{Which kinds of build logs are subject to
+  analysis (RQ 1.3)?}
+As the structure of build logs can change greatly depending on which
+build tools output to it~\citep{staahl2014modeling},
+we were interested in which build tools are
+investigated in the literature.
+\Cref{fig:litsur:log_producer} shows the distribution of
+build tools whose logs were analyzed by the works in our survey.
+Of the works, 30\% analyzed
+Maven~\citep{maven2019website},
+16\% analyzed Gradle~\citep{gradle2020website},
+and 10\% analyzed Ant build logs~\citep{ant2020website}.
+
+A large fraction of the works analyze build logs
+from a small number of build tools.
+In most cases, this is because the format of build logs
+changes and
+therefore ``parsers must be specialized to each build and test
+framework''~\citep{tomassi2019bugswarm}.
+Sometimes, aspects separate from the build log analysis motivate
+the limitation to a specific build tool.
+For example, Shi et al.
+focussed on Maven
+build logs because they also chose the PIT tool~\citep{coles2016pit}
+to calculate coverage
+and mutation score~\citep{shi2018evaluating}.
+PIT is only available as a Maven plugin.
+Only 7\% of the proposed techniques claimed to be
+build tool-agnostic, while
+several described that they cover multiple build tools.
+The majority of works (42\%) analyzed logs produced by a build tool
+that no second work investigated.
+
+In 38\% of cases, the works collected build logs from Travis
+CI~\citep{travisci2019webpage};
+18\% of the works analyzed logs from TravisTorrent; and 8\% included
+build logs from industrial projects.
+The number of logs analyzed varied greatly between the works
+and we were not always able to
+extract it confidently.
+23 of the works analyzed more than a thousand build logs, while one
+investigated up to 122 million logs.
+Of the surveyed works, 31\% claim to have published their data to
+enable further research.
+However, we found no clear reuse of build log data sets with the
+exception of TravisTorrent~\citep{beller2017travistorrent}, which
+Vassallo et al.~\citep{vassallo2017a-tale},
+Ghaleb et al.~\citep{ghaleb2019studying},
+and several others have studied~\citep{hassan2017change,
+hassan2019tackling,hassan2017automatic,orellana2017differences,
+haghighatkhah2018test,madeyski2017continuous,ghaleb2019empirical,
+santolucito2018statically,gallaba2018noise,shi2018evaluating}.
+
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth, trim={1.5cm 0.4cm
+		1.5cm 0.5cm},
+		clip]{img/lit-sur/log_producer_annotated.pdf}
+		\caption{Frequency of supported build tools.}
+		\label{fig:litsur:log_producer}
+\end{figure}
+
+\subsection{Discussion}
+\label{sec:lit-sur:discussion}
+% tense: present
+
+% ----- descriptive / general -----
+Our literature survey shows that \emph{there is a rapidly growing body
+of works using build log analysis,}
+with 61 works in different venues making use of it for a variety of
+purposes.
+We saw that various researchers analyze build logs, with the
+logs often being the only available source for the
+information they need for their studies~\citep{ren2018automated,
+seo2014programmers,beller2017oops,zampetti2017open,rausch2017empirical}.
+
+% ----- information RQ 1.1 -----
+In regards to the information that is targeted, \emph{most build log
+analysis approaches aim to retrieve the reason a build failed} by
+targeting ``errors'' or ``failing tests.''
+% which is what we also do in LogChunks
+\emph{The majority of approaches retrieves specific chunks of
+text from the logs.} Chunks are the overarching concept to
+the almost equally much used categorization: one can deduce a
+categorization from chunks, but not vice versa.
+
+% ----- technique RQ 1.2 -----
+\emph{Most log analysis is automated.} Automated approaches are
+necessary because many studies target a large number of builds.
+Works
+that explicitly mention manual analysis of the logs, mostly
+restrict themselves to few logs or take a ``representative sample to
+make manual analysis feasible''~\citep{zolfagharinia2017not}.
+We observed \emph{very little reuse of build log analysis tools},
+even though works reported that
+\emph{developing automated analysis tools requires a lot of effort}.
+Urli et al.~\citep{urli2018design} strongly discouraged from parsing
+build logs for information as it is ``too error prone,'' while other
+works pointed to the effort of developing a custom tool.
+We know from other research lines that regular expressions, the second
+most popular way to analyze log files (\Cref{tab:litsur:techniques}),
+are tedious to
+maintain~\citep{michael2019regexes}.
+In addition, we rarely saw works justifying why they use a certain
+technique to analyze build logs as there is a general \emph{lack of
+guidance on when to use which technique.}
+
+% ----- kinds of build logs RQ1.3 -----
+Several works noted the variety in log formats for different build
+tools, which requires customizing build log techniques for
+every supported build tool.
+\Cref{fig:litsur:log_producer} shows that there are only a handful of
+build tools whose build logs more than one study analyzed, mainly in
+the Java ecosystem (area \circlenum{A}).
+Many works target a unique build tool that did not appear in any other
+study (area \circlenum{B}).
+We follow that \emph{many seldomly-investigated
+environments would benefit from the
+existence of a more generic solution.}
+
+The literature survey shows the need for
+build log
+analysis techniques that are \emph{automated},
+\emph{build tool-agnostic}
+and that a user can \emph{configure with little effort}.
+\section{Chunk Retrieval Techniques}
+\label{sec:techniques}
+
+In this section, we formally define the concept of chunk
+retrievals from build logs.
+Then, we motivate and present the choice of three such techniques that
+we implemented and evaluated for this study.
+
+\subsection{Characteristics of Chunk Retrieval Techniques}
+\label{sec:crt-characteristics}
+
+With the term ``chunk retrieval technique,'' we refer to a way of
+automatically extracting strings that appear literally in build
+logs, i.e., techniques that do not aggregate, combine, or deduct
+information.
+We call such pieces of information in build logs
+\emph{chunks}.
+Depending on the format of the chunks within the build log we
+separate them into different \emph{structural categories}.
+
+Generally, chunk retrieval techniques
+can also be used to classify build logs, e.g.\, by checking
+which substring was retrieved.
+Therefore, they
+cover the great majority of the types of log analysis we saw in
+\Cref{sec:lit-sur:discussion}.
+
+The techniques we investigate here do not require a formal lexer and
+parser to analyze the entire structure of build logs, but focus on
+ad hoc extraction of just one specific information piece per
+configuration.
+
+With the term \textit{configuration}, we abstract over the training
+and parametrization that different techniques require in different
+forms.
+A configuration can be explicitly stated or implicitly derived
+by learning through provided examples.
+It is therefore a manual
+specification of which information the chunk retrieval should target.
+It also supplies the necessary information for the technique to
+identify the targeted chunk in a build log.
+Each chunk
+retrieval technique has a specific \textit{granularity}, i.e.,\ the
+smallest piece of text it can return (e.g., a line, or a word).
+% The
+% granularity might be adjustable by configuration.
+
+\emph{Running a
+chunk retrieval technique} means
+executing a fully configured
+technique to a build log.
+The technique then outputs a (possibly empty) list of substrings of the
+build log text.
+
+\subsection{Choice of Chunk Retrieval Techniques}
+\label{sec:choice}
+
+\begin{table*}[htb]
+\centering
+\caption{Chunk retrieval techniques.}
+\begin{tabularx}{\textwidth}{@{}llXll@{}}
+\toprule
+Name & Acronym & Identification Technique & Granularity &
+Configuration \\
+\midrule
+Programming by Example & PBE	 & Regular expression program
+& Character   & In/output examples	\\
+Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
+expected number of lines & Line        & Output examples	   \\
+Keyword Search		     & KWS     & Keywords, expected number of
+lines			 & Line        & Keywords, context length  \\
+Random Line Retrieval	     & RLR     & Random sample
+& Line	      & Retrieval length	  \\
+\bottomrule
+\end{tabularx}
+\label{tab:techniques}
+\end{table*}
+
+For this article, we designed and implemented three automated chunk
+retrieval techniques.
+Our findings of techniques in the literature
+survey (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
+particular) inspired the strategies that underlie them.
+\Cref{tab:techniques} summarizes the techniques, which we describe here
+in detail.
+
+Techniques based on custom parsers (\#1
+in \Cref{tab:litsur:techniques}) are inadequate for our comparison,
+since their creation is manual and one parser would never generalize
+to the wide variety of build logs we are interested in.
+The closest
+we could come to the second most popular entry, regular expression, is
+a technique to automatically derive them: in particular, we implement
+a technique based on
+\emph{Programming by Example (PBE)}.
+It uses regular expressions internally, while simplifying their
+development.
+
+To work effectively with build logs, many humans anecdotally search
+(``grep'') the logs for key phrases such as ``fail.'' Researchers often
+resorted to such a strategy when doing manual analysis (\#2
+in \Cref{tab:litsur:techniques}), describing it with the word ``scan''
+or other paraphrases.
+Imitating this ad hoc approach of searching for
+specific strings, we automatize it as \emph{Keyword Search (KWS)}.
+
+Finally, from the fields of information retrieval (IR) and natural
+language
+processing (NLP, see \Cref{tab:litsur:techniques}), we leverage
+a widely-used text similarity measure and call this approach \emph{Common
+Text Similarity (CTS)}.
+The intuition behind it is that the relevant,
+failing parts of build logs often look similar to each other, even if
+the exact failure reasons might differ.
+
+Other techniques, specifically ones based on deep learning, are
+thinkable, but we did not evaluate them in this article since they did
+not emerge from the literature survey.
+Moreover, they typically
+require lots of training and tuning.
+However, our premise was to ease
+the creation of build log analysis for developers.
+First having to
+label thousands of logs on their project before they can start to
+analyze build logs is therefore infeasible.
+Similarly, as a manual
+effort, the \emph{LogChunks} data set is not big enough to support the
+training of such supervised techniques.
+Finding a way to train them in
+an unsupervised fashion would rapidly increase their applicability and
+appeal to build log analysis.
+
+\subsection{Programming by Example (PBE)}
+The idea behind \emph{Programming by Example} is to automatically
+generate a program, by capturing the
+intent of the user through examples that the user provides.
+Leveraging this approach, we designed a chunk retrieval technique
+for build logs.
+The \emph{PROSE library}~\citep{prose2019webpage} forms the basis for
+our implementation.
+This library builds on the generic program synthesis framework
+\emph{FlashMeta}~\citep{polozov2015flashmeta:} and the specialized
+text extraction DSL \emph{FlashExtract}~\citep{le2014flashextract:}.
+% Both enable \emph{PROSE} to synthesize regular expression programs
+% consistent~\citep{mitchell1982generalization} with a set of in-
+% and output examples.
+% The usage of example enables the user to configure a chunk
+% retrieval without understanding the whole structure of
+% the build log.
+
+\subsubsection{Configuration}
+In- and output example pairs are the main driver of PBE;
+The \emph{input} is the full text of the build log file.
+The \emph{output} is
+a substring of the log file text, representing the
+substring that the synthesized program should retrieve when
+given the corresponding input file.
+One or multiple examples, the
+training set, \emph{configure} a specific chunk retrieval with PBE:
+they define the chunk of a build log that should be retrieved.
+The PROSE program synthesis then tries to construct a program
+consistent with all training
+examples~\citep{mitchell1982generalization}.
+If PROSE cannot synthesize a program, e.g.,\
+because the required regular expression
+is too complicated to be synthesized, PBE returns the
+error message ``no program found.''
+
+\subsubsection{Chunk Retrieval Run}
+A run of PBE takes a build log file as input and executes the
+synthesized regular expression program on it.
+It then returns the substring
+of the build log matched by the program.
+If the program finds no match because the analyzed build log
+does not contain the structure that the training examples define,
+PBE returns the error message ``no match found.''
+
+\subsection{Common Text Similarity (CTS)}
+Text Similarity approaches are widely used to filter unstructured
+textual software artifacts~\citep{runeson2007detection,
+marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+These approaches fall into the broader area of information retrieval
+techniques, which several of the works from our literature survey
+used to analyze build logs.
+Similar to these approaches, we designed a chunk retrieval
+technique that
+retrieves those lines from a build log which are most
+similar to the specified examples.
+
+\subsubsection{Configuration}
+To configure CTS we chose to use the same concept of examples as for
+PBE: lines of the targeted chunks from the training examples define
+the search query.
+Using a Vector Space
+Model~\citep{schutze2008introduction} (VSM), an algebraic model for
+representing textual documents, we encode each line as a separate term
+vector.
+The terms that make up the dictionary are simply all words
+that appear in the example logs.
+We separate words by spaces and
+punctuation.
+The vectors comprise points counting
+how many times a word out of the dictionary appears in the specific
+line at hand.
+
+The idea behind a representation in the VSM is that text lines as more
+similar if they contain the same words in similar frequencies,
+making their term vectors point in a similar direction in vector
+space.
+We use \emph{cosine similarity}~\citep{korenius2007principal}
+to calculate the angle between two term vectors.
+The smaller the
+angle between term vectors is, the more similar are the corresponding
+lines.
+
+To improve the similarity calculation, we prune very often or
+very rarely appearing words.
+Finally, the
+algorithm weighs the vectors using \emph{term frequency-inverse
+document frequency (TF-IDF)}, an established technique to give a higher
+impact to words that occur in a smaller number of
+documents~\citep{lee1997document}.
+
+\subsubsection{Chunk Retrieval Run}
+To retrieve the desired information from a build log, we encode every
+line of the input build log in VSM.
+The algorithm calculates the cosine
+similarity to compare each line of the
+build log with each line of the search query.
+After summing up the
+similarities of each build log line to all search query lines, we sort
+the build log lines in decreasing similarity.
+The average number of
+lines in the chunks of the training examples determines how many of
+the most similar lines our approach returns as the output of the retrieval
+run.
+
+\subsection{Keyword Search (KWS)}
+When developers scavenge for a specific piece of information within a
+large amount of unstructured information, a first ad hoc approach they
+use is to search for related keywords.
+To investigate the performance of this approach, we designed a chunk
+retrieval technique mimicking this human behavior based on keyword
+search.
+
+\subsubsection{Configuration}
+A set of keywords configures the chunk retrieval with KWS\@.
+To better
+compare KWS with PBE and CTS, we also configure it through examples.
+From each example, we extract a list of keywords that appeared in the
+training examples and that we expect to appear
+in, or close to, the targeted chunk in a new build log.
+Finally, we merge the lists from all examples to build one unified
+list of the most commonly occurring keywords for the search with KWS.
+
+\subsubsection{Chunk Retrieval Run}
+For a retrieval run, we take an entire build log file as input and
+search for all exact occurrences of the search keywords.
+As keywords are
+often not directly describing the desired information, but rather
+appear close to it, KWS also retrieves a context of lines
+around the found keyword.
+The number of surrounding lines retrieved is
+the average number of lines in the chunks of the training examples.
+
+\subsection{Random Line Retrieval (RLR)}
+\label{sec:expl-rlr}
+To fully comprehend how difficult the task of build log analysis really
+is without any a priori knowledge, we include a comparison with a
+baseline of
+picking lines at random from the build log.
+RLR mimics the
+situation of guessing blindly which lines are interesting.
+The only configuration option for RLR is the number of lines it should
+retrieve.
+For a fair comparison to the other techniques (whose number of
+returned lines is largely determined by the training set),
+we configure RLR to return the average
+number of lines in the chunks of the training examples.
+
+\subsection{Concrete Example}
+\label{sec:crt-example}
+
+\lstset{escapeinside=//}
+\begin{figure}[tbp]
+  \centering
+\begin{subfigure}[tbp]{\columnwidth}
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+FAILURE: Build failed with an exception.
+
+* What went wrong:
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
+Could not determine the dependencies of task ':app:jacocoTestDebugReport'.
+> Task with path 'testDebug' not found in project ':app'.
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+
+* Try:
+  \end{lstlisting}
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[tbp]{\columnwidth}
+  \centering
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+FAILURE: Build failed with an exception.
+
+* What went wrong:
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk1.txt}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+
+* Try:
+  \end{lstlisting}
+    \caption{Two examples of log chunks explaining why an Android
+  build failed.}
+  \label{lst:chunk-example}
+\end{subfigure}
+
+\begin{subfigure}[tbp]{\columnwidth}
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+=== RUN   TestSeparator
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk2.txt}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+=== RUN   TestGenerateHTML
+  \end{lstlisting}
+  \caption{Example of a log chunk showing a linter error.}
+  \label{lst:chunk-example-3}
+\end{subfigure}
+
+\caption{Exemplary log excerpts.}
+\label{lst:logexamples}
+\end{figure}
+
+\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
+RegexPair,
+  EndExtraction}, keywordstyle=\bfseries\color{black}}
+\begin{figure}[tbp]
+  \centering
+  \lstinputlisting[breaklines=true]{listings/prose.txt}
+  \caption{Simplified regular expression produced by PBE when trained
+  with examples from \Cref{lst:chunk-example}.}
+  \label{lst:prose-program-simplified}
+\end{figure}
+
+In this section, we illustrate how the different chunk retrieval
+techniques work practically on the example of the build logs
+in \Cref{lst:logexamples}.
+Marked in blue in \Cref{lst:logexamples}
+are the chunks we target.
+They contain the information on why the
+corresponding build failed.
+\Cref{lst:chunk-example} shows two excerpts
+from Android build logs.
+The chunk to be retrieved starts after a
+colon and a line separator and before a capital letter.
+It ends
+before two line separators.
+All these characteristics are consistent
+with the two example chunks
+from \Cref{lst:chunk-example}.
+\Cref{lst:chunk-example-3} is very
+different.
+For example, it does not have the two extraneous newlines
+after the chunk.
+
+When we train PBE with the two examples from \Cref{lst:chunk-example},
+it produces a regular expression program similar to the one presented
+in
+\Cref{lst:prose-program-simplified}.
+This shows that the characters structuring the text around the chunk are
+crucial for regular expressions to identify a log chunk.
+In fact, if we add the third example from
+to the training set (which has a
+different structural representation),
+PBE is not able to synthesize a program anymore and returns
+``\texttt{no program found}.''
+The chunks from \Cref{lst:chunk-example}
+are in the \emph{same structural category}, while the chunk from
+\Cref{lst:chunk-example-3} is in a
+\emph{different structural category}.
+
+If we train CTS with the example chunks from
+\Cref{lst:chunk-example},
+CTS will rank the lines from an analyzed build log which are most
+similar to the chunks in the training examples.
+It will then return the two lines ranked highest, as the chunks in
+the training examples have on average 2.0 lines.
+In this example,
+CTS will have difficulty extracting the lines from
+\Cref{lst:chunk-example-3} as there are no words that appear
+in both the training and the test chunks.
+The same applies if we train with the first chunk from
+\Cref{lst:chunk-example} and try to retrieve the second chunk,
+as the only shared word is ``task''.
+
+Keywords that appear in or close to the chunk within
+the build log configure the technique KWS\@.
+For the examples from \Cref{lst:chunk-example} these could be
+``FAILURE,'' ``wrong,'' or ``failed.''
+The example from \Cref{lst:chunk-example-3} could be found
+by searching for ``FAIL.''
+If we train KWS with all three examples and the aforementioned
+associated keywords, it would search for the three keywords from
+\Cref{lst:chunk-example}, as they appear twice---most often within
+the training set of three examples.
+
+\subsection{Tool Implementation}
+For the comparison study, we implemented the three chunk retrieval
+techniques described in this section and a unifying interface.
+We implemented PBE in C\# based on the Microsoft PROSE
+library~\citep{prose2019webpage} and CTS, KWS, and RLR using
+R and the {\tt text2vec} library~\citep{text2vec2019webpage}.
+
+\section{Chunk Retrieval Comparison}
+\label{sec:study}
+
+\begin{figure*}[tb]
+\begin{algorithmic}[1]
+\ForEach{$technique \in\{PBE,CTS,KWS,RLR\}$}
+ \ForEach{$project  \in \emph{LogChunks}$}
+ \Comment{$|\emph{LogChunks}|$=80}
+  \For{$i \in\{1,2,3,4,5\}$}
+   \State $training\_logs \gets getBuildLogsByTime(project, 0, i)$
+   \Comment{Logs
+   returned ordered by time of creation.}
+   \State $test\_log \gets  getBuildLogByTime(project, i)$
+   \State $n \gets |structuralCategories(test\_logs)|$
+   \State
+   \State $train(technique, training\_logs)$
+       \State $retrievedLines \gets run(technique, test\_log)$
+       \State $metrics \gets calculateMetrics(retrievedLines,
+       desiredLines(test\_log))$
+       \State
+       \State $saveMetrics(technique, project, n, i, metrics)$
+
+  \EndFor
+ \EndFor
+ \State $aggregateMetrics(technique)$
+\EndFor
+\end{algorithmic}
+
+	\caption{Study procedure.}
+	\label{fig:study}
+\end{figure*}
+
+In the literature survey, we noted that previous work seemed to choose
+a log analysis technique arbitrarily and that is a lack of guidance on
+when to use which technique.
+% add (see \Cref{sec:lit-sur:discussion}) ?
+To address this, in this section, we conduct an empirical study
+comparing the three novel chunk retrieval techniques we presented in
+\Cref{sec:techniques}.
+
+In particular, we are interested in how many examples a technique
+should be trained with (\textbf{RQ2.1}),
+how similar the structural representation of the targeted log chunks
+has to be (\textbf{RQ2.2}), and how reliable the quality of the
+produced retrievals is (\textbf{RQ2.3}).
+This leads us to the following research questions:
+
+\begin{simplebox}[minipage boxed title*=-1.5cm,
+attach boxed title to top center={yshift=-6mm}]
+{\textbf{RQ2:} How do build log analysis techniques compare?}
+\begin{itemize}[leftmargin=1.2cm]
+  \item[\textbf{RQ2.1:}] With how many training examples does a
+	technique perform best?
+  \item[\textbf{RQ2.2:}] How structurally variable can training
+  examples be?
+  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
+\end{itemize}
+\end{simplebox}
+
+In the following, we first introduce the data set we created for this
+study, and then describe the study design and its
+results.
+We answer these RQs separately for each technique.
+
+\subsection{LogChunks Data Set}
+\label{sec:logchunks}
+To conduct the study in this paper, we created the
+\emph{LogChunks} data set~\citep{brandt2020logchunks}.
+We collected 797 build logs that
+from 80 GitHub projects and 29
+programming languages on Travis CI, the most-used source of build logs
+according to our literature survey.
+This wide variety of projects and the large number of different build
+tools they employ enables us to measure the generic
+applicability of chunk retrieval techniques.
+
+For each build log in \emph{LogChunks}, we manually marked
+the chunk that describes why the build
+failed---the information targeted by most of the works in our
+literature survey (see \Cref{sec:lit-sur:discussion}).
+To be able to configure the keyword search technique,
+we associated each chunk in the data set with keywords that we
+would use to search for the selected chunk within the log.
+In
+addition, we categorized the log chunks according to their format
+within the log.
+If the chunks were, for example, surrounded by the same markings
+within the log, we assigned them the \emph{same structural category},
+as described in \Cref{sec:crt-example}.
+
+As explained in \Cref{sec:crt-characteristics}, examples are the basic
+unit by which we configure each technique.
+The full build log text,
+the chunk, the search keywords, and the assigned
+structural category make
+up one \emph{example} in \emph{LogChunks}.
+
+\subsection{Study Procedure}
+
+In the following, we explain our study procedure
+and introduce the metrics that
+we measure to answer RQ2.
+\Cref{fig:study} depicts the individual steps of our study as an
+algorithmic procedure.
+
+For each chunk retrieval technique and each project, we create
+training example sets consisting of 1, 2, \dots 5 examples (lines
+\circlenum{1}--\circlenum{3}).
+We vary the training set size to measure how many examples we need to
+confidently configure a technique, addressing \textbf{RQ2.1}.
+While this is atypical for an IR-based technique such as CTS---where
+the default is to split the whole corpus at a given percentage, often
+80/20---we did this for the specific task of build logs.
+We want to find out how many examples one has to manually specify with a
+lot of effort~\Cref{sec:lit-sur:discussion} and at which point techniques
+become efficient.
+
+The test set consists of the first build log produced
+chronologically after the build logs in the training set \circlenum{5}.
+This way, we train on examples from past build logs and test on
+a more recent log, just as one would apply these techniques in the
+real world.
+
+In line \circlenum{6}, we obtain how many different structural categories
+are present in the trained logs and store this to be able to answer
+\textbf{RQ2.2}.
+
+In the next step, we configure the chosen chunk retrieval technique with
+the examples from the training set \circlenum{8} and run the technique
+on the
+test set, producing the retrieval output \circlenum{9}.
+
+Based on this, we calculate the following metrics in
+\emph{calculateMetrics}, addressing \textbf{RQ2.3}:
+
+\vspace{0.2cm}
+\begin{itemize}[leftmargin=0.4cm] \itemsep1em
+	\item $|\mbox{True\ Positives}| = \mathit{desiredLines} \cap
+	\mathit{retrievedLines}$ \vspace{0.2cm}\\
+	True positives are lines that appear both in the output of a
+	technique as well as the chunk defined in the
+  test example.
+
+	% What about when a line is replicated twice?
+	% I.e., Are line numbers part of this? => no.
+	% not checked, but if lines are identical they also contain
+	% the same information so if someone asks we can defend I think
+
+	\item $\mbox{Precision} = \dfrac{|\mathit{True\
+	Positives}|}{|\mathit{retrievedLines}|}$ \vspace{0.21cm} \\
+	Precision of a chunk retrieval describes which proportion of
+	the retrieved lines were actually desired.
+
+	\item $\mbox{Recall} =
+	\dfrac{|\mathit{True\ Positives}|}{|\mathit{desiredLines}|}$
+	\vspace{0.2cm} \\
+	Recall of a chunk retrieval describes which proportion of the
+	desired lines were retrieved.
+
+	\item $\mbox{F$_{1}$-score} = 2 \cdot \dfrac{\mathit{Precision}
+	\cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
+	\vspace{0.2cm}\\
+	In addition, we calculate the F$_{1}$-score, the harmonic mean
+	of precision and recall.
+  We prefer F$_{1}$ to other aggregate
+	measures such as accuracy because of the
+	``needle-in-the-haystack'' scenario, we want to avoid bloating
+	our results by correctly not finding lots of irrelevant log
+	lines.
+
+	% actually that is now giving recall another (nicer) name
+	% improved if we just talk about recall later?
+	\item Successful retrieval = $\mathit{true}\ \mathit{iff}\
+	\mathit{Recall} = 1, \vspace{0.1cm}\\$
+	Partially successful retrieval = $\mathit{true}\ \mathit{iff}\
+	0<\mathit{Recall}<1, \vspace{0.1cm}\\$
+	Unsuccessful retrieval = $\mathit{true}\ \mathit{iff}\
+	\mathit{Recall} = 0, \vspace{0.1cm}$
+
+	We define a successful retrieval as one where all desired
+	lines were extracted, therefore when recall is one.
+	A retrieval is partially successful if at least some of the
+	desired lines were extracted,
+	and if the retrieved lines contain none of the desired lines
+	a retrieval was unsuccessful.
+\end{itemize}
+\vspace{0.2cm}
+
+\noindent
+Finally, we aggregate the results to be able to reason per technique
+\circlenum{15}, completing our study design to answer \textbf{RQ2}
+overall.
+
+\subsection{Results}
+In this section, we first present the metrics for each chunk retrieval
+technique separately.
+Afterwards, we compare the three techniques with each other and with a
+random baseline.
+
+\subsubsection{Programming by Example (PBE)}
+\label{sec:r:pbe}
+
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/failure-reason-pbe.pdf}
+		\caption{High-level results of chunk retrieval with
+		Programming by Example (PBE).}
+		\label{fig:failure-reason-PBE}
+\end{figure}
+
+\lstset{
+  language=,
+  morekeywords={Test, Output, Desired},
+  keywordstyle=\textbf,
+	frame=single
+}
+\begin{figure}[tbp]
+  \centering
+\begin{subfigure}[b]{\columnwidth}
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+[0K$ test/sass-compile-tester.sh
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \lstinputlisting[backgroundcolor=\color{Yellow!60},breaklines=true,frame=rl]
+	{listings/chunk3.txt}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+	from line 5 of sass/components/_all.sass
+  \end{lstlisting}
+	\caption{Actual chunk retrieval output ($retrievedLines$
+	in yellow).}
+	\label{lst:pbe-part-success-output}
+\end{subfigure}
+
+\begin{subfigure}[b]{\columnwidth}
+  \begin{lstlisting}[breaklines=true,frame=tlr]
+[0K$ test/sass-compile-tester.sh
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
+	{listings/chunk3.txt}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
+	from line 5 of sass/components/_all.sass
+	from line 6 of bulma.sass
+  \end{lstlisting}
+  \vspace{-\baselineskip}
+  \begin{lstlisting}[breaklines=true,frame=blr]
+  Use --trace for backtrace.
+  \end{lstlisting}
+	\caption{Targeted chunk ($desiredLines$ in blue).}
+	\label{lst:pbe-part-success-desired}
+\end{subfigure}
+  \caption{Example of a partially successful retrieval
+  (PBE retrieved only
+  two of the four targeted lines).}
+  \label{lst:pbe-partially-successful}
+\end{figure}
+
+\begin{figure*}
+\centering
+    \textbf{Programming by Example (PBE)}\par\medskip
+\begin{subfigure}[b]{\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
+				\caption{Successfulness of retrieval
+				compared by structural category count
+				in training and test sets.}
+		\label{fig:failure-reason-categorycount-PBE}
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[b]{\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
+				\caption{Precision, recall, and
+				F$_{1}$-score when PBE could synthesize
+				a consistent program compared with the
+				size of the training set.}
+		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
+\end{subfigure}
+\caption{Results of chunk retrieval with Programming by Example
+(PBE).}
+\end{figure*}
+
+% actually, we could cut this figure and move it's explanation
+% to the next one (this is an aggregation of the next one)
+% however, having them separate eases the entry into the results a bit
+% and we have explanation of the categories before the more complicated
+% aspect of the change with more structural categories
+\Cref{fig:failure-reason-PBE} shows the results of chunk
+retrieval with PBE.
+It shows how many of the retrieval runs were successful,
+partially successful, or unsuccessful,
+as well as the number of runs where the
+synthesized program did not match on the analyzed build log or where
+no program could be synthesized.
+% The last two results stem from the regular expressions and their
+% synthesis, therefore only apply to PBE.
+Out of the 400 runs, 5 per each one of the 80 projects,
+PBE extracted all desired lines successfully in 138 cases.
+In 18 cases, the synthesized program only extracted a
+subset of the desired lines, while in 12 cases it extracted none of
+the desired lines.
+For the 18 partially successful runs, the average recall
+was 47\%.
+\Cref{lst:pbe-partially-successful} shows an example of such
+a partially successful retrieval.
+In it, the synthesized program only
+retrieved two (\Cref{lst:pbe-part-success-output})
+of the four (\Cref{lst:pbe-part-success-desired}) targeted lines.
+In 59 cases, PBE could synthesize a regular expression program, though
+the program did not match on the test build log.
+In 173 of the 400 cases
+could PROSE not synthesize a program consistent with all of the training
+examples.
+
+\Cref{fig:failure-reason-categorycount-PBE} shows how
+the results of PBE
+runs depend on the number of structural categories in the training and
+test examples.
+% It shows the categories from above change depending on how many
+% structural categories are present.
+The figure demonstrates that programming by example mostly
+returns exactly the desired output when there is only one
+structural category present in the training and test examples.
+However, when
+two or more structural categories are simultaneously present,
+PROSE could in most cases not synthesize a program.
+For four or more present
+categories PROSE could never synthesize a consistent program.
+
+Zooming in on only the 227 runs where PBE could synthesize a program,
+\Cref{fig:recall-precision-examplecount-sythesisworked-PBE}
+presents violin plots and averages of the precision, the recall
+and the F$_{1}$-score
+of these runs compared with the number of examples in the training set.
+We chose violin plots to show spread in distributions of values.
+Specifically, we see an hour glass shape for training set size 1.
+In this case, it means that for recall (and F$_1$-score) there are about
+as many observations with low recall as there are with high.
+This is a striking difference to set size 2, where we have mostly
+correct extractions.
+When the training set
+size increases from one to two, recall, and F$_{1}$-score increase by
+about 25\%, precision increases by about 10\%.
+For two or more
+training examples, recall, and F$_{1}$-score stay around 75\% and
+precision around 96\%.
+
+\subsubsection{Common Text Similarity (CTS)}
+\label{sec:r:cts}
+
+\begin{figure*}
+\centering
+    \textbf{Common Text Similarity (CTS)}\par\medskip
+\begin{subfigure}[tb]{\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
+		\caption{training set size.}
+		\label{fig:recall-precision-examplecount-CTS}
+
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[tb]{\columnwidth}
+		\centering
+				\includegraphics[width=\columnwidth,
+				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
+		\caption{structural category count
+		in training and test set.}
+		\label{fig:recall-precision-categorycount-CTS}
+\end{subfigure}
+\caption{Precision, recall, and F$_{1}$-score of chunk
+retrieval with Common Text Similarity (CTS) compared by \ldots}
+\label{fig:results-CTS}
+\end{figure*}
+
+% The following sections are each quite short...
+% we could merge them, but then it loses consistency with the other
+% result subsections where each plot gets an own paragraph
+\Cref{fig:results-CTS} shows violin plots
+of the precision,
+recall, and F$_{1}$-score of the chunk retrieval runs with CTS.
+The black horizontal lines show the average of these measurements.
+For some measurements, the violin plot is not visible because there is
+only one available data point or all data points have the same value.
+
+\Cref{fig:recall-precision-examplecount-CTS} presents the
+measurements for an
+increasing number of training examples.
+When using one to five
+training examples, the size of the training set has no noticeable
+influence on precision, recall or F$_{1}$-score of the chunk retrieval
+with CTS.
+
+\Cref{fig:recall-precision-categorycount-CTS} shows the
+measurements for an increasing number of structural categories in the
+training and test examples.
+With increasing category count, precision,
+recall, and F$_{1}$-score decrease.
+% Especially for more than four
+% categories present we have no chunk retrieval runs where all desired
+% lines were extracted.
+
+\subsubsection{Keyword Search (KWS)}
+\label{sec:r:kws}
+\begin{figure*}
+\centering
+    \textbf{Keyword Search (KWS)}\par\medskip
+\begin{subfigure}[b]{\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
+		\caption{training set size.}
+		\label{fig:recall-precision-examplecount-KWS}
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[b]{\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
+		\caption{structural category count
+		in training and test sets.}
+		\label{fig:recall-precision-categorycount-KWS}
+\end{subfigure}
+\caption{Precision, recall, and F$_{1}$-score of chunk retrieval with
+Keyword Search (KWS) compared by \ldots}
+\label{fig:results-KWS}
+\end{figure*}
+
+We present the precision,
+recall, and F$_{1}$-score of the chunk retrieval runs with KWS in
+\Cref{fig:results-KWS}.
+Violin plots show the distribution the values of each measurement,
+while the black horizontal lines show their average.
+If the figure shows no violin plot for a measurement, we only have one
+data point available or all values are the same.
+
+\Cref{fig:recall-precision-examplecount-KWS} presents these
+measurements for different
+numbers of training examples.
+The recall increases by about 12\% when
+increasing the size of the training set to more than one example,
+while the precision stays constant around 16\%.
+The F$_{1}$-score
+stays around 26\%.
+
+\Cref{fig:recall-precision-categorycount-KWS} shows the same
+measurements for an increasing number of structural categories in the
+training and test examples.
+For more than one structural category in
+the training and test examples the recall decreases by about 20\% and
+the precision decreases about 6\%.
+For more than two structural
+categories there is no clear trend in precision, recall, or
+F$_{1}$-score.
+
+% M: Perhaps, above in our section about logchunks, we would need some
+% basic empirical stats -- e.g., how long are the files and how much
+% do we usually extract from the log
+% C: yup, that would be nice
+% sadly, it's quite a bit of work to get those :/
+% maybe I/We'll do it at the end
+\subsubsection{Random Line Retrieval (RLR)}
+\label{sec:r:rlr}
+The baseline of randomly
+picking lines from build logs delivers the expected low and
+``random'' results: precision ranges between 5\% and 8\%,
+recall between 6\% and 8\%.
+As expected, the size of the training set has no impact on precision
+or recall of retrieving chunks with RLR.
+With a larger number of structural categories within the training and
+test sets, the precision of RLR decreases from 7\% to 0\%, while
+the recall varies between 0\% and 11\%.
+
+\subsubsection{Comparison of All Techniques}
+In this section, we compare the results of all four chunk retrieval
+techniques and show the impact of structural categories on precision,
+recall and F$_{1}$-scores of the different techniques.
+
+% absolute results? is there a nice word for these results
+\Cref{fig:success-partial-all} compares the results all of chunk
+retrievals techniques in our study.
+It shows how many runs per technique were successful, partially
+successful or unsuccessful in retrieving the chunk defined in the
+test example.
+CTS and KWS
+extract at least some of the desired lines in 79\% and 88.5\%
+of the chunk retrieval runs.
+With 38.25\%, KWS also has the highest proportion of fully
+successful extractions, followed by PBE with 34.5\%.
+PBE has the
+lowest number of partial retrievals with only 18 out of 400 chunk
+retrieval runs.
+All techniques clearly outperform the random baseline (RLR).
+
+\Cref{fig:category-all}
+shows the influence of all training and test examples being from the
+same structural category
+(\Cref{fig:recall-precision-singlecategory-all})
+compared to being from multiple categories
+(\Cref{fig:recall-precision-multicategory-all}).
+For more
+than one category present, the recall of PBE decreases greatly.
+For CTS and KWS the values also decrease, while RLR is not affected by
+the number of structural categories present.
+Again, all techniques---except for PBE with multiple structural
+categories---yield better retrievals than RLR.
+
+The runtime of the evaluation varied from technique to technique.
+The 400 runs of PBE took 19 hours to complete on a dedicated server.
+This is due to the long time needed for the program synthesis to
+complete, which increases the more training examples are used and
+ranges from about 10 to 30 minutes.
+Running a configured technique takes a similar amount of time for all
+techniques.
+Executing the 400 evaluation runs for CTS took 15 minutes, for KWS 25
+minutes and for RLR 5 minutes.
+
+\begin{figure}[!t]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/success-partial-all.pdf}
+		\caption{Success of chunk retrievals across all
+		techniques.}
+		\label{fig:success-partial-all}
+\end{figure}
+
+\begin{figure*}
+\centering
+    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
+\begin{subfigure}[b]{\columnwidth}
+		\centering
+				\includegraphics[width=\columnwidth,
+				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
+		\caption{Training and test examples in 1
+		structural category.}
+		\label{fig:recall-precision-singlecategory-all}
+\end{subfigure}\hspace{\fill}
+\begin{subfigure}[b]{\columnwidth}
+		\centering
+				\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/big-study/recall-precision-multicategory-all.pdf}
+		\caption{Training and test examples in \textgreater
+		1 structural
+		category.}
+		\label{fig:recall-precision-multicategory-all}
+\end{subfigure}
+\caption{Precision, recall, and F$_{1}$-score of all
+techniques compared, split by structural category count.}
+\label{fig:category-all}
+\end{figure*}
+
+\subsection{Discussion}
+\label{sec:discussion}
+
+Following from the results of the empirical study, in this section,
+we give recommendations for
+which types of log chunks and how many training examples
+each technique is suited, as well as
+how their output can be used further.
+We summarize these recommendations in
+\Cref{tab:single-technique-recommendations}.
+
+\begin{table}[tbp]
+\caption{Recommendations for each of the investigated chunk retrieval
+techniques.}
+\label{tab:single-technique-recommendations}
+
+\resizebox{\columnwidth}{!}{%
+\centering
+\begin{tabular}{lllll}
+  \toprule
+  & & \textbf{PBE} & \textbf{CTS} & \textbf{KWS} \\
+
+	\midrule
+
+	\textbf{RQ2.1} & \textbf{Training Set Size} & 2 & no influence &
+	2 \\
+
+  \midrule
+
+	\textbf{RQ2.2} & \textbf{Structural Categories} & 1 & less
+	is better
+	& \makecell[l]{best 1 \\ multiple okay} \\
+
+	\midrule
+
+  \multirow{6}{*}{\textbf{RQ2.3}} & \textbf{Precision} &
+	\makecell[l]{high \\ (if synthesis succeeds)} &
+  medium & low \\
+
+	\cmidrule{2-5}
+
+  & \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} &
+  medium & high \\
+
+	\cmidrule{2-5}
+
+  & \makecell[l]{\textbf{Confidence in} \\ \textbf{Output Correctness}}
+  & high & low &
+  \makecell[l]{low (precision) \\ high (recall)} \\
+
+	\cmidrule{2-5}
+
+  & \textbf{Output Consumer} & program & human & human \\
+  \bottomrule
+\end{tabular}%
+}
+\end{table}
+
+\subsubsection{Programming by Example (PBE)}
+
+\noindent
+\textbf{With how many training examples does PBE perform best (RQ2.1)?}
+When the training examples are of the same structure, one or two
+two training examples are enough input for PROSE to synthesize a regular
+expression program with good recall.
+In the study, additional training
+examples from the same structural category
+did not improve the chunk retrieval.
+In fact, unless they
+were in some sense redundant, adding more training examples even
+hindered the applicability of PBE.
+
+\noindent
+\textbf{How structurally variable can training examples be (RQ2.2)?}
+The study results show that chunk retrieval with PBE gives best
+results when the log chunks are structurally identical.
+This is
+because PROSE has difficulty synthesizing OR-based
+programs~\citep{mayer2015user}.
+PBE is thus suited to retrieve information
+chunks that always have the same defining surrounding or internal
+structure.
+To extract for example the reason a build failed, the log
+passage describing the failure would always have to start and
+end the same way.
+
+\noindent
+\textbf{How accurate are the retrievals of PBE (RQ2.3)?}
+If the program synthesis succeeds and running the regular expression
+program yields an output, PBE has high precision and recall.
+The technique
+clearly identifies a failing synthesis or when the regular expression
+finds no match on a build log.
+Therefore, if PBE produces
+an output, the user can have high confidence that it is the desired
+output.
+This preciseness makes output from PBE chunk retrieval
+well-suited for machine consumption and therefore automatic onward
+processing.
+
+\subsubsection{Common Text Similarity (CTS)}
+
+\noindent
+\textbf{With how many training examples does CTS perform best (RQ2.1)?}
+The number of training examples had no noticeable influence on
+precision or recall.
+Information retrieval techniques
+like text similarity commonly learn on a higher number of examples
+than we chose in the study.
+Future work should investigate how many
+examples yield improvements in the chunk retrieval over a single
+training example.
+
+\noindent
+\textbf{How structurally variable can training examples be (RQ2.2)?}
+CTS yields better results the
+fewer structural categories are present in the training and test
+examples.
+
+\noindent
+\textbf{How accurate are the retrievals of CTS (RQ2.3)?}
+CTS has good precision and recall on average, though with a high
+variation.
+This means that the quality of an output by CTS is hard to
+determine, which makes it unsuited for automatic processing and requires
+a human to further inspect and interpret the output.
+This could include semi-automated procedures such as sending
+developers an email with the extracted build failure reason.
+
+\subsubsection{Keyword Search (KWS)}
+\noindent
+\textbf{With how many training examples does KWS perform best (RQ2.1)?}
+Going from one to two training examples, KWS's recall improves
+significantly.
+However, further enlarging the training set
+does not lead to further improvements.
+
+\noindent
+\textbf{How structurally variable can training examples be (RQ2.2)?}
+KWS has a higher recall than the two other techniques for multiple
+structural categories present in the training and test examples.
+This
+makes KWS a good technique if there is little prior knowledge of how
+the targeted log chunk is represented in the build log.
+For the
+example of extracting the reason the build failed, KWS is best suited
+if a build can fail in various steps logged by different build
+tools and no
+pre-categorization of where the build failed is available.
+
+\noindent
+\textbf{How accurate are the retrievals of KWS (RQ2.3)?}
+While KWS has the highest recall of all three techniques, its
+precision is the lowest.
+The output of a chunk retrieval with KWS is
+well-suited to be read by humans, but ill-suited for consumption by
+automated tools.
+
+\subsection{Usage Recommendation}
+In this section, we derive a decision tree to help practitioners and
+researchers choose a suitable chunk retrieval technique.
+We then
+illustrate its use on two examples.
+
+\subsubsection{Derivation of Decision Tree}
+\begin{figure}[bt]
+		\centering
+		\includegraphics[width=\columnwidth,
+		clip]{img/crt-recommendation.pdf}
+		\caption{Decision tree for chunk
+		retrieval techniques.}
+		\label{fig:crt-recommendation}
+\end{figure}
+
+Abstractly, we have learned that every chunk retrieval technique
+differs in its suitability depending on the kinds of logs it should
+operate on and the sort of output one expects.
+In this section, we
+unify these findings, culminating in the creation of a decision tree
+to help developers and researchers choose an adequate technique in
+\Cref{fig:crt-recommendation}.
+
+The first and most important aspect that influences the decision for a
+chunk retrieval technique is the presence of different structural
+categories in the log (or lack therefore).
+Are the targeted log
+chunks always present in the same structural way
+within the build logs? If so, the chunks
+in all training examples and the analyzed build log are in the same
+structural category (first question in \Cref{fig:crt-recommendation}).
+
+On the leftmost path of the decision tree,
+when the chunks are from one structural category and the user
+needs high confidence in the correctness of the output or prefers
+no output over output with low recall, we recommend PBE\@.
+If the user does not
+require high confidence in the correctness of the output and prefers
+to receive some output even with low recall, we recommend CTS\@.
+
+On the rightmost path of the decision tree,
+if the chunks are from multiple structural categories and recall is
+more important than precision, we recommend to use KWS\@.
+If precision is more important than recall, we
+recommend CTS\@.
+
+As a final recommendation, one could create a ``super analyzer'' by
+combining the different build log analysis techniques studied in this
+paper.
+Such a super analyzer would likely always first employ PBE
+(because of its high accuracy), followed by a combination of CTS and
+KWS\@.
+Other than initial setup and training time, there is no
+downside to this approach if it is implemented in a transparent way:
+the output of the super analyzer could include from which
+sub-technique it originated and thus facilitate automatic onward
+processing or interpretation of the result.
+
+\subsubsection{Example Use Cases}
+To illustrate how one would use the decision tree to find a suitable
+chunk retrieval technique we describe here two concrete examples:
+a software team monitoring build performance and a
+group of researchers investigating why builds fail.
+
+In the first example, a software development team wants to monitor
+the performance of the phases within their CI build.
+They are using
+Travis CI, which documents the duration of build phases
+within the build log.
+As all relevant log statements are formatted the same way,
+the targeted log chunks are from one structural category.
+Therefore, following the leftmost path in
+\Cref{fig:crt-recommendation},
+they should use PBE.
+
+In the second example, researchers wants to investigate the names
+of test cases that cause build failures.
+Their study should cover a wide range of test tools, therefore are the
+log chunks they target in various, non-predictable structural
+representations.
+As they have to manually inspect the results of both CTS
+and KWS, they prefer higher recall over higher precision to
+avoid inspecting
+the whole log in case the relevant chunk was not retrieved.
+Therefore, following the rightmost path in
+\Cref{fig:crt-recommendation},
+the decision tree recommends the researcher to use KWS\@.
+
+An alternate, more precise solution
+could be for researchers to first separate the build logs by the
+test tool responsible for logging the results.
+Then, the
+targeted log chunks are from one structural category and they can use
+PBE, trained with examples from each test tool separately.
+
+\section{Threats to Validity}
+In this section, we outline threats to the validity of our work and
+show how we mitigated them.
+
+% M: fill in the maven analyzer plugin and others.
+% C: added to the jenkins bl analyzer, though I left out th maven
+% analyzer cause it has 1 star on github so kinda not 'industry' grade
+\textbf{Limitation to Scholarly Articles.} We limited our literature
+survey to scholarly articles.
+However, the field of build log analysis is extremely relevant to
+practitioners, too.
+While it is difficult to systematically sight all such non-scientific
+material, we ran several Google search queries related to build log
+analysis and evaluated them informally.
+Our findings include the Jenkins build log
+analyzer~\citep{jenkins2020failure-analyzer}, where a user can
+define custom regular expressions to parse a build log, and a web page
+on which Microsoft details how its CI service, Azure Pipelines, uses a
+PBE approach for certain log formats such as Python.
+This inspired the choice of PBE in \Cref{sec:choice}.
+Our impression is that non-scientific tools are often based on
+parsing with the help of regular expressions---similar to the
+techniques mentioned in scientific literature and the PBE technique
+we proposed.
+
+\textbf{Implementation.}
+Our results depend on the implementation of the investigated chunk
+retrieval techniques and the libraries we used.
+
+The program synthesis
+provided by PROSE is the basis for our implementation of PBE\@.
+The
+idiosyncrasies of this framework influence the PBE results.
+Other
+frameworks similar to PROSE might have somewhat different strengths
+and weaknesses.
+For example, the need for examples from a single
+structural category stems from the fact that PROSE cannot learn
+regular expression programs with arbitrary boolean conjunctions and
+disjunctions~\citep{mayer2015user}.
+PROSE introduced this constraint
+to keep the synthesis performance reasonable.
+At the same time, this
+is clearly a current theoretical challenge of all PBE implementations,
+and we therefore attribute it to the technique itself, rather than the
+specific implementation.
+
+Similarly, the library
+{\tt text2vec}~\citep{text2vec2019webpage}
+and the way it splits strings into word tokens is influencing
+our implementation of CTS\@.
+On the other hand,
+{\tt text2vec} is the de-facto standard library to do word embeddings
+in R.
+We intentionally chose a simple, minimally configured or tuned
+approach to compare against.
+Tuning the text similarity
+meta-parameters more to the specific use case of chunk retrieval from
+build logs would yield better chunk retrieval results.
+
+Overall, we believe our implementations and their weaknesses stand
+prototypical for the techniques.
+We tried to limit idiosyncrasies as
+much as possible, by choosing standard approaches and minimizing
+configuration, instead of parameterizing and fine-tuning methods
+specific to our data set.
+
+\textbf{Data Set.}
+Just like the implementations, the specific build logs from the
+\emph{LogChunks} data set affect
+the outcomes of the comparison study.
+\emph{LogChunks} consists of build
+logs from open source projects and therefore it is unclear to which
+degree our results apply to industry projects that use build tools not
+popular in open source development.
+However, since \emph{LogChunks}
+covers a wide array of build tools and programming languages, we
+believe that the findings do generalize.
+In addition, build log output
+of such a tool would need to be wildly different from how the over 27
+tools covered in our study do it---this seems unlikely.
+
+We collected build logs from
+Travis CI.
+Yet, the format of the log chunk we chose for the
+evaluation is largely independent of Travis CI\@, because the reason
+the build failed is described within the build logs by the tools
+themselves and not the Travis CI environment.
+
+\textbf{Training Set Size.}
+Especially the results for CTS might be influenced by the fact that we
+only trained on one to five examples.
+We chose this small training
+set size as a human has to provide the training examples and one of
+the central aims of the chunk retrieval techniques is that they can be
+set up wit little effort.
+The fact that KWS and CTS performed best
+with already two training examples indicates that the maximum training
+set size of five is sufficiently large for research evaluation.
+
+\textbf{Few Samples with Many Structural Categories.}
+Our comparison study includes fewer measurements with many structural
+categories than with one structural category category.
+50\% of the measurements were conducted with one structural category
+in the training and test sets
+(34\% with two, 16\% with more than two categories).
+This distribution mirrors the
+structural categories in a real-world data set, where there were
+mostly few structural categories within one project.
+In addition, the
+third of the measurements we conducted with two structural categories
+already showed the negative effect of an increasing number of
+structural categories on the performance of the chunk retrieval
+techniques.
+
+\section{Future Work}
+In this section, we give an outline of fruitful future
+research directions in the field of build log analysis.
+We base our
+suggestions on the results of the literature survey and the
+findings from our technique comparison study.
+
+\textbf{Systematic Survey of Industry Approaches for Build
+Log Analysis.}	Our survey is limited to scholarly material.
+However,
+handling build logs is a challenge for a wide range of practitioners
+as well.
+We propose to investigate the techniques used in industry to
+analyze build logs.
+An example is the
+Jenkins \emph{build-failure-analyzer}
+plugin~\citep{jenkins2020failure-analyzer} or automatically inferred
+test results in Azure~\citep{azure2020inferred}.
+Such a study might
+also need to tackle the more abstract problem of how to survey
+non-scholarly material systematically, which might be an important
+contribution to Software Engineering research.
+
+\textbf{Further Analysis of \emph{LogChunks}.}
+We created the
+\emph{LogChunks} data set \citep{brandt2020logchunks} specifically for
+the comparative
+study in this paper, though it can be the basis for various further
+analyses of build log data.
+For example, we can investigate the keywords to answer which
+keywords developers use to mark errors that lead to a build failure
+within build logs.
+
+\textbf{Cross-Project Build Log Analysis.}
+We trained and
+tested each chunk retrieval technique on examples from the same
+project.
+We propose to analyze how techniques could be trained
+across projects, building the cornerstones for build
+environment-agnostic analysis tools.
+This has the advantage of creating
+a default build log analyzer that would work without any pre-training.
+
+\textbf{Comparison with more Chunk Retrieval Techniques.}
+In this article, we investigated the three chunk retrieval techniques PBE,
+CTS, and
+KWS\@.
+Our study design can be reused to evaluate other build log
+analysis techniques, such as for example deep learning-based
+techniques (discussed in \Cref{sec:choice}) or manually-written
+programs such as the parser Tomassi et al.
+created for
+BugSwarm~\citep{tomassi2019bugswarm} or the regex-based approach
+Beller et al.
+created for TravisTorrent~\citep{beller2017oops}.
+
+One could also interpret the techniques we implemented
+differently.
+For example, for CTS, we look for similarity between the
+lines we want to extract.
+One could find similarity between the
+context that surrounds them, instead of the actual chunk to be
+extracted.
+The intuition behind this approach would be that often the
+error chunk is variable, but the context around it is
+stable---essentially the principle by which extraction by PBE
+works.
+Such a version of ``inverse CTS'' might yield better retrieval
+results.
+
+\textbf{Refinement of Retrieval Quality.} We
+investigated basic configurations of existing techniques applied to
+chunk retrieval from build logs.
+In a next step, each of these
+techniques could be refined to better customize it to the domain of build
+logs.
+The \emph{LogChunks} data set and our study results can act as a
+baseline to benchmark such technique improvements.
+We propose the
+following improvements:
+\begin{itemize}[leftmargin=0.4cm]
+  \item \textbf{Custom Ranking and Tokens for PBE.} Program
+  synthesis through PROSE ranks possible programs according to
+  what the user most likely intended.
+  One could adapt the ranking
+  rules provided by the \emph{FlashExtract} DSL to fit common build log
+  chunk retrieval tasks.
+  \emph{FlashExtract} includes special tokens when
+  enumerating possible regular expressions~\citep{le2014flashextract:}.
+  One could extend these
+  with tokens found in build logs, such as ``-,''
+	``=,'' ``ERROR,''
+  or ``[OK]'' to improve results.
+  \item \textbf{Meta-Parameter Optimization for CTS.} Information
+  retrieval techniques have various meta-parameters which can be
+  optimized for the specific use
+  case~\citep{panichella2016parameterizing}.
+  We propose to further
+  investigate improvements in preprocessing of the log text, in
+  tokenization of the log lines into terms, and in stop words
+  lists.
+
+  For CTS, we currently have no concept of semantic
+  similarity.
+	Therefore, the synonyms ``Fail'' and ``Failure'' would
+  fall into two different frequency counts.
+	Using a
+  wordnet~\citep{pedersen2004wordnet} or other NLP techniques to
+  capture synonyms might improve similarity measure between related
+  lines, and therefore overall performance of CTS.
+\end{itemize}
+
+\textbf{Usability Analysis of Chunk Retrieval Output.}
+Our
+analysis of the chunk retrieval output focuses on
+precision and recall.
+A next step could be to investigate how useful these
+outputs really are to developers through controlled experiments or
+user studies.
+
+\section{Conclusion}
+\label{sec:conclusion-fw}
+
+The goal of this paper is to support practitioners and researchers in
+their decision on how to analyze build logs.
+To this end, we
+conducted a systematic mapping survey to map out the available build
+log analysis techniques.
+We saw that build log analysis is an
+emerging field.
+At the same time, articles largely do not justify why
+they use a certain technique, nor do they document it in detail or
+open-sourced its implementation.
+Moreover, the survey showed that,
+while there is a niche for custom parsers and plugins for very popular
+tools such as the Java ecosystem, there is a wide variety of build
+tool and environment combinations for which the creation of such
+bespoke tooling is unlikely.
+Overall, this study showed the need for a new
+generation of generic and automated build log analysis techniques that
+need little effort to set up, both for practitioners as well as
+researchers.
+
+Based on common approaches we observed in literature,
+we implemented three promising chunk retrieval techniques:
+PBE synthesizes regular expression programs based on examples of logs
+and corresponding chunks, CTS leverages a common text similarity
+measure to retrieve those lines which are most similar to example
+chunks, and KWS finds the targeted chunks in a build log by searching
+for identifying keywords.
+
+We evaluated the performance of these chunk retrieval techniques on the
+\emph{LogChunks} data set and saw varying results.
+CTS had the highest average F$_{1}$-score with 51\%, while the other
+techniques showed higher average scores for precision (95\%, PBE) and
+recall (70\%, KWS).
+Overall, all techniques vastly outperformed a
+baseline of random line retrieval.
+
+To guide researchers and developers on which technique suits their
+use case,
+we summarized our results in a decision tree.
+We found
+that the structural representation of the targeted information in the
+build logs is the main factor one should consider when
+choosing a build log analysis
+technique.
+Secondary factors are the desired confidence in recall and
+precision of the produced output and whether precision or recall is
+more important for the task at hand.
+
+Finally, we gave an
+outline to guide future research efforts in the area of build log
+analysis.
+Important themes are a systematic investigation of industry approaches,
+benchmarks of existing build log analysis approaches, and further
+refinement of the chunk retrieval techniques we proposed.
+We strongly believe that further research into the techniques to
+analyze build logs will support researchers and developers alike to
+leverage the vast amounts of valuable information hidden
+in build logs.
+
+%\begin{acknowledgements}
+%If you'd like to thank anyone, place your comments here
+%and remove the percent signs.
+%\end{acknowledgements}
+
+% Authors must disclose all relationships or interests that 
+% could have direct or potential influence or impart bias on 
+% the work: 
 %
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
-% Computer Society journal (but not conference!) papers do something unusual
-% with the very first section heading (almost always called "Introduction").
-% They place it ABOVE the main text! IEEEtran.cls does not automatically do
-% this for you, but you can achieve this effect with the provided
-% \IEEEraisesectionheading{} command. Note the need to keep any \label that
-% is to refer to the section immediately after \section in the above as
-% \IEEEraisesectionheading puts \section within a raised box.
-
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps (small caps for compsoc).
+% \section*{Conflict of interest}
 %
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by the IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-% \IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
-% for IEEE Computer Society journal papers produced under \LaTeX\ using
-% IEEEtran.cls version 1.8b and later.
-% % You must have at least 2 lines in the paragraph with the drop letter
-% % (should never be an issue)
-% I wish you the best of success.
-
-% \hfill mds
-
-% \hfill August 26, 2015
-
-% \subsection{Subsection Heading Here}
-% Subsection text here.
-
-% % needed in second column of first page if using \IEEEpubid
-% %\IEEEpubidadjcol
-
-% \subsubsection{Subsubsection Heading Here}
-% Subsubsection text here.
-
-\input{content.tex}
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-% However, the Computer Society has been known to put floats at the bottom.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-
-% \section{Conclusion}
-% The conclusion goes here.
-
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-
-% \appendices
-% \section{Proof of the First Zonklar Equation}
-% Appendix one text goes here.
-
-% % you can choose not to have a title for an appendix
-% % if you want by leaving the argument blank
-% \section{}
-% Appendix two text goes here.
-
-% use section* for acknowledgment
-% \ifCLASSOPTIONcompsoc
-%   % The Computer Society usually uses the plural form
-%   \section*{Acknowledgments}
-% \else
-%   % regular IEEE prefers the singular form
-%   \section*{Acknowledgment}
-% \fi
-
-% The authors would like to thank...
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
+% The authors declare that they have no conflict of interest.
+
+% BibTeX users please use one of
+\bibliographystyle{spbasic}      % basic style, author-year citations
+%\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{spphys}       % APS-like style for physics
+%\bibliography{}   % name your BibTeX data base
 
@@
 
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-\begin{IEEEbiography}{Carolin E. Brandt}
-Biography text here.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}{Moritz Beller}
-Biography text here.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-% \begin{IEEEbiographynophoto}{John Doe}
-% Biography text here.
-% \end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-% \begin{IEEEbiographynophoto}{Jane Doe}
-% Biography text here.
-% \end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
 \end{document}
+% end of file template.tex

### 2021-03-12 tse-paper/rebuttal.tex
add first version of 'rebuttal' doc, update lit survey process figure

\documentclass[10pt,a4wide]{article}
\usepackage[paper=a4paper,margin=0.85in]{geometry}
\usepackage{relsize}
\usepackage{paralist} % so that compactitems and enumerations can be made more compact
\usepackage{graphicx}
\usepackage{url}
\usepackage{booktabs}
\usepackage{color}
\usepackage{boxedminipage}
\usepackage{wasysym}
\usepackage{framed}
\usepackage{etoolbox}

% Vertical line that highlights quotations in an email.
% Use \begin{leftbar} and \end{leftbar} environment.
% Width of the line = 0.4pt
% Space between the line and the text = 15pt
% Requires \usepackage{framed}
\renewenvironment{leftbar}{%
	\vspace{0.1cm}
	\def\FrameCommand{\vrule width 0.4pt \hspace{15pt}}%
	\MakeFramed {\advance\hsize-\width \FrameRestore}}%
{\endMakeFramed\vspace{0.1cm}}

\makeatletter
% uncomment the following if you don't want \clubpenalty\@M ...
% \let\nearly@afterheading\@afterheading
% \patchcmd\nearly@afterheading
%   {\@M}% original temporary setting for \clubpenalty replaced by ...
%   {\@clubpenalty}% ... or whichever value you deem right
%   {}{}
% ... and use \nearly@afterheading instead of \@afterheading here:
\newcommand*\NoIndentAfterEnv[1]{%
	\AfterEndEnvironment{#1}{\par\@afterindentfalse\@afterheading}}
\makeatother

\NoIndentAfterEnv{leftbar}

\begin{document}

\title{\textbf {--- Rebuttal ---}}
%{\small {A Controlled Experiment for Program Comprehension through Trace Visualization}}}

\date{}
\maketitle

\vspace{-1cm}

\begin{tabular}{|lp{11cm}|}
\hline
%\textbf{Manuscript number} & \\
\textbf{Original Title} & 
How to Analyze Build Logs: A Systematic Survey and Comparative Study of Chunk Retrieval Techniques \\
\textbf{Authors} & Carolin Brandt, Moritz Beller\\
\textbf{Corresponding author} & Carolin Brandt (c.e.brandt@tudelft.nl)\\
\textbf{Revision date} & TODO \\ %\date October 1st, 2020\\
\textbf{Journal} & IEEE Software \\
\hline
\end{tabular}
\vspace{1cm}

\noindent
Dear Editor,\\
Dear Reviewers,
\\\\
\noindent

We thank reviewers for their in-depth and constructive feedback. All reviewers are
positive about the relevance of the paper for IEEE Software’s
readership (assessing it Very Relevant or Relevant). Reviewer 2 calls it a “great paper” and
Reviewer 1 “clearly written and easy to read,” “highly relevant and
fits well for IEEE Software and its target audience.” Reviewer 3,
while being perhaps most critical overall, notes that “[the paper]
focuses on a much needed dual perspective integrating the developer’s
own perception to measure productivity. The paper is very well
motivated and overall easy to read.”

That said, there were a number of points that needed to be changed in the paper, in particular as regards scope and structure. We have made several improvements to
the paper following your recommendations for this major revision.  Key changes include:
\begin{itemize}
\item Re-structuring the manuscript, by putting visualizations into a side bar to make the article focused on the productivity study alone.
  \item Adding further details on study methodology and execution to the Telemetry and Regression Model sections while keeping the spirit of a light-weight, practitioner-oriented paper. In particular, we made the section on regression models easier to read for readers without a statistics background. 
\item Fixing the detailed remarks by the reviewers (throughout the paper).
\end{itemize}

\noindent
Below we outline the remarks from the reviewers and our response in e-mail quotation and 
answer style.
\\
\\
%\noindent
Best regards,
\\
Carolin Brandt and Moritz Beller
\\\\
\noindent

\begin{leftbar}

\end{leftbar}

\section*{Editor Comments}

\begin{leftbar}
The reviewers identified a number of severe limitations that must be addressed before the paper can be reconsidered for publication. The reviewers reported that the paper is too long and difficult to read; a general reorganization is needed to make the intended contribution more accessible. The reviewers also called for a discussion of motivations for this work and highlighted several conceptual limitations in the study. The presentation of results must be improved to better highlight strengths and weaknesses of the techniques; implications for researchers and practitioners must be better discussed. Comparison among techniques and literature review needs improvements, too. The accurate concerns of reviewers are so serious and numerous that addressing them means doing further substantial work. This is not to say that this work has no interest or value. Indeed, the reviewers agree that the paper deals with a relevant problem; some further work along the detailed directions indicated by the reviewers might result in a better contribution.
\end{leftbar}

\subsection*{Reviewer 1}

% \begin{leftbar}
% 1. Scope and structure of the manuscript need to be reconsidered. As noted by Reviewer \#1 and Reviewer \#3, the title does not properly reflect the content of the manuscript. Also, as Reviewer \#2 and Reviewer \#3 noted, the relationship between what seem to be two separate studies (study to understand the gap between self-reported and measured productivity *and* user study to evaluate personalized reports) is not clear. Furthermore, Reviewer \#3 suggests focusing the scope of the manuscript.

% \noindent
% -$>$ Title does not reflect content \\
% -$>$ Relationship between two studies unclear \\
% -$>$ Reviewer 3: focus scope?
% \end{leftbar}

\begin{leftbar}
The authors conducted a literature review to better understand prior approaches that analyze build logs to identify build failures. Then, the authors proposed and evaluated three novel approaches to identify build failures.

The paper provides a good contribution to log analysis literature. However, I believe that the paper should benefit from a large body of improvements. The paper is very difficult to read, I had to go back and forth to understand many sections and many details appear too late in the paper. I have some concerns about the literature review, their 3 proposed approaches, as well as the evaluation of the approaches. More details are below.

Abstract: mention the exact number of studied log files and projects.

Introduction:

The authors mention that a guideline on when to use which of their three proposed techniques is a contribution. I think this is just a discussion of the evaluation and not a novel contribution.

The paper also mentions a set of ideas for future work. That is part of a future work section and not a contribution by itself.

The authors mention in Figure 1 that they propose 3 “promising” approaches. Why they are promising?

Section 2:

The authors performed backward snowballing to include more papers to their literature study. However, they missed the forward snowballing.

The authors mentioned that they used Google scholar to find their papers. They should instead use official scientific publications databases as suggested by Petersen et al. (the guideline the authors followed for the literature review) as well.

The paper mentions that the first author and the second author first studied five papers, then discuss when disagreement occurs to find a consensus. Then, each of the two authors studied a separate number of papers. I think that five papers are too low number and the disagreement should be discussed in the paper. That is because if the two authors disagree on all the classifications of the first 5 papers, they are more likely to disagree on the classification of the remaining papers. By the way, why 5? 5 is not even 10% of the studied papers. So, I suggest that the authors revise more papers and report some (dis)agreement measurements.

The authors used just one keyword search (i.e., “build log”). What about other search keywords? E.g., build trace.

Could you provide more details on how you excluded the papers that are related to system logs? I would suggest adding a table that summarizes the inclusion, exclusion criteria and the rationale behind each of them.

Extension papers should not be excluded. That is, in particular, because the authors discuss the approaches that are proposed in the literature and their limitations. Maybe, some limitations are addressed in the extension and not in the original paper.

Subsection 2.4.1 is not part of the results of the paper. In other words, where the papers are published is not the goal of the paper or the analysis, so it’s not a result. You might include 2.4.1 in 2.3.

Change figure 5 to a table that shows which papers focus on which category so readers can go back to the papers that consider a given category. That table should also include a description of each category.

The following finding is not clear: “The majority of works (46%) used the outcome of their build log analysis to drive future research”, what this 46% are doing or what kind of suggestions they are providing for future work?

“31% claim to have published their data”. What do you mean by claim? Did they publish their data or not? or did they put a link to their data and that link is not working?

Please add a description to each log analysis technique to Table 1, and no need for a barplot to show the frequency in the last column of the table. You can put just a number and save some space for the description. That is in particular since the definition of the categories of Table 1 is scattered all over the Section.

You can’t make the following association: “we rarely saw works justifying why they use a certain technique to analyze build logs as there is a general lack of guidance on when to use which technique”. That is because you can’t know why the authors didn’t justify why they use a technique.

Section 3:

What is the difference between the existing approaches and your three approaches?

From where are your 3 proposed approaches coming from? Although the authors claimed that “previous work seemed to choose a log analysis technique arbitrary ...” in Section 4, they didn’t justify their approaches neither.

The authors claim that some of the existing approaches are not generalizable to all the projects. The question is why the generalizability matters. One doesn’t need for her project something that is generalizable to others’ projects.

The authors mention “techniques … based on deep learning, are thinkable, but we did not evaluate them in this article since they did not emerge from the literature survey”. I do not fully understand this. Does it mean that these techniques exist, but you missed them on the literature review? So the literature review is incomplete. Or are the deep learning techniques not used at all in the build log analysis, so no need to even mention them in the paper.

3.3., 3.4., 3.5 are so difficult to understand. Support these sections with examples (instead of having a subsection of examples that comes very late, i.e., 3.5).

Fig. 7.a is no explaining “why” Android build failed, it’s showing just the symptom of an error. So update the caption of the figure accordingly.

KWS comes after CTS in Table 2, while CTS comes before KWS in the textual explanation; so switch the order of KWS and CTS either in the text or in the Table.

A major concern I have about the baseline approach that is used in the evaluation. It’s not clear why the authors compared their three novel approaches to a random-based approach instead of comparing their approaches to the existing studies or at least to state of the art approaches?

Section 4:

Section 4.3 is almost just repeating figures with very few discussions.

The authors didn’t define what they mean by the “structural category” when most of the evaluation is around that word. I had a hard time to deduce what it means.

The authors classified the recalls into three categories: successful (i.e., recall = 1), unsuccessful (i.e., recall = 0), and everything in between is classified as partially successful. That is not fair since the recall of 0.001% and the recall of 99.9999% will be the same.

Do you measure precision and recall at the file or project level? By the way, what is the distribution of log files across the projects that you studied? Does the evaluation consider projects separately?

Do you consider a training set from different projects or do you train and test within the same project? That should be discussed and justified.

For Fig. 12, I’m wondering what one example means? Are you able to accurately identify the chunks from one example? It’s surprising. How come the approach is that good from one example? That comes to another concern, can you discuss the why of your evaluation. Why the approach works well and why it doesn’t work well?

For Fig. 15, why do you use a barplot instead of a violin plot similar to the other figures? That what also triggered my comments about how do you conduct the evaluation and which data do you consider in the training and testing (i.e., do you train and test the approach on the whole data level, at a project level, or at a file level).

You can’t report the execution time since you are using different infrastructures for each of your approaches. E.g., you used C\# for one of the three approaches, and R for another approach. So, you can’t know if one approach is slower than the other approaches because of the approach itself or because it’s developed on a given programming language (e.g., R). For example, R loops are much slower than C\# loops.

A lot of terms are used but never defined, which makes the paper difficult to read. E.g., what OR-based programs are? Please double-check this problem throughout the whole paper.

Fig. 16, use a statistical approach (e.g., Wilcoxon test) to compare the four approaches (i.e., the three approaches and the baseline).

Section 5:

I don’t get what is the threat to validity on the implementation and the dataset? E.g., “text2vec … is influencing our implementation of CTS”. How it is influencing? What is the threat here and how did you mitigate it?
\end{leftbar}

\subsection*{Reviewer 2}

\begin{leftbar}
1. Paper summary
-----------------------------------------
This paper provides a literature mapping survey in the emerging field of build log analysis. In a subsequent phase, the authors have developed three prototypical implementations for analyzing build logs. Their implementations have been validated through an empirical study on 797 build logs extracted from different projects written with a variety of programming languages and using different build automation tools.
Their findings point out that there is no technique that is always better than the others. Indeed, based on the strengths and weaknesses of each technique, they provided guidelines on when to choose a specific technique.

2. General Evaluation
-----------------------------------------
The paper addresses a very hot topic in the software engineering field; the study methodology for the literature mapping study is sound while the methodology adopted in the second phase is not completely clear and have some weaknesses. Finally, there are no practical implications. Most of the strengths and weaknesses seem to be related to the technique itself and are not related to their application to the emerging field of build logs analysis.
Looking at the comparison among the different techniques, the methodology used is completely hidden, e.g., have you trained your implementations by project? and how many build logs for each project do you have? or How different are in terms of information the build logs in your dataset per each project? and are your approaches aimed only at analyzing build failures?
Finally, looking at the decision tree constructed for identifying the best technique to adopt, it seems to follow the technique and not the technique applied to the build logs. So, I do not think that your result as is, is ready for publication and is ready to be used by practitioners and/or researchers.

3.Points in Favor
-----------------------------------------
-Interesting literature mapping survey.
-Appropriate identification of related literature.
-Interesting topic.

4. Points against the paper
------------------------------------------
-No practical usage of your findings.
-No novelty in the provided results, strengths and weaknesses due to the techniques and not to their application on build logs (obvious results).
-Study methodology not completely clear with some hidden details.

5. Suggestions for improvement
-------------------------------------------
-Looking at the literature review, among the 61 works are there some works that justify the reasons behind the adoption of a specific technique? This information has to be reported in the paper, and in presence of this information, it may be of interest to see how the results of the second phase are in line with what already stated in the literature. You state only that this occurs only rarely but I think that you need to go deeper on this, instead of only looking at which kind of information are developers/researchers looking at.
-Your results are provided without discriminating among different build automation tools. Since the community knows that different build tools generate differently structured build logs it may be of interest to check whether there exists a technique that is able to work the best while applied to a specific kind of build automation tool.
-Among the RQ1 results, you state that there is a need for defining a more generic solution for extracting useful information from build logs. However, both the design and the results in RQ2 do not seem to go in this direction.
-Another unclear point while reporting the study methodology for RQ2 is how are your prototypical implementations generalizable? Each technique requires the identification of training examples. These ones have to be changed each time the build process changes into the system.
-You stated that KWS is automatized, but how? How do the keywords have been defined? How the keywords can be generalized to different build automation tools and for different purposes?
-Even if you have provided a section with a concrete example, it is unclear to me how your approach effectively works. In order to create regular expressions, PBE needs to have input/output chunks so can you be more detailed on how to run your techniques? What is the current input being provided? The same happens for the CTS where you talk about a search query to be compared with each line inside your build log but what is the search query you have used in your study?
-In Section 3.6 you have defined a random baseline, however, a more realistic case to compare with is the one that only looks at the lines in the bottom part of the build logs. Usually, there you can find a possible reason for the failure. So think about using a different baseline.
-The context of your study misses important information: how many different build automation tools are in your dataset? How many build logs do you have for each different build tool? What is the distribution of build logs by project in your dataset?
-Clarify whether while running your techniques you have done a training phase per each project. The latter requires the answer to my previous point.
-While comparing the results provided by the different techniques, did you have computed the metrics by project and then you have averaged the results? Please be more specific here otherwise it is not possible to follow the provided results.
-As regards the presentation of your results, please clarify and discuss the results in each figure being attached to the paper, as well as make them more readable. The discussion phase may help the readers in understanding the guidelines you provide as the outcome of this study.
-It may be of interest to know in how many of the 61 works the technique being used does not follow your guidelines. If the guidelines are always met probably researchers/developers do not need more guidance on this.  
\end{leftbar}

\subsection*{Reviewer 3}

\begin{leftbar}
Build logs contain important information about the build process, and it is essential for software engineers to analyze these logs to investigate build errors and test failures. However, understanding the extensive build logs generated is a tedious task. Therefore, a foremost step in build log analysis is the retrieval of the relevant information.  The authors' goals are to provide a comprehensive view of the existing techniques to extract relevant information from build logs and evaluate them. In order to achieve goals, the authors performed a Systematic Literature Review in the general area of build log analysis then implemented and evaluated three of the ten identified techniques.

The manuscript is well-written and presents substantial effort and different methods to convince readers about the importance of building log analysis. However, the manuscript presents some major issues.

**Motivations issues**

One of the soundness issues in the manuscript is the lack of consistent motivation. The motivation is supposedly motivated by two references. From reference [5], the authors claim that

“This manual activity is tedious and prone to errors [5].”

However, the reference [5] is a non-peer-reviewed manuscript of

M. Santolucito, J. Zhang, E. Zhai, and R. Piskac, “Statically verifying continuous integration configurations,” arXiv preprint arXiv:1805.04473, 2018.

And analysing Santolucite et al. [5] draft, we found that

“We demonstrate the functionality of VeriCI by using a real-world example of a TravisCI build failure from thesferik/railsadmin repository (bbenezech 2016) on GitHub. [...]  Manually checking the log information is a tedious process and it is very difficult to gain any helpful information for understanding or correcting the issue.”

Thus,  it is possible to conclude that the motivation claim is an anecdotal observation from a non-peer-reviewed article.

The second reference is from a previous work from one of the authors

[2] M. Beller, G. Gousios, and A. Zaidman, “Oops, my tests broke
the build: An explorative analysis of travis ci with github,”
in Proceedings of the 14th IEEE/ACM International Conference on
Mining Software Repositories (MSR). IEEE, 2017, pp. 356–367.

The manuscript presents the fact from the reference that a single build log can be over 50 megabytes Large [2]. However, in paper [2], there is any discussion about the size of build logs. There is only

“As a consequence, the amount of information we can extract from a build log varies perbuild technology used.”

Thus, the manuscript lacks soundness and reliability when 1) it uses as motivation a non-peer-reviewed paper to present a general statement from anecdotal observation, and 2) it uses a previous work to present an incorrect observation.

Unfortunately, the manuscript presents essential soundness issues that compromise the main motivation and reliability, and it could not be relevant if the motivation arguments are false.  Please, address those issues with more robust evidence about the problems with build log analysis.

Assuming that build log analysis is not an actual problem, the main RQ  “What is the state-of-research to analyze build logs?” is irrelevant. Moreover, the claim “In summary, the outcome of our literature survey shows the need for a new generation of automated techniques to analyze build logs,” could be false, because if build log analysis is not an actual problem to engineers, it is evident that there is not in the literature solutions for a possible irrelevant problem.

However, I will assume the authors will provide strong evidence to support the claim that build log analysis is an important issue that justifies automatic mechanisms of log analysis in a new version of the manuscript to continue this report.

**Log conceptual issues**

Log mining/management solutions include three phases log collection, log abstraction/parsing and log analysis. The log abstraction component is responsible for abstracting the unstructured log messages in a log dataset into a structured log event list that is then inputted in the log analysis component. Also, log abstraction is a two-tier process - first, log message templates (or another form of matching rules) must be found (discovered), and only after that can be the incoming log messages abstracted into higher-level representations (matched).

Thus, the authors fail (1) to clearly distinguish between the log abstraction step and the log analysis step and (2)  to distinguish between the log abstraction two separate phases.  Therefore, we suggest the authors (1) clearly distinguish between the log abstraction step and the log analysis step; (2)  highlight the two phases of log abstraction separately. I suggest the authors observe the discussion from the paper “A systematic literature review on automated log abstraction techniques, Information and Software Technology 122 (2020)”  for further detail and description on log abstraction/parsing and as a related paper.

Besides, it would be beneficial for the readers to give an illustrative example of a build log to show how a system log differs from a build log. I suggest the authors add a section on build logs format and where/how they are created.

**Systematic mapping issues**

I am concerned about the use of Google scholar alone for an SLR. The authors could complement their search strategy with at least another source such as Scopus, Engineering village, IEEE xplore or ACM library to ensure the rigour, completeness, and repeatability of the process.

The authors did not perform a quality assessment filtering on the retrieved papers. If they did, I suggest the authors should clearly describe their quality assessment strategy and their quality assessment criteria. It is particularly important because the authors are considering grey literature in their SLR.

Why did the authors not perform forward sampling as well? The authors should add a justification for their decision. Also, please, describe in the manuscript the number of backward snowball levels were applied.

What are the inclusion/exclusion criteria for the third filter?

To evaluate the search string, I performed a simple search in Google Scholar using [“build log analysis"]. Surprisingly, I found several papers in which should be evaluated in systematic mapping. For example, why the papers

“Hirebuild: An automatic approach to history-driven repair of build scripts
F Hassan, X Wang - 2018 IEEE/ACM 40th International …, 2018 - ieeexplore.ieee.org”

What are the factors impacting build breakage?
Y Luo, Y Zhao, W Ma, L Chen - 2017 14th Web Information …, 2017 - ieeexplore.ieee.org

A quantitative study of java software buildability
M Sulír, J Porubän - Proceedings of the 7th International Workshop on …, 2016 - dl.acm.org

are not in the mapping dataset?

I strongly recommend that authors perform a careful review of the search strings and present inclusion/exclusion criteria. Besides, authors should perform a card sort to analyze the works systematically.

Also, include, in the replicability kit, all raw data from each analysis step. There is no evidence about the intermediate analysis/filtering steps.

Minor:
- The title of section 2 “systematic literature mapping survey” might lead to confusion, I advise to not use “survey” in this title. Same comment for the use of the term “systematic survey” in the paper can be replaced by “systematic mapping”
Fig1. is useful but its size could easily be reduced without a negative impact.
- Fig. 2 shows the 259 paper as the output of the first filter but in section 2.2 the output of the first filter is 256 papers.

The authors merge the results from peer-reviewed literature and grey literature. I can understand that the authors need to use grey literature in their SLR since the number of peer-reviewed papers is low. However, the authors should present the results from grey literature separately from the results from peer-reviewed literature.

- In Table 1, the authors present the identified build log analysis techniques. However, having an “analysis” technique for “build log analysis” is not informative and confusing. The same goes for “ scan”, “others” and “non identified”. The “machine learning” and “information retrieval” are very general, which ML techniques were used? I suggest the authors provide a clear and more detailed description/definition of each identified technique in Table 1.

The authors chose not to include and evaluate the machine learning techniques because they did not emerge from their literature survey and labeling is “unfeasible”. However, machine learning was the fourth most used technique in Table 1. Not considering at least one machine learning technique is a weak part in this work. I strongly suggest the authors expand their study and include ML techniques.

**Chunk retrieval comparison issues**

In section 4, authors claim that

“In the literature survey, we noted that previous work seemed to choose a log analysis technique arbitrarily and that is a lack of guidance on when to use which technique.”

As the literature mapping presents several issues, I can not assume that claim is true. However, I discuss some observations assuming that there is a lack of guidance.

The authors evaluate their chosen techniques according to precision and recall. However, many other characteristics are important for software engineers and practitioners to make an informed decision on the best techniques for their case such as scalability and efficiency. I suggest the authors discuss and consider these important metrics.

I do not understand the value of the decision tree for the given paper, given that it is the second classification of the same techniques after the classification introduced in Section 4.3 and Figures 16. I would suggest avoiding this section altogether.

I am not convinced that the orientation of the use-cases on different human-roles is a way to go. Why would a researcher need different information retrieval techniques than a software engineer? For example, is there a reason why one of them would want low recall or low precision of their information retrieval technique when having other structural category files? What if they have multiple structures and need to have both high recall and high precision? Wouldn't it be better to map the decision tree to some real needs and the input data characteristics? Or drop it altogether?

Despite great effort from authors, the manuscript presents essential soundness issues that compromise the main motivation and reliability. It is not relevant if the motivation arguments are false.  Please, address these issues carefully with more robust evidence about the problem with build log analysis. I recommend a revision on this paper due to the following major and minor concerns or suggestions.
\end{leftbar}

\end{document}

### 2021-03-12 tse-paper/paper.tex
add first version of 'rebuttal' doc, update lit survey process figure

@@
 \usepackage{relsize}
+\usepackage{subcaption}
 
@@
 In the second part of the paper, we then develop prototypical implementations of three promising
-techniques to analyze build logsx, namely program synthesis
+techniques to analyze build logs, namely program synthesis
 by example, textual similarity, and keyword search.
@@
 build log analysis.
-\keywords{Build Log Analysis \and Chunk Retrieval \and Continuous Integration}
+\keywords{Continuous Integration \and Build Log Analysis \and Chunk Retrieval}
 \end{abstract}
@@
 \item a large empirical study comparing the three techniques.
-\item guidelines on when to use which technique.
-\item a detailed research map to inspire future contributions to the
-field.
 \item a documented replication package~\citep{brandt2020chunk-replication}.
@@
 	\centering
-	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
+	\includegraphics[width=0.7\columnwidth, clip]{img/lit_survey_svg2.pdf}
 	\caption{Literature selection (following Petersen et
@@
 \centering
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth,
-		clip]{img/lit-sur/info_target.pdf}
-		\caption{Information targeted in build log analysis.}
-		\label{fig:litsur:info_target}
-
-\end{subfigure}\hspace{\fill}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-				\includegraphics[width=\columnwidth,
-				clip]{img/lit-sur/kind.pdf}
-		\caption{Class of information analyzed.}
-		\label{fig:litsur:kind}
-
-\end{subfigure}
-\begin{subfigure}[t]{\columnwidth}
-		\centering
-				\includegraphics[width=\columnwidth,
-				clip]{img/lit-sur/use.pdf}
-		\caption{Purpose of build log analysis.}
-		\label{fig:litsur:use}
-
-\end{subfigure}
+\begin{minipage}[b]{0.45\textwidth}
+		\subcaptionbox{Information targeted in build log analysis.
+		\label{fig:litsur:info_target}}
+		{\includegraphics[width=\textwidth,
+    trim={2cm 0 0 0},
+		clip]{img/lit-sur/info_target.pdf}}
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.45\textwidth}
+		\subcaptionbox{Class of information analyzed
+		\label{fig:litsur:kind}}
+		{\includegraphics[width=\textwidth,
+    clip]{img/lit-sur/kind.pdf}}
+    \vskip\baselineskip
+    \subcaptionbox{Purpose of build log analysis.
+		\label{fig:litsur:use}}
+		{\includegraphics[width=\columnwidth,
+		clip]{img/lit-sur/use.pdf}}
+\end{minipage}
 
@@
 \midrule
-Programming by Example & PBE	 & Regular expression program
+\makecell[l]{Programming\\by Example} & PBE	 & Regular expression program
 & Character   & In/output examples	\\
-Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
+\makecell[l]{Common Text\\Similarity}	     & CTS     & TF-IDF \& cosine similarity,
 expected number of lines & Line        & Output examples	   \\
-Keyword Search		     & KWS     & Keywords, expected number of
-lines			 & Line        & Keywords, context length  \\
-Random Line Retrieval	     & RLR     & Random sample
+\makecell[l]{Keyword Search}		     & KWS     & Keywords, expected number of
+lines			 & Line        & \makecell[l]{Keywords,\\context length}  \\
+\makecell[l]{Random Line\\Retrieval}	     & RLR     & Random sample
 & Line	      & Retrieval length	  \\
@@
 
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
+\begin{acknowledgements}
+We would like to thank Annibale Panichella for his valuable input during the conception, implementation and evaluation of the chunk retrieval techniques.
+\end{acknowledgements}
 

### 2021-04-16 tse-paper/rebuttal.tex
fix some feedback + literature authors missing + overhanging table

@@
 \usepackage{booktabs}
-\usepackage{color}
 \usepackage{boxedminipage}
@@
 \usepackage{etoolbox}
+\usepackage{xcolor}
+
+\definecolor{todo}{HTML}{00a3cc}
+\newcommand{\todo}[1] {{\bfseries \color{todo} #1}}
+\newcommand{\caro}[1] {\todo{[Caro: #1]} }
 
@@
 
-We thank reviewers for their in-depth and constructive feedback. All reviewers are
-positive about the relevance of the paper for IEEE Software’s
-readership (assessing it Very Relevant or Relevant). Reviewer 2 calls it a “great paper” and
-Reviewer 1 “clearly written and easy to read,” “highly relevant and
-fits well for IEEE Software and its target audience.” Reviewer 3,
-while being perhaps most critical overall, notes that “[the paper]
-focuses on a much needed dual perspective integrating the developer’s
-own perception to measure productivity. The paper is very well
-motivated and overall easy to read.”
-
-That said, there were a number of points that needed to be changed in the paper, in particular as regards scope and structure. We have made several improvements to
-the paper following your recommendations for this major revision.  Key changes include:
-\begin{itemize}
-\item Re-structuring the manuscript, by putting visualizations into a side bar to make the article focused on the productivity study alone.
-  \item Adding further details on study methodology and execution to the Telemetry and Regression Model sections while keeping the spirit of a light-weight, practitioner-oriented paper.
-In particular, we made the section on regression models easier to read for readers without a statistics background.
-\item Fixing the detailed remarks by the reviewers (throughout the paper).
-\end{itemize}
+We submitted a previous version of this manuscript to the ``Transactions on Software Engineering'' journal,
+which \todo{resulted in a ``revise and resubmit" verdict''}
+Based on the feedback from the reviewers, we revised the manuscript 
+\todo{describe key points, like improving the structure to make our intentions clearer and make the paper easier to follow for readers}
+We decided to submit this paper to the Empirical Software Engineering Journal,
+as we believe that a core part of our paper---the empirical evaluation of the
+chunk retrieval techniques---fit the scope of this journal better.
+We thank the original reviewers for their in-depth and constructive feedback
+which enabled us to improve and sharpen our work.
 
 \noindent
-Below we outline the remarks from the reviewers and our response in e-mail quotation and 
-answer style.
-\\
-\\
+Below we outline the remarks from the original reviews and our response
+in e-mail quotation and answer style.
+
+% We thank reviewers for their in-depth and constructive feedback. All reviewers are
+% positive about the relevance of the paper for IEEE Software’s
+% readership (assessing it Very Relevant or Relevant). Reviewer 2 calls it a “great paper” and
+% Reviewer 1 “clearly written and easy to read,” “highly relevant and
+% fits well for IEEE Software and its target audience.” Reviewer 3,
+% while being perhaps most critical overall, notes that “[the paper]
+% focuses on a much needed dual perspective integrating the developer’s
+% own perception to measure productivity. The paper is very well
+% motivated and overall easy to read.”
+
+% That said, there were a number of points that needed to be changed in the paper, in particular as regards scope and structure. We have made several improvements to
+% the paper following your recommendations for this major revision.  Key changes include:
+% \begin{itemize}
+% \item Re-structuring the manuscript, by putting visualizations into a side bar to make the article focused on the productivity study alone.
+%   \item Adding further details on study methodology and execution to the Telemetry and Regression Model sections while keeping the spirit of a light-weight, practitioner-oriented paper.
+In particular, we made the section on regression models easier to read for readers without a statistics background.
+% \item Fixing the detailed remarks by the reviewers (throughout the paper).
+% \end{itemize}
+
+% \noindent
+% Below we outline the remarks from the reviewers and our response in e-mail quotation and 
+% answer style.
+
 %\noindent

### 2021-04-16 tse-paper/paper.tex
fix some feedback + literature authors missing + overhanging table

@@
 
+\usepackage{pdflscape}
+
 \newcommand{\smallish}{\fontsize{6.15pt}{20pt}\selectfont}
@@
 \newcommand\circlenum[1]{\raisebox{1.2pt}{\textcircled{\hspace{0.35pt}\scriptsize{\raisebox{-.4pt}{#1}}}}}
+
+\definecolor{todo}{HTML}{00a3cc}
+% \newcommand{\todo}[1] {{\bfseries \color{todo} #1}}
+% \newcommand{\caro}[1] {\todo{[Caro: #1]} } 
+% hide todos:
+\newcommand{\todo}[1] {}
+\newcommand{\caro}[1] {}
 
@@
 }
-\subtitle{A~Systematic Survey and Comparative Study of Chunk~Retrieval~Techniques}
+\subtitle{A~Systematic Mapping and Comparative Study of Chunk~Retrieval~Techniques}
 
@@
 In this paper, we give a systematic overview of the emerging field of build log analysis.
-In a broad literature mapping survey, we first survey and categorize the existing methods to
+In a broad literature mapping, we first survey and categorize the described methods to
 extract information chunks from build logs.
@@
 the logs for information related to the source of the error.
+\todo{cite bart paper?}
 This
@@
 As a single build log can be
-over 50 megabytes large~\citep{beller2017oops}, finding the small chunk
+over 50 megabytes large~\citep{beller2017oops} \todo{check, reviewer comment}, finding the small chunk
 of information linked to the actual error, is akin to
@@
 the problem---an alternate would be to integrate live plugins into the
-build process
- such as the JUnit
-plugin for Jenkins~\citep{jenkins2020junit-plugin} or
-Deflaker by Bell et al.~\citep{bell2018deflaker}.
+build process such as the JUnit
+plugin for Jenkins\footnote{https://plugins.jenkins.io/junit/} or
+Deflaker~\citep{bell2018deflaker}.
 
@@
 However, such plugins are not available for all build tools, they are
-non-trivial to implement one-off solutions, and they
+non-trivial to implement, and
 do not enable the analysis of historical builds.
@@
 Moreover, build log analysis is the more general solution.
-While they serve an important niche, custom plugins do not make build
+While custom plugins serve an important niche, they do not make build
 log analysis redundant.
@@
 \Cref{fig:overview}---with an
-extensive literature survey (step \circlenum{1}).
-The survey identifies various strategies to
+extensive literature mapping (step \circlenum{1}).
+Researchers describe various strategies to
 analyze build logs, among which are developing
@@
 
-However, it also identifies that there is currently no guidance on when
-to use which of these
-approaches.
-Unfortunately, our survey also shows that
+However, the mapping identifies that there is currently no guidance on when
+to use which of these approaches.
+Unfortunately, it also shows that
 less than half of the 61 works which rely on build log analysis
@@
 logs from different build tools, and is prone to errors,
-as the experience of
-TravisTorrent has
-shown~\citep{beller2017travistorrent,travistorrentquestions}.
+as the experience of TravisTorrent has
+shown~\citep{beller2017travistorrent}.
 In fact, some even ``strongly discourage'' the creation of such
 parsers~\citep{urli2018design}.
-In summary, the outcome of our literature survey shows the need for a new
+In summary, the outcome of our literature mapping shows the need for a new
 generation of automated techniques to analyze build logs, which are
@@
 to automatically analyze build logs (step \circlenum{2}) by retrieving
-a substring (chunk)
-from the build log.
+a substring (chunk) from the build log.
 Our
-implementations are based on the most widely used approaches
-from the literature survey and as such, are meant to serve as
+implementations are based on widely described approaches
+from the literature mapping and as such, are meant to serve as
 the ``smallest common denominator,'' with as little tuning and
@@
 	retrieval, which we call \emph{Common Text Similarity (CTS)},
-	\item inspired by the manual ad hoc search for key parts in the
+	\item inspired by the manual ad-hoc search for key parts in the
 	log, a
@@
 In cases where the textual representation of the desired
-information in the log is unpredictable or varies greatly, KWS seems
-to be the best choice.
+information in the log is unpredictable or varies greatly, KWS is
+the best choice.
 However, its low precision---it extracts a
@@
 Instead, KWS requires a human
-to further inspect and interpret the output chunk.
+to further inspect and interpret the output.
 A hybrid solution combining the three techniques might be the best
@@
 of build log analysis.
+Our implementation, experiment and analysis are documented
+in our replication package~\citep{brandt2020chunk-replication}.
 
@@
 \begin{itemize}
-\item the first systematic survey of the emerging field of build log
+\item the first systematic mapping of the emerging field of build log
 analysis.
@@
 \item a large empirical study comparing the three techniques.
-\item a documented replication package~\citep{brandt2020chunk-replication}.
 \end{itemize}
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth, clip]{img/lit_survey_svg2.pdf}
+	\includegraphics[width=0.7\columnwidth, clip]{img/lit_mapping_svg2.pdf}
 	\caption{Literature selection (following Petersen et
 	al.~\citep{petersen2015guidelines}).}
-	\label{fig:lit-survey}
+	\label{fig:lit-mapping}
 \end{figure}
 
-\section{Systematic Literature Mapping Survey}
-\label{sec:survey}
+\section{Systematic Literature Mapping}
+\label{sec:mapping}
 % tense: past
 
-In this section, we report on the state-of-research in the emerging
-field of build log analysis by means of a systematic mapping study.
+In this section, we report on our systematic mapping study of how
+researchers analyze build logs.
 We start with a differentiation of build log analysis
-from the older field of
-system log analysis.
+from the older field of system log analysis.
 % ref to fig 2 so it can be here and above fig 3
-Then, we describe the methodology (\Cref{fig:lit-survey})
-and results of our systematic mapping
-survey following the
+Then, we describe the methodology (\Cref{fig:lit-mapping})
+and results of our systematic mapping study following the
 guidelines by Petersen et
@@
 % This is the easiest example matching here
-% amar et al are not in our literature survey
+% amar et al are not in our literature mapping
 However, the number of
@@
 
-The first step in a systematic literature survey is to
+The first step in a systematic literature mapping is to
 establish which works one wants to cover and how to find
@@
 Since the field of build log analysis is relatively young, we
-surveyed as broad a population of scientific material as possible.
+mapped as broad a population of scientific material as possible.
 We did not limit the sources to specific Software Engineering
@@
 
-\Cref{fig:lit-survey} gives an overview of the literature selection
+\Cref{fig:lit-mapping} gives an overview of the literature selection
 process.
@@
 
+\begin{figure}[tbp]
+		\centering
+		\includegraphics[width=0.8\textwidth,
+		clip]{img/lit-sur/years.pdf}
+		\caption{Number of works analyzing build logs per year.}
+		\label{fig:lit-years}
+\end{figure}
+
+\paragraph{Descriptive Study Statistics}
+After the third filtering phase, we finally included 61 works in the
+literature mapping.
+The majority of these are scientific articles (81\%), of which all but
+three have been peer-reviewed and published (94\%).
+The remaining works are theses (14\%), two books, and one slide deck.
+
+\Cref{fig:lit-years} depicts the year of appearance of these
+works.
+Although we applied no filtering by year in our initial search queries
+(see \Cref{sec:litsel}), the earliest work in our literature corpus
+stems only from 2001.
+There are various scattered works in the years between then and 2016,
+when the field of build log analysis started to grow rapidly.
+
 \subsection{Literature Classification}
@@
 As recommended by Petersen et
-al.~\citep{petersen2015guidelines}, we started the mapping survey with a
+al.~\citep{petersen2015guidelines}, we started the mapping with a
 pilot:
@@
 
-In this section, we first give a general overview over our paper
-population.
-We then present the results of the analysis phase along RQs 1.1 through
+In this section, we present the results of the analysis phase along RQs 1.1 through
 1.3.
-
-\subsubsection{Descriptive Study Statistics}
-\begin{figure}[tbp]
-		\centering
-		\includegraphics[width=\columnwidth,
-		clip]{img/lit-sur/years.pdf}
-		\caption{Number of works analyzing build logs per year.}
-		\label{fig:lit-years}
-\end{figure}
-
-After the third filtering phase, we finally included 61 works in the
-literature survey.
-The majority of these are scientific articles (81\%), of which all but
-three have been peer-reviewed and published (94\%).
-The remaining works are theses (14\%), two books, and one slide deck.
-
-\Cref{fig:lit-years} depicts the year of appearance of these
-works.
-Although we applied no filtering by year in our initial search queries
-(see \Cref{sec:litsel}), the earliest work in our literature corpus
-stems only from 2001.
-There are various scattered works in the years between then and 2016,
-when the field of build log analysis started to grow rapidly.
+\todo{if defining the RQs went up in the last section, rephrase the rqs here too}
 
@@
 In this section, we describe what sort of information the works in
-our survey usually retrieve from build logs.
+our mapping usually retrieve from build logs.
 \Cref{fig:litsur_r} depicts these results.
@@
 
-\subsubsection{Which analysis techniques exist (RQ 1.2)?}
-
+\begin{landscape}
 \addtolength{\tabcolsep}{-5pt}
@@
 \caption{Overview of build log analysis techniques.}
-\begin{tabularx}{\textwidth}{@{}lXl@{}}
+\begin{tabularx}{1.5\textwidth}{lXl}
 
@@
 
-\raisebox{0.8mm}{Parser} &
-\raisebox{0.8mm}{
-\citep{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
+{Parser} &
+\citep{vassallo2018un-break} \citep{zhang2016android} \citep{seo2014programmers} \citep{hassan2019tackling} \citep{hassan2017automatic} \citep{chromy2007integration} \citep{mesbah2019deepdelta} \citep{wen2018blimp} \citep{kwon2018prioritizing} \citep{adams2007design} \citep{rahman2018impact} \citep{brandyberry2006continuous} \citep{tomassi2019bugswarm} \citep{ren2018automated} \citep{vassallo2019automated} \citep{cavalcanti2019impact} \citep{sippola2013qt} \citep{felipe2012towards} \citep{shi2018evaluating} \citep{urli2018design} \citep{selberg2012use}
+ &
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
 \\
 
-\raisebox{0.8mm}{Regular expression} &
-\raisebox{0.8mm}{
-\citep{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
-} &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
+{Regular expression} &
+\citep{beller2017oops} \citep{hassan2017change} \citep{macho2018automatically} \citep{vassallo2017a-tale} \citep{lou2019history} \citep{hassan2017automatic} \citep{rott2019empirische} \citep{zampetti2019study} \citep{zhao2018comparing} \citep{rausch2017empirical} \citep{ghaleb2019studying} \citep{zampetti2017open} \citep{zhang2019large} \citep{kavaler2019tool} \citep{morris2010experience}
+ &
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
 \\
 
-\raisebox{0.8mm}{Manual inspection} &
-\raisebox{0.8mm}{
+{Manual inspection} &
+{
 \citep{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
 } &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
 \\
 
-\raisebox{0.8mm}{Machine Learning} &
-\raisebox{0.8mm}{
+{Machine Learning} &
+{
 \citep{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
 } &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
 \\
 
-\raisebox{0.8mm}{Natural Language Processing}	&
-\raisebox{0.8mm}{
+{Natural Language Processing}	&
+{
 \citep{hassan2017change,lou2019history,schulz2017active}
 } &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
 
-\raisebox{0.8mm}{Information Retrieval} &
-\raisebox{0.8mm}{
+{Information Retrieval} &
+{
 \citep{hassan2017change,lindqvist2019detection,ren2018automated}
 } &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
 
-\raisebox{0.8mm}{Analysis} &
-\raisebox{0.8mm}{
+{Analysis} &
+{
 \citep{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
 } &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
 
-\raisebox{0.8mm}{Keyword Search} &
-\raisebox{0.8mm}{
+{Keyword Search} &
+{
 \citep{brandyberry2006continuous,zhang2019large,kavaler2019tool}
 } &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
 \\
 
-\raisebox{0.8mm}{Scan} &
-\raisebox{0.8mm}{
+{Scan} &
+{
 \citep{clemencic2014new,hibbard2001visualization}
 } &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
 \\
 
-\raisebox{0.8mm}{Other} &
-\raisebox{0.8mm}{
+{Other} &
+{
 \citep{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
 } &
-\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
+\todo{why is this not in the graph?, find bar graphic}
 \\
 
-\raisebox{0.8mm}{None identified} &
-\raisebox{0.8mm}{
+{None identified} &
+{
 \citep{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
 } &
+\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
 \\
@@
 \addtolength{\tabcolsep}{5pt}
+\end{landscape}
+
+\subsubsection{Which analysis techniques exist (RQ 1.2)?}
 
@@
 
-Only 25\% of the works claimed their implementation is available.
-Moreover, we
-saw some reuse of the few available build log analysis tools.
+Only 25\% of the works stated that they make their
+implementation available for reuse.
+We saw some reuse of the few available build log analysis tools.
 Five works employed the tools used to create
@@
 \emph{Maven Log Analyzer}~\citep{macho2018automatically,gallaba2018noise},
-and
-another two
+and another two
 \emph{MAKAO}~\citep{wen2018blimp,adams2007design}.
@@
 \Cref{fig:litsur:log_producer} shows the distribution of
-build tools whose logs were analyzed by the works in our survey.
+build tools whose logs were analyzed by the works in our mapping.
 Of the works, 30\% analyzed
-Maven~\citep{maven2019website},
-16\% analyzed Gradle~\citep{gradle2020website},
-and 10\% analyzed Ant build logs~\citep{ant2020website}.
+Maven\footnote{https://maven.apache.org/},
+16\% analyzed Gradle\footnote{https://gradle.org/},
+and 10\% analyzed Ant build logs\footnote{https://ant.apache.org/}.
 
@@
 In 38\% of cases, the works collected build logs from Travis
-CI~\citep{travisci2019webpage};
+CI\footnote{https://travis-ci.org};
 18\% of the works analyzed logs from TravisTorrent; and 8\% included
@@
 investigated up to 122 million logs.
-Of the surveyed works, 31\% claim to have published their data to
+Of the mapped works, 31\% claim to have published their data to
 enable further research.
@@
 		\centering
-		\includegraphics[width=\columnwidth, trim={1.5cm 0.4cm
+		\includegraphics[width=0.8\textwidth, trim={1.5cm 0.4cm
 		1.5cm 0.5cm},
@@
 % ----- descriptive / general -----
-Our literature survey shows that \emph{there is a rapidly growing body
+Our literature mapping shows that \emph{there is a rapidly growing body
 of works using build log analysis,}
@@
 categorization from chunks, but not vice versa.
+\todo{catedorization was called classification before}
 
@@
 
-The literature survey shows the need for
+The literature mapping shows the need for
 build log
 analysis techniques that are \emph{automated},
-\emph{build tool-agnostic}
-and that a user can \emph{configure with little effort}.
+and can be \emph{configured} to target an \emph{arbitrary build tool}
+with \emph{little effort} from the user.
+
 \section{Chunk Retrieval Techniques}
@@
 
-With the term ``chunk retrieval technique,'' we refer to a way of
-automatically extracting strings that appear literally in build
+With the term ``chunk retrieval technique,'' we refer to methods that
+automatically extract strings that appear literally in build
 logs, i.e., techniques that do not aggregate, combine, or deduct
@@
 separate them into different \emph{structural categories}.
+\todo{is it necessary to introduce strcutural categories here?
+if yes, we should define it and give an example}
 
@@
 
+\todo{incorporate that this is done to adapt the chunk retrieval
+technique for a certain build tool or other kind of information}
 With the term \textit{configuration}, we abstract over the training
@@
 Our findings of techniques in the literature
-survey (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
+mapping (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
 particular) inspired the strategies that underlie them.
@@
 to the wide variety of build logs we are interested in.
+\todo{make clearer: to automatically derive them from a few
+user-given examples}
 The closest
@@
 
+From the fields of information retrieval (IR) and natural
+language
+processing (NLP, see \Cref{tab:litsur:techniques}), we leverage
+a widely-used text similarity measure and call this approach \emph{Common
+Text Similarity (CTS)}.
+The intuition behind it is that the relevant,
+failing parts of build logs often look similar to each other, even if
+the exact failure reasons might differ.
+
 To work effectively with build logs, many humans anecdotally search
@@
 
-Finally, from the fields of information retrieval (IR) and natural
-language
-processing (NLP, see \Cref{tab:litsur:techniques}), we leverage
-a widely-used text similarity measure and call this approach \emph{Common
-Text Similarity (CTS)}.
-The intuition behind it is that the relevant,
-failing parts of build logs often look similar to each other, even if
-the exact failure reasons might differ.
-
 Other techniques, specifically ones based on deep learning, are
-thinkable, but we did not evaluate them in this article since they did
-not emerge from the literature survey.
-Moreover, they typically
-require lots of training and tuning.
+thinkable, but we did not evaluate them in this article.
+They typically require lots of training and tuning,
+together with a large body of high quality training data.
 However, our premise was to ease
-the creation of build log analysis for developers.
+the creation of build log analysis.
 First having to
-label thousands of logs on their project before they can start to
-analyze build logs is therefore infeasible.
+label thousands of logs on a project before one can start to
+analyze its build logs is therefore infeasible.
 Similarly, as a manual
@@
 training of such supervised techniques.
-Finding a way to train them in
+Finding a way to train deep learning techniques in
 an unsupervised fashion would rapidly increase their applicability and
@@
 for build logs.
-The \emph{PROSE library}~\citep{prose2019webpage} forms the basis for
-our implementation.
+The \emph{PROSE library}\footnote{https://microsoft.github.io/prose/}
+forms the basis for our implementation.
 This library builds on the generic program synthesis framework
@@
 These approaches fall into the broader area of information retrieval
-techniques, which several of the works from our literature survey
+techniques, which several of the works from our literature mapping
 used to analyze build logs.
@@
 We implemented PBE in C\# based on the Microsoft PROSE
-library~\citep{prose2019webpage} and CTS, KWS, and RLR using
-R and the {\tt text2vec} library~\citep{text2vec2019webpage}.
+library\footnote{https://microsoft.github.io/prose/}
+and CTS, KWS, and RLR using
+R and the {\tt text2vec} library\footnote{http://text2vec.org/}.
 
@@
 
-In the literature survey, we noted that previous work seemed to choose
+In the literature mapping, we noted that previous work seemed to choose
 a log analysis technique arbitrarily and that is a lack of guidance on
@@
 programming languages on Travis CI, the most-used source of build logs
-according to our literature survey.
+according to our literature mapping.
 This wide variety of projects and the large number of different build
@@
 failed---the information targeted by most of the works in our
-literature survey (see \Cref{sec:lit-sur:discussion}).
+literature mapping (see \Cref{sec:lit-sur:discussion}).
 To be able to configure the keyword search technique,
@@
 		\centering
-		\includegraphics[width=\columnwidth,
+		\includegraphics[width=0.8\columnwidth,
 		clip]{img/big-study/failure-reason-pbe.pdf}
@@
 		\centering
-		\includegraphics[width=\columnwidth,
+		\includegraphics[width=0.8\columnwidth,
 		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
@@
 		\centering
-		\includegraphics[width=\columnwidth,
+		\includegraphics[width=0.8\columnwidth,
 		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
@@
 		\centering
-		\includegraphics[width=\columnwidth,
+		\includegraphics[width=0.8\columnwidth,
 		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
@@
 		\centering
-				\includegraphics[width=\columnwidth,
+				\includegraphics[width=0.8\columnwidth,
 				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
@@
 		\centering
-		\includegraphics[width=\columnwidth,
+		\includegraphics[width=0.8\columnwidth,
 		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
@@
 		\centering
-		\includegraphics[width=\columnwidth,
+		\includegraphics[width=0.8\columnwidth,
 		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
@@
 		\centering
-		\includegraphics[width=\columnwidth,
+		\includegraphics[width=0.8\columnwidth,
 		clip]{img/big-study/success-partial-all.pdf}
@@
 		\centering
-				\includegraphics[width=\columnwidth,
+				\includegraphics[width=0.8\columnwidth,
 				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
@@
 				\centering
-		\includegraphics[width=\columnwidth,
+		\includegraphics[width=0.8\columnwidth,
 		clip]{img/big-study/recall-precision-multicategory-all.pdf}
@@
 results when the log chunks are structurally identical.
-This is
-because PROSE has difficulty synthesizing OR-based
-programs~\citep{mayer2015user}.
 PBE is thus suited to retrieve information
@@
 structure.
-To extract for example the reason a build failed, the log
+To extract, e.g., the reason a build failed, the log
 passage describing the failure would always have to start and
@@
 		\centering
-		\includegraphics[width=\columnwidth,
+		\includegraphics[width=0.8\columnwidth,
 		clip]{img/crt-recommendation.pdf}
@@
 \textbf{Limitation to Scholarly Articles.} We limited our literature
-survey to scholarly articles.
+mapping to scholarly articles.
 However, the field of build log analysis is extremely relevant to
@@
 Our findings include the Jenkins build log
-analyzer~\citep{jenkins2020failure-analyzer}, where a user can
+analyzer\footnote{https://plugins.jenkins.io/build-failure-analyzer/}, where a user can
 define custom regular expressions to parse a build log, and a web page
@@
 Similarly, the library
-{\tt text2vec}~\citep{text2vec2019webpage}
+{\tt text2vec}\footnote{http://text2vec.org/}
 and the way it splits strings into word tokens is influencing
@@
 We base our
-suggestions on the results of the literature survey and the
+suggestions on the results of the literature mapping and the
 findings from our technique comparison study.
 
-\textbf{Systematic Survey of Industry Approaches for Build
-Log Analysis.}	Our survey is limited to scholarly material.
+\textbf{Systematic Mapping of Industry Approaches for Build
+Log Analysis.}	Our mapping is limited to scholarly material.
 However,
@@
 Jenkins \emph{build-failure-analyzer}
-plugin~\citep{jenkins2020failure-analyzer} or automatically inferred
-test results in Azure~\citep{azure2020inferred}.
+plugin\footnote{https://plugins.jenkins.io/build-failure-analyzer/} or automatically inferred
+test results in Azure\footnote{https://docs.microsoft.com/en-us/azure/devops/pipelines/test/review-continuous-test-results-after-build?view=azure-devops\#automatically\_inferred\_tests}.
 Such a study might
-also need to tackle the more abstract problem of how to survey
-non-scholarly material systematically, which might be an important
+also need to tackle the more abstract problem of how to map
+non-scholarly material systematically, which would be an important
 contribution to Software Engineering research.
@@
 environment-agnostic analysis tools.
+\todo{for tools that do not have to be manually configure to fit a
+specific project or build environment}
 This has the advantage of creating
@@
 techniques (discussed in \Cref{sec:choice}) or manually-written
-programs such as the parser Tomassi et al.
-created for
+programs such as the parser created for
 BugSwarm~\citep{tomassi2019bugswarm} or the regex-based approach
-Beller et al.
 created for TravisTorrent~\citep{beller2017oops}.
@@
 To this end, we
-conducted a systematic mapping survey to map out the available build
-log analysis techniques.
-We saw that build log analysis is an
-emerging field.
+conducted a systematic mapping to investigate how researchers
+currently analyze build logs.
+We saw that build log analysis is an emerging field.
 At the same time, articles largely do not justify why
 they use a certain technique, nor do they document it in detail or
-open-sourced its implementation.
-Moreover, the survey showed that,
+open-source its implementation.
+Moreover, the mapping showed that,
 while there is a niche for custom parsers and plugins for very popular
-tools such as the Java ecosystem, there is a wide variety of build
+tools, such as the Java ecosystem, there is a wide variety of build
 tool and environment combinations for which the creation of such
@@
 Overall, this study showed the need for a new
+\todo{not generic, but configurable}
 generation of generic and automated build log analysis techniques that

### 2021-04-19 tse-paper/paper.tex
start re-ordering chunk retrieval techniques section

@@
 \definecolor{todo}{HTML}{00a3cc}
-% \newcommand{\todo}[1] {{\bfseries \color{todo} #1}}
-% \newcommand{\caro}[1] {\todo{[Caro: #1]} } 
+\newcommand{\todo}[1] {{\bfseries \color{todo} #1}}
+\newcommand{\caro}[1] {\todo{[Caro: #1]} } 
 % hide todos:
-\newcommand{\todo}[1] {}
-\newcommand{\caro}[1] {}
+% \newcommand{\todo}[1] {}
+% \newcommand{\caro}[1] {}
 
@@
 
-\section{Introduction}\label{sec:introduction}
+\section{Introduction}
+\label{sec:introduction}
 In the past two decades, Continuous Integration (CI) has become a
@@
 
-The literature mapping shows the need for
-build log
-analysis techniques that are \emph{automated},
-and can be \emph{configured} to target an \emph{arbitrary build tool}
-with \emph{little effort} from the user.
+% \caro{can we soften this to lead into the new arguments in the following section?}
+% The literature mapping shows the need for
+% build log
+% analysis techniques that are \emph{automated},
+% and can be \emph{configured} to target an \emph{arbitrary build tool}
+% with \emph{little effort} from the user.
 
@@
 
-In this section, we formally define the concept of chunk
-retrievals from build logs.
-Then, we motivate and present the choice of three such techniques that
-we implemented and evaluated for this study.
-
-\subsection{Characteristics of Chunk Retrieval Techniques}
-\label{sec:crt-characteristics}
-
-With the term ``chunk retrieval technique,'' we refer to methods that
-automatically extract strings that appear literally in build
-logs, i.e., techniques that do not aggregate, combine, or deduct
-information.
-We call such pieces of information in build logs
-\emph{chunks}.
-Depending on the format of the chunks within the build log we
-separate them into different \emph{structural categories}.
-\todo{is it necessary to introduce strcutural categories here?
-if yes, we should define it and give an example}
-
-Generally, chunk retrieval techniques
-can also be used to classify build logs, e.g.\, by checking
-which substring was retrieved.
-Therefore, they
-cover the great majority of the types of log analysis we saw in
-\Cref{sec:lit-sur:discussion}.
-
-The techniques we investigate here do not require a formal lexer and
-parser to analyze the entire structure of build logs, but focus on
-ad hoc extraction of just one specific information piece per
-configuration.
-
-\todo{incorporate that this is done to adapt the chunk retrieval
-technique for a certain build tool or other kind of information}
-With the term \textit{configuration}, we abstract over the training
-and parametrization that different techniques require in different
-forms.
-A configuration can be explicitly stated or implicitly derived
-by learning through provided examples.
-It is therefore a manual
-specification of which information the chunk retrieval should target.
-It also supplies the necessary information for the technique to
-identify the targeted chunk in a build log.
-Each chunk
-retrieval technique has a specific \textit{granularity}, i.e.,\ the
-smallest piece of text it can return (e.g., a line, or a word).
-% The
-% granularity might be adjustable by configuration.
-
-\emph{Running a
-chunk retrieval technique} means
-executing a fully configured
-technique to a build log.
-The technique then outputs a (possibly empty) list of substrings of the
-build log text.
-
-\subsection{Choice of Chunk Retrieval Techniques}
-\label{sec:choice}
-
-\begin{table*}[htb]
-\centering
-\caption{Chunk retrieval techniques.}
-\begin{tabularx}{\textwidth}{@{}llXll@{}}
-\toprule
-Name & Acronym & Identification Technique & Granularity &
-Configuration \\
-\midrule
-\makecell[l]{Programming\\by Example} & PBE	 & Regular expression program
-& Character   & In/output examples	\\
-\makecell[l]{Common Text\\Similarity}	     & CTS     & TF-IDF \& cosine similarity,
-expected number of lines & Line        & Output examples	   \\
-\makecell[l]{Keyword Search}		     & KWS     & Keywords, expected number of
-lines			 & Line        & \makecell[l]{Keywords,\\context length}  \\
-\makecell[l]{Random Line\\Retrieval}	     & RLR     & Random sample
-& Line	      & Retrieval length	  \\
-\bottomrule
-\end{tabularx}
-\label{tab:techniques}
-\end{table*}
-
-For this article, we designed and implemented three automated chunk
-retrieval techniques.
-Our findings of techniques in the literature
-mapping (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
-particular) inspired the strategies that underlie them.
-\Cref{tab:techniques} summarizes the techniques, which we describe here
-in detail.
-
-Techniques based on custom parsers (\#1
-in \Cref{tab:litsur:techniques}) are inadequate for our comparison,
-since their creation is manual and one parser would never generalize
-to the wide variety of build logs we are interested in.
-\todo{make clearer: to automatically derive them from a few
-user-given examples}
-The closest
-we could come to the second most popular entry, regular expression, is
-a technique to automatically derive them: in particular, we implement
-a technique based on
-\emph{Programming by Example (PBE)}.
-It uses regular expressions internally, while simplifying their
-development.
-
-From the fields of information retrieval (IR) and natural
-language
-processing (NLP, see \Cref{tab:litsur:techniques}), we leverage
-a widely-used text similarity measure and call this approach \emph{Common
-Text Similarity (CTS)}.
-The intuition behind it is that the relevant,
-failing parts of build logs often look similar to each other, even if
-the exact failure reasons might differ.
-
-To work effectively with build logs, many humans anecdotally search
-(``grep'') the logs for key phrases such as ``fail.'' Researchers often
-resorted to such a strategy when doing manual analysis (\#2
-in \Cref{tab:litsur:techniques}), describing it with the word ``scan''
-or other paraphrases.
-Imitating this ad hoc approach of searching for
-specific strings, we automatize it as \emph{Keyword Search (KWS)}.
-
-Other techniques, specifically ones based on deep learning, are
-thinkable, but we did not evaluate them in this article.
-They typically require lots of training and tuning,
-together with a large body of high quality training data.
-However, our premise was to ease
-the creation of build log analysis.
-First having to
-label thousands of logs on a project before one can start to
-analyze its build logs is therefore infeasible.
-Similarly, as a manual
-effort, the \emph{LogChunks} data set is not big enough to support the
-training of such supervised techniques.
-Finding a way to train deep learning techniques in
-an unsupervised fashion would rapidly increase their applicability and
-appeal to build log analysis.
-
-\subsection{Programming by Example (PBE)}
-The idea behind \emph{Programming by Example} is to automatically
-generate a program, by capturing the
-intent of the user through examples that the user provides.
-Leveraging this approach, we designed a chunk retrieval technique
-for build logs.
-The \emph{PROSE library}\footnote{https://microsoft.github.io/prose/}
-forms the basis for our implementation.
-This library builds on the generic program synthesis framework
-\emph{FlashMeta}~\citep{polozov2015flashmeta:} and the specialized
-text extraction DSL \emph{FlashExtract}~\citep{le2014flashextract:}.
-% Both enable \emph{PROSE} to synthesize regular expression programs
-% consistent~\citep{mitchell1982generalization} with a set of in-
-% and output examples.
-% The usage of example enables the user to configure a chunk
-% retrieval without understanding the whole structure of
-% the build log.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of PBE;
-The \emph{input} is the full text of the build log file.
-The \emph{output} is
-a substring of the log file text, representing the
-substring that the synthesized program should retrieve when
-given the corresponding input file.
-One or multiple examples, the
-training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the chunk of a build log that should be retrieved.
-The PROSE program synthesis then tries to construct a program
-consistent with all training
-examples~\citep{mitchell1982generalization}.
-If PROSE cannot synthesize a program, e.g.,\
-because the required regular expression
-is too complicated to be synthesized, PBE returns the
-error message ``no program found.''
-
-\subsubsection{Chunk Retrieval Run}
-A run of PBE takes a build log file as input and executes the
-synthesized regular expression program on it.
-It then returns the substring
-of the build log matched by the program.
-If the program finds no match because the analyzed build log
-does not contain the structure that the training examples define,
-PBE returns the error message ``no match found.''
-
-\subsection{Common Text Similarity (CTS)}
-Text Similarity approaches are widely used to filter unstructured
-textual software artifacts~\citep{runeson2007detection,
-marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
-These approaches fall into the broader area of information retrieval
-techniques, which several of the works from our literature mapping
-used to analyze build logs.
-Similar to these approaches, we designed a chunk retrieval
-technique that
-retrieves those lines from a build log which are most
-similar to the specified examples.
-
-\subsubsection{Configuration}
-To configure CTS we chose to use the same concept of examples as for
-PBE: lines of the targeted chunks from the training examples define
-the search query.
-Using a Vector Space
-Model~\citep{schutze2008introduction} (VSM), an algebraic model for
-representing textual documents, we encode each line as a separate term
-vector.
-The terms that make up the dictionary are simply all words
-that appear in the example logs.
-We separate words by spaces and
-punctuation.
-The vectors comprise points counting
-how many times a word out of the dictionary appears in the specific
-line at hand.
-
-The idea behind a representation in the VSM is that text lines as more
-similar if they contain the same words in similar frequencies,
-making their term vectors point in a similar direction in vector
-space.
-We use \emph{cosine similarity}~\citep{korenius2007principal}
-to calculate the angle between two term vectors.
-The smaller the
-angle between term vectors is, the more similar are the corresponding
-lines.
-
-To improve the similarity calculation, we prune very often or
-very rarely appearing words.
-Finally, the
-algorithm weighs the vectors using \emph{term frequency-inverse
-document frequency (TF-IDF)}, an established technique to give a higher
-impact to words that occur in a smaller number of
-documents~\citep{lee1997document}.
-
-\subsubsection{Chunk Retrieval Run}
-To retrieve the desired information from a build log, we encode every
-line of the input build log in VSM.
-The algorithm calculates the cosine
-similarity to compare each line of the
-build log with each line of the search query.
-After summing up the
-similarities of each build log line to all search query lines, we sort
-the build log lines in decreasing similarity.
-The average number of
-lines in the chunks of the training examples determines how many of
-the most similar lines our approach returns as the output of the retrieval
-run.
-
-\subsection{Keyword Search (KWS)}
-When developers scavenge for a specific piece of information within a
-large amount of unstructured information, a first ad hoc approach they
-use is to search for related keywords.
-To investigate the performance of this approach, we designed a chunk
-retrieval technique mimicking this human behavior based on keyword
-search.
-
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@.
-To better
-compare KWS with PBE and CTS, we also configure it through examples.
-From each example, we extract a list of keywords that appeared in the
-training examples and that we expect to appear
-in, or close to, the targeted chunk in a new build log.
-Finally, we merge the lists from all examples to build one unified
-list of the most commonly occurring keywords for the search with KWS.
-
-\subsubsection{Chunk Retrieval Run}
-For a retrieval run, we take an entire build log file as input and
-search for all exact occurrences of the search keywords.
-As keywords are
-often not directly describing the desired information, but rather
-appear close to it, KWS also retrieves a context of lines
-around the found keyword.
-The number of surrounding lines retrieved is
-the average number of lines in the chunks of the training examples.
-
-\subsection{Random Line Retrieval (RLR)}
-\label{sec:expl-rlr}
-To fully comprehend how difficult the task of build log analysis really
-is without any a priori knowledge, we include a comparison with a
-baseline of
-picking lines at random from the build log.
-RLR mimics the
-situation of guessing blindly which lines are interesting.
-The only configuration option for RLR is the number of lines it should
-retrieve.
-For a fair comparison to the other techniques (whose number of
-returned lines is largely determined by the training set),
-we configure RLR to return the average
-number of lines in the chunks of the training examples.
+Based on our observations from the literature mapping, we believe that
+researchers and developers would benefit from pre-made
+build log analysis tools they
+can re-use and configure to fit the kind of build logs and information
+they are targeting.
+Such \emph{configurable build log analysis tools} would save high effort
+of developing custom tools we observed, and, when openly available,
+improve the reproducibility of studies that mine information from
+CI build logs.
+
+To make a first step, this paper investigates three different approaches
+to realize configurable build log analysis.
+One of our central requirements is, that a future user should be able
+to adapt the analysis with little effort to their use case.
+
+To enable configurable build log analysis, we evaluate the following
+techniques:
+\begin{itemize}
+  \item \textbf{\emph{Programming by Example (PBE)}}, which learns
+  regular expressions based on few user-given log excerpts.
+  We rely on the PROSE Framework \caro{link!} that is also responsible for auto-filling
+  cells in Microsoft Excel.
+
+  \item Inspired by information retrieval, a
+  \textbf{\emph{Common Text Similarity (CTS)}} approach that finds log
+  parts with similar vocabulary than that of user-given log excerpts.
+
+  \item A \textbf{\emph{Keyword Search (KWS)}} that searches for terms
+  provided by the user.
+\end{itemize}
+
+All these three techniques retrieve \emph{chunks} of text from an
+analyzed build log, which is why we will further call them
+\emph{Chunk Retrieval Techniques}.
+
+In this section, we introduce these three techniques with the help of an
+example, discuss their realization in our prototypes in more detail
+and discuss the option of using machine learning to create a configurable
+build log analysis approach.
 
@@
 
+% \subsection{Characteristics of Chunk Retrieval Techniques}
+% \label{sec:crt-characteristics}
+
+% With the term ``chunk retrieval technique,'' we refer to methods that
+% automatically extract strings that appear literally in build
+% logs, i.e., techniques that do not aggregate, combine, or deduct
+% information.
+% We call such pieces of information in build logs
+% \emph{chunks}.
+% Depending on the format of the chunks within the build log we
+% separate them into different \emph{structural categories}.
+% \todo{is it necessary to introduce strcutural categories here?
+% if yes, we should define it and give an example}
+
+% Generally, chunk retrieval techniques
+% can also be used to classify build logs, e.g.\, by checking
+% which substring was retrieved.
+% Therefore, they
+% cover the great majority of the types of log analysis we saw in
+% \Cref{sec:lit-sur:discussion}.
+
+% The techniques we investigate here do not require a formal lexer and
+% parser to analyze the entire structure of build logs, but focus on
+% ad hoc extraction of just one specific information piece per
+% configuration.
+
+% \todo{incorporate that this is done to adapt the chunk retrieval
+% technique for a certain build tool or other kind of information}
+% With the term \textit{configuration}, we abstract over the training
+% and parametrization that different techniques require in different
+% forms.
+% A configuration can be explicitly stated or implicitly derived
+% by learning through provided examples.
+% It is therefore a manual
+% specification of which information the chunk retrieval should target.
+% It also supplies the necessary information for the technique to
+% identify the targeted chunk in a build log.
+% Each chunk
+% retrieval technique has a specific \textit{granularity}, i.e.,\ the
+% smallest piece of text it can return (e.g., a line, or a word).
+% % The
+% % granularity might be adjustable by configuration.
+
+% \emph{Running a
+% chunk retrieval technique} means
+% executing a fully configured
+% technique to a build log.
+% The technique then outputs a (possibly empty) list of substrings of the
+% build log text.
+
+\subsection{Choice of Chunk Retrieval Techniques}
+\label{sec:choice}
+
+\begin{table*}[htb]
+\centering
+\caption{Chunk retrieval techniques.}
+\begin{tabularx}{\textwidth}{@{}llXll@{}}
+\toprule
+Name & Acronym & Identification Technique & Granularity &
+Configuration \\
+\midrule
+\makecell[l]{Programming\\by Example} & PBE	 & Regular expression program
+& Character   & In/output examples	\\
+\makecell[l]{Common Text\\Similarity}	     & CTS     & TF-IDF \& cosine similarity,
+expected number of lines & Line        & Output examples	   \\
+\makecell[l]{Keyword Search}		     & KWS     & Keywords, expected number of
+lines			 & Line        & \makecell[l]{Keywords,\\context length}  \\
+\makecell[l]{Random Line\\Retrieval}	     & RLR     & Random sample
+& Line	      & Retrieval length	  \\
+\bottomrule
+\end{tabularx}
+\label{tab:techniques}
+\end{table*}
+
+For this article, we designed and implemented three automated chunk
+retrieval techniques.
+Our findings of techniques in the literature
+mapping (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
+particular) inspired the strategies that underlie them.
+\Cref{tab:techniques} summarizes the techniques, which we describe here
+in detail.
+
+Techniques based on custom parsers (\#1
+in \Cref{tab:litsur:techniques}) are inadequate for our comparison,
+since their creation is manual and one parser would never generalize
+to the wide variety of build logs we are interested in.
+\todo{make clearer: to automatically derive them from a few
+user-given examples}
+The closest
+we could come to the second most popular entry, regular expression, is
+a technique to automatically derive them: in particular, we implement
+a technique based on
+\emph{Programming by Example (PBE)}.
+It uses regular expressions internally, while simplifying their
+development.
+
+From the fields of information retrieval (IR) and natural
+language
+processing (NLP, see \Cref{tab:litsur:techniques}), we leverage
+a widely-used text similarity measure and call this approach \emph{Common
+Text Similarity (CTS)}.
+The intuition behind it is that the relevant,
+failing parts of build logs often look similar to each other, even if
+the exact failure reasons might differ.
+
+To work effectively with build logs, many humans anecdotally search
+(``grep'') the logs for key phrases such as ``fail.'' Researchers often
+resorted to such a strategy when doing manual analysis (\#2
+in \Cref{tab:litsur:techniques}), describing it with the word ``scan''
+or other paraphrases.
+Imitating this ad hoc approach of searching for
+specific strings, we automatize it as \emph{Keyword Search (KWS)}.
+
+Other techniques, specifically ones based on deep learning, are
+thinkable, but we did not evaluate them in this article.
+They typically require lots of training and tuning,
+together with a large body of high quality training data.
+However, our premise was to ease
+the creation of build log analysis.
+First having to
+label thousands of logs on a project before one can start to
+analyze its build logs is therefore infeasible.
+Similarly, as a manual
+effort, the \emph{LogChunks} data set is not big enough to support the
+training of such supervised techniques.
+Finding a way to train deep learning techniques in
+an unsupervised fashion would rapidly increase their applicability and
+appeal to build log analysis.
+
+\subsection{Programming by Example (PBE)}
+The idea behind \emph{Programming by Example} is to automatically
+generate a program, by capturing the
+intent of the user through examples that the user provides.
+Leveraging this approach, we designed a chunk retrieval technique
+for build logs.
+The \emph{PROSE library}\footnote{https://microsoft.github.io/prose/}
+forms the basis for our implementation.
+This library builds on the generic program synthesis framework
+\emph{FlashMeta}~\citep{polozov2015flashmeta:} and the specialized
+text extraction DSL \emph{FlashExtract}~\citep{le2014flashextract:}.
+% Both enable \emph{PROSE} to synthesize regular expression programs
+% consistent~\citep{mitchell1982generalization} with a set of in-
+% and output examples.
+% The usage of example enables the user to configure a chunk
+% retrieval without understanding the whole structure of
+% the build log.
+
+\subsubsection{Configuration}
+In- and output example pairs are the main driver of PBE;
+The \emph{input} is the full text of the build log file.
+The \emph{output} is
+a substring of the log file text, representing the
+substring that the synthesized program should retrieve when
+given the corresponding input file.
+One or multiple examples, the
+training set, \emph{configure} a specific chunk retrieval with PBE:
+they define the chunk of a build log that should be retrieved.
+The PROSE program synthesis then tries to construct a program
+consistent with all training
+examples~\citep{mitchell1982generalization}.
+If PROSE cannot synthesize a program, e.g.,\
+because the required regular expression
+is too complicated to be synthesized, PBE returns the
+error message ``no program found.''
+
+\subsubsection{Chunk Retrieval Run}
+A run of PBE takes a build log file as input and executes the
+synthesized regular expression program on it.
+It then returns the substring
+of the build log matched by the program.
+If the program finds no match because the analyzed build log
+does not contain the structure that the training examples define,
+PBE returns the error message ``no match found.''
+
+\subsection{Common Text Similarity (CTS)}
+Text Similarity approaches are widely used to filter unstructured
+textual software artifacts~\citep{runeson2007detection,
+marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
+These approaches fall into the broader area of information retrieval
+techniques, which several of the works from our literature mapping
+used to analyze build logs.
+Similar to these approaches, we designed a chunk retrieval
+technique that
+retrieves those lines from a build log which are most
+similar to the specified examples.
+
+\subsubsection{Configuration}
+To configure CTS we chose to use the same concept of examples as for
+PBE: lines of the targeted chunks from the training examples define
+the search query.
+Using a Vector Space
+Model~\citep{schutze2008introduction} (VSM), an algebraic model for
+representing textual documents, we encode each line as a separate term
+vector.
+The terms that make up the dictionary are simply all words
+that appear in the example logs.
+We separate words by spaces and
+punctuation.
+The vectors comprise points counting
+how many times a word out of the dictionary appears in the specific
+line at hand.
+
+The idea behind a representation in the VSM is that text lines as more
+similar if they contain the same words in similar frequencies,
+making their term vectors point in a similar direction in vector
+space.
+We use \emph{cosine similarity}~\citep{korenius2007principal}
+to calculate the angle between two term vectors.
+The smaller the
+angle between term vectors is, the more similar are the corresponding
+lines.
+
+To improve the similarity calculation, we prune very often or
+very rarely appearing words.
+Finally, the
+algorithm weighs the vectors using \emph{term frequency-inverse
+document frequency (TF-IDF)}, an established technique to give a higher
+impact to words that occur in a smaller number of
+documents~\citep{lee1997document}.
+
+\subsubsection{Chunk Retrieval Run}
+To retrieve the desired information from a build log, we encode every
+line of the input build log in VSM.
+The algorithm calculates the cosine
+similarity to compare each line of the
+build log with each line of the search query.
+After summing up the
+similarities of each build log line to all search query lines, we sort
+the build log lines in decreasing similarity.
+The average number of
+lines in the chunks of the training examples determines how many of
+the most similar lines our approach returns as the output of the retrieval
+run.
+
+\subsection{Keyword Search (KWS)}
+When developers scavenge for a specific piece of information within a
+large amount of unstructured information, a first ad hoc approach they
+use is to search for related keywords.
+To investigate the performance of this approach, we designed a chunk
+retrieval technique mimicking this human behavior based on keyword
+search.
+
+\subsubsection{Configuration}
+A set of keywords configures the chunk retrieval with KWS\@.
+To better
+compare KWS with PBE and CTS, we also configure it through examples.
+From each example, we extract a list of keywords that appeared in the
+training examples and that we expect to appear
+in, or close to, the targeted chunk in a new build log.
+Finally, we merge the lists from all examples to build one unified
+list of the most commonly occurring keywords for the search with KWS.
+
+\subsubsection{Chunk Retrieval Run}
+For a retrieval run, we take an entire build log file as input and
+search for all exact occurrences of the search keywords.
+As keywords are
+often not directly describing the desired information, but rather
+appear close to it, KWS also retrieves a context of lines
+around the found keyword.
+The number of surrounding lines retrieved is
+the average number of lines in the chunks of the training examples.
+
+\subsection{Random Line Retrieval (RLR)}
+\label{sec:expl-rlr}
+To fully comprehend how difficult the task of build log analysis really
+is without any a priori knowledge, we include a comparison with a
+baseline of
+picking lines at random from the build log.
+RLR mimics the
+situation of guessing blindly which lines are interesting.
+The only configuration option for RLR is the number of lines it should
+retrieve.
+For a fair comparison to the other techniques (whose number of
+returned lines is largely determined by the training set),
+we configure RLR to return the average
+number of lines in the chunks of the training examples.
+
 \subsection{Tool Implementation}
@@
 \end{figure*}
+
+\caro{To investigate which of the three techniques are feasible to
+facilitate configurable build log analysis, we conduct an empirical
+comparison on a large dataset of real world log files and excerpts.
+}
 
@@
 Overall, this study showed the need for a new
-\todo{not generic, but configurable}
-generation of generic and automated build log analysis techniques that
+\todo{not generic, but configurable}generation of generic and automated build log analysis techniques that
 need little effort to set up, both for practitioners as well as

### 2021-04-19 tse-paper/paper.tex
inccl. system log description feedback, remove snowballing term

@@
 When a build or one of its steps fails, developers typically scavenge
-the logs for information related to the source of the error.
-\todo{cite bart paper?}
-This
-manual activity is tedious and prone to
+the logs for information related to the source of the error
+~\citep{vassallo2019every}.
+This manual activity is tedious and prone to
 errors~\citep{santolucito2018statically}.
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth, clip]{img/lit_mapping_svg2.pdf}
+	\includegraphics[width=0.7\columnwidth, clip]{img/lit_mapping.pdf}
 	\caption{Literature selection (following Petersen et
@@
 
-When analyzing system log files, the first goal is generally to
-separate the constant and variable parts within a log
+Before system logs can be analyzed, the raw log data needs to be
+abstracted into a structured
+events list~\citep{el-masri2020a-systematic}.
+The first step of this log abstraction is to define or discover
+log message templates, e.g. by
+separating the constant and variable parts within a log
 message~\citep{nagappan2010abstracting,he2017towards}.
-Next, the log
-messages are clustered into log events, unifying messages with
-identical constant parts and varying parameters.
+In the second step of the log abstraction, the log
+messages are matched to the templates, unifying messages with
+identical constant parts and varying parameters under the same event.
 The output is an
@@
 This structured log can serve as
-input to various machine learning and data mining processes.
+input to log analysis approaches based on, e.g.,
+machine learning and data mining processes.
 Apart
@@
 
-With these 256 remaining works, we followed a backward snowball
-sampling for related work.
 If a work referenced a new work in the context

### 2021-04-19 tse-paper/paper.tex
simplify technique descriptions

@@
   regular expressions based on few user-given log excerpts.
-  We rely on the PROSE Framework \caro{link!} that is also responsible for auto-filling
+  We rely on the PROSE
+  Framework\footnote{https://microsoft.github.io/prose/},
+  which also provides the auto-filling for
   cells in Microsoft Excel.
@@
 
+\todo{Intro section? In this section we discuss the details of our
+prototypes that apply the three chosen techniques to build log
+analysis.}
+
 \subsection{Programming by Example (PBE)}
@@
 text extraction DSL \emph{FlashExtract}~\citep{le2014flashextract:}.
-% Both enable \emph{PROSE} to synthesize regular expression programs
-% consistent~\citep{mitchell1982generalization} with a set of in-
-% and output examples.
-% The usage of example enables the user to configure a chunk
-% retrieval without understanding the whole structure of
-% the build log.
-
-\subsubsection{Configuration}
-In- and output example pairs are the main driver of PBE;
-The \emph{input} is the full text of the build log file.
-The \emph{output} is
-a substring of the log file text, representing the
-substring that the synthesized program should retrieve when
-given the corresponding input file.
-One or multiple examples, the
-training set, \emph{configure} a specific chunk retrieval with PBE:
-they define the chunk of a build log that should be retrieved.
+
+To configure our prototype, the user supplies one or more build logs
+together with the excerpt of these logs they would like to be
+retrieved.
 The PROSE program synthesis then tries to construct a program
@@
 because the required regular expression
-is too complicated to be synthesized, PBE returns the
+is too complicated to be synthesized, our prototype returns the
 error message ``no program found.''
 
-\subsubsection{Chunk Retrieval Run}
-A run of PBE takes a build log file as input and executes the
-synthesized regular expression program on it.
-It then returns the substring
-of the build log matched by the program.
-If the program finds no match because the analyzed build log
+When our PBE prototype analyzes a build log, it tries to match
+the synthesized regular expression program.
+It then returns the matched substring.
+If there is no match, because the analyzed build log
 does not contain the structure that the training examples define,
@@
 technique that
-retrieves those lines from a build log which are most
-similar to the specified examples.
-
-\subsubsection{Configuration}
-To configure CTS we chose to use the same concept of examples as for
-PBE: lines of the targeted chunks from the training examples define
-the search query.
+retrieves those lines from a build log which have a similar
+vocabulary to the log excerpts the user provides as configuration.
+
 Using a Vector Space
 Model~\citep{schutze2008introduction} (VSM), an algebraic model for
-representing textual documents, we encode each line as a separate term
-vector.
+representing textual documents, we encode each line of the
+user-provided log excerpts as a separate term vector.
 The terms that make up the dictionary are simply all words
@@
 
-\subsubsection{Chunk Retrieval Run}
-To retrieve the desired information from a build log, we encode every
-line of the input build log in VSM.
+To analyze a build log, we encode every
+line of the build log in VSM.
 The algorithm calculates the cosine
@@
 
-\subsubsection{Configuration}
-A set of keywords configures the chunk retrieval with KWS\@.
+The user provides a list of search terms to configure KWS.
+To analyze a build log, our prototype searches for all
+exact occurrences of the search keywords.
+
 To better
-compare KWS with PBE and CTS, we also configure it through examples.
-From each example, we extract a list of keywords that appeared in the
+compare KWS with the other two techniques,
+we also configure it through a set of log excerpts.
+From each excerpts, we manually extract a list of keywords that
+appear in the
 training examples and that we expect to appear
@@
 list of the most commonly occurring keywords for the search with KWS.
-
-\subsubsection{Chunk Retrieval Run}
-For a retrieval run, we take an entire build log file as input and
-search for all exact occurrences of the search keywords.
 As keywords are
@@
 returned lines is largely determined by the training set),
-we configure RLR to return the average
-number of lines in the chunks of the training examples.
+we let RLR return the average
+number of lines in the log excerpts used as configuration.
 

### 2021-04-19 tse-paper/paper.tex
better motivation for study / metrics, use classification consistently

@@
 1.3.
-\todo{if defining the RQs went up in the last section, rephrase the rqs here too}
 
@@
 tools~\citep{kavaler2019tool}.
-Categorization is the more abstract representation, chunks
-contain more information and could be turned into a categorization.
+Classification is the more abstract representation, chunks
+contain more information and could be turned into a classification.
 
@@
 Seo et al.~\citep{seo2014programmers}, for example,
-categorized the types of compile errors encountered at
+classified the types of compile errors encountered at
 Google.
@@
 {Parser} &
-\citep{vassallo2018un-break} \citep{zhang2016android} \citep{seo2014programmers} \citep{hassan2019tackling} \citep{hassan2017automatic} \citep{chromy2007integration} \citep{mesbah2019deepdelta} \citep{wen2018blimp} \citep{kwon2018prioritizing} \citep{adams2007design} \citep{rahman2018impact} \citep{brandyberry2006continuous} \citep{tomassi2019bugswarm} \citep{ren2018automated} \citep{vassallo2019automated} \citep{cavalcanti2019impact} \citep{sippola2013qt} \citep{felipe2012towards} \citep{shi2018evaluating} \citep{urli2018design} \citep{selberg2012use}
+\citep{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
  &
@@
 {Regular expression} &
-\citep{beller2017oops} \citep{hassan2017change} \citep{macho2018automatically} \citep{vassallo2017a-tale} \citep{lou2019history} \citep{hassan2017automatic} \citep{rott2019empirische} \citep{zampetti2019study} \citep{zhao2018comparing} \citep{rausch2017empirical} \citep{ghaleb2019studying} \citep{zampetti2017open} \citep{zhang2019large} \citep{kavaler2019tool} \citep{morris2010experience}
+\citep{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
  &
@@
 text from the logs.} Chunks are the overarching concept to
-the almost equally much used categorization: one can deduce a
-categorization from chunks, but not vice versa.
-\todo{catedorization was called classification before}
+the almost equally much used classification: one can deduce a
+classification from chunks, but not vice versa.
 
@@
 Marked in blue in \Cref{lst:logexamples}
+\todo{chunks not introduced yet}
 are the chunks we target.
@@
 from \Cref{lst:chunk-example}.
-\Cref{lst:chunk-example-3} is very
+The chunk in \Cref{lst:chunk-example-3} is very
 different.
@@
 after the chunk.
+\caro{introduce sturctural categories here?}
 
@@
 \Cref{lst:chunk-example},
-CTS will rank the lines from an analyzed build log which are most
-similar to the chunks in the training examples.
+CTS will rank the lines from an analyzed build log whose vocabulary is
+most similar to the chunks in the training examples.
 It will then return the two lines ranked highest, as the chunks in
@@
 In this example,
-CTS will have difficulty extracting the lines from
+CTS, trained on \Cref{lst:chunk-example},
+will have difficulty extracting the lines from
 \Cref{lst:chunk-example-3} as there are no words that appear
@@
 
-Keywords that appear in or close to the chunk within
-the build log configure the technique KWS\@.
-For the examples from \Cref{lst:chunk-example} these could be
+To configure KWS, the user has to provide search terms.
+If log excerpts such as the ones from \Cref{lst:chunk-example}
+are targeted, possible search terms would be
 ``FAILURE,'' ``wrong,'' or ``failed.''
@@
 Our findings of techniques in the literature
-mapping (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
-particular) inspired the strategies that underlie them.
+mapping (\Cref{sec:litsurresults}) and \Cref{tab:litsur:techniques} in
+particular) inspired the strategies that underlie them and our central
+requirement of enabling a user to configure the technique to their use
+case with little effort.
 \Cref{tab:techniques} summarizes the techniques, which we describe here
@@
 
-\caro{To investigate which of the three techniques are feasible to
-facilitate configurable build log analysis, we conduct an empirical
-comparison on a large dataset of real world log files and excerpts.
-}
-
-In the literature mapping, we noted that previous work seemed to choose
-a log analysis technique arbitrarily and that is a lack of guidance on
-when to use which technique.
-% add (see \Cref{sec:lit-sur:discussion}) ?
-To address this, in this section, we conduct an empirical study
-comparing the three novel chunk retrieval techniques we presented in
-\Cref{sec:techniques}.
-
-In particular, we are interested in how many examples a technique
+% \caro{To investigate which of the three techniques are feasible to
+% facilitate configurable build log analysis, we conduct an empirical
+% comparison on a large dataset of real world log files and excerpts.
+% }
+
+% In the literature mapping, we noted that previous work seemed to choose
+% a log analysis technique arbitrarily and that is a lack of guidance on
+% when to use which technique.
+% % add (see \Cref{sec:lit-sur:discussion}) ?
+% To address this, in this section, we conduct an empirical study
+% comparing the three novel chunk retrieval techniques we presented in
+% \Cref{sec:techniques}.
+
+We conduct an empirical study to compare how well the three
+configurable chunk retrieval techniques can be applied to analyze
+build logs.
+With this evaluation we want to give a future user guidance on which
+technique to choose for their build log analysis use case.
+
+To understand the amount of configuration necessary, we investigate
+how many log excerpts a technique
 should be trained with (\textbf{RQ2.1}),
 how similar the structural representation of the targeted log chunks
-has to be (\textbf{RQ2.2}), and how reliable the quality of the
+has to be (\textbf{RQ2.2}).
+To determine whether the output of the build log analysis is suited
+to be analyzed automatically or by a human user, without the need to
+refer back to the full build log, we measure how
+reliable the quality of the
 produced retrievals is (\textbf{RQ2.3}).
@@
 
-In the following, we first introduce the data set we created for this
-study, and then describe the study design and its
-results.
-We answer these RQs separately for each technique.
+In the following, we introduce the data set we created for this
+study, describe the study design and our results.
+We discuss the answers to the RQs separately for each technique
+and compare them to give recommendations on which technique
+a future user should configure to analyze their build logs.
 
@@
 	desired lines were extracted,
+  \todo{motivate this distinction: partially means not suited for
+  automatic processing? unsuccessful for have to go back to log}
 	and if the retrieved lines contain none of the desired lines
@@
 It shows how many runs per technique were successful, partially
-successful or unsuccessful in retrieving the chunk defined in the
-test example.
+successful or unsuccessful in retrieving the complete
+chunk defined in the test example.
 CTS and KWS
@@
 Following from the results of the empirical study, in this section,
-we give recommendations for
+we discuss how accurate the three different techniques retrieve
+information from build logs and infer how their
+output can be used further.
+Further, we give recommendations for
 which types of log chunks and how many training examples
-each technique is suited, as well as
-how their output can be used further.
+each technique is suited.
 We summarize these recommendations in
@@
 We created the
-\emph{LogChunks} data set \citep{brandt2020logchunks} specifically for
+\emph{LogChunks} data set~\citep{brandt2020logchunks} specifically for
 the comparative
